### 2020-03-10 AlgebraicTopology2020/algtop1/algtop1.tex
Create archive, add algtop homework

% !TeX encoding = UTF-8
% !TeX spellcheck = en_US
% !TeX TXS-program:bibliography = biber -l zh__pinyin --output-safechars %

\documentclass[a4paper,10pt]{article}

\newcommand{\hwNumber}{1}

\input{../algtop_preamble.tex}
\input{../.modules/basics/biblatex.tex}

%%% ID: sensitive, do NOT publish!
%\InputIfFileExists{../id.tex}{}{}

\begin{document}
\maketitle
\pagestyle{headings}
\pagenumbering{arabic}
\thispagestyle{empty}

	\begin{enumerate}
	\item \textbf{Equivalence of categories is fully faithful}:

	$F\colon \mcal{C}\to\mcal{D}$ equivalence of categories, i.e.\ $\exists\ G\colon\mcal{D}\to\mcal{C}$, s.t.
	\begin{equation}
		G\circ F \simeq \idty_{\mcal{C}},\quad
		F\circ G \simeq \idty_{\mcal{D}}
	\end{equation}
	Here $\mquote{\simeq}$ means naturally isomorphic as functors, i.e., 
	\begin{equation}
		\exists\ \tau\colon
			G\circ F\Rightarrow\idty_{\mcal{C}},\quad
		\sigma\colon
			F\circ G\Rightarrow\idty_{\mcal{D}}%
		\,\colon\ \text{natural isomorphisms}
	\end{equation}

	By the definition of natural transformation, for $f\in\Hom_{\mcal{C}}(A,B)$, we have:
	\begin{center}
	\begin{tikzcd}[row sep=3em,column sep=4em]
	G\circ F(A)
		\arrow{r}{G\circ F(f)}
		\arrow[swap]{d}{\tau_A} & 
	G\circ F(B)
		\arrow{d}{\tau_B} \\
	A
		\arrow{r}{f} &
	B
	\end{tikzcd}
	\begin{equation}
		\tau_B
			\circ (G\circ F)(f)
			\circ \tau^{-1}_A
		= f,\quad
		\forall\ f\in\Hom_{\mcal{C}}(A,B)
	\end{equation}
	\end{center}
	Here $\tau_{A,B}$ are isomorphisms, which means that $G\circ F$ must be a bijection between hom-sets, which further implies that $F$ is injective and $G$ is surjective. 
%	(onto $
%		\Hom_{\mcal{C}}(G\circ F(A),G\circ F(B))
%	$)
	Switch the roles of $F,G$, we find that $G$ is injective and $F$ is surjective. Therefore, $F,G$ are both fully faithful. \qedfull

	\item \textbf{Forgetful functors to \Cat{Set} are often representable}:

	For $F\colon \Cat{Group}\to\Cat{Set}$, consider the free group generated by a single element $\mbb{Z}$. We have:
	\begin{equation}
	\begin{aligned}
		\Hom(\mbb{Z},-)\colon\
			\Cat{Group}\ &\longto\ \Cat{Set} \\
			G\ &\longmapsto\ \Hom(\mbb{Z},G)
	\end{aligned}
	\end{equation}
	This is a covariant functor representable by $\mbb{Z}$.

	On the other hand, $\Hom(\mbb{Z},G)$ consists of group homomorphisms:
	\begin{equation}
		\Hom(\mbb{Z},G)
		= \Bqty{
			\begin{aligned}
				\mbb{Z} &\to G \\[-1.5ex]
				1 &\mapsto g
			\end{aligned}
			\,\bigg|\,
			g\in G
		}
	\end{equation}
	More specifically, to fix any $\mbb{Z}\to G$, we need only assign its generator\footnote{
		Note that $0\in\mbb{Z}$ is the group identity of addiction group $\mbb{Z}$, not $1\in\mbb{Z}$. 
	} $1\mapsto g$. Image of any other $\mbb{Z}$ element is generated automatically from the group law, without further specifications. This means that the hom-set is in one-to-one correspondence with $G$ elements (as a set). Therefore, $F\cong\Hom_{\Cat{Group}}(\mbb{Z},-)$, i.e.\ forgetful $F\colon\Cat{Group}\to\Cat{Set}$ is representable by $\mbb{Z}$. \qed
\pagebreak[3]

	Similarly, for $F\colon \Cat{Ring}\to\Cat{Set}$, the free object generated by some generic element $x$ is $\mbb{Z}[x]$, the polynomial ring in one variable; we have:
	\begin{equation}
		F\cong\Hom_{\Cat{Ring}}(\mbb{Z}[x],-),\quad
		\Hom_{\Cat{Ring}}(\mbb{Z}[x],R)
		= \Bqty{
			\begin{aligned}
				\mbb{Z}[x] &\to R \\[-1.5ex]
				x &\mapsto r
			\end{aligned}
			\,\bigg|\,
			r\in R
		}
	\end{equation}
	\textit{Lesson}: Forgetful $\Cat{Cat} \to \Cat{Set}$ are often representable by the free object in \Cat{Cat}. \qedfull

	\item \textbf{Properties of contractible space}:

	\begin{enumerate}
	\item $X$ contractible: $\idty_X \simeq f_0\colon X\to X$ some constant map, $f_0(X) = \{x_0\}$. We can restrict the codomain of $f_0$ so that $f_0\colon X\to\{x_0\}$, in this way we have:
	\begin{subequations}
	\renewcommand{\theequation}{\theparentequation.\arabic{equation}}
	\begin{align}
		X\xrightarrow{f_0} \{x_0\}
			\hookrightarrow X
		&\simeq \idty_X,
		\label{eq:homotopy_on_X}\\
		\{x_0\}\hookrightarrow X
			\xrightarrow{f_0} \{x_0\}
		&\simeq \idty_{\{x_0\}},
	\end{align}
	\label{eq:homotopic_equiv}
	\end{subequations}
	This means that $f_0\colon X\to\{x_0\}$ isomorphic in $\Cat{hTop} = \Cat{Top}/\simeq$, which is precisely the definition of homotopic equivalence $X\simeq\{x_0\}$. ($\Rightarrow$)

	On the other hand ($\Leftarrow$), if $X\simeq\{x_0\}$, there exists some $f_0\colon X\to\{x_0\}$ that fulfills \eqref{eq:homotopic_equiv}. We can then extend the codomain s.t.\ $f_0\colon X\to X$, in this way \eqref{eq:homotopy_on_X} reads $f_0 \simeq \idty_X$, i.e.\ $X$ is contractible. 
	Therefore, $X$ contractible iff.\ homotopic equivalent to a single point. \qedfull[(a)]

	\item $\forall\ X$: Topological space, we can define its \textit{cone} as\footnote{
		See \wikiref{https://en.wikipedia.org/wiki/Cone\_(topology)}{Cone (topology)}. 
	}:
	\begin{equation}
		CX = (X\times I) / (X\times\{0\}),\quad
		I = [0,1]
	\end{equation}
	i.e.\ gluing together one end of the cylinder $X\times I$. Naturally $X\subset CX$ as a subspace; now we show that $CX$ is contractible. Using (a), we need only show that $\idty_{CX}\simeq f_0$ some constant map.

	In fact, any point in $CX$ can be uniquely labeled by $[x,h]\in X\times I$, with the exception of the vertex $v \sim [x,0]\sim [x',0],\ \forall\ x,x'\in X$. We can then construct a homotopy $F$ by shrinking the cone towards the vertex $v$:
	\begin{equation}
	\begin{gathered}
		F\colon CX\times I\to CX,\quad
		F\pqty\big{[x,h],t} = [x,h\cdot t],\\
		F|_{CX\times 0} = v = \mrm{const},\quad
		F|_{CX\times 1} = \idty_X
	\end{gathered}
	\end{equation}
	This confirms that $\idty_{CX}\simeq v$: constant map. By (a), $CX$ is contractible. \qedfull[(b)]
\pagebreak[3]

	\item For $Y\simeq \{y_0\}$ contractible, given any $g\colon X\to Y$, we can deform the image $g(X)\subset Y$ to a single point, hence $g\simeq y_0$: constant map. 
	More precisely, we have:
	\begin{equation}
		\exists\ G \colon X\times I\to Y,\quad
		\text{s.t.}\quad
		G|_{X\times 0} = y_0 = \mrm{const},\quad
		G|_{X\times 1} = g
	\end{equation}
	Such $G$ can be explicitly constructed using $\idty_Y\simeq y_0$:
	\begin{gather}
		F \colon Y\times I\to Y,\quad
		F|_{Y\times 0} = y_0 = \mrm{const},\quad
		F|_{Y\times 1} = \idty_Y,
		\label{eq:contractible_explicit}\\[1ex]
		G(x,t) = F\pqty\big{g(x),t}
%		\left\lbrace
%		\begin{aligned}
%			\,& F\pqty\big{g(x),1-2t},
%			&& 0\le t\le\tfrac{1}{2}\\
%			& F\pqty\big{g'(x),2t-1},
%			&& \tfrac{1}{2}\le t\le 1\\
%		\end{aligned}
%		\right.
	\end{gather}
\pagebreak[3]

	In summary, we have proven that $g\simeq y_0,\ \forall\ g\in\Hom_{\Cat{Top}}(X,Y)$. By definition, this means that $\Hom_{\Cat{hTop}}(X,Y) = \Hom_{\Cat{Top}}(X,Y)\big/_{\simeq} = \Bqty\big{[y_0]}$ a single point. \qedfull[(c)]

	\item For $X\simeq \{x_0\}$ contractible, similar to \eqref{eq:contractible_explicit}, we have homotopy $F\colon X\times I \to X$. Given any $f\colon X\to Y$, the composition $f\circ F\colon X\times I \to Y$ yields $f\simeq f(x_0)$: constant map.

	Furthermore, for $Y$: path connected, there is a path $\gamma\colon I\to Y$ connecting $f(x_0)$ and some $y_0\in Y$, therefore $f(x_0) \simeq y_0\colon X\to Y$ constant maps. More precisely, we have:
	\begin{equation}
		\gamma\colon I\to Y,\quad
			\gamma(0) = y_0,\quad
			\gamma(1) = f(x_0),\\
		G\colon X\times I\to Y,\quad
			G(x,t) = \gamma(t)
	\end{equation}
	Which gives $f(x_0) \simeq y_0,\ \forall\,f$, independent of the choice of $f$. This means that $f\simeq f(x_0) \simeq y_0$: constant map, therefore $\Hom_{\Cat{hTop}}(X,Y) = \Bqty\big{[y_0]}$ a single point. \qedfull[(d)]

	\end{enumerate}

	\item \textbf{Example of homotopic inequivalence}\footnote{
		This proof is produced thanks to helpful insights from \textit{谷夏} and \textit{於子雄}. 
	}:
	\begin{equation}
	\begin{gathered}
		X = \{0\} \cup \Bqty{
			\frac{1}{n} \,\bigg|\, n\in\mbb{Z}_+
		},\quad
		Y = \{0\} \cup \mbb{Z}_+\\[.5ex]
		X,Y\subset\mbb{R}\colon
		\text{subspace topology}
	\end{gathered}
	\end{equation}
	Assume $X\simeq Y$, then similar to \eqref{eq:homotopic_equiv}, we have $
		Y\xrightarrow{g}X
		\xrightarrow{f}Y
		\simeq\idty_Y
	$. However, note that $Y$ has discrete topology, in such case any map $f\circ g$ homotopic to $\idty_Y$ must be $\idty_Y$ itself: $f\circ g = \idty_Y$.

	More specifically, consider:
	\begin{equation}
		F \colon Y\times I\to Y,\quad
		F|_{Y\times 0} = f\circ g,\quad
		F|_{Y\times 1} = \idty_Y
	\end{equation}
	Any point $n\in Y$ is both open and closed, therefore its pre-image $F^{-1}(n)\subset Y\times I$ is also both open and closed, and by $F|_{Y\times 1} = \idty_Y$ we know that $F(y,1) = y,\ (y,1)\in F^{-1}(y)$, therefore the only possibility is that $F(\{y\}\times I) = y$, i.e.\ $f\circ g=\idty_Y$, which implies that $g$ is injective and $f$ is surjective.

	However, $f\colon X\to Y$ cannot be surjective due to the complication around $0\in X$. Consider $f^{-1}\pqty\big{f(0)}\ni 0$, since $f(0)\in Y$ both open and closed, $f^{-1}\pqty\big{f(0)}\subset X$ must also be both open and closed. But any open set $U\subset X$ is induced via subspace topology $X\subset\mbb{R}$; for $0\in U\subset X\subset\mbb{R}$, $U$ must contain $\infty$-many elements: 
	\begin{equation}
		\Bqty{
			\frac{1}{n} \,\bigg|\, n\ge N_0
		}
		\subset U
		\subset f^{-1}\pqty\big{f(0)},\quad
		\text{for some $N_0$, for any $U\ni x$}
	\end{equation}
	Hence $f(X) = f(0)\cup f(
		\Bqty{
			\frac{1}{n} \,|\, n< N_0
		}
	),\ f(X)\subset Y$ a finite set, i.e. $f\colon X\to Y$ is never surjective. Therefore, $X\not\simeq Y$ by contradiction. \qedfull
\pagebreak

	\item \textbf{Fundamental group of topological group is abelian}\footnote{%
		This proof is produced with the help of \https{math.stackexchange.com/q/727999}. 
	}:

	From a categorical point of view, the fundamental group $\pi_1(G)$ of a topological group $G$ can be seen as a functor:
	\begin{equation}
		G\in\Cat{TopGroup}
		\ \xhookrightarrow{\quad}\ \Cat{Top}
		\ \xrightarrow{\ \pi_1\,}\ \Cat{Group}
		\ni \pi_1(G)
	\end{equation}
%	
	$\Cat{TopGroup}\subset\Cat{Top}$ is a subcategory with additional group structure, i.e.\ $(G,\cdot)\in\Cat{TopGroup}$ is a \textit{group object}\footnote{
		See \wikiref{https://en.wikipedia.org/wiki/Group\_object}{Group object}. 
	} in \Cat{Top}, with $\mquote{\cdot}$ denoting its product operation $(\cdot)\colon G\times G\to G$. Correspondingly, $\pi_1(\Cat{TopGroup})$ should be \textit{group objects of \Cat{Group}}, which have an \textit{additional} group structure $(\star) = \pi_1(\cdot)$, along with the usual group product $\mquote{*}$ in \Cat{Group}.

	In total, we have three different group structures (represented by their product operation):
	\begin{align}
		(\cdot)\colon\ %
			&G\times G\to G,\\
		(*)\colon\ %
			&\pi_1(G)\times\pi_1(G)\to\pi_1(G),\\
		(\star) = \pi_1(\cdot)\colon\ %
			&\pi_1(G)\times\pi_1(G)\to\pi_1(G),
	\end{align}
	Note that $\pi_1(G) = \mop{Aut}_{\Pi_1(G)}\idty_G$, i.e.\ loop classes $[\gamma]$ in $G$; $(*)$ is defined as joining two loops, while $(\star) = \pi_1(\cdot)$ is defined as the translation of loop classes by pointwise group product $(\cdot)$, 
	\begin{equation}
		[\gamma_1]\star[\gamma_2]
		= [\gamma_1\cdot\gamma_2]
	\end{equation}

	With the above definitions, we observe that:
	\begin{equation}
		([\gamma_1]\star[\gamma_2])
		* ([\eta_1]\star[\eta_2])
		= ([\gamma_1]*[\eta_1])
		\star ([\gamma_2]*[\eta_2])
		\label{eq:distributive_law}
	\end{equation}
	By definition, they are both equal to $
		[(\gamma_1\cdot\gamma_2)*(\eta_1\cdot\eta_2)]
	$. What's surprising is that by using only the group axioms and ``distributive law'' \eqref{eq:distributive_law}, we can show that $(\star)$ and $(*)$ must always coincide: $(\star) = (*)$, and they have to be in fact, commutative. This is the \textit{Eckmann–Hilton argument}\footnote{
		See \wikiref{https://en.wikipedia.org/wiki/Eckmann\%E2\%80\%93Hilton\_argument}{Eckmann–Hilton argument}. 
	}.

	Proof of this argument is straight-forward; first, observe that the units of the two operations coincide:
	\begin{equation}
		1_{\star}
		= 1_{\star}\star 1_{\star}
		= (1_{*} * 1_{\star})
			\star (1_{\star} * 1_{*})
		\xlongequal{\eqref{eq:distributive_law}}
			(1_{*}\star 1_{\star})
			* (1_{\star}\star 1_{*})
		= 1_{*} * 1_{*}
		= 1_{*}
	\end{equation}
	Further manipulation using \eqref{eq:distributive_law} confirms that the two operations coincide and are commutative:
	\begin{align}
	\begin{aligned}
		[\gamma] * [\eta]
		&= (1\star [\gamma]) * ([\eta]\star 1)
		\xlongequal{\eqref{eq:distributive_law}}
			(1 * [\eta])\star ([\gamma] * 1) \\
		&= [\eta]\star [\gamma] \\
		&= ([\eta] * 1)\star (1 * [\gamma])
		\xlongequal{\eqref{eq:distributive_law}}
			([\eta]\star 1) * (1\star [\gamma]) \\
		&= [\eta] * [\gamma]
	\end{aligned}
	\end{align}

	In summary, we find that the group objects in $\Cat{Group}$ are indeed abelian groups, which means that $\pi_1(G)$ for $G\in\Cat{TopGroup}$ must be abelian. \qedfull

	\end{enumerate}

\printbibliography[%
	title = {参考文献} %
	,heading = bibintoc
]
\end{document}

### 2020-03-10 Strings2020/strings1/strings1.tex
Add strings homework

% !TeX encoding = UTF-8
% !TeX spellcheck = en_US
% !TeX TXS-program:bibliography = biber -l zh__pinyin --output-safechars %

\documentclass[a4paper,10pt]{article}

\newcommand{\hwNumber}{1}

\input{../strings_preamble.tex}
\input{../.modules/basics/biblatex.tex}

%%% ID: sensitive, do NOT publish!
%\InputIfFileExists{../id.tex}{}{}

\newcommand{\oppower}[2]{\mop{{#1}^{#2}}\!}
\newcommand{\sqsinh}{\oppower{\sinh}{2}}
\newcommand{\sqcosh}{\oppower{\cosh}{2}}

\newcommand{\Vir}{\mathbf{V}\mfrak{ir}}

\begin{document}
\maketitle
\pagestyle{headings}
\pagenumbering{arabic}
\thispagestyle{empty}

%{
%	\noindent\itshape%
%	本文约定：度规$\eta\sim\pqty{-,+,+,+}$, 指标$\mu,\nu,\dots = 0,1,2,3,\ i,j,\dots = 1,2,3$.
%}
	\begin{enumerate}
	\item \textbf{Read \textit{Polchinski} Sections 1.3 and 1.4}:

	Read, \textit{mostly} understood. \qed

	\item \textbf{Spinning Closed String in AdS Space}:

	For a classical spinning string, we have Nambu--Goto action:
	\begin{equation}
		S_{NG}
		= -T \int \dd{\tau} \dd{\sigma}
			\sqrt{-\det \gamma_{ab}},\quad
		\gamma_{ab} = G_{\mu\nu}
			\pdd{a}X^\mu \pdd{b}X^\nu
	\end{equation}
	Here $G_{\mu\nu}$ is the spacetime metric. $\gamma_{ab}$ can be treated as the induced metric on the worldsheet.

	In AdS space we have:
	\begin{equation}
		ds^2
		= R^2\pqty{
			- \sqcosh\rho \dd{t}^2
			+ \dd{\rho}^2
			+ \sqsinh\rho \dd{\Omega}^2
		}
	\end{equation}
	Where $\dd{\Omega}^2$ is the metric of a unit $(d-2)$--sphere $S^{d-2}$. For convenience let's define unit $S^{d-2}$ metric $G^1_{ij}$, and raise or lower the $i,j,\cdots$ indices using $G^1_{ij}$ instead of $G_{ij}$, i.e.,
	\begin{equation}
		G^1_{ij} = G_{ij} /\,\pqty{
			R^2 \sqsinh\rho
		},\quad
		i,j = 2,\cdots,d-1
	\end{equation}

	Furthermore, we consider the special case that the closed string is \textit{folded}, like a rubber band stretched along a line; in this case we can choose the worldsheet parameter $(\tau,\sigma) = (t,\rho)$ while $\Omega = \Omega(t,\rho) = \Omega(\tau,\sigma)$, which leads to the following decomposition:
	\begin{align}
		\pdd{a} X^\mu
		&= \delta^\mu_a + \delta^\mu_i\,
			\pdd{a}\Omega^i,\quad
			a = 0,1,\quad
			i = 2,\cdots,d-1,\\[.5ex]
		\gamma_{ab}
		&= G_{\mu\nu}\,
			\pdd{a}X^\mu \pdd{b}X^\nu
		\notag\\
		&= G_{ab} + G_{ij}\,
			\pdd{a}\Omega^i\,\pdd{b}\Omega^j
		\notag\\
		&= G_{ab} + R^2\sqsinh\rho\,G^1_{ij}\,
			\pdd{a}\Omega^i\,\pdd{b}\Omega^j
		\notag\\
		&= R^2\Bqty{\mat{
			-\sqcosh\rho & \\
			& 1 \\
		} + \sqsinh\rho\,\mat{
			(\pdd{a}\Omega)^2 &
			\pdd{a}\Omega\cdot\pdd{b}\Omega \\
			\pdd{b}\Omega\cdot\pdd{a}\Omega &
			(\pdd{b}\Omega)^2 \\
		}}
%		\notag\\
%		&= R^2\,\sqsinh\rho\,\Bqty{\mat{
%			-\oppower{\coth}{2}\rho & \\
%			& \oppower{\csch}{2}\rho \\
%		} + \,\mat{
%			(\pdd{a}\Omega)^2 &
%			\pdd{a}\Omega\cdot\pdd{b}\Omega \\
%			\pdd{b}\Omega\cdot\pdd{a}\Omega &
%			(\pdd{b}\Omega)^2 \\
%		}}
	\end{align}
	Here $
		\pdd{a}\Omega\cdot\pdd{b}\Omega
		\equiv \pdd{a}\Omega^i\,\pdd{b}\Omega_i
		\equiv G^1_{ij}\,
			\pdd{a}\Omega^i\,\pdd{b}\Omega^j
	$, and we have:
	\begin{equation}
	\begin{aligned}
		\det \gamma_{ab}
		&= (R^2)^2\,\Big\{
			\oppower{\sinh}{4}\rho\,
			\det\,(\pdd{a}\Omega^i\pdd{b}\Omega_i)
		\\
		&\qquad\qquad\qquad
			+ \oppower{\sinh}{2}\rho\,\pqty{
				(\pdd{a}\Omega)^2
				- (\pdd{b}\Omega)^2
				\oppower{\cosh}{2}\rho
			}
		\\
		&\qquad\qquad\qquad
			- \oppower{\cosh}{2}\rho\,
		\Big\},\\[.5ex]
		\sqrt{-\det \gamma_{ab}}
		&= R^2\,\Big\{
			\oppower{\cosh}{2}\rho
			- \oppower{\sinh}{2}\rho\,\pqty{
				(\pdd{a}\Omega)^2
				- (\pdd{b}\Omega)^2
				\oppower{\cosh}{2}\rho
			}
		\\[-.5ex]
		&\qquad\qquad\quad
			- \oppower{\sinh}{4}\rho\,
			\det\,(\pdd{a}\Omega^i\pdd{b}\Omega_i)
		\Big\}^{\!1/2}
	\end{aligned}
	\end{equation}

	Mark the end points of the string with $\rho = r(t)$, then the total length of such closed folded string is $\ell = 4r$. We then have:
	\begin{equation}
		S = -4TR^2 \int\dd{t} \int_0^r \dd{\rho}
		\sqrt{
			\oppower{\cosh}{2}\rho
			- \oppower{\sinh}{2}\rho\,\pqty{
				(\pdd{a}\Omega)^2
				- (\pdd{b}\Omega)^2
				\oppower{\cosh}{2}\rho
			}
			- \oppower{\sinh}{4}\rho\,
			\det\,(\pdd{a}\Omega^i\pdd{b}\Omega_i)
		}
	\end{equation}
\pagebreak[3]

%	Variation of metric determinant $
%		\gamma \equiv \det\gamma_{ab}
%	$ is give by the following formula:
%	\begin{equation}
%		\var{\sqrt{-\gamma}}
%		= \frac{1}{2\sqrt{-\gamma}}
%			\var{(-\gamma)}
%		= \frac{1}{2\sqrt{-\gamma}}\,
%			(-\gamma)
%			\var{\ln\gamma}
%		= \frac{1}{2} \sqrt{-\gamma}\,
%			\gamma^{ab} \var{\gamma_{ab}}
%	\end{equation}

	Further simplification comes from the fact that, due to rotational symmetry, the string's motion can be restricted in a plane where its position is characterized by some angle $\theta = \Omega^{i_0}\in \{\Omega^i\}_i$. In this case other angle parameters $\Omega^i|_{i\ne i_0} = 0$, and the action is further reduced to:
	\begin{gather}
		S = -4TR^2 \int\dd{t} \int_0^r \dd{\rho}
			\sqrt{
				\oppower{\cosh}{2}\rho
				- \oppower{\sinh}{2}\rho\,\pqty{
					(\pdd{a}\theta)^2
					- (\pdd{b}\theta)^2
					\oppower{\cosh}{2}\rho
				}
			}
		= \int\dd{t} \int_0^r \dd{\rho} \mcal{L},\\
		\mcal{L} = -4TR^2
			\sqrt{
				\oppower{\cosh}{2}\rho
				- \omega^2\oppower{\sinh}{2}\rho
			},\quad
			\omega = \pdd{t}\theta,\,
			\pdd{\rho}\theta = 0
	\end{gather}
	We consider the special solution $\theta = \omega t$, while in general the endpoint $r = r(t)$ could be dynamical; variation of the action w.r.t.\ $r(t)$ gives\footnote{
		The above reasoning is confirmed in e.g.\ \arxiv{hep-th/0204051}.
	}:
	\begin{gather}
		0 = \var{S} = -4TR^2 \int\dd{t}
			\int\limits_r^{r+\var{r}} \dd{\rho}
			\sqrt{
				\oppower{\cosh}{2}\rho
				- \omega^2\oppower{\sinh}{2}\rho
			}
		= -4TR^2 \int\dd{t}
			\sqrt{
				\oppower{\cosh}{2}r
				- \omega^2\oppower{\sinh}{2}r
			} \var{r},\\
		\omega^2 = \frac{\sqcosh r}{\sqsinh r}
		= \oppower{\coth}{2} r
		\label{eq:string_endpt_constraint}
	\end{gather}

	Note that if $\omega$ is constant, then $r$ must be fixed by \eqref{eq:string_endpt_constraint}. 
	Taking $\theta$ as the only dynamical variable, it is then straight-forward to write the energy $E$ and angular momentum $J$ for such folded closed string:
	\begin{gather}
		\omega = \dot{\theta},\quad
		\Pi = \pdv{\mcal{L}}{\omega}
		= 4TR^2\,\frac{\omega\sqsinh\rho}{
			\sqrt{
				\oppower{\cosh}{2}\rho
				- \omega^2\oppower{\sinh}{2}\rho
			}
		},\\
		J = \int_0^r \dd{\rho} \Pi
		= 4TR^2 \int_0^r \dd{\rho}
		\frac{\omega\sqsinh\rho}{
			\sqrt{
				\oppower{\cosh}{2}\rho
				- \omega^2\oppower{\sinh}{2}\rho
			}
		},\\
		E = \int_0^r \dd{\rho} \pqty{
			\Pi\omega - \mcal{L}
		}
		= 4TR^2 \int_0^r \dd{\rho}
		\frac{\sqcosh\rho}{
			\sqrt{
				\oppower{\cosh}{2}\rho
				- \omega^2\oppower{\sinh}{2}\rho
			}
		},
	\end{gather}

	In the large string limit, $r\to\infty,\ \omega = \coth r\to 1$. Expand in terms of $\epsilon = \omega - 1 > 0$, we find that $
		r = \frac{1}{2} \ln\pqty{
			1 + \frac{2}{\epsilon}
		}
		\sim \frac{1}{2} \ln\frac{2}{\epsilon}
	$, or alternatively, $e^{2r}\cdot\epsilon\sim 2$. With some help from Mathematica\texttrademark, we get:
	\begin{equation}
	\begin{aligned}
		E - J
		&= 4TR^2 \int_0^r \dd{\rho}
		\frac{\sqcosh\rho - \omega\sqsinh\rho}{
			\sqrt{
				\oppower{\cosh}{2}\rho
				- \omega^2\oppower{\sinh}{2}\rho
			}
		}
%		\\[.5ex]
%		&
		= 4TR^2 \int_0^r \dd{\rho} \pqty\Big{
			1 + \frac{\epsilon^2}{8}\sinh^2(2\rho)
			+ \order{\epsilon^3}
		} \\[1ex]
		&= 4TR^2 \pqty{
			r \pqty\Big{
				1 - \frac{\epsilon^2}{16}
				+ \order{\epsilon^3}
			} + \order{1}
		}
%		\\[.5ex]
%		&
		= \pqty{2TR^2 \ln\frac{2}{\epsilon}}
		\pqty\Big{
			1 - \frac{\epsilon^2}{16}
			+ \order{\epsilon^3}
		} \\[1ex]
		&\sim 2TR^2
			\pqty{\ln\frac{2}{\epsilon}}
	\end{aligned}
	\end{equation}
	Similarly, $
		J \sim 4TR^2 \mathlarger{\int_0^r}
			\dd{\rho} \sqsinh \rho
		\sim TR^2 \pqty{\frac{2}{\epsilon}}
	$, this gives:
	\begin{equation}
		E - J
		\sim 2TR^2 \ln \frac{J}{TR^2}
	\end{equation}
	\qedfull
\pagebreak[4]

	\item \textbf{Special Conformal Transformations:}
	\begin{equation}
		x^\mu
		\xmapsto{\ K(a)\ }
		\tilde{x}^\mu
		= \frac{x^\mu + x^2 a^\mu}{
			1 + 2a\cdot x + a^2 x^2
		}
	\end{equation}

	\begin{enumerate}
	\item Under special conformal transformation $K(a)$, metric $\delta_{\mu\nu}\mapsto g_{\mu\nu}$ while:
	\begin{equation}
		g_{\alpha\beta}
			\dd{\tilde{x}^\alpha}
			\dd{\tilde{x}^\beta}
		= \delta_{\mu\nu}
			\dd{x^\mu}
			\dd{x^\nu},\quad
		g_{\alpha\beta}
		= \delta_{\mu\nu}
			\pdv{x^\mu}{\tilde{x}^\alpha}
			\pdv{x^\nu}{\tilde{x}^\beta}
		\label{eq:metric_transform}
	\end{equation}
	To calculate this we have to know the inverse transformation $x = K^{-1}(a)\,\tilde{x}$. First, notice the following decomposition\footnote{
		See \textit{Di Francesco et al}, and also \https{github.com/davidsd/ph229}. 
	} of $K(a)$:
	\begin{equation}
		\tilde{x}^\mu
		= \frac{\frac{x^\mu}{x^2} + a^\mu}{
			\frac{1}{x^2}
			+ \frac{2a\cdot x}{x^2} + a^2
		}
		= \frac{\frac{x^\mu}{x^2} + a^\mu}{
			\abs{\frac{x^\mu}{x^2} + a^\mu}^2
		},\\[1ex]
		\text{i.e.}\quad
		K(a)\colon\ %
			x^\mu
			\ \xmapsto{\ I\ }\ %
			\frac{x^\mu}{x^2}
			\ \xmapsto{\ T(a)\ }\ %
			y^\mu = \frac{x^\mu}{x^2} + a^\mu
			\ \xmapsto{\ I\ }\ %
			\tilde{x}^\mu
			= \frac{y^\mu}{y^2},
		\label{eq:special_conformal_decomp} \\[.5ex]
		\text{i.e.}\quad
		\frac{\tilde{x}^\mu}{\tilde{x}^2}
			= \flatfrac{
				\frac{y^\mu}{y^2}
			}{
				\frac{1}{y^2}
			}
			= y^\mu = \frac{x^\mu}{x^2} + a^\mu
		\label{eq:special_conformal_simplified}
	\end{equation}

	From \eqref{eq:special_conformal_simplified}, we see that the transformation parameter $a^\mu$ composes linearly: $K(b)\,K(a) = K(a+b)$, therefore $K^{-1}(a) = K(-a)$, and we have:
	\begin{equation}
		x^\mu = K(-a)\,\tilde{x}^\mu
		= \frac{\tilde{x}^\mu - \tilde{x}^2 a^\mu}{
			1 - 2a\cdot \tilde{x} + a^2 \tilde{x}^2
		}
		= \frac{\tilde{y}^\mu}{y^2},\\[1.5ex]
	\begin{aligned}
		\pdv{x^\mu}{\tilde{x}^\alpha}
		&= \pdv{x^\mu}{\tilde{y}^\sigma}
			\pdv{\tilde{y}^\sigma}{\tilde{x}^\alpha}
		= \pqty{
			\pdv{\tilde{y}^\sigma}
			\frac{\tilde{y}^\mu}{\tilde{y}^2}
		} \pdv{\tilde{x}^\alpha} \pqty{
			\frac{\tilde{x}^\sigma}{\tilde{x}^2}
			- a^\sigma\!
		}
		= \pqty{
			\pdv{\tilde{y}^\sigma}
			\frac{\tilde{y}^\mu}{\tilde{y}^2}
		} \pqty{
			\pdv{\tilde{x}^\alpha}
			\frac{\tilde{x}^\sigma}{\tilde{x}^2}
		} \\[1ex]
		&= \pqty{
			\tilde{y}^2\delta^\mu_\sigma
			- 2\tilde{y}^\mu \tilde{y}_\sigma
		} \pqty{
			\tilde{x}^2\delta^\sigma_\alpha
			- 2\tilde{x}^\sigma \tilde{x}_\alpha
		} \Big/ \pqty{\tilde{y}^4 \tilde{x}^4},
	\end{aligned}\\[1ex]
	\begin{aligned}
		g_{\alpha\beta}
		&\xlongequal{\eqref{eq:metric_transform}}
		\delta_{\mu\nu} \pqty{
			\tilde{y}^2\delta^\mu_\sigma
			- 2\tilde{y}^\mu \tilde{y}_\sigma
		} \pqty{
			\tilde{x}^2\delta^\sigma_\alpha
			- 2\tilde{x}^\sigma \tilde{x}_\alpha
		} \pqty{
			\tilde{y}^2\delta^\nu_\rho
			- 2\tilde{y}^\nu \tilde{y}_\rho
		} \pqty\big{
			\tilde{x}^2\delta^\rho_\beta
			- 2\tilde{x}^\rho \tilde{x}_\beta
		} \Big/ \pqty{\tilde{y}^8 \tilde{x}^8}\\
		&\xlongequal{\sum_{\mu,\nu}}
		\tilde{y}^{-4} \delta_{\sigma\rho} \pqty{
			\tilde{x}^2\delta^\sigma_\alpha
			- 2\tilde{x}^\sigma \tilde{x}_\alpha
		} \pqty\big{
			\tilde{x}^2\delta^\rho_\beta
			- 2\tilde{x}^\rho \tilde{x}_\beta
		} \Big/ \tilde{x}^8 \\
		&\xlongequal{\sum_{\sigma,\rho}}
			\tilde{y}^{-4} \tilde{x}^{-4}
			\delta_{\alpha\beta}
	\end{aligned}
	\end{equation}
	We see that $g_{\alpha\beta} = f(x)\,\delta_{\alpha\beta}$, with coefficient:
	\begin{equation}
		f(x) = \tilde{y}^{-4} \tilde{x}^{-4}
		\xlongequal{%
			\eqref{eq:special_conformal_decomp}%
		} \frac{x^4}{\tilde{x}^4}
		\xlongequal{%
			\eqref{eq:special_conformal_simplified}%
		} \pqty{
			1 + 2a\cdot x + a^2 x^2
		}^2
	\end{equation}
	\qed[(a)]
	\vspace*{-1\baselineskip}

%	Note that the transformation depends smoothly on parameter $a$, therefore we can consider infinitesimal transformation generator:
%	\begin{equation}
%		k_\nu
%		= k\id{^\mu_\nu}\pdd{\mu}
%		= \pdv{\tilde{x}^\mu}{a^\nu}
%			\bigg|_{a=0} \!\pdd{\mu}
%		= \pqty{x^2\delta^\mu_\nu
%			- 2x^\mu x_\nu}\pdd{\mu}
%	\end{equation}

	\item In 2D with $z = x^1 + ix^2,\ x^\mu\sim (z,\bar{z})$, we see from \eqref{eq:special_conformal_simplified} that:
	\begin{equation}
		\frac{x^\mu}{x^2}
		\sim \frac{z}{\abs{z}^2}
		= \frac{1}{\bar{z}}
		\ \longmapsto\ %
		\frac{1}{\bar{z}} + a,\quad
		\text{i.e.}\quad
		z\ \longmapsto\ 
		w = \frac{1}{\frac{1}{z} + \bar{a}}
		= \frac{z}{1 + z\bar{a}}
	\end{equation}
	Expand in the $\bar{a}\to 0$ limit, we find that $
		w = z\,\pqty{
			1 - z\bar{a} - \cdots
		} \sim z - z^2 \bar{a}
	$, i.e.\ it is generated by:
	\begin{equation}
		K_{\bar{z}}
		= -z^2 \pdd{z}
		= -z^2 \pd,\quad
		\pd \equiv \pdd{z}
	\end{equation}
\pagebreak[3]

	Note that when considering non-holomorphic functions, we have to consider $(z,\bar{z})$ as \textit{two} independent variables; hence the anti-holomorphic transformation $
		\bar{z}\mapsto\bar{w}
		= \frac{\bar{z}}{1 + \bar{z} a}
		\sim \bar{z} - \bar{z}^2 a
	$ provides another degree of freedom, namely:
	\begin{gather}
		K_\mu\ \sim\ \pqty{
			K_{\bar{z}} = -z^2 \pd,\ %
			K_{{z}} = -\bar{z}^2 \pdbar
		},\\
		\pd \equiv \pdd{z},\ %
		\pdbar \equiv \pdd{\bar{z}}\notag
	\end{gather}
	Similarly, for translation $z\mapsto z+a$ and its conjugate, we have $
		P_\mu\sim
		\pqty{P_z = \pd, P_{\bar{z}} = \pdbar}
	$. However, dilation and rotation are both encoded in a complex rescaling $
		z\mapsto \lambda z,\ %
		\lambda = re^{i\theta}\in\mbb{C}
	$; we have:
	\begin{equation}
		z\mapsto \lambda z,\quad
		\lambda = re^{i\theta}\in\mbb{C},\quad
	\begin{aligned}
		\var{r} \ \longleftrightarrow\ %
		D &= z\,\pd + \bar{z}\,\pdbar,\\[-.5ex]
		\var{\theta} \ \longleftrightarrow\ %
		M &= i\,\pqty{z\,\pd - \bar{z}\,\pdbar},
	\end{aligned}
	\end{equation}

	In summary, we have $
		\mop{span}_\mbb{R}\Bqty{
			P_\mu, K_\mu, D, M
		} = \mfrak{so}(3,1)
	$ generating the ``global'' transformation subgroup of the 2D conformal group; here, the $\mfrak{so}(3,1)$ boost is a linear combination\footnote{
		See e.g.\ \https{github.com/davidsd/ph229}. 
	} of $P_\mu$ and $K_\mu$. More specifically, in 2D any holomorphic or anti-holomorphic function gives a conformal transformation, hence the (classical) 2D conformal group is generated by:
	\begin{equation}
		\ell_m = z^{m+1} \pd,\quad
		\bar{\ell}_m = \bar{z}^{m+1} \pdbar,\quad
		m\in\mbb{Z}
	\end{equation}
	i.e.\ the \textit{Witt algebra} (or Virasoro algbera $\Vir_c$ with $c = 0$). It is clear that a (complexified) $\mfrak{so}(3,1)$ lives inside $\Vir_c$, i.e.,
	\begin{equation}
	\begin{aligned}
		\mfrak{so}(3,1)^\mbb{C}
		&= \mop{span}_\mbb{C}\Bqty{
			P_\mu, K_\mu, D, M
		} \\
		&= \mop{span}_\mbb{C}\Bqty{
			\ell_m,\bar{\ell}_m
			\,\big|\, m = 0,\pm 1
		}
		= \mfrak{sl}(2,\mbb{R})^\mbb{C}
			\oplus_\mbb{C}
			\mfrak{sl}(2,\mbb{R})^\mbb{C}
		\subset \Vir_{c}
	\end{aligned}
	\end{equation}
	\end{enumerate}
	\vspace{-1.2\baselineskip}

	\qedfull

	\item \textbf{$bc$ CFT}:
	\begin{equation}
		S = \frac{1}{2\pi}
			\int \dd[2]{z} b\,\pdbar c
	\end{equation}

	Stress tensor of a theory can be obtained via variation over the metric, or equivalently, over the fields $\phi^i$ with $\var{\phi}$ induced by some \textit{local} spacetime translation $
		x^\mu\mapsto x^\mu + \var{x}^\mu,\ %
		\var{x}^\mu = \epsilon(x)\,a^\mu
	$. Here $\epsilon(x)$ is any compactly supported bump function, centered around some point $x_0$.

	In 2D, we have $\mu = z,\bar{z}$; for $\phi(z,\bar{z})$ with conformal weight $(h,\bar{h})$, consider $
		z\mapsto z',\,
		\bar{z}\mapsto \bar{z}'
	$. For convenience, let's first consider a generic variation $\var{z} = \epsilon(z,\bar{z})$ before restricting to spacetime translation; we have:
	\begin{equation}
		\phi'(z',\bar{z}')
		= \pqty\Big{\dv{z'}{z}}^{\!\! -h}
			\pqty\Big{\dv{\bar{z}'}{\bar{z}}}^{
				\!\! -\bar{h}
			}
			\phi(z,\bar{z}),\\[1ex]
		\tilde{\delta}\phi
		= \pqty{
			- h\,\pd\epsilon
			- \bar{h}\,\pdbar\bar{\epsilon}\,
		}\,\phi,\\
		\var{\phi} 
		= \tilde{\delta}\phi
			-\pdv{\phi}{x^\mu} \var{x^\mu}
		= \pqty{
			- h\,\pd\epsilon
			- \bar{h}\,\pdbar\bar{\epsilon}\,
		}\,\phi
			- \epsilon\,\pd\phi
			- \bar{\epsilon}\,\pdbar\phi,
		\label{eq:var_field_compact_supp}
	\end{equation}
	Here we use $\tilde{\delta}\phi$ to denote the ``internal'' variation related to the conformal weights.

	Note that $\phi = b,c$ are anti-commuting Grassmann numbers, variation of the action gives:
	\begin{equation}
	\begin{aligned}
		\var{S}[b,c,\var{b},\var{c}]
		&= \frac{1}{2\pi} \int \dd[2]{z} \pqty{
			\var{b}\,\pdbar c
			+ b\,\pdbar \var{c}
		} \\
		&= \frac{1}{2\pi} \int \dd[2]{z} \pqty{
			- \pdbar c\,\var{b}
			- \pdbar b\,\var{c}
		} + \frac{1}{2\pi} \int \dd[2]{z}
			\pdbar \pqty{b\var{c}}
	\end{aligned}
	\label{eq:bc_action_var}
	\end{equation}
	For \textit{unknown} $b,c$ and {arbitary} $\var{b},\var{c}$, the second term is reduced to a boundary term at infinity and can be dropped; imposing $\var{S} = 0$ gives the equation of motion (EOM): $\pdbar b = \pdbar c = 0$.

	On the other hand, for \textit{on-shell} $b,c$ and compactly supported $\varphi = \var{b},\var{c}$ given in \eqref{eq:var_field_compact_supp}, the first term in \eqref{eq:bc_action_var} vanishes while $\var{S}_0 = 0$ still holds; this gives:
	\begin{equation}
	\begin{aligned}
		0 = \var{S}_0
		&= \frac{1}{2\pi} \int \dd[2]{z}
			\pdbar \pqty{b\var{c}}
		= \frac{1}{2\pi} \int \dd[2]{z}
			\pdbar\,\pqty\big{
				- (1-\lambda)\,bc\,\pd\epsilon
				- b\,\pd c\,\epsilon
			} \\
		&= \frac{1}{2\pi} \int \dd[2]{z}
			\pqty\big{
				- (1-\lambda)\,bc\,
					\pdbar\pd\epsilon
				- b\,\pd c\,\pdbar\epsilon
			}
	\end{aligned}
	\end{equation}
	Here we've distributed the $\pdbar$ operator and dropped all terms that vanish automatically by EOM. Next we shall collect the $\pd\epsilon,\pdbar\epsilon$ terms; integrating by parts on the first integrand gives:
	\begin{equation}
	\begin{aligned}
		0 = \var{S}_0
		&= \frac{1}{2\pi} \int \dd[2]{z}
			\pqty\big{
				(1-\lambda)\,\pd(bc)\,
				- b\,\pd c
			}\,\pdbar\epsilon \\
		&= \frac{1}{2\pi} \int \dd[2]{z}
			\pqty\big{
				(\pd b)\,c
				- \lambda\,\pd(bc)
			}\,\pdbar\epsilon \\
		&= - \frac{1}{2\pi} \int \dd[2]{z}
			\epsilon(z,\bar{z})\,\pd_{\bar{z}}
			\pqty\big{
				(\pd b)\,c
				- \lambda\,\pd(bc)
			}
	\end{aligned}
	\label{eq:conserved_current}
	\end{equation}

	Notice that we have obtained a conserved current using a generic $
		\var{z}
		= \epsilon(z,\bar{z}),
		\var{\bar{z}}
		= \bar{\epsilon}(z,\bar{z})
	$; by setting $\epsilon = \epsilon(z)$, we get \textit{a} energy momentum tensor\footnote{
		Note that the energy momentum tensor obtained in this way is generally \textit{not} unique: it can be off by a boundary term; see Luboš' comment at \https{physics.stackexchange.com/a/96100}, also \arxiv{1601.03616}. However, it is possible to fix this redundancy by considering $Tb$ OPE and match its conformal dimension. I would like to thank \textit{林般} for pointing this out. 
	}:
	\begin{equation}
		T(z)
		= \normorder{(\pd b)\,c}
			- \lambda\,\pd(\normorder{bc})
	\end{equation}
	Normal ordering is added manually to remove singular terms.

	To compute $TT$ OPE, we need the OPE of $b(z)\,c(0)$; this is obtained by examining the following path integral, which is zero since the integrand is a total functional derivative:
	\begin{equation}
		0 = \int \mscr{D}b\,\mscr{D}c\,
			\fdv{\phi}\pqty{e^{-S}\,\phi}
	\end{equation}
	Taking $\phi=b,c$, this generates operator equations such as $
		\pdbar b(z)\,c(0)
		= 2\pi\delta^2(z,\bar{z})
	$. Note that $
		\pdbar(\frac{1}{z})
		= 2\pi\delta^2(z,\bar{z})
	$, which gives:
	\begin{equation}
		b(z)\,c(0) \sim c(z)\,b(0)
		\sim \frac{1}{z}
	\end{equation}

	With the $bc$ OPE in hand, the $TT$ OPE is computed directly with blunt force. This gives:
	\begin{equation}
		T(z)\,T(0)
		\sim \frac{
			-6\lambda^2 + 6\lambda - 1
		}{z^4} + \cdots
	\end{equation}
	In general we have $
		-6\lambda^2 + 6\lambda - 1
		= \frac{c}{2}
	$; for $\lambda = 2$ this gives $c = -26$. 
	\qedfull

	\item \textbf{Free Fermion CFT:}
	\begin{equation}
		S = \int \dd[2]{z}
			\psi_i\,\pdbar\psi^i,\quad
		\psi^i = \psi_i^*,\quad
		\psi_i = \psi_i(z)
	\end{equation}

	\begin{enumerate}
	\item Mode expansion of such chiral fermion is given by:
	\begin{equation}
		\psi_i = \sum_{
			k\in\mbb{Z}+\frac{1}{2}
		} \frac{b_{ik}}{z^{k+\frac{1}{2}}},\quad
		b_{ik}
		= \frac{1}{2\pi i} \oint \dd{z}
			z^{k-\frac{1}{2}} \psi_i
	\end{equation}
	Canonical quantization is achieved by simply imposing anti-commutation relations; this is justified by mapping the system onto a cylinder, then $b_{ik}$'s indeed map to modes on the spatial circle\footnote{
		This can be proven rigorously by considering operator equations like in the $bc$ CFT problem. 
	}. The only non-zero commutators are:
	\begin{equation}
		\Bqty{b_{ik},b^{j\dagger}_q}
		= \delta_{k+q,0}\,\delta^j_i
	\end{equation}

	This gives the only non-zero 2-point functions:
	\begin{equation}
	\begin{aligned}
		\ave{
			\psi_i(z)\,\psi^j(w)
		}
		&= \sum_{k,q\in\mbb{Z}+\frac{1}{2}}
			\frac{1}{z^{k+\frac{1}{2}}}
			\frac{1}{w^{q+\frac{1}{2}}}
			\ave{b_{ik} b^{j\dagger}_q} \\
		&= \sum_{k,q\in\mbb{Z}+\frac{1}{2}}
			\frac{1}{z^{k+\frac{1}{2}}}
			\frac{1}{w^{q+\frac{1}{2}}}
			\mel{0}{
				\Bqty{b_{ik},b^{j\dagger}_q}
			}{0}
		= \frac{\delta^j_i}{z-w}
	\end{aligned}
	\end{equation}
	Note that $
		b^i_k\ket{0} = 0,\ %
		\forall\ k\ge\frac{1}{2}
	$.

	\item[(b)(c)] Combining two $\psi$ expansions gives the mode expansion of $
		J\id{_i^j}
		= \normorder{\psi_i(z)\,\psi^j(z)}
	$:
	\begin{equation}
		J\id{_i^j}(z)
		= \sum_{k\in\mbb{Z}}
			\frac{(J\id{_i^j})_k}{z^{k+1}},\quad
		(J\id{_i^j})_k
		= \sum_{q\in\mbb{Z}+\frac{1}{2}}
			\normorder{
				b_{iq}\,b^{j\dagger}_{k-q}
			}
	\end{equation}
	It is in fact more convenient to obtain the $JJ$ OPE first, and then use it to find the  $[J_0,J_0]$ mode commutator\footnote{
		I would like to thank \textit{谷夏} for providing this hint. 
	}; note that $
		{
			{\psi}_i(z)\,{\psi}^j(w)
		}
	$ contraction gives $\frac{\delta^j_i}{z-w}$, we have:
	\begin{equation}
		J\id{_i^j}(z)\,J\id{_k^l}(0)
		\sim \frac{
			\delta_i^l\delta_k^j
		}{z^4} + \frac{
			\delta^j_k J\id{_i^l}(0)
			- \delta^l_i J\id{_k^j}(0)
		}{z},\\[1ex]
		\bqty{
			(J\id{_i^j})_0, (J\id{_k^l})_0
		}
		= \frac{1}{(2\pi i)^2}
			\oint_0 \dd{w}
			\oint_w \dd{z}
				J\id{_i^j}(z)\,J\id{_k^l}(w)
		= \delta_i^l\,(J\id{_k^j})_0
			- \delta_k^j\,(J\id{_i^l})_0
	\end{equation}

	\item[(d)] Similar to $bc$ CFT, we have:
	\begin{equation}
		T(z) = \frac{1}{2} \normorder{\psi_i\,\pd\psi^i}
			- \normorder{\pd\psi_i\,\psi^i}\,
		,\quad
		T(z)\,T(w)
		\sim \frac{n/2}{(z-w)^4}
			+ \frac{2T(w)}{(z-w)^2}
			+ \frac{\pd T(w)}{z-w}
	\end{equation}
	With each field contributing $\frac{1}{2}$ central charge.

	\item[(e)] For real fermions, there is an additional reality condition:
	\begin{equation}
		\psi^i = \psi^\star_i = \psi_i 
	\end{equation}
	The canonical quantization still holds without the extra adjoint, same as the 2-point function:
	\begin{equation}
		\ave{\psi_i(z)\,\psi_j(w)}
		= \frac{\delta_{ij}}{z - w}
	\end{equation}

	Similar holds for $J_{ij} = \normorder{\psi_i\psi_j}$ and its OPE, but we no longer need to distinguish upper/lower indices; we have:
	\begin{equation}
		J_{ij}(z)\,J_{kl}(0)
		\sim \frac{
			- \delta_{ik}\delta_{jl}
			+ \delta_{il}\delta_{jk}
		}{z^4} + \frac{
			- \delta_{ik} J_{jl}(0)
			+ \delta_{il} J_{jk}(0)
			+ \delta_{jk} J_{il}(0)
			- \delta_{jl} J_{ik}(0)
		}{z}\\[1ex]
		\bqty{
			(J_{ij})_0, (J_{kl})_0
		}
		= - \delta_{ik} (J_{jl})_0
			+ \delta_{il} (J_{jk})_0
			+ \delta_{jk} (J_{il})_0
			- \delta_{jl} (J_{ik})_0
	\end{equation}
	This is precisely the $\mfrak{o}(n)$ algebra. 
	\qedfull

	\end{enumerate}

	\end{enumerate}

\printbibliography[%
%	title = {参考文献} %
	,heading = bibintoc
]
\end{document}

### 2020-03-11 Strings2020/strings1/strings1.tex
Add revisions & updates to strings1

@@
 		0 = \int \mscr{D}b\,\mscr{D}c\,
-			\fdv{\phi}\pqty{e^{-S}\,\phi}
+			\fdv{\phi}\pqty{e^{-S}\,\psi}
 	\end{equation}
-	Taking $\phi=b,c$, this generates operator equations such as $
+	Taking $\phi,\psi=b,c$, this generates operator equations such as $
 		\pdbar b(z)\,c(0)
@@
 		b(z)\,c(0) \sim c(z)\,b(0)
-		\sim \frac{1}{z}
+		\sim \frac{1}{z},\quad
+		b(z)\,b(0) \sim 0
+		\sim c(z)\,c(0)
 	\end{equation}
 
-	With the $bc$ OPE in hand, the $TT$ OPE is computed directly with blunt force. This gives:
+	With the $bc$ OPE in hand, the $TT$ OPE is computed directly with brute force, by repeatedly applying Wick's theorem. This gives:
 	\begin{equation}
@@
 		= \normorder{\psi_i(z)\,\psi^j(z)}
-	$:
+	$, namely:
 	\begin{equation}
@@
 			\delta_i^l\delta_k^j
-		}{z^4} + \frac{
+		}{z^2} + \frac{
 			\delta^j_k J\id{_i^l}(0)
@@
 	\begin{equation}
-		T(z) = \frac{1}{2} \normorder{\psi_i\,\pd\psi^i}
-			- \normorder{\pd\psi_i\,\psi^i}\,
-		,\quad
+		T(z) = \frac{1}{2}\,\pqty{
+			\normorder{\psi_i\,\pd\psi^i}
+			- \normorder{\pd\psi_i\,\psi^i}
+		},\quad
 		T(z)\,T(w)
@@
 	\end{equation}
-	With each field contributing $\frac{1}{2}$ central charge.
+	With each (complex) field contributing $\frac{1}{2}\times 2$ central charge\footnote{
+		In fact a complex (Dirac) fermion can be ``treated like'' (\textit{dual to}) a boson; this is \textit{bosonization}. 
+	}.
 
@@
 			+ \delta_{il}\delta_{jk}
-		}{z^4} + \frac{
+		}{z^2} + \frac{
 			- \delta_{ik} J_{jl}(0)

### 2020-03-14 Strings2020/strings2/strings2.tex
Add strings2 & update CI

--- 2020-03-11 Strings2020/strings1/strings1.tex
@@
 
-\newcommand{\hwNumber}{1}
+\newcommand{\hwNumber}{2 [WIP]}
 
@@
 \newcommand{\Vir}{\mathbf{V}\mfrak{ir}}
+\usepackage{cancel}
 
@@
 	\begin{enumerate}
-	\item \textbf{Read \textit{Polchinski} Sections 1.3 and 1.4}:
+	\item \textbf{BRST Quantization of Bosonic String}: 
+	\begin{gather}
+		S = S^X + S^{bc},\\
+		S^X = - \frac{1}{2\pi\alpha'} \int\dd[2]{z}
+			\pd X^\mu \pdbar X_\mu,\quad
+		S^{bc} = \frac{1}{2\pi} \int\dd[2]{z}
+			\pqty\Big{
+				b\,\pdbar c
+				+ \tilde{b}\,\pd\tilde{c}
+			}
+	\end{gather}
+	This is the gauge fixed action. The corresponding BRST transformation is listed in \textit{Polchinski}; for each of the subsystems, we have its (classical) energy-momentum:
+	\begin{equation}
+		T^X(z)
+		= - \frac{1}{\alpha'}\,
+			\normorder{\pd X^\mu \pd X_\mu}\,,\quad
+		\tilde{T}^X(\bar{z})
+		= - \frac{1}{\alpha'}\,
+			\normorder{\pdbar X^\mu \pdbar X_\mu}\,,
+		\\[.5ex]
+		T^{bc}(z) = \normorder{(\pd b)\,c}
+			- 2\,\pd(\normorder{bc}),\quad
+		\tilde{T}^{bc}(\bar{z}) = \normorder{
+			(\pdbar \tilde{b})\,\tilde{c}
+		} - 2\,\pdbar(\normorder{
+			\tilde{b}\tilde{c}
+		}),
+	\end{equation}
 
-	Read, \textit{mostly} understood. \qed
+	\begin{enumerate}
+	\item To get the energy-momentum of $S$, let's visit each of the subsystems respectively; first, BRST transformation of $X$ is given by:
+	\begin{equation}
+		\var{X^\mu}
+		= i\epsilon\,\pqty{
+			c\pd + \tilde{c}\pdbar
+		} X^\mu
+	\end{equation}
+	Compared with the conformal transformation\footnote{
+		We follow the convention of \textit{Polchinski} unless otherwise stated. 
+	}: $
+		\var{X^\mu}
+		= -\epsilon\,\pqty{
+			v\pd
+			+ \tilde{v}\pdbar
+		} X^\mu
+	$, we see that they are in fact identical under the equivalence $
+		-\epsilon v \sim i\epsilon c,\ %
+		-\epsilon \tilde{v} \sim i\epsilon \tilde{c}
+	$, hence we can simply follow the derivation of conformal current and write down $\var{S}^X$'s contribution to the conserved current:
+	\begin{equation}
+		j^X = c(z)\,T^X(z)
+	\end{equation}
+
+	The transformation of $b,c$ is less obvious; for holomorphic current, we need only focus on the holomorphic part of $S^{bc}$; on-shell variation yields:
+	\begin{equation}
+		0 = \var{S}^{bc}
+		= \pqty{\frac{1}{2\pi} \int \dd[2]{z} \pqty{
+			- \pdbar c\,\var{b}
+			- \pdbar b\,\var{c}
+		}}_{\!\!=\mspace{1mu}0}
+		+ \frac{1}{2\pi} \int \dd[2]{z}
+			\pdbar \pqty{b\var{c}}
+		= \frac{1}{2\pi} \int \dd[2]{z}
+			\pdbar\epsilon\,\pqty\big{
+				-ibc\,\pd c
+			} 
+	\end{equation}
+	Here we've plugged in $
+		\var{c} = i\epsilon(z,\bar{z})\,c\pd c
+	$, and we have moved $\pdbar\epsilon$ to the beginning of the expression, while respecting the anti-commuting nature of $\epsilon$.
+With a conventional $i$ coefficent (which agrees with the convention of $j^X$), we have $bc$'s contribution to the conserved current:
+	\begin{equation}
+		j^{bc} = i\,\pqty\big{
+			-ibc\,\pd c
+		} = bc\,\pd c
+	\end{equation}
+
+	Note that $j^{bc}$ is, in fact, related to the energy-momentum (at least classically):
+	\begin{equation}
+		\frac{1}{2}\,cT^{bc}
+		= \frac{1}{2}\,c\,{(\pd b)\,c}
+			- c\,\pd({bc})
+		= - c\,\pd({bc})
+		= - cb\,\pd c
+		= bc\,\pd c = j^{bc}
+	\end{equation}
+	Hence we have the classical BRST current:
+	\begin{equation}
+		j(z) = c(z)\,\pqty{
+			T^X + \frac{1}{2}\,T^{bc}
+		}
+	\end{equation}
+
+	For a quantum version, redefine $j(z)$ with normal ordering, and we have:
+	\begin{gather}
+		T(z)\,j(0)
+		\sim T^X(z)\,T^X(0)\,c(0)
+			+ T^{bc}(z)\,cT^X(0)
+			+ T^{bc}(z)\,
+				\normorder{bc\,\pd c}_{\,(0)},
+		\label{eq:BRST_Tj_OPE}\\
+		\text{where}\quad
+		T^X(z)\,T^X(0)\,c(0)
+		\sim \pqty{
+			\frac{D}{2z^4}
+			+ \frac{2}{z^2}\,{T^X(0)}
+			+ \frac{1}{z}\,{\pd T^X(0)}
+		}\,c(0),
+		\label{eq:BRST_Tj_OPE_partI}
+	\end{gather}
+	Here we've used the fact that $X$ and $b,c$ is de-coupled in the gauge-fixed action, hence their OPE is trivial.
+Also, we've expanded the first term using $TT$ OPE of the free boson.
+Additionally, note that $c(z)$ is primary with weight $(-1,0)$, we have:
+	\begin{equation}
+	\begin{aligned}
+		T^{bc}(z)\,cT^X(0)
+		&\sim \Bqty{T^{bc}(z)\,c(0)}\,T^X(0) \\
+		&\sim \pqty{
+			\frac{-1}{z^2}\,c(0)
+			+ \frac{1}{z}\,\pd c(0)
+		}\,T^X(0),
+	\end{aligned}
+	\label{eq:BRST_Tj_OPE_partII}
+	\end{equation}
+	The last term in \eqref{eq:BRST_Tj_OPE} can be brute-forced as follows:
+	\begin{equation}
+		T^{bc}(z)\,\normorder{bc\,\pd c}_{\,(0)}
+		= \pqty\big{
+			\normorder{(\pd b)\,c}
+			- 2\,\pd(\normorder{bc})
+		}_{(z)}\,\normorder{bc\,\pd c}_{\,(0)}\,,
+	\end{equation}
+	\vspace{-1\baselineskip}
+	\begin{align}
+		\normorder{(\pd b)\,c}_{\,(z)}\,
+		\normorder{bc\,\pd c}_{\,(0)}
+		&\sim \normorder{
+			\wick{
+				(\pd \c b)\,c_{(z)}\,
+				b\c c\,\pd c_{(0)}
+			}
+		} + \normorder{
+			\wick{
+				(\pd \c b)\,c_{(z)}\,
+				bc\,\pd \c c_{(0)}
+			}
+		} + \normorder{
+			\wick{
+				(\pd b)\,\c c_{(z)}\,
+				\c b c\,\pd c_{(0)}
+			}
+		} \notag\\
+		&\qquad + \normorder{
+			\wick{
+				(\pd \c1 b)\,\c2 c_{(z)}\,
+				\c2 b \c1 c\,\pd c_{(0)}
+			}
+		} + \normorder{
+			\wick{
+				(\pd \c1 b)\,\c2 c_{(z)}\,
+				\c2 bc \,\pd \c1 c_{(0)}
+			}
+		} \notag\\[.5ex]
+		&\sim \frac{-1}{z^2}\,(+1)\,\normorder{
+			c_{(z)}\,b\,\pd c_{(0)}
+		} + \frac{-2}{z^3}\,(-1)\,\normorder{
+			c_{(z)}\,bc_{(0)}
+		} + \frac{1}{z}\,(+1)\,\normorder{
+			\pd b_{(z)}\,c\pd c_{(0)}
+		} \notag\\
+		&\qquad + \frac{-1}{z^2}\cdot\frac{1}{z}\,
+			(+1)\,\pd c(0)
+		+ \frac{-2}{z^3}\cdot\frac{1}{z}\,
+			(-1)\,c(0) \notag\\[.5ex]
+		&\sim \frac{-1}{z^2}\,\pqty{
+			-j^{bc}(0) + \order*{z^2}
+		} + \frac{2}{z^3}\,\pqty{
+			z\,j^{bc}(0)
+			+ \frac{z^2}{2}\,\normorder{
+				bc\,\pd^2 c
+			}_{\,(0)}
+			+ \order*{z^3}
+		} \notag\\[-.3ex]
+		&\qquad + \frac{1}{z}\,\pqty\big{
+			\normorder{
+				(\pd b)\,c\,\pd c
+			}_{\,(0)} + \order{z}
+		} + \frac{-1}{z^3}\,\pd c(0)
+			+ \frac{2}{z^4}\,c(0) \notag\\[.7ex]
+		&\sim \frac{4}{2z^4}\,c(0)
+			+ \frac{-1}{z^3}\,\pd c(0)
+			+ \frac{3}{z^2}\,j^{bc}(0)
+			+ \frac{1}{z}\,\normorder{\pqty{
+				bc\,\pd^2 c
+				+ (\pd b)\,c\,\pd c
+			}}_{\,(0)}\,, \notag\\[1ex]
+		&\sim \frac{4}{2z^4}\,c(0)
+			+ \frac{-1}{z^3}\,\pd c(0)
+			+ \frac{3}{z^2}\,j^{bc}(0)
+			+ \frac{1}{z}\,\pd j^{bc}(0), \\[3ex]
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%		THIS IS INSANE!
+%		ANOTHER OPE ...
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+		\normorder{bc}_{\,(z)}\,
+		\normorder{bc\,\pd c}_{\,(0)}
+		&\sim \normorder{
+			\wick{
+				\c1 b c_{(z)}\,
+				b \c1 c\, \pd c_{(0)}
+			}
+		} + \normorder{
+			\wick{
+				\c1 b c_{(z)}\,
+				b c\, \pd \c1 c_{(0)}
+			}
+		} + \normorder{
+			\wick{
+				b \c1 c_{(z)}\,
+				\c1 b c\, \pd c_{(0)}
+			}
+		} \notag\\
+		&\qquad + \normorder{
+			\wick{
+				\c1 b \c2 c_{(z)}\,
+				\c2 b \c1 c\, \pd c_{(0)}
+			}
+		} + \normorder{
+			\wick{
+				\c1 b \c2 c_{(z)}\,
+				\c2 b c\, \pd \c1 c_{(0)}
+			}
+		} \notag\\[.5ex]
+		&\sim \frac{1}{z}\,(+1)\,\normorder{
+			c_{(z)}\,b\,\pd c_{(0)}
+		} + \frac{1}{z^2}\,(-1)\,\normorder{
+			c_{(z)}\,bc_{(0)}
+		} + \frac{1}{z}\,(+1)\,\normorder{
+			b_{(z)}\,c\pd c_{(0)}
+		} \notag\\
+		&\qquad + \frac{1}{z}\cdot\frac{1}{z}\,
+			(+1)\,\pd c(0)
+		+ \frac{1}{z^2}\cdot\frac{1}{z}\,
+			(-1)\,c(0) \notag\\[1ex]
+		&\sim \frac{1}{z}\,\pqty\big{
+			-j^{bc}(0)
+		} + \frac{-1}{z^2}\,\pqty\big{
+			z\,j^{bc}(0)
+		} + \frac{1}{z}\,\pqty\big{
+			j^{bc}(0)
+		} + \frac{1}{z^2}\,\pd c(0)
+		+ \frac{-1}{z^3}\,c(0) \notag\\[1ex]
+		&\sim \frac{-1}{z^3}\,c(0)
+			+ \frac{1}{z^2}\,\pd c(0)
+			+ \frac{-1}{z}\,j^{bc}(0), \\[2ex]
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%		DERIVATIVE
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+		\pd (\normorder{bc})_{(z)}\,
+		\normorder{bc\,\pd c}_{\,(0)}
+		&\sim \frac{6}{2z^4}\,c(0)
+			+ \frac{-2}{z^3}\,\pd c(0)
+			+ \frac{1}{z^2}\,j^{bc}(0),
+	\end{align}
+	\begin{gather}
+		T^{bc}(z)\,\normorder{bc\,\pd c}_{\,(0)}
+		\sim \frac{-8}{2z^4}\,c(0)
+			+ \frac{3}{z^3}\,\pd c(0)
+			+ \frac{1}{z^2}\,j^{bc}(0)
+			+ \frac{1}{z}\,\pd j^{bc}(0),
+		\label{eq:BRST_Tj_OPE_partIII}\\[2ex]
+		T(z)\,j(0)
+		\sim \eqref{eq:BRST_Tj_OPE_partI}
+			+ \eqref{eq:BRST_Tj_OPE_partII}
+			+ \eqref{eq:BRST_Tj_OPE_partIII}
+		\sim \frac{D-8}{2z^4}\,c(0)
+			+ \frac{3}{z^3}\,\pd c(0)
+			+ \frac{1}{z^2}\,j(0)
+			+ \frac{1}{z}\,\pd j(0),
+	\end{gather}
+
+	We see that $j(z)$ defined with na\"ive normal ordering is \textit{almost} but \textit{not quite} a primary.
+It differs from primary OPE at $\order{\frac{1}{z^4}}$ and $\order{\frac{1}{z^3}}$.
+However, it is possible to make it into a primary by adding extra terms that do not interfere with current conservation $\pdbar j = 0$.
+To cancel the $\frac{3}{z^3}\,\pd c(0)$ term, notice that $
+		b(z)\,\pd^2 c(0) \sim \frac{2}{z^3}
+	$, therefore it may be helpful to look at:
+	\begin{equation}
+	\begin{aligned}
+		T(z)\,\pd^2 c(0)
+		\sim T^{bc}(z)\,\pd^2 c(0)
+		&\sim \pd^2_w \pqty{
+			T^{bc}(z)\,c(w)
+		}_{w\to 0} \\
+		&\sim \pd^2_w \pqty{
+			\frac{-1}{(z-w)^2}\,c(w)
+			+ \frac{1}{z-w}\,\pd c(w)
+		}_{\!w\to 0} \\[.5ex]
+		&\sim \frac{-12}{2z^4}\,c(0)
+			+ \frac{-2}{z^3}\,\pd c(0)
+			+ \frac{1}{z^2}\,\pd^2 c(0)
+			+ \frac{1}{z}\,\pd^3 c(0),
+	\end{aligned}
+	\end{equation}
+	Again we've used $Tc$ OPE of the primary $c(w)$. We see that indeed, the $\frac{1}{z^3}\,\pd c(0)$ term can be canceled by shifting $j(z)$:
+	\begin{gather}
+		j(z)\ \longmapsto\ j(z)
+			+ \frac{3}{2}\,\pd^2 c(z),\quad
+		j(z) = j^X + j^{bc}
+			+ \frac{3}{2}\,\pd^2 c,\\[1ex]
+		T(z)\,j(0)
+		\sim \frac{D-26}{2z^4}\,c(0)
+			+ \frac{1}{z^2}\,j(0)
+			+ \frac{1}{z}\,\pd j(0),
+	\end{gather}
+
+	We see that $j(z)$ defined in this way is a primary of weight $(1,0)$ in $D = 26$. This is the quantum BRST current. 
+	\qedfull
+
+%	note that $b,c$ are primaries with weight $(2,0)$ and $(-1,0)$, hence $Tb,Tc$ OPEs take the standard form of a $T\cdot(\text{primary})$ OPE. We have:
+%	\begin{equation}
+%	\begin{aligned}
+%		T^{bc}(z)\,\normorder{bc\,\pd c}_{\,(0)}
+%		&\sim \pqty{
+%				\frac{2}{z^2}\,
+%					\normorder{bc\,\pd c}
+%				+ \frac{1}{z}\,\normorder{
+%					(\pd b)\,c\pd c
+%				}
+%			} \\
+%		&\phantom{\sim \quad}
+%			+ \pqty{
+%				\frac{-1}{z^2}\,
+%					\normorder{bc\,\pd c}
+%				+ \frac{1}{z}\,\normorder{
+%					b\,(\pd c)(\pd c)
+%				}
+%			} \\
+%		&\phantom{\sim \quad}
+%			+ \pqty{
+%				\frac{-1}{z^2}\,
+%					\normorder{bc\,\pd c}
+%				+ \frac{1}{z}\,\normorder{
+%					bc\,\pd^2 c
+%				}
+%			} \\
+%		&\sim \frac{1}{z}\,\pd\,
+%			\normorder{bc\,\pd c}
+%		\sim \frac{1}{z}\,\pd\,\pqty{
+%			j - cT^X
+%		}_{(0)} \\
+%		&\sim \frac{1}{z}\,\pd j(0)
+%		- \frac{1}{z}\,c(0)\,\pd T^X(0)
+%		- \frac{1}{z}\,T^X(0)\,\pd c(0),
+%	\end{aligned}\\
+%		T(z)\,j(0)
+%		\sim \frac{D}{2z^4}\,c(0)
+%			+ \frac{2}{z^2}\,T^X(0)\,c(0)
+%			+ \frac{1}{z}\,\pqty{
+%				\pd j(0)
+%				- T^X(0)\,\pd c(0)
+%			}
+%	\end{equation}
+
+	\item
+
+	\end{enumerate}
+
+	\item \textbf{Linear Dilaton CFT:}
+
+	\clearpage
+
+	\quad
+	\vfill\pagebreak
 

### 2020-03-14 .github/workflows/compile.sh

@@ -2,7 +2,7 @@
 
 name: Build with XeLaTeX
 
-# Controls when the action will run. Triggers the workflow on push or pull request 
+# Controls when the action will run. Triggers the workflow on push or pull request
 # events but only for the master branch
 on:
   push:
@@ -23,7 +23,20 @@ jobs:
     - uses: actions/checkout@v2
 
     - name: Compile LaTeX document
-      uses: xu-cheng/latex-action@master
+      # Reference: <xu-cheng/latex-action>
+      runs:
+        using: docker
+        image: Dockerfile
+
+    - name: Upload to Release
+      id: upload-release-asset
+      uses: softprops/action-gh-release@v1
       with:
-        root_file: '*/*/*.tex'
-        args: -xelatex -file-line-error -interaction=nonstopmode
+        tag_name: v0.1.0-alpha
+        files: |
+          '*/*/*.pdf'
+      env:
+        GITHUB_TOKEN: ${{ secrets.GITHUB_TOKEN }}
+      if: always()
+
+# vim: ts=2 sw=2

### 2020-03-14 compile.sh

@@ -1,0 +1,23 @@
+#!/bin/bash
+
+DIR=$(dirname "$(readlink -f "${BASH_SOURCE[0]}")")
+cd "$DIR" || exit 1
+
+FILES=$(find . \
+    -regex "./[^/]+/[^/]+/[^/]+.tex" \
+    -not -path "./Templates/*"
+)
+
+for file in $FILES; do
+    echo "# Compiling \`$file\` ..."
+    cd "$(dirname "$file")" || exit 1
+
+    latexmk \
+        -xelatex \
+        -synctex=1 \
+        -interaction=nonstopmode \
+        -shell-escape \
+        "$(basename "$file")"
+
+    cd "$DIR" || exit 1
+done

### 2020-03-14 .github/workflows/compile.sh
Fix github workflow

@@ -1,42 +1,0 @@
-# This is a basic workflow to help you get started with Actions
-
-name: Build with XeLaTeX
-
-# Controls when the action will run. Triggers the workflow on push or pull request
-# events but only for the master branch
-on:
-  push:
-    branches: [ master ]
-  pull_request:
-    branches: [ master ]
-
-# A workflow run is made up of one or more jobs that can run sequentially or in parallel
-jobs:
-  # This workflow contains a single job called "build"
-  build:
-    # The type of runner that the job will run on
-    runs-on: ubuntu-latest
-
-    # Steps represent a sequence of tasks that will be executed as part of the job
-    steps:
-    # Checks-out your repository under $GITHUB_WORKSPACE, so your job can access it
-    - uses: actions/checkout@v2
-
-    - name: Compile LaTeX document
-      # Reference: <xu-cheng/latex-action>
-      runs:
-        using: docker
-        image: Dockerfile
-
-    - name: Upload to Release
-      id: upload-release-asset
-      uses: softprops/action-gh-release@v1
-      with:
-        tag_name: v0.1.0-alpha
-        files: |
-          '*/*/*.pdf'
-      env:
-        GITHUB_TOKEN: ${{ secrets.GITHUB_TOKEN }}
-      if: always()
-
-# vim: ts=2 sw=2

### 2020-03-14 compile.sh

@@ -1,15 +1,19 @@
-#!/bin/bash
+#!/bin/sh
+# shellcheck disable=2011
 
-DIR=$(dirname "$(readlink -f "${BASH_SOURCE[0]}")")
-cd "$DIR" || exit 1
+DIR=$PWD
+echo "### $DIR"
+ls | xargs
 
 FILES=$(find . \
     -regex "./[^/]+/[^/]+/[^/]+.tex" \
     -not -path "./Templates/*"
 )
+echo "### Files:"
+echo "$FILES"
 
 for file in $FILES; do
-    echo "# Compiling \`$file\` ..."
+    echo "### Compiling \`$file\` ..."
     cd "$(dirname "$file")" || exit 1
 
     latexmk \

### 2020-03-14 compile.sh
Add bash & utils in docker

@@ -1,7 +1,10 @@
-#!/bin/sh
+#!/bin/bash
 # shellcheck disable=2011
 
-DIR=$PWD
+[[ -n $1 ]] \
+    && DIR=$1 \
+    || DIR=$(dirname "$(readlink -f "$0")")
+
 echo "### $DIR"
 ls | xargs
 

### 2020-03-18 AlgebraicTopology2020/algtop3/algtop3.tex
Add algtop3, update Templates

% !TeX encoding = UTF-8
% !TeX spellcheck = en_US
% !TeX TXS-program:bibliography = biber -l zh__pinyin --output-safechars %

\documentclass[a4paper,10pt]{article}

\newcommand{\hwNumber}{3 [WIP]}

\input{../algtop_preamble.tex}
\input{../.modules/basics/biblatex.tex}

%%% ID: sensitive, do NOT publish!
%\InputIfFileExists{../id.tex}{}{}

\newcommand{\vset}[1]{\Bqty{\ \begin{gathered}
	#1
\end{gathered}\ }}
\newcommand{\Zpoly}[1]{\mbb{Z}[x]\big/x^{#1}}
\newcommand{\colim}{\mop{colim}}

\begin{document}
\maketitle
\pagestyle{headings}
\pagenumbering{arabic}
\thispagestyle{empty}

	\begin{enumerate}
	\item \textbf{Example of limit in \Cat{Vect}:}
	\begin{equation}
	\begin{tikzcd}[row sep=-3.5ex,column sep=8ex]
		& \vset{0 \\ \mbb{R}} \\
		I = \vset{\bullet \\ \star}
			\arrow[ur,mapsto,%
				"F"]
			\arrow[dr,mapsto,swap,%
				"\Delta(V)" near end]
		& \\
		& \vset{V \\ V}
	\end{tikzcd}
		\ \supset\ \Cat{Vect}\colon \text{
			$\mbb{R}$ vector space
		},
	\end{equation}

	\begin{enumerate}
	\item By definition, we have:
	\begin{equation}
	\begin{tikzcd}[row sep=8.5ex,column sep=7ex]
		& \Delta(\lim F)
			\arrow[d,Rightarrow,"\sigma"] \\
		\Delta(V)
			\arrow[r,Rightarrow,"\eta"]
			\arrow[ur,Rightarrow,dashed,%
				"\exists!\,\Delta(g)"] &
		F
	\end{tikzcd}
	\label{eq:def_limit}
	\end{equation}
	Where $g\colon V\to \lim F$. 
	More intuitively, for the above $F\colon I\to\Cat{Vect}$, this translates to the following diagram in \Cat{Vect}:
	\begin{equation}
	\begin{tikzcd}[row sep=2ex,column sep=8ex]
		&& 0 \\
		V
			\arrow[r,dashed,
				"\exists!\, g"]
			\arrow[urr,bend left,%
				"\eta_\bullet"]
			\arrow[drr,bend right,swap,%
				"\eta_\star"] &
		\lim F
			\arrow[ur,%
				"\sigma_\bullet"]
			\arrow[dr,swap,%
				"\sigma_\star"] & \\
		&& \mbb{R}
	\end{tikzcd}
	\label{eq:lim_in_vect}
	\end{equation}
	\end{enumerate}

	Now we verify that $\lim F = \mbb{R}$, along with the following choice of $\sigma$:
	\begin{equation}
		\sigma_\bullet = 0,\quad
		\sigma_\star = \idty_\mbb{R}
	\end{equation}
	In fact, for the above diagram \eqref{eq:lim_in_vect} to be commutative, we must have $g = \eta_\star$. Note that such $g$ is unique once $\sigma$ is chosen; for our choice of $\sigma$, if $g \ne \eta_\star$, then the diagram \textit{cannot} commute. Hence $\lim F = \mbb{R}$, along with the above choice of $
		\sigma\colon \Delta(\mbb{R})\Rightarrow F
	$. In other words, we have:
	\begin{equation}
	\begin{tikzcd}[row sep=1ex,column sep=2.5em]
		& \Bqty\big{\ \bullet,\ \star\ }
			\arrow[ddl,"\Delta(\mbb{R})",swap]
			\arrow[ddr,"F"]
		& \\
		& \xRightarrow{\quad\sigma\quad} & \\
		\mbb{R} & & \Bqty\big{\ 0,\ \mbb{R}\ }
	\end{tikzcd}
	\end{equation}
	\vspace{-2.25\baselineskip}

	\qed

	\item[(b)(c)] From diagram \eqref{eq:def_limit} and discussions in (a), we know that: 
	\begin{equation}
		\exists\,!\ \tau = \Delta(g)\colon\ %
		\Delta(V)\Longrightarrow \Delta(\mbb{R})
	\end{equation}
	Here $g\colon V\to\mbb{R}$ is fixed uniquely once $\sigma$ is fixed. However, $\sigma$ may vary up to isomorphism; therefore, a generic choice of $\sigma$ is given by:
	\begin{equation}
		\sigma_\bullet = 0,\quad
		\sigma_\star = k\,\idty_\mbb{R},\quad
		k\in\mbb{R}
	\end{equation}

	For such $g$, by the same arguments in (a), we have:
	\begin{equation}
		\exists\,!\,\ %
			g = \frac{1}{k}\,\eta_\star\,,\ %
			\tau
			= \Delta(g)
			= \frac{1}{k}\,\Delta(\eta_\star),\quad
		\textsl{s.\,t.\quad
			\eqref{eq:def_limit},
			\eqref{eq:lim_in_vect} commutes}
	\end{equation}
	Note that $k\in\mbb{R}$, for every $k$ there is a different $g$ and $\tau$; hence there are $
		\norm{\{k\}} = \norm{\mbb{R}}
	$ many choices of $\tau$ to make the diagram commute. In particular, for $k = 1$ we recover $
		\tau = \Delta(\eta_\star)
	$. \qedfull

	\item \textbf{Limit and colimit of polynomial ring:}

	By definition,
	\begin{equation}
	\begin{tikzcd}[row sep=7ex,column sep=8ex,baseline=-.8ex]
		&&[-4ex] Q
			\arrow[ddll]
			\arrow[ddl,"\eta_{n+1}" near end,swap]
			\arrow[ddr,"\eta_{n}" near end]
			\arrow[ddrr]
			\arrow[ddrrr]
			\arrow[d,dotted,"\exists! f" description]
		&[-4ex] && \\
		&& \lim F
			\arrow[dl,"\pi_{n+1}"]
			\arrow[dr,"\pi_{n}",swap]
		&&& \\
		\cdots
			\arrow[ddrr]
			\arrow[r,"p_{n+1}"] &
		\Zpoly{n+1}
			\arrow[dr,"\sigma_{n+1}"]
			\arrow[ddr,
				"\tau_{n+1}\!" near start,swap]
			\arrow[rr,"p_n"] 
		&&
		\Zpoly{n}
			\arrow[dl,"\sigma_{n}",swap]
			\arrow[ddl,
				"\tau_{n}" near start]
			\arrow[r,"p_{n-1}"] &
		\cdots
			\arrow[ddll]
			\arrow[r,"p_1"] &
		\Zpoly{1} = \mbb{Z}
			\arrow[ddlll,
				"\tau_1" near start] \\
		&& \colim F
			\arrow[d,dotted,"\exists! g" description]
		&&& \\
		&& R
		&&&
	\end{tikzcd}
	\label{eq:polynomial_ring_tower}
	\end{equation}
	Here $p_n\colon\Zpoly{n+1}\to\Zpoly{n}$ is the natural projection.

	Intuitively, if such $\lim F$ exists, it shall be the ``smallest'' object that ``contains'' $\Zpoly{n}$ when $n\to\infty$. Note that $\Zpoly{n}$ is naturally a $\mbb{Z}^n$ vector space:
	\begin{equation}
		\Zpoly{n}\ \ni\ \sum_{m=0}^{n-1} a_m x^m
		\ \sim\ \pqty{
			a_0, a_1, \cdots, a_{n-1}
		}\ \in\ \mbb{Z}^n
	\end{equation}
	While $n\to\infty$, this gives an $\infty$--tuple which corresponds to the \textit{formal power series}\footnote{
		See \wikiref{https://en.wikipedia.org/wiki/Formal\_power\_series}{Formal power series}. This is in fact the \textit{adic completion} of $\mbb{Z}[x]$. I would like to thank \mbox{\textit{刘逸华}} \& \textit{谢贤进} for this hint. 
	}: 
	\begin{equation}
		\mbb{Z}[[x]] \ \ni\ \sum_{m=0}^\infty
			a_m x^m
	\end{equation}

	The difference between $\mbb{Z}[x]$ and $\mbb{Z}[[x]]$ is that the latter may contain infinite series while the former may not. Now we confirm that, indeed, $\lim F = \mbb{Z}[[x]]$, along with natural projections $
		\pi_n\colon\mbb{Z}[[x]]\to\Zpoly{n}
	$.

	In fact, the $f\colon R\to \lim F$ in \eqref{eq:polynomial_ring_tower} can be explicitly written down as:
	\begin{equation}
	\begin{aligned}
		f &= \eta_1 + x\,\pqty{
			\dv{x}\,\eta_2
		} + x^2\,\pqty{
			\frac{1}{2}\,\dv{x}\,\eta_3
		} + \cdots
		= \sum_{m=0}^\infty x^m\,\Bqty{
			\frac{1}{m!}\,\dv[m]{x}\,\eta_{m+1}
		} \\
		&\sim \pqty\big{
			\eta_{1,0},\,
			\eta_{2,1},\,
			\cdots,\,
			\eta_{n,n-1},\,
			\cdots
		}
	\end{aligned}
	\end{equation}
	Here $\frac{1}{m!}\,\dv[m]{x}$ is used to extract the $a_{n-1}$ coefficient in $\Zpoly{n}$; this is the last component of $\eta_n$, denoted by $\eta_{n,n-1}$. Any other choice of $f$ will break communitativity of \eqref{eq:polynomial_ring_tower}, hence $f$ is fixed uniquely by $\mbb{Z}[[x]]$ and $\pi_n$'s. Therefore, $\lim F = \mbb{Z}[[x]]$. \qed

	On the other hand, $\colim F$ is the ``largest'' object that any map \textit{out of} $\Zpoly{n}$ must ``passes through''. Also, this should hold for all $n\in\mbb{Z}_+$. Naturally, projections $
		\sigma_n\colon\Zpoly{n}\to\mbb{Z}
	$ satisfy the above requirements; we have:
	\begin{gather}
		\sigma_n\colon\ x\longmapsto 0,\quad
			\sum_{m=0}^{n-1} a_m x^m
			\longmapsto a_0,\\
		\sigma_{n+1}
		= p_1\circ p_2\circ\cdots p_n
	\end{gather}
	$g\colon \mbb{Z}\to R$ in \eqref{eq:polynomial_ring_tower} is fixed uniquely for such choice of $\sigma_n$; in fact, descend along the $p_n$ tower in \eqref{eq:polynomial_ring_tower}, and we have: $
		\tau_{n+1}
		= \tau_n\circ p_n
		= \tau_{n-1}\circ p_{n-1}\circ p_n
		= \cdots
		= \tau_1\circ p_1\circ p_2\circ\cdots p_n
		= \tau_1\circ \sigma_{n+1},
		\ \forall\ n\in\mbb{Z}_+
	$, hence $\exists\,!\ g = \tau_1$. Therefore, $\colim F = \mbb{Z}$. \qed

	\item

	\end{enumerate}

	\legacyReference

	\begin{enumerate}
	\item For $F_i \to E_i \xrightarrow{p_i} B$: coverings in $\mop{Cov}_0(B)$ with $E_i$: connected and $B$: path connected and locally path connected, the following diagram commutes:
	\begin{center}
	\begin{tikzcd}[row sep=5ex,column sep=3em]
		E_1
			\arrow{rr}{f}
			\arrow[swap]{dr}{p_1} & &
		E_2
			\arrow{dl}{p_2} \\
		& B &
	\end{tikzcd}
	\quad
	$\begin{gathered}
%		p_1 = p_2 \circ f,\\
		e_2 = f(e_1),\\
		b = p_1(e_1) = p_2(e_2),
	\end{gathered}$
	\end{center}
	To show that $f$ is itself a covering, we need only verify that $f$ is locally trivial with some discrete fiber $F$. 
	In fact, given any $e_2\in E_2$ and $b = p_2(e_2)$, there exists some neighborhood $U\subset B$ that the following diagram holds (by restriction):
	\begin{center}
	\begin{tikzcd}[row sep=5ex,column sep=2.5em]
		U\times F_1
			\arrow{rr}{f}
			\arrow[swap]{dr}{p_1} & &
		U\times F_2
			\arrow{dl}{p_2} \\
		& U &
	\end{tikzcd}
	\quad
	$\begin{aligned}
		e_1 &= \pqty\big{b,k_1},\\
		e_2 &= \pqty\big{b,k_2(b,k_1)},
	\end{aligned}
	\quad k_i \in F_i
	$
	\end{center}

	Generally, $k_2 = k_2(b,k_1)$ depends on the base point $b \in B$. However, since $B$ is locally path connected, we can restrict $U$ to be path connected, while $k_2\in F_2$: discrete. Since continuous maps preserve path connectedness, $k_2$ is in fact independence of $b$, i.e.\ $k_2 = \varphi(k_1)$.

	On the other hand, $\forall\ e_2 = (b,k_2)\in U\times\{k_2\}\subset E_2$, we have its preimage $f^{-1}(e_2) = \{b\}\times\varphi^{-1}(k_2)$. Note that $E_2$ is connected while $\varphi^{-1}(k_2) \in F_1$ is discrete; for the same reasoning as above, $\varphi^{-1}(k_2) = F$ is in fact independent of $k_2$. This is the discrete fiber $F$ we have been looking for. Hence $f$ is also a covering map\footnote{
		Reference: \https{math.stackexchange.com/a/109774}. 
	}. \qedfull

	\item \textbf{Cylinder with ends pinched --- $\pi_1$ and universal cover:}
	\begin{equation}
		Y = \flatfrac{(X\times I)}{(X\times \pd I)},
		\quad I = [0,1]
	\end{equation}
	Note that $Y$ is homeomorphic to two cones\footnote{
		See discussions from Problem Set \textnumero 1. 
	} $CX_1\coprod CX_2$ with ``bases'' $X_i\subset CX_i$ and ``vertices'' $v_i$~respectively identified: $X_1\sim X_2,\ v_1\sim v_2\equiv v$. $X$ is path connected and so is $Y$, hence we are free to choose $\pi_1(Y) = \pi_1(Y,y_0)$.

	First note that paths that do \textit{not} pass through the vertex $v$ are all homotopic, since they are contained in a cone and cones are contractible\footnote{
		$[\gamma_1]
		= [\gamma_2\star\gamma_2^{-1}\star\gamma_1]
		= [\gamma_2]$. 
	}. Therefore all contributions to $\pi_1(Y)$ are loop classes that \textit{do} pass through the vertex $v$. 
	In other words, morphisms in $\Pi_1 Y$ are in one-to-one correspondence with morphisms in:
	\begin{equation}
		\Pi_1\pqty\big{[0,1]/_{0\sim 1}} = \Pi_1 S^1
	\end{equation}
	Therefore, $\pi_1(Y) \cong \pi_1(S^1) = \mbb{Z}$. 
	\qed

	The universal cover $\tilde{Y}$ of $Y$ can be constructed by assigning an induced topology to the space of path classes, same as in the general proof of its existence. Since $Y$ is ``degenerate'' at its vertex, this is equivalent to ``cutting open'' $Y$ at its vertex $v$, and joining $\mbb{Z}$ copies them end-to-end. More explicitly, it can be written as:
	\begin{equation}
		\tilde{Y} = {(X\times \mbb{R})}\Big/{
			\sim
		}\,,\quad
		(x,n)\sim (x',n),\ \forall\ 
			x\in X,\,n\in\mbb{Z}
	\end{equation}
	While the covering map: $\tilde{Y}\ni[x,t]\mapsto [x,t-\lfloor t\rfloor]\in Y$, here $\lfloor t\rfloor$ is the integer part of $t\in\mbb{R}$. 
	\qedfull

	\item \textbf{$\pi_1$ of fiber in fibration:}
	\label{item:fibration_fundamental}
	\begin{center}
	\begin{tikzcd}[row sep=8.5ex,column sep=7ex]
		X\times\{0\}
			\arrow[r]
			\arrow[hook,d] &
		E
			\arrow[d,"p"] \\
		X\times I
			\arrow[r,"f"]
			\arrow[ur,dashed,"\exists\,\tilde{f}"] &
		B
	\end{tikzcd}
	\end{center}

	For $F \to E \xrightarrow{p} B$: fibration, by homotopy lifting property (HLP), any homotopy in $B$ can be uniquely lifted to path class in $E$, provided some \textit{``initial condition''} $X\times\{0\}$. 
	This leads to the following results:

	\begin{enumerate}
	\item For $B$: simply-connected, take any loop class $[\tilde{\gamma}]\in\pi_1(E,e)$ as initial condition; its projection $[p\circ\tilde{\gamma}]\in\pi_1(B,b) = \Bqty\big{[\idty_b]}$ is trivial, i.e.\ $p\circ\tilde{\gamma} \simeq \idty_b$. By HLP, such homotopy can be lifted into $E$, i.e.
	\begin{equation}
		p\circ\tilde{\gamma} \simeq \idty_b
		\quad\xRightarrow{\ \text{lift}\,\ }\quad
		\tilde{\gamma} \simeq \tilde{\gamma}',\quad
		p\circ\tilde{\gamma}' = \idty_b
	\end{equation}
	In other words, $
		\tilde{\gamma}
		\simeq \tilde{\gamma}' \subset p^{-1}(b)
	$, i.e.\ any loop in $E$ is homotopic to some loop in $p^{-1}(b) \cong F$. This implies a surjective group homomorphism $
		\pi_1(p^{-1}(b),e)\to \pi_1(E,e)
	$, i.e.\ an epimorphism. 
	\qed

	\item For $E$: simply-connected, take any loop class $[\gamma]\in\pi_1(B,b)$ and consider its lifting $[\tilde{\gamma}]$. Note that in general $\tilde{\gamma}$ is \textit{not} a loop; however, we have $p\circ\tilde{\gamma} = \gamma$, hence $\tilde{\gamma}(0),\tilde{\gamma}(1)\in p^{-1}(b)$. In general, we have:
	\begin{equation}
		\gamma \simeq \gamma'
		\quad\xRightarrow{\ \text{lift}\,\ }\quad
		\tilde{\gamma} \simeq \tilde{\gamma}',\quad
		p\circ\tilde{\gamma}^{(\prime)}
		= \gamma^{(\prime)}
	\end{equation}
	By continuity, $\tilde{\gamma}(0),\tilde{\gamma}'(0)\in F_0$: a path component of $p^{-1}(b)$; similarly, $\tilde{\gamma}(1),\tilde{\gamma}'(1)\in F_1$. In other words, the start and end points of $\tilde{\gamma}$ are confined in path components $F_0$ and $F_1$, respectively. Hence a loop class in $\pi_1(B,b)$ maps to \textit{transport} between path components:
	\begin{equation}
	\begin{aligned}
		T_{(\cdot)}(e) \colon\ %
		\pi_1(B,b)
		&&&\longto &&
		\pi_0\pqty\big{p^{-1}(b)}\\[.5ex]
		[\gamma]
		&&&\longmapsto &&
		T_{[\gamma]}(e)
%		\colon\ %
%		\pi_0\pqty\big{p^{-1}(b)}
%		\longto \pi_0\pqty\big{p^{-1}(b)}
	\end{aligned}
	\end{equation}

	As a matter of fact, $T_{(\cdot)}(e)$ is a bijection. For $
		T_{[\gamma]} = T_{[\gamma']}
	$, they are characterized by two lifted paths $\tilde{\gamma},\tilde{\gamma}'$; since $E$ is simply connected, they are always homotopic: $
		\tilde{\gamma}\simeq\tilde{\gamma}'
	$, hence $
		[\gamma] = [\gamma']
	$ by projection $p$. This means that $T$ is injective. Surjectivity also follows from projection $\gamma = p\circ\gamma'$. Therefore, $T_{(\cdot)}(e)$ gives a bijection between $
		\pi_1(B,b)
	$ and $
		\pi_0\pqty\big{p^{-1}(b)}
	$. \qedfull

	\end{enumerate}

	\item \textbf{Pull-back of fibration is fibration:}
	\begin{center}
	\begin{tikzcd}[row sep=9ex,column sep=8ex]
		Y\times\{0\}
			\arrow[r]
			\arrow[d,hook] &[-1.2em]
		f^*(E)
			\arrow[r]
			\arrow[d] &
		E
			\arrow[d,"p"] \\
		Y\times I
			\arrow[r,"G"]
			\arrow[urr%
				,"\ \exists\,\tilde{F}\ %
					\text{(HLP)}"
				,swap
				,crossing over
			]
			\arrow[ur,dashed%
				,"\exists\,\tilde{G}"
			] &
		X
			\arrow[r,"f"] &
		B
	\end{tikzcd}\\[2ex]
	$
		(x,e) \in f^*(E)\subset X\times E,\quad
		f(x) = p(e)
	$
	\end{center}

	We need only verify that $f^*(E)\to X$ also has HLP, i.e.\ the existence of $\tilde{F}$ in the above diagram\footnote{
		Notice that $f^*(E)$ is the limit of the diagram, hence this is automatically true by the universal property of $f^*(E)$. I would like to thank \textit{刘逸华} for pointing this out. For now, we will stick to a more traditional proof. 
	}. By HLP of $
		E\xrightarrow{p} B,\ %
		\exists\ \tilde{F}\colon Y\times I \to E
	$ as shown above. We can use $\tilde{F}$ to construct $\tilde{G}$ explicitly; in fact, first consider:
	\begin{equation}
	\begin{aligned}
		\tilde{G} \colon\ %
		Y\times I
		&&&\longto &&
		X\times E\\
		(y,t)
		&&&\longmapsto &&
		\pqty\big{G(y,t),\tilde{F}(y,t)}
%		\colon\ %
%		\pi_0\pqty\big{p^{-1}(b)}
%		\longto \pi_0\pqty\big{p^{-1}(b)}
	\end{aligned}
	\end{equation}
	Note that $
		f\circ G = p\circ \tilde{F}
	$; compared with the definition of $f^*(E)$, this implies that the image of $\tilde{G}$ lies within $
		f^*(E)\subset X\times E
	$, hence after restriction of its codomain, $\tilde{G}$ becomes a well-defined lifting of $G$ into $f^*(E)$. Therefore, $f^*(E)\to X$ has HLP, i.e.\ it is also a fibration. \qedfull

	\item \textbf{More properties of fibration:}

	\begin{enumerate}

	\item By HLP, given any initial condition $e\in p^{-1}(b_1)$, lifting of any path $b_1\xrightarrow{\gamma} b_2$ exists. The lifted path with dependence of $e$ can then be written as $F\colon p^{-1}(b_1)\times I\to E$. 
	This is just a generalization of \ref{item:fibration_fundamental} for non-loop paths. 
	\qed

	\item Similarly, transport $T_{[\gamma]}$ defined in \ref{item:fibration_fundamental} can be generalized for non-loop paths. $T_{[\gamma]}$ is well-defined for path class $[\gamma]$, since by HLP homotopic paths can be lifted to homotopy in $E$. Therefore, the transport is fixed up to homotopy, i.e.
	\begin{equation}
	\begin{aligned}
		T \colon\ %
		\Hom_{\,\Pi_1 B} (b_0,b_1)
		&&&\longto &&
		\Hom_{\,\Cat{hTop}} \pqty\big{
			p^{-1}(b_0),p^{-1}(b_1)
		}
		\\[.5ex]
		[\gamma]
		&&&\longmapsto &&
		T_{[\gamma]}
	\end{aligned}
	\end{equation}
	Note that $T$ defined in this way is also independent of the choice of $F$, since $F$ simply specifies the starting point of the lifted path; no matter which $F$ we choose, the lifted paths will always be homotopic in $E$. Hence $T$ is well-defined in the above sense.
	\qed

	\item $T$ defined above is a functor: $
		\Pi_1 B\to \Cat{hTop}
	$. To verify this, we need only check that it is compatible with composition and maps identity morphisms to identity morphisms. Indeed, $
		T_{[\idty_b]} = [\idty_{p^{-1}(b)}]
	$, and $
		T_{[\gamma']\star[\gamma]}
		= T_{[\gamma'\star\gamma]}
		= T_{[\gamma']} \circ T_{[\gamma]}
	$ by joining two lifted paths (up to homotopy).
	\qed

	\item For $B$: path connected, there exists an isomorphism between any two objects in $\Pi_1 B$ (a path connecting any two points in $B$), which is mapped to isomorphisms between fibers $p^{-1}(b)$ in $\Cat{hTop}$. Hence any two fibers of $E\xrightarrow{p} B$ have the same homotopy type. 
	\qedfull

	\end{enumerate}
	\end{enumerate}

\printbibliography[%
%	title = {参考文献} %
	,heading = bibintoc
]
\end{document}

### 2020-03-18 AlgebraicTopology2020/algtop3/algtop3.tex
Update algtop3 & fix \Cat spacing

@@
 	\begin{equation}
-	\begin{tikzcd}[row sep=8.5ex,column sep=7ex]
+	\begin{tikzcd}[row sep=8.5ex,column sep=5ex]
 		& \Delta(\lim F)
@@
 		\ \forall\ n\in\mbb{Z}_+
-	$, hence $\exists\,!\ g = \tau_1$. Therefore, $\colim F = \mbb{Z}$. \qed
+	$, hence $\exists\,!\ g = \tau_1$. Therefore, $\colim F = \mbb{Z}$. \qedfull
+
+	\item \textbf{Example of push-out in \Cat{Groupoid}:}
+	\begin{equation}
+	\begin{tikzcd}[row sep=8.5ex,column sep=6.5ex]
+		\{0,1\}
+			\arrow[r,"f_1"]
+			\arrow[d,"f_2",swap] &
+		\bullet
+			\arrow[d,"\tau_1"]
+			\arrow[ddr,bend left,"\eta_1"] &[1ex] \\
+		\{ 0\leftrightarrow 1 \}
+			\arrow[r,"\tau_2"]
+			\arrow[drr,bend right,"\eta_2"] &
+		P
+			\arrow[dr,dotted
+				,"\!\!\exists!\,g" description]
+		& \\[-2.5ex]
+		&& Q
+	\end{tikzcd}
+	\end{equation}
+
+	Following the same observation as before, the push-out $P$ is the ``largest'' object that any map out of $\bullet$ and $\{0\leftrightarrow  1\}$ must pass through.
+By such universal property, $P$ can be no larger than the coproduct: $
+		\{\bullet\} \coprod \{0\leftrightarrow 1\}
+	$. However, we should also consider the equivalence imposed by: 
+	\begin{equation}
+		\bullet
+		\xlongleftarrow{\ f_1\,} \{0,1\}
+		\xlongrightarrow{\ f_2\ }
+		\{0\leftrightarrow 1\}
+	\end{equation}
+	Therefore, we simply have $P = \bullet$, with $\tau_{1,2}$ the natural projection.
+This can be verified with ease: we have $g = \eta_1$.
+It is unique since its image is a single point (with identity map to itself) $\star \in Q$, and the point $\star$ is fixed by commutativity.
+\qedfull
+
+	\item \textbf{Product and coproduct in \Cat{Ab}:}
+
+	For $G_\alpha\in\Cat{Ab}\subset\Cat{Group}$, note that we have:
+	\begin{equation}
+		\mop{Free}:
+			\Cat{Set}
+			\xrightleftharpoons{\quad}
+			\Cat{Group}
+		:\mop{Forget}
+	\label{eq:free_forget_adjoint}
+	\end{equation}
+	Therefore, for $F$: some diagram in \Cat{Group}, $
+		\boxed{\lim\,(\mop{Forget}\circ F)
+		= \mop{Forget}\circ\lim F}
+	$ if $\lim F$ exists.
+
+	By definition, the product $\prod_\alpha G_\alpha\in \Cat{Group}$ is a limit, hence it is idential (as in $\Cat{Set}\mspace{.2mu}$) to the \textit{direct product}, with additional entry-wise group multiplication.
+Same applies for the full subcategory: abelian group $\Cat{Ab}\subset\Cat{Group}$.
+
+	On the other hand, the disjoint union of $G_\alpha$'s as sets will not necessary be a group, the identities $\idty_\alpha\in G_\alpha$ must be glued together to produce a group structure.
+Furthermore, free-forgetful adjunction \eqref{eq:free_forget_adjoint} implies that for $F'$: some diagram in \Cat{Set},
+	\begin{equation}
+		\colim\,(\mop{Free}\circ F')
+		= \mop{Free}\circ\colim F',\quad
+	\end{equation}
+	Whenever $\colim F'$ exists; in our case, $\colim F'$ is the disjoint union of sets: $
+		\coprod_\alpha \mop{Forget}(G_\alpha)
+	$. Therefore, we should construct a free object in \Cat{Ab}.
+
+	Here we restrict our discussion to \Cat{Ab}, since the coproduct in $\Cat{Ab}$ is \textit{not} the same as in $\Cat{Group}$ --- the free product of abelian group is not necessary abelian.
+Hence, the coproduct in \Cat{Ab} shall be:
+	\begin{equation}
+		\coprod_\alpha G_\alpha
+		= \bigoplus_\alpha G_\alpha,\quad
+		i_\alpha\colon\, G_\alpha
+			\ \xhookrightarrow{\quad}\ %
+			\bigoplus_\alpha G_\alpha
+	\end{equation}
+	As a set, this is precisely the disjoint union with identities $0_\alpha \in G_\alpha \subset \Cat{Ab}$ glued together.
+
+	It is then straight-forward to verify its universal property: for $f_\alpha\colon G_\alpha\to H$,
+	\begin{equation}
+		\exists\,!\ f\colon\,%
+			\bigoplus_\alpha G_\alpha
+			\ \longto\ H,\quad
+		(g_\alpha)_\alpha
+			\ \longmapsto\ %
+			\sum_\alpha f_\alpha(g_\alpha)
+	\end{equation}
+	This is compatible with the abelian group multiplication.
+Note that for the summation to be well-defined, the coproduct must only contain finitely many components; otherwise it is identical to the product in \Cat{Ab}.
+	\qedfull
 

### 2020-03-19 release.sh
Update tagging strategy: use `latest` for CI

@@ -1,0 +1,4 @@
+#!/bin/bash
+
+git tag --force latest
+git push --force --tags

### 2020-03-23 Strings2020/strings1/strings1.tex
Finalize strings2, update advqft2

@@
 	} of $K(a)$:
-	\begin{equation}
+	\begin{gather}
 		\tilde{x}^\mu
@@
 		\label{eq:special_conformal_simplified}
-	\end{equation}
+	\end{gather}
 
 	From \eqref{eq:special_conformal_simplified}, we see that the transformation parameter $a^\mu$ composes linearly: $K(b)\,K(a) = K(a+b)$, therefore $K^{-1}(a) = K(-a)$, and we have:
-	\begin{equation}
+	\begin{gather}
 		x^\mu = K(-a)\,\tilde{x}^\mu
@@
 	\end{aligned}
-	\end{equation}
+	\end{gather}
 	We see that $g_{\alpha\beta} = f(x)\,\delta_{\alpha\beta}$, with coefficient:
@@
 	$. For convenience, let's first consider a generic variation $\var{z} = \epsilon(z,\bar{z})$ before restricting to spacetime translation; we have:
-	\begin{equation}
+	\begin{gather}
 		\phi'(z',\bar{z}')
@@
 		\label{eq:var_field_compact_supp}
-	\end{equation}
+	\end{gather}
 	Here we use $\tilde{\delta}\phi$ to denote the ``internal'' variation related to the conformal weights.
@@
 	Note that $\phi = b,c$ are anti-commuting Grassmann numbers, variation of the action gives:
-	\begin{equation}
-	\begin{aligned}
+	\begin{align}
 		\var{S}[b,c,\var{b},\var{c}]
@@
 			+ b\,\pdbar \var{c}
-		} \\
+		} \notag\\
 		&= \frac{1}{2\pi} \int \dd[2]{z} \pqty{
@@
 			\pdbar \pqty{b\var{c}}
-	\end{aligned}
 		\label{eq:bc_action_var}
-	\end{equation}
+	\end{align}
 	For \textit{unknown} $b,c$ and {arbitary} $\var{b},\var{c}$, the second term is reduced to a boundary term at infinity and can be dropped; imposing $\var{S} = 0$ gives the equation of motion (EOM): $\pdbar b = \pdbar c = 0$.
 
-	On the other hand, for \textit{on-shell} $b,c$ and compactly supported $\varphi = \var{b},\var{c}$ given in \eqref{eq:var_field_compact_supp}, the first term in \eqref{eq:bc_action_var} vanishes while $\var{S}_0 = 0$ still holds; this gives:
+	On the other hand, for \textit{on-shell} $b,c$ and compactly supported $\phi = \var{b},\var{c}$ given in \eqref{eq:var_field_compact_supp}, the first term in \eqref{eq:bc_action_var} vanishes while $\var{S}_0 = 0$ still holds; this gives:
 	\begin{equation}
@@
 	Taking $\phi,\psi=b,c$, this generates operator equations such as $
-		\pdbar b(z)\,c(0)
+		\pdbar\,b(z)c(0)
 		= 2\pi\delta^2(z,\bar{z})
@@
 	$ contraction gives $\frac{\delta^j_i}{z-w}$, we have:
-	\begin{equation}
+	\begin{gather}
 		J\id{_i^j}(z)\,J\id{_k^l}(0)
@@
 			- \delta_k^j\,(J\id{_i^l})_0
-	\end{equation}
+	\end{gather}
 
@@
 	Similar holds for $J_{ij} = \normorder{\psi_i\psi_j}$ and its OPE, but we no longer need to distinguish upper/lower indices; we have:
-	\begin{equation}
+	\begin{gather}
 		J_{ij}(z)\,J_{kl}(0)
@@
 			- \delta_{jl} (J_{ik})_0
-	\end{equation}
+	\end{gather}
 	This is precisely the $\mfrak{o}(n)$ algebra. 

### 2020-03-23 Strings2020/strings2/strings2.tex
Finalize strings2, update advqft2

@@
 
-\newcommand{\hwNumber}{2 [WIP]}
+\newcommand{\hwNumber}{2}
 
@@
 \newcommand{\Vir}{\mathbf{V}\mfrak{ir}}
-\usepackage{cancel}
 
@@
 %}
+
 	\begin{enumerate}
@@
 		S = S^X + S^{bc},\\
-		S^X = - \frac{1}{2\pi\alpha'} \int\dd[2]{z}
+		S^X = \frac{1}{2\pi\alpha'} \int\dd[2]{z}
 			\pd X^\mu \pdbar X_\mu,\quad
@@
 	\end{gather}
-	This is the gauge fixed action. The corresponding BRST transformation is listed in \textit{Polchinski}; for each of the subsystems, we have its (classical) energy-momentum:
-	\begin{equation}
+	This is the gauge fixed action. The corresponding BRST transformation is listed in \textit{Polchinski}; for each of the subsystems, we have its energy-momentum:
+	\begin{gather}
 		T^X(z)
@@
 		}),
-	\end{equation}
+	\end{gather}
 
@@
 	$, and we have moved $\pdbar\epsilon$ to the beginning of the expression, while respecting the anti-commuting nature of $\epsilon$.
-With a conventional $i$ coefficent (which agrees with the convention of $j^X$), we have $bc$'s contribution to the conserved current:
+With a conventional $i$ coefficient (which agrees with the convention of $j^X$), we have $bc$'s contribution to the conserved current:
 	\begin{equation}
@@
 	\end{equation}
+	\vspace*{-1.5\baselineskip}
+
+	\qed
 
@@
 		T(z)\,j(0)
-		\sim \eqref{eq:BRST_Tj_OPE_partI}
+		\sim \pqty\big{
+			\eqref{eq:BRST_Tj_OPE_partI}
 			+ \eqref{eq:BRST_Tj_OPE_partII}
 			+ \eqref{eq:BRST_Tj_OPE_partIII}
+		}
 		\sim \frac{D-8}{2z^4}\,c(0)
@@
 	\end{aligned}
+	\label{eq:BRST_Td2c_OPE}
 	\end{equation}
@@
 			+ \frac{3}{2}\,\pd^2 c(z),\quad
-		j(z) = j^X + j^{bc}
+		j(z) = cT^X + \normorder{bc\,\pd c}
 			+ \frac{3}{2}\,\pd^2 c,\\[1ex]
@@
 	We see that $j(z)$ defined in this way is a primary of weight $(1,0)$ in $D = 26$. This is the quantum BRST current. 
-	\qedfull
+	\qed
 
@@
 
-	\item
+	\item For $jj$ OPE, we have:
+	\begin{gather}
+		j = cT^X + j',\quad
+		j' \equiv j^{bc}
+			+ \frac{3}{2}\,\pd^2 c,\quad
+		j^{bc}
+		= \frac{1}{2}\normorder{cT^{bc}}
+		= \normorder{bc\,\pd c}\,,\\[1ex]
+%		
+%		j = \frac{1}{2}\,cT^X
+%			+ \frac{1}{2}\,\normorder{cT}
+%			+ \frac{3}{2}\,\pd^2 c,\\
+%
+	\begin{aligned}
+		j_z j_0
+		&\sim \normorder{\Bqty{T^X_z T^X_0}\,c_z c_0}
+			+ \normorder{\Bqty{c_z j'_0}\,T^X_z}
+			+ \normorder{\Bqty{j'_z c_0}\,T^X_0}
+			+ {j'_z j'_0} \\[.5ex]
+		&\sim \normorder{\Bqty{T^X_z T^X_0}\,c_z c_0}
+			+ \normorder{\Bqty{c_z j^{bc}_0}\,T^X_z}
+			+ \normorder{\Bqty{j^{bc}_z c_0}\,T^X_0}
+			+ {j'_z j'_0}\,,
+	\end{aligned}
+	\end{gather}
+	From now on, for convenience and clarity, we will use subscripts to denote variable dependence: $c_z = c(z)$. Let's compute this term by term. We have:
+	\begin{align}
+		\normorder{\Bqty{T^X_z T^X_0}\,c_z c_0}
+		&\sim \normorder{\pqty{
+			\frac{D}{2z^4}
+			+ \frac{2}{z^2}\,{T^X_0}
+			+ \frac{1}{z}\,{\pd T^X_0}
+		}\pqty{
+			z\,\pd c_0
+			+ \frac{z^2}{2}\,\pd^2 c_0
+			+ \frac{z^3}{6}\,\pd^3 c_0
+		} c_0} \notag\\
+		&\sim -\pqty{
+			\frac{D}{2z^3}\,c\,\pd c_0
+			+ \frac{D}{4z^2}\,c\,\pd^2 c_0
+			+ \frac{D}{12z}\,c\,\pd^3 c_0
+			+ \frac{2}{z}\,\normorder{T^X c\,\pd c_0}
+		}, 
+		\label{eq:BRST_TTcc_OPE} \\[2ex]
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%		jc OPE ...
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+		j^{bc}_z c_0
+		&\sim \frac{1}{2}\,
+			\normorder{cT^{bc}}_{\,z}\,c_0
+		\sim \frac{1}{2}\,c_z \Bqty{
+			\normorder{T^{bc}}_{\,z}\,c_0
+		}
+		\sim \frac{1}{2}\,c_z \Bqty{
+			T_z\,c_0
+		} \notag\\
+		&\sim -\frac{1}{2}\,\pqty{
+			\frac{-1}{z^2}\,c_0
+			+ \frac{1}{z}\,\pd c_0
+		}\pqty\big{
+			c_0 + z\,\pd c_0
+		} \sim 0, \\
+		j^{bc}_0 c_z
+		&\sim 0,
+	\end{align}
+	\begin{equation}
+	\begin{aligned}
+		j'_z j'_0
+		&\sim j^{bc}_z j^{bc}_0
+			+ \frac{3}{2}\,j^{bc}_z\,\pd^2 c_0
+			+ \frac{3}{2}\,\pd^2 c_z\,j^{bc}_0 \\
+		&\sim \frac{1}{2}\,
+			\normorder{cT^{bc}}_{\,z}\,j^{bc}_0
+		+ \frac{3}{2}\,\pqty{
+			j^{bc}_z\,\pd^2 c_0
+			+ \pd^2 c_z\,j^{bc}_0
+		},
+	\end{aligned}
+	\end{equation}
+
+	The task is now reduced to calculating terms in the above $j'j'$ OPE, which can be laboriously computed following a similar procedure as before. Note that there will be a $
+		\frac{1}{z}\,\normorder{cT^{bc}}\,\pd c_0
+	$ term which combines with the $
+		\frac{2}{z}\,\normorder{cT^{X}}\,\pd c_0
+	$ term in \eqref{eq:BRST_TTcc_OPE}. In total, we obtain the final $jj$ OPE:
+	\begin{equation}
+		j_z j_0
+		\sim - \frac{D-18}{2z^3}\,c\,\pd c_0
+			- \frac{D-18}{4z^2}\,c\,\pd^2 c_0
+			- \frac{D-26}{12z}\,c\,\pd^3 c_0
+	\end{equation}
+
+%	For the first term, we have:
+%	\begin{equation}
+%	\begin{aligned}
+%		\normorder{cT^{bc}}_{\,z}\,j^{bc}_0
+%		&\sim \normorder{\wick{
+%			\c1 c T^{bc}_z \c1 j^{bc}_0
+%		}} + \normorder{\wick{
+%			c \c1 T^{bc}_z \c1 j^{bc}_0
+%		}} + \normorder{\wick{
+%			\bcontraction[1.1ex]{c}{T}{^{bc}_z}{j}
+%			\c1 c T^{bc}_z \c1 j^{bc}_0
+%		}} \\[.5ex]
+%		&\sim \frac{1}{z}\,(+1)\,\normorder{
+%			T^{bc}_z c\,\pd c_0
+%		} + \normorder{c_z \Bqty{
+%			\eqref{eq:BRST_Tj_OPE_partIII}
+%		}} + \frac{1}{z}\,\normorder{\pqty\Big{
+%			\Bqty{T^{bc}_z c_0}\,\pd c_0
+%			+ (+1)\,
+%				c_0\,\Bqty{T^{bc}_z\,\pd c_0}
+%		}} \\
+%		&\sim \frac{1}{z}\,\normorder{
+%			T^{bc} c\,\pd c_0
+%		} + \normorder{c_z \Bqty{
+%			\eqref{eq:BRST_Tj_OPE_partIII}
+%		}} + \frac{1}{z}\,\normorder{\pqty\Big{
+%			\Bqty{T^{bc}_z c_0}\,\pd c_0
+%			+ c_0\,\Bqty{T^{bc}_z\,\pd c_0}
+%		}}
+%	\end{aligned}
+%	\end{equation}
+%	Here we've used the fact that there is only one $b$ in $T^{bc}$, hence all non-singular are accounted for in the above expression.
+Note again that $c$ is primary; similar to \eqref{eq:BRST_Td2c_OPE}, we have:
+%	\begin{equation}
+%	\begin{aligned}
+%		\normorder{cT^{bc}}_{\,z}\,j^{bc}_0
+%		&\sim \normorder{\pqty{
+%			c_0 + z\,\pd c_0
+%			+ \frac{z^2}{2}\,\pd^2 c_0
+%			+ \frac{z^3}{6}\,\pd^3 c_0
+%		} \pqty{
+%			\frac{-4}{z^4}\,c_0
+%			+ \frac{3}{z^3}\,\pd c_0
+%			+ \frac{1}{z^2}\,j^{bc}_0
+%			+ \frac{1}{z}\,\pd j^{bc}_0,
+%		}} \\
+%		&\qquad + \frac{1}{z}\,\pqty{
+%			\frac{-1}{z^2}\,c\,\pd c_0
+%			+ c_0\cdot\frac{1}{z}\,\pd^2 c_0
+%		} \\
+%		&\sim \frac{3+4-1}{z^3}\,c\,\pd c_0
+%			+ \frac{4/2+1}{z^2}\,c\,\pd^2 c_0
+%			+ \frac{4/6}{z}\,c\,\pd^3 c_0 \\
+%	\end{aligned}
+%	\end{equation}
+%	
+%	
+%	\begin{align}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%		ANOTHER OPE ...
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%		j^{bc}_z\,\pd^2 c_0
+%		&\sim \frac{1}{2}\,c_z\,\Bqty{
+%			T^{bc}_z\,\pd^2 c_0
+%		} \\
+%		\sim\eqref{eq:BRST_Td2c_OPE}
+%		&\sim \frac{1}{2}\,c_z\,\pqty{
+%			\frac{-6}{z^4}\,c_0
+%			+ \frac{-2}{z^3}\,\pd c_0
+%			+ \frac{1}{z^2}\,\pd^2 c_0
+%			+ \frac{1}{z}\,\pd^3 c_0
+%		} \\
+%		\sim (\textsl{Taylor})
+%		&\sim \frac{1}{2}\,\pqty{
+%			\frac{6-2}{z^3}\,
+%				c_0\,\pd c_0
+%			+ \frac{6/2+1}{z^2}\,
+%				c_0\,\pd^2 c_0
+%			+ \frac{6/6+1}{z}\,
+%				c_0\,\pd^3 c_0
+%		} \\
+%		&\sim \frac{1}{2}\,\pqty{
+%			\frac{4}{z^3}\,
+%				c_0\,\pd c_0
+%			+ \frac{4}{z^2}\,
+%				c_0\,\pd^2 c_0
+%			+ \frac{2}{z}\,
+%				c_0\,\pd^3 c_0
+%		} \\[2ex]
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%		ANOTHER OPE ...
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%		\pd^2 c_z\,j^{bc}_0
+%		&\sim -j^{bc}_0\,\pd^2 c_z \\
+%		&\sim - \frac{1}{2}\,c_0\,\Bqty{
+%			T^{bc}_0\,\pd^2 c_z
+%		} \\
+%		\sim\eqref{eq:BRST_Td2c_OPE}
+%		&\sim -\frac{1}{2}\,c_0\,\pqty{
+%			\frac{-2}{(-z)^3}\,\pd c_z
+%			+ \frac{1}{(-z)^2}\,\pd^2 c_z
+%			+ \frac{1}{-z}\,\pd^3 c_z
+%		} \\
+%		&\sim -\frac{1}{2}\,c_0\,\pqty{
+%			\frac{2}{z^3}\,\pd c_z
+%			+ \frac{1}{z^2}\,\pd^2 c_z
+%			+ \frac{-1}{z}\,\pd^3 c_z
+%		} \\
+%		\sim (\textsl{Taylor})
+%		&\sim -\frac{1}{2}\,\pqty{
+%			\frac{2}{z^3}\,c_0\,\pd c_0
+%			+ \frac{1+2}{z^2}\,c_0\,\pd^2 c_0
+%			+ \frac{-1+1+1}{z}\,c_0\,\pd^3 c_0
+%		} \\
+%		&\sim -\frac{1}{2}\,\pqty{
+%			\frac{2}{z^3}\,c_0\,\pd c_0
+%			+ \frac{3}{z^2}\,c_0\,\pd^2 c_0
+%			+ \frac{1}{z}\,c_0\,\pd^3 c_0
+%		} \\[1ex]
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%		\frac{3}{2}\,\pqty{
+%			j^{bc}_z\,\pd^2 c_0
+%			+ \pd^2 c_z\,j^{bc}_0
+%		} &\sim \frac{3}{4}\,\pqty{
+%			\frac{2}{z^3}\,c_0\,\pd c_0
+%			+ \frac{1}{z^2}\,c_0\,\pd^2 c_0
+%			+ \frac{1}{z}\,c_0\,\pd^3 c_0
+%		}
+%	\end{align}
+
+	\item Following the convention of \textit{Polchinski}, expand $X^\mu,b,c$ into modes $\alpha^\mu_n,b_n,c_n$, then a generic level 2 state of an open string can be created as\footnote{
+		Reference: Bram M.~Wouters, \href{https://esc.fnwi.uva.nl/thesis/centraal/files/f1989820784.pdf}{\textit{BRST quantization and string theory spectra}}. 
+	}:
+	\begin{equation}
+	\begin{aligned}
+		\ket{\psi} = \big(
+			&e_{\mu\nu}
+				\alpha^\mu_{-1}
+				\alpha^\nu_{-1}
+			+ \beta_\mu
+				\alpha^\mu_{-1} b_{-1}
+			+ \gamma_\mu
+				\alpha^\mu_{-1} c_{-1}
+			\\ &\qquad
+			+ \eta\,b_{-1} c_{-1}
+			+ e_\mu \alpha^\mu_{-2}
+			+ \beta\,b_{-2}
+			+ \gamma\,c_{-2}
+		\big)\,\ket{k;0}
+	\end{aligned}
+	\end{equation}
+	Here $e_{\mu\nu}$ is chosen to be symmetric since $
+		\alpha^\mu_{-1}
+		\alpha^\nu_{-1}
+	$ commutes. 
+	By acting on $L_0$ (expanded in modes), we find that $
+		m^2 = -k^2 = \frac{1}{\alpha'}
+	$: massive.
+
+	The BRST charge $
+		Q = \frac{1}{2\pi i} \oint \pqty{
+			\dd{z} j(z)
+			- \dd{\bar{z}} \tilde{j}(z)
+		}
+	$ can also be expanded in modes; the physical states are firstly, $Q$-closed; i.e.
+	\begin{equation}
+		Q_B \ket{\psi} = 0
+		\ \Longrightarrow\ %
+		k^\mu e_{\mu\nu} = 0,\quad
+		k^\mu e_\mu = 0,\quad
+		\beta_\mu = \beta = 0,
+	\end{equation}
+	This is also the negative-norm states.
+
+	On the other hand, $Q$-exact states generate gauge transformations; this gives:
+	\begin{equation}
+		\gamma_\nu
+		\mapsto \gamma_\nu + k^\mu e_{\mu\nu},\quad
+		\gamma
+		\mapsto \gamma + k^\mu e_{\mu},\quad
+		e_{\mu\nu}
+		\mapsto e_{\mu\nu}
+			+ \beta_\mu k_\nu
+			+ \beta_\nu k_\mu,\quad
+		e_\mu
+		\mapsto e_\mu + \beta k_\mu
+	\end{equation}
+	Here $e_{\mu\nu},e_\mu,\beta_\mu,\beta$ are seen as arbitrary gauge parameters.
+For closed string the result can be obtained by the doubling trick, i.e.\ by introducing anti-holomorphic modes $\tilde{\alpha},\tilde{b},\tilde{c}$ and imposing reality conditions.
+The result is similar.
+\qedfull
 
@@
 
-	\clearpage
-
-	\quad
-	\vfill\pagebreak
-
-	\item \textbf{Spinning Closed String in AdS Space}:
-
-	For a classical spinning string, we have Nambu--Goto action:
-	\begin{equation}
-		S_{NG}
-		= -T \int \dd{\tau} \dd{\sigma}
-			\sqrt{-\det \gamma_{ab}},\quad
-		\gamma_{ab} = G_{\mu\nu}
-			\pdd{a}X^\mu \pdd{b}X^\nu
-	\end{equation}
-	Here $G_{\mu\nu}$ is the spacetime metric. $\gamma_{ab}$ can be treated as the induced metric on the worldsheet.
-
-	In AdS space we have:
-	\begin{equation}
-		ds^2
-		= R^2\pqty{
-			- \sqcosh\rho \dd{t}^2
-			+ \dd{\rho}^2
-			+ \sqsinh\rho \dd{\Omega}^2
-		}
-	\end{equation}
-	Where $\dd{\Omega}^2$ is the metric of a unit $(d-2)$--sphere $S^{d-2}$.
-For convenience let's define unit $S^{d-2}$ metric $G^1_{ij}$, and raise or lower the $i,j,\cdots$ indices using $G^1_{ij}$ instead of $G_{ij}$, i.e.,
-	\begin{equation}
-		G^1_{ij} = G_{ij} /\,\pqty{
-			R^2 \sqsinh\rho
-		},\quad
-		i,j = 2,\cdots,d-1
-	\end{equation}
-
-	Furthermore, we consider the special case that the closed string is \textit{folded}, like a rubber band stretched along a line; in this case we can choose the worldsheet parameter $(\tau,\sigma) = (t,\rho)$ while $\Omega = \Omega(t,\rho) = \Omega(\tau,\sigma)$, which leads to the following decomposition:
-	\begin{align}
-		\pdd{a} X^\mu
-		&= \delta^\mu_a + \delta^\mu_i\,
-			\pdd{a}\Omega^i,\quad
-			a = 0,1,\quad
-			i = 2,\cdots,d-1,\\[.5ex]
-		\gamma_{ab}
-		&= G_{\mu\nu}\,
-			\pdd{a}X^\mu \pdd{b}X^\nu
-		\notag\\
-		&= G_{ab} + G_{ij}\,
-			\pdd{a}\Omega^i\,\pdd{b}\Omega^j
-		\notag\\
-		&= G_{ab} + R^2\sqsinh\rho\,G^1_{ij}\,
-			\pdd{a}\Omega^i\,\pdd{b}\Omega^j
-		\notag\\
-		&= R^2\Bqty{\mat{
-			-\sqcosh\rho & \\
-			& 1 \\
-		} + \sqsinh\rho\,\mat{
-			(\pdd{a}\Omega)^2 &
-			\pdd{a}\Omega\cdot\pdd{b}\Omega \\
-			\pdd{b}\Omega\cdot\pdd{a}\Omega &
-			(\pdd{b}\Omega)^2 \\
-		}}
-%		\notag\\
-%		&= R^2\,\sqsinh\rho\,\Bqty{\mat{
-%			-\oppower{\coth}{2}\rho & \\
-%			& \oppower{\csch}{2}\rho \\
-%		} + \,\mat{
-%			(\pdd{a}\Omega)^2 &
-%			\pdd{a}\Omega\cdot\pdd{b}\Omega \\
-%			\pdd{b}\Omega\cdot\pdd{a}\Omega &
-%			(\pdd{b}\Omega)^2 \\
-%		}}
-	\end{align}
-	Here $
-		\pdd{a}\Omega\cdot\pdd{b}\Omega
-		\equiv \pdd{a}\Omega^i\,\pdd{b}\Omega_i
-		\equiv G^1_{ij}\,
-			\pdd{a}\Omega^i\,\pdd{b}\Omega^j
-	$, and we have:
+	For $z\mapsto z + \epsilon(z)$, we have:
+	\begin{equation}
+		\var{X^\mu}
+		= - \epsilon\pd X^\mu
+			- \bar{\epsilon}\pdbar X^\mu
+			- \frac{\alpha'V^\mu}{2}\,\pqty{
+				\pd\epsilon
+				+ \pdbar\bar{\epsilon}
+			}
+	\end{equation}
+	Note that the $\alpha'$ term has no dependence on $X$.
+
+	\begin{enumerate}
+	\item For simplicity, assume for now $X = X(z)$: holomorphic. Note that the $\alpha'$ term comes from the transformation of \textit{internal} degrees of freedom. We have:
+	\begin{gather}
+		X'(z') - X(z)
+		= -\frac{\alpha' V}{2}\,\pd\epsilon
+			+ \order{\epsilon^2},
+%		\simeq -\frac{\alpha' V}{2}\,\pqty{
+%			\dv{z'}{z} - 1
+%		},\\[.5ex]
+%		X'(z') - \frac{\alpha' V}{2}
+%		\simeq X(z) - \frac{\alpha' V}{2}\,
+%			\dv{z'}{z},
+%		\\[1ex]
+%		X'(z')
+%		\simeq X(z) + \frac{\alpha' V}{2}\,\pqty{
+%				1 - \pd w + \order{\pd w}^2
+%			},
+		\label{eq:dilaton_holomorphic}
+	\end{gather}
+	This is a first order approximation of the finite transformation $z\mapsto z' = w(z)$.
+
+	To obtain a full expression, notice that for the above transformation to be a \textit{symmetry}, the action should be invariant under $X(z)\mapsto X'(z)$:
+	\begin{equation}
+		S' = S
+		\propto \int \dd[2]{z}
+			\pd X^\mu \pdbar X_\mu
+		= \int \dd[2]{z'}
+			\pd' X'^\mu \pdbar' X'_\mu
+%		= \int \dd[2]{z'}
+%			\pd' X'^\mu \pdbar' X'_\mu (z',\bar{z}')
+	\end{equation}
+	Restore the anti-holomorphic component and insert \eqref{eq:dilaton_holomorphic}, then we find that in order to cancel the $\order{\epsilon^2}$ terms, we have to fix:
+%	\begin{gather}
+%		X'(z',\bar{z}') - \alpha'V
+%		\simeq X(z,\bar{z})
+%			- \frac{\alpha' V}{2}\,\pqty{
+%				\dv{z'}{z} + \dv{\bar{z}'}{\bar{z}}
+%			},\\[1ex]
+%		X\longmapsto
+%		X'(z,\bar{z})
+%		\simeq X\pqty\Big{
+%				w^{-1}(z),\bar{w}^{-1}(\bar{z})
+%			} + \alpha'V
+%			- \frac{\alpha' V}{2}\,\pqty{
+%				\dv{w}{z} + \dv{\bar{w}}{\bar{z}}
+%			},
+%	\end{gather}
+	\begin{equation}
+		X'(z') - X(z)
+		= -\frac{\alpha' V}{2}\,\pqty{
+			\pd\epsilon
+			- \frac{1}{2}\,(\pd\epsilon)^2
+			+ \order{\epsilon^3}
+		}
+	\end{equation}
+	The above process can be done order by order, in the end we obtain that\footnote{
+		I would like to thank Lucy Smith for helpful discussions. 
+	}:
 	\begin{equation}
 	\begin{aligned}
-		\det \gamma_{ab}
-		&= (R^2)^2\,\Big\{
-			\oppower{\sinh}{4}\rho\,
-			\det\,(\pdd{a}\Omega^i\pdd{b}\Omega_i)
-		\\
-		&\qquad\qquad\qquad
-			+ \oppower{\sinh}{2}\rho\,\pqty{
-				(\pdd{a}\Omega)^2
-				- (\pdd{b}\Omega)^2
-				\oppower{\cosh}{2}\rho
-			}
-		\\
-		&\qquad\qquad\qquad
-			- \oppower{\cosh}{2}\rho\,
-		\Big\},\\[.5ex]
-		\sqrt{-\det \gamma_{ab}}
-		&= R^2\,\Big\{
-			\oppower{\cosh}{2}\rho
-			- \oppower{\sinh}{2}\rho\,\pqty{
-				(\pdd{a}\Omega)^2
-				- (\pdd{b}\Omega)^2
-				\oppower{\cosh}{2}\rho
-			}
-		\\[-.5ex]
-		&\qquad\qquad\quad
-			- \oppower{\sinh}{4}\rho\,
-			\det\,(\pdd{a}\Omega^i\pdd{b}\Omega_i)
-		\Big\}^{\!1/2}
+		X'(z',\bar{z}') - X(z,\bar{z})
+		&= -\frac{\alpha' V}{2}\,\pqty{
+			\pd\epsilon
+			- \frac{1}{2}\,(\pd\epsilon)^2
+			+ \frac{1}{3}\,(\pd\epsilon)^2
+			- \cdots
+		} + \pqty{\mrm{conjugate}} \\
+		&= -\frac{\alpha' V}{2}\,
+			\ln (1 + \pd\epsilon)
+		+ \pqty{\mrm{conjugate}} \\[.5ex]
+		&= -\frac{\alpha' V}{2}\,
+			\ln \pqty{
+				\dv{z'}{z}
+				\dv{\bar{z}'}{\bar{z}}
+			}
 	\end{aligned}
@@
 
-	Mark the end points of the string with $\rho = r(t)$, then the total length of such closed folded string is $\ell = 4r$. We then have:
-	\begin{equation}
-		S = -4TR^2 \int\dd{t} \int_0^r \dd{\rho}
-		\sqrt{
-			\oppower{\cosh}{2}\rho
-			- \oppower{\sinh}{2}\rho\,\pqty{
-				(\pdd{a}\Omega)^2
-				- (\pdd{b}\Omega)^2
-				\oppower{\cosh}{2}\rho
-			}
-			- \oppower{\sinh}{4}\rho\,
-			\det\,(\pdd{a}\Omega^i\pdd{b}\Omega_i)
-		}
-	\end{equation}
+	\item Perform the usual Noether's procedure on the free boson action, and we have:
+	\begin{equation}
+		\var{\mcal{L}}
+		\propto \frac{1}{\alpha'} \pqty{
+				\pd \var{X}^\mu \pdbar X_\mu
+				+ \pd X^\mu \pdbar \var{X}_\mu
+			}
+		\sim \pdbar \epsilon \pqty{
+			V^\mu \pd^2 X^\mu
+			- \frac{1}{\alpha'}
+				\pd X^\mu \pdbar X_\mu
+		}
+	\end{equation}
+	Here we've plugged in the holomorphic part of $\var{X}^\mu$, used integration by parts to move $\pdbar$ before $\epsilon$, and collected the $\pdbar\epsilon$ coefficients. This gives:
+	\begin{equation}
+		T(z) = - \frac{1}{\alpha'}\,\normorder{
+				\pd X^\mu \pdbar X_\mu\!
+			} + V^\mu \pd^2 X^\mu
+	\end{equation}
+
+	With $
+		X^\mu_z X^\nu_0
+		\sim -\frac{\alpha'}{2}\,\eta^{\mu\nu}
+			\ln \abs{z}^2
+	$ unchanged, the $TT$ OPE can be calculated following the usual procedure, as shown in great detail before. Here we can use the known result from free boson theory to speed up our calculation:
+	\begin{equation}
+	\begin{aligned}
+		T_z T_0
+		&\sim \pqty{
+				V_\mu \pd^2 X^\mu + T'
+			}_{\!z}\,\pqty{
+				V_\mu \pd^2 X^\mu + T'
+			}_{\!0} \\
+		&\sim V_\mu V_\nu\,
+				\pd^2 X^\mu_z\,\pd^2 X^\nu_0
+			+ V_\mu\,\pd^2 X^\mu_z\,T'_0
+			+ V_\mu T'_z\,\pd^2 X^\mu_0
+			+ T'_z\,T'_0
+	\end{aligned}
+	\end{equation}
+	Here $T'$ is the usual free boson stress tensor. Combining all terms yields:
+	\begin{equation}
+		T_z T_0
+		\sim \frac{D + 6\alpha' V^2}{2z^4}
+			+ \frac{2}{z^2}\,T_0
+			+ \frac{1}{z}\,\pd T_0,\quad
+		c = D + 6\alpha' V^2
+	\end{equation}
+	\vspace{-1.8\baselineskip}
+	\end{enumerate}
+	\qedfull
+
+	\item \textbf{Bosonic Strings on $S^3$:}
+
+	For bosonic strings moving on $S^3$ (radius $R$) with background dilaton $\Phi = \mrm{const.}$ and $B$-field:
+	\begin{equation}
+		B = R^2\sin\theta\,\pqty{
+			\psi - \sin\psi \cos\psi
+		}\,\dd{\theta}\wedge \dd{\phi}
+	\end{equation}
+	The corresponding $\beta$-functions and trace anomaly can be computed using the formulae given in \textit{Polchinski}; here $(\psi,\theta,\phi)$ is the usual spherical coordinates on $S^3$. 
 \pagebreak[3]
 
-%	Variation of metric determinant $
-%		\gamma \equiv \det\gamma_{ab}
-%	$ is give by the following formula:
-%	\begin{equation}
-%		\var{\sqrt{-\gamma}}
-%		= \frac{1}{2\sqrt{-\gamma}}
-%			\var{(-\gamma)}
-%		= \frac{1}{2\sqrt{-\gamma}}\,
-%			(-\gamma)
-%			\var{\ln\gamma}
-%		= \frac{1}{2} \sqrt{-\gamma}\,
-%			\gamma^{ab} \var{\gamma_{ab}}
-%	\end{equation}
-
-	Further simplification comes from the fact that, due to rotational symmetry, the string's motion can be restricted in a plane where its position is characterized by some angle $\theta = \Omega^{i_0}\in \{\Omega^i\}_i$.
-In this case other angle parameters $\Omega^i|_{i\ne i_0} = 0$, and the action is further reduced to:
-	\begin{gather}
-		S = -4TR^2 \int\dd{t} \int_0^r \dd{\rho}
-			\sqrt{
-				\oppower{\cosh}{2}\rho
-				- \oppower{\sinh}{2}\rho\,\pqty{
-					(\pdd{a}\theta)^2
-					- (\pdd{b}\theta)^2
-					\oppower{\cosh}{2}\rho
-				}
-			}
-		= \int\dd{t} \int_0^r \dd{\rho} \mcal{L},\\
-		\mcal{L} = -4TR^2
-			\sqrt{
-				\oppower{\cosh}{2}\rho
-				- \omega^2\oppower{\sinh}{2}\rho
-			},\quad
-			\omega = \pdd{t}\theta,\,
-			\pdd{\rho}\theta = 0
-	\end{gather}
-	We consider the special solution $\theta = \omega t$, while in general the endpoint $r = r(t)$ could be dynamical; variation of the action w.r.t.\ $r(t)$ gives\footnote{
-		The above reasoning is confirmed in e.g.\ \arxiv{hep-th/0204051}.
-	}:
-	\begin{gather}
-		0 = \var{S} = -4TR^2 \int\dd{t}
-			\int\limits_r^{r+\var{r}} \dd{\rho}
-			\sqrt{
-				\oppower{\cosh}{2}\rho
-				- \omega^2\oppower{\sinh}{2}\rho
-			}
-		= -4TR^2 \int\dd{t}
-			\sqrt{
-				\oppower{\cosh}{2}r
-				- \omega^2\oppower{\sinh}{2}r
-			} \var{r},\\
-		\omega^2 = \frac{\sqcosh r}{\sqsinh r}
-		= \oppower{\coth}{2} r
-		\label{eq:string_endpt_constraint}
-	\end{gather}
-
-	Note that if $\omega$ is constant, then $r$ must be fixed by \eqref{eq:string_endpt_constraint}. 
-	Taking $\theta$ as the only dynamical variable, it is then straight-forward to write the energy $E$ and angular momentum $J$ for such folded closed string:
-	\begin{gather}
-		\omega = \dot{\theta},\quad
-		\Pi = \pdv{\mcal{L}}{\omega}
-		= 4TR^2\,\frac{\omega\sqsinh\rho}{
-			\sqrt{
-				\oppower{\cosh}{2}\rho
-				- \omega^2\oppower{\sinh}{2}\rho
-			}
-		},\\
-		J = \int_0^r \dd{\rho} \Pi
-		= 4TR^2 \int_0^r \dd{\rho}
-		\frac{\omega\sqsinh\rho}{
-			\sqrt{
-				\oppower{\cosh}{2}\rho
-				- \omega^2\oppower{\sinh}{2}\rho
-			}
-		},\\
-		E = \int_0^r \dd{\rho} \pqty{
-			\Pi\omega - \mcal{L}
-		}
-		= 4TR^2 \int_0^r \dd{\rho}
-		\frac{\sqcosh\rho}{
-			\sqrt{
-				\oppower{\cosh}{2}\rho
-				- \omega^2\oppower{\sinh}{2}\rho
-			}
-		},
-	\end{gather}
-
-	In the large string limit, $r\to\infty,\ \omega = \coth r\to 1$. Expand in terms of $\epsilon = \omega - 1 > 0$, we find that $
-		r = \frac{1}{2} \ln\pqty{
-			1 + \frac{2}{\epsilon}
-		}
-		\sim \frac{1}{2} \ln\frac{2}{\epsilon}
-	$, or alternatively, $e^{2r}\cdot\epsilon\sim 2$. With some help from Mathematica\texttrademark, we get:
+	In fact, field strength:
+	\begin{equation}
+		H = \dd{B}
+		= 2R^2 \sin\theta \sin\psi 
+			\dd{\psi}
+			\wedge\dd{\theta}
+			\wedge\dd{\phi}
+	\end{equation}
+	While the spacetime curvature for a maximally symmetric sphere\footnote{
+		I would like to thank \textit{林般} for some very helpful hints. 
+	}: $
+		\mscr{R}_{\mu\nu}
+		= \frac{2}{R^2}\,g_{\mu\nu},\ %
+		\mscr{R} = \frac{6}{R^2}
+	$. Plug in these results, and we have:
+	\begin{equation}
+		\beta^G = \beta^B = 0,\quad
+		T\id{^a_a}
+		\simeq -\frac{1}{2}\,\beta^{\Phi} \mcal{R}
+		= -\frac{D-26 - \alpha'\mscr{R}}{12}\,
+			\mcal{R}
+	\end{equation}
+
+	\begin{enumerate}
+	\item Compared with the trace anomaly formula of a CFT: $
+		T\id{^a_a} = -\frac{1}{12}\,c\mcal{R}
+	$, where $\mcal{R}$ is the worldsheet Ricci scalar, we see that our theory is indeed conformally invariant with Weyl anomaly. Its central charge is given by:
+	\begin{equation}
+		c \simeq D-26 - \alpha'\mscr{R}
+		= 3 - 26 - \frac{6\alpha'}{R^2}
+	\end{equation}
+	This includes ghost contribution $(-26)$. If we do not gauge the conformal symmetry, then there will not be ghost contribution, and we will have $
+		c \simeq 3 - \frac{6\alpha'}{R^2}
+	$.
+
+	\item The background $B$ field given above is not single-valued on the $\psi$ circle.
+Note that we've encountered such difficulty in electromagnetism with a multi-valued $A^\mu(x)$.
+In fact, the resolution for this issue is very similar to Dirac's quantization of the magnetic monopole\footnote{
+		Reference: J.~J.~Sakurai, \textit{Modern Quantum Mechanics}. 
+	}: by allowing the action $S$ to be invariant modulo $2\pi$, since $
+		e^{-(S + 2\pi i)} = e^{-S}
+	$. More specifically, for $\psi\mapsto\psi + 2\pi$, we have:
 	\begin{equation}
 	\begin{aligned}
-		E - J
-		&= 4TR^2 \int_0^r \dd{\rho}
-		\frac{\sqcosh\rho - \omega\sqsinh\rho}{
-			\sqrt{
-				\oppower{\cosh}{2}\rho
-				- \omega^2\oppower{\sinh}{2}\rho
-			}
-		}
-%		\\[.5ex]
-%		&
-		= 4TR^2 \int_0^r \dd{\rho} \pqty\Big{
-			1 + \frac{\epsilon^2}{8}\sinh^2(2\rho)
-			+ \order{\epsilon^3}
-		} \\[1ex]
-		&= 4TR^2 \pqty{
-			r \pqty\Big{
-				1 - \frac{\epsilon^2}{16}
-				+ \order{\epsilon^3}
-			} + \order{1}
-		}
-%		\\[.5ex]
-%		&
-		= \pqty{2TR^2 \ln\frac{2}{\epsilon}}
-		\pqty\Big{
-			1 - \frac{\epsilon^2}{16}
-			+ \order{\epsilon^3}
-		} \\[1ex]
-		&\sim 2TR^2
-			\pqty{\ln\frac{2}{\epsilon}}
+		2\pi i\, n = \Delta S
+		&= \frac{1}{4\pi\alpha'}
+		\int \dd[2]{\sigma}
+			i\epsilon^{ab} 
+			R^2\sin\theta\,\pqty{
+				2\pi - 0
+			}\,\pqty{
+				\pdd{a} \theta\,
+				\pdd{b} \phi
+				- \pdd{a} \phi\,
+				\pdd{b} \theta
+			} \\[.5ex]
+		&= i\,\frac{R^2}{\alpha'}
+		\int \dd[2]{\sigma}
+			\sin\theta\,\epsilon^{ab}\,
+				\pdd{a} \theta\,
+				\pdd{b} \phi
 	\end{aligned}
 	\end{equation}
-	Similarly, $
-		J \sim 4TR^2 \mathlarger{\int_0^r}
-			\dd{\rho} \sqsinh \rho
-		\sim TR^2 \pqty{\frac{2}{\epsilon}}
-	$, this gives:
-	\begin{equation}
-		E - J
-		\sim 2TR^2 \ln \frac{J}{TR^2}
-	\end{equation}
+	Choose $
+		(\sigma^1,\sigma^2) = (\theta,\phi)
+	$ while $
+		\psi = \psi(\theta,\phi)
+	$, then the integral is reduced to $
+		\tilde{A}
+		= \int \dd[2]{\sigma} \sin\theta
+		= 2\pi R\tilde{\ell}
+	$, where $\tilde{\ell}$ is the string length weighted by $\sin\theta$. This leads to the following quantization:
+	\begin{equation}
+		\frac{R^3 \tilde{\ell}}{\alpha'}
+		= n \in\mbb{Z},\quad
+		R = \pqty\big{
+			{n\alpha'}\big/{\tilde{\ell}}
+			\mspace{3.5mu}
+		}^{1/3}
+		\ge \pqty\big{
+			{\alpha'}\big/{\ell}
+			\mspace{2.5mu}
+		}^{1/3}
+	\end{equation}
+	In particular, in string units: $\alpha' = \ell = 1$, we have $R\ge 1$.
 	\qedfull
-\pagebreak[4]
-
-	\item \textbf{Special Conformal Transformations:}
-	\begin{equation}
-		x^\mu
-		\xmapsto{\ K(a)\ }
-		\tilde{x}^\mu
-		= \frac{x^\mu + x^2 a^\mu}{
-			1 + 2a\cdot x + a^2 x^2
-		}
-	\end{equation}
+	\end{enumerate}
+
+	\item \textbf{Anomalous Currents:}
 
 	\begin{enumerate}
-	\item Under special conformal transformation $K(a)$, metric $\delta_{\mu\nu}\mapsto g_{\mu\nu}$ while:
-	\begin{equation}
-		g_{\alpha\beta}
-			\dd{\tilde{x}^\alpha}
-			\dd{\tilde{x}^\beta}
-		= \delta_{\mu\nu}
-			\dd{x^\mu}
-			\dd{x^\nu},\quad
-		g_{\alpha\beta}
-		= \delta_{\mu\nu}
-			\pdv{x^\mu}{\tilde{x}^\alpha}
-			\pdv{x^\nu}{\tilde{x}^\beta}
-		\label{eq:metric_transform}
-	\end{equation}
-	To calculate this we have to know the inverse transformation $x = K^{-1}(a)\,\tilde{x}$. First, notice the following decomposition\footnote{
-		See \textit{Di Francesco et al}, and also \https{github.com/davidsd/ph229}. 
-	} of $K(a)$:
-	\begin{equation}
-		\tilde{x}^\mu
-		= \frac{\frac{x^\mu}{x^2} + a^\mu}{
-			\frac{1}{x^2}
-			+ \frac{2a\cdot x}{x^2} + a^2
-		}
-		= \frac{\frac{x^\mu}{x^2} + a^\mu}{
-			\abs{\frac{x^\mu}{x^2} + a^\mu}^2
-		},\\[1ex]
-		\text{i.e.}\quad
-		K(a)\colon\ %
-			x^\mu
-			\ \xmapsto{\ I\ }\ %
-			\frac{x^\mu}{x^2}
-			\ \xmapsto{\ T(a)\ }\ %
-			y^\mu = \frac{x^\mu}{x^2} + a^\mu
-			\ \xmapsto{\ I\ }\ %
-			\tilde{x}^\mu
-			= \frac{y^\mu}{y^2},
-		\label{eq:special_conformal_decomp} \\[.5ex]
-		\text{i.e.}\quad
-		\frac{\tilde{x}^\mu}{\tilde{x}^2}
-			= \flatfrac{
-				\frac{y^\mu}{y^2}
-			}{
-				\frac{1}{y^2}
-			}
-			= y^\mu = \frac{x^\mu}{x^2} + a^\mu
-		\label{eq:special_conformal_simplified}
-	\end{equation}
-
-	From \eqref{eq:special_conformal_simplified}, we see that the transformation parameter $a^\mu$ composes linearly: $K(b)\,K(a) = K(a+b)$, therefore $K^{-1}(a) = K(-a)$, and we have:
-	\begin{equation}
-		x^\mu = K(-a)\,\tilde{x}^\mu
-		= \frac{\tilde{x}^\mu - \tilde{x}^2 a^\mu}{
-			1 - 2a\cdot \tilde{x} + a^2 \tilde{x}^2
-		}
-		= \frac{\tilde{y}^\mu}{y^2},\\[1.5ex]
-	\begin{aligned}
-		\pdv{x^\mu}{\tilde{x}^\alpha}
-		&= \pdv{x^\mu}{\tilde{y}^\sigma}
-			\pdv{\tilde{y}^\sigma}{\tilde{x}^\alpha}
-		= \pqty{
-			\pdv{\tilde{y}^\sigma}
-			\frac{\tilde{y}^\mu}{\tilde{y}^2}
-		} \pdv{\tilde{x}^\alpha} \pqty{
-			\frac{\tilde{x}^\sigma}{\tilde{x}^2}
-			- a^\sigma\!
-		}
-		= \pqty{
-			\pdv{\tilde{y}^\sigma}
-			\frac{\tilde{y}^\mu}{\tilde{y}^2}
-		} \pqty{
-			\pdv{\tilde{x}^\alpha}
-			\frac{\tilde{x}^\sigma}{\tilde{x}^2}
-		} \\[1ex]
-		&= \pqty{
-			\tilde{y}^2\delta^\mu_\sigma
-			- 2\tilde{y}^\mu \tilde{y}_\sigma
-		} \pqty{
-			\tilde{x}^2\delta^\sigma_\alpha
-			- 2\tilde{x}^\sigma \tilde{x}_\alpha
-		} \Big/ \pqty{\tilde{y}^4 \tilde{x}^4},
-	\end{aligned}\\[1ex]
-	\begin{aligned}
-		g_{\alpha\beta}
-		&\xlongequal{\eqref{eq:metric_transform}}
-		\delta_{\mu\nu} \pqty{
-			\tilde{y}^2\delta^\mu_\sigma
-			- 2\tilde{y}^\mu \tilde{y}_\sigma
-		} \pqty{
-			\tilde{x}^2\delta^\sigma_\alpha
-			- 2\tilde{x}^\sigma \tilde{x}_\alpha
-		} \pqty{
-			\tilde{y}^2\delta^\nu_\rho
-			- 2\tilde{y}^\nu \tilde{y}_\rho
-		} \pqty\big{
-			\tilde{x}^2\delta^\rho_\beta
-			- 2\tilde{x}^\rho \tilde{x}_\beta
-		} \Big/ \pqty{\tilde{y}^8 \tilde{x}^8}\\
-		&\xlongequal{\sum_{\mu,\nu}}
-		\tilde{y}^{-4} \delta_{\sigma\rho} \pqty{
-			\tilde{x}^2\delta^\sigma_\alpha
-			- 2\tilde{x}^\sigma \tilde{x}_\alpha
-		} \pqty\big{
-			\tilde{x}^2\delta^\rho_\beta
-			- 2\tilde{x}^\rho \tilde{x}_\beta
-		} \Big/ \tilde{x}^8 \\
-		&\xlongequal{\sum_{\sigma,\rho}}
-			\tilde{y}^{-4} \tilde{x}^{-4}
-			\delta_{\alpha\beta}
-	\end{aligned}
-	\end{equation}
-	We see that $g_{\alpha\beta} = f(x)\,\delta_{\alpha\beta}$, with coefficient:
-	\begin{equation}
-		f(x) = \tilde{y}^{-4} \tilde{x}^{-4}
-		\xlongequal{%
-			\eqref{eq:special_conformal_decomp}%
-		} \frac{x^4}{\tilde{x}^4}
-		\xlongequal{%
-			\eqref{eq:special_conformal_simplified}%
-		} \pqty{
-			1 + 2a\cdot x + a^2 x^2
-		}^2
-	\end{equation}
-	\qed[(a)]
-	\vspace*{-1\baselineskip}
-
-%	Note that the transformation depends smoothly on parameter $a$, therefore we can consider infinitesimal transformation generator:
-%	\begin{equation}
-%		k_\nu
-%		= k\id{^\mu_\nu}\pdd{\mu}
-%		= \pdv{\tilde{x}^\mu}{a^\nu}
-%			\bigg|_{a=0} \!\pdd{\mu}
-%		= \pqty{x^2\delta^\mu_\nu
-%			- 2x^\mu x_\nu}\pdd{\mu}
-%	\end{equation}
-
-	\item In 2D with $z = x^1 + ix^2,\ x^\mu\sim (z,\bar{z})$, we see from \eqref{eq:special_conformal_simplified} that:
-	\begin{equation}
-		\frac{x^\mu}{x^2}
-		\sim \frac{z}{\abs{z}^2}
-		= \frac{1}{\bar{z}}
-		\ \longmapsto\ %
-		\frac{1}{\bar{z}} + a,\quad
-		\text{i.e.}\quad
-		z\ \longmapsto\ 
-		w = \frac{1}{\frac{1}{z} + \bar{a}}
-		= \frac{z}{1 + z\bar{a}}
-	\end{equation}
-	Expand in the $\bar{a}\to 0$ limit, we find that $
-		w = z\,\pqty{
-			1 - z\bar{a} - \cdots
-		} \sim z - z^2 \bar{a}
-	$, i.e.\ it is generated by:
-	\begin{equation}
-		K_{\bar{z}}
-		= -z^2 \pdd{z}
-		= -z^2 \pd,\quad
-		\pd \equiv \pdd{z}
-	\end{equation}
-\pagebreak[3]
-
-	Note that when considering non-holomorphic functions, we have to consider $(z,\bar{z})$ as \textit{two} independent variables; hence the anti-holomorphic transformation $
-		\bar{z}\mapsto\bar{w}
-		= \frac{\bar{z}}{1 + \bar{z} a}
-		\sim \bar{z} - \bar{z}^2 a
-	$ provides another degree of freedom, namely:
-	\begin{gather}
-		K_\mu\ \sim\ \pqty{
-			K_{\bar{z}} = -z^2 \pd,\ %
-			K_{{z}} = -\bar{z}^2 \pdbar
-		},\\
-		\pd \equiv \pdd{z},\ %
-		\pdbar \equiv \pdd{\bar{z}}\notag
-	\end{gather}
-	Similarly, for translation $z\mapsto z+a$ and its conjugate, we have $
-		P_\mu\sim
-		\pqty{P_z = \pd, P_{\bar{z}} = \pdbar}
-	$. However, dilation and rotation are both encoded in a complex rescaling $
-		z\mapsto \lambda z,\ %
-		\lambda = re^{i\theta}\in\mbb{C}
-	$; we have:
-	\begin{equation}
-		z\mapsto \lambda z,\quad
-		\lambda = re^{i\theta}\in\mbb{C},\quad
-	\begin{aligned}
-		\var{r} \ \longleftrightarrow\ %
-		D &= z\,\pd + \bar{z}\,\pdbar,\\[-.5ex]
-		\var{\theta} \ \longleftrightarrow\ %
-		M &= i\,\pqty{z\,\pd - \bar{z}\,\pdbar},
-	\end{aligned}
-	\end{equation}
-
-	In summary, we have $
-		\mop{span}_\mbb{R}\Bqty{
-			P_\mu, K_\mu, D, M
-		} = \mfrak{so}(3,1)
-	$ generating the ``global'' transformation subgroup of the 2D conformal group; here, the $\mfrak{so}(3,1)$ boost is a linear combination\footnote{
-		See e.g.\ \https{github.com/davidsd/ph229}. 
-	} of $P_\mu$ and $K_\mu$. More specifically, in 2D any holomorphic or anti-holomorphic function gives a conformal transformation, hence the (classical) 2D conformal group is generated by:
-	\begin{equation}
-		\ell_m = z^{m+1} \pd,\quad
-		\bar{\ell}_m = \bar{z}^{m+1} \pdbar,\quad
-		m\in\mbb{Z}
-	\end{equation}
-	i.e.\ the \textit{Witt algebra} (or Virasoro algbera $\Vir_c$ with $c = 0$). It is clear that a (complexified) $\mfrak{so}(3,1)$ lives inside $\Vir_c$, i.e.,
-	\begin{equation}
-	\begin{aligned}
-		\mfrak{so}(3,1)^\mbb{C}
-		&= \mop{span}_\mbb{C}\Bqty{
-			P_\mu, K_\mu, D, M
-		} \\
-		&= \mop{span}_\mbb{C}\Bqty{
-			\ell_m,\bar{\ell}_m
-			\,\big|\, m = 0,\pm 1
-		}
-		= \mfrak{sl}(2,\mbb{R})^\mbb{C}
-			\oplus_\mbb{C}
-			\mfrak{sl}(2,\mbb{R})^\mbb{C}
-		\subset \Vir_{c}
-	\end{aligned}
-	\end{equation}
-	\end{enumerate}
-	\vspace{-1.2\baselineskip}
-
-	\qedfull
-
-	\item \textbf{$bc$ CFT}:
-	\begin{equation}
-		S = \frac{1}{2\pi}
-			\int \dd[2]{z} b\,\pdbar c
-	\end{equation}
-
-	Stress tensor of a theory can be obtained via variation over the metric, or equivalently, over the fields $\phi^i$ with $\var{\phi}$ induced by some \textit{local} spacetime translation $
-		x^\mu\mapsto x^\mu + \var{x}^\mu,\ %
-		\var{x}^\mu = \epsilon(x)\,a^\mu
-	$. Here $\epsilon(x)$ is any compactly supported bump function, centered around some point $x_0$.
-
-	In 2D, we have $\mu = z,\bar{z}$; for $\phi(z,\bar{z})$ with conformal weight $(h,\bar{h})$, consider $
-		z\mapsto z',\,
-		\bar{z}\mapsto \bar{z}'
-	$. For convenience, let's first consider a generic variation $\var{z} = \epsilon(z,\bar{z})$ before restricting to spacetime translation; we have:
-	\begin{equation}
-		\phi'(z',\bar{z}')
-		= \pqty\Big{\dv{z'}{z}}^{\!\! -h}
-			\pqty\Big{\dv{\bar{z}'}{\bar{z}}}^{
-				\!\! -\bar{h}
-			}
-			\phi(z,\bar{z}),\\[1ex]
-		\tilde{\delta}\phi
-		= \pqty{
-			- h\,\pd\epsilon
-			- \bar{h}\,\pdbar\bar{\epsilon}\,
-		}\,\phi,\\
-		\var{\phi} 
-		= \tilde{\delta}\phi
-			-\pdv{\phi}{x^\mu} \var{x^\mu}
-		= \pqty{
-			- h\,\pd\epsilon
-			- \bar{h}\,\pdbar\bar{\epsilon}\,
-		}\,\phi
-			- \epsilon\,\pd\phi
-			- \bar{\epsilon}\,\pdbar\phi,
-		\label{eq:var_field_compact_supp}
-	\end{equation}
-	Here we use $\tilde{\delta}\phi$ to denote the ``internal'' variation related to the conformal weights.
-
-	Note that $\phi = b,c$ are anti-commuting Grassmann numbers, variation of the action gives:
-	\begin{equation}
-	\begin{aligned}
-		\var{S}[b,c,\var{b},\var{c}]
-		&= \frac{1}{2\pi} \int \dd[2]{z} \pqty{
-			\var{b}\,\pdbar c
-			+ b\,\pdbar \var{c}
-		} \\
-		&= \frac{1}{2\pi} \int \dd[2]{z} \pqty{
-			- \pdbar c\,\var{b}
-			- \pdbar b\,\var{c}
-		} + \frac{1}{2\pi} \int \dd[2]{z}
-			\pdbar \pqty{b\var{c}}
-	\end{aligned}
-	\label{eq:bc_action_var}
-	\end{equation}
-	For \textit{unknown} $b,c$ and {arbitary} $\var{b},\var{c}$, the second term is reduced to a boundary term at infinity and can be dropped; imposing $\var{S} = 0$ gives the equation of motion (EOM): $\pdbar b = \pdbar c = 0$.
-
-	On the other hand, for \textit{on-shell} $b,c$ and compactly supported $\varphi = \var{b},\var{c}$ given in \eqref{eq:var_field_compact_supp}, the first term in \eqref{eq:bc_action_var} vanishes while $\var{S}_0 = 0$ still holds; this gives:
-	\begin{equation}
-	\begin{aligned}
-		0 = \var{S}_0
-		&= \frac{1}{2\pi} \int \dd[2]{z}
-			\pdbar \pqty{b\var{c}}
-		= \frac{1}{2\pi} \int \dd[2]{z}
-			\pdbar\,\pqty\big{
-				- (1-\lambda)\,bc\,\pd\epsilon
-				- b\,\pd c\,\epsilon
-			} \\
-		&= \frac{1}{2\pi} \int \dd[2]{z}
-			\pqty\big{
-				- (1-\lambda)\,bc\,
-					\pdbar\pd\epsilon
-				- b\,\pd c\,\pdbar\epsilon
-			}
-	\end{aligned}
-	\end{equation}
-	Here we've distributed the $\pdbar$ operator and dropped all terms that vanish automatically by EOM.
-Next we shall collect the $\pd\epsilon,\pdbar\epsilon$ terms; integrating by parts on the first integrand gives:
-	\begin{equation}
-	\begin{aligned}
-		0 = \var{S}_0
-		&= \frac{1}{2\pi} \int \dd[2]{z}
-			\pqty\big{
-				(1-\lambda)\,\pd(bc)\,
-				- b\,\pd c
-			}\,\pdbar\epsilon \\
-		&= \frac{1}{2\pi} \int \dd[2]{z}
-			\pqty\big{
-				(\pd b)\,c
-				- \lambda\,\pd(bc)
-			}\,\pdbar\epsilon \\
-		&= - \frac{1}{2\pi} \int \dd[2]{z}
-			\epsilon(z,\bar{z})\,\pd_{\bar{z}}
-			\pqty\big{
-				(\pd b)\,c
-				- \lambda\,\pd(bc)
-			}
-	\end{aligned}
-	\label{eq:conserved_current}
-	\end{equation}
-
-	Notice that we have obtained a conserved current using a generic $
-		\var{z}
-		= \epsilon(z,\bar{z}),
-		\var{\bar{z}}
-		= \bar{\epsilon}(z,\bar{z})
-	$; by setting $\epsilon = \epsilon(z)$, we get \textit{a} energy momentum tensor\footnote{
-		Note that the energy momentum tensor obtained in this way is generally \textit{not} unique: it can be off by a boundary term; see Luboš' comment at \https{physics.stackexchange.com/a/96100}, also \arxiv{1601.03616}.
-However, it is possible to fix this redundancy by considering $Tb$ OPE and match its conformal dimension.
-I would like to thank \textit{林般} for pointing this out.
-	}:
-	\begin{equation}
-		T(z)
-		= \normorder{(\pd b)\,c}
-			- \lambda\,\pd(\normorder{bc})
-	\end{equation}
-	Normal ordering is added manually to remove singular terms.
-
-	To compute $TT$ OPE, we need the OPE of $b(z)\,c(0)$; this is obtained by examining the following path integral, which is zero since the integrand is a total functional derivative:
-	\begin{equation}
-		0 = \int \mscr{D}b\,\mscr{D}c\,
-			\fdv{\phi}\pqty{e^{-S}\,\psi}
-	\end{equation}
-	Taking $\phi,\psi=b,c$, this generates operator equations such as $
-		\pdbar b(z)\,c(0)
-		= 2\pi\delta^2(z,\bar{z})
-	$. Note that $
-		\pdbar(\frac{1}{z})
-		= 2\pi\delta^2(z,\bar{z})
-	$, which gives:
-	\begin{equation}
-		b(z)\,c(0) \sim c(z)\,b(0)
-		\sim \frac{1}{z},\quad
-		b(z)\,b(0) \sim 0
-		\sim c(z)\,c(0)
-	\end{equation}
-
-	With the $bc$ OPE in hand, the $TT$ OPE is computed directly with brute force, by repeatedly applying Wick's theorem. This gives:
-	\begin{equation}
-		T(z)\,T(0)
-		\sim \frac{
-			-6\lambda^2 + 6\lambda - 1
-		}{z^4} + \cdots
-	\end{equation}
-	In general we have $
-		-6\lambda^2 + 6\lambda - 1
-		= \frac{c}{2}
-	$; for $\lambda = 2$ this gives $c = -26$. 
-	\qedfull
-
-	\item \textbf{Free Fermion CFT:}
-	\begin{equation}
-		S = \int \dd[2]{z}
-			\psi_i\,\pdbar\psi^i,\quad
-		\psi^i = \psi_i^*,\quad
-		\psi_i = \psi_i(z)
-	\end{equation}
-
-	\begin{enumerate}
-	\item Mode expansion of such chiral fermion is given by:
-	\begin{equation}
-		\psi_i = \sum_{
-			k\in\mbb{Z}+\frac{1}{2}
-		} \frac{b_{ik}}{z^{k+\frac{1}{2}}},\quad
-		b_{ik}
-		= \frac{1}{2\pi i} \oint \dd{z}
-			z^{k-\frac{1}{2}} \psi_i
-	\end{equation}
-	Canonical quantization is achieved by simply imposing anti-commutation relations; this is justified by mapping the system onto a cylinder, then $b_{ik}$'s indeed map to modes on the spatial circle\footnote{
-		This can be proven rigorously by considering operator equations like in the $bc$ CFT problem. 
-	}. The only non-zero commutators are:
-	\begin{equation}
-		\Bqty{b_{ik},b^{j\dagger}_q}
-		= \delta_{k+q,0}\,\delta^j_i
-	\end{equation}
-
-	This gives the only non-zero 2-point functions:
-	\begin{equation}
-	\begin{aligned}
-		\ave{
-			\psi_i(z)\,\psi^j(w)
-		}
-		&= \sum_{k,q\in\mbb{Z}+\frac{1}{2}}
-			\frac{1}{z^{k+\frac{1}{2}}}
-			\frac{1}{w^{q+\frac{1}{2}}}
-			\ave{b_{ik} b^{j\dagger}_q} \\
-		&= \sum_{k,q\in\mbb{Z}+\frac{1}{2}}
-			\frac{1}{z^{k+\frac{1}{2}}}
-			\frac{1}{w^{q+\frac{1}{2}}}
-			\mel{0}{
-				\Bqty{b_{ik},b^{j\dagger}_q}
-			}{0}
-		= \frac{\delta^j_i}{z-w}
-	\end{aligned}
-	\end{equation}
-	Note that $
-		b^i_k\ket{0} = 0,\ %
-		\forall\ k\ge\frac{1}{2}
-	$.
-
-	\item[(b)(c)] Combining two $\psi$ expansions gives the mode expansion of $
-		J\id{_i^j}
-		= \normorder{\psi_i(z)\,\psi^j(z)}
-	$, namely:
-	\begin{equation}
-		J\id{_i^j}(z)
-		= \sum_{k\in\mbb{Z}}
-			\frac{(J\id{_i^j})_k}{z^{k+1}},\quad
-		(J\id{_i^j})_k
-		= \sum_{q\in\mbb{Z}+\frac{1}{2}}
-			\normorder{
-				b_{iq}\,b^{j\dagger}_{k-q}
-			}
-	\end{equation}
-	It is in fact more convenient to obtain the $JJ$ OPE first, and then use it to find the  $[J_0,J_0]$ mode commutator\footnote{
-		I would like to thank \textit{谷夏} for providing this hint. 
-	}; note that $
-		{
-			{\psi}_i(z)\,{\psi}^j(w)
-		}
-	$ contraction gives $\frac{\delta^j_i}{z-w}$, we have:
-	\begin{equation}
-		J\id{_i^j}(z)\,J\id{_k^l}(0)
-		\sim \frac{
-			\delta_i^l\delta_k^j
-		}{z^2} + \frac{
-			\delta^j_k J\id{_i^l}(0)
-			- \delta^l_i J\id{_k^j}(0)
-		}{z},\\[1ex]
-		\bqty{
-			(J\id{_i^j})_0, (J\id{_k^l})_0
-		}
-		= \frac{1}{(2\pi i)^2}
-			\oint_0 \dd{w}
-			\oint_w \dd{z}
-				J\id{_i^j}(z)\,J\id{_k^l}(w)
-		= \delta_i^l\,(J\id{_k^j})_0
-			- \delta_k^j\,(J\id{_i^l})_0
-	\end{equation}
-
-	\item[(d)] Similar to $bc$ CFT, we have:
-	\begin{equation}
-		T(z) = \frac{1}{2}\,\pqty{
-			\normorder{\psi_i\,\pd\psi^i}
-			- \normorder{\pd\psi_i\,\psi^i}
-		},\quad
-		T(z)\,T(w)
-		\sim \frac{n/2}{(z-w)^4}
-			+ \frac{2T(w)}{(z-w)^2}
-			+ \frac{\pd T(w)}{z-w}
-	\end{equation}
-	With each (complex) field contributing $\frac{1}{2}\times 2$ central charge\footnote{
-		In fact a complex (Dirac) fermion can be ``treated like'' (\textit{dual to}) a boson; this is \textit{bosonization}. 
-	}.
-
-	\item[(e)] For real fermions, there is an additional reality condition:
-	\begin{equation}
-		\psi^i = \psi^\star_i = \psi_i 
-	\end{equation}
-	The canonical quantization still holds without the extra adjoint, same as the 2-point function:
-	\begin{equation}
-		\ave{\psi_i(z)\,\psi_j(w)}
-		= \frac{\delta_{ij}}{z - w}
-	\end{equation}
-
-	Similar holds for $J_{ij} = \normorder{\psi_i\psi_j}$ and its OPE, but we no longer need to distinguish upper/lower indices; we have:
-	\begin{equation}
-		J_{ij}(z)\,J_{kl}(0)
-		\sim \frac{
-			- \delta_{ik}\delta_{jl}
-			+ \delta_{il}\delta_{jk}
-		}{z^2} + \frac{
-			- \delta_{ik} J_{jl}(0)
-			+ \delta_{il} J_{jk}(0)
-			+ \delta_{jk} J_{il}(0)
-			- \delta_{jl} J_{ik}(0)
-		}{z}\\[1ex]
-		\bqty{
-			(J_{ij})_0, (J_{kl})_0
-		}
-		= - \delta_{ik} (J_{jl})_0
-			+ \delta_{il} (J_{jk})_0
-			+ \delta_{jk} (J_{il})_0
-			- \delta_{jl} (J_{ik})_0
-	\end{equation}
-	This is precisely the $\mfrak{o}(n)$ algebra. 
-	\qedfull
+	\item For a conserved current in flat worldsheet to be anomalous in curved worldsheet, then its deviation from conservation must be proportional to the Ricci scalar:
+	\begin{equation}
+		\cdv{a} j^a = QR,\quad
+		Q = \mrm{const}. 
+	\end{equation}
+	The logic here is similar to the Weyl anomaly\footnote{
+		See \textit{Polchinski} for reference. 
+	}: $\cdv{a} j^a$ is diff- and Poincaré-invariant with dimension~2, because we have preserved these symmetries, and it vanishes in the ﬂat case; this leaves only one possibility --- $
+		\cdv{a} j^a \propto R
+	$: the Ricci scalar.
+
+	For conformal transformation $
+		z\mapsto z + \epsilon(z),\ %
+		\bar{z}\mapsto \bar{z}
+			+ \bar{\epsilon}(\bar{z})
+	$, we have:
+	\begin{equation}
+		\delta_\epsilon j(0)
+		= -\operatorname*{Res}\limits_{z\to 0}
+				\epsilon(z)\,
+				T(z)\,j(0)
+			-\operatorname*{Res}\limits_{\bar{z}\to 0}
+				\bar{\epsilon}(\bar{z})\,
+				\tilde{T}(\bar{z})\,j(0)
+	\end{equation}
+	Hence the $z^{-3},\bar{z}^{-3}$ coefficients of the OPE reflect the $
+		\epsilon = z^2,\ %
+		\bar{\epsilon} = \bar{z}^2
+	$ transformation of $j$.  By comparing the Weyl transformations, this yields a total coefficient of $4Q$.
+
+	\item For $bc$ CFT with $j = \normorder{cb}\,$, the anomaly can be explicitly calculated using our results in (a), i.e.\ by calculating $Tj$ OPE. Following the standard procedure\footnote{
+		For more detailed discussions, see Blumenhagen et al, \textit{Basic Concepts of String Theory}. 
+	}, we obtain that:
+	\begin{equation}
+		T_z j_0 \sim \frac{1 - 2\lambda}{z^3}
+			+ \order{\frac{1}{z^2}}
+	\end{equation}
+	Note that the anti-holomorphic part is zero, therefore, we have: $
+		Q = \frac{1}{4}\,(1 - 2\lambda)
+	$. \qedfull
 

### 2020-03-26 Strings2020/strings2/strings2.tex
Complete advqft2, fix some ambiguities
... about finite symmetry transformations in previous work

@@
 		S' = S
-		\propto \int \dd[2]{z}
-			\pd X^\mu \pdbar X_\mu
-		= \int \dd[2]{z'}
-			\pd' X'^\mu \pdbar' X'_\mu
-%		= \int \dd[2]{z'}
-%			\pd' X'^\mu \pdbar' X'_\mu (z',\bar{z}')
+		\ \Longrightarrow\ %
+		\int \dd[2]{z}
+			\pd X'^\mu \pdbar X'_\mu (z,\bar{z})
+		\xlongequal{(*)} \int \dd[2]{z'}
+			\pd' X'^\mu \pdbar' X'_\mu (z',\bar{z}')
+		= \int \dd[2]{z}
+			\pd X^\mu \pdbar X_\mu (z,\bar{z})
 	\end{equation}
+	Here at $(*)$ we use the diff-invariant property of the action. 
 	Restore the anti-holomorphic component and insert \eqref{eq:dilaton_holomorphic}, then we find that in order to cancel the $\order{\epsilon^2}$ terms, we have to fix:

### 2020-04-06 Strings2020/strings2/strings2.tex
Add corrections to strings2

@@
 
-	For a quantum version, redefine $j(z)$ with normal ordering, and we have:
+	For a quantum version, redefine $j(z)$ with normal ordering\footnote{
+		Normal ordering between $\ge 3$ operators is in fact \textit{not} associative; this directly leads to the ambiguity we are about to discover.
+See \textit{Di Francesco et al} for more detailed discussions.
+		Na\"ively, $\normorder{bc\,\pd c}_{\,(0)}$ is \textit{defined} as $b(0)\,c(z_1)\,\pd c(z_2)$ while $z_1,z_2\to 0$, with singular terms subtracted; however, different ways of taking the limit might lead to different results.
+For example, we can first take $z_1\to 0$ then $z_2\to 0$, or we can first take $z_1\to z_2$ then $z_2\to 0$.
+This two procedures will differ by $
+			\frac{3}{2}\,\pd^2 c(z)
+		$, which is precisely the correction we are about to find out. \sidenote{\textit{I suppose this is somehow related to topology, e.g.\ braid group?}}
+	}, and we have:
 	\begin{gather}
@@
 			(-1)\,c(0) \notag\\[1ex]
+		\normorder{bc}_{\,(z)}\,
+		\normorder{bc\,\pd c}_{\,(0)}
 		&\sim \frac{1}{z}\,\pqty\big{
@@
 	By acting on $L_0$ (expanded in modes), we find that $
-		m^2 = -k^2 = \frac{1}{\alpha'}
+		m^2 = -k^2 = \frac{1}{\alpha'} = l_s
 	$: massive.
@@
 		}
-	$ can also be expanded in modes; the physical states are firstly, $Q$-closed; i.e.
+	$ can also be expanded in modes; note that:
+	\begin{equation}
+		Q^2 = \frac{1}{2}\,\{Q,Q\}
+		\propto \oint \frac{\dd{z}}{2\pi i} 
+			\operatorname*{Res}\limits_{z'\to z}
+			j(z')\,j(z) + \pqty{\mrm{conjugate}}
+	\end{equation}
+	Compared with the $jj$ OPE, we see that $Q$ is nilpotent iff.\ $D = 26$, i.e.\ the critical dimension of bosonic string theory. This condition is necessary for consistent BRST quantization.
+
+	The physical states are firstly, $Q$-closed; i.e.
 	\begin{equation}
@@
 		\ \Longrightarrow\ %
-		k^\mu e_{\mu\nu} = 0,\quad
-		k^\mu e_\mu = 0,\quad
+		4l_s\,k^\mu e_{\mu\nu}
+			+ l_s\,k_\nu\eta
+			+ e_\nu = 0,\quad
+		2\sqrt{2}\,l_s\,k^\mu
+			+ e^\nu_\nu e_\mu = 0,\quad
 		\beta_\mu = \beta = 0,
@@
 		\gamma_\nu
-		\mapsto \gamma_\nu + k^\mu e_{\mu\nu},\quad
+		\mapsto \gamma_\nu
+			+ \gamma'_\nu,\quad
 		\gamma
-		\mapsto \gamma + k^\mu e_{\mu},\quad
+		\mapsto \gamma
+			+ \gamma',\quad
+		\eta
+		\mapsto \eta + \eta',\quad
 		e_{\mu\nu}
-		\mapsto e_{\mu\nu}
-			+ \beta_\mu k_\nu
-			+ \beta_\nu k_\mu,\quad
-		e_\mu
-		\mapsto e_\mu + \beta k_\mu
-	\end{equation}
-	Here $e_{\mu\nu},e_\mu,\beta_\mu,\beta$ are seen as arbitrary gauge parameters.
+		\mapsto e_{\mu\nu} + l_s\,\pqty{
+			\beta'_\mu k_\nu
+			+ \beta'_\nu k_\mu
+		},
+%		\quad
+%		e_\mu
+%		\mapsto e_\mu + \beta k_\mu\,l_s
+	\end{equation}
+	Here $
+		\beta'_\mu,\gamma'_\nu,\gamma',\eta'
+	$ are arbitrary gauge parameters.
 For closed string the result can be obtained by the doubling trick, i.e.\ by introducing anti-holomorphic modes $\tilde{\alpha},\tilde{b},\tilde{c}$ and imposing reality conditions.
@@
 		I would like to thank Lucy Smith for helpful discussions.
+A better recipe to find finite transformations is to consider its properties under composition, which will lead to some constraints that can be solved to obtain the result.
 	}:
@@
 	\end{equation}
+\pagebreak[3]
 
@@
 		e^{-(S + 2\pi i)} = e^{-S}
-	$. More specifically, for $\psi\mapsto\psi + 2\pi$, we have:
+	$.
+
+	More specifically, for $\psi\mapsto\psi + 2\pi$, we have:
 	\begin{equation}
@@
 		2\pi i\, n = \Delta S
-		&= \frac{1}{4\pi\alpha'}
-		\int \dd[2]{\sigma}
-			i\epsilon^{ab} 
-			R^2\sin\theta\,\pqty{
-				2\pi - 0
-			}\,\pqty{
-				\pdd{a} \theta\,
-				\pdd{b} \phi
-				- \pdd{a} \phi\,
-				\pdd{b} \theta
-			} \\[.5ex]
-		&= i\,\frac{R^2}{\alpha'}
-		\int \dd[2]{\sigma}
-			\sin\theta\,\epsilon^{ab}\,
-				\pdd{a} \theta\,
-				\pdd{b} \phi
+%		&= \frac{1}{4\pi\alpha'}
+%		\int \dd[2]{\sigma}
+%			i\epsilon^{ab} 
+%			R^2\sin\theta\,\pqty{
+%				2\pi - 0
+%			}\,\pqty{
+%				\pdd{a} \theta\,
+%				\pdd{b} \phi
+%				- \pdd{a} \phi\,
+%				\pdd{b} \theta
+%			} \\[.5ex]
+%		&= i\,\frac{R^2}{\alpha'}
+%		\int \dd[2]{\sigma}
+%			\sin\theta\,\epsilon^{ab}\,
+%				\pdd{a} \theta\,
+%				\pdd{b} \phi
+		= \frac{i}{2\pi\alpha'}
+			\,\Delta\! \int_\Sigma
+				X^* B
+		= \frac{i}{2\pi\alpha'}
+			\,\Delta\! \int_{X(\Sigma)}
+				B
+		= \frac{i}{2\pi\alpha'}
+			\,\Delta\! \int_M H
 	\end{aligned}
 	\end{equation}
-	Choose $
-		(\sigma^1,\sigma^2) = (\theta,\phi)
-	$ while $
-		\psi = \psi(\theta,\phi)
-	$, then the integral is reduced to $
-		\tilde{A}
-		= \int \dd[2]{\sigma} \sin\theta
-		= 2\pi R\tilde{\ell}
-	$, where $\tilde{\ell}$ is the string length weighted by $\sin\theta$. This leads to the following quantization:
-	\begin{equation}
-		\frac{R^3 \tilde{\ell}}{\alpha'}
+	$B$ is a 2-form in $S^3$, $X^* B$ denotes its pullback to the worldsheet, and $X(\Sigma)\subset S^3$ denotes the embedding of $\Sigma$ into $S^3$.
+Note that $H$ is proportional to the volume form in $S^3$, hence we have:
+	\begin{equation}
+		\Delta\! \int_M H
+		= 2R^2\,\Delta\! \mop{Vol}(M)
+		= 2R^2\,\mbb{Z} \mop{Vol}(S^3)
+		= 2R^2\,2\pi^2\,\mbb{Z}
+		= 4\pi^2 R^2\,\mbb{Z}
+	\end{equation}
+%	Choose $
+%		(\sigma^1,\sigma^2) = (\theta,\phi)
+%	$ while $
+%		\psi = \psi(\theta,\phi)
+%	$, then the integral is reduced to $
+%		\tilde{A}
+%		= \int \dd[2]{\sigma} \sin\theta
+%		= 2\pi R\tilde{\ell}
+%	$, where $\tilde{\ell}$ is the string length weighted by $\sin\theta$. 
+	This leads to the following quantization:
+	\begin{equation}
+%		\frac{R^3 \tilde{\ell}}{\alpha'}
+		\frac{R^2}{\alpha'}
 		= n \in\mbb{Z},\quad
-		R = \pqty\big{
-			{n\alpha'}\big/{\tilde{\ell}}
-			\mspace{3.5mu}
-		}^{1/3}
+		R \ge \sqrt{\alpha'}
+%		R = \pqty\big{
+%			{n\alpha'}\big/{\tilde{\ell}}
+%			\mspace{3.5mu}
+%		}^{1/3}
 		\ge \pqty\big{
@@
 	\end{equation}
-	In particular, in string units: $\alpha' = \ell = 1$, we have $R\ge 1$.
+	In particular, in string units: $
+		\alpha'
+%		= \ell
+		= 1
+	$, we have $R\ge 1$.
 	\qedfull
@@
 		\bar{\epsilon} = \bar{z}^2
-	$ transformation of $j$.  By comparing the Weyl transformations, this yields a total coefficient of $4Q$.
+	$ transformation of $j$.  By comparing the Weyl transformations\footnote{
+		Note that $
+			(\textit{Conformal}\,)
+			= (\textit{Weyl}\,)
+				+ (\textit{Translation}\,)
+		$. 
+	}, this yields a total coefficient of $4Q$.
 

### 2020-04-17 compile.sh
Update compile.sh to support lualatex in %!TeX

@@ -17,14 +17,30 @@ echo "$FILES"
 
 for file in $FILES; do
     echo "### Compiling \`$file\` ..."
-    cd "$(dirname "$file")" || exit 1
 
-    latexmk \
-        -xelatex \
-        -synctex=1 \
-        -interaction=nonstopmode \
-        -shell-escape \
-        "$(basename "$file")"
+    cd "$(dirname "$file")" || exit 1
+    filename=$(basename "$file")
+
+    # Process magic comment
+    tex_program=$(
+        grep "%[ ]*\!TeX[ ]*TS-program[ ]*=[ ]*" "$filename" \
+        | cut -d '=' -f2 | xargs
+    )
+
+    if [[ $tex_program == pdflatex ]] \
+    || [[ $tex_program == xelatex ]] \
+    || [[ $tex_program == lualatex ]]; then
+        latexmk \
+            "-$tex_program" \
+            -synctex=1 \
+            -interaction=nonstopmode \
+            -shell-escape \
+            "$filename"
+    else
+        eval "$tex_program" \
+            "$filename"
+    fi
+
 
     cd "$DIR" || exit 1
 done

### 2020-04-30 compile.sh
Update magic comment regex in compile.sh
Double comment: '%%' will disable the magic comment

@@ -23,7 +23,7 @@ for file in $FILES; do
 
     # Process magic comment
     tex_program=$(
-        grep "%[ ]*\!TeX[ ]*TS-program[ ]*=[ ]*" "$filename" \
+        grep -E "^[ \t]*%[ ]*\!TeX[ ]*TS-program[ ]*=[ ]*" "$filename" \
         | cut -d '=' -f2 | xargs
     )
 

### 2020-05-10 Strings2020/strings5/strings5.tex
Add strings5, fix typo in strings4

% !TeX encoding = UTF-8
% !TeX spellcheck = en_US
% !TeX TXS-program:bibliography = biber -l zh__pinyin --output-safechars %
%% !TeX TS-program = lualatex
%%% LuaLaTeX is required for `tikz-feynman`

\documentclass[a4paper,10pt]{article}

\newcommand{\hwNumber}{5}

\input{../strings_preamble.tex}
\input{../.modules/basics/biblatex.tex}

%%% ID: sensitive, do NOT publish!
\InputIfFileExists{../id.tex}{}{}

\newcommand{\oppower}[2]{\mop{{#1}^{#2}}\!}
\newcommand{\sqsinh}{\oppower{\sinh}{2}}
\newcommand{\sqcosh}{\oppower{\cosh}{2}}

\newcommand{\Vir}{\mathbf{V}\mfrak{ir}}
\newcommand{\zbar}{\bar{z}}
\usepackage{tikz-feynman,cancel}

\begin{document}
\maketitle
\pagestyle{headings}
\pagenumbering{arabic}
\thispagestyle{empty}

%{
%	\noindent\itshape%
%	本文约定：度规$\eta\sim\pqty{-,+,+,+}$, 指标$\mu,\nu,\dots = 0,1,2,3,\ i,j,\dots = 1,2,3$.
%}

	\begin{enumerate}

	\item \textbf{Partition Function for Compact Scalars}

	\begin{enumerate}
	\item Mode expansion of $X$ CFT is\footnote{
		Again we follow the convention of \textit{Polchinski}. 
	}:
	\begin{gather}
		\pd X(z) =
			-i\,\sqrt{\frac{\alpha'}{2}}
			\sum_{m = -\infty}^\infty
				\frac{\alpha_m}{z^{m+1}},\quad
		\pdbar X(\bar{z}) =
			-i\,\sqrt{\frac{\alpha'}{2}}
			\sum_{m = -\infty}^\infty
				\frac{\tilde{\alpha}_m}{\bar{z}^{m+1}},\\
		X = x
			- i\,\sqrt{\frac{\alpha'}{2}}
			\,\pqty\big{
				\alpha_0 \ln z
				+ \tilde{\alpha}_0 \ln \bar{z}
			}
			+ i\,\sqrt{\frac{\alpha'}{2}}
			\sum_{m \ne 0}
				\frac{1}{m}
				\pqty{
					\frac{\alpha_m}{z^m}
					+ \frac{\tilde{\alpha}_m}{\bar{z}^m}
				},
	\end{gather}
	Momentum $p$ is the charge for \textit{spacetime} translation; we have:
	\begin{gather}
		X\mapsto X + \mrm{const},\quad
		j_a = \frac{i}{\alpha'}\,\pdd{a} X,
	\\
		p = \frac{1}{2\pi i} \oint_C \pqty{
				\dd{z} j - \dd{\bar{z}} \tilde{j}\,
			}
		= \frac{1}{\alpha'} \sqrt{\frac{\alpha'}{2}}\,
			\pqty\big{\alpha_0 + \tilde{\alpha}_0}
		= \sqrt{\frac{1}{2\alpha'}}\,
			\pqty\big{\alpha_0 + \tilde{\alpha}_0}
	\end{gather}

	Additionally, for compact free boson, $X$ is only defined modulo $2\pi R$; therefore, states after $X + 2\pi R$ translation should be identical to the original states, i.e.
	\begin{equation}
		e^{ip\,(2\pi R)} = \idty,\quad
		p = \frac{n}{R},\quad n\in\mbb{Z}
	\end{equation}
	This, in fact, holds for any field theory\footnote{
		Reference: discussions in \textit{Polchinski}, Chapter 8. 
	} defined for $X\in S^1$, including the ordinary quantum mechanics (a classical field theory) on $S^1$.

	On the other hand, there are additional constraints in string theory: for the state of a \textit{single} closed string, there is a discrete translational symmetry on the \textit{worldsheet}:
	\begin{equation}
		X(\sigma^1 + 2\pi) \cong X(\sigma^1),\quad
		X(\sigma^1 + 2\pi) = X(\sigma^1) + 2\pi Rw,\quad
		w \in\mbb{Z}
	\end{equation}
	With some definite winding number $w$. In $(z,\bar{z})$ coordinates, we have:
	\begin{gather}
		2\pi Rw
		= X\pqty{
				z\,e^{2\pi i},\zbar\,e^{-2\pi i}\,
			} - X(z,\zbar)
		= -i\sqrt{\frac{\alpha'}{2}}\,
			2\pi i\,\pqty\big{
				\alpha_0 - \tilde{\alpha}_0
			}
		= 2\pi\sqrt{\frac{\alpha'}{2}}\,
			\pqty\big{
				\alpha_0 - \tilde{\alpha}_0
			},
	\\
		p = \frac{p_L + p_R}{2},\quad
		p_L = \sqrt{\frac{2}{\alpha'}}\,\alpha_0,\quad
		p_R = \sqrt{\frac{2}{\alpha'}}\,\tilde{\alpha}_0,
	\\[1ex]
		p_{L,R} = \frac{n}{R} \pm \frac{wR}{\alpha'}\,,
	\\[1ex]
		X = x
			- i\,\frac{\alpha'}{2}\,
			\pqty\big{
				p_L \ln z
				+ p_R \ln \bar{z}
			}
			+ i\,\sqrt{\frac{\alpha'}{2}}
			\sum_{m \ne 0}
				\frac{1}{m}
				\pqty{
					\frac{\alpha_m}{z^m}
					+ \frac{\tilde{\alpha}_m}{\bar{z}^m}
				},
	\end{gather}

	For the oscillator expressions for $L_0$, recall that:
	\begin{gather}
		T(z)
		= - \frac{1}{\alpha'}\,
			\normorder{\pd X\,\pd X}
		= \sum_m \frac{L_m}{z^{m+2}},
	\\
		L_{m\ne 0}
		= \frac{1}{2}
			\sum_l \alpha_{m-l} \alpha_l,\quad
		L_0 = \frac{1}{2}\,\normorder{
			\sum_l \alpha_{-l} \alpha_l
		}
		\sim \frac{\alpha'p_L^2}{4}
			+ \sum_{l > 0} \alpha_{-l} \alpha_l,
	\end{gather}
	The $L_0$ expression may be off by some normal ordering constant; this ambiguity can be resolved by considering:
	\begin{equation}
		2L_0 \ket{0,0;n = w = 0}
		= \pqty{
				L_1 L_{-1} - L_{-1} L_1
			} \ket{0,0;p_L = p_R = 0}
		= 0 - 0 = 0
	\end{equation}
	Therefore the normal ordering constant is, in fact, trivial, and we have:
	\begin{equation}
		L_0 = \frac{\alpha'p_L^2}{4}
			+ \sum_{l > 0}
				\alpha_{-l} \alpha_l,\quad
		\tilde{L}_0 = \frac{\alpha'p_R^2}{4}
			+ \sum_{l > 0}
				\tilde{\alpha}_{-l} \tilde{\alpha}_l,
	\end{equation}

	\item The torus partition function is given by:
	\begin{equation}
		\ave{\idty}_{T^2}
		\equiv Z(\tau = \tau_1 + i\tau_2)
		= \int \DD X e^{-S}
		= \Tr e^{-(2\pi\tau_2) H} e^{i\,(2\pi\tau_1) P}
	\end{equation}
	Here $P$ generates \textit{worldsheet} translation along $\sigma^1$, not to be confused with $p$ which generates \textit{spacetime} translation; with $
		z = e^{-iw},\ w = \sigma^1 + i\sigma^2
	$, 
	\begin{gather}
	\begin{aligned}
		T\id{^0_1}
		= \eta^{00}\, (\pdd{0} \sigma^2)\, T_{21}
		= -iT_{12}
		&= -i\,\pqty\big{
				T_{ww}\,
					(\pdd{1} w)(\pdd{2} w)
				+ T_{\bar{w}\bar{w}}\,
					(\pdd{1} \bar{w})(\pdd{2} \bar{w})
			} \\
		&= T_{ww} - T_{\bar{w}\bar{w}} \\
		&= \pqty{
				T_{zz}\,
					(\pdd{w} z)^2
				+ \tfrac{c}{24}
			}
			- \pqty{
				T_{\bar{z}\bar{z}}\,
					(\pdd{\bar{w}} \bar{z})^2
				+ \tfrac{\tilde{c}}{24}
			} \\
		&= T(z)\, (-iz)^2
			- \tilde{T}(\bar{z})\, (+i\bar{z})^2
			+ \frac{c - \tilde{c}}{24},
	\end{aligned}
	\\[1ex]
	\begin{aligned}
		P = \int \frac{\dd{\sigma_1}}{2\pi}\,
				\pqty{- T\id{^0_1}\!}
		&= - \int \frac{\dd{\sigma_1}}{2\pi}\,
				T(z)\, (-iz)^2
			+ \int \frac{\dd{\sigma_1}}{2\pi}\,
				\tilde{T}(\bar{z})\, (+i\bar{z})^2
			- \frac{c - \tilde{c}}{24} \\
		&= + \ointctrclockwise
				\frac{\dd{z}}{2\pi\,(-iz)}\,
				T(z)\, (-iz)^2
			+ \ointctrclockwise
				\frac{\dd{\bar{z}}}{2\pi\,(+i\bar{z})}\,
				\tilde{T}(\bar{z})\, (+i\bar{z})^2
			- \frac{c - \tilde{c}}{24} \\
		&= \oint \frac{\dd{z}}{2\pi i}\,
				zT(z)
			- \oint \frac{\dd{\bar{z}}}{2\pi i}\,
				\bar{z}\tilde{T}(\bar{z})
			- \frac{c - \tilde{c}}{24} \\
		&= L_0 - \tilde{L}_0
			- \frac{c - \tilde{c}}{24} \\
		&= \pqty{L_0 - \tfrac{c}{24}}
			- \pqty\big{
				\tilde{L}_0 - \tfrac{\tilde{c}}{24}
			},
	\\[1.5ex]
		H = \int \frac{\dd{\sigma_1}}{2\pi}\,
				T\id{^0_0}
		&= \int \frac{\dd{\sigma_1}}{2\pi}\,
				T_{22} \\
		&= L_0 + \tilde{L}_0
			- \frac{c + \tilde{c}}{24} \\
		&= \pqty{L_0 - \tfrac{c}{24}}
			+ \pqty\big{
				\tilde{L}_0 - \tfrac{\tilde{c}}{24}
			},
	\end{aligned}
	\end{gather}
	Here we've used the fact that $
		\displaystyle\oint \frac{\dd{\bar{z}}}{\bar{z}}
		= \ointctrclockwise
			\frac{\dd{\bar{z}}}{\bar{z}}
		= 2\pi i
	$. Therefore,
	\begin{equation}
		Z(\tau)
		= \Tr e^{-(2\pi\tau_2) H} e^{i\,(2\pi\tau_1) P}
		= \Tr q^{L_0 - \tfrac{c}{24}}\,
			\bar{q}^{\tilde{L}_0 - \tfrac{\tilde{c}}{24}}
		,\quad q = e^{2\pi i\tau}
	\end{equation}

	Using the expressions in (a), we find that $L_0$ action on a state $\ket{\psi}$ created by $\alpha_{-l},\tilde{\alpha}_{-l}$ yields the sum of occupation numbers $N_l$ weighted by $l$:
	\begin{equation}
		L_0 \ket{\psi}
		= \pqty{
				\frac{\alpha'k_L^2}{4}
				+ \sum_{l > 0} l\cdot N_l
			} \ket{\psi}
	\end{equation}
	With $c = \tilde{c} = 1$, we obtain:
	\begin{equation}
	\begin{aligned}
		Z(\tau)
		&= (q\bar{q})^{-\frac{1}{24}}
			\sum_{n,w}
				e^{
					- 2\pi \tau_2
					\alpha'\frac{k_L^2 + k_R^2}{4}
				}
				e^{
					2\pi i \tau_1
					\alpha'\frac{k_L^2 - k_R^2}{4}
				}
			\sum_{(N_l),(\tilde{N}_l)}
				q^{
					\,\sum\limits_{l>0}  l\cdot N_l
				}
				\bar{q}^{
					\,\sum\limits_{l>0}  l\cdot \tilde{N}_l
				} \\
		&= (q\bar{q})^{-\frac{1}{24}}
			\sum_{n,w}
				e^{
					- \pi \tau_2 \pqty{
						\frac{\alpha'n^2}{R^2}
						+ \frac{w^2 R^2}{\alpha'}
					}
					+ 2\pi i \tau_1 nw
				}
			\sum_{(N_l),(\tilde{N}_l)} \prod_{l>0}
				q^{l\cdot N_l}
				\bar{q}^{\,l\cdot \tilde{N}_l} \\
		&= \abs{\eta(\tau)}^{-2}
			\sum_{n,w}
				e^{
					- \pi \tau_2 \pqty{
						\frac{\alpha'n^2}{R^2}
						+ \frac{w^2 R^2}{\alpha'}
					}
					+ 2\pi i \tau_1 nw
				}
	\end{aligned}
	\end{equation}
	We've simplified the contributions from the oscillator modes using $\eta(\tau)$, since they are identical to the oscillator contributions of the non-compact $X\in\mbb{R}^1$:
	\begin{equation}
	\begin{aligned}
		(q\bar{q})^{-\frac{1}{24}}\!\!\!\!\!
		\sum_{(N_l),(\tilde{N}_l)} \prod_{l>0}
			q^{l\cdot N_l}
			\bar{q}^{\,l\cdot \tilde{N}_l}
		&= (q\bar{q})^{-\frac{1}{24}}
			\prod_{l>0} \sum_{N_l,\tilde{N}_l = 0}^\infty
				q^{l\cdot N_l}
				\bar{q}^{\,l\cdot \tilde{N}_l} \\
		&= (q\bar{q})^{-\frac{1}{24}}
			\prod_{l>0}
				\frac{1}{1 - q^l}
				\frac{1}{1 - \bar{q}^{\,l}}
		= \abs{\eta(\tau)}^{-2}
	\end{aligned}
	\end{equation}

	In the $R\to\infty$ limit, only the $w = 0$ modes survive; all other modes are exponentially suppressed by the $
		e^{
			- \pi \tau_2 w^2 R^2 / \alpha'
		}
	$ factor; i.e.
	\begin{equation}
	\begin{aligned}
		Z(\tau)
		&= \abs{\eta(\tau)}^{-2}
			\sum_{n,w}
				\exp \Bqty{
					- \pi \tau_2 \pqty{
						\frac{\alpha'n^2}{R^2}
						+ \frac{w^2 R^2}{\alpha'}
					}
					+ 2\pi i \tau_1 nw
				} \\
		&\to \abs{\eta(\tau)}^{-2}
			\sum_{n}
				\exp \Bqty{
					- \pi \tau_2\,
						\frac{\alpha'n^2}{R^2}
				},\quad k = \frac{n}{R} \\
		&\to \abs{\eta(\tau)}^{-2}
			\,V\!\!\int \frac{\dd{k}}{2\pi}
				\exp \Bqty{
					- \pi \tau_2\,\alpha' k^2
				} \\
		&= V\,\abs{\eta(\tau)}^{-2}
			\pqty{
				4\pi^2 \alpha' \tau_2
			}^{-\frac{1}{2}} \\
		&\equiv V\cdot Z_X(\tau)
		= 2\pi R\, Z_X(\tau)
	\end{aligned}
	\end{equation}
	We recover the partition function $V\cdot Z_X(\tau)$ for non-compact $X$, as expected.

	\item Using the Poisson resummation formula, we find that:
	\begin{equation}
	\begin{aligned}
		Z(\tau)
		&= 2\pi R\, Z_X(\tau) \sum_{m,w}
			\exp \pqty{
				- \frac{
					\pi R^2 \abs{m - w\tau}^2
				}{\alpha'\tau_2}
			}
	\end{aligned}
	\end{equation}
	$Z_X(\tau)$ is modular invariant by the properties of the Dedekind $\eta(\tau)$ function, as is demonstrated for the non-compact $X$ in \textit{Polchinski}.

	The sum, on the other hand, is naturally invariant under $T\colon \tau \mapsto \tau + 1$, by making a change of variables $m \mapsto m + w$. It is also invariant under $S\colon \tau \mapsto -1/\tau$ with $m \mapsto −w, w \mapsto m$\,\footnote{
		Reference: \textit{Polchinski}. 
	}. Therefore, $Z(\tau)$ is modular invariant.

	\end{enumerate}

	\item \textbf{$\mbb{Z}_2$ Orbifold}

	The $\mbb{Z}_2$ orbifold is constructed by imposing an additional identification on $X\in S^1$:
	\begin{equation}
		X\cong -X
	\end{equation}
	The target space is then reduced to $S^1/\mbb{Z}_2 \cong [0,\pi R]$.

	\begin{enumerate}
	\item The first contributions to the orbifold partition function comes from the states that are invariant reflection $r$; we have:
	\begin{equation}
		\Tr_{S^1/\mbb{Z}_2}
		= \Tr_{S^1} \frac{1 + r}{2}
		= \frac{1}{2}\,{\Tr_{S^1}}
			+ \frac{1}{2}\,{\Tr_{S^1}} \circ r
	\end{equation}
	Acting on $
		q^{L_0 - \tfrac{c}{24}}\,
		\bar{q}^{\tilde{L}_0 - \tfrac{\tilde{c}}{24}}
	$, the first term gives $\frac{1}{2}\,Z_{S^1}(\tau)$ where $Z_{S^1}$ is the $S^1$ partition function we've obtained in \boxed{1}\,.

	For the second term, note that:
	\begin{equation}
		r\colon\ %
				\ket{(N_l),(\tilde{N}_l);n,w}
			\longmapsto (−1)^{\sum_l (N_l + \tilde{N}_l)}
				\ket{(N_l),(\tilde{N}_l);-n,-w}
	\end{equation}
	In particular, it reverses $n,w$, hence $r$ insertion gives vanishing amplitude unless $n = w = 0$; the summation is very much similar to the $Z_{S^1}$ case, i.e. we have:
	\begin{equation}
	\begin{aligned}
		\frac{1}{2} \Tr_{S^1} \pqty\Big{
			r\,
			q^{L_0 - \tfrac{c}{24}}\,
			\bar{q}^{\tilde{L}_0 - \tfrac{\tilde{c}}{24}}
		}
		&= \frac{1}{2}\,(q\bar{q})^{-\frac{1}{24}}
			\prod_{l>0} \sum_{N_l,\tilde{N}_l = 0}^\infty
				(−1)^{N_l + \tilde{N}_l}
				q^{l\cdot N_l}
				\bar{q}^{\,l\cdot \tilde{N}_l} \\
		&= \frac{1}{2}\,(q\bar{q})^{-\frac{1}{24}}
			\prod_{l>0}
				\frac{1}{1 - (-q^l)}
				\frac{1}{1 - (-\bar{q}^{\,l})}
		= \abs{\frac{\eta(\tau)}{\theta_2(\tau)}}
	\end{aligned}
	\end{equation}
	Where we've used the fact that\footnote{
		Reference: Blumenhagen \& Plauschinn, \textit{Introduction to CFT}, and also \textit{Polchinski}. 
	}: $
		q^{-\frac{1}{24}}
		\prod_{l>0} \frac{1}{1 - (-q^l)}
		= \sqrt{2} \sqrt{
			\frac{\eta(\tau)}{\theta_2(\tau)}
		}
	$. Therefore, the total contributions from $r$--invariant states are:
	\begin{equation}
		\frac{1}{2}\,Z_{S^1}(\tau)
		+ \abs{\frac{\eta(\tau)}{\theta_2(\tau)}}
	\end{equation}

	\item With $X\cong -X$, new possibilities emerge as the boundary condition along $\sigma^1$:
	\begin{equation}
		X(\sigma^1 + 2\pi) \cong X(\sigma^1),\quad
		X(\sigma^1 + 2\pi) = \pm X(\sigma^1) + 2\pi Rw,\quad
		w\in\mbb{Z}
	\end{equation}
	The $\mquote{-}$ sign corresponds to the \textit{twisted states}. Due to the anti-periodicity, $\pd X$ has a half-integer mode expansion:
	\begin{gather}
		\allowdisplaybreaks
		\pd X\pqty{z\,e^{2\pi i}} = - \pd X(z),\\
		\pd X(z) =
			-i\,\sqrt{\frac{\alpha'}{2}}
			\sum_{m = -\infty}^\infty
				\frac{\alpha_{m-\frac{1}{2}}}
					{z^{m+\frac{1}{2}}},\quad
		\pdbar X(\bar{z}) =
			-i\,\sqrt{\frac{\alpha'}{2}}
			\sum_{m = -\infty}^\infty
				\frac{\tilde{\alpha}_{m-\frac{1}{2}}}
					{\bar{z}^{m+\frac{1}{2}}},\\
		X = x + i\,\sqrt{\frac{\alpha'}{2}}
			\sum_{m = -\infty}^\infty
				\frac{1}{m+\frac{1}{2}}
				\pqty{
					\frac{\alpha_{m+\frac{1}{2}}}
						{z^{m+\frac{1}{2}}}
					+ \frac{\tilde{\alpha}_{m+\frac{1}{2}}}
						{\bar{z}^{m+\frac{1}{2}}}
				},
	\end{gather}
	Apply the boundary condition on $X$, and we find that $x = \pi R w'$; however, due to the identification $X + 2\pi R \cong X \cong -X$, there are only two inequivalent choices: $x = 0$ and $x =\pi R$, which correspond to the string localized around either of the two fixed points of the $\mbb{Z}_2$ action.

	Much similar to the case in \boxed{1}\,, we have:
	\begin{gather}
		\bqty{
			\alpha_{\frac{1}{2} + l},
			\alpha_{- \frac{1}{2} - l}
		} = \frac{1}{2} + l,\\[1ex]
		L_{m\ne 0}
		= \frac{1}{2}
			\sum_l \alpha_{m - \frac{1}{2} - l}
					\alpha_{\frac{1}{2} + l},\quad
		L_0 = \frac{1}{2}\,\normorder{
			\sum_l \alpha_{-\frac{1}{2}-l}
					\alpha_{\frac{1}{2}+l}
		}
		\sim \sum_{l \ge 0}
				\alpha_{-\frac{1}{2}-l}
				\alpha_{\frac{1}{2}+l}
	\end{gather}
	We can use the same trick to fix the normal ordering constant in $L_0$; this time it is non-trivial:
	\begin{gather}
		L_{-1} = \frac{1}{2}\,
				\alpha_{-\frac{1}{2}}^2
			+ \sum_{l \ge 0}
				\alpha_{-\frac{1}{2}-l}
				\alpha_{\frac{1}{2}+l},\quad
		L_1 = \frac{1}{2}\,
				\alpha_{\frac{1}{2}}^2
			+ \sum_{l > 0}
				\alpha_{\frac{1}{2}-l}
				\alpha_{\frac{1}{2}+l}, \\
	\begin{aligned}
		L_0 \ket{0,0;x}
		&= \frac{1}{2}\,\pqty{
				L_1 L_{-1} - L_{-1} L_1
			} \ket{0,0;x} \\
		&= \frac{1}{2}\times \frac{1}{4}\,
				\alpha_{\frac{1}{2}}^2
				\alpha_{-\frac{1}{2}}^2
			\ket{0,0;x} - 0 \\
		&= \frac{1}{16} \ket{0,0;x},
	\end{aligned}
	\\[1ex]
		L_0
		= \frac{1}{16}
			+ \sum_{l \ge 0}
				\alpha_{-\frac{1}{2}-l}
				\alpha_{\frac{1}{2}+l}
		= \frac{1}{16}
			+ \sum_{l \ge 0}
				\pqty{l + \frac{1}{2}}\,
				N_{l + \frac{1}{2}}
		= \frac{1}{16}
			+ \sum_{l > 0}
				\pqty{l - \frac{1}{2}}\,
				N_{l - \frac{1}{2}},
	\end{gather}

	The trace can then be computed, following the same recipe as before:
	\begin{equation}
	\begin{aligned}
		\Tr_{S^1} \pqty{
			\frac{1 + r}{2}\,
			q^{L_0 - \tfrac{c}{24}}\,
			\bar{q}^{\tilde{L}_0 - \tfrac{\tilde{c}}{24}}
		}
		&= (q\bar{q})^{
				-\frac{1}{24} + \frac{1}{16}
			}
			\prod_{l + \frac{1}{2} \in \mbb{Z}^+}
			\sum_{N_l,\tilde{N}_l = 0}^\infty
				\frac{1 + (−1)^{N_l + \tilde{N}_l}}{2}\,
				q^{l\cdot N_l}
				\bar{q}^{\,l\cdot \tilde{N}_l} \times 2 \\
		&= \frac{1}{2}\,(q\bar{q})^{+\frac{1}{48}}
		\Bqty{\,
			\prod_{l>0}
				\abs{\frac{1}{1 - q^{l - \frac{1}{2}}}}^2
			+ \prod_{l>0}
				\abs{\frac{1}{1 + q^{l - \frac{1}{2}}}}^2
		}\times 2 \\
		&= \abs{\frac{\eta(\tau)}{\theta_4(\tau)}}
			+ \abs{\frac{\eta(\tau)}{\theta_3(\tau)}}
	\end{aligned}
	\end{equation}
	There is an extra factor of 2 from the number of twisted sectors: $x = 0$ and $x = \pi R$.

	\item The full partition function is therefore:
	\begin{equation}
		Z(\tau)
		= \frac{1}{2}\,Z_{S^1}(\tau)
			+ \abs{\frac{\eta(\tau)}{\theta_2(\tau)}}
			+ \abs{\frac{\eta(\tau)}{\theta_4(\tau)}}
			+ \abs{\frac{\eta(\tau)}{\theta_3(\tau)}}
	\end{equation}
	The first term is modular invariant, as is proved in \boxed{1}\,.

	The remaining terms are also modular invariant, due to the transformational properties of $\eta$ and $\theta$ functions\footnote{
		Reference: \textit{Blumenhagen \& Plauschinn}. 
	}:
	\begin{equation}
		T \circlearrowright
		\abs{\frac{\eta(\tau)}{\theta_2(\tau)}}
		\xleftrightarrow{\ S\ }
		\abs{\frac{\eta(\tau)}{\theta_4(\tau)}}
		\xleftrightarrow{\ T\ }
		\abs{\frac{\eta(\tau)}{\theta_3(\tau)}}
		\circlearrowleft S
	\end{equation}
	Therefore, the full partition function is modular invariant.

	\end{enumerate}

	\item \textbf{Torus 4-point function in $bc$ CFT}
	\begin{equation}
		\ave[\big]{
			c(w_1)\,b(w_2)\,
			\tilde{c}(\bar{w}_3)\,\tilde{b}(\bar{w}_4)
		}
		= \int \DD b\,\DD \tilde{b}\,
				\DD c\,\DD \tilde{c}\ %
			c(w_1)\,b(w_2)\,
			\tilde{c}(\bar{w}_3)\,\tilde{b}(\bar{w}_4)\,
			e^{-S'}
		\equiv Z'
	\end{equation}
	First we argue that only the zero modes of the insertions survive the path integral\footnote{
		I would like to thank \textit{谷夏} for some very helpful discussions about this problem.
	}. In fact, as anti-commuting replacements of the gauge degrees of freedom, ghost modes are \textit{defined} to be the eigenvalues of $P^\dagger P$, where $P$ is the conformal Killing differential\footnote{
		Reference: \textit{Polchinski}, Chapter 3 \& 5. 
	}. 
	More specifically, given a conformal Killing vector (CKV) $\var{\sigma^a}$, the conformal Killing equation can be written as:
	\begin{equation}
		P \var{\sigma} = 0
	\end{equation}
	While $P^\dagger \var'\! g = 0$ gives moduli variation $\var'\! g_{ab}$ of the metric. Roughly speaking, $P$ captures the variation of gauge fixing under an arbitrary gauge transformation; naturally, CKV's are given by $(\ker P)$, while $(\det P) \sim \Delta_{FP}$ is the Faddeev--Popov functional measure near the gauge slice. $(\det P)$ can then be calculated with:
	\begin{gather}
		\var{\sigma^a} \mapsto c^a,\quad
		\var'\! g_{ab} \mapsto b_{ab},\quad
		\Delta_{FP}
		\sim \det P
		\sim \int \DD b\,\DD \tilde{b}\,
				\DD c\,\DD \tilde{c}\ e^{-S'},\\
		S'
		= \frac{1}{2\pi} \int \dd[2]{\sigma}
			g^{1/2}\, b_{ab}\,(P\cdot c)^{ab}
		= \frac{1}{2\pi} \int \dd[2]{w}
			\pqty\big{
				b\,\pdbar_w c
				+ \tilde{b}\,\pd_w \tilde{c}
			}
	\end{gather}
	In the end we have chosen conformal gauge, such that\footnote{
		References:
		\begin{itemize}[
			labelindent=3em,labelsep=1pt,
			topsep=.1\baselineskip
		]
		\item Nakahara, \textit{Geometry, Topology and Physics}; 
		\item Blumenhagen et al, \textit{Basic Concepts of String Theory}. 
		\end{itemize}
	} $
		P \sim (\pdbar_w, \pd_w),\ %
		P^\dagger P \sim -\pdbar_w\pd_w = -\laplacian
	$. In the $w = \sigma^1 + i\sigma^2$ coordinates, CKV's are simple translations: $c^a = \mrm{const}$; with $z = e^{-iw}$, it gets mapped to $
		c^z
		= c^w \,\pd_w z
		= c^w \,(-iz)
	$, which agrees with the zero mode $c_0$ in the $c(z)$ expansion:
	\begin{equation}
		c(z)
		= \sum_{m = -\infty}^\infty
			\frac{c_m}{z^{m + 1 - \lambda}}
		= c_0\,z + \sum_{m \ne 0}
			\frac{c_m}{z^{m - 1}}
		,\quad \lambda = 2
		\label{eq:cghost_holomorphic}
	\end{equation}

	Now we are finally ready to prove our argument: for anti-commuting variables like $c(z)$, 
	\begin{equation}
		\int \DD{c}
		\sim \prod_m \int \dd{c_m}
		\sim \prod_m \pdv{c_m}
	\end{equation}
	Since $c_0$ corresponds to a CKV, $P \cdot c_0 = 0$, therefore it vanishes in $S' = \int \dd[2]{\sigma}\pqty{b\cdot P\cdot c}$; for the path integral to be non-zero, there has to be some additional $c_0$ insertions, i.e.
	\begin{equation}
		Z'
		\sim \int \DD b\,\DD \tilde{b}\,
				\DD c\,\DD \tilde{c}\ %
			c_0 b_0
			\tilde{c}_0 \tilde{b}_0\,
			e^{-S'}
		\sim \pqty{\frac{1}{\sqrt{\tau_2}}}^{\!\!4}\!\!
			\int \DD' b\,\DD' \tilde{b}\,
				\DD' c\,\DD' \tilde{c}\ %
			e^{-S'},\quad
		\int \DD' c
		\sim \prod_{m\ne 0} \int \dd{c_m}
	\end{equation}

	Note the additional $
		\pqty\big{\frac{1}{\sqrt{\tau_2}}}^4
	$ factor coming from the zero modes\footnote{
		Reference: \textit{Di Francesco et al}. 
	}; this has to do with the normalization of the zero modes, each contributing a factor of $\frac{1}{\sqrt{A}}$, where $A \sim \tau_2$ is the volume (surface area) of the torus. On a different note, since it is very difficult, if not impossible, to keep track of various (often divergent) constant factors in the path integral, we have been and will be calculating $Z'$ up to an overall constant coefficient.

	Now we have to deal with the path integral over non-zero modes. Note that the holomorphic mode expansion \eqref{eq:cghost_holomorphic} is incomplete for our purpose: it gives the \textit{on-shell} mode expansion, while our path integral should go over all possible configurations, including the off-shell modes, which is \textit{not} holomorphic. However, on $T^2 = S^1\times S^1$, the full modes are simple\footnote{
		References: (1) \textit{Nakahara}, (2) \textit{Di Francesco et al.}, and (3) \url{http://theory.uchicago.edu/~sethi/Teaching/P483-W2018/p483-sol3.pdf}. 
	}:
	\begin{gather}
		-\laplacian \psi_{n_1,n_2}
		= \lambda_{n_1,n_2} \psi_{n_1,n_2},
	\\[1ex]
	\begin{aligned}
		\psi_{n_1,n_2}
		&= \exp \pqty\big{
				i\,\pqty*{
					n_1\tilde{\sigma}^1
					+ n_2\tilde{\sigma}^2
				}
			},\quad
		\tilde{\sigma}^2
		= \frac{\sigma^2}{\tau_2},\quad
		\tilde{\sigma}^1
		= \sigma^1 - \sigma^2 \frac{\tau_1}{\tau_2}, \\[1ex]
		&= \exp \Bqty{
				i\,\pqty{
					n_1 \sigma^1
					+ \frac{n_2 - n_1 \tau_1}{\tau_2}\,
						\sigma^2
				}
			},
	\end{aligned}
	\end{gather}
	Here we first use the ``rectangular'' coordinates $(\tilde{\sigma}^1, \tilde{\sigma}^2) \in [0,2\pi]^2$ to write down the obvious eigen-functions $\psi_{n_1,n_2}$, and then relate them back to the $(\sigma^1,\sigma^2)$ coordinates. Therefore, we have:
	\begin{gather}
	\begin{aligned}
		\lambda_{n_1,n_2}
		&= \Bqty{
				n_1^2 + \pqty{
					\frac{n_2 - n_1 \tau_1}{\tau_2}
				}^{\!2}
			} \\
		&= \frac{1}{\tau_2^2}\,
			\Bqty{
				(n_1 \tau_2)^2 + \pqty\big{
					n_1 \tau_1 - n_2
				}^2
			} \\
		&= \frac{1}{\tau_2^2}\,
			\abs{n_1\tau - n_2}^2,
	\end{aligned}
	\\[.5ex]
		\det\nolimits' P
		\sim \pqty{\,
				\sideset{}{'}\prod_{n_1,n_2} 
					\sqrt{\lambda_{n_1,n_2}}
%					\frac{1}{\tau_2}\,
%					\abs{n_1\tau - n_2}
			}^2
		\sim \sideset{}{'}\prod_{n_1,n_2} 
			\lambda_{n_1,n_2}
	\end{gather}

	The determinant can be computed with $\zeta$-function regularization, as is performed in detail in \textit{Di Francesco}; the result can be nicely summarized using the Eisenstein series, as shown in \textit{Nakahara}:
	\begin{gather}
		E(\tau,s)
		= \sideset{}{'}\sum_{n_1,n_2} 
			\frac{\tau_2^s}{\abs{n_1\tau - n_2}^{2s}},
	\\
		\det\nolimits' P
		\sim \sideset{}{'}\prod_{n_1,n_2}
			\frac{1}{\tau_2^2}\,
			\abs{n_1\tau - n_2}^2
		\sim \tau_2 \exp \Bqty\Big{
				-\pdd{s} E'(\tau,s)_{s = 0}
			}
		= \tau_2^2\,\abs{\eta(\tau)}^4
	\end{gather}
	Finally, we have:
	\begin{equation}
		Z'
		\sim \tau_2^{-2} \det\nolimits' P
		\sim \tau_2^{-2} \tau_2^2\,\abs{\eta(\tau)}^4
		\sim \abs{\eta(\tau)}^4
	\end{equation}

	\item \textbf{Torus Propagator as a Trace}
	\begin{equation}
		w'\to 0,\quad
		\ave[\big]{\pdd{w} X(w)\,\pdd{w'} X(w')}
		= \Tr \pqty{
			\pdd{w} X(w)\,\pdd{w'} X(w')\,
			q^{L_0 - \tfrac{c}{24}}\,
			\bar{q}^{\tilde{L}_0 - \tfrac{\tilde{c}}{24}}
		}
	\end{equation}
	Here we've dropped the time ordering in the $w' \to 0$ limit. 
	Recall the mode expansion of $\pd X$ in \boxed{1}\,; we see that only the ``diagonal'' components of $
		\pd X(w)\,\pd X(w')
	$ survive in the trace, i.e.
	\begin{equation}
	\begin{aligned}
		\pdd{w} X(w)\,\pdd{w'} X(w')
		&= (\pdd{w} z)(\pdd{w'} z')\,
			\pdd{z} X(z)\,\pdd{z'} X(z')
		,\quad z = e^{-iw}
		,\quad 1\le\abs{z}\le e^{2\pi\tau_2} \\
		&\sim -\frac{\alpha'}{2}
			\sum_{n = -\infty}^\infty
				\frac{\alpha_{-n} \alpha_n}
					{z^{-n+1} z'^{n+1}}\,
				(-iz)(-iz') \\
		&= \frac{\alpha'}{2} \pqty{
				\alpha_0^2
				+ \sum_{n > 0}
					\pqty{
						\pqty\Big{\frac{z}{z'}}^{\!n}
						+ \pqty\Big{\frac{z'}{z}}^{\!\!n\,}
					}\, \alpha_{-n} \alpha_n
				+ \sum_{n > 0}
					n\,
					\pqty\Big{\frac{z'}{z}}^{\!\!n\,}
			}
		\\
		&= \frac{\alpha'}{2} \pqty{
				\alpha_0^2
				+ \sum_{n > 0}
					\pqty{
						\pqty\Big{\frac{z}{z'}}^{\!n}
						+ \pqty\Big{\frac{z'}{z}}^{\!\!n\,}
					}\, \alpha_{-n} \alpha_n
				+ \frac{zz'}{(z - z')^2}
			}
	\end{aligned}
	\end{equation}
	The last term is a normal ordering constant; here it is naturally regularized by $
		\pqty\big{\frac{z'}{z}}^{\!n\,}
	$.

	The $\alpha_0^2$ term can be substituted with spacetime momentum $p$; we have:
	\begin{gather}
		p = \sqrt{\frac{1}{2\alpha'}}\,
			\pqty\big{\alpha_0 + \tilde{\alpha}_0}
		= \sqrt{\frac{1}{2\alpha'}}\, 2\alpha_0
		= \sqrt{\frac{2}{\alpha'}}\, \alpha_0,
	\\[1ex]
	\begin{aligned}
		\pdd{w} X(w)\,\pdd{w'} X(w')
		&\sim \frac{\alpha'}{2} \pqty{
				\frac{\alpha' p^2}{2}
				+ \sum_{n > 0}
					\pqty{
						\pqty\Big{\frac{z}{z'}}^{\!n}
						+ \pqty\Big{\frac{z'}{z}}^{\!\!n\,}
					}\, n N_n
			}
	\end{aligned}
	\end{gather}
	On the other hand, the partition function is:
	\begin{equation}
	\begin{aligned}
		Z(\tau) = \ave{\idty}
		&= (q\bar{q})^{-\frac{1}{24}}
			\,V\!\!\int \frac{\dd{k}}{2\pi}\,
				e^{- \pi \tau_2\,\alpha' k^2}
			\!\!\!
			\sum_{(N_l),(\tilde{N}_l)}
				q^{
					\,\sum\limits_{l>0}  l\cdot N_l
				}
				\bar{q}^{
					\,\sum\limits_{l>0}  l\cdot \tilde{N}_l
				} \\
		&= (q\bar{q})^{-\frac{1}{24}}
			\,V\!\!\int \frac{\dd{k}}{2\pi}\,
				e^{- \pi \tau_2\,\alpha' k^2}
			\!\!\!
			\sum_{(N_l),(\tilde{N}_l)} \prod_{l>0}
				q^{l\cdot N_l}
				\bar{q}^{\,l\cdot \tilde{N}_l} \\
		&= \abs{\eta(\tau)}^{-2}
			\,V\!\!\int \frac{\dd{k}}{2\pi}\,
				e^{- \pi \tau_2\,\alpha' k^2}
			\!\!\!
	\end{aligned}
	\end{equation}

	We can work out $Z^{-1} \ave{\pd X \pd X}$ by considering term by term insertion of the $\pd X \pd X$ mode expansion into the above expression. For the $\frac{\alpha'p^2}{2}$ term, we have a contribution of:
	\begin{equation}
		\frac{\displaystyle
			\int \frac{\dd{k}}{2\pi}\,
				\frac{\alpha'k^2}{2}\,
				e^{- \pi \tau_2\,\alpha' k^2}
		}{\displaystyle
			\int \frac{\dd{k}}{2\pi}\,
				e^{- \pi \tau_2\,\alpha' k^2}
		}
		= \frac{\alpha'}{2}\,
			\frac{1}{2\cdot \pi\alpha'\tau_2}
		= \frac{1}{4\pi\tau_2}
	\end{equation}

	For the $nN_n$ insertion, we have a contribution of:
	\begin{equation}
	\begin{aligned}
%		\frac{1}{\abs{\eta(\tau)}^{-2}}
%		\cdot
%		(q\bar{q})^{-\frac{1}{24}}
%			\!\!\!
%			\sum_{(N_l),(\tilde{N}_l)}
%			\!\!
%				nN_n\,
%				q^{
%					\,\sum\limits_{l>0}  l\cdot N_l
%				}
%				\bar{q}^{
%					\,\sum\limits_{l>0}  l\cdot \tilde{N}_l
%				}
		\frac{\displaystyle
			\sum_{(N_l)}
				nN_n\,
				q^{
					\,\sum\limits_{l>0}  l\cdot N_l
				}
		}{\displaystyle
			\sum_{(N_l)}
				q^{
					\,\sum\limits_{l>0}^{\,}  l\cdot N_l
				}
		}
		&= \frac{\displaystyle
			\sum_{(N_l)}
				nN_n\,
				\prod_{l>0} q^{l\cdot N_l}
		}{\displaystyle
			\sum_{(N_l)}^{\,}
				\prod_{l>0} q^{l\cdot N_l}
		}
		= \frac{\displaystyle
			\sum_{N_n = 0}^\infty
				nN_n\, q^{n\cdot N_n}
		}{\displaystyle
			\sum_{N_n = 0}^\infty
				q^{n\cdot N_n}
		}
		= \frac{\displaystyle
			n q^n \pdv{(q^n)}
			\sum_{N_n = 0}^\infty q^{n\cdot N_n}
		}{\displaystyle
			\sum_{N_n = 0}^\infty q^{n\cdot N_n}
		} \\
		&= \frac{
			n q^n \pdv{(q^n)} \frac{1}{1 - q^n}
		}{
			\frac{1}{1 - q^n}
		}
		= \frac{n q^n}{1 - q^n}
	\end{aligned}
	\end{equation}
	Therefore, the complete result is given by:
	\begin{equation}
	\begin{aligned}
		\frac{1}{Z(\tau)}
		\ave[\big]{
			\pdd{w} X(w)\,\pdd{w'} X(w')
		}
		= {} & \frac{\alpha'}{2} \pqty{
				\frac{1}{4\pi\tau_2}
				+ \sum_{n > 0}
					\pqty{
						\pqty\Big{\frac{z}{z'}}^{\!n}
						+ \pqty\Big{\frac{z'}{z}}^{\!\!n\,}
					}\,
					\frac{n q^n}{1 - q^n}
				+ \frac{zz'}{(z - z')^2}
			} \\
		\xrightarrow[z'\to 1]{\, w'\to 0\ }\ &
			\frac{\alpha'}{2} \pqty{
				\frac{1}{4\pi\tau_2}
				+ \sum_{n > 0}
					\pqty{
						z^{n}
						+ z^{-n}
					}\,
					\frac{n q^n}{1 - q^n}
				+ \frac{z}{(z - 1)^2}
			}
	\end{aligned}
	\label{eq:propagator_diff_sum}
	\end{equation}

	On the other hand, the torus propagator is given by:
	\begin{gather}
		G'(w,\bar{w};w',\bar{w}')
		= - \frac{\alpha'}{2}\,
				\ln \abs{f(w - w',\tau)}^2
			+ \frac{\alpha'}{4\pi\tau_2}\,
				\pqty\big{\Im \pqty{w - w'}}^2,\\
		f(w,\tau) \equiv
		\theta_1 \pqty{
				\frac{w}{2\pi}
				\,\bigg\vert\,
				\tau
			}
		= 2\,e^{\frac{i\pi\tau}{4}} \sin \frac{w}{2}\,
			\prod_{m > 0}^\infty
				(1 - q^m)
				(1 - z^{-1}q^m)
				(1 - zq^m),\quad
		z = e^{-iw}
	\end{gather}
	We find that $
		\pdd{w} \pdd{w'} G'
	$ contains the same zero mode contribution $
		\frac{\alpha'}{8\pi\tau_2}
	$ and normal ordering contribution $
		\frac{\alpha'}{2} \frac{z}{(z - 1)^2}
	$ as in \eqref{eq:propagator_diff_sum}:
	\begin{gather}
		\pdd{w} \pdd{w'} G'(w,\bar{w};w',\bar{w}')_{
			w' = 0
		}
		= \frac{\alpha'}{8\pi\tau_2}
			+ \frac{\alpha'}{2}
				\pdd{w}^2 \ln f(w,\tau),
	\\[1ex]
		\pdd{w}^2 \ln f(w,\tau)
		= \pdd{w}^2 \ln \sin \frac{w}{2}
			+ \pdd{w}^2 \sum_{m > 0}  \pqty\Big{
				\ln \,(1 - zq^m)
				+ \ln \,(1 - z^{-1}q^m)
			},
	\\
		\pdd{w}^2 \ln \sin \frac{w}{2}
		= \pdd{w}^2 \ln \sin \frac{w}{2}
		= - \frac{1}{4\sin^2 \!\frac{w}{2}}
		= \frac{1}{2\,\pqty{\cos w - 1}}
		= \frac{1}{z + z^{-1} - 2}
		= \frac{z}{(z - 1)^2},
	\end{gather}

	The remaining parts come from oscillator modes; they also match with \eqref{eq:propagator_diff_sum}, but the equivalence is less obvious: we have\footnote{
		Reference: \url{http://theory.uchicago.edu/~sethi/Teaching/P483-W2018/p483-sol3.pdf}. I would like to thank {Lucy Smith} for providing this hint. 
	}:
	\begin{gather}
	\begin{aligned}
		\pdd{w}^2 \sum_{m > 0}
			\ln \,(1 - zq^m)
		&= \pdd{w}^2
			\sum_{m > 0}
			\sum_{n > 0}
				-\frac{1}{n}\,\pqty\big{zq^m}^n \\
		&= \sum_{n > 0}
				\pdd{w}^2 \pqty{-\frac{1}{n}\,z^n}
			\sum_{m > 0}
				q^{mn},\quad \pdd{w} = -iz\,\pdd{z} \\
		&= \sum_{n > 0}
				- \frac{(-in)^2}{n}\,z^n
				\cdot
				\frac{q^n}{1 - q^n} \\
		&= \sum_{n > 0}
				z^n \frac{nq^n}{1 - q^n},
	\end{aligned}
	\allowdisplaybreaks
	\\[1ex]
		\pdd{w}^2 \sum_{m > 0}
			\ln \,(1 - z^{-1} q^m)
		= \sum_{n > 0}
				z^{-n} \frac{nq^n}{1 - q^n},
	\end{gather}
	This is precisely the contribution from oscillator modes in \eqref{eq:propagator_diff_sum}. Therefore, we have:
	\begin{equation}
		\frac{1}{Z(\tau)}
		\ave[\big]{
			\pdd{w} X(w)\,\pdd{w'} X(w')
		}_{w' = 0}
		= \pdd{w} \pdd{w'}
			G'(w,\bar{w};w',\bar{w}')_{w' = 0}
	\end{equation}

	\end{enumerate}

\printbibliography[%
%	title = {参考文献} %
	,heading = bibintoc
]
\end{document}

### 2020-05-10 compile.sh
Fix $tex_program handling in compile.sh

@@ -26,6 +26,7 @@ for file in $FILES; do
         grep -E "^[ \t]*%[ ]*\!TeX[ ]*TS-program[ ]*=[ ]*" "$filename" \
         | cut -d '=' -f2 | xargs
     )
+    [[ -z $tex_program ]] && tex_program=xelatex
 
     if [[ $tex_program == pdflatex ]] \
     || [[ $tex_program == xelatex ]] \

### 2020-06-04 Strings2020/strings6/strings6.tex
Add strings6 [WIP], check CI for thermal3 bug

--- 2020-05-10 Strings2020/strings5/strings5.tex
@@
 % !TeX TXS-program:bibliography = biber -l zh__pinyin --output-safechars %
-%% !TeX TS-program = lualatex
+% !TeX TS-program = xelatex
 %%% LuaLaTeX is required for `tikz-feynman`
@@
 
-\newcommand{\hwNumber}{5}
+\newcommand{\hwNumber}{6 [WIP]}
 
@@
 %%% ID: sensitive, do NOT publish!
-\InputIfFileExists{../id.tex}{}{}
+%\InputIfFileExists{../id.tex}{}{}
 
@@
 \newcommand{\zbar}{\bar{z}}
-\usepackage{tikz-feynman,cancel}
+%\usepackage{tikz-feynman,cancel}
+
+\newcommand{\NS}{\ensuremath{\mrm{NS}}}
+\newcommand{\R}{\ensuremath{\mrm{R}}}
 
@@
 
-	\item \textbf{Partition Function for Compact Scalars}
+	\item \textbf{Type 0 Superstrings}
+
+	A closed superstring theory consists of sectors labeled by the boundary conditions of $(\psi,\tilde{\psi})$ along with suitable GSO projections $(-1)^F = \pm 1$.
+Here we follow the discussions of \textit{Polchinski}, with $\mrm{R}\colon \alpha = 1$ and $\mrm{NS}\colon \alpha = 0$.
+
+	There are also some consistency conditions: by modular invariance, there must be at least one left-moving R sector and at least one right-moving R sector; on the other hand, the OPE must close, and since $\mrm{R} \times \mrm{R} = \mrm{NS}$ there must be corresponding NS sector for each R sector.
+
+	If we includes only the (NS, NS) and the (R, R) sectors, then both must exist due to the above conditions.
+In fact, closure of OPE implies that the (\,NS$+$, NS$+$) sector must exist.
+In addition, NS$-$ sector must be paired with another NS$-$ sector due to the level matching condition of the closed string, i.e.
+it is possible to have a (\,NS$-$, NS$-$) sector.
+
+	The full possiblities can be generated by enumerating all possible (R, R) sectors (there is $2\times 2 = 4$ of them), while applying an extra consistency check that all pairs of vertex operators $O_1,O_2$ are mutually local, i.e.
+	\begin{equation}
+		\exp i\pi \pqty{
+				  F_1 \alpha_2
+				- F_2 \alpha_1
+				- \tilde{F}_1 \tilde{\alpha}_2
+				+ \tilde{F}_2 \tilde{\alpha}_1
+			}
+		= 1
+	\end{equation}
+	If $O_1 \in (\,\NS+, \NS+)$, then we have $\alpha_1 = \tilde{\alpha}_1 = 0 = F_1 = \tilde{F}_1$, hence the above factor is always trivial; for $O_1 \in (\R,\R)$, however, $\alpha_1 = \tilde{\alpha}_1 = 1$, which yields a non-trivial constraint for the second operator: $
+		F_2 - \tilde{F}_2
+		= F_1 \alpha_2 - \tilde{F}_1 \tilde{\alpha}_2
+		= \alpha_2 \pqty\big{F_1 - \tilde{F}_1}
+		\ (\mop{mod} 2)
+	$, assuming $\alpha_2 = \tilde{\alpha}_2$. With $\alpha_2 = 0$ this gives $F_2 = \tilde{F}_2$, and with $\alpha_2 = 1$ this gives $
+		F_2 - \tilde{F}_2
+		= F_1 - \tilde{F}_1
+	$, which means that all (R, R) sectors have the same sign difference between $F$ and $\tilde{F}$. The possible solutions can then be narrowed down to:
+	\begin{gather}
+		\mrm{0A}\colon\ %
+			(\,\NS+,\NS+),\ %
+			(\,\NS−,\NS−),\ %
+			(\,\R+,\R-),\ %
+			(\,\R−,\R+), \\
+		\mrm{0B}\colon\ %
+			(\,\NS+,\NS+),\ %
+			(\,\NS−,\NS−),\ %
+			(\,\R+,\R+),\ %
+			(\,\R−,\R−), \\
+		\text{And additionally, $(\,\NS+,\NS+)$ with any \textit{single one} of the 4 possible (R, R) sectors.}
+	\end{gather}
+
+	If there are two (R, R) sectors, then there must be an acompanying $(\,\NS−,\NS−)$ sector due to the closure of OPE.
+It is straight-foward to check that these possiblilities are all valid under the above constaints: (0) level matching of closed strings, (1) mutual locality, (2) closure of OPE, and (3) (apparent) modular invariance (not sufficient yet, to be checked below).
+
+	\begin{enumerate}
+	\item The torus partition function of the theory breaks up into a product of independent sums over the bosonic $X$ and fermionic $(\psi,\tilde{\psi})$ oscillators.
+The bosonic part is identical to the bosonic string situation, therefore modular invariant; to check the total partition function for modular invariance, we will look at the fermionic contributions $Z = Z_{\psi,\tilde{\psi}}$ explicitly.
+
+	Similar to the Type II case, the building block of $Z$ is given by:
+	\begin{equation}
+		Z\id{^\alpha_\beta}
+		= \Tr_\alpha \bqty{
+				(-1)^{\beta F} q^H
+			}
+	\end{equation}
+	Where $\alpha,\beta$ labels the periodicity in the spatial and temporal directions ($\sigma^1,\sigma^2$); note that for fermionic fields, anti-periodicity in the time direction gives the simple trace, while the periodic path integral gives the trace weighted by $(−1)^F̂$, as is explained in \textit{Polchinski}, Appendix A.
+	\end{enumerate}
+
+	\legacyReference
 

### 2020-06-04 compile.sh
Add revisions to thermal2 & 3, try to fix CI

@@ -1,22 +1,25 @@
 #!/bin/bash
 # shellcheck disable=2011
 
+function log { echo "### " "$@"; }
+
 [[ -n $1 ]] \
     && DIR=$1 \
     || DIR=$(dirname "$(readlink -f "$0")")
 
-echo "### $DIR"
+log "$DIR"
 ls | xargs
+mkdir -p release
 
 FILES=$(find . \
     -regex "./[^/]+/[^/]+/[^/]+.tex" \
     -not -path "./Templates/*"
 )
-echo "### Files:"
+log "Files:"
 echo "$FILES"
 
 for file in $FILES; do
-    echo "### Compiling \`$file\` ..."
+    log "Compiling \`$file\` ..."
 
     cd "$(dirname "$file")" || exit 1
     filename=$(basename "$file")
@@ -42,6 +45,10 @@ for file in $FILES; do
             "$filename"
     fi
 
+    log "Check & release PDF:"
+    pdf="$(basename "$filename" .tex).pdf"
+    ls "$pdf" \
+        && mv -v -f "$pdf" "$DIR/release/."
 
     cd "$DIR" || exit 1
 done

### 2020-06-04 compile.sh
Fix workflow permission, lock latex docker version
- Permission issue ref: https://vsupalov.com/docker-shared-permissions/
- Latest (latexmk + xelatex) tends to fail;
    lock version for now until further investigation;
- Also, cleanse stale files in `resources/homework` before every upload.

@@ -1,7 +1,7 @@
 #!/bin/bash
 # shellcheck disable=2011
 
-function log { echo "### " "$@"; }
+function log { echo "###" "$@"; }
 
 [[ -n $1 ]] \
     && DIR=$1 \
@@ -52,3 +52,6 @@ for file in $FILES; do
 
     cd "$DIR" || exit 1
 done
+
+ls -alF release
+cp README.md LICENSE release

### 2020-06-18 Strings2020/strings6/strings6.tex
Update strings6

@@
 
-\newcommand{\NS}{\ensuremath{\mrm{NS}}}
-\newcommand{\R}{\ensuremath{\mrm{R}}}
+% NS & R with spacing
+\newcommand{\NS}{\ensuremath{\mspace{2mu}\mrm{NS}}}
+\newcommand{\R}{\ensuremath{\mspace{2mu}\mrm{R}}}
+
+% representations
+\newcommand{\mbf}[1]{\mathbf{#1}}
 
@@
 
-	A closed superstring theory consists of sectors labeled by the boundary conditions of $(\psi,\tilde{\psi})$ along with suitable GSO projections $(-1)^F = \pm 1$.
+	A closed superstring theory consists of sectors labeled by the boundary conditions $(-1)^\alpha$ of $(\psi,\tilde{\psi})$ along with suitable GSO projections $(-1)^F = \pm 1$.
 Here we follow the discussions of \textit{Polchinski}, with $\mrm{R}\colon \alpha = 1$ and $\mrm{NS}\colon \alpha = 0$.
 
-	There are also some consistency conditions: by modular invariance, there must be at least one left-moving R sector and at least one right-moving R sector; on the other hand, the OPE must close, and since $\mrm{R} \times \mrm{R} = \mrm{NS}$ there must be corresponding NS sector for each R sector.
+	There are also some consistency conditions: by modular invariance, there must be at least one left-moving R sector and at least one right-moving R sector; on the other hand, the OPE must close, and since $\mrm{R} \times \mrm{R} = \mrm{NS}$ there must be some corresponding NS sector for each R sector.
 
 	If we includes only the (NS, NS) and the (R, R) sectors, then both must exist due to the above conditions.
-In fact, closure of OPE implies that the (\,NS$+$, NS$+$) sector must exist.
+In fact, closure of OPE implies that the $(\NS+, \NS+)$ sector must exist.
 In addition, NS$-$ sector must be paired with another NS$-$ sector due to the level matching condition of the closed string, i.e.
-it is possible to have a (\,NS$-$, NS$-$) sector.
-
-	The full possiblities can be generated by enumerating all possible (R, R) sectors (there is $2\times 2 = 4$ of them), while applying an extra consistency check that all pairs of vertex operators $O_1,O_2$ are mutually local, i.e.
+it is possible (but not required) to have a $(\NS-, \NS-)$ sector.
+
+	The full possiblities can then be generated by enumerating all possible (R, R) sectors (there are $2\times 2 = 4$ of them), while applying an extra consistency check that all pairs of vertex operators $O_1,O_2$ are mutually local, i.e.
 	\begin{equation}
@@
 		= F_1 - \tilde{F}_1
-	$, which means that all (R, R) sectors have the same sign difference between $F$ and $\tilde{F}$. The possible solutions can then be narrowed down to:
+	$; this means that all (R, R) sectors have the same sign difference between $F$ and $\tilde{F}$. The possible solutions can then be narrowed down to:
 	\begin{gather}
 		\mrm{0A}\colon\ %
-			(\,\NS+,\NS+),\ %
-			(\,\NS−,\NS−),\ %
-			(\,\R+,\R-),\ %
-			(\,\R−,\R+), \\
+			(\NS+,\NS+),\ %
+			(\NS−,\NS−),\ %
+			(\R+,\R-),\ %
+			(\R−,\R+), \\
 		\mrm{0B}\colon\ %
-			(\,\NS+,\NS+),\ %
-			(\,\NS−,\NS−),\ %
-			(\,\R+,\R+),\ %
-			(\,\R−,\R−), \\
-		\text{And additionally, $(\,\NS+,\NS+)$ with any \textit{single one} of the 4 possible (R, R) sectors.}
-	\end{gather}
-
-	If there are two (R, R) sectors, then there must be an acompanying $(\,\NS−,\NS−)$ sector due to the closure of OPE.
+			(\NS+,\NS+),\ %
+			(\NS−,\NS−),\ %
+			(\R+,\R+),\ %
+			(\R−,\R−), \\
+		\text{And additionally, $(\NS+,\NS+)$ with any \textit{single one} of the 4 possible (R, R) sectors.}
+		\label{eq:type0_deviant}
+	\end{gather}
+
+	If there are two (R, R) sectors, then there must be an acompanying $(\NS−,\NS−)$ sector due to the closure of OPE.
 It is straight-foward to check that these possiblilities are all valid under the above constaints: (0) level matching of closed strings, (1) mutual locality, (2) closure of OPE, and (3) (apparent) modular invariance (not sufficient yet, to be checked below).
@@
 				(-1)^{\beta F} q^H
-			}
+			},\quad
+		q = e^{2\pi i\tau}
 	\end{equation}
 	Where $\alpha,\beta$ labels the periodicity in the spatial and temporal directions ($\sigma^1,\sigma^2$); note that for fermionic fields, anti-periodicity in the time direction gives the simple trace, while the periodic path integral gives the trace weighted by $(−1)^F̂$, as is explained in \textit{Polchinski}, Appendix A.
+
+	In 10\,D, $\mu = 1,\cdots,10$, in total there are $
+		N = 10 - 2 = 4\times 2 = 8
+	$ real, \textit{transverse} spinor components in $(\psi^\mu,\tilde{\psi}^\mu)$; pairing them into complex chiral spinors like $\psi^1 \pm \psi^2$, each one of them contributes a factor of $Z\id{^\alpha_0}$ in the total partition function.
+
+	Note that for type II theories, the boundary conditions and GSO projections $(\alpha,F)$ for the left and right movers are ``decoupled''; any possible $(\alpha,F)$ can be paired with any possible $(\tilde{\alpha},\tilde{F})$, hence the left and right contributions can be calculated separately.
+For type 0 theories, however, the left and right $(\alpha,F)$'s are coupled, hence we have to calculate their contributions together.
+With the above considerations, we have:
+	\begin{equation}
+	\renewcommand{\NS}{\mrm{NS}} % no spacing
+	\renewcommand{\R}{\mrm{R}}   % no spacing
+	\begin{aligned}
+		\Tr_{(\NS,\NS)} \bqty{
+				\frac{1 + (-1)^{F-\tilde{F}}}{2}\,
+				q^H
+			}
+		&= \frac{1}{2}\, \Bqty\Big{
+				\Tr_{(\NS,\NS)} q^H
+				+ \Tr_{(\NS,\NS)}
+					\bqty{(-1)^{F-\tilde{F}} q^H}
+			} \\
+		&= \frac{1}{2}\, \Bqty{
+				\abs{(Z\id{^0_0})^{N/2}}^2
+				+ \abs{(Z\id{^0_1})^{N/2}}^2
+			} \\
+		&= \frac{1}{2}\, \Bqty{
+				\abs{Z\id{^0_0}}^N
+				+ \abs{Z\id{^0_1}}^N
+			},
+	\\[2ex]
+		\Tr_{(\R,\R)} \bqty{
+				\frac{1 \mp (-1)^{F-\tilde{F}}}{2}\,
+				q^H
+			}
+		&= \frac{1}{2}\, \Bqty\Big{
+				\Tr_{(\R,\R)} q^H
+				\mp \Tr_{(\R,\R)}
+					\bqty{(-1)^{F-\tilde{F}} q^H}
+			} \\
+		&= \frac{1}{2}\, \Bqty{
+				\abs{Z\id{^1_0}}^N
+				\mp \abs{Z\id{^1_1}}^N
+			},
+	\end{aligned}
+	\end{equation}
+	\begin{equation}
+		Z^{\mrm{0A|B}}
+		= \frac{1}{2}\, \Bqty{
+				\abs{Z\id{^0_0}}^N
+				+ \abs{Z\id{^0_1}}^N
+				+ \abs{Z\id{^1_0}}^N
+				\mp \abs{Z\id{^1_1}}^N
+			}
+	\end{equation}
+	Similarly, for the situation in \eqref{eq:type0_deviant} with no $(\NS-,\NS-)$ sector, 
+	depending on the GSO projections $(F,\tilde{F})$ in the single (R, R) sector, we have:
+	\begin{equation}
+	\let\bar\overline
+	\footnotesize
+	\begin{aligned}
+		Z'
+		&= \abs{\frac{1}{2}\,\pqty{
+				(Z\id{^0_0})^{N/2}
+				+ (Z\id{^0_1})^{N/2}
+			}}^2
+			+ \frac{1}{2}\,\pqty{
+				(Z\id{^1_0})^{N/2}
+				+ (-1)^F (Z\id{^1_1})^{N/2}
+			}
+			\cdot \frac{1}{2}\,\pqty{
+				(Z\id{^1_0})^{N/2}
+				+ (-1)^{\tilde{F}} (Z\id{^1_1})^{N/2}
+			}^* \\
+		&= \frac{1}{2}\, \Bqty{
+				Z^{0A|B}
+				+ \Re\,
+					(Z\id{^0_0} \bar{Z\id{^0_1}})^{N/2}
+				+ (-1)^{\tilde{F}} \pqty{\Re| \,i\Im}\,
+					(Z\id{^1_0} \bar{Z\id{^1_1}})^{N/2}
+			}
+	\end{aligned}
+	\end{equation}
+
+	To check for modular invariance, note that\footnote{
+		See \textit{Polchinski}, Chapter 10. Note that the factor $
+			\exp \pqty{
+				- i\pi\, \frac{3\alpha^2 - 1}{12}
+			}
+		$ comes from a global gravitational anomaly, but does not matter in $Z^{0A|B}$ since we are taking absolute values. 
+	}:
+	\begin{equation}
+		Z\id{^\alpha_\beta}(\tau)
+		= Z\id{^\beta_{-\alpha}}(-\tfrac{1}{\tau})
+		= Z\id{^\alpha_{\alpha + \beta - 1}}(\tau + 1)\,
+			\cdot \exp \pqty{
+				- i\pi\, \frac{3\alpha^2 - 1}{12}
+			}
+	\end{equation}
+	We see that $Z^{0A|B}$ is indeed modular invariant, while $
+		Z' = \frac{1}{2} Z^{0A|B}
+			+ \pqty{\cdots}
+	$ is \textit{not} modular invariant, due to the extra ``mixing'' terms in $(\cdots)$.
+
+	\item Consider the ground states in the type 0 theories; the NS ground state is tachyonic: 
+	\begin{equation}
+		m^2 = -k^2 = -\frac{1}{2\alpha'}
+	\end{equation}
+	With $(-1)^F = -1$, while the level 1 states are massless and form a vector representation $\mbf{8}_v$ of the massless little group $\mrm{SO}(8)$.
+After GSO projections, the NS ground state becomes the (NS$-$) ground state, while the level 1 massless states become the (NS$+$) ground states.
+
+	On the other hand, the R ground state is massless.
+In general, 10\,D Dirac spinors form a representation $\mbf{32}_{\mrm{Dirac}}$ of $\mrm{SO}(9,1)$; however, in the massless case it can be further reduced into two Weyl spinors $\mbf{16} + \mbf{16}'$, labeled by chirality $\Gamma^{11} = (-1)^F$.
+They are spinor representations of $\mrm{SO}(8)$.
+The on-shell condition (i.e.\ the Dirac equation) further reduces the representation into $\mbf{8}$ and $\mbf{8}'$, one for $(\R+)$ and one for $(\R-)$.
+
+	The closed string spectrum is then obtained by tensor product of the left and right moving part.
+For type 0 theories, we see that there is a tachyonic state: the $(\NS-,\NS-)$ ground state is a $\mbf{1}\times \mbf{1} = \mbf{1}$ scalar tachyon; with a momentum rescale $k\mapsto k/2$, the mass is now given by $m^2 = -2/\alpha'$.
+The remaining massless states are:
+	\begin{alignat}{2}
+		(\NS+,\NS+)\colon&\quad&
+			\mbf{8}_v \times \mbf{8}_v
+			&= [0] + [2] + (2) \\
+		(\R\pm,\R\pm)\colon&&
+			\mbf{8}^{(\prime)} \times \mbf{8}^{(\prime)}
+			&= [0] + [2] + [4]_\pm \\
+		(\R+,\R-)\colon&&
+			\mbf{8} \times \mbf{8}'
+			&= [1] + [3]
+	\end{alignat}
+	Where we've listed the irreducible decompositions of the various $\mbf{8} \times \mbf{8}$ tensor product, following the notations of \textit{Polchinski}.
+
+	\end{enumerate}
+
+	\item \textbf{Kaluza--Klein Mechanism}
+
+	The $D = d+1$ dimensional metric can be parameterized as follows:
+	\begin{gather}
+		\dd{s}^2
+		= G_{MN}^D \dd{x^M} \dd{x^N}
+		= G_{\mu\nu} \dd{x^\mu} \dd{x^\nu}
+			+ e^{2\sigma}\,\pqty{
+				\dd{x^d} + A_\mu \dd{x^\mu}
+			}^2,
+	\\
+		G^D_{\mu\nu}
+		= G_{\mu\nu} + e^{2\sigma} A_\mu A_\nu,\quad
+		x^d \cong x^d + 2\pi R
+	\end{gather}
+	Where $\mu = 0,1,\cdots,(d-1)$ labels the noncompact directions, and the $x^d$ direction is compactified.
+$G_{\mu\nu},\sigma$ and $A_\mu$ should depend only on the noncompact coordinates $x^\mu$, $A^\mu = G^{\mu\nu} A_\nu$.
+
+	$G_{MN}^D$ can be inverted by solving $
+		\delta^L_N
+		= G^{LM}_D G^D_{MN}
+	$, or in components:
+	\begin{gather}
+		0 = G_D^{\mu\nu}\, e^{2\sigma} A_\nu
+			+ G_D^{\mu d}\, e^{2\sigma}
+	\quad\Longrightarrow\quad
+		G_D^{\mu d}
+		= - G_D^{\mu\nu} A_\nu,
+	\\
+		1 = G_D^{\mu d}\, e^{2\sigma} A_\mu
+			+ G_D^{dd}\, e^{2\sigma}
+	\quad\Longrightarrow\quad
+		G_D^{dd}
+		= e^{-2\sigma} - G_D^{\mu d} A_\mu
+		= e^{-2\sigma} + G_D^{\mu\nu} A_\mu A_\nu,
+	\\
+		\delta^\mu_\rho
+		= G^{\mu\nu} G_{\nu\rho}
+		= G_D^{\mu\nu} G^D_{\nu\rho}
+			+ G_D^{\mu d}\, e^{2\sigma} A_\rho,
+	\end{gather}
+	Contract the last equation with $A^\rho$, and we can solve for $G_D^{\mu d}$ and then all other components. 
+	Alternatively, we can use the inversion formula for a block matrix\footnote{
+		See e.g.~\wikiref{https://en.wikipedia.org/wiki/Block\_matrix\#Block\_matrix\_inversion}{Block matrix \# Block matrix inversion}. 
+	}; either way, we obtain a nice and clean result:
+	\begin{equation}
+		G_D^{\mu d}
+		= -A^\mu,\quad
+		G_D^{dd}
+		= e^{-2\sigma} + A^2,\quad
+		G_D^{\mu\nu}
+		= G^{\mu\nu},
+	\end{equation}
+	There is also a formula\footnote{
+		See e.g.~\wikiref{https://en.wikipedia.org/wiki/Determinant\#Block\_matrices}{Determinant \# Block matrices}. 
+	} for the determinant $G_D$; we have:
+	\begin{equation}
+		G_D^{-1}
+		= G_d^{-1} \pqty{
+				e^{-2\sigma}
+				+ A^2 - A^2
+			}
+		= G_d^{-1} e^{-2\sigma},\quad
+		G_D
+		= G_d\, e^{2\sigma}
+	\end{equation}
+
+%	we have:
+%	\begin{equation}
+%	\begin{aligned}
+%		(\Gamma_D)^\lambda_{\mu\nu}
+%		&= G_D^{\lambda\rho}\,\Gamma_{\rho\mu\nu}
+%			+ G_D^{\lambda d}\cdot
+%			\frac{1}{2}\, \pqty\Big{
+%				\pdd{\mu} (e^{2\sigma} A_\nu)
+%				+ \pdd{\nu} (e^{2\sigma} A_\mu)
+%				- 0
+%			} \\
+%		&= \Gamma^\lambda_{\mu\nu}
+%			- A^\lambda e^{2\sigma}
+%				\pqty\Big{
+%					2A_{(\mu} \pdd{\nu)} \sigma
+%					+ \pdd{(\mu} A_{\nu)}
+%				},
+%	\end{aligned}
+%	\end{equation}
+%	\begin{equation}
+%	\begin{aligned}
+%		(\Gamma_D)^d_{\mu\nu}
+%		&= G_D^{\rho d}\,\Gamma_{\rho\mu\nu}
+%			+ G_D^{dd}\, e^{2\sigma}
+%				\pqty\Big{
+%					2A_{(\mu} \pdd{\nu)} \sigma
+%					+ \pdd{(\mu} A_{\nu)}
+%				} \\
+%		&= -A_\rho \Gamma^\rho_{\mu\nu}
+%			+ (1 + A^2 e^{2\sigma})
+%				\pqty\Big{
+%					2A_{(\mu} \pdd{\nu)} \sigma
+%					+ \pdd{(\mu} A_{\nu)}
+%				},
+%	\end{aligned}
+%	\end{equation}
+%	\begin{equation}
+%	\begin{aligned}
+%		(\Gamma_D)^\lambda_{\mu d}
+%		= (\Gamma_D)^\lambda_{d\mu}
+%		&= G^{\lambda\rho}\,\Gamma_{\rho\mu d}
+%			+ G_D^{\lambda d}\,\Gamma_{d\mu d} \\
+%		&= G^{\lambda\rho}\,
+%				\pdd{[\mu} \pqty{A_{\rho]} e^{2\sigma}}
+%			- A^\lambda\,\tfrac{1}{2}
+%				\pdd{\mu} e^{2\sigma} \\
+%		&= e^{2\sigma} \pqty\Big{
+%				G^{\lambda\rho}\, \pqty{
+%						\tfrac{1}{2} F_{\mu\rho}
+%						+ 2A_{[\rho} \pdd{\mu]} \sigma
+%					}
+%				- A^\lambda\,
+%					\pdd{\mu} \sigma
+%			} \\
+%		&= e^{2\sigma} \pqty{
+%				\tfrac{1}{2} F\id{_\mu^\lambda}
+%				- A_\mu \pd^\lambda \sigma
+%			},
+%	\end{aligned}
+%	\end{equation}
+%	\begin{equation}
+%	\begin{aligned}
+%		(\Gamma_D)^d_{\mu d}
+%		= (\Gamma_D)^d_{d\mu}
+%		&= e^{2\sigma} \pqty\Big{
+%				- A^\rho\, \pqty{
+%						\tfrac{1}{2} F_{\mu\rho}
+%						+ 2A_{[\rho} \pdd{\mu]} \sigma
+%					}
+%				+ (e^{-2\sigma} + A^2)\,
+%					\pdd{\mu} \sigma
+%			} \\
+%		&= e^{2\sigma} \pqty{
+%				- \tfrac{1}{2} F_{\mu\rho} A^\rho
+%				+ A_\mu A^\rho \pdd{\rho} \sigma
+%				+ e^{-2\sigma} \pdd{\mu}\sigma
+%			},
+%	\end{aligned}
+%	\end{equation}
+%	\begin{equation}
+%		(\Gamma_D)^\lambda_{dd}
+%		= G_D^{\lambda\rho}\,\Gamma_{\rho dd}
+%		= e^{2\sigma} \pd^\lambda \sigma,\quad
+%		(\Gamma_D)^d_{dd}
+%		= G_D^{d\rho}\,\Gamma_{\rho dd}
+%		= A^\lambda e^{2\sigma}
+%			\pdd{\rho} \sigma,
+%	\end{equation}
+
+	\begin{enumerate}
+	\item The Christoffel symbols can hence be calculated explicitly, using the $G^D_{MN}$ components; the Ricci scalar can then be computed with brute force\footnote{
+		Reference: \http{www.weylmann.com/kaluza.pdf}, and \textit{Polchinski}, Chapter 8. 
+	}; in the end, we have:
+	\begin{equation}
+		R_D = R_d
+			- 2e^{-\sigma}\laplacian e^\sigma
+			- \frac{1}{4} e^{2\sigma}
+				F_{\mu\nu} F^{\mu\nu},
+	\end{equation}
+	\vspace*{-.8\baselineskip}
+	\begin{equation}
+	\begin{aligned}
+		S
+		&= \frac{1}{2\kappa_0^2}
+			\int \dd[D]{x} \sqrt{-G_D}\, R_D \\
+		&= \frac{1}{2\kappa_0^2}\cdot 2\pi R
+			\int \dd[d]{x} \sqrt{-G_d}\, e^{\sigma}
+				R_D \\
+		&\sim \frac{\pi R}{\kappa_0^2}
+			\int \dd[d]{x} \sqrt{-G_d}\, e^{\sigma}
+			\pqty{
+				R_d
+				- \frac{1}{4} e^{2\sigma}
+					F_{\mu\nu} F^{\mu\nu}
+			}
+	\end{aligned}
+	\end{equation}
+	Here we've dropped the $
+		\laplacian e^\sigma
+	$ term in the Einstein--Hilbert action, for it is a total derivative:
+	\begin{equation}
+		\laplacian e^\sigma
+		= \frac{1}{\sqrt{-G_d}}\,
+			\pdd{\mu} \pqty{
+				\sqrt{-G_d}\, G_d^{\mu\nu}
+				\pdd{\nu} e^\sigma
+			}
+	\end{equation}
+	However, if there is a $D$-dimensional dilaton $\Phi$ coupled to gravity: $
+		\mcal{L}_D \sim e^{-2\Phi} R_D
+	$, then the $
+		e^{-2\Phi} \laplacian e^\sigma
+	$ term cannot be dropped, since it will contribute a $\Phi$--$\sigma$ coupling term. Here we are setting $\Phi\equiv 0$.
+
+	The $e^\sigma$ factor before $R_d$ can be absorbed by rescaling; first we eliminate the zero mode of $\sigma$ by rescaling the coupling $\kappa_0\to\kappa$:
+	\begin{gather}
+		\sigma = \sigma_0 + \sigma',\quad
+		\ave{\sigma} = \sigma_0,\quad
+		\ave{\sigma'} = 0,
+	\\
+		\frac{1}{\kappa_0^2}\, e^\sigma
+		= \frac{1}{\kappa^2}\, e^{\sigma'},\quad
+		\kappa
+		= \kappa_0\, e^{-\sigma_0/2},
+	\end{gather}
+	Then we work on the remaining $
+		\sigma' = \sigma - \sigma_0
+	$. Note that:
+	\begin{gather}
+		G'_{\mu\nu}
+		= e^{2\omega(x)} G_{\mu\nu},\quad
+		G'
+		= e^{2\omega\cdot d} G,\quad
+		G'^{\mu\nu}
+		= e^{-2\omega} G^{\mu\nu},
+	\\
+		R'_d
+		= e^{-2\omega} \pqty\Big{
+				R_d
+				- 2\,(d-1) \laplacian\omega
+				- (d-2)(d-1)\,
+					\pdd{\mu}\omega\,
+					\pd^\mu\omega
+			},
+	\\[1ex]
+		\sqrt{-G}\, e^{\sigma'} R_d
+		\sim \sqrt{-G'}\, R'_d
+		\sim \sqrt{-G}\, e^{(d-2)\omega} R_d,\quad
+		\omega
+		= \frac{\sigma'}{d - 2},
+	\end{gather}
+
+	Before we proceed, let's first work out the Weyl transformation of the Laplacian:
+	\begin{equation}
+	\begin{aligned}
+		\nabla'^2 \sigma'
+		&= \frac{1}{\sqrt{-G'}}\,
+			\pdd{\mu} \pqty{
+				\sqrt{-G'} G'^{\mu\nu}
+				\pdd{\nu} \sigma'
+			} \\
+		&= \frac{1}{\sqrt{-G}}\,
+			e^{-\omega d}\,
+			\pdd{\mu} \pqty{
+				\sqrt{-G}\,
+					e^{+\omega d}
+					e^{-2\omega}\,
+				G^{\mu\nu}
+				\pdd{\nu} \sigma'
+			} \\
+		&= e^{-\omega d}\,
+				(\pdd{\mu} e^{\sigma'})\,
+				G^{\mu\nu} \pdd{\nu} \sigma'
+			+ e^{-2\omega} \laplacian \sigma' \\
+		&= G'^{\mu\nu}
+				\pdd{\mu} \sigma'
+				\pdd{\nu} \sigma'
+			+ e^{-2\omega} \laplacian \sigma' \\
+	\end{aligned}
+	\end{equation}
+	The transformed Ricci scalar can then be rewritten as:
+	\begin{equation}
+	\begin{aligned}
+		R'_d
+		&= e^{-2\omega} R_d
+			- 2\,\frac{d-1}{d-2}\, e^{-2\omega}
+				\nabla^2 \sigma'
+			- \frac{d-1}{d-2}\,
+				\pdd{\mu}\sigma'\,
+				\pd'^\mu\sigma' \\
+		&= e^{-2\omega} R_d
+			- 2\,\frac{d-1}{d-2}
+				\pqty\Big{
+					\nabla'^2 \sigma'
+					- \pdd{\mu}\sigma'\,
+						\pd'^\mu\sigma'
+				}
+			- \frac{d-1}{d-2}\,
+				\pdd{\mu}\sigma'\,
+				\pd'^\mu\sigma' \\
+		&= e^{-2\omega} R_d
+			- 2\,\frac{d-1}{d-2}\,
+				\nabla'^2 \sigma'
+			+ \frac{d-1}{d-2}\,
+				\pdd{\mu}\sigma'\,
+				\pd'^\mu\sigma' \\
+	\end{aligned}
+	\end{equation}
+
+	Again, the $\nabla'^2 \sigma'$ term is a total derivative and can be dropped in the action. In the end, we get:
+	\begin{equation}
+	\begin{aligned}
+		S
+		&\sim \frac{\pi R}{\kappa^2}
+			\int \dd[d]{x} \sqrt{-G'_d}
+			\pqty{
+				R'_d
+				- \frac{d-1}{d-2}\,
+					\pdd{\mu}\sigma'\,
+					\pd'^\mu\sigma'
+				- \frac{1}{4}
+					e^{
+						2(\sigma \sidenote{+} \omega)
+					} F_{\mu\nu} F'^{\mu\nu}
+			}
+	\end{aligned}
+	\end{equation}
+	This is the effective $d$-dimensional theory that we have been looking for, with a gauge field $F_{\mu\nu}$ and a massless dilaton $\sigma'$.
+Roughly speaking, the dilaton $\sigma'$ can be treated as a Goldstone boson due to the breaking of scale invariance by compactification\footnote{
+		For a more careful discussion, see \textit{Polchinski}. See also \https{physics.stackexchange.com/q/138537}. 
+	}.
+
+	Following the convention of \textit{Polchinski}, we define $
+		A_\mu = R\tilde{A}_\mu,\ %
+		\rho = R e^\sigma,\ %
+		\rho_0 = \ave{\rho} = R e^{\sigma_0}
+	$, then the gravitational and gauge couplings are given by:
+	\begin{gather}
+		\frac{1}{2\kappa_d^2}
+		= \frac{\pi R}{\kappa^2},\quad
+		-\frac{1}{4 g_d^2}
+		= -\frac{1}{4}\,
+			e^{2\ave{\sigma + \omega}} R^2
+			\cdot\frac{\pi R}{\kappa^2}
+		= -\frac{1}{4}\, e^{2\sigma_0} R^2
+			\cdot \frac{1}{2\kappa_d^2},
+	\\[.5ex]
+		\therefore\quad
+		\kappa_d^2
+		= \frac{\kappa^2}{2\pi R}
+		= \frac{\kappa_0^2}{2\pi \rho_0},\quad
+		g_d^2
+		= \frac{2\kappa_d^2}{\rho_0^2}
+		= \frac{\kappa_0^2}{\pi \rho_0^3},\quad
+		\rho_0
+		= R e^{\sigma_0}
+	\end{gather}
+
+	\item The above mechanism provides a natural theory of gravity and electromagnetism in $d = 4$. Note that the gravitational and gauge couplings are related with the radius of the compact dimension:
+	\begin{equation}
+		\frac{g_d^2}{\kappa_d^2}
+		= \frac{2}{\rho_0^2}
+	\end{equation}
+	In reality gravity is much weaker than electromagnetism, which means that $\rho_0 \to 0$, or $R\to 0$ if we gauge-fix $\sigma_0 \equiv 0$.
+In other words, the radius is constrained by the ratio of the couplings:
+	\begin{equation}
+		R \sim \sqrt{2}\,\frac{\kappa_d}{g_d}
+	\end{equation}
 	\end{enumerate}

### 2020-06-19 Strings2020/strings6/strings6.tex
Add strings6 & update advqft2
... about FP quantization

@@
 			}^2,
+	\label{eq:metric_decomp}
 	\\
@@
 		x^d \cong x^d + 2\pi R
+	\label{eq:sub_metric_convention}
 	\end{gather}
@@
 	\end{equation}
+
+	\end{enumerate}
+
+	\item \textbf{Fiberwise T-Duality and the Dilaton}
+	\begin{enumerate}
+	\item For a bosonic string moving in a general background of massless fields in $D = d + 1 = 26$, its worldsheet action is given by:
+	\begin{equation}
+		S = \frac{1}{4\pi\alpha'}
+			\int \dd[2]{\sigma} \sqrt{g}\,
+			\Bqty\Big{
+				\pqty{
+					g^{ab} G_{MN}(X)
+					+ i\epsilon^{ab} B_{MN}(X)
+				}\,
+				\pdd{a} X^M
+				\pdd{b} X^N
+				+ \alpha'\mcal{R}\,\Phi(X)
+			}
+	\end{equation}
+	Where $\Phi$ is the worldsheet Ricci scalar. The $X^{25}$ direction is to be compactified, and the background fields $G_{MN}, B_{MN}$ and $\Phi$ depends only on $X^\mu,\,\mu = 0,1,\cdots,(d-1) = 24$.
+
+	$G_{MN}$ can be further split into $G_{\mu\nu},G_{\mu d}$ and $G_{dd}$ with $d = 25$, in a way similar to \eqref{eq:metric_decomp}, but here we are using a simpler convention, with $G^D_{\mu\nu} = G_{\mu\nu}$ instead of \eqref{eq:sub_metric_convention}.
+Similar goes for $B_{MN}$, with $B_{\mu\nu},B_{\mu d}$, and $B_{dd} = 0$, due to anti-symmetricity.
+
+	\item After replacing $\pdd{a} X^d\mapsto \pdd{a} X^d + A_a$ where $A_a$ is an auxilary abelian gauge field on the worldsheet, the $X^d$ related parts in the Lagrangian become:
+	\begin{equation}
+	\small
+	\begin{aligned}
+		\mcal{L}_d[X^d,A_a]
+		&= \frac{\sqrt{g}}{4\pi\alpha'}
+			\Bqty\Big{
+				2\,\pqty{
+					g^{ab} G_{\mu d}
+					+ i\epsilon^{ab} B_{\mu d}
+				}
+					\,(\pdd{a} X^d + A_a)\,
+					\pdd{b} X^\mu
+				+ g^{ab} G_{dd}
+					\,(\pdd{a} X^d + A_a)\,
+					\,(\pdd{b} X^d + A_b)
+			} \\
+	\end{aligned}
+	\end{equation}
+
+	Consider a translation $
+		X^d\mapsto X^d + \lambda
+	$, where $\lambda$ depends on $X^\mu = X^\mu(\sigma)$ and hence depends on the worldsheet coordinates $\sigma$; it is clear that:
+	\begin{gather}
+		\pdd{a} \pqty{X^d + \lambda}
+			+ \pqty{A_a - \pdd{a}\lambda}
+		= \pdd{a} X^d + A_a,
+	\quad
+		\mcal{L}_d \bqty{
+			\pqty{X^d + \lambda},
+			\pqty{A_a - \pdd{a}\lambda}
+		}
+		= \mcal{L}_d\bqty{
+			X^d, A_a
+		}
+	\end{gather}
+	i.e.\ $X^d$ translation is equivalent to a local gauge transformation $A_a\mapsto A_a - \pdd{a}\lambda$.
+
+	In fact, we would like $A_a$ to be ``pure gauge'', capturing only the $X^d$ translational symmetry and nothing more; this can be achieved by adding yet another auxilary field $\phi(\sigma)$ and an extra term:
+	\begin{equation}
+		\mcal{L}_d
+		\longmapsto \mcal{L}_d
+			+ i\epsilon^{ab} F_{ab}\,\phi,
+	\quad
+		F_{ab}
+		= \pdd{a} A_b - \pdd{b} A_a,
+	\quad
+		\int \DD{\phi}\,
+			e^{-i\epsilon^{ab} F_{ab}\,\phi}
+		\sim \delta\bqty{
+				\epsilon^{ab} F_{ab}
+			}
+	\end{equation}
+	Which forces $F_{12} \equiv 0$ in the remaining path integral.
+Note that the only non-zero independent component of $F_{ab}$ in 2D is $F_{12}$, therefore $F_{12} \equiv 0$ implies that $F_{ab} \equiv 0$, or $
+		F = \dd{A} = 0
+	$. On the plane, this implies that $A = \dd{\lambda}$, i.e.\ it is indeed pure gauge\footnote{
+		However, if there are punctures on the worldsheet, then there is non-trivial cohomology, and $A$ need not be $\dd{\lambda}$.
+I have not yet understood how this would affect our result; this problem is also acknowledged in \textit{Blumenhagen et al}, Chapter 14, yet it seems to simply ignore such issue.
+	}.
+
+%	\begin{equation}
+%		\int \DD{X}\,\DD{A_a}\,\DD{\phi}\,
+%			e^{-S'}
+%	\end{equation}
+
+	We can then proceed to integrate out $A_a$. Since $A = \dd{\lambda}$, we can gauge fix $A \equiv 0$, and the action reduces to the original one:
+	\begin{equation}
+		S'\bqty{X,\phi=0,A_a=0}
+		= S\bqty{X}
+	\end{equation}
+	Following the Faddeev--Popov procedure, we find that the path integral also reduces to the original one, up to some additional gauge volume determinant $\Delta_{FP}$, which is independent of $X$.
+This implies that the theory for the fields $(X,\phi,A_a)$ is, indeed, equivalent to that of the original string theory which has only the $X$ fields.
+
+	\item Following our discussions in (b), we see that:
+	\begin{equation}
+		\pdd{a} X^d + A_a
+		= 0 + A_a - \pdd{a} \lambda,\quad
+		\lambda = -\pdd{a} X^d,
+%	\\
+%		\int \DD{X^d}\,
+%			e^{-S'[X,\phi,A]}
+%		= \int \DD{\lambda}\,
+%			e^{-S'[X^d\equiv 0,\phi,A_\lambda]},\quad
+%		A_\lambda = A - \dd{\lambda},
+	\end{equation}
+%	i.e.\ integrating over $X^d$ is equivalent to integrating over all the gauge configurations of $A$, labeled by $\lambda$, but with $X^d \equiv 0$. 
+	Before completing the path integral, we perform a gauge transformation $
+		A_a \mapsto A_a - \pdd{a} \lambda
+	$, with $\lambda =  -X^d$.
+Assuming that there is no anomaly, we can ignore the functional Jacobian of the transformation, and the path integral shall be gauge invariant; in this case, the $\pdd{a} X^d$ term is canceled precisely by the gauge transformation, which is equivalent to setting $X^d = 0$ in the action:
+	\begin{equation}
+		S''\bqty{
+				X^\mu,\phi,A
+			}
+		= S'\bqty{
+				X^\mu,X^d = 0,\phi,A
+			}
+	\end{equation}
+
 	\end{enumerate}

### 2020-06-22 Strings2020/strings6/strings6.tex
Complete strings6

@@
+% !TeX document-id = {39d24ce0-844d-44a8-943b-2a9698211621}
 % !TeX encoding = UTF-8
@@
 
-\newcommand{\hwNumber}{6 [WIP]}
+\newcommand{\hwNumber}{6}
 
@@
 %%% ID: sensitive, do NOT publish!
-%\InputIfFileExists{../id.tex}{}{}
+\InputIfFileExists{../id.tex}{}{}
 
@@
 \newcommand{\mbf}[1]{\mathbf{#1}}
+
+\addbibresource{strings6.bib}
 
@@
 
-	If we includes only the (NS, NS) and the (R, R) sectors, then both must exist due to the above conditions.
+	If we include only the (NS, NS) and the (R, R) sectors, then both must exist due to the above conditions.
 In fact, closure of OPE implies that the $(\NS+, \NS+)$ sector must exist.
@@
 
-	The full possiblities can then be generated by enumerating all possible (R, R) sectors (there are $2\times 2 = 4$ of them), while applying an extra consistency check that all pairs of vertex operators $O_1,O_2$ are mutually local, i.e.
+	All possibilities can then be generated by enumerating all possible (R, R) sectors (there are $2\times 2 = 4$ of them), while applying an extra consistency check that all pairs of vertex operators $O_1,O_2$ are mutually local, i.e.
 	\begin{equation}
@@
 
-	If there are two (R, R) sectors, then there must be an acompanying $(\NS−,\NS−)$ sector due to the closure of OPE.
-It is straight-foward to check that these possiblilities are all valid under the above constaints: (0) level matching of closed strings, (1) mutual locality, (2) closure of OPE, and (3) (apparent) modular invariance (not sufficient yet, to be checked below).
+	If there are two (R, R) sectors, then there must be an accompanying $(\NS−,\NS−)$ sector due to the closure of OPE.
+It is straightforward to check that these possibilities are all valid under the above constraints: (0) level matching of closed strings, (1) mutual locality, (2) closure of OPE, and (3) (apparent) modular invariance (not sufficient yet, to be checked below).
 
@@
 	\end{equation}
-	Where $\Phi$ is the worldsheet Ricci scalar. The $X^{25}$ direction is to be compactified, and the background fields $G_{MN}, B_{MN}$ and $\Phi$ depends only on $X^\mu,\,\mu = 0,1,\cdots,(d-1) = 24$.
+	Where $\Phi$ is the worldsheet Ricci scalar.
+The $X^d \equiv X^{25}$ direction is to be compactified, and the background fields $G_{MN}, B_{MN}$ and $\Phi$ depends only on $X^\mu,\,\mu = 0,1,\cdots,(d-1) = 24$.
 
 	$G_{MN}$ can be further split into $G_{\mu\nu},G_{\mu d}$ and $G_{dd}$ with $d = 25$, in a way similar to \eqref{eq:metric_decomp}, but here we are using a simpler convention, with $G^D_{\mu\nu} = G_{\mu\nu}$ instead of \eqref{eq:sub_metric_convention}.
-Similar goes for $B_{MN}$, with $B_{\mu\nu},B_{\mu d}$, and $B_{dd} = 0$, due to anti-symmetricity.
-
-	\item After replacing $\pdd{a} X^d\mapsto \pdd{a} X^d + A_a$ where $A_a$ is an auxilary abelian gauge field on the worldsheet, the $X^d$ related parts in the Lagrangian become:
+Similar goes for $B_{MN}$, with $B_{\mu\nu},B_{\mu d}$, and $B_{dd} = 0$, due to anti-symmetry.
+
+	\item After replacing $\pdd{a} X^d\mapsto \pdd{a} X^d + A_a$ where $A_a$ is an auxiliary abelian gauge field on the worldsheet, the $X^d$ related parts in the Lagrangian become:
 	\begin{equation}
@@
 					\,(\pdd{b} X^d + A_b)
-			} \\
+			}
 	\end{aligned}
@@
 
-	In fact, we would like $A_a$ to be ``pure gauge'', capturing only the $X^d$ translational symmetry and nothing more; this can be achieved by adding yet another auxilary field $\phi(\sigma)$ and an extra term:
+	In fact, we would like $A_a$ to be ``pure gauge'', capturing only the $X^d$ translational symmetry and nothing more; this can be achieved by adding yet another auxiliary field $\phi(\sigma)$ and an extra term:
 	\begin{equation}
@@
 		However, if there are punctures on the worldsheet, then there is non-trivial cohomology, and $A$ need not be $\dd{\lambda}$. 
-I have not yet understood how this would affect our result; this problem is also acknowledged in \textit{Blumenhagen et al}, Chapter 14, yet it seems to simply ignore such issue.
+		Instead, the gauge field can have non-trivial holonomy around the cycles of the worldsheet.
+One can show that these holonomies are gauge trivial if $\phi$ has periodicity $2\pi$.
+In this case, the partition function is again equivalent to the original one.
+Reference: \textit{Tong}, String Theory; see also \arxiv{0812.4408}.
 	}.
@@
 	\begin{equation}
-		S''\bqty{
+		S\bqty{
 				X^\mu,\phi,A
@@
 
-	\end{enumerate}
-
-	\legacyReference
-
-	\begin{enumerate}
-	\item Mode expansion of $X$ CFT is\footnote{
-		Again we follow the convention of \textit{Polchinski}. 
+	Furthermore, the $A_a$ related parts in the Lagrangian is now nice and quadratic:
+	\begin{equation}
+%	\small
+	\begin{aligned}
+		\mcal{L}_A
+		&= \frac{\sqrt{g}}{4\pi\alpha'}
+			\Bqty\Big{
+				2\,\pqty{
+					g^{ab} G_{\mu d}
+					+ i\epsilon^{ab} B_{\mu d}
+				}\,A_a\,\pdd{b} X^\mu
+				+ g^{ab} G_{dd}\, A_a A_b
+				+ i\epsilon^{ab} F_{ab}\,\phi
+			} \\
+		&= \frac{\sqrt{g}}{4\pi\alpha'}
+			\Bqty\Big{
+				2\,\pqty{
+					g^{ab} G_{\mu d}
+					- i\epsilon^{ab} B_{\mu d}
+				}\,\pdd{a} X^\mu A_b
+				+ g^{ab} G_{dd}\, A_a A_b
+				+ 2i\epsilon^{ab} \phi\, \pdd{a} A_b
+			} \\
+		&\sim \frac{1}{4\pi\alpha'}
+			\Bqty\Big{
+				2\,\pqty{
+					\delta^{ab} G_{\mu d}
+					- i\epsilon^{ab} B_{\mu d}
+				}\,\pdd{a} X^\mu A_b
+				+ \delta^{ab} G_{dd}\, A_a A_b
+				- 2i\epsilon^{ab}
+					\,\pdd{a}\phi\, A_b
+			} \\
+		&= \frac{1}{4\pi\alpha'}
+			\Bqty\Big{
+				2\,\pqty\Big{
+					\pqty{
+						\delta^{ab} G_{\mu d}
+						- i\epsilon^{ab} B_{\mu d}
+					}\,\pdd{a} X^\mu
+					- i\epsilon^{ab} \,\pdd{a}\phi
+				} A_b
+				+ \delta^{ab} G_{dd}\, A_a A_b
+			}
+	\end{aligned}
+	\end{equation}
+	Here we've fixed the conformal gauge $g_{ab} = \delta_{ab}$ and integrated by parts, so that $
+		\phi\, \pdd{a} A_b
+		\mapsto -\pdd{a}\phi\, A_b
+	$.
+
+	It is convenient to define\footnote{
+		Reference: \textit{Blumenhagen et al}, Basic Concepts of String Theory, Chapter 14. 
 	}:
+	\begin{equation}
+	\begin{aligned}
+		J^b
+		&= \frac{1}{G_{dd}} \pqty\Big{
+				\pqty{
+					\delta^{ab} G_{\mu d}
+					- i\epsilon^{ab} B_{\mu d}
+				}\,\pdd{a} X^\mu
+				- i\epsilon^{ab} \,\pdd{a}\phi
+			}
+	\end{aligned}
+	\end{equation}
+	The path integral over $A_a$ can then be completed as a Gaussian integral.
+Note that this time we integrate out $A_a$ first, leaving $\phi$ in place; therefore we do not impose any gauge fixing.
+We have:
 	\begin{gather}
-		\pd X(z) =
-			-i\,\sqrt{\frac{\alpha'}{2}}
-			\sum_{m = -\infty}^\infty
-				\frac{\alpha_m}{z^{m+1}},\quad
-		\pdbar X(\bar{z}) =
-			-i\,\sqrt{\frac{\alpha'}{2}}
-			\sum_{m = -\infty}^\infty
-				\frac{\tilde{\alpha}_m}{\bar{z}^{m+1}},\\
-		X = x
-			- i\,\sqrt{\frac{\alpha'}{2}}
-			\,\pqty\big{
-				\alpha_0 \ln z
-				+ \tilde{\alpha}_0 \ln \bar{z}
-			}
-			+ i\,\sqrt{\frac{\alpha'}{2}}
-			\sum_{m \ne 0}
-				\frac{1}{m}
-				\pqty{
-					\frac{\alpha_m}{z^m}
-					+ \frac{\tilde{\alpha}_m}{\bar{z}^m}
+		\mcal{L}_A
+		= \frac{G_{dd}}{4\pi\alpha'}
+			\Bqty\Big{
+				2J^b A_b
+				+ \delta^{ab} A_a A_b
+			}
+		= \frac{G_{dd}}{4\pi\alpha'}
+			\Bqty\Big{
+				(A + J)^2
+				- \delta^{ab} J_a J_b
+			},
+	\\[1ex]
+		S = \int \dd[2]{\sigma} \pqty\big{
+				\mcal{L}_A + \mcal{L}_0
+			},
+	\quad
+		\int \DD{A_a}\,e^{-S}
+		\sim \det \bqty{
+				\frac{
+					G_{dd}\pqty\big{X^\mu(\sigma)}
+				}{2\pi\alpha'}
+			}^{-\frac{1}{2}} e^{-\tilde{S}},
+	\\[.5ex]
+		\tilde{S} = \int \dd[2]{\sigma} \pqty{
+				\mcal{L}_0
+				- \frac{G_{dd}}{4\pi\alpha'}\,
+					J^a J_a
 			},
 	\end{gather}
-	Momentum $p$ is the charge for \textit{spacetime} translation; we have:
+
+	If we identify $X^d \cong X^d + 2\pi$, then the radius of the $X^d$ circle is given by $R(X^\mu) = \sqrt{G_{dd}}$.
+When $R^2 \gg \alpha'$ or $R \gg \sqrt{\alpha'}$, the above path integral approaches the classical limit, and its main contribution comes from the classical saddle $A_a = -J_a$, which is included in the $e^{-\tilde{S}}$ factor.
+The functional determinant is sub-leading and can be ignored.
+
+	Expand the action $\tilde{S}$ in terms of $(X^\mu,\phi)$, we find that:
 	\begin{gather}
-		X\mapsto X + \mrm{const},\quad
-		j_a = \frac{i}{\alpha'}\,\pdd{a} X,
+		\tilde{S} = \frac{1}{4\pi\alpha'}
+			\int \dd[2]{\sigma}
+			\Bqty\Big{
+				\pqty{
+					\delta^{ab} \tilde{G}_{MN}
+					+ i\epsilon^{ab} \tilde{B}_{MN}
+				}\,
+				\pdd{a} \tilde{X}^M
+				\pdd{b} \tilde{X}^N
+%				+ \alpha'\mcal{R}\,\Phi(X)
+			},\quad
+		\tilde{X}
+		= (\tilde{X}^\mu,\tilde{X}^d)
+		= (X^\mu,\phi),
 	\\
-		p = \frac{1}{2\pi i} \oint_C \pqty{
-				\dd{z} j - \dd{\bar{z}} \tilde{j}\,
-			}
-		= \frac{1}{\alpha'} \sqrt{\frac{\alpha'}{2}}\,
-			\pqty\big{\alpha_0 + \tilde{\alpha}_0}
-		= \sqrt{\frac{1}{2\alpha'}}\,
-			\pqty\big{\alpha_0 + \tilde{\alpha}_0}
-	\end{gather}
-
-	Additionally, for compact free boson, $X$ is only defined modulo $2\pi R$; therefore, states after $X + 2\pi R$ translation should be identical to the original states, i.e.
-	\begin{equation}
-		e^{ip\,(2\pi R)} = \idty,\quad
-		p = \frac{n}{R},\quad n\in\mbb{Z}
-	\end{equation}
-	This, in fact, holds for any field theory\footnote{
-		Reference: discussions in \textit{Polchinski}, Chapter 8. 
-	} defined for $X\in S^1$, including the ordinary quantum mechanics (a classical field theory) on $S^1$.
-
-	On the other hand, there are additional constraints in string theory: for the state of a \textit{single} closed string, there is a discrete translational symmetry on the \textit{worldsheet}:
-	\begin{equation}
-		X(\sigma^1 + 2\pi) \cong X(\sigma^1),\quad
-		X(\sigma^1 + 2\pi) = X(\sigma^1) + 2\pi Rw,\quad
-		w \in\mbb{Z}
-	\end{equation}
-	With some definite winding number $w$. In $(z,\bar{z})$ coordinates, we have:
-	\begin{gather}
-		2\pi Rw
-		= X\pqty{
-				z\,e^{2\pi i},\zbar\,e^{-2\pi i}\,
-			} - X(z,\zbar)
-		= -i\sqrt{\frac{\alpha'}{2}}\,
-			2\pi i\,\pqty\big{
-				\alpha_0 - \tilde{\alpha}_0
-			}
-		= 2\pi\sqrt{\frac{\alpha'}{2}}\,
-			\pqty\big{
-				\alpha_0 - \tilde{\alpha}_0
+		\tilde{G}_{dd}
+		= \frac{1}{G_{dd}},\quad
+		\tilde{G}_{\mu d}
+		= \frac{1}{G_{dd}} B_{\mu d},\quad
+		\tilde{G}_{\mu\nu}
+		= G_{\mu\nu}
+			- \frac{1}{G_{dd}} \pqty\big{
+				G_{\mu d} G_{\nu d}
+				- B_{\mu d} B_{\nu d}
 			},
 	\\
-		p = \frac{p_L + p_R}{2},\quad
-		p_L = \sqrt{\frac{2}{\alpha'}}\,\alpha_0,\quad
-		p_R = \sqrt{\frac{2}{\alpha'}}\,\tilde{\alpha}_0,
-	\\[1ex]
-		p_{L,R} = \frac{n}{R} \pm \frac{wR}{\alpha'}\,,
-	\\[1ex]
-		X = x
-			- i\,\frac{\alpha'}{2}\,
-			\pqty\big{
-				p_L \ln z
-				+ p_R \ln \bar{z}
-			}
-			+ i\,\sqrt{\frac{\alpha'}{2}}
-			\sum_{m \ne 0}
-				\frac{1}{m}
-				\pqty{
-					\frac{\alpha_m}{z^m}
-					+ \frac{\tilde{\alpha}_m}{\bar{z}^m}
+		\tilde{B}_{\mu d}
+		= \frac{1}{G_{dd}} G_{\mu d},\quad
+		\tilde{B}_{\mu\nu}
+		= B_{\mu\nu}
+			- \frac{1}{G_{dd}} \pqty\big{
+				G_{\mu d} B_{\nu d}
+				- B_{\mu d} G_{\nu d}
 			},
 	\end{gather}
-
-	For the oscillator expressions for $L_0$, recall that:
+	i.e.\ we've found the T-dual theory with $\tilde{R}\propto \frac{1}{R}$. Rescale $\phi\mapsto \phi/\sqrt{\alpha'}$ and $G_{dd}\mapsto \alpha'G_{dd}$, we recover the usual result: $
+		\tilde{R} = \frac{\alpha'}{R}
+	$.
+
+	\item Now we return to the determinant; roughly speaking, we have:
+	\begin{equation}
+		\det \bqty{
+				\frac{
+					G_{dd}\pqty\big{X^\mu(\sigma)}
+				}{2\pi\alpha'}
+			}^{-\frac{1}{2}}
+		= \exp \pqty{
+				- \frac{1}{2}
+				\ln \det \bqty{\cdots}
+			}
+		\sim \exp \pqty{
+				- \frac{1}{2}
+				\tr \frac{\ln G_{dd}}{\alpha'}
+			}
+	\end{equation}
+	Which appears to add a term $\sim - \frac{1}{2} \ln G_{dd}$ in the Lagrangian.
+
+	However, the $\mquote{\det}$ and $\mquote{\tr}$ in the above equation are divergent and ill-defined, and would only make sense after some careful regularization\footnote{
+		I would like to thank \textit{谷夏} for hints about this problem. 
+	}, which was introduced by \textit{Buscher} \cite{Buscher:1987qj} and nicely reviewed by \textit{Alvarez et al} \cite{Alvarez:1994dn}.
+The regularized determinant along with the Jacobian adds the following contribution in the Lagrangian:
+	\begin{equation}
+		- \alpha'\mcal{R}\cdot \frac{1}{2}
+			\ln \frac{G_{dd}}{\alpha'}
+	\end{equation}
+	Which is equivalent to a dilaton shift:
+	\begin{equation}
+		\tilde{\Phi}
+		= \Phi - \frac{1}{2}
+			\ln \frac{G_{dd}}{\alpha'}
+	\end{equation}
+
+	In the limit of constant size $R = \sqrt{G_{dd}}$, note that the string coupling $g_s \sim e^{\Phi_0}$, and we recover the usual result: $\tilde{g}_s = g_s \sqrt{\alpha'} / R$.
+
+	\end{enumerate}
+
+	\item \textbf{Only One Coupling Constant in String Theory}\footnote{
+		Reference: \arxiv{0812.4408}. 
+	}
+	\begin{enumerate}
+	\item Consider the open string one-loop diagram, which is topologically a cylinder. To represent such geometry on the place, we start from the ``rectangular'' torus:
+	\begin{equation}
+		w \cong w + 2\pi \cong w + 2\pi\tau,\quad
+		\tau = it
+	\end{equation}
+	And identify under an \textit{involution}, i.e.\ a reflection through the imaginary axis:
+	\begin{equation}
+		w' = -\bar{w},
+	\quad\Longrightarrow\quad
+		0 \le \Re w \le \pi
+	\end{equation}
+
+	The amplitude is similar to the torus amplitude; first, with a fixed $t = -i\tau$, we have:
+	\begin{equation}
+		\ave*{
+			\prod_i \normorder{e^{ik_i\cdot X_i}}
+		}_{\!\!t}
+		= iC\, (2\pi)^d\,
+			\delta^d\pqty{\textstyle\sum_i k_i}\,
+			\exp \Bqty{
+				- \sum_{i<j} k_i\cdot k_j\,
+					G'(w_i,w_j)
+				- \frac{1}{2} \sum_{i} k_i^2
+					G'(w_i,w_i)
+			}
+	\label{eq:amp_generic}
+	\end{equation}
+	But with a different propagator $G'$, which can be obtained via the method of images; this leads to a doubling of the exponents compared to the torus amplitude:
 	\begin{gather}
-		T(z)
-		= - \frac{1}{\alpha'}\,
-			\normorder{\pd X\,\pd X}
-		= \sum_m \frac{L_m}{z^{m+2}},
+		G'(w,w')
+		= G'_{T^2}(w,w')
+			+ G'_{T^2}(w,-\bar{w}'),
 	\\
-		L_{m\ne 0}
-		= \frac{1}{2}
-			\sum_l \alpha_{m-l} \alpha_l,\quad
-		L_0 = \frac{1}{2}\,\normorder{
-			\sum_l \alpha_{-l} \alpha_l
-		}
-		\sim \frac{\alpha'p_L^2}{4}
-			+ \sum_{l > 0} \alpha_{-l} \alpha_l,
+		\ave*{
+			\prod_i \normorder{e^{ik_i\cdot X_i}}
+		}_{\!\!t}
+		= iC\, (2\pi)^d\,
+			\delta^d\pqty{\textstyle\sum_i k_i}\,
+			\prod_{i < j}
+				\abs{W_{ij}(t)}^{
+					2\times \alpha'k_i\cdot k_j
+				}
 	\end{gather}
-	The $L_0$ expression may be off by some normal ordering constant; this ambiguity can be resolved by considering:
-	\begin{equation}
-		2L_0 \ket{0,0;n = w = 0}
-		= \pqty{
-				L_1 L_{-1} - L_{-1} L_1
-			} \ket{0,0;p_L = p_R = 0}
-		= 0 - 0 = 0
-	\end{equation}
-	Therefore the normal ordering constant is, in fact, trivial, and we have:
-	\begin{equation}
-		L_0 = \frac{\alpha'p_L^2}{4}
-			+ \sum_{l > 0}
-				\alpha_{-l} \alpha_l,\quad
-		\tilde{L}_0 = \frac{\alpha'p_R^2}{4}
-			+ \sum_{l > 0}
-				\tilde{\alpha}_{-l} \tilde{\alpha}_l,
-	\end{equation}
-
-	\item The torus partition function is given by:
-	\begin{equation}
-		\ave{\idty}_{T^2}
-		\equiv Z(\tau = \tau_1 + i\tau_2)
-		= \int \DD X e^{-S}
-		= \Tr e^{-(2\pi\tau_2) H} e^{i\,(2\pi\tau_1) P}
-	\end{equation}
-	Here $P$ generates \textit{worldsheet} translation along $\sigma^1$, not to be confused with $p$ which generates \textit{spacetime} translation; with $
-		z = e^{-iw},\ w = \sigma^1 + i\sigma^2
-	$, 
-	\begin{gather}
-	\begin{aligned}
-		T\id{^0_1}
-		= \eta^{00}\, (\pdd{0} \sigma^2)\, T_{21}
-		= -iT_{12}
-		&= -i\,\pqty\big{
-				T_{ww}\,
-					(\pdd{1} w)(\pdd{2} w)
-				+ T_{\bar{w}\bar{w}}\,
-					(\pdd{1} \bar{w})(\pdd{2} \bar{w})
-			} \\
-		&= T_{ww} - T_{\bar{w}\bar{w}} \\
-		&= \pqty{
-				T_{zz}\,
-					(\pdd{w} z)^2
-				+ \tfrac{c}{24}
-			}
-			- \pqty{
-				T_{\bar{z}\bar{z}}\,
-					(\pdd{\bar{w}} \bar{z})^2
-				+ \tfrac{\tilde{c}}{24}
-			} \\
-		&= T(z)\, (-iz)^2
-			- \tilde{T}(\bar{z})\, (+i\bar{z})^2
-			+ \frac{c - \tilde{c}}{24},
-	\end{aligned}
-	\\[1ex]
-	\begin{aligned}
-		P = \int \frac{\dd{\sigma_1}}{2\pi}\,
-				\pqty{- T\id{^0_1}\!}
-		&= - \int \frac{\dd{\sigma_1}}{2\pi}\,
-				T(z)\, (-iz)^2
-			+ \int \frac{\dd{\sigma_1}}{2\pi}\,
-				\tilde{T}(\bar{z})\, (+i\bar{z})^2
-			- \frac{c - \tilde{c}}{24} \\
-		&= + \ointctrclockwise
-				\frac{\dd{z}}{2\pi\,(-iz)}\,
-				T(z)\, (-iz)^2
-			+ \ointctrclockwise
-				\frac{\dd{\bar{z}}}{2\pi\,(+i\bar{z})}\,
-				\tilde{T}(\bar{z})\, (+i\bar{z})^2
-			- \frac{c - \tilde{c}}{24} \\
-		&= \oint \frac{\dd{z}}{2\pi i}\,
-				zT(z)
-			- \oint \frac{\dd{\bar{z}}}{2\pi i}\,
-				\bar{z}\tilde{T}(\bar{z})
-			- \frac{c - \tilde{c}}{24} \\
-		&= L_0 - \tilde{L}_0
-			- \frac{c - \tilde{c}}{24} \\
-		&= \pqty{L_0 - \tfrac{c}{24}}
-			- \pqty\big{
-				\tilde{L}_0 - \tfrac{\tilde{c}}{24}
-			},
-	\\[1.5ex]
-		H = \int \frac{\dd{\sigma_1}}{2\pi}\,
-				T\id{^0_0}
-		&= \int \frac{\dd{\sigma_1}}{2\pi}\,
-				T_{22} \\
-		&= L_0 + \tilde{L}_0
-			- \frac{c + \tilde{c}}{24} \\
-		&= \pqty{L_0 - \tfrac{c}{24}}
-			+ \pqty\big{
-				\tilde{L}_0 - \tfrac{\tilde{c}}{24}
-			},
-	\end{aligned}
-	\end{gather}
-	Here we've used the fact that $
-		\displaystyle\oint \frac{\dd{\bar{z}}}{\bar{z}}
-		= \ointctrclockwise
-			\frac{\dd{\bar{z}}}{\bar{z}}
-		= 2\pi i
-	$. Therefore,
-	\begin{equation}
-		Z(\tau)
-		= \Tr e^{-(2\pi\tau_2) H} e^{i\,(2\pi\tau_1) P}
-		= \Tr q^{L_0 - \tfrac{c}{24}}\,
-			\bar{q}^{\tilde{L}_0 - \tfrac{\tilde{c}}{24}}
-		,\quad q = e^{2\pi i\tau}
-	\end{equation}
-
-	Using the expressions in (a), we find that $L_0$ action on a state $\ket{\psi}$ created by $\alpha_{-l},\tilde{\alpha}_{-l}$ yields the sum of occupation numbers $N_l$ weighted by $l$:
-	\begin{equation}
-		L_0 \ket{\psi}
-		= \pqty{
-				\frac{\alpha'k_L^2}{4}
-				+ \sum_{l > 0} l\cdot N_l
-			} \ket{\psi}
-	\end{equation}
-	With $c = \tilde{c} = 1$, we obtain:
-	\begin{equation}
-	\begin{aligned}
-		Z(\tau)
-		&= (q\bar{q})^{-\frac{1}{24}}
-			\sum_{n,w}
-				e^{
-					- 2\pi \tau_2
-					\alpha'\frac{k_L^2 + k_R^2}{4}
-				}
-				e^{
-					2\pi i \tau_1
-					\alpha'\frac{k_L^2 - k_R^2}{4}
-				}
-			\sum_{(N_l),(\tilde{N}_l)}
-				q^{
-					\,\sum\limits_{l>0}  l\cdot N_l
-				}
-				\bar{q}^{
-					\,\sum\limits_{l>0}  l\cdot \tilde{N}_l
-				} \\
-		&= (q\bar{q})^{-\frac{1}{24}}
-			\sum_{n,w}
-				e^{
-					- \pi \tau_2 \pqty{
-						\frac{\alpha'n^2}{R^2}
-						+ \frac{w^2 R^2}{\alpha'}
-					}
-					+ 2\pi i \tau_1 nw
-				}
-			\sum_{(N_l),(\tilde{N}_l)} \prod_{l>0}
-				q^{l\cdot N_l}
-				\bar{q}^{\,l\cdot \tilde{N}_l} \\
-		&= \abs{\eta(\tau)}^{-2}
-			\sum_{n,w}
-				e^{
-					- \pi \tau_2 \pqty{
-						\frac{\alpha'n^2}{R^2}
-						+ \frac{w^2 R^2}{\alpha'}
-					}
-					+ 2\pi i \tau_1 nw
-				}
-	\end{aligned}
-	\end{equation}
-	We've simplified the contributions from the oscillator modes using $\eta(\tau)$, since they are identical to the oscillator contributions of the non-compact $X\in\mbb{R}^1$:
-	\begin{equation}
-	\begin{aligned}
-		(q\bar{q})^{-\frac{1}{24}}\!\!\!\!\!
-		\sum_{(N_l),(\tilde{N}_l)} \prod_{l>0}
-			q^{l\cdot N_l}
-			\bar{q}^{\,l\cdot \tilde{N}_l}
-		&= (q\bar{q})^{-\frac{1}{24}}
-			\prod_{l>0} \sum_{N_l,\tilde{N}_l = 0}^\infty
-				q^{l\cdot N_l}
-				\bar{q}^{\,l\cdot \tilde{N}_l} \\
-		&= (q\bar{q})^{-\frac{1}{24}}
-			\prod_{l>0}
-				\frac{1}{1 - q^l}
-				\frac{1}{1 - \bar{q}^{\,l}}
-		= \abs{\eta(\tau)}^{-2}
-	\end{aligned}
-	\end{equation}
-
-	In the $R\to\infty$ limit, only the $w = 0$ modes survive; all other modes are exponentially suppressed by the $
-		e^{
-			- \pi \tau_2 w^2 R^2 / \alpha'
-		}
-	$ factor; i.e.
-	\begin{equation}
-	\begin{aligned}
-		Z(\tau)
-		&= \abs{\eta(\tau)}^{-2}
-			\sum_{n,w}
-				\exp \Bqty{
-					- \pi \tau_2 \pqty{
-						\frac{\alpha'n^2}{R^2}
-						+ \frac{w^2 R^2}{\alpha'}
-					}
-					+ 2\pi i \tau_1 nw
-				} \\
-		&\to \abs{\eta(\tau)}^{-2}
-			\sum_{n}
-				\exp \Bqty{
-					- \pi \tau_2\,
-						\frac{\alpha'n^2}{R^2}
-				},\quad k = \frac{n}{R} \\
-		&\to \abs{\eta(\tau)}^{-2}
-			\,V\!\!\int \frac{\dd{k}}{2\pi}
-				\exp \Bqty{
-					- \pi \tau_2\,\alpha' k^2
-				} \\
-		&= V\,\abs{\eta(\tau)}^{-2}
-			\pqty{
-				4\pi^2 \alpha' \tau_2
-			}^{-\frac{1}{2}} \\
-		&\equiv V\cdot Z_X(\tau)
-		= 2\pi R\, Z_X(\tau)
-	\end{aligned}
-	\end{equation}
-	We recover the partition function $V\cdot Z_X(\tau)$ for non-compact $X$, as expected.
-
-	\item Using the Poisson resummation formula, we find that:
-	\begin{equation}
-	\begin{aligned}
-		Z(\tau)
-		&= 2\pi R\, Z_X(\tau) \sum_{m,w}
-			\exp \pqty{
-				- \frac{
-					\pi R^2 \abs{m - w\tau}^2
-				}{\alpha'\tau_2}
-			}
-	\end{aligned}
-	\end{equation}
-	$Z_X(\tau)$ is modular invariant by the properties of the Dedekind $\eta(\tau)$ function, as is demonstrated for the non-compact $X$ in \textit{Polchinski}.
-
-	The sum, on the other hand, is naturally invariant under $T\colon \tau \mapsto \tau + 1$, by making a change of variables $m \mapsto m + w$.
-It is also invariant under $S\colon \tau \mapsto -1/\tau$ with $m \mapsto −w, w \mapsto m$\,\footnote{
-		Reference: \textit{Polchinski}. 
-	}. Therefore, $Z(\tau)$ is modular invariant.
-
-	\end{enumerate}
-
-	\item \textbf{$\mbb{Z}_2$ Orbifold}
-
-	The $\mbb{Z}_2$ orbifold is constructed by imposing an additional identification on $X\in S^1$:
-	\begin{equation}
-		X\cong -X
-	\end{equation}
-	The target space is then reduced to $S^1/\mbb{Z}_2 \cong [0,\pi R]$.
-
-	\begin{enumerate}
-	\item The first contributions to the orbifold partition function comes from the states that are invariant reflection $r$; we have:
-	\begin{equation}
-		\Tr_{S^1/\mbb{Z}_2}
-		= \Tr_{S^1} \frac{1 + r}{2}
-		= \frac{1}{2}\,{\Tr_{S^1}}
-			+ \frac{1}{2}\,{\Tr_{S^1}} \circ r
-	\end{equation}
-	Acting on $
-		q^{L_0 - \tfrac{c}{24}}\,
-		\bar{q}^{\tilde{L}_0 - \tfrac{\tilde{c}}{24}}
-	$, the first term gives $\frac{1}{2}\,Z_{S^1}(\tau)$ where $Z_{S^1}$ is the $S^1$ partition function we've obtained in \boxed{1}\,.
-
-	For the second term, note that:
-	\begin{equation}
-		r\colon\ %
-				\ket{(N_l),(\tilde{N}_l);n,w}
-			\longmapsto (−1)^{\sum_l (N_l + \tilde{N}_l)}
-				\ket{(N_l),(\tilde{N}_l);-n,-w}
-	\end{equation}
-	In particular, it reverses $n,w$, hence $r$ insertion gives vanishing amplitude unless $n = w = 0$; the summation is very much similar to the $Z_{S^1}$ case, i.e. we have:
-	\begin{equation}
-	\begin{aligned}
-		\frac{1}{2} \Tr_{S^1} \pqty\Big{
-			r\,
-			q^{L_0 - \tfrac{c}{24}}\,
-			\bar{q}^{\tilde{L}_0 - \tfrac{\tilde{c}}{24}}
-		}
-		&= \frac{1}{2}\,(q\bar{q})^{-\frac{1}{24}}
-			\prod_{l>0} \sum_{N_l,\tilde{N}_l = 0}^\infty
-				(−1)^{N_l + \tilde{N}_l}
-				q^{l\cdot N_l}
-				\bar{q}^{\,l\cdot \tilde{N}_l} \\
-		&= \frac{1}{2}\,(q\bar{q})^{-\frac{1}{24}}
-			\prod_{l>0}
-				\frac{1}{1 - (-q^l)}
-				\frac{1}{1 - (-\bar{q}^{\,l})}
-		= \abs{\frac{\eta(\tau)}{\theta_2(\tau)}}
-	\end{aligned}
-	\end{equation}
-	Where we've used the fact that\footnote{
-		Reference: Blumenhagen \& Plauschinn, \textit{Introduction to CFT}, and also \textit{Polchinski}. 
-	}: $
-		q^{-\frac{1}{24}}
-		\prod_{l>0} \frac{1}{1 - (-q^l)}
-		= \sqrt{2} \sqrt{
-			\frac{\eta(\tau)}{\theta_2(\tau)}
-		}
-	$. Therefore, the total contributions from $r$--invariant states are:
-	\begin{equation}
-		\frac{1}{2}\,Z_{S^1}(\tau)
-		+ \abs{\frac{\eta(\tau)}{\theta_2(\tau)}}
-	\end{equation}
-
-	\item With $X\cong -X$, new possibilities emerge as the boundary condition along $\sigma^1$:
-	\begin{equation}
-		X(\sigma^1 + 2\pi) \cong X(\sigma^1),\quad
-		X(\sigma^1 + 2\pi) = \pm X(\sigma^1) + 2\pi Rw,\quad
-		w\in\mbb{Z}
-	\end{equation}
-	The $\mquote{-}$ sign corresponds to the \textit{twisted states}. Due to the anti-periodicity, $\pd X$ has a half-integer mode expansion:
-	\begin{gather}
-		\allowdisplaybreaks
-		\pd X\pqty{z\,e^{2\pi i}} = - \pd X(z),\\
-		\pd X(z) =
-			-i\,\sqrt{\frac{\alpha'}{2}}
-			\sum_{m = -\infty}^\infty
-				\frac{\alpha_{m-\frac{1}{2}}}
-					{z^{m+\frac{1}{2}}},\quad
-		\pdbar X(\bar{z}) =
-			-i\,\sqrt{\frac{\alpha'}{2}}
-			\sum_{m = -\infty}^\infty
-				\frac{\tilde{\alpha}_{m-\frac{1}{2}}}
-					{\bar{z}^{m+\frac{1}{2}}},\\
-		X = x + i\,\sqrt{\frac{\alpha'}{2}}
-			\sum_{m = -\infty}^\infty
-				\frac{1}{m+\frac{1}{2}}
-				\pqty{
-					\frac{\alpha_{m+\frac{1}{2}}}
-						{z^{m+\frac{1}{2}}}
-					+ \frac{\tilde{\alpha}_{m+\frac{1}{2}}}
-						{\bar{z}^{m+\frac{1}{2}}}
-				},
-	\end{gather}
-	Apply the boundary condition on $X$, and we find that $x = \pi R w'$; however, due to the identification $X + 2\pi R \cong X \cong -X$, there are only two inequivalent choices: $x = 0$ and $x =\pi R$, which correspond to the string localized around either of the two fixed points of the $\mbb{Z}_2$ action.
-
-	Much similar to the case in \boxed{1}\,, we have:
-	\begin{gather}
-		\bqty{
-			\alpha_{\frac{1}{2} + l},
-			\alpha_{- \frac{1}{2} - l}
-		} = \frac{1}{2} + l,\\[1ex]
-		L_{m\ne 0}
-		= \frac{1}{2}
-			\sum_l \alpha_{m - \frac{1}{2} - l}
-					\alpha_{\frac{1}{2} + l},\quad
-		L_0 = \frac{1}{2}\,\normorder{
-			\sum_l \alpha_{-\frac{1}{2}-l}
-					\alpha_{\frac{1}{2}+l}
-		}
-		\sim \sum_{l \ge 0}
-				\alpha_{-\frac{1}{2}-l}
-				\alpha_{\frac{1}{2}+l}
-	\end{gather}
-	We can use the same trick to fix the normal ordering constant in $L_0$; this time it is non-trivial:
-	\begin{gather}
-		L_{-1} = \frac{1}{2}\,
-				\alpha_{-\frac{1}{2}}^2
-			+ \sum_{l \ge 0}
-				\alpha_{-\frac{1}{2}-l}
-				\alpha_{\frac{1}{2}+l},\quad
-		L_1 = \frac{1}{2}\,
-				\alpha_{\frac{1}{2}}^2
-			+ \sum_{l > 0}
-				\alpha_{\frac{1}{2}-l}
-				\alpha_{\frac{1}{2}+l}, \\
-	\begin{aligned}
-		L_0 \ket{0,0;x}
-		&= \frac{1}{2}\,\pqty{
-				L_1 L_{-1} - L_{-1} L_1
-			} \ket{0,0;x} \\
-		&= \frac{1}{2}\times \frac{1}{4}\,
-				\alpha_{\frac{1}{2}}^2
-				\alpha_{-\frac{1}{2}}^2
-			\ket{0,0;x} - 0 \\
-		&= \frac{1}{16} \ket{0,0;x},
-	\end{aligned}
-	\\[1ex]
-		L_0
-		= \frac{1}{16}
-			+ \sum_{l \ge 0}
-				\alpha_{-\frac{1}{2}-l}
-				\alpha_{\frac{1}{2}+l}
-		= \frac{1}{16}
-			+ \sum_{l \ge 0}
-				\pqty{l + \frac{1}{2}}\,
-				N_{l + \frac{1}{2}}
-		= \frac{1}{16}
-			+ \sum_{l > 0}
-				\pqty{l - \frac{1}{2}}\,
-				N_{l - \frac{1}{2}},
-	\end{gather}
-
-	The trace can then be computed, following the same recipe as before:
-	\begin{equation}
-	\begin{aligned}
-		\Tr_{S^1} \pqty{
-			\frac{1 + r}{2}\,
-			q^{L_0 - \tfrac{c}{24}}\,
-			\bar{q}^{\tilde{L}_0 - \tfrac{\tilde{c}}{24}}
-		}
-		&= (q\bar{q})^{
-				-\frac{1}{24} + \frac{1}{16}
-			}
-			\prod_{l + \frac{1}{2} \in \mbb{Z}^+}
-			\sum_{N_l,\tilde{N}_l = 0}^\infty
-				\frac{1 + (−1)^{N_l + \tilde{N}_l}}{2}\,
-				q^{l\cdot N_l}
-				\bar{q}^{\,l\cdot \tilde{N}_l} \times 2 \\
-		&= \frac{1}{2}\,(q\bar{q})^{+\frac{1}{48}}
-		\Bqty{\,
-			\prod_{l>0}
-				\abs{\frac{1}{1 - q^{l - \frac{1}{2}}}}^2
-			+ \prod_{l>0}
-				\abs{\frac{1}{1 + q^{l - \frac{1}{2}}}}^2
-		}\times 2 \\
-		&= \abs{\frac{\eta(\tau)}{\theta_4(\tau)}}
-			+ \abs{\frac{\eta(\tau)}{\theta_3(\tau)}}
-	\end{aligned}
-	\end{equation}
-	There is an extra factor of 2 from the number of twisted sectors: $x = 0$ and $x = \pi R$.
-
-	\item The full partition function is therefore:
-	\begin{equation}
-		Z(\tau)
-		= \frac{1}{2}\,Z_{S^1}(\tau)
-			+ \abs{\frac{\eta(\tau)}{\theta_2(\tau)}}
-			+ \abs{\frac{\eta(\tau)}{\theta_4(\tau)}}
-			+ \abs{\frac{\eta(\tau)}{\theta_3(\tau)}}
-	\end{equation}
-	The first term is modular invariant, as is proved in \boxed{1}\,.
-
-	The remaining terms are also modular invariant, due to the transformational properties of $\eta$ and $\theta$ functions\footnote{
-		Reference: \textit{Blumenhagen \& Plauschinn}. 
-	}:
-	\begin{equation}
-		T \circlearrowright
-		\abs{\frac{\eta(\tau)}{\theta_2(\tau)}}
-		\xleftrightarrow{\ S\ }
-		\abs{\frac{\eta(\tau)}{\theta_4(\tau)}}
-		\xleftrightarrow{\ T\ }
-		\abs{\frac{\eta(\tau)}{\theta_3(\tau)}}
-		\circlearrowleft S
-	\end{equation}
-	Therefore, the full partition function is modular invariant.
-
-	\end{enumerate}
-
-	\item \textbf{Torus 4-point function in $bc$ CFT}
-	\begin{equation}
-		\ave[\big]{
-			c(w_1)\,b(w_2)\,
-			\tilde{c}(\bar{w}_3)\,\tilde{b}(\bar{w}_4)
-		}
-		= \int \DD b\,\DD \tilde{b}\,
-				\DD c\,\DD \tilde{c}\ %
-			c(w_1)\,b(w_2)\,
-			\tilde{c}(\bar{w}_3)\,\tilde{b}(\bar{w}_4)\,
-			e^{-S'}
-		\equiv Z'
-	\end{equation}
-	First we argue that only the zero modes of the insertions survive the path integral\footnote{
-		I would like to thank \textit{谷夏} for some very helpful discussions about this problem.
-	}.
-In fact, as anti-commuting replacements of the gauge degrees of freedom, ghost modes are \textit{defined} to be the eigenvalues of $P^\dagger P$, where $P$ is the conformal Killing differential\footnote{
-		Reference: \textit{Polchinski}, Chapter 3 \& 5. 
-	}. 
-	More specifically, given a conformal Killing vector (CKV) $\var{\sigma^a}$, the conformal Killing equation can be written as:
-	\begin{equation}
-		P \var{\sigma} = 0
-	\end{equation}
-	While $P^\dagger \var'\!
-g = 0$ gives moduli variation $\var'\!
-g_{ab}$ of the metric.
-Roughly speaking, $P$ captures the variation of gauge fixing under an arbitrary gauge transformation; naturally, CKV's are given by $(\ker P)$, while $(\det P) \sim \Delta_{FP}$ is the Faddeev--Popov functional measure near the gauge slice.
-$(\det P)$ can then be calculated with:
-	\begin{gather}
-		\var{\sigma^a} \mapsto c^a,\quad
-		\var'\! g_{ab} \mapsto b_{ab},\quad
-		\Delta_{FP}
-		\sim \det P
-		\sim \int \DD b\,\DD \tilde{b}\,
-				\DD c\,\DD \tilde{c}\ e^{-S'},\\
-		S'
-		= \frac{1}{2\pi} \int \dd[2]{\sigma}
-			g^{1/2}\, b_{ab}\,(P\cdot c)^{ab}
-		= \frac{1}{2\pi} \int \dd[2]{w}
-			\pqty\big{
-				b\,\pdbar_w c
-				+ \tilde{b}\,\pd_w \tilde{c}
-			}
-	\end{gather}
-	In the end we have chosen conformal gauge, such that\footnote{
-		References:
-		\begin{itemize}[
-			labelindent=3em,labelsep=1pt,
-			topsep=.1\baselineskip
-		]
-		\item Nakahara, \textit{Geometry, Topology and Physics}; 
-		\item Blumenhagen et al, \textit{Basic Concepts of String Theory}. 
-		\end{itemize}
-	} $
-		P \sim (\pdbar_w, \pd_w),\ %
-		P^\dagger P \sim -\pdbar_w\pd_w = -\laplacian
-	$. In the $w = \sigma^1 + i\sigma^2$ coordinates, CKV's are simple translations: $c^a = \mrm{const}$; with $z = e^{-iw}$, it gets mapped to $
-		c^z
-		= c^w \,\pd_w z
-		= c^w \,(-iz)
-	$, which agrees with the zero mode $c_0$ in the $c(z)$ expansion:
-	\begin{equation}
-		c(z)
-		= \sum_{m = -\infty}^\infty
-			\frac{c_m}{z^{m + 1 - \lambda}}
-		= c_0\,z + \sum_{m \ne 0}
-			\frac{c_m}{z^{m - 1}}
-		,\quad \lambda = 2
-		\label{eq:cghost_holomorphic}
-	\end{equation}
-
-	Now we are finally ready to prove our argument: for anti-commuting variables like $c(z)$, 
-	\begin{equation}
-		\int \DD{c}
-		\sim \prod_m \int \dd{c_m}
-		\sim \prod_m \pdv{c_m}
-	\end{equation}
-	Since $c_0$ corresponds to a CKV, $P \cdot c_0 = 0$, therefore it vanishes in $S' = \int \dd[2]{\sigma}\pqty{b\cdot P\cdot c}$; for the path integral to be non-zero, there has to be some additional $c_0$ insertions, i.e.
-	\begin{equation}
-		Z'
-		\sim \int \DD b\,\DD \tilde{b}\,
-				\DD c\,\DD \tilde{c}\ %
-			c_0 b_0
-			\tilde{c}_0 \tilde{b}_0\,
-			e^{-S'}
-		\sim \pqty{\frac{1}{\sqrt{\tau_2}}}^{\!\!4}\!\!
-			\int \DD' b\,\DD' \tilde{b}\,
-				\DD' c\,\DD' \tilde{c}\ %
-			e^{-S'},\quad
-		\int \DD' c
-		\sim \prod_{m\ne 0} \int \dd{c_m}
-	\end{equation}
-
-	Note the additional $
-		\pqty\big{\frac{1}{\sqrt{\tau_2}}}^4
-	$ factor coming from the zero modes\footnote{
-		Reference: \textit{Di Francesco et al}. 
-	}; this has to do with the normalization of the zero modes, each contributing a factor of $\frac{1}{\sqrt{A}}$, where $A \sim \tau_2$ is the volume (surface area) of the torus.
-On a different note, since it is very difficult, if not impossible, to keep track of various (often divergent) constant factors in the path integral, we have been and will be calculating $Z'$ up to an overall constant coefficient.
-
-	Now we have to deal with the path integral over non-zero modes.
-Note that the holomorphic mode expansion \eqref{eq:cghost_holomorphic} is incomplete for our purpose: it gives the \textit{on-shell} mode expansion, while our path integral should go over all possible configurations, including the off-shell modes, which is \textit{not} holomorphic.
-However, on $T^2 = S^1\times S^1$, the full modes are simple\footnote{
-		References: (1) \textit{Nakahara}, (2) \textit{Di Francesco et al.}, and (3) \url{http://theory.uchicago.edu/~sethi/Teaching/P483-W2018/p483-sol3.pdf}. 
-	}:
-	\begin{gather}
-		-\laplacian \psi_{n_1,n_2}
-		= \lambda_{n_1,n_2} \psi_{n_1,n_2},
-	\\[1ex]
-	\begin{aligned}
-		\psi_{n_1,n_2}
-		&= \exp \pqty\big{
-				i\,\pqty*{
-					n_1\tilde{\sigma}^1
-					+ n_2\tilde{\sigma}^2
-				}
-			},\quad
-		\tilde{\sigma}^2
-		= \frac{\sigma^2}{\tau_2},\quad
-		\tilde{\sigma}^1
-		= \sigma^1 - \sigma^2 \frac{\tau_1}{\tau_2}, \\[1ex]
-		&= \exp \Bqty{
-				i\,\pqty{
-					n_1 \sigma^1
-					+ \frac{n_2 - n_1 \tau_1}{\tau_2}\,
-						\sigma^2
-				}
-			},
-	\end{aligned}
-	\end{gather}
-	Here we first use the ``rectangular'' coordinates $(\tilde{\sigma}^1, \tilde{\sigma}^2) \in [0,2\pi]^2$ to write down the obvious eigen-functions $\psi_{n_1,n_2}$, and then relate them back to the $(\sigma^1,\sigma^2)$ coordinates.
-Therefore, we have:
-	\begin{gather}
-	\begin{aligned}
-		\lambda_{n_1,n_2}
-		&= \Bqty{
-				n_1^2 + \pqty{
-					\frac{n_2 - n_1 \tau_1}{\tau_2}
-				}^{\!2}
-			} \\
-		&= \frac{1}{\tau_2^2}\,
-			\Bqty{
-				(n_1 \tau_2)^2 + \pqty\big{
-					n_1 \tau_1 - n_2
-				}^2
-			} \\
-		&= \frac{1}{\tau_2^2}\,
-			\abs{n_1\tau - n_2}^2,
-	\end{aligned}
-	\\[.5ex]
-		\det\nolimits' P
-		\sim \pqty{\,
-				\sideset{}{'}\prod_{n_1,n_2} 
-					\sqrt{\lambda_{n_1,n_2}}
-%					\frac{1}{\tau_2}\,
-%					\abs{n_1\tau - n_2}
-			}^2
-		\sim \sideset{}{'}\prod_{n_1,n_2} 
-			\lambda_{n_1,n_2}
-	\end{gather}
-
-	The determinant can be computed with $\zeta$-function regularization, as is performed in detail in \textit{Di Francesco}; the result can be nicely summarized using the Eisenstein series, as shown in \textit{Nakahara}:
-	\begin{gather}
-		E(\tau,s)
-		= \sideset{}{'}\sum_{n_1,n_2} 
-			\frac{\tau_2^s}{\abs{n_1\tau - n_2}^{2s}},
-	\\
-		\det\nolimits' P
-		\sim \sideset{}{'}\prod_{n_1,n_2}
-			\frac{1}{\tau_2^2}\,
-			\abs{n_1\tau - n_2}^2
-		\sim \tau_2 \exp \Bqty\Big{
-				-\pdd{s} E'(\tau,s)_{s = 0}
-			}
-		= \tau_2^2\,\abs{\eta(\tau)}^4
-	\end{gather}
-	Finally, we have:
-	\begin{equation}
-		Z'
-		\sim \tau_2^{-2} \det\nolimits' P
-		\sim \tau_2^{-2} \tau_2^2\,\abs{\eta(\tau)}^4
-		\sim \abs{\eta(\tau)}^4
-	\end{equation}
-
-	\item \textbf{Torus Propagator as a Trace}
-	\begin{equation}
-		w'\to 0,\quad
-		\ave[\big]{\pdd{w} X(w)\,\pdd{w'} X(w')}
-		= \Tr \pqty{
-			\pdd{w} X(w)\,\pdd{w'} X(w')\,
-			q^{L_0 - \tfrac{c}{24}}\,
-			\bar{q}^{\tilde{L}_0 - \tfrac{\tilde{c}}{24}}
-		}
-	\end{equation}
-	Here we've dropped the time ordering in the $w' \to 0$ limit. 
-	Recall the mode expansion of $\pd X$ in \boxed{1}\,; we see that only the ``diagonal'' components of $
-		\pd X(w)\,\pd X(w')
-	$ survive in the trace, i.e.
-	\begin{equation}
-	\begin{aligned}
-		\pdd{w} X(w)\,\pdd{w'} X(w')
-		&= (\pdd{w} z)(\pdd{w'} z')\,
-			\pdd{z} X(z)\,\pdd{z'} X(z')
-		,\quad z = e^{-iw}
-		,\quad 1\le\abs{z}\le e^{2\pi\tau_2} \\
-		&\sim -\frac{\alpha'}{2}
-			\sum_{n = -\infty}^\infty
-				\frac{\alpha_{-n} \alpha_n}
-					{z^{-n+1} z'^{n+1}}\,
-				(-iz)(-iz') \\
-		&= \frac{\alpha'}{2} \pqty{
-				\alpha_0^2
-				+ \sum_{n > 0}
-					\pqty{
-						\pqty\Big{\frac{z}{z'}}^{\!n}
-						+ \pqty\Big{\frac{z'}{z}}^{\!\!n\,}
-					}\, \alpha_{-n} \alpha_n
-				+ \sum_{n > 0}
-					n\,
-					\pqty\Big{\frac{z'}{z}}^{\!\!n\,}
-			}
-		\\
-		&= \frac{\alpha'}{2} \pqty{
-				\alpha_0^2
-				+ \sum_{n > 0}
-					\pqty{
-						\pqty\Big{\frac{z}{z'}}^{\!n}
-						+ \pqty\Big{\frac{z'}{z}}^{\!\!n\,}
-					}\, \alpha_{-n} \alpha_n
-				+ \frac{zz'}{(z - z')^2}
-			}
-	\end{aligned}
-	\end{equation}
-	The last term is a normal ordering constant; here it is naturally regularized by $
-		\pqty\big{\frac{z'}{z}}^{\!n\,}
-	$.
-
-	The $\alpha_0^2$ term can be substituted with spacetime momentum $p$; we have:
-	\begin{gather}
-		p = \sqrt{\frac{1}{2\alpha'}}\,
-			\pqty\big{\alpha_0 + \tilde{\alpha}_0}
-		= \sqrt{\frac{1}{2\alpha'}}\, 2\alpha_0
-		= \sqrt{\frac{2}{\alpha'}}\, \alpha_0,
-	\\[1ex]
-	\begin{aligned}
-		\pdd{w} X(w)\,\pdd{w'} X(w')
-		&\sim \frac{\alpha'}{2} \pqty{
-				\frac{\alpha' p^2}{2}
-				+ \sum_{n > 0}
-					\pqty{
-						\pqty\Big{\frac{z}{z'}}^{\!n}
-						+ \pqty\Big{\frac{z'}{z}}^{\!\!n\,}
-					}\, n N_n
-			}
-	\end{aligned}
-	\end{gather}
-	On the other hand, the partition function is:
-	\begin{equation}
-	\begin{aligned}
-		Z(\tau) = \ave{\idty}
-		&= (q\bar{q})^{-\frac{1}{24}}
-			\,V\!\!\int \frac{\dd{k}}{2\pi}\,
-				e^{- \pi \tau_2\,\alpha' k^2}
-			\!\!\!
-			\sum_{(N_l),(\tilde{N}_l)}
-				q^{
-					\,\sum\limits_{l>0}  l\cdot N_l
-				}
-				\bar{q}^{
-					\,\sum\limits_{l>0}  l\cdot \tilde{N}_l
-				} \\
-		&= (q\bar{q})^{-\frac{1}{24}}
-			\,V\!\!\int \frac{\dd{k}}{2\pi}\,
-				e^{- \pi \tau_2\,\alpha' k^2}
-			\!\!\!
-			\sum_{(N_l),(\tilde{N}_l)} \prod_{l>0}
-				q^{l\cdot N_l}
-				\bar{q}^{\,l\cdot \tilde{N}_l} \\
-		&= \abs{\eta(\tau)}^{-2}
-			\,V\!\!\int \frac{\dd{k}}{2\pi}\,
-				e^{- \pi \tau_2\,\alpha' k^2}
-			\!\!\!
-	\end{aligned}
-	\end{equation}
-
-	We can work out $Z^{-1} \ave{\pd X \pd X}$ by considering term by term insertion of the $\pd X \pd X$ mode expansion into the above expression.
-For the $\frac{\alpha'p^2}{2}$ term, we have a contribution of:
-	\begin{equation}
-		\frac{\displaystyle
-			\int \frac{\dd{k}}{2\pi}\,
-				\frac{\alpha'k^2}{2}\,
-				e^{- \pi \tau_2\,\alpha' k^2}
-		}{\displaystyle
-			\int \frac{\dd{k}}{2\pi}\,
-				e^{- \pi \tau_2\,\alpha' k^2}
-		}
-		= \frac{\alpha'}{2}\,
-			\frac{1}{2\cdot \pi\alpha'\tau_2}
-		= \frac{1}{4\pi\tau_2}
-	\end{equation}
-
-	For the $nN_n$ insertion, we have a contribution of:
-	\begin{equation}
-	\begin{aligned}
-%		\frac{1}{\abs{\eta(\tau)}^{-2}}
-%		\cdot
-%		(q\bar{q})^{-\frac{1}{24}}
-%			\!\!\!
-%			\sum_{(N_l),(\tilde{N}_l)}
-%			\!\!
-%				nN_n\,
-%				q^{
-%					\,\sum\limits_{l>0}  l\cdot N_l
-%				}
-%				\bar{q}^{
-%					\,\sum\limits_{l>0}  l\cdot \tilde{N}_l
-%				}
-		\frac{\displaystyle
-			\sum_{(N_l)}
-				nN_n\,
-				q^{
-					\,\sum\limits_{l>0}  l\cdot N_l
-				}
-		}{\displaystyle
-			\sum_{(N_l)}
-				q^{
-					\,\sum\limits_{l>0}^{\,}  l\cdot N_l
-				}
-		}
-		&= \frac{\displaystyle
-			\sum_{(N_l)}
-				nN_n\,
-				\prod_{l>0} q^{l\cdot N_l}
-		}{\displaystyle
-			\sum_{(N_l)}^{\,}
-				\prod_{l>0} q^{l\cdot N_l}
-		}
-		= \frac{\displaystyle
-			\sum_{N_n = 0}^\infty
-				nN_n\, q^{n\cdot N_n}
-		}{\displaystyle
-			\sum_{N_n = 0}^\infty
-				q^{n\cdot N_n}
-		}
-		= \frac{\displaystyle
-			n q^n \pdv{(q^n)}
-			\sum_{N_n = 0}^\infty q^{n\cdot N_n}
-		}{\displaystyle
-			\sum_{N_n = 0}^\infty q^{n\cdot N_n}
-		} \\
-		&= \frac{
-			n q^n \pdv{(q^n)} \frac{1}{1 - q^n}
-		}{
-			\frac{1}{1 - q^n}
-		}
-		= \frac{n q^n}{1 - q^n}
-	\end{aligned}
-	\end{equation}
-	Therefore, the complete result is given by:
-	\begin{equation}
-	\begin{aligned}
-		\frac{1}{Z(\tau)}
-		\ave[\big]{
-			\pdd{w} X(w)\,\pdd{w'} X(w')
-		}
-		= {} & \frac{\alpha'}{2} \pqty{
-				\frac{1}{4\pi\tau_2}
-				+ \sum_{n > 0}
-					\pqty{
-						\pqty\Big{\frac{z}{z'}}^{\!n}
-						+ \pqty\Big{\frac{z'}{z}}^{\!\!n\,}
-					}\,
-					\frac{n q^n}{1 - q^n}
-				+ \frac{zz'}{(z - z')^2}
-			} \\
-		\xrightarrow[z'\to 1]{\, w'\to 0\ }\ &
-			\frac{\alpha'}{2} \pqty{
-				\frac{1}{4\pi\tau_2}
-				+ \sum_{n > 0}
-					\pqty{
-						z^{n}
-						+ z^{-n}
-					}\,
-					\frac{n q^n}{1 - q^n}
-				+ \frac{z}{(z - 1)^2}
-			}
-	\end{aligned}
-	\label{eq:propagator_diff_sum}
-	\end{equation}
-
-	On the other hand, the torus propagator is given by:
-	\begin{gather}
-		G'(w,\bar{w};w',\bar{w}')
-		= - \frac{\alpha'}{2}\,
-				\ln \abs{f(w - w',\tau)}^2
-			+ \frac{\alpha'}{4\pi\tau_2}\,
-				\pqty\big{\Im \pqty{w - w'}}^2,\\
-		f(w,\tau) \equiv
-		\theta_1 \pqty{
-				\frac{w}{2\pi}
-				\,\bigg\vert\,
-				\tau
-			}
-		= 2\,e^{\frac{i\pi\tau}{4}} \sin \frac{w}{2}\,
-			\prod_{m > 0}^\infty
-				(1 - q^m)
-				(1 - z^{-1}q^m)
-				(1 - zq^m),\quad
-		z = e^{-iw}
-	\end{gather}
-	We find that $
-		\pdd{w} \pdd{w'} G'
-	$ contains the same zero mode contribution $
-		\frac{\alpha'}{8\pi\tau_2}
-	$ and normal ordering contribution $
-		\frac{\alpha'}{2} \frac{z}{(z - 1)^2}
-	$ as in \eqref{eq:propagator_diff_sum}:
-	\begin{gather}
-		\pdd{w} \pdd{w'} G'(w,\bar{w};w',\bar{w}')_{
-			w' = 0
-		}
-		= \frac{\alpha'}{8\pi\tau_2}
-			+ \frac{\alpha'}{2}
-				\pdd{w}^2 \ln f(w,\tau),
-	\\[1ex]
-		\pdd{w}^2 \ln f(w,\tau)
-		= \pdd{w}^2 \ln \sin \frac{w}{2}
-			+ \pdd{w}^2 \sum_{m > 0}  \pqty\Big{
-				\ln \,(1 - zq^m)
-				+ \ln \,(1 - z^{-1}q^m)
+	Here $W_{ij}(t)$ is the ``corrected'' distance on $T^2$; as $w\to w'$ we have $W_{ij}\sim w_{ij} = w_i - w_j$.
+
+	On the other hand, the vacuum amplitude is given by:
+	\begin{equation}
+		Z = iV_d \int_0^\infty
+			\frac{\dd{t}}{2t}\,
+			\pqty{8\pi^2\alpha't}^{-d/2}
+			\eta(it)^{-(d-2)}
+	\end{equation}
+	The $bc$ ghost contributions is included in the $
+		\abs{\eta(it)}^2
+		= \pqty\big{\eta(it)}^2
+	$ factor; note that for $t > 0,\,\eta(it)>0$. Combining this and $
+		\ave*{\prod_i \normorder{e^{ik_i\cdot X_i}}}_t
+	$, we obtain the final $n$-tachyon amplitude:
+	\begin{equation}
+		\mcal{A}
+		= ig_o^n\, (2\pi)^d\,
+			\delta^d\pqty{\textstyle\sum_i k_i}
+			\int_0^\infty
+				\frac{\dd{t}}{2t}\,
+				\pqty{8\pi^2\alpha't}^{-d/2}
+				\eta(it)^{-(d-2)}
+			\prod_k \int_{\pd M} \dd{w_k}
+			\prod_{i<j}
+				\abs{W_{ij}(t)}^{
+					2\times \alpha'k_i\cdot k_j
+				}
+	\end{equation}
+	Here $\pd M$ is the two ends of the cylinder.
+
+	As is suggested in \arxiv{0812.4408}, it is convenient to introduce the following parametrization for the operator insertions at each boundary:
+	\begin{equation}
+		w_i = \frac{1 - (-1)^\sigma}{2}\,\pi
+			+ 2\pi it\cdot x_i,
+	\quad
+		0\le x_i\le 1
+	\end{equation}
+	$\sigma = 0,1$ labels the left and right boundary.
+
+	We want 2 insertions at each boundary, labeled by $
+		i = 1,2,\,\sigma = 0
+	$, and $
+		i = 3,4,\,\sigma = 1
+	$; the amplitude can then be reduced to:
+	\begin{equation}
+	\small
+	\begin{gathered}
+		\mcal{A}
+		= ig_o^n\, (2\pi)^d\,
+			\delta^d\pqty{\textstyle\sum_i k_i}
+			\prod_k 2\!\int_0^1 \dd{x_k}
+			\int_0^\infty
+				\frac{\dd{t}}{2t}\,
+				\pqty{8\pi^2\alpha't}^{-d/2}
+				\eta(it)^{-(d-2)}
+				(2\pi t)^n
+			\prod_{i<j}
+				\abs{W_{ij}(x_{ij},t)}^{
+					2 \alpha'k_i\cdot k_j
 				},
 	\\
-		\pdd{w}^2 \ln \sin \frac{w}{2}
-		= \pdd{w}^2 \ln \sin \frac{w}{2}
-		= - \frac{1}{4\sin^2 \!\frac{w}{2}}
-		= \frac{1}{2\,\pqty{\cos w - 1}}
-		= \frac{1}{z + z^{-1} - 2}
-		= \frac{z}{(z - 1)^2},
-	\end{gather}
-
-	The remaining parts come from oscillator modes; they also match with \eqref{eq:propagator_diff_sum}, but the equivalence is less obvious: we have\footnote{
-		Reference: \url{http://theory.uchicago.edu/~sethi/Teaching/P483-W2018/p483-sol3.pdf}. I would like to thank {Lucy Smith} for providing this hint. 
-	}:
-	\begin{gather}
-	\begin{aligned}
-		\pdd{w}^2 \sum_{m > 0}
-			\ln \,(1 - zq^m)
-		&= \pdd{w}^2
-			\sum_{m > 0}
-			\sum_{n > 0}
-				-\frac{1}{n}\,\pqty\big{zq^m}^n \\
-		&= \sum_{n > 0}
-				\pdd{w}^2 \pqty{-\frac{1}{n}\,z^n}
-			\sum_{m > 0}
-				q^{mn},\quad \pdd{w} = -iz\,\pdd{z} \\
-		&= \sum_{n > 0}
-				- \frac{(-in)^2}{n}\,z^n
-				\cdot
-				\frac{q^n}{1 - q^n} \\
-		&= \sum_{n > 0}
-				z^n \frac{nq^n}{1 - q^n},
-	\end{aligned}
-	\allowdisplaybreaks
-	\\[1ex]
-		\pdd{w}^2 \sum_{m > 0}
-			\ln \,(1 - z^{-1} q^m)
-		= \sum_{n > 0}
-				z^{-n} \frac{nq^n}{1 - q^n},
-	\end{gather}
-	This is precisely the contribution from oscillator modes in \eqref{eq:propagator_diff_sum}. Therefore, we have:
-	\begin{equation}
-		\frac{1}{Z(\tau)}
-		\ave[\big]{
-			\pdd{w} X(w)\,\pdd{w'} X(w')
-		}_{w' = 0}
-		= \pdd{w} \pdd{w'}
-			G'(w,\bar{w};w',\bar{w}')_{w' = 0}
-	\end{equation}
+		W_{ij}(x_{ij},t)
+		= \eta(it)^{-3}\,
+			\vartheta_{1,2} \pqty{
+				ix_{ij} t \,\big|\, it
+			}\,
+			\exp \pqty{-\pi x^2_{ij} t}
+	\end{gathered}
+	\end{equation}
+	There is an additional factor of $2$ since $
+		\int_{\pd M} \dd{\omega} = 2\int \dd{x}
+	$, which includes the contribution after exchange of the two ends $
+		12\leftrightarrow 34
+	$. 
+	Also, $\vartheta_{1,2} = \vartheta_1$ or $\vartheta_2$, depending on whether the vertex operators $i$ and $j$ are on the same boundary or not; this is because:
+	\begin{equation}
+		\vartheta_1 \pqty{
+			ix_{ij} t - \tfrac{1}{2} \,\big|\, it
+		}
+		= -\vartheta_2 \pqty{
+			ix_{ij} t \,\big|\, it
+		}
+	\end{equation}
+
+	The $\eta(it)^{-3}$ factor in $W_{ij}$ can be further extracted using the on-shell condition $\alpha'k_i^2 = 1$. More specifically, we have:
+	\begin{equation}
+		\sum_{i<j}
+			2 \alpha'k_i\cdot k_j
+		= \alpha' \pqty\bigg{\sum_i k_i}^{\!\!2}
+			- \alpha' \sum_i k_i^2
+		= 0 - n = -n
+	\end{equation}
+	Therefore, we have:
+	\begin{equation}
+	\small
+	\begin{gathered}
+		\mcal{A}
+		= ig_o^n\, (2\pi)^d\,
+			\delta^d\pqty{\textstyle\sum_i k_i}
+			\prod_k \int_0^1 \dd{x_k}
+			\int_0^\infty
+				\frac{\dd{t}}{t}\,
+				\pqty{8\pi^2\alpha't}^{-d/2}
+				(2\pi t)^n
+				\eta(it)^{\bm{3n}-(d-2)}
+			\prod_{i<j}
+				\abs{W'_{ij}(x_{ij},t)}^{
+					2 \alpha'k_i\cdot k_j
+				},
+	\\
+		W'_{ij}(x_{ij},t)
+		= \vartheta_{1,2} \pqty{
+				ix_{ij} t \,\big|\, it
+			}\,
+			\exp \pqty{-\pi x^2_{ij} t}
+	\end{gathered}
+	\end{equation}
+
+	To further simplify the expression, collect all the numerical coefficients:
+	\begin{equation}
+		ig_o^n\, (2\pi)^d\,
+			\pqty{8\pi^2\alpha'}^{-d/2}
+			(2\pi)^n
+		= ig_o^n\, (2\pi)^d\,
+			2^{-d/2} (2\pi)^{-d} \alpha'^{-d/2}
+			(2\pi)^n
+		= ig_o^n\, (2\pi)^n\,
+			2^{-d/2} \alpha'^{-d/2}
+	\end{equation}
+	In our case $n = 4$ and $d = 26$.
+
+	The $t$ integral can be magically simplified using modular transformations of the $\vartheta$ functions\footnote{
+		Reference: \arxiv{0812.4408} and \textit{Polchinski}'s summary of $\vartheta$ function properties. 
+	}; with $t = \frac{1}{u}$, we have:
+	\begin{equation}
+	\begin{aligned}
+		F(x)
+		&= \int_0^\infty \dd{t}
+			t^{n-1-d/2}
+			\eta(it)^{3n-(d-2)}
+			\prod_{i<j}
+				\abs{W'_{ij}(x_{ij},t)}^{
+					2 \alpha'k_i\cdot k_j
+				} \\
+		&= \int_0^\infty \dd{u}
+			\eta(iu)^{3n-(d-2)}
+			\prod_{i<j}
+				\abs{
+					\vartheta_{1,4} \pqty{
+						x_{ij} | iu
+					}
+				}^{
+					2 \alpha'k_i\cdot k_j
+				}
+	\end{aligned}
+	\end{equation}
+	The amplitude can then be neatly written as:
+	\begin{equation}
+		\mcal{A}
+		= ig_o^n\, (2\pi)^n\,
+			2^{-d/2} \alpha'^{-d/2}\,
+			\delta^d\pqty{\textstyle\sum_i k_i}
+			\prod_k \int_0^1 \dd{x_k} F(x)
+	\end{equation}
+
+	\item The ``long cylinder'' limit corresponds to the $t\to 0$ contributions in the above amplitude. Note that the full amplitude is an integral over the moduli $t = \frac{1}{u}$, 
+	\begin{equation}
+		F(x)
+		= \int_0^\infty \dd{u} f(x,u),
+	\quad
+		u = \frac{1}{t},
+	\quad
+		f(x,u)
+		= \eta(iu)^{3n-(d-2)}
+			\prod_{i<j}
+				\abs{
+					\vartheta_{1,4} \pqty{
+						x_{ij} | iu
+					}
+				}^{
+					2 \alpha'k_i\cdot k_j
+				}, 
+	\end{equation}
+	We need only look at the integrand $f(x,u)$ as $u\to\infty$, or $
+		q \equiv e^{-2\pi u} \to 0
+	$.
+In this case $f(x,u)$ can be expanded as power series; $\vartheta_4$ contributions turn out to be sub-leading, hence the product only needs to go over $i,j$ on the same side, denoted as $(i,j)_\sigma$.
+We have:
+	\begin{equation}
+		f(x,u)
+		= q^{\frac{3n-(d-2)}{24}}
+			\prod_{(i<j)_\sigma}
+				\abs{
+					2\sin \pi x_{ij}
+				}^{2\alpha'k_i\cdot k_j}
+			q^{\frac{2\alpha'k_i\cdot k_j}{8}}
+			\pqty\big{
+				1 + \order{q}
+			}
+	\end{equation}
+
+	Again we can simplify using on-shell conditions and Mandelstam variables; we have:
+	\begin{equation}
+	\begin{aligned}
+		\sum_{(i<j)_\sigma}
+				2\alpha'k_i\cdot k_j
+		&= \sum_{i<j}
+				2\alpha'k_i\cdot k_j
+			- \sum_{i,\sigma=0} \sum_{j,\sigma=1}
+				2\alpha'k_i\cdot k_j \\
+		&= -n - 2\alpha' \sum_{i,\sigma=0} k_i
+			\sum_{j,\sigma=1} k_j \\
+		&= -n - 2\alpha's,
+	\quad
+		s = -\pqty\bigg{\,\sum_{i,\sigma=0} k_i}^{\!\!2}
+		= -\pqty\bigg{\,\sum_{i,\sigma=1} k_i}^{\!\!2}
+	\end{aligned}
+	\end{equation}
+	Where $s$ is the mass squared of the intermediate state propagating along the long cylinder, from one end to another. With this we find that:
+	\begin{equation}
+	\begin{aligned}
+		f(x,u)
+		&= q^{
+				\frac{3n-(d-2)}{24}
+				+ \frac{-n-2\alpha's}{8}
+			}
+			\prod_{(i<j)_\sigma}
+				\abs{
+					2\sin \pi x_{ij}
+				}^{2\alpha'k_i\cdot k_j}
+			\pqty\big{
+				1 + \order{q}
+			} \\
+		&= q^{
+				-1 - \frac{\alpha's}{4}
+			}
+			\prod_{(i<j)_\sigma}
+				\abs{
+					2\sin \pi x_{ij}
+				}^{2\alpha'k_i\cdot k_j}
+			\pqty\big{
+				1 + \order{q}
+			}
+	\end{aligned}
+	\end{equation}
+
+	Upon integrating over $u$, each $q^k$ in the power series above produces a pole in $s$:
+	\begin{equation}
+		\int_0^\infty \dd{u}
+			q^{
+				-1 - \frac{\alpha's}{4}
+			} q^k
+		\propto \frac{1}{k - 1 - \frac{\alpha's}{4}}
+		\propto \frac{1}{s - \frac{4}{\alpha'}(k-1)}
+	\end{equation}
+	Apparently every integer power $k$ appears in the expansion, hence we have the full closed string spectrum at $s = \frac{4}{\alpha'}(k-1),\,k=0,1,2,\cdots$.
+
+	\newparagraph
+	Consider the tachyon pole, i.e.\ $
+		k = 0,\,s = -\frac{4}{\alpha'}
+	$; this contribution is represented as two disk diagrams linked by a closed string tachyon propagator; each disk has 3 insertions, two incoming (or outgoing) open string tachyons and one outgoing (or incoming) closed string tachyon.
+
+	By unitarity of the 4-point amplitude\footnote{
+		Reference: \textit{Polchinski}, Chapter 9. 
+	}, sum of all such factorized diagrams should be equal to the original cylinder diagram; therefore, the strength of the tachyon pole, calculated from such two-disk diagram, should be equal to our previous calculations from the cylinder diagram.
+
+	On the other hand, by unitarity of the 3-point amplitude, the incoming and the outgoing disk diagrams have the same contributions.
+Therefore, we should expect that the closed string tachyon pole strength is equal to the \textit{square} of the disk amplitude with 3 insertions.
+
+	\item For the disk diagram, we have two open string insertions at the boundary, and one close string insertion in the disk; when mapped to the upper half plane, we can use the 3 CKVs to fix the closed string insertion at $(z,\bar{z})$ and one open string insertions at $x_1$, while integrating over the position $x_2$ of the remaining open string insertion:
+	\begin{equation}
+	\begin{aligned}
+		\mcal{A}_D
+		&= g_c g_o^2 e^{-\lambda}
+			\int \dd{x_2}
+			\ave[\Big]{
+				\normorder{
+					c\tilde{c}\,
+					e^{ik\cdot X}
+				}\,
+				\normorder{
+					c^x_1\,
+					e^{ik_1\cdot X_1}
+				}\,
+				\normorder{
+					e^{ik_2\cdot X_2}
+				}
+			} \\
+		&= g_c g_o^2\, iC\,(2\pi)^d\,
+			\delta^d\pqty{\textstyle\sum_i k_i}\,
+				\abs{z - x_1}
+				\abs{\bar{z} - x_1}
+				\abs{z - \bar{z}}
+		\\ & \hspace{2em} \times
+			\int \dd{x_2}
+				\abs{z - \bar{z}}^{\alpha'k^2/2}
+				\abs{x_1 - x_2}^{2\alpha'k_1\cdot k_2}
+			\prod_i
+				\abs{z - x_i}^{2\alpha'k\cdot k_i} \\
+	\end{aligned}
+	\end{equation}
+	Again note the doubling of exponents due to the image charges. With on-shell conditions, we get:
+	\begin{equation}
+	\begin{aligned}
+		\mcal{A}_D
+		&= iC g_c g_o^2\,
+			(2\pi)^d\,
+			\delta^d\pqty{\textstyle\sum_i k_i}\,
+				\abs{z - x_1}^{-2}
+				\abs{z - \bar{z}}^{3}
+			\int \dd{x_2}
+				\abs{x_1 - x_2}^{2}
+				\abs{z - x_2}^{-4} \\
+		&= iC g_c g_o^2\,
+			(2\pi)^d\,
+			\delta^d\pqty{\textstyle\sum_i k_i}\,
+			\cdot 4\pi
+	\end{aligned}
+	\end{equation}
+
+	Furthermore, $C$ can be fixed by comparing the 4-tachyon and 3-tachyon open string disk amplitudes\footnote{
+		Reference: \textit{Polchinski}, Chapter 6. 
+	}; we get:
+	\begin{equation}
+		C = \frac{1}{\alpha'g_o^2},\quad
+		\mcal{A}_D
+		= \frac{4\pi i g_c}{\alpha'}\,
+			(2\pi)^d\,
+			\delta^d\pqty{\textstyle\sum_i k_i}
+	\end{equation}
+	Combined with the closed string tachyon propagator, the factorized diagram described in (b) is then given by:
+	\begin{equation}
+		\mcal{A}'_0
+		= \pqty{\frac{4\pi i g_c}{\alpha'}}^2
+			\frac{i}{s - (-\frac{4}{\alpha'})}\,
+			(2\pi)^d\,
+			\delta^d\pqty{\textstyle\sum_i k_i}
+	\end{equation}
+
+	On the other hand, the tachyon pole in (b) is given by:
+	\begin{equation}
+	\begin{aligned}
+		\mcal{A}_0
+		&= ig_o^4\, (2\pi)^4\,
+			2^{-d/2} \alpha'^{-d/2}\,
+			\delta^d\pqty{\textstyle\sum_i k_i}
+			\prod_k \int_0^1 \dd{x_k} F(x) \\
+		&\simeq ig_o^4\, (2\pi)^4\,
+			2^{-d/2} \alpha'^{-d/2}\,
+			\delta^d\pqty{\textstyle\sum_i k_i}
+			\prod_k \int_0^1 \dd{x_k}
+			\pqty{
+				-\sin^2 (\pi x_{12})\,
+				\sin^2 (\pi x_{34})\,
+				\frac{2^5}{\pi\alpha'}
+				\frac{1}{s - (-\frac{4}{\alpha'})}
+			} \\
+		&= -ig_o^4\, (2\pi)^3\,
+			2^{-d/2+4} \alpha'^{-d/2-1}\,
+			\delta^d\pqty{\textstyle\sum_i k_i}
+			\frac{1}{s - (-\frac{4}{\alpha'})}
+	\end{aligned}
+	\end{equation}
+	Imposing $\mcal{A}'_0 = \mcal{A}_0$ gives our desired relation, with $l_s = \sqrt{\alpha'}$:
+	\begin{equation}
+		g_o^2
+		= 2^{3(d-2)/4} \pi^{(d-1)/2} \alpha'^{(d-2)/4} g_c
+		= 2^{18} \pi^{25/2} l_s^{12} g_c
+	\end{equation}
+
+	\end{enumerate}
 

### 2020-06-24 Strings2020/strings7/strings7.tex
Add strings7

% !TeX document-id = {39d24ce0-844d-44a8-943b-2a9698211621}
% !TeX encoding = UTF-8
% !TeX spellcheck = en_US
% !TeX TXS-program:bibliography = biber -l zh__pinyin --output-safechars %
% !TeX TS-program = xelatex
%%% LuaLaTeX is required for `tikz-feynman`

\documentclass[a4paper,10pt]{article}

\newcommand{\hwNumber}{7 [WIP]}

\input{../strings_preamble.tex}
\input{../.modules/basics/biblatex.tex}

%%% ID: sensitive, do NOT publish!
\InputIfFileExists{../id.tex}{}{}

\newcommand{\oppower}[2]{\mop{{#1}^{#2}}\!}
\newcommand{\sqsinh}{\oppower{\sinh}{2}}
\newcommand{\sqcosh}{\oppower{\cosh}{2}}

\newcommand{\Vir}{\mathbf{V}\mfrak{ir}}
\newcommand{\zbar}{\bar{z}}
%\usepackage{tikz-feynman,cancel}

% NS & R with spacing
\newcommand{\NS}{\ensuremath{\mspace{2mu}\mrm{NS}}}
\newcommand{\R}{\ensuremath{\mspace{2mu}\mrm{R}}}

% representations
\newcommand{\mbf}[1]{\mathbf{#1}}

%\addbibresource{strings6.bib}

\begin{document}
\maketitle
\pagestyle{headings}
\pagenumbering{arabic}
\thispagestyle{empty}

%{
%	\noindent\itshape%
%	本文约定：度规$\eta\sim\pqty{-,+,+,+}$, 指标$\mu,\nu,\dots = 0,1,2,3,\ i,j,\dots = 1,2,3$.
%}

\begin{enumerate}

\item \textbf{T-duality of Heterotic Strings}\footnote{
		I would like to thank Lucy Smith for help with this problem. 
	}

	We use $d \le 10$ to denote the number of noncompact dimensions; the remaining $m \ge d$ dimensions are compactified. For heterotic strings, the $I\ge 10$ dimensions of the left-moving sector are already compactified on a lattice $\Gamma_{16}$ or $\Gamma_8\times \Gamma_8$. Here we use the label $I$ to index the 16 internal dimensions.

	\begin{enumerate}
	\item Generally, if we compactify an open string on the $x^m$ direction: $x^m \cong x^m + 2\pi R$ with constant backgrounds $A_m$, then its zero mode spectrum, \textit{with winding $w = 0$}, can be obtained from canonical quantization of the effective point particle action, with an additional gauge action term in the form of a Wilson line\footnote{
		Reference: \textit{Polchinski}, Chapter 8. 
	}:
	\begin{equation}
		-W_q
		= -iq \int \dd{x^m} A_m
		\sim -iq \int \dd{\tau} A_m \dot{X}^m
	\end{equation}
	By imposing that the canonical momentum to be periodic along $x^m$, we find that:
	\begin{equation}
		k_m = \frac{n_m}{R} - q A_m
	\label{eq:effective_momentum}
	\end{equation}

	To obtain the winding states, we have to reproduce the above action from the world-sheet description. For heterotic strings with $m < 10 \le I \le 26$, this can be achieved by adding the following term to the usual world-sheet action\footnote{
		Reference: \textit{Blumenhagen et al}, Basic Concepts of String Theory. 
	}:
	\begin{equation}
		S_A \propto \int \dd[2]{\sigma}
			\epsilon^{ab} A^I_\mu
			\,\pdd{a} X^\mu
			\,\pdd{b} X_I
	\end{equation}
	With proper normalizations to match the result in \eqref{eq:effective_momentum}.

	Canonical quantization then produces\footnote{
		Reference: \textit{Polchinski}, Chapter 11. 
	}:
	\begin{gather}
		k_m
		= \frac{n_m}{R}
			\pm \frac{w_m R}{\alpha'}
			- q_I A^I_m
			- \frac{w_n R}{2} A^n_I A_m^I,
	\\
		k^I_L
		= \sqrt{\frac{2}{\alpha'}}\,
			\pqty{
				q^I + w^m R A^I_m
			},
	\end{gather}
	The \mquote{\pm} signs in $k_m$ correspond to the left and right-moving sector, respectively. Only the left-moving sector has an additional 16 dimensional internal torus, therefore $k^I$ is labeled with an $\mquote{L}$.

	Note that the charge $q^I$ now takes value on the $\Gamma_{16}$ or $\Gamma_8\times \Gamma_8$ lattice, and:
	\begin{equation}
		l\circ l'
		= \frac{\alpha'}{2} \pqty{
				k^I_L\, k'_{L,I}
				+ k^m_L\, k'_{L,m}
				- k^m_R\, k'_{R,m}
			}
		= q^I q'_I
			+ 2nw
	\end{equation}
	We can then see that the new ``extended'' lattice indeed satisfies the even and self-dual conditions, which follows from the even and self-dual properties of $\Gamma_{16}$ or $\Gamma_8\times \Gamma_8$.

	\item With $m = 9$ and $G_{dd} = 1$, we have:
	\begin{equation}
		W_q = \exp \pqty{-iq_I\theta^I},
	\quad
		A^I_9 = - \frac{\theta^I}{2\pi R}
	\end{equation}
	Note that $W_q$ captures the phase change of the paths that wind around $x^9$; the extra phase from a non-trivial Wilson line might affect the boundary condition of some states while leaving others intact, thus breaking the original gauge symmetry. Our discussions here closely follow \textit{Polchinski}, Chapter 11.

	For the SO(32) theory with:
	\begin{equation}
		RA^I_9
		= \mop{diag} \pqty{
				(\tfrac{1}{2})^8,
				0^8
			}
	\end{equation}
	Adjoint states are labeled by a pair of indices valued in $1,\cdots,32$; those with one index from $1 \le A \le 16$ and one from $17 \le A \le 32$ are antiperiodic due to the additional phase $e^{i\pi} = -1$ from the Wilson line, so the gauge symmetry is reduced to $\mrm{SO}(16) \times \mrm{SO}(16)$.

	Similarly, for the $E_8 \times E_8$ theory with:
	\begin{equation}
		R' A^I_9
		= \mop{diag} \pqty{
				1,0^7,
				1,0^7
			}
	\end{equation}
	Note that $\Gamma_8$, the root lattice of $E_8$, is basically the root lattice union an additional spinor weight lattice of SO(16). With the above Wilson line, the integer-charged states from the SO(16) root lattice in each $E_8$ remain periodic, while the half-integer charged states from the SO(16) spinor lattices become antiperiodic, due to the additional phase $e^{i\frac{1}{2}\cdot 2\pi} = -1$. Again the gauge symmetry is broken down to SO(16) × SO(16).

	In summary, with the above Wilson line, the SO(32) and $E_8 \times E_8$ theory shares a unbroken gauge of SO(16) × SO(16). Consider he spectrum of the SO(16) × SO(16) \textit{neutral states}, i.e.\ those with internal momentum:
	\begin{equation}
		k^I_L
		= \sqrt{\frac{2}{\alpha'}}\,
			\pqty{
				q^I + w R A^I_9
			}
		= 0
	\end{equation}
	For the $\mrm{SO}(32)$ theory, since $q^I \in \Gamma_{16}$
%	or $\Gamma_8\times \Gamma_8$ 
%	and adjoint states in  are integer-charged 
	while $
		RA^I_9
		= \mop{diag} \pqty{
				(\tfrac{1}{2})^8,
				0^8
			}
	$, we must have $w = 2m$ for this to hold. The same goes for the $E_8 \times E_8$ theory;
	therefore, we have:
	\begin{gather}
		k_{L,R} = \frac{\tilde{n}}{R}
			\pm \frac{2mR}{\alpha'},
	\quad
		k'_{L,R} = \frac{\tilde{n}'}{R'}
			\pm \frac{2m'R'}{\alpha'},
	\\
		\tilde{n} = n + 2m,\quad
		\tilde{n}' = n' + 2m'
	\end{gather}

	\item If the two theories are related by T-duality, then we should expect:
	\begin{equation}
		(k_L, k_R) \longleftrightarrow (k'_L, −k'_R),
	\end{equation}
	Under suitable mapping of parameters. Indeed, it is straightforward to verify that $
		(\tilde{n},m)\leftrightarrow (m',\tilde{n}')
	$ realizes this, along with $
		RR' = \alpha'/2
	$. The above arguments can then be generalized to higher levels, by acting on fermionized left-moving fields $\lambda^A$ and carefully organizing representations. We see that the two heterotic string theories are equivalent under T-duality.
	\end{enumerate}

\item \textbf{String Junction}\footnote{
		Reference: \arxiv{0812.4408}. 
	}
%	\begin{figure}[!ht]
%	\centering
%	\includegraphics[width=.2\linewidth]{FD_bound.png}
%	\caption{String Junction}
%	\label{fig:string_junction}
%	\end{figure}

	\nopagebreak
	For a string junction to be mechanically stable, the tension force exerted on the junction must cancel each other; this is a Newtonian mechanics problem, but with $(p,q)$-string tension given by the BPS bound:
	\begin{equation}
		\tau_{(p,q)}
		= \frac{\sqrt{p^2 + q^2/g^2}}{2\pi\alpha'}
	\end{equation}
	Stabibility of the system implies that the BPS bound should be saturated.

	From Newtonian mechanics, we know that three forces cannot cancel each other unless they are co-planar. Therefore, a 3-string junction must be co-planar in order to be stable. Suppose they lie in the $(X^1,X^2)$ plane, then the tension exerted on the junction can expressed as:
	\begin{equation}
		\vec{T}_i = \tau_{(p_i,q_i)}\,\pqty{
				\cos\theta_i,
				\sin\theta_i
			},
	\quad i = 1,2,3,
	\end{equation}
	$\sum_i \vec{T}_i = 0$ gives two equations, and we have two independent unknowns (the angle between two pairs of strings); therefore if a solution exists, it should be unique up to rotations and reflections.

	In fact, a solution can be found by simple observations:
	\begin{equation}
		\cos\theta_i
		= \frac{p_i}{\sqrt{p^2 + q^2/g^2}},
	\quad
		\sin\theta_i
		= \frac{q_i/g}{\sqrt{p^2 + q^2/g^2}},
	\end{equation}
	It satisfies $\sum_i \vec{T}_i = 0$ since that total $(p,q)$ vanishes at each junction.

	To find the remaining supersymmetries of this system, we start from the original supersymmetries of a $(p,q)$ string (which saturates the BPS bound) extended along the $\hat{X} = (\cos\theta,\sin\theta)$ direction:
	\begin{gather}
		\frac{1}{2L\tau_{(p,q)}} \Bqty{
			\bqty{\mqty{
				Q_\alpha \\
				\tilde{Q}_\alpha
			}},
			\bqty{
				Q^\dagger_\beta
				\ \tilde{Q}^\dagger_\beta}
		}
		= \delta_{\alpha\beta}
				\bmqty{
					1 & 0 \\
					0 & 1 \\
				}
			+ (\Gamma^0 \Gamma^\theta)_{\alpha\beta}
				\bmqty{
					\cos\theta & \sin\theta \\
					\sin\theta & -\cos\theta \\
				},
	\\
		\Gamma^\theta
		= \hat{X}\cdot \vec{\Gamma}
		= \Gamma^1\cos\theta + \Gamma^2\sin\theta
	\end{gather}
	We see that the algebra depends on $\theta$, i.e.\ it is different for strings in different directions. However, if we can find a (maximal) subalgebra that is independent of $\theta$, then we would have found the remaining supersymmetries of the full system\footnote{
		The $\tau_{(p,q)}$ factor can be absorbed by rescaling generators, hence does not matter in our discussions. 
	}.

	We begin with diagonalizing the matrix on the RHS with:
	\begin{gather}
		U(\tfrac{\theta}{2}) = \bmqty{
				\cos\frac{\theta}{2} &
				-\sin\frac{\theta}{2} \\
				\sin\frac{\theta}{2} &
				\cos\frac{\theta}{2} \\
			},
	\\[1ex]
		\frac{1}{2L\tau_{(p,q)}} \Bqty{
			U^{\mrm{T}}
			\bqty{\mqty{
				Q_\alpha \\
				\tilde{Q}_\alpha
			}},
			\bqty{
				Q^\dagger_\beta
				\ \tilde{Q}^\dagger_\beta
			}
			U
		}
		= \bmqty{
			(\idty + \Gamma^0\Gamma^\theta)_{\alpha\beta} &
			0 \\
			0 &
			(\idty - \Gamma^0\Gamma^\theta)_{\alpha\beta} \\
		},
	\end{gather}
	Note that $
		(\idty + \Gamma^0\Gamma^\theta)
		(\idty - \Gamma^0\Gamma^\theta)
		= 0
	$ and $
		(\idty + \Gamma^0\Gamma^\theta)
		+ (\idty - \Gamma^0\Gamma^\theta)
		= 2\idty
	$, i.e.\ they are orthogonal to each other; acting $
		(\idty \pm \Gamma^0\Gamma^\theta)
	$ on both sides, we find the following combinations, which gives the 16 SUSYs of a $(p,q)$ string:
	\begin{equation}
		(\idty - \Gamma^0\Gamma^\theta)
		\pqty{
			\cos\tfrac{\theta}{2}\, Q
			+ \sin\tfrac{\theta}{2}\, \tilde{Q}
		}_\alpha
		= 0 =
		(\idty + \Gamma^0\Gamma^\theta)
		\pqty{
			- \sin\tfrac{\theta}{2}\, Q
			+ \cos\tfrac{\theta}{2}\, \tilde{Q}
		}_\beta
	\label{eq:pq_string_susy}
	\end{equation}

\pagebreak[4]

	For further simplification, we can isolate the $\theta$ dependence in $\Gamma^\theta$ by working in a specific representation of the Clifford algebra, e.g.\ the Dirac representation given by \textit{Polchinski}. Then $\alpha$ is given by 10\,D spinor components: $
		\alpha = (s_0,s_1,s_2,s_3,s_4),\ %
		s_i = \pm
	$, with additional chirality constraints from both $Q$ and $\tilde{Q}$: $
		\prod_i s_i = +
	$. In the end, we have 16 independent components as expected.

	Details of the expansion is given in \arxiv{0812.4408}. When the dust settles, we find that the 16 SUSYs in \eqref{eq:pq_string_susy} is given by:
	\begin{subequations}
	\begin{gather}
		\sin\tfrac{\theta}{2}\,
		\pqty{
			\cos\tfrac{\theta}{2}\, Q
			+ \sin\tfrac{\theta}{2}\, \tilde{Q}
		}_{(++s)}
		+ \cos\tfrac{\theta}{2}\,
		\pqty{
			\cos\tfrac{\theta}{2}\, Q
			+ \sin\tfrac{\theta}{2}\, \tilde{Q}
		}_{(--s)},
	\\
		\sin\tfrac{\theta}{2}\,
		\pqty{
			\cos\tfrac{\theta}{2}\, Q
			+ \sin\tfrac{\theta}{2}\, \tilde{Q}
		}_{(+-s)}
		- \cos\tfrac{\theta}{2}\,
		\pqty{
			\cos\tfrac{\theta}{2}\, Q
			+ \sin\tfrac{\theta}{2}\, \tilde{Q}
		}_{(-+s)},
	\\
		\cos\tfrac{\theta}{2}\,
		\pqty{
			- \sin\tfrac{\theta}{2}\, Q
			+ \cos\tfrac{\theta}{2}\, \tilde{Q}
		}_{(++s)}
		- \sin\tfrac{\theta}{2}\,
		\pqty{
			- \sin\tfrac{\theta}{2}\, Q
			+ \cos\tfrac{\theta}{2}\, \tilde{Q}
		}_{(--s)},
	\\
		\cos\tfrac{\theta}{2}\,
		\pqty{
			- \sin\tfrac{\theta}{2}\, Q
			+ \cos\tfrac{\theta}{2}\, \tilde{Q}
		}_{(+-s)}
		+ \sin\tfrac{\theta}{2}\,
		\pqty{
			- \sin\tfrac{\theta}{2}\, Q
			+ \cos\tfrac{\theta}{2}\, \tilde{Q}
		}_{(-+s)},
	\end{gather}
	\end{subequations}
	\vspace{-.8\baselineskip}
	\begin{equation}
		s = (s_2 s_3 s_4),\quad
		\prod_i s_i = +
	\end{equation}

	By trial and error, we can find the 8 linear combinations that are independent of $\theta$; they are:
	\begin{gather}
		(a) + (c)
		\quad\Longrightarrow\quad
		\tilde{Q}_{(++s)} + Q_{(--s)},
	\\
		(b) + (d)
		\quad\Longrightarrow\quad
		\tilde{Q}_{(+-s)} - Q_{(-+s)},
	\end{gather}
	Therefore, the string junction is $\frac{8}{32} = \frac{1}{4}$ BPS.

\item \textbf{Two and Three-Point Functions in AdS/CFT}

\end{enumerate}

\printbibliography[%
%	title = {参考文献} %
	,heading = bibintoc
]
\end{document}

### 2020-06-24 Strings2020/strings7/strings7.tex
Finish strings7

@@
 \item \textbf{Two and Three-Point Functions in AdS/CFT}
+\def\adsFive/{$\mrm{AdS}_5$}
+
+	Consider a scalar field $\phi(x,z)$ in Poincar\'e \adsFive/ (with radius $R = 1$) satisfying:
+	\begin{equation}
+		\pqty{\laplacian - m^2}\,
+			\phi(x,z) = 0,
+	\quad
+		\phi(x,z) \to
+		\left\lbrace\vbox to 12.5pt {}\right.
+		\begin{aligned}
+			& z^\delta \phi_0(x)\,,
+				&& z\to 0, \\[-.35ex]
+			& \mrm{regular},
+				&& z\to\infty,
+		\end{aligned}
+	\quad
+		\delta = 2 - \sqrt{m^2 + 4}
+	\end{equation}
+	It can be constructed via the boundary-to-bulk propagator $K_\Delta$:
+	\begin{gather}
+		\phi(x,z)
+		= \int \dd[4]{x'}
+			K_\Delta(x,z;x')\,
+			\phi(x'),
+	\\
+		K_\Delta(x,z;x')
+		= \frac{(\Delta - 1)(\Delta - 2)}{\pi^2}
+			\pqty{\frac{z}{
+				z^2 + \norm{x - x'}^2
+			}}^{\!\!\Delta},
+	\quad
+		\Delta = 2 + \sqrt{m^2 + 4}
+	\end{gather}
+
+	\begin{enumerate}
+	\item To verify this, we first check that the boundary conditions are indeed satisfied by $K_\Delta$; note that $\Delta \ge 2 > 0$, and we have:
+	\begin{equation}
+		z\to 0,\quad l \ne 0,
+	\quad
+		\pqty{\frac{z}{
+			z^2 + l^2
+		}}^{\!\!\Delta} \to 0,
+	\end{equation}
+	i.e.\ the only contribution comes from the $l\to 0$ case, where we have:
+	\begin{equation}
+	\begin{aligned}
+		l = \norm{x - x'} \to 0,
+	\quad
+		\int \dd[4]{x'}
+			K_\Delta(x,z;x')
+		&= \frac{(\Delta - 1)(\Delta - 2)}{\pi^2}
+			\int_0^\infty 2\pi^2 l^3 \dd{l}
+				\pqty{\frac{z}{
+					z^2 + l^2
+				}}^{\!\!\Delta} \\
+		&= \frac{(\Delta - 1)(\Delta - 2)}{\pi^2}\cdot
+			\frac{2\pi^2}{2\,(\Delta - 1)(\Delta - 2)}\,
+			z^{4 - \Delta} \\
+		&= z^\delta
+	\end{aligned}
+	\end{equation}
+	Therefore, we have:
+	\begin{equation}
+		z \to 0,
+	\quad
+		K_\Delta(x,z;x')
+		\to z^\delta \delta^4(x - x'),
+	\quad
+		\phi(x,z)
+		\to z^\delta \phi_0(x),
+	\end{equation}
+	The other boundary condition is convenient to check; we have:
+	\begin{equation}
+		z \to \infty,
+	\quad
+		K_\Delta(x,z;x')
+		\propsim z^{-\Delta} \to 0,
+	\quad
+		\phi(x,z)
+		\,\ \text{regular.}
+	\end{equation}
+
+	Now we need only check that $K_\Delta$ satisfies the equation of motion; in Poincar\'e \adsFive/ we have:
+	\begin{equation}
+		\laplacian
+		= z^2 \pqty{
+				\pdd{z}^2
+				- \frac{3}{z}\, \pdd{z}
+				+ \pdd{x}^2
+			}
+	\end{equation}
+	With the help of Mathematica\textsuperscript{TM}, it is straightforward to check that $
+		\pqty{\laplacian - m^2}\,
+			\pqty\big{\frac{z}{
+				z^2 + l^2
+			}}^{\Delta}
+		= 0
+	$, therefore $
+		\pqty{\laplacian - m^2}\,
+			\phi(x,z) = 0
+	$.
+
+	\newparagraph
+	The AdS/CFT dictionary is given by:
+	\begin{equation}
+		\ave*{
+			e^{
+				\int\dd[4]{x}\,
+					C_O\, \phi_0(x)\, O(x)
+			}
+		}_{\mrm{CFT}}
+		= e^{-S[\phi_0]}
+	\end{equation}
+	Where $S[\phi_0]$ the bulk effective action evaluated on the solution to the equation of motion:
+%	We have taken the classical limit in the RHS, since the AdS/CFT correspondence is a strong/weak duality; for a strongly coupled CFT the bulk theory is weakly coupled, 
+	\begin{equation}
+		S[\phi_0]
+		= \int \dd[4]{x} \dd{z}
+			\sqrt{-G}\,\Bqty{
+				\frac{1}{2}\,\pqty{\pdd{\mu}\phi}^2
+				+ \frac{1}{2}\,m^2 \phi^2
+				+ \frac{1}{3}\,g \phi^3
+				+ \cdots
+			}
+	\end{equation}
+
+	\item The CFT 2-point function $
+		\ave{O(x)\,O(y)}
+	$ can be computed with the above dictionary, using the usual effective formalism, but with the bulk action instead of the boundary action:
+	\begin{equation}
+		\ave{O(x)\,O(y)}
+		= \frac{1}{C_O^2}
+			\eval{
+				\frac{\var[2]}{
+					\var{\phi_0(x)} \var{\phi_0(y)}
+				}\, e^{-S[\phi_0]}
+			}_{\phi_0=0}\!\!
+	\end{equation}
+	For 2-point function, we only need terms $\sim\order{\phi^2}$; note that:
+	\begin{equation}
+		\fdv{\phi(x,z)}{\phi_0(x')}
+		= K_\Delta(x,z;x'),
+	\end{equation}
+	\vspace{-.5\baselineskip}
+	\begin{equation}
+	\begin{aligned}
+		\var{S}[\phi_0]
+		&\sim \int \dd[4]{x} \dd{z} \sqrt{-G}\,
+				\pqty{-\laplacian + m^2}\,\phi \var{\phi}
+			+ \int_{z\to 0} \dd[4]{x} \sqrt{-G}\,
+				\pd^{z} \phi \var{\phi} \\
+		&= 0 - \int_{z\to 0} \dd[4]{x}
+				z^{-5} z^2
+				\pdd{z} \phi \var{\phi}
+		= -\int_{z\to 0} \dd[4]{x}
+				z^{-3}
+				\pdd{z} \phi \var{\phi},
+	\end{aligned}
+	\end{equation}
+	\begin{equation}
+	\begin{aligned}
+		\therefore\quad
+		\ave{O(x)\,O(y)}
+		&= +\frac{1}{C_O^2}
+			\eval{
+				\frac{\var}{
+					\var{\phi_0(x)}
+				}\, e^{-S[\phi_0]}
+				\int_{z\to 0} \dd[4]{x'} z^{-3}
+					\pdd{z} \phi(x',z)\,
+					K_\Delta(x',z;y)\,
+			}_{\phi_0=0}\!\! \\
+		&= \frac{1}{C_O^2}
+				\int_{z\to 0} \dd[4]{x'} z^{-3}
+					\pdd{z} K_\Delta(x',z;x)\,
+					K_\Delta(x',z;y) \\
+		&= \frac{1}{C_O^2}
+				\int_{z\to 0} \dd[4]{x'} z^{-3}
+					\pdd{z} K_\Delta(x',z;x)\,
+					z^\delta \delta^4(x' - y) \\
+		&= \frac{z^{\delta - 3}}{C_O^2}\,
+			\pdd{z} K_\Delta(x,z;y) \\
+		&\sim \frac{z^{\delta-3}}{C_O^2}\,
+			\frac{(\Delta - 1)(\Delta - 2)}{\pi^2}
+			\frac{
+				\Delta z^{\Delta-1}
+			}{\norm{x - y}^{2\Delta}} \\
+		&= \frac{1}{C_O^2}\,
+			\frac{\Delta(\Delta - 1)(\Delta - 2)}{\pi^2}
+			\frac{1}{\norm{x - y}^{2\Delta}} \\
+	\end{aligned}
+	\end{equation}
+
+	Therefore, if we want $
+		\ave{O(x)\,O(y)}
+		= \frac{1}{\norm{x - y}^{2\Delta}}
+	$, then we have\footnote{
+		Reference: \arxiv{hep-th/9804058}. Again I would like to thank Lucy Smith for hints with this problem. 
+	}:
+	\begin{equation}
+		C_O
+		= \frac{1}{\pi} \sqrt{
+				\Delta(\Delta - 1)(\Delta - 2)
+			}
+	\end{equation}
+	Here $z\to 0$ is a cutoff parameter.
+
+	\item Similarly, we can use the dictionary to compute 3-point functions; we have\footnote{
+		Reference: \arxiv{hep-th/9905111}, and \arxiv{hep-th/9804058}. 
+	}:
+	\begin{equation}
+		\ave{O(x_1)\,O(x_2)\,O(x_3)}
+		= \frac{1}{C_O^3}\,
+			\pqty{-\frac{g}{3}}
+			\int \dd[4]{x} \dd{z} \sqrt{-G}\,
+				K_\Delta(x,z;x_1)\,
+				K_\Delta(x,z;x_2)\,
+				K_\Delta(x,z;x_3)
+	\end{equation}
+	This is a difficult integral; as is suggested by \arxiv{hep-th/9804058}, we can use an important symmetry of AdS/CFT --- the inversion $
+		\vec{x}\mapsto \frac{\vec{x}}{x^2}
+	$, to complete the integration.
+
+	By conformal symmetry, we know that the 3-point function is of the form:
+	\begin{equation}
+		\ave{O(x_1)\,O(x_2)\,O(x_3)}
+		= A(x_1,x_2,x_3)
+		= \frac{C_{OOO}}{
+				\abs{x_{12}}^\Delta
+				\abs{x_{23}}^\Delta
+				\abs{x_{31}}^\Delta
+			},\quad x_{ij} = x_i - x_j
+	\end{equation}
+	First set $x_3 = 0$, then perform inversion on all other points:
+	\begin{gather}
+		x_i = \frac{x'_i}{x'^2_i}, \quad
+		(x,z) = \frac{(x',z')}{\,r'^2},
+	\quad
+		r^2 = x^2 + z^2,\quad
+		r^2 r'^2 = 1 = x_i^2 x_i'^2,
+	\\
+		\frac{\dd[4]{x} \dd{z}}{z^5}
+		= \frac{\dd[4]{x'} \dd{z'}}{z'^5},
+	\\
+	\begin{aligned}
+		\frac{z}{z^2 + \norm{x - x_i}^2}
+		&= \frac{z}{r^2 + x_i^2 - 2x\cdot x_i}
+		= \frac{z'/r'^2}{
+				1/r'^2 + 1/x'^2_i
+				- 2x'\cdot x'_i/\pqty{r'^2 x'^2_i}
+			} \\
+		&= \frac{z'}{r'^2 + x'^2_i - 2x'\cdot x'_i}
+			\,x'^2_i
+		= \frac{z'}{z'^2 + \norm{x' - x'_i}^2}
+			\,x'^2_i,
+	\end{aligned}
+	\\[1ex]
+		K_\Delta(x,z;x_i)
+		= K_\Delta(x',z';x'_i)\,\abs{x'_i}^{2\Delta}
+		= \frac{1}{\abs{x_i}^{2\Delta}}\,
+			K_\Delta(x',z';x'_i),
+	\end{gather}
+	With these in mind, we find that:
+	\begin{equation}
+		A(x_1,x_2,0)
+		= -\frac{g}{3C_O^3}\,
+			\frac{1}{\abs{x_1}^{2\Delta}}
+			\frac{1}{\abs{x_2}^{2\Delta}}
+			\frac{(\Delta - 1)(\Delta - 2)}{\pi^2}
+		\int \frac{\dd[4]{x'} \dd{z'}}{z'^5}
+			K_\Delta(x',z';x'_1)\,
+			K_\Delta(x',z';x'_2)\,
+			z'^\Delta
+	\end{equation}
+	The integral can then be completed using Feynman parameters; in the end we obtain:
+	\begin{gather}
+		A(x_1,x_2,0)
+		\propto
+			\frac{1}{\abs{x_1}^{2\Delta}}
+			\frac{1}{\abs{x_2}^{2\Delta}}
+			\frac{1}{\abs{x'_1 - x'_2}^{2\Delta}}
+		= \frac{1}{
+				\abs{x_1}^{\Delta}
+				\abs{x_2}^{\Delta}
+				\abs{x_1 - x_2}^{\Delta}
+			},
+	\\[1ex]
+		C_{OOO}
+		= -\frac{g}{3C_O^3}\,
+			\frac{1}{2\pi^4}
+			\pqty{
+				\frac{\Gamma(\tfrac{\Delta}{2})}{
+					\Gamma(\Delta - 2)
+				}
+			}^{\!\!3}
+			\Gamma\pqty{
+				\frac{3\Delta - 4}{2}
+			}
+	\end{gather}
+
+	\end{enumerate}
 

### 2020-06-24 Strings2020/strings7/strings7.tex
Update strings7

@@
 
-\newcommand{\hwNumber}{7 [WIP]}
+\newcommand{\hwNumber}{7}
 
@@
 For heterotic strings with $m < 10 \le I \le 26$, this can be achieved by adding the following term to the usual world-sheet action\footnote{
-		Reference: \textit{Blumenhagen et al}, Basic Concepts of String Theory. 
+		Reference: \textit{Blumenhagen et al.}, Basic Concepts of String Theory. 
 	}:
@@
 	\end{equation}
-	With proper normalizations to match the result in \eqref{eq:effective_momentum}.
+	With proper normalization to match the result in \eqref{eq:effective_momentum}.
 
@@
 	\end{equation}
-	Adjoint states are labeled by a pair of indices valued in $1,\cdots,32$; those with one index from $1 \le A \le 16$ and one from $17 \le A \le 32$ are antiperiodic due to the additional phase $e^{i\pi} = -1$ from the Wilson line, so the gauge symmetry is reduced to $\mrm{SO}(16) \times \mrm{SO}(16)$.
+	Adjoint states are labeled by a pair of indices valued in $1,\cdots,32$; those with one index from $1 \le A \le 16$ and one from $17 \le A \le 32$ are anti-periodic due to the additional phase $e^{i\pi} = -1$ from the Wilson line, so the gauge symmetry is reduced to $\mrm{SO}(16) \times \mrm{SO}(16)$.
 
@@
 	Note that $\Gamma_8$, the root lattice of $E_8$, is basically the root lattice union an additional spinor weight lattice of SO(16).
-With the above Wilson line, the integer-charged states from the SO(16) root lattice in each $E_8$ remain periodic, while the half-integer charged states from the SO(16) spinor lattices become antiperiodic, due to the additional phase $e^{i\frac{1}{2}\cdot 2\pi} = -1$.
+With the above Wilson line, the integer-charged states from the SO(16) root lattice in each $E_8$ remain periodic, while the half-integer charged states from the SO(16) spinor lattices become anti-periodic, due to the additional phase $e^{i\frac{1}{2}\cdot 2\pi} = -1$.
 Again the gauge symmetry is broken down to SO(16) × SO(16).
 
-	In summary, with the above Wilson line, the SO(32) and $E_8 \times E_8$ theory shares a unbroken gauge of SO(16) × SO(16).
-Consider he spectrum of the SO(16) × SO(16) \textit{neutral states}, i.e.\ those with internal momentum:
+	In summary, with the above Wilson line, the SO(32) and $E_8 \times E_8$ theory shares an unbroken gauge of SO(16) × SO(16).
+Consider the spectrum of the SO(16) × SO(16) \textit{neutral states}, i.e.\ those with internal momentum:
 	\begin{equation}
@@
 	\end{equation}
-	Stabibility of the system implies that the BPS bound should be saturated.
+	Stability of the system implies that the BPS bound should be saturated.
 
@@
 
-	Details of the expansion is given in \arxiv{0812.4408}. When the dust settles, we find that the 16 SUSYs in \eqref{eq:pq_string_susy} is given by:
+	Details of the expansion are given in \arxiv{0812.4408}. When the dust settles, we find that the 16 SUSYs in \eqref{eq:pq_string_susy} is given by:
 	\begin{subequations}
@@
 	$, then we have\footnote{
-		Reference: \arxiv{hep-th/9804058}. Again I would like to thank Lucy Smith for hints with this problem. 
+		Reference: \arxiv{hep-th/9804058}. Again I would like to thank Lucy Smith for helpful hints. 
 	}:

### 2020-06-25 compile.sh
Lock custom texlive version, restructure release

@@ -11,6 +11,7 @@ log "$DIR"
 ls | xargs
 mkdir -p release
 
+# naming: $project/$sub_project/$main.tex
 FILES=$(find . \
     -regex "./[^/]+/[^/]+/[^/]+.tex" \
     -not -path "./Templates/*"
@@ -21,8 +22,10 @@ echo "$FILES"
 for file in $FILES; do
     log "Compiling \`$file\` ..."
 
-    cd "$(dirname "$file")" || exit 1
+    pathname=$(dirname "$file")
     filename=$(basename "$file")
+
+    cd "$pathname" || exit 1
 
     # Process magic comment
     tex_program=$(
@@ -47,8 +50,17 @@ for file in $FILES; do
 
     log "Check & release PDF:"
     pdf="$(basename "$filename" .tex).pdf"
-    ls "$pdf" \
-        && mv -v -f "$pdf" "$DIR/release/."
+    if ls "$pdf"; then
+
+        # shortened name: $project/$sub_project.tex
+        target="$DIR/release/$(dirname "$pathname")"
+        mkdir -p "$target"
+
+        # shellcheck disable=2015
+        [[ $USER == bryan ]] \
+            && cp -a -v -f "$pdf" "$target/." \
+            || mv -v -f "$pdf" "$target/."
+    fi
 
     cd "$DIR" || exit 1
 done

### 2020-06-26 compile.sh
Update workflow to include timestamp

@@ -67,3 +67,5 @@ done
 
 ls -alF release
 cp README.md LICENSE release
+
+TZ='Asia/Shanghai' date +'%F %R UTC+8' > release/TIMESTAMP

### 2020-06-26 AlgebraicTopology2020/algtop3/algtop3.tex
Add TOC to everything, along with minor tweaks

@@
 	\begin{equation}
-	\begin{tikzcd}[row sep=2ex,column sep=8ex]
+	\begin{tikzcd}[row sep=1.5ex,column sep=8ex]
 		&& 0 \\
@@
 				"\exists!\, g"]
-			\arrow[urr,bend left,%
+			\arrow[urr,bend left=25,%
 				"\eta_\bullet"]
-			\arrow[drr,bend right,swap,%
+			\arrow[drr,bend right=25,swap,%
 				"\eta_\star"] &
@@
 
-	\item
+	\item \textbf{Composition of pull-backs:}
+	\begin{equation}
+	\begin{tikzcd}[row sep=7.5ex,column sep=7.5ex]
+		Q
+			\arrow[ddr,bend right,"g_1",swap]
+			\arrow[dr,"f_1"]
+			\arrow[drr,"f_2",bend left=12]
+			\arrow[drrr,"f_3",bend left=20]
+		&[1ex] && \\[-1ex]
+		& A_1
+			\arrow[rr,"\phi'" description
+				,bend left,swap
+				,crossing over]
+			\arrow[r,dashed]
+			\arrow[d] &
+		A_2
+			\arrow[d]
+			\arrow[r,"\phi"] &
+		A_3
+			\arrow[d] \\
+		& B_1
+			\arrow[rr,"\psi'" description
+				,bend right=25,swap]
+			\arrow[r,"\psi",swap,dashed] &
+		B_2
+			\arrow[from=uull,"g_2",swap
+				,bend right=20
+				,crossing over]
+			\arrow[r] &
+		B_3
+	\end{tikzcd}
+	\end{equation}
+
+	\begin{enumerate}
+	\item If $A_1$ is the pull-back of $A_2$ and $A_2$ is the pull-back of $A_3$, then given $Q$ with $f_3,g_1$, we have $g_2 = \psi\circ g_1$, and $f_2$ is fixed uniquely by universal property of $A_2$, while $f_1$ is fixed uniquely by universal property of $A_1$.
+Hence, $A_1$ is the pull-back of $A_3$.
+
+	\item If $A_1,A_2$ are pull-backs of $A_3$, then given $Q$ with $f_2,g_1$, we have $f_3 = \phi\circ f_2$, and $f_2$ is fixed uniquely by universal property of $A_2$, and $f_1$ is fixed uniquely by universal property of $A_1$.
+Hence, $A_1$ is the pull-back of $A_3$.
+
+	\end{enumerate}
 

### 2020-06-26 compile.sh

@@ -68,4 +68,4 @@ done
 ls -alF release
 cp README.md LICENSE release
 
-TZ='Asia/Shanghai' date +'%F %R UTC+8' > release/TIMESTAMP
+TZ='Asia/Shanghai' date +'%F %R UTC+8' > release/TIMESTAMP.txt

### 2020-06-26 SpinorGR/spinor/spinor.tex
Add spinor notes

% !TeX document-id = {17e347e4-2d27-4494-abb3-36b9e7f18795}
% !TeX encoding = UTF-8
% !TeX spellcheck = en_US
% !TeX TXS-program:bibliography = biber -l zh__pinyin --output-safechars %

\documentclass[a4paper,11pt]{article}
\input{../preamble.tex}
\addbibresource{spinor.bib}
%\ctexset{fontset = ubuntu}

%Title
	\title{Positive Energy Theorem\\[.5ex]
		\& Spin Structure
%		\vspace*{-.2ex}\newline\large\{\textsl{based on \textit{Straumann}} \cite{Straumann:2013spu}\}%
	}
	\author{
		{\signature Bryan}, %
		\sf%
		X.~J.~Xie, %
		H.~Q.~Wu
	}
	\date{}

\begin{document}
\maketitle
\pagenumbering{arabic}
\pagestyle{headings}
\thispagestyle{empty}

\vspace{.2\baselineskip}

\setlength{\parskip}{.1\baselineskip}
\tableofcontents
\setlength{\parskip}{\parskipnorm}

\vspace{1\baselineskip}

\section{Introduction}
	Relativity and quantum mechanics are the two cornerstones of modern physics. Attempted unions of these two theories have produced some highly non-trivial results in theoretical physics. Most surprisingly, by considering \textit{classical limits} of quantum effects in general relativity, we can reveal some new structures of classical spacetime. 
	Witten's proof of the positive energy theorem \cite{Witten:1981mf} is a major example of such treatment.

	In general relativity, matter curves spacetime, and its effects are captured by Einstein's equations. \textsc{The positive energy conjecture} claims that ``regular'' matter\footnote{
		In theory, there \textit{can} be ``exotic'' matter, however unlikely in reality. For example, matter with negative mass can be used to create traversable wormhole. 
	} should give rise to spacetime with a positive energy, and the energy of spacetime is zero iff.~it is flat \cite{Straumann:2013spu}.

	This is a statement about purely classical general relativity. It feels natural in physics, but is extremely hard to prove in a rigorous way. The first complete proof is given by Schon and Yau \cite{Schon:1979rg} using techniques from geometric analysis. Witten's proof, on the other hand, relies heavily on the existence of \textit{spinor fields} on a given spacetime. Although it is inspired by ideas from quantum mechanics and even supersymmetry, the proof by itself is still fully contained in general relativity.

	Spinor field is a natural consequence of quantum field theory, and can be treated {semi-classically} by introducing additional \textit{spin structure} on the spacetime $\mcal{M}$. This will be the focus of our following discussions.

	As an introductory review, we try to illustrate the geometric aspects of spin structure and its role in Witten's proof of the positive energy theorem. To avoid technicalities of spinor analysis, we will only sketch some main ideas of the proof. For a more detailed treatment, see \cite{Witten:1981mf,Straumann:2013spu} for physicists and \cite{Parker:1981uy,jost2011riemannian} for mathematicians. 
\subsection{Review of General Relativity and Conventions}
	General relativity is formulated on a \textit{pseudo}-Riemannian (Lorentzian) manifold $(\mcal{M},g)$. $\mcal{M}$ is locally identical to $\mbb{R}^{3,1}$, here $\mbb{R}^{3,1} \approxeq \mbb{R\times}\mbb{R}^3$ with the {first} component being the {time} coordinate. From now on we will use the symbol ``$\approxeq$'' to denote diffeomorphism, or \textit{diffeo} for short. However, when there is extra structure involved (e.g.~group product), ``$\cong$'' will stand for \textit{isomorphism}, and we will use ``$\approxeq$'' for mere diffeo.

	Metric tensor can then be pointwise diagonalized:
	\begin{equation}
		g_{\mu\nu}
		= \eta_{ab}\,e\id{^a_\mu} e\id{^b_\nu}
			+ \order{x^2},\quad
		\eta_{ab} \sim \mop{diag}(-1,1,1,1)
			\sim\text{flat}
	\end{equation}
	Here $\mu,\nu, \cdots = 0,1,2,3$ denotes tensor components w.r.t.~local coordinates, while $a,b,\cdots = 0,1,2,3$ denotes components w.r.t.~a \textit{orthonormal frame field}\footnote{
		This is basically Cartan's \textit{moving frame} formalism. 
	} or \textit{vierbein}:
	\begin{equation}
		\Bqty\Big{
			\theta^a(x)
			= e\id{^a_\mu}(x) \dd{x^\mu}
		}_{a=0,1,2,3}
		\ \longleftrightarrow\ %
		\Bqty{
			e_a(x)
			= e\id{_a^\mu}(x)\,\pdv{x^\mu}
		}_{a=0,1,2,3}
		\label{eq:orthonormal_frame}
	\end{equation}

	It is often helpful to think of $\mcal{M}$ as the \textit{foliation / time-evolution} of a spacelike (Riemannian) codimension-1 hypersurface $\Sigma$ along a time direction\footnote{%
		In fact, global existence of such time slice $\Sigma$ (so-called \textit{Cauchy slice}) as an initial value surface is \textit{not} automatically guaranteed, but relies on the causal structure of $\mcal{M}$, see \cite{Wald:1984rg}; but locally we can always assume such structure. 
	}.

	Coordinates on $\Sigma$ is indexed with $i,j,\cdots = 1,2,3$. In fact, we assume that:
	\begin{equation}
		\mcal{M}_{(t_1,t_2)}
		\cong (t_1,t_2) \times \Sigma
		\cong \mbb{R} \times \Sigma
		\label{eq:local_decomp}
	\end{equation}
	Where $t\in (t_1,t_2)$ is some \textit{global time} coordinate restricted in an interval.

	Following the usual approach of Riemannian geometry, we can similarly define Riemann curvature $R\id{^\lambda_{\rho\mu\nu}}$, Ricci tensor $R_{\mu\nu}$ and scalar curvature $R$. Einstein's equations of relativity is then neatly organized into the following covariant tensorial expression\footnote{
		Here we have set Newton's constant $G_N = 1$ and cosmological constant $\Lambda = 0$. Proof of the Positive Energy Theorem with $\Lambda\ne 0$ is still incomplete to this day, and still an important field of research; see e.g.~\cite{Zhang:2015iua}. 
	}:
	\begin{equation}
		R_{\mu\nu} - \frac{1}{2} g_{\mu\nu} R
		= 8\pi T_{\mu\nu}
		\label{eq:einstein}
	\end{equation}
	The left-hand side (LHS) of the equation is purely geometric, while the right-hand side (RHS) is proportional to the symmetric \textit{energy--momentum stress tensor} $T_{\mu\nu}$, which describes matter distribution in spacetime. In general, we expect natural matter on the RHS will lead to well-behaved spacetime on the LHS; positive energy theorem is one exact case of such observation. 
\section{Positive Energy Theorem}
	Although Witten's proof relies on insights from quantum mechanics, the statement of positive energy theorem is purely \textit{classical} (in the sense that it does \textit{not} depend on quantum mechanics)\footnote{
		There are some variations between statements in the literature; here we will follow {Straumann}'s simplified version \cite{Straumann:2013spu} and {Witten}'s original work \cite{Witten:1981mf}, with mathematical supplements from Parker \textit{et al} \cite{Parker:1981uy}. 
	}. Here we summarize the main components of the theorem. 
\subsection{Constraints on Manifold and Total Energy}
\label{subsect:adm_energy}
	As is illustrated in \eqref{eq:local_decomp}, the main object to study can be reduced to a usual Riemannian manifold $\Sigma$. To make things easier, we shall further assume that $\Sigma$ is \textit{asymptotically flat}, i.e.~$\Sigma$ has finitely many non-compact asymptotic \textit{ends}\footnote{
		It might be helpful to visualize this as the spatial ``end'' of the world, \textit{世界尽头}。This poetic translation is due to X.~J.~Xie. 
	} $\Sigma_\ell \subset \Sigma$. Asymptotic flatness is then captured by the asymptotic behavior the metric: $g_{ij}\sim \delta_{ij}$.

	\begin{definition*}[Asymptotic Flatness]
		A Riemannian 3--fold $\Sigma\subset\mcal{M}$ as a hyperspace in spacetime is \textit{asymptotically flat} when it has the following decomposition:
		\begin{equation}
			\Sigma
			\cong \Sigma_0
			\cup \coprod_{\ell\ne 0} \Sigma_\ell
		\end{equation}%
\pagebreak[4]\\
		Where $\{\ell\}$: finite indices, and:
		\begin{itemize}[noitemsep,topsep=.3\baselineskip]
		\item $\Sigma_0$: compact;
		\item $\{\Sigma_\ell\}_\ell$: asymptotic ends, each diffeo to the complement of a contractible compact set in $\mbb{R}^3$; 
		\item Under such diffeo $\Sigma_\ell\to\mbb{R}^3$, the metric $g$ of every end $\Sigma_\ell\subset\mcal{M}$ is asymptotically flat, i.e.
		\begin{equation}
		\begin{gathered}
			g_{ij} = \delta_{ij} + h_{ij},\\[.5ex]
			h_{ij}
				\sim \order{\tfrac{1}{r}},\quad
			\pdd{k} h_{ij}
				\sim \order{\tfrac{1}{r^2}},\quad
			\pdd{l}\pdd{k} h_{ij}
				\sim \order{\tfrac{1}{r^3}}
		\end{gathered}
		\end{equation}
		\item The second fundamental form $K$ of $\Sigma_\ell\subset\mcal{M}$ is also constrained:
		\begin{equation}
			K_{ij}
				\sim \order{\tfrac{1}{r^2}},\quad
			\pdd{k} K_{ij}
				\sim \order{\tfrac{1}{r^3}}
		\end{equation}
		\end{itemize}
	\end{definition*}

	In general, it is quite difficult to define a total energy for some arbitrary spacetime $\mcal{M}$. However, when asymptotic flatness is imposed, it can be treated as a \textit{symmetry} of the ends $\Sigma_\ell$. Energy of the spacetime\footnote{
		This includes contributions from gravitational field and matter field.
	} can then be defined as the \textit{conserved charge} corresponding to the time translation Killing vector field $\xi = \pdd{t}$, or more explicitly, by integrating the \textit{Noether current} of such symmetry on $\Sigma_\ell$, as is done in \textit{Noether's theorem}. See \cite{Banados:2016zim} for a comprehensive review; for a covariant treatment, see \cite{crnkovic1987covariant,Harlow:2019yfa}.

	In fact, the Noether current can be further shown to be exact: $\dd{Q}_\xi$, then by Stokes' theorem, energy as a conserved charge can be further reduced to some integral along the ``asymptotic boundaries'' (plus some extra boundary terms, shown below in ``$\cdots$'') \cite{Iyer:1994ys,Harlow:2019yfa}:
	\begin{equation}
	\begin{gathered}
		E_\ell = P^0(\Sigma_\ell)
		= \int_{\Sigma_\ell} \dd{Q_\xi}
			+ \int_{S^2_\ell} (\cdots)
		= \int_{S^2_\ell} \pqty\big{
			Q_\xi + \cdots
		},\\[.5ex]
		S^2_\ell = \mquote{\,\partial\Sigma_\ell}
		\subset\Sigma_\ell
		\subset\mbb{R}^3,\quad
		\xi = \pdd{t}
	\end{gathered}
	\end{equation}
	Here $S^2_\ell$ is a sphere with radius $R\to\infty$\,\footnote{
		Discussions here are clearly not mathematically exact (hence the quotation marks), but can be made rigorous by taking a cutoff geometry $\mcal{M}'$ with (true) boundary $\partial\mcal{M}' = \coprod_{\ell\ne 0} S_\ell$, and then prove that the end result is in fact cutoff independent. 
	}. This is the so-called \textit{ADM energy} \cite{Arnowitt:1962hi}. In fact, we can take $\xi = \pdd{\mu},\mu=0,1,2,3$ and obtain the ADM 4--momentum \cite{Straumann:2013spu}:
	\begin{equation}
		P^\mu_\ell \equiv P^\mu(\Sigma_\ell)
		\simeq -\frac{1}{16\pi} \int_{S^2_\ell}
			\sqrt{\abs{g}}\,
			\omega_{\rho\sigma} \wedge
			\hodgedual \pqty\big{
				\dd{x^\rho}\wedge
				\dd{x^\sigma}\wedge
				\dd{x^\mu}
			},\\[.5ex]
		\omega_{\rho\sigma}
		= \Gamma_{\rho\mu\sigma} \dd{x^\mu}
		= g_{\rho\lambda}
			\Gamma\id{^{\lambda}_{\mu\sigma}}
			\dd{x^\mu}
	\end{equation}
	Where $\omega_{\rho\sigma}$ is the Levi-Civita connection form. This can be further expanded in induced metric (\nth{1} fundamental form) $g_{ij}$ and \nth{2} fundamental form $K_{ij}$ when $R\to\infty$, which gives the explicit expressions below.

	\begin{definition*}[ADM Energy--Momentum]
		Total ADM energy--momentum $P^\mu_\ell$ of an asymptotically flat end $\Sigma_\ell \subset \Sigma \subset \mcal{M}$ is defined in the following explicit form\footnote{
			Note that the $E_\ell$ given in \cite{Parker:1981uy} has a typo. Check \cite{Witten:1981mf,Wald:1984rg} for the correct expression. 
		}:
		\begin{equation}
		\begin{aligned}
			E_\ell \equiv P^0_\ell
			&= \lim\limits_{R \to \infty}
				\frac{1}{16\pi} \int_{S^2_\ell}
				\pqty{
					\pdd{j} g_{ij}
					- \pdd{i} g_{jj}
				} \dd{\Omega^i},\\[.5ex]
			P^k_\ell
			&= \lim\limits_{R \to \infty}
				\frac{1}{16\pi} \int_{S^2_\ell}
				2\,\pqty{
					K_{ik} - \delta_{ik} K_{jj}
				} \dd{\Omega^i},
		\end{aligned}
		\label{eq:adm_energy}
		\end{equation}
		Where $R$ is the radius of 2--sphere $S^2_\ell \subset \Sigma_\ell \cong \mbb{R}^3$, 
		\begin{itemize}[noitemsep,topsep=.3\baselineskip]
		\item $g_{ij}$ is the induced metric (\nth{1} fundamental form),
		\item $K_{ij}$ is the \nth{2} fundamental form on $\Sigma_\ell \cong \mbb{R}^3$, 
		\end{itemize}
		and repeated indices are summed over. 
		\vspace*{1ex}
	\end{definition*}
\subsection{Energy Conditions}
	On the other hand, there are physical constraints on the stress tensor $T_{\mu\nu}$, which describes \textit{local} energy--momentum density. Physical constraints on $T_{\mu\nu}$ are called \textit{energy conditions} (EC), see \textit{Wald} \cite{Wald:1984rg} or \cite{Curiel:2014zba} for some detailed discussions. Here we assume the \textit{dominant} EC (DEC), which requires that mass / energy can never be observed to be flowing faster than light.

	Specifically, a non-rotating observer moving along some path $x(\tau)\in\mcal{M}$ is characterized by a local velocity 4--vector $v^\mu = x'(\tau) = \mrm{T}_x \mcal{M}$. The observed energy--momentum flow $p^\mu$ and energy density $\rho$ w.r.t.~$v^\mu$ is obtained by the contraction\footnote{
		Minus signs in \eqref{eq:energy_flow_stress_tensor} is due to the $\eta_{ab}\sim\pqty{-1,+1,+1,+1}$ metric convention, in this case $v^a\sim\pqty{1,0,0,0}\mapsto v_a\sim\pqty{-1,0,0,0}$, therefore we need an extra sign flip to get the correct sign of energy. 
	}:
	\begin{equation}
		\begin{aligned}
			p^\mu &= - v_\nu T^{\mu\nu},\\[-.2ex]
			\rho &= - v_\nu p^\nu,
		\end{aligned}\quad%
		v^\nu\colon\ \text{timelike, i.e.}\ \ %
		v^\nu v_\nu
		= g_{\mu\nu} v^\mu v^\nu
		< 0
		\label{eq:energy_flow_stress_tensor}
	\end{equation}
	$p^\mu$ should be a \textit{timelike} or \textit{lightlike} (non-spacelike) 4--vector, i.e.~$p^\mu p_\mu \le 0,\,\forall\,v^\mu\colon\text{timelike}$. Also, matter density should always be non-negative\footnote{
		The condition $\rho\ge 0$ by itself is also a common energy condition, called the weak EC (WEC). 
	}, i.e.~$\rho \ge 0$. These two constraints can be equivalently captured by simple restrictions of $T_{\mu\nu}$ components \cite{Straumann:2013spu}, shown below. 
\pagebreak[3]

	\begin{definition*}[Dominant Energy Condition]
		The symmetric stress tensor $T_{\mu\nu}$ satisfies the dominant energy condition (DEC), iff.
		\begin{equation}
			T^{00} \ge \abs{T^{\mu\nu}},\quad
			T^{00} \ge \sqrt{-T_{0i} T^{0i}}
			\label{eq:DEC}
		\end{equation}
		Which is equivalent to $\rho \ge 0,\,p^\mu p_\mu \le 0$, where $\rho,p^\mu$ is defined in \eqref{eq:energy_flow_stress_tensor}. 
	\end{definition*}
\subsection{Statement of the Theorem}
	With the above preparation, we can now state the positive energy theorem in a mathematically precise manner.

	\begin{theorem*}[Positive Energy Theorem]
		For a spacelike hypersurface $\Sigma\subset\mcal{M}$ that:
		\begin{itemize}[noitemsep,topsep=.3\baselineskip]
		\item is asymptotically flat, $
			\Sigma \cong \Sigma_0
			\cup \coprod_{\ell\ne 0} \Sigma_\ell
		$, and
		\item the dominant energy condition holds; 
		\end{itemize}
		Then the total energy-momentum $P^\mu_\ell$ is a future directed timelike or lightlike (non-spacelike) vector on each end $\Sigma_\ell$, i.e.~
		\begin{equation}
			E_\ell - \abs{P_\ell}
			\equiv E_\ell
				- \sqrt{P_{\ell,i} P^i_\ell}
			\ge 0
		\end{equation}
		Furthermore, if $E_\ell = 0$ for some $\ell$ then ${\Sigma}$ has only one end and $\mcal{M}$ is flat along $\Sigma$, i.e.~$\mcal{M}$ is flat in a neighborhood of $\Sigma$, as is described in \eqref{eq:local_decomp}. 
	\end{theorem*}

	The proof of the positive energy theorem and its various generalizations has been the pursuit of many mathematicians and physicists, as is described in \cite{Witten:1981mf}. Witten's proof provides an attracting alternative to the first proof \cite{Schon:1979rg}, and is much more approachable for physicists.

	As is mentioned before, Witten's proof is based on the assumption that there is matter described by some \textit{spinor field} $\psi$ on the manifold $\mcal{M}$. This is not so surprising to physicists, as spinors are the mathematical descriptions of \textit{fermions} (incl.~electrons, protons, and basically all ``matter'' in the usual sense).

	The use of spinor is also suggested by considerations involving \textit{supersymmetry} (SUSY)\,\footnote{
		Basically, SUSY is a new spacetime symmetry that relates spinor with their vector partners, and tries to describe them in a single framework. This simple idea has generated numerous developments in both math and physics. 
	}, as is discussed by Witten \cite{Witten:1981mf}. In supersymmetric gravity (\textit{supergravity}, SUGRA), the energy is \textit{formally} written as the sum of squares of Hermitian supercharges $H = \frac{1}{\hbar}\sum_\alpha Q_\alpha^2$, which is \textit{formally} positive. Witten's proof is then found by designing a \textit{classical limit} of SUGRA.

	Besides physical considerations, spinors are also fascinating objects in geometry. In the following part of our review we will focus the physical and geometric properties of spinor and spin structure, and give a very brief sketch of Witten's proof at the end of this review. 
\section[Spinor from Quantization]{%
Spinor from Quantization\footnote{%
	This section is far too physical, therefore inappropriate in a report for differential manifold, and deserves to be dumped into an appendix. However, some necessary concepts are introduced in this section, so we will leave it here for now. 
}}
	This section serves as a non-technical introduction to spinor for a general audience. We follow \textit{Weinberg} \cite{Weinberg:1995mt} for this informal discussion about quantization.

	Particles have \textit{spin}. Classically, spin is described by a local 3-\textit{vector} $s^i \in \mrm{T}_x \Sigma$. This vector can be na\"ively promoted to a 4-\textit{vector} in its rest frame\footnote{
		In this review particles are always assumed to move slower than light, for simplicity. Therefore, it is possible to change the coordinates to follow a particle in its comoving rest frame. Most of our arguments here can be generalized to particles moving at the speed of light, but with considerable amount of subtleties.
	}:
	\begin{equation}
		s^i
		\quad\longrightarrow\quad
		s^\mu \sim (0, s^i),\quad
		\tup{rest frame}
	\end{equation}
	In quantum mechanics, particle ceases to be a localized entity; rather, it is described by a \textit{wave function} spread across the spacetime. Furthermore, in field theory, a particle is considered as an \textit{excitation} of some \textit{field}, just like a ripple in the pond. Therefore, instead of localized vectors, we should consider \textit{vector fields}, i.e.~sections of the tangent bundle:
	\begin{equation}
		s^\mu \in \mrm{T}_x\mcal{M}
		\quad\longrightarrow\quad
		\phi^\mu
		\in \Gamma(\mcal{M},\mrm{T}\mcal{M})
		\,\colon\ 
		\mcal{M}\to\mrm{T}\mcal{M}
		\label{eq:vector_bundle}
	\end{equation}

	Another feature of the wave function description is that there is always a \textit{Hilbert space} $\mcal{H}$ of wave functions corresponding to the actual spacetime manifold $\mcal{M}$. Quantum mechanical evolution of a system is in fact formulated in its Hilbert space, rather than its spacetime manifold. Symmetries of spacetime $\mcal{M}$ lead to symmetries on the Hilbert space; in fact, the Hilbert space $\mcal{H}$ can be seen as a \textit{representation} of the spacetime symmetries.

	For a flat spacetime, 4--momentum $p_\mu$ and (relativistic) angular momentum tensor $j_{\mu\nu}$ are symmetry generators, i.e.~Killing vector fields of the spacetime; with the standard orthonormal bases of $\mbb{R}^{3,1}$, we have:
	\begin{equation}
		p_\mu = \pdd{\mu},\quad
		j_{\mu\nu} = x_\mu \pdd{\nu} - x_\nu \pdd{\mu}
	\end{equation}
	Killing vector fields as derivations form a closed Lie algebra; for $\mbb{R}^{3,1}$ this is the so called \textit{Poincar\'e} algebra, here denoted as the Lie algebra $\mathfrak{iso}(3,1)$ of Lie group $\mrm{ISO}^+(3,1)$,  where ``\,$\mrm{I}$\," stands for inhomogeneous, i.e.~with translations, and ``\,$+$\," denotes its identity component. The finite transformation generated by $p_\mu, j_{\mu\nu}$ is exactly the Lorentz transformation. This shows that a (local) change of coordinates is interpreted in physics as switching between reference frames.

	Quantum mechanically, $p_\mu, j_{\mu\nu}$ is \textit{represented} (literally and mathematically) as linear operators $P_\mu, J_{\mu\nu}$ on Hilbert space $\mcal{H}$,
	\begin{equation}
		p_\mu\ \longrightarrow\ P_\mu,\quad
		j_{\mu\nu}\ \longrightarrow\ J_{\mu\nu}
	\end{equation}
	Intuitively, particles are characterized with its energy\footnote{
		Conventionally, $H = P^0$ serves as the energy operator, i.e.~\textit{Hamiltonian}, while $E$ denotes its eigenvalue. 
	} $H = P^0$, momentum $\vb{P}^i = P^i$ and their relations: $H = H(\vb{P})$. Conveniently, $P_\mu$'s commute with each other; therefore in field theory, particles are \textit{defined} by simultaneous eigenstates of $P_\mu$'s.

	For a given Lie algebra and its representation, we can construct \textit{Casimir invariants} which commute with all generators, therefore are invariant (or \textit{conserved}) under symmetry transformation. Naturally, we expect them to describe \textit{intrinsic properties} of a particle, which is not affected by a change of coordinates.

	For Poincar\'e algebra in $(3+1)$ dimensions, there are exactly two linearly independent Casimirs\footnote{
		For Poincar\'e algebra in higher dimensions, i.e.~$\mathfrak{iso}(d,1)$ with $d\ge 4$, there are more Casimirs, see e.g.~\cite{Bekaert:2006py}. Unfortunately, we (i.e.~authors of this review) haven't found any reference about the physical interpretation of these higher order Casimirs. 
	}:
	\begin{equation}
		M^2 = -P_\mu P^\mu,\quad
		W^2 = W_\mu W^\mu,\quad
		W_\lambda = -\frac{1}{2}\,
			\epsilon_{\lambda\mu\nu\rho}
			J^{\mu\nu} P^\rho
	\end{equation}
	Here $\epsilon_{\lambda\mu\nu\rho}$ is the totally anti-symmetric Levi-Civita symbol, and the minus signs are merely conventional. $W_\lambda$ is the \textit{Pauli–Lubanski pseudovector}.

	Physical states are required\footnote{
		By one of the fundamental postulates of relativity, there is no faster-than-light travel, which implies $m^2 = -p_\mu p^\mu \ge 0$. This is represented in the Hilbert space as $M^2 = -P_\mu P^\mu \ge 0$. 
	} to have $M^2 > 0$, and states of the same eigenvalue $M = m \ge 0$ form a sub-representation (\textit{submodule}) of $\mrm{ISO}^+(3,1)$ acting on $\mcal{H}$. Different species of particles are therefore distinguished by different values of $M = m$. Physically, $m$ is naturally interpreted as the \textit{mass} of a particle. Similarly, $W^2$ should characterize another intrinsic property of a particle; let's further define sub-species of particle labeled by different eigenvalues of $W^2$. Assume $m > 0$ for simplicity, then in the rest frame of some particle with constant eigenvalue $W^2$, we have $P^\mu = p^\mu \sim (p^0,0) = (m,0)$,
	\begin{gather}
		W_\lambda = - \frac{1}{2}\,
			\epsilon_{\lambda\mu\nu\rho}
			J^{\mu\nu} P^\rho
		= - \frac{1}{2}\,
			\epsilon_{\lambda\mu\nu 0}
			J^{\mu\nu} m
		\sim (0,W_k),\ \,\textsl{rest frame},\\
		W_k	= \frac{1}{2}\,m\,\epsilon_{ijk} J^{ij}
		= mJ_k = ms_k
	\end{gather}
	Where $J_k = \frac{1}{2}\,\epsilon_{ijk} J^{ij}$ is the \textit{angular momentum} operator, which is the Hilbert space representation of rotation generator: $
		j_{ij} = x_i\pdd{j} - x_j\pdd{i}
		= \pdv{\theta^k}
	$, here $\theta^k$ parameterizes rotation angle around the $k$--th axis. Physically, \textit{spin} is exactly the intrinsic angular momentum of a particle: $J_k = s_k$, therefore the spin 4--vector shall be rigorously defined as the eigenvalue of Pauli–Lubanski pseudovector.

	To sum up, assuming that there is no extra symmetry beyond Poincar\'e $\mathfrak{iso}(3,1)$, particles can be completely reduced and classified by representations of $\mathfrak{iso}(3,1)$ on $\mcal{H}$. We have:
	\begin{equation}
		P^\mu{} \ket{p^\mu,s^\mu}
		= p^\mu \ket{p^\mu,s^\mu},\quad
		J^\mu \ket{p^\mu,s^\mu}
		\approx s^\mu \ket{p^\mu,s^\mu},\quad
		J^\mu = \frac{W^\mu}{m}
		\label{eq:momentum_eigenstates}
	\end{equation}
	Here $\ket{p^\mu,s^\mu}\in\mcal{H}$ denotes a particle state in the Hilbert space.

	However, the above notation is \textit{not} quite exact (as is indicated by the ``\,$\approx$\," sign). Note that $W_\mu$'s do \textit{not} commute, hence it is impossible to find simultaneous eigenstates for all four $W_\mu$'s. The best we can manage is to pick a special $W_\mu$, say $\mu = z$ in the rest frame, and then index the eigenstates with eigenvalues of $J_z = \frac{W_z}{m}$. \eqref{eq:momentum_eigenstates} is then modified to be:
	\begin{equation}
		P^\mu{} \ket{p^\mu,s_z}
		= p^\mu \ket{p^\mu,s_z},\quad
		J_z \ket{p^\mu,s_z}
		= s_z \ket{p^\mu,s_z}
	\end{equation}

	The action of $W^\mu$ on a resting particle is the representation of stabilizer subgroup\footnote{
		In physics literature this is the so-called Wigner's \textit{little group}.
	} $\mrm{SO}(3)\subset\mrm{ISO}^+(3,1)$, which keeps $p^\mu \sim (m,0)$ fixed. Since $\mrm{SO}(3)$ is a compact Lie group, according to Peter--Weyl theorem, its irreducible representations (\textit{irrep}s) are finite dimensional. It is natural to define \textit{elementary} particles as irreps, since they cannot be decomposed further (physically or mathematically); hence $s^\mu$ for an elementary particle can only take on discrete values.

	Therefore, the rigorous label of a particle state should be:
	\begin{equation}
	\begin{gathered}
		\mcal{H}\supset\mcal{H}_{m,j}
			\ni\ket{m,p^\mu;j,s_z}
		\equiv\ket{p^\mu,s_z},\\
		p_\mu p^\mu = -m^2,\quad
		s_z = -j, -j+1,\cdots, +j,\quad
		j \in\mbb{Z}_+
	\end{gathered}
	\label{eq:particle_repr}
	\end{equation}
	Here $m,j$ labels the representation $\mcal{H}_{m,j}$, which stays invariant under Poincar\'e transformations, while $p,s_z$ labels the state in such irrep. The allowed values of $s_z$ come from the representation of $\mrm{SO}(3)$.

	Now we are finally prepared to embrace another quirk from quantum mechanics --- \textit{projective representation}, which leads directly to the existence of spinors. 
\subsection{Projective Representation and Spinor}
	As mentioned before, in quantum mechanics the state and dynamics of a system is described with a $\mbb{C}$--valued \textit{wave function} $\Psi(\xi)$, or equivalently an abstract \textit{state} $\ket{\Psi}$ in Hilbert space $\mcal{H}$. The variable $\xi$ labels simultaneous eigenstate $\ket{\xi}$ of some Hermitian \textit{observables}, e.g.~momentum $P^\mu$ and spin-$z$ component $W^z$. The set of all such eigenstates $\{\ket{\xi}\}$ forms an orthonormal\footnote{
		Although mathematically imprecise, it is common in physics to treat \textit{distributions} such as Fourier basis $\{e^{ikx}\}_{k\in\mbb{R}}$ as ``orthonormal", with the modified orthonormal relations $\frac{1}{2\pi} \int\dd{x} e^{-ik'x}e^{ikx} = \delta(k-k')$, where $\delta$ is the Dirac delta distribution. This can be made mathematically rigorous in functional analysis, hence there is no need to worry. 
	} basis of $\mcal{H}$.

	Wave function $\Psi(\xi)$ can be regarded as the projection of state $\Psi$ onto the orthonormal basis $\ket{\xi}$, i.e.~$\Psi(\xi) = \braket{\xi}{\Psi}$, where $\braket{\cdot}{\cdot}$ is the Hermitian inner product. Here we adopt the physics convention that $\braket{\cdot}{\cdot}$ is $\mbb{C}$ linear in its \textit{second} entry, while conjugate-linear in its first entry. 
\pagebreak[4]

	Projective representation arises from Born's \textit{statistical interpretation} of the wave function, which relates the probability of observed outcome with its wave function, namely,
	\begin{equation}
		\abs{\braket{\xi}{\Psi}}^2
		\ \sim\ \pqty\Big{\tup{
			Probability of observing state $\ket{\Psi}$ in eigenstate $\ket{\xi}$
		}}
	\end{equation}
	This means that states differ by an overall phase $e^{i\alpha}$ represents the same physical state, i.e.~$e^{i\alpha}\ket{\Psi} \sim \ket{\Psi}$. Mathematically speaking, the physical Hilbert space is actually the projective space $\mrm{P}\mcal{H}$.

	The projective nature of physical Hilbert space has two direct consequences. First, representations of symmetries in Hilbert space should be \textit{unitary} to preserve probability $\abs{\braket{\cdot}{\cdot}}^2$, i.e.,
	\begin{equation}
		\mscr{U}\colon G\to\mrm{U}(\mcal{H})
		\subset\mrm{GL}(\mcal{H})
	\end{equation}
	Here $\mscr{U}$ and $U(\cdot)$ stands for unitary representation and unitary group, respectively. Second, since we do not require invariance of $\braket{\cdot}{\cdot}$ but only its norm $\abs{\braket{\cdot}{\cdot}}$, $\mscr{U}$ need not be an ``exact" representation, but can differ by a phase; this is a so-called \textit{projective representation}:
	\begin{equation}
		\mscr{U}(\Lambda')\,\mscr{U}(\Lambda)
		= e^{i\alpha}\,\mscr{U}(\Lambda'\Lambda),\quad
		\Lambda\in G
	\end{equation}

	At first, it seems that the extra phase adds great complexity to possible representations. Fortunately, projective representations have been well understood in mathematics (even before its quantum mechanical origin, e.g.~by Schur \cite{schur1911darstellung} in 1911 for finite groups). In fact, a projective representation can always be \textit{lifted} to an ordinary representation, see e.g.~\cite{Weinberg:1995mt,Schottenloher:2008zz}. Generally, we have:

	\begin{theorem*}[Lifting Projective Representations]
		A unitary representation of group $G$ on projective Hilbert space $\mscr{U}\colon G\to\mrm{U}(\mrm{P}\mcal{H})$ can always be lifted to a unitary representation of its \textit{central extension} $\tilde{G}$ on linear Hilbert space $\tilde{\mscr{U}}\colon \tilde{G}\to\mrm{U}(\mcal{H})$, i.e.~the following diagram commutes:
		\begin{center}
		\begin{tikzcd}[row sep=2.5em,column sep=2em]
		\tilde{G}
			\arrow{r}{\pi}
			\arrow[swap]{d}{\tilde{\mscr{U}}} & 
		G
			\arrow{d}{\mscr{U}} \\
		\mrm{U}(\mcal{H})
			\arrow{r}{} &
		\mrm{U}(\mrm{P}\mcal{H})
		\end{tikzcd}
		\end{center}
		Moreover, central extension $\tilde{G}$ of Lie group $G$ can be constructed as follows:
		\begin{enumerate}[topsep=.5\baselineskip]
		\item Extension by discrete $\mbb{Z}_n$, in this case $\tilde{G}$ is the covering group of $G$; the maximal extension of this kind is naturally the \textit{universal covering} of $G$, with $\mbb{Z}_n = \pi_1(G)$ its fundamental group. This kind of extension is \textit{topological} and does not change the corresponding Lie algebra, i.e.~$\mathfrak{g} = \mop{Lie}G = \mop{Lie}\tilde{G}$. 
		\item Extension by continuous $\mrm{U}(1)$, which descends into a non-trivial central extension of its Lie algebra:
		\begin{equation}
			\dd{\pi}\colon\ %
			\tilde{\mathfrak{g}} = \mop{Lie}\tilde{G}
			\ \longrightarrow\ %
			\mathfrak{g} = \mop{Lie}G
		\end{equation}
		$\tilde{\mathfrak{g}},\tilde{G}$ therefore has an extra dimension generated by such $\mrm{U}(1)$ subgroup. 
		\end{enumerate}
	\end{theorem*}

	For Poincar\'e symmetry, there is no need to consider central extension of the Lie algebra $\mathfrak{iso}(3,1)$; in fact, representation of such Lie algebra central extension is always equivalent of some representation of the original $\mathfrak{iso}(3,1)$, by a redefinition of basis\footnote{
		See \cite{Weinberg:1995mt,Schottenloher:2008zz}. A general criterion is given by Bargmann's Theorem \cite{Bargmann:1954gh}; it states that \textit{every projective representation of a connected, simply connected, finite-dimensional Lie group $\tilde{G}$ with Lie algebra second cohomology $H^2(\mop{Lie}\tilde{G},\mbb{R}) = 0$ can be simply lifted as a unitary representation}, i.e.~such $\tilde{G}$ is the ``maximal" extension. 
	}. However, $\mrm{ISO}^+(3,1)$ has non-trivial $\pi_1$ due to its rotation subgroup $\mrm{SO}(3)$; topologically,
	\begin{equation}
	\begin{gathered}
		\mrm{ISO}^+(3,1)
		\cong \mbb{R}^4\rtimes\mrm{SO}^+(3,1)
		\approxeq
			\mbb{R}^4\times\mbb{R}^3\times\mrm{SO}(3)
		\approxeq
			\mbb{R}^4\times\mbb{R}^3\times \pqty{S^3/\mbb{Z}_2},\\[.5ex]
		\cong\colon\text{isomorphic as groups},\quad
		\approxeq\colon\text{diffeo as manifolds}
	\end{gathered}
	\end{equation}
	Where $\mbb{R}^4$, $\mbb{R}^3$ and $\mrm{SO}(3)$ corresponds to translations $P^\mu$, Lorentz boosts $J^{0i} = -J^{i0}$ and spatial rotations $J_k = \frac{1}{2}\,\epsilon_{ijk} J^{ij}$. Therefore, $\mrm{ISO}^+(3,1)$ can be centrally extended by $\mbb{Z}_2 = \pi_1\pqty\big{\mrm{ISO}^+(3)}$.

	Generally, We define \textit{spin group} $\mrm{Spin}(p,q)$ as the $\mbb{Z}_2$ extension (double cover) of $\mrm{SO}(p,q)$\footnote{
		More concretely, it can be explicitly constructed via Clifford algebra $\cliff(p,q)$. 
	}. Note that $\mrm{Spin}(p,q)$ is \textit{not} always connected, and its identity component $\mrm{Spin}^+(p,q)$ is \textit{not} always simply connected\footnote{
		For example, $\pi_1\pqty\big{\mrm{Spin}(2,1)} = \mbb{Z}$ infinite cyclic, this gives rise to fractional spin $s\in\mbb{Q}_+$ (\textit{anyons}) in $(2+1)$ dimensions \cite{Wilczek:1982wy}. If we consider central extension of Lie algebra, then particle spin can even take arbitrary $s\in\mbb{R}_+$ values. 
	}. However, for $p>2>q\ge 0$, $\mrm{Spin}^+(p,q)$ is indeed simply connected, therefore it's the universal cover of $\mrm{SO}^+(p,q)$. For $(3+1)$ dimensional spacetime $\mbb{R}^{3,1}$, we have the following diagram:
	\begin{center}
	\begin{tikzcd}[row sep=2.5em,column sep=3em]
	\mrm{Spin}(3,1)
		\arrow[r]
		\arrow[d,"\tilde{\pi}"',"/\mbb{Z}_2"] & 
	\mrm{Spin}^+(3,1)\cong\mrm{SL}(2,\mbb{C})
		\arrow{r}{}
		\arrow[d,"/\mbb{Z}_2"] &[-1em] 
	\mrm{Spin}(3)\cong\mrm{SU}(2)
		\arrow[d,"\pi"',"/\mbb{Z}_2"] \\
	\mrm{SO}(3,1)
		\arrow{r}{} &
	\mrm{SO}^+(3,1)
		\arrow{r}{} &
	\mrm{SO}(3)
	\end{tikzcd}
	\end{center}
	All arrows in this diagram are homomorphic projections: the vertical downwards arrows are $\mbb{Z}_2$ covering maps, while the horizontal right arrows are projections onto subgroups. 
\pagebreak[4]

	For $(3+1)$ dimensions, we have accidental isomorphisms: 
	\begin{gather}
		\mrm{Spin}^+(3,1)
			\cong\mrm{SL}(2,\mbb{C})
			\approxeq
				\mbb{R}^3\times S^3 \\
		\mrm{Spin}(3)
			\cong\mrm{SU}(2)
			\approxeq S^3
	\end{gather}
	Where $\mrm{SL}(2,\mbb{C}),\,\mrm{SU}(2)$ are classical $\mbb{R}$--Lie groups.

	Back to physics, an elementary particle in $(3+1)$ dimensional spacetime is therefore a unitary irrep of $\mrm{Spin}^+(3,1)$, which is, furthermore\footnote{
		For more discussion about the irreducibility of such induced representation, see \cite{tung1985group}. 
	}, an induced representation from the irrep of $\mrm{Spin}(3)\cong\mrm{SU}(2)$. 
\subsection{Vector and Spinor Representations}
\label{subsect:repr}
	As is evidenced before, we shall only consider irreps of $\mrm{Spin}(3)\cong\mrm{SU}(2)$; general representations of spin group is then closely related (induced by or composed of) $\mrm{SU}(2)$ irreps. Here we list some key facts about irreps of $\mrm{Spin}(3)\cong\mrm{SU}(2)$. 
	\begin{itemize}
	\item Recall $\mrm{SO}(3)$ irreps mentioned in \eqref{eq:particle_repr}; they are basically spin-$z$ eigenstates: 
	\begin{equation}
		\ket{s_z},\quad
		s_z = -j, -j+1,\cdots, +j,\quad
		j\in\mbb{Z}_{\ge 0}
	\end{equation}
	Here $p^\mu$ label is suppressed for sake of simplicity. All $\mrm{SO}(3)$ irreps can always be lifted as a $\mrm{Spin}(3)\cong\mrm{SU}(2)$ irrep, by allowing its $\mbb{Z}_2$ center to act trivially. In this way, we obtain the \textit{tensor representations} of $\mrm{SU}(2)$.
	\item Since $\mrm{SU}(2)$ is simply connected, to obtain \textit{all} of its $\mbb{R}$-irreps, we need only consider irreps of Lie algebra $\mfrak{spin}(3)\cong\mfrak{su}(2)$. It turns out they are structurally identical to $\mrm{SO}(3)$ irreps (naturally, since $\mfrak{so}(3)\cong\mfrak{su}(2)$ are identical Lie algebras), but with allowed $j$ values extended to include half integers: $j\in\mbb{Z}/2$. Irreps of $\mrm{SU}(2)$ that are \textit{not} irreps of $\mrm{SO}(3)$ are called \textit{spinor representations}. 
	\item Therefore, all of $\mrm{Spin}(3)\cong\mrm{SU}(2)$ irreps, and equivalently $\mfrak{so}(3)\cong\mfrak{su}(2)$ irreps, are of the following form:
	\begin{gather}
		\ket{s_z},\quad
		s_z = -j, -j+1,\cdots, +j,\\[1ex]
		j \in \Bqty{
			0,\tfrac{1}{2},1,\tfrac{3}{2},2,\cdots
		} = \bigg\lbrace
		\begin{aligned}
			\ %
			&\mbb{Z}_{\ge 0},
				&&\textsl{tensor repr.}\\
			&\mbb{Z}_{\ge 0} + \tfrac{1}{2},
				&&\textsl{spinor repr.}
		\end{aligned}
	\end{gather}
	The set of all tensor irreps of $\mrm{SU}(2)$ descends to the full irreps of $\mrm{SO}(3)$, while spinor irreps are only irreps of $\mrm{SU}(2)$, not irreps of $\mrm{SO}(3)$. However, they are indeed projective representations of $\mrm{SO}(3)$. 
\pagebreak[4]

	\item Note that the dimension of irrep is given by:
	\begin{equation}
		\dim_\mbb{C}%
		\mop{span}_\mbb{C}%
			\{\ket{s_z}\} = 2j+1
	\end{equation}
	\textit{Weyl spinor} is then defined to be the fundamental representation $V$ with $j = \frac{1}{2}$, which is simply the defining module $\mrm{SU}(2)$:
	\begin{equation}
		V = \mop{span}_\mbb{C} \Bqty{
			\ket{s_z = +\tfrac{1}{2}},
			\ket{s_z = -\tfrac{1}{2}}
		} \equiv \mop{span}_\mbb{C} \Bqty{
			\ket{\uparrow}_z,\ket{\downarrow}_z
		}
	\end{equation}
	\item Rotation generators $J_k = \frac{1}{2}\,\epsilon_{ijk} J^{ij}$ is represented on $V$ by Pauli matrices:
	\begin{equation}
		\newcommand{\mat}[1]{\pqty\Big{
			\footnotesize
			\hspace{-.2em}
				\begin{array}{cc}
					#1
				\end{array}
			\hspace{-.2em}
		}}
		J_k = \frac{1}{2}\,\sigma_k,\quad
		\sigma_x = \mat{
			0 & 1 \\
			1 & 0
		},\quad
		\sigma_y = \mat{
			0 & -i \\
			i & 0
		},\quad
		\sigma_z = \mat{
			1 & 0 \\
			0 & -1
		}
		\label{eq:pauli_mat}
	\end{equation}
	Notice how $2\pi$ rotation is not $+\idty$ but $-\idty$, which again confirms that $V$ is an irrep for $\mrm{SU}(2)$, but only a projective representation for $\mrm{SO}(3)$:
	\begin{equation}
		e^{-i J_{z} \theta}
		= e^{-i\sigma_{z}
			\frac{\theta}{2}}
		\xlongequal{\theta = 2\pi}
		-\idty
	\end{equation}
	In physics we would like $J_k$ to be Hermitian or self-adjoint, hence the $-i$ coefficient in the exponential map $e^{-i J_{z} \theta}$. This is one key feature of spinor: $2\pi$ rotation action is not identity $\idty$, but will produce a minus sign on the spinor! In some sense we can think of spinor as the $\mbb{C}\text{omplex}$ ``square root'' of a vector \cite{AlvarezGaume:1986es}.

	\item In general, transformation of operators (e.g.~Pauli--Lubanski $W_\mu$) in Hilbert space is related to its transformation as a tensor in spacetime. If we neglect projective representation for now, we have:
	\begin{equation}
		\mscr{U}^\dagger\,
			W_\mu
		\mscr{U}
		= \Lambda\id{^\nu_\mu} W_\nu,\quad
		\mscr{U}\colon
			\Lambda\in\mrm{SO}(3,1)
			\to
			\mrm{U}(\mcal{H}),\quad
		(\textsl{without projective repr.})
	\end{equation}
	This is a direct consequence of $\mscr{U}$ being a unitary representation, i.e.~preserving group multiplication and having $\mscr{U}^\dagger = \mscr{U}^{-1}$.

	\item However, due to the projective nature of the Hilbert space, $\mscr{U}(\Lambda)$ in the LHS should be lifted to $\tilde{\mscr{U}}(\tilde{\Lambda})$, while the $\Lambda$ in the RHS remains unchanged, i.e.,
	\begin{equation}
		\tilde{\mscr{U}}^\dagger\,
			W_\mu
		\tilde{\mscr{U}}
		= \Lambda\id{^\nu_\mu} W_\nu,\quad
		\tilde{\mscr{U}}
		= \tilde{\mscr{U}}(\tilde{\Lambda}),\quad
		\tilde{\Lambda}\in\mrm{SL}(2,\mbb{C})
		\label{eq:proj_repr_pauli_lubanski}
	\end{equation}

	\item The natural lift from $\Lambda$ to $\tilde{\Lambda}$ while preserving Lie group structure is by considering homotopic paths from $\idty$ to $\Lambda$. As is discussed before, we need only consider the doubly connected rotation subgroup $\mrm{SO}(3)\subset\mrm{SO}(3,1)$. Consider axis--angle parametrization of $\mrm{SO}(3)$, we have:
	\begin{equation}
		\Lambda
		= e^{iJ_k\theta^k}
		\longmapsto
		(\theta^k)
		= (\theta^x,\theta^y,\theta^z),\quad
		\theta^k\in [0,2\pi)
	\end{equation}
	Here $iJ_k\in\mfrak{so}(3)$ belongs to the defining module, then parametrization of $\mrm{SU}(2)$ can be easily achieved by extending the range of $\theta^k$, i.e., we have $\tilde{J}_k\in\mfrak{su}(2)$ defining module and:
	\begin{equation}
		\tilde{\Lambda}
		= e^{i\tilde{J}_k\theta^k}
		\longmapsto
		(\theta^k)
		= (\theta^x,\theta^y,\theta^z),\quad
		\theta^k\in [0,4\pi)
	\end{equation}

	\item $\tilde{\Lambda}$ is related to unit quartenions $
		S^3 \subset \mbb{H}
		= \mop{span}_\mbb{R} \Bqty{
			\mathbf{1},
			\mathbf{i},
			\mathbf{j},
			\mathbf{k}
		}
	$ by the following identity, which is a direct analog of Euler's identity $
		e^{i\theta}
		= \cos\theta + i\sin\theta
	$:
	\begin{equation}
	\begin{gathered}
		\tilde{\Lambda}
		= e^{i\tilde{J}_k\theta^k}
		\sim
			\cos\frac{\abs{\theta}}{2}
			+ \hat{\theta}
			\sin\frac{\abs{\theta}}{2},\\[1ex]
		\abs{\theta} = \sqrt{\theta_k\theta^k}
		= \sqrt{
			\theta_x^2 + \theta_y^2 + \theta_z^2
		},\qquad
		\hat{\theta}
		= \pqty\big{\mathbf{i}\,\theta_x
			+ \mathbf{j}\,\theta_y
			+ \mathbf{k}\,\theta_z
		} \big/ \abs{\theta}
	\end{gathered}
	\end{equation}
	$\theta$ is the rotation angle, while $\hat{\theta}$ describes the rotation axis, hence axis--angle parametrization. Replace $\tilde{\Lambda}$ in \eqref{eq:proj_repr_pauli_lubanski} with $(\theta^k)$, and we have:
	\begin{equation}
		\tilde{\mscr{U}}^\dagger\,
			W_\mu
		\tilde{\mscr{U}}
		= \Lambda\id{^\nu_\mu} W_\nu,\quad
		\tilde{\mscr{U}}
		= \tilde{\mscr{U}}(\theta),\quad
		\theta = (\theta^k),\quad
		\theta_k\in[0,4\pi)
	\end{equation}
	\end{itemize}
\section{Spin Structure and Spinor Field}
	From our previous discussions, we have established that in quantum mechanics, an elementary particle $\ket{p^\mu,s_z}\in\mcal{H}$ is something that lives in a unitary irrep of extended Poincar\'e group $\mbb{R}^4\rtimes\mrm{Spin}^+(3,1)$. By definition, particles become eigenstates in the Hilbert space $\mcal{H}$ of wave functions, which is often de-localized in spacetime.

	On the other hand, in field theory, a particle should be an excitation of some local field $\phi(x)$, like a ripple in the pond. Is it possible to relate these two pictures?

	The answer is yes, and the idea behind this relation is in fact quite basic. Roughly speaking, $\ket{p^\mu,s_z}$ serves as \textit{Fourier modes} of field $\phi(x)$. Details of this correspondence in quantum field theory are give in \textit{Weinberg}'s chapter: \textit{Quantum Fields and Antiparticles} \cite{Weinberg:1995mt}, but similar holds for ordinary quantum mechanics. The end result is that similar to an elementary particle $\ket{p^\mu,s_z}$, elementary fields $\phi(x)$ also becomes a representation of the Poincar\'e symmetry, where not only the symmetry acts on coordinates $x$ in the regular way:
	\begin{equation}
		\phi(x)
		\quad\longmapsto\quad
		\phi(x-\var{x})
	\end{equation}
	but also the Lorentz symmetry $\mrm{Spin}^+(3,1) \cong \mrm{SL}(2,\mbb{C})$ gets represented pointwise on the \textit{fiber} $\phi(x_0)$. This naturally leads us to consider \textit{fiber bundles} based on $\mcal{M}$. 
\subsection{Introduction to Principal Bundle}
	To introduce spin structure in a natural way, we follow the discussions of \cite{figueroa2010spin,Nakahara:2003nw,AlvarezGaume:1986es,Wernli:2019hpf}. For a mathematically rigorous understanding of spin geometry, see \cite{lawson2016spin,bourguignon2015spinorial,jost2011riemannian}. Our notation will mostly conform to \textit{Lee} \cite{lee2012introduction}. We shall use the language of fiber bundles, introduced in \cite{Nakahara:2003nw,lee2012introduction}. 
\pagebreak[4]

	To simplify the situation, we will again work on hypersurface $\Sigma\subset\mcal{M}$. It is illuminating to first consider the classical situation, then we have a natural poinwise fundamental representation of $\mrm{SO}(3)$ --- the tangent space $T_x\Sigma$. Union of tangent spaces at each point gives the tangent bundle:
	\begin{equation}
		T\Sigma = \coprod_{p\in\Sigma} T_p\Sigma
	\end{equation}
	$\mrm{SO}(3)$ action is reflected in the transformation $T_p\Sigma$ under isometric coordinate transformations, or equivalently, isometric \textit{transition function} between charts $\Bqty{(U_\alpha,\Phi_\alpha)}_\alpha$:
	\begin{equation}
		\Phi_\alpha\circ\Phi_\beta^{\smash{-1}}
			\big|_p
		= \tau_{\alpha\beta} (p),\quad
		\tau_{\alpha\beta} \in \mrm{SO}(3)
			\subset \mrm{GL}(3,\mbb{R})
	\end{equation}
	Where $\Phi_\alpha$ is the local trivialization on $U_\alpha$. In other words, $\mrm{SO}(3)$ is hence the \textit{structure group} of tangent bundle, when the transitions between charts is restricted to isometries defined by the metric.

	However, there is one subtlety that needs to be addressed: the refinement of $\mrm{GL}(3,\mbb{R})$ transition to $\mrm{SO}(3)$ is locally feasible, but might fail if we consider \textit{global} transition around a manifold that is not orientable. To see this, we first observe that transition functions should always satisfy such \textit{cocycle condition} (\textit{Lee} \cite{lee2012introduction}, Problem 10-5):
	\begin{equation}
		\tau_{UV}\circ\tau_{VW}\circ\tau_{WU} = \idty
	\end{equation}
	For a Möbius strip however, this is impossible if we restrict $\tau\in\mrm{SO}(3)$. It is not hard to see that $
		\tau_{UV}\circ\tau_{VW}\circ\tau_{WU} = -\idty
	$, if we only allow $\tau\in\mrm{SO}(3)$. In fact, given a metric, we can only guarantee the refinement of $\mrm{GL}(3,\mbb{R})\supset\mrm{O}(3)$.

	From now on we shall assume that our manifold $\Sigma\in\mcal{M}$ is orientable, therefore the tangent bundle becomes a natural realization of the local $\mrm{SO}(3)$ isometry w.r.t.~the metric. In fact, any representation of $\mrm{SO}(3)$ can be expressed as tensor products and direct sums of the fundamental representations, therefore the \textit{tensor fields} realize all possible $\mrm{SO}(3)$ representations:
	\begin{equation}
		\phi\id{
			^{\mu_1\mu_2\cdots\mu_k}
			_{\nu_1\nu_2\cdots\nu_l}
		}
		\in \Gamma(\Sigma,T^{(k,l)}\Sigma)
		\,\colon\ 
		\Sigma\to T^{(k,l)}\Sigma
	\end{equation}
	If we require only local $\mrm{SO}(3)$ symmetry, then the job is done; everything is naturally provided by the tensor bundle. However, after quantization the symmetry must be extended to $\mrm{Spin}(3)$, therefore our job is to somehow \textit{lift} the tensor bundle to a \textit{spinor bundle}, in a natural manner that is compatible to the $\mbb{Z}_2$ covering:
	\begin{equation}
		\pi\colon
		\mrm{Spin}(3)\cong\mrm{SU}(2)
		\to
		\mrm{SO}(3)
	\end{equation}

	In order to obtain a compatible spinor bundle, it is helpful to re-examine the common structure of all tensor bundles --- the $\mrm{SO}(3)$ transition between charts. In general, it is possible to remove all unnecessary data of a fiber bundle, leaving only the information of how it transitions between charts. This gives the so-called \textit{principal bundle}.

	\begin{definition*}[Principal $G$--Bundle]
		A principal $G$--bundle $P_G\to\Sigma$ is a fiber bundle whose model fiber is a manifold diffeo to the structure group $G$. 
	\end{definition*}

	For tensor bundles transforming under $\mrm{SO}(3)$ isometry, they correspond to the same principal $\mrm{SO}(3)$ bundle $P_{\mrm{SO}(3)}$. In fact, it can be explicitly constructed by considering the orthonormal frames fields on the tangent bundle, i.e.~the \textit{frame bundle}.

	Since its fiber is diffeo to the structure group itself, principal bundle has a natural \textit{left and right} group action, defined by the usual group multiplication on $G$. This two-sided group action corresponds to the action on the contra-variant and covariant component of a tensor.

	In the physics community, we often say that \textit{a tensor is something that transform like a tensor}. Now we can see that this saying is not without its merits, since indeed the essence of a tensor is its transformation property, captured by the principal bundle.

	Even better, given a principal $G$--bundle and a $G$--module $F$ as the model fiber, it is possible to reconstruct the \textit{associated fiber bundle} up to equivalence. This is precisely the \textsc{vector bundle construction theorem} given in \textit{Lee} \cite{lee2012introduction}, Problem 10-6, and we will not restate it here. We need only these two conditions:
	\begin{itemize}[noitemsep]
	\item Transition function is a $G$ representation on $F$: 
	\begin{equation}
		\tau_{UV}(p)
%		= \rho\circ \Lambda_{UV}(p),\quad
%		\rho\colon G\to\mop{End}(F),\quad
%		\Lambda\in G
		\in G \subset \mop{End} F
	\end{equation}
	\item Cocycle condition:
	\begin{equation}
		\tau_{UV}\circ\tau_{VW}\circ\tau_{WU} = \idty
	\end{equation}
	\end{itemize}
	With the idea of principal bundle and construction theorem of associated bundle, our task of defining a spinor field can now be decomposed into the following two steps:
	\begin{itemize}[leftmargin=*]
	\item Find a natural and compatible lift of $P_{\mrm{SO}(3)}$ to some principal $\mrm{Spin(3)}$--bundle $P_{\mrm{Spin}(3)}$; this is called the \textit{spin structure} on $\Sigma$;
	\item Construct a spinor bundle associated with $P_{\mrm{Spin}(3)}$, then its section is precisely the spinor field we want to obtain. 
	\end{itemize}
\subsection{Spin Structure}
	What kind of lift of $P_{\mrm{SO}(3)}$ to $P_{\mrm{Spin}(3)}$ is considered natural? This is characterized by the definition of spin structure. We follow closely the discussions in \cite{figueroa2010spin,Nakahara:2003nw}. 
\pagebreak[4]

	\begin{definition*}[Spin Structure]
		A spin structure is a principal $\mrm{Spin}(p,q)$--bundle $P_{\mrm{Spin}}$ together with a bundle morphism:
		\begin{center}
		\begin{tikzcd}[row sep=5ex,column sep=1.0em]
			P_{\mrm{Spin}}
				\arrow[dr]
				\arrow[rr,"\displaystyle\tilde{\pi}"] &
			& P_{\mrm{SO}(p,q)} \arrow[dl] \\
			& \mcal{M} & 
		\end{tikzcd}
		\end{center}
		Which restricts fiber-wise to the $\mbb{Z}_2$ covering homomorphism $
			\pi\colon
			\mrm{Spin}(p,q)
			\to
			\mrm{SO}(p,q)
		$. 
	\end{definition*}

	Spin structures need not exist and even if they do they need not be unique. We shall see the obstruction to such lifting by explicit construction.

	Again, we choose to work on the hypersurface $\Sigma$. Starting from the $\mrm{SO}(3)$ structure, transition function $\tau \in \mrm{SO}(3)$ satisfies the cocycle condition:
	\begin{equation}
		\tau_{UV}\circ
		\tau_{VW}\circ
		\tau_{WU} = \idty,\quad
		\tau\in \mrm{SO}(3)
	\end{equation}
	The lifting of $\tau\in\mrm{SO}(3)$ to $\tilde{\tau}\in\mrm{Spin}(3)$ always exists locally. First, we simply choose one of the pre-images of the $\mbb{Z}_2$ covering at some point $p\in\Sigma$, i.e.~
	\begin{equation}
		\pi\pqty\big{\tilde{\tau}(p)}
		= \tau(p),\quad
		\pi\colon \mrm{Spin}(3) \to \mrm{SO}(3),\quad
		p\in\Sigma
	\end{equation}
	Then we need to extend such choice of $\tilde{\tau}$ smoothly around the manifold. There will be no obstruction of such extension around a small neighborhood of $p\in U \subset\Sigma$, but it may fail globally if two different ``paths'' of extension yields incompatible results. In the end, we can only guarantee that:
	\begin{gather}
		\pi\pqty\big{
			\tilde{\tau}_{UV}\circ
			\tilde{\tau}_{VW}\circ
			\tilde{\tau}_{WU}
		} = \idty,\\[.5ex]
		\tilde{\tau}_{UV}\circ
		\tilde{\tau}_{VW}\circ
		\tilde{\tau}_{WU}
		= f_{UVW}
		= \pm\idty
		\in \ker \pi
		= \mbb{Z}_2
	\end{gather}
	But for a spin structure $P_{\mrm{Spin}}\to P_{\mrm{SO}(3)}$,  $\tau\in\mrm{SO}(3)$ and $\tilde{\tau}\in\mrm{Spin}(3)$ should both satisfy the cocycle condition. This is possible iff.~$f_{UVW} = 1$. It turns out that $f_{UVW}$ as a function of charts is in fact independent of the choice of local frames; it is completely fixed by the manifold $\Sigma$, i.e.~$f_{UVW} = f(\Sigma)$ is a \textit{characteristic class} of $\Sigma$.

	Notice that our discussions about spin structure greatly resemble those in the last section, about the existence of $\mrm{SO}(3)$ transition. Note that the $\mrm{GL}(3,\mbb{R})\to\mrm{O}(3)\to\mrm{SO}(3)$ refinement is also locally trivial, but obstruction occurs in the form of (\textit{non-})\,orientability when we try to extend it globally on the whole manifold. The situation with spin structure is quite similar, with the obstruction given by $f(\Sigma)$.

	In fact, these two things can be described in a unifying way by \textit{Stiefel–Whitney class} $w_n$ and \textit{\v{C}ech cohomology} $H^n(\Sigma,\mbb{Z}_2)$. $f_{UVW} = f(\Sigma)$ defined above is precisely the \nth{2} Stiefel–Whitney class $w_2(T\Sigma)$. 
\pagebreak[3]

	We will not dive too deep into this subject; for further discussions, see \cite{Nakahara:2003nw,lawson2016spin}. Rather, we simply summarize some relevant results below:
	\begin{itemize}[noitemsep]
	\item Given any bundle $E\to\Sigma$, $w_n(E)\in H^n(\Sigma,\mbb{Z}_2)$; 
	\item $\Sigma$ orientable iff.~$w_1(T\Sigma)$ is trivial; 
	\item $\Sigma$ has spin structures iff.~$w_2(T\Sigma)$ is trivial; furthermore, if this is the case, then the spin structures on $\Sigma$ are in one-to-one correspondence with elements of $H^1(\Sigma,\mbb{Z}_2)$. 
	\item $H^1(\Sigma,\mbb{Z}_2)\cong \mop{Hom}(\pi_1(\Sigma),\mbb{Z}_2)$, i.e.~ways of assigning $(\pm)$ signs to non-contractible loops ($S^1$) in $\Sigma$; here $\pi_1(\Sigma)$ is the fundamental group. 
	\end{itemize}
	In general, the refinement and lifting of structure group happens in the following steps:
	\begin{itemize}[noitemsep]
	\item We start with a $C^\infty$ manifold $\Sigma$ with $\tau\in\mrm{GL}(n,\mbb{R})$;
	\item With Riemannian metric $g_{ij}$, by restricting to isometries, $\tau\in\mrm{O}(n)\subset\mrm{GL}(n,\mbb{R})$;
	\item With orientability we can further restrict $\tau\in\mrm{SO}(n)\subset\mrm{O}(n)$;
	\item With spin structure, we can lift $\tau\in\mrm{SO}(n)$ to $\tilde{\tau}\in\mrm{Spin}(n)$. 
	\end{itemize}

	To better understand spin structure, we shall look at the most basic example $\Sigma = S^1$ with unit radius the usual flat metric. Note that $S^1$ is an oriented 1--fold, $w_1(\mrm{T}S^1) = \idty$, and its tangent bundle is just the trivial line bundle:
	\begin{equation}
		\mrm{T}S^1 \cong S^1\times \mbb{R}
		\label{eq:trivial_S1_bundle}
	\end{equation}
	whose isometric transition function is trivial $\tau\equiv\idty = \mrm{SO}(1)$, so the frame bundle is just $S^1\times\{\idty\}\cong S^1$. The spin group, however, is non-trivial: $\mrm{Spin}(1)\cong\mbb{Z}_2$, hence there might be non-trivial liftings to $P_{\mrm{Spin}}$.

	Indeed, $w_2(\mrm{T}S^1) = \idty$, but $H^1(\Sigma,\mbb{Z}_2)\cong \mop{Hom}(\pi_1(\Sigma),\mbb{Z}_2) = {\pm\idty}$, and we have two inequivalent spin structures on $S^1$. It is more intuitive to look at their associated line bundles. One of them is simply $S^1\times\mbb{R}$, but the other one consists of a non-trivial \textit{twist} on the fiber:
	\begin{equation}
	\begin{gathered}
		E = S^1\times_{\mbb{Z}_2} \mbb{R},\quad
		\psi\in \Gamma(\Sigma,E)
			\,\colon\,
			\Sigma\to E,\\[.5ex]
		\psi(\theta + 2\pi) = -\psi(\theta)
	\end{gathered}
	\end{equation}
	This is precisely the \textit{M\"obius bundle} studied extensively in \textit{Lee} \cite{lee2012introduction}. In fact, the lifting of $\tau\equiv\idty$ to $\tilde{\tau}\in\mbb{Z}_2$ is explicitly given in \textit{Lee} \cite{lee2012introduction}, Problem 10-13. By introducing the $\mbb{C}$omplex label $z = e^{i\theta} \in {S}^1$ and two charts $U_{\pm} = S^1\setminus\{\pm 1\}$, we have:
	\begin{equation}
		\tilde{\tau}_{+,-}(z)
		= \bigg\lbrace
		\begin{aligned}
			\ %
			& {+\idty}, && \Im z > 0,\\[-.3ex]
			& {-\idty}, && \Im z < 0,
		\end{aligned}\quad
		z = e^{i\theta} \in S^1
	\end{equation}

	In summary, $S^1$ has two distinct spin structures, and their associated $\mbb{R}$ line bundles are respectively, $S^1 \times\mbb{R}$ and $S^1\times_{\mbb{Z}_2} \mbb{R}$, which also correspond to periodic and anti-periodic boundary conditions on $\theta\in[0,2\pi]$.

	In some literature (incl.~most physics texts), these two spin structures are affectionally named \textit{Neveu--Schwarz} (NS) and \textit{Ramond} (R). In general, a genus $g$ Riemann surface has $2g$ distinct periods, which give rise to $2^{2g}$ inequivalent spin structures. 
\subsection{Dirac Operator and Spin Connection}
	Back to Witten's proof of the positive energy theorem, we have an asymptotic flat 3--fold $\Sigma\subset\mcal{M}$, and indeed $w_{1,2}(T\mcal{M}) = w_{1,2}(T\Sigma) = \idty$ are all trivial, so the existence of spin structure is guaranteed \cite{Parker:1981uy}.

	With a spin structure, we can construct associated \textit{spinor bundles} just like the $S^1$ case. However, the model fiber $F$ of a spinor bundle is generally some $\mbb{C}$ vector space, since the related Hilbert space on $\Sigma$ is a $\mbb{C}$ linear space.

	In general, the model fiber $F$ can be any spin representation. In Witten's original proof, the (complexified) Clifford $\cliff(3,1)^{\mbb{C}}$ module is chosen, with $F\cong
	\mbb{C}^4$ as a vector space. This is in fact the defining module of $\mrm{Spin}(3,1)$, and corresponds to the famous \textit{Dirac spinor}. Dirac spinor bundle is then pulled back to the hypersurface $\Sigma\subset\mcal{M}$ and treated as a $\mrm{Spin}(3)$ spinor bundle.

	Dirac spinor first arose in the effort of finding a wave equation compatible with relativity. Dirac noted that relativistic wave equation for an electron should be \nth{1} order in time dependence, so that it behaves nicely as an initial value problem \cite{dirac1981principles}. This leads to the need of taking a ``square root'' of the d'Alembert operator $\partial^a\pdd{a}$, i.e.~finding some scalar operator $i\slashed{\partial}$ so that:
	\begin{equation}
		\pqty{\smash{
			i\slashed{\partial}
		}}^2 = \partial^a \pdd{a}
		\label{eq:dirac_square}
	\end{equation}
	Here $i$ is introduced to ensure that $i\slashed{\partial}$ is self-adjoint, much like $\partial^a \pdd{a}$ itself. Dirac discovered that such $i\slashed{\partial}$ could be realized using $\gamma^a \in \cliff(3,1)$, namely,
	\begin{gather}
		\slashed{\partial}
		= \gamma^a \pdd{a},\quad
		\slashed{\partial}^2 = -\idty\,\partial^a \pdd{a},\\[.5ex]
		\idty,\gamma^a \in \cliff(3,1),\\[.5ex]
		\tfrac{1}{2} \Bqty\big{\gamma^a,\gamma^b}
		= \tfrac{1}{2} \pqty\big{
			\gamma^a\gamma^b
			+ \gamma^a\gamma^b
		} = -\eta^{ab}
	\end{gather}
	$\slashed{\partial}$ is the so-called \textit{Dirac operator}. $\cliff(3,1)$ is faithfully represented by $4\times 4$ $\mbb{C}$omplex matrices, and the field $\psi$ it acts on shall be a column vector $\psi\in F \cong\mbb{C}^4$. This is the Dirac spinor.

	Dirac operator and Clifford $\gamma^a$ can then be generalized in curved spacetime; we have:
	\begin{equation}
		\slashed{\nabla} = \gamma^a \cdv{a}
		\equiv \theta^a.\cdv{a}
	\end{equation}
	Where $\theta^a$ is the orthonormal coframe defined in \eqref{eq:orthonormal_frame}, and ``$.$'' denotes some Clifford multiplication. Without referencing $\gamma^a$, the latter expression can then be generalized to arbitrary fiber $F$, as long as $F$ is some spin representation. \textit{Dirac's equation} in curved spacetime can then be expressed in the following form\footnote{
		There are numerous conventions for $\cliff(3,1)$ and $\slashed{\nabla}$. We have chosen a convention that is compatible with Witten's proof \cite{Witten:1981mf,Parker:1981uy}. Note that this differs from Weinberg's convention \cite{Weinberg:1995mt}. 
	}:
	\begin{equation}
		\pqty{i\slashed{\nabla} - m}\,\psi(x) = 0
	\end{equation}

	In Witten's proof, since we are only working on 3--fold $\Sigma\in\mcal{M}$, this is further truncated to the \textit{hypersurface Dirac operator}:
	\begin{equation}
		\mscr{D} = \theta^i.\cdv{i}
		= \sum_{i=1}^{3} \theta^i.\cdv{i}
		\label{eq:hypersurface_dirac}
	\end{equation}
	In fact, on such 3--fold $\Sigma$, Witten's proof can actually be simplified using basic $\mrm{Spin}(3)$ representations, i.e.~\textit{Weyl spinors} introduced in Section \ref{subsect:repr}. Then, the $\theta^i$ multiplications can be expressed with Pauli matrices $\sigma^i$, defined in \eqref{eq:pauli_mat}, and the fiber is thus reduced to $F = V\cong \mbb{C}^2$. See \cite{Straumann:2013spu} for this simplified version of Witten's proof.

	Note that we haven't addressed the nature of covariant derivative $\nabla$. Since we are no longer working on a tensor bundle, this could not be the usual Levi-Civita connection. In fact, the lifting of $P_{\mrm{SO}(3)}$ to $P_{\mrm{Spin}}$ naturally induces a lifting of the usual Levi-Civita connection; this is the so-called \textit{spin connection}. See \cite{figueroa2010spin,Wernli:2019hpf} for further discussions.

	Generally, for $\Sigma\subset\mcal{M}$, $\nabla$: spin connection on $\mcal{M}$, $\mscr{D}$: hypersurface Dirac operator, \eqref{eq:dirac_square} is modified to be the \textit{Lichnerowicz–Weitzenböck formula}:
	\begin{equation}
		\mscr{D}^\dagger\mscr{D}
		= D^2 = \nabla^\dagger \nabla + \mscr{R}
		\label{eq:fancy_math_formula}
	\end{equation}
	Where ``$\dagger$'' denotes $\mbb{C}$--adjoint w.r.t.~the standard Hermitian form on $F\cong\mbb{C}^n$, and $\mscr{R}$ is some curvature corrections \cite{Parker:1981uy}. 
\section{Sketch of the Proof}
	With previous preparations, we are finally ready to sketch the main ideas of Witten's proof, following \cite{Witten:1981mf,Parker:1981uy,Straumann:2013spu}. 
	\begin{itemize}[leftmargin=*]
	\item First, assume there is matter described by {spinor field} $\psi$ on the manifold $\mcal{M}$.

	The motivation and validity of this assumption is the main content of this review. It is indeed the essence of Witten's proof; following steps, though technically difficult, are conceptually simple compared to this first step. 
	\item The dynamics of spinor field respects spacetime symmetries, and $\psi(x)$ transforms as a \textit{spinor representation} on its fiber, specified in section \ref{subsect:repr}. Just as is discussed in section \ref{subsect:adm_energy}, we can construct a conserved Noether current of $\psi$:
	\begin{equation}
		j^\mu = \psi^\dagger.\theta^0.\theta^\mu.\psi
	\end{equation}
	This is a null (lightlike) vector near the asymptotic boundary, hence the contraction of $j^\mu$ with the ADM energy \eqref{eq:adm_energy} yields:
	\begin{equation}
		j^\mu P_\mu \propto E - \abs{P}
	\end{equation}
	\item On the other hand, by definition, $j^\mu P_\mu$ can be expanded with curvature $R_{\mu\nu}$ and field $\psi$. Using Einstein's equations, $R_{\mu\nu}$ can be further expressed in local energy--momentum $T_{\mu\nu}$ in the following form:
	\begin{equation}
		j^\mu P_\mu
		= \int_\Sigma
			\pqty\big{-T_{0\nu} j^\nu + \cdots}
			\dd{\textit{Vol}}
		\label{eq:contracted_adm}
	\end{equation}
	Where the $(\cdots)$ part contains only $\cdv{\mu}\psi$ terms. This can be seen as the integral form of the Lichnerowicz–Weitzenböck formula \eqref{eq:fancy_math_formula}, where $\mscr{R}$ is replaced by $T_{\mu\nu}$.

	Calculations from now on relies heavily on tricks from spinor analysis, including extensive use of \eqref{eq:fancy_math_formula} and \textit{Bochner formula}, which is well-reviewed in math texts such as \cite{jost2011riemannian,bourguignon2015spinorial}. Witten, on the other hand, refers to supergravity for inspirations \cite{Witten:1981mf}.

	\item $T_{\mu\nu}$ satisfies the dominant energy condition (DEC) \eqref{eq:DEC}, so the first term of \eqref{eq:contracted_adm} is positive. There are also spinor bilinear $\norm{\nabla\psi}^2$ in \eqref{eq:contracted_adm}, which are also automatically positive. The only remaining part is proportional to $\mscr{D}\psi$. If we can choose some non-zero $\psi$ so that:
	\begin{equation}
		\mscr{D}\psi = 0
		\label{eq:dirac_witten}
	\end{equation}
	Then the proof is done. 
	\item \eqref{eq:dirac_witten} is called the \textit{Dirac--Witten} equation. Proof of the theorem now comes down to analyzing this PDE. In fact, on asymptotically flat $\Sigma\subset\mcal{M}$, if $\psi$ vanishes at infinity \textit{fast enough} ($\sim \frac{1}{r^{1-\epsilon}}$), then it has to be zero $\psi = 0$. This gives $E = 0$ and $\mcal{M}$ flat.

	Furthermore, if $\psi$ is asymptotically constant, then the right-hand side of \eqref{eq:contracted_adm} is positive, since it contains spinor bilinear $\norm{\nabla\psi}^2$.

	These results are the so-called \textit{Witten's vanishing theorem} \cite{Parker:1981uy}. It can be proven rigorously using Green's function of operator $\mscr{D}$, as is proved and well-reviewed in \cite{Witten:1981mf,Parker:1981uy}. This concludes Witten's proof of the positive energy theorem. 
	\end{itemize}

	\hfill\qedsymbol
\section{Acknowledgements}
	We thank Dr.~Luis Apolo for his extensive proof-reading and valuable suggestions for this review. We thank Prof.~Mauricio Romo, fellow student Yuan Zhong and Kai Xu for many inspiring discussions. We thank Prof.~Hui Ma for her great teachings in the \textit{Smooth Manifolds} class.

\renewcommand*{\bibfont}{%
	\linespread{1.}\selectfont
}
\raggedright
\printbibliography[%
	title = {References} %
	,heading = bibintoc
]
\end{document}

### 2020-06-26 Strings2020/strings1/strings1.tex
Clean up preambles, update templates

@@
 
-\newcommand{\oppower}[2]{\mop{{#1}^{#2}}\!}
-\newcommand{\sqsinh}{\oppower{\sinh}{2}}
-\newcommand{\sqcosh}{\oppower{\cosh}{2}}
+\newcommand{\sqsinh}{\moppower{\sinh}{2}}
+\newcommand{\sqcosh}{\moppower{\cosh}{2}}
 
@@
 
-%{
-%	\noindent\itshape%
-%	本文约定：度规$\eta\sim\pqty{-,+,+,+}$, 指标$\mu,\nu,\dots = 0,1,2,3,\ i,j,\dots = 1,2,3$.
-%}
 	\begin{enumerate}
@@
 	Furthermore, we consider the special case that the closed string is \textit{folded}, like a rubber band stretched along a line; in this case we can choose the worldsheet parameter $(\tau,\sigma) = (t,\rho)$ while $\Omega = \Omega(t,\rho) = \Omega(\tau,\sigma)$, which leads to the following decomposition:
+	{
+	\newcommand{\mat}[1]{\pqty\Big{
+		\footnotesize
+		\hspace{-.2em}
+			\begin{array}{cc}
+				#1
+			\end{array}
+		\hspace{-.2em}
+	}}
 	\begin{align}
@@
 %		&= R^2\,\sqsinh\rho\,\Bqty{\mat{
-%			-\oppower{\coth}{2}\rho & \\
-%			& \oppower{\csch}{2}\rho \\
+%			-\moppower{\coth}{2}\rho & \\
+%			& \moppower{\csch}{2}\rho \\
 %		} + \,\mat{
@@
 	\end{align}
+	}%
 	Here $
@@
 		&= (R^2)^2\,\Big\{
-			\oppower{\sinh}{4}\rho\,
+			\moppower{\sinh}{4}\rho\,
 			\det\,(\pdd{a}\Omega^i\pdd{b}\Omega_i)
@@
 		&\qquad\qquad\qquad
-			+ \oppower{\sinh}{2}\rho\,\pqty{
+			+ \sqsinh\rho\,\pqty{
 				(\pdd{a}\Omega)^2
 				- (\pdd{b}\Omega)^2
-				\oppower{\cosh}{2}\rho
+				\sqcosh\rho
 			}
@@
 		&\qquad\qquad\qquad
-			- \oppower{\cosh}{2}\rho\,
+			- \sqcosh\rho\,
 		\Big\},\\[.5ex]
@@
 		&= R^2\,\Big\{
-			\oppower{\cosh}{2}\rho
-			- \oppower{\sinh}{2}\rho\,\pqty{
+			\sqcosh\rho
+			- \sqsinh\rho\,\pqty{
 				(\pdd{a}\Omega)^2
 				- (\pdd{b}\Omega)^2
-				\oppower{\cosh}{2}\rho
+				\sqcosh\rho
 			}
@@
 		&\qquad\qquad\quad
-			- \oppower{\sinh}{4}\rho\,
+			- \moppower{\sinh}{4}\rho\,
 			\det\,(\pdd{a}\Omega^i\pdd{b}\Omega_i)
@@
 		\sqrt{
-			\oppower{\cosh}{2}\rho
-			- \oppower{\sinh}{2}\rho\,\pqty{
+			\sqcosh\rho
+			- \sqsinh\rho\,\pqty{
 				(\pdd{a}\Omega)^2
 				- (\pdd{b}\Omega)^2
-				\oppower{\cosh}{2}\rho
+				\sqcosh\rho
 			}
-			- \oppower{\sinh}{4}\rho\,
+			- \moppower{\sinh}{4}\rho\,
 			\det\,(\pdd{a}\Omega^i\pdd{b}\Omega_i)
@@
 			\sqrt{
-				\oppower{\cosh}{2}\rho
-				- \oppower{\sinh}{2}\rho\,\pqty{
+				\sqcosh\rho
+				- \sqsinh\rho\,\pqty{
 					(\pdd{a}\theta)^2
 					- (\pdd{b}\theta)^2
-					\oppower{\cosh}{2}\rho
+					\sqcosh\rho
 				}
@@
 			\sqrt{
-				\oppower{\cosh}{2}\rho
-				- \omega^2\oppower{\sinh}{2}\rho
+				\sqcosh\rho
+				- \omega^2\sqsinh\rho
 			},\quad
@@
 			\sqrt{
-				\oppower{\cosh}{2}\rho
-				- \omega^2\oppower{\sinh}{2}\rho
+				\sqcosh\rho
+				- \omega^2\sqsinh\rho
 			}
@@
 			\sqrt{
-				\oppower{\cosh}{2}r
-				- \omega^2\oppower{\sinh}{2}r
+				\sqcosh r
+				- \omega^2\sqsinh r
 			} \var{r},\\
 		\omega^2 = \frac{\sqcosh r}{\sqsinh r}
-		= \oppower{\coth}{2} r
+		= \moppower{\coth}{2} r
 		\label{eq:string_endpt_constraint}

### 2020-06-26 Strings2020/strings2/strings2.tex
Clean up preambles, update templates

@@
 %\InputIfFileExists{../id.tex}{}{}
-
-\newcommand{\oppower}[2]{\mop{{#1}^{#2}}\!}
-\newcommand{\sqsinh}{\oppower{\sinh}{2}}
-\newcommand{\sqcosh}{\oppower{\cosh}{2}}
-
-\newcommand{\Vir}{\mathbf{V}\mfrak{ir}}
 
@@
 \thispagestyle{empty}
-
-%{
-%	\noindent\itshape%
-%	本文约定：度规$\eta\sim\pqty{-,+,+,+}$, 指标$\mu,\nu,\dots = 0,1,2,3,\ i,j,\dots = 1,2,3$.
-%}
 
@@
 See \textit{Di Francesco et al} for more detailed discussions.
-		Na\"ively, $\normorder{bc\,\pd c}_{\,(0)}$ is \textit{defined} as $b(0)\,c(z_1)\,\pd c(z_2)$ while $z_1,z_2\to 0$, with singular terms subtracted; however, different ways of taking the limit might lead to different results.
+		Na\"ively, $\normorder{bc\,\pd c}_{(0)}$ is \textit{defined} as $b(0)\,c(z_1)\,\pd c(z_2)$ while $z_1,z_2\to 0$, with singular terms subtracted; however, different ways of taking the limit might lead to different results.
 For example, we can first take $z_1\to 0$ then $z_2\to 0$, or we can first take $z_1\to z_2$ then $z_2\to 0$.
@@
 			+ T^{bc}(z)\,
-				\normorder{bc\,\pd c}_{\,(0)},
+				\normorder{bc\,\pd c}_{(0)},
 		\label{eq:BRST_Tj_OPE}\\
@@
 	\begin{equation}
-		T^{bc}(z)\,\normorder{bc\,\pd c}_{\,(0)}
+		T^{bc}(z)\,\normorder{bc\,\pd c}_{(0)}
 		= \pqty\big{
@@
 			- 2\,\pd(\normorder{bc})
-		}_{(z)}\,\normorder{bc\,\pd c}_{\,(0)}\,,
+		}_{(z)}\,\normorder{bc\,\pd c}_{(0)}\,,
 	\end{equation}
@@
 	\begin{align}
-		\normorder{(\pd b)\,c}_{\,(z)}\,
-		\normorder{bc\,\pd c}_{\,(0)}
+		\normorder{(\pd b)\,c}_{(z)}\,
+		\normorder{bc\,\pd c}_{(0)}
 		&\sim \normorder{
@@
 				bc\,\pd^2 c
-			}_{\,(0)}
+			}_{(0)}
 			+ \order*{z^3}
@@
 				(\pd b)\,c\,\pd c
-			}_{\,(0)} + \order{z}
+			}_{(0)} + \order{z}
 		} + \frac{-1}{z^3}\,\pd c(0)
@@
 				+ (\pd b)\,c\,\pd c
-			}}_{\,(0)}\,, \notag\\[1ex]
+			}}_{(0)}\,, \notag\\[1ex]
 		&\sim \frac{4}{2z^4}\,c(0)
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-		\normorder{bc}_{\,(z)}\,
-		\normorder{bc\,\pd c}_{\,(0)}
+		\normorder{bc}_{(z)}\,
+		\normorder{bc\,\pd c}_{(0)}
 		&\sim \normorder{
@@
 			(-1)\,c(0) \notag\\[1ex]
-		\normorder{bc}_{\,(z)}\,
-		\normorder{bc\,\pd c}_{\,(0)}
+		\normorder{bc}_{(z)}\,
+		\normorder{bc\,\pd c}_{(0)}
 		&\sim \frac{1}{z}\,\pqty\big{
@@
 		\pd (\normorder{bc})_{(z)}\,
-		\normorder{bc\,\pd c}_{\,(0)}
+		\normorder{bc\,\pd c}_{(0)}
 		&\sim \frac{6}{2z^4}\,c(0)
@@
 	\begin{gather}
-		T^{bc}(z)\,\normorder{bc\,\pd c}_{\,(0)}
+		T^{bc}(z)\,\normorder{bc\,\pd c}_{(0)}
 		\sim \frac{-8}{2z^4}\,c(0)
@@
 %	\begin{aligned}
-%		T^{bc}(z)\,\normorder{bc\,\pd c}_{\,(0)}
+%		T^{bc}(z)\,\normorder{bc\,\pd c}_{(0)}
 %		&\sim \pqty{
@@
 		&\sim \frac{1}{2}\,
-			\normorder{cT^{bc}}_{\,z}\,c_0
+			\normorder{cT^{bc}}_{z}\,c_0
 		\sim \frac{1}{2}\,c_z \Bqty{
-			\normorder{T^{bc}}_{\,z}\,c_0
+			\normorder{T^{bc}}_{z}\,c_0
 		}
@@
 		&\sim \frac{1}{2}\,
-			\normorder{cT^{bc}}_{\,z}\,j^{bc}_0
+			\normorder{cT^{bc}}_{z}\,j^{bc}_0
 		+ \frac{3}{2}\,\pqty{
@@
 %	\begin{aligned}
-%		\normorder{cT^{bc}}_{\,z}\,j^{bc}_0
+%		\normorder{cT^{bc}}_{z}\,j^{bc}_0
 %		&\sim \normorder{\wick{
@@
 %	\begin{aligned}
-%		\normorder{cT^{bc}}_{\,z}\,j^{bc}_0
+%		\normorder{cT^{bc}}_{z}\,j^{bc}_0
 %		&\sim \normorder{\pqty{

### 2020-06-26 compile.sh

@@ -39,7 +39,7 @@ for file in $FILES; do
     || [[ $tex_program == lualatex ]]; then
         latexmk \
             "-$tex_program" \
-            -synctex=1 \
+            -synctex=15 \
             -interaction=nonstopmode \
             -shell-escape \
             "$filename"

### 2020-10-06 Renormalization/wilson.tex
Add RG note, migrated from markdown

% !TeX document-id = {b5392a94-51a3-49d1-9ba5-698bc09f9d35}
% !TeX encoding = UTF-8
% !TeX spellcheck = en_US
% !TeX TXS-program:bibliography = biber -l zh__pinyin --output-safechars %

\documentclass[a4paper,10pt]{article}

\input{preamble.tex}
\input{modules/basics/biblatex.tex}

\title{A Modern Take on Renormalization}
%\addbibresource{.bib}

%%% ID: sensitive, do NOT publish!
%\InputIfFileExists{../id.tex}{}{}

\usepackage{cancel}

\begin{document}
\maketitle
\pagestyle{headings}
\pagenumbering{arabic}
\thispagestyle{empty}

\vspace*{-.5\baselineskip}
	The continuum limit $\Lambda\to\infty$ is \textbf{not} well defined.
	Renormalization provides a way to \emph{define} the theory when
	$\Lambda\to\infty$.

	\textbf{My belief:} The only way to fully understand renormalization is
	through Wilson's arguments; all other ``interpretations'' of
	renormalization are only \emph{heuristic}.

\textbf{Key words:}
\begin{itemize}[nosep]
\item Renormalization group
\item Counterterms
\item Regularization and cutoff
\end{itemize}

\setlength{\parskip}{.1\baselineskip}
\tableofcontents
\setlength{\parskip}{\parskipnorm}

\section{References}

\noindent \textsl{Ranked by importance:}

	\begin{itemize}
	\item David Skinner's note:
	  \begin{itemize}[nosep]
	  \item \url{https://www.damtp.cam.ac.uk/user/dbs26/AQFT.html}
	    \begin{itemize}[nosep]
	    \item \url{https://www.damtp.cam.ac.uk/user/dbs26/AQFT/Wilsonchap.pdf}
	    \item \url{https://www.damtp.cam.ac.uk/user/dbs26/AQFT/chap5.pdf}
	    \end{itemize}
	  \end{itemize}
	\item Schwartz, Chapter 15
	\item Peskin \& Schroeder, Chapter 10 \& 12
	\item Hollowood's book:
	  \begin{itemize}[nosep]
	  \item \url{https://arxiv.org/abs/0909.0859}
	  \item \url{https://link.springer.com/book/10.1007/978-3-642-36312-2}
	  \end{itemize}
	\end{itemize}

\section{Wilson's picture}
	Seed theory parameters (i.e.\ \emph{bare parameters}):
	$(g_0,\Lambda_0)$, $g = (m,\lambda,\cdots)$ a collection of all
	possible couplings.

	\begin{equation}
	\begin{aligned}
	  \phi_{\Lambda_0}(x)
	  \sim \int^{\Lambda_0} \dd p
	    e^{ip\cdot x}
	    \tilde{\phi}(p)
	  &= \int^{\Lambda} \dd p
	    e^{ip\cdot x}
	    \tilde{\phi}(p)
	    + \int_{\Lambda}^{\Lambda_0} \dd p
	    e^{ip\cdot x}
	    \tilde{\phi}(p) \\
	  &=\colon \phi_{\Lambda}(x) + \chi(x)
	\end{aligned}
	\end{equation}

	\begin{equation}
	\begin{aligned}
	  \DD\phi_{\Lambda_0}(x)
	  \sim \prod_{\norm{p} < \Lambda_0}
	    \dd{\tilde{\phi}(p)}
	  &= \prod_{\norm{p} < \Lambda}
	    \dd{\tilde{\phi}(p)}
	    \prod_{\Lambda < \norm{p} < \Lambda_0}
	    \dd{\tilde{\phi}(p)} \\
	  &\sim
	    \DD\phi_{\Lambda}(x)\,
	    \DD\chi(x)
	\end{aligned}
	\end{equation}

	\begin{equation}
	\begin{aligned}
	  \mcal{Z} (g_0,\Lambda_0)
	  &= \int \DD \phi_{\Lambda_0}
	      e^{iS[\phi_{\Lambda_0}]} \\
	  &= \int \DD \phi_{\Lambda}
	    \int \DD \chi\,
	      e^{iS[\phi_\Lambda + \chi]} \\
	  &=\colon \int \DD \phi_{\Lambda}\,
	      e^{iS_{\mathrm{eff}} [\phi_\Lambda]}
	  =\colon \mcal{Z}\pqty{g(\Lambda),\Lambda}
	\end{aligned}
	\end{equation}
	Renormalized parameters: $(g,\Lambda)$.

	\begin{quote}
	\textbf{Subtlety:} the notation above is only schematic; in practice we
	first Wick-rotate to Euclidean signature, so that the momentum cutoff is
	easily imposed: $\norm{p} = \sqrt{p_0^2 + \vb{p}^2} < \Lambda$. In
	Lorentzian signature, it's hard to define a covariant cutoff since
	$p_\mu p^\mu = - p_0^2 + \vb{p}^2$. This process can be made rigorous;
	just think of the 8-shaped contour in loop integrals.
	\end{quote}

	\textbf{Effective action:}
	\begin{equation}
	  S_{\mathrm{eff}}[\phi]
	  = -i \ln \int \DD \chi
	      e^{iS[\phi + \chi]} \\
	\end{equation}
	$\phi = \phi_\Lambda$ is treated as constant when doing
	$\int \DD \chi$.
	\begin{equation}
	\begin{aligned}
	  \mcal{L}[\phi + \chi]
	  &= - \frac{1}{2}
	      \partial_\mu (\phi + \chi)\,
	      \partial^\mu (\phi + \chi)
	    - \frac{1}{2} m^2
	      (\phi + \chi)^2
	    - \frac{1}{4!} \lambda\,
	      (\phi + \chi)^4\\
	  &= \cdots \\
	  &= \mcal{L}[\phi]
	    + \Delta\mcal{L} [\phi,\chi]
	\end{aligned}
	\end{equation}

	\begin{equation}
	  S_{\mathrm{eff}}[\phi_\Lambda]
	  = S[\phi_\Lambda]
	    - i \ln \int \DD \chi
	      e^{i\,\Delta S[\phi_\Lambda + \chi]} \\
	\end{equation}

	If $\Lambda \lesssim \Lambda_0$, then $S_{\mathrm{eff}}$ is almost
	the same as the original $S$, with minor corrections from the
	$\int \DD\chi$ term. Note that in our regularization scheme there will
	be no mixed terms of $\phi$ and $\chi$ in the effective action,
	since they have orthogonal Fourier modes.

	Note that $\mcal{Z}$ clearly does not depend on the intermediate scale $\Lambda$, we have:
	\begin{equation}
	  0
	  = \Lambda \dv{}{\Lambda}\,
	    \mcal{Z}\pqty{g(\Lambda),\Lambda}
	  = \pqty{
	      \Lambda \pdv{}{\Lambda}
	      + \Lambda \pdv{g^{(i)}}{\Lambda}
	        \pdv{}{g^{(i)}}
	    }
	    \mcal{Z}\pqty{g(\Lambda),\Lambda}
	\end{equation}
	This is an example of a \textbf{RG Equation}.
\section{Perturbative Renormalization}
	However, in naïve perturbation theory, we wish to complete the entire
	path integral $\mcal{Z} (g_0,\Lambda_0)$. We can think of this as
	integrating out more and more high energy modes, until we reach the IR
	scale $\Lambda \to 0$.

	When $\Lambda \ll \Lambda_0$, we have no reason to believe the
	renormalized couplings $g(\Lambda)$ are close to the original
	couplings $g_0$ at $\Lambda_0$. In fact, they may differ by a large
	(but finite) renormalization factor $Z$: $g_0 = Zg$.

\subsection{Counterterms}
	In the above analysis, the theory flows from UV to IR. However, in
	reality, the IR results are known from experiments, and we are trying to
	\emph{extrapolates} from IR to UV.

	We achieve this by \emph{tuning} the bare parameters $(g_0,\Lambda_0)$
	so that after RG flow, the IR results fit our experimental observations.
	If the IR couplings $g(\Lambda)$ are finite and small, then since
	$\Lambda \ll \Lambda_0$, we expect $g_0$ to be very large.

	We often \emph{split} $g_0$ into 2 parts for convenience:
	\begin{equation}
	  g_0 = g + \var{g}
	  = g + (Z - 1)\,g
	\end{equation}
	$\var{g}$ is the so-called \emph{counterterm}; intuitively, it's the
	(large) correction that gets integrated out when we go from
	$\Lambda_0$ all the way to IR.

	Basically, we have the following procedure:

	\begin{figure}[!h]
	\centering
	\includegraphics[width=.5\linewidth]{img/RG-process.png}
	\end{figure}

	\begin{enumerate}[noitemsep,midpenalty=100]
	\setcounter{enumi}{-1}

	\item
	  Select some UV parameters $(g_0,\Lambda_0)$
	\item
	  Perform the RG flow: $(g_0,\Lambda_0)\to (g,\Lambda)$
	\item
	  Tune (redefine) $g_0$ so that $(g,\Lambda)$ matches with
	  experiments
	\item
	  Use the tuned data to predicts phenomena at a different scale
	  $(g',\Lambda')$
	\end{enumerate}

	Note that the tuning of UV parameters $g_0$ is \emph{far from unique!}
	This is easy to understand: many UV theories might flow to the same IR
	theory. For this reason, some would say that RG is a \emph{semi-group}.

	However, for a \emph{renormalizable} theory, we can restrict the tuning
	to a \emph{finite} dimensional subspace formed by the \emph{relevant}
	couplings, since most other parameters $g^{(i)}$ are \emph{irrelevant}
	and get suppressed by $\Lambda/\Lambda_0$ in the IR. After such
	restriction to a relevant subspace, the RG flow is a group, and we can
	reverse the flow to \emph{extrapolate} towards UV.

\subsection{Perturbation}

	The above results are non-perturbative and should always hold.
	Perturbation theory is only a way to calculate the RG flow from UV to
	IR; it is reliable only if the IR coupling $g$ is sufficiently small.
	In this case we can tune $(g_0,\Lambda_0)$ with the following
	recursive / iterative algorithm:

	\begin{enumerate}[noitemsep]
	\item
	  Perturbative calculation of RG flow:
	  $(g_0,\Lambda_0)\to (g,\Lambda)$ at $\order{g^n}$
	\item
	  Tune (redefine) $(g_0,\Lambda_0)$ by adding counterterms, so that
	  $(g,\Lambda)$ matches with experiments
	\item
	  Increase order $n$ and go to step 1
	\end{enumerate}

	The (non-)renormalizability of a theory is evident in the perturbative
	expansion, by counting the \textbf{superficial degrees of divergence}
	$D$ of the Feynman diagrams. Basically,

	\begin{itemize}
	\item
	  Interaction vertices create loops, and loops create UV divergences.
	  Higher order interaction vertices create more loops, which lead to
	  more divergences.
	\item
	  External lines suppress UV divergences by factors like
	  $\frac{1}{\cancel{p}}$ or $\frac{1}{p^2}$.
	\end{itemize}

	For a renormalizable theory, there will be no divergence for diagrams
	with a sufficient number $E$ of external legs; for a
	non-renormalizable theory, however, there will always be divergences, no
	matter how large $E$ is.

\subsection{Renormalization Schemes}

	There is a subtlety in the above procedure: how do we actually relate IR
	parameters $(g,\Lambda)$ with actual physical quantities,
	e.g.~amplitudes $\mcal{M}(\mu)$?

	In fact, we've assumed that $(g,\Lambda)_{\Lambda\to 0}$ gives the
	physical couplings that we are familiar with, e.g.~mass, electric charge
	and so on. This is not quite true, since physical quantities are
	actually defined with scattering amplitudes. There are different choices
	of relating $g$ with physical observables; this lead to various
	renormalization schemes:

	\begin{itemize}[nosep]

	\item
	  On-shell / pole-mass scheme
	\item
	  Minimal subtraction ($\mathrm{MS}$) \& modified MS
	  ($\overline{\mathrm{MS}}$)
	\end{itemize}

	\hypertarget{renormalizability}{%
	\section{Renormalizability}\label{renormalizability}}

	Most parameters $g^{(i)}$ are, in fact, \emph{irrelevant} --- such
	terms in the Lagrangian get suppressed by $\Lambda/\Lambda_0$ in IR.
	If the IR theory has only \emph{relevant} couplings, then one should be
	able to recover their physical values by tuning a finite amount of
	relevant couplings in the UV, and usually the tuning is unique. This is
	the defining characteristic of a \textbf{renormalizable} theory.
	Basically, this means that we can naturally obtain a UV theory by
	extrapolation.

	\begin{quote}
	However, the tuning process described above might encounter some serious
	obstruction: the tuned $g_0$ could blow up at some finite
	$\Lambda_{\mathrm{UV}}$; this is the so-called \emph{Landau pole}.
	This tells us that the theory only works under some
	$\Lambda_{\mathrm{UV}}$, i.e.~it is not \emph{UV complete}; it's only
	an \emph{effective} theory. One have to ``embed'' this Lagrangian into a
	bigger theory that works beyond $\Lambda_{\mathrm{UV}}$; this is the
	non-trivial \emph{UV completion} of an effective theory.
	\end{quote}

	On the other hand, a theory is \textbf{non-renormalizable} if it
	contains irrelevant couplings in the IR. In this case the IR parameters
	$g$ depend sensitively on small perturbations of the UV parameters
	$g_0$, and one has to tune infinitely many bare parameters to obtain
	the physical IR values. Such theory is hardly \emph{fundamental}, since
	it depends on infinitely many parameters; but it's a good
	\emph{effective theory} nonetheless.

\section{Effective Action}

	Furthermore, after $\phi_\Lambda$ is completely integrated out, we
	have:

	\begin{equation}
	  S_{\mathrm{eff}}[\phi] \to W,\quad
	  Z(g_0,\Lambda_0) = e^{iW}
	\end{equation}
	Note that $W$ no longer has any $\phi$ dependence, but it is a
	function of $(g_0,\Lambda_0)$, which in turn is tuned by physical
	$(g,\Lambda)$. $W$ in fact contains all information about the seed
	theory, labeled by $(g_0,\Lambda_0)$. To extract this information, we
	usually perturb the original action $S[\phi]$ with a source term; then
	we have:

	\begin{equation}
	  S[\phi,J]
	  = S[\phi] + \int \dd{x}\,J(x)\,\phi(x),\quad
	  W \to W[J]
	\end{equation}

	Expand $W[J]$ in terms of $J$-modes, and its coefficient gives us
	physical coupling constants in the IR. More precisely, we can define the Legendre-transformed $\Gamma[\varphi]$.

\printbibliography[%
%	title = {参考文献} %
	,heading = bibintoc
]
\end{document}

### 2020-10-06 HW-AdvancedQFT2020/advqft1/advqft1.tex
Restructure to gather quick notes

% !TeX encoding = UTF-8
% !TeX spellcheck = en_US
% !TeX TXS-program:bibliography = biber -l zh__pinyin --output-safechars %

\documentclass[a4paper,10pt]{article}

\newcommand{\hwNumber}{1}

\input{../advqft_preamble.tex}
\input{../.modules/basics/biblatex.tex}

%%% ID: sensitive, do NOT publish!
%\InputIfFileExists{../id.tex}{}{}

\begin{document}
\maketitle
\pagestyle{headings}
\pagenumbering{arabic}
\thispagestyle{empty}

\vspace*{-1.5\baselineskip}

\section{Symmetry \& Noether's Theorem}
\subsection{2D $\sigma$-Model}
	\vspace{-.8\baselineskip}
	\begin{equation}
		\mcal{L} = -\frac{1}{2}\,
			\eta_{\alpha\beta}\,
			\eta_{\mu\nu}\,
			\pd^\alpha X^\mu\,
			\pd^\beta X^\nu
		= -\frac{1}{2}\,
			\pd^\alpha X_\mu\,
			\pd_\alpha X^\mu,\quad
		X^\mu\in\mbb{R}^{1,D-1}
	\end{equation}
	\begin{itemize}
	\item For $
		\var{X}^\mu
		= a^\mu + \lambda\id{^\mu_\nu} X^\nu
	$, the Lagrangian (density) transforms as follows:
	\begin{equation}
	\begin{aligned}
		\var{\mcal{L}}
		&= -\pd^\alpha X_\mu\,
			\pd_\alpha \var{X^\mu} \\
		&= -\pd^\alpha X_\mu\,
			\pd_\alpha \pqty{
				a^\mu
				+ \lambda\id{^\mu_\nu} X^\nu
			} \\
		&= -\pd^\alpha X_\mu\,
			\pqty{
				\pdd{\alpha} a^\mu
				+ X^\nu\,
					\pdd{\alpha} \lambda\id{^\mu_\nu}
				+ \lambda\id{^\mu_\nu}\,
					\pdd{\alpha} X^\nu
			} \\
		&= -\pd^\alpha X_\mu\,\pdd{\alpha} a^\mu
		- \pd^\alpha X^\mu\,
			\pdd{\alpha} X^\nu\,
			\lambda_{\mu\nu}
		- X^\nu\,\pd^\alpha X^\mu\,
			\pdd{\alpha} \lambda_{\mu\nu} \\
		&= -\pd^\alpha X_\mu\,\pdd{\alpha} a^\mu
		- \pd^\alpha X^\mu\,
			\pdd{\alpha} X^\nu\,
			\lambda_{(\mu\nu)}
		- X^\nu\,\pd^\alpha X^\mu\,
			\pdd{\alpha} \lambda_{\mu\nu}
		\label{eq:lorentz_variation}
	\end{aligned}
	\end{equation}
	Since $a^\mu$ and $\lambda\id{^\mu_\nu}$ are independent, imposing $\var{L} = 0$ yields $\pdd{\alpha} a^\mu = 0,\,a = \mrm{const}$. Furthermore, if $\var{L} = 0$ is to hold for arbitrary $X^\mu$ fields, then $\pdd{\alpha} \lambda_{\mu\nu} = 0,\,\lambda_{(\mu\nu)} = 0$, i.e.\ $\lambda_{\mu\nu}$ is constant and anti-symmetric over its indices.

%	\item Variation over any generic $\var{X}$ yields:
%	\begin{equation}
%	\begin{aligned}
%		\var{S} = \int \dd[2]{x}
%			\var{\mcal{L}}
%		&= - \int \dd[2]{x}
%			\pd^\alpha X_\mu\,
%			\pd_\alpha \var{X^\mu} \\
%		&= \int \dd[2]{x}
%			\pqty{\pd^\alpha \pdd{\alpha} X_\mu}
%			\var{X^\mu}
%		- \int \dd[2]{x} \pdd{\alpha} \pqty\big{
%			\pd^\alpha X_\mu\,
%			\var{X^\mu}
%		} \\
%	\end{aligned}
%	\end{equation}
%	This gives the equation of motion (EOM) $
%		\pd^\alpha \pdd{\alpha} X = 0
%	$.

	\item Promote $
		\var{X}\mapsto \epsilon(x)\var{X}
		= \epsilon(x)\,\pqty{
			a^\mu + \lambda\id{^\mu_\nu} X^\nu
		}
	$, with $\epsilon(x)$ some localized bump function; using \eqref{eq:lorentz_variation} and considering \textit{on-shell} variation, we have:
	\begin{equation}
	\begin{aligned}
		0 = \var{S}
		&= - \int \dd[2]{x} \pqty{
			\pd^\alpha X_\mu\,
				a^\mu\,
				\pdd{\alpha}\epsilon
			+ X^\nu\,\pd^\alpha X^\mu\,
				\lambda_{\mu\nu}\,
				\pdd{\alpha}\epsilon
		} \\
		&= - \int \dd[2]{x} \pqty{
			\pd^\alpha X_\mu\,
				a^\mu\,
			+ X_{[\nu}\,\pd^\alpha X_{\mu]}\,
				\lambda^{[\mu\nu]}\,
		}\,\pdd{\alpha}\epsilon
	\end{aligned}
	\end{equation}
	It is evident (after partial integration) that the following currents are conserved; they are the Noether currents associated with $a^\mu$ and $\lambda^{[\mu\nu]}$:
	\begin{equation}
		j^\alpha_\mu
		= -\pd^\alpha X_\mu,\quad
		j^\alpha_{\mu\nu}
		= -X_{[\nu}\,\pd^\alpha X_{\mu]}
		= \frac{1}{2}\,\pqty{
			X_\mu\,\pd^\alpha X_\nu
			- X_\nu\,\pd^\alpha X_\mu
		}
	\end{equation}

	Conserved charge $
		Q = \int\dd[2]{x} j^0(x)
	$, we have:
	\begin{equation}
		P_\mu = - \int\dd{x^1} \pd^0 X_\mu
		= \int\dd{x^1} \pd_0 X_\mu,\quad
		M_{\mu\nu}
		= \frac{1}{2}\,\int\dd{x^1}\pqty{
			X_\nu\,\pd_0 X_\mu
			- X_\mu\,\pd_0 X_\nu
		}
	\end{equation}
	They can be interpreted as spacetime momentum and spacetime angular momentum. 
	\qedfull
	\end{itemize}
\pagebreak[3]
\subsection{Real Scalar in $(3+1)$\,D}
	\vspace{-.8\baselineskip}
	\begin{equation}
		\mcal{L}
		= -\frac{1}{2}\,
			\pd^\mu\phi\,
			\pdd{\mu}\phi
		-\frac{1}{2}\,m^2\phi^2
	\end{equation}
	\begin{itemize}
	\item For $\phi$: scalar, under $
		x' = \lambda\circ x
	$, $\phi(x)\mapsto \phi'(x)$, while:
	\begin{equation}
		\phi'(x') = \phi(x)
		\ \Longrightarrow\ %
		\phi'(x) = \phi(\lambda^{-1}\circ x)
	\end{equation}
	For $\lambda\sim \lambda\id{^\mu_\nu}$: Lorentz transformation, $
		\eta_{\mu\nu}
			\lambda\id{^\mu_\rho}
			\lambda\id{^\nu_\sigma}
		= \eta_{\rho\sigma}
	$, or equivalently, $
		(\lambda^{-1})\id{^\mu_\nu}
		= \lambda\id{_\nu^\mu}
	$. Therefore,
	\begin{equation}
		\phi'(x^\mu) = \phi(\lambda^{-1}\circ x^\mu)
		= \phi(x^\nu\lambda\id{_\nu^\mu})
	\end{equation}
\pagebreak[3]

	\item Under $
		x'^\mu = \lambda\id{^\mu_\nu} x^\nu
%		,\ %
%		\phi(x)\mapsto\phi'(x)
	$, we have:
	\begin{equation}
	\begin{aligned}
		\mcal{L}'(x')
		&= - \frac{1}{2}\,
			\pd'^\mu\phi'(x')\,
			\pdd{\mu}'\phi'(x')
		- \frac{1}{2}\,m^2\phi'^2(x') \\
		&= - \frac{1}{2}\,
			\pd'^\mu\phi(x)\,
			\pdd{\mu}'\phi(x)
		- \frac{1}{2}\,m^2\phi^2(x) \\
		&= - \frac{1}{2}\,
			\eta^{\mu\nu}
			\pdv{x^\rho}{x'^\mu}\,
			\pdd{\rho}\phi(x)\,
			\pdv{x^\sigma}{x'^\nu}\,
			\pdd{\sigma}\phi(x)
		- \frac{1}{2}\,m^2\phi^2(x) \\
		&= - \frac{1}{2}\,
			\eta^{\rho\sigma}
			\pdd{\rho}\phi(x)\,
			\pdd{\sigma}\phi(x)
		- \frac{1}{2}\,m^2\phi^2(x) \\[.5ex]
		&= \mcal{L}(x)
	\end{aligned}
	\end{equation}
	Here we've used $
		\eta^{\mu\nu}
		\pdv{x^\rho}{x'^\mu}\,
		\pdv{x^\sigma}{x'^\nu}
		= \eta^{\mu\nu}
			\lambda\id{_\mu^\rho}
			\lambda\id{_\nu^\sigma}
		= \eta^{\rho\sigma}
	$. Furthermore, $
		S' = \int \dd[4]{x} \mcal{L}'(x)
		= \int \dd[4]{x'} \mcal{L}'(x')
		= \int \dd[4]{x'} \mcal{L}(x)
		= \int \dd[4]{x} \mcal{L}(x)
		= S
	$, hence the action is invariant under Lorentz transformation.

	\item Consider an infinitesimal Lorentz transformation: $\lambda \sim \idty + \omega$, then $
		\eta_{\mu\nu}
			\lambda\id{^\mu_\rho}
			\lambda\id{^\nu_\sigma}
		= \eta_{\rho\sigma}
	$ implies that $\omega_{\mu\nu}$ is anti-symmetric: $
		\omega_{\mu\nu} + \omega_{\nu\nu} = 0
	$. For $
		\var{x}^\mu
		= \omega\id{^\mu_\nu} x^\nu
	$, we have:
	\begin{equation}
		\var{\phi} = - \pdv{\phi}{x^\mu}
			\var{x}^\mu
		= - \omega\id{^\mu_\nu} x^\nu\,
			\pdd{\mu}\phi
%		= - \omega_{\rho\sigma} x^\sigma\,
%			\pd^\rho \phi
	\end{equation}

	To obtain the corresponding Noether charges, we can simply repeat the operations done in our previous problem; alternatively, we can try to derive a general recipe\footnote{
		References: \arxiv{1601.03616} and \textit{Tong:} \url{http://damtp.cam.ac.uk/user/tong/qft.html}
	}: for $
		\mcal{L} = \mcal{L}(\phi,\pdd{\mu}\phi)
	$ and $
		S = \int \dd[4]{x} \mcal{L}
	$, we have:
	\begin{equation}
	\begin{aligned}
		\var{S}
		&= \int\dd[4]{x} \var{\mcal{L}} \\
		&= \int\dd[4]{x} \pqty{
			\pdv{\mcal{L}}{\phi} \var{\phi}
			+ \pdv{\mcal{L}}{(\pdd{\mu}\phi)}
				\var{\pdd{\mu}\phi}
		} \\[.5ex]
		&= \int\dd[4]{x} \pqty{
				\pdv{\mcal{L}}{\phi}
				- \pdd{\mu}
				\pdv{\mcal{L}}{(\pdd{\mu}\phi)}
			} \var{\phi}
		+ \int\dd[4]{x}
			\pdd{\mu} \pqty{
				\pdv{\mcal{L}}{(\pdd{\mu}\phi)}
				\var{\phi}
			}
	\end{aligned}
	\end{equation}
	If we vary $S$ w.r.t.\ a symmetry of the system, we will have $\var{\mcal{L}} = \pdd{\mu} K^\mu$ some total derivative; when on-shell, such variation gives the conserved current with boundary term $K^\mu$:
	\begin{equation}
		j^\mu
		= \pdv{\mcal{L}}{(\pdd{\mu}\phi)}
			\var{\phi} - K^\mu
	\end{equation}

	Back to our Lorentz transformation $
		\var{\phi}
		= -\omega\id{^\mu_\nu} x^\nu\pdd{\mu}\phi
	$, we have symmetry variation:
	\begin{equation}
		\var{\mcal{L}}
		= - \omega\id{^\mu_\nu} x^\nu
			\pdd{\mu} \mcal{L}
		= - \pdd{\mu} \pqty{
			\omega\id{^\mu_\nu} x^\nu
			\mcal{L}
		}
	\end{equation}
	This gives a boundary term $
		K^\mu = -\omega\id{^\mu_\nu} x^\nu \mcal{L}
	$, and the Noether current and its corresponding conserved charge can be calculated as follows:
	\begin{gather}
		j^\mu = -\omega\id{^\sigma_\nu} x^\nu
		\pqty{
			\pdv{\mcal{L}}{(\pdd{\mu}\phi)}
				\,\pdd{\sigma} \phi
			- \delta^\mu_\sigma \mcal{L}
		},\\[1ex]
		Q = \int \dd[3]{x} j^0
		= - \omega\id{^\sigma_\nu} \int \dd[3]{x}
		x^\nu \pqty{
			\pdd{0}\phi\,\pdd{\sigma}\phi
			- \delta^0_\sigma \mcal{L}
		},
	\end{gather}

	Note that $\omega\id{^\mu_\nu}$ is arbitrary, therefore $Q$ can be decomposed into independent charges:
	\begin{equation}
		Q = \omega_{\mu\nu} M^{\mu\nu},\quad
		M^{\mu\nu}
		= - \int \dd[3]{x}
		x^{[\mu} \pqty{
			\pdd{0}\phi\,\pd^{\nu]}\phi
			- \eta^{\nu] 0} \mcal{L}
		},
	\end{equation}
	The indices of $M^{\mu\nu}$ are anti-symmetrized to match the degrees of freedom in $\omega_{\mu\nu}$. Note that the $\mcal{L}$ term only appears when one of the indices is 0.

	Canonical quantization:
	\begin{gather}
		\dot{\phi} = \pdd{0}\phi,\quad
		\Pi = \pdv{\mcal{L}}{\dot{\phi}}
		= \dot{\phi},\quad
		[\phi(\vb{x}),\Pi(\vb{y})]
		= [\phi,\dot{\phi}](\vb{x})
		= i\delta(\vb{x} - \vb{y})
	\end{gather}
	Other equal-time commutators between $\phi,\Pi$ all just vanish. We have:
	\begin{equation}
		M^{0i} = -M^{i0}
		= -\frac{1}{2}\,
		\int \dd[3]{x} \pqty{
			\dot{\phi}\,\pqty{
				x^0 \pd^i
				- x^i \pd^0
			}\,\phi
			+ x^i \mcal{L}
		},\\
		M^{ij}
		= -\frac{1}{2}\,\int \dd[3]{x}
			\dot{\phi}\,\pqty{
				x^i \pd^j
				- x^j \pd^i
			}\,\phi
	\end{equation}

	Notice that $
		x^{[\mu} \pd^{\nu]}
		= \frac{1}{2}\,\pqty{
			x^\mu \pd^\nu - x^\nu \pd^\mu
		} = \frac{1}{2} D^{ij}
	$ is the Killing vector fields of $\mbb{R}^{3,1}$, hence they naturally follow the commutation relations of $\mfrak{so}(3,1)$ (up to a constant coefficient)\footnote{
		I would like to thank \textit{林般} for pointing this out. 
	}. We have:
	\begin{equation}
	\begin{aligned}
		[M^{ij}, M^{kl}]
		&= \frac{1}{4}\,\int \dd[3]{x}
			\int \dd[3]{y} \bqty{
				\dot{\phi} D^{ij}\phi(x),
				\dot{\phi} D^{kl}\phi(y)
			} \\
		&= \frac{1}{4}\,\int \dd[3]{x}
			\dot{\phi}\,\bqty{
				 D^{ij}, D^{kl}
			}\,\phi
	\end{aligned}
	\end{equation}
	Similar holds for $M^{i0}$. Therefore, $M^{\mu\nu}$'s indeed form the Lie algebra $\mfrak{so}(3,1)$. 
	\qedfull

	\end{itemize}

\printbibliography[%
%	title = {参考文献} %
	,heading = bibintoc
]
\end{document}

### 2020-10-06 HW-AdvancedQFT2020/gauge/gauge.tex
Restructure to gather quick notes

% !TeX document-id = {b5392a94-51a3-49d1-9ba5-698bc09f9d35}
% !TeX encoding = UTF-8
% !TeX spellcheck = en_US
% !TeX TXS-program:bibliography = biber -l zh__pinyin --output-safechars %

\documentclass[a4paper,11pt]{article}

\newcommand{\hwNumber}{Final}

\input{../advqft_preamble.tex}
\input{../.modules/basics/biblatex.tex}

\title{The Geometry of Gauge Fields}
\addbibresource{gauge.bib}

%%% ID: sensitive, do NOT publish!
\InputIfFileExists{../id.tex}{}{}
\usepackage{cancel}

\begin{document}
\maketitle
\pagestyle{headings}
\pagenumbering{arabic}
\thispagestyle{empty}

%\vspace*{-1.5\baselineskip}

\setlength{\parskip}{.1\baselineskip}
\tableofcontents
\setlength{\parskip}{\parskipnorm}

\section{Introduction}
	A common way to introduce gauge fields in a non-gauge system is by promoting some global symmetry to a local one. For example, consider some fundamental matter with $\mrm{SU}(N)$ global symmetry, and we have: 
	\begin{equation}
		\mcal{L}
		= -\bar{\psi} \gamma^\mu \pdd{\mu} \psi
		\quad\longmapsto\quad
			-\bar{\psi} \gamma^\mu D_\mu \psi,
		\quad
			D_\mu = \pdd{\mu} + A_\mu
	\end{equation}
	The $\mrm{SU}(N)$ gauge potential $A_\mu$ arises naturally as a \textit{connection}, and $D_\mu$ serves as the \textit{covariant derivative}, such that the Lagrangian is manifestly invariant under the local $\mrm{SU}(N)$ symmetry. This is very much similar to the geometry of general relativity; in fact, the notion of \textit{curvature} as a geometric invariant generalizes nicely in this framework, leading to the definition of the gauge-invariant field strength:
	\begin{equation}
		F_{\mu\nu} = [D_\mu,D_\nu]
	\end{equation}

	However, such na\"ive analogy between gauge theory and relativity has its limitation, since gravity itself is only a very special example of gauge theory. In general, the matter fields in a gauge theory may live on some non-trivial fiber over the base manifold, while in gravity the basic fiber is simply the tangent space of the base manifold. Therefore, for a generic gauge theory, it is helpful to look at the more general mathematical structure — a \textit{vector bundle}, to better understand the geometry of gauge theory.

	This note aims to provide a minimal introduction to the basic pictures of vector bundles and its applications in gauge theory. We will try to capture the basic concepts  in a less rigorous manner, without getting lost in the realm of definitions. Our main references are \textit{Baez \& Muniain} \cite{baez1994gauge}, \textit{Marsh} \cite{Marsh:2016hdj}, \textit{Göckeler \& Schücker} \cite{gockeler1989differential} and \textit{Nakahara} \cite{Nakahara:2003nw}. 
\section{Basics of Bundles}
\subsection{Vector Bundle}
	A \textit{fiber bundle} $E$ is a ``bundle'' of identical fibers $\{E_p \,|\, E_p\cong F\}_{p\in M}$ with smooth projections down to the base manifold $\pi\colon E\to M$. When the fiber is a vector space, it is then a vector bundle.

	\begin{figure}[!ht]
	\centering
	\includegraphics[width=.3\linewidth]{img/bundle_construct.png}
	\caption{Building a bundle out of trivial bundles; image borrowed from \cite{baez1994gauge}. }
	\label{fig:bundle_construct}
	\end{figure}

	As is common in differential geometry, such object can be constructed by gluing some trivial parts together; in this case it is some simple product spaces $\{U \times F \,|\, U \subset E\}$ with overlaps, as is shown in \autoref{fig:bundle_construct}. This is the \textsc{vector bundle construction theorem}. However, we have to make sure that such gluing is compatible between patches, without producing some nasty singularities. This can be achieved by imposing consistency conditions on \textit{transition functions} \cite{baez1994gauge,Nakahara:2003nw} between patches.

	More specifically, consider the \textit{local trivialization} $\Phi\colon \pi^{-1}(U)\to U\times F$ that realizes the identification of some region $\pi^{-1}(U)\in E$ to the product space $U \times F$. This, in effect, specifies a coordinate patch on $\pi^{-1}(U)$. Coordinate transformations between patches are then given by the transition function:
	\begin{equation}
		\Phi_U\circ\Phi_V^{\smash{-1}}
			\big|_p
		= g_{UV} (p),\quad
		g_{UV}
		\in \mrm{GL}(n,\mbb{C})
		= \mop{End} F
	\end{equation}
	For a tangent bundle, $g_{UV}$ is precisely the \textit{Jacobian matrix} between different coordinates. Here $\mquote{g}$ stands for \textit{gauge}, not to be confused with the metric tensor.

	Note that transition functions form a representation of some group $G$ on the fiber $F$:
	\begin{equation}
		g_{UV}(p)
		\in G \subset \mop{End} F
	\end{equation}
	The compatibility between patches is further ensured by the \textit{cocycle condition}: $
		g_{UV}
		\circ g_{VW}
		\circ g_{WU} = \idty
	$. Sometimes it is possible to restrict the type of transitions between patches to a subgroup of $\mrm{GL}(n,\mbb{C})$, which leads to additional structure of the vector bundle; for example, restriction to $G = \mrm{O}(3)$ means that there is a consistently defined \textit{metric} on the bundle.

	In the mathematics literature, $G$ is commonly referred to as the \textit{structure group} \cite{lee2012introduction}; however, in a physicist's point of view, this is precisely the \textit{gauge group} \cite{baez1994gauge}. Gauge transformations are then reduced to coordinate transformations on the bundle, which are different descriptions of the same geometry. This is in agreement with physics, where different gauges are only different descriptions, leading to the same physical result. 
\subsection{Principal Bundle}
	In general, it is possible to remove all unnecessary data of a vector bundle, leaving only the information of how it transitions between patches. This gives the so-called \textit{principal bundle}. Intuitively, we can extract a principal bundle $P$ from a vector bundle, by replacing each of its fiber with the gauge group $G$ itself. Then the transition between patches is simply a usual group multiplication on $G$.

	All gauge transformations are then encoded in the transitions between local sections of the principal bundle. It is then straight-forward to reconstruct the \textit{associated vector bundle} from the principal bundle, where the fiber $F$ serves as a point-wise representation of the gauge group $G$. Different choices of the $G$-representation $F$ corresponds to different types of matter $\psi$, which gets coupled to the gauge potential.

	In fact, the connection on the associated vector bundle can be induced from the connection on the principal bundle, as we shall see below. 
\section{Connection and its Applications}
\subsection{Connection on the Vector Bundle}
	To introduce a connection on the vector bundle, consider a set of frame fields $\{e_i\}_{i = 1}^n$ which spans $F$ at each point $p$. For a trivial bundle $M\times F$ with a parallel-transported $\{e_i\}$, we would expect $D_\mu e_i = 0$; however, for a non-trivial bundle, or even a trivial bundle with non-parallel $\{e_i\}$, we should expect ``twists'' on the ``vertical'' fiber direction.

	For example, consider the world-volume of the comoving frame $\{e_i\}$ of a spinning top; it forms a trivial vector bundle based on the worldline $\mbb{R}$, however $D_\mu e_i \ne 0$ due to the non-trivial spinning $\{e_i\}$. Such ``twists'' would lead to a non-trivial connection:
	\begin{equation}
		D_\mu e_j
		= A^i_{\mu j} e_i
		= A^a_\mu\,\pqty{T_a}\id{^i_j} e_i,
	\quad
		A^i_{\mu j}
		= A^a_\mu\,\pqty{T_a}\id{^i_j}
	\end{equation}
	A visualization of the fiber structure is shown in \autoref{fig:vertical_derivative}. 
	This is very much similar to basic differential geometry, where we have $e_\mu = \pd_\mu$ in place of $e_i$, and $A^i_{\mu j}$ becomes the Levi-Civita connection $\Gamma^\lambda_{\mu\nu}$.

	\begin{figure}[!ht]
	\centering
	\includegraphics[width=.85\linewidth]{img/vertical_derivative.png}
	\caption{Illustration of a fiber bundle, with vertical field space and horizontal spacetime. This image also shows some additional structure: if we include ``descendants'' fields such as $
		\pdd{\mu}\psi,\,\pdd{\mu}\pdd{\nu}\psi,\cdots
	$ in the fiber, then we have a \textit{jet bundle}, which is useful in the study of Noether's theorem and conserved charges. This image is borrowed from \cite{Compere:2018aar}. }
	\label{fig:vertical_derivative}
	\end{figure}

	The ability to split $
		A^i_{\mu j}
		= A^a_\mu\,\pqty{T_a}\id{^i_j}
	$ relies on our discussion from the last section: there is only one true connection given the gauge structure of the vector bundle, and that is the connection on the principal bundle. All other connections are then induced from the connection on the principal bundle, labeled by the representation $\pqty{T_a}\id{^i_j}$. It is then convenient to write $A_\mu = A^a_\mu\,T_a$, with the $i,j,\cdots$ indices suppressed. Alternatively, since $T_a$ belongs to the Lie algebra $\mfrak{g} = \mop{Lie} G$, we can think of $A_\mu$ as a $\mfrak{g}$-valued function.

	We can then derive the gauge transformation of $A_\mu$, by comparing with the usual Levi-Civita connection. Recall that under a coordinate transformation $x^\mu \to x'^{\mu'}$, we have:
	\begin{equation}
	\begin{aligned}
		{\Gamma'}^{\lambda'}_{\mu'\nu'}
		&= \dd{x'^{\lambda'}}
			\nabla'_{\mu'}
			e'_{\nu'},
		\quad
			e'_{\nu'}
			= \pdv{x'^{\nu'}}
			= \pdv{x^\nu} \pdv{x^\nu}{x'^{\nu'}}
			= e_\nu \pdv{x^\nu}{x'^{\nu'}},
		\\[.5ex]
		&= \pdv{x'^{\lambda'}}{x^\lambda}\,
			\Gamma^{\lambda}_{\mu\nu}\,
			\pdv{x^\mu}{x'^{\mu'}}
			\pdv{x^\nu}{x'^{\nu'}}
			+ \dd{x'^{\lambda'}} e_\nu\,
				\pdv{x'^{\mu'}}
				\pdv{x^\nu}{x'^{\nu'}}
		\\[.5ex]
		&= \pqty\bigg{\pdv{x'^{\lambda'}}{x^\lambda}}\,
			\Gamma^{\lambda}_{\mu\nu}\,
			\pdv{x^\mu}{x'^{\mu'}}
			\pqty{\pdv{x^\nu}{x'^{\nu'}}}
			+ \pqty\bigg{\pdv{x'^{\lambda'}}{x^\lambda}}\,
				\delta^\lambda_\nu\,
				\pdv{x'^{\mu'}}
				\pqty{\pdv{x^\nu}{x'^{\nu'}}}
	\end{aligned}
	\end{equation}
	We can repeat the same process but with a gauge transition Jacobian $g\id{^{i'}_{i}}$ in place of $
		\pdv{x'^{\lambda'}}{x^\lambda}
	$, while keeping the $\mu$ index fixed; this gives:
	\begin{equation}
		A'_\mu
		= g A_\mu g^{-1}
			+ g\,\pdd{\mu} (g^{-1})
	\end{equation}
	Consider the abelian case where $g = e^{-\lambda(x)}$, then this reduces to the usual electromagnetic gauge transformation: $A' = A + \dd{\lambda}$. It is then easy to verify the gauge covariance of $D_\mu$:
	\begin{equation}
		D'_\mu
		= \pdd{\mu}
			+ g A_\mu g^{-1}
			+ g\,\pdd{\mu} (g^{-1})
		= g\circ D_\mu \circ g^{-1}
	\end{equation}
\subsection{Holonomy}
	With the notion of connection, it is then possible to discuss \textit{parallel transport} in a more precise language. In fact, parallel transport of $\psi = \psi(t)$ along a curve $\gamma(t)$ is given by the familiar equation:
	\begin{gather}
		\pqty{\gamma'(t)}^\mu D_\mu \psi(t)
		= \pqty{
				\dv{t} + A\pqty{\gamma'(t)}\!
			}\,\psi(t)
		= 0,\\
		A\pqty{\gamma'(t)}
		= A_\mu \dd{x^\mu}
			\pqty{\gamma'^\nu \pdd{\nu}}
		= \gamma'^\mu A_\mu,
	\end{gather}
	This first order differential equation can be solved perturbatively, just as we did for the Schr\"odinger equation. Instead of time ordering, the result is written formally as the \textit{path-ordered exponential}:
	\begin{equation}
		H_\gamma = \mcal{P} \exp \Bqty{
				- \int_0^t A\pqty{\gamma'(t)} \dd{t}
			}
		= \mcal{P} e^{-\int_\gamma A},
		\quad
			\psi(t) = H_\gamma \psi(0)
	\end{equation}

	This is the expression that we acquired when studying Dirac's monopole \cite{Sakurai:2011zz}: if the gauge group $G$ is abelian, then the path ordering has no effect, and we have:
	\begin{equation}
		\psi(t)
		= e^{-\int_\gamma A} \psi(0),
		\quad
			A = A_\mu \dd{x^\mu}
	\end{equation}
	which describes the phase acquired by a charged particle as it moves along a path through a magnetic field. To restore the usual convention in electromagnetism, we should replace $A\mapsto ieA$, and we can see that it is indeed the familiar phase factor.

	$H_\gamma$ as a linear map from $E_0$ to $E_p$ is called the \textit{holonomy} along the path $\gamma$. By applying gauge transformation to the parallel transport equation, we can verify that $H_\gamma$ transforms nicely under $g$:
	\begin{equation}
		H_\gamma(D')
		= g_t H_\gamma(D)\, g^{-1}_0,
		\quad
			g_t = g(p)|_{p = \gamma(t)},
		\quad
			D' = \pd + A'
	\end{equation}
	But for non-abelian $G$, $H_\gamma$ is not exactly gauge invariant. However, if $\gamma$ is a loop: $\gamma(T) = \gamma(0)$, then $\Tr H_\gamma$ is gauge-invariant. This gives the famous \textit{Wilson loop}:
	\begin{equation}
		W_\gamma
		= \Tr H_\gamma
		= \Tr \mcal{P} e^{-\int_\gamma A}
	\end{equation}

	Finally, recall that in differential geometry, curvature is basically holonomy along a small loop; more specifically, we have:
	\begin{equation}
		H_\gamma
		= 1 - \epsilon^2 F_{\mu\nu}
	\end{equation}
	Where $\gamma$ is a small square in the $x^\mu$--$x^\nu$ plane with a size of $\epsilon^2$. The proof of this in the context of vector bundles is identical to that in differential geometry, see e.g.~\cite{carroll_2019}. In fact, it is natural to motivate the abstract definition of curvature using this relation. 
\subsection{Curvature}
	As is mentioned before, it is straight-forward to generalize the Riemannian curvature on a vector bundle; we have:
	\begin{equation}
		F(u,v)
		\equiv [D_u\,,D_v] - D_{[u,v]},
	\end{equation}
	It is illuminating to rewrite this in terms of differential forms:
	\begin{gather}
		\pqty{F_{\mu\nu}}\id{^i_j}
		= e^i \,\pqty{2 D_{[\mu} D_{\nu]}}\, e_j,
	\\[.5ex]
	\begin{aligned}
		e^i D_\mu D_\nu e_j
		&= D_\mu \pqty{e^i D_\nu e_j}
			- (D_\mu e^i)(D_\nu e_j) \\
		&= \pdd{\mu} A^i_{\nu j}
			- (-A^i_{\mu k} e^k)
				(A^\ell_{\nu j} e_\ell) \\
		&= \pdd{\mu} A^i_{\nu j}
			+ A^i_{\mu k} A^k_{\nu j},
	\end{aligned}
	\\
		F
		= \frac{1}{2}\,F_{\mu\nu}
			\dd{x^\mu} \wedge \dd{x^\nu}
		= \pqty\Big{
				\pdd{[\mu} A_{\nu]}
				+ A_{[\mu} A_{\nu]}
			} \dd{x^\mu} \wedge \dd{x^\nu}
		= \dd{A} + A\wedge A
	\end{gather}

	In fact, this result is none other than \textit{Cartan's (second) structural equation} in differential geometry \cite{gockeler1989differential,liangcanbin2006relativity}. It is more commonly written as $
		\Omega
		= \dd{\omega} + \omega\wedge\omega
	$ in mathematics literature. Again, if we have $e_i\mapsto e_\lambda = \pd_\lambda$, we recover the Riemann curvature $
		\pqty{F_{\mu\nu}}\id{^i_j}
		\mapsto R\id{^\lambda_{\sigma\mu\nu}}
	$.

	The Lagrangian is then constructed from the gauge-invariant, local field strength. This is when we see the difference between gravity and a generic, Yang--Mills theory. In gravity, all 4 indices of the field strength are spacetime indices, therefore we can construct a scalar curvature by tracing over indices: 
	\begin{equation}
		\mcal{L}
		\quad\sim\quad
			R
			= R\id{^\sigma_\sigma}
			= g^{\sigma\nu} R\id{^\mu_{\sigma\mu\nu}}
		\pagebreak
	\end{equation}
	Note that the metric $g_{\mu\nu}$ itself is also a dynamic field in gravity, resulting in a non-trivial base manifold $M$. On the other hand, in a generic Yang--Mills theory, it is impossible to construct a $\order{F}$ Lagrangian, since we only have 2 anti-symmetric spacetime indices, and 2 fiber indices. The only choices are then of $\order{F^2}$, for example,
	\begin{equation}
		\mcal{L}
		\quad\sim\quad
			\Tr \pqty{F\wedge\star F},\quad
			\Tr \pqty{F\wedge F},\quad
			\cdots
	\end{equation}
\section{Tetrad Formalism of Gravity}
	Although we've seen that the dynamics of gravity is very different from a generic Yang--Mills theory, the formalism we've introduced is, in fact, very useful in the study of gravity. As a postlude, we would like to introduce the \textit{tetrad formalism}, which is just an application of what we've learned, in the context of gravity.

	First note that a feature of the connection on a vector bundle is that we can choose any set of frame fields $\{e_i\}$ as the basis, as long as they span the fiber $E_p \cong F$ at each point $p$. In particular, we can choose a set of orthonormal frames $\{e_a\}$, with its dual basis $\{e^a = e_a^\sharp\}$. For $E = \mrm{T}M$ the tangent bundle, such choice of basis gives the \textit{spin connection} \cite{Compere:2018aar}:
	\begin{equation}
		\omega^a_{\mu b}
		= e^a \cdv{\mu} e_b,
	\quad
		\omega^c_{a b}
		= e^c e_a^\mu \cdv{\mu} e_b
		= e^c_\lambda e_a^\mu \,\pqty{
				\pdd{\mu} e_b^\lambda
				+ e_b^\nu \Gamma^\lambda_{\mu\nu}
			}
	\end{equation}
	$\{e^a\}$ is usually called a \textit{tetrad} or a \textit{vierbein}\footnote{
		Note that technically these words are only valid for frame fields in 4 dimensions, since ``tetrad'' means ``a set of four'', and ``vierbein'' is German for ``four-legged''. 
	}. The tetrad indices $a,b,\cdots$ are raised or lowered using the flat metric $\eta_{ab}$.

	The spin connection seems like a rewrite of Levi-Civita connection; however, it is essential when dealing with \textit{spinors} in spacetime \cite{gockeler1989differential}. Note that by considering orthonormal frames, we have restricted:
	\begin{equation}
		\omega_\mu
		\in \mfrak{so}(3,1)\cong \mfrak{spin}(3,1)
	\end{equation}
	The isomorphic Lie algebras imply that $\omega_\mu$ is not only a connection for the $G = \mrm{SO}(3,1)$ gauge group, but also one for the \textit{spinor bundle} with $G = \mrm{Spin}(3,1)$, if such structure exists.

	In 3D spacetime, another interesting thing happens that further relates gravity and gauge theory\footnote{
		Actually, many other interesting things happen in 3D that we are not able to discuss here, including gauge/gravity duality. 
	}. As is mentioned before, gravity is different from an usual Yang--Mills gauge theory; however, it is possible to reformulate 3D gravity into a \textit{Chern--Simons} theory using the spin connection \cite{Achucarro:1987vz,Witten:1988hc,Compere:2018aar}. More specifically, we have:
	\begin{equation}
		\omega^a
		\equiv \frac{1}{2} \epsilon^{abc}
			\omega_{bcd} e^d,\quad
		A^a_\pm
		= \omega^a \pm \frac{e^a}{\ell},\quad
		\Lambda = -\frac{1}{\ell^2}
	\end{equation}
	$A_\pm = A^a_\pm T_a$ is a pair of $\mfrak{so}(3,1)$-valued 1-forms, $\epsilon^{abc}$ is the antisymmetric symbol with $\epsilon^{012} = 1$, and $\ell$ is the cosmological scale. Using $A_\pm$, the Einstein--Hilbert action can be rewritten as:
	\begin{equation}
		S \sim \frac{k}{4\pi}
			\int_M \Tr \pqty\big{
				I[A_+] - I[A_-]
			},\quad
		k = \frac{\ell}{4G}
	\end{equation}
	Up to some boundary terms; here the Chern--Simons form $I[A]$ is given by:
	\begin{equation}
		I[A]
		= A \wedge \dd{A}
			+ \frac{2}{3} A\wedge A\wedge A
	\end{equation}

	The Chern--Simons form $I[A]$ can be seen as a remnant of the 4D $\Tr \pqty{F\wedge F}$ action: 
	\begin{equation}
		\Tr \pqty{F\wedge F}
		= \dd{\Tr I[A]}
	\end{equation}
	The meaning of such equivalence between 3D gravity and Chern--Simons remains mysterious to me, and is still an actively studied subject. For more detailed discussions, see e.g.~\cite{Compere:2018aar}. 
\section*{Acknowledgements}
	I would like to thank Prof.~Wenbin Yan and Prof.~Dan Xie for their great teachings in the field theory lectures. I would also like to thank Gu Xia for many inspiring discussions.

\printbibliography[%
%	title = {参考文献} %
	,heading = bibintoc
]
\end{document}

### 2020-10-06 HW-AlgebraicTopology2020/algtop2/algtop2.tex
Restructure to gather quick notes

--- 2020-03-18 AlgebraicTopology2020/algtop3/algtop3.tex
@@
 
-\newcommand{\hwNumber}{3 [WIP]}
+\newcommand{\hwNumber}{2}
 
@@
 %\InputIfFileExists{../id.tex}{}{}
-
-\newcommand{\vset}[1]{\Bqty{\ \begin{gathered}
-	#1
-\end{gathered}\ }}
-\newcommand{\Zpoly}[1]{\mbb{Z}[x]\big/x^{#1}}
-\newcommand{\colim}{\mop{colim}}
 
@@
 	\begin{enumerate}
-	\item \textbf{Example of limit in \Cat{Vect}:}
-	\begin{equation}
-	\begin{tikzcd}[row sep=-3.5ex,column sep=8ex]
-		& \vset{0 \\ \mbb{R}} \\
-		I = \vset{\bullet \\ \star}
-			\arrow[ur,mapsto,%
-				"F"]
-			\arrow[dr,mapsto,swap,%
-				"\Delta(V)" near end]
-		& \\
-		& \vset{V \\ V}
-	\end{tikzcd}
-		\ \supset\ \Cat{Vect}\colon \text{
-			$\mbb{R}$ vector space
-		},
-	\end{equation}
+	\item \textbf{Morphism between coverings is covering:}
 
-	\begin{enumerate}
-	\item By definition, we have:
-	\begin{equation}
-	\begin{tikzcd}[row sep=8.5ex,column sep=7ex]
-		& \Delta(\lim F)
-			\arrow[d,Rightarrow,"\sigma"] \\
-		\Delta(V)
-			\arrow[r,Rightarrow,"\eta"]
-			\arrow[ur,Rightarrow,dashed,%
-				"\exists!\,\Delta(g)"] &
-		F
-	\end{tikzcd}
-	\label{eq:def_limit}
-	\end{equation}
-	Where $g\colon V\to \lim F$. 
-	More intuitively, for the above $F\colon I\to\Cat{Vect}$, this translates to the following diagram in \Cat{Vect}:
-	\begin{equation}
-	\begin{tikzcd}[row sep=2ex,column sep=8ex]
-		&& 0 \\
-		V
-			\arrow[r,dashed,
-				"\exists!\, g"]
-			\arrow[urr,bend left,%
-				"\eta_\bullet"]
-			\arrow[drr,bend right,swap,%
-				"\eta_\star"] &
-		\lim F
-			\arrow[ur,%
-				"\sigma_\bullet"]
-			\arrow[dr,swap,%
-				"\sigma_\star"] & \\
-		&& \mbb{R}
-	\end{tikzcd}
-	\label{eq:lim_in_vect}
-	\end{equation}
-	\end{enumerate}
-
-	Now we verify that $\lim F = \mbb{R}$, along with the following choice of $\sigma$:
-	\begin{equation}
-		\sigma_\bullet = 0,\quad
-		\sigma_\star = \idty_\mbb{R}
-	\end{equation}
-	In fact, for the above diagram \eqref{eq:lim_in_vect} to be commutative, we must have $g = \eta_\star$.
-Note that such $g$ is unique once $\sigma$ is chosen; for our choice of $\sigma$, if $g \ne \eta_\star$, then the diagram \textit{cannot} commute.
-Hence $\lim F = \mbb{R}$, along with the above choice of $
-		\sigma\colon \Delta(\mbb{R})\Rightarrow F
-	$. In other words, we have:
-	\begin{equation}
-	\begin{tikzcd}[row sep=1ex,column sep=2.5em]
-		& \Bqty\big{\ \bullet,\ \star\ }
-			\arrow[ddl,"\Delta(\mbb{R})",swap]
-			\arrow[ddr,"F"]
-		& \\
-		& \xRightarrow{\quad\sigma\quad} & \\
-		\mbb{R} & & \Bqty\big{\ 0,\ \mbb{R}\ }
-	\end{tikzcd}
-	\end{equation}
-	\vspace{-2.25\baselineskip}
-
-	\qed
-
-	\item[(b)(c)] From diagram \eqref{eq:def_limit} and discussions in (a), we know that: 
-	\begin{equation}
-		\exists\,!\ \tau = \Delta(g)\colon\ %
-		\Delta(V)\Longrightarrow \Delta(\mbb{R})
-	\end{equation}
-	Here $g\colon V\to\mbb{R}$ is fixed uniquely once $\sigma$ is fixed. However, $\sigma$ may vary up to isomorphism; therefore, a generic choice of $\sigma$ is given by:
-	\begin{equation}
-		\sigma_\bullet = 0,\quad
-		\sigma_\star = k\,\idty_\mbb{R},\quad
-		k\in\mbb{R}
-	\end{equation}
-
-	For such $g$, by the same arguments in (a), we have:
-	\begin{equation}
-		\exists\,!\,\ %
-			g = \frac{1}{k}\,\eta_\star\,,\ %
-			\tau
-			= \Delta(g)
-			= \frac{1}{k}\,\Delta(\eta_\star),\quad
-		\textsl{s.\,t.\quad
-			\eqref{eq:def_limit},
-			\eqref{eq:lim_in_vect} commutes}
-	\end{equation}
-	Note that $k\in\mbb{R}$, for every $k$ there is a different $g$ and $\tau$; hence there are $
-		\norm{\{k\}} = \norm{\mbb{R}}
-	$ many choices of $\tau$ to make the diagram commute. In particular, for $k = 1$ we recover $
-		\tau = \Delta(\eta_\star)
-	$. \qedfull
-
-	\item \textbf{Limit and colimit of polynomial ring:}
-
-	By definition,
-	\begin{equation}
-	\begin{tikzcd}[row sep=7ex,column sep=8ex,baseline=-.8ex]
-		&&[-4ex] Q
-			\arrow[ddll]
-			\arrow[ddl,"\eta_{n+1}" near end,swap]
-			\arrow[ddr,"\eta_{n}" near end]
-			\arrow[ddrr]
-			\arrow[ddrrr]
-			\arrow[d,dotted,"\exists! f" description]
-		&[-4ex] && \\
-		&& \lim F
-			\arrow[dl,"\pi_{n+1}"]
-			\arrow[dr,"\pi_{n}",swap]
-		&&& \\
-		\cdots
-			\arrow[ddrr]
-			\arrow[r,"p_{n+1}"] &
-		\Zpoly{n+1}
-			\arrow[dr,"\sigma_{n+1}"]
-			\arrow[ddr,
-				"\tau_{n+1}\!" near start,swap]
-			\arrow[rr,"p_n"] 
-		&&
-		\Zpoly{n}
-			\arrow[dl,"\sigma_{n}",swap]
-			\arrow[ddl,
-				"\tau_{n}" near start]
-			\arrow[r,"p_{n-1}"] &
-		\cdots
-			\arrow[ddll]
-			\arrow[r,"p_1"] &
-		\Zpoly{1} = \mbb{Z}
-			\arrow[ddlll,
-				"\tau_1" near start] \\
-		&& \colim F
-			\arrow[d,dotted,"\exists! g" description]
-		&&& \\
-		&& R
-		&&&
-	\end{tikzcd}
-	\label{eq:polynomial_ring_tower}
-	\end{equation}
-	Here $p_n\colon\Zpoly{n+1}\to\Zpoly{n}$ is the natural projection.
-
-	Intuitively, if such $\lim F$ exists, it shall be the ``smallest'' object that ``contains'' $\Zpoly{n}$ when $n\to\infty$. Note that $\Zpoly{n}$ is naturally a $\mbb{Z}^n$ vector space:
-	\begin{equation}
-		\Zpoly{n}\ \ni\ \sum_{m=0}^{n-1} a_m x^m
-		\ \sim\ \pqty{
-			a_0, a_1, \cdots, a_{n-1}
-		}\ \in\ \mbb{Z}^n
-	\end{equation}
-	While $n\to\infty$, this gives an $\infty$--tuple which corresponds to the \textit{formal power series}\footnote{
-		See \wikiref{https://en.wikipedia.org/wiki/Formal\_power\_series}{Formal power series}.
-This is in fact the \textit{adic completion} of $\mbb{Z}[x]$.
-I would like to thank \mbox{\textit{刘逸华}} \& \textit{谢贤进} for this hint.
-	}: 
-	\begin{equation}
-		\mbb{Z}[[x]] \ \ni\ \sum_{m=0}^\infty
-			a_m x^m
-	\end{equation}
-
-	The difference between $\mbb{Z}[x]$ and $\mbb{Z}[[x]]$ is that the latter may contain infinite series while the former may not.
-Now we confirm that, indeed, $\lim F = \mbb{Z}[[x]]$, along with natural projections $
-		\pi_n\colon\mbb{Z}[[x]]\to\Zpoly{n}
-	$.
-
-	In fact, the $f\colon R\to \lim F$ in \eqref{eq:polynomial_ring_tower} can be explicitly written down as:
-	\begin{equation}
-	\begin{aligned}
-		f &= \eta_1 + x\,\pqty{
-			\dv{x}\,\eta_2
-		} + x^2\,\pqty{
-			\frac{1}{2}\,\dv{x}\,\eta_3
-		} + \cdots
-		= \sum_{m=0}^\infty x^m\,\Bqty{
-			\frac{1}{m!}\,\dv[m]{x}\,\eta_{m+1}
-		} \\
-		&\sim \pqty\big{
-			\eta_{1,0},\,
-			\eta_{2,1},\,
-			\cdots,\,
-			\eta_{n,n-1},\,
-			\cdots
-		}
-	\end{aligned}
-	\end{equation}
-	Here $\frac{1}{m!}\,\dv[m]{x}$ is used to extract the $a_{n-1}$ coefficient in $\Zpoly{n}$; this is the last component of $\eta_n$, denoted by $\eta_{n,n-1}$.
-Any other choice of $f$ will break communitativity of \eqref{eq:polynomial_ring_tower}, hence $f$ is fixed uniquely by $\mbb{Z}[[x]]$ and $\pi_n$'s.
-Therefore, $\lim F = \mbb{Z}[[x]]$.
-\qed
-
-	On the other hand, $\colim F$ is the ``largest'' object that any map \textit{out of} $\Zpoly{n}$ must ``passes through''. Also, this should hold for all $n\in\mbb{Z}_+$. Naturally, projections $
-		\sigma_n\colon\Zpoly{n}\to\mbb{Z}
-	$ satisfy the above requirements; we have:
-	\begin{gather}
-		\sigma_n\colon\ x\longmapsto 0,\quad
-			\sum_{m=0}^{n-1} a_m x^m
-			\longmapsto a_0,\\
-		\sigma_{n+1}
-		= p_1\circ p_2\circ\cdots p_n
-	\end{gather}
-	$g\colon \mbb{Z}\to R$ in \eqref{eq:polynomial_ring_tower} is fixed uniquely for such choice of $\sigma_n$; in fact, descend along the $p_n$ tower in \eqref{eq:polynomial_ring_tower}, and we have: $
-		\tau_{n+1}
-		= \tau_n\circ p_n
-		= \tau_{n-1}\circ p_{n-1}\circ p_n
-		= \cdots
-		= \tau_1\circ p_1\circ p_2\circ\cdots p_n
-		= \tau_1\circ \sigma_{n+1},
-		\ \forall\ n\in\mbb{Z}_+
-	$, hence $\exists\,!\ g = \tau_1$. Therefore, $\colim F = \mbb{Z}$. \qed
-
-	\item
-
-	\end{enumerate}
-
-	\legacyReference
-
-	\begin{enumerate}
-	\item For $F_i \to E_i \xrightarrow{p_i} B$: coverings in $\mop{Cov}_0(B)$ with $E_i$: connected and $B$: path connected and locally path connected, the following diagram commutes:
+	For $F_i \to E_i \xrightarrow{p_i} B$: coverings in $\mop{Cov}_0(B)$ with $E_i$: connected and $B$: path connected and locally path connected, the following diagram commutes:
 	\begin{center}

### 2020-10-10 alpha/Renormalization/wilson.tex
Restructure to gather quick notes
Update note on RG

--- 2020-10-06 Renormalization/wilson.tex
@@
 
-\documentclass[a4paper,10pt]{article}
+\documentclass[a4paper
+	,10pt
+%	,twoside
+]{article}
 
-\input{preamble.tex}
-\input{modules/basics/biblatex.tex}
+\input{../preamble.tex}
+\input{../.modules/basics/biblatex.tex}
 
@@
 \maketitle
-\pagestyle{headings}
 \pagenumbering{arabic}
@@
 \vspace*{-.5\baselineskip}
-	The continuum limit $\Lambda\to\infty$ is \textbf{not} well defined.
+	\textbf{Reason:} The continuum limit $\Lambda\to\infty$ is \textbf{not} well-defined.
 	Renormalization provides a way to \emph{define} the theory when
@@
 
-\textbf{Key words:}
-\begin{itemize}[nosep]
+	\textbf{Keywords:}
+	\begin{itemize}[nosep,topsep=-.5\parskip]
 	\item Renormalization group
@@
 
-\noindent \textsl{Ranked by importance:}
+%\noindent \textsl{Ranked by importance:}
 
-	\begin{itemize}
+	\begin{itemize}[parsep=0pt,itemsep=.5\parskip]
 	\item David Skinner's note:
@@
 	Seed theory parameters (i.e.\ \emph{bare parameters}):
-	$(g_0,\Lambda_0)$, $g = (m,\lambda,\cdots)$ a collection of all
-	possible couplings.
+	$(Z_\phi,g,\Lambda)_0$, where $g = (m,\lambda,\cdots)$ is the collection of all possible couplings. $Z_\phi$ is the coefficient of the kinetic term.
 
@@
 	  \phi_{\Lambda_0}(x)
-	  \sim \int^{\Lambda_0} \dd p
+	  \sim \int^{\Lambda_0} \dd{p}
 	    e^{ip\cdot x}
 	    \tilde{\phi}(p)
-	  &= \int^{\Lambda} \dd p
+	  &= \int^{\Lambda} \dd{p}
 	    e^{ip\cdot x}
 	    \tilde{\phi}(p)
-	    + \int_{\Lambda}^{\Lambda_0} \dd p
+	    + \int_{\Lambda}^{\Lambda_0} \dd{p}
 	    e^{ip\cdot x}
@@
 	  \mcal{Z} (g_0,\Lambda_0)
-	  &= \int \DD \phi_{\Lambda_0}
+	  &= \int \DD\phi_{\Lambda_0}
 	      e^{iS[\phi_{\Lambda_0}]} \\
-	  &= \int \DD \phi_{\Lambda}
-	    \int \DD \chi\,
+	  &= \int \DD\phi_{\Lambda}
+	    \int \DD\chi
 	      e^{iS[\phi_\Lambda + \chi]} \\
-	  &=\colon \int \DD \phi_{\Lambda}\,
+	  &=: \int \DD\phi_{\Lambda}
 	      e^{iS_{\mathrm{eff}} [\phi_\Lambda]}
-	  =\colon \mcal{Z}\pqty{g(\Lambda),\Lambda}
+	  =: \mcal{Z}\pqty{g(\Lambda),\Lambda}
 	\end{aligned}
 	\end{equation}
-	Renormalized parameters: $(g,\Lambda)$.
+	Coarse-grained parameters: $(Z_\phi,g,\Lambda)$.
 
-	\begin{quote}
 	\textbf{Subtlety:} the notation above is only schematic; in practice we
@@
 	just think of the 8-shaped contour in loop integrals.
-	\end{quote}
 
@@
 	$\phi = \phi_\Lambda$ is treated as constant when doing
-	$\int \DD \chi$.
+	$\int \DD \chi$. Perturbatively, we integrate over loops with $\chi$ propagators as internal lines
 	\begin{equation}
@@
 	  \mcal{L}[\phi + \chi]
-	  &= - \frac{1}{2}
+	  &= - \frac{Z_\phi}{2}\,
 	      \partial_\mu (\phi + \chi)\,
 	      \partial^\mu (\phi + \chi)
-	    - \frac{1}{2} m^2
+	    - \frac{1}{2}\, m^2
 	      (\phi + \chi)^2
-	    - \frac{1}{4!} \lambda\,
+	    - \frac{1}{4!}\, \lambda\,
 	      (\phi + \chi)^4\\
@@
 	the same as the original $S$, with minor corrections from the
-	$\int \DD\chi$ term. Note that in our regularization scheme there will
-	be no mixed terms of $\phi$ and $\chi$ in the effective action,
-	since they have orthogonal Fourier modes.
+	$\int \DD\chi$ term.
+Note that in such regularization scheme there will be no \textit{quadratic} cross terms $\sim \phi\chi,\, \pd\phi\,\pd\chi$ in the effective action, since they have orthogonal Fourier modes.
+However, there will be non-vanishing \textit{quartic} cross terms $\sim \phi^2\chi^2,\, \phi^3\chi$.
+After we integrate out $\chi$, the $\phi^2\chi^2$ term will cause a shift in $m^2$, while the $\phi^3\chi$ will generate a new $\phi^6$ vertex (by a $\chi\chi$ contraction).
 
-	Note that $\mcal{Z}$ clearly does not depend on the intermediate scale $\Lambda$, we have:
+	Note that $\mcal{Z}$ clearly does not depend on the intermediate scale $\Lambda$, and we have:
 	\begin{equation}
@@
 	        \pdv{}{g^{(i)}}
-	    }
+	    }\,
 	    \mcal{Z}\pqty{g(\Lambda),\Lambda}
@@
 	This is an example of a \textbf{RG Equation}.
+\subsection{Free theory \& CFT}
+	We first observe that a massless free theory with $
+		\mcal{L}[\phi]
+		\sim \int \dd[d]{x} (\pd\phi)^2
+	$ is ``not renormalized'' when we integrate out high energy modes. Roughly speaking, we have:
+	\begin{equation}
+	\begin{aligned}
+	  \mcal{Z}
+	  &= \int \DD\phi_{\Lambda_0}
+	      e^{iS[\phi_0]} \\
+	  &= \int \DD\phi_{\Lambda}
+	    \int \DD\chi
+	      e^{iS[\phi + \chi]} \\
+	  &\sim \int \DD\phi_{\Lambda}
+	      e^{iS[\phi]}
+	      \sqrt{Z_\phi^\#}
+	\end{aligned}
+	\label{eq:PI_free}
+	\end{equation}
+	Integrating over $\Lambda = s\Lambda_0 \le \abs{p} \le \Lambda_0$ produces the $Z_\phi$ factor, where $\#$ is the total number of modes in this range.
+One can give an explicit expression of $\#$ with some IR cutoff $L$.
+
+	On the other hand, we can restore $\Lambda = s\Lambda_0$ back to $\Lambda_0$ by rescaling.
+This is easy to understand when we think of a lattice theory: to probe the IR behavor, we first ``coarse-grain'' by grouping points together, effectively lowering $\Lambda$; then we ``zoom out'' to see the bigger picture.
+Rescaling $\Lambda = s\Lambda_0$ back to $\Lambda_0$ is precisely the ``zooming-out'' process.
+
+	When taking $\Lambda\mapsto \Lambda_0 = \Lambda / s$, first note that the kinetic term $\int \dd[d]{x} (\pd\phi)^2$ is scale-invariant if we rescale $\phi$ accordingly:
+	\begin{equation}
+		\Lambda\mapsto \Lambda_0 = \Lambda / s,
+	\quad
+		x\mapsto x' = sx,
+	\quad
+		\phi(x) \mapsto
+		\phi'(x') = s^{1 - \frac{d}{2}} \phi(x)
+	\end{equation}
+	The $s^{1 - \frac{d}{2}}$ factor is consistent with the mass dimension of $\phi$, and we have $S'[\phi'] = S[\phi]$ invariant under rescaling.
+
+	The path integral measure, however, is \textit{not} scale-invariant; we have to add back some Fourier modes in between to return the path integral back to $\Lambda_0$.
+Luckily, the additional modes happen to cancels out the $Z_\phi$ factor in \eqref{eq:PI_free}:
+	\begin{equation}
+		\sqrt{Z_\phi^\#} \DD\phi_{\Lambda}
+		\sim \sqrt{Z_\phi^\#}
+			\prod_{\norm{p} < \Lambda = s\Lambda_0}
+			\dd{\tilde{\phi}(p)}
+		= \prod_{\norm{p'} < \Lambda_0}
+			\dd{\tilde{\phi}'(p')}
+		\sim \DD\phi'_{\Lambda_0}
+	\end{equation}
+	Therefore the complete path integral is invariant under RG flow \& rescaling; $Z_\phi$ is also unchanged during this process.
+Therefore we can simply set $Z_\phi \equiv 1$ by an appropriate \textit{normalization} of $\phi$.
+
+	One can see how this process might fail in a curved background: in flat space the Fourier modes are equally spaced, and rescaling $\DD\phi_{\Lambda}$ can be achived by simply adding back a total of $\#$ modes.
+However, in a curved background the Fourier modes are complicated (e.g.\ think of spherical harmonics) and we generally do not expect the Jacobian of $\DD\phi_{\Lambda} \mapsto \DD\phi'_{\Lambda_0}$ to cancel out the $Z_\phi$ factor precisely.
+This is a hint of \textit{Weyl anomaly} in curved backgrounds.
+For a concrete discussion with path integral, see \textit{Di Francesco et al}, 5.A.
+\pagebreak[4]
+
+	Generally, $Z_\phi$ \textit{will} change after rescaling:
+	\begin{equation}
+		Z_\phi \sim \Lambda^{-2\gamma_\phi},
+	\quad
+		\gamma_\phi
+		\mathbin{:=}
+		-\frac{1}{2}\,\Lambda \pdv{\ln Z_\phi}{\Lambda}
+	\end{equation}
+	The scaling of $Z_\phi$ can be absorbed by \textit{field strength renormalization} (or ``wave function'' renormalization); i.e.\ if we \textit{demand} $\phi$ to retain the canonical normalization such that $Z_\phi \equiv 1$, then $\phi$ must scale with an \textit{anomalous dimension} $\gamma_\phi$:
+	\begin{equation}
+		\phi(x) 
+		\ \longmapsto\ %
+		\phi'(x') = s^{1 - \frac{d}{2} - \gamma_\phi} \phi(x)
+	\end{equation}
+	In practice we don't actually redefine the scaling of $\phi$, just simplify keep track of it using the $Z_\phi$ factor; but we should know that due to quantum corrections, the mass dimension of $\phi$ is, effectively,
+	\begin{equation}
+		\Delta_\phi
+		= \frac{d}{2} - 1 + \gamma_\phi
+	\end{equation}
+
+	In summary, we've argued that the classical \& quantum theory of a massless free boson on flat space is \textit{scale-invariant}; $\gamma_\phi = 0$. In fact, this is a first example of free CFTs. 
+	CFTs are the \textit{fixed points} of RG flow.
+\subsection{Massive theory \& the space of theories}
+	What about \textit{massive} free theories?
+We do know that they don't receive loop corrections, therefore ``invariant'' under coarse-graining; however, mass \textit{do} flow when we zoom out.
+This is very natural; as we zoom out the energy-momentum of all modes are enhanced by a factor of $s^{-1}$, and we have $m\mapsto m/s$.
+Therefore $m$ is a \textit{relevant} parameter as we flow towards IR; it grows and flows away from the massless free CFT.
+For an explicitly path integral calculation (along with $\phi^{2n}$ interactions), see \textit{Hollowood}, 2.1.
+
+	Generally, for small $g$ we can think of the theory $(g,\Lambda)$ as a \textit{deformation} away from the massless free CFT.
+A neat trick to stop worrying about rescaling is to re-define $g$ as dimensionless couplings:
+	\begin{equation}
+		g(\Lambda) = \pqty{
+			g^{(2)} = \frac{m^2_{(\Lambda)}}{\Lambda^2},
+			\ g^{(4)} = \lambda,
+			\ g^{(6)} = \cdots
+		}
+	\end{equation}
+	Here we use $m^2_{(\Lambda)}$ to denote the mass \textit{after} coarse-graining but \textit{before} rescaling. The mass term is then given by $
+		\sim \int \dd[d]{x} m^2 \phi^2
+		= \int \dd[d]{x} g^{(2)} \Lambda^2 \phi^2
+	$.
+$g$ is thus invariant under rescaling, as the rescaling factor is absorbed by the $\Lambda$ factor.
+We also don't have to worry about the anomalous path integral measure, as it's captured by the $Z_\phi$ factor.
+
+	After rescaling $\Lambda \mapsto \Lambda_0$, the dimensionful mass is given by:
+	\begin{equation}
+		m'^2_{(\Lambda)}
+		= g^{(2)}_{(\Lambda)} \Lambda_0^2
+		= m^2_{(\Lambda)}
+			\pqty{\frac{\Lambda_0}{\Lambda}}^2
+	\end{equation}
+	In general, the rescaled, dimensional coupling is simply the dimensionless coupling times some factors of the \textit{initial} cutoff $\Lambda_0$.
+Therefore its $\Lambda$ dependence is identical to that of the dimensionless coupling.
+On the other hand, the coarse-grained, dimensionful couplings \textit{before} rescaling is given by $g_{\Lambda}$ times some power of $\Lambda$ (instead of $\Lambda_0$); e.g.
+	\begin{equation}
+		m^2_{(\Lambda)}
+		= g^{(2)}_{(\Lambda)} \Lambda^2
+		\xrightarrow{\ \text{free}\ }
+		m_0^2
+	\end{equation}
+	i.e.\ it is constant for a free theory. Intuitively, this is because low \& high energy modes are completely decoupled in a free theory.
+
+	\begin{figure}[!h]
+	\centering
+	\includegraphics[width=.35\linewidth]{img/RG-flow.png}
+	\end{figure}
+\subsection{Physical Scales vs the Cutoff}
+	LSZ reduction (with the ``mostly plus'' metric convention, see \textit{Srednicki}):
+	\begin{equation}
+		\int \dd[d]{x} e^{-ip\cdot x}
+		\int \dd[d]{y} e^{+ik\cdot y}
+		\ave[\big]{\phi(x)\,\phi(y)}
+	\xmapsto{\ p,k\ \text{on-shell}\ }
+		\frac{-i\sqrt{Z_\phi}}{p^2 + m^2 - i\epsilon}
+		\frac{-i\sqrt{Z_\phi}}{k^2 + m^2 - i\epsilon}
+		\mel{p}{S}{k}
+	\end{equation}
+	\begin{equation}
+		\ave[\big]{\phi(x)\,\phi(y)}
+		= \frac{1}{\mcal{Z}}
+			\int \DD{\phi_\Lambda} e^{iS_\Lambda[\phi]}\,
+			\phi(x)\,\phi(y)
+	\end{equation}
+	$S \sim \idty + i\mcal{M}(\mu)$, physical amplitude $\mcal{M}(\mu)$ scale with energy $\mu$, but is cutoff-independent.
+
+	How to relate $\mcal{M}(\mu)$ to $g(\Lambda)$? Note that the canonical Green function \textit{does} scale with $\Lambda$! With the help of Poincar\'e invariance, we have:
+	\begin{equation}
+		Z_\Lambda \ave[\big]{\phi(x)\,\phi(y)}
+		\mathbin{=:} G_\Lambda\pqty\big{x,y; g(\Lambda)}
+		= G_\Lambda\pqty\big{l; g(\Lambda)},
+	\quad
+		Z_\lambda := (Z_\phi)_\Lambda
+	\end{equation}
+	Physical scale: $l = \abs{x_1 - x_2}$, or center of mass momentum $\mu$ in amplitudes; $l\cdot \mu \sim 1$. $\Lambda$-dependence enters through $Z_\phi$. For general $n$-pt function, RG flow:
+	\begin{equation}
+	\begin{aligned}
+		\ave[\big]{\phi^n(\cdots)}
+		= \frac{1}{\mcal{Z}}
+			\int \DD{\phi_\Lambda} e^{iS_\Lambda[\phi]}\,
+			\phi^n(\cdots)
+		&= Z^{-n/2}_\Lambda
+			G_\Lambda \pqty\big{l; g(\Lambda)} \\
+		&= Z^{-n/2}_{s\Lambda}
+			G_{\Lambda} \pqty\big{sl; g(s\Lambda)}\,
+			\pqty{s^{1 - \frac{d}{2}}}^{-n}
+	\end{aligned}
+	\end{equation}
+
+	This is a key result! We have:
+	\begin{equation}
+		G_\Lambda \pqty\big{l; g(\Lambda)}
+		= G_{\Lambda} \pqty\big{sl; g(s\Lambda)}
+			\pqty{
+				s^{1 - \frac{d}{2}}
+				\sqrt{\frac{Z_\Lambda}{Z_{s\Lambda}}}
+			}^n
+		\simeq G_{\Lambda} \pqty\big{sl; g(s\Lambda)}
+			\,s^{n\Delta_\phi}
+	\end{equation}
+	Or in terms of energy scale $\mu$,
+	\begin{gather}
+		\mcal{M} \pqty\big{\mu; g(\Lambda)}
+		= \mcal{M} \pqty\big{\mu/s; g(s\Lambda)},
+	\\[1ex]
+		\mu\,\pdv{\mcal{M}}{\mu}
+		= \pdv{M}{g}\,\pqty{
+				\Lambda\,\pdv{g}{\Lambda}
+			}
+	\end{gather}
 \section{Perturbative Renormalization}
@@
 	couplings, since most other parameters $g^{(i)}$ are \emph{irrelevant}
-	and get suppressed by $\Lambda/\Lambda_0$ in the IR. After such
+	and get suppressed by $\Lambda/\Lambda_0$ in the IR. We shall see this in more details later. After such
 	restriction to a relevant subspace, the RG flow is a group, and we can
@@
 
+	\begin{quote}
+	\textbf{Subtlety:} the tuning process described above might encounter some serious
+	obstruction: the tuned $g_0$ could blow up at some finite
+	$\Lambda_{\mathrm{UV}}$; this is the so-called \emph{Landau pole}.
+	This tells us that the theory only works under some
+	$\Lambda_{\mathrm{UV}}$, i.e.~it is not \emph{UV complete}; it's only
+	an \emph{effective} theory. One have to ``embed'' this Lagrangian into a
+	bigger theory that works beyond $\Lambda_{\mathrm{UV}}$; this is the
+	non-trivial \emph{UV completion} of an effective theory.
+	\end{quote}
+
 \subsection{Perturbation}
-
 	The above results are non-perturbative and should always hold.
@@
 
-	\hypertarget{renormalizability}{%
-	\section{Renormalizability}\label{renormalizability}}
+\section{Renormalizability}
+	As we've mentioned before, most parameters $g^{(i)} \in g$ are, in fact, \emph{irrelevant} --- such terms in the Lagrangian get suppressed by $\Lambda/\Lambda_0$ in IR.
+We shall see how this arise from dimensional anlaysis.
 
-	Most parameters $g^{(i)}$ are, in fact, \emph{irrelevant} --- such
-	terms in the Lagrangian get suppressed by $\Lambda/\Lambda_0$ in IR.
 	If the IR theory has only \emph{relevant} couplings, then one should be
@@
 	extrapolation.
-
-	\begin{quote}
-	However, the tuning process described above might encounter some serious
-	obstruction: the tuned $g_0$ could blow up at some finite
-	$\Lambda_{\mathrm{UV}}$; this is the so-called \emph{Landau pole}.
-	This tells us that the theory only works under some
-	$\Lambda_{\mathrm{UV}}$, i.e.~it is not \emph{UV complete}; it's only
-	an \emph{effective} theory. One have to ``embed'' this Lagrangian into a
-	bigger theory that works beyond $\Lambda_{\mathrm{UV}}$; this is the
-	non-trivial \emph{UV completion} of an effective theory.
-	\end{quote}
 
@@
 \section{Effective Action}
-
-	Furthermore, after $\phi_\Lambda$ is completely integrated out, we
+	After $\phi_\Lambda$ is completely integrated out, we
 	have:

### 2020-10-12 ThermalFieldTheory2020/thermal1/thermal1.tex
Add thermal1, tweak wilson note

% !TeX encoding = UTF-8
% !TeX spellcheck = en_US
% !TeX TXS-program:bibliography = biber -l zh__pinyin --output-safechars %

\documentclass[a4paper,10pt]{article}

\newcommand{\hwNumber}{1}

\input{../thermal_preamble.tex}
\input{../.modules/basics/biblatex.tex}

%%% ID: sensitive, do NOT publish!
\InputIfFileExists{../id.tex}{}{}

\begin{document}
\maketitle
\pagestyle{headings}
\pagenumbering{arabic}
\thispagestyle{empty}

\vspace*{-1.5\baselineskip}

\section*{Thermal propagator for harmonic oscilators}
\vspace*{-.8\baselineskip}
	\begin{equation}
		G(\tau)
		= \frac{1}{Z}
			\Tr \pqty{
				e^{-\beta H}
				x(\tau)\,
				x(0)
			}
	\end{equation}

\noindent
	The Hamiltonian is $
		H = \omega\pqty{
			a^\dagger a + \frac{1}{2}
		}
	$, while $
		x = \frac{1}{\sqrt{2m\omega}}\pqty{
			a + a^\dagger
		}
	$. 
\subsection*{Operator formalism}
	Mode expansion of Lorentzian operator in the Heisenberg picture:
	\begin{equation}
		x(t)
		= e^{iHt} \,x(0)\, e^{-iHt}
		= \frac{1}{\sqrt{2m\omega}} \pqty\Big{
				a\,e^{-i\omega t}
				+ a^\dagger e^{i\omega t}
			}
	\end{equation}
	This follows from the commutation relation between $a^{(\dagger)}$ and $H$, or from the quantum EOM in the Heisenberg picture. Wick-rotation to Euclidean signature: $\tau = it,\ t = -i\tau$, and we have:
	\begin{equation}
		x(\tau)
		= e^{H\tau} \,x(0)\, e^{-H\tau}
		= \frac{1}{\sqrt{2m\omega}} \pqty\Big{
				a\,e^{-\omega\tau}
				+ a^\dagger e^{\omega\tau}
			}
	\end{equation}

	Insert $x(\tau)\,x(0)$ into the definition of $G(\tau)$, and note that only $aa^\dagger$ and $a^\dagger a$ contribute to non-zero amplitudes, then we have:
	\begin{equation}
	\begin{aligned}
		G(\tau)
		&= \frac{1}{Z} \sum_{n=0}^\infty
			\mel**{n}{
				e^{-\beta\omega(n + \frac{1}{2})}\,
				\frac{
					aa^\dagger e^{-\omega\tau}
					+ a^\dagger a\, e^{\omega\tau}
				}{2m\omega}
			}{n} \\
		&= \frac{1}{Z} \sum_{n=0}^\infty
			\mel**{n}{
				e^{-\beta\omega(n + \frac{1}{2})}\,
				\frac{
					(n+1)\, e^{-\omega\tau}
					+ n\, e^{\omega\tau}
				}{2m\omega}
			}{n} \\
	\end{aligned}
	\end{equation}

	Note that:
	\begin{equation}
		\sum_{n=0}^\infty
			n\,e^{-\beta\omega n}
		= -\frac{1}{\beta} \pdv{\omega}
		\sum_{n=0}^\infty
			e^{-\beta\omega n}
	\label{eq:generatingTrick}
	\end{equation}
	The summations in $G(\tau)$ can be completed, and we get:
	\begin{equation}
		G(\tau)
		= \frac{1}{2m\omega}
			\frac{
				\cos \pqty\big{
					\pqty*{\frac{\beta}{2}-\tau} \omega
				}
			}{
				\sin \pqty\big{\frac{\beta\omega}{2}}
			}
	\end{equation}
\subsection*{Path Integral}
	The mathematical trick in \eqref{eq:generatingTrick} is crucial in our path integral derivation of $G(\tau)$. We have:
	\begin{gather}
		G(\tau)
		= \ave[\big]{x(\tau)\,x(0)}
		= \frac{1}{Z} \int \DD{x} e^{-S}
			x(\tau)\,x(0),\\
		S
		= \int_0^\beta \dd{t} \mcal{L}_E,
	\quad
		\mcal{L}_E
		= \frac{1}{2}\, m\dot{x}^2_{(\tau)}
			+ \frac{1}{2}\, m\omega^2 x^2_{(\tau)}
	\end{gather}
	Note that the path integral of a total derivative vanishes: $0 = \int \DD{x} \fdv{x}$ (see \textit{Polchinski}), we have:
	\begin{equation}
	\begin{aligned}
		0 &= \int \DD{x} \fdv{x(\tau)} \Bqty\Big{
				e^{-S} x(\tau')
			}
%		\\ &
		= \int \DD{x} e^{-S}\,\Bqty{
				- \fdv{S}{x(\tau)}\,x(\tau')
				+ \delta(\tau - \tau')
			}
	\end{aligned}
	\end{equation}
%\pagebreak[3]

	$\fdv{S}{x(\tau)}$ yields precisely the quantum EOM:
	\begin{equation}
		\fdv{S}{x(\tau)}
		= m\,\pqty{
				-\pdv[2]{}{\tau}
				+ \omega^2
			}\,x(\tau)
	\end{equation}
	After some re-organization, we get the quantum equation for the Green function (which, for such a free theory, is identical to the classical one):
	\begin{equation}
		m\,\pqty{
			-\pdv[2]{}{\tau}
			+ \omega^2
		} \int \DD{x} e^{-S}
			x(\tau)\,x(\tau')
		= \delta(\tau - \tau')
			\int \DD{x} e^{-S},
	\end{equation}
	\vspace{-.5\baselineskip}
	\begin{equation}
		\pqty{
			-\pdv[2]{}{\tau}
			+ \omega^2
		}\, G(\tau,\tau')
		= \frac{1}{m}\, \delta(\tau - \tau'),
	\quad
		G(\tau) = G(\tau,0)
	\end{equation}

	Note that $\tau \in [0,\beta]$ and $x(\tau)$ satisfies the periodic boundary condition: $x(\beta) = x(0)$, hence also $G(\beta) = G(0)$; we can extend the domain so that $x(\tau)$ is a function with period $\beta$, defined for $\tau\in\mbb{R}$. Furthermore, note that by definition $G(\tau,\tau') = G(\tau',\tau)$; this is the Feynman propagator! Integrating around $\tau = \tau'$ then setting $\tau' = 0$ gives:
	\begin{equation}
		G'(\beta^-) - G'(0^+)
		= \frac{1}{m}
	\end{equation}
	While $G(\tau)$ away from $\tau = 0$ grows (or decays) exponentially: $
		G(\tau)
		\propto e^{\omega\tau} + e^{\omega(\beta - \tau)}
	$. This fixes $G(\tau)$ uniquely:
	\begin{equation}
		G(\tau)
		= \frac{1}{2m\omega}
			\frac{
				\cos \pqty\big{
					\pqty*{\frac{\beta}{2}-\tau} \omega
				}
			}{
				\sin \pqty\big{\frac{\beta\omega}{2}}
			}
	\end{equation}

\printbibliography[%
%	title = {参考文献} %
	,heading = bibintoc
]
\end{document}

### 2020-10-12 ThermalFieldTheory2020/thermal1/thermal1.tex
Add minor tweaks of recent updates

@@
 	\end{equation}
-	After some re-organization, we get the quantum equation for the Green function (which, for such a free theory, is identical to the classical one):
+	After some re-organization, we get the quantum equation for the Green's function (which, for a free theory, is identical to the classical one):
 	\begin{equation}

### 2020-10-18 alpha/Exam/exam.tex
Add solutions for the qualifying exam

% !TeX document-id = {b5392a94-51a3-49d1-9ba5-698bc09f9d35}
% !TeX encoding = UTF-8
% !TeX spellcheck = en_US
% !TeX TXS-program:bibliography = biber -l zh__pinyin --output-safechars %
% !TeX TS-program = lualatex
%%% LuaLaTeX is required for `tikz-feynman`

\documentclass[a4paper
	,10pt
%	,twoside
]{article}

\input{../preamble.tex}
\input{../.modules/basics/biblatex.tex}

\title{Qualifying Exam\phantom{:}%
	\,\normalsize Physics 2020 @ YMSC, Tsinghua%
}
%\addbibresource{.bib}

%%% ID: sensitive, do NOT publish!
%\InputIfFileExists{id.tex}{}{}

\renewcommand{\ccbyncsajp}{}

\usepackage{cancel}
\usepackage{tikz-feynman}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
	@book{Peskin:1995ev,
	    author = "Peskin, Michael E. and Schroeder, Daniel V.",
	    title = "{An Introduction to Quantum Field Theory}",
	    isbn = "978-0-201-50397-5",
	    publisher = "Addison-Wesley",
	    address = "Reading, USA",
	    year = "1995"
	}
\end{filecontents}
\addbibresource{\jobname.bib}

\begin{document}
\maketitle
\pagenumbering{arabic}
\thispagestyle{empty}

\section{Gravity}
	\vspace{-1.5\baselineskip}
	\begin{equation}
		\dd{s^2}
		= - f(r) \dd{t^2}
			+ \frac{1}{f(r)} \dd{r^2}
			+ r^2 \dd{\Omega^2}
	\end{equation}
	\vspace{-.3\baselineskip}
	\begin{equation}
		\ f(r)
		= 1 - \frac{GM}{r} + \frac{Q^2}{r^2}
		= \frac{(r - r_+)(r - r_-)}{r^2}
	\end{equation}

\begin{enumerate}
\item Event horizon(s): $f(r) = 0$, we have:
	\begin{enumerate}
	\item $M > \abs{Q}$, $r_\pm = M \pm \sqrt{M^2 - Q^2}$, 2 event horizons;
	\item $M = \abs{Q}$, $r_\pm = M$, 1 event horizons;
	\item $M < \abs{Q}$, no event horizons! ``Naked'' singularity.
	\end{enumerate}

\item New coordinate: $v = t + r^*$,
	\begin{equation}
		r^* = r
			+ \frac{1}{2k_+}
				\ln \frac{\abs{r - r_+}}{r_+}
			+ \frac{1}{2k_-}
				\ln \frac{\abs{r - r_-}}{r_-},
	\quad
		k_\pm
		= \frac{r_\pm - r_\mp}{2r_\pm^2}
	\label{eq:def_coord}
	\end{equation}
	We have:
	\begin{align}
		\dd{t}
		= \dd{v} - \dd{r^*}
		&= \dd{v} - \pqty{
				1 + \frac{1}{2k_+} \frac{1}{r - r_+}
				+ \frac{1}{2k_-} \frac{1}{r - r_-}
			} \dd{r}
		\label{eq:diff_coord}
		\\
		&= \dd{v} - \pqty{
				1 + \frac{1}{r^2 f(r)}
				\frac{
					r_+^2 (r - r_-)
					- r_-^2 (r - r_+)
				}{r_+ - r_-}
			} \dd{r} \notag\\
		&= \dd{v} - \pqty{
				1 + \frac{1}{r^2 f(r)}\,
				\pqty\Big{
					(r_+ + r_-)\,r
					- r_+ r_-
				}
			} \dd{r} \notag\\
		&= \dd{v} - \frac{1}{f(r)} \dd{r}
		\label{eq:diff_coord_goal}
	\end{align}

	Therefore,
	\begin{enumerate}[parsep=\parskip]
	\item The new metric:
	\begin{align}
		\dd{s^2}
		&= - f(r) \pqty{
				\dd{v}
				- \frac{1}{f(r)} \dd{r}
			}^{\!\!2}
			+ \frac{1}{f(r)} \dd{r^2}
			+ r^2 \dd{\Omega^2} \\
		&= - f(r) \dd{v^2}
			+ 2 \dd{v} \dd{r}
			+ r^2 \dd{\Omega^2} \notag
	\end{align}
	It is only singular at $r = 0$.

	\begin{quote}
	\textbf{Note:} during the exam I panicked when I saw \eqref{eq:def_coord}, and I made a very stupid mistake in step \eqref{eq:diff_coord}. However, I knew what this new coordinate is trying to achieve --- it's aiming to eliminate the coordinate singularities in $\frac{1}{f} \dd{r^2}$ by absorbing it into $\dd{v^2}$, so I guessed the result \eqref{eq:diff_coord_goal} correctly and carried on. I hope they gave me some points for getting the right answer, despite with some wrong process (>\_<).
	\end{quote}

	\item $\pdv{v}$ is a Killing vector field, for the metric components are all $v$-independent. More precisely, since $\pdv{v}$ itself is a coordinate basis, we have the Lie derivative:
	\begin{equation}
		\ldv{\pdv{v}} g_{\mu\nu}
		= \pdd{v} g_{\mu\nu}
		= 0
	\end{equation}

	\item $
		\norm{\pdv{v}}^2
		= g_{\mu\nu} \delta^\mu_v \delta^\nu_v
		= g_{vv}
		= -f(r)
	$, therefore, for $M > \abs{Q}$ we have:
	\begin{itemize}[topsep=.3\baselineskip]
	\item $\pdv{v}$ timelike: $r > r_+$ and $r < r_-$
	\item spacelike: $r_- < r < r_+$
	\item null: $r = r_+$ and $r = r_-$
	\end{itemize}

	\end{enumerate}
\end{enumerate}
\section{QFT}
We shall restore the reasonable convention: $
	\eta_{\mu\nu}
	\sim \pqty{-,+,+,+}
$. 
\begin{enumerate}
\item 1PI: diagrammatic contribution to the (1-particle) propagator that cannot be split into 2 disconnected parts by cutting one line; e.g.\,%
	\raisebox{-.4\baselineskip}{
		\feynmandiagram[
			scale=.4
			,small
			,layered layout
			,horizontal=a to d
		]{
			a -- b[{small,dot}] -- c[{small,dot}] -- d,
			b -- [half left,looseness=1.5]
			c -- [half left,looseness=1.5]
			b,
		};
	}
\item Consider the following Lagrangian:
	\begin{equation}
		\mcal{L}
		= -\frac{1}{2} Z(\pd\phi_r)^2
			-\frac{1}{2} m^2 Z\phi_r^2
			-\frac{\lambda}{4!} \phi_r^4
		-\frac{1}{2} \delta_Z(\pd\phi_r)^2
			-\frac{1}{2} \delta_m \phi_r^2
			-\frac{\delta_\lambda}{4!} \phi_r^4
	\label{eq:lagrangian}
	\end{equation}
	The convention here is rather bizarre; normally we write down the UV Lagrangian $\mcal{L}_{\mrm{UV}}$ and split it into 2 parts, one is the effective IR Lagrangian $\mcal{L}_{\mrm{IR}}$ and the other one is the counterterm:
	\begin{equation}
	\begin{aligned}
		\mcal{L}_{\mrm{UV}}
		&= -\frac{1}{2} Z(\pd\phi_r)^2
			-\frac{1}{2} m^2 Z\phi_r^2
			-\frac{\lambda}{4!} \phi_r^4 \\
		&= \pqty{
			-\frac{1}{2} (\pd\phi_r)^2
			-\frac{1}{2} m_p^2 \phi_r^2
			-\frac{\lambda_p}{4!} \phi_r^4
		}
		- \pqty{
			-\frac{1}{2} \delta_Z(\pd\phi_r)^2
			-\frac{1}{2} \delta_m \phi_r^2
			-\frac{\delta_\lambda}{4!} \phi_r^4
		} \\
		&= \mcal{L}_{\mrm{IR}}
			+ \mcal{L}_{\mrm{ct}}
	\end{aligned}
	\end{equation}

	Normally, we use $\mcal{L}$ to denote the UV Lagrangian $\mcal{L}_{\mrm{UV}}$; this is the convention adopted by numerous standard textbooks, incl.~\textit{Peskin \& Schroeder} \cite{Peskin:1995ev}, \textit{Weinberg}, and also \textit{Srednicki}. However, the Lagrangian in \eqref{eq:lagrangian} seems to be $\mcal{L}_{\mrm{IR}}$ instead of $\mcal{L}_{\mrm{UV}}$. Anyway, we have:
	\begin{equation}
		Z + \delta_Z = 1,
	\quad
		m^2 Z + \delta_m = m_p^2,
	\quad
		\lambda + \delta_\lambda = \lambda_p
	\end{equation}
	Where $m_p,\lambda_p$ is the physical IR couplings, fixed by the renormalization scheme. The convention here is really confusing and somewhat inconsistent; e.g.\ if we choose to write the UV mass term as $
		-\frac{1}{2} m^2 Z \phi_r^2
	$, then the corresponding UV interaction term should look like $
		-\frac{\lambda}{4!} Z^2 \phi_r^4
	$, but here we do not have the $Z^2$ factor. Also, we usually use $m_0,\lambda_0$ to denote bare couplings, but here it seems that they are denoted by $m,\lambda$.

	We can write down the renormalized Feynman rules nonetheless, despite some sign issues due to the conventions; to avoid further confusion, we will adopt the usual notation: $m_0,\lambda_0$ for bare couplings, and $m = m_p, \lambda = \lambda_p$ for physical couplings. We have:
	\begin{itemize}[noitemsep]
	\item Renormalized propagator: $
			\frac{-i}{p^2 + m^2 - i\epsilon}
		$
	\item Renormalized vertex: $-i\lambda$
	\item Counterterm $\phi^2$ vertex: $+i\pqty{\delta_Z (-p^2) + \delta_m}$,
		\raisebox{0.\baselineskip}{
			\feynmandiagram[
				scale=.4
				,small
				,layered layout
				,horizontal=a to c
			]{
				a -- b[{small,crossed dot}] -- c,
			};
		}
	\item Counterterm $\phi^4$ vertex: $+i\delta_\lambda$
	\end{itemize}
\pagebreak

\item The sum of all two point 1PI diagrams (no propagator on external legs) is given by:
	\begin{equation}
		-iM(p^2)
		= \raisebox{-.3\height}{
			\feynmandiagram[
				scale=.7
				,small
				,layered layout
			]{
				b[blob],
			};
		}
	\end{equation}
	The full propagator is thus:
	\begin{equation}
	\begin{aligned}
		G(p^2)
		&= \raisebox{+.15\baselineskip}{
			\feynmandiagram[
				scale=.7
				,small
				,layered layout
				,horizontal=a to b
			]{
				a -- b,
			};
		}
		+ \raisebox{-.3\height}{
			\feynmandiagram[
				scale=.7
				,small
				,layered layout
				,horizontal=a to c
			]{
				a -- b[blob] -- c,
			};
		}
		+ \raisebox{-.3\height}{
			\feynmandiagram[
				scale=.7
				,small
				,layered layout
				,horizontal=a to d
			]{
				a -- b[blob] -- c[blob] -- d,
			};
		}
		+ \cdots \\
		&= \tfrac{-i}{p^2 + m^2}
			+ \tfrac{-i}{p^2 + m^2}
				(-iM) \tfrac{-i}{p^2 + m^2}
			+ \tfrac{-i}{p^2 + m^2}
				(-iM) \tfrac{-i}{p^2 + m^2}
				(-iM) \tfrac{-i}{p^2 + m^2}
			+ \cdots
	\end{aligned}
	\end{equation}
%\pagebreak[4]

	With $\sum_{n=0}^\infty q^n = \frac{1}{1 - q}$, we get:
	\begin{equation}
		G(p^2)
		= \frac{-i}{p^2 + m^2} \cdot
			\frac{1}{1 - (-iM) \tfrac{-i}{p^2 + m^2}}
		= \frac{-i}{p^2 + m^2 + M(p^2)}
	\end{equation}
	Here we've suppressed the $(-i\epsilon)$ prescription in the above expressions, but it's presence is always implied.

	\item On-shell renormalization scheme --- the full propagator:
	\begin{equation}
		G(p^2)
		= \frac{-i}{p^2 + m^2 + M(p^2) - i\epsilon}
		\xrightarrow{\ p^2\to -m^2}
		\frac{-i}{p^2 + m^2 - i\epsilon}
	\end{equation}
	This means that $
		M(p^2 = -m^2) = 0
	$. Furthermore, $M(p^2) \sim \#\,(p^2 + m^2) + \order{p^4}$, to ensure that the residue is 1 at the pole, we should have $\# \sim 0$, i.e.
	\begin{equation}
		M(p^2)\big|_{p^2 = -m^2}
		= 0,
	\quad
		\pdv{(p^2)} M(p^2)\big|_{p^2 = -m^2}
		= 0
	\label{eq:renorm_cond}
	\end{equation}

	\item At 1-loop $\order{\lambda}$, if we do not include counterterm contributions, then there is only one diagram contributing to $M(p^2)$:
	\begin{equation}
	%% ref: <https://tex.stackexchange.com/q/387810/193356>
		\raisebox{-.2\height}{
			\feynmandiagram[
				scale=.7
				,small
				,layered layout
				,horizontal=a to b
			]{
				a -- b [dot]
				-- [out=135, in=45, loop
					,min distance=3.5\baselineskip
					] b
				-- c
			};
		}
		= (-i\lambda)\cdot\frac{1}{2}
			\int \frac{\dd[D]{k}}{(2\pi)^D}
				\frac{-i}{k^2 + m^2 - i\epsilon}
	\end{equation}
	Here $\frac{1}{2}$ is the symmetry factor of the diagram; alternative, we can count the distinct ways of connection the 4 legs of the $\phi^4$ vertex and divide it by $4!$, which is indeed $
		\frac{4\times 3}{4!} = \frac{1}{2}
	$.

	The $p^0$ integral has poles at $p_0^2 = \vb{p}^2 + m^2 - i\epsilon$, i.e.\ $p^0 = \pm\sqrt{\vb{p}^2 + m^2} \mp i\epsilon$, and it's regular everywhere else; we can thus compute the $p^0$ integral on the $\mbb{C}$ plane using a right-tilted 8-shaped contour, which does not enclose the poles. Effectively, we've performed a Wick rotation $p^0 \mapsto ip^0$ so that the integral happens in Euclidean $p$ space:
	\begin{equation}
		\frac{-i\lambda}{2}
			\int \frac{\dd[D]{k}}{(2\pi)^D}
				\frac{1}{k^2 + m^2}
		= \frac{-i\lambda}{2}\,
			\frac{A(S^d)}{(2\pi)^D}
			\int \frac{k^d \dd{k}}{k^2 + m^2}
	\end{equation}
	Here $D = d + 1$, $d$ is the spatial dimension. There are many ways to regularize this integral; if we continue to work in general $D = d + 1$ dimensions, then dimensional regularization is automatically implied. We have:
	\begin{equation}
		A(S^d) = \frac{2\pi^{D/2}}{\Gamma(D/2)},
	\quad
		\int \frac{k^d \dd{k}}{k^2 + m^2}
		= \frac{m^D}{m^2}
			\int \frac{t^d \dd{t}}{1 + t^2}
	\end{equation}
\pagebreak[4]

	The $t$-integral is related to Beta functions; consider $t\mapsto \frac{t^2}{1 + t^2}$, and we have:
	\begin{equation}
		\int_0^\infty \frac{t^d \dd{t}}{1 + t^2}
		= \frac{1}{2}
		\int_0^1 t^{\frac{D}{2} - 1}
			(1-t)^{-\frac{D}{2}} \dd{t}
		= \frac{
				\Gamma(\tfrac{D}{2})\,
				\Gamma(1 - \tfrac{D}{2})
			}{2\Gamma(1)}
		= \frac{1}{2} \Gamma(\tfrac{D}{2})\,
			\Gamma(1 - \tfrac{D}{2})
		= \frac{\pi}{2\sin \frac{\pi D}{2}}
	\end{equation}
	The last line is the \textit{Euler's reflection formula}, but here we actually don't need that since the $\Gamma(\tfrac{D}{2})$ factor is canceled by $A(S^d)$. In the end we have:
	\begin{equation}
		\int \frac{\dd[D]{k}}{(2\pi)^D}
			\frac{1}{k^2 + m^2}
		= \frac{\pi^{D/2}}{(2\pi)^D}
			\Gamma(1 - \tfrac{D}{2})\,m^{D-2}
		= \frac{1}{(4\pi)^{D/2}}
			\Gamma(1 - \tfrac{D}{2})\,m^{D-2},
	\end{equation}
	\vspace{-.5\baselineskip}
	\begin{equation}
	%% ref: <https://tex.stackexchange.com/q/387810/193356>
		\raisebox{-.2\height}{
			\feynmandiagram[
				scale=.7
				,small
				,layered layout
				,horizontal=a to b
			]{
				a -- b [dot]
				-- [out=135, in=45, loop
					,min distance=3.5\baselineskip
					] b
				-- c
			};
		}
		= \frac{-i\lambda}{2} \frac{1}{(4\pi)^{D/2}}
			\Gamma(1 - \tfrac{D}{2})\,m^{D-2}
	\end{equation}

	We then have to include counterterm contributions so that the renormalization condition \eqref{eq:renorm_cond} is satisfies; we have:
	\begin{equation}
	%% ref: <https://tex.stackexchange.com/q/387810/193356>
	\begin{aligned}
		-iM(p^2)
		&\sim \hspace{-1em}
		\raisebox{-.2\height}{
			\feynmandiagram[
				scale=.7
				,small
				,layered layout
				,horizontal=a to b
			]{
				a -- b [dot]
				-- [out=135, in=45, loop
					,min distance=3.5\baselineskip
					] b
				-- c
			};
		}\hspace{-1em}
		+ \raisebox{0.\baselineskip}{
			\feynmandiagram[
				scale=.7
				,small
				,layered layout
				,horizontal=a to c
			]{
				a -- b[{small,crossed dot}] -- c,
			};
		}
		= \frac{-i\lambda}{2} \frac{1}{(4\pi)^{D/2}}
				\Gamma(1 - \tfrac{D}{2})\,m^{D-2}
			+ i\pqty{\delta_Z (-p^2) + \delta_m} \\
		&\sim 0
			+ 0\cdot (p^2 + m^2)
			+ \order{p^4}
	\end{aligned}
	\end{equation}
	Therefore,
	\begin{equation}
		\delta_Z = 0,
	\quad
		\delta_m
		= \frac{\lambda}{2} \frac{1}{(4\pi)^{D/2}}
			\Gamma(1 - \tfrac{D}{2})\,m^{D-2}
	\end{equation}

	Alternatively, if we are working in $D = 4 = 3 + 1$ dimensions, it's easier to impose a naïve cutoff $\Lambda$, which gives:
	\begin{equation}
	\begin{aligned}
		\int^\Lambda \frac{k^d \dd{k}}{k^2 + m^2}
		&\sim \int^\Lambda k^{d-2} \dd{k}
			+ \int^\Lambda k^d \dd{k}
				\pqty{
					\frac{1}{k^2 + m^2}
					- \frac{1}{k^2}
				} \\
		&= \int^\Lambda k^{d-2} \dd{k}
			- m^2 \int^\Lambda 
				\frac{k^{d-2} \dd{k}}{k^2 + m^2},
		\quad d = D - 1 = 3 \\
		&= \frac{\Lambda^2}{2}
			- \frac{m^2}{2} \ln \pqty{
				1 + \frac{\Lambda^2}{m^2}
			},
	\end{aligned}
	\end{equation}
	Similarly, with $A(S^3) = 2\pi^2$, we have:
	\begin{equation}
	\begin{aligned}
		\delta_Z = 0,
	\quad
		\delta_m
		&= \frac{\lambda}{2}
			\frac{2\pi^2}{(2\pi)^4} \Bqty{
				\frac{\Lambda^2}{2}
				- \frac{m^2}{2} \ln \pqty{
					1 + \frac{\Lambda^2}{m^2}
				}
			} \\
		&= \frac{\lambda}{32\pi^2} \Bqty{
				\frac{\Lambda^2}{2}
				- \frac{m^2}{2} \ln \pqty{
					1 + \frac{\Lambda^2}{m^2}
				}
			}
	\end{aligned}
	\end{equation}

\end{enumerate}
\printbibliography
\end{document}

### 2020-10-20 alpha/Exam/exam.tex
Rename submodule -> TeXplates & add tweaks
Including:
- build.sh script
- exam.tex

@@
 	\item $M > \abs{Q}$, $r_\pm = M \pm \sqrt{M^2 - Q^2}$, 2 event horizons;
-	\item $M = \abs{Q}$, $r_\pm = M$, 1 event horizons;
-	\item $M < \abs{Q}$, no event horizons! ``Naked'' singularity.
+	\item $M = \abs{Q}$, $r_\pm = M$, 1 event horizon;
+	\item $M < \abs{Q}$, no event horizon! ``Naked'' singularity.
 	\end{enumerate}
@@
 \begin{enumerate}
-\item 1PI: diagrammatic contribution to the (1-particle) propagator that cannot be split into 2 disconnected parts by cutting one line; e.g.\,%
+\item 1PI: diagrammatic correction to the (1-particle) propagator that cannot be split into 2 disconnected parts by cutting one line; e.g.\,%
 	\raisebox{-.4\baselineskip}{
@@
 	\end{equation}
-	The last line is the \textit{Euler's reflection formula}, but here we actually don't need that since the $\Gamma(\tfrac{D}{2})$ factor is canceled by $A(S^d)$. In the end we have:
+	The last line is \textit{Euler's reflection formula}, but here we actually don't need that since the $\Gamma(\tfrac{D}{2})$ factor is canceled by $A(S^d)$. In the end we have:
 	\begin{equation}
@@
 		&= \frac{\lambda}{32\pi^2} \Bqty{
-				\frac{\Lambda^2}{2}
-				- \frac{m^2}{2} \ln \pqty{
+				\Lambda^2
+				- m^2 \ln \pqty{
 					1 + \frac{\Lambda^2}{m^2}

### 2020-10-20 build.sh

@@ -13,8 +13,8 @@ mkdir -p release
 
 # naming: $project/$sub_project/$main.tex
 FILES=$(find . \
-    -regex "./[^/]+/[^/]+/[^/]+.tex" \
-    -not -path "./Templates/*"
+    -regex "./[^/]+/[^/]+/[^/]+\.tex" \
+    -not -path "./TeXplates/*"
 )
 log "Files:"
 echo "$FILES"

### 2021-01-03 HW-AdvancedQFT2020/advqft1/advqft1.tex
Update advqft notes, add YM2 notes
... include more details about:
    - quantum charges
    - FP quantization

@@
 	\end{itemize}
-\pagebreak[3]
+%\pagebreak[3]
 \subsection{Real Scalar in $(3+1)$\,D}
@@
 	\end{equation}
-\pagebreak[3]
+%\pagebreak[3]
 
@@
 	\end{equation}
+	We can write this down without explicit calculations, since we know $\mcal{L}$ itself is a Lorentz scalar, and that's how scalar transforms under Lorentz transformations. \\
 	This gives a boundary term $
@@
 	\begin{equation}
-		Q = \omega_{\mu\nu} M^{\mu\nu},\quad
+		Q
+		= \frac{1}{2}\,
+			\omega_{\mu\nu} M^{\mu\nu},\quad
 		M^{\mu\nu}
 		= - \int \dd[3]{x}
-		x^{[\mu} \pqty{
+			2x^{[[\mu} \pqty{
 				\pdd{0}\phi\,\pd^{\nu]}\phi
@@
 
-	Canonical quantization:
-	\begin{gather}
-		\dot{\phi} = \pdd{0}\phi,\quad
-		\Pi = \pdv{\mcal{L}}{\dot{\phi}}
-		= \dot{\phi},\quad
-		[\phi(\vb{x}),\Pi(\vb{y})]
-		= [\phi,\dot{\phi}](\vb{x})
-		= i\delta(\vb{x} - \vb{y})
-	\end{gather}
-	Other equal-time commutators between $\phi,\Pi$ all just vanish. We have:
+	Note that the canonical momentum:
 	\begin{equation}
+		\varpi
+		= \pdv{\mcal{L}}{\dot{\phi}}
+		= \dot{\phi}
+		= \pd_0\phi
+	\end{equation}
+	It is thus natural to re-organize $M^{0i}$ in the following way:
+	\begin{equation}
+	\begin{aligned}
 		M^{0i} = -M^{i0}
-		= -\frac{1}{2}\,
-		\int \dd[3]{x} \pqty{
-			\dot{\phi}\,\pqty{
+		&= - \int \dd[3]{x} \pqty{
+			\varpi\,\pqty{
 				x^0 \pd^i
@@
 			}\,\phi
-			+ x^i \mcal{L}
-		},\\
+			- x^i \mcal{L}
+		} \\
+		&= - \int \dd[3]{x} \pqty{
+			x^0 \varpi\,\pd^i \phi
+			+ x^i \pqty\big{
+				\varpi\dot{\phi} - \mcal{L}
+			}
+		} \\
+		&= - \int \dd[3]{x} \pqty{
+			x^0 \varpi\,\pd^i \phi
+			+ x^i \mcal{H}
+		} \\
+	\end{aligned}
+	\end{equation}
+
+	We've obtained an interesting result: the expression for the boost generator $M^{i0}$ contains the Hamiltonian density $\mcal{H}$, weighted by the radial distance $x^i$.
+This is natural since a boost does indeed contains time evolution for states away from the origin.
+It's an important result utilized by the so-called \textit{Rindler decomposition}; in fact, $M^{i0}$ becomes the Hamiltonian for an accelerated observer in the Rindler patch\footnote{
+		See the lecture notes of Tom Hartman: \http{hartmanhep.net/topics2015/gravity-lectures.pdf} or Daniel Harlow \arxiv{1409.1231}. 
+	}.
+
+	For $M^{ij}$, we have:
+	\begin{equation}
 		M^{ij}
-		= -\frac{1}{2}\,\int \dd[3]{x}
+		= - \int \dd[3]{x}
 			\dot{\phi}\,\pqty{
@@
 	\end{equation}
+	This is interpreted as the angular momentum of the field $\phi$.
+Suppose $\phi$ is a wave packet localized around $\vb{x}$ with momentum $\approx \vb{p}$, then we have the classical angular momentum up to some factor:
+	\begin{equation}
+		M^{ij}
+		\sim \pqty{
+				x^i p^j
+				- x^j p^i
+			} \int \dd[3]{x}
+				E \phi^2,
+	\quad
+		E = \sqrt{\vb{p}^2 + m^2}
+	\end{equation}
+
+	The $
+		\int \dd[3]{x} E \phi^2
+	$ factor in the above expression is an $\order{1}$ normalization constant for a particle-like wave packet; to see this, note that $\phi\in\mbb{R}$ has a phase factor $
+		\phi
+		\sim a\,e^{+ik\cdot x} + a^\dagger e^{-ik\cdot x}
+		\sim \cos\,(k\cdot x)
+	$,
+	\begin{gather}
+	\small
+		E = \int \dd[3]{x} \mcal{H}
+		= \int \dd[3]{x} \pqty{
+				\frac{1}{2} \dot{\phi}^2
+				+ \frac{1}{2} (\grad{\phi})^2
+				+ \frac{1}{2} m^2 \phi^2
+				+ \cdots
+			}
+		\sim \pqty{E^2 + \vb{p^2} + m^2 + \cdots}
+			\int \dd[3]{x} \frac{1}{2}\,\phi^2,
+	\end{gather}
+	\vspace{-.7\baselineskip}
+	\begin{equation}
+		E\int \dd[3]{x} \phi^2 \sim 1,
+	\end{equation}
+	Indeed, we have: $
+		M^{ij}
+		\sim \pqty{
+				x^i p^j
+				- x^j p^i
+			}
+	$.
+
+	Canonical quantization:
+	\begin{gather}
+		[\phi(\vb{x}),\varpi(\vb{y})]
+		= [\phi(\vb{x}),\dot{\phi}(\vb{y})]
+		= i\delta(\vb{x} - \vb{y})
+	\end{gather}
+	Other equal-time commutators between $\phi,\varpi$ all just vanish.
+Operator products are then regularized by normal ordering: $M\mapsto \normorder{M}$, which can be explicitly implemented by normal ordering of the oscilator modes:
+	\begin{equation}
+		\phi(x)
+		= \int \frac{\dd[3]{k}}{(2\pi)^3}
+			\frac{1}{\sqrt{2E_k}}
+			\pqty{
+				a_{\vb{k}} e^{ik\cdot x}
+				+ a^\dagger_{\vb{k}'} e^{-ik\cdot x}
+			},
+	\quad
+		[a_{\vb{k}}, a^\dagger_{\vb{k}'}]
+		= (2\pi)^3 \delta(\vb{k} - \vb{k}')
+	\end{equation}
+
+	For example, the first term in $M^{0i} = -M^{i0}$ can be expanded as:
+	\begin{equation}
+	\begin{aligned}
+		- x^0 \int \dd[3]{x}
+			\varpi\,\pd^i \phi
+		= x^0 \int \frac{\dd[3]{k}}{(2\pi)^3}\,
+				k^i a^\dagger_k a_k
+		= x^0 P^i
+	\end{aligned}
+	\end{equation}
+	Here $P^\mu$ is the momentum operator on the Hilbert space, promoted from the classical $-i\pd^\mu$. $M^{0i}$ is thus further reduced to:
+	\begin{equation}
+		M^{0i} = -M^{i0}
+		= x^0 P^i - \int \dd[3]{x}
+			x^i \mcal{H}
+	\end{equation}
+
+	We note that this result is almost the classical $
+		x^0 P^i - x^i P^0
+	$, but here $x^i P^0$ is replaced with the integral over energy density $\mcal{H}$.
+The result can be nicely re-written with the stress tensor $T^{\mu\nu}$; just run the Noether's procedure with $\var{x^\mu} = \epsilon^\mu$, then we shall obtain:
+	\begin{equation}
+	\begin{gathered}
+		j'^\mu
+		= \epsilon_\nu T^{\mu\nu},
+	\quad
+		T^{\mu\nu}
+		= \pd^\mu\phi\,\pd^\nu\phi
+			+ \eta^{\mu\nu} \mcal{L},
+	\\
+		Q' = \epsilon_\mu P^\mu,
+	\quad
+		P^\mu
+		= \int \dd[3]{x} T^{\mu 0}
+		= \int \dd[3]{x} \pqty{
+			\pd^0\phi\,\pd^\mu\phi
+			+ \eta^{0\mu} \mcal{L}
+		}
+	\\
+		M^{\mu\nu}
+		= \int \dd[3]{x}
+			2x^{[\mu} T^{\nu]0}
+	\end{gathered}
+	\end{equation}
+	The quantization $M\mapsto \normorder{M}$ is thus reduced to the quantization of $T_{0\nu}$.
+
+	\sidenote{TODO: Detailed analysis! HINT: Ward identity!}
 
@@
 			x^\mu \pd^\nu - x^\nu \pd^\mu
-		} = \frac{1}{2} D^{ij}
-	$ is the Killing vector fields of $\mbb{R}^{3,1}$, hence they naturally follow the commutation relations of $\mfrak{so}(3,1)$ (up to a constant coefficient)\footnote{
+		} = \frac{1}{2} D^{\mu\nu}
+	$ is the Killing vector fields of $\mbb{R}^{3,1}$, hence they naturally follow the commutation relations of $\mfrak{so}(3,1)$ (up to a constant coefficient, or an isomorphism)\footnote{
 		I would like to thank \textit{林般} for pointing this out. 
@@
 	\begin{aligned}
-		[M^{ij}, M^{kl}]
-		&= \frac{1}{4}\,\int \dd[3]{x}
+		[M^{\mu\nu}, M^{\rho\sigma}]
+		&= \int \dd[3]{x}
 			\int \dd[3]{y} \bqty{
-				\dot{\phi} D^{ij}\phi(x),
-				\dot{\phi} D^{kl}\phi(y)
+				\dot{\phi} D^{\mu\nu}\phi(x),
+				\dot{\phi} D^{\rho\sigma}\phi(y)
 			} \\
-		&= \frac{1}{4}\,\int \dd[3]{x}
+		&= \int \dd[3]{x}
 			\dot{\phi}\,\bqty{
-				 D^{ij}, D^{kl}
+				 D^{\mu\nu}, D^{\rho\sigma}
 			}\,\phi

### 2021-01-07 alpha/YangMills2D/ym2d.tex
Update advqft notes, add YM2 notes
... include more details about:
    - quantum charges
    - FP quantization
Update YM2 notes

--- 2020-10-06 Renormalization/wilson.tex
@@
 
-\documentclass[a4paper,10pt]{article}
+\documentclass[a4paper
+	,10pt
+%	,twoside
+]{article}
 
-\input{preamble.tex}
-\input{modules/basics/biblatex.tex}
+\input{../preamble.tex}
+\input{../.modules/basics/biblatex.tex}
 
-\title{A Modern Take on Renormalization}
-%\addbibresource{.bib}
+\title{2D Yang--Mills \\ \& Cohomological Field Theory}
+\addbibresource{ym2d.bib}
 
@@
 
-\usepackage{cancel}
+%\usepackage{cancel}
+\usepackage{xspace}
+\newcommand{\YM}{{\ensuremath{\mrm{YM}_2}}\xspace}
 
@@
 
-\vspace*{-.5\baselineskip}
-	The continuum limit $\Lambda\to\infty$ is \textbf{not} well defined.
-	Renormalization provides a way to \emph{define} the theory when
-	$\Lambda\to\infty$.
-
-	\textbf{My belief:} The only way to fully understand renormalization is
-	through Wilson's arguments; all other ``interpretations'' of
-	renormalization are only \emph{heuristic}.
-
-\textbf{Key words:}
-\begin{itemize}[nosep]
-\item Renormalization group
-\item Counterterms
-\item Regularization and cutoff
-\end{itemize}
+%\vspace*{-.5\baselineskip}
 
@@
 
-\section{References}
+\addtocounter{section}{-1}
+\section{Main References}
+	This review is almost entirely based on the following references:
+	\begin{enumerate}[
+		noitemsep
+		,labelindent=\parindent
+		,align=left
+		,leftmargin=*
+	]
+	\item[\cite{Cordes:1994fc}] \textit{Cordes, Moore, Ramgoolam}, \arxiv{hep-th/9411210}
+	\item[\cite{Witten:1991we}] Witten, \textit{On Quantum Gauge Theories in Two Dimensions}, 1991
+	\end{enumerate}
+	It is basically a condensed, more pedagocial version of \cite{Cordes:1994fc}.
+Many basic facts in this review are therefore uncited to avoid repeated citations of \cite{Cordes:1994fc}.
+All uncited claims, unless otherwise specified, can be traced back to \cite{Cordes:1994fc}.
+\section{Introduction}
+	We start by writing down the usual Yang--Mills action in 2D (\YM), in Euclidean signature:
+	\begin{equation}
+		I_{\YM}
+		= +\frac{1}{8e^2}
+			\int_{\Sigma_T} \dd[2]{x}
+			\sqrt{G}
+			\,\Tr \pqty{F_{ij} F^{ij}},
+	\quad
+		\sqrt{G} = \sqrt{\det G_{ij}}
+	\end{equation}
+	Here we will try follow the convention of \cite{Cordes:1994fc}, despite the fact that it is, unfortunately, not quite self-consistent.
+$\Sigma_T$ stands for the 2D \textit{target}; \sidenote{as we shall see,} in the large $N$ limit, it is possible to realize 2D Yang--Mills as a string theory with worldsheet $\Sigma_W$, as is proposed by D.~Gross and W.~Taylor, among others \cite{Gross:1992tu,Gross:1993hu,Gross:1993yt}.
 
-\noindent \textsl{Ranked by importance:}
-
-	\begin{itemize}
-	\item David Skinner's note:
-	  \begin{itemize}[nosep]
-	  \item \url{https://www.damtp.cam.ac.uk/user/dbs26/AQFT.html}
-	    \begin{itemize}[nosep]
-	    \item \url{https://www.damtp.cam.ac.uk/user/dbs26/AQFT/Wilsonchap.pdf}
-	    \item \url{https://www.damtp.cam.ac.uk/user/dbs26/AQFT/chap5.pdf}
-	    \end{itemize}
-	  \end{itemize}
-	\item Schwartz, Chapter 15
-	\item Peskin \& Schroeder, Chapter 10 \& 12
-	\item Hollowood's book:
-	  \begin{itemize}[nosep]
-	  \item \url{https://arxiv.org/abs/0909.0859}
-	  \item \url{https://link.springer.com/book/10.1007/978-3-642-36312-2}
-	  \end{itemize}
-	\end{itemize}
-
-\section{Wilson's picture}
-	Seed theory parameters (i.e.\ \emph{bare parameters}):
-	$(g_0,\Lambda_0)$, $g = (m,\lambda,\cdots)$ a collection of all
-	possible couplings.
-
+	Note that in 2D, the $\mfrak{g}$-valued curvature form $F = F^a_{ij}\,T_a \dd{x^i} \wedge \dd{x^j}$ is a \textit{top form}; here $T_a$ is the generator of Lie algebra $\mfrak{g} = \mop{Lie} G$, and $G$ is the compact gauge group, e.g.~$G = \mrm{SU}(N)$.
+This means that in 2D, we have:
+	\begin{gather}
+		F = f\mu,\quad f = \hodgedual F,
+	\\
+		\mu = \sqrt{G} \dd[2]{x},\quad
+		F^a_{ij} = \sqrt{G}\,\epsilon_{ij} f^a
+	\end{gather}
+	Here $\mu$ is the volume form on $\Sigma_T$, and $f$ is some $\mfrak{g}$-valued 0-form. The original \YM action can thus be rewritten as:
 	\begin{equation}
-	\begin{aligned}
-	  \phi_{\Lambda_0}(x)
-	  \sim \int^{\Lambda_0} \dd p
-	    e^{ip\cdot x}
-	    \tilde{\phi}(p)
-	  &= \int^{\Lambda} \dd p
-	    e^{ip\cdot x}
-	    \tilde{\phi}(p)
-	    + \int_{\Lambda}^{\Lambda_0} \dd p
-	    e^{ip\cdot x}
-	    \tilde{\phi}(p) \\
-	  &=\colon \phi_{\Lambda}(x) + \chi(x)
-	\end{aligned}
+		I_{\YM}
+		= \frac{1}{4e^2}
+			\int_{\Sigma_T} \dd[2]{x}
+			\sqrt{G}
+			\,\Tr\,(f^2)
+		= \frac{1}{4e^2}
+			\int_{\Sigma_T} \mu \Tr\,(f^2)
 	\end{equation}
 
+	First we would like to examine the $e^2 \to 0$ limit of this theory. This can be achieved by a \textit{Hubbard--Stratonovich transformation}\footnote{
+		See \wikiref{https://en.wikipedia.org/wiki/Hubbard\%E2\%80\%93Stratonovich\_transformation}{Hubbard–Stratonovich transformation}. 
+	}; namely, we introduce an additional $\mfrak{g}$-valued field $\phi$ that serves as a Lagrangian multiplier; consider:
 	\begin{equation}
-	\begin{aligned}
-	  \DD\phi_{\Lambda_0}(x)
-	  \sim \prod_{\norm{p} < \Lambda_0}
-	    \dd{\tilde{\phi}(p)}
-	  &= \prod_{\norm{p} < \Lambda}
-	    \dd{\tilde{\phi}(p)}
-	    \prod_{\Lambda < \norm{p} < \Lambda_0}
-	    \dd{\tilde{\phi}(p)} \\
-	  &\sim
-	    \DD\phi_{\Lambda}(x)\,
-	    \DD\chi(x)
-	\end{aligned}
+		I[\phi,A] = \frac{1}{2} \int \mu\,\pqty{
+				i \Tr\,(\phi f)
+				+ \frac{1}{2}\, e^2 \Tr\,(\phi^2)
+			}
+	\end{equation}
+	Using the functional version of the integral identity: $
+		\int \frac{\dd{x}}{\sqrt{2\pi}}
+			e^{
+				-\frac{1}{2} \pqty\big{
+					\frac{e^2}{2} x^2
+					+ ixy
+				}
+			}
+		= e^{-y^2/(4e^2)}
+	$, it is straightforward to verify that\footnote{
+		See \cite{Witten:1991we} for a more detailed explanation. With $e\mapsto \sqrt{2}\,e,\ y\mapsto 2y$, we recover the original formula in \cite{Witten:1991we}.
+	}:
+	\begin{equation}
+		\int \DD{\phi} e^{-I[\phi,A]}
+		= e^{-I_\YM[A]}
 	\end{equation}
 
+	The advantage of this formulation is that the $e^2 \to 0$ limit becomes non-singular; in fact, now we can simply set $e^2 = 0$, and get:
 	\begin{equation}
-	\begin{aligned}
-	  \mcal{Z} (g_0,\Lambda_0)
-	  &= \int \DD \phi_{\Lambda_0}
-	      e^{iS[\phi_{\Lambda_0}]} \\
-	  &= \int \DD \phi_{\Lambda}
-	    \int \DD \chi\,
-	      e^{iS[\phi_\Lambda + \chi]} \\
-	  &=\colon \int \DD \phi_{\Lambda}\,
-	      e^{iS_{\mathrm{eff}} [\phi_\Lambda]}
-	  =\colon \mcal{Z}\pqty{g(\Lambda),\Lambda}
-	\end{aligned}
+		I[\phi,A]
+		\longto I_0[\phi,A]
+		= \frac{1}{2} \int i \Tr\,(\phi F)
 	\end{equation}
-	Renormalized parameters: $(g,\Lambda)$.
+	This action is in fact \textit{topological}; there is no explicit metric dependence in the action.
+Integrating out $\phi$ fixes $F = 0$, i.e.~we need only sum over the moduli of \textit{flat connections}.
+For a principal $G$ bundle $P\to\Sigma_T$, this is given by:
+	\begin{gather}
+		\mcal{M}_0
+		= \mcal{M}\pqty{F = 0, P\to\Sigma_T}
+		= \Bqty{
+				A\in \mcal{A}(P)
+				\,\Big|\,
+				F(A) = 0
+			} \Big/ \mcal{G}(P)
+		\ \subset\ %
+		\mcal{A}(P) \Big/ \mcal{G}(P)
+	\\[1ex]
+%	\begin{aligned}
+		\mcal{A}(P)
+%		&
+		= \Bqty\Big{
+			\text{all possible connections $A$ on $P$}
+		} \notag\\
+		\mcal{G}(P)
+%		&
+		= \Bqty\Big{
+			\text{all possible gauge transformations on $P$}
+		} \notag
+%		\\
+%	\end{aligned}\notag
+	\end{gather}
 
-	\begin{quote}
-	\textbf{Subtlety:} the notation above is only schematic; in practice we
-	first Wick-rotate to Euclidean signature, so that the momentum cutoff is
-	easily imposed: $\norm{p} = \sqrt{p_0^2 + \vb{p}^2} < \Lambda$. In
-	Lorentzian signature, it's hard to define a covariant cutoff since
-	$p_\mu p^\mu = - p_0^2 + \vb{p}^2$. This process can be made rigorous;
-	just think of the 8-shaped contour in loop integrals.
-	\end{quote}
+	The moduli space $\mcal{M}_0$ is far from trivial.
+Flatness implies that all contractible loops correspond to trivial holonomy; only non-trivial circles, i.e.~elements of the homotopy group $\pi_1(\Sigma_T)$, may have non-trivial holonomy.
+Furthermore, holonomies that differ by a global gauge transformation are by definition, equivalent.
+In fact, we have \cite{michiels2013moduli}:
+	\begin{equation}
+		\mcal{M}_0 = \Hom \pqty\big{
+				\pi_1(\Sigma_T), G
+			} \big/ G
+	\end{equation}
+	Note that this only identifies the topology of $\mcal{M}_0$; to compute the path integral, we need to derive the measure on $\mcal{M}_0$ following the Faddeev--Popov procedure, which is implemented in \cite{Witten:1991we}.
 
-	\textbf{Effective action:}
+	For $e^2 \ne 0$, the action $I[\phi,A]$ is metric dependent.
+Somewhat surprisingly, the path integral still contains information about the topology of $\mcal{M}$.
+This is an example of a so-called \textit{cohomological field theory}.
+	The idea of \cite{Cordes:1994fc} is to start from 2D Yang--Mills as a concrete example, and then use its results to motivate a thorough study of {cohomological field theory}.
+
+	As is summarized in \cite{Cordes:1994fc}, topological field theories (TFT's), largely introduced by E.~Witten, may be grouped into two classes: \textit{Schwarz type} and \textit{cohomological type}\footnote{
+		Cohomological type TFT's are also called \textit{Witten type} TFT's, e.g.~in \cite{Birmingham:1991ty}.
+However, \cite{Cordes:1994fc} chooses to call them \textit{cohomological}, probably to avoid confusion, since Witten has done wonderful work on both types of the theories.
+	}. 
+	Cohomological field theories, including 2D Yang--Mills with coupling $e^2 \ne 0$, are \textit{not} manifestly metric independent; however, they have a Grassmann-odd nilpotent BRST operator $Q$, and physical observables are $Q$-cohomology classes; amplitudes involving these observables are metric independent, thus they are indeed \textit{topological}.
+%	because of decoupling of BRST trivial degrees of freedom.
+
+	On the other hand, \textit{Schwarz type} theories have Lagrangians which are metric independent and hence, formally, the quantum theory is expected to be topological. 
+	Examples of such theories include the $e^2 = 0$ \YM described above, and also the Chern--Simons theory in 3D. Also, there is a 4D analog of the action $I[\phi,A]$, given by:
 	\begin{equation}
-	  S_{\mathrm{eff}}[\phi]
-	  = -i \ln \int \DD \chi
-	      e^{iS[\phi + \chi]} \\
+		\int \pqty\Big{
+			\Tr\,(BF)
+			+ e^2 \Tr\,(B\wedge\hodgedual B)
+		}
 	\end{equation}
-	$\phi = \phi_\Lambda$ is treated as constant when doing
-	$\int \DD \chi$.
+	The first term with $BF$ is also manifestly topological, similar to $e^2 = 0$ \YM; therefore Schwarz type theories are also called $BF$ type theories.
+
+	Following \cite{Cordes:1994fc}, we will first review the exact solution of \YM, and then try to generalize some aspects for a generic cohomological field theory.
+%	
+%	In chapter 4 we relate the Hilbert space of class functions to some simple conformal field theories.
+The main goal is to show how bosonization leads to a natural interpretation of the Hilbert space in terms of string states.
+%	
+%	4.7
+%	
+\section{Exact Solution of 2D Yang Mills}
+\subsection{Canonical Quantization on the Cylinder}
+	One can perform the usual canonical quantization with $I_\YM$ on the cylinder, with coordinates $(x^0,x^1) = (t,x) \in \mbb{R}^1\times S^1$.
+We shall make full use of the gauge redundancies in 2D; recall that a generic gauge transformation can be written as:
 	\begin{equation}
-	\begin{aligned}
-	  \mcal{L}[\phi + \chi]
-	  &= - \frac{1}{2}
-	      \partial_\mu (\phi + \chi)\,
-	      \partial^\mu (\phi + \chi)
-	    - \frac{1}{2} m^2
-	      (\phi + \chi)^2
-	    - \frac{1}{4!} \lambda\,
-	      (\phi + \chi)^4\\
-	  &= \cdots \\
-	  &= \mcal{L}[\phi]
-	    + \Delta\mcal{L} [\phi,\chi]
-	\end{aligned}
+		A'_\mu
+		= g A_\mu g^{-1}
+			+ g\,\pdd{\mu} (g^{-1}),
+	\quad
+		A_\mu = A^a_\mu(t,x),
+	\quad
+		g = e^{-\lambda^a(t,x)\,T_a}
+	\end{equation}
+	It is thus possible to choose the \textit{temporal gauge} $A_0 = 0$, by simply solving a first order ODE of the gauge parameters $\lambda^a(t,x)$, with respect to the variable $x^0 = t$.
+
+	We can further reduce $A_1(t,x)$ with remaining gauge redundancies; with some $t$-independent, but $x$-dependent $g = g(x)$, we can preserve $A_0 = 0$, while reducing $A_1(t,x) = A_1(t)$.
+This is basically the \textit{Coulomb gauge} in 2D, i.e.~we have $\pdd{1} A_1 = 0$.
+
+	We can further simplify the results by working in the \textit{Schr\"odinger picture}.
+A nice treatment of QED from this ``novel'' perspective can be found in \cite{Hatfield:234595}.
+In conventional formulations of QFT, we are used to work in the \textit{Heisenberg} or \textit{interactive picture}, where the fields evolve in time: $A_1 = A_1(t)$ and satisfy some operator equations of motion (EOM's), which for free theories look identical to the classical EOM's.
+Alternatively, we can take the quantum mechanical approach, and decompose the fields at each time slice $t = t_0$ to a set of time-independent energy eigenstates; in the case of \YM, we have $A_1 = \mrm{const}$.
+	The time evolution is then tracked by the \textit{wave functional} $\Psi_t[A_1]$.
+Since the gauge-fixed $A_1$ has no spacetime dependence, we've actually obtained a equivalent 0-dimensional field theory, i.e.~a quantum mechanical system.
+
+	There are still remaining gauge redundancies; with another spacetime independent, \textit{global} gauge transformation, we can rotate $
+		A_1 = A_1^a\,T_a \in \mfrak{g}
+	$ to the \textit{Cartan subalgebra}, i.e.~the maximal abelian subalgebra of $\mfrak{g}$.
+Finally, we demand that $A_1$ is invariant under the \textit{Weyl group}, which is the symmetry of the Cartan subalgebra.
+Therefore, the \textit{physical} Hilbert space of \YM consists of states given by:
+	\begin{equation}
+		\Psi[A_1],\quad
+		A_1
+		= A_1^a\,T_a
+		\in \textsl{Cartan} \,\Big/ \textsl{Weyl}
 	\end{equation}
 
+	Alternatively, we can also work with a partial gauge fixing, e.g.~we only impose the temporal gauge $A_0 = 0$, and try to solve for $\Psi_t[A_1(x)]$ by looking at the ``Maxwell's equation" in 2D.
+The time evolution is taken care of by the Schr\"odinger equation for $\Psi_t$; for now we need only look at the spatial constraints.
+We have:
+	\begin{gather}
+		D_1 F_{10} = 0
+	\label{eq:gauss_law_constraint}
+	\\[.5ex]
+		D_\mu = \pdd{\mu} + A^a_\mu\,T_a,
+	\quad
+		F_{\mu\nu} = [D_\mu,D_\nu]
+	\end{gather}
+	This is simply the \YM version of the \textit{Gauss's law} $\vec{\nabla}\cdot\vec{E} = 0$.
+
+	One can think of the Gauss's law constraint as the result of integrating out $A_0$, which imposes it's EOM $\fdv{I_\YM}{A_0} = 0$, which is precisely \eqref{eq:gauss_law_constraint}. 
+	However, for a gauged system, there are subtleties that we need to look out for.
+One should account for the gauge volume, which can be treated properly with Faddeev--Popov path integral; and the proper way to implement the constraints is through BRST quantization.
+
+	Fortunately, the Gauss's law constraint \textit{does} work in this example.
+In fact, if we solve the Gauss's law constraint as an operator equation of $A_1$, we will get further gauge-fixing \cite{Hatfield:234595}.
+	Alternatively, if we ignore the constraint and proceed with canonical quantization, which might be more convenient in some cases, we would expect \textit{unphysical} degrees of freedom like \textit{null states} to show up, due to the unfixed gauge redundancies.
+The constraint can then be utilized to identify \textit{physical} degrees of freedom, by demanding that it annilates physical states:
 	\begin{equation}
-	  S_{\mathrm{eff}}[\phi_\Lambda]
-	  = S[\phi_\Lambda]
-	    - i \ln \int \DD \chi
-	      e^{i\,\Delta S[\phi_\Lambda + \chi]} \\
+		D_1 F_{10} \ket{\Psi} = 0
+	\label{eq:gauss_law_constraint_state}
+	\end{equation}
+	Note that this idea is very much similar to \textit{old covariant quantization} and the \textit{Virasoro constraint} in string theory \cite{Polchinski:1998rq}.
+Again, for a more rigorous treatment, we should turn to the BRST cohomology, but for now this is sufficient.
+In fact, we can actually proved \eqref{eq:gauss_law_constraint_state} by demanding the wave functional $\Psi[A_1(x)]$ to be gauge-invariant under the remaining gauge transformations \cite{Hatfield:234595}:
+	\begin{equation}
+		0 = \var{\Psi[A_1(x)]}
+		= \sidenote{...}
 	\end{equation}
 
-	If $\Lambda \lesssim \Lambda_0$, then $S_{\mathrm{eff}}$ is almost
-	the same as the original $S$, with minor corrections from the
-	$\int \DD\chi$ term. Note that in our regularization scheme there will
-	be no mixed terms of $\phi$ and $\chi$ in the effective action,
-	since they have orthogonal Fourier modes.
+	To actually solve \eqref{eq:gauss_law_constraint_state}, we shall work in the $A_1(x)$ basis, with $\Psi[A_1(x)] = \braket{A_1(x)}{\Psi}$. The canonical momentum operator is then given by:
+	\begin{equation}
+		E = \fdv{A_1},
+	\quad
+		\bqty{
+			E(x), A_1(x')
+		} = \delta(x - x')
+	\end{equation}
+	Just like the usual quantum mechanical $P = - i\pdv{X}$; the $(-i)$ factor is gone since we are working in Euclidean signature. \sidenote{Just like Schr\"odinger, but with path-ordering...}
 
-	Note that $\mcal{Z}$ clearly does not depend on the intermediate scale $\Lambda$, we have:
-	\begin{equation}
-	  0
-	  = \Lambda \dv{}{\Lambda}\,
-	    \mcal{Z}\pqty{g(\Lambda),\Lambda}
-	  = \pqty{
-	      \Lambda \pdv{}{\Lambda}
-	      + \Lambda \pdv{g^{(i)}}{\Lambda}
-	        \pdv{}{g^{(i)}}
-	    }
-	    \mcal{Z}\pqty{g(\Lambda),\Lambda}
-	\end{equation}
-	This is an example of a \textbf{RG Equation}.
-\section{Perturbative Renormalization}
-	However, in naïve perturbation theory, we wish to complete the entire
-	path integral $\mcal{Z} (g_0,\Lambda_0)$. We can think of this as
-	integrating out more and more high energy modes, until we reach the IR
-	scale $\Lambda \to 0$.
-
-	When $\Lambda \ll \Lambda_0$, we have no reason to believe the
-	renormalized couplings $g(\Lambda)$ are close to the original
-	couplings $g_0$ at $\Lambda_0$. In fact, they may differ by a large
-	(but finite) renormalization factor $Z$: $g_0 = Zg$.
-
-\subsection{Counterterms}
-	In the above analysis, the theory flows from UV to IR. However, in
-	reality, the IR results are known from experiments, and we are trying to
-	\emph{extrapolates} from IR to UV.
-
-	We achieve this by \emph{tuning} the bare parameters $(g_0,\Lambda_0)$
-	so that after RG flow, the IR results fit our experimental observations.
-	If the IR couplings $g(\Lambda)$ are finite and small, then since
-	$\Lambda \ll \Lambda_0$, we expect $g_0$ to be very large.
-
-	We often \emph{split} $g_0$ into 2 parts for convenience:
-	\begin{equation}
-	  g_0 = g + \var{g}
-	  = g + (Z - 1)\,g
-	\end{equation}
-	$\var{g}$ is the so-called \emph{counterterm}; intuitively, it's the
-	(large) correction that gets integrated out when we go from
-	$\Lambda_0$ all the way to IR.
-
-	Basically, we have the following procedure:
-
-	\begin{figure}[!h]
-	\centering
-	\includegraphics[width=.5\linewidth]{img/RG-process.png}
-	\end{figure}
-
-	\begin{enumerate}[noitemsep,midpenalty=100]
-	\setcounter{enumi}{-1}
-
-	\item
-	  Select some UV parameters $(g_0,\Lambda_0)$
-	\item
-	  Perform the RG flow: $(g_0,\Lambda_0)\to (g,\Lambda)$
-	\item
-	  Tune (redefine) $g_0$ so that $(g,\Lambda)$ matches with
-	  experiments
-	\item
-	  Use the tuned data to predicts phenomena at a different scale
-	  $(g',\Lambda')$
-	\end{enumerate}
-
-	Note that the tuning of UV parameters $g_0$ is \emph{far from unique!}
-	This is easy to understand: many UV theories might flow to the same IR
-	theory. For this reason, some would say that RG is a \emph{semi-group}.
-
-	However, for a \emph{renormalizable} theory, we can restrict the tuning
-	to a \emph{finite} dimensional subspace formed by the \emph{relevant}
-	couplings, since most other parameters $g^{(i)}$ are \emph{irrelevant}
-	and get suppressed by $\Lambda/\Lambda_0$ in the IR. After such
-	restriction to a relevant subspace, the RG flow is a group, and we can
-	reverse the flow to \emph{extrapolate} towards UV.
-
-\subsection{Perturbation}
-
-	The above results are non-perturbative and should always hold.
-	Perturbation theory is only a way to calculate the RG flow from UV to
-	IR; it is reliable only if the IR coupling $g$ is sufficiently small.
-	In this case we can tune $(g_0,\Lambda_0)$ with the following
-	recursive / iterative algorithm:
-
-	\begin{enumerate}[noitemsep]
-	\item
-	  Perturbative calculation of RG flow:
-	  $(g_0,\Lambda_0)\to (g,\Lambda)$ at $\order{g^n}$
-	\item
-	  Tune (redefine) $(g_0,\Lambda_0)$ by adding counterterms, so that
-	  $(g,\Lambda)$ matches with experiments
-	\item
-	  Increase order $n$ and go to step 1
-	\end{enumerate}
-
-	The (non-)renormalizability of a theory is evident in the perturbative
-	expansion, by counting the \textbf{superficial degrees of divergence}
-	$D$ of the Feynman diagrams. Basically,
-
-	\begin{itemize}
-	\item
-	  Interaction vertices create loops, and loops create UV divergences.
-	  Higher order interaction vertices create more loops, which lead to
-	  more divergences.
-	\item
-	  External lines suppress UV divergences by factors like
-	  $\frac{1}{\cancel{p}}$ or $\frac{1}{p^2}$.
-	\end{itemize}
-
-	For a renormalizable theory, there will be no divergence for diagrams
-	with a sufficient number $E$ of external legs; for a
-	non-renormalizable theory, however, there will always be divergences, no
-	matter how large $E$ is.
-
-\subsection{Renormalization Schemes}
-
-	There is a subtlety in the above procedure: how do we actually relate IR
-	parameters $(g,\Lambda)$ with actual physical quantities,
-	e.g.~amplitudes $\mcal{M}(\mu)$?
-
-	In fact, we've assumed that $(g,\Lambda)_{\Lambda\to 0}$ gives the
-	physical couplings that we are familiar with, e.g.~mass, electric charge
-	and so on. This is not quite true, since physical quantities are
-	actually defined with scattering amplitudes. There are different choices
-	of relating $g$ with physical observables; this lead to various
-	renormalization schemes:
-
-	\begin{itemize}[nosep]
-
-	\item
-	  On-shell / pole-mass scheme
-	\item
-	  Minimal subtraction ($\mathrm{MS}$) \& modified MS
-	  ($\overline{\mathrm{MS}}$)
-	\end{itemize}
-
-	\hypertarget{renormalizability}{%
-	\section{Renormalizability}\label{renormalizability}}
-
-	Most parameters $g^{(i)}$ are, in fact, \emph{irrelevant} --- such
-	terms in the Lagrangian get suppressed by $\Lambda/\Lambda_0$ in IR.
-	If the IR theory has only \emph{relevant} couplings, then one should be
-	able to recover their physical values by tuning a finite amount of
-	relevant couplings in the UV, and usually the tuning is unique. This is
-	the defining characteristic of a \textbf{renormalizable} theory.
-	Basically, this means that we can naturally obtain a UV theory by
-	extrapolation.
-
-	\begin{quote}
-	However, the tuning process described above might encounter some serious
-	obstruction: the tuned $g_0$ could blow up at some finite
-	$\Lambda_{\mathrm{UV}}$; this is the so-called \emph{Landau pole}.
-	This tells us that the theory only works under some
-	$\Lambda_{\mathrm{UV}}$, i.e.~it is not \emph{UV complete}; it's only
-	an \emph{effective} theory. One have to ``embed'' this Lagrangian into a
-	bigger theory that works beyond $\Lambda_{\mathrm{UV}}$; this is the
-	non-trivial \emph{UV completion} of an effective theory.
-	\end{quote}
-
-	On the other hand, a theory is \textbf{non-renormalizable} if it
-	contains irrelevant couplings in the IR. In this case the IR parameters
-	$g$ depend sensitively on small perturbations of the UV parameters
-	$g_0$, and one has to tune infinitely many bare parameters to obtain
-	the physical IR values. Such theory is hardly \emph{fundamental}, since
-	it depends on infinitely many parameters; but it's a good
-	\emph{effective theory} nonetheless.
-
-\section{Effective Action}
-
-	Furthermore, after $\phi_\Lambda$ is completely integrated out, we
-	have:
-
-	\begin{equation}
-	  S_{\mathrm{eff}}[\phi] \to W,\quad
-	  Z(g_0,\Lambda_0) = e^{iW}
-	\end{equation}
-	Note that $W$ no longer has any $\phi$ dependence, but it is a
-	function of $(g_0,\Lambda_0)$, which in turn is tuned by physical
-	$(g,\Lambda)$. $W$ in fact contains all information about the seed
-	theory, labeled by $(g_0,\Lambda_0)$. To extract this information, we
-	usually perturb the original action $S[\phi]$ with a source term; then
-	we have:
-
-	\begin{equation}
-	  S[\phi,J]
-	  = S[\phi] + \int \dd{x}\,J(x)\,\phi(x),\quad
-	  W \to W[J]
-	\end{equation}
-
-	Expand $W[J]$ in terms of $J$-modes, and its coefficient gives us
-	physical coupling constants in the IR. More precisely, we can define the Legendre-transformed $\Gamma[\varphi]$.
+\raggedright
 

### 2021-01-09 alpha/YangMills2D/ym2d.tex
Update notes, now with complete solution of YM2

@@
 %%% ID: sensitive, do NOT publish!
-%\InputIfFileExists{../id.tex}{}{}
+\InputIfFileExists{id.tex}{}{}
 
@@
 
-\addtocounter{section}{-1}
-\section{Main References}
+%\addtocounter{section}{-1}
+\section*{Main References}
 	This review is almost entirely based on the following references:
@@
 All uncited claims, unless otherwise specified, can be traced back to \cite{Cordes:1994fc}.
+However, it is highly possible that I, in my infinite stupidity, misunderstood some ideas from \cite{Cordes:1994fc}; so please feel free to point out my mistakes.
 \section{Introduction}
@@
 		I_{\YM}
-		= +\frac{1}{8e^2}
+		= +\frac{1}{4e^2}
 			\int_{\Sigma_T} \dd[2]{x}
 			\sqrt{G}
-			\,\Tr \pqty{F_{ij} F^{ij}},
+			\,\Tr \pqty{F_{\mu\nu} F^{\mu\nu}},
 	\quad
-		\sqrt{G} = \sqrt{\det G_{ij}}
+		\sqrt{G} = \sqrt{\det G_{\mu\nu}}
 	\end{equation}
 	Here we will try follow the convention of \cite{Cordes:1994fc}, despite the fact that it is, unfortunately, not quite self-consistent.
-$\Sigma_T$ stands for the 2D \textit{target}; \sidenote{as we shall see,} in the large $N$ limit, it is possible to realize 2D Yang--Mills as a string theory with worldsheet $\Sigma_W$, as is proposed by D.~Gross and W.~Taylor, among others \cite{Gross:1992tu,Gross:1993hu,Gross:1993yt}.
+$\Sigma_T$ stands for the 2D \textit{target}; in the large $N$ limit, it is possible to realize \YM as a string theory with worldsheet $\Sigma_W$, as is proposed by D.~Gross and W.~Taylor, among others \cite{Gross:1992tu,Gross:1993hu,Gross:1993yt}.
 
-	Note that in 2D, the $\mfrak{g}$-valued curvature form $F = F^a_{ij}\,T_a \dd{x^i} \wedge \dd{x^j}$ is a \textit{top form}; here $T_a$ is the generator of Lie algebra $\mfrak{g} = \mop{Lie} G$, and $G$ is the compact gauge group, e.g.~$G = \mrm{SU}(N)$.
+	Note that in 2D, the $\mfrak{g}$-valued curvature form $F = F^a_{\mu\nu}\,T_a \dd{x^\mu} \wedge \dd{x^\nu}$ is a \textit{top form}; here $T_a$ is the generator of Lie algebra $\mfrak{g} = \mop{Lie} G$, and $G$ is the compact gauge group, e.g.~$G = \mrm{SU}(N)$.
 This means that in 2D, we have:
@@
 		\mu = \sqrt{G} \dd[2]{x},\quad
-		F^a_{ij} = \sqrt{G}\,\epsilon_{ij} f^a
+		F^a_{\mu\nu} = \sqrt{G}\,\epsilon_{\mu\nu} f^a
 	\end{gather}
@@
 		I_{\YM}
-		= \frac{1}{4e^2}
+		= \frac{1}{2e^2}
 			\int_{\Sigma_T} \dd[2]{x}
@@
 			\,\Tr\,(f^2)
-		= \frac{1}{4e^2}
+		= \frac{1}{2e^2}
 			\int_{\Sigma_T} \mu \Tr\,(f^2)
+	\label{eq:scalar_action}
 	\end{equation}
@@
 	\begin{equation}
-		I[\phi,A] = \frac{1}{2} \int \mu\,\pqty{
-				i \Tr\,(\phi f)
-				+ \frac{1}{2}\, e^2 \Tr\,(\phi^2)
+		I[\phi,A] = \int \pqty{
+				i \Tr\,(\phi F)
+				+ \frac{1}{2}\, e^2\mu \Tr\,(\phi^2)
 			}
+	\label{eq:convenient_action}
 	\end{equation}
 	Using the functional version of the integral identity: $
-		\int \frac{\dd{x}}{\sqrt{2\pi}}
+		\int \dd{x}
 			e^{
-				-\frac{1}{2} \pqty\big{
-					\frac{e^2}{2} x^2
-					+ ixy
+				- \frac{e^2}{2} x^2
+				- ixy
 			}
-			}
-		= e^{-y^2/(4e^2)}
-	$, it is straightforward to verify that\footnote{
-		See \cite{Witten:1991we} for a more detailed explanation. With $e\mapsto \sqrt{2}\,e,\ y\mapsto 2y$, we recover the original formula in \cite{Witten:1991we}.
-	}:
+		\sim e^{-y^2/(2e^2)}
+	$, it is straightforward to verify that \cite{Witten:1991we}, up to an overall coefficient,
 	\begin{equation}
 		\int \DD{\phi} e^{-I[\phi,A]}
-		= e^{-I_\YM[A]}
+		\sim e^{-I_\YM[A]}
 	\end{equation}
@@
 		\longto I_0[\phi,A]
-		= \frac{1}{2} \int i \Tr\,(\phi F)
+		= \int i \Tr\,(\phi F)
+	\label{eq:top_action}
 	\end{equation}
 	This action is in fact \textit{topological}; there is no explicit metric dependence in the action.
+The measure $\mu$ comes with $e^2$ in the $I[\phi,A]$ action; setting $e^2 \to 0$ eliminates the metric dependence.
 Integrating out $\phi$ fixes $F = 0$, i.e.~we need only sum over the moduli of \textit{flat connections}.
 For a principal $G$ bundle $P\to\Sigma_T$, this is given by:
-	\begin{gather}
+	\begin{equation}
 		\mcal{M}_0
@@
 		\mcal{A}(P) \Big/ \mcal{G}(P)
-	\\[1ex]
+	\end{equation}
+	\vspace{-1.2\baselineskip}
+	\begin{gather}
 %	\begin{aligned}
@@
 			\text{all possible connections $A$ on $P$}
-		} \notag\\
+		} \notag
+	\\
 		\mcal{G}(P)
@@
 
-	As is summarized in \cite{Cordes:1994fc}, topological field theories (TFT's), largely introduced by E.~Witten, may be grouped into two classes: \textit{Schwarz type} and \textit{cohomological type}\footnote{
+	As is summarized in \cite{Cordes:1994fc}, \textit{topological field theories} (TFT's), largely introduced by E.~Witten, may be grouped into two classes: \textit{Schwarz type} and \textit{cohomological type}\footnote{
 		Cohomological type TFT's are also called \textit{Witten type} TFT's, e.g.~in \cite{Birmingham:1991ty}.
@@
 	Cohomological field theories, including 2D Yang--Mills with coupling $e^2 \ne 0$, are \textit{not} manifestly metric independent; however, they have a Grassmann-odd nilpotent BRST operator $Q$, and physical observables are $Q$-cohomology classes; amplitudes involving these observables are metric independent, thus they are indeed \textit{topological}.
+Generally speaking, a TFT need \textit{not} be metric independent; the important thing is that it computes \textit{topological invariants}.
 %	because of decoupling of BRST trivial degrees of freedom.
@@
 	\begin{equation}
+	\begin{aligned}
 		A'_\mu
-		= g A_\mu g^{-1}
-			+ g\,\pdd{\mu} (g^{-1}),
-	\quad
+		&= g A_\mu g^{-1}
+			+ g\,\pdd{\mu} (g^{-1}) \\
+		&\simeq A_\mu
+			+ D_\mu\circ\lambda,
+	\end{aligned}
+	\qquad
 		A_\mu = A^a_\mu(t,x),
 	\quad
-		g = e^{-\lambda^a(t,x)\,T_a}
+		g = e^{-\lambda^a(t,x)\,T_a},
 	\end{equation}
-	It is thus possible to choose the \textit{temporal gauge} $A_0 = 0$, by simply solving a first order ODE of the gauge parameters $\lambda^a(t,x)$, with respect to the variable $x^0 = t$.
+	\vspace{-1.2\baselineskip}
+	\begin{gather}
+		D_\mu = \pdd{\mu} + A_\mu^a\,T_a,
+	\\[1ex]
+		\pqty{D_\mu\circ\lambda}^a
+		= \pdd{\mu} \lambda^a
+			+ A_\mu^b\,f\id{^a_{bc}} \lambda^c,
+	\quad
+		(T_b)\id{^a_c} = f\id{^a_{bc}}
+	\end{gather}
+	Here $D_\mu$ is the $\mfrak{g}$-valued covariant derivative; it acts on the $\mfrak{g}$-valued gauge parameters $\lambda^a(t,x)$ by the adjoint representation $(T_b)\id{^a_c} = f\id{^a_{bc}}$. 
+	It is thus possible to choose the \textit{temporal gauge} $A_0 = 0$, by simply solving a first order ODE of $\lambda^a(t,x)$, with respect to the variable $x^0 = t$.
 
@@
 
-	We can further simplify the results by working in the \textit{Schr\"odinger picture}.
-A nice treatment of QED from this ``novel'' perspective can be found in \cite{Hatfield:234595}.
+	Further simplifications can be achieved by working in the \textit{Schr\"odinger picture}, or \textit{Schr\"odinger representation}.
+A nice treatment of 4D Yang--Mills from this ``novel'' perspective can be found in \cite{Hatfield:234595}.
 In conventional formulations of QFT, we are used to work in the \textit{Heisenberg} or \textit{interactive picture}, where the fields evolve in time: $A_1 = A_1(t)$ and satisfy some operator equations of motion (EOM's), which for free theories look identical to the classical EOM's.
@@
 		\in \textsl{Cartan} \,\Big/ \textsl{Weyl}
+	\label{eq:hilbert_space}
 	\end{equation}
@@
 We have:
-	\begin{gather}
-		D_1 F_{10} = 0
-	\label{eq:gauss_law_constraint}
-	\\[.5ex]
-		D_\mu = \pdd{\mu} + A^a_\mu\,T_a,
+	\begin{equation}
+		D_1 F_{10} = 0,
 	\quad
 		F_{\mu\nu} = [D_\mu,D_\nu]
-	\end{gather}
-	This is simply the \YM version of the \textit{Gauss's law} $\vec{\nabla}\cdot\vec{E} = 0$.
+	\label{eq:gauss_law_constraint}
+	\end{equation}
+	This is simply the \YM version of the \textit{Gauss's law} $\vec{\nabla}\cdot\vec{E} = 0$. In \YM, we have only one $\mfrak{g}$-valued component of the field strength:
+	\begin{equation}
+		E = E^a T_a = F_{10}
+	\end{equation}
 
@@
 	However, for a gauged system, there are subtleties that we need to look out for.
-One should account for the gauge volume, which can be treated properly with Faddeev--Popov path integral; and the proper way to implement the constraints is through BRST quantization.
+One should account for the gauge volume, which can be treated properly with Faddeev--Popov path integral, and the proper way to implement the constraints is through BRST quantization.
 
-	Fortunately, the Gauss's law constraint \textit{does} work in this example.
+	Fortunately, the na\"ive Gauss's law constraint \textit{does} work in this example.
 In fact, if we solve the Gauss's law constraint as an operator equation of $A_1$, we will get further gauge-fixing \cite{Hatfield:234595}.
@@
 	\begin{equation}
-		D_1 F_{10} \ket{\Psi} = 0
+		D_1 \circ E \ket{\Psi} = 0,
+	\quad E = F_{10}
 	\label{eq:gauss_law_constraint_state}
@@
 Again, for a more rigorous treatment, we should turn to the BRST cohomology, but for now this is sufficient.
-In fact, we can actually proved \eqref{eq:gauss_law_constraint_state} by demanding the wave functional $\Psi[A_1(x)]$ to be gauge-invariant under the remaining gauge transformations \cite{Hatfield:234595}:
-	\begin{equation}
-		0 = \var{\Psi[A_1(x)]}
-		= \sidenote{...}
-	\end{equation}
 
-	To actually solve \eqref{eq:gauss_law_constraint_state}, we shall work in the $A_1(x)$ basis, with $\Psi[A_1(x)] = \braket{A_1(x)}{\Psi}$. The canonical momentum operator is then given by:
+	In fact, we can actually proved \eqref{eq:gauss_law_constraint_state} by demanding the wave functional $\Psi[A_1(x)]$ to be gauge-invariant \cite{Hatfield:234595}; we shall work in the $A_1(x)$ basis, with $\Psi[A_1(x)] = \braket{A_1(x)}{\Psi}$.
+	The canonical momentum operator is then given by:
 	\begin{equation}
@@
 	\end{equation}
-	Just like the usual quantum mechanical $P = - i\pdv{X}$; the $(-i)$ factor is gone since we are working in Euclidean signature. \sidenote{Just like Schr\"odinger, but with path-ordering...}
+	Just like the usual quantum mechanical $P = - i\pdv{X}$; the $(-i)$ factor is gone since we are working in Euclidean signature.
+
+	We demand that $\Psi[A_1(x)]$ is gauge-invariant under the \textit{remaining} $t$-independent gauge transformations, $\lambda = \lambda(x)$:
+	\begin{equation}
+	\begin{aligned}
+		0 = \var{\Psi[A_1(x)]}
+		&= \int \dd{x}
+			\fdv{\Psi}{A_1(x)} \var{A_1(x)},
+		\quad \var{A_1(x)} = D_1 \circ \lambda(x) \\
+		&= -\int \dd{x}
+			\lambda(x)\,
+			\pqty{D_1 \circ \fdv{A_1(x)}}
+			\Psi[A_1(x)],
+		\quad E = \fdv{A_1(x)} \\
+		&= -\int \dd{x}
+			\lambda(x)\,
+			\pqty{D_1 \circ E}\,
+			\Psi[A_1(x)],
+		\quad \forall\ \lambda(x)
+	\end{aligned}
+	\end{equation}
+	Indeed this is \eqref{eq:gauss_law_constraint_state} in the $A_1(x)$ basis.
+The formal solution of \eqref{eq:gauss_law_constraint_state} is quite similar to the Schr\"odinger equation, but with path-ordering instead of time-ordering \cite{Minahan:1993np}:
+	\begin{equation}
+		\Psi = \Psi[W],
+	\quad
+		W = \mcal{P} \exp \int_0^L A_1(x)
+	\label{eq:gauss_law_solution}
+	\end{equation}
+
+	From \eqref{eq:gauss_law_solution} we see that in fact there is no direct dependence of $A_1(x)$ in $\Psi[A_1(x)]$; it only depends on the holonomy $W$ around the $S^1$ circle.
+Note that $W$ is similar to the \textit{Wilson loop} operator, but not quite, due to the lack of a trace $\Tr$.
+Such $W$ is not exactly gauge-invariant, but in fact gauge-covariant with respect to the base point:
+	\begin{equation}
+		W' = g_0 W g_0^{-1},
+	\quad
+		g_0 = g(x = 0)
+	\end{equation}
+	Hence further demanding invariance under global gauge transformations requires that $\Psi$ only depends on the \textit{conjugacy class} of $W$. Again we recover \eqref{eq:hilbert_space}, namely,
+	\begin{empheq}{equation}
+		\textbf{
+			The Hilbert space of \YM is the space of \textit{class functions} on $G$
+		}
+	\end{empheq}
+
+	By the Peter--Weyl theorem for
+$G$ compact we can decompose the Hilbert space by the unitary irreducible
+representations (\textit{irreps}) $\{R\}$ of $G$. 
+	Consequently, a natural basis for the Hilbert space is provided by the \textit{characters} $\{\chi_R\}$ of the irreps; thus we have, relative to the $W$ basis,
+	\begin{equation}
+		\braket{W}{R}
+		= \chi_R (W)
+		= \Tr_R (W)
+	\end{equation}
+	This is the wave function of the $R$ basis.
+	Here $\Tr_R$ denotes trace with respect to the irrep $R$; recall that $W$ is $\mfrak{g}$-valued and do not have a well-defined trace until we specify a irrep, in this case $R$.
+This is the gauge-invariant Wilson loop operator.
+Note that we are considering pure \YM without matter; the irrep $R$ is not some \textit{a priori} matter representation, but arises naturally as we consider class functions on $G$.
+\sidenote{This is kind of mysterious; does it has a physical interpretation, e.g.~like sum over possible matter representations?}
+\subsection{Hamiltonian and the Dynamics}
+	Let us now find the Hamiltonian for this theory. We are familiar with the the Hamiltonian density in 4D: $
+		\frac{e^2}{2} \pqty\big{
+			\vec{E}^2 + \vec{B}^2
+		}
+	$; here in 2D, we do not have the magnetic field $\vec{B}$, just a one component $\mfrak{g}$-valued $E = E^a T_a = F_{10}$. Therefore,
+	\begin{gather}
+		H = \frac{e^2}{2} \int \dd{x} \Tr E^2
+		= \frac{e^2}{2} \int \dd{x}
+			\delta^{ab}
+			\fdv{A_1^a(x)}
+			\fdv{A_1^b(x)}
+		\to \frac{1}{2}\,e^2 L
+			\Tr \pqty{W \pdv{W}}^2,
+	\\[1ex]
+		E_a = \fdv{A^a_1(x)}
+		\to T_a W \pdv{W},
+	\quad
+		\Tr\,(T_a T_b) = \delta_{ab}
+	\end{gather}
+	Note that we've followed a more convenient trace convention. 
+	In the last step we've restricted to the physical Hilbert space with $\Psi = \Psi(W)$. Consider $H$ action on the basis $
+		\braket{W}{R}
+		= \chi_R (W)
+		= \Tr_R (W)
+	$, we have:
+	\begin{equation}
+		E_a\, \chi_R (W)
+		= E_a \Tr_R (W)
+		= \Tr_R (T_a W),
+	\end{equation}
+	\vspace{-.9\baselineskip}
+	\begin{equation}
+	\begin{aligned}
+		H\, \chi_R (W)
+		&= \frac{1}{2}\,e^2 L
+			\Tr_R \pqty\big{\delta^{ab} T_a T_b W} \\
+		&= \frac{1}{2}\,e^2 L\,
+			\pqty\big{\delta^{ab} T_a T_b}_R
+			\Tr_R (W) \\
+		&= \frac{1}{2}\,e^2 L
+			C_2(R)\,\chi_R (W),
+	\end{aligned}
+	\end{equation}
+	\vspace{-.3\baselineskip}
+	\begin{equation}
+		C_2(R)
+		= \pqty\big{\delta^{ab} T_a T_b}_R
+	\end{equation}
+	Here $C_2(R)$ is the
+\textit{quadratic Casimir} of the irrep $R$; it is proportional to $\idty_R$, or can be treated as a $c$-number when restricted to the irrep. We find out that:
+	\begin{empheq}{equation}
+		\textbf{The Hamiltonian $H$ is diagonalized in the $R$ basis and $\propto C_2$}
+	\end{empheq}
+	\vspace{-.3\baselineskip}
+	\begin{equation}
+		H = \frac{1}{2}\,e^2 L C_2
+	\end{equation}
+\subsection{Basic Amplitudes}
+	Having diagonalized the Hamiltonian, we can immediately write down the $W$ basis propagator by summing over the $R$ basis; we have:
+	\begin{gather}
+	\begin{aligned}
+		\mel*{W_1}{e^{-HT}}{W_2}
+		&= \sum_R
+			\braket{W_1}{R\,}
+			e^{-H(R)\,T}
+			\braket{R}{W_2} \\
+		&= \sum_R
+			\chi_R(W_1)\,
+			\chi_R(W_2^\dagger)\,
+			e^{-\frac{1}{2}\,e^2 a\,C_2(R)}
+		= Z(W_1,W_2;a),
+	\end{aligned}
+	\\[.3ex]
+		a = LT,
+	\quad
+		\chi_R^\dagger(W)
+		= \pqty{\Tr_R W}^\dagger
+		= \Tr_R (W^\dagger)
+		= \chi_R(W^\dagger)
+	\end{gather}
+	This is the \textbf{cylinder amplitude}. 
+	Note that the combination
+$\frac{1}{2} e^2 a$ enters
+together, where $a = LT$ is the area of the cylinder; this is evident from the action $I[\phi,A]$ in \eqref{eq:convenient_action}, where $e^2 \mu$ comes together as a parameter.
+The area dependence is also evident from the scalar action \eqref{eq:scalar_action}, where we that the theory is invariant under \textit{area preserving diffeomorphism}, $\mop{SDiff}(\Sigma_T)$.
+From now on we will absorb $\frac{e^2}{2}$ into $a$, and it will be the only dimensionful parameter of the theory.
+
+	By the orthogonality relations of characters, it is straightforward to verify that the propagator satisfy the \textit{gluing property}:
+	\begin{equation}
+		\int \dd{W}
+			Z(W_1,W;T_1)\,Z(W,W_2;T_2)
+		= Z(W_1,W_2;T_1 + T_2)
+	\end{equation}
+	We see that \YM has very similar properties as those from the categorical approach of CFT and TFT, given by Segal and Atiyah \cite{Segal1988,Atiyah1988}.
+
+	With the gluing property, we can see what happens when one end of the cylinder shrinks to zero size; this is achieved by gluing one cylinder with finite size $a$, with another one that has $a'\to 0$.
+As $a'\to 0$, the corresponding amplitude should be well approximated by the topological action $I_0[\phi,A]$ given in \eqref{eq:top_action}; as we've mentioned before, integrating out $\phi$ sets $F = 0$, which in turn forces the holonomy $W \equiv \idty$.
+The wave function is then given by a Dirac delta function:
+	\begin{equation}
+		\Psi(W) = \delta(W - \idty)
+	\end{equation}
+	This is, up to an overall coefficient, the delta function with respect to the bi-invariant \textit{Haar measure} on the compact $G$.
+Here \textit{bi-invariance} means that the measure is invariant under left and right group multiplication, hence also invariant under conjugacy; therefore it is also a well-defined measure on $G$ classes, where $W$ actually belongs.
+Gluing the cylinder $a$ with the infinitesimal cylinder $a'\to 0$, we find the \textbf{disk (cap) amplitude}:
+	\begin{equation}
+		Z(W,\idty;a)
+		= \sum_R \chi_R(W)\,
+			\pqty{\Tr_R \idty}\,
+			e^{-aC_2(R)}
+		= \sum_R (\dim R)\, \chi_R(W)\,
+			e^{-aC_2(R)}
+	\end{equation}
+
+	By now it is clear that the theory is indeed \textit{topological}; there are no $x$-dependent, propagating degrees of freedom.
+To see degrees of freedom, we must investigate the theory on spacetimes of
+nontrivial topology\footnote{\sidenote{
+		Then isn't this, in some sense, a theory of Euclidean ``gravity'', or at least a ``string theory'' by itself? As it includes a sum over topologies.
+	}}. In fact, we can compute the amplitudes for more complicated surfaces by standard gluing
+techniques familiar from axiomatic TFT.
 

### 2021-01-10 alpha/YangMills2D/ym2d.tex
Update YM2 note with general cohomological theory

@@
 	\end{enumerate}
-	It is basically a condensed, more pedagocial version of \cite{Cordes:1994fc}.
+	It is basically a miniaturized, reorganized, pedagocial subset of \cite{Cordes:1994fc}, focusing on its section 3, with brief summary of its section 9, 10 and 14.
 Many basic facts in this review are therefore uncited to avoid repeated citations of \cite{Cordes:1994fc}.
-All uncited claims, unless otherwise specified, can be traced back to \cite{Cordes:1994fc}.
-However, it is highly possible that I, in my infinite stupidity, misunderstood some ideas from \cite{Cordes:1994fc}; so please feel free to point out my mistakes.
+All uncited claims, unless otherwise specified, can be traced back to~\cite{Cordes:1994fc}.
+However, it is highly possible that I, in my infinite stupidity, misunderstood some ideas from~\cite{Cordes:1994fc}; so please feel free to point out my mistakes.
 \section{Introduction}
@@
 		\mcal{A}(P) \Big/ \mcal{G}(P)
+	\label{eq:flat_moduli}
 	\end{equation}
@@
 %	
-%	In chapter 4 we relate the Hilbert space of class functions to some simple conformal field theories.
-The main goal is to show how bosonization leads to a natural interpretation of the Hilbert space in terms of string states.
+%	The abstract discussion concludes in section 14.6 where we give a unified description of an arbitrary cohomological field theory.
 %	
-%	4.7
-%	
-\section{Exact Solution of 2D Yang Mills}
-\subsection{Canonical Quantization on the Cylinder}
+%	The principles of chapter 14 are illustrated in a standard example in chapters 15, on topological Yang-Mills.
+
+\section{Exact solution of 2D Yang--Mills}
+\subsection{Canonical quantization on the cylinder}
 	One can perform the usual canonical quantization with $I_\YM$ on the cylinder, with coordinates $(x^0,x^1) = (t,x) \in \mbb{R}^1\times S^1$.
@@
 
-	By the Peter--Weyl theorem for
-$G$ compact we can decompose the Hilbert space by the unitary irreducible
-representations (\textit{irreps}) $\{R\}$ of $G$. 
+	By the Peter--Weyl theorem for $G$ compact we can decompose the Hilbert space by the unitary irreducible representations (\textit{irreps}) $\{R\}$ of $G$. 
 	Consequently, a natural basis for the Hilbert space is provided by the \textit{characters} $\{\chi_R\}$ of the irreps; thus we have, relative to the $W$ basis,
@@
 \sidenote{This is kind of mysterious; does it has a physical interpretation, e.g.~like sum over possible matter representations?}
-\subsection{Hamiltonian and the Dynamics}
+\subsection{Hamiltonian and time evolution}
 	Let us now find the Hamiltonian for this theory. We are familiar with the the Hamiltonian density in 4D: $
@@
 	\end{equation}
-	Here $C_2(R)$ is the
-\textit{quadratic Casimir} of the irrep $R$; it is proportional to $\idty_R$, or can be treated as a $c$-number when restricted to the irrep. We find out that:
+	Here $C_2(R)$ is the \textit{quadratic Casimir} of the irrep $R$; it is proportional to $\idty_R$, or can be treated as a $c$-number when restricted to the irrep. We find out that:
 	\begin{empheq}{equation}
@@
 	\end{equation}
-\subsection{Basic Amplitudes}
+\subsection{Basic amplitudes}
 	Having diagonalized the Hamiltonian, we can immediately write down the $W$ basis propagator by summing over the $R$ basis; we have:
@@
 	This is the \textbf{cylinder amplitude}. 
-	Note that the combination
-$\frac{1}{2} e^2 a$ enters
-together, where $a = LT$ is the area of the cylinder; this is evident from the action $I[\phi,A]$ in \eqref{eq:convenient_action}, where $e^2 \mu$ comes together as a parameter.
+	Note that the combination $\frac{1}{2} e^2 a$ enters together, where $a = LT$ is the area of the cylinder; this is evident from the action $I[\phi,A]$ in \eqref{eq:convenient_action}, where $e^2 \mu$ comes together as a parameter.
 The area dependence is also evident from the scalar action \eqref{eq:scalar_action}, where we that the theory is invariant under \textit{area preserving diffeomorphism}, $\mop{SDiff}(\Sigma_T)$.
@@
 	By now it is clear that the theory is indeed \textit{topological}; there are no $x$-dependent, propagating degrees of freedom.
-To see degrees of freedom, we must investigate the theory on spacetimes of
-nontrivial topology\footnote{\sidenote{
+To see degrees of freedom, we must investigate the theory on spacetimes of nontrivial topology\footnote{\sidenote{
 		Then isn't this, in some sense, a theory of Euclidean ``gravity'', or at least a ``string theory'' by itself? As it includes a sum over topologies.
-	}}. In fact, we can compute the amplitudes for more complicated surfaces by standard gluing
-techniques familiar from axiomatic TFT.
+	}}. In fact, we can compute the amplitudes for more complicated surfaces by standard gluing techniques familiar from axiomatic TFT.
+
+\section{From \YM to general cohomological theory}
+	We've learned quite a few things from our study of \YM; for example, we see that a topological theory need not be manifestly metric independent.
+Also, it is possible, and sometimes more elegant, to solve the theory without a complete gauge fixing.
+These ideas can all be utilized for the study of a general cohomological field theory.
+
+	From a mathematical point of view, topological field theory is the study of \textit{intersection theory} on moduli spaces using physical methods \cite{Cordes:1994fc,Witten:1990bs}.
+In the physical framework these moduli spaces are presented in the general form:
+	\begin{equation}
+		\mcal{M}
+		= \Bqty{
+				A\in \mcal{A}
+				\,\Big|\,
+				DA = 0
+			} \Big/ \mcal{G}
+	\end{equation}
+	We've seen an example of this, from \eqref{eq:flat_moduli}.
+
+	Note that the usual Faddeev--Popov procedure and coventional BRST cohomology requires gauge-fixing.
+Now we would like to develop an alternative method which does not rely on a specific gauge choice.
+In \YM, postponing the gauge fixing leads us to the class functions on $G$, which is more convenient to work with than the gauge-fixed $\textsl{Cartan} \,\big/ \textsl{Weyl}$.
+More generally, we can directly work on the space of fields $\mcal{A}$ before gauge fixing, and consider \textit{$\mcal{G}$-equivariant} quantities on $\mcal{A}$.
+Here $\mcal{G}$ is generally an infinite-dimensional Lie group, the group of all possible gauge transformations.
+This is the idea of \textit{equivariant cohomology}.
+\subsection{Differential complex from ``supersymmetry''}
+	Here we will briefly illustrate the construction of a differential complex, which will be a model for equivariant cohomology.
+We want something that is ``BRST-like'', without going through the Faddeev--Popov gauge-fixing process.
+The idea is to mimic the BRST field contents by introducing \textit{ghosts}, which can be systematically constructed using differential graded algebra (DGA); the grading is the \textit{ghost number}.
+
+	One can then think of these fields as coordinates of some \textit{superspace}, and write down actions of the \textit{superfield} \cite{Cordes:1994fc,Horne:1988yn}.
+It turns out that the \textit{usual} Lie algebra cohomology of this \textit{supersymmetrized} Lie algebra $\mfrak{g}^S$ is the same as the equivariant cohomology of the original Lie algebra $\mfrak{g}$ \cite{Cordes:1994fc,Witten:1990bs}.
+
+	Example $\mcal{N} = (2,2)$
+
+\subsection{Localization}
+
+	2. Fields: When we study equivariant cohomology we must choose a model for the
+	cohomology. A choice of differential complex amounts to a choice of fields.
+	3. Equations: Mathematically, the ultimate objects of study are intersection numbers.
+	The equations are used to isolate interesting subspaces of C.
+One writes Poincaré duals to these subspaces using MQ representatives of Thom forms (thus introducing further fields).
+The equations are viewed as the vanishing of a section of a vector bundle: s = 0 where s(φ) = Dφ is the section of a vector bundle we will call the
+	localization bundle: s ∈ Γ[E localization → C].
+
+	:
 

### 2021-01-11 alpha/YangMills2D/ym2d.tex
Update YM2 note & spinor note

@@
 \newcommand{\YM}{{\ensuremath{\mrm{YM}_2}}\xspace}
+\newcommand{\Vir}{\mathbf{V}\mfrak{ir}}
 
@@
 	\end{enumerate}
-	It is basically a miniaturized, reorganized, pedagocial subset of \cite{Cordes:1994fc}, focusing on its section 3, with brief summary of its section 9, 10 and 14.
+	It is basically a miniaturized, reorganized, pedagocial subset of \cite{Cordes:1994fc}, focusing on its section 3, with brief summary of its section 9, 10, 14 and 15.
 Many basic facts in this review are therefore uncited to avoid repeated citations of \cite{Cordes:1994fc}.
@@
 This is the idea of \textit{equivariant cohomology}.
-\subsection{Differential complex from ``supersymmetry''}
+\subsection{Equivariant cohomology from ``supersymmetry''}
 	Here we will briefly illustrate the construction of a differential complex, which will be a model for equivariant cohomology.
@@
 
-	One can then think of these fields as coordinates of some \textit{superspace}, and write down actions of the \textit{superfield} \cite{Cordes:1994fc,Horne:1988yn}.
-It turns out that the \textit{usual} Lie algebra cohomology of this \textit{supersymmetrized} Lie algebra $\mfrak{g}^S$ is the same as the equivariant cohomology of the original Lie algebra $\mfrak{g}$ \cite{Cordes:1994fc,Witten:1990bs}.
+	Note that ``physical'' fields such as $A^a_\mu$ and matter fields are form a $\mscr{g}$-module, where $\mscr{g} = \mop{Lie} \mcal{G}$; to include ghost fields, we basically add an additional grading and work with the $\mscr{g}[\epsilon]$-module.
+Here $\epsilon$ is a Grassmann-odd parameter with $\deg\epsilon = -1$, and:
+	\begin{equation}
+		\mscr{g}[\epsilon]
+		= \pqty{\mscr{g} \otimes 1}
+			\oplus \pqty{\mscr{g} \otimes \epsilon}
+	\end{equation}
+%	One can then think of these fields as coordinates of some \textit{superspace}, and write down actions of the \textit{superfield} \cite{Cordes:1994fc,Horne:1988yn}.  
+	It turns out that the \textit{usual} Lie algebra cohomology of this \textit{supersymmetrized} Lie algebra $\mscr{g}[\epsilon]$ is the same as the equivariant cohomology of the original Lie algebra $\mscr{g}$ \cite{Cordes:1994fc}.
 
-	Example $\mcal{N} = (2,2)$
+	In fact, the Lie (super)algebra cohomology for $\mscr{g}[\epsilon]$ is precisely the BRST cohomology with $b,c,\beta,\gamma$ ghosts, known from superstring theory \cite{Polchinski:1998rr,Cordes:1994fc}.
+	Hence it's possible to relate equivariant cohomology with familiar Lie superalgebra cohomology. 
+	An example of this is $\mcal{G} = \mrm{U}(1)$, whose equivariant cohomology is given by the Lie algebra cohomology of the \textit{twisted} $\mcal{N} = 2$ supersymmetry algebra in 2D \cite{Cordes:1994fc}.
+The twisted algebra is obtained from the original algebra by a \textit{topological twist}, which redefines the energy-momentum tensor and makes it $Q$-exact, thus rendering the theory topological \cite{Witten:1991zz,MauricioStuff}.
+From the level of the algebra, we have:
+	\begin{equation}
+		L_0 = \{G_0, Q_0\}
+	\end{equation}
+	Where $L_0$ is the zero mode of the energy momentum. 
+	There is a beautiful generalization of this by considering $\mcal{G} = \mop{Diff}(S^1)$, whose corresponding Lie algebra is given by the \textit{Witt algebra}, or \textit{Virasoro algebra} $\Vir_c$ with central charge $c=0$.
+The $\mcal{G} = \mrm{U}(1)$ we've considered is just the \textit{global} part of the local symmetry group $\mcal{G} = \mop{Diff}(S^1)$.
+Similarly, the $\mop{Diff}(S^1)$-equivariant cohomology is precisely the Lie algebra cohomology of the twisted $\mcal{N} = 2$ \textit{superconformal algebra}.
+
+	For a more concrete example, let's go back to Yang--Mills, and consider the $\mcal{G}$-equivariant cohomology of the space of connections $\mcal{A}$.
+Again, fields are simply $\mscr{g}[\epsilon]$-modules; to compute equivariant cohomology we must construct a differential complex, which is achieved by adding ghosts.
+A choice of differential complex amounts to a choice of ghosts.
+One of the simpliest choice is given by the \textit{Cartan model} \cite{Witten:1990bs,Cordes:1994fc}; we have:
+	\begin{itemize}[noitemsep]
+	\item Degree 0: $A^a_\mu(x)$, Yang--Mills
+	\item Degree 1: $\psi^a_\mu(x)$, 1-form ghosts
+	\item Degree 2: $\phi^a(x)$, commuting 0-form
+	\end{itemize}
+	The BRST-like symmetry $\delta = [Q,-]_\pm$ is given by:
+	\begin{equation}
+		\var{A_\mu} = \psi_\mu,
+	\quad
+		\var{\psi_\mu} = -D_\mu \phi,
+	\quad
+		\var{\phi} = 0
+	\end{equation}
+	On the other hand, the conventional BRST symmetry from Faddeev--Popov is given by:
+	\begin{equation}
+		\tilde{\delta}{A_\mu} = -D_\mu c,
+	\quad
+		\tilde{\delta}{c} = \frac{1}{2}\,[c,c]
+	\end{equation}
 
@@
 
-	2. Fields: When we study equivariant cohomology we must choose a model for the
-	cohomology. A choice of differential complex amounts to a choice of fields.
-	3. Equations: Mathematically, the ultimate objects of study are intersection numbers.
-	The equations are used to isolate interesting subspaces of C.
-One writes Poincaré duals to these subspaces using MQ representatives of Thom forms (thus introducing further fields).
-The equations are viewed as the vanishing of a section of a vector bundle: s = 0 where s(φ) = Dφ is the section of a vector bundle we will call the
-	localization bundle: s ∈ Γ[E localization → C].
+	p121 11.12.3
 
-	:
+	p195 15.12
+
+	nonabelian localization theorem
+
+	Mathematically, the ultimate objects of study are intersection numbers.
 

### 2021-01-15 alpha/YangMills2D/ym2d.tex
Add final version of YM2 note

@@
 	\item[\cite{Witten:1991we}] Witten, \textit{On Quantum Gauge Theories in Two Dimensions}, 1991
+	\item[\cite{Witten:1992xu}] Witten, \textit{Two Dimensional Gauge Theories Revisited}, 1992
 	\end{enumerate}
-	It is basically a miniaturized, reorganized, pedagocial subset of \cite{Cordes:1994fc}, focusing on its section 3, with brief summary of its section 9, 10, 14 and 15.
+	It is basically a miniaturized, reorganized, pedagogical subset of \cite{Cordes:1994fc}, focusing on its section 3, with brief summary of its section 9, 10, 14 and 15.
 Many basic facts in this review are therefore uncited to avoid repeated citations of \cite{Cordes:1994fc}.
@@
 	\end{equation}
-	Here we will try follow the convention of \cite{Cordes:1994fc}, despite the fact that it is, unfortunately, not quite self-consistent.
+	Here we will try to follow the convention of \cite{Cordes:1994fc}, despite the fact that it is, unfortunately, not quite self-consistent.
 $\Sigma_T$ stands for the 2D \textit{target}; in the large $N$ limit, it is possible to realize \YM as a string theory with worldsheet $\Sigma_W$, as is proposed by D.~Gross and W.~Taylor, among others \cite{Gross:1992tu,Gross:1993hu,Gross:1993yt}.
@@
 	\end{equation}
-	Note that this only identifies the topology of $\mcal{M}_0$; to compute the path integral, we need to derive the measure on $\mcal{M}_0$ following the Faddeev--Popov procedure, which is implemented in \cite{Witten:1991we}.
+	Note that this only identifies the topology of $\mcal{M}_0$; to compute the path integral, we need to derive the measure on $\mcal{M}_0$ following e.g.~the Faddeev--Popov procedure, which is implemented in \cite{Witten:1991we}.
 
 	For $e^2 \ne 0$, the action $I[\phi,A]$ is metric dependent.
-Somewhat surprisingly, the path integral still contains information about the topology of $\mcal{M}$.
-This is an example of a so-called \textit{cohomological field theory}.
+Naturally, as $e^2 \to 0$, the path integral will be well approximated by the topological theory, and it still contains information about the topology of $\mcal{M}$.
+This is closely related to \textit{cohomological field theory}.
+
 	The idea of \cite{Cordes:1994fc} is to start from 2D Yang--Mills as a concrete example, and then use its results to motivate a thorough study of {cohomological field theory}.
@@
 	}. 
-	Cohomological field theories, including 2D Yang--Mills with coupling $e^2 \ne 0$, are \textit{not} manifestly metric independent; however, they have a Grassmann-odd nilpotent BRST operator $Q$, and physical observables are $Q$-cohomology classes; amplitudes involving these observables are metric independent, thus they are indeed \textit{topological}.
+	Cohomological field theories
+%	, including 2D Yang--Mills with coupling $e^2 \ne 0$, 
+	are \textit{not} manifestly metric independent; however, they have a Grassmann-odd nilpotent BRST-like operator $Q$, and physical observables are $Q$-cohomology classes; amplitudes involving these observables are metric independent, thus they are indeed \textit{topological}.
 Generally speaking, a TFT need \textit{not} be metric independent; the important thing is that it computes \textit{topological invariants}.
@@
 
-	Following \cite{Cordes:1994fc}, we will first review the exact solution of \YM, and then try to generalize some aspects for a generic cohomological field theory.
+	Following \cite{Cordes:1994fc}, we will first review the exact solution of \YM, and then try to generalize some aspects of \YM for a generic cohomological field theory.
 %	
@@
 	It is thus possible to choose the \textit{temporal gauge} $A_0 = 0$, by simply solving a first order ODE of $\lambda^a(t,x)$, with respect to the variable $x^0 = t$. 
-
+\subsubsection{Complete gauge fixing}
 	We can further reduce $A_1(t,x)$ with remaining gauge redundancies; with some $t$-independent, but $x$-dependent $g = g(x)$, we can preserve $A_0 = 0$, while reducing $A_1(t,x) = A_1(t)$.
@@
 A nice treatment of 4D Yang--Mills from this ``novel'' perspective can be found in \cite{Hatfield:234595}.
-In conventional formulations of QFT, we are used to work in the \textit{Heisenberg} or \textit{interactive picture}, where the fields evolve in time: $A_1 = A_1(t)$ and satisfy some operator equations of motion (EOM's), which for free theories look identical to the classical EOM's.
+In conventional formulations of QFT, we are used to working in the \textit{Heisenberg} or \textit{interactive picture}, where the fields evolve in time: $A_1 = A_1(t)$ and satisfy some operator equations of motion (EOM's), which for free theories look identical to the classical EOM's.
 Alternatively, we can take the quantum mechanical approach, and decompose the fields at each time slice $t = t_0$ to a set of time-independent energy eigenstates; in the case of \YM, we have $A_1 = \mrm{const}$.
@@
 	$ to the \textit{Cartan subalgebra}, i.e.~the maximal abelian subalgebra of $\mfrak{g}$.
-Finally, we demand that $A_1$ is invariant under the \textit{Weyl group}, which is the symmetry of the Cartan subalgebra.
+Finally, we quotient $A_1$ by the action of the \textit{Weyl group}, which is the symmetry of the Cartan subalgebra.
 Therefore, the \textit{physical} Hilbert space of \YM consists of states given by:
@@
 	\end{equation}
-
-	Alternatively, we can also work with a partial gauge fixing, e.g.~we only impose the temporal gauge $A_0 = 0$, and try to solve for $\Psi_t[A_1(x)]$ by looking at the ``Maxwell's equation" in 2D.
+\subsubsection{Partial gauge fixing}
+	Alternatively, we can also work with a partial gauge fixing, e.g.~we only impose the temporal gauge $A_0 = 0$, and try to solve for $\Psi_t[A_1(x)]$ by looking at the ``Maxwell's equation'' in 2D.
 The time evolution is taken care of by the Schr\"odinger equation for $\Psi_t$; for now we need only look at the spatial constraints.
@@
 
-	One can think of the Gauss's law constraint as the result of integrating out $A_0$, which imposes it's EOM $\fdv{I_\YM}{A_0} = 0$, which is precisely \eqref{eq:gauss_law_constraint}. 
+	One can think of the Gauss's law constraint as the result of integrating out $A_0$, which imposes its EOM $\fdv{I_\YM}{A_0} = 0$, which is precisely \eqref{eq:gauss_law_constraint}. 
 	However, for a gauged system, there are subtleties that we need to look out for.
@@
 In fact, if we solve the Gauss's law constraint as an operator equation of $A_1$, we will get further gauge-fixing \cite{Hatfield:234595}.
-	Alternatively, if we ignore the constraint and proceed with canonical quantization, which might be more convenient in some cases, we would expect \textit{unphysical} degrees of freedom like \textit{null states} to show up, due to the unfixed gauge redundancies.
-The constraint can then be utilized to identify \textit{physical} degrees of freedom, by demanding that it annilates physical states:
+	Alternatively, if we ignore the constraint and proceed with canonical quantization, which might be more convenient in many cases, we would expect \textit{unphysical} degrees of freedom like \textit{null states} to show up, due to the unfixed gauge redundancies.
+The constraint can then be utilized to identify \textit{physical} degrees of freedom, by demanding that it annihilates physical states:
 	\begin{equation}
@@
 
-	In fact, we can actually proved \eqref{eq:gauss_law_constraint_state} by demanding the wave functional $\Psi[A_1(x)]$ to be gauge-invariant \cite{Hatfield:234595}; we shall work in the $A_1(x)$ basis, with $\Psi[A_1(x)] = \braket{A_1(x)}{\Psi}$.
+	In fact, we can actually prove \eqref{eq:gauss_law_constraint_state} by demanding the wave functional $\Psi[A_1(x)]$ to be gauge-invariant \cite{Hatfield:234595}; we shall work in the $A_1(x)$ basis, with $\Psi[A_1(x)] = \braket{A_1(x)}{\Psi}$.
 	The canonical momentum operator is then given by:
@@
 	This is the wave function of the $R$ basis.
-	Here $\Tr_R$ denotes trace with respect to the irrep $R$; recall that $W$ is $\mfrak{g}$-valued and do not have a well-defined trace until we specify a irrep, in this case $R$.
+	Here $\Tr_R$ denotes trace with respect to the irrep $R$; recall that $W$ is $\mfrak{g}$-valued and do not have a well-defined trace until we specify an irrep, in this case $R$.
 This is the gauge-invariant Wilson loop operator.
-Note that we are considering pure \YM without matter; the irrep $R$ is not some \textit{a priori} matter representation, but arises naturally as we consider class functions on $G$.
-\sidenote{This is kind of mysterious; does it has a physical interpretation, e.g.~like sum over possible matter representations?}
+Note that we are considering pure \YM without matter; the irrep $R$ is not some \textit{a priori} matter representation, but arises naturally\footnote{
+		This result is somewhat mysterious to me; does the sum over irreps $R$ has a physical interpretation, e.g.~like integrating out all possible matter representations?
+	} as we consider class functions on $G$.
 \subsection{Hamiltonian and time evolution}
-	Let us now find the Hamiltonian for this theory. We are familiar with the the Hamiltonian density in 4D: $
+	Let us now find the Hamiltonian for this theory. We are familiar with the Hamiltonian density in 4D: $
 		\frac{e^2}{2} \pqty\big{
@@
 	Note that the combination $\frac{1}{2} e^2 a$ enters together, where $a = LT$ is the area of the cylinder; this is evident from the action $I[\phi,A]$ in \eqref{eq:convenient_action}, where $e^2 \mu$ comes together as a parameter.
-The area dependence is also evident from the scalar action \eqref{eq:scalar_action}, where we that the theory is invariant under \textit{area preserving diffeomorphism}, $\mop{SDiff}(\Sigma_T)$.
+The area dependence is also evident from the scalar action \eqref{eq:scalar_action}, where we've noticed that the theory is invariant under \textit{area preserving diffeomorphism}, $\mop{SDiff}(\Sigma_T)$.
 From now on we will absorb $\frac{e^2}{2}$ into $a$, and it will be the only dimensionful parameter of the theory.
@@
 Here \textit{bi-invariance} means that the measure is invariant under left and right group multiplication, hence also invariant under conjugacy; therefore it is also a well-defined measure on $G$ classes, where $W$ actually belongs.
-Gluing the cylinder $a$ with the infinitesimal cylinder $a'\to 0$, we find the \textbf{disk (cap) amplitude}:
+Gluing the cylinder $a$ with the infinitesimal cylinder $a'\to 0$, we find the \textbf{cap (disk) amplitude}:
 	\begin{equation}
@@
 	By now it is clear that the theory is indeed \textit{topological}; there are no $x$-dependent, propagating degrees of freedom.
-To see degrees of freedom, we must investigate the theory on spacetimes of nontrivial topology\footnote{\sidenote{
-		Then isn't this, in some sense, a theory of Euclidean ``gravity'', or at least a ``string theory'' by itself? As it includes a sum over topologies.
-	}}. In fact, we can compute the amplitudes for more complicated surfaces by standard gluing techniques familiar from axiomatic TFT.
+To see degrees of freedom, we must investigate the theory with Wilson loops \cite{Cordes:1994fc} or place it on spacetimes of nontrivial topology.
+	In fact, we can compute the amplitudes for more complicated surfaces by standard gluing techniques familiar from axiomatic TFT; then the theory in a sense becomes a theory of Euclidean ``gravity'', as it includes a sum over topologies \cite{Cordes:1994fc}.
 
 \section{From \YM to general cohomological theory}
-	We've learned quite a few things from our study of \YM; for example, we see that a topological theory need not be manifestly metric independent.
-Also, it is possible, and sometimes more elegant, to solve the theory without a complete gauge fixing.
+	We've learned quite a few things from our study of \YM; for example, 
+	\begin{itemize}[noitemsep,leftmargin=*]
+	\item A topological theory need not be manifestly metric independent;
+	\item It is possible, and sometimes more elegant, to solve the theory without a complete gauge fixing;
+	\end{itemize}
 	These ideas can all be utilized for the study of a general cohomological field theory.
@@
 
-	Note that the usual Faddeev--Popov procedure and coventional BRST cohomology requires gauge-fixing.
+	Note that the usual Faddeev--Popov procedure and conventional BRST cohomology requires gauge-fixing.
 Now we would like to develop an alternative method which does not rely on a specific gauge choice.
 In \YM, postponing the gauge fixing leads us to the class functions on $G$, which is more convenient to work with than the gauge-fixed $\textsl{Cartan} \,\big/ \textsl{Weyl}$.
+
 	More generally, we can directly work on the space of fields $\mcal{A}$ before gauge fixing, and consider \textit{$\mcal{G}$-equivariant} quantities on $\mcal{A}$.
@@
 \subsection{Equivariant cohomology from ``supersymmetry''}
-	Here we will briefly illustrate the construction of a differential complex, which will be a model for equivariant cohomology.
+	Here we will briefly illustrate the construction of a differential complex, which will be the \textit{model} for $\mcal{G}$-equivariant cohomology.
 We want something that is ``BRST-like'', without going through the Faddeev--Popov gauge-fixing process.
@@
 
-	Note that ``physical'' fields such as $A^a_\mu$ and matter fields are form a $\mscr{g}$-module, where $\mscr{g} = \mop{Lie} \mcal{G}$; to include ghost fields, we basically add an additional grading and work with the $\mscr{g}[\epsilon]$-module.
+	Note that ``physical'' fields such as $A^a_\mu$ and matter fields are form a $\mscr{g}$-module, where $\mscr{g} = \mop{Lie} \mcal{G}$; to include ghost fields, we basically introduce an additional \textit{grading} and work with the $\mscr{g}[\epsilon]$-module.
 Here $\epsilon$ is a Grassmann-odd parameter with $\deg\epsilon = -1$, and:
@@
 	In fact, the Lie (super)algebra cohomology for $\mscr{g}[\epsilon]$ is precisely the BRST cohomology with $b,c,\beta,\gamma$ ghosts, known from superstring theory \cite{Polchinski:1998rr,Cordes:1994fc}.
-	Hence it's possible to relate equivariant cohomology with familiar Lie superalgebra cohomology. 
+	Hence it's possible to relate equivariant cohomology with familiar Lie superalgebras. 
 	An example of this is $\mcal{G} = \mrm{U}(1)$, whose equivariant cohomology is given by the Lie algebra cohomology of the \textit{twisted} $\mcal{N} = 2$ supersymmetry algebra in 2D \cite{Cordes:1994fc}.
@@
 	Where $L_0$ is the zero mode of the energy momentum.
+
 	There is a beautiful generalization of this by considering $\mcal{G} = \mop{Diff}(S^1)$, whose corresponding Lie algebra is given by the \textit{Witt algebra}, or \textit{Virasoro algebra} $\Vir_c$ with central charge $c=0$.
@@
 Similarly, the $\mop{Diff}(S^1)$-equivariant cohomology is precisely the Lie algebra cohomology of the twisted $\mcal{N} = 2$ \textit{superconformal algebra}.
-
+\subsection{Cohomological \YM}
 	For a more concrete example, let's go back to Yang--Mills, and consider the $\mcal{G}$-equivariant cohomology of the space of connections $\mcal{A}$.
@@
 A choice of differential complex amounts to a choice of ghosts.
-One of the simpliest choice is given by the \textit{Cartan model} \cite{Witten:1990bs,Cordes:1994fc}; we have:
+One of the simplest choice is given by the \textit{Cartan model} \cite{Witten:1990bs,Cordes:1994fc}; we have:
 	\begin{itemize}[noitemsep]
@@
 	\end{equation}
-	On the other hand, the conventional BRST symmetry from Faddeev--Popov is given by:
+
+	The idea is that the BRST-like symmetry $\delta$ acts like a ``square-root'' of the gauge transformation, and the $\phi$ field acts like a gauge parameter; we have:
+	\begin{equation}
+		\delta^2 A_\mu = -D_\mu \phi
+	\end{equation}
+	On the other hand, the conventional BRST symmetry $\tilde{\delta}$ from Faddeev--Popov acts like a gauge transformation parametrized by a ghost; it is given by:
 	\begin{equation}
@@
 
-\subsection{Localization}
+	One can then write down a gauge-invariant action with ghosts. For \YM, this is given by \cite{Cordes:1994fc,Witten:1992xu}:
+	\begin{equation}
+		I[A,\psi,\phi]
+		= \int \pqty{
+				i \Tr\,(\phi F - \tfrac{1}{2}\psi\wedge\psi)
+				+ \frac{1}{2}\, e^2\mu \Tr\,(\phi^2)
+			}
+	\label{eq:cartan_action}
+	\end{equation}
+	We immediately notice that this is almost identical to the $I[\phi,A]$ in \eqref{eq:convenient_action}, just with an additional $\psi$ term, which is actually decoupled from the other fields and can be simply integrated out.
+Therefore, the theory in this form is indeed equivalent with the original $I_\YM$.
 
-	p121 11.12.3
+	The $\psi$ field, however, is far from useless.
+The main difficulty of computing the path integral for a gauge field $A$ is that we should treat the measure $\DD{A}$ with great care.
+But now we have a fermionic $\psi$ field; note that although there is no natural measure for $A$ or $\psi$ separately, there is a natural measure $\DD{A} \DD{\psi}$, since the Jacobian in a change of variables would cancel between bosons and fermions \cite{Witten:1992xu}.
 
-	p195 15.12
+	In fact, the $\psi$ term gives precisely the \textit{symplectic volume element} on the space of connections $\mcal{A}$, up to some normalization:
+	\begin{equation}
+		\DD{A} \DD{\psi}
+			\exp \pqty{
+				\frac{i}{4\pi^2}
+				\int \Tr (\tfrac{1}{2} \psi\wedge\psi)
+			}
+	\end{equation}
+	The action $I[A,\psi,\phi]$ thus provides a nice expression of the path integral at $e^2 = 0$, by specifying a measure of the flat moduli $\mcal{M}_0$ in \eqref{eq:flat_moduli}, which coincides with the result from Faddeev--Popov quantization \cite{Witten:1991we}.
+On the other hand, $\DD{\phi}$ provides a natural measure on the group of gauge transformations $\mcal{G}$.
+The path integral is thus automatically gauge-invariant.
 
-	nonabelian localization theorem
+	Furthermore, to write down the Lagrangian for a ``standard'' \textit{cohomological field theory}, one need to include additional \textit{anti-ghosts}, and then construct a functional $V$ such that the Lagrangian \cite{Witten:1992xu}:
+	\begin{equation}
+		\mcal{L} = -i\,\{Q,V\}
+	\label{eq:coh_action}
+	\end{equation}
+	i.e.~$\mcal{L}$ is manifestly $Q$-exact, which in turn leads to a $Q$-exact energy momentum tensor \cite{Cordes:1994fc}.
+We wish also to pick $V$ so that all fields will have a non-degenerate kinetic energy.
+A suitable choice of $V$ will then lead us to the 2D analog of \textit{Donaldson theory} \cite{Witten:1992xu}.
 
-	Mathematically, the ultimate objects of study are intersection numbers.
+	The \textit{cohomological \YM} constructed in this way is a ``fully topological'' theory of the cohomological type; however, it is \textit{not} equivalent to the \textit{physical \YM}, given by actions such as $I_\YM$, $I[\phi,A]$ or $I[A,\psi,\phi]$, found in \eqref{eq:scalar_action}, \eqref{eq:convenient_action}, and \eqref{eq:cartan_action}.
+The physical theory does have \textit{some} degrees of freedom beyond the topology, as evidenced by the $e^2 a$ dependence.
+
+	On the other hand, it is possible to relate the cohomological \YM with the physical \YM, as is explained by Witten in \cite{Witten:1992xu}, with \textit{equivariant localization}.
+This is precisely analogous to \textit{supersymmetric localization}; as we've learned before, the algebraic structures associated with equivariant cohomology is closely related to supersymmetry.
+For more on this, see 11.12.3 and 15.12 of \cite{Cordes:1994fc}, and 3.2 of \cite{Witten:1992xu}.
+
+%\subsection{Localization}
+%	When deriving the {cap amplitude} in \YM, we use the fact that as $e^2 a\to 0$, the theory gets reduced to a ``fully topological'' theory of the Schwarz type. 
+%	We can think of this as taking a \textit{semi-classical} limit of the path integral, since $e^2$ in $I_\YM$ is like an $\hbar$ parameter. 
+%	The accuracy of such approximation is closely related to the general phenomenon of \textit{localization} \cite{Pestun:2016zxk}.
 

### 2021-01-17 build.sh
Try parallel builds in build.sh

@@ -14,7 +14,7 @@ mkdir -p release
 # naming: $project/$sub_project/$main.tex
 FILES=$(find . \
     -regex "./[^/]+/[^/]+/[^/]+\.tex" \
-    -not -path "./TeXplates/*"
+    -not -path "./TeXplates/*" | sort
 )
 log "Files:"
 echo "$FILES"
@@ -34,37 +34,42 @@ for file in $FILES; do
     )
     [[ -z $tex_program ]] && tex_program=xelatex
 
-    if [[ $tex_program == pdflatex ]] \
-    || [[ $tex_program == xelatex ]] \
-    || [[ $tex_program == lualatex ]]; then
-        latexmk \
-            "-$tex_program" \
-            -synctex=15 \
-            -interaction=nonstopmode \
-            -shell-escape \
-            "$filename"
-    else
-        eval "$tex_program" \
-            "$filename"
-    fi
+    {
+        if [[ $tex_program == pdflatex ]] \
+        || [[ $tex_program == xelatex ]] \
+        || [[ $tex_program == lualatex ]]; then
+            latexmk \
+                "-$tex_program" \
+                -synctex=15 \
+                -interaction=nonstopmode \
+                -shell-escape \
+                "$filename" \
+                1>/dev/null
+        else
+            eval "$tex_program" \
+                "$filename" \
+                1>/dev/null
+        fi
 
-    log "Check & release PDF:"
-    pdf="$(basename "$filename" .tex).pdf"
-    if ls "$pdf"; then
+        log "Check & release PDF:"
+        pdf="$(basename "$filename" .tex).pdf"
+        if ls "$pdf"; then
 
-        # shortened name: $project/$sub_project.tex
-        target="$DIR/release/$(dirname "$pathname")"
-        mkdir -p "$target"
+            # shortened name: $project/$sub_project.tex
+            target="$DIR/release/$(dirname "$pathname")"
+            mkdir -p "$target"
 
-        # shellcheck disable=2015
-        [[ $USER == bryan ]] \
-            && cp -a -v -f "$pdf" "$target/." \
-            || mv -v -f "$pdf" "$target/."
-    fi
+            # shellcheck disable=2015
+            [[ $USER == bryan ]] \
+                && cp -a -v -f "$pdf" "$target/." \
+                || mv -v -f "$pdf" "$target/."
+        fi
+    } &
 
     cd "$DIR" || exit 1
 done
 
+wait
 ls -alF release
 cp README.md LICENSE release
 

### 2021-02-22 HW-AdvancedQFT2020/advqft1/advqft1.tex
Update note on the quantum boost generator

@@
 	\end{equation}
-	It is evident (after partial integration) that the following currents are conserved; they are the Noether currents associated with $a^\mu$ and $\lambda^{[\mu\nu]}$:
+	It is then evident (after partial integration) that the following currents are conserved; they are the Noether currents associated with $a^\mu$ and $\lambda^{[\mu\nu]}$:
 	\begin{equation}
@@
 	We've obtained an interesting result: the expression for the boost generator $M^{i0}$ contains the Hamiltonian density $\mcal{H}$, weighted by the radial distance $x^i$.
-This is natural since a boost does indeed contains time evolution for states away from the origin.
+This is natural since a boost does indeed contains time evolution for excitations away from the origin.
 It's an important result utilized by the so-called \textit{Rindler decomposition}; in fact, $M^{i0}$ becomes the Hamiltonian for an accelerated observer in the Rindler patch\footnote{
@@
 	This is interpreted as the angular momentum of the field $\phi$.
-Suppose $\phi$ is a wave packet localized around $\vb{x}$ with momentum $\approx \vb{p}$, then we have the classical angular momentum up to some factor:
+Suppose $\phi$ is a wave packet localized around $\vb{x}$ with momentum $\approx \vb{k}$, then we have the classical angular momentum up to some factor:
 	\begin{equation}
@@
 		\sim \pqty{
-				x^i p^j
-				- x^j p^i
+				x^i k^j
+				- x^j k^i
 			} \int \dd[3]{x}
@@
 	\quad
-		E = \sqrt{\vb{p}^2 + m^2}
+		E = \sqrt{\vb{k}^2 + m^2}
 	\end{equation}
@@
 			}
-		\sim \pqty{E^2 + \vb{p^2} + m^2 + \cdots}
+		\sim \pqty{E^2 + \vb{k^2} + m^2 + \cdots}
 			\int \dd[3]{x} \frac{1}{2}\,\phi^2,
@@
 		\sim \pqty{
-				x^i p^j
-				- x^j p^i
+				x^i k^j
+				- x^j k^i
 			}
@@
 			\pqty{
-				a_{\vb{k}} e^{ik\cdot x}
-				+ a^\dagger_{\vb{k}'} e^{-ik\cdot x}
+				a_{k} e^{ik\cdot x}
+				+ a^\dagger_{k} e^{-ik\cdot x}
 			},
 	\quad
-		[a_{\vb{k}}, a^\dagger_{\vb{k}'}]
+		[a_{k}, a^\dagger_{k'}]
 		= (2\pi)^3 \delta(\vb{k} - \vb{k}')
 	\end{equation}
+	The $k$ dependence in $a_k, E_k$ is, in fact, only a $\vb{k}$ dependence; we've dropped the boldface in the subscripts simply for convenience.
 
@@
 	\end{equation}
-	The quantization $M\mapsto \normorder{M}$ is thus reduced to the quantization of $T_{0\nu}$.
+	The quantization $M\mapsto \normorder{M}$ is thus reduced to the quantization of $T^{\nu 0}$, weighted by a $x^\mu$ factor.
+
+	First let's look at $T^{00} = \mcal{H}$; note that:
+	\begin{equation}
+		\int \dd[3]{x}
+			x^i e^{i\vb{k}\cdot\vb{x}}
+		= (2\pi)^3 \pqty{
+				-i\,\pdv{k_i}
+			} \delta(\vb{k})
+	\end{equation}
+	One can then check explicitly with mode expansion that, up to normal ordering, we have\footnote{
+		See a similar result in \url{https://physics.stackexchange.com/q/27906}.
+Moreover, the charge can be computed at arbitrary time slice $t$, but the $t$-dependence ($\sim e^{\pm iEt}$) drops out in the final result, due to the on-shell condition $E_k^2 = \vb{k}^2 + m^2$ and symmetries, e.g.\ $\int \dd[3]{k} k^i = 0$.
+Note that $\pdv{E_k}{k_i} = \frac{k^i}{E_k}$.
+	}:
+	\begin{gather}
+		H = \int \dd[3]{x} \mcal{H}
+		= \int \frac{\dd[3]{k}}{(2\pi)^3}\,
+			E_k\, a^\dagger_k a_k,
+	\\
+		\mcal{O}^i = \int \dd[3]{x} x^i \mcal{H}
+		= \int \frac{\dd[3]{k}}{(2\pi)^3}\,
+			E_k\, a^\dagger_k
+				\pqty{+i\,\pdv{k_i}}
+			a_k,
+	\end{gather}
+
+%\pagebreak[3]
+	At first glance, derivative of $a_k = a_{\vb{k}}$ with respect to $k^i$ seems puzzling; however, note that $\pqty\big{+i\,\pdv{k_i}}$ is precisely the $x^i$ operator in ``momentum-space'', and one can make sense of it by considering a generic $n$-particle state:
+	\begin{equation}
+		\ket{\Psi}
+		= \int \dd[3]{k_1}\cdots \dd[3]{k_n}
+			\Psi(\vb{k}_1,\cdots,\vb{k}_n)
+			\,a^\dagger_{k_1}
+			\cdots a^\dagger_{k_n} \ket{0}
+	\end{equation}
+	Where $\Psi(\vb{k}_1,\cdots,\vb{k}_n)$ is the $n$-particle wave function; using $
+		a_k a^\dagger_{k'}
+		= a^\dagger_{k'} a_k
+			+ (2\pi)^3\delta(\vb{k} - \vb{k'})
+	$ recursively, we get in the end that:
+	\begin{equation}
+		\mcal{O}_i \ket{\Psi}
+		= \int \dd[3]{k_1}\cdots \dd[3]{k_n}
+			\Bqty{
+				\sum_{m = 1}^n
+				E_{k_m}
+				\pqty{+i\,\pdv{k^i_m}}\,
+				\Psi(\vb{k}_1,\cdots,\vb{k}_n)
+			}
+			\,a^\dagger_{k_1}
+			\cdots a^\dagger_{k_n} \ket{0}
+	\end{equation}
+
+	We see that indeed $\mcal{O}_i$ acts as $
+		E_k \pqty{+i\,\pdv{k^i}}
+	$ on the momentum-space $n$-particle wave function, consistent with the result of ordinary quantum mechanics; ...
 

### 2021-03-12 HW-Gravity/gravity1/gravity1.tex
Add gravity homework

% !TeX encoding = UTF-8
% !TeX spellcheck = en_US
% !TeX TXS-program:bibliography = biber -l zh__pinyin --output-safechars %

\documentclass[a4paper,10pt]{article}

\newcommand{\hwNumber}{1}

\input{../gravity_preamble.tex}
\input{../.modules/basics/biblatex.tex}

%%% ID: sensitive, do NOT publish!
\InputIfFileExists{../id.tex}{}{}

\begin{document}
\maketitle
\pagenumbering{arabic}
\thispagestyle{empty}

%\vspace*{-1.5\baselineskip}

%1  Solve the spacelike geodesic equation for AdSd+1in Poincar ́e coordinates.In particular, write down the leading order terms for two points near theboundaryz=with a coordinate separation in a spatial direction,  sayx2−x1=L.
%2  Consider the world-line action of a point particleS=12∫dτ(η−1 ̇Xμ ̇Xμ−ηm2).(1)How doesηtransform under the reparameterization of the parameterτ?Show that it is classically equivalent to the action ̃S=−m∫dτ(−gαβ ̇Xα ̇Xβ)1/2.(2)
%3  Work out the Ricci tensor for the metricds2=−f(r)dt2+h(r)dr2+r2(dθ2+ sin2θdφ2)(3)
%4  Derive the equations of motion for the Jackiw-Teitelboim gravity, a twodimensional theory of gravity coupled with dilatonS=116πG∫dx2√−gΦ(R+ 2)(4)where Φ is a dilaton field.1

\section{Spacelike Geodesic for Poincar\'e AdS}
	The Poincar\'e $\mrm{AdS}_{d+1}$ metric is given by:
	\begin{equation}
		\dd{s}^2
		= G_{IJ} \dd{X^I} \dd{X^J}
		= \frac{
				-\dd{t}^2 + \dd{\vec{x}}^2 + \dd{z}^2
			}{z^2}
%		= \frac{\dd{w}^2}{z^2}
		= \frac{
				\dd{x}^2 + \dd{z}^2
			}{z^2},
	\end{equation}
	\\[-1.8\baselineskip]
	\begin{equation}
		\dd{x}^2
		= -\dd{t}^2 + \dd{\vec{x}}^2
		= \eta_{\mu\nu} \dd{x}^\mu \dd{x}^\nu,
	\quad
		X^I \sim (t,\vec{x},z)
		\sim (x^\mu, z),
	\end{equation}
	Note that here we define $\dd{x}^2$ using the flat metric $\eta$, while $\dd{X}$ has an index that should be raised and lowered using the curved metric $G_{IJ} = \frac{1}{z^2}\,\eta_{IJ}$. Generally upper case tensors are handled with $G_{IJ}$, while lower case ones are handled with $\eta$. 
	The full isometry of such spacetime is then given by $\mrm{SO}(d,2)$ with $\frac{(d+2)(d+1)}{2}$ generators, including:
	\begin{enumerate}[itemsep=.2\baselineskip]
	\item Among the $x^\mu \sim (x^0,\vec{x}) \equiv (t,\vec{x})$ directions:
		\begin{enumerate}[noitemsep]
		\item $\frac{d(d-1)}{2}$ $\mrm{SO}(d-1,1)$ rotations $
			x_\mu \pdd{\nu} - x_\nu \pdd{\mu}
		$, boosts included;
		\item $d$ translations $\pdd{\mu}$;
		\end{enumerate}
	\item Dilation with $X^I \sim (x^\mu,z)\mapsto \lambda X^I = \lambda\,(x^\mu,z)$, generated by $\Delta = X^I \pdd{I} = z\pdd{z} + x^\mu \pdd{\mu}$;
	\item Special conformal transformations; these can be understood as translations conjugated by \textit{inversions}. Note that $\frac{\dd{z}^2}{z^2}$ is invariant under $z\mapsto \frac{1}{z}$; if we include the $x^\mu$ directions, we can consider:
	\begin{equation}
		\mcal{I}\colon\ \chi^I \mapsto
			\frac{\chi^I}{\chi^2},
%			= \frac{\chi^I}{x^2 + z^2}
	\quad
		\chi^2 = -t^2 + \vec{x}^2 + z^2,
	\end{equation}
	\\[-1.5\baselineskip]
	\begin{equation}
		\mcal{I}^2 = \idty,
	\quad
		\dd{s}^2
		\mapsto \pqty{
				\frac{
					\delta^I_J
					- 2\,\frac{\chi^I \chi_J}{\chi^2}
				}{\chi^2}
				\dd{\chi^J}
			}^{\!\!2}
			\bigg/ \pqty{
				\frac{z}{\chi^2}
			}^{\!\!2}
		= \frac{\dd{\chi}^2}{z^2}
		= \dd{s}^2
	\end{equation}
	\end{enumerate}
	We see that inversion $\mcal{I}$ is indeed a (discrete) symmetry of the metric. 
	Here we've defined yet another lower case variable $\chi^I \sim (x^\mu, z)$, which as a contravariant vector has the same components as $X^I$, but with an index that should be lowered by the flat metric $\eta_{IJ}$, i.e.~$\chi_I = \eta_{IJ} \chi^J = \eta_{IJ} X^J$. 
	The $d$ special conformal generators are then given by:
	\begin{equation}
	\begin{aligned}
		K_\mu
		&= \pdv{a^\mu} \pqty{
				\mcal{I}
				\circ e^{a^\nu P_\nu}
				\circ \mcal{I}
				\circ X^I
			}_{\!a = 0} \ \pdv{X^I} \\
		&= \pdv{a^\mu}\pqty{
				\frac{\frac{\chi^I}{\chi^2} + a^I}{
					\abs\big{\frac{\chi^J}{\chi^2} + a^J}^2
				}
			}_{\!\!a = 0} \,\pdv{X^I} \\
		&= \pdv{a^\mu}\pqty{
				\frac{\chi^I + a^I \chi^2}{
					1 + 2a^I \chi_I + a^2 \chi^2
				}
			}_{\!\!a = 0} \,\pdv{X^I} \\
		&= \chi^2 \pdd{\mu}
			- 2x_\mu X^I \pdd{I} \\
		&= \chi^2 \pdd{\mu}
			- 2\eta_{\mu\nu} x^\nu \Delta \\
		&= \pqty{
				\chi^2 \delta^I_\mu
				- 2\eta_{\mu\nu} x^\nu X^I
			} \pdd{I}
	\end{aligned}
	\end{equation}

	By Noether's theorem, $Q_\Xi = V_I \Xi^I = G_{IJ} \Xi^I V^J$ is conserved along the geodesic; here $V^I$ is the normalized tangent vector, while $\Xi^I$ is some Killing vector of the spacetime, e.g.~one from the list above.

	We can then write down the conserved charges along a geodesic $\gamma$ in Poincar\'e AdS:
	\begin{subequations}
%	\allowdisplaybreaks
	\begin{align}
		p_\mu &= G_{\mu I} V^I = V_\mu \\
		m\id{^\mu_\nu} &= X^\mu V_\nu - X^\nu V_\mu \\
		\Delta &= X^I V_I
			= \frac{z V^z + x^\mu p_\mu}{z^2}
%	,\quad
%		V^I \sim (v^\mu, v^z)
		\\
		k_\mu &= (z^2 + x^2)\, V_\mu - 2\eta_{\mu\nu} x^\nu \Delta
	\end{align}
	\end{subequations}
	These are all integration constants along $\gamma$. 
	Again note that $X,V$ have indices that should be handled with $G_{IJ}$, in particular,
	\begin{equation}
		X_\mu = G_{\mu I} X^I = \frac{1}{z^2} x_\mu
	\end{equation}

	Equation (a) above implies that $X_\mu(\lambda) = X_\mu(0) + p_\mu \lambda$,
%	 linear in the affine parameter $\lambda$, 
	therefore:
	\begin{equation}
		x^\mu(\lambda) = X^\mu(\lambda)
		= X^\mu(0) + p^\mu \lambda z^2,
	\quad z = z(\lambda)
	\end{equation}
	Note the additional $z^2$ factor due to the metric $G$. Plug this into (c)(d)
%	and ensure that $u^\mu$ is properly normalized
	and we have:
	\begin{equation}
	\begin{gathered}
%		\delta = g_{IJ} \dd{X^I} \dd{X^J}
%		= \frac{p^2 + u_z^2}{z^2},
%	\quad
%		\delta = 0,\pm 1,
%	\quad
%		p^2 = p_\mu p^\mu = \eta_{\mu\nu} p^\mu p^\nu,
%	\\
		\Delta = \frac{1}{z} V^z
			+ \frac{1}{z^2}\, x^\mu(0)\, p_\mu
			+ p^2 \lambda,
	\\
		(z^2 + x^2)\,p^\mu
		= k^\mu + 2x^\mu \Delta,
%	\\
%		z^2 + x^2 - 2\Delta\lambda
%		= \frac{p_\mu (k^\mu + 2x^\mu(0))}{p_\mu p^\mu},
%	\\
%		(z^2 + x^2)\,p^\mu
%		= k^\mu + 2x^\mu \Delta
%		= k^\mu + 2x^\mu(0) \Delta + 2\Delta p^\mu \lambda,
	\end{gathered}
	\end{equation}

%	For $\delta = 0$, we have $u_z^2 = -p^2$ constant, $z(z) = z(0) + u_z \lambda$ also linear in $\lambda$, i.e.~null geodesics are ``straight'' lines in the $X^I$ coordinates; this agrees with the conformal flatness of the metric. For $\delta \ne 0,\delta^2 = 1$, we have:
	For $p^\mu = 0$, we have $x^\mu = x^\mu(0)$ while (c) implies that $
		\Delta
		= \frac{1}{z}\dv{z}{\lambda}
	$, i.e.~$z(\lambda) = z(0) \,e^{\lambda\Delta}$, with $\norm{V}^2 = \frac{(V^z)^2}{z^2} = \Delta^2$. With the standard normalization $\norm{V}^2 = 1$, we get $\Delta = \pm 1$, $z(\lambda) = z(0) \,e^{\lambda\Delta}$; this is a spacelike ``straight'' line along the $z$ direction.

	For $p^\mu \ne 0$, we can always find some $c_\mu$ such that $c_\mu p^\mu \ne 0$, therefore (d) implies that:
	\begin{equation}
		z^2 + x^2 - 2\lambda z^2\Delta
		= \frac{c_\mu \pqty{k^\mu + 2x^\mu(0)\,\Delta}}{c_\mu p^\mu}
	\end{equation}
	The right hand side is constant; note that $x^\mu$ is also linear in $\lambda z^2$, therefore we can complete the square on the left hand side such that:
	\begin{equation}
		z^2 + \pqty{x - a}^2
		= \pqty{\frac{L}{2}}^{\!\!2}
		= \mrm{const.},
	\quad
		\Delta
		= p_\mu a^\mu
	\end{equation}

	We see that $\gamma$ lands on a ``sphere'' centered at $z = 0, x = a$ in $\mbb{R}^{d,1}$; with the Lorentzian metric, it is actually a hyperboloid. Note that for now the radius $\pqty{\frac{L}{2}}^{\!2}$ can actually be negative or zero; more specifically,
	\begin{enumerate}[noitemsep]
	\item $L^2 > 0$: one-sheet hyperboloid;
	\item $L^2 < 0$: two-sheet hyperboloid;
	\item $L^2 = 0$: conic surface. 
	\end{enumerate}

\printbibliography[%
%	title = {参考文献} %
	,heading = bibintoc
]
\end{document}

### 2021-03-13 HW-Gravity/gravity1/gravity1.tex
Finish the calculation of Poincare geodesics
... and update TeXplates for enumitem formats

@@
 			}{z^2}
-%		= \frac{\dd{w}^2}{z^2}
 		= \frac{
@@
 	The full isometry of such spacetime is then given by $\mrm{SO}(d,2)$ with $\frac{(d+2)(d+1)}{2}$ generators, including:
-	\begin{enumerate}[itemsep=.2\baselineskip]
+	\begin{enumerate}[noitemsep]
 	\item Among the $x^\mu \sim (x^0,\vec{x}) \equiv (t,\vec{x})$ directions:
-		\begin{enumerate}[noitemsep]
+		\begin{enumerate}[noitemsep,topsep=.5\baselineskip]
 		\item $\frac{d(d-1)}{2}$ $\mrm{SO}(d-1,1)$ rotations $
@@
 	\item Dilation with $X^I \sim (x^\mu,z)\mapsto \lambda X^I = \lambda\,(x^\mu,z)$, generated by $\Delta = X^I \pdd{I} = z\pdd{z} + x^\mu \pdd{\mu}$;
-	\item Special conformal transformations; these can be understood as translations conjugated by \textit{inversions}.
+	\item Special conformal transformations; see \autoref{sect:special_conformal} for an intuitive derivation. We have: 
+	\begin{equation}
+		k_\mu
+		= (z^2 + x^2)\,\pdd{\mu}
+			- 2x_\mu \Delta
+	\end{equation}
+	\end{enumerate}
+
+	By Noether's theorem, $Q_\Xi = V_I \Xi^I = G_{IJ} \Xi^I V^J$ is conserved along the geodesic; here $V^I$ is the normalized tangent vector, while $\Xi^I$ is some Killing vector of the spacetime, e.g.~one from the list above.
+	We can then write down the conserved charges along a geodesic $\gamma$ in Poincar\'e AdS:
+	\begin{equation}
+%	\allowdisplaybreaks
+%	\renewcommand{\theequation}{\theparentequation.\alph{equation}}
+	\begin{aligned}
+		p_\mu
+			&= G_{\mu I} V^I = V_\mu \\
+		m_{\mu\nu}
+			&= x_\mu V_\nu - x_\nu V_\mu \\
+		\Delta
+			&= X^I V_I
+			= \frac{z V^z}{z^2} + x^\mu p_\mu
+%	,\quad
+%		V^I \sim (v^\mu, v^z)
+		\\
+		k_\mu &= (z^2 + x^2)\, p_\mu - 2x_\mu \Delta
+	\end{aligned}
+	\end{equation}
+	These are all integration constants along $\gamma$. 
+	Again note that $X,V$ have indices that should be handled with $G_{IJ}$, in particular,
+	\begin{equation}
+		\dd{X}_\mu
+		= G_{\mu I} \dd{X}^I
+		= \frac{1}{z^2} \dd{x}_\mu,
+	\quad
+		V^\mu = \dv{X^\mu}{\lambda} = z^2 p^\mu
+	\label{eq:p_conserved}
+	\end{equation}
+
+	On the other hand, $V^\mu$ should be properly normalized, therefore:
+	\begin{equation}
+	\begin{gathered}
+		\norm{V}^2
+		= g_{IJ} V^I V^J
+		= \frac{(V^z)^2}{z^2} + z^2 p^2
+		= \delta = 0,\pm 1,
+%	\quad
+%		p^2 = p_\mu p^\mu = \eta_{\mu\nu} p^\mu p^\nu,
+	\label{eq:tangent_norm}
+	\end{gathered}
+	\end{equation}
+	For $p^2 = 0$, we have $
+		\norm{V}^2
+		= \frac{(V^z)^2}{z^2}
+		\ge 0
+	$, thus $\gamma$ can be either spacelike or null, but not timelike. In fact, $
+		\frac{1}{z}\dv{z}{\lambda} = 0,\pm 1
+	$, along with $\dv{x^\mu}{\lambda} = z^2 p^\mu$, we obtain:
+	\begin{equation}
+	p^2 = 0,\qquad
+	\begin{aligned}
+		\text{spacelike}\colon\ &
+			z(\lambda)
+			= z(0)\,e^{\pm\lambda},
+		&&
+			x^\mu(\lambda)
+			= x^\mu(0) \pm z(0)^2\,p^\mu\,
+				\tfrac{
+					e^{\pm 2\lambda} - 1
+				}{2}, \\
+		\text{null}\colon\ &
+			z(\lambda)
+			= z(0),
+		&&
+			x^\mu(\lambda)
+			= x^\mu(0) + z(0)^2\,p^\mu \lambda,
+	\end{aligned}
+	\label{eq:null_type}
+	\end{equation}
+
+	From now on we shall focus on the $p^2 \ne 0$ situation. Note that we can complete the square on the right hand side of the $k^\mu$ conservation such that:
+	\begin{equation}
+		k_\mu + p_\mu a^2
+		= p_\mu \pqty{
+			z^2 + (x - a)^2
+		},
+	\quad \Delta = p_\mu a^\mu
+	\end{equation}
+	For $p^\mu \ne 0$, we can always find some $c_\mu$ such that $c_\mu p^\mu \ne 0$, therefore we have:
+	\begin{equation}
+		z^2 + \pqty{x - a}^2
+		= \frac{c_\mu k^\mu}{c_\mu p^\mu}
+			+ a^2
+		= \pqty{\frac{L}{2}}^{\!\!2}
+		= \mrm{const.},
+	\quad \Delta = p_\mu a^\mu
+	\end{equation}
+
+	We see that $\gamma$ lands on a ``sphere'' centered at $z = 0, x = a$ in $\mbb{R}^{d+1}$; with the Lorentzian metric, it is actually a hyperboloid.
+Note that for now the radius $\pqty{\frac{L}{2}}^{\!2}$ can actually be negative or zero; more specifically,
+	\begin{enumerate}[noitemsep]
+	\item $L^2 > 0$: one-sheet hyperboloid;
+	\item $L^2 < 0$: two-sheet hyperboloid;
+	\item $L^2 = 0$: conic surface. 
+	\end{enumerate}
+	On the other hand, we can actually solve $X^I$ completely by combining \eqref{eq:p_conserved}, \eqref{eq:tangent_norm}; we have:
+	\begin{equation}
+		\dv{x^\mu}{\lambda} = z^2 p^\mu,
+	\quad
+		\dv{z}{\lambda}
+		= \pm z\sqrt{\delta - z^2 p^2},
+	\quad
+		\dv{x^\mu}{z}
+		= \pm \frac{zp^\mu}{\sqrt{\delta - z^2 p^2}},
+	\quad
+		\delta - z^2 p^2
+		= \pqty{\tfrac{V^z}{z}}^{\!2} \ge 0
+	\end{equation}
+	\\[-1.5\baselineskip]
+	\begin{equation}
+	\Longrightarrow\quad
+		\gamma \ \subset\ % 
+		x^\mu
+		= a^\mu \pm\frac{p^\mu}{p^2}
+			\sqrt{\delta - z^2 p^2},
+	\quad
+		z^2 + (x - a)^2
+		= \frac{\delta}{p^2}
+		= \pqty{\frac{L}{2}}^{\!\!2}
+	\label{eq:unified_geodesic}
+	\end{equation}
+
+	This confirms our observation above, and further reveals that $\gamma$ lies in a ``plane'' in the $\mbb{R}^d$ subspace consisting of the $x^\mu$ coordinates.
+The behavior of $\gamma$ is sensitive to the sign of $\delta$ and $p^2$; more specifically,
+	\begin{enumerate}
+	\item $\delta = -1$, i.e.~for timelike $\gamma$, we must have $p^2 < 0$, and $z \ge \frac{1}{\abs{\norm{p}}} = \frac{L}{2} > 0$, namely $z$ is bounded from below.
+This means that timelike geodesic can never reach the asymptotic boundary $z \to 0$.
+In this case, $\gamma$ is a section of the one-sheet hyperboloid.
+	\item $\delta = +1$, i.e.~for spacelike $\gamma$, we can have $p^2 > 0$ or $p^2 < 0$.
+		\begin{enumerate}
+		\item For $p^2 > 0$, again we have $\frac{L}{2} = \frac{1}{\norm{p}} > 0$, and $\gamma$ is again a cross section of the one-sheet hyperboloid.
+However, now we have $z \le \frac{L}{2}$, namely $z$ is bounded from above, and:
+		\begin{equation}
+			z\to 0,
+		\quad
+			x^\mu
+			= a^\mu \pm \frac{p^\mu}{p^2}
+			= a^\mu \pm \frac{L}{2}\,\widehat{p}^\mu,
+		\quad
+			\widehat{p}^\mu = \frac{p^\mu}{\norm{p}}
+		\end{equation}
+		We can also nicely parametrize $X^I$ in terms of the proper length $\lambda$; for convenience, set $x^\mu(0) = a^\mu$, $z(0) = \frac{L}{2}$, then we have:
+		\begin{equation}
+			z(\lambda)
+			= \frac{L}{2} \frac{1}{\cosh \lambda},
+		\quad
+			x^\mu(\lambda)
+			= a^\mu \pm \widehat{p}^\mu \frac{L}{2}
+				\tanh \lambda
+		\label{eq:elliptic}
+		\end{equation}
+
+		\item For $p^2 < 0$, we have $(\frac{L}{2})^2 = \frac{1}{p^2} < 0$, and $\gamma$ is now a cross section of the two-sheet hyperboloid.
+Again as $z\to 0$ it lands at $x^\mu = a^\mu \pm \frac{L}{2}\,\widehat{p}^\mu$; however, $\abs{x^\mu}$ grows with $z$ and extends into the bulk instead of returning to the boundary, i.e.~$z,\abs{x^\mu} \to \infty$.
+
+		The differential equation in this case is almost the same as in (a), but now we have to choose a different initial condition, since $\gamma$ won't even reach $x = a$.
+However, we can actually set $x(0),z(0) \to \infty$; we then have:
+		\begin{equation}
+			z(\lambda)
+			= \abs{\frac{L}{2}} \frac{1}{\sinh \lambda},
+		\quad
+			x^\mu(\lambda)
+			= a^\mu \pm \widehat{p}^\mu \abs{\frac{L}{2}}
+				\coth \lambda
+		\label{eq:hyperbolic}
+		\end{equation}
+		This is an evidence that $z\to\infty$ might not be the ``end of the world'' after all; it's likely that $z\to\infty$ is only a horizon, since a spacelike geodesic $\gamma$ can reach it within finite proper length $\lambda$.
+
+		\end{enumerate}
+
+	\end{enumerate}
+
+	In summary, there are 3 types of spacelike geodesics in Poincar\'e AdS, which closely resemble the 3 types of conic sections:
+	\begin{enumerate}
+	\item $p^2 = 0$: parabolic, given in \eqref{eq:null_type}, with one end going to $z\to 0$ and the other end going to $z\to\infty$; it takes infinite proper length $\lambda$ for it to reach $0$ or $\infty$.
+	\item $p^2 > 0$: hyperbolic, given in \eqref{eq:unified_geodesic} and \eqref{eq:hyperbolic}, also with one end going to $z\to 0$ and the other end going to $z\to\infty$, but it reaches $\infty$ within finite $\lambda$.
+	\item $p^2 > 0$: elliptic, given in \eqref{eq:unified_geodesic} and \eqref{eq:elliptic}, with both ends going to $z\to 0$, and it takes infinite proper length $\lambda$ for it to reach either end. 
+	\end{enumerate}
+
+	Now consider two points $x_1,x_2$ near the boundary $z = \epsilon$ connected by a spacelike geodesic $\gamma$. This can only be the ``elliptic type'' discussed above. We have:
+	\begin{equation}
+		x^\mu
+		= a^\mu \pm \widehat{p}^\mu
+			\sqrt{\pqty{\frac{L}{2}}^{\!\!2} - z^2},
+	\quad
+		z^2 + (x - a)^2
+		= \pqty{\frac{L}{2}}^{\!\!2},
+	\end{equation}
+	\\[-1.5\baselineskip]
+	\begin{equation}
+		a = \frac{x_1 + x_2}{2},
+	\quad
+		\widehat{p} \propto x_2 - x_1
+	\end{equation}
+	It's length is then given by:
+	\begin{equation}
+	\begin{aligned}
+		A
+		&= \int_{z=-\epsilon}^{z=\epsilon}
+			\frac{\dd{x}^2 + \dd{z}^2}{z^2} \\
+		&= \int_{-\Lambda}^{\Lambda}
+			\frac{
+				(\dd{\tanh\lambda})^2
+				+ (\dd{\sech\lambda})^2
+			}{(\sech\lambda)^2},
+		\quad \Lambda
+			= \cosh^{-1} (\tfrac{L}{2\epsilon}) \\
+		&= \int_{-\Lambda}^{\Lambda}
+			\dd{\lambda}
+		= 2\Lambda
+		= 2\cosh^{-1} \pqty{\frac{L}{2\epsilon}}
+		\sim 2\log \frac{L}{\epsilon},
+	\quad \epsilon \to 0
+	\end{aligned}
+	\end{equation}
+
+\appendix
+
+\section{Derivation of the special conformal transformations}
+\label{sect:special_conformal}
+
+	Special conformal transformations can be understood as translations conjugated by \textit{inversions}.
 Note that $\frac{\dd{z}^2}{z^2}$ is invariant under $z\mapsto \frac{1}{z}$; if we include the $x^\mu$ directions, we can consider:
@@
 	\end{equation}
-	\end{enumerate}
 	We see that inversion $\mcal{I}$ is indeed a (discrete) symmetry of the metric. 
@@
 	\begin{aligned}
-		K_\mu
+		k_\mu
 		&= \pdv{a^\mu} \pqty{
@@
 		&= \chi^2 \pdd{\mu}
-			- 2\eta_{\mu\nu} x^\nu \Delta \\
-		&= \pqty{
-				\chi^2 \delta^I_\mu
-				- 2\eta_{\mu\nu} x^\nu X^I
-			} \pdd{I}
+			- 2x_\mu \Delta
+%	\\
+%		&= \pqty{
+%				\chi^2 \delta^I_\mu
+%				- 2x_\mu X^I
+%			} \pdd{I}
 	\end{aligned}
 	\end{equation}
-
-	By Noether's theorem, $Q_\Xi = V_I \Xi^I = G_{IJ} \Xi^I V^J$ is conserved along the geodesic; here $V^I$ is the normalized tangent vector, while $\Xi^I$ is some Killing vector of the spacetime, e.g.~one from the list above.
-
-	We can then write down the conserved charges along a geodesic $\gamma$ in Poincar\'e AdS:
-	\begin{subequations}
-%	\allowdisplaybreaks
-	\begin{align}
-		p_\mu &= G_{\mu I} V^I = V_\mu \\
-		m\id{^\mu_\nu} &= X^\mu V_\nu - X^\nu V_\mu \\
-		\Delta &= X^I V_I
-			= \frac{z V^z + x^\mu p_\mu}{z^2}
-%	,\quad
-%		V^I \sim (v^\mu, v^z)
-		\\
-		k_\mu &= (z^2 + x^2)\, V_\mu - 2\eta_{\mu\nu} x^\nu \Delta
-	\end{align}
-	\end{subequations}
-	These are all integration constants along $\gamma$. 
-	Again note that $X,V$ have indices that should be handled with $G_{IJ}$, in particular,
-	\begin{equation}
-		X_\mu = G_{\mu I} X^I = \frac{1}{z^2} x_\mu
-	\end{equation}
-
-	Equation (a) above implies that $X_\mu(\lambda) = X_\mu(0) + p_\mu \lambda$,
-%	 linear in the affine parameter $\lambda$, 
-	therefore:
-	\begin{equation}
-		x^\mu(\lambda) = X^\mu(\lambda)
-		= X^\mu(0) + p^\mu \lambda z^2,
-	\quad z = z(\lambda)
-	\end{equation}
-	Note the additional $z^2$ factor due to the metric $G$. Plug this into (c)(d)
-%	and ensure that $u^\mu$ is properly normalized
-	and we have:
-	\begin{equation}
-	\begin{gathered}
-%		\delta = g_{IJ} \dd{X^I} \dd{X^J}
-%		= \frac{p^2 + u_z^2}{z^2},
-%	\quad
-%		\delta = 0,\pm 1,
-%	\quad
-%		p^2 = p_\mu p^\mu = \eta_{\mu\nu} p^\mu p^\nu,
-%	\\
-		\Delta = \frac{1}{z} V^z
-			+ \frac{1}{z^2}\, x^\mu(0)\, p_\mu
-			+ p^2 \lambda,
-	\\
-		(z^2 + x^2)\,p^\mu
-		= k^\mu + 2x^\mu \Delta,
-%	\\
-%		z^2 + x^2 - 2\Delta\lambda
-%		= \frac{p_\mu (k^\mu + 2x^\mu(0))}{p_\mu p^\mu},
-%	\\
-%		(z^2 + x^2)\,p^\mu
-%		= k^\mu + 2x^\mu \Delta
-%		= k^\mu + 2x^\mu(0) \Delta + 2\Delta p^\mu \lambda,
-	\end{gathered}
-	\end{equation}
-
-%	For $\delta = 0$, we have $u_z^2 = -p^2$ constant, $z(z) = z(0) + u_z \lambda$ also linear in $\lambda$, i.e.~null geodesics are ``straight'' lines in the $X^I$ coordinates; this agrees with the conformal flatness of the metric.
-For $\delta \ne 0,\delta^2 = 1$, we have:
-	For $p^\mu = 0$, we have $x^\mu = x^\mu(0)$ while (c) implies that $
-		\Delta
-		= \frac{1}{z}\dv{z}{\lambda}
-	$, i.e.~$z(\lambda) = z(0) \,e^{\lambda\Delta}$, with $\norm{V}^2 = \frac{(V^z)^2}{z^2} = \Delta^2$.
-With the standard normalization $\norm{V}^2 = 1$, we get $\Delta = \pm 1$, $z(\lambda) = z(0) \,e^{\lambda\Delta}$; this is a spacelike ``straight'' line along the $z$ direction.
-
-	For $p^\mu \ne 0$, we can always find some $c_\mu$ such that $c_\mu p^\mu \ne 0$, therefore (d) implies that:
-	\begin{equation}
-		z^2 + x^2 - 2\lambda z^2\Delta
-		= \frac{c_\mu \pqty{k^\mu + 2x^\mu(0)\,\Delta}}{c_\mu p^\mu}
-	\end{equation}
-	The right hand side is constant; note that $x^\mu$ is also linear in $\lambda z^2$, therefore we can complete the square on the left hand side such that:
-	\begin{equation}
-		z^2 + \pqty{x - a}^2
-		= \pqty{\frac{L}{2}}^{\!\!2}
-		= \mrm{const.},
-	\quad
-		\Delta
-		= p_\mu a^\mu
-	\end{equation}
-
-	We see that $\gamma$ lands on a ``sphere'' centered at $z = 0, x = a$ in $\mbb{R}^{d,1}$; with the Lorentzian metric, it is actually a hyperboloid.
-Note that for now the radius $\pqty{\frac{L}{2}}^{\!2}$ can actually be negative or zero; more specifically,
-	\begin{enumerate}[noitemsep]
-	\item $L^2 > 0$: one-sheet hyperboloid;
-	\item $L^2 < 0$: two-sheet hyperboloid;
-	\item $L^2 = 0$: conic surface. 
-	\end{enumerate}
 

### 2021-03-14 alpha/GravitationalEntropy/entropy.tex
Add note on gravitational entropy
... & update TeXplates for better cite style

--- 2021-01-10 alpha/YangMills2D/ym2d.tex
@@
 
-\title{2D Yang--Mills \\ \& Cohomological Field Theory}
-\addbibresource{ym2d.bib}
+\title{Notes on Gravitational Entropy}
+\addbibresource{entropy.bib}
 
@@
 \InputIfFileExists{id.tex}{}{}
-
-%\usepackage{cancel}
-\usepackage{xspace}
-\newcommand{\YM}{{\ensuremath{\mrm{YM}_2}}\xspace}
 
@@
 %\addtocounter{section}{-1}
-\section*{Main References}
-	This review is almost entirely based on the following references:
-	\begin{enumerate}[
-		noitemsep
-		,labelindent=\parindent
-		,align=left
-		,leftmargin=*
-	]
-	\item[\cite{Cordes:1994fc}] \textit{Cordes, Moore, Ramgoolam}, \arxiv{hep-th/9411210}
-	\item[\cite{Witten:1991we}] Witten, \textit{On Quantum Gauge Theories in Two Dimensions}, 1991
-	\end{enumerate}
-	It is basically a miniaturized, reorganized, pedagocial subset of \cite{Cordes:1994fc}, focusing on its section 3, with brief summary of its section 9, 10 and 14.
-Many basic facts in this review are therefore uncited to avoid repeated citations of \cite{Cordes:1994fc}.
-All uncited claims, unless otherwise specified, can be traced back to~\cite{Cordes:1994fc}.
-However, it is highly possible that I, in my infinite stupidity, misunderstood some ideas from~\cite{Cordes:1994fc}; so please feel free to point out my mistakes.
-\section{Introduction}
-	We start by writing down the usual Yang--Mills action in 2D (\YM), in Euclidean signature:
+\section{Entanglement Entropy}
+	Ref: \textcite{Apolo:2020qjm}.
+
+	A boundary interval $\mcal{A} \Leftrightarrow \rho_\mcal{A} = e^{-\mcal{H}_\mcal{A}}$.
+$\mcal{H}_\mcal{A}$ is generically nonlocal, but in a highly symmetric background (e.g.~vaccuum) it might be geometrically realized and corresponds to a symmetry of the underlying quantum field theory.
+	In this case there is a generalized Rindler transformation $f$ that maps the casual $\mcal{D} \to \{(\tau,\tilde{x})\}$ in some noncompact generalized Rindler spacetime, with $\pdd{\tau}$ an isometry of the spacetime.
+Then we have:
 	\begin{equation}
-		I_{\YM}
-		= +\frac{1}{4e^2}
-			\int_{\Sigma_T} \dd[2]{x}
-			\sqrt{G}
-			\,\Tr \pqty{F_{\mu\nu} F^{\mu\nu}},
+		\zeta = 2\pi \pdd{\tau}
+		= 2\pi a^i H_i,
 	\quad
-		\sqrt{G} = \sqrt{\det G_{\mu\nu}}
+		\tau \sim \tau + 2\pi i
 	\end{equation}
-	Here we will try follow the convention of \cite{Cordes:1994fc}, despite the fact that it is, unfortunately, not quite self-consistent.
-$\Sigma_T$ stands for the 2D \textit{target}; in the large $N$ limit, it is possible to realize \YM as a string theory with worldsheet $\Sigma_W$, as is proposed by D.~Gross and W.~Taylor, among others \cite{Gross:1992tu,Gross:1993hu,Gross:1993yt}.
+	$H_i$: symmetry generators. Vaccuum$|_\mcal{D}\to$ some thermal state with well-defined temperature $2\pi$.
 
-	Note that in 2D, the $\mfrak{g}$-valued curvature form $F = F^a_{\mu\nu}\,T_a \dd{x^\mu} \wedge \dd{x^\nu}$ is a \textit{top form}; here $T_a$ is the generator of Lie algebra $\mfrak{g} = \mop{Lie} G$, and $G$ is the compact gauge group, e.g.~$G = \mrm{SU}(N)$.
-This means that in 2D, we have:
-	\begin{gather}
-		F = f\mu,\quad f = \hodgedual F,
-	\\
-		\mu = \sqrt{G} \dd[2]{x},\quad
-		F^a_{\mu\nu} = \sqrt{G}\,\epsilon_{\mu\nu} f^a
-	\end{gather}
-	Here $\mu$ is the volume form on $\Sigma_T$, and $f$ is some $\mfrak{g}$-valued 0-form. The original \YM action can thus be rewritten as:
-	\begin{equation}
-		I_{\YM}
-		= \frac{1}{2e^2}
-			\int_{\Sigma_T} \dd[2]{x}
-			\sqrt{G}
-			\,\Tr\,(f^2)
-		= \frac{1}{2e^2}
-			\int_{\Sigma_T} \mu \Tr\,(f^2)
-	\label{eq:scalar_action}
-	\end{equation}
+\section{Entropy as Noether Charge}
+	Ref: \textcite{Wald:1993nt,Lewkowycz:2013nqa,Faulkner:2013ana}.
 
-	First we would like to examine the $e^2 \to 0$ limit of this theory. This can be achieved by a \textit{Hubbard--Stratonovich transformation}\footnote{
-		See \wikiref{https://en.wikipedia.org/wiki/Hubbard\%E2\%80\%93Stratonovich\_transformation}{Hubbard–Stratonovich transformation}. 
-	}; namely, we introduce an additional $\mfrak{g}$-valued field $\phi$ that serves as a Lagrangian multiplier; consider:
-	\begin{equation}
-		I[\phi,A] = \int \pqty{
-				i \Tr\,(\phi F)
-				+ \frac{1}{2}\, e^2\mu \Tr\,(\phi^2)
-			}
-	\label{eq:convenient_action}
-	\end{equation}
-	Using the functional version of the integral identity: $
-		\int \dd{x}
-			e^{
-				- \frac{e^2}{2} x^2
-				- ixy
-			}
-		\sim e^{-y^2/(2e^2)}
-	$, it is straightforward to verify that \cite{Witten:1991we}, up to an overall coefficient,
-	\begin{equation}
-		\int \DD{\phi} e^{-I[\phi,A]}
-		\sim e^{-I_\YM[A]}
-	\end{equation}
-
-	The advantage of this formulation is that the $e^2 \to 0$ limit becomes non-singular; in fact, now we can simply set $e^2 = 0$, and get:
-	\begin{equation}
-		I[\phi,A]
-		\longto I_0[\phi,A]
-		= \int i \Tr\,(\phi F)
-	\label{eq:top_action}
-	\end{equation}
-	This action is in fact \textit{topological}; there is no explicit metric dependence in the action.
-The measure $\mu$ comes with $e^2$ in the $I[\phi,A]$ action; setting $e^2 \to 0$ eliminates the metric dependence.
-Integrating out $\phi$ fixes $F = 0$, i.e.~we need only sum over the moduli of \textit{flat connections}.
-For a principal $G$ bundle $P\to\Sigma_T$, this is given by:
-	\begin{equation}
-		\mcal{M}_0
-		= \mcal{M}\pqty{F = 0, P\to\Sigma_T}
-		= \Bqty{
-				A\in \mcal{A}(P)
-				\,\Big|\,
-				F(A) = 0
-			} \Big/ \mcal{G}(P)
-		\ \subset\ %
-		\mcal{A}(P) \Big/ \mcal{G}(P)
-	\label{eq:flat_moduli}
-	\end{equation}
-	\vspace{-1.2\baselineskip}
-	\begin{gather}
-%	\begin{aligned}
-		\mcal{A}(P)
-%		&
-		= \Bqty\Big{
-			\text{all possible connections $A$ on $P$}
-		} \notag
-	\\
-		\mcal{G}(P)
-%		&
-		= \Bqty\Big{
-			\text{all possible gauge transformations on $P$}
-		} \notag
-%		\\
-%	\end{aligned}\notag
-	\end{gather}
-
-	The moduli space $\mcal{M}_0$ is far from trivial.
-Flatness implies that all contractible loops correspond to trivial holonomy; only non-trivial circles, i.e.~elements of the homotopy group $\pi_1(\Sigma_T)$, may have non-trivial holonomy.
-Furthermore, holonomies that differ by a global gauge transformation are by definition, equivalent.
-In fact, we have \cite{michiels2013moduli}:
-	\begin{equation}
-		\mcal{M}_0 = \Hom \pqty\big{
-				\pi_1(\Sigma_T), G
-			} \big/ G
-	\end{equation}
-	Note that this only identifies the topology of $\mcal{M}_0$; to compute the path integral, we need to derive the measure on $\mcal{M}_0$ following the Faddeev--Popov procedure, which is implemented in \cite{Witten:1991we}.
-
-	For $e^2 \ne 0$, the action $I[\phi,A]$ is metric dependent.
-Somewhat surprisingly, the path integral still contains information about the topology of $\mcal{M}$.
-This is an example of a so-called \textit{cohomological field theory}.
-	The idea of \cite{Cordes:1994fc} is to start from 2D Yang--Mills as a concrete example, and then use its results to motivate a thorough study of {cohomological field theory}.
-
-	As is summarized in \cite{Cordes:1994fc}, \textit{topological field theories} (TFT's), largely introduced by E.~Witten, may be grouped into two classes: \textit{Schwarz type} and \textit{cohomological type}\footnote{
-		Cohomological type TFT's are also called \textit{Witten type} TFT's, e.g.~in \cite{Birmingham:1991ty}.
-However, \cite{Cordes:1994fc} chooses to call them \textit{cohomological}, probably to avoid confusion, since Witten has done wonderful work on both types of the theories.
-	}. 
-	Cohomological field theories, including 2D Yang--Mills with coupling $e^2 \ne 0$, are \textit{not} manifestly metric independent; however, they have a Grassmann-odd nilpotent BRST operator $Q$, and physical observables are $Q$-cohomology classes; amplitudes involving these observables are metric independent, thus they are indeed \textit{topological}.
-Generally speaking, a TFT need \textit{not} be metric independent; the important thing is that it computes \textit{topological invariants}.
-%	because of decoupling of BRST trivial degrees of freedom.
-
-	On the other hand, \textit{Schwarz type} theories have Lagrangians which are metric independent and hence, formally, the quantum theory is expected to be topological. 
-	Examples of such theories include the $e^2 = 0$ \YM described above, and also the Chern--Simons theory in 3D. Also, there is a 4D analog of the action $I[\phi,A]$, given by:
-	\begin{equation}
-		\int \pqty\Big{
-			\Tr\,(BF)
-			+ e^2 \Tr\,(B\wedge\hodgedual B)
-		}
-	\end{equation}
-	The first term with $BF$ is also manifestly topological, similar to $e^2 = 0$ \YM; therefore Schwarz type theories are also called $BF$ type theories.
-
-	Following \cite{Cordes:1994fc}, we will first review the exact solution of \YM, and then try to generalize some aspects for a generic cohomological field theory.
-%	
-%	The abstract discussion concludes in section 14.6 where we give a unified description of an arbitrary cohomological field theory.
-%	
-%	The principles of chapter 14 are illustrated in a standard example in chapters 15, on topological Yang-Mills.
-
-\section{Exact solution of 2D Yang--Mills}
-\subsection{Canonical quantization on the cylinder}
-	One can perform the usual canonical quantization with $I_\YM$ on the cylinder, with coordinates $(x^0,x^1) = (t,x) \in \mbb{R}^1\times S^1$.
-We shall make full use of the gauge redundancies in 2D; recall that a generic gauge transformation can be written as:
-	\begin{equation}
-	\begin{aligned}
-		A'_\mu
-		&= g A_\mu g^{-1}
-			+ g\,\pdd{\mu} (g^{-1}) \\
-		&\simeq A_\mu
-			+ D_\mu\circ\lambda,
-	\end{aligned}
-	\qquad
-		A_\mu = A^a_\mu(t,x),
-	\quad
-		g = e^{-\lambda^a(t,x)\,T_a},
-	\end{equation}
-	\vspace{-1.2\baselineskip}
-	\begin{gather}
-		D_\mu = \pdd{\mu} + A_\mu^a\,T_a,
-	\\[1ex]
-		\pqty{D_\mu\circ\lambda}^a
-		= \pdd{\mu} \lambda^a
-			+ A_\mu^b\,f\id{^a_{bc}} \lambda^c,
-	\quad
-		(T_b)\id{^a_c} = f\id{^a_{bc}}
-	\end{gather}
-	Here $D_\mu$ is the $\mfrak{g}$-valued covariant derivative; it acts on the $\mfrak{g}$-valued gauge parameters $\lambda^a(t,x)$ by the adjoint representation $(T_b)\id{^a_c} = f\id{^a_{bc}}$. 
-	It is thus possible to choose the \textit{temporal gauge} $A_0 = 0$, by simply solving a first order ODE of $\lambda^a(t,x)$, with respect to the variable $x^0 = t$.
-
-	We can further reduce $A_1(t,x)$ with remaining gauge redundancies; with some $t$-independent, but $x$-dependent $g = g(x)$, we can preserve $A_0 = 0$, while reducing $A_1(t,x) = A_1(t)$.
-This is basically the \textit{Coulomb gauge} in 2D, i.e.~we have $\pdd{1} A_1 = 0$.
-
-	Further simplifications can be achieved by working in the \textit{Schr\"odinger picture}, or \textit{Schr\"odinger representation}.
-A nice treatment of 4D Yang--Mills from this ``novel'' perspective can be found in \cite{Hatfield:234595}.
-In conventional formulations of QFT, we are used to work in the \textit{Heisenberg} or \textit{interactive picture}, where the fields evolve in time: $A_1 = A_1(t)$ and satisfy some operator equations of motion (EOM's), which for free theories look identical to the classical EOM's.
-Alternatively, we can take the quantum mechanical approach, and decompose the fields at each time slice $t = t_0$ to a set of time-independent energy eigenstates; in the case of \YM, we have $A_1 = \mrm{const}$.
-	The time evolution is then tracked by the \textit{wave functional} $\Psi_t[A_1]$.
-Since the gauge-fixed $A_1$ has no spacetime dependence, we've actually obtained a equivalent 0-dimensional field theory, i.e.~a quantum mechanical system.
-
-	There are still remaining gauge redundancies; with another spacetime independent, \textit{global} gauge transformation, we can rotate $
-		A_1 = A_1^a\,T_a \in \mfrak{g}
-	$ to the \textit{Cartan subalgebra}, i.e.~the maximal abelian subalgebra of $\mfrak{g}$.
-Finally, we demand that $A_1$ is invariant under the \textit{Weyl group}, which is the symmetry of the Cartan subalgebra.
-Therefore, the \textit{physical} Hilbert space of \YM consists of states given by:
-	\begin{equation}
-		\Psi[A_1],\quad
-		A_1
-		= A_1^a\,T_a
-		\in \textsl{Cartan} \,\Big/ \textsl{Weyl}
-	\label{eq:hilbert_space}
-	\end{equation}
-
-	Alternatively, we can also work with a partial gauge fixing, e.g.~we only impose the temporal gauge $A_0 = 0$, and try to solve for $\Psi_t[A_1(x)]$ by looking at the ``Maxwell's equation" in 2D.
-The time evolution is taken care of by the Schr\"odinger equation for $\Psi_t$; for now we need only look at the spatial constraints.
-We have:
-	\begin{equation}
-		D_1 F_{10} = 0,
-	\quad
-		F_{\mu\nu} = [D_\mu,D_\nu]
-	\label{eq:gauss_law_constraint}
-	\end{equation}
-	This is simply the \YM version of the \textit{Gauss's law} $\vec{\nabla}\cdot\vec{E} = 0$. In \YM, we have only one $\mfrak{g}$-valued component of the field strength:
-	\begin{equation}
-		E = E^a T_a = F_{10}
-	\end{equation}
-
-	One can think of the Gauss's law constraint as the result of integrating out $A_0$, which imposes it's EOM $\fdv{I_\YM}{A_0} = 0$, which is precisely \eqref{eq:gauss_law_constraint}. 
-	However, for a gauged system, there are subtleties that we need to look out for.
-One should account for the gauge volume, which can be treated properly with Faddeev--Popov path integral, and the proper way to implement the constraints is through BRST quantization.
-
-	Fortunately, the na\"ive Gauss's law constraint \textit{does} work in this example.
-In fact, if we solve the Gauss's law constraint as an operator equation of $A_1$, we will get further gauge-fixing \cite{Hatfield:234595}.
-	Alternatively, if we ignore the constraint and proceed with canonical quantization, which might be more convenient in some cases, we would expect \textit{unphysical} degrees of freedom like \textit{null states} to show up, due to the unfixed gauge redundancies.
-The constraint can then be utilized to identify \textit{physical} degrees of freedom, by demanding that it annilates physical states:
-	\begin{equation}
-		D_1 \circ E \ket{\Psi} = 0,
-	\quad E = F_{10}
-	\label{eq:gauss_law_constraint_state}
-	\end{equation}
-	Note that this idea is very much similar to \textit{old covariant quantization} and the \textit{Virasoro constraint} in string theory \cite{Polchinski:1998rq}.
-Again, for a more rigorous treatment, we should turn to the BRST cohomology, but for now this is sufficient.
-
-	In fact, we can actually proved \eqref{eq:gauss_law_constraint_state} by demanding the wave functional $\Psi[A_1(x)]$ to be gauge-invariant \cite{Hatfield:234595}; we shall work in the $A_1(x)$ basis, with $\Psi[A_1(x)] = \braket{A_1(x)}{\Psi}$.
-	The canonical momentum operator is then given by:
-	\begin{equation}
-		E = \fdv{A_1},
-	\quad
-		\bqty{
-			E(x), A_1(x')
-		} = \delta(x - x')
-	\end{equation}
-	Just like the usual quantum mechanical $P = - i\pdv{X}$; the $(-i)$ factor is gone since we are working in Euclidean signature.
-
-	We demand that $\Psi[A_1(x)]$ is gauge-invariant under the \textit{remaining} $t$-independent gauge transformations, $\lambda = \lambda(x)$:
-	\begin{equation}
-	\begin{aligned}
-		0 = \var{\Psi[A_1(x)]}
-		&= \int \dd{x}
-			\fdv{\Psi}{A_1(x)} \var{A_1(x)},
-		\quad \var{A_1(x)} = D_1 \circ \lambda(x) \\
-		&= -\int \dd{x}
-			\lambda(x)\,
-			\pqty{D_1 \circ \fdv{A_1(x)}}
-			\Psi[A_1(x)],
-		\quad E = \fdv{A_1(x)} \\
-		&= -\int \dd{x}
-			\lambda(x)\,
-			\pqty{D_1 \circ E}\,
-			\Psi[A_1(x)],
-		\quad \forall\ \lambda(x)
-	\end{aligned}
-	\end{equation}
-	Indeed this is \eqref{eq:gauss_law_constraint_state} in the $A_1(x)$ basis.
-The formal solution of \eqref{eq:gauss_law_constraint_state} is quite similar to the Schr\"odinger equation, but with path-ordering instead of time-ordering \cite{Minahan:1993np}:
-	\begin{equation}
-		\Psi = \Psi[W],
-	\quad
-		W = \mcal{P} \exp \int_0^L A_1(x)
-	\label{eq:gauss_law_solution}
-	\end{equation}
-
-	From \eqref{eq:gauss_law_solution} we see that in fact there is no direct dependence of $A_1(x)$ in $\Psi[A_1(x)]$; it only depends on the holonomy $W$ around the $S^1$ circle.
-Note that $W$ is similar to the \textit{Wilson loop} operator, but not quite, due to the lack of a trace $\Tr$.
-Such $W$ is not exactly gauge-invariant, but in fact gauge-covariant with respect to the base point:
-	\begin{equation}
-		W' = g_0 W g_0^{-1},
-	\quad
-		g_0 = g(x = 0)
-	\end{equation}
-	Hence further demanding invariance under global gauge transformations requires that $\Psi$ only depends on the \textit{conjugacy class} of $W$. Again we recover \eqref{eq:hilbert_space}, namely,
-	\begin{empheq}{equation}
-		\textbf{
-			The Hilbert space of \YM is the space of \textit{class functions} on $G$
-		}
-	\end{empheq}
-
-	By the Peter--Weyl theorem for $G$ compact we can decompose the Hilbert space by the unitary irreducible representations (\textit{irreps}) $\{R\}$ of $G$. 
-	Consequently, a natural basis for the Hilbert space is provided by the \textit{characters} $\{\chi_R\}$ of the irreps; thus we have, relative to the $W$ basis,
-	\begin{equation}
-		\braket{W}{R}
-		= \chi_R (W)
-		= \Tr_R (W)
-	\end{equation}
-	This is the wave function of the $R$ basis.
-	Here $\Tr_R$ denotes trace with respect to the irrep $R$; recall that $W$ is $\mfrak{g}$-valued and do not have a well-defined trace until we specify a irrep, in this case $R$.
-This is the gauge-invariant Wilson loop operator.
-Note that we are considering pure \YM without matter; the irrep $R$ is not some \textit{a priori} matter representation, but arises naturally as we consider class functions on $G$.
-\sidenote{This is kind of mysterious; does it has a physical interpretation, e.g.~like sum over possible matter representations?}
-\subsection{Hamiltonian and time evolution}
-	Let us now find the Hamiltonian for this theory. We are familiar with the the Hamiltonian density in 4D: $
-		\frac{e^2}{2} \pqty\big{
-			\vec{E}^2 + \vec{B}^2
-		}
-	$; here in 2D, we do not have the magnetic field $\vec{B}$, just a one component $\mfrak{g}$-valued $E = E^a T_a = F_{10}$. Therefore,
-	\begin{gather}
-		H = \frac{e^2}{2} \int \dd{x} \Tr E^2
-		= \frac{e^2}{2} \int \dd{x}
-			\delta^{ab}
-			\fdv{A_1^a(x)}
-			\fdv{A_1^b(x)}
-		\to \frac{1}{2}\,e^2 L
-			\Tr \pqty{W \pdv{W}}^2,
-	\\[1ex]
-		E_a = \fdv{A^a_1(x)}
-		\to T_a W \pdv{W},
-	\quad
-		\Tr\,(T_a T_b) = \delta_{ab}
-	\end{gather}
-	Note that we've followed a more convenient trace convention. 
-	In the last step we've restricted to the physical Hilbert space with $\Psi = \Psi(W)$. Consider $H$ action on the basis $
-		\braket{W}{R}
-		= \chi_R (W)
-		= \Tr_R (W)
-	$, we have:
-	\begin{equation}
-		E_a\, \chi_R (W)
-		= E_a \Tr_R (W)
-		= \Tr_R (T_a W),
-	\end{equation}
-	\vspace{-.9\baselineskip}
-	\begin{equation}
-	\begin{aligned}
-		H\, \chi_R (W)
-		&= \frac{1}{2}\,e^2 L
-			\Tr_R \pqty\big{\delta^{ab} T_a T_b W} \\
-		&= \frac{1}{2}\,e^2 L\,
-			\pqty\big{\delta^{ab} T_a T_b}_R
-			\Tr_R (W) \\
-		&= \frac{1}{2}\,e^2 L
-			C_2(R)\,\chi_R (W),
-	\end{aligned}
-	\end{equation}
-	\vspace{-.3\baselineskip}
-	\begin{equation}
-		C_2(R)
-		= \pqty\big{\delta^{ab} T_a T_b}_R
-	\end{equation}
-	Here $C_2(R)$ is the \textit{quadratic Casimir} of the irrep $R$; it is proportional to $\idty_R$, or can be treated as a $c$-number when restricted to the irrep. We find out that:
-	\begin{empheq}{equation}
-		\textbf{The Hamiltonian $H$ is diagonalized in the $R$ basis and $\propto C_2$}
-	\end{empheq}
-	\vspace{-.3\baselineskip}
-	\begin{equation}
-		H = \frac{1}{2}\,e^2 L C_2
-	\end{equation}
-\subsection{Basic amplitudes}
-	Having diagonalized the Hamiltonian, we can immediately write down the $W$ basis propagator by summing over the $R$ basis; we have:
-	\begin{gather}
-	\begin{aligned}
-		\mel*{W_1}{e^{-HT}}{W_2}
-		&= \sum_R
-			\braket{W_1}{R\,}
-			e^{-H(R)\,T}
-			\braket{R}{W_2} \\
-		&= \sum_R
-			\chi_R(W_1)\,
-			\chi_R(W_2^\dagger)\,
-			e^{-\frac{1}{2}\,e^2 a\,C_2(R)}
-		= Z(W_1,W_2;a),
-	\end{aligned}
-	\\[.3ex]
-		a = LT,
-	\quad
-		\chi_R^\dagger(W)
-		= \pqty{\Tr_R W}^\dagger
-		= \Tr_R (W^\dagger)
-		= \chi_R(W^\dagger)
-	\end{gather}
-	This is the \textbf{cylinder amplitude}. 
-	Note that the combination $\frac{1}{2} e^2 a$ enters together, where $a = LT$ is the area of the cylinder; this is evident from the action $I[\phi,A]$ in \eqref{eq:convenient_action}, where $e^2 \mu$ comes together as a parameter.
-The area dependence is also evident from the scalar action \eqref{eq:scalar_action}, where we that the theory is invariant under \textit{area preserving diffeomorphism}, $\mop{SDiff}(\Sigma_T)$.
-From now on we will absorb $\frac{e^2}{2}$ into $a$, and it will be the only dimensionful parameter of the theory.
-
-	By the orthogonality relations of characters, it is straightforward to verify that the propagator satisfy the \textit{gluing property}:
-	\begin{equation}
-		\int \dd{W}
-			Z(W_1,W;T_1)\,Z(W,W_2;T_2)
-		= Z(W_1,W_2;T_1 + T_2)
-	\end{equation}
-	We see that \YM has very similar properties as those from the categorical approach of CFT and TFT, given by Segal and Atiyah \cite{Segal1988,Atiyah1988}.
-
-	With the gluing property, we can see what happens when one end of the cylinder shrinks to zero size; this is achieved by gluing one cylinder with finite size $a$, with another one that has $a'\to 0$.
-As $a'\to 0$, the corresponding amplitude should be well approximated by the topological action $I_0[\phi,A]$ given in \eqref{eq:top_action}; as we've mentioned before, integrating out $\phi$ sets $F = 0$, which in turn forces the holonomy $W \equiv \idty$.
-The wave function is then given by a Dirac delta function:
-	\begin{equation}
-		\Psi(W) = \delta(W - \idty)
-	\end{equation}
-	This is, up to an overall coefficient, the delta function with respect to the bi-invariant \textit{Haar measure} on the compact $G$.
-Here \textit{bi-invariance} means that the measure is invariant under left and right group multiplication, hence also invariant under conjugacy; therefore it is also a well-defined measure on $G$ classes, where $W$ actually belongs.
-Gluing the cylinder $a$ with the infinitesimal cylinder $a'\to 0$, we find the \textbf{disk (cap) amplitude}:
-	\begin{equation}
-		Z(W,\idty;a)
-		= \sum_R \chi_R(W)\,
-			\pqty{\Tr_R \idty}\,
-			e^{-aC_2(R)}
-		= \sum_R (\dim R)\, \chi_R(W)\,
-			e^{-aC_2(R)}
-	\end{equation}
-
-	By now it is clear that the theory is indeed \textit{topological}; there are no $x$-dependent, propagating degrees of freedom.
-To see degrees of freedom, we must investigate the theory on spacetimes of nontrivial topology\footnote{\sidenote{
-		Then isn't this, in some sense, a theory of Euclidean ``gravity'', or at least a ``string theory'' by itself? As it includes a sum over topologies.
-	}}. In fact, we can compute the amplitudes for more complicated surfaces by standard gluing techniques familiar from axiomatic TFT.
-
-\section{From \YM to general cohomological theory}
-	We've learned quite a few things from our study of \YM; for example, we see that a topological theory need not be manifestly metric independent.
-Also, it is possible, and sometimes more elegant, to solve the theory without a complete gauge fixing.
-These ideas can all be utilized for the study of a general cohomological field theory.
-
-	From a mathematical point of view, topological field theory is the study of \textit{intersection theory} on moduli spaces using physical methods \cite{Cordes:1994fc,Witten:1990bs}.
-In the physical framework these moduli spaces are presented in the general form:
-	\begin{equation}
-		\mcal{M}
-		= \Bqty{
-				A\in \mcal{A}
-				\,\Big|\,
-				DA = 0
-			} \Big/ \mcal{G}
-	\end{equation}
-	We've seen an example of this, from \eqref{eq:flat_moduli}.
-
-	Note that the usual Faddeev--Popov procedure and coventional BRST cohomology requires gauge-fixing.
-Now we would like to develop an alternative method which does not rely on a specific gauge choice.
-In \YM, postponing the gauge fixing leads us to the class functions on $G$, which is more convenient to work with than the gauge-fixed $\textsl{Cartan} \,\big/ \textsl{Weyl}$.
-More generally, we can directly work on the space of fields $\mcal{A}$ before gauge fixing, and consider \textit{$\mcal{G}$-equivariant} quantities on $\mcal{A}$.
-Here $\mcal{G}$ is generally an infinite-dimensional Lie group, the group of all possible gauge transformations.
-This is the idea of \textit{equivariant cohomology}.
-\subsection{Differential complex from ``supersymmetry''}
-	Here we will briefly illustrate the construction of a differential complex, which will be a model for equivariant cohomology.
-We want something that is ``BRST-like'', without going through the Faddeev--Popov gauge-fixing process.
-The idea is to mimic the BRST field contents by introducing \textit{ghosts}, which can be systematically constructed using differential graded algebra (DGA); the grading is the \textit{ghost number}.
-
-	One can then think of these fields as coordinates of some \textit{superspace}, and write down actions of the \textit{superfield} \cite{Cordes:1994fc,Horne:1988yn}.
-It turns out that the \textit{usual} Lie algebra cohomology of this \textit{supersymmetrized} Lie algebra $\mfrak{g}^S$ is the same as the equivariant cohomology of the original Lie algebra $\mfrak{g}$ \cite{Cordes:1994fc,Witten:1990bs}.
-
-	Example $\mcal{N} = (2,2)$
-
-\subsection{Localization}
-
-	2. Fields: When we study equivariant cohomology we must choose a model for the
-	cohomology. A choice of differential complex amounts to a choice of fields.
-	3. Equations: Mathematically, the ultimate objects of study are intersection numbers.
-	The equations are used to isolate interesting subspaces of C.
-One writes Poincaré duals to these subspaces using MQ representatives of Thom forms (thus introducing further fields).
-The equations are viewed as the vanishing of a section of a vector bundle: s = 0 where s(φ) = Dφ is the section of a vector bundle we will call the
-	localization bundle: s ∈ Γ[E localization → C].
-
-	:
-
+\vspace{1.2\baselineskip}
 \raggedright
-
 \printbibliography[%

### 2021-03-14 HW-Gravity/gravity1/gravity1.tex
Update gravity homework: add einbein solution

@@
 
+\section{Einbein Action}
+	The einbein action of a point particle is given by:
+	\begin{equation}
+		S[\eta,X] = \frac{1}{2} \int \dd{\tau} \pqty{
+				\eta^{-1} \dot{X}_\mu \dot{X}^\mu
+				- \eta m^2
+			}
+	\end{equation}
+	Under worldline reparametrization: $\tau \mapsto \tau' = f(\tau)$, we have $X'(\tau') = X(\tau)$, i.e.~$X^\mu$ transforms like a \textbf{scalar} under worldline diffeomorphism; $
+		X(\tau)
+		\mapsto X'(\tau)
+		= X\pqty{f^{-1}(\tau)}
+	$.
+
+	On the other hand, $\eta$ should be treated like an einbein: $\eta = \sqrt{-\gamma}$, here $\gamma = \gamma_{\tau\tau}$ is the worldline metric; $\gamma < 0$ due to the Lorentzian signature. We have:
+	\begin{gather}
+		\eta = \sqrt{-\gamma}
+		\longmapsto \eta' = \eta\,
+			\det \pdv{\tau}{\tau'}
+		= \eta \pdv{\tau}{\tau'},
+	\\[1ex]
+		\eta^{-1}
+		= - \sqrt{-\gamma}\,\gamma^{-1}
+		\longmapsto (\eta')^{-1} = \eta^{-1}
+			\pqty{\pdv{\tau}{\tau'}}
+			\pqty{
+				\pdv{\tau'}{\tau}
+				\pdv{\tau'}{\tau}
+			}
+		= \eta^{-1} \pdv{\tau'}{\tau}
+	\end{gather}
+	It is clear that the action is invariant under the transformation:
+	\begin{equation}
+	\begin{aligned}
+		S'
+		&= \frac{1}{2} \int \dd{\tau'} \pqty\Big{
+				(\eta')^{-1}
+					\pdd{\tau'} X_\mu
+					\pdd{\tau'} X^\mu
+				- (\eta') m^2
+			} \\
+		&= \frac{1}{2} \int \dd{\tau}
+			\pdv{\tau'}{\tau}\,
+			\pqty{
+				\eta^{-1}
+					\pdv{\tau'}{\tau}
+					\cdot
+					\pdv{\tau}{\tau'}
+					\pdd{\tau} X_\mu
+					\cdot
+					\pdv{\tau}{\tau'}
+					\pdd{\tau} X^\mu
+				- \eta\,\pdv{\tau}{\tau'}\,m^2
+			} = S
+	\end{aligned}
+	\end{equation}
+
+	We can eliminate $\eta$ classically by placing it on shell:
+	\begin{equation}
+		0 = \fdv{S}{\eta}
+		= - \eta^{-2} \dot{X}_\mu \dot{X}^\mu
+			- m^2,
+	\quad
+		\eta[X] = \frac{1}{m}
+			\sqrt{-\dot{X}_\mu \dot{X}^\mu}
+	\end{equation}
+	Substitute this back to the action, and we have:
+	\begin{equation}
+	\begin{aligned}
+		S[X] = S[\eta = \eta[X], X]
+		&= \frac{1}{2} \int \dd{\tau} \pqty{
+				m\,(
+					-\dot{X}_\mu \dot{X}^\mu
+				)^{-\frac{1}{2}}
+				\dot{X}_\mu \dot{X}^\mu
+				- m\,(
+					-\dot{X}_\mu \dot{X}^\mu
+				)^{+\frac{1}{2}}
+			} \\
+		&= -m \int \dd{\tau}
+			\sqrt{-\dot{X}_\mu \dot{X}^\mu}
+	\end{aligned}
+	\end{equation}
+
+\section{Ricci Tensor for Static Spherical Metric}
+	Consider the metric:
+	\begin{equation}
+	\begin{aligned}
+		\dd{s}^2
+		= - f(r) \dd{t}^2
+			+ h(r) \dd{r}^2
+			+ r^2 \pqty{
+				\dd{\theta}^2
+				+ \sin^2\theta \dd{\phi}^2
+			}
+		= \eta_{ab}\, e^a e^b
+	\end{aligned}
+	\end{equation}
+	Here we've defined the following vierbein:
+	\begin{equation}
+	\begin{aligned}
+		e^t &= \sqrt{f(r)} \dd{t} \\
+		e^r &= \sqrt{h(r)} \dd{r} \\
+		e^\theta &= r \dd{\theta} \\
+		e^\phi   &= r \sin\theta \dd{\phi} \\
+	\end{aligned}
+	\end{equation}
+
 \appendix

### 2021-03-23 alpha/GravitationalEntropy/entropy.tex
Update notes on grav entropy w/ mod flow

@@
 
-%\addtocounter{section}{-1}
-\section{Entanglement Entropy}
+\addtocounter{section}{-1}
+\section{Conventions}
+	We try to follow the conventions of the TsT paper: \textcite{Apolo:2019zai}. 
+	\begin{itemize}
+	\item Lightcone coordinates: $u,v = x\pm t$, following \cite{Apolo:2019zai} (except that in \cite{Apolo:2019zai} the $x$ direction is compactified into the $\varphi$ circle).
+Constant $t$ slice is therefore given by $u = v$.
+
+	\item Poincar\'e $\mrm{AdS}_3$ coordinates: $
+			X^I \sim (x^\mu,z) \sim (t,x,z) \sim (u,v,z)
+		$, metric: $
+			\dd{s}^2 = \frac{+\dd{u} \dd{v} + \dd{z}^2}{z^2}
+		$. Note the \mquote{+} before $\dd{u} \dd{v}$. 
+	\end{itemize}
+\section{Entanglement Entropy as Thermal Entropy}
 	Ref: \textcite{Apolo:2020qjm}.
@@
 	\begin{equation}
-		\zeta = 2\pi \pdd{\tau}
+		\xi = 2\pi \pdd{\tau}
 		= 2\pi a^i H_i,
@@
 	\end{equation}
-	$H_i$: symmetry generators. Vaccuum$|_\mcal{D}\to$ some thermal state with well-defined temperature $2\pi$.
+	$H_i$: symmetry generators.
+Vaccuum$|_\mcal{D}\to$ some thermal state with normalized inverse temperature $2\pi$.
+Here we choose to absorb such $2\pi$ into the definition of $\xi$, so the Euclidean periodicity w.r.t.~$\xi$ is simply $\beta = 1 = \frac{1}{T}$, which means the surface gravity along the horizon is given by $\kappa = 2\pi T = 2\pi$.
+\subsection{Exercise: Poincar\'e $\mrm{AdS}_3/\mrm{CFT}_2$}
+	We illustrate the above ideas in Poincar\'e $\mrm{AdS}_3$ vaccuum, which is the simplest situation and can be easily compared with the results of \textcite{Lewkowycz:2019xse}. 
+\subsubsection{Bulk / boundary Killings}
+	In Poincar\'e $\mrm{AdS}_3/\mrm{CFT}_2$, the $H_i$'s are given by $L_n,\bar{L}_n$ with $n=0,\pm 1$. At $z\to 0$ we recover the usual global $\mfrak{sl}(2,\mbb{R})$ generators:
+	\begin{equation}
+		z\to 0,
+	\quad
+		      L_n \to -u^{n+1} \pdd{u},\quad
+		\bar{L}_n \to -v^{n+1} \pdd{v}
+	\end{equation}
+	Q: Why we only include the global generators on the field theory side? A: These are the symmetries of the Poincar\'e vaccuum.
+
+	One could argue that $L_{n>1}$ still annihilates the vaccuum $\ket{0}$, however we should actually consider all possible correlations w.r.t.~$\ket{0}$, and require that they remain unchanged under variation of $\ket{0}$.
+This translates to:
+	\begin{equation}
+		0 = \bqty{\rho,L_n}
+		= \bqty\Big{\dyad{0},L_n}
+	\end{equation}
+	Note that $L^\dagger_n = L_{-n}$, we thus have the restriction that $n = 0,\pm 1$.
+
+	To extend it to the bulk, think of the corresponding bulk isometries: translations, rotations, dilations and special conformal transformations:
+	\begin{equation}
+	\begin{aligned}
+		P_\mu
+		&= \pdd{\mu},\\
+		m_{uv}
+		&= x_\mu \pdd{\nu} - x_\nu \pdd{\mu}
+		= u\pdd{u} - v\pdd{v},\\
+		\Delta
+		&= X^I \pdd{I}
+		= u\pdd{u} + v\pdd{v} + z\pdd{z},\\
+		K_\mu
+		&= (z^2 + uv)\,\pdd{\mu}
+			- 2\eta_{\mu\nu} x^\nu \Delta,
+	\end{aligned}
+	\end{equation}
+	\begin{equation}
+		K_u = (z^2 + uv)\,\pdd{u} - v \Delta,
+	\quad
+		K_v = (z^2 + uv)\,\pdd{v} - u \Delta
+	\end{equation}
+	By requiring that a linear combination of these generators reduce to the boundary $L_n$'s, one can uniquely extend the $L_n,\bar{L}_n$'s into the bulk; see \texttt{modFlowCheck.nb}.
+The result for $L_n$ is listed below; for $\bar{L}_n$ one need only exchange all $u\leftrightarrow v$.
+	\begin{equation}
+		L_{-1} = -\pdd{u},
+	\quad
+		L_0 = -u\,\pdd{u} - \frac{z}{2}\,\pdd{z},
+	\quad
+		L_1 = -u^2\pdd{u} + z^2 \pdd{v}
+			- uz\,\pdd{z}
+	\end{equation}
+\subsubsection{Bulk modular flow}
+	RT surface (spacelike geodesic of Poincar\'e AdS with both ends attached to the boundary) is parametrized in terms of its end points $(t,x)_\pm$; its the intersection of a ``sphere'' (hyperboloid) and a plane through its center:
+	\begin{equation}
+	\text{``sphere'':}\quad
+		z^2
+		+ \pqty{x - \frac{x_+ + x_-}{2}}^{\!\!2}
+		- \pqty{t - \frac{t_+ + t_-}{2}}^{\!\!2}
+		= \pqty{\frac{L}{2}}^{\!\!2}
+		= \pqty{\frac{x_+ - x_-}{2}}^{\!\!2}
+		- \pqty{\frac{t_+ - t_-}{2}}^{\!\!2}
+	\end{equation}
+	\begin{equation}
+		L^2
+		= \pqty{x_+ - x_-}^2
+			- \pqty{t_+ - t_-}^2
+		= (u_+ - u_-)(v_+ - v_-)
+	\end{equation}
+	\begin{equation}
+	\text{plane:}\quad
+		\frac{x - \frac{1}{2} (x_+ + x_-)}{x_+ - x_-}
+		= \frac{t - \frac{1}{2} (t_+ + t_-)}{t_+ - t_-}
+	\end{equation}
+	See \href{https://bryango.github.io/resources/archive/HW-Gravity/gravity1.pdf}{\underline{this homework}} for a detailed derivation. 
+	Alternatively, it can be more compactly rewritten with $x^\mu \sim (t,x)$ or $(u,v)$; mind the various $\pm$ signs in the above expressions: 
+	\begin{equation}
+	\begin{aligned}
+		0 &= z^2
+			+ \eta_{\mu\nu} (x - x_+)^\mu (x - x_-)^\nu \\
+		& = z^2
+			+ (x - x_+)(x - x_-)
+			- (t - t_+)(t - t_-) \\
+		&= z^2 + \frac{
+				(u - u_+)(v - v_-)
+				+ (v - v_+)(u - u_-)
+			}{2}
+	\end{aligned}
+	\end{equation}
+
+	Bulk modular generator vanishes along the RT surface, i.e.~RT surface is the fixed point of the modular flow; with this condition we can fix the coefficients of the modular generator, up to an overall coefficient\footnote{
+		One can compare this with similar results in the literature such as \cite{Lashkari:2016idm,Czech:2019vih,Apolo:2020qjm}. 
+	}:
+	\begin{equation}
+		\xi = 2\pi \sum_{n=0,\pm 1} \pqty{
+				s_n L_n - \bar{s}_n \bar{L}_n
+			},
+	\end{equation}
+	\begin{equation}
+		s_{-1} = \frac{u_+ u_-}{u_+ - u_-},\quad
+		s_0 = - \frac{u_+ + u_-}{u_+ - u_-},\quad
+		s_{+1} = \frac{1}{u_+ - u_-}
+	\end{equation}
+	One need only exchange all $u\leftrightarrow v$ to obtain $\bar{s}_n$.
+The overall coefficient of $\xi$ (in this case, $2\pi$) is fixed by normalizing the temperature of the horizon, namely we demand that the surface gravity is $2\pi$ along the RT surface:
+	\begin{equation}
+		T = \frac{\kappa}{2\pi} = 1,
+	\quad
+		\kappa^2
+		= (2\pi)^2
+		= -\frac{1}{2}\,
+			(\nabla_{\mu} \xi_{\nu})
+			(\nabla^{\mu} \xi^{\nu})
+	\end{equation}
+
+\subsubsection{Modular flow at the cutoff surface}
+	We now restrict to an interval centered at the origin: $
+		u_\pm v_\pm
+		= x^2_\pm - t^2_\pm
+		= (\frac{L}{2})^2
+	$, $x_\pm = -x_\mp$, and same for $t_\pm, u_\pm, v_\pm$. 
+	We then introduce the \textit{rapidity} variable $\theta$ to nicely parametrized the boosted interval; for a constant time slice, we have $\theta = 0$. For a general boosted interval, we have:
+	\begin{equation}
+		x_\pm = \pm \frac{L}{2} \cosh \theta,
+	\quad
+		t_\pm = \pm \frac{L}{2} \sinh \theta,
+	\end{equation}
+	For now the coordinates $u_\pm, v_\pm, x_\pm, t_\pm$ are all specified at $z\to 0$, i.e.~at the \textbf{asymptotic boundary}. Note that the RT surface lies on the plane $
+		t_\pm / x_\pm = \tanh \theta
+	$, namely $\theta$ is constant along the RT surface. 
+	We have:
+	\begin{gather}
+	\begin{aligned}
+		\xi &= \frac{2\pi}{L} \bigg\{
+			\pqty\Big{
+				\pqty{
+					(\tfrac{L}{2})^2 - z^2
+					- (t^2 + x^2)
+				} \cosh\theta
+				+ 2tx \sinh\theta
+			} \,\pdd{t}
+		\\ &\qquad\qquad 
+			+ \pqty\Big{
+				\pqty{
+					(\tfrac{L}{2})^2 - z^2
+					+ (t^2 + x^2)
+				} \sinh\theta
+				- 2tx \cosh\theta
+			} \,\pdd{x}
+		\\ &\qquad\qquad 
+			+ \pqty\big{
+				x\sinh\theta
+				- t\cosh\theta
+			} \,2z\pdd{z}
+		\bigg\}
+	\end{aligned}
+	\end{gather}
+
+	We see that the $\pdd{z}$ term vanishes in the following two cases:
+	\begin{itemize}[noitemsep]
+	\item as $z\to 0$, i.e.~near the asymptotic boundary;
+	\item within the plane $
+			x\sinh\theta
+			= t\cosh\theta
+		$ where the RT surface lies. 
+	\end{itemize}
+	Now we'd like to study $\xi$ not at the asymptotic boundary, but at some \textbf{constant finite cutoff} $z = z_c$. 
+	Note that is the size (coordinate length) of the interval at the {asymptotic boundary}; the coordinate length of the \textbf{cutoff interval $l$}, on the other hand, is given by:
+	\begin{equation}
+		\pqty{\frac{l}{2}}^{\!\!2}
+		= \pqty{\frac{L}{2}}^{\!\!2} - z_c^2,
+	\quad
+		x_\pm^c
+		= \pm \frac{l}{2}
+	\end{equation}
+	\begin{equation}
+	\begin{aligned}
+%		\xi_c \equiv
+		\xi|_{z=z_c, \pdd{z}\to 0}
+		= \frac{2\pi}{\sqrt{
+				l^2 + (2z_c)^2
+			}}
+		& \bigg\{
+			\pqty\Big{
+				\pqty{
+					(\tfrac{l}{2})^2
+					- (t^2 + x^2)
+				} \cosh\theta
+				+ 2tx \sinh\theta
+			} \,\pdd{t}
+		\\[-.5ex] &\quad 
+			+ \pqty\Big{
+				\pqty{
+					(\tfrac{l}{2})^2
+					+ (t^2 + x^2)
+				} \sinh\theta
+				- 2tx \cosh\theta
+			} \,\pdd{x}
+		\\ &\quad 
+			+ \pqty\big{
+				x\sinh\theta
+				- t\cosh\theta
+			} \,2z_c\pdd{z}
+		\bigg\}
+	\end{aligned}
+	\end{equation}
+
+\pagebreak[3]
+	This seems nice and all but there is a subtlety for finite cutoff $z = z_c$. 
+	In the bulk the constant surface gravity $
+		\xi^\nu \cdv{\nu} \xi^\mu
+		= \kappa \xi^\mu
+		= 2\pi \xi^\mu
+	$ guarantees that after Wick rotation, the Euclidean periodicity around the horizon is normalized to $\beta = 1$.
+However, if we restrict to the field theory living at $z = z_c$, which corresponds to a $T\bar{T}$ deformed theory, since it has no knowledge of the $\pdd{z}$ component of $\xi$, we should project the $z$ component out, which leaves us:
+	\begin{equation}
+	\begin{aligned}
+		\xi^{\mrm{FT}}_c
+		\equiv \proj{z_c} \xi|_{z_c}
+		= \frac{2\pi}{\sqrt{
+				l^2 + (2z_c)^2
+			}}
+		& \bigg\{
+			\pqty\Big{
+				\pqty{
+					(\tfrac{l}{2})^2
+					- (t^2 + x^2)
+				} \cosh\theta
+				+ 2tx \sinh\theta
+			} \,\pdd{t}
+		\\[-2ex] &\quad 
+			+ \pqty\Big{
+				\pqty{
+					(\tfrac{l}{2})^2
+					+ (t^2 + x^2)
+				} \sinh\theta
+				- 2tx \cosh\theta
+			} \,\pdd{x}
+		\bigg\}
+	\end{aligned}
+	\end{equation}
+	Which no longer has normalized $\beta$ if $z_c \ne 0$.
+In fact, compared to the $z_c \to 0$ situation which \textit{does} have $\beta = 1$, $\xi^{\mrm{FT}}_c$ is rescaled by a factor of $\frac{l}{L}$, which means that:
+	\begin{equation}
+		\beta^{\mrm{FT}}_c
+		= \sqrt{1 + (2z_c/l)^2}
+		\sim 1 + 2z_c^2 / l^2
+	\end{equation}
+
+	How should we understand this?
+	\begin{itemize}
+	\item $T\bar{T}$ deformation might somehow correspond to a variation of temperature at the cutoff; instead of $\rho = e^{-\mcal{H}}$, we now have:
+	\begin{equation}
+		\rho = e^{-\beta\mcal{H}},
+	\quad \beta \sim 1 + \frac{1}{l^2} \order{\mu}
+	\end{equation}
+	Where $\mu$ is the deformation parameter (see \cite{Apolo:2019zai} for the convention we follow). Q: how do we make this precise?
+
+	\item The non-local nature of $T\bar{T}$ deformation creates some $\order{z_c}$ ``fuzziness'' in the cutoff theory at $z = z_c$; $\beta \sim 1$ holds, but only up to some coarse-graining of points.
+Q: again, how do we make this precise?
+
+	\item Instead of projecting out the $\pdd{z}$ component of $\xi$, maybe we could \textit{define} the evolution of the cutoff interval by following the flow of $\xi$ starting from the RT surface at $z = z_c$.
+Now there is no longer a projection of $\xi$; we are always following it along the boundary, so the periodicity is preserved: $\beta = 1$.
+But now this is no longer a \textit{constant} cutoff away from $z = z_c$.
+In particular, the forward and backward evolved interval will approach the upper and lower endpoints of the diamond at $z \to 0$.
+Q: does this make sense?
+Will it be compatible with \textcite{McGough:2016lol}?
+	\end{itemize}
+
+	\begin{figure}[!h]
+	\centering
+	\includegraphics[width=.8\linewidth]{img/modFlowXsection.pdf}
+	\hspace{2em}
+	\vspace{-2ex}
+	\caption{Modular flow at constant $x$ slices}
+	\end{figure}
 
 \section{Entropy as Noether Charge}
-	Ref: \textcite{Wald:1993nt,Lewkowycz:2013nqa,Faulkner:2013ana}.
+	Ref: \textcite{Wald:1993nt,Iyer:1994ys,Iyer:1995kg}.
+
+	Ref: \textcite{Lewkowycz:2013nqa,Faulkner:2013ana}.
+
+	Gravitational entropy is the Noether charge $Q_\xi$ associated with some horizon generator $\xi$.
+In the case of entanglement entropy between a simple interval and its complement, we've found its corresponding modular flow in the bulk, which is precisely the horizon generator of the Rindler patch.
+We then aim to compute the charge variation using the covariant formula:
+	\begin{equation}
+		\var{Q}_{\xi} [\var{g}, g]
+		= \frac{1}{16 \pi G}
+			\int_{\pd\Sigma}
+			\sqrt{|g|} \dd{x}^{\alpha}
+				\varepsilon_{\alpha\mu\nu}\,
+				k_\xi^{\mu\nu} [\var{g}, g]
+	\end{equation}
+	However, to compute $\var{Q}$ we need to consider a particular metric variation $\var{g}_{\mu\nu}$ in the phase space of solutions.
+There is no free parameter in Poincar\'e $\mrm{AdS}_3$, unless we turn on temperature; this leads to the BTZ geometry.
+
+	We thus have to repeat the calculations above to get the geodesic $\gamma$ and modular generators $\xi^\mu$ in the new backgrounds.
+However, it is convenient to remember that all BTZ black holes are locally equivalent to the pure $\mrm{AdS}_3$; we can map Poincar\'e $(u,v,z)$ to BTZ $(t,r,\phi)$ by \cite{Hubeny:2007xt}:
+	\begin{equation}
+		u,v = \sqrt{\frac{r^2 - r_+^2}{r^2 - r_-^2}}\,
+			e^{(\phi\pm t)\,2T_{u,v}},
+	\quad
+		z = \sqrt{\frac{r_+^2 - r_-^2}{r^2 - r_-^2}}\,
+			e^{\phi r_+ + t r_-},
+	\end{equation}
+	\begin{gather}
+		r_\pm = T_u \pm T_v,
+	\quad
+		8GM = r_+^2 + r_-^2
+		= 2\,(T_u^2 + T_v^2),
+	\quad
+		4GJ = r_+ r_-
+		= T_u^2 - T_v^2,
+	\end{gather}
 

### 2021-03-25 alpha/GravitationalEntropy/entropy.tex
Update note on entropy

@@
 	A boundary interval $\mcal{A} \Leftrightarrow \rho_\mcal{A} = e^{-\mcal{H}_\mcal{A}}$.
-$\mcal{H}_\mcal{A}$ is generically nonlocal, but in a highly symmetric background (e.g.~vaccuum) it might be geometrically realized and corresponds to a symmetry of the underlying quantum field theory.
+$\mcal{H}_\mcal{A}$ is generically nonlocal, but in a highly symmetric background (e.g.~vacuum) it might be geometrically realized and corresponds to a symmetry of the underlying quantum field theory.
 	In this case there is a generalized Rindler transformation $f$ that maps the casual $\mcal{D} \to \{(\tau,\tilde{x})\}$ in some noncompact generalized Rindler spacetime, with $\pdd{\tau}$ an isometry of the spacetime.
@@
 		\xi = 2\pi \pdd{\tau}
-		= 2\pi a^i H_i,
+		= 2\pi \sum_i a^i H_i,
 	\quad
@@
 	$H_i$: symmetry generators.
-Vaccuum$|_\mcal{D}\to$ some thermal state with normalized inverse temperature $2\pi$.
+The causal domain of dependence $\mcal{D}\to$ some thermal state with normalized inverse temperature $2\pi$.
 Here we choose to absorb such $2\pi$ into the definition of $\xi$, so the Euclidean periodicity w.r.t.~$\xi$ is simply $\beta = 1 = \frac{1}{T}$, which means the surface gravity along the horizon is given by $\kappa = 2\pi T = 2\pi$.
 \subsection{Exercise: Poincar\'e $\mrm{AdS}_3/\mrm{CFT}_2$}
-	We illustrate the above ideas in Poincar\'e $\mrm{AdS}_3$ vaccuum, which is the simplest situation and can be easily compared with the results of \textcite{Lewkowycz:2019xse}. 
+	We illustrate the above ideas in Poincar\'e $\mrm{AdS}_3$ vacuum, which is the simplest situation and can be easily compared with the results of \textcite{Lewkowycz:2019xse}. 
 \subsubsection{Bulk / boundary Killings}
@@
 		      L_n \to -u^{n+1} \pdd{u},\quad
-		\bar{L}_n \to -v^{n+1} \pdd{v}
+		\bar{L}_n \to -v^{n+1} \pdd{v},\quad
+	n = 0,\pm 1
 	\end{equation}
-	Q: Why we only include the global generators on the field theory side? A: These are the symmetries of the Poincar\'e vaccuum.
+	Q: Why we only include the global generators on the field theory side? A: These are the symmetries of the Poincar\'e vacuum.
 
-	One could argue that $L_{n>1}$ still annihilates the vaccuum $\ket{0}$, however we should actually consider all possible correlations w.r.t.~$\ket{0}$, and require that they remain unchanged under variation of $\ket{0}$.
-This translates to:
+	One could argue that $L_{n>1}$ still annihilates the vacuum $\ket{0}$, however we should actually consider all possible correlations w.r.t.~$\ket{0}$, and require that they remain unchanged under variation of $\ket{0}$.
+This means that:
 	\begin{equation}
@@
 	\end{equation}
-	By requiring that a linear combination of these generators reduce to the boundary $L_n$'s, one can uniquely extend the $L_n,\bar{L}_n$'s into the bulk; see \texttt{modFlowCheck.nb}.
-The result for $L_n$ is listed below; for $\bar{L}_n$ one need only exchange all $u\leftrightarrow v$.
+	By requiring that a linear combination of these generators reduce to the boundary $L_n$'s, one can uniquely extend the $L_n,\bar{L}_n$'s into the bulk; see \texttt{modFlowPoincare.nb}.
+The result for $L_n$'s is listed below; for $\bar{L}_n$ one need only exchange all $u\leftrightarrow v$.
 	\begin{equation}
@@
 \subsubsection{Bulk modular flow}
-	RT surface (spacelike geodesic of Poincar\'e AdS with both ends attached to the boundary) is parametrized in terms of its end points $(t,x)_\pm$; its the intersection of a ``sphere'' (hyperboloid) and a plane through its center:
+	The RT surface (spacelike geodesic of Poincar\'e AdS with both ends attached to the boundary) is parametrized in terms of its end points $(t,x)_\pm$; it's the intersection of a ``sphere'' (hyperboloid) and a plane through its center:
 	\begin{equation}
@@
 
-	Bulk modular generator vanishes along the RT surface, i.e.~RT surface is the fixed point of the modular flow; with this condition we can fix the coefficients of the modular generator, up to an overall coefficient\footnote{
+	The bulk modular generator vanishes along the RT surface, i.e.~the RT surface is the fixed point of the modular flow; with this condition we can fix the coefficients of the modular generator, up to an overall coefficient\footnote{
 		One can compare this with similar results in the literature such as \cite{Lashkari:2016idm,Czech:2019vih,Apolo:2020qjm}. 
@@
 		= x^2_\pm - t^2_\pm
-		= (\frac{L}{2})^2
+		= (\frac{L_\infty}{2})^2
 	$, $x_\pm = -x_\mp$, and same for $t_\pm, u_\pm, v_\pm$. 
@@
 	\begin{equation}
-		x_\pm = \pm \frac{L}{2} \cosh \theta,
+		x_\pm = \pm \frac{L_\infty}{2} \cosh \theta,
 	\quad
-		t_\pm = \pm \frac{L}{2} \sinh \theta,
+		t_\pm = \pm \frac{L_\infty}{2} \sinh \theta,
 	\end{equation}
-	For now the coordinates $u_\pm, v_\pm, x_\pm, t_\pm$ are all specified at $z\to 0$, i.e.~at the \textbf{asymptotic boundary}. Note that the RT surface lies on the plane $
+	For now the coordinates $u_\pm, v_\pm, x_\pm, t_\pm$ and the coordinate length $L_\infty$ are all specified at $z\to 0$, i.e.~at the \textbf{asymptotic boundary}.
+Note that the RT surface lies on the plane $
 		t_\pm / x_\pm = \tanh \theta
@@
 	\begin{aligned}
-		\xi &= \frac{2\pi}{L} \bigg\{
+		\xi &= \frac{2\pi}{L_\infty} \bigg\{
 			\pqty\Big{
 				\pqty{
-					(\tfrac{L}{2})^2 - z^2
+					(\tfrac{L_\infty}{2})^2 - z^2
 					- (t^2 + x^2)
@@
 				\pqty{
-					(\tfrac{L}{2})^2 - z^2
+					(\tfrac{L_\infty}{2})^2 - z^2
 					+ (t^2 + x^2)
@@
 
+\pagebreak[3]
 	We see that the $\pdd{z}$ term vanishes in the following two cases:
@@
 	\item as $z\to 0$, i.e.~near the asymptotic boundary;
-	\item within the plane $
+	\item within the whole plane $
 			x\sinh\theta
@@
 	Now we'd like to study $\xi$ not at the asymptotic boundary, but at some \textbf{constant finite cutoff} $z = z_c$. 
-	Note that is the size (coordinate length) of the interval at the {asymptotic boundary}; the coordinate length of the \textbf{cutoff interval $l$}, on the other hand, is given by:
+	Note that is the size (coordinate length) of the interval at the {asymptotic boundary}; the coordinate length of the \textbf{cutoff interval $L$}, on the other hand, is given by:
 	\begin{equation}
-		\pqty{\frac{l}{2}}^{\!\!2}
-		= \pqty{\frac{L}{2}}^{\!\!2} - z_c^2,
+		\pqty{\frac{L}{2}}^{\!\!2}
+		= \pqty{\frac{L_\infty}{2}}^{\!\!2} - z_c^2,
 	\quad
 		x_\pm^c
-		= \pm \frac{l}{2}
+		= \pm \frac{L}{2}
 	\end{equation}
@@
 		= \frac{2\pi}{\sqrt{
-				l^2 + (2z_c)^2
+				L^2 + (2z_c)^2
 			}}
@@
 				\pqty{
-					(\tfrac{l}{2})^2
+					(\tfrac{L}{2})^2
 					- (t^2 + x^2)
@@
 				\pqty{
-					(\tfrac{l}{2})^2
+					(\tfrac{L}{2})^2
 					+ (t^2 + x^2)
@@
 	Which no longer has normalized $\beta$ if $z_c \ne 0$.
-In fact, compared to the $z_c \to 0$ situation which \textit{does} have $\beta = 1$, $\xi^{\mrm{FT}}_c$ is rescaled by a factor of $\frac{l}{L}$, which means that:
+In fact, compared to the $z_c \to 0$ situation which \textit{does} have $\beta = 1$, $\xi^{\mrm{FT}}_c$ is rescaled by a factor of $\frac{L}{L_\infty}$, which means that:
 	\begin{equation}
 		\beta^{\mrm{FT}}_c
-		= \sqrt{1 + (2z_c/l)^2}
-		\sim 1 + 2z_c^2 / l^2
+		= \sqrt{1 + (2z_c/L)^2}
+		\sim 1 + 2z_c^2 / L^2
 	\end{equation}
@@
 	\begin{itemize}
-	\item $T\bar{T}$ deformation might somehow correspond to a variation of temperature at the cutoff; instead of $\rho = e^{-\mcal{H}}$, we now have:
+	\item The $T\bar{T}$ deformation might somehow correspond to a variation of temperature at the cutoff; instead of $\rho = e^{-\mcal{H}}$, we now have:
 	\begin{equation}
 		\rho = e^{-\beta\mcal{H}},
-	\quad \beta \sim 1 + \frac{1}{l^2} \order{\mu}
+	\quad \beta \sim 1 + \frac{1}{L^2} \order{\mu}
 	\end{equation}
@@
 
-	\item Instead of projecting out the $\pdd{z}$ component of $\xi$, maybe we could \textit{define} the evolution of the cutoff interval by following the flow of $\xi$ starting from the RT surface at $z = z_c$.
+	\item Instead of projecting out the $\pdd{z}$ component of $\xi$, maybe we could \textit{define} the evolution of the cutoff interval by following the flow of $\xi = 2\pi\pdd{\tau}$ starting from the RT surface at $z = z_c$.
 Now there is no longer a projection of $\xi$; we are always following it along the boundary, so the periodicity is preserved: $\beta = 1$.
+
 	But now this is no longer a \textit{constant} cutoff away from $z = z_c$.
@@
 
-	\begin{figure}[!h]
+	\begin{figure}[!ht]
 	\centering
@@
 	\caption{Modular flow at constant $x$ slices}
+	\end{figure}
+
+	\begin{figure}[!ht]
+	\centering
+	\includegraphics[width=.35\linewidth]{img/modFlowCutoff.pdf}
+%	\hspace{2em}
+%	\vspace{-2ex}
+	\caption{Integral surface of the modular flow starting from $t = 0,\ z = z_c$. Here we've chosen $\frac{L}{2} = 1$ while $z_c = 0.35$.}
 	\end{figure}
@@
 		\var{Q}_{\xi} [\var{g}, g]
+		= \int_{\pd\Sigma}
+			\chi_\xi
 		= \frac{1}{16 \pi G}
@@
 	\end{equation}
+	\begin{equation}
+	\begin{aligned}
+		k_\xi^{\mu\nu}[\var g, g]
+		= \frac{1}{2} \Big \{
+		& \xi^{\nu}\nabla^{\mu} \var g^{\alpha}{}_{\alpha}
+		- \xi^{\nu} \nabla_{\alpha} \var g^{\alpha\mu}
+		+ \xi_{\alpha} \nabla^{\nu} \var g^{\alpha\mu}  \\
+		&+ \frac{1}{2} \var g^{\alpha}{}_{\alpha} \nabla^{\nu} \xi^{\mu}
+		- \frac{1}{2} \var g^{\nu\alpha} \nabla_{\alpha}\xi^{\mu}
+		+ \frac{1}{2} \var g^{\nu\alpha} \nabla^{\mu} \xi_{\alpha} \\
+		&- (\mu \leftrightarrow \nu) \Big \}
+	\end{aligned}
+	\label{kdef}
+	\end{equation}
 	However, to compute $\var{Q}$ we need to consider a particular metric variation $\var{g}_{\mu\nu}$ in the phase space of solutions.
@@
 	We thus have to repeat the calculations above to get the geodesic $\gamma$ and modular generators $\xi^\mu$ in the new backgrounds.
-However, it is convenient to remember that all BTZ black holes are locally equivalent to the pure $\mrm{AdS}_3$; we can map Poincar\'e $(u,v,z)$ to BTZ $(t,r,\phi)$ by \cite{Hubeny:2007xt}:
+However, it is convenient to remember that all BTZ black holes are locally equivalent to the pure $\mrm{AdS}_3$; we can then map Poincar\'e $(u,v,z)$ to BTZ $(t,r,\phi)$ by \cite{Hubeny:2007xt}:
 	\begin{equation}
@@
 	\end{gather}
+	\begin{equation}
+		\dd{s}^2
+		= \frac{r^2 \dd{r}^2}{
+				(r^2 - r_+^2)
+				(r^2 - r_-^2)
+			}
+			+ T_u^2 \dd{u}^2
+			+ T_v^2 \dd{v}^2
+			+ (r^2 - T_u^2 - T_v^2) \dd{u} \dd{v}
+	\end{equation}
+	$\gamma$ and $\xi^\mu$ in BTZ coordinates both follow from this map.
+
+	We now restrict to $t_\pm = 0, \phi_- = -\phi_+$ and set $T_u = T_v = T$ for convenience; in this case the RT surface is given by \cite{Rangamani:2016dms}:
+	\begin{equation}
+		r(\phi) = \frac{2T\cosh TL}{
+				\sqrt{\cosh^2 TL - \cosh^2 2T\phi}
+			}
+	\end{equation}
+	The charge variation has a nice form under the above simplifications; in this case we have $
+		\var{Q}_{\xi}
+		= \int \dd{\phi} (\chi_\xi)_\phi
+	$, where:
+	\begin{equation}
+		(\chi_\xi)_\phi
+		= \frac{\var{T} \coth (LT)}{2G}
+			\pqty{
+				1 - {\frac{r}{\sqrt{r^2 - 4T^2}}}
+				\frac{\cosh (2T\phi)}{\cosh (TL)}
+			}
+	\end{equation}
+
+	The $\int_\gamma \dd{\phi}$ integration can be done at the asymptotic infinity $r\to\infty$ instead, due to Stokes' theorem; this gives the following result:
+	\begin{equation}
+		\var{Q}_\xi
+		= \frac{\var{T}}{2G} \pqty{
+				L \coth (LT) - \frac{1}{T}
+			}
+	\end{equation}
+	With a final integration w.r.t.~$\var{T}$ in the phase phase, we recover the resulting charge, which agrees with the entanglement entropy in \cite{Rangamani:2016dms} up to an overall constant shift:
+	\begin{equation}
+		Q_\xi = \frac{1}{2G} \log \frac{\sinh (LT)}{T}
+	\end{equation}
+
+\subsection{With constant cutoff}
+	Now we consider constant cutoff at $r = r_c$.
+Again we need to trade $L_\infty$ above with the coordinate length of the interval $L$ at the cutoff $r_c$.
+The relation can be solved by looking at the geodesic equation, which is slightly non-trivial this time:
+	\begin{equation}
+		\frac{\cosh (L_\infty T)}{\cosh (LT)}
+		= \frac{r_c}{\sqrt{r_c^2 - 4T^2}}
+	\end{equation}
+	\begin{equation}
+		r(\phi) = \frac{2T\cosh TL}{
+				\sqrt{\cosh^2 TL - \pqty\big{
+					1 - \frac{4T^2}{r_c^2}
+				}\cosh^2 2T\phi}
+			}
+	\end{equation}
+	We then compute the charges like before, and we have:
+	\begin{equation}
+		\var{Q}_\xi
+		= \frac{\var{T}}{2G} \pqty{
+				L \coth (LT) - \frac{1}{T}
+			}
+			\frac{1}{\sqrt{
+				1 + \frac{4T^2}{r_c^2 \sinh^2 LT}
+			}}
+	\end{equation}
+
+	We haven't found a nice way to compute this integral directly, but we note that the magical square root factor appears again in the $T\to 0$ limit:
+	\begin{equation}
+		T\to 0,
+	\quad
+		\sqrt{
+			1 + \frac{4T^2}{r_c^2 \sinh^2 LT}
+		}
+		\to \sqrt{
+			1 + \frac{4}{r_c^2 L^2}
+		}
+		\to \sqrt{
+			1 + \frac{4z_c^2}{L^2}
+		}
+	\end{equation}
+	This inspire us to take $L\pdd{L}$ first, and then compute the $\int \var{T}$; this is, surprisingly, doable, and reproduces the $C(L)$ function in \textcite{Lewkowycz:2019xse} in the $T \to 0$ limit:
+	\begin{equation}
+		L \pdv{L}\,Q_\xi
+		= \frac{1}{2G}
+			\frac{LT \coth LT}{\sqrt{
+				1 + \frac{4T^2}{r_c^2 \sinh^2 LT}
+			}}
+	\qquad\text{(up to const.)}
+	\end{equation}
+
+	Note that we have \textit{not} been very careful about the possible $L,T$ dependent integration constants.
+If we then do the $L$ integration from the above $L \pdv{L}\,Q_\xi$, we then find the charge up to some $L,T$ dependent integration constants:
+	\begin{equation}
+		Q_\xi
+		= \frac{1}{2G} \mop{arctanh}
+			\frac{1}{\sqrt{
+				1 + \frac{4T^2}{r_c^2 \sinh^2 LT}
+			}}
+		= \frac{1}{2G} \log
+			\frac{
+				\sqrt{
+					1 + \frac{4T^2}{r_c^2 \sinh^2 LT}
+				} + 1
+			}{
+				\sqrt{
+					1 + \frac{4T^2}{r_c^2 \sinh^2 LT}
+				} - 1
+			}
+	\qquad\text{(up to const.)}
+	\end{equation}
 

### 2021-04-01 alpha/CelestialHolography/celestial.tex
Add note on celestial holography

% !TeX document-id = {b5392a94-51a3-49d1-9ba5-698bc09f9d35}
% !TeX encoding = UTF-8
% !TeX spellcheck = en_US
% !TeX TXS-program:bibliography = biber -l zh__pinyin --output-safechars %

\documentclass[a4paper
	,10pt
%	,twoside
]{article}

\input{../preamble.tex}
\input{../.modules/basics/biblatex.tex}

\title{A First Look at Celestial Holography}
\addbibresource{celestial.bib}

%%% ID: sensitive, do NOT publish!
\InputIfFileExists{id.tex}{}{}

\makeatletter
\newcommand{\nobeginpar}{\@beginparpenalty=10000}
\makeatother

\begin{document}
\maketitle
\pagenumbering{arabic}
\thispagestyle{empty}

%\vspace*{-.5\baselineskip}

\setlength{\parskip}{.1\baselineskip}
\tableofcontents
\setlength{\parskip}{\parskipnorm}

\addtocounter{section}{-1}
\section{References}
	\begin{itemize}
	\item \textbf{Primary reference:} \fullcite{Strominger:2017zoo}. 
	\item \textbf{Secondary:} \fullcite{Ball:2019atb}.

	See also \fullcite{deBoer:2003vf}. 
	\item \textbf{Also:} \fullcite{Pate:2019mfs}
	\end{itemize}

	\noindent
	Talks by the authors:
	\begin{itemize}[noitemsep]
	\item Andy Strominger: \url{https://www.youtube.com/watch?v=By9hFSvl9MA}
	\item Monica Pate: \url{https://www.youtube.com/watch?v=4M4iZ8Hnc4Q}
	\item Andy Strominger, recent progress: \url{https://www.youtube.com/watch?v=wNLNIL81T_s}

	\vspace{.5\baselineskip}

	\item[**] Not very relevant, but there is an very recent, very interesting, very physical talk by Susskind at IAS on dS holography: \url{https://www.youtube.com/watch?v=4GKjr-y5MY0}
	\end{itemize}

\pagebreak

\section{Basics}
\subsection{\textsl{What} is the celestial sphere?}
	The celestial sphere, \textit{天球}, is a basic concept in astronomy. According to \href{https://en.wikipedia.org/wiki/Celestial_sphere}{\textsl{Wikipedia}}, the celestial sphere is an abstract sphere that has an arbitrarily large radius and is concentric to the observer. All objects in the sky can be conceived as being projected upon the inner surface of the celestial sphere.

	The idea of celestial sphere in celestial holography is almost precisely the same as that in usual astronomy. Suppose we, the observers, are at the origin of a \textbf{asymptotically flat} universe; the stars we see in the sky are null rays coming from somewhere closed to the past null infinity $\mscr{I}^-$, i.e.~what we see in the night sky is precisely the celestial sphere $CS^-$ closed to $\mscr{I}^-$. Similarly, there is another celestial sphere $CS^+$ located near $\mscr{I}^+$.

	\begin{figure}[!h]
	\centering
	\includegraphics[width=.85\linewidth]{img/bond.pdf}
	\caption[Penrose diamond of Minkowski spacetime]{
		\textbf{Penrose \textsl{diamond}} of Minkowski spacetime, from \cite{Strominger:2017zoo}. Compared to the standard Penrose diagram, we can see the celestial sphere more clearly in this kind of diamond diagrams. Roughly speaking, we have $\mscr{I}^\pm = \mbb{R}^\pm \times CS^\pm$, where $\mbb{R}^\pm$ stands for the $u,v$ coordinates.
	}
	\end{figure}

	\textsl{We will primarily work in \textbf{4D}, where the celestial spheres are \textbf{2-spheres}}, $CS^\pm \ni (z,\bar{z})$. 
	\begin{equation}
		\dd{s}^2
		= - \dd{u}^2 - 2\dd{u} \dd{r}
			+ r^2 \dd{\Omega}^2,
	\quad
		u = t - r,
	\end{equation}
	\vspace{-.8\baselineskip}
	\begin{equation}
		\dd{\Omega}^2
		= 2\gamma_{z\bar{z}} \dd{z} \dd{\bar{z}},
	\quad
		\gamma_{z\bar{z}}
		= \frac{2}{(1 + z\bar{z})^2}
	\label{eq:metric_null_plus}
	\end{equation}
	$u$: \textbf{retarded time}. 
	These coordinates work well near $\mscr{I}^+$ where $t,r\to\infty$ but $u = t - r$ stays finite. It's no good around $\mscr{I}^-$ where $u\to -\infty$; instead we need \textbf{advanced coordinates}:
	\begin{equation}
		\dd{s}^2
		= - \dd{v}^2
			\mathbin{\sidenote{+}} 2\dd{v} \dd{r}
			+ r^2 \dd{\Omega}^2,
	\quad
		v = t + r,
	\end{equation}
%	\meaning\sidenote

\pagebreak[4]
	Note that the $(z,\bar{z})$ in $CS^\pm$ are not na\"ively identical, but identified with the \textbf{antipodal map}:
	\begin{equation}
		z \mapsto -\frac{1}{\bar{z}},
	\quad
		\text{i.e.}\,\ %
		z_+ = - \frac{1}{\bar{z}_-},
	\ %
		z_- = - \frac{1}{\bar{z}_+},
	\end{equation}
	This is actually the more natural choice: a ``free'' light ray starting from $z_- = z$ ends at $z_+ = z$. This in fact binds $\mcal{I}^+$ with $\mcal{I}^-$. 
	This gives the natural antipodal matching condition for fields around $i^0$:
	\begin{equation}
		F(u,z,\bar{z})|_{\mscr{I}^+\to i^0}
		= F(v,z,\bar{z})|_{\mscr{I}^-\to i^0}
	\end{equation}
\subsection{\textsl{Why} do we want to study that?}
	\begin{enumerate}
	\item As an approach to \textbf{flat holography}. Another interesting observation: one can do some sort of a ``double holography'' by \textit{uplifting} $\mrm{AdS}_3/\mrm{CFT}_2$; this discussed in e.g.~\cite{deBoer:2003vf,Ball:2019atb}.

	\begin{figure}[!h]
	\centering
	\includegraphics[width=.5\linewidth]{img/hyperbolicslicing.pdf}
	\caption[Hyperbolic slicing of Minkowski]{
		Hyperbolic slicing of Minkowski, taken from \cite{Strominger:2017zoo}.

		One can implement the \textbf{Euclidean holography} $\mrm{EAdS}_3/\mrm{CFT}_2$ in the red patch, along \textbf{a specific time slice} of the causal future \cite{deBoer:2003vf,Ball:2019atb}. 
		On the other hand, in the blue Rindler patches we can apply Lorentzian $\mrm{dS}_3/\mrm{CFT}_2$.

		Note that in the $\mrm{dS}_3/\mrm{CFT}_2$ here, although the bulk $\mrm{dS}_3$ is Lorentzian, the dual $\mrm{CFT}_2$ is again a \textbf{Euclidean theory} living at $\mscr{I}^\pm$, very different from the usual global $\mrm{AdS}_3/\mrm{CFT}_2$, where the $\mrm{CFT}_2$ is a Lorentzian theory living at $i^0$. 
	}
	\end{figure}

\pagebreak[4]
	For more on of $\mrm{dS}/\mrm{CFT}$, see\footnote{
		We can read these papers in future journal clubs. Fun facts: just before \citefield{Strominger:2001pn}[eprint:arxivid]{eprint}, we have \arxiv{hep-th/0106112} which is the famous AdS two-sided black hole paper by Maldacena. 
	}:
	\begin{itemize}[noitemsep]
	\item The $\mrm{dS}/\mrm{CFT}$ paper by \textcite{Strominger:2001pn},
	\item Also \textcite{Witten:2001kn},
	\item And Maldacena's comments \textcite{Maldacena:2002vr}. 
	\end{itemize}
	This flavor of $\mrm{dS}/\mrm{CFT}$ is far more ambiguous than the usual $\mrm{AdS}/\mrm{CFT}$ and somewhat ``suspicious''; see Maldacena's comments in \cite{Maldacena:2002vr} and Susskind's recent talk at IAS.

%\pagebreak[4]

	\item As part of the universal \textbf{IR structure}.

	\begin{itemize}[noitemsep]
	\item IR: Integrate out massive modes $\to$ massless particles;

	\item Enhanced symmetries in the IR: asymptotic conformal-like symmetries (e.g.~BMS);

	\item IR physics largely ``regulated'' by symmetries.

	\end{itemize}

	There is a sense of \textbf{IR universality}: similar structures appear in all kinds of gauge theory, including gravity.

	\end{enumerate}

\section{Massless Scattering}

	IR divergences in QED: Every time we breathe, an infinite number of soft photons and gravitons are produced. Usual resolution in QFT: cutoff \& resummation of diagrams, but it's hard to understand why it works; the reason: symmetries!
	\begin{figure}[!ht]
	\centering
	\includegraphics[width=.7\linewidth]{img/Resum.png}
	\caption[Resummation cures IR divergences]{
		Resummation cures IR divergences; this is an illustration of the amplitude for Bhabha scattering, taken from \cite{Strominger:2017zoo}. 
	}
	\end{figure}

	Antipodal identification $\to \infty$ amount of conserved charge (in the IR limit). Consider any function $\epsilon$ on Minkowski space such that:
	\begin{equation}
		\epsilon(u,z,\bar{z})|_{\mscr{I}^+}
		= \epsilon(z,\bar{z})
		= \epsilon(v,z,\bar{z})|_{\mscr{I}^-}
	\end{equation}
	In particular, it obeys the boundary condition near $i^0$:
	\begin{equation}
		\epsilon(u,z,\bar{z})|_{\mscr{I}^+\to i^0}
		= \epsilon(z,\bar{z})
		= \epsilon(v,z,\bar{z})|_{\mscr{I}^-\to i^0}
	\end{equation}

	With such $\epsilon(z,\bar{z})$, charge conservation is almost tautological, as both $\epsilon$ and the field $F$ obey the antipodal identification; for example, in QED we have:
	\begin{equation}
	\begin{aligned}
		Q_\epsilon^+
		:=& \int_{\mscr{I}^+} \Bqty\Big{
				\epsilon(z,\bar{z})\,
					(\hodgedual j)
				+ \dd{\epsilon}
					\wedge \hodgedual F(u,z,\bar{z})
			}\\
		=& \int_{\mscr{I}^+}
			\dd{\Bqty\Big{
				\epsilon\,
				(\hodgedual F)
			}}
		= \int_{CS_{\mscr{I}^+\to i^0}}
			\hodgedual F(u,z,\bar{z})\,
			\epsilon(z,\bar{z})
		= \int_{CS_{\mscr{I}^-\to i^0}}
			\hodgedual F(v,z,\bar{z})\,
			\epsilon(z,\bar{z})
		= Q_\epsilon^-
	\end{aligned}
	\end{equation}
	Here we've used Gauss law (Stokes' theorem), and we've assumed no massive flux passes through the $i^\pm$ endpoints. With $\epsilon = \mrm{const.}$ we recover charge conservation; with general $\epsilon(z,\bar{z})$ we can construct $\infty$ many conserved charges.

	\begin{figure}[!h]
	\centering
	\includegraphics[width=.5\linewidth]{img/minkowskipenrose.pdf}
	\caption[Worldlines of massive and massless particles]{
		Worldlines of massive and massless particles traveling through the Penrose diamond, taken from \cite{Strominger:2017zoo}.
	}
	\end{figure}

	Incoming / outgoing asymptotic states are organized by asymptotic symmetries. If we restrict to massless scattering, $\mscr{I}^\pm$ are nice ``Cauchy surfaces''. 
	After understanding massless scattering, we can then extend the results carefully to include massive particles, which travels from $i^-$ to $i^+$. The $\mrm{EAdS}$ slicing mentioned above is a nice way to ``regularize'' the singular behavior around $i^\pm$. They correspond to operators that are \textit{smeared} on $CS$.

\subsection{Soft theorem \& memory effect}
	Ward identity:
	\begin{equation}
		0
		= \mel{\textsl{out}}{
				\bqty\big{Q_\epsilon, \mcal{S}}
			}{\textsl{in}}
	\end{equation}
	When expanded, gives constraints to the $\mcal{S}$ matrix elements; this gives precisely the \textit{soft theorem}. In fact the $
%		\displaystyle
		\int_{\mscr{I}^+} \Bqty\big{
			\dd{\epsilon}
			\wedge \hodgedual F(u,z,\bar{z})
		}
	$ term creates \textbf{zero energy soft photons} with polarization $\pdd{\alpha} \epsilon$, namely it shifts the \textbf{$\infty$-ly degenerate vacuum}.

	The same mechanism leads to the \textbf{memory effect}; one can think of them as same equations for scattering but one in momentum space and the other one in position space.

	\begin{figure}[!h]
	\centering
	\includegraphics[width=.45\linewidth]{img/memdet.pdf}
	\caption[Gravitational memory effect]{
		Gravitational memory effect, taken from \cite{Strominger:2017zoo}. Amazingly memory effect are very realistic physics and there has been many proposals to measure this in real experiments, both for gravitational memory and other memory effects.
	}
	\end{figure}
\subsection{Asymptotic symmetries}

	Boundary conditions: suitable choice of asymptotic falloffs and gauge conditions; 
	\begin{equation}
		\mrm{ASG}
		= \frac{
			\textsl{allowed gauge symmetries: repect boundary conditions}
		}{
			\textsl{trivial gauge symmetries: act trivially on boundary data (charges)}
		}
	\end{equation}
	e.g.~$\mop{ASG}\,(\textsl{asymptotically flat}_4) = \mrm{BMS}_4 \supset \mrm{Poincar\'e}$, i.e.~it is $\infty$-ly \textbf{larger} than the isometry of Minkowski! According to \cite{Strominger:2017zoo}, this is not the full story yet; BMS is ``both too big and too small''. In fact, analyses of ASG are ``more of an art than a science'', in part because of ambiguities in the choice of boundary conditions, which are often only a posteriori justified \cite{Strominger:2017zoo}.

	More specifically, we fix Bondi gauge, which is just \eqref{eq:metric_null_plus} plus small fluctuations, and then solve the Killing equation:
	\begin{equation}
		\ldv{\zeta} g = 0
	\end{equation}
	Naturally $\zeta \in \mfrak{SO}(3,1)$ is part of the solutions, i.e~the 6 Lorentz generators; these are large $\order{r}$ Killing vectors around $\mscr{I}^\pm$. 
	We then consider small transformations around $\mscr{I}^+$, by imposing that the vector field is $\order{1}$ at large $r$ in an orthonormal frame. 
	\begin{equation}
		\zeta^u,\zeta^r
		\sim \order{1},
	\quad
		\zeta^z,\zeta^{\bar{z}}
		\sim \order{\frac{1}{r}}
	\end{equation}

	The solution of the Killing equation is then given by an $\infty$-ly generated \textbf{supertranslations} parametrized by $\epsilon = \epsilon(z,\bar{z})$,
	\begin{equation}
		\zeta
		= \epsilon\,\pdd{u}
		- \frac{1}{r} \pqty{
			(\nabla^z \epsilon)\,\pdd{z}
			+ (\nabla^{\bar{z}} \epsilon)\,\pdd{\bar{z}}
		} + (\nabla^2 \epsilon)\,\pdd{r},
	\quad
		\epsilon = \epsilon(z,\bar{z})
	\end{equation}
	$\mrm{BMS}^+ = \mrm{Supertranslations}^+ * \mrm{Lorentz}$. Similar for $\mrm{BMS}^-$.

	\begin{figure}[!h]
	\centering
	\includegraphics[width=.45\linewidth]{img/supertranslation.pdf}
	\caption[Supertranslations on $\mscr{I}^+$]{
		Supertranslations on $\mscr{I}^+$, taken from \cite{Strominger:2017zoo}.
	}
	\end{figure}

\subsection{Scattering on the celestial sphere}

	Usually we use 4-\textbf{energy momentum} $P_\mu$ to label asymptotic states, but for massless particles it's more natural to use \textbf{boosts}: note that a boost along $\vec{p}$ of a null $p^\mu = (\abs{\vec{p}},\vec{p})$ only rescales its magnitude: $p^\mu\mapsto \lambda p^\mu$. This corresponds to \textbf{dilations} on the celestial CFT. 
	\begin{equation}
		T\sim \pdd{x},
	\quad
		\tilde{f}(p)
		\sim \int \dd{x} e^{-ipx} f(x)
	\end{equation}
	\vspace{-.5\baselineskip}
	\begin{equation}
		B\sim \omega\,\pdd{\omega},
	\quad
		\tilde{f}(\Delta)
		\sim \int \frac{\dd{\omega}}{\omega}\,
				\omega^\Delta f(\omega),
	\quad
		p^\mu = \epsilon\,\omega\, q^\mu(z,\bar{z})
	\end{equation}
	$q^\mu = \pqty{
		1 + z\bar{z},
		z + \bar{z},
		-i(z - \bar{z}),
		1 - z\bar{z}
	}$ is a standard 4-momentum constructed only with the celestial direction $(z,\bar{z})$. $\omega$ is the energy (frequency), and $\epsilon = \pm 1$ (for outgoing and ingoing particles respectively. 
	This is a so-called Mellin transform, with boost weight: $\Delta$. When combined with spin, we can similarly define $(h,\bar{h})$ for the 2D celestial sphere, $\Delta = h + \bar{h}$; \textit{Conformally soft}: $h\to 0$ or $\bar{h}\to 0$. Soft theorem $\to$ conformal soft theorem; see \cite{Pate:2019mfs}.

\vspace{1.2\baselineskip}
\raggedright
\printbibliography[%
%	title = {参考文献} %
	,heading = bibintoc
]
\end{document}

### 2021-04-04 alpha/CelestialHolography/celestial.tex
Finish note on celestial holography
... also update TeXplates with nicer colors

@@
 
-	\item[**] Not very relevant, but there is an very recent, very interesting, very physical talk by Susskind at IAS on dS holography: \url{https://www.youtube.com/watch?v=4GKjr-y5MY0}
+	\item[**] Not very relevant, but there is a very recent, very interesting, very physical talk by Susskind at IAS on de Sitter holography: \url{https://www.youtube.com/watch?v=4GKjr-y5MY0}
 	\end{itemize}
@@
 \pagebreak[4]
-	Note that the $(z,\bar{z})$ in $CS^\pm$ are not na\"ively identical, but identified with the \textbf{antipodal map}:
+	Note that the $(z,\bar{z})$ in $CS^\pm$ are actually \textbf{not the same coordinates}, but are related to each other by the \textbf{antipodal map}:
 	\begin{equation}
@@
 	This is actually the more natural choice: a ``free'' light ray starting from $z_- = z$ ends at $z_+ = z$. This in fact binds $\mcal{I}^+$ with $\mcal{I}^-$.
-	This gives the natural antipodal matching condition for fields around $i^0$:
+
+	Now consider a scattering process happening ``around $i^0$'', from $\mscr{I}^-$ to $\mscr{I}^+$; this is ``far away'' from the ``center'' where all the interactions take place, so the scattering process is almost trivial.
+	This gives the natural \textbf{antipodal matching condition} for fields around $i^0$:
 	\begin{equation}
 		F(u,z,\bar{z})|_{\mscr{I}^+\to i^0}
+		= F(u\to -\infty,z,\bar{z})
+		\equiv F(z,\bar{z})
+		= F(v\to +\infty,z,\bar{z})
 		= F(v,z,\bar{z})|_{\mscr{I}^-\to i^0}
 	\end{equation}
+	Note that this antipodal matching condition will prove crucial to our discussions later on. 
 \subsection{\textsl{Why} do we want to study that?}
@@
 
-		Note that in the $\mrm{dS}_3/\mrm{CFT}_2$ here, although the bulk $\mrm{dS}_3$ is Lorentzian, the dual $\mrm{CFT}_2$ is again a \textbf{Euclidean theory} living at $\mscr{I}^\pm$, very different from the usual global $\mrm{AdS}_3/\mrm{CFT}_2$, where the $\mrm{CFT}_2$ is a Lorentzian theory living at $i^0$.
+		Note that in the $\mrm{dS}_3/\mrm{CFT}_2$ here, although the bulk $\mrm{dS}_3$ is Lorentzian, the dual $\mrm{CFT}_2$ is again a \textbf{Euclidean theory} living at $\mscr{I}^\pm$, which is very different from the usual global $\mrm{AdS}_3/\mrm{CFT}_2$, where the $\mrm{CFT}_2$ is a Lorentzian theory living at $i^0$.
 	}
@@
 
+	\begin{figure}[!h]
+	\centering
+	\includegraphics[width=.7\linewidth]{img/IRtriangle.pdf}
+	\caption[The universal IR triangle]{
+		The universal IR triangle, modeled after the one in \cite{Strominger:2017zoo}. 
+	}
+	\end{figure}
+
 	\end{enumerate}
@@
 	\caption[Resummation cures IR divergences]{
-		Resummation cures IR divergences; this is an illustration of the amplitude for Bhabha scattering, taken from \cite{Strominger:2017zoo}. 
+		Resummation cures IR divergences in the usual diagrammatic analysis of QFT; this is an illustration of the amplitude for Bhabha scattering, taken from \cite{Strominger:2017zoo}.
+
+		Such infinite sum of infinites doesn't make sense mathematically, but this procedure can be made more rigorous with the help with \textit{renormalization}, as we add counterterms to suppress each divergence.
 	}
@@
 	\begin{equation}
-		\epsilon(u,z,\bar{z})|_{\mscr{I}^+}
-		= \epsilon(z,\bar{z})
+		\epsilon
+		= \epsilon(u,z,\bar{z})|_{\mscr{I}^+}
 		= \epsilon(v,z,\bar{z})|_{\mscr{I}^-}
@@
 	\begin{equation}
-	\begin{aligned}
-		Q_\epsilon^+
-		:=& \int_{\mscr{I}^+} \Bqty\Big{
-				\epsilon(z,\bar{z})\,
+	\begin{alignedat}{2}
+		Q_\epsilon^-
+		:=& \mathrlap{
+			\int_{\mscr{I}^-} \Big\{
+				\epsilon(v,z,\bar{z})\,
 					(\hodgedual j)
 				+ \dd{\epsilon}
-					\wedge \hodgedual F(u,z,\bar{z})
-			}\\
-		=& \int_{\mscr{I}^+}
+					\wedge \hodgedual F(v,z,\bar{z})
+			\Big\}
+		} \\
+		=& \int_{\mscr{I}^-}
 			\dd{\Bqty\Big{
@@
 			}}
-		= \int_{CS_{\mscr{I}^+\to i^0}}
-			\hodgedual F(u,z,\bar{z})\,
-			\epsilon(z,\bar{z})
-		= \int_{CS_{\mscr{I}^-\to i^0}}
-			\hodgedual F(v,z,\bar{z})\,
-			\epsilon(z,\bar{z})
-		= Q_\epsilon^-
-	\end{aligned}
+		&{}=& \int_{CS_{\mscr{I}^-\to i^0}}
+			(\hodgedual F)(v,z,\bar{z})\,
+			\epsilon(v,z,\bar{z})\big|_{
+				v\to +\infty
+			} \\
+		&&=& \int_{CS_{\mscr{I}^-\to i^0}}
+			(\hodgedual F)(z,\bar{z})\,
+			\epsilon(z,\bar{z}) \\
+		&&=& \int_{CS_{\mscr{I}^+\to i^0}}
+			(\hodgedual F)(u,z,\bar{z})\,
+			\epsilon(u,z,\bar{z})\big|_{
+				u\to -\infty
+			}
+		= Q_\epsilon^+
+	\end{alignedat}
 	\end{equation}
-	Here we've used Gauss law (Stokes' theorem), and we've assumed no massive flux passes through the $i^\pm$ endpoints.
+	Here we've used Gauss law (Stokes' theorem), and we've assumed no flux due to massive particles passes through the $i^\pm$ endpoints.
 With $\epsilon = \mrm{const.}$ we recover charge conservation; with general $\epsilon(z,\bar{z})$ we can construct $\infty$ many conserved charges.
+
+	In the above derivation we've taken a general $\epsilon(u,z,\bar{z})$ and $\epsilon(v,z,\bar{z})$ defined near $\mscr{I}^\pm$, but note that as the charge reduced to a codim-2 integral on the $CS$ closed to $i^0$, only the angular dependence $\epsilon = \epsilon(z,\bar{z})$ survived; this function actually corresponds to the \textbf{asymptotic symmetries} of QED.
+
+	Our derivation here is similar to some popular treatment of conformal symmetries (see e.g.\ \textit{Polchinski} \cite{Polchinski:1998rq}, section 2.4): we first formally construct a conserved current, in this case:
+	\begin{equation}
+		\hodgedual J
+		= \epsilon(v,z,\bar{z})\,
+				(\hodgedual j)
+			+ \dd{\epsilon}
+				\wedge \hodgedual F(v,z,\bar{z})
+		= \dd{(\hodgedual k)},
+	\quad
+		(\hodgedual k) = \epsilon\,(\hodgedual F)
+	\end{equation}
+	This conserved current actually gets reduced to the conserved 2-form $\hodgedual k$, and the charge is integrated at a codim-2 surface.
+This is a common feature of gauge fields.
+And then, we try to find the corresponding asymptotic symmetries; this is like running the Noether's procedure backwards.
+After promoting $Q_\epsilon$ to an operator, we see that the asymptotic gauge symmetries are indeed generated by $\epsilon(z,\bar{z})$, and the $u,v$-dependence drops out:
+	\begin{equation}
+		r\to\infty,
+	\quad
+		i\var_\epsilon A_\mu
+		\equiv \bqty{
+			Q_\epsilon, A_\mu
+		}
+		= i \pdd{\mu} \epsilon,
+	\quad \epsilon = \epsilon(z,\bar{z})
+	\end{equation}
 
@@
 	\caption[Worldlines of massive and massless particles]{
-		Worldlines of massive and massless particles traveling through the Penrose diamond, taken from \cite{Strominger:2017zoo}.
+		Worldlines of massive and massless particles traveling through the Penrose diamond, taken from \cite{Strominger:2017zoo}. Note that the worldlines of massive always pass through $i^\pm$. 
 	}
@@
 
-	Incoming / outgoing asymptotic states are organized by asymptotic symmetries. If we restrict to massless scattering, $\mscr{I}^\pm$ are nice ``Cauchy surfaces''. 
+	Incoming / outgoing asymptotic states are then organized by asymptotic symmetries. If we restrict to massless scattering, $\mscr{I}^\pm$ are nice ``Cauchy surfaces''. 
+	The asymptotic states can then be reduced to operator insertions on a celestial sphere $CS$.
+
 	After understanding massless scattering, we can then extend the results carefully to include massive particles, which travels from $i^-$ to $i^+$.
@@
 
+%\pagebreak[4]
 \subsection{Soft theorem \& memory effect}
@@
 		}
-	$ term creates \textbf{zero energy soft photons} with polarization $\pdd{\alpha} \epsilon$, namely it shifts the \textbf{$\infty$-ly degenerate vacuum}.
+	$ term creates \textbf{zero energy ``soft'' photons} with transverse polarization $\pdd{\alpha} \epsilon$, $\alpha = z,\bar{z}$, namely it shifts the \textbf{$\infty$-ly degenerate vacuum}.
 
@@
 		Gravitational memory effect, taken from \cite{Strominger:2017zoo}.
-Amazingly memory effect are very realistic physics and there has been many proposals to measure this in real experiments, both for gravitational memory and other memory effects.
+Amazingly memory effects are very realistic physics and there has been many proposals to measure this in real experiments, both for gravitational memory and other memory effects.
 	}
 	\end{figure}
-\subsection{Asymptotic symmetries}
+\subsection{More on asymptotic symmetries}
 
@@
 	\end{equation}
-	e.g.~$\mop{ASG}\,(\textsl{asymptotically flat}_4) = \mrm{BMS}_4 \supset \mrm{Poincar\'e}$, i.e.~it is $\infty$-ly \textbf{larger} than the isometry of Minkowski!
-According to \cite{Strominger:2017zoo}, this is not the full story yet; BMS is ``both too big and too small''.
-In fact, analyses of ASG are ``more of an art than a science'', in part because of ambiguities in the choice of boundary conditions, which are often only a posteriori justified \cite{Strominger:2017zoo}.
+	e.g.~In asymptotically flat 4D gravity, if we restrict to Lorentz plus ``small translations'', we obtain $\mrm{BMS}_4 = \mrm{BMS}^+ \times \mrm{BMS}^- \supset \mrm{Poincar\'e}$, i.e.~it is \textbf{$\infty$-ly larger} than the isometry of Minkowski!
 
-	More specifically, we fix Bondi gauge, which is just \eqref{eq:metric_null_plus} plus small fluctuations, and then solve the Killing equation:
+	However, this is not the full story yet; the conventional BMS is ``both too big and too small'' \cite{Strominger:2017zoo}: ``too big'' because $\mrm{BMS}^+$ and $\mrm{BMS}^-$ should in fact be bound together by the antipodal map; what remains is only the diagonal subgroup; ``too small'' because we can generalize Lorentz transformations to \textit{superrotations}, just like we generalize translations in Poincar\'e to \textit{supertranslations} in BMS.
+
+	Note that according to \cite{Strominger:2017zoo}, analyses of ASG are ``more of an art than a science'', in part because of ambiguities in the choice of boundary conditions, which are often only a posteriori justified.
+
+	Let's first see in detail how we find $\mrm{BMS}^+$. We fix Bondi gauge, which is just \eqref{eq:metric_null_plus} plus small fluctuations with desired falloffs, and then solve the Killing equation:
 	\begin{equation}
@@
 	\end{equation}
-	Naturally $\zeta \in \mfrak{SO}(3,1)$ is part of the solutions, i.e~the 6 Lorentz generators; these are large $\order{r}$ Killing vectors around $\mscr{I}^\pm$. 
-	We then consider small transformations around $\mscr{I}^+$, by imposing that the vector field is $\order{1}$ at large $r$ in an orthonormal frame. 
+	Naturally $\zeta \in \mfrak{so}(3,1)$ is part of the solutions, i.e~the 6 Lorentz generators; these are large $\order{r}$ Killing vectors around $\mscr{I}^\pm$. 
+	We then consider \textbf{small transformations} around $\mscr{I}^+$, by imposing that the vector field is $\order{1}$ at large $r$ in an orthonormal frame. 
 	\begin{equation}
@@
 	\end{equation}
-	$\mrm{BMS}^+ = \mrm{Supertranslations}^+ * \mrm{Lorentz}$. Similar for $\mrm{BMS}^-$.
+	We have $\mrm{BMS}^+ = \mrm{Supertranslations}^+ * \mrm{Lorentz}$.
+Similar result holds for $\mrm{BMS}^-$.
+If we relax the ``small'' restrictions for $\zeta$, we find that the Lorentz part gets enhanced to \textbf{superrotations}:
+	\begin{equation}
+		\zeta
+		= Y^z \pdd{z}
+			+ \frac{u}{2}\,(\nabla_z Y^z)\,\pdd{u}
+			+ (\textsl{complex conjugates}),
+	\quad
+		Y^z = Y^z(z),\ %
+		Y^{\bar{z}} = Y^{\bar{z}}(\bar{z})
+	\end{equation}
 
-	\begin{figure}[!h]
+	\begin{figure}[!t]
 	\centering
@@
 
+%\pagebreak[4]
 \subsection{Scattering on the celestial sphere}
 
-	Usually we use 4-\textbf{energy momentum} $P_\mu$ to label asymptotic states, but for massless particles it's more natural to use \textbf{boosts}: note that a boost along $\vec{p}$ of a null $p^\mu = (\abs{\vec{p}},\vec{p})$ only rescales its magnitude: $p^\mu\mapsto \lambda p^\mu$.
+	\begin{figure}[!ht]
+	\centering
+	\includegraphics[width=.7\linewidth]{img/celestialsphere.pdf}
+	\caption[Scattering on the celestial sphere]{
+		Scattering reduced onto the celestial sphere, taken from \cite{Strominger:2017zoo}.
+	}
+	\end{figure}
+
+\pagebreak[3]
+
+	Usually we use 4-\textbf{energy momentum} $P_\mu$ to label asymptotic states, but for massless particles it's more natural to use \textbf{boosts} \cite{Pasterski:2017kqt,Pate:2019mfs}: note that a boost along $\vec{p}$ of a null $p^\mu = (\abs{\vec{p}},\vec{p})$ only rescales its magnitude: $p^\mu\mapsto \lambda p^\mu$.
 This corresponds to \textbf{dilations} on the celestial CFT.
@@
 	}$ is a standard 4-momentum constructed only with the celestial direction $(z,\bar{z})$. $\omega$ is the energy (frequency), and $\epsilon = \pm 1$ (for outgoing and ingoing particles respectively. 
-	This is a so-called Mellin transform, with boost weight: $\Delta$.
+	This is a so-called \textbf{Mellin transform}, with boost weight: $\Delta$.
+
 	When combined with spin, we can similarly define $(h,\bar{h})$ for the 2D celestial sphere, $\Delta = h + \bar{h}$; \textit{Conformally soft}: $h\to 0$ or $\bar{h}\to 0$.
 Soft theorem $\to$ conformal soft theorem; see \cite{Pate:2019mfs}.
+
+\appendix
+\section{Symmetries of asymptotically flat spacetime}
+	\begin{center}
+	\includegraphics[width=.8\linewidth]{img/ASGflat.pdf}
+	\end{center}
 

### 2021-04-04 HW-AlgebraicTopology2020/algtop1/algtop1.tex
Restructure to gather quick notes
Add various format tweaks

--- 2020-03-10 AlgebraicTopology2020/algtop1/algtop1.tex
@@
 	\end{subequations}
+	\\[-\baselineskip]
 	This means that $f_0\colon X\to\{x_0\}$ isomorphic in $\Cat{hTop} = \Cat{Top}/\simeq$, which is precisely the definition of homotopic equivalence $X\simeq\{x_0\}$. ($\Rightarrow$)
@@
 		This proof is produced with the help of \https{math.stackexchange.com/q/727999}.
+Another (easier) proof lies in the fact that group translation induces $\pi_1$ conjugation, therefore $\gamma^{-1} \alpha \gamma = \alpha$, hence abelian.
 	}:

### 2021-04-04 alpha/CelestialHolography/celestial.tex
Add various format tweaks
Add comments on Bondi mass; add some bib

@@
 	\centering
-	\includegraphics[width=.5\linewidth]{img/hyperbolicslicing.pdf}
+	\includegraphics[width=.45\linewidth]{img/hyperbolicslicing.pdf}
 	\caption[Hyperbolic slicing of Minkowski]{
@@
 
+	The calculation of conserved charges in gravity is similar to that in gauge theory, but now we already have the symmetry in terms of diffeomorphic generators, thus we need only run the usual Noether's procedure (``forwards'' instead of ``backwards'', compared with what we did in gauge theory), to get the conserved charges.
+
+	Again we integrate the conserved current on the codim-1 $\mcal{I}^\pm$, and it gets reduced to an integral of the codim-2 $CS$ near $i^0$.
+$\epsilon = 0$ corresponds to $\zeta \propto \pdd{u}$, and the conserved charge is the \textbf{total Bondi mass}; for Kerr spacetimes in the usual conventions, the conserved charge is exactly the mass parameter $M$.
+
 	\begin{figure}[!t]
@@
 \section{Symmetries of asymptotically flat spacetime}
+	\vspace{-.5\baselineskip}
 	\begin{center}
-	\includegraphics[width=.8\linewidth]{img/ASGflat.pdf}
+	\includegraphics[width=.635\linewidth]{img/ASGflat.pdf}
 	\end{center}

### 2021-04-08 alpha/GravitationalEntropy/entropy.tex
Update note on EETTbar

@@
 
+\makeatletter
+\newcommand{\nobeginpar}{\@beginparpenalty=10000}
+\makeatother
+
 \begin{document}
@@
 	\begin{itemize}
-	\item Lightcone coordinates: $u,v = x\pm t$, following \cite{Apolo:2019zai} (except that in \cite{Apolo:2019zai} the $x$ direction is compactified into the $\varphi$ circle).
-Constant $t$ slice is therefore given by $u = v$.
+	\item Lightcone coordinates: $u,v = x\pm t$, similar to \cite{Apolo:2019zai}. This convention has the following features:
+
+		\begin{itemize}
+		\item The constant $t$ slice is given by $u = v$;
+		\item It preserves the orientation as we go from $(t,x)$ to $(u,v)$. Note that the ordering of coordinates matters here.
+		\end{itemize}
 
@@
 	\end{itemize}
+
+\pagebreak[4]
 \section{Entanglement Entropy as Thermal Entropy}
@@
 The causal domain of dependence $\mcal{D}\to$ some thermal state with normalized inverse temperature $2\pi$.
-Here we choose to absorb such $2\pi$ into the definition of $\xi$, so the Euclidean periodicity w.r.t.~$\xi$ is simply $\beta = 1 = \frac{1}{T}$, which means the surface gravity along the horizon is given by $\kappa = 2\pi T = 2\pi$.
+Here we choose to absorb such $2\pi$ into the definition of $\xi$, so the Euclidean periodicity w.r.t.~$\xi$ is simply $\beta_\xi = 1 = \frac{1}{T_\xi}$, which means the surface gravity along the horizon is given by $\kappa_\xi = 2\pi T_\xi = 2\pi$.
 \subsection{Exercise: Poincar\'e $\mrm{AdS}_3/\mrm{CFT}_2$}
@@
 	\end{equation}
-	See \href{https://bryango.github.io/resources/archive/HW-Gravity/gravity1.pdf}{\underline{this homework}} for a detailed derivation. 
+	See \href{https://bryango.github.io/resources/archive/HW-Gravity/gravity1.pdf}{\textsl{this homework}}\footnote{
+		URL: \https{bryango.github.io/resources/archive/HW-Gravity/gravity1.pdf}. 
+	} for a detailed derivation. 
 	Alternatively, it can be more compactly rewritten with $x^\mu \sim (t,x)$ or $(u,v)$; mind the various $\pm$ signs in the above expressions: 
@@
 	\begin{equation}
-		T = \frac{\kappa}{2\pi} = 1,
+		T_\xi = \frac{\kappa_\xi}{2\pi} = 1,
 	\quad
-		\kappa^2
+		\kappa_\xi^2
 		= (2\pi)^2
@@
 	\end{equation}
+
+	We then consider $\xi$ evaluated at the {constant finite cutoff} $z = z_c$,
 	\begin{equation}
 	\begin{aligned}
-%		\xi_c \equiv
-		\xi|_{z=z_c, \pdd{z}\to 0}
-		= \frac{2\pi}{\sqrt{
-				L^2 + (2z_c)^2
-			}}
+		\xi|_{z=z_c}
+		= \frac{2\pi}{
+				L\sqrt{1 + (2z_c/L)^2}
+			}
 		& \bigg\{
@@
 	\end{equation}
+	Note that the $\pdd{z}$ component is generally non-zero, i.e.~$\xi|_{z=z_c}$ is not entirely contained in the $z = z_c$ plane. 
+	We observe the factor $
+		\sqrt{1 + (2z_c/L)^2}
+	$ which is featured prominently in the $T\bar{T}$ deformed $C(L)$ function, given in \cite{Lewkowycz:2019xse}:
+	\begin{equation}
+		C(L) = L\,\pdd{L} S(L)
+		= \frac{c}{3} 
+			\frac{1}{
+				\sqrt{1 + (2z_c/L)^2}
+			}
+	\end{equation}
 
-\pagebreak[3]
 	This seems nice and all but there is a subtlety for finite cutoff $z = z_c$. 
@@
 		\xi^\nu \cdv{\nu} \xi^\mu
-		= \kappa \xi^\mu
+		= \kappa_\xi \xi^\mu
 		= 2\pi \xi^\mu
 	$ guarantees that after Wick rotation, the Euclidean periodicity around the horizon is normalized to $\beta = 1$.
-However, if we restrict to the field theory living at $z = z_c$, which corresponds to a $T\bar{T}$ deformed theory, since it has no knowledge of the $\pdd{z}$ component of $\xi$, we should project the $z$ component out, which leaves us:
+However, if we restrict to the field theory living at $z = z_c$, which corresponds to a $T\bar{T}$ deformed theory, since it has no knowledge of the $\pdd{z}$ component of $\xi$, we should reduce it to a modular flow within the $z = z_c$ plane by, e.g.~projecting the $z$ component out, which leaves us:
 	\begin{equation}
@@
 		\xi^{\mrm{FT}}_c
-		\equiv \proj{z_c} \xi|_{z_c}
-		= \frac{2\pi}{\sqrt{
-				L^2 + (2z_c)^2
-			}}
+		\equiv \proj{\sslash} \xi|_{z_c}
+		= \frac{2\pi}{
+				\sqrt{1 + (2z_c/L)^2}
+			}
 		& \bigg\{
@@
 	\end{equation}
-	Which no longer has normalized $\beta$ if $z_c \ne 0$.
-In fact, compared to the $z_c \to 0$ situation which \textit{does} have $\beta = 1$, $\xi^{\mrm{FT}}_c$ is rescaled by a factor of $\frac{L}{L_\infty}$, which means that:
+	Which no longer has normalized $\beta$ if $z_c \ne 0$. In fact, compared to the $z_c \to 0$ situation which \textit{does} have $\beta = 1$, $\xi^{\mrm{FT}}_c$ is rescaled by a factor of $
+		\frac{L}{L_\infty}
+		= 1/\sqrt{1 + (2z_c/L)^2}
+	$, which means that:
 	\begin{equation}
@@
 
+{\nobeginpar
 	How should we understand this?
@@
 	\end{itemize}
+}
 
 	\begin{figure}[!ht]
+	\vspace{-1.5ex}
 	\centering
@@
 	\centering
-	\includegraphics[width=.35\linewidth]{img/modFlowCutoff.pdf}
+%	\includegraphics[width=.35\linewidth]{img/modFlowCutoff.pdf}
+	\includegraphics[width=.35\linewidth]{img/modFlowAnalytic.pdf}
 %	\hspace{2em}
 %	\vspace{-2ex}
-	\caption{Integral surface of the modular flow starting from $t = 0,\ z = z_c$. Here we've chosen $\frac{L}{2} = 1$ while $z_c = 0.35$.}
+	\caption{Integral surface of the modular flow starting from $t = 0,\ z = z_c$. Here we've chosen $\frac{L_\infty}{2} = 1$ while $z_c = 0.4$.}
+	\end{figure}
+
+\subsubsection{Flow from constant cutoff}
+	For an interval lying on a constant time slice $t_\pm = 0$, i.e.~$\theta = 0$, we can actually solve the flow of $\xi$ by hand without much difficulty.
+
+	Consider the flow starting from $(t,x,z) = (0,x_c,z_c)$, we note that $
+		\dd{x}/\dd{z}
+		= {\dv{x}{\lambda}}/{\dv{z}{\lambda}}
+		= {x}/{z}
+	$, which implies that ${x}/{x_c} = {z}/{z_c}$ along the flow lines.
+Intuitively, the flow when restricted in $x$-$z$ plane points towards / away froms $x = z = 0$, which is the upper / lower tip of the entanglement wedge.
+
+	We can further replace the flow parameter $\lambda$ with time coordinate $t$ by considering $
+		\dd{z}/\dd{t}
+		= {\dv{z}{\lambda}}/{\dv{t}{\lambda}}
+	$, which leads to the following equations:
+	\begin{equation}
+		\dv{z}{t}
+		= \frac{2tz}{\alpha z^2 + t^2 - (L_\infty/2)^2},
+	\quad
+		\alpha = 1 + \frac{x_c^2}{z_c^2},
+	\quad
+		\frac{x}{x_c} = \frac{z}{z_c}
+	\end{equation}
+	The solution is then given by:
+	\begin{equation}
+		z = z(t;x_c,z_c)
+		= \frac{
+				(L_\infty/2)^2 + \alpha z_c^2
+				- \sqrt{
+					\pqty\big{(L_\infty/2)^2 - \alpha z_c^2}^2
+					+ 4t^2 \alpha z_c^2
+				}
+			}{2\alpha z_c}
+	\end{equation}
+
+%\subsubsection{Map to the Rindler coordinates}
+	To gain more understanding of the modular flow of the cutoff theory, we can look at the map to the Rindler coordinates.
+In the Poincar\'e $\mrm{AdS}_3$ case this is explicitly given in Appendix B by \textcite{Song:2016gtd}; the Poincar\'e $(t,x,z)$ is mapped to BTZ $(u,v,\rho)$:
+	\begin{equation}
+	\begin{aligned}
+		t &= \frac{L_\infty}{2} \frac{
+				\pqty{\rho - T_u T_v}
+				\,\sinh\,(T_u u - T_v v)
+			}{
+				\sqrt{\rho^2 - T_u^2 T_v^2}
+					\,\cosh\,(T_u u + T_v v)
+				+ \pqty{\rho - T_u T_v}
+					\,\cosh\,(T_u u - T_v v)
+			},
+	\\
+		x &= \frac{L_\infty}{2} \frac{
+				\sqrt{\rho^2 - T_u^2 T_v^2}
+				\,\sinh\,(T_u u + T_v v)
+			}{
+				\sqrt{\rho^2 - T_u^2 T_v^2}
+					\,\cosh\,(T_u u + T_v v)
+				+ \pqty{\rho - T_u T_v}
+					\,\cosh\,(T_u u - T_v v)
+			},
+	\\
+		z &= \frac{L_\infty}{2} \frac{
+				\sqrt{2T_u T_v}
+				\sqrt{\rho - T_u T_v}
+			}{
+				\sqrt{\rho^2 - T_u^2 T_v^2}
+					\,\cosh\,(T_u u + T_v v)
+				+ \pqty{\rho - T_u T_v}
+					\,\cosh\,(T_u u - T_v v)
+			},
+	\end{aligned}
+	\label{eq:poincare2btz}
+	\end{equation}
+	\begin{equation}
+		\dd{s}^2
+		= \frac{\dd{\rho}^2}{4\,(\rho^2 - T_u^2 T_v^2)}
+			+ T_u^2 \dd{u}^2
+			+ T_v^2 \dd{v}^2
+			+ 2\rho \dd{u} \dd{v},
+	\end{equation}
+	Here we've reused the variable names $(u,v)$ for the BTZ coordinates, and we've tweaked the expressions in \cite{Song:2016gtd} to be more symmetric in $(u,v)$.
+
+	TO CHECK: At the boundary this reduces to the result of \textcite{Casini:2011kv}, which is used by \textcite{Lewkowycz:2019xse}.
+
+	We note that $T_{u,v}$ is \textit{not exactly} the physical (Hawking) temperature of the spacetime; the physical temperature, on the other hand, is given by (see e.g.~\cite{Compere:2018aar}):
+	\begin{equation}
+		T_\tau = \frac{\kappa_\tau}{2\pi}
+		= \frac{1}{\pi}\,
+			\frac{2}{T_u^{-1} + T_v^{-1}},
+	\quad
+		\tau = \frac{u - v}{2}
+	\end{equation}
+	For $T_u = T_v = T$, we have $T_\tau = \frac{T}{\pi}$, i.e.~the Hawking temperature differs from $T_u = T_v = T$ by a factor of $\frac{1}{\pi}$.
+In this case, the temperature can also be found easily by Euclidean expansion around the horizon $\rho = T_u T_v \cosh r$,
+	\begin{gather}
+		\dd{s}^2|_{\rho,\tau}
+		\sim \frac{1}{4} \dd{r}^2
+			+ 2T^2 \pqty{\cosh r - 1}
+				\dd{\tau}^2
+		\sim \frac{1}{4}\,\pqty{
+				\dd{r}^2
+				+ (2T)^2\,r^2 \dd{\tau}^2
+			},
+	\\[1ex]
+		2T\beta_\tau = 2\pi,
+	\quad
+		T_\tau = \frac{1}{\beta_\tau} = \frac{T}{\pi}
+	\end{gather}
+
+	To achieve our normalization convention $\xi = 2\pi \pdd{\tau}$ as before, we simply set:
+	\begin{equation}
+		\beta_\tau = 2\pi,
+	\quad
+		T_u = T_v = T = \frac{1}{2}
+	\end{equation}
+	We can then verify using the coordinate transformation \eqref{eq:poincare2btz} that the modular generator in these coordinates is indeed what we are expecting:
+	\begin{equation}
+		\xi
+		= 2\pi\,(\pdd{u} - \pdd{v})
+		= 2\pi\pdd{\tau}
+	\end{equation}
+
+	With these BTZ coordinates, the flow of $\xi = 2\pi\pdd{\tau}$ is almost trivial; we need only identify the initial conditions, which is given by $z = z_c$ and $t = 0$ in Poincar\'e coordinates.
+The integral surface is thus given by:
+	\begin{equation}
+		z_c = \frac{L_\infty}{2} \frac{
+				\sqrt{2}\,T
+				\sqrt{\rho - T^2}
+			}{
+				\sqrt{\rho^2 - T^4}
+					\,\cosh\,(2T\phi)
+				+ \pqty{\rho - T^2}
+			},
+	\quad
+		T_u = T_v = T = \frac{1}{2}
+	\end{equation}
+	This is a surface in the BTZ coordinates that parallels $\pdd{\tau}$ and intersects the horizon. 
+	With some basic algebraic manipulation, this can be solved in terms of $\rho(\phi)$:
+	\begin{equation}
+		\rho(\phi;z_c)
+		= T^2 \pqty{
+			1 + \frac{1}{2} \pqty{
+				\frac{
+					\cosh\,(2T\phi) \sqrt{
+						1 - (\frac{2z_c}{L_\infty})^2 \sinh^2 (2T\phi)
+					} - 1
+				}{z_c\sinh^2 (2T\phi)}
+			}^{\!\!\!\!2\ }
+		},\quad
+		T = \frac{1}{2}
+	\end{equation}
+
+	We note that there is also a mysterious square root structure here: $
+		\sqrt{
+			1 - (\frac{2z_c}{L_\infty})^2 \sinh^2 (2T\phi)
+		}
+	$, which resembles the familiar $
+		\sqrt{1 + (\frac{2z_c}{L})^2}
+	$ but has a minus sign, and the $\frac{2z_c}{L}$ factor is weighted by $\sinh\,(2T\phi)$.
+
+	\begin{figure}[!ht]
+	\centering
+	\includegraphics[width=.7\linewidth]{img/modFlowCutoff2BTZ.pdf}
+%	\hspace{2em}
+%	\vspace{-2ex}
+	\caption{Integral surface of the modular flow when mapped to the BTZ coordinates, starting from $t = 0,\ z = z_c$.
+Here we've chosen $\frac{L_\infty}{2} = 1$ while $z_c = 0.1,\,0.2,\,\cdots,\,0.9$.
+Also we've taken $T_u = T_v = T = \frac{1}{2}$ as discussed before, and the horizon is at $T^2 = \frac{1}{4}$.
+}
 	\end{figure}
@@
 	We thus have to repeat the calculations above to get the geodesic $\gamma$ and modular generators $\xi^\mu$ in the new backgrounds.
-However, it is convenient to remember that all BTZ black holes are locally equivalent to the pure $\mrm{AdS}_3$; we can then map Poincar\'e $(u,v,z)$ to BTZ $(t,r,\phi)$ by \cite{Hubeny:2007xt}:
+However, it is convenient to remember that all BTZ black holes are locally equivalent to the pure $\mrm{AdS}_3$; we can then map Poincar\'e $(u,v,z)$ to BTZ Schwarzschild $(t,r,\phi)$ by \cite{Hubeny:2007xt}:
 	\begin{equation}
@@
 
-	We now restrict to $t_\pm = 0, \phi_- = -\phi_+$ and set $T_u = T_v = T$ for convenience; in this case the RT surface is given by \cite{Rangamani:2016dms}:
+	What's the difference between this map and \eqref{eq:poincare2btz}?
+First, the coordinates are different: in \eqref{eq:poincare2btz} we have $(u,v,\rho)$ and here we have Schwarzschild $(t,r,\phi)$; but that's not essential.
+What's crucial is that here, we map \textbf{the \textsl{whole} of Poincar\'e into BTZ with a \textsl{compact} $\phi$ circle}, while before in \eqref{eq:poincare2btz} we map a \textbf{$L_\infty$-sized wedge in Poincar\'e into BTZ with a \textsl{non-compact} $\phi$ line}.
+
+	We now restrict to $t_\pm = 0, \phi_- = -\phi_+$ and again set $T_u = T_v = T$ for convenience; in this case the RT surface is given by \textcite{Rangamani:2016dms} (section 6.1.2):
 	\begin{equation}
@@
 		\var{Q}_{\xi}
-		= \int \dd{\phi} (\chi_\xi)_\phi
-	$, where:
+		= \int \dd{x^\mu} (\chi_\xi)_\mu
+	$, wher e.g.
 	\begin{equation}
@@
 
-	The $\int_\gamma \dd{\phi}$ integration can be done at the asymptotic infinity $r\to\infty$ instead, due to Stokes' theorem; this gives the following result:
+	By definition the $\int_\gamma$ integration goes along the RT surface; we should be careful in the calculations and include the contributions from the $(\chi_\xi)_r \dd{r}$ component. 
+	Alternatively, using Stokes' theorem, it can be done at the asymptotic infinity $r\to\infty$ instead; in this case we need only the $\phi$ component.
+These two integration contours give the same result:
 	\begin{equation}
@@
 	Now we consider constant cutoff at $r = r_c$.
-Again we need to trade $L_\infty$ above with the coordinate length of the interval $L$ at the cutoff $r_c$.
+Again we need to trade the $L_\infty$ above with the coordinate length of the interval $L$ at the cutoff $r_c$.
 The relation can be solved by looking at the geodesic equation, which is slightly non-trivial this time:
 	\begin{equation}
-		\frac{\cosh (L_\infty T)}{\cosh (LT)}
+		\frac{\cosh L_\infty T}{\cosh LT}
 		= \frac{r_c}{\sqrt{r_c^2 - 4T^2}}
@@
 		= \frac{\var{T}}{2G} \pqty{
-				L \coth (LT) - \frac{1}{T}
+				L \coth LT - \frac{1}{T}
 			}
@@
 				1 + \frac{4T^2}{r_c^2 \sinh^2 LT}
-			}}
-	\qquad\text{(up to const.)}
+			}},
+	\quad\textsl{up to const.}
 	\end{equation}
@@
 	\begin{equation}
+	\begin{aligned}
 		Q_\xi
-		= \frac{1}{2G} \mop{arctanh}
+		&= \frac{1}{2G} \mop{arctanh}
 			\frac{1}{\sqrt{
@@
 				} - 1
-			}
-	\qquad\text{(up to const.)}
+			},
+	\quad\textsl{up to const.} \\
+		&= \frac{1}{2G} \mop{arcsinh}
+			\frac{r_c \sinh LT}{2T}
+	\end{aligned}
 	\end{equation}
+	Although we haven't been careful about integration constants, this result happens to agree with the entropy in \cite{Lewkowycz:2019xse}.
 
 \vspace{1.2\baselineskip}
+\pagebreak[4]
 \raggedright

### 2021-04-15 alpha/GravitationalEntropy/entropy.tex
Update note on TsT EE

@@
 		$. Note the \mquote{+} before $\dd{u} \dd{v}$.
+
+	\item The $T\bar{T}$ deformation is parametrized by the deformation parameter $\mu$, defined in \cite{Apolo:2019zai}; for the single-trace situation, it is more convenient to use the \textit{worldsheet} deformation parameter $\lambda = \mu/\ell_s^2$, where $\ell_s$ is the string length.
+See \cite{Apolo:2019zai} section 2.3 and its (2.43).
 	\end{itemize}
@@
 Here we choose to absorb such $2\pi$ into the definition of $\xi$, so the Euclidean periodicity w.r.t.~$\xi$ is simply $\beta_\xi = 1 = \frac{1}{T_\xi}$, which means the surface gravity along the horizon is given by $\kappa_\xi = 2\pi T_\xi = 2\pi$.
-\subsection{Exercise: Poincar\'e $\mrm{AdS}_3/\mrm{CFT}_2$}
+\subsection{Case study: Poincar\'e $\mrm{AdS}_3/\mrm{CFT}_2$}
 	We illustrate the above ideas in Poincar\'e $\mrm{AdS}_3$ vacuum, which is the simplest situation and can be easily compared with the results of \textcite{Lewkowycz:2019xse}. 
@@
 		= \pm \frac{L}{2}
+	\label{eq:length_relations}
 	\end{equation}
@@
 	To gain more understanding of the modular flow of the cutoff theory, we can look at the map to the Rindler coordinates.
-In the Poincar\'e $\mrm{AdS}_3$ case this is explicitly given in Appendix B by \textcite{Song:2016gtd}; the Poincar\'e $(t,x,z)$ is mapped to BTZ $(u,v,\rho)$:
+In the Poincar\'e $\mrm{AdS}_3$ case this is explicitly given in Appendix B by \textcite{Song:2016gtd}; the entanglement wedge in Poincar\'e $(t,x,z)$ is mapped to the planar BTZ $(u,v,\rho)$:
 	\begin{equation}
@@
 	\end{equation}
-	Here we've reused the variable names $(u,v)$ for the BTZ coordinates, and we've tweaked the expressions in \cite{Song:2016gtd} to be more symmetric in $(u,v)$.
+	This is a BTZ \textit{black string} with \textit{non-compact} $\phi$ direction. 
+	One can check that the $(u,v,\rho)$ coordinates indeed cover the $L_\infty$-sized entanglement wedge specified by $\xi$. 
+	Here we've reused the variable names $(u,v)$ for the planar BTZ coordinates, and we've tweaked the expressions in \cite{Song:2016gtd} to be more symmetric in $(u,v)$.
 
@@
 
-	With these BTZ coordinates, the flow of $\xi = 2\pi\pdd{\tau}$ is almost trivial; we need only identify the initial conditions, which is given by $z = z_c$ and $t = 0$ in Poincar\'e coordinates.
+	With these planar BTZ coordinates, the flow of $\xi = 2\pi\pdd{\tau}$ is almost trivial; we need only identify the initial conditions, which is given by $z = z_c$ and $t = 0$ in Poincar\'e coordinates.
 The integral surface is thus given by:
@@
 	\end{equation}
-	This is a surface in the BTZ coordinates that parallels $\pdd{\tau}$ and intersects the horizon. 
+	This is a surface in the planar BTZ coordinates that parallels $\pdd{\tau}$ and intersects the horizon.
+The horizon length, which is ``cut off'' by this surface, gives the finite entanglement entropy of the cutoff interval.
 	With some basic algebraic manipulation, this can be solved in terms of $\rho(\phi)$:
@@
 	\centering
-	\includegraphics[width=.7\linewidth]{img/modFlowCutoff2BTZ.pdf}
+	\includegraphics[width=.6\linewidth]{img/modFlowCutoff2BTZ.pdf}
 %	\hspace{2em}
 %	\vspace{-2ex}
-	\caption{Integral surface of the modular flow when mapped to the BTZ coordinates, starting from $t = 0,\ z = z_c$.
-Here we've chosen $\frac{L_\infty}{2} = 1$ while $z_c = 0.1,\,0.2,\,\cdots,\,0.9$.
-Also we've taken $T_u = T_v = T = \frac{1}{2}$ as discussed before, and the horizon is at $T^2 = \frac{1}{4}$.
+	\caption[Integral surface of the modular flow when mapped to the planar BTZ coordinates]{%
+		Integral surface of the modular flow when mapped to the planar BTZ coordinates. Note that the $\rho$ axis is logarithmic.
+
+		The flow starts from $t = 0,\ z = z_c$, and here we've chosen $\frac{L_\infty}{2} = 1$ while $z_c = 0.1,\,0.2,\,\cdots,\,0.9$. 
+		Also we've taken $T_u = T_v = T = \frac{1}{2}$ as discussed before, and the horizon is at $\rho = T_u T_v = T^2$. 
 	}
 	\end{figure}
+\subsection{The cutoff field theory perspective}
+	From the field theory's perspective, the above calculations seem to suggest that the modular flow \underline{for an $L$-sized interval in the cutoff theory} is given by the modular flow \underline{of a CFT for an $L_\infty$ interval}; we denote this modular flow by $\xi = \xi(L_\infty)$.
 
+	One natural question is that whether this observation holds for a generic $T\bar{T}$ deformation, e.g.~the single-trace deformation of the opposite sign, which is dual to the TsT black string solution in the bulk, described by \textcite{Apolo:2019zai}.
+This will be explored in the later sections.
+The idea is:
+
+	\begin{enumerate}
+	\item There is a flow $f(\mu)$ from the undeformed $\mrm{AdS}/\mrm{CFT}$ to the deformed geometry, parametrized by $\mu$, that maps $L_\mrm{CFT}\mapsto L$. 
+	In the cutoff picture, $f(\mu)$ moves the boundary into the bulk, and we have $L_\mrm{CFT} = L_\infty\mapsto L$.
+
+	Note that $f(\mu)$ is generally \textit{not} a diffeomorphism, otherwise the geometries will be equivalent; therefore, the action of $f(\mu)$ on quantities e.g.~the metric needs to be specified, and cannot be na\"ively induced from the map of coordinates.
+
+	\item The modular flow in the deformed theory is the ``push-forward'' of the CFT modular flow, namely $\xi_\mrm{CFT} \mapsto \xi = f^* \circ \xi_\mrm{CFT}$.
+However, such ``push-forward'' remains ambiguous, since $f(\mu)$ is \textit{not} a diffeomorphism, and we need an explicit prescription of this procedure.
+
+	\item We then compute the entropy w.r.t.~the push-forward modular flow $\xi$, which is then reduced to the area of an RT surface in the deformed geometry.
+
+	\sidenote{The end result \textit{might} simply be a flow of the RT surface, induced by the flow $f(\mu)$ of the coordinates. Its area, on the other hand, depends on the flow of the metric.}
+	\end{enumerate}
+	This program echoes the idea advocated by \textcite{Guica:2019nzm}. 
 \section{Entropy as Noether Charge}
+
 	Ref: \textcite{Wald:1993nt,Iyer:1994ys,Iyer:1995kg}.
 
-	Ref: \textcite{Lewkowycz:2013nqa,Faulkner:2013ana}.
+	Ref: \textcite{Lewkowycz:2013nqa}, \\
+	\hspace*{4em} and \textcite{Faulkner:2013ana}.
 
@@
 There is no free parameter in Poincar\'e $\mrm{AdS}_3$, unless we turn on temperature; this leads to the BTZ geometry.
-
-	We thus have to repeat the calculations above to get the geodesic $\gamma$ and modular generators $\xi^\mu$ in the new backgrounds.
+\subsection{Case study: BTZ}
+	We thus have to repeat the calculations above to get the geodesic $\gamma$ and modular generators $\xi^\mu$ in the new BTZ backgrounds.
 However, it is convenient to remember that all BTZ black holes are locally equivalent to the pure $\mrm{AdS}_3$; we can then map Poincar\'e $(u,v,z)$ to BTZ Schwarzschild $(t,r,\phi)$ by \cite{Hubeny:2007xt}:
@@
 		= \int \dd{x^\mu} (\chi_\xi)_\mu
-	$, wher e.g.
+	$, where e.g.
 	\begin{equation}
 		(\chi_\xi)_\phi
-		= \frac{\var{T} \coth (LT)}{2G}
+		= \frac{\var{T} \coth LT}{2G}
 			\pqty{
 				1 - {\frac{r}{\sqrt{r^2 - 4T^2}}}
-				\frac{\cosh (2T\phi)}{\cosh (TL)}
+				\frac{\cosh 2T\phi}{\cosh TL}
 			}
@@
 	\begin{equation}
-		Q_\xi = \frac{1}{2G} \log \frac{\sinh (LT)}{T}
+		Q_\xi = \frac{1}{2G} \log \frac{\sinh LT}{T}
 	\end{equation}
 
-\subsection{With constant cutoff}
+\subsubsection{With constant cutoff}
 	Now we consider constant cutoff at $r = r_c$.
@@
 	Although we haven't been careful about integration constants, this result happens to agree with the entropy in \cite{Lewkowycz:2019xse}. 
+\section{Entanglement in the TsT Background}
+	We are interested in the holographic entanglement entropy of the single-trace $T\bar{T}$ deformed theory, and we are considering the case where the deformation parameter carries a sign different from the cutoff picture.
+The setup is described by e.g.~\textcite{Apolo:2019zai,Chakraborty:2018kpr}.
+
+	Namely, we are considering a flow towards UV, instead of the flow towards IR studied by e.g.~\cite{McGough:2016lol,Lewkowycz:2019xse}. 
+	The field theory side calculation of entanglement entropy \cite{Donnelly:2018bef,Lewkowycz:2019xse} seems to survive through the sign flip; when dualed to the bulk it suggests that:
+	\begin{equation}
+		S = \frac{1}{2G} \mop{arccosh}
+			\frac{L}{L_0},
+	\quad
+		C(L) = L \pdv{L}\,S
+		= \frac{1}{2G} \frac{1}{
+				\sqrt{1 - (\frac{L_0}{L})^2}
+			}
+	\label{eq:tst_ft_ee}
+	\end{equation}
+	There is a length scale $L_0$ here which is the minimal length of the entanglement interval; for $L < L_0$ the entropy becomes complex, thus unphysical.
+This can be interpreted as a UV length scale arised from the deformation.
+In terms of the worldsheet deformation parameter $\lambda$ and w.r.t.~to the TsT metric given in \cite{Apolo:2019zai}, we have:
+	\begin{equation}
+		L_0 = \sqrt{8\lambda}
+	\end{equation}
+
+	Although we've expressed everything in terms of the bulk parameters and the worldsheet deformation parameter $\lambda$, we'd like to emphasize that the above results comes from purely field theoretical calculations, and they are mapped to the bulk using the holographic dictionary.
+Our goal is to reproduce them as gravitational entropy, from bulk calculations.
+\subsection{Case study: Ramond vacuum $T_u = T_v = 0$}
+	For simplicity, we first look at the \textsl{Ramond vacuum}, i.e.~the TsT background with $T_u = T_v = 0$. In this case the string frame metric and dilaton is given by:
+	\begin{equation}
+		\dd{s}^2
+		= \frac{\dd{z}^2}{z^2}
+			+ \frac{\dd{u}\dd{v}}{z^2 + 2\lambda},
+	\quad
+		e^{2\Phi}
+		= \frac{k}{p}
+			\frac{z^2}{z^2 + 2\lambda}\,
+			e^{-2\phi_0},
+		\label{eq:staticMetricPoincare}
+	\end{equation}
+	To avoid confusion with the dilaton, we denote the angular direction with the curvy $\varphi = \frac{u + v}{2}$. 
+	This is derived from (3.13) of \cite{Apolo:2019zai}, with $r = \frac{1}{z^2}$; we've set the AdS radius $\ell_{\mrm{AdS}} = 1$ for now and neglected the $B$ field.
+For more simplifications, we further set:
+	\begin{equation}
+		p = k = 1
+	\end{equation}
+\subsubsection{RT surface}
+	The Einstein frame metric $G_{\mu\nu}$ is related to the string frame metric $g_{\mu\nu}$ by:
+	\begin{equation}
+		G_{\mu\nu} = e^{-4\Phi} g_{\mu\nu}
+	\end{equation}
+	Now consider a spacelike geodesic in Einstein frame within the time slice $t = 0$; we can nicely parametrize it  with its peak $z_0$ at $\varphi = 0$.
+The $\pdd{\varphi}$ symmetry implies that along the geodesic $\gamma$,
+	\begin{equation}
+		\pqty{\dv{z}{\varphi}}_{\!\gamma}^{\!2}
+		= \frac{z_0^2}{z^2}
+				\frac{z_0^2}{z_0^2 + 2\lambda}
+			- \frac{z^2}{z^2 + 2\lambda}
+	\end{equation}
+
+	The coordinate length $L$ at the boundary is given by:
+	\begin{equation}
+	\begin{aligned}
+	  L = L(z_0;\mu)
+	  &= \int \dd{\varphi}
+	  = 2\int_0^{z_0}
+	      \abs{\dv{\varphi}{z}}
+	      \dd{z} \\
+	  &= 2\int_0^{z_0}
+	      \frac{1}{\sqrt{
+	          \frac{z_0^2}{z^2}
+	          \frac{z_0^2}{z_0^2 + 2\lambda}
+	          - \frac{z^2}{z^2 + 2\lambda}
+	      }}
+	      \dd{z}
+	\end{aligned}
+	\label{eq:length_function}
+	\end{equation}
+
+\pagebreak\noindent
+	Note that:
+	\begin{itemize}
+	\item $\mu\to 0,\, L(z_0;\mu) \to 2z_0$, we recover the AdS result: in this case the geodesic $\gamma$ is a semi-circle with radius $z_0$.
+
+	\item $z_0\to 0,\,
+		L(z_0;\mu) \to \sqrt{\frac{\pi^2}{2} \lambda}
+	$, we see that $L$ is bounded from below by:
+	\begin{equation}
+		L_{\min} (\mu)
+		= \sqrt{\frac{\pi^2}{2} \lambda}
+	\end{equation}
+	This feature is very similar to the lower bound $L_0$ of entanglement length, but they do \textit{not} agree; in fact,
+	\begin{equation}
+		L_{\min} / L_0 = \pi / 4
+	\end{equation}
+	\end{itemize}
+
+	The entanglement entropy, as proposed by RT, is given by:
+	\begin{equation}
+	\begin{aligned}
+	  S_\mrm{RT}
+	  &= \frac{1}{4G} \int_\gamma
+	    \frac{z^2 + 2\lambda}{z^2}
+	    \sqrt{
+	        \frac{\dd{z}^2}{z^2}
+	        + \frac{\dd{\varphi}^2}{z^2 + 2\lambda}
+	    } \\
+	  &= \frac{1}{2G} \int_0^{z_0} \dd{z}
+	    \frac{z^2 + 2\lambda}{z^2}
+	      \sqrt{
+	          \frac{1}{z^2}
+	          + \frac{1}{z^2 + 2\lambda}
+	          \Big/
+	          \pqty{\dv{z}{\varphi}}^{\!\!2}
+	      } \\
+	  &= \frac{1}{2G} \int_0^{z_0} \dd{z}
+	    \frac{z^2 + 2\lambda}{z^2}
+	      \sqrt{
+	          \frac{1}{z^2}
+	          + \frac{1}{z^2 + 2\lambda}
+	          \Big/
+	          \pqty{
+					\frac{z_0^2}{z^2}
+					\frac{z_0^2}{z_0^2 + 2\lambda}
+					- \frac{z^2}{z^2 + 2\lambda}
+	          }
+	      }
+	\end{aligned}
+	\end{equation}
+	We don't have an explicit analytic result for the above integral, but numerical calculations suggest that it does not agree with \eqref{eq:tst_ft_ee}. 
+	As is inspired by the cutoff picture, we would like to tweak it such that it matches with \eqref{eq:tst_ft_ee}.
+
+	We have the following observations: 
+	\begin{itemize}
+	\item If we denote $L_{\mrm{CFT}} = 2z_0$, and instead of using \eqref{eq:length_function}, we use:
+	\begin{equation}
+		L' = 2\sqrt{z_0^2 + 2\lambda},
+	\quad\text{i.e.}\quad
+		\pqty{\frac{L'}{2}}^{\!\!2}
+		= \pqty{\frac{L_\mrm{CFT}}{2}}^{\!\!2} + 2\lambda,
+	\end{equation}
+	Which mimic the relation \eqref{eq:length_relations}, then the $C(L)$ from the field theory calculations can be re-written as:
+	\begin{equation}
+		C(L')
+		= \frac{L'}{L_{\mrm{CFT}}}
+		= \frac{1}{\sqrt{1 - (\frac{L_0}{L'})^2}},
+	\quad L_0 = \sqrt{8\lambda}
+	\end{equation}
+	Where the relation $C(L') = \frac{L'}{L_{\mrm{CFT}}}$ is completely analogous to the double-trace situation; in that case we have $L_\mrm{CFT} = L_\infty$.
+
+	\item With quite a bit of numeric experimentations, we find that:
+	\begin{equation}
+		L_\mrm{CFT}\,\pdv{L_\mrm{CFT}}\,S_\mrm{RT}
+		= z_0\,\pdv{z_0}\,S_\mrm{RT}
+		\sim \frac{1}{2G}
+	\label{eq:RT_entropy_derivative}
+	\end{equation}
+	In fact the result seems to be $\lambda$ independent; but we know that:
+	\begin{equation}
+		S_{\lambda = 0}
+		= \frac{1}{2G}
+			\log \frac{L_\mrm{CFT}}{\epsilon}
+		= \frac{1}{2G}
+			\log \frac{2z_0}{\epsilon}
+	\end{equation}
+	Namely $
+		z_0\,\pdv{z_0}\,S_{\lambda = 0}
+		= \frac{1}{2G}
+	$ exactly. Combined with the numerical results, this hints at the fact that \eqref{eq:RT_entropy_derivative} holds exactly with no $\lambda$ dependence.
+
+	\item Therefore, we have:
+	\begin{equation}
+		L' \pdv{S_\mrm{RT}}{L'}
+		= L_\mrm{CFT} \pdv{S_\mrm{RT}}{L_\mrm{CFT}}
+			\pdv{L_\mrm{CFT}}{L'}
+			\frac{L'}{L_\mrm{CFT}}
+		\sim \frac{1}{2G}
+			\pqty{\frac{L'}{L_\mrm{CFT}}}^{\!\!2}
+		= C(L')^2
+	\end{equation}
+	We find that \textit{numerically}, this does hold very well. Unfortunately this is not what we expected. How should we interpret this?
+	\end{itemize}
+
+	\begin{figure}[!ht]
+	\centering
+	\includegraphics[width=.7\linewidth]{img/cFunctionGame.pdf}
+%	\hspace{2em}
+%	\vspace{-2ex}
+	\caption[Numerical construction of the $C(L)$ function]{%
+		Numerical construction of the $C(L)$ function from $S_\mrm{RT}$ by considering $
+			\sqrt{
+				\frac{1}{2G}
+				L' \pdv{S}{L'}
+			}
+		$. What's happening? I have no idea.
+	}
+	\end{figure}
 

### 2021-04-27 alpha/Schwarzian/schwarzian.tex
Add note on Schwarzian derivative

% !TeX document-id = {b5392a94-51a3-49d1-9ba5-698bc09f9d35}
% !TeX encoding = UTF-8
% !TeX spellcheck = en_US
% !TeX TXS-program:bibliography = biber -l zh__pinyin --output-safechars %

\documentclass[a4paper
	,10pt
%	,twoside
]{article}

\input{../preamble.tex}
\input{../.modules/basics/biblatex.tex}

\title{Finding finite transformations}
\addbibresource{schwarzian.bib}

%%% ID: sensitive, do NOT publish!
\InputIfFileExists{id.tex}{}{}

\makeatletter
\newcommand{\nobeginpar}{\@beginparpenalty=10000}
\makeatother

\usepackage{cancel}
%\counterwithout{equation}{section}

\begin{document}
\maketitle
\pagenumbering{arabic}
\thispagestyle{empty}

\vspace*{-.5\baselineskip}

	Sometimes we encounter infinitesimal transformations and we'd like to integrate them to some finite transformations. The trick of doing this is to use the fact that transformations should \textbf{compose nicely}; this idea is well introduced in classical texts of group theory such as \textcite{wybourne1993classical}; here we shall use it to construct the finite transformations\footnote{
		I'd like to thank \cjk[gkai]{\textit{孙悠然}} for re-inventing this method and explaining it to me. Another good reference for this is \url{http://personalpages.to.infn.it/~billo/didatt/gruppi/gruppi.html}, or more specifically, \url{http://personalpages.to.infn.it/~billo/didatt/gruppi/liegroups.pdf}. 
	}.

\section{Stress Tensor and the Schwarzian Derivative}
	We will work with a well-known example: the transformation of the stress tensor $T(z)$ in a 2D CFT. We know that the $TT$ OPE takes the following form:
	\begin{equation}
		T(z)\,T(0)
		\sim \frac{c/2}{z^4}
			+ \frac{h\,T(0)}{z^2}
			+ \frac{\pd T(0)}{z},
	\quad h = 2
	\end{equation}
	This is related to the algebra of its modes, namely the Virasoro algebra with central charge $c$. Using Ward identity, we can further relate this to the infinitesimal transformation of $T$, under the conformal map $z\mapsto z+\epsilon$:
	\begin{equation}
		\var_\epsilon {T(z)}
		= - \operatorname*{Res}_{z'\to z}
				\epsilon(z')\,T(z')\,T(z)
		= - \epsilon\,\pd T
			- h\,\pd\epsilon\,T
			- \frac{c}{12}\,\pd^3 \epsilon,
	\quad h = 2
	\end{equation}

	We see that $T(z) = T_{zz}(z)$ is almost like a tensor: the first two terms in the infinitesimal transformation are from translations and rotations, as expected, but there is a third \textit{anomalous} term which is \textbf{independent of $T$}. Thus the integrated, finite transformation of this term should be a \textbf{functional of $w(z)$} that is independent of $T$, i.e.
	\begin{equation}
		- \frac{c}{12}\,\pd^3 \epsilon
	\longrightarrow
		- \frac{c}{12}\, S[w]_{(z)}
		\equiv - \frac{c}{12} \Bqty{w,z},
	\quad
		S[w]_{(z)} = S[w,\pd_z w,\cdots]
	\end{equation}
	The full integrated transformation of $T$ can then be written as:
	\begin{equation}
		T_{zz}(z)
		= T_{ww}(w) \pqty{\pdv{w}{z}}^{\!2}
			+ \frac{c}{12} \Bqty{w,z},
	\end{equation}
	\vspace{-.6\baselineskip}
	\begin{equation}
		T_{ww}(w) \dd{w}^2
		= T_{zz}(z) \dd{z}^2
			- \frac{c}{12} \Bqty{w,z} \dd{z}^2
	\end{equation}

	To find $S = S[w]$, consider \textbf{two successive transformations:}
	\begin{equation}
		z \xmapsto{\ w\ } w \xmapsto{\ v\ } v
	\end{equation}
	Here we've abused the symbols $w,v$ to label both the transformations and their images: $w\colon z\mapsto w(z)$, $v\colon w\mapsto v = v(w) = v(w(z))$. 
	To say that \textbf{$S[w]_{(z)}$ compose nicely} under successive transformations is to say that $S[w]_{(z)} = \Bqty{w,z}$ satisfies the following \textbf{chain rule:}
	\begin{equation}
		\Bqty{v,z} \dd{z}^2
		= \Bqty{v,w} \dd{w}^2
		+ \Bqty{w,z} \dd{z}^2
	\end{equation}
\pagebreak

	Generally, we can think of the chain rules as \textit{representations} of the transformation group; in this case the group product is given by the composition $v\circ w$. For example, the usual chain rule is a representation on the cotangent bundle by the pullback $
		(v\circ w)^*
		= w^* \circ v^*
	$; we have:
	\begin{equation}
		(v\circ w)^* \dd{v}
		= \dv{v}{z} \dd{z}
		= \dv{v}{w} \dv{w}{z} \dd{z}
		= w^* \circ v^* \dd{v}
	\end{equation}
	The Schwarzian derivative is just another representation of the chain rule, on the bundle of symmetric 2-differentials $\dd{z}^2$.

	To actually solve for the functional dependence $S = S[w]_{(z)}$, we consider the special case:
	\begin{equation}
		v = w + \var{w},
	\quad \var{w} = \epsilon
	\end{equation}
	Going back to the chain rule, we then have:
	\begin{equation}
		\pqty{S[w + \epsilon] - S[w]}_{(z)} \dd{z}^2
		= S[w + \epsilon]_{(w)} \dd{w}^2
		= \pd_w^3 \epsilon \dd{w}^2
	\end{equation}
	\vspace{-.8\baselineskip}
	\begin{equation}
		\var{S}
		= \pqty{\pdv[3]{w} \var{w}} (\pd_z w)^2
	\label{eq:functional_eq}
	\end{equation}

	We see that the chain rule can be re-written as functional differentials; in this form it has \textbf{no explicit dependence of $z$, and it's a functional equation for $
		S[w]_{(z)} = S[w,\pd_z w,\cdots]
	$}. This reveals the nature of the above 2-step transformation $z\mapsto w\mapsto v$: with $z\mapsto w$ we construct the function $w(z)$, while with $w\mapsto v = w + \var{w}$ we consider the variation of $S[w]_{(z)}$ w.r.t.~$w(z)$.

	\newparagraph
	Now suppose that $w(z)$ is constructed by composing infinitesimal transformations $z\mapsto z + \epsilon$; namely, $w = w_t(z)$ is the integral curve of a series of infinitesimal transformations along $\epsilon$, starting from $z$. From the perspective of differential geometry, \textbf{$w = w_t(z)$ is the flow of vector field $\epsilon$}, and $t$ is the flow parameter. This is precisely the \textbf{exponential map} that brings $t\epsilon$ in the Lie algebra to $w_t(z)$ in the Lie group.

	The crucial observation is that \textbf{the functional equation \eqref{eq:functional_eq} should hold for any $w = w_t(z)$}. Along the flow, we have:
	\begin{equation}
		\var{w_t} = \var{t} \pdd{t} w_t
	\end{equation}
	We then have:
	\begin{equation}
		\pdd{t} S
		= (\pd_z w_t)^2
			\pdv[3]{w_t}\,\pdd{t} w_t
	\end{equation}

	To solve the above equation, we try to complete the right-hand side into a total $t$-differential: $
		\pdd{t} S = \pdd{t} ({\cdots})
	$. Note that:
	\begin{equation}
		\pdv{w} = \frac{1}{\pd w}\pdv{z},
	\quad
		\pdv[3]{w}
		= \frac{1}{(\pd w)^3} \pd^3
			- 3 \frac{\pd^2 w}{(\pd w)^4} \pd^2
			+ \pqty{
				3\frac{(\pd^2 w)^2}{(\pd w)^5}
				- \frac{\pd^3 w}{(\pd w)^4}
			} \pd
	\end{equation}
	Namely, we can trade the functional derivative w.r.t.~$w$ to regular derivative $\pd = \pdd{z}$, with a $\frac{1}{\pd w}$ factor. 
	From now on we shall drop the subscript $t$ for $w = w_t$, but the $t$-dependence is not forgotten. We thus have:
	\begin{equation}
	\begin{aligned}
		\pdd{t} S
		&= \frac{1}{\pd w}
				\pd_t \pd^3 w
			- 3 \frac{\pd^2 w}{(\pd w)^2}
				\pd_t \pd^2 w
			+ \pqty{
				3\frac{(\pd^2 w)^2}{(\pd w)^3}
				- \frac{\pd^3 w}{(\pd w)^2}
			} \pd_t \pd w \\
		&= \pdd{t} \frac{\pd^3 w}{\pd w}
			- 3 \frac{\pd^2 w}{(\pd w)^2}
				\pd_t \pd^2 w
			+ 3\frac{(\pd^2 w)^2}{(\pd w)^3}
				\pd_t \pd w \\
		&= \pdd{t} \frac{\pd^3 w}{\pd w}
			- \frac{3}{2}\,\pdd{t} 
				\pqty{\frac{\pd^2 w}{\pd w}}^{\!\!2} \\
	\end{aligned}
	\end{equation}

	Indeed, the right-hand side can be arranged into a total $t$-derivative; we have:
	\begin{equation}
		S[w](z)
		\equiv \Bqty{w,z}
		= \frac{\pd^3 w}{\pd w}
			- \frac{3}{2}
			\pqty{\frac{\pd^2 w}{\pd w}}^{\!\!2}
	\end{equation}
	This is the \textit{Schwarzian derivative}. The $t$-integration constant is fixed by requiring that $\Bqty{z,z} = 0$. We see that to find the finite transformation, instead of explicit integrating $\var_\epsilon T$, we can \textbf{assume that there is a flow $S[w]_{(z)}$ where $w = w_t(z)$; by completing the total derivative $\pdd{t} S$ along $w_t(z)$ with arbitrary $t$, we can recover the functional dependence $S = S[w]$}.

\section{Linear Dilaton}
	Let's look at another example: the linear dilaton $X$ with infinitesimal transformation:
	\begin{equation}
		\var{X}
		= - \epsilon\,\pd X
			- \bar{\epsilon}\,\pdbar X
			- \frac{\alpha'V}{2}\,\pqty{
				\pd\epsilon
				+ \pdbar\bar{\epsilon}
			}
	\label{eq:dilaton_transformation}
	\end{equation}
	Here we've dropped the spacetime index $X^\mu \leadsto X$. We see that it is again in the form of translation plus a shift, and the shift is independent of the field $X$.

	To understand this infinitesimal transformation, first recall that $
		\pqty{
			\pd\epsilon
			+ \pdbar\bar{\epsilon}
		}
	$ is precisely the contribution of Weyl rescaling in the conformal symmetry; we have:
	\begin{equation}
		0 = \var{g_{ab}}
		= \pqty{2\var{\omega} - \mcal{L}_\epsilon}\,
			g_{ab}
		= 2\,\pqty{
				\var{\omega} g_{ab}
				- \nabla_{[a} \epsilon_{b]}
			},
	\quad
		2\var{\omega}
		= \frac{2}{d}\,\nabla\cdot\epsilon,
	\label{eq:conformal_Killing}
	\end{equation}
	This is in fact the \textit{conformal Killing equation}; the generators of conformal symmetry $\epsilon$ is the solution to this equation, which holds for general dimension $d$. 
	Here we have $d = 2$, and conformal generators are given by $\epsilon(z), \bar{\epsilon}(\bar{z})$. If we further restrict to flat metric, then we have $
		2\var{\omega}
		= \pd\epsilon
			+ \pdbar\bar{\epsilon}
	$.

	Therefore, the infinitesimal transformation is saying that $X$ transforms in a non-trivial manner under Weyl rescaling:
	\begin{equation}
		\var_\omega g_{ab} = 2\var{\omega} g_{ab},
	\quad
		\var_\omega X
		= - \frac{\alpha' V}{2}\, 2\var{\omega}
	\end{equation}
	Actually, we have a similar result for the stress tensor transformation discussed above, which is associated with Weyl anomaly:
	\begin{equation}
		\var_\omega T(z)
		= - \frac{c}{12}\,\pd^2 (2\var{\omega})
	\end{equation}

	In fact, from $\var_\omega {X}$ we can already integrate over $\omega$ and recover the finite transformation for $\var_\omega {X}$, using the finite version of $
		2\var{\omega}
		= \pd\epsilon
			+ \pdbar\bar{\epsilon}
	$, namely the conformal Killing equation \eqref{eq:conformal_Killing}:
	\begin{equation}
		g'_{ab}
		= g_{ab}
		= e^{2\omega} \pdv{\sigma^c}{\sigma'^a}
			\pdv{\sigma^d}{\sigma'^b}\,g_{cd},
	\quad
		e^{-2\omega}
		= \frac{1}{d}\,
			g^{ab}
			\pdv{\sigma^c}{\sigma'^a}
			\pdv{\sigma^d}{\sigma'^b}
			\,g_{cd}
	\end{equation}
	For $d = 2$, note that $g_{z\bar{z}} = g_{\bar{z}z} = 2$, after carefully summing over indices, we have:
	\begin{equation}
		e^{-2\omega}
		= \frac{1}{2}\, g^{w\bar{w}}
			\pdv{z}{w}
			\pdv{\bar{z}}{\bar{w}}\,
			g_{z\bar{z}} \cdot 2
		= \pdv{z}{w} \pdv{\bar{z}}{\bar{w}},
	\quad
		e^{2\omega}
		= \pdv{w}{z} \pdv{\bar{w}}{\bar{z}}
		= \abs{\pd w}^2,
	\end{equation}
	\vspace{-.5\baselineskip}
	\begin{equation}
		X'(w)
		= X(z) - \frac{\alpha' V}{2}\, 2\omega
		= X(z) - \frac{\alpha' V}{2}\, \ln e^{2\omega}
		= X(z) - \frac{\alpha' V}{2}\, \ln \abs{\pd w}^2
	\end{equation}
\subsection{Worldsheet Dilaton Action}
	We see that under Weyl rescaling, $X$ gets a $X$-independent shift, proportional to the Weyl exponent. What does this mean physically? In fact, this is a ``remnant'' of the worldsheet dilaton term in bosonic string theory \cite{Polchinski:1998rq}:
	\begin{equation}
		S^\Phi = \frac{1}{4\pi\alpha'}
			\int \dd[2]{\sigma} \sqrt{g}\,
				\alpha' R\,\Phi(X)
	\end{equation}
	Although this term vanishes in the flat limit $R \to 0$, its effects persist in the stress tensor, since the stress tensor depends on the functional derivative of $g^{ab}$, and this does not vanish when $R \to 0$ \cite{Tong:2009np}:
	\begin{equation}
		T^\Phi_{ab}
		= -4\pi \frac{1}{\sqrt{g}} \fdv{S^\Phi}{g^{ab}}
		= \pqty{
				\cdv{a} \cdv{b} {}
				- g_{ab} \nabla^c \nabla_c
			}\,\Phi
		\xrightarrow{\ g_{ab} = \delta_{ab}\ }
		\pqty{
				\pd_a \pd_b
				- \delta_{ab}\, \pd^c \pd_c
			}\,\Phi
	\end{equation}

	Note that $T_{ab}$ is not traceless, namely the dilaton coupling $S^\Phi$ is generally \textbf{not Weyl invariant} at the classical level, unless $\pd^c \pd_c \Phi = 0$, or $\Phi(X) \equiv \Phi_0$ constant. 
	However, note that $R\,\Phi(X)$ comes with an $\alpha'$ in the Lagrangian; therefore, it's contribution mixes with $\order{\alpha'}$ loop corrections from the other terms, and it's possible that the \textbf{total combined Weyl anomaly cancels} in the presence of a non-trivial $\Phi(X)$, thus restoring Weyl invariance.

	In fact, the full theory is Weyl invariant if the \textit{dilaton profile} $\Phi(X)$, the spacetime metric $G_{\mu\nu}(X)$ and gauge field $B_{\mu\nu}(X)$ all have vanishing beta functions:
	\begin{equation}
		\beta^G_{\mu\nu}
		= \beta^B_{\mu\nu}
		= \beta^\Phi = 0
	\label{eq:beta_constraints}
	\end{equation}
	Which gives the spacetime equations of motion for $G_{\mu\nu}(X), B_{\mu\nu}(X)$ and $\Phi(X)$. 
	Suppose $B_{\mu\nu}(X) \equiv 0$; at 1-loop, we have:
	\begin{equation}
		0 = \beta^\Phi
		= \frac{D - 26}{6}
			- \frac{\alpha'}{2} \nabla^\mu \cdv{\mu} \Phi
			+ \alpha' \nabla^\mu \Phi \cdv{\mu} \Phi
			+ \order{\alpha'^2},
	\quad
		B_{\mu\nu}(X) \equiv 0
	\end{equation}
	We see that it's actually possible to move away from the critical dimension $D = 26$ by turning on a large gradient of $\Phi$, while keeping the theory consistent. In particular, the \textit{linear dilaton theory} is an \textit{exact} solution of \eqref{eq:beta_constraints} to \textit{all loops} given by:
	\begin{equation}
		G_{\mu\nu}(X) = \eta_{\mu\nu},
	\quad
		B_{\mu\nu}(X) = 0,
	\quad
		\Phi(X) = V_\mu X^\mu,
	\quad
		V^2 = \frac{26 - D}{6\alpha'}
	\end{equation}
	\vspace{-.5\baselineskip}
	\begin{equation}
		T(z)
		= T^X + T^\Phi
		= -\frac{1}{\alpha'}\, \normorder{\pd X \pd X}
			+ V \pd^2 X
	\end{equation}

	Finally, by computing $TX$ OPE and applying Ward identity, we can recover the transformation rule \eqref{eq:dilaton_transformation}.

%	TODO: repeat integration program
%	restrict to the holomorphic part of the transformation.

%\nocite{Polchinski:1998rq}

\vspace{1.2\baselineskip}
%\pagebreak[4]
\raggedright
\printbibliography[%
%	title = {参考文献} %
	,heading = bibintoc
]
\end{document}

### 2021-04-28 alpha/Schwarzian/schwarzian.tex
Finish note on Schwarzian and finite transforms

@@
 
-\vspace*{-.5\baselineskip}
-
 	Sometimes we encounter infinitesimal transformations and we'd like to integrate them to some finite transformations.
@@
 	}.
+
+\setlength{\parskip}{.1\baselineskip}
+\tableofcontents
+\setlength{\parskip}{\parskipnorm}
 
@@
 		+ \Bqty{w,z} \dd{z}^2
+	\label{eq:schwarzian_chain}
 	\end{equation}
-\pagebreak
+%\pagebreak
 
@@
 	\end{equation}
-	Actually, we have a similar result for the stress tensor transformation discussed above, which is associated with Weyl anomaly:
+	Actually, we have a similar result for the stress tensor transformation discussed above, which is associated with \textbf{Weyl anomaly}:
 	\begin{equation}
@@
 		= X(z) - \frac{\alpha' V}{2}\, \ln \abs{\pd w}^2
+	\label{eq:finite_Weyl}
 	\end{equation}
 \subsection{Worldsheet Dilaton Action}
-	We see that under Weyl rescaling, $X$ gets a $X$-independent shift, proportional to the Weyl exponent.
+	We see that under Weyl rescaling, $X$ gets an $X$-independent shift, proportional to the Weyl exponent.
 What does this mean physically?
@@
 	Note that $T_{ab}$ is not traceless, namely the dilaton coupling $S^\Phi$ is generally \textbf{not Weyl invariant} at the classical level, unless $\pd^c \pd_c \Phi = 0$, or $\Phi(X) \equiv \Phi_0$ constant.
-	However, note that $R\,\Phi(X)$ comes with an $\alpha'$ in the Lagrangian; therefore, it's contribution mixes with $\order{\alpha'}$ loop corrections from the other terms, and it's possible that the \textbf{total combined Weyl anomaly cancels} in the presence of a non-trivial $\Phi(X)$, thus restoring Weyl invariance.
+	However, note that $R\,\Phi(X)$ comes with an $\alpha'$ in the Lagrangian; therefore, its contribution mixes with $\order{\alpha'}$ loop corrections from the other terms, and it's possible that the \textbf{total combined Weyl anomaly cancels} in the presence of a non-trivial $\Phi(X)$, thus restoring Weyl invariance.
 
@@
 	We see that it's actually possible to move away from the critical dimension $D = 26$ by turning on a large gradient of $\Phi$, while keeping the theory consistent.
+
 	In particular, the \textit{linear dilaton theory} is an \textit{exact} solution of \eqref{eq:beta_constraints} to \textit{all loops} given by:
@@
 		T(z)
-		= T^X + T^\Phi
-		= -\frac{1}{\alpha'}\, \normorder{\pd X \pd X}
+		= T^X_{zz} + T^\Phi_{zz}
+		= -\frac{1}{\alpha'}\,\normorder{\,\pd X \pd X}
 			+ V \pd^2 X
 	\end{equation}
+	The reason that this holds to \textit{all loops} is that we can \textit{define} an exact CFT with this action and stress tensor $T(z)$.
+Although $T^\Phi_{ab}$ is generally not traceless, in this case its trace vanishes on-shell: $\pd \pdbar X = 0$, so indeed we have conformal invariance.
 
-	Finally, by computing $TX$ OPE and applying Ward identity, we can recover the transformation rule \eqref{eq:dilaton_transformation}.
+	Finally, by computing $TX$ OPE and applying Ward identity, we \textbf{basically \textit{impose} the transformation rule \eqref{eq:dilaton_transformation} on the field $X$}.
+One can thus interpret $\var_\omega X$ as some sort of \textbf{anomalous quantum ``dimension'' of $X$}; in this case it is not a rescaling of $X$ like what we usually encounter, but is instead a \textit{shift}, introduced to preserve Weyl (conformal) invariance in the quantum theory.
 
-%	TODO: repeat integration program
-%	restrict to the holomorphic part of the transformation.
+\subsection{Finite Transformation of Linear Dilaton}
+	Although we've already obtained the finite transformation \eqref{eq:finite_Weyl} by viewing it as a Weyl rescaling, we would like to repeat the same program for finding finite transformations, just like what we've done for the Schwarzian derivative, and then confirm the above results.
+
+	In the case of linear dilaton, there are no indices of worldsheet coordinates in $X$, so the composition of finite transformations $F[w]_{(z)}$ simply gives the following ``chain rule'':
+	\begin{equation}
+		F[v]_{(z)} = F[v]_{(w)} + F[w]_{(z)}
+	\end{equation}
+	There is no extra $\dd{z}^2$ factors like the ones in the Schwarzian chain rule \eqref{eq:schwarzian_chain}.
+
+	For simplicity, we shall restrict to the \textbf{holomorphic part} of the transformation.
+	We note that $F$ converts the product in the usual chain rule $
+		\dv{v}{z}
+		= \dv{v}{w} \dv{w}{z} 
+	$ into a sum. This in fact implies that $F$ must be proportional to $\log \pd w$. But let's be patient and again consider the flow $w_t(z)$ as in the Schwarzian case; we now have:
+	\begin{equation}
+		\pdd{t} F
+		= - \frac{\alpha'V}{2}
+				\pdv{w_t} \pdd{t} w_t
+		= - \frac{\alpha'V}{2}
+				\frac{1}{\pd w_t} \pdd{t} \pd w_t
+		= - \frac{\alpha'V}{2}
+				\pdd{t} \ln \pd w_t
+	\end{equation}
+	Indeed we have $
+		F = - \frac{\alpha'V}{2} \ln \pd w
+	$, as expected. If we include the anti-holomorphic part, we recover the finite transformation \eqref{eq:finite_Weyl}:
+	\begin{equation}
+		X'(w)
+		= X(z) - \frac{\alpha' V}{2}\, \ln \abs{\pd w}^2
+	\end{equation}
 
@@
 
-\vspace{1.2\baselineskip}
+%\vspace{1.2\baselineskip}
 %\pagebreak[4]

### 2021-05-09 alpha/CovariantPhaseSpace/charge.tex
Add note on covariant formalism

% !TeX document-id = {b5392a94-51a3-49d1-9ba5-698bc09f9d35}
% !TeX encoding = UTF-8
% !TeX spellcheck = en_US
% !TeX TXS-program:bibliography = biber -l zh__pinyin --output-safechars %

\documentclass[a4paper
	,10pt
%	,twoside
]{article}

\input{../preamble.tex}
\input{../.modules/basics/biblatex.tex}

\title{Covariant Phase Space\\\large\it A Pedagogical Introduction}
\addbibresource{charge.bib}

%%% ID: sensitive, do NOT publish!
\InputIfFileExists{id.tex}{}{}

\makeatletter
\newcommand{\nobeginpar}{\@beginparpenalty=10000}
\makeatother

\usepackage{cancel}

\begin{document}
\maketitle
\pagenumbering{arabic}
\thispagestyle{empty}

%\vspace*{-.5\baselineskip}

\setlength{\parskip}{.1\baselineskip}
\tableofcontents
\setlength{\parskip}{\parskipnorm}

\addtocounter{section}{-1}
\section{Conventions}
	We follow Prof.~Wei Song's lecture notes on $\mrm{AdS}_3/\mrm{CFT}_2$, which include a very nice introduction to the covariant formalism and its application. 
	When it comes to notations, we try to follow the conventions of \textcite{Harlow:2019yfa}, with the following exceptions and extensions:

	\begin{itemize}
	\item $\mcal{F}$ denotes the field space including \textbf{off-shell} configurations; the variation $\delta$ is assumed to be off-shell unless otherwise specified.

	\item $\tilde{\mcal{P}}$ denotes the field space including \textbf{on-shell} configurations only; one can then define a symplectic form $\omega$ on $\tilde{\mcal{P}}$, but it might be degenerate due to gauge redundancies;

	\item $\mcal{P}$ denotes the \textbf{physical phase space}, with a nice, non-degenerate sympletic structure.

	\end{itemize}
\smallskip
\textit{Differential geometry:}

	\begin{itemize}
	\item Contraction between a (poly-)vector $V$ with the \textbf{first few indices} of a form $\omega$ is denoted as:
	\begin{equation}
		V\cdot \omega = \iota_V \omega
	\end{equation}
	In differential geometry, this is more commonly referred to as the \textit{interior product} (or interior derivative, interior multiplication, etc), but there is no need for such fancy notion as it's just simple contraction.

	\item Raising and lowering indices are denoted by $\sharp$ and $\flat$ respectively; these are given the cool name of \textit{musical isomorphisms}.

	\item The Levi-Civita \textbf{symbol} is denoted as $\epsilon_{\cdots}$ with \textbf{no} $\sqrt{\abs{g}}$ factor; we will try to keep the $\sqrt{\abs{g}}$ explicit. Therefore, the Levi-Civita \textbf{tensor}, i.e.~the standard volume form, is given by:
	\begin{equation}
	\begin{aligned}
		\mrm{Vol}_M
		= \sqrt{\abs{g}} \dd[D]{x}
		&= \sqrt{\abs{g}}\, \epsilon_{\cdots}
			\dd{x^\bullet} \otimes
			\dd{x^\bullet} \otimes
			\cdots \otimes
			\dd{x^\bullet}
		= \sqrt{\abs{g}} \dd{x^1} \wedge
			\cdots \wedge \dd{x^D} \\
		&= \sqrt{\abs{g}}
			\ \frac{1}{D!}\,
			\epsilon_{\cdots}
			\dd{x^\bullet} \wedge
			\dd{x^\bullet} \wedge
			\cdots \otimes
			\dd{x^\bullet}
	\end{aligned}
	\end{equation}
	We see here that our $\mquote{\wedge}$ is defined by anti-symmetrizing $\mquote{\otimes}$ \textit{without} averaging with a $\frac{1}{D!}$ factor; the $\frac{1}{D!}$ in the second line is to cancel an \textit{additional} contraction with the $\epsilon_{\cdots}$ symbol. 
	If we raise its indices, we get:
	\begin{equation}
		(\sqrt{\abs{g}} \dd[D]{x})^{\sharp,\cdots}
		= \frac{(-1)^s}{\sqrt{\abs{g}}}\,
			\epsilon^{\cdots}
	\end{equation}
	Here $\epsilon^{\cdots}$ is still the Levi-Civita \textbf{symbol} without $\sqrt{\abs{g}}$ factor, and we have $\epsilon_{\cdots} \epsilon^{\cdots} = D!$. The $(-1)^s$ comes from signature of the metric; for $
		\eta_{ab} \sim \mop{diag}(-1,1,1,\cdots)
	$ we have $s = 1$. By the way we adopt the \textit{mostly plus} convention for Lorentzian metric, as any sane person should do; through Wick rotation it gets mapped to an \textit{all plus} Euclidean metric.

	\item Hodge dual of a $p$-form $\omega$ is defined as contraction with the volume form:
	\begin{equation}
		\hstar\omega
		= \frac{1}{p!}\,
			\omega^\sharp \cdot \mrm{Vol}_M
	\quad\Longleftrightarrow\quad
		\eta\wedge \hstar\omega
		= \aqty{\eta,\omega} \,\mrm{Vol}_M
	\end{equation}
	$\aqty{\cdot,\cdot}$ is the induced inner product on the space of $p$-forms. 
	The $\frac{1}{p!}$ factor is necessary to guarentee that $\hstar\hstar\omega = (-1)^s\cdot(-1)^{p(D-p)} \omega$. Again the $(-1)^s$ comes from signature of the metric. In particular, for a scalar $f$ and a vector $V$, we have:
	\begin{equation}
		\hstar f
		= f\sqrt{\abs{g}} \dd[D]{x},
	\quad
		\hstar\,(f\sqrt{\abs{g}} \dd[D]{x})
		= (-1)^s f,
	\quad
		\hstar V^\flat
		= V\cdot \sqrt{\abs{g}} \dd[D]{x}
	\end{equation}
	A particular useful relation is:
	\begin{equation}
		\dd{\hstar V^\flat}
		= \hstar\,(\cdv{\mu} V^\mu)
	\end{equation}
	This is derived around \eqref{eq:divergence_form}. The inner product $\aqty{\cdot,\cdot}$ is particularly convenient for 1-forms; in this case we have:
	\begin{equation}
		n \wedge\hstar j^\flat
		= n_\mu j^\mu \,\mrm{Vol}_M
	\end{equation}

	\end{itemize}
%\smallskip
\textit{Diffeomorphism and stress tensor:}

	\begin{itemize}
	\item A infinitesimal diffeomorphism (diffeo) generated by vector field $\xi$ is given by:
	\begin{equation}
		x\mapsto x - \xi = x + \var_\xi {x},
	\quad
		\var_\xi {x}
		= -\xi,
	\quad
		\var_\xi \phi
		= X_\xi \cdot \var{\phi}
		= +\ldv{\xi} \phi,
	\end{equation}
	Here the sign convention is chose such that $\var_\xi \phi$ corresponds to a positive Lie derivative along $\xi$. Note that \cite{Banados:2016zim} chose a unconventional Lie derivative which contains a minus sign in its definition; we are \textit{not} going to follow that. In this convention the usual current for spacetime translation is given by:
	\begin{equation}
		\xi = -\pdd{\sigma},
	\quad
		j^\mu_\xi = j^\mu_{-\pdd{\sigma}}
		= T^{\mu\nu} \eta_{\nu\sigma}
		= T^{\mu\nu} (\pdd{\sigma})_\nu
	\label{eq:Noether_stress_convention}
	\end{equation}
	Where $T^{\mu\nu}$ is the Noether stress tensor.

	\item Wick rotation between Lorentzian and Euclidean signatures is defined such that:
	\begin{equation}
		\tau = it,
	\quad
		V^0_E = iV^0_L,
	\quad
		(\dd[D]{x})_E
		= i\,(\dd[D]{x})_L,
	\quad
		e^{iS_L} = e^{-S_E},
	\quad
		\mcal{L}_E
		= -\mcal{L}_L
	\label{eq:Wick_rotation}
	\end{equation}
	Where $
		S = \int \dd[D]{x} \sqrt{\abs{g}}\,\mcal{L}
	$ in both cases, and $V^0$ is the 0-th component of some $V^\mu$. Other scalar quantities, such as $
		g_{\mu\nu} V^\mu W^\nu
	$, are left invariant. This is the convention introduced in \textcite{Polchinski:1998rq}, Appendix A.

	For example, the Einstein-Hilbert action is given by:
	\begin{equation}
		S_L = \frac{1}{16\pi G_N}
			\int \sqrt{-g} \dd[D]{x} R,
	\quad
		S_E = -\frac{1}{16\pi G_N}
			\int \sqrt{g} \dd[D]{x} R
	\end{equation}
	For a closed Riemann surface in 2D, by Gauss--Bonnet theorem, we see that the Euclidean action is proportional to genus of the surface:
	\begin{equation}
		S_E = -\frac{1}{16\pi G_N}\,
			4\pi \chi(M)
		= -\frac{1}{4G_N}\,\chi(M),
	\quad
		\chi(M) = 2 - 2g,
	\quad
		e^{-S_E}
		\propto e^{-\frac{1}{2G_N} g}
	\end{equation}
	Note that in \textcite{Polchinski:1998rq}, the dilaton term in the Euclidean worldsheet action  goes like $+R\,\Phi(X)$, namely it's missing the minus sign; this is due to the convention for the dilaton $\Phi$: in the perturbative regime we have $\ave{\Phi} = \lambda < 0$, and thus $
		e^{-S_E} \sim e^{-\lambda \chi}
		\sim (g_c^2)^g
	$, where $
		g_c \sim e^\lambda < 1
	$ is the closed string coupling.

	In 2D, $z,\bar{z} = x \pm i\tau = x \mp t = -u, v$, where $(u,v)$ are the lightcone coordinates. Following \textcite{Polchinski:1998rq}, the Euclidean volume form is then given by:
	\begin{equation}
		\dd{\tau} \wedge \dd{x}
		= \frac{1}{2i} \dd{z} \wedge \dd{\bar{z}}
		= \frac{1}{2} \dd[2]{z},
	\quad
		\dd[2]{z} = 2 \dd{\tau} \wedge \dd{x}
		= -i \dd{z} \wedge \dd{\bar{z}}
	\end{equation}
	The divergence theorem in complex coordinates can then be expanded as:
	\begin{equation}
		\int_R \dd[2]{z} \pdd{a} V^a
		= (-1) \oint_{\pd R}
			\dd{\ell} n_a V^a
		= (-1) \oint_{\pd R}
			V \cdot \dd[2]{z}
		= (-1)(-i) \oint_{\pd R} \pqty{
				V^z \dd{\bar{z}}
				- V^{\bar{z}} \dd{z}
			}
	\end{equation}
	The $(-1)$ factor comes from the conventional counter-clockwise contour integral $\oint_{\pd R}$ in complex \mbox{analysis}, which differs from the $\dd{\tau} \wedge \dd{x}$ orientation chosen here.

	\item The Hilbert stress tensor is defined with the Lorentzian action:
	\begin{equation}
		T_{\mu\nu}(x)
		= - \frac{2}{\sqrt{-g}}
			\fdv{S_L}{g^{\mu\nu}(x)},
	\quad
		T^{\mu\nu}(x)
		= + \frac{2}{\sqrt{-g}}
			\fdv{S_L}{g_{\mu\nu}(x)}
	\end{equation}\\[-1.25\baselineskip]
	\begin{equation}
		\var{S_L}
		= \int \sqrt{-g} \dd[D]{x} 
			\pqty{
				-\frac{1}{2}\, T_{\mu\nu}
				\var{g^{\mu\nu}}
				+ \cdots
			}
		= \int \sqrt{-g} \dd[D]{x} 
			\pqty{
				+\frac{1}{2}\, T^{\mu\nu}
				\var{g_{\mu\nu}}
				+ \cdots
			}
	\end{equation}
	To understand the variational derivative here, we note that in the space of fields it's convenient to think of $x$ as an index to be contracted; the contraction is implemented by $
		\int \dd[D]{x}
	$, without the $\sqrt{\abs{g}}$ factor.

	An action can thus be thought of as the contraction between some fields and some operators with multiple $x$ ``indices'': $\Box_{x,x',\cdots}$. For example, we might have some bi-local operator $\Box_{x,x'}$ connecting $\phi(x)$ and $\phi(x')$. 
	In a \textit{local} action all these operators should be \textit{diagonal} in $x$, i.e.~$
		\Box_{x,x'} = \delta^D(x - x')\,\Box_x
	$.

	The above definition of stress tensor agrees with \cite{Harlow:2019yfa,Compere:2018aar} and differs from \textcite{Polchinski:1998rq} (the conventional string normalization) by a factor of $(-2\pi)$. We shall see that this definition agrees with \eqref{eq:Noether_stress_convention} up to a total derivative.

	We would like the functional dependence of $
		T_{\mu\nu}
		= T_{\mu\nu}[\phi,\cdv{\mu} \phi,\cdots]
	$ to persist under Wick rotation, just like any other tensorial quantities; therefore we have to add an additional minus sign to the stress tensor computed with the Euclidean action $S_E$, due to our convention \eqref{eq:Wick_rotation}:
	\begin{equation}
		T_{\mu\nu}
		= + \frac{2}{\sqrt{g}}
			\fdv{S_E}{g^{\mu\nu}},
	\quad
		T^{\mu\nu}
		= - \frac{2}{\sqrt{g}}
			\fdv{S_E}{g_{\mu\nu}}
	\end{equation}
	For a gravitational theory (with dynamical $g_{\mu\nu}$), the \textit{total} Hilbert stress tensor is the left-hand side of the EoM, thus it vanishes on-shell. Therefore, we usually use $T_{\mu\nu}$ to denote the non-vanishing \textit{matter} stress tensor.

	\end{itemize}

\pagebreak[4]
\section{Covariant formalism and Noether's theorem}
	The phase space is understood as the space of \textit{all solutions} of the equations of motion (EoMs), satisfying the boundary conditions; alternatively, we can think of it as a collection of all possible \textit{initial configurations} of the system, and the additional \textit{symplectic structure} specifies their evolutions. This idea is best explained by \textcite{Crnkovic:1986ex}.

	Traditionally we construct the phase space variables $(\pi,\phi)$ as follows: we first pick a special time coordinate $t$, and then introduce the canonical momentum:
	\begin{equation}
		\pi = \pdv{\mcal{L}}{\dot{\phi}},
	\quad
		\dot{\phi} = \pdd{t} \phi
	\end{equation}
	Unfortunately, this procedure breaks general covariance. We would like to find a construction of phase space that respects general covariance.

	The inspiration comes from the Lagrangian treatment of field theory, where we work with:
	\begin{equation}
		\pi^\mu = \pdv{\mcal{L}}{(\pd_\mu\phi)}
	\end{equation}
	Which preserves general covariance. But $(\pi_\mu,\phi)$ is not a set of independent coordinates; they are constrained by the equations of motion (EoMs). The rough idea is that we start with $(\pi_\mu,\phi)$, and then reduce it to the independent variables $(\pi,\phi)$ by imposing the EoMs, and possibly, additional constraints due to gauge redundancy. 
\subsection{Off-shell variation on the field space}
	\noindent
	Let's start by considering a general action with boundary terms \cite{Harlow:2019yfa}:
	\begin{equation}
		S = \int_M L + \int_{\pd M} l,
	\quad
		L = \dd[D]{x} \sqrt{\abs{g}}\,\mcal{L}
	\end{equation}

	Variation $\var$ is now treated as an \textit{exterior derivative} on the space of fields. We can think of it as an \textit{enlarged} space with \textit{redundant variables} $(\pi_\mu,\phi)_I$, where $I$ labels all fields in the system. We have:
	\begin{equation}
		\var{S}
		= \int_M \var{L}
			+ \int_{\pd M} \var{l}
		= \int_M E_I \var{\phi^I}
			+ \int_{\pd M} \pqty{\Theta + \var{l}},
	\end{equation}
%	We've promoted $\phi^\mu$ to $\phi^I$ to include all fields, e.g.~the metric $g_{\mu\nu}$. 
	We've defined $\Theta$ which comes from the total derivative terms of the bulk $M$ variation, and we've performed an integration by parts and reduced $\int_M \dd{\Theta} = \int_{\pd M} \Theta$. Basically,
	\begin{empheq}{equation}
		\var{L}
		= E_I \var{\phi^I} + \dd{\Theta}
	\end{empheq}
	\vspace{-.3\baselineskip}
	\begin{equation}
		({\cdots})_I \var{(\dd{\phi^I})}
		= ({\cdots})_I \dd{(\var{\phi^I})}
		\sim \dd{(\cdots \var{\phi})}
		= \dd{\Theta},
	\quad
		\Theta \sim ({\cdots})_I \var{\phi^I}
	\end{equation}

	Here we haven't imposed the EoMs, thus $\var$ is understood as an \textbf{off-shell variation} on the space of fields. We will hence refers to the whole space including off-shell configurations as the \textbf{field space $\mcal{F}$}, and use \textbf{phase space $\mcal{P}$} for \textbf{on-shell configurations only}.

	Note that $\mcal{F}$ \textbf{includes possible ``background'' fields $\phi^B$} such as the fixed metric $g^{\mu\nu}$ for a field theory defined on a curved spacetime. These fields are fixed on-shell and therefore are absent in $\tilde{\mcal{P}}$.

	Also, we will \textit{not} distinguish phase space with $(\pi,\phi) $ coordinates and the so-called \textit{configuration space} with $(\phi,\dot{\phi})$ coordinates; though they are indeed different, they are dual to each other and related by Legendre transforms.

	What we've done here is simply a rewrite of the usual variation procedure; we just re-think it as a differential in the field space. To get to the physical phase space, we \textbf{suppress the variation of ``background'' fields $\phi^B$}, and then require the action to be \textbf{stationary, up to terms in the future / past boundary $\Sigma^\pm$:}
	\begin{empheq}{equation}
		\var{\phi^B}|_{\tilde{\mcal{P}}}
		= 0,
	\quad
		\var{S}|_{\tilde{\mcal{P}}}
		= \int_{\Sigma^+} ({\cdots})
			- \int_{\Sigma^-} ({\cdots})
		= \int_{\Sigma^\pm} ({\cdots})
	\end{empheq}
%\pagebreak[4]

	This differs slightly from what we are used to in most physics literature, where we simply set $\var{S} = 0$ to find the EoMs. The reason is that in physics, we usually impose the initial \& final conditions, or in other words, in \& out states, and the variation at $\Sigma^\pm$ is \textit{required} to vanish: $\var{\phi}|_{\Sigma^\pm} = 0$. Consider the simplest example: the (0+1)\,D worldline action of a point particle; we have:
	\begin{equation}
		S = \int L = \int \dd{t} \mcal{L},
	\quad
		\var{S}
		= \int E_I(t) \var{q^I(t)}
			+ \Theta\Big|^{\Sigma^+}_{\Sigma^-}
	\end{equation}
	\vspace{-.5\baselineskip}
	\begin{equation}
		E_I = \pqty{
			\pdv{\mcal{L}}{q^I}
			- \dv{t} \pdv{\mcal{L}}{\dot{q}^I}
		} \dd{t},
	\quad
		\Theta
		= \pdv{\mcal{L}}{\dot{q}^I} \var{q^I}
		= p_I \var{q^I},
	\quad
		p_I = \pdv{\mcal{L}}{\dot{q}^I}
	\end{equation}
	Traditionally, we impose $\var{q^I}|_{\Sigma^\pm} = 0$ as we fix the in \& out states, and then we find the EoMs $E_I = 0$. 
	However, this is slightly clumsy to implement in our new language, since $\var{\phi}$ is now a differential form in the phase space. We thus simply require that $\var{S}|_{\tilde{\mcal{P}}}$ vanish up to boundary terms at $\Sigma^\pm$, which achieve the same result.

	Generally, we have:
	\begin{equation}
		\var{\phi^B}|_{\tilde{\mcal{P}}}
		= 0,
	\quad
		\var{S}|_{\tilde{\mcal{P}}}
		= \int_{\Sigma^\pm} ({\cdots})
	\quad\Longrightarrow\quad
		E_{I\ne B}|_{\tilde{\mcal{P}}} = 0,
	\quad
		\int_N \pqty{\Theta + \var{l}}_{\tilde{\mcal{P}}}
		= \int_{\Sigma^\pm} ({\cdots}),
	\end{equation}
	\vspace{-.8\baselineskip}
	\begin{equation}
		\pd M = N \cup \Sigma^+ \cup (-\Sigma^-),
	\end{equation}
	Here $N$ is the spatial boundary. 
	In this way we've obtained the subspace (submanifold) $\tilde{\mcal{P}}$ of solutions constrained by the EoMs. We are one step closer to the physical phase space; in fact this \textit{is} the physical phase space if there are no gauge redundancies in the fields.

	Besides the EoMs, the boundary integral at $N$ should also vanish; this means that \textbf{not all boundary conditions are consistent with the theory}. 
	In fact, $N$ is where the dual theory lives for many holographic systems, so one would imagine that it's highly non-trivial. Generally \cite{Harlow:2019yfa},
	\begin{equation}
		(\Theta + \var{l})_{\tilde{\mcal{P}},N}
		= \dd{C},
	\quad
		\dd{C}\colon\ %
		\text{some 1-form on $N \subset \pd M$},
	\label{eq:boundary_cond}
	\end{equation}
	\vspace{-.8\baselineskip}
	\begin{equation}
%	\Longrightarrow\ %
		\int_{N} (\Theta + \var{l})_{\tilde{\mcal{P}}}
		= \int_{\pd M} \dd{C}
			+ ({\cdots})
		= \int_{\pd \pd M = \varnothing} C
			+ ({\cdots})
		= 0
			+ \int_{\Sigma^\pm} ({\cdots})
	\end{equation}

	\eqref{eq:boundary_cond} gives the allowed boundary conditions for the fields at $N$. A prominent example of this is the worldsheet Polyakov action for an open string with $l = 0$. Explicit calculation shows that:
	\begin{equation}
		\Theta = - \dd{\tau} \sqrt{-\gamma}\,
			\pd^\sigma X \var{X}
	\end{equation}
	up to some overall coefficients; see e.g.~\textsl{\citeauthor{Polchinski:1998rq}} \cite{Polchinski:1998rq}. Here $\phi = X$ is the field, $(\tau,\sigma)$ is the worldsheet coordinates, and $\gamma$ is the worldsheet metric. The allowed boundary conditions are given by $\var{X} = 0$ or $\pd^\sigma X = 0$, which both corresponds to $C = 0$; examples given in \cite{Harlow:2019yfa} shows that a non-trivial $C$ arises for higher derivative theories and gravity.

	By restricting to $\tilde{\mcal{P}}$, the variation $\delta|_{\tilde{\mcal{P}}}$ is understood as \textbf{on-shell}, since we've imposed the EoMs and the boundary conditions. Also, $\tilde{\mcal{P}}$ is where we actually define our symplectic structure. However, we will always try to first work with the \textbf{off-shell variation $\delta$ in the off-shell field space $\mcal{F}$}, keep the EoMs explicit, and then impose them at the very end.

	We shall see that this formalism will help us avoid confusions with boundary terms, which is best explained by \textcite{Banados:2016zim}. Also, off-shell variation will be quite useful if we want to quantize our theory, where we have to integrate over off-shell configurations as well.

%\pagebreak
\subsection{Symmetry variation and the Noether current}
	To get back to the familiar Noether's procedure, we need only plug in (contract with) a vector field $X_\xi$ in the field space $\mcal{F}$, labeled by the symmetry $\xi$:
	\begin{equation}
		\var_\xi
		= X_\xi \cdot \var
		= \iota_{X_\xi} \var
	\colon\ \Omega^0_\delta(\mcal{F})
		\to \Omega^0_\delta(\mcal{F})
	\end{equation}
	$\xi\mapsto X_\xi$ is the representation of $\xi$ in the field space, and $\Omega^0_\delta(\mcal{F})$ denotes 0-forms, i.e.~functions on $\mcal{F}$. 
	As an example, for diffeomorphism (diffeo), the induced variation is given by:
	\begin{equation}
		x\mapsto x - \xi,
	\quad
		\var_\xi \phi
		= X_\xi \cdot \var{\phi}
		= \ldv{\xi} \phi,
	\quad
		X_\xi
		= \int_M \dd[D]{x}
			\pqty\big{\ldv{\xi} \phi^I(x)}
			\fdv{\phi^I(x)}
	\label{eq:symmetry_var_field}
	\end{equation}

	We've hence defined symmetry variation $\var_\xi$ as some sort of \textit{directional derivative} on $\mcal{F}$, acting on $\Omega^0(\mcal{F})$. For its action on generic $n$-forms $\Omega^\bullet(\mcal{F})$, the more natural definition is the Lie derivative $\mscr{L}$ on the field space, along the flow of $X_\xi$:
	\begin{equation}
		\var_\xi
		= \mscr{L}_{X_\xi}
		= \iota_{X_\xi} \var + \var\circ\iota_{X_\xi}
		= X_\xi \cdot \var + \var\circ\iota_{X_\xi}
	\end{equation}
	Here we've used \textit{Cartan's magic formula} for the Lie derivative. Note that $\mscr{L}_{X_\xi}$ is the Lie derivative on the field space $\mcal{F}$, which generally differs from the Lie derivative $\ldv{\xi}$ on the spacetime $M$.

	By now we've written down the above expressions \eqref{eq:symmetry_var_field} covariantly on the off-shell field space $\mcal{F}$, in terms of the redundant coordinates $\phi^I$. However, we can still interpret it as a variation on $\tilde{\mcal{P}}$, by simple restriction. 
\pagebreak

	In fact, by the definition of a \textit{symmetry} $\xi$, we have the \textbf{off-shell symmetry variation}:
	\begin{empheq}{equation}
		\var_\xi {\phi^B}
		= 0,
	\quad
		\var_\xi S = X_\xi \cdot \var{S}
		= \int_{\Sigma^\pm} ({\cdots})
	\end{empheq}
	In other words, symmetries should act trivially on the background fields $\phi^B$, and its action in the field space is characterized by the kernel, or \textit{zero modes} (0-modes) of $\var{S}$, \textbf{again up to boundary terms at $\Sigma^\pm$}.

	The reasoning for keeping the boundary terms here is, however, different from the on-shell case, where physically we require $\var{\phi}|_{\Sigma^\pm} = 0$. Here the reason is that we generally \textbf{do allow symmetries to act no-trivially on the in and out states.} For example, time translation evolves the states at $\Sigma^\pm$, so it is natural to assume that it will lead to a boundary term at $\Sigma^\pm$. We shall see that this is indeed the case.

	Compared to the definition of $\tilde{\mcal{P}}$, namely $\var{S}|_{\tilde{\mcal{P}}}$ vanishes up to $\Sigma^\pm$ terms, we see that for a symmetry $\xi$, $X_\xi$ is always tangent to $\tilde{\mcal{P}}$, so that the restriction of the off-shell $\var_\xi \phi$ to on-shell $\tilde{\mcal{P}}$ is well-defined, as expected.

	To finally arrive at Noether's theorem, we note that:
	\begin{equation}
		\var_\xi S|_{\tilde{\mcal{P}}}
		= (X_\xi \cdot \var{S})\big|_{\tilde{\mcal{P}}}
		= X_\xi \cdot (\var{S}|_{\tilde{\mcal{P}}})
		= \int_{\Sigma^\pm} ({\cdots})
	\end{equation}
	Namely, the \textbf{on-shell symmetry variation}, which is generally \textbf{non-zero} but vanishes up to $\Sigma^\pm$ terms, can be obtained in two ways: by first computing the off-shell symmetry variation $\var_\xi S$ and then restricting it on shell, or by first computing the on-shell variation $\var{S}|_{\tilde{\mcal{P}}}$ and then inserting the symmetry. We should get the same result either way, which means that:
	\begin{equation}
		0 = X_\xi \cdot (\var{S}|_{\tilde{\mcal{P}}})
		- (X_\xi \cdot \var{S})\big|_{\tilde{\mcal{P}}}
		= \int_{\Sigma^\pm} ({\cdots})
		= \pqty{
				\int_{\Sigma^+} - \int_{\Sigma^-}
			}\, ({\cdots})
		= H_\xi^+ - H_\xi^-
	\label{eq:charge_conserve_schematic}
	\end{equation}

	We've thus obtained the conserved charge $H_\xi$ associated with $\xi$. The above arguments are a bit schematic; now let's write down the $({\cdots})$ explicitly. Let's assume that the off-shell symmetry variation is given by:
	\begin{empheq}{equation}
		\var_\xi S
		= X_\xi \cdot \var{S}
		= \int_M \dd{K_\xi}
		= \int_{\pd M} K_\xi
		= \int_{\Sigma^\pm} K_\xi,
	\quad
		\dd{K_\xi}
		= \var_\xi{L} + \dd{(\var_\xi l)}
	\label{eq:symmetry_var_action}
	\end{empheq}
	Given $\xi$, such $K_\xi$ can be explicitly computed; see \cite{Banados:2016zim,Harlow:2019yfa} for examples. The fact that we can reduce $\var_\xi S$ to an integral on $\Sigma^\pm$ means that the \textbf{symmetry $\xi$ must respect the boundary $N$; this actually leads to constraints on $\xi$} \cite{Harlow:2019yfa}. For example, not all na\"ive diffeo will keep the boundary $N$ invariant. Only those that respect the boundary will be true symmetries. 
	On the other hand, from on-shell variation, we have:
	\begin{equation}
		X_\xi \cdot (\var{S}|_{\tilde{\mcal{P}}})
		= \int_M E_I|_{\tilde{\mcal{P}}} \,\var_\xi {\phi^I}
			+ \int_{\pd M} \pqty{
				X_\xi \cdot \Theta + \var_\xi {l}
			}_{\tilde{\mcal{P}}}
		= 0 + \int_{\Sigma^\pm} \pqty{
				X_\xi \cdot \Theta + \var_\xi {l}
			},
	\end{equation}

\pagebreak[3]

	We can then define the Noether current (form) by:
	\begin{empheq}{equation}
		J_\xi = X_\xi \cdot \Theta
			+ \var_\xi {l} - K_\xi
	\end{empheq}
	With this we can re-write \eqref{eq:charge_conserve_schematic} explicitly as:
	\begin{empheq}{equation}
		0 = X_\xi \cdot (\var{S}|_{\tilde{\mcal{P}}})
		- (X_\xi \cdot \var{S})\big|_{\tilde{\mcal{P}}}
		= \int_{\Sigma^\pm} J_\xi
		= \pqty{
				\int_{\Sigma^+} - \int_{\Sigma^-}
			}\, J_\xi
		= H_\xi^+ - H_\xi^-
	\label{eq:charge_conserve_global}
	\end{empheq}

	The above derivation is a proof of the \textit{global} version of Noether's theorem, namely charge conservation from $\Sigma_-$ to $\Sigma_+$. However, there is also a \textit{local} version, namely current conservation.

	To see this, we note that we can always choose $\var_\xi \phi(x)$ to be compactly supported around some point $x_0$, by weighting it with some arbitrary, localized bump function. We can then shrink $M$ to surround the support of $\var_\xi \phi(x)$. This means that \eqref{eq:charge_conserve_global} actually holds around any point $x_0$, which further implies that $\dd{J_\xi} = 0$. This can be proven rigorously via explicit calculation; first we have:
	\begin{equation}
		\dd{J_\xi}
		= X_\xi\cdot \dd{\Theta}
			+ \dd (\var_\xi l - K_\xi)
	\label{eq:current_differential}
	\end{equation}
	$\mquote{\dd}$ does not act on $X_\xi$, since $X_\xi$ is a vector in the field space $\mcal{F}$ and the spacetime coordinate $x$ in $X_\xi$ are like contracted indices, so there is actually no spacetime dependence; see e.g.~\eqref{eq:symmetry_var_field}. To make this more explicit, we can write:
	\begin{equation}
		\Theta = \Theta[\phi,\var{\phi}],
	\quad
		\Theta_\xi
		= X_\xi \cdot \Theta
		= \Theta[\phi,\var_\xi \phi],
	\quad
		\dd{\Theta_\xi}
		= \dd{(X_\xi \cdot \Theta)}
		= X_\xi \cdot \dd{\Theta}
		= \dd{\Theta[\phi,\var_\xi \phi]}
	\end{equation}

	On the other hand, $\mquote{\dd}$ \textit{does} act on $\Theta$, since $\Theta$ is not only a field space 1-form but also a spacetime 1-form; we have $
		\dd{\Theta}
		= \var{L} - E_I \var{\phi^I}
	$ by definition. Therefore,
	\begin{empheq}{equation}
	\begin{aligned}
		\dd{J_\xi}
		&= X_\xi\cdot \dd{\Theta}
			+ \dd (\var_\xi l - K_\xi) \\
		&= \var_\xi {L} - E_I \,\var_\xi{\phi^I}
			+ \dd (\var_\xi l - K_\xi) \\
		&= - E_I \,\var_\xi{\phi^I}
			+ \pqty\big{
				\var_\xi {L} 
				+ \dd (\var_\xi l - K_\xi)
			} \\
		&= - E_I \,\var_\xi{\phi^I},
	\,\ \textsl{\footnotesize by \eqref{eq:symmetry_var_field}}
	\end{aligned}
	\end{empheq}

	We've finally arrived at the current conservation $\dd{J_\xi}|_{\tilde{\mcal{P}}} = 0$, which only holds \textbf{on-shell}. Note that the boundary term $K_\xi$ is crucial in all of the above derivations, so it cannot be dropped casually. Let's go back to the point particle example, and consider time translation $\xi = \pdd{t}$; we have:
	\begin{equation}
		\var_\xi {q^I} = \dot{q}^I,
	\quad
		X_\xi\cdot\Theta
		= p_I \,\var_\xi{q^I}
		= p_I \dot{q}^I,
	\quad
		\dd{K_\xi}
		= \var_\xi{L}
		= \dd{t}\,\var_\xi \mcal{L}
		= \dd{\mcal{L}},
	\quad
		K_\xi
		= \mcal{L}
	\end{equation}
	We see that $K_\xi$ does \textit{not} vanish, and we have precisely $K_\xi = \mcal{L}$. This leads to the conserved current (and charge) associated with $\pdd{t}$, which is precisely the \textbf{Hamiltonian:}
	\begin{equation}
		H = J_\xi
		= X_\xi \cdot \Theta - K_\xi
		= p_I \dot{q}^I - \mcal{L}
	\end{equation}
\subsection{Diffeomorphism in scalar field theory}
	A generalization of the above point particle results is to consider \textit{field theory}; we have:
	\begin{equation}
	\begin{aligned}
		\var{L}
		&= \dd[D]{x} \var{(\sqrt{\abs{g}}\,\mcal{L})} \\
		&= \dd[D]{x} \pqty{
				\sqrt{\abs{g}} \var{\mcal{L}}
				+ \var{(\sqrt{\abs{g}})} \mcal{L}
			} \\
		&= \dd[D]{x} \sqrt{\abs{g}}\,\pqty{
				\var{\mcal{L}}
				- \frac{1}{2}\,
					g_{\mu\nu} \mcal{L}
					\var{g^{\mu\nu}} \!
			} \\
	\end{aligned}
	\label{eq:Lagrangian_form_to_density}
	\end{equation}
	Here we've used the fact that $
		\var{\sqrt{\abs{g}}}
		= \sqrt{\abs{g}}\,\pqty{
			- \frac{1}{2} g_{\mu\nu} \var{g^{\mu\nu}}
		}
	$, which has the same structure as the second term in the Einstein tensor: $
		G_{\mu\nu}
		= R_{\mu\nu} - \frac{1}{2} g_{\mu\nu} R
	$. More explicitly, the measure variation can be computed with the Jacobi's formula\footnote{
		See \wikiref{https://en.wikipedia.org/wiki/Jacobi\%27s\_formula}{Jacobi's formula}. 
	}; note the minus sign when we switch from $\var{g_{\mu\nu}}$ to $\var{g^{\mu\nu}}$:
	\begin{equation}
		\var{\det g}
		= \pqty{\det g}\,g^{\mu\nu} \var{g_{\mu\nu}},
	\quad
		\var{\abs{g}}
		= \abs{g}\,g^{\mu\nu} \var{g_{\mu\nu}}
		= - \abs{g}\,g_{\mu\nu} \var{g^{\mu\nu}}
	\label{eq:measure_variation}
	\end{equation}

	Let's now restrict to scalar field $\phi$, where we have:
	\begin{equation}
		\var{\mcal{L}}
		= \pdv{\mcal{L}}{\phi} \var{\phi}
			+ \pdv{\mcal{L}}{(\cdv{\mu} \phi)}
				\var{\cdv{\mu}\phi}
	\end{equation}
	We now use the covariant derivative since it commutes with the metric, which will soon prove to be convenient. We now perform the integration by parts:
	\begin{equation}
		\pdv{\mcal{L}}{(\cdv{\mu} \phi)}
			\var{\cdv{\mu}\phi}
		= \cdv{\mu} \pqty{
				\pdv{\mcal{L}}{(\cdv{\mu} \phi)}
				\var{\phi}
			}
		- \pqty{
				\cdv{\mu}
				\pdv{\mcal{L}}{(\cdv{\mu} \phi)}
			} \var{\phi}
	\label{eq:integrate_by_parts}
	\end{equation}

	To convert the divergence into differential forms, we note that the $\mquote{\dd}$ action on the coefficents can be realized by \textbf{any torsion-free derivatives}, including the covariant derivative:
	\begin{equation}
	\begin{aligned}
		\dd{(V\cdot \sqrt{\abs{g}} \dd[D]{x})}
		&= \dd{\pqty{
			V^\mu \sqrt{\abs{g}}
			\ \frac{1}{d!}\,
			\epsilon_{\mu\mu_1\cdots\mu_d}
			\dd{x^{\mu_1}} \wedge
			\cdots \wedge \dd{x^{\mu_d}}
		}},
	\quad d = D-1 \\
		&= \cdv{\sigma} V^\mu \sqrt{\abs{g}}
			\ \frac{1}{d!}\,
			\epsilon_{\mu\mu_1\cdots\mu_d}
			\dd{x^\sigma} \wedge
			\dd{x^{\mu_1}} \wedge
			\cdots \wedge \dd{x^{\mu_d}} \\
		&= \cdv{\sigma} V^\mu \sqrt{\abs{g}}\,
			\delta^\sigma_\mu \dd[D]{x} \\
		&= \cdv{\mu} V^\mu
			\sqrt{\abs{g}} \dd[D]{x}
	\end{aligned}
	\label{eq:divergence_form}
	\end{equation}
	Here $\cdv{\sigma}$ does not act on $\sqrt{\abs{g}}$ due to metric compatibility. This fact can be conveniently re-written with Hodge dual:
	\begin{equation}
		\star \dd{(V\cdot \sqrt{\abs{g}} \dd[D]{x})}
		= \star \dd{\hstar V^\flat}
		= \sidenote{(-1)^s}\cdv{\mu} V^\mu
	\end{equation}

	With $V^\mu = \pi^\mu \var{\phi}$, $
		\pi^\mu = \pdv{\mcal{L}}{(\cdv{\mu} \phi)}
	$, we can now rephrase our familiar identity \eqref{eq:integrate_by_parts} with the new language of differential forms:
	\begin{equation}
		\sqrt{\abs{g}} \dd[D]{x} \pqty{
			\pi \cdot \var{\dd{\phi}}
		}
		= \dd \pqty\big{
				\var{\phi}
				(\hstar \pi^\flat)
			}
		- \var{\phi} \pqty\big{
				\dd{(\hstar \pi^\flat)}
			}
	\label{eq:integrate_by_parts_forms}
	\end{equation}
	In this form, the identity can be proven directly by noting that the right hand side (RHS) is simply $
		(\dd{\var{\phi}}) \wedge
		(\pi\cdot \sqrt{\abs{g}} \dd[D]{x})
	$ by Leibnitz's rule, and the left hand side (LHS) and RHS are identical since $\sqrt{\abs{g}} \dd[D]{x}$ is a top form, and thus $
		\pi \cdot \pqty{
			(\dd{\var{\phi}}) \wedge
			(\sqrt{\abs{g}} \dd[D]{x})
		}
		= \pi\cdot 0
		= 0
	$.

	Finally, we are ready to deploy Stokes' theorem for differential forms. We have:
	\begin{equation}
		E = \hstar \pdv{\mcal{L}}{\phi}
			- \dd{(\star \pi^\flat)}
		= \hstar \pqty{
				\pdv{\mcal{L}}{\phi}
				- (-1)^s \hstar \dd{\star \pi^\flat}
			}
		= \hstar \pqty{
				\pdv{\mcal{L}}{\phi}
				- \cdv{\mu}
				\pdv{\mcal{L}}{(\cdv{\mu} \phi)}
			},
	\end{equation}
	\vspace*{-.3\baselineskip}
	\begin{equation}
		\Theta = (\hstar \pi^\flat) \var{\phi}
		= \pi \var{\phi}
			\cdot \sqrt{\abs{g}} \dd[D]{x}
		= \var{\phi} \pdv{\mcal{L}}{(\nabla \phi)}
			\cdot \sqrt{\abs{g}} \dd[D]{x}
		= \theta \cdot \sqrt{\abs{g}} \dd[D]{x}
		= \hstar \theta
	\end{equation}
	As we've seen before, $\Theta$ is to be integrated along $\pd M$, so we mostly care about its projection $\Theta_{\pd M}$ along the induced volume form $\mrm{Vol}_{\pd M}$. We have\footnote{
		We've been cavaliar about the index of $n$, by treating $n$ both as a vector and as a co-vector, without raising or lowering indices using musical isomorphisms. Whether it should be a vector or a co-vector can be inferred from the context. 
	}:
	\begin{equation}
		\mrm{Vol}_{\pd M}
		= \hstar n
		= n \cdot \mrm{Vol}_M,
	\quad
		\mrm{Vol}_M
		= n\wedge \hstar n,
%		= n\wedge \mrm{Vol}_{\pd M}
%		= n\wedge (n^\sharp\cdot \mrm{Vol}_M)
	\quad
		n^2 = 1
	\end{equation}
	\vspace*{-1.2\baselineskip}
	\begin{equation}
		\Theta_{\pd M}
		= \theta\cdot n\,\mrm{Vol}_{\pd M}
		= n_\mu \theta^\mu\,
			(n\cdot \sqrt{\abs{g}} \dd[D]{x})
	\end{equation}

	Now let's consider diffeo $x\mapsto x-\xi$. We then have:
	\begin{equation}
		\var_\xi {\phi} = \xi \cdot \dd{\phi},
	\quad
		\Theta_\xi
		= X_\xi\cdot\Theta
		= \hstar \pi \,\var_\xi{\phi},
	\end{equation}
	There are various ways to compute $K_\xi$; the ``modern'' way is to work with $L$ directly, which gives:
	\begin{empheq}{equation}
		\dd{K_\xi}
		= \var_\xi{L}
		= \ldv{\xi} L
		= \dd{(\xi\cdot L)},
	\quad
		K_\xi
		= \xi\cdot L
		= \mcal{L}\,(\hstar \xi)
	\label{eq:diffeo_boundary_term}
	\end{empheq}

	We then repeat the same calculation with the ``traditional'' language, namely by plugging $\xi$ into \eqref{eq:Lagrangian_form_to_density}; using the same techniques for \eqref{eq:integrate_by_parts_forms}, we demonstrate that it indeed gives the same result:
	\begin{equation}
	\begin{aligned}
%	\textsl{\small And then,}\ \,
		\dd{K_\xi}
		&= \dd[D]{x} \sqrt{\abs{g}}\,\pqty{
				\var_\xi {\mcal{L}}
				- \frac{1}{2}\,
					g_{\mu\nu} \mcal{L}
					\,\var_\xi {g^{\mu\nu}} \!
			} \\
		&= \dd[D]{x} \sqrt{\abs{g}}\,\pqty\big{
				\xi \cdot \dd{\mcal{L}}
				+ \mcal{L} \cdv{\mu} \xi^\mu
			} \\
		&= \hstar \pqty{\xi \cdot \dd{\mcal{L}}}
			+ \mcal{L} \dd{\hstar \xi} \\
		&= \hstar \pqty{\xi \cdot \dd{\mcal{L}}}
			+ \dd{\pqty\big{
				\mcal{L}\,(\hstar \xi)
			}} - \dd{\mcal{L}} \wedge \hstar \xi \\
		&= \dd{\pqty\big{
				\mcal{L}\,(\hstar \xi)
			}}
			+ \xi \cdot \cancel{
				(\dd{\mcal{L}} \wedge \mrm{Vol}_M)
			} \\
		&= \dd{\pqty\big{
				\mcal{L}\,(\hstar \xi)
			}},
	\,\ \textsl{\small indeed}\ \,
		K_\xi = \mcal{L}\,(\hstar \xi) = \xi\cdot L
	\end{aligned}
	\end{equation}
	Here we see explicitly that \textbf{the $\var_\xi {g^{\mu\nu}}$ contribution combines with $\var_\xi {\mcal{L}}$ to give a total derivative.} This is a hint of the \textbf{diff-invariance} of the theory: if we turn on dynamical $g^{\mu\nu}$, then \textbf{any arbitrary $\xi$} (compatible with the boundary condition) is a ``symmetry'' generator of the theory\footnote{
		More precisely, only some of them generate ``true'' symmetry, while others just generate diffeo redundancies. We will come back to this in the future.
	}.

\pagebreak[4]

	On the other hand, if $g^{\mu\nu}$ is a fixed background field, then we have additional \textbf{constraints on $\xi$}, namely $\var_\xi {g^{\mu\nu}} = 0$ since $\var{g^{\mu\nu}}|_{\tilde{\mcal{P}}} \equiv 0$. 
	This is precisely the \textit{Killing equation}; $\xi$ has to be a \textit{Killing vector}, which generates some \textit{isometry} instead of arbitrary diffeo:
	\begin{equation}
		\var_\xi {g^{\mu\nu}}
		= \ldv{\xi} {g^{\mu\nu}}
		= 0
	\end{equation}

	Finally, the conserved current for diffeo in scalar field theory is given by:
	\begin{equation}
		J_\xi = \hstar \pi\,(\xi\cdot \dd{\phi})
			- \xi\cdot L
		= \hstar \pqty{
				\pi\,(\xi\cdot \dd{\phi})
				- \xi \mcal{L}
			}
		= \hstar j_\xi,
	\quad
		j_\xi^\mu = \pi^\mu\,(\xi\cdot \dd{\phi})
			- \xi^\mu \mcal{L}
	\end{equation}
	We now consider flat spacetime; the energy-momentum \textit{stress tensor} $T^{\mu\nu}$ is then found by plugging in $\xi^\mu = \sidenote{-}\delta^\mu_\nu$, i.e.~the generator of translations; note that we've included \textbf{an extra minus sign} in the definition of $T^{\mu\nu}$ for future convenience:
	\begin{equation}
		\xi = -\pdd{\sigma},
	\quad
		x^\mu \mapsto x^\mu - \xi^\mu
		= x^\mu + \delta^\mu_\sigma,
	\end{equation}
	\begin{empheq}{equation}
		T\id{^\mu_\sigma}
		\equiv j^\mu_{\sidenote{-}\pdd{\sigma}},
	\quad
		j^\mu_{-\pdd{\sigma}}
		= T^{\mu\nu} \eta_{\nu\sigma}
		= T^{\mu\nu} (\pdd{\sigma})_\nu,
	\quad
		T^{\mu\nu}
		= -\pi^\mu \pd^\nu\phi + \eta^{\mu\nu} \mcal{L}
	\label{eq:Noether_stress_tensor}
	\end{empheq}

	Note that for now $T^{\mu\nu}$ is generally \textit{not} symmetric as $\mu\leftrightarrow \nu$, and only $\mu$ is the index for $j^\mu$, while $\nu$ is an index labeling the $D$ translations.

	More explicitly, consider free scalar field in Lorentzian signature, then we have:
	\begin{equation}
		\mcal{L}
		= -\frac{1}{2}
			\cdv{\mu} \phi
			\nabla^\mu \phi,
	\quad
		T_{\mu\nu}
		= +\cdv{\mu} \phi \cdv{\nu} \phi
			+ g_{\mu\nu} \mcal{L}
	\end{equation}
	We've lowered the indices and restored the metric $g_{\mu\nu}$ for future convenience. In this case the stress tensor is symmetric by accident, but this is generally not true; one counter-example is the Noether stress tensor for QED; see e.g.~\cite{Banados:2016zim}. 
\subsection{More on charge conservation}
	\vspace{-1\baselineskip}
	\begin{empheq}{equation*}
		\textsl{\textbf{Note:} for simplicity, quantities in this sub-section are taken to be \textbf{on-shell} by default. }
	\end{empheq}

	We now define the charge on a general codim-1 $\Sigma$ by integrating the \textbf{on-shell} current:
	\begin{equation}
		H_\xi(\Sigma)
		= \int_\Sigma J_\xi,
	\quad
		J_\xi = J_\xi|_{\tilde{\mcal{P}}}
	\end{equation}
	Charge conservation is then formulated as follows: we consider a deformation of $\Sigma$ along the flow of $\alpha$, and examine its effects $\Delta_{\alpha} H_\xi(\Sigma)$; we have:
	\begin{equation}
	\begin{aligned}
		\Delta_{\alpha} H_\xi(\Sigma)
		&= \int_\Sigma
			\ldv{\alpha} J_\xi,
	\quad
		\ldv{\alpha} J_\xi
		= \dd{\pqty\big{
				\alpha \cdot J_\xi
			}}
			+ \alpha \cdot \cancel{\dd{J_\xi}}, \\
		&= \int_{\pd\Sigma}
			\alpha \cdot J_\xi,
	\quad J_\xi = \hstar j_\xi, \\
		&= \int_{\pd\Sigma}
			\alpha \cdot \pqty{\mspace{2mu}
				j_\xi \cdot \mrm{Vol}_M
			},
	\quad
		\iota_\alpha \iota_{j_\xi}
		= -\iota_{j_\xi} \iota_\alpha, \\
		&= - \int_{\pd\Sigma}
			j_\xi \cdot \pqty{\mspace{2mu}
				\alpha \cdot \mrm{Vol}_M
			},
	\end{aligned}
	\end{equation}
	\begin{empheq}{equation}
		\Delta_{\alpha} H_\xi(\Sigma)
		= - \int_{\pd\Sigma}
			j_\xi \cdot \pqty{\mspace{2mu}
				\alpha \cdot \mrm{Vol}_M
			}
	\end{empheq}

	This result is very intuitive: the change of charge $H_\xi$ on the codim-1 slice $\Sigma$ is given by the flux entering the codim-2 boundary surface $\pd\Sigma$. 
	To see this more explicitly, consider a non-vanishing $\alpha$ normal to $\Sigma$; we can then decompose the volume form along $\pd\Sigma$:
	\begin{equation}
		\alpha^2 \mrm{Vol}_M|_{\pd\Sigma}
		= \alpha\wedge n_{(\pd\Sigma)}
			\wedge \pqty{
				n_{(\pd\Sigma)}
				\cdot \alpha
				\cdot \mrm{Vol}_M
			}
		= \alpha\wedge n_{(\pd\Sigma)}
			\wedge \abs{\alpha}\,\mrm{Vol}_{\pd\Sigma},
	\quad
		n_{(\pd\Sigma)} \perp \alpha
		\perp \Sigma
	\end{equation}
	Here we do not demand that $\alpha$ has unit norm; this leads to the modified volume form $\abs{\alpha}\,\mrm{Vol}_{\pd\Sigma}$ on $\pd\Sigma$. 
%	On the other hand, for convenience, we can always choose $n_{(\pd\Sigma)}$ such that it's orthogonal to $\alpha$ along $\pd \Sigma$. 
	With such decomposition,
	\begin{equation}
	\begin{aligned}
		\Delta_{\alpha} H_\xi(\Sigma)
		&= - \int_{\pd\Sigma}
			j_\xi \cdot \pqty{\mspace{2mu}
				\alpha \cdot \mrm{Vol}_M
			} \\
		&= - \int_{\pd\Sigma}
			j_\xi \cdot \pqty{
				n_{(\pd\Sigma)} \wedge 
				\abs{\alpha}\,\mrm{Vol}_{\pd\Sigma}
			} \\
		&= - \int_{\pd\Sigma} \abs{\alpha}\,
			j_\xi \cdot n_{(\pd\Sigma)}
			\mrm{Vol}_{\pd\Sigma}
	\end{aligned}
	\end{equation}

	In particular, if $\Sigma$ is a constant time slice orthogonal to $\alpha = \pdd{t}$, then:
	\begin{equation}
		\pdd{t} \perp \Sigma,
	\quad
		\dv{t} H_\xi
		= \int_\Sigma \dv{t} J_\xi
		= - \int_\Sigma
			\pqty{\cdv{i}\,j^i_\xi}\,
			\pqty{\mspace{2mu}
				\pdd{t} \cdot \mrm{Vol}_M
			}
		= - \int_{\pd\Sigma} \abs{\pdd{t}}\,
			j_\xi \cdot n_{(\pd\Sigma)}
			\mrm{Vol}_{\pd\Sigma}
	\end{equation}
	On the other hand, if $\pd\Sigma = \varnothing$, then $\Delta_{\alpha} H_\xi(\Sigma) \equiv 0$ for any choice of $\alpha$. This means that $H_\xi(\Sigma)$ is insensitive to small deformations, i.e.~it's a codim-1 \textbf{topological operator}.

	For the free scalar field theory in flat sapcetime, with $\xi^\mu = -\delta^\mu_\nu$, we have:
	\begin{equation}
		P_\nu \equiv H_{\pd_\nu}
		= \int_\Sigma \dd[d]{x} T\id{^0_\nu},
	\quad
		T\id{^0_\nu}
		= T^{0\mu} \eta_{\mu\nu}
	\end{equation}
	The minus sign we've introduced in \eqref{eq:Noether_stress_tensor} guarantees that \textbf{the conserved charge with upper indices is the usual energy-momentum 4-vector, and $T^{0\nu}$ is precisely the energy momentum density:}
	\begin{equation}
		P^\nu = \int_\Sigma \dd[d]{x} T^{0\nu}
	\end{equation}

%	It is generally safe to assume that the integrand decays fast enough when it approaches $\Sigma^\pm$, so we can drop the contribution from $\Sigma^\pm$.

%	We can then safely assume the boundary integral vanishes at $\Sigma^\pm$, thus:
%	\begin{equation}
%		0 = \int_N \pqty{
%				X_\xi \cdot \Theta + \var_\xi {l}
%			},
%	\end{equation}

\subsection{Improvement of the stress tensor}
	We've noted above that the stress tensor obtained from the standard Noether's procedure is generally \textit{not} symmetric. In general, we can \textit{improve} the stress tensor by making use of an \textbf{ambiguity in the definition of the Noether current $J_\xi$}; note that:
	\begin{equation}
		\Theta \mapsto \Theta + \dd{Y},
	\quad
		J_\xi \mapsto J_\xi + X_\xi \cdot \dd{Y}
		= J_\xi + \dd{Y_\xi},
	\quad
		\dd{\pqty{
			J_\xi + \dd{Y_\xi}
		}} = \dd{J_\xi} = 0
	\end{equation}
	Here we've commuted $\mquote{\dd}$ past $X_\xi$, using the same arguments as in \eqref{eq:current_differential}. 
	We see that current conservation still holds if we add an arbitrary total derivative to $J_\xi$. 
	As we shall see later, this $Y$-ambiguity actually has non-trivial effects in the phase space; picking the ``canonical'' $Y$ then becomes a delicate issue.

	However, for the stress tensor $T_{\mu\nu}$ in a \textbf{diff-invariant theory}, there is a natural improvement for the current; here the \textbf{diff-invariance of a theory is \textit{defined} through \eqref{eq:diffeo_boundary_term}}: given an arbitrary vector field $\xi$, the theory is said to be diff-invariant iff.~\cite{Harlow:2019yfa,Compere:2018aar}:
	\begin{empheq}{equation}
		\var_\xi \phi^I
		= \ldv{\xi} \phi^I,
	\quad
		\var_\xi L
		= \dd{K_\xi},
	\quad
		K_\xi
		= \xi \cdot L
	\end{empheq}
	Technically we should also require that $\xi$ generates a diffeomorphism that respects the boundary conditions \cite{Harlow:2019yfa}, but we will ignore this subtlety for now.

	For a diff-invariant theory, one can then define the \textit{Hilbert stress tensor} by varying the action w.r.t.~the metric $g_{\mu\nu}$, or equivalently, the metric inverse $g^{\mu\nu}$:
	\begin{empheq}{equation}
		T_{\mu\nu}
		= - \frac{2}{\sqrt{-g}}
			\fdv{S_L}{g^{\mu\nu}},
	\quad
		\var{S_L}
		= \int \sqrt{-g} \dd[D]{x} 
			\pqty{
				-\frac{1}{2}\, T_{\mu\nu}
				\var{g^{\mu\nu}}
				+ \cdots
			}
	\end{empheq}
	Again this has the same structure as the second term in the Einstein tensor: $
		G_{\mu\nu}
		= R_{\mu\nu} - \frac{1}{2} g_{\mu\nu} R
	$. 
	Similar to \eqref{eq:measure_variation}, we have:
	\begin{empheq}{equation}
		- \frac{1}{2}\, T_{\mu\nu}
			\var{g^{\mu\nu}}
		= + \frac{1}{2}\, T^{\mu\nu}
			\var{g_{\mu\nu}},
	\quad
		T^{\mu\nu}
		= + \frac{2}{\sqrt{-g}}
			\fdv{S_L}{g_{\mu\nu}}
	\end{empheq}

	We see an immediate consequence of this definition: if the metric $g_{\mu\nu}$ in a theory is dynamical, then the EoM for $g_{\mu\nu}$ is precisely given by:
	\begin{equation}
		T_{\mu\nu} = 0
	\end{equation}
	Namely, the \textbf{\textit{total} stress tensor} must vanish. This is what happens in gravity; examples include string theory, where $T_{ab} = 0$ is the so-called \textit{Virasoro constraint} on the worldsheet, and Einstein gravity, where we have the Einstein equations:
	\begin{equation}
		0 = T_{\mu\nu}
		= T^M_{\mu\nu}
			- \frac{1}{8\pi G_N}\,G_{\mu\nu}
	\end{equation}
	Here $T^M_{\mu\nu}$ is the \textit{matter} stress tensor. We now have a new puzzle: since $T_{\mu\nu} = 0$ in gravity, how should we define the stress tensor for the gravitational field itself? As we shall see later, the covariant formalism provides a neat solution for this problem. \textbf{Also, from now on we will use $T_{\mu\nu} = T^M_{\mu\nu}$ to denote the non-vanishing \textit{matter} stress tensor.}

	\newparagraph
	On the other hand, given a fixed background $\hat{g}_{\mu\nu}$, we have another subtlety in the above definition: there could be various ways to promote $
		\hat{g}_{\mu\nu} \mapsto
		g_{\mu\nu}
	$ and vary w.r.t.\ $g_{\mu\nu}$. In particular, if $\hat{g}_{\mu\nu} = \eta_{\mu\nu}$, then the Ricci scalar $R \equiv 0$, thus any term that is proportional to $R$ can be added to the action without spoiling the diff-invariance.

\pagebreak[4]

	One can think of this process as \textit{turning on} a dynamic $g_{\mu\nu}$ field coupled to the matter theory; there is the usual \textbf{minimal coupling}, i.e.~we replace $\eta_{\mu\nu} \mapsto g_{\mu\nu}$, $\pdd{\mu} \mapsto \cdv{\mu}$, and then compute the variation. However, we can introduce additional couplings between the matter fields and $g_{\mu\nu}$, e.g.~the dilaton coupling \cite{Polchinski:1998rq}:
	\begin{equation}
		S \propto \int
			\sqrt{\abs{g}} \dd[D]{x}
			R\,\Phi[\phi^I]
	\end{equation}
	Where the dilaton $\Phi = \Phi[\phi^I]$ is a functional of the fields. This term vanishes in flat space, yet it contributes extra improvement terms to the stress tensor. This is an example of \textit{non-minimal} coupling.

	\newparagraph
	To understand the equivalence of the Hilbert stress tensor with the Noether stress tensor, we shall revisit the idea that \textbf{Noether's theorem is in fact a local statement,} even when the symmetries involved are global symmetries. 
\subsection{Noether current from ``localized'' variation}
	As we've noted before, we can always choose $\var_\eta \phi(x)$ to be compactly supported around some point $x_0$, by weighting it with some arbitrary, localized bump function $\epsilon(x)$. One can think of this as promoting\footnote{
		This process is described in \textcite{Polchinski:1998rq}, Section 2.3 and Exercise 2.5, and a solution of this exercise is given by \cite{Headrick:2008ke}. We will reproduce the solution here with the language of differential forms.
	}:
	\begin{equation}
		\var_\xi \phi
		\mapsto \var_\eta \phi
		= \epsilon(x)\,\var_\xi \phi,
	\quad\text{i.e.}\ \,
		X_\xi \cdot \var{\phi}
		\mapsto X_\eta \cdot \var{\phi}
		= \epsilon(x)\,X_\xi \cdot \var{\phi}
	\end{equation}
	Here we are considering general $\xi,\eta$ which act locally on the fields; they don't have to be diffeos for this to hold.

	We see that \textbf{when contracted with $\var{\phi}$, we can simply replace $
		X_\eta \mapsto \epsilon(x)\,X_\xi
	$}. \textbf{However, note that this does \textit{not} imply that $
		X_\eta = \epsilon(x)\, X_\xi 
	$}, nor does it work for contractions with general variations such as $\var{L}$. In fact, $X_\eta$ is a flow in the field space $\mcal{F}$, so it should not have explicit dependence on the $x$ coordinate; see e.g.~\eqref{eq:symmetry_var_field}. By definition, the correct form of $X_\eta$ should be:
	\begin{equation}
		X_\eta
		= \int_M \dd[D]{x}
			\epsilon(x)\,
			\pqty\big{
				X_\xi \cdot \var{\phi^I(x)}
			}
			\fdv{\phi^I(x)}
	\end{equation}
%	
	We then look at the variation $\var_\eta L$; by definition,
	\begin{equation}
	\begin{aligned}
		\var_\eta L
		&= X_\eta \cdot \var{L} \\
		&= \epsilon\,E_I\,\var_\xi {\phi^I}
			+ \dd{(X_\eta \cdot \Theta)} \\
		&= \epsilon\,E_I\,\var_\xi {\phi^I}
			+ \dd{\pqty{
				\epsilon(x)\, X_\xi \cdot \Theta
			}} \\
		&= \epsilon\,E_I\,\var_\xi {\phi^I}
			+ \epsilon \dd{(X_\xi \cdot \Theta)}
			+ (\dd{\epsilon}) \wedge
				X_\xi \cdot \Theta \\
		&= \epsilon\,\var_\xi L
			+ (\dd{\epsilon}) \wedge
				X_\xi \cdot \Theta \\
	\end{aligned}
	\end{equation}
	On the other hand, we know that $\var_\xi L$ is a symmetry variation: $\var_\xi L = \dd{(K_\xi - \var_\xi l)}$; we thus have:
	\begin{empheq}{equation}
	\begin{aligned}
		\var_\eta L
		&= \epsilon\,\var_\xi L
			+ (\dd{\epsilon}) \wedge
				X_\xi \cdot \Theta \\
		&= \epsilon \dd{(K_\xi - \var_\xi l)}
			+ (\dd{\epsilon}) \wedge
				X_\xi \cdot \Theta \\
		&= \dd{\pqty\big{
				\epsilon(K_\xi - \var_\xi l)
			}} 
			+ (\dd{\epsilon}) \wedge \pqty{
				X_\xi \cdot \Theta
				+ \var_\xi l - K_\xi
			} \\
		&= \dd{\pqty\big{
				\epsilon(K_\xi - \var_\xi l)
			}} 
			+ (\dd{\epsilon}) \wedge J_\xi
	\end{aligned}
	\end{empheq}

	We see that we've recovered the Noether current $J_\xi$ with this formalism. 
	Our calculation thus far has been \textbf{off-shell;} we see that while $\xi$ is a symmetry by construction: $
		\var_\xi L = \dd{(K_\xi - \var_\xi l)}
	$, \textbf{$\eta$~is generally \textit{not} a symmetry of the action:} by definition, we require an \textbf{off-shell} symmetry variation of the action to be a total derivative; this is not the case for $\var_\eta L$, as we have an extra term $
		(\dd{\epsilon}) \wedge J_\xi
	$ which does \textit{not} vanish \textit{off-shell}.

	We can integrate by parts once more and get:
	\begin{empheq}{equation}
	\begin{aligned}
		\var_\eta L
		&= \dd{\pqty\big{
				\epsilon(K_\xi - \var_\xi l)
			}} 
			+ (\dd{\epsilon}) \wedge J_\xi \\
		&= \dd{\pqty\big{
				\epsilon X_\xi \cdot \Theta
			}} 
			- \epsilon \dd{J_\xi} \\
		&= \dd{\Theta_\eta} 
			- \epsilon \dd{J_\xi}
	\end{aligned}
	\end{empheq}
	Current conservation follows from the fact that since we pick $\epsilon(x)$ to be compactly supported around some point $x_0$, the \textbf{on-shell variation} of the action vanishes completely, as long as $\pd M$ encloses the support of $\epsilon(x)$; his holds for \textit{arbitrary} $\epsilon(x)$ supported within $M$, which guarantees that $\dd{J_\xi}|_{\tilde{\mcal{P}}} = 0$:
	\begin{empheq}{equation}
	\begin{aligned}
		0 = \var_\eta S|_{\tilde{\mcal{P}}}
		= \int_M \var_\eta L|_{\tilde{\mcal{P}}}
		&= \cancel{
			\int_{\pd M} \epsilon(x)\,
				X_\xi \cdot \Theta|_{\tilde{\mcal{P}}}
			}
			- \int_M \epsilon(x) \wedge
				\dd{J_\xi}|_{\tilde{\mcal{P}}},
	\quad
		\dd{J_\xi}|_{\tilde{\mcal{P}}} = 0
		\mspace{-16mu}
	\end{aligned}
	\end{empheq}

	The on-shell condition is necessary to guarantee that $
		\var_\eta S|_{\tilde{\mcal{P}}} = 0
	$, and any possible boundary terms at $\Sigma^\pm$ vanishes since it's weighted by $\epsilon(x)$. Alternatively, we can see this locally by noting that:
	\begin{equation}
		\dd{\Theta_\eta}
			+ \epsilon\, E_I \,\var_\xi \phi^I
		= \var_\eta L
		= \dd{\Theta_\eta} 
			- \epsilon \dd{J_\xi}
	\end{equation}
	We see that the boundary term $\dd{\Theta_\eta}$ actually cancels between the left and right-hand side, therefore even we choose some $\epsilon(x)$ which does not vanish along $\pd M$, we still have $
		\dd{J_\xi} = -E_I \,\var_\xi \phi^I
	$ which vanishes on-shell, as we've seen before.

	\newparagraph
	This formalism of promoting $
		\var_\xi \phi
		\mapsto \var_\eta \phi
	$ suggests a convenient method of finding the Noether current $J_\xi$, without worrying about the boundary term $K_\xi$; we need only compute $\var_\eta L$, ignore the total derivatives, and collect the factors of $\dd{\epsilon}$, which will automatically include $K_\xi$ contributions and give us a conserved $J_\xi$. There will still be ambiguities as one can shift $\Theta$ by a total derivative $\dd{Y}$, as we've seen before.

%\legacyReference

%	\begin{figure}[!ht]
%	\centering
%%	\includegraphics[width=.6\linewidth]{img/}
%%	\hspace{2em}
%%	\vspace{-2ex}
%	\caption[]{}
%	\end{figure}

\vspace{1.2\baselineskip}
\pagebreak[4]
\raggedright
\printbibliography[%
%	title = {参考文献} %
	,heading = bibintoc
]
\end{document}

### 2021-05-09 Strings2020/strings1/strings1.tex
Add minor tweaks to various notes

@@
 	$; by setting $\epsilon = \epsilon(z)$, we get \textit{a} energy momentum tensor\footnote{
-		Note that the energy momentum tensor obtained in this way is generally \textit{not} unique: it can be off by a boundary term; see Luboš' comment at \https{physics.stackexchange.com/a/96100}, also \arxiv{1601.03616}.
+		Note that the energy momentum tensor obtained in this way is generally \textit{not} unique: it can be off by a boundary term or any term that vanish on-shell; see Luboš' comment at \https{physics.stackexchange.com/a/96100}, also \arxiv{1601.03616}.
 However, it is possible to fix this redundancy by considering $Tb$ OPE and match its conformal dimension.

### 2021-05-09 alpha/Exam/exam.tex
Add minor tweaks to various notes

@@
 	\end{equation}
-	Here $\frac{1}{2}$ is the symmetry factor of the diagram; alternative, we can count the distinct ways of connection the 4 legs of the $\phi^4$ vertex and divide it by $4!$, which is indeed $
+	Here $\frac{1}{2}$ is the symmetry factor of the diagram; alternative, we can count the distinct ways of connecting the 4 legs of the $\phi^4$ vertex and divide it by $4!$, which is indeed $
 		\frac{4\times 3}{4!} = \frac{1}{2}

### 2021-05-16 alpha/GravitationalEntropy/entropy.tex
Update note on gravitational entropy

@@
 	\end{equation}
-\subsubsection{RT surface}
+\subsubsection{The usual RT surface}
 	The Einstein frame metric $G_{\mu\nu}$ is related to the string frame metric $g_{\mu\nu}$ by:
@@
 
-	The coordinate length $L$ at the boundary is given by:
+	The coordinate length $L_\mrm{RT}$ at the boundary is given by:
 	\begin{equation}
 	\begin{aligned}
-	  L = L(z_0;\mu)
+	  L_\mrm{RT} = L_\mrm{RT}(z_0;\lambda)
 	  &= \int \dd{\varphi}
@@
 	\end{equation}
-
-\pagebreak\noindent
+%	
+%\pagebreak\noindent
 	Note that:
 	\begin{itemize}
-	\item $\mu\to 0,\, L(z_0;\mu) \to 2z_0$, we recover the AdS result: in this case the geodesic $\gamma$ is a semi-circle with radius $z_0$.
+	\item $\lambda\to 0$, \textsl{or} $z_0\to \infty$, we have $L_\mrm{RT}(z_0;\lambda) \to 2z_0$, i.e.~we recover the AdS result: in this case the geodesic $\gamma$ is a semi-circle with radius $z_0$.
 
 	\item $z_0\to 0,\,
-		L(z_0;\mu) \to \sqrt{\frac{\pi^2}{2} \lambda}
-	$, we see that $L$ is bounded from below by:
-	\begin{equation}
-		L_{\min} (\mu)
+		L_\mrm{RT}(z_0;\lambda) \to \sqrt{\frac{\pi^2}{2} \lambda}
+	$, we see that $L_\mrm{RT}$ seems to be bounded from below by:
+	\begin{equation}
+		L_{\mrm{RT},0} (\lambda)
 		= \sqrt{\frac{\pi^2}{2} \lambda}
@@
 	\begin{equation}
-		L_{\min} / L_0 = \pi / 4
+		L_{\mrm{RT},0} / L_0 = \pi / 4
 	\end{equation}
@@
 	\end{aligned}
-	\end{equation}
-	We don't have an explicit analytic result for the above integral, but numerical calculations suggest that it does not agree with \eqref{eq:tst_ft_ee}. 
-	As is inspired by the cutoff picture, we would like to tweak it such that it matches with \eqref{eq:tst_ft_ee}.
-
-	We have the following observations: 
+	\label{eq:RT_integral}
+	\end{equation}
+	We don't have an explicit analytic result for the above integral\footnote{
+		Note that there are some analytic expressions given by \cite{Asrat:2019end}, but we haven't confirmed their results. 
+		We can map \cite{Asrat:2019end} to our convention by matching the aysmptotic behavior of $L_\mrm{RT}$; namely, we have $z_0 \to \infty$, $L_\mrm{RT}(z_0;\lambda)\to 2z_0$, while $z_0 \to 0$, $L_\mrm{RT}(z_0;\lambda)\to \sqrt{\frac{\pi^2}{2} \lambda}$.
+It seems that for (3.17) and (4.3) in \cite{Asrat:2019end}, we have $
+			\alpha \mapsto \frac{\lambda/2}{z^2}
+		$.
+With this the length $L_\mrm{RT}$ given by \cite{Asrat:2019end} as a function of $z$ is \textit{not} monotonic, which sounds suspicious and does not agree with numerical results.
+\label{foot:asrat_matching}
+	},
+	but numerical calculations suggest that it does not agree with \eqref{eq:tst_ft_ee}.
+\sidenote{However, its qualitative behavior is quite close to \eqref{eq:tst_ft_ee}, and it fits \eqref{eq:tst_ft_ee} nicely as $L\to \infty$.
+}
+
+\pagebreak[3]
+
+	As is inspired by the cutoff picture, we would like to tweak the holographic entropy such that it matches with \eqref{eq:tst_ft_ee}. 
+	We start with the following observations: 
 	\begin{itemize}
@@
 		C(L')
-		= \frac{L'}{L_{\mrm{CFT}}}
-		= \frac{1}{\sqrt{1 - (\frac{L_0}{L'})^2}},
+		= \frac{1}{\sqrt{1 - (\frac{L_0}{L'})^2}}
+		= \frac{L'}{L_{\mrm{CFT}}},
 	\quad L_0 = \sqrt{8\lambda}
@@
 	Where the relation $C(L') = \frac{L'}{L_{\mrm{CFT}}}$ is completely analogous to the double-trace situation; in that case we have $L_\mrm{CFT} = L_\infty$.
+
+	\pagebreak[3]
+
+	\item Maybe one can ``engineer'' a suitable curve $\gamma'$ which has peak $z_0$ and boundary length $
+		L' = 2\sqrt{z_0^2 + 2\lambda}
+	$; we can require that it reproduces the desired entanglement entropy \eqref{eq:tst_ft_ee}:
+	\begin{equation}
+		\frac{1}{2G} \mop{arccosh}
+			\frac{
+				\sqrt{z_0^2 + 2\lambda}
+			}{\sqrt{2\lambda}}
+	  = \frac{1}{2G} \int_0^{z_0} \dd{z}
+	    \frac{z^2 + 2\lambda}{z^2}
+	      \sqrt{
+	          \frac{1}{z^2}
+	          + \frac{1}{z^2 + 2\lambda}
+	          \pqty{\dv{\varphi}{z}}^{\!\!2}
+	      } 
+	\end{equation}
+	This is a integral equation for $\dv{\varphi}{z} \equiv F$. The above equation can be greatly simplified by:
+	\begin{equation}
+		z = \sqrt{2\lambda} \sinh y,
+	\quad
+		F(y;y_0,\lambda)
+		= \abs{\dv{\varphi}{z}},
+	\end{equation}
+	\begin{empheq}{equation}
+		y_0
+		= \int_0^{y_0} \dd{y}
+			\coth^2 y\,\sqrt{
+				\coth^2 y
+				+ F^2(y;y_0,\lambda)
+			}
+	\end{empheq}
+
+	$z_0$ or $y_0$ labels the peak of $\gamma$, thus we have:
+	\begin{empheq}{equation}
+		F(y\to y_0;y_0,\lambda) \to \infty
+	\end{empheq}
+	Also the boundary length should be:
+	\begin{gather}
+	  L' = 2\sqrt{z_0^2 + 2\lambda}
+	  = 2\int_0^{z_0}
+	      \abs{\dv{\varphi}{z}}
+	      \dd{z},
+	\end{gather}
+	\begin{empheq}{equation}
+		\cosh y_0
+		= \int_0^{y_0}
+			F(y;y_0,\lambda) \cosh y \dd{y}
+	\end{empheq}
+
+	In principle one might be able to find some candidate $F = F(y;y_0,\lambda)$ from the boxed equations. This corresponds to candidate curve $\gamma'$ that reproduces the desired entropy.
+
+	\item There is a $B$-field in the TsT background; however, as is argued in \texttt{areaTTbar.pdf}, it should not contribute to the on-shell action.
+However, one might be able to promote the original $\gamma_\mrm{RT}$ to a tube surrounding $\gamma_\mrm{RT}$, and treat it as a string worldsheet, where the $B$-field couples nicely in the worldsheet action.
+
+	There are two ways going forward: one is to compute the string EoMs which is related to the \textit{string frame} geodesic; this is done in \texttt{notesEETTbar.pdf} and to be discussed in the next section.
+
+	\sidenote{Another way is to come up with a procedure that reduces the string action to a particle action close to $S_{\mrm{RT}}$, but with $B$-field corrections.
+One can also construct a new connection with $H = \dd{B}$ and solve the geodesic with this new connection\footnote{
+		Thank Yuan Zhong for this great idea. Also he helped a lot with simplying the integral equations. 
+	}. }
 
@@
 
-	\item Therefore, we have:
+	However, if we use the analytic result of \cite{Asrat:2019end} (see footnote \ref{foot:asrat_matching}), then this is \textit{not} correct!
+But one should check that result first to see if it's valid first.
+	\sidenote{Also,} if we take the $z_0$ derivative before integrating in \eqref{eq:RT_integral}, we can show that indeed we have, approximately, $
+		z_0\,\pdv{z_0}\,S_\mrm{RT}
+		\approx \frac{1}{2G}
+	$, but the result is \sidenote{\textit{not} exactly constant and \textit{not} $\lambda$ independent;} see \texttt{zDzNonConstant.nb}.
+
+\pagebreak[3]
+
+	If we proceed anyways with $
+		z_0\,\pdv{z_0}\,S_\mrm{RT}
+		\approx \frac{1}{2G}
+	$, then we have:
 	\begin{equation}
@@
 			\frac{L'}{L_\mrm{CFT}}
-		\sim \frac{1}{2G}
+		\approx \frac{1}{2G}
 			\pqty{\frac{L'}{L_\mrm{CFT}}}^{\!\!2}
@@
 			}
-		$. What's happening? I have no idea.
+		$. What's happening? I have no idea. \sidenote{Update: it seems that this only holds approximately, perhaps it's simply a numerical coincidence. }
 	}
 	\end{figure}
+\subsubsection{The TsT deformed geodesic}
+	If we take the usual geodesic (semi-circle) in the undeformed background, and consider a TsT transformation, we get the TsT deformed geodesic $\gamma_\mrm{TsT}$.
+This also coincides with the \textit{string frame} geodesic, which minimizes the string frame length without the dilaton factor, instead of the Einstein frame length.
+See \texttt{notesEETTbar.pdf} for a description of this process.
+
+	However, the on-shell action should still be the Einstein frame length; fortunately, this time the result is nice and clean:
+	\begin{equation}
+		S_E[\gamma_\mrm{TsT}(z0;\epsilon)]
+		= \frac{1}{2}
+			\frac{\sqrt{z_0^2 + 2\lambda}}{z_0}
+			\pqty{
+				\frac{\lambda}{\epsilon^2}
+				\frac{\sqrt{z_0^2 - \epsilon^2}}{z_0}
+				+ \frac{z_0^2 + \lambda}{z_0^2}
+				\mop{arctanh}
+					\frac{\sqrt{z_0^2 - \epsilon^2}}{z_0}
+			}
+	\end{equation}
+	Unfortunately, the result is highly divergent: $\sim \frac{1}{\epsilon^2}$, even worse than the $\log \frac{1}{\epsilon}$ divergence of a CFT. 
+	\sidenote{It might be possible to "renormalize" out the $\sim \frac{1}{\epsilon^2}$ divergence} which might also help us recover a more reasonable on-shell action.
 

### 2021-05-20 alpha/CutoffModularFlow/cutoffModular-alpha.tex
Add notes on cutoff modular flow

--- 2021-04-08 alpha/GravitationalEntropy/entropy.tex
@@
-% !TeX document-id = {b5392a94-51a3-49d1-9ba5-698bc09f9d35}
-% !TeX encoding = UTF-8
-% !TeX spellcheck = en_US
-% !TeX TXS-program:bibliography = biber -l zh__pinyin --output-safechars %
+% !TeX TS-program = pdflatex
+% !BIB TS-program = biblatex
 
-\documentclass[a4paper
-	,10pt
-%	,twoside
-]{article}
+\documentclass[11pt,a4paper]{article}
+\pdfoutput=1
 
-\input{../preamble.tex}
-\input{../.modules/basics/biblatex.tex}
+\input{preamble.tex}
 
-\title{Notes on Gravitational Entropy}
-\addbibresource{entropy.bib}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-%%% ID: sensitive, do NOT publish!
-\InputIfFileExists{id.tex}{}{}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\title{Modular flow and holographic entanglement entropy in cutoff AdS} 
+\author[a]{The EE $T\bar{T}$ Project}
+%\author[a]{Luis Apolo,} 
+%\author[a]{Pengxiang Hao,} 
+%\author[a]{Wen-Xin Lai,}
+%\author[a]{and Wei Song}
 
-\makeatletter
-\newcommand{\nobeginpar}{\@beginparpenalty=10000}
-\makeatother
+\affiliation[a]{Yau Mathematical Sciences Center, Tsinghua University, Beijing 100084, China}
 
+%  \emailAdd{apolo@mail.tsinghua.edu.cn, wsong2014@mail.tsinghua.edu.cn}
+
+\abstract{
+	\begin{itemize}
+
+	\item[] In Section 1,
+
+	\item We follow the recipe from the swing surface proposal \cite{Apolo:2020bld,Apolo:2020qjm} to extend the boundary modular flow to the bulk, by matching symmetries of the bulk and the boundary.
+This reproduces known results in e.g.~\cite{Lashkari:2016idm,Czech:2019vih,Apolo:2020qjm} \sidenote{[more citations needed]}.
+We first compute everything in Poincar\'e $\mrm{AdS}_3$ for simplicity.
+
+	\item We look at the flow at constant cutoff $z = z_c$, which has non-trivial $\pdd{z}$ component, which in turn leads to a violation of the $2\pi$ periodicity for $\xi$ along the horizon.
+This could be related to the violation of boosted strong subadditivity (boosted SSA) in \cite{Lewkowycz:2019xse}.
+
+	\item We then note that the periodicity can be restored by following the flow of $\xi$ starting from a codim-2 cutoff surface.
+This could be related to the \textit{restricted maximin} proposal of \cite{Marolf:2019bgj,Grado-White:2020wlb}.
+
+	\item We try to obtain the entanglement entropy using the modular flow at the \mbox{codim-2} cutoff surface, by defining a \textit{local entanglement entropy $\beta(x)$}, which relates the entanglement entropy to some thermal entropy.
+
+	\item[] In Section 2,
+
+	\item We map the the modular flow in the Poincar\'e $\mrm{AdS}_3$ vacuum to the BTZ background, and compute the entanglement entropy as gravitational charge.
+
+	\item We then consider constant $r$ cutoff in the Schwarzschild coordinates, which corresponds to the proposal of \cite{McGough:2016lol}.
+This gives a finite temperature generalization of the result of \cite{Lewkowycz:2019xse}.
+
+	\end{itemize}
+}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{document}
 \maketitle
-\pagenumbering{arabic}
-\thispagestyle{empty}
+%\flushbottom
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-%\vspace*{-.5\baselineskip}
-
-\setlength{\parskip}{.1\baselineskip}
-\tableofcontents
-\setlength{\parskip}{\parskipnorm}
+\setlength{\parskip}{.5\baselineskip}
 
@@
 \section{Conventions}
-	We try to follow the conventions of the TsT paper: \textcite{Apolo:2019zai}. 
+	We try to follow the conventions of the TsT paper \textcite{Apolo:2019zai}. 
 	\begin{itemize}
@@
 			X^I \sim (x^\mu,z) \sim (t,x,z) \sim (u,v,z)
-		$, metric: $
-			\dd{s}^2 = \frac{+\dd{u} \dd{v} + \dd{z}^2}{z^2}
-		$. Note the \mquote{+} before $\dd{u} \dd{v}$. 
+		$, metric: 
+	\begin{equation}
+		\dd{s}^2
+		= \frac{+\dd{u} \dd{v} + \dd{z}^2}{z^2}
+	\end{equation}
+	Note the \mquote{+} before $\dd{u} \dd{v}$.
+
+	\item The $T\bar{T}$ deformation is parametrized by the deformation parameter $\mu$ with mass dimension $(-2)$, defined in \cite{Apolo:2019zai}; sometimes it is more convenient to use the dimensionless \textit{worldsheet} deformation parameter $\lambda = \mu/\ell_s^2$, where $\ell_s$ is the string length.
+See \cite{Apolo:2019zai} section 2.3 and its (2.43).
+
+	\item Coordinate length of the boundary interval $\mcal{A}$ at the asymptotic infinity is denoted as $L_\infty$; the coordinate length at finite cutoff is denoted as $L$.
+For an interval lying on the constant time slice $t = 0$ in the Poincar\'e patch, we have $L = \Delta x$; for a boosted interval, we have $
+		L = \eta_{\mu\nu}\, \Delta x^\mu\, \Delta x^\nu
+	$. 
 	\end{itemize}
 
-\pagebreak[4]
-\section{Entanglement Entropy as Thermal Entropy}
-	Ref: \textcite{Apolo:2020qjm}.
+\pagebreak
 
-	A boundary interval $\mcal{A} \Leftrightarrow \rho_\mcal{A} = e^{-\mcal{H}_\mcal{A}}$.
-$\mcal{H}_\mcal{A}$ is generically nonlocal, but in a highly symmetric background (e.g.~vacuum) it might be geometrically realized and corresponds to a symmetry of the underlying quantum field theory.
-	In this case there is a generalized Rindler transformation $f$ that maps the casual $\mcal{D} \to \{(\tau,\tilde{x})\}$ in some noncompact generalized Rindler spacetime, with $\pdd{\tau}$ an isometry of the spacetime.
+\section{Modular flow in the Poincar\'e patch}
+
+\subsection{Review of the general recipe}
+	A boundary interval $\mcal{A}$ defines a denisty matrix $\rho_\mcal{A} = \tr_{\bar{\mcal{A}}} \rho = e^{-\mcal{H}_\mcal{A}}$.
+$\mcal{H}_\mcal{A}$ is generically nonlocal, but in a highly symmetric background (e.g.~AdS vacuum) it might be geometrically realized and corresponds to a symmetry of the underlying quantum field theory.
+This is the modular flow $\xi$.
+
+	In such case there is a generalized Rindler transformation $f$ that maps the casual domain $\mcal{D}$ to a patch $\{(\tau,\tilde{x})\}$ in some noncompact generalized Rindler spacetime, with $\pdd{\tau}$ an isometry of the spacetime.
 Then we have:
@@
 	\end{equation}
-	$H_i$: symmetry generators.
-The causal domain of dependence $\mcal{D}\to$ some thermal state with normalized inverse temperature $2\pi$.
+	Here $H_i$ are the symmetry generators.
+The causal domain of dependence $\mcal{D}$ is mapped to some thermal state with normalized inverse temperature $2\pi$.
 Here we choose to absorb such $2\pi$ into the definition of $\xi$, so the Euclidean periodicity w.r.t.~$\xi$ is simply $\beta_\xi = 1 = \frac{1}{T_\xi}$, which means the surface gravity along the horizon is given by $\kappa_\xi = 2\pi T_\xi = 2\pi$.
-\subsection{Exercise: Poincar\'e $\mrm{AdS}_3/\mrm{CFT}_2$}
-	We illustrate the above ideas in Poincar\'e $\mrm{AdS}_3$ vacuum, which is the simplest situation and can be easily compared with the results of \textcite{Lewkowycz:2019xse}. 
-\subsubsection{Bulk / boundary Killings}
+
+\pagebreak
+
+\subsection{Modular flow for Poincar\'e $\mrm{AdS}_3/\mrm{CFT}_2$}
+
+\textbf{Summary:} We follow the recipe from the swing surface proposal \cite{Apolo:2020bld,Apolo:2020qjm} to extend the boundary modular flow to the bulk, by matching symmetries of the bulk and the boundary.
+This reproduce known results such as \cite{Lashkari:2016idm,Czech:2019vih,Apolo:2020qjm} [more citations needed].
+
+\noindent\textbf{Mathematica:} \texttt{modFlowPoincare.nb}
+
+\subsubsection{Matching bulk and boundary symmetries}
 	In Poincar\'e $\mrm{AdS}_3/\mrm{CFT}_2$, the $H_i$'s are given by $L_n,\bar{L}_n$ with $n=0,\pm 1$. At $z\to 0$ we recover the usual global $\mfrak{sl}(2,\mbb{R})$ generators:
@@
 	\end{equation}
-	Q: Why we only include the global generators on the field theory side? A: These are the symmetries of the Poincar\'e vacuum.
-
-	One could argue that $L_{n>1}$ still annihilates the vacuum $\ket{0}$, however we should actually consider all possible correlations w.r.t.~$\ket{0}$, and require that they remain unchanged under variation of $\ket{0}$.
-This means that:
-	\begin{equation}
-		0 = \bqty{\rho,L_n}
-		= \bqty\Big{\dyad{0},L_n}
-	\end{equation}
-	Note that $L^\dagger_n = L_{-n}$, we thus have the restriction that $n = 0,\pm 1$.
 
@@
 	\end{equation}
-	By requiring that a linear combination of these generators reduce to the boundary $L_n$'s, one can uniquely extend the $L_n,\bar{L}_n$'s into the bulk; see \texttt{modFlowPoincare.nb}.
+	By requiring that a linear combination of these generators reduce to the boundary $L_n$'s, one can uniquely extend the $L_n,\bar{L}_n$'s into the bulk.
 The result for $L_n$'s is listed below; for $\bar{L}_n$ one need only exchange all $u\leftrightarrow v$.
@@
 	\end{equation}
-\subsubsection{Bulk modular flow}
-	The RT surface (spacelike geodesic of Poincar\'e AdS with both ends attached to the boundary) is parametrized in terms of its end points $(t,x)_\pm$; it's the intersection of a ``sphere'' (hyperboloid) and a plane through its center:
+
+\subsubsection{RT surface and the modular flow}
+
+\textbf{Derivation of RT surface:} \\
+ \url{https://bryango.github.io/resources/archive/HW-Gravity/gravity1.pdf}.
+
+	The RT surface (spacelike geodesic of Poincar\'e AdS with both ends attached to the boundary) is parametrized in terms of its end points $(t,x)_\pm$; it's the intersection of a AdS ``sphere'' (hyperboloid) and a plane through its center:
 	\begin{equation}
-	\text{``sphere'':}\quad
+	\text{``sphere'':}\quad\mathsmaller{
 		z^2
@@
 		- \pqty{t - \frac{t_+ + t_-}{2}}^{\!\!2}
-		= \pqty{\frac{L}{2}}^{\!\!2}
+		= \pqty{\frac{L_\infty}{2}}^{\!\!2}
 		= \pqty{\frac{x_+ - x_-}{2}}^{\!\!2}
 		- \pqty{\frac{t_+ - t_-}{2}}^{\!\!2}
+	}
 	\end{equation}
@@
 	\end{equation}
-	See \href{https://bryango.github.io/resources/archive/HW-Gravity/gravity1.pdf}{\textsl{this homework}}\footnote{
-		URL: \https{bryango.github.io/resources/archive/HW-Gravity/gravity1.pdf}. 
-	} for a detailed derivation. 
 	Alternatively, it can be more compactly rewritten with $x^\mu \sim (t,x)$ or $(u,v)$; mind the various $\pm$ signs in the above expressions: 
@@
 
-\subsubsection{Modular flow at the cutoff surface}
+	\begin{figure}[!ht]
+%	\vspace{-1.5ex}
+	\centering
+	\includegraphics[width=.4\linewidth]{img/modFlowLorentzian.png}
+	\hspace{2em}
+	\includegraphics[width=.4\linewidth]{img/modFlowEuclidean.png}
+%	\vspace{-2ex}
+	\caption{Modular flow at the boundary, for an interval lying on a constant $t = 0$ slice, in Lorentzian and Euclidean signature}
+	\end{figure}
+
+\pagebreak[4]
+
 	We now restrict to an interval centered at the origin: $
@@
 		= (\frac{L_\infty}{2})^2
-	$, $x_\pm = -x_\mp$, and same for $t_\pm, u_\pm, v_\pm$. 
-	We then introduce the \textit{rapidity} variable $\theta$ to nicely parametrized the boosted interval; for a constant time slice, we have $\theta = 0$. For a general boosted interval, we have:
+	$, where $x_\pm = -x_\mp$, and same for $t_\pm, u_\pm, v_\pm$. 
+	We then introduce the \textit{rapidity} $\theta$ to nicely parametrized the boosted interval; for a constant time slice, we have $\theta = 0$. For a general boosted interval, we have:
 	\begin{equation}
@@
 
-\pagebreak[3]
-	We see that the $\pdd{z}$ term vanishes in the following two cases:
+	We note that the $\pdd{z}$ term vanishes in the following two cases:
 	\begin{itemize}[noitemsep]
 	\item as $z\to 0$, i.e.~near the asymptotic boundary;
-	\item within the whole plane $
+	\item within the whole plane: $
 			x\sinh\theta
@@
 	\end{itemize}
+
+\FloatBarrier
+\pagebreak
+\subsection{Cutoff $\mrm{AdS}_3$ and the loss of $2\pi$ periodicity}
+
+\textbf{Summary:} We look at the flow at constant cutoff $z = z_c$, which has non-trivial $\pdd{z}$ component, which in turn leads to a violation of the $2\pi$ periodicity for $\xi$ along the horizon.
+
 	Now we'd like to study $\xi$ not at the asymptotic boundary, but at some \textbf{constant finite cutoff} $z = z_c$. 
@@
 	$ guarantees that after Wick rotation, the Euclidean periodicity around the horizon is normalized to $\beta = 1$.
-However, if we restrict to the field theory living at $z = z_c$, which corresponds to a $T\bar{T}$ deformed theory, since it has no knowledge of the $\pdd{z}$ component of $\xi$, we should reduce it to a modular flow within the $z = z_c$ plane by, e.g.~projecting the $z$ component out, which leaves us:
+However, if we restrict to the field theory living at constant cutoff $z = z_c$, which corresponds to a $T\bar{T}$ deformed theory \cite{McGough:2016lol,Lewkowycz:2019xse} \sidenote{[more citations needed]}, since it has no knowledge of the $\pdd{z}$ component of $\xi$, we should reduce it to a modular flow within the $z = z_c$ plane by, e.g.~projecting the $z$ component out, which leaves us:
 	\begin{equation}
@@
 
-{\nobeginpar
-	How should we understand this?
-	\begin{itemize}
-	\item The $T\bar{T}$ deformation might somehow correspond to a variation of temperature at the cutoff; instead of $\rho = e^{-\mcal{H}}$, we now have:
-	\begin{equation}
-		\rho = e^{-\beta\mcal{H}},
-	\quad \beta \sim 1 + \frac{1}{L^2} \order{\mu}
-	\end{equation}
-	Where $\mu$ is the deformation parameter (see \cite{Apolo:2019zai} for the convention we follow). Q: how do we make this precise?
-
-	\item The non-local nature of $T\bar{T}$ deformation creates some $\order{z_c}$ ``fuzziness'' in the cutoff theory at $z = z_c$; $\beta \sim 1$ holds, but only up to some coarse-graining of points.
-Q: again, how do we make this precise?
-
-	\item Instead of projecting out the $\pdd{z}$ component of $\xi$, maybe we could \textit{define} the evolution of the cutoff interval by following the flow of $\xi = 2\pi\pdd{\tau}$ starting from the RT surface at $z = z_c$.
-Now there is no longer a projection of $\xi$; we are always following it along the boundary, so the periodicity is preserved: $\beta = 1$.
-
-	But now this is no longer a \textit{constant} cutoff away from $z = z_c$.
-In particular, the forward and backward evolved interval will approach the upper and lower endpoints of the diamond at $z \to 0$.
-Q: does this make sense?
-Will it be compatible with \textcite{McGough:2016lol}?
-	\end{itemize}
-}
-
 	\begin{figure}[!ht]
@@
 	\end{figure}
+
+\pagebreak[3]
+
+	How should we understand this?
+	\begin{itemize}
+	\item The $T\bar{T}$ deformation might somehow correspond to a variation of temperature at the cutoff; instead of $\rho = e^{-\mcal{H}}$, we now have:
+	\begin{equation}
+		\rho = e^{-\beta\mcal{H}},
+	\quad \beta \sim 1 + \frac{1}{L^2} \order{\mu}
+	\end{equation}
+	Where $\mu$ is the deformation parameter (see \cite{Apolo:2019zai} for the convention we follow).
+\sidenote{This might also be related to the \textit{local entanglement temperature} defined in later sections.}
+%	Q: how do we make this precise?
+
+	\item The non-local nature of $T\bar{T}$ deformation creates some $\order{z_c}$ ``fuzziness'' in the cutoff theory at $z = z_c$; $\beta \sim 1$ holds only up to some coarse-graining of points. 
+%	Q: again, how do we make this precise?
+
+	\item Maybe we shouldn't project out the $\pdd{z}$ component of $\xi$, but instead \textit{define} the cutoff by following the flow of $\xi = 2\pi\pdd{\tau}$; in this way the periodicity is preserved by construction: $\beta_\xi = 1$.
+We will discuss this in the next section.
+	\end{itemize}
+
+\pagebreak
+\subsection{Restoring the $2\pi$ periodicity by following the flow}
+
+\textbf{Summary:} We note that the periodicity can be restored by following the flow of $\xi$ starting from a codim-2 cutoff surface. This is related to the proposal of \cite{Grado-White:2020wlb}.
+
+	Instead of projecting out the $\pdd{z}$ component of $\xi$, we could \textit{define} the evolution of the cutoff interval by following the flow of $\xi = 2\pi\pdd{\tau}$ starting from the RT surface at $z = z_c$.
+Now there is no longer a projection of $\xi$; we are always following it along the boundary, so the periodicity is preserved: $\beta = 1$.
+
+	But now this is no longer a \textit{constant} cutoff away from $z = z_c$.
+In particular, the forward and backward evolved interval will approach the upper and lower endpoints of the diamond at $z \to 0$.
+Q: will it be compatible with \textcite{McGough:2016lol}?
+
+	\sidenote{\textbf{On the other hand, this seems highly related to the restricted maximin proposal of \cite{Marolf:2019bgj,Grado-White:2020wlb} [comments needed],}} which discusses the violation of boosted strong subadditivity (SSA) due to the constant finite cutoff observed in \cite{Lewkowycz:2019xse}, and offers a similar resolution of using a codim-2 cutoff surface instead of the usual codim-1 cutoff.
+Namely, the cutoff is given by $
+		z = z_c, t = 0
+	$, instead of just $z = z_c$.
 
@@
 
-\subsubsection{Flow from constant cutoff}
-	For an interval lying on a constant time slice $t_\pm = 0$, i.e.~$\theta = 0$, we can actually solve the flow of $\xi$ by hand without much difficulty.
+\pagebreak
 
+	For an interval lying on a constant time slice $t_\pm = 0$, i.e.~$\theta = 0$, we can actually solve the flow of $\xi$ without much difficulty.
 	Consider the flow starting from $(t,x,z) = (0,x_c,z_c)$, we note that $
@@
 
-%\subsubsection{Map to the Rindler coordinates}
-	To gain more understanding of the modular flow of the cutoff theory, we can look at the map to the Rindler coordinates.
-In the Poincar\'e $\mrm{AdS}_3$ case this is explicitly given in Appendix B by \textcite{Song:2016gtd}; the Poincar\'e $(t,x,z)$ is mapped to BTZ $(u,v,\rho)$:
+%
+
+	To gain more understanding of the modular flow of the cutoff theory, we can look at the \textit{CHM map} \cite{Casini:2011kv} to the Rindler coordinates.
+In the Poincar\'e $\mrm{AdS}_3$ case this is explicitly given in Appendix B of \cite{Song:2016gtd}; the entanglement wedge in Poincar\'e $(t,x,z)$ is mapped to the planar BTZ $(u,v,\rho)$:
 	\begin{equation}
@@
 	\end{equation}
-	Here we've reused the variable names $(u,v)$ for the BTZ coordinates, and we've tweaked the expressions in \cite{Song:2016gtd} to be more symmetric in $(u,v)$.
+	This is a BTZ \textit{black string} with \textit{non-compact} $\phi$ direction. 
+	One can check that the $(u,v,\rho)$ coordinates indeed cover the $L_\infty$-sized entanglement wedge specified by $\xi$. 
+	Here we've reused the variable names $(u,v)$ for the planar BTZ coordinates, and we've tweaked the expressions in \cite{Song:2016gtd} to be more symmetric in $(u,v)$.
 
-	TO CHECK: At the boundary this reduces to the result of \textcite{Casini:2011kv}, which is used by \textcite{Lewkowycz:2019xse}.
+	\noindent\sidenote{\textbf{TO CHECK:}} At the boundary this reduces to the result of \textcite{Casini:2011kv}, which is used by \textcite{Lewkowycz:2019xse}. Also see the note \texttt{EETTbar.pdf}.
 
-	We note that $T_{u,v}$ is \textit{not exactly} the physical (Hawking) temperature of the spacetime; the physical temperature, on the other hand, is given by (see e.g.~\cite{Compere:2018aar}):
+	We note that $T_{u,v}$ is \textit{not quite} the physical Hawking temperature of the spacetime; the physical temperature is given by (see e.g.~\cite{Compere:2018aar}):
 	\begin{equation}
@@
 	\end{equation}
-	This is a surface in the BTZ coordinates that parallels $\pdd{\tau}$ and intersects the horizon. 
+
+	\begin{figure}[!ht]
+	\centering
+	\includegraphics[width=.6\linewidth]{img/modFlowCutoff2BTZ.pdf}
+%	\hspace{2em}
+%	\vspace{-2ex}
+	\caption[Integral surface of the modular flow when mapped to the planar BTZ coordinates]{%
+		Integral surface of the modular flow when mapped to the planar BTZ coordinates. Note that the $\rho$ axis is logarithmic.
+
+		The flow starts from $t = 0,\ z = z_c$, and here we've chosen $\frac{L_\infty}{2} = 1$ while $z_c = 0.1,\,0.2,\,\cdots,\,0.9$. 
+		Note that the asymptotic boundary $z\to 0$ corresponds to $\rho \to \infty$. 
+		Also we've taken $T_u = T_v = T = \frac{1}{2}$ as discussed before, and the horizon is at $\rho = T_u T_v = T^2$; this is the image of the RT surface under the CHM map.
+	}
+	\end{figure}
+
+\pagebreak[3]
+
+	This is a surface in the planar BTZ coordinates that parallels $\pdd{\tau}$ and intersects the horizon.
+The horizon length, which is ``cut off'' by this surface, gives the finite entropy of the cutoff interval.
 	With some basic algebraic manipulation, this can be solved in terms of $\rho(\phi)$:
@@
 
-	We note that there is also a mysterious square root structure here: $
+\textit{
+	We note that there is also a mysterious square root structure here: $\mathsmaller{
 		\sqrt{
@@
 		}
-	$, which resembles the familiar $
+	}$, which resembles the familiar $
 		\sqrt{1 + (\frac{2z_c}{L})^2}
 	$ but has a minus sign, and the $\frac{2z_c}{L}$ factor is weighted by $\sinh\,(2T\phi)$. 
+}
 
-	\begin{figure}[!ht]
-	\centering
-	\includegraphics[width=.7\linewidth]{img/modFlowCutoff2BTZ.pdf}
-%	\hspace{2em}
-%	\vspace{-2ex}
-	\caption{Integral surface of the modular flow when mapped to the BTZ coordinates, starting from $t = 0,\ z = z_c$.
-Here we've chosen $\frac{L_\infty}{2} = 1$ while $z_c = 0.1,\,0.2,\,\cdots,\,0.9$.
-Also we've taken $T_u = T_v = T = \frac{1}{2}$ as discussed before, and the horizon is at $T^2 = \frac{1}{4}$.
+\pagebreak
+\subsection{Modular flow for the cutoff field theory}
+\textbf{Summary:} We try to obtain the entanglement entropy using the modular flow at the \mbox{codim-2} cutoff surface, by defining a \textit{local entanglement entropy $\beta(x)$}, which relates the entanglement entropy to some thermal entropy.
+
+	From the field theory's perspective, the above calculations seem to suggest that the modular flow $\xi$ of [[ an $L$-sized interval in the cutoff theory ]] is given by the modular flow $\xi = \xi(L_\infty)$ of [[ a CFT for an $L_\infty$ interval ]].
+
+	We note that there is a trick to read out the entanglement entropy from the modular flow: it is possible to define a \textit{local entanglement temperature}, and then use it to read the entanglement entropy from the modular flow generator, by comparing with the Hamiltonian of a thermal field theory, where we have:
+	\begin{equation}
+	\mcal{H}=\int \beta\,T_{00}\,dx,\quad \beta = 2\pi,
+	\quad \xi|_{t=0} = \beta\,\pdd{t}
+	\label{eq:beta_thermal}
+	\end{equation}
+	In general, the modular Hamiltonian is given by:
+	\begin{equation}
+	\mcal{H}_\mcal{A}=\int \beta(x)\, T_{00}\,dx,\quad \xi|_{t=0} = \beta(x)\, \pdd{t}
+	\end{equation}
+
+	Let's see this shortcut in action in CFT$_2$; the \textit{entropy density} is given by:
+	\begin{equation}
+	\partial_x S = \frac{c}{3} \frac{\pi}{\beta(x)}
+	\end{equation}
+	in terms of the local entanglement temperature $\beta(x)$, and the total entropy of the interval $\mcal{A}$ is given by:
+	\begin{equation}
+	S= \frac{c}{3}
+		\int_\mcal{A} \frac{\pi}{\beta(x)}dx
+	\end{equation}
+
+	For example, for a single interval in CFT$_2$,
+	\begin{equation}
+	\beta(x)=\frac{2\pi}{L_\infty}
+		\pqty{\frac{L_\infty^2}{4}-x^2}
+	\end{equation}
+	\begin{equation}
+	S= \frac{c}{3} \int_{-L_\infty/2}^{L_\infty/2}
+			\frac{L_\infty/2}{(L_\infty/2)^2-x^2}dx,
+	\end{equation}
+	The indefinite integral $
+		\int \frac{L_\infty/2}{(L_\infty/2)^2-x^2}dx
+		= \mop{arctanh}\frac{2x}{L_\infty}
+		\rightarrow\infty
+	$, as $x\rightarrow L_\infty/2$, so one needs a cutoff:
+	\begin{equation}
+	S=\frac{c}{3}\int_{-L_\infty/2+a}^{L_\infty/2-a}
+		\frac{L_\infty/2}{(L_\infty/2)^2-x^2}dx
+	=\frac{2c}{3} \mop{arctanh} \pqty{
+			1-\frac{2a}{L_\infty}
 		}
-	\end{figure}
+	\end{equation}
+	As $a\rightarrow 0$,
+	\begin{equation}
+		\mop{arctanh} \pqty{
+			1-\frac{2a}{L_\infty}
+		}\rightarrow \frac{1}{2}\log\frac{L_\infty}{a}
+	\end{equation}
+	So we get the usual result
+	\begin{equation}
+	S=\frac{c}{3}\log\frac{L_\infty}{a}
+	\end{equation}
 
-\section{Entropy as Noether Charge}
-	Ref: \textcite{Wald:1993nt,Iyer:1994ys,Iyer:1995kg}.
+	Another case is the Rindler patch,
+	\begin{equation}
+	\xi\propto x\partial_x-t\partial_x
+	\end{equation}
+	\begin{equation}
+	\beta(x)=2\pi x
+	\label{eq:beta_rindler}
+	\end{equation}
+	\begin{equation}
+	S=\int_{a}^{l}\frac{c}{6x}=\frac{c}{6}\log \frac{l}{a}
+	\end{equation}
+	The factor $\frac{c}{6}$ is that in this case, one only considers one of the endpoints instead of two.
+One can read the C-function from \eqref{eq:beta_thermal}\eqref{eq:beta_rindler}, when $\beta$ is linear of $x$.
+	\begin{equation}
+	C=\frac{c}{6}
+	\end{equation}
 
-	Ref: \textcite{Lewkowycz:2013nqa,Faulkner:2013ana}.
+%	Now consider the modular flow generator, there are two effects.
+On the one hand, if one changes the overall factor, one will change the temperature, giving an overall factor of the entanglement entropy.
+%	(The case we discussed last week is this case, where we used the Rindler map to get the result.) 
+%	Otherwise, it will change the Rindler map, and give different entanglement entropy.
+
+	Now for the cutoff field theory living at the boundary, consider a modular flow generator of this form,
+	\begin{equation}
+	\xi|_{t=0}=\frac{2\pi}{L_\infty}(L_\infty^2/4-x^2)\partial_t
+	\end{equation}
+	Namely in the same form as the modular flow of a CFT, but we have:
+	\begin{equation}
+	L^2/4+a^2=L_\infty^2/4
+	\end{equation}
+	Where the interval for the cutoff theory is of length $L$. The entanglement entropy is
+	\begin{equation}
+	S=\frac{c}{6}\mop{arctanh}\frac{2x}{L_\infty}\Big|_{-L/2}^{L/2}
+	=\frac{c}{3}\mop{arctanh}\frac{L}{\sqrt{L^2+4a^2}}
+	=\frac{c}{3}\mop{arcsinh}\frac{L}{2a}
+	\end{equation}
+	with C-function
+	\begin{equation}
+	C(l)=\frac{c}{3}\frac{1}{\sqrt{1+\frac{4a^2}{L^2}}}
+	\end{equation}
+	Which agrees with \cite{Lewkowycz:2019xse}.
+
+	In the field theory side, such modular flow generator means that the Rindler transformation map a slightly large region $D(\tilde{A})$ to the hyperbolic cylinder, and keep track of the endpoints of the interval $A$.
+The endpoints are implied in the range of the integration in the local entanglement temperature method, and also in the length of the cylinder in the Rindler map method.
+	\begin{equation}
+	M:D(A)\rightarrow R\times S
+	\end{equation}
+	\begin{equation}
+	\tilde{M}:D(\tilde{A})\rightarrow R\times S
+	\end{equation}
+	A is the interval with length $L$, $\tilde{A}$ is the interval with length $L_\infty$.
+
+	In the cutoff AdS picture, it seems that the modular flow generator for the interval with lenght $L$ is on the asymptotic boundary but with the interval length $L_\infty$ instead of $L$.
+
+\textit{
+	The discussion above is in the framework of $\mrm{CFT}_2$, but with different modular flow generator.
+Now we consider the framework of $T\bar{T}$ deformed theories.
+The thermal entropy with unit length is
+	\begin{equation}
+	S_{thermal}=\frac{\pi c}{3\beta}\eta
+	\end{equation}
+	\begin{equation}
+	\eta=\frac{1}{\sqrt{1+\frac{4\pi^2c\mu}{3\beta^2}}}
+	\end{equation}
+	Consider the half line case,
+	\begin{equation}
+	\beta(x)=2\pi x
+	\end{equation}
+	One can get the C-function,
+	\begin{equation}
+	C(l)=\frac{c}{6}\frac{1}{\sqrt{1+\frac{c\mu}{3l^2}}}
+	\end{equation}
+	Again, there is ``one endpoint'' in this case, which will give one half contribution of the C-function with the pre-factor $c/3$.
+}
+
+\pagebreak
+\section{Entanglement Entropy as Gravitational Charge}
+	Ref: \textcite{Wald:1993nt,Iyer:1994ys,Iyer:1995kg}, \textcite{Lewkowycz:2013nqa}, and \textcite{Faulkner:2013ana}.
 
@@
 
-	We thus have to repeat the calculations above to get the geodesic $\gamma$ and modular generators $\xi^\mu$ in the new backgrounds.
+\subsection{Modular flow in $\mrm{BTZ}_3$ and entanglement entropy}
+\textbf{Summary:} We map the the modular flow in the Poincar\'e $\mrm{AdS}_3$ vacuum to the BTZ background, and compute the entanglement entropy as gravitational charge.
+
+	We thus have to repeat the calculations above to get the geodesic $\gamma$ and modular generators $\xi^\mu$ in the new BTZ backgrounds.
 However, it is convenient to remember that all BTZ black holes are locally equivalent to the pure $\mrm{AdS}_3$; we can then map Poincar\'e $(u,v,z)$ to BTZ Schwarzschild $(t,r,\phi)$ by \cite{Hubeny:2007xt}:
@@
 	\begin{equation}
-		Q_\xi = \frac{1}{2G} \log \frac{\sinh (LT)}{T}
+		Q_\xi = \frac{1}{2G} \log \frac{\sinh LT}{T}
 	\end{equation}
 
-\subsection{With constant cutoff}
+\pagebreak
+\subsection{BTZ with constant cutoff}
+\textbf{Summary:} We then consider constant $r$ cutoff in the Schwarzschild coordinates, which corresponds to the proposal of \cite{McGough:2016lol}.
+This gives a finite temperature generalization of the result of \cite{Lewkowycz:2019xse}.
+
 	Now we consider constant cutoff at $r = r_c$.
@@
 
-\vspace{1.2\baselineskip}
-\pagebreak[4]
-\raggedright
-\printbibliography[%
-%	title = {参考文献} %
-	,heading = bibintoc
-]
+\FloatBarrier
+
+\pagebreak
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\bibliographystyle{JHEP} 
+\bibliography{cutoffModular-alpha.bib}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \end{document}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2021-05-27 alpha/CutoffModularFlow/cutoffModular-alpha.tex
Update note on local entanglement entropy

@@
 \input{preamble.tex}
+
+\newcommand{\lui}[2]{\textcolor{red}{#1}\todo[color=yellow]{\scriptsize{L: #2}}}
 
@@
 
-	\item We try to obtain the entanglement entropy using the modular flow at the \mbox{codim-2} cutoff surface, by defining a \textit{local entanglement entropy $\beta(x)$}, which relates the entanglement entropy to some thermal entropy.
+	\item We try to obtain the entanglement entropy using the modular flow at the \mbox{codim-2} cutoff surface, using the \textit{effective inverse temperature $\beta(x)$} introduced in \cite{Wong:2013gua,Cardy:2016fqc}, which relates the entanglement entropy to some thermal entropy.
+\sidenote{[relation with partial entanglement entropy?]}
+
+	\item \sidenote{We should look at the boosted interval.}
 
@@
 \subsection{Modular flow for the cutoff field theory}
-\textbf{Summary:} We try to obtain the entanglement entropy using the modular flow at the \mbox{codim-2} cutoff surface, by defining a \textit{local entanglement entropy $\beta(x)$}, which relates the entanglement entropy to some thermal entropy.
+\textbf{Summary:} We try to obtain the entanglement entropy using the modular flow at the \mbox{codim-2} cutoff surface, using the \textit{effective inverse temperature $\beta(x)$} introduced in \cite{Cardy:2016fqc}, which relates the entanglement entropy to some thermal entropy.
 
@@
 
-	We note that there is a trick to read out the entanglement entropy from the modular flow: it is possible to define a \textit{local entanglement temperature}, and then use it to read the entanglement entropy from the modular flow generator, by comparing with the Hamiltonian of a thermal field theory, where we have:
+	We note that there is a trick to read out the entanglement entropy from the modular flow: it is possible to define a \textit{local entanglement temperature}, and then use it to read the entanglement entropy from the modular flow generator \cite{Cardy:2016fqc}.
+The result is obtained by comparing with the Hamiltonian of a thermal field theory, where we have:
 	\begin{equation}
@@
 
-	Let's see this shortcut in action in CFT$_2$; the \textit{entropy density} is given by:
-	\begin{equation}
-	\partial_x S = \frac{c}{3} \frac{\pi}{\beta(x)}
+	Let's see this trick in action in CFT$_2$; the \textit{entropy density} is given by:
+	\begin{equation}
+	s_\mcal{A} = \frac{c}{3} \frac{\pi}{\beta(x)}
 	\end{equation}
@@
 		= \mop{arctanh}\frac{2x}{L_\infty}
-		\rightarrow\infty
-	$, as $x\rightarrow L_\infty/2$, so one needs a cutoff:
+%		\rightarrow\infty
+	$ diverges as $x\rightarrow L_\infty/2$, so one needs a cutoff:
 	\begin{equation}
@@
 
-	Another case is the Rindler patch,
+	Another case is the Rindler patch, \sidenote{better to integrate from $l$ to $\infty$},
 	\begin{equation}
@@
 	\begin{equation}
-	L^2/4+a^2=L_\infty^2/4
+	L^2/4+z_c^2=L_\infty^2/4
 	\end{equation}
@@
 	\begin{equation}
-	S=\frac{c}{6}\mop{arctanh}\frac{2x}{L_\infty}\Big|_{-L/2}^{L/2}
-	=\frac{c}{3}\mop{arctanh}\frac{L}{\sqrt{L^2+4a^2}}
-	=\frac{c}{3}\mop{arcsinh}\frac{L}{2a}
+	S=\frac{c}{6}\mop{arctanh}\frac{2x}{L_\infty}\Big|_{x=-L/2}^{x=L/2}
+	=\frac{c}{3}\mop{arctanh}\frac{L}{\sqrt{L^2+4z_c^2}}
+	=\frac{c}{3}\mop{arcsinh}\frac{L}{2z_c}
 	\end{equation}
@@
 	\begin{equation}
-	C(l)=\frac{c}{3}\frac{1}{\sqrt{1+\frac{4a^2}{L^2}}}
-	\end{equation}
-	Which agrees with \cite{Lewkowycz:2019xse}.
+	C(l)=\frac{c}{3}\frac{1}{\sqrt{1+\frac{4z_c^2}{L^2}}}
+	\end{equation}
+	Which agrees with \cite{Lewkowycz:2019xse}. \sidenote{This provides a field theory side calculation of the cutoff entanglement entropy, based on the input of the modular flow $\xi$. }
+
+	\textit{Note that we only need to know the modular flow $\xi$ along some time slice.
+We don't need to know the full modular flow.
+This seems to be consistent with Lewkowycz--Maldacena \cite{Lewkowycz:2013nqa} and the holographic entropy, where it only depends linearly on $\xi$ along the RT surface, as long as $\xi$ is a Killing vector.
+See \eqref{kdef}.
+}
 
@@
 	\begin{equation}
-	M:D(A)\rightarrow R\times S
-	\end{equation}
-	\begin{equation}
-	\tilde{M}:D(\tilde{A})\rightarrow R\times S
+	f:D(A)\rightarrow R\times S
+	\end{equation}
+	\begin{equation}
+	\tilde{f}:D(\tilde{A})\rightarrow R\times S
 	\end{equation}
@@
 
+\subsubsection*{Reasoning for this trick}
+	The validity of this trick can be argued from the Rindler map; suppose we have the following Rindler map at the boundary:
+	\begin{equation}
+	\begin{aligned}
+		f\colon
+		\mcal{D}(\mcal{A})
+		&\longto \mcal{R} = S^1_\beta \times f(\mcal{A}), \\
+		(t,x)
+		&\longmapsto (\tau,\tilde{x}),
+	\end{aligned}
+	\end{equation}
+	Here $f(\mcal{A})$ is the image of the boundary interval.
+$f$ by construction ``normalizes'' the temperature for the modular generator, namely, the modular flow $\xi$ is now realized as the pullback of $2\pi\pdd{\tau}$:
+	\begin{equation}
+		\xi = \xi^\mu \pdd{\mu}
+		= 2\pi\pdd{\tau}
+	\end{equation}
+	In particular, along the interval $\mcal{A}$ at the $t = 0$ time slice, we have:
+	\begin{equation}
+		\xi|_{t = 0}
+		= \beta(x)\,\pdd{t}
+		= 2\pi\pdd{\tau},
+	\quad
+		\pdv{t}{\tau}
+		= \frac{\beta(x)}{2\pi}
+	\end{equation}
+	Note that although $\xi$ is a Killing vector when it's extended to the bulk, it is only a \textit{conformal Killing vector} when it's restricted to the boundary.
+
+	Here we think of $f$ as a simple coordinates transformation or diffeomorphism, which keeps the metric $\dd{s}^2$ invariant, and maps the flat coordinates to a conformally flat coordinates:
+	\begin{equation}
+		\dd{s}^2
+		= \dd{t}^2 + \dd{x}^2
+		= \Omega^2(\tau,\tilde{x}) \pqty{
+				\dd{\tau}^2 + \dd{\tilde{x}}^2
+			},
+	\quad
+		\Omega_{t = 0} = \pdv{t}{\tau}
+		= \frac{\beta(x)}{2\pi}
+	\end{equation}
+
+	Due to conformal symmetry, one can further drop the conformal factor $\Omega^2(\tau,\tilde{x})$ from the metric, while the thermal entropy of the system remains unchanged. We now have a flat annulus:
+	\begin{equation}
+		\tilde{\mcal{R}}
+		= S^1_\beta \times [0,\tilde{L}],
+	\quad
+		\dd{\tilde{s}}^2
+		= \frac{1}{\Omega^2} \dd{s}^2
+		= \dd{\tau}^2 + \dd{\tilde{x}}^2
+	\end{equation}
+	This is the corresponding geometry of a thermal partition function, with a constant temperature $\beta_\tau = 2\pi$. 
+	Now $\pdd{\tau}$ is truly a Killing vector of $\tilde{\mcal{R}}$. 
+	In this case the thermal entropy is extensive: the total entropy $S_\mcal{A}$ is proportional to the size of the system:
+	\begin{equation}
+		S_\mcal{A}
+%		= s\,\norm{f(\mcal{A})}_{\tilde{\mcal{R}}}
+		= \frac{c}{6}\,\norm{f(\mcal{A})}_{\tilde{\mcal{R}}}
+	\end{equation}
+	Here $\norm{f(\mcal{A})}_{\tilde{\mcal{R}}}$ denotes the $\tilde{R}$ length of the interval $f(\mcal{A})$:
+	\begin{equation}
+		\norm{f(\mcal{A})}_{\tilde{\mcal{R}}}
+		= \int_{f(\mcal{A})} \dd{\tilde{s}}
+		= \int_{f(\mcal{A})} \frac{\dd{s}}{\Omega}
+		= \int_{\mcal{A}} \frac{\dd{s}}{\Omega}
+		= \int_{\mcal{A}} \frac{2\pi}{\beta(x)} \dd{x}
+	\end{equation}
+	We've used the fact the $f$ is a diffeomorphism, to reduce the integral back to an integral along $\mcal{A}$ in the original coordinates. 
+	The entropy is thus given by:
+	\begin{equation}
+		S_\mcal{A}
+		= \frac{c}{6}
+			\int_{\mcal{A}} \frac{2\pi}{\beta(x)} \dd{x}
+	\end{equation}
+
+\pagebreak
 \textit{

### 2021-05-31 alpha/CutoffModularFlow/cutoffModular-alpha.tex
Update note on cutoff modular flow
- add comments
- tweak notations

@@
 This could be related to the \textit{restricted maximin} proposal of \cite{Marolf:2019bgj,Grado-White:2020wlb}.
+\sidenote{[With this cutoff the causal wedge again coincides with the entanglement wedge]}
 
@@
 
-\section{Modular flow in the Poincar\'e patch}
+\section{Zero temperature: modular flow in the Poincar\'e patch}
 
 \subsection{Review of the general recipe}
-	A boundary interval $\mcal{A}$ defines a denisty matrix $\rho_\mcal{A} = \tr_{\bar{\mcal{A}}} \rho = e^{-\mcal{H}_\mcal{A}}$.
+	A boundary interval $\mcal{A}$ defines a denisty matrix:
+	\begin{equation}
+		\rho_\mcal{A}
+		= \tr_{\bar{\mcal{A}}} \rho
+		= e^{-\mcal{H}_\mcal{A}}
+	\end{equation}
+	where $\bar{\mcal{A}}$ is the complement of $\mcal{A}$ and $\mcal{H}_\mcal{A}$ is the corresponding modular Hamiltonian.
 $\mcal{H}_\mcal{A}$ is generically nonlocal, but in a highly symmetric background (e.g.~AdS vacuum) it might be geometrically realized and corresponds to a symmetry of the underlying quantum field theory.
@@
 		\tau \sim \tau + 2\pi i
+		= \tau + i\beta_\tau,
+	\quad
+		\beta_\tau = 2\pi
 	\end{equation}
 	Here $H_i$ are the symmetry generators.
-The causal domain of dependence $\mcal{D}$ is mapped to some thermal state with normalized inverse temperature $2\pi$.
-Here we choose to absorb such $2\pi$ into the definition of $\xi$, so the Euclidean periodicity w.r.t.~$\xi$ is simply $\beta_\xi = 1 = \frac{1}{T_\xi}$, which means the surface gravity along the horizon is given by $\kappa_\xi = 2\pi T_\xi = 2\pi$.
+The causal domain of dependence $\mcal{D}$ is mapped to some thermal state with normalized inverse temperature $\beta_\tau = 2\pi$.
+Here we choose to absorb such $2\pi$ into the definition of $\xi$, so the Euclidean periodicity w.r.t.~$\xi$ is simply $\beta_\xi = 1$, which means the surface gravity along the horizon is given by:
+	\begin{equation}
+		\kappa_\xi = \frac{2\pi}{\beta_\xi} = 2\pi,
+	\quad
+		\beta_\xi = 1
+	\end{equation}
 
@@
 \subsubsection{Matching bulk and boundary symmetries}
-	In Poincar\'e $\mrm{AdS}_3/\mrm{CFT}_2$, the $H_i$'s are given by $L_n,\bar{L}_n$ with $n=0,\pm 1$. At $z\to 0$ we recover the usual global $\mfrak{sl}(2,\mbb{R})$ generators:
+	In Poincar\'e $\mrm{AdS}_3/\mrm{CFT}_2$, the $H_i$'s are given by $L_n,\tilde{L}_n$ with $n=0,\pm 1$. At $z\to 0$ we recover the usual global $\mfrak{sl}(2,\mbb{R})$ generators:
 	\begin{equation}
@@
 		      L_n \to -u^{n+1} \pdd{u},\quad
-		\bar{L}_n \to -v^{n+1} \pdd{v},\quad
+		\tilde{L}_n \to -v^{n+1} \pdd{v},\quad
 	n = 0,\pm 1
@@
 	\end{equation}
-	By requiring that a linear combination of these generators reduce to the boundary $L_n$'s, one can uniquely extend the $L_n,\bar{L}_n$'s into the bulk.
-The result for $L_n$'s is listed below; for $\bar{L}_n$ one need only exchange all $u\leftrightarrow v$.
+	By requiring that a linear combination of these generators reduce to the boundary $L_n$'s, one can uniquely extend the $L_n,\tilde{L}_n$'s into the bulk.
+The result for $L_n$'s is listed below; for $\tilde{L}_n$ one need only exchange all $u\leftrightarrow v$.
 	\begin{equation}
@@
 	\begin{equation}
-	\text{``sphere'':}\quad\mathsmaller{
+	\begin{aligned}
+	\text{``sphere'':} &&&\mathsmaller{
 		z^2
@@
 		- \pqty{\frac{t_+ - t_-}{2}}^{\!\!2}
-	}
-	\end{equation}
-	\begin{equation}
+	},\\
+	&&& \text{i.e.}\ \,
 		L^2
@@
 			- \pqty{t_+ - t_-}^2
-		= (u_+ - u_-)(v_+ - v_-)
-	\end{equation}
-	\begin{equation}
-	\text{plane:}\quad
+		= (u_+ - u_-)(v_+ - v_-),
+	\\[1.5ex]
+	\text{plane:} &&&
 		\frac{x - \frac{1}{2} (x_+ + x_-)}{x_+ - x_-}
 		= \frac{t - \frac{1}{2} (t_+ + t_-)}{t_+ - t_-}
-	\end{equation}
-	Alternatively, it can be more compactly rewritten with $x^\mu \sim (t,x)$ or $(u,v)$; mind the various $\pm$ signs in the above expressions: 
+	\end{aligned}
+	\end{equation}
+	Alternatively, it can be more compactly rewritten with $x^\mu \sim (t,x)$ or $(u,v)$; mind the various $\pm$ signs in the expressions: 
 	\begin{equation}
@@
 		\xi = 2\pi \sum_{n=0,\pm 1} \pqty{
-				s_n L_n - \bar{s}_n \bar{L}_n
+				s_n L_n - \tilde{s}_n \tilde{L}_n
 			},
@@
 	\end{equation}
-	One need only exchange all $u\leftrightarrow v$ to obtain $\bar{s}_n$.
+	One need only exchange all $u\leftrightarrow v$ to obtain $\tilde{s}_n$.
 The overall coefficient of $\xi$ (in this case, $2\pi$) is fixed by normalizing the temperature of the horizon, namely we demand that the surface gravity is $2\pi$ along the RT surface:
 	\begin{equation}
-		T_\xi = \frac{\kappa_\xi}{2\pi} = 1,
+		\beta_\xi = \frac{2\pi}{\kappa_\xi} = 1,
 	\quad
@@
 	We note that the $\pdd{z}$ term vanishes in the following two cases:
-	\begin{itemize}[noitemsep]
+	\begin{itemize}[noitemsep,topsep=0pt]
 	\item as $z\to 0$, i.e.~near the asymptotic boundary;
@@
 
+	\sidenote{One oddity of this prescription is that the codim-1 cutoff geometry depends on the choice of the interval $\mcal{A}$}.
+This seems to suggest that there is no canonical way to embed the entire time-evolved deformed field theory into the bulk.
+The best we can do is to embed the causal diamond $\mcal{D}(\mcal{A})$ (\sidenote{and maybe $\mcal{D}(\mcal{A})$}), given an interval $\mcal{A}$.
+This is the price we have to pay for SSA to hold.
+
+	Maybe we should not expect that the entire time-evolved deformed theory can be embedded into the bulk.
+\sidenote{We could look at the proof of $T\bar{T}$ duality and check if this is really implied.
+It is quite possible that we only need to embed the boundary theory at a specific time slice, and the trace flow arguments will go through.}
+
 \pagebreak
@@
 
-	Due to conformal symmetry, one can further drop the conformal factor $\Omega^2(\tau,\tilde{x})$ from the metric, while the thermal entropy of the system remains unchanged. We now have a flat annulus:
+	Due to conformal symmetry [\sidenote{what about the TTbar case?
+Perhaps the reason it still works is again, that the conformal factor vanishes at the endpoints, due to $2\pi$ periodicity of $\xi$}], one can further drop the conformal factor $\Omega^2(\tau,\tilde{x})$ from the metric, while the thermal entropy of the system remains unchanged.
+We now have a flat annulus:
 	\begin{equation}
@@
 \pagebreak
-\section{Entanglement Entropy as Gravitational Charge}
+\section{Finite temperature: modular flow in BTZ background}
+\subsection{Entanglement Entropy as Gravitational Charge}
 	Ref: \textcite{Wald:1993nt,Iyer:1994ys,Iyer:1995kg}, \textcite{Lewkowycz:2013nqa}, and \textcite{Faulkner:2013ana}.
@@
 			}
-	\end{equation}
+		= \var{S_\mcal{A}}
+		= \var{\ave{\mcal{H}_\mcal{A}}}
+	\end{equation}
+	This is the holographic realization of the first law of entanglement.
+
 	With a final integration w.r.t.~$\var{T}$ in the phase phase, we recover the resulting charge, which agrees with the entanglement entropy in \cite{Rangamani:2016dms} up to an overall constant shift:
@@
 
+\subsection{Field theory side calculation}
+
 \FloatBarrier

### 2021-06-03 alpha/CutoffModularFlow/cutoffModular-alpha.tex
Add comments on entropy density & update build.sh

@@
 
-	Here we think of $f$ as a simple coordinates transformation or diffeomorphism, which keeps the metric $\dd{s}^2$ invariant, and maps the flat coordinates to a conformally flat coordinates:
+	Here we think of $f$ as a simple coordinates transformation or diffeomorphism, which keeps the metric $\dd{s}^2$ invariant, and maps the flat coordinates to the conformally flat coordinates:
 	\begin{equation}
@@
 	\end{equation}
+	Here we've properly rescaled the $\tilde{x}$ coordinate to make the $(\tau,\tilde{x})$ coordinates conformally flat.
 
@@
 		S_\mcal{A}
-%		= s\,\norm{f(\mcal{A})}_{\tilde{\mcal{R}}}
-		= \frac{c}{6}\,\norm{f(\mcal{A})}_{\tilde{\mcal{R}}}
-	\end{equation}
-	Here $\norm{f(\mcal{A})}_{\tilde{\mcal{R}}}$ denotes the $\tilde{R}$ length of the interval $f(\mcal{A})$:
-	\begin{equation}
-		\norm{f(\mcal{A})}_{\tilde{\mcal{R}}}
+		= \frac{c}{6} \tilde{L}
+	\end{equation}
+	Here $\tilde{L}$ denotes the $\tilde{\mcal{R}}$ length of the interval $f(\mcal{A})$:
+	\begin{equation}
+		\tilde{L}
 		= \int_{f(\mcal{A})} \dd{\tilde{s}}
@@
 	\end{equation}
+
+	In the above arguments we rely on the fact that the thermal entropy density of a CFT is given by $
+		\frac{c}{6}
+	$. This can be derived from the Cardy formula\footnote{
+		The easiest way to see this is by applying the AdS/CFT dictionary, where we find that $c = \frac{3\ell_\mrm{AdS}}{2G_N}$ thus $\frac{c}{6} = \frac{\ell_\mrm{AdS}}{4G_N}$, which is precisely the Bekenstein--Hawking entropy (per unit area, with $\ell_\mrm{AdS} = 1$).
+But now we are committed to a purely field theoretical calculation, so we shall reproduce Cardy's arguments here, which do not rely on holographic duality.
+	}.
+First note that by rescaling the Rindler map $f$ we can tune the temperature of the Rindler spacetime $\mcal{R}$ to be arbitrarily high.
+We've chosen $\beta_\tau = 2\pi$ only for convenience.
+\sidenote{[is this argument valid?
+check!]} Therefore we may apply the high temperature (or low $\beta$) limit of the Cardy formula; namely, by modular invariance of the partition function, we have:
+	\begin{equation}
+	\begin{aligned}
+		Z[\tau = i\tfrac{\beta}{2\pi}]
+		&= Z[-\tfrac{1}{\tau} = i\tfrac{2\pi}{\beta}],
+	\\[1ex]
+		Z[\beta]
+		&= Z[\beta\to \tfrac{4\pi^2}{\beta}] \\
+		&= \Tr e^{
+			-\frac{4\pi^2}{\beta} \pqty{
+				L_0 + \tilde{L}_0 - \frac{c}{12}
+			} \frac{\tilde{L}}{2\pi}
+		}, \quad \beta\ll 1 \\
+		&\sim e^{
+			\frac{4\pi^2}{\beta}
+			\frac{c}{12}
+			\frac{\tilde{L}}{2\pi}
+		}
+		= e^{
+			\frac{2\pi}{\beta}
+			\frac{c}{12} \tilde{L}
+		},
+	\end{aligned}
+	\end{equation}
+	Here we've used the saddle point approximation and assumed that the vacuum (the $h = \tilde{h} = 0$ state) contribution dominates. The entropy is thus given by:
+	\begin{equation}
+		S = \pqty{
+				1 - \beta\, \pdd{\beta}
+			} \log Z[\beta]
+		= \frac{2\pi}{\beta} \frac{c}{6} \tilde{L}
+	\end{equation}
+	With $\beta = \beta_\tau = 2\pi$, we recover the result $
+		S = \frac{c}{6} \tilde{L}
+	$.
 

### 2021-06-03 build.sh

@@ -14,7 +14,9 @@ mkdir -p release
 # naming: $project/$sub_project/$main.tex
 FILES=$(find . \
     -regex "./[^/]+/[^/]+/[^/]+\.tex" \
-    -not -path "./TeXplates/*" | sort
+    -not -path "./TeXplates/*" \
+    | sort \
+    | grep -v -E "CutoffModularFlow|AreaTTbar|GravitationalEntropy"
 )
 log "Files:"
 echo "$FILES"

### 2021-06-05 alpha/CutoffModularFlow/draft1.tex
Rename alpha document to draft

--- 2021-06-03 alpha/CutoffModularFlow/cutoffModular-alpha.tex
@@
 This seems to suggest that there is no canonical way to embed the entire time-evolved deformed field theory into the bulk.
-The best we can do is to embed the causal diamond $\mcal{D}(\mcal{A})$ (\sidenote{and maybe $\mcal{D}(\mcal{A})$}), given an interval $\mcal{A}$.
+The best we can do is to embed the causal diamonds $\mcal{D}(\mcal{A}) \cup \mcal{D}(\bar{\mcal{A}})$, given an interval $\mcal{A}$ and its complement $\bar{\mcal{A}}$.
 This is the price we have to pay for SSA to hold.

### 2021-06-06 alpha/Ising/ising.tex
Add notes on Ising model

% !TeX document-id = {b5392a94-51a3-49d1-9ba5-698bc09f9d35}
% !TeX encoding = UTF-8
% !TeX spellcheck = en_US
% !TeX TXS-program:bibliography = biber -l zh__pinyin --output-safechars %

\documentclass[a4paper
	,10pt
%	,twoside
]{article}

\input{../preamble.tex}
\input{../.modules/basics/biblatex.tex}

\title{Understanding the Ising CFT}
\addbibresource{ising.bib}

%%% ID: sensitive, do NOT publish!
\InputIfFileExists{id.tex}{}{}

\makeatletter
\newcommand{\nobeginpar}{\@beginparpenalty=10000}
\makeatother

\begin{document}
\maketitle
\pagenumbering{arabic}
\thispagestyle{empty}

%\vspace*{-.5\baselineskip}

\setlength{\parskip}{.1\baselineskip}
\tableofcontents
\setlength{\parskip}{\parskipnorm}

\addtocounter{section}{-1}
\section{References}
\raggedright
	\begin{itemize}
	\item \cite{Atanasov:2017abc}~\fullcite{Atanasov:2017abc}
		\begin{itemize}
		\item \textbf{Appendix E} of: \par
		\cite{Belavin:1984vu}~\fullcite{Belavin:1984vu}.

		\item \textbf{Section \Romannum{4}} of: \par
		\cite{Kogut:1979wt}~\fullcite{Kogut:1979wt}.

		\item \textbf{Chapter 5} of:\par
		\cite{Fradkin:1991nr}~\fullcite{Fradkin:1991nr}.

		\end{itemize}
	\end{itemize}
\justifying

\section{Primaries and their physical meanings}
	Primaries:
	\begin{itemize}[noitemsep]
	\item $\idty$
	\item Spin field: $\sigma(z,\bar{z})$ w/ weight $(\frac{1}{16},\frac{1}{16})$
	\item Energy operator: $\epsilon(z,\bar{z})$ w/ weight $(\frac{1}{2},\frac{1}{2})$
	\end{itemize}
	Question: how do we get this?
	One can answer this question through bootstrap, namely under the constraints of conformal symmetry and unitarity, this is the only possible situation for a $c = \tilde{c} = \frac{1}{2}$ CFT. But this doesn't quite explain the physical meaning of these fields.

	To really understand the physical origin, we have to go back to the lattice model. Taking the continuous limit of the lattice model is quite a subtle process. We will summarize this procedure here, in a very rough and very schematic language. For a detailed account with exact equations, see e.g.~\cite{Atanasov:2017abc,Kogut:1979wt,Fradkin:1991nr}. 
\subsection{Ising model on the lattice}
	First, we start with the 2D Ising action, with the field $s(x,\tau) = \pm\frac{1}{2}$, defined on a square lattice labeled by $(x,\tau)$. Consider:
	\begin{equation}
		\mcal{Z} = \int \DD{s} e^{-S[s]}
	\end{equation}
	It can be interpreted in the following 2 ways:
	\begin{enumerate}
	\item If we think of $\tau$ as another spatial direction, then $\mcal{Z}$ is precisely the \textbf{classical partition function} of this 2D lattice. The inverse temperature $\beta$ is related with the coupling of the system. When it's tuned to the critical point, we have a CFT.

	\item Alternatively, if the column direction is interpreted as the Euclidean time $\tau$, while the row direction is interpreted as the only spatial direction $x$, then this is the \textbf{Euclidean path integral} of a quantum system, where $\beta$ is the size of the $\tau$ circle. 
	\end{enumerate}

	Some choose to call this the \textit{quantum--classical correspondence}\footnote{
		See \cite{Simmons-Duffin:2016gjk} and \url{https://mcgreevy.physics.ucsd.edu/s19/2019-215C-lectures.pdf}. 
	}. Here we shall take the second perspective, and the Hilbert space consists of the 2-component Pauli spinor $s(x)$ located at each site~$x$.

	We first take the continous $\tau$ limit by switching to the Hamiltonian description. We then rewrite the time evolution using the \textit{transfer matrix}:
	\begin{equation}
		e^{-\tau H}
	\end{equation}
	Where $H$ is a $2\times 2$ matrix acting on the vector space of $s(x,\tau)$ values. 
	$H[\sigma^\pm]$ can be written down explicitly using the Pauli matrices $\sigma^\pm$, and it is in fact $\tau$-independent. Roughly speaking, we have:
	\begin{equation}
		\sigma \sim \sigma^z
		= 2\sigma^+ \sigma^- - 1
	\end{equation}

	Note that the original Ising action contains only the $s \sim s^z$ field, with no mention of the $s^x,s^y$ or $s^\pm$ component. Why do we have $\sigma^\pm$ now? In fact, this captures the dynamics of spin flips and serves as the momentum term in the Hamiltonian.

	Note that $H = H[\sigma^\pm]$ itself closely resembles a 1D Ising model with $s$ replaced by $\sigma$, defined along the one spatial direction: $\sigma = \sigma(x)$. 
	Some would like to call it the 1D ``quantum'' Ising model, and call this the correspondence between the 2D ``classical'' model and the 1D ``quantum'' model. But we see here that this is simply the Lagrangian and Hamiltonian descriptions of the same system.

\subsection{Fermionization by Jordan--Wigner}

	Why the central charge is only $\frac{1}{2}$? We are looking at Weyl fermions. $\mrm{Ising}^2$ is $c = \tilde{c} = 1$ free boson CFT, with the usual fermionization as in string theory.

\vspace{1.2\baselineskip}
\pagebreak[4]
\raggedright
\printbibliography[%
%	title = {参考文献} %
	,heading = bibintoc
]
\end{document}

### 2021-06-09 Strings2020/strings5/strings5.tex
Fix $tex_program handling in compile.sh
Clean up preambles, update templates
Tweak strings homework
Add comments on string partition function & more

@@
 %%% ID: sensitive, do NOT publish!
-\InputIfFileExists{../id.tex}{}{}
-
-\newcommand{\oppower}[2]{\mop{{#1}^{#2}}\!}
-\newcommand{\sqsinh}{\oppower{\sinh}{2}}
-\newcommand{\sqcosh}{\oppower{\cosh}{2}}
-
-\newcommand{\Vir}{\mathbf{V}\mfrak{ir}}
+%\InputIfFileExists{../id.tex}{}{}
+
 \newcommand{\zbar}{\bar{z}}
-\usepackage{tikz-feynman,cancel}
 
@@
 
-	Using the expressions in (a), we find that $L_0$ action on a state $\ket{\psi}$ created by $\alpha_{-l},\tilde{\alpha}_{-l}$ yields the sum of occupation numbers $N_l$ weighted by $l$:
+	Note that here we are working in the grand canonical ensemble, where we have temperature $\beta = 2\pi\tau_2$ and chemical potential $2\pi\tau_1$.
+At this stage $P$ is \textit{not} fixed, and we should sum over all states with various $P$.
+To go to the canonical ensemble, we do a Legendre transform and trade $\tau_1$ for some $P_0$.
+This is implemented by a Laplace / Fourier transform $\int \dd{\tau_1} e^{-i\,(2\pi\tau_1) P_0}$ of the partition function.
+
+	In string theory, we should actually work with the canonical ensemble (and eventually, the \textit{micro-}canonical ensemble), since we would like to impose the \textit{level matching condition}, namely $P_0 = 0$.
+
+	However, in string theory, the Legendre transform is implicit as we integrate along $\tau_1$ in the moduli space; roughly speaking, we have:
+	\begin{equation}
+		\int \dd{\tau_1} e^{-i\,(2\pi\tau_1) (P - 0)}
+		\propto \delta(P - 0)
+	\end{equation}
+	As $\tau_1$ gets integrated out, we are effectively computing $\Tr' e^{-\beta H}$ where the trace only goes over the $P = 0$ sector of the Hilbert space\footnote{
+		This is nicely explained in David Tong's \href{https://www.damtp.cam.ac.uk/user/tong/string.html}{\textit{String Theory}}.
+See also section 6.3 of Blumenhagen et al, \textit{Basic Concepts of String Theory}.
+	}.
+
+	On the other hand, since we are computing the grand partition function $Z(\tau_1 + i\tau_2)$ for now, we should \textit{not} impose the level matching condition, and the sum should go over all states with various $P$, although this is a much larger Hilbert space than the physical $P = 0$ subspace in string theory.
+
+	Using the expressions in (a), we find that $L_0$ action on a state $\ket{\psi}$ created by $\alpha_{-l},\tilde{\alpha}_{-l}$ yields the sum of occupation number $N_l$ weighted by $l$:
 	\begin{equation}
@@
 	The sum, on the other hand, is naturally invariant under $T\colon \tau \mapsto \tau + 1$, by making a change of variables $m \mapsto m + w$.
-It is also invariant under $S\colon \tau \mapsto -1/\tau$ with $m \mapsto −w, w \mapsto m$\,\footnote{
+It is also invariant under $S\colon \tau \mapsto -1/\tau$ with $m \mapsto -w, w \mapsto m$\,\footnote{
 		Reference: \textit{Polchinski}. 
@@
 				\ket{(N_l),(\tilde{N}_l);n,w}
-			\longmapsto (−1)^{\sum_l (N_l + \tilde{N}_l)}
+			\longmapsto (-1)^{\sum_l (N_l + \tilde{N}_l)}
 				\ket{(N_l),(\tilde{N}_l);-n,-w}
@@
 			\prod_{l>0} \sum_{N_l,\tilde{N}_l = 0}^\infty
-				(−1)^{N_l + \tilde{N}_l}
+				(-1)^{N_l + \tilde{N}_l}
 				q^{l\cdot N_l}
@@
 			\sum_{N_l,\tilde{N}_l = 0}^\infty
-				\frac{1 + (−1)^{N_l + \tilde{N}_l}}{2}\,
+				\frac{1 + (-1)^{N_l + \tilde{N}_l}}{2}\,
 				q^{l\cdot N_l}
@@
 		}
-		= \int \DD b\,\DD \tilde{b}\,
-				\DD c\,\DD \tilde{c}\ %
+		= \int \DD{b} \DD{\tilde{b}}
+				\DD{c} \DD{\tilde{c}}\,
 			c(w_1)\,b(w_2)\,
@@
 		\sim \det P
-		\sim \int \DD b\,\DD \tilde{b}\,
-				\DD c\,\DD \tilde{c}\ e^{-S'},\\
+		\sim \int \DD{b} \DD{\tilde{b}}
+				\DD{c} \DD{\tilde{c}} e^{-S'},\\
 		S'
@@
 		Z'
-		\sim \int \DD b\,\DD \tilde{b}\,
-				\DD c\,\DD \tilde{c}\ %
+		\sim \int \DD{b} \DD{\tilde{b}}
+				\DD{c} \DD{\tilde{c}}\,
 			c_0 b_0
@@
 		\sim \pqty{\frac{1}{\sqrt{\tau_2}}}^{\!\!4}\!\!
-			\int \DD' b\,\DD' \tilde{b}\,
-				\DD' c\,\DD' \tilde{c}\ %
+			\int \DD{'b} \DD{'\tilde{b}}
+				\DD{'c} \DD{'\tilde{c}}\,
 			e^{-S'},\quad
-		\int \DD' c
+		\int \DD{'c}
 		\sim \prod_{m\ne 0} \int \dd{c_m}

### 2021-06-09 alpha/Ising/ising.tex
Add comments on string partition function & more

@@
 	Some choose to call this the \textit{quantum--classical correspondence}\footnote{
-		See \cite{Simmons-Duffin:2016gjk} and \url{https://mcgreevy.physics.ucsd.edu/s19/2019-215C-lectures.pdf}. 
+		See \cite{Simmons-Duffin:2016gjk} and \https{mcgreevy.physics.ucsd.edu/s19/2019-215C-lectures.pdf}, and also \href{https://mcgreevy.physics.ucsd.edu/s14/239a-lectures.pdf}{\texttt{/s14/239a-lectures.pdf}}.
 	}. Here we shall take the second perspective, and the Hilbert space consists of the 2-component Pauli spinor $s(x)$ located at each site~$x$.

### 2021-06-10 alpha/CutoffModularFlow/draft1.tex
Add appendix to draft
Remove usual AdS/CFT flow (moved to appendix)
Rename bib file for cutoff modular flow
Restructure note on cutoff modular flow

@@
 
-	\item[] In Section 1,
+%	\item[] In Section 1,
 
@@
 
-	\item[] In Section 2,
+%	\item[] In Section 2,
 
@@
 
-\section{Zero temperature: modular flow in the Poincar\'e patch}
-
-\subsection{Review of the general recipe}
+\section{Introduction}
+
+\section{Boundary story}
 	A boundary interval $\mcal{A}$ defines a denisty matrix:
@@
 		\xi = 2\pi \pdd{\tau}
-		= 2\pi \sum_i a^i H_i,
+		= 2\pi \sum_i s^i H_i,
 	\quad
@@
 The causal domain of dependence $\mcal{D}$ is mapped to some thermal state with normalized inverse temperature $\beta_\tau = 2\pi$.
-Here we choose to absorb such $2\pi$ into the definition of $\xi$, so the Euclidean periodicity w.r.t.~$\xi$ is simply $\beta_\xi = 1$, which means the surface gravity along the horizon is given by:
-	\begin{equation}
-		\kappa_\xi = \frac{2\pi}{\beta_\xi} = 2\pi,
-	\quad
-		\beta_\xi = 1
+Here we choose to absorb such $2\pi$ into the definition of $\xi$, so the Euclidean periodicity w.r.t.~$\xi$ is simply normalized to 1, which means the surface gravity along the horizon is given by:
+	\begin{equation}
+		\kappa_\xi = 2\pi
+	\end{equation}
+\subsection{Boundary modular flows}
+	In usual $\mrm{CFT}_2$, this prescription gives us the modular flow generators for a single interval $\mcal{A}$:
+	\begin{equation}
+		\xi_\mrm{CFT} = 2\pi \sum_{n=0,\pm 1} \pqty{
+				s_n L_n - \tilde{s}_n \tilde{L}_n
+			},
+	\end{equation}
+	\begin{equation}
+		s_{-1} = \frac{u_+ u_-}{u_+ - u_-},\quad
+		s_0 = - \frac{u_+ + u_-}{u_+ - u_-},\quad
+		s_{+1} = \frac{1}{u_+ - u_-}
+	\end{equation}
+	Where the $H_i$'s are given by $L_n,\tilde{L}_n$ with $n=0,\pm 1$, i.e.~the global conformal generators, and $(u,v)_\pm$ or $(t,x)_\pm$ marks the endpoints of the interval $\mcal{A}$.
+The overall coefficient $2\pi$ is fixed by requiring that $\kappa_\xi = 2\pi$.
+
+	For simplicity, we now restrict to an interval centered at the origin: $
+		u_\pm v_\pm
+		= x^2_\pm - t^2_\pm
+		= (\frac{L_\mrm{CFT}}{2})^2
+	$, where $x_\pm = -x_\mp$, and same for $t_\pm, u_\pm, v_\pm$. 
+	We then introduce the \textit{rapidity} $\theta$ to nicely parametrized the boosted interval. For a constant time slice, we have $\theta = 0$. For a general boosted interval, we have:
+	\begin{equation}
+		x_\pm = \pm \frac{L_\mrm{CFT}}{2} \cosh \theta,
+	\quad
+		t_\pm = \pm \frac{L_\mrm{CFT}}{2} \sinh \theta,
+	\end{equation}
+	Note that the RT surface lies on the plane $
+		t_\pm / x_\pm = \tanh \theta
+	$, namely $\theta$ is constant along the RT surface. 
+	We have:
+	\begin{gather}
+	\begin{aligned}
+		\xi_\mrm{CFT} &= \frac{2\pi}{L_\mrm{CFT}} \bigg\{
+			\pqty\Big{
+				\pqty{
+					(\tfrac{L_\mrm{CFT}}{2})^2
+					- (t^2 + x^2)
+				} \cosh\theta
+				+ 2tx \sinh\theta
+			} \,\pdd{t}
+		\\ &\qquad\qquad 
+			+ \pqty\Big{
+				\pqty{
+					(\tfrac{L_\mrm{CFT}}{2})^2
+					+ (t^2 + x^2)
+				} \sinh\theta
+				- 2tx \cosh\theta
+			} \,\pdd{x}
+		\bigg\}
+	\end{aligned}
+	\end{gather}
+	Suppose the interval $\mcal{A}$ lies on the constant $t = 0$ slice; around the constant $t = 0$ slice, the modular flow becomes:
+	\begin{equation}
+		\xi_\mrm{CFT}|_{t = 0} 
+		= \frac{2\pi}{L_\mrm{CFT}}
+			\pqty{
+				\pqty{\frac{L_\mrm{CFT}}{2}}^2
+				- x^2
+			} \,\pdd{t}
+	\end{equation}
+
+	However, after the $T\bar{T}$-deformation, the scaling and special conformal transformations are no longer symmetries of the theory, so we cannot simply take $\xi_\mrm{CFT}$ as the modular flow in the deformed theory.
+
+	On the other hand, we still expect the basic properties of the modular flow to hold after the deformation; for example, we expect the endpoints $\pd\mcal{A}$ of $\mcal{A}$ to be fixed under the modular flow, and we suppose the $\xi_{T\bar{T}}$ should reduce back to $\xi_\mrm{CFT}$ as the deformation parameter $\lambda \to 0$.
+This leads us to the following proposal of $\xi_{T\bar{T}}|_{t = 0}$, for an interval $\mcal{A}$ with coordinate length $L$:
+	\begin{equation}
+		\xi_{T\bar{T}}|_{t = 0} 
+		= \frac{2\pi}{\sqrt{L^2 + 8\lambda}}
+			\pqty{
+				\pqty{\frac{L}{2}}^2
+				- x^2
+			} \,\pdd{t}
+	\end{equation}
+	Note that:
+	\begin{enumerate}[topsep=0pt]
+	\item The dependence of $\xi_{T\bar{T}}|_{t = 0}$ w.r.t.~$L$ is very similar to the dependence of $\xi_\mrm{CFT}|_{t = 0}$ w.r.t.~$L_\mrm{CFT}$, except that now the normalization is slightly modified to include the deformation parameter $\lambda$.
+	\item This is not yet a proposal for the full modular flow, but only its values around the $t = 0$ slice.
+But we shall see that this is enough to give us the entanglement entropy of a $T\bar{T}$-deformed theory.
+	\end{enumerate}
+
+\subsection{Effective local temperature and entanglement entropy}
+
+	We note that there is a trick to read out the entanglement entropy from the modular flow: it is possible to define a \textit{local entanglement temperature}, and then use it to read the entanglement entropy from the modular flow generator \cite{Wong:2013gua,Cardy:2016fqc}.
+The result is obtained by comparison with the Hamiltonian of a thermal field theory, where we have:
+	\begin{equation}
+	\mcal{H}=\int \beta\,T_{00}\,dx,\quad \beta = 2\pi,
+	\quad \xi|_{t=0} = \beta\,\pdd{t}
+	\label{eq:beta_thermal}
+	\end{equation}
+	On the other hand, the modular Hamiltonian is given by:
+	\begin{equation}
+	\mcal{H}_\mcal{A}=\int \beta(x)\, T_{00}\,dx,\quad \xi|_{t=0} = \beta(x)\, \pdd{t}
+	\end{equation}
+
+	Let's see this trick in action in CFT$_2$; the \textit{entropy density} is given by:
+	\begin{equation}
+	s = \frac{c}{6} \frac{2\pi}{\beta(x)}
+	\end{equation}
+	in terms of the effective inverse temperature $\beta(x)$, and the total entropy of the interval $\mcal{A}$ is given by:
+	\begin{equation}
+	S = \frac{c}{6}
+		\int_\mcal{A} \frac{2\pi}{\beta(x)} \dd{x}
+	\end{equation}
+
+	For example, for a single interval in CFT$_2$,
+	\begin{equation}
+		\beta(x)
+		= \frac{2\pi}{L_\mrm{CFT}}
+			\pqty{
+				\pqty{\frac{L_\mrm{CFT}}{2}}^2
+				- x^2
+			} \,\pdd{t}
+	\end{equation}
+	\begin{equation}
+	S= \frac{c}{3} \int_{-L_\mrm{CFT}/2}^{L_\mrm{CFT}/2}
+			\frac{L_\mrm{CFT}/2}{(L_\mrm{CFT}/2)^2-x^2}dx,
+	\end{equation}
+	The indefinite integral $
+		\int \frac{L_\mrm{CFT}/2}{(L_\mrm{CFT}/2)^2-x^2}dx
+		= \mop{arctanh}\frac{2x}{L_\mrm{CFT}}
+%		\rightarrow\mrm{CFT}
+	$ diverges as $x\rightarrow L_\mrm{CFT}/2$, so one needs a cutoff:
+	\begin{equation}
+	S=\frac{c}{3}\int_{-L_\mrm{CFT}/2+\epsilon}^{L_\mrm{CFT}/2-\epsilon}
+		\frac{L_\mrm{CFT}/2}{(L_\mrm{CFT}/2)^2-x^2}dx
+	=\frac{2c}{3} \mop{arctanh} \pqty{
+			1-\frac{2\epsilon}{L_\mrm{CFT}}
+		}
+	\end{equation}
+	As $\epsilon\rightarrow 0$,
+	\begin{equation}
+		\mop{arctanh} \pqty{
+			1-\frac{2\epsilon}{L_\mrm{CFT}}
+		}\rightarrow \frac{1}{2}\log\frac{L_\mrm{CFT}}{\epsilon}
+	\end{equation}
+	So we get the usual result
+	\begin{equation}
+	S=\frac{c}{3}\log\frac{L_\mrm{CFT}}{\epsilon}
+	\end{equation}
+
+	Now for the cutoff field theory living at the boundary, where
+	\begin{equation}
+		\beta(x) = \frac{2\pi}{\sqrt{L^2 + 8\lambda}}
+			\pqty{
+				\pqty{\frac{L}{2}}^2
+				- x^2
+			} \,\pdd{t}
+	\end{equation}
+	The entanglement entropy is
+	\begin{equation}
+	S=\frac{c}{6}\mop{arctanh}\frac{2x}{\sqrt{L^2 + 8\lambda}}\Big|_{x=-L/2}^{x=L/2}
+	=\frac{c}{3}\mop{arctanh}\frac{L}{\sqrt{L^2 + 8\lambda}}
+	=\frac{c}{3}\mop{arcsinh}\frac{L}{2\sqrt{2\lambda}}
+	\end{equation}
+	with the Casini--Huerta $C(L)$-function:
+	\begin{equation}
+	C(l)=\frac{c}{3}\frac{1}{\sqrt{1+\frac{8\lambda}{L^2}}}
+	\end{equation}
+	Which agrees with \cite{Lewkowycz:2019xse}. \sidenote{This provides a field theory side calculation of the cutoff entanglement entropy, based on the input of the modular flow $\xi$. }
+	Note that we only need to know the modular flow $\xi$ along the $t = 0$ slice. We don't need to know the full modular flow\footnote{
+		\sidenote{This seems to be consistent with holographic entropy, a la Lewkowycz--Maldacena \cite{Lewkowycz:2013nqa}, where the charge only depends linearly on $\xi$ along the RT surface, as long as $\xi$ is a Killing vector.
+See \eqref{kdef}.
+}
+	}.
+
+	The validity of this trick can be argued from the Rindler map; suppose we have the following Rindler map at the boundary:
+	\begin{equation}
+	\begin{aligned}
+		f\colon
+		\mcal{D}(\mcal{A})
+		&\longto \mcal{R} = S^1_\beta \times f(\mcal{A}), \\
+		(t,x)
+		&\longmapsto (\tau,\tilde{x}),
+	\end{aligned}
+	\end{equation}
+	Here $f(\mcal{A})$ is the image of the boundary interval.
+$f$ by construction ``normalizes'' the temperature for the modular generator, namely, the modular flow $\xi$ is now realized as the pullback of $2\pi\pdd{\tau}$:
+	\begin{equation}
+		\xi = \xi^\mu \pdd{\mu}
+		= 2\pi\pdd{\tau}
+	\end{equation}
+	In particular, along the interval $\mcal{A}$ at the $t = 0$ time slice, we have:
+	\begin{equation}
+		\xi|_{t = 0}
+		= \beta(x)\,\pdd{t}
+		= 2\pi\pdd{\tau},
+	\quad
+		\pdv{t}{\tau}
+		= \frac{\beta(x)}{2\pi}
+	\end{equation}
+	Note that although $\xi$ is a Killing vector when it's extended to the bulk, it is only a \textit{conformal Killing vector} when it's restricted to the boundary.
+
+	Here we think of $f$ as a simple coordinates transformation or diffeomorphism, which keeps the metric $\dd{s}^2$ invariant, and maps the flat coordinates to the conformally flat coordinates:
+	\begin{equation}
+		\dd{s}^2
+		= \dd{t}^2 + \dd{x}^2
+		= \Omega^2(\tau,\tilde{x}) \pqty{
+				\dd{\tau}^2 + \dd{\tilde{x}}^2
+			},
+	\quad
+		\Omega_{t = 0} = \pdv{t}{\tau}
+		= \frac{\beta(x)}{2\pi}
+	\end{equation}
+	Here we've properly rescaled the $\tilde{x}$ coordinate to make the $(\tau,\tilde{x})$ coordinates conformally flat.
+
+	In the case where the theory is conformally invariant, one can further drop the conformal factor $\Omega^2(\tau,\tilde{x})$ from the metric, while the thermal entropy of the system remains unchanged.
+We now have a flat annulus:
+	\begin{equation}
+		\tilde{\mcal{R}}
+		= S^1_\beta \times [0,\tilde{L}],
+	\quad
+		\dd{\tilde{s}}^2
+		= \frac{1}{\Omega^2} \dd{s}^2
+		= \dd{\tau}^2 + \dd{\tilde{x}}^2
+	\end{equation}
+	This is the corresponding geometry of a thermal partition function, with a constant temperature $\beta_\tau = 2\pi$. 
+	Now $\pdd{\tau}$ is truly a Killing vector of $\tilde{\mcal{R}}$. 
+	In this case the thermal entropy is extensive: the total entropy $S_\mcal{A}$ is proportional to the size of the system:
+	\begin{equation}
+		S_\mcal{A}
+		= \frac{c}{6} \tilde{L}
+	\end{equation}
+	Here $\tilde{L}$ denotes the $\tilde{\mcal{R}}$ length of the interval $f(\mcal{A})$:
+	\begin{equation}
+		\tilde{L}
+		= \int_{f(\mcal{A})} \dd{\tilde{s}}
+		= \int_{f(\mcal{A})} \frac{\dd{s}}{\Omega}
+		= \int_{\mcal{A}} \frac{\dd{s}}{\Omega}
+		= \int_{\mcal{A}} \frac{2\pi}{\beta(x)} \dd{x}
+	\end{equation}
+	We've used the fact the $f$ is a diffeomorphism, to reduce the integral back to an integral along $\mcal{A}$ in the original coordinates. 
+	The entropy is thus given by:
+	\begin{equation}
+		S_\mcal{A}
+		= \frac{c}{6}
+			\int_{\mcal{A}} \frac{2\pi}{\beta(x)} \dd{x}
+	\end{equation}
+
+	In the above arguments we rely on the fact that the thermal entropy density of a CFT is given by $
+		\frac{c}{6}
+	$. This can be derived from the Cardy formula\footnote{
+		The easiest way to see this is by applying the AdS/CFT dictionary, where we find that $c = \frac{3\ell_\mrm{AdS}}{2G_N}$ thus $\frac{c}{6} = \frac{\ell_\mrm{AdS}}{4G_N}$, which is precisely the Bekenstein--Hawking entropy (per unit area, with $\ell_\mrm{AdS} = 1$).
+But now we are committed to a purely field theoretical calculation, so we will apply Cardy's arguments here, which do not rely on holographic duality.
+	}, where we have: 
+%	First note that by rescaling the Rindler map $f$ we can tune the temperature of the Rindler spacetime $\mcal{R}$ to be arbitrarily high.
+We've chosen $\beta_\tau = 2\pi$ only for convenience.
+\sidenote{[is this argument valid?
+check!]}
+%	Therefore we may apply the high temperature (or low $\beta$) limit of the Cardy formula; namely, by modular invariance of the partition function, we have:
+%	\begin{equation}
+%	\begin{aligned}
+%		Z[\tau = i\tfrac{\beta}{2\pi}]
+%		&= Z[-\tfrac{1}{\tau} = i\tfrac{2\pi}{\beta}],
+%	\\[1ex]
+%		Z[\beta]
+%		&= Z[\beta\to \tfrac{4\pi^2}{\beta}] \\
+%		&= \Tr e^{
+%			-\frac{4\pi^2}{\beta} \pqty{
+%				L_0 + \tilde{L}_0 - \frac{c}{12}
+%			} \frac{\tilde{L}}{2\pi}
+%		}, \quad \beta\ll 1 \\
+%		&\sim e^{
+%			\frac{4\pi^2}{\beta}
+%			\frac{c}{12}
+%			\frac{\tilde{L}}{2\pi}
+%		}
+%		= e^{
+%			\frac{2\pi}{\beta}
+%			\frac{c}{12} \tilde{L}
+%		},
+%	\end{aligned}
+%	\end{equation}
+%	Here we've used the saddle point approximation and assumed that the vacuum (the $h = \tilde{h} = 0$ state) contribution dominates. The entropy is thus given by:
+	\begin{equation}
+		S
+%		= \pqty{
+%				1 - \beta\, \pdd{\beta}
+%			} \log Z[\beta]
+		= \frac{2\pi}{\beta} \frac{c}{6} \tilde{L}
+	\end{equation}
+	With $\beta = \beta_\tau = 2\pi$, we recover the result $
+		S = \frac{c}{6} \tilde{L}
+	$.
+
+	Note that in the above arguments we've assumed conformal symmetry, which we no longer have after a $T\bar{T}$ deformation.
+However, as we've demonstrated above, it seems that this trick still works for the deformed theory.
+\sidenote{Perhaps the reason is again, that the conformal factor vanishes at the endpoints, due to $2\pi$ periodicity of $\xi$, which we will show in later sections.
+}
+
+	***
+
+	In the thermal CFT$_2$,
+	\begin{equation}
+	w=e^{\frac{2\pi z}{\beta}}
+	\end{equation}
+	From this transformation between the cylinder and the plane, we can find the "local" temperature $\tilde{\beta}$
+	\begin{equation}
+	\tilde{\beta}(x)=2\pi\frac{sinh[\pi(x+l_b)/\beta]sinh[\pi(x-l_b)/\beta]}{sinh(2\pi l_b/\beta)}
+	\end{equation}
+	After integrating out,
+	\begin{equation}
+	f(x)=\frac{\log(sinh\frac{\pi(l_b+x)}{\beta})-\log(sinh\frac{\pi(l_b-x)}{\beta})}{2\pi}
+	\end{equation}
+	The relation between $l_b$ and $l$ comes from the gravitational side,
+	\begin{equation}
+	2l_b=Arccoth(\frac{r_c\cosh(lr_1/2)}{\sqrt{r_1^2+r_c^2\sinh^2(lr_1/2)}})/r_1
+	\end{equation}
+	where
+	\begin{equation}
+	r_1=\frac{2\pi}{\beta}
+	\end{equation}
+	is the outer horizon, and $r_c$ is the cutoff, related to the deformation parameter $\lambda$. The entanglement entropy reads,
+	\begin{equation}
+	S(L=2l)=\frac{\pi c}{6}(f(l)-f(-l))=\frac{c}{3}\log(\frac{r_c}{r_1}\sinh(l r_1)+\sqrt{1+\frac{r_c^2}{r_1^2}\sinh^2(l r_1)})
+	\end{equation}
+	The C-function is
+	\begin{equation}
+	C(l)=lS'(l)=\frac{c}{3}lr_1\coth(lr_1)\sqrt{\frac{r_c^2}{r_c^2+r_1^2csch^2(l r_1)}}
+	\end{equation}
+	\begin{equation}
+	C(L)=\frac{L\pi c}{3\beta}\coth\frac{L\pi}{\beta}\sqrt{\frac{1}{1+\frac{4\pi^2\epsilon^2}{\beta^2\sinh^2\frac{L\pi}{\beta}}}}
+	\end{equation}
+	In CFT
+	\begin{equation}
+	S(L)=\frac{c}{3}\log(\frac{\beta}{\pi \epsilon}\sinh\frac{L\pi}{\beta})
+	\end{equation}
+	\begin{equation}C(L)=\frac{L\pi c}{3\beta}\coth\frac{L\pi}{\beta}
+	\end{equation}
+
+\subsection{Rindler map in finite temperature}
+	One can use the method in (1909.13808) to calculate the entanglement entropy in the thermal case and finite size case from the field theory side.
+The Rindler transformation from the domain of dependence of the interval $(-l_p,l_p)$ to the sphere is
+	\begin{equation}
+	t=l_p\frac{\sin\theta \sinh(\tau/l_p)}{1+\sin\theta \cosh(\tau/l_p)},\ \  x=l_p\frac{\cos\theta}{1+\sin\theta\cosh(\tau/l_p)}
+	\end{equation}
+	the conformal factor reads,
+	\begin{equation}
+	\Omega=\frac{1}{1+\sin\theta\cosh(\tau/l_p)}
+	\end{equation}
+	At endpoints, it becomes $1$.
+From the discussion in (1909.13808), the contribution to the entanglement entropy totally comes from the endpoints of the interval, so one can use the such conformal transformation where the conformal factor at the endpoints is $1$ to calculate the entanglement entropy.
+Also, in the conformal map above from the casual diamond to the sphere, only the length of the interval matters.
+If these two endpoints lie at other position, one can use the rotation and translation symmetry to put it at $(0,\pm l_p)$, since the $T\bar T$ deformed theory also admits these symmetries.
+Now let's consider the thermal case, the conformal transformation from the thermal cylinder to the plane reads,
+	\begin{equation}
+	z=\frac{1}{ir_1}e^{ir_1w},\ \ \ r_1=\frac{2\pi}{\beta}
+	\end{equation} 
+	where $z$ is the coordinate on the plane, and $w$ is the coordinate on the thermal cylinder with identification,
+	\begin{equation}
+	w\sim w+\beta
+	\end{equation}
+	The endpoints of the interval on the thermal cylinder is
+	\begin{equation}
+	w=\pm l i
+	\end{equation} 
+	The length of the interval is $L=2l$. Under the conformal map, the endpoints on the plane is
+	\begin{equation}
+	\frac{1}{ir_1}e^{\mp r_1 l}
+	\end{equation}
+	the length is $\frac{2}{r_1}\sinh(l r_1)$, so
+	\begin{equation}
+	l_p=\frac{1}{r_1}\sinh(l r_1)
+	\end{equation}
+	The conformal factor is
+	\begin{equation}
+	e^{ir_1(w+\bar{w})}
+	\end{equation}
+	Note that compared to the usual map from cylinder to plane $z=e^{ir_1 w}$, we put the overall scaling factor $\frac{1}{ir_1}$ to make sure that the conformal factor at the endpoints is $1$.
+From 1806.07444, the entanglement entropy for $l_p$ is
+	\begin{equation}
+	S_p(l)=\frac{c}{3}ArcSinh\frac{l_p}{a}
+	\end{equation}
+	where
+	\begin{equation}
+	a^2=\frac{\mu c}{12}
+	\end{equation}
+	The C-function reads,
+	\begin{equation}
+	C(L)=L S'(L=2l)=\frac{c}{3}\frac{1}{\sqrt{1+4a^2/L^2}}
+	\end{equation}
+	Now in the thermal case, $l_p\rightarrow \frac{1}{r_1}\sinh(l r_1)$
+	\begin{equation}
+	S_t=\frac{c}{3}ArcSinh(\frac{1}{r_1 a}\sinh(l r_1))
+	\end{equation}
+	which is the same as the results obtained from the local temperature trick \eqref{} and the gravity calculation\eqref{}. Now consider the finite size case, the conformal transformation is,
+	\begin{equation}
+	z=\frac{1}{r_1}e^{wr_1}
+	\end{equation}
+	where $w$ is the cylinder coordinate,
+	\begin{equation}
+	w\sim w+i{\color{red} R}
+	\end{equation}
+	The endpoints of the interval are 
+	\begin{equation}
+	w\pm i l
+	\end{equation}
+	The conformal factor is
+	\begin{equation}
+	e^{r_1(w+\bar{w})}
+	\end{equation}
+	which is $1$ at the endpoints. The plane length reads,
+	\begin{equation}
+	l_p=\frac{1}{r_1}\sin lr_1
+	\end{equation}
+	So the final result is
+	\begin{equation}
+	S_f=\frac{c}{3}ArcSinh(\frac{1}{r_1a}\sin(lr_1))
+	\end{equation}
+	The global AdS reads,
+	\begin{equation}
+	 ds^2=-(r^2+1)dt^2+\frac{dr^2}{r^2+1}+r^2d\phi^2,\ \ \phi\sim\phi+2\pi
+	\end{equation}
+	\begin{equation}
+	\phi\rightarrow r1\phi,\ \ r\rightarrow \frac{r}{r_1}, \ \ \ t\rightarrow r_2 t
+	\end{equation}
+	\begin{equation}
+	 ds^2=-(r^2+r_1^2)dt^2+\frac{dr^2}{r^2+r_1^2}+r^2d\phi^2,\ \ \phi\sim\phi+\beta
+	\end{equation}
+	Compared to the planer BTZ,
+	\begin{equation}
+	ds^2=-(r^2-r_1^2)dt^2+\frac{dr^2}{r^2-r_1^2}+r^2dx^2
+	\end{equation}
+	For the holographic entanglement entropy
+	\begin{equation}
+	r_1\rightarrow ir_1
+	\end{equation}
+	There is no topological obstacle in global AdS, so one can do the replacement above to get the holographic entanglement entropy in global AdS from the HEE in planer BTZ.
+	\begin{equation}
+	S_f=\frac{c}{3}ArcSinh(\frac{1}{r_1a}\sin(lr_1))
 	\end{equation}
@@
 
-\subsection{Modular flow for Poincar\'e $\mrm{AdS}_3/\mrm{CFT}_2$}
-
-\textbf{Summary:} We follow the recipe from the swing surface proposal \cite{Apolo:2020bld,Apolo:2020qjm} to extend the boundary modular flow to the bulk, by matching symmetries of the bulk and the boundary.
-This reproduce known results such as \cite{Lashkari:2016idm,Czech:2019vih,Apolo:2020qjm} [more citations needed].
-
-\noindent\textbf{Mathematica:} \texttt{modFlowPoincare.nb}
-
-\subsubsection{Matching bulk and boundary symmetries}
-	In Poincar\'e $\mrm{AdS}_3/\mrm{CFT}_2$, the $H_i$'s are given by $L_n,\tilde{L}_n$ with $n=0,\pm 1$. At $z\to 0$ we recover the usual global $\mfrak{sl}(2,\mbb{R})$ generators:
-	\begin{equation}
-		z\to 0,
-	\quad
-		      L_n \to -u^{n+1} \pdd{u},\quad
-		\tilde{L}_n \to -v^{n+1} \pdd{v},\quad
-	n = 0,\pm 1
-	\end{equation}
-
-	To extend it to the bulk, think of the corresponding bulk isometries: translations, rotations, dilations and special conformal transformations:
-	\begin{equation}
-	\begin{aligned}
-		P_\mu
-		&= \pdd{\mu},\\
-		m_{uv}
-		&= x_\mu \pdd{\nu} - x_\nu \pdd{\mu}
-		= u\pdd{u} - v\pdd{v},\\
-		\Delta
-		&= X^I \pdd{I}
-		= u\pdd{u} + v\pdd{v} + z\pdd{z},\\
-		K_\mu
-		&= (z^2 + uv)\,\pdd{\mu}
-			- 2\eta_{\mu\nu} x^\nu \Delta,
-	\end{aligned}
-	\end{equation}
-	\begin{equation}
-		K_u = (z^2 + uv)\,\pdd{u} - v \Delta,
-	\quad
-		K_v = (z^2 + uv)\,\pdd{v} - u \Delta
-	\end{equation}
-	By requiring that a linear combination of these generators reduce to the boundary $L_n$'s, one can uniquely extend the $L_n,\tilde{L}_n$'s into the bulk.
+\section{Bulk story}
+	We follow the recipe from the swing surface proposal \cite{Apolo:2020bld,Apolo:2020qjm} to extend the boundary modular flow to the bulk, by matching symmetries of the bulk and the boundary.
+This reproduces known results in e.g.~\cite{Lashkari:2016idm,Czech:2019vih,Apolo:2020qjm} \sidenote{[more citations needed]}.
+We first compute everything in Poincar\'e $\mrm{AdS}_3$ for simplicity.
+\subsection{Bulk modular flows for Poincar\'e $\mrm{AdS}_3$}
+	By requiring that a linear combination of the bulk Killing vectors for Poincar\'e $\mrm{AdS}_3$ reduces to the boundary $L_n$'s, one can uniquely extend the $L_n,\tilde{L}_n$'s into the bulk.
 The result for $L_n$'s is listed below; for $\tilde{L}_n$ one need only exchange all $u\leftrightarrow v$.
@@
 	\end{equation}
-
-\subsubsection{RT surface and the modular flow}
-
-\textbf{Derivation of RT surface:} \\
- \url{https://bryango.github.io/resources/archive/HW-Gravity/gravity1.pdf}.
-
-	The RT surface (spacelike geodesic of Poincar\'e AdS with both ends attached to the boundary) is parametrized in terms of its end points $(t,x)_\pm$; it's the intersection of a AdS ``sphere'' (hyperboloid) and a plane through its center:
-	\begin{equation}
-	\begin{aligned}
-	\text{``sphere'':} &&&\mathsmaller{
-		z^2
-		+ \pqty{x - \frac{x_+ + x_-}{2}}^{\!\!2}
-		- \pqty{t - \frac{t_+ + t_-}{2}}^{\!\!2}
-		= \pqty{\frac{L_\infty}{2}}^{\!\!2}
-		= \pqty{\frac{x_+ - x_-}{2}}^{\!\!2}
-		- \pqty{\frac{t_+ - t_-}{2}}^{\!\!2}
-	},\\
-	&&& \text{i.e.}\ \,
-		L^2
-		= \pqty{x_+ - x_-}^2
-			- \pqty{t_+ - t_-}^2
-		= (u_+ - u_-)(v_+ - v_-),
-	\\[1.5ex]
-	\text{plane:} &&&
-		\frac{x - \frac{1}{2} (x_+ + x_-)}{x_+ - x_-}
-		= \frac{t - \frac{1}{2} (t_+ + t_-)}{t_+ - t_-}
-	\end{aligned}
-	\end{equation}
-	Alternatively, it can be more compactly rewritten with $x^\mu \sim (t,x)$ or $(u,v)$; mind the various $\pm$ signs in the expressions: 
-	\begin{equation}
-	\begin{aligned}
-		0 &= z^2
-			+ \eta_{\mu\nu} (x - x_+)^\mu (x - x_-)^\nu \\
-		& = z^2
-			+ (x - x_+)(x - x_-)
-			- (t - t_+)(t - t_-) \\
-		&= z^2 + \frac{
-				(u - u_+)(v - v_-)
-				+ (v - v_+)(u - u_-)
-			}{2}
-	\end{aligned}
-	\end{equation}
-
-	The bulk modular generator vanishes along the RT surface, i.e.~the RT surface is the fixed point of the modular flow; with this condition we can fix the coefficients of the modular generator, up to an overall coefficient\footnote{
-		One can compare this with similar results in the literature such as \cite{Lashkari:2016idm,Czech:2019vih,Apolo:2020qjm}. 
-	}:
+	With this dictionary the boundary modular flow can be simply mapped to the bulk:
 	\begin{equation}
@@
 	\end{equation}
-	\begin{equation}
-		s_{-1} = \frac{u_+ u_-}{u_+ - u_-},\quad
-		s_0 = - \frac{u_+ + u_-}{u_+ - u_-},\quad
-		s_{+1} = \frac{1}{u_+ - u_-}
-	\end{equation}
-	One need only exchange all $u\leftrightarrow v$ to obtain $\tilde{s}_n$.
-The overall coefficient of $\xi$ (in this case, $2\pi$) is fixed by normalizing the temperature of the horizon, namely we demand that the surface gravity is $2\pi$ along the RT surface:
-	\begin{equation}
-		\beta_\xi = \frac{2\pi}{\kappa_\xi} = 1,
-	\quad
+
+	Alternatively, we can re-derive the bulk modular generator from scratch by requiring that it vanishes along the RT surface, i.e.~the RT surface is the fixed point of the modular flow; with this condition we can fix the coefficients of the modular generator, up to an overall coefficient\footnote{
+		One can compare this with similar results in the literature such as \cite{Lashkari:2016idm,Czech:2019vih,Apolo:2020qjm}. 
+	}. See \autoref{sect:modFlowPoincare} for a detailed description. 
+	Again, the overall coefficient of $\xi$ (in this case, $2\pi$) is fixed by normalizing the temperature of the horizon; we demand that the surface gravity is $2\pi$ along the RT surface:
+	\begin{equation}
+%		\beta_\xi = \frac{2\pi}{\kappa_\xi} = 1,
+%	\quad
 		\kappa_\xi^2
@@
 	\end{equation}
-
-	\begin{figure}[!ht]
-%	\vspace{-1.5ex}
-	\centering
-	\includegraphics[width=.4\linewidth]{img/modFlowLorentzian.png}
-	\hspace{2em}
-	\includegraphics[width=.4\linewidth]{img/modFlowEuclidean.png}
-%	\vspace{-2ex}
-	\caption{Modular flow at the boundary, for an interval lying on a constant $t = 0$ slice, in Lorentzian and Euclidean signature}
-	\end{figure}
-
-\pagebreak[4]
-
-	We now restrict to an interval centered at the origin: $
+	Again, we restrict to an interval centered at the origin: $
 		u_\pm v_\pm
@@
 	$, where $x_\pm = -x_\mp$, and same for $t_\pm, u_\pm, v_\pm$. 
-	We then introduce the \textit{rapidity} $\theta$ to nicely parametrized the boosted interval; for a constant time slice, we have $\theta = 0$. For a general boosted interval, we have:
-	\begin{equation}
-		x_\pm = \pm \frac{L_\infty}{2} \cosh \theta,
-	\quad
-		t_\pm = \pm \frac{L_\infty}{2} \sinh \theta,
-	\end{equation}
+	$L_\infty$ is the coordinate length of the boundary interval $\mcal{A}$ at the asymptotic infinity; this corresponds to the field theory side $L_\mrm{CFT}$. 
 	For now the coordinates $u_\pm, v_\pm, x_\pm, t_\pm$ and the coordinate length $L_\infty$ are all specified at $z\to 0$, i.e.~at the \textbf{asymptotic boundary}.
@@
 
-\FloatBarrier
-\pagebreak
-\subsection{Cutoff $\mrm{AdS}_3$ and the loss of $2\pi$ periodicity}
+\subsubsection{Zero temperature: cutoff Poincar\'e $\mrm{AdS}_3$ and the loss of $2\pi$ periodicity}
 
@@
 		\rho = e^{-\beta\mcal{H}},
-	\quad \beta \sim 1 + \frac{1}{L^2} \order{\mu}
+	\quad \beta \sim 1 + \order{\lambda}
 	\end{equation}
@@
 \pagebreak
-\subsection{Restoring the $2\pi$ periodicity by following the flow}
+
+\subsubsection{Restoring the $2\pi$ periodicity by following the flow}
 
@@
 \pagebreak
-\subsection{Modular flow for the cutoff field theory}
-\textbf{Summary:} We try to obtain the entanglement entropy using the modular flow at the \mbox{codim-2} cutoff surface, using the \textit{effective inverse temperature $\beta(x)$} introduced in \cite{Cardy:2016fqc}, which relates the entanglement entropy to some thermal entropy.
-
-	From the field theory's perspective, the above calculations seem to suggest that the modular flow $\xi$ of [[ an $L$-sized interval in the cutoff theory ]] is given by the modular flow $\xi = \xi(L_\infty)$ of [[ a CFT for an $L_\infty$ interval ]].
-
-	We note that there is a trick to read out the entanglement entropy from the modular flow: it is possible to define a \textit{local entanglement temperature}, and then use it to read the entanglement entropy from the modular flow generator \cite{Cardy:2016fqc}.
-The result is obtained by comparing with the Hamiltonian of a thermal field theory, where we have:
-	\begin{equation}
-	\mcal{H}=\int \beta\,T_{00}\,dx,\quad \beta = 2\pi,
-	\quad \xi|_{t=0} = \beta\,\pdd{t}
-	\label{eq:beta_thermal}
-	\end{equation}
-	In general, the modular Hamiltonian is given by:
-	\begin{equation}
-	\mcal{H}_\mcal{A}=\int \beta(x)\, T_{00}\,dx,\quad \xi|_{t=0} = \beta(x)\, \pdd{t}
-	\end{equation}
-
-	Let's see this trick in action in CFT$_2$; the \textit{entropy density} is given by:
-	\begin{equation}
-	s_\mcal{A} = \frac{c}{3} \frac{\pi}{\beta(x)}
-	\end{equation}
-	in terms of the local entanglement temperature $\beta(x)$, and the total entropy of the interval $\mcal{A}$ is given by:
-	\begin{equation}
-	S= \frac{c}{3}
-		\int_\mcal{A} \frac{\pi}{\beta(x)}dx
-	\end{equation}
-
-	For example, for a single interval in CFT$_2$,
-	\begin{equation}
-	\beta(x)=\frac{2\pi}{L_\infty}
-		\pqty{\frac{L_\infty^2}{4}-x^2}
-	\end{equation}
-	\begin{equation}
-	S= \frac{c}{3} \int_{-L_\infty/2}^{L_\infty/2}
-			\frac{L_\infty/2}{(L_\infty/2)^2-x^2}dx,
-	\end{equation}
-	The indefinite integral $
-		\int \frac{L_\infty/2}{(L_\infty/2)^2-x^2}dx
-		= \mop{arctanh}\frac{2x}{L_\infty}
-%		\rightarrow\infty
-	$ diverges as $x\rightarrow L_\infty/2$, so one needs a cutoff:
-	\begin{equation}
-	S=\frac{c}{3}\int_{-L_\infty/2+a}^{L_\infty/2-a}
-		\frac{L_\infty/2}{(L_\infty/2)^2-x^2}dx
-	=\frac{2c}{3} \mop{arctanh} \pqty{
-			1-\frac{2a}{L_\infty}
-		}
-	\end{equation}
-	As $a\rightarrow 0$,
-	\begin{equation}
-		\mop{arctanh} \pqty{
-			1-\frac{2a}{L_\infty}
-		}\rightarrow \frac{1}{2}\log\frac{L_\infty}{a}
-	\end{equation}
-	So we get the usual result
-	\begin{equation}
-	S=\frac{c}{3}\log\frac{L_\infty}{a}
-	\end{equation}
-
-	Another case is the Rindler patch, \sidenote{better to integrate from $l$ to $\infty$},
-	\begin{equation}
-	\xi\propto x\partial_x-t\partial_x
-	\end{equation}
-	\begin{equation}
-	\beta(x)=2\pi x
-	\label{eq:beta_rindler}
-	\end{equation}
-	\begin{equation}
-	S=\int_{a}^{l}\frac{c}{6x}=\frac{c}{6}\log \frac{l}{a}
-	\end{equation}
-	The factor $\frac{c}{6}$ is that in this case, one only considers one of the endpoints instead of two.
-One can read the C-function from \eqref{eq:beta_thermal}\eqref{eq:beta_rindler}, when $\beta$ is linear of $x$.
-	\begin{equation}
-	C=\frac{c}{6}
-	\end{equation}
-
-%	Now consider the modular flow generator, there are two effects.
-On the one hand, if one changes the overall factor, one will change the temperature, giving an overall factor of the entanglement entropy.
-%	(The case we discussed last week is this case, where we used the Rindler map to get the result.) 
-%	Otherwise, it will change the Rindler map, and give different entanglement entropy.
-
-	Now for the cutoff field theory living at the boundary, consider a modular flow generator of this form,
-	\begin{equation}
-	\xi|_{t=0}=\frac{2\pi}{L_\infty}(L_\infty^2/4-x^2)\partial_t
-	\end{equation}
-	Namely in the same form as the modular flow of a CFT, but we have:
-	\begin{equation}
-	L^2/4+z_c^2=L_\infty^2/4
-	\end{equation}
-	Where the interval for the cutoff theory is of length $L$. The entanglement entropy is
-	\begin{equation}
-	S=\frac{c}{6}\mop{arctanh}\frac{2x}{L_\infty}\Big|_{x=-L/2}^{x=L/2}
-	=\frac{c}{3}\mop{arctanh}\frac{L}{\sqrt{L^2+4z_c^2}}
-	=\frac{c}{3}\mop{arcsinh}\frac{L}{2z_c}
-	\end{equation}
-	with C-function
-	\begin{equation}
-	C(l)=\frac{c}{3}\frac{1}{\sqrt{1+\frac{4z_c^2}{L^2}}}
-	\end{equation}
-	Which agrees with \cite{Lewkowycz:2019xse}. \sidenote{This provides a field theory side calculation of the cutoff entanglement entropy, based on the input of the modular flow $\xi$. }
-
-	\textit{Note that we only need to know the modular flow $\xi$ along some time slice.
-We don't need to know the full modular flow.
-This seems to be consistent with Lewkowycz--Maldacena \cite{Lewkowycz:2013nqa} and the holographic entropy, where it only depends linearly on $\xi$ along the RT surface, as long as $\xi$ is a Killing vector.
-See \eqref{kdef}.
-}
-
-	In the field theory side, such modular flow generator means that the Rindler transformation map a slightly large region $D(\tilde{A})$ to the hyperbolic cylinder, and keep track of the endpoints of the interval $A$.
-The endpoints are implied in the range of the integration in the local entanglement temperature method, and also in the length of the cylinder in the Rindler map method.
-	\begin{equation}
-	f:D(A)\rightarrow R\times S
-	\end{equation}
-	\begin{equation}
-	\tilde{f}:D(\tilde{A})\rightarrow R\times S
-	\end{equation}
-	A is the interval with length $L$, $\tilde{A}$ is the interval with length $L_\infty$.
-
-	In the cutoff AdS picture, it seems that the modular flow generator for the interval with lenght $L$ is on the asymptotic boundary but with the interval length $L_\infty$ instead of $L$.
-
-\subsubsection*{Reasoning for this trick}
-	The validity of this trick can be argued from the Rindler map; suppose we have the following Rindler map at the boundary:
-	\begin{equation}
-	\begin{aligned}
-		f\colon
-		\mcal{D}(\mcal{A})
-		&\longto \mcal{R} = S^1_\beta \times f(\mcal{A}), \\
-		(t,x)
-		&\longmapsto (\tau,\tilde{x}),
-	\end{aligned}
-	\end{equation}
-	Here $f(\mcal{A})$ is the image of the boundary interval.
-$f$ by construction ``normalizes'' the temperature for the modular generator, namely, the modular flow $\xi$ is now realized as the pullback of $2\pi\pdd{\tau}$:
-	\begin{equation}
-		\xi = \xi^\mu \pdd{\mu}
-		= 2\pi\pdd{\tau}
-	\end{equation}
-	In particular, along the interval $\mcal{A}$ at the $t = 0$ time slice, we have:
-	\begin{equation}
-		\xi|_{t = 0}
-		= \beta(x)\,\pdd{t}
-		= 2\pi\pdd{\tau},
-	\quad
-		\pdv{t}{\tau}
-		= \frac{\beta(x)}{2\pi}
-	\end{equation}
-	Note that although $\xi$ is a Killing vector when it's extended to the bulk, it is only a \textit{conformal Killing vector} when it's restricted to the boundary.
-
-	Here we think of $f$ as a simple coordinates transformation or diffeomorphism, which keeps the metric $\dd{s}^2$ invariant, and maps the flat coordinates to the conformally flat coordinates:
-	\begin{equation}
-		\dd{s}^2
-		= \dd{t}^2 + \dd{x}^2
-		= \Omega^2(\tau,\tilde{x}) \pqty{
-				\dd{\tau}^2 + \dd{\tilde{x}}^2
-			},
-	\quad
-		\Omega_{t = 0} = \pdv{t}{\tau}
-		= \frac{\beta(x)}{2\pi}
-	\end{equation}
-	Here we've properly rescaled the $\tilde{x}$ coordinate to make the $(\tau,\tilde{x})$ coordinates conformally flat.
-
-	Due to conformal symmetry [\sidenote{what about the TTbar case?
-Perhaps the reason it still works is again, that the conformal factor vanishes at the endpoints, due to $2\pi$ periodicity of $\xi$}], one can further drop the conformal factor $\Omega^2(\tau,\tilde{x})$ from the metric, while the thermal entropy of the system remains unchanged.
-We now have a flat annulus:
-	\begin{equation}
-		\tilde{\mcal{R}}
-		= S^1_\beta \times [0,\tilde{L}],
-	\quad
-		\dd{\tilde{s}}^2
-		= \frac{1}{\Omega^2} \dd{s}^2
-		= \dd{\tau}^2 + \dd{\tilde{x}}^2
-	\end{equation}
-	This is the corresponding geometry of a thermal partition function, with a constant temperature $\beta_\tau = 2\pi$. 
-	Now $\pdd{\tau}$ is truly a Killing vector of $\tilde{\mcal{R}}$. 
-	In this case the thermal entropy is extensive: the total entropy $S_\mcal{A}$ is proportional to the size of the system:
-	\begin{equation}
-		S_\mcal{A}
-		= \frac{c}{6} \tilde{L}
-	\end{equation}
-	Here $\tilde{L}$ denotes the $\tilde{\mcal{R}}$ length of the interval $f(\mcal{A})$:
-	\begin{equation}
-		\tilde{L}
-		= \int_{f(\mcal{A})} \dd{\tilde{s}}
-		= \int_{f(\mcal{A})} \frac{\dd{s}}{\Omega}
-		= \int_{\mcal{A}} \frac{\dd{s}}{\Omega}
-		= \int_{\mcal{A}} \frac{2\pi}{\beta(x)} \dd{x}
-	\end{equation}
-	We've used the fact the $f$ is a diffeomorphism, to reduce the integral back to an integral along $\mcal{A}$ in the original coordinates. 
-	The entropy is thus given by:
-	\begin{equation}
-		S_\mcal{A}
-		= \frac{c}{6}
-			\int_{\mcal{A}} \frac{2\pi}{\beta(x)} \dd{x}
-	\end{equation}
-
-	In the above arguments we rely on the fact that the thermal entropy density of a CFT is given by $
-		\frac{c}{6}
-	$. This can be derived from the Cardy formula\footnote{
-		The easiest way to see this is by applying the AdS/CFT dictionary, where we find that $c = \frac{3\ell_\mrm{AdS}}{2G_N}$ thus $\frac{c}{6} = \frac{\ell_\mrm{AdS}}{4G_N}$, which is precisely the Bekenstein--Hawking entropy (per unit area, with $\ell_\mrm{AdS} = 1$).
-But now we are committed to a purely field theoretical calculation, so we shall reproduce Cardy's arguments here, which do not rely on holographic duality.
-	}.
-First note that by rescaling the Rindler map $f$ we can tune the temperature of the Rindler spacetime $\mcal{R}$ to be arbitrarily high.
-We've chosen $\beta_\tau = 2\pi$ only for convenience.
-\sidenote{[is this argument valid?
-check!]} Therefore we may apply the high temperature (or low $\beta$) limit of the Cardy formula; namely, by modular invariance of the partition function, we have:
-	\begin{equation}
-	\begin{aligned}
-		Z[\tau = i\tfrac{\beta}{2\pi}]
-		&= Z[-\tfrac{1}{\tau} = i\tfrac{2\pi}{\beta}],
-	\\[1ex]
-		Z[\beta]
-		&= Z[\beta\to \tfrac{4\pi^2}{\beta}] \\
-		&= \Tr e^{
-			-\frac{4\pi^2}{\beta} \pqty{
-				L_0 + \tilde{L}_0 - \frac{c}{12}
-			} \frac{\tilde{L}}{2\pi}
-		}, \quad \beta\ll 1 \\
-		&\sim e^{
-			\frac{4\pi^2}{\beta}
-			\frac{c}{12}
-			\frac{\tilde{L}}{2\pi}
-		}
-		= e^{
-			\frac{2\pi}{\beta}
-			\frac{c}{12} \tilde{L}
-		},
-	\end{aligned}
-	\end{equation}
-	Here we've used the saddle point approximation and assumed that the vacuum (the $h = \tilde{h} = 0$ state) contribution dominates. The entropy is thus given by:
-	\begin{equation}
-		S = \pqty{
-				1 - \beta\, \pdd{\beta}
-			} \log Z[\beta]
-		= \frac{2\pi}{\beta} \frac{c}{6} \tilde{L}
-	\end{equation}
-	With $\beta = \beta_\tau = 2\pi$, we recover the result $
-		S = \frac{c}{6} \tilde{L}
-	$.
-
-\pagebreak
-\textit{
-	The discussion above is in the framework of $\mrm{CFT}_2$, but with different modular flow generator.
-Now we consider the framework of $T\bar{T}$ deformed theories.
-The thermal entropy with unit length is
-	\begin{equation}
-	S_{thermal}=\frac{\pi c}{3\beta}\eta
-	\end{equation}
-	\begin{equation}
-	\eta=\frac{1}{\sqrt{1+\frac{4\pi^2c\mu}{3\beta^2}}}
-	\end{equation}
-	Consider the half line case,
-	\begin{equation}
-	\beta(x)=2\pi x
-	\end{equation}
-	One can get the C-function,
-	\begin{equation}
-	C(l)=\frac{c}{6}\frac{1}{\sqrt{1+\frac{c\mu}{3l^2}}}
-	\end{equation}
-	Again, there is ``one endpoint'' in this case, which will give one half contribution of the C-function with the pre-factor $c/3$.
-}
-
-\pagebreak
-\section{Finite temperature: modular flow in BTZ background}
-\subsection{Entanglement Entropy as Gravitational Charge}
+\subsection{Gravitational charges}
+
 	Ref: \textcite{Wald:1993nt,Iyer:1994ys,Iyer:1995kg}, \textcite{Lewkowycz:2013nqa}, and \textcite{Faulkner:2013ana}.
@@
 
-\subsection{Modular flow in $\mrm{BTZ}_3$ and entanglement entropy}
+\subsubsection{Finite temperature: modular flow in $\mrm{BTZ}_3$ and entanglement entropy}
 \textbf{Summary:} We map the the modular flow in the Poincar\'e $\mrm{AdS}_3$ vacuum to the BTZ background, and compute the entanglement entropy as gravitational charge.
@@
 \pagebreak
-\subsection{BTZ with constant cutoff}
+\subsubsection{BTZ with constant cutoff}
 \textbf{Summary:} We then consider constant $r$ cutoff in the Schwarzschild coordinates, which corresponds to the proposal of \cite{McGough:2016lol}.
@@
 
-\subsection{Field theory side calculation}
+\appendix
+
+\section{Modular flow for Poincar\'e $\mrm{AdS}_3/\mrm{CFT}_2$}
+\label{sect:modFlowPoincare}
+
+\textbf{Summary:} We follow the recipe from the swing surface proposal \cite{Apolo:2020bld,Apolo:2020qjm} to extend the boundary modular flow to the bulk, by matching symmetries of the bulk and the boundary.
+This reproduce known results such as \cite{Lashkari:2016idm,Czech:2019vih,Apolo:2020qjm} [more citations needed].
+
+\noindent\textbf{Mathematica:} \texttt{modFlowPoincare.nb}
+
+\subsection{Matching bulk and boundary symmetries}
+	In Poincar\'e $\mrm{AdS}_3/\mrm{CFT}_2$, the $H_i$'s are given by $L_n,\tilde{L}_n$ with $n=0,\pm 1$. At $z\to 0$ we recover the usual global $\mfrak{sl}(2,\mbb{R})$ generators:
+	\begin{equation}
+		z\to 0,
+	\quad
+		      L_n \to -u^{n+1} \pdd{u},\quad
+		\tilde{L}_n \to -v^{n+1} \pdd{v},\quad
+	n = 0,\pm 1
+	\end{equation}
+
+	To extend it to the bulk, think of the corresponding bulk isometries: translations, rotations, dilations and special conformal transformations:
+	\begin{equation}
+	\begin{aligned}
+		P_\mu
+		&= \pdd{\mu},\\
+		m_{uv}
+		&= x_\mu \pdd{\nu} - x_\nu \pdd{\mu}
+		= u\pdd{u} - v\pdd{v},\\
+		\Delta
+		&= X^I \pdd{I}
+		= u\pdd{u} + v\pdd{v} + z\pdd{z},\\
+		K_\mu
+		&= (z^2 + uv)\,\pdd{\mu}
+			- 2\eta_{\mu\nu} x^\nu \Delta,
+	\end{aligned}
+	\end{equation}
+	\begin{equation}
+		K_u = (z^2 + uv)\,\pdd{u} - v \Delta,
+	\quad
+		K_v = (z^2 + uv)\,\pdd{v} - u \Delta
+	\end{equation}
+	By requiring that a linear combination of these generators reduce to the boundary $L_n$'s, one can uniquely extend the $L_n,\tilde{L}_n$'s into the bulk.
+The result for $L_n$'s is listed below; for $\tilde{L}_n$ one need only exchange all $u\leftrightarrow v$.
+	\begin{equation}
+		L_{-1} = -\pdd{u},
+	\quad
+		L_0 = -u\,\pdd{u} - \frac{z}{2}\,\pdd{z},
+	\quad
+		L_1 = -u^2\pdd{u} + z^2 \pdd{v}
+			- uz\,\pdd{z}
+	\end{equation}
+
+\subsection{RT surface and the modular flow}
+
+%\textbf{Derivation of RT surface:} \\
+%	\url{https://bryango.github.io/resources/archive/HW-Gravity/gravity1.pdf}.
+
+	The RT surface (spacelike geodesic of Poincar\'e AdS with both ends attached to the boundary) is parametrized in terms of its end points $(t,x)_\pm$; it's the intersection of a AdS ``sphere'' (hyperboloid) and a plane through its center:
+	\begin{equation}
+	\begin{aligned}
+	\text{``sphere'':} &&&\mathsmaller{
+		z^2
+		+ \pqty{x - \frac{x_+ + x_-}{2}}^{\!\!2}
+		- \pqty{t - \frac{t_+ + t_-}{2}}^{\!\!2}
+		= \pqty{\frac{L_\infty}{2}}^{\!\!2}
+		= \pqty{\frac{x_+ - x_-}{2}}^{\!\!2}
+		- \pqty{\frac{t_+ - t_-}{2}}^{\!\!2}
+	},\\
+	&&& \text{i.e.}\ \,
+		L^2
+		= \pqty{x_+ - x_-}^2
+			- \pqty{t_+ - t_-}^2
+		= (u_+ - u_-)(v_+ - v_-),
+	\\[1.5ex]
+	\text{plane:} &&&
+		\frac{x - \frac{1}{2} (x_+ + x_-)}{x_+ - x_-}
+		= \frac{t - \frac{1}{2} (t_+ + t_-)}{t_+ - t_-}
+	\end{aligned}
+	\end{equation}
+	Alternatively, it can be more compactly rewritten with $x^\mu \sim (t,x)$ or $(u,v)$; mind the various $\pm$ signs in the expressions: 
+	\begin{equation}
+	\begin{aligned}
+		0 &= z^2
+			+ \eta_{\mu\nu} (x - x_+)^\mu (x - x_-)^\nu \\
+		& = z^2
+			+ (x - x_+)(x - x_-)
+			- (t - t_+)(t - t_-) \\
+		&= z^2 + \frac{
+				(u - u_+)(v - v_-)
+				+ (v - v_+)(u - u_-)
+			}{2}
+	\end{aligned}
+	\end{equation}
+
+	The bulk modular generator vanishes along the RT surface, i.e.~the RT surface is the fixed point of the modular flow; with this condition we can fix the coefficients of the modular generator, up to an overall coefficient\footnote{
+		One can compare this with similar results in the literature such as \cite{Lashkari:2016idm,Czech:2019vih,Apolo:2020qjm}. 
+	}:
+	\begin{equation}
+		\xi = 2\pi \sum_{n=0,\pm 1} \pqty{
+				s_n L_n - \tilde{s}_n \tilde{L}_n
+			},
+	\end{equation}
+	\begin{equation}
+		s_{-1} = \frac{u_+ u_-}{u_+ - u_-},\quad
+		s_0 = - \frac{u_+ + u_-}{u_+ - u_-},\quad
+		s_{+1} = \frac{1}{u_+ - u_-}
+	\end{equation}
+	One need only exchange all $u\leftrightarrow v$ to obtain $\tilde{s}_n$.
+The overall coefficient of $\xi$ (in this case, $2\pi$) is fixed by normalizing the temperature of the horizon, namely we demand that the surface gravity is $2\pi$ along the RT surface:
+	\begin{equation}
+%		\beta_\xi = \frac{2\pi}{\kappa_\xi} = 1,
+%	\quad
+		\kappa_\xi^2
+		= (2\pi)^2
+		= -\frac{1}{2}\,
+			(\nabla_{\mu} \xi_{\nu})
+			(\nabla^{\mu} \xi^{\nu})
+	\end{equation}
+
+	\begin{figure}[!ht]
+%	\vspace{-1.5ex}
+	\centering
+	\includegraphics[width=.4\linewidth]{img/modFlowLorentzian.png}
+	\hspace{2em}
+	\includegraphics[width=.4\linewidth]{img/modFlowEuclidean.png}
+%	\vspace{-2ex}
+	\caption{Modular flow at the boundary, for an interval lying on a constant $t = 0$ slice, in Lorentzian and Euclidean signature}
+	\end{figure}
+
+\pagebreak[4]
+
+	We now restrict to an interval centered at the origin: $
+		u_\pm v_\pm
+		= x^2_\pm - t^2_\pm
+		= (\frac{L_\infty}{2})^2
+	$, where $x_\pm = -x_\mp$, and same for $t_\pm, u_\pm, v_\pm$. 
+	We then introduce the \textit{rapidity} $\theta$ to nicely parametrized the boosted interval; for a constant time slice, we have $\theta = 0$. For a general boosted interval, we have:
+	\begin{equation}
+		x_\pm = \pm \frac{L_\infty}{2} \cosh \theta,
+	\quad
+		t_\pm = \pm \frac{L_\infty}{2} \sinh \theta,
+	\end{equation}
+	For now the coordinates $u_\pm, v_\pm, x_\pm, t_\pm$ and the coordinate length $L_\infty$ are all specified at $z\to 0$, i.e.~at the \textbf{asymptotic boundary}.
+Note that the RT surface lies on the plane $
+		t_\pm / x_\pm = \tanh \theta
+	$, namely $\theta$ is constant along the RT surface. 
+	We have:
+	\begin{gather}
+	\begin{aligned}
+		\xi &= \frac{2\pi}{L_\infty} \bigg\{
+			\pqty\Big{
+				\pqty{
+					(\tfrac{L_\infty}{2})^2 - z^2
+					- (t^2 + x^2)
+				} \cosh\theta
+				+ 2tx \sinh\theta
+			} \,\pdd{t}
+		\\ &\qquad\qquad 
+			+ \pqty\Big{
+				\pqty{
+					(\tfrac{L_\infty}{2})^2 - z^2
+					+ (t^2 + x^2)
+				} \sinh\theta
+				- 2tx \cosh\theta
+			} \,\pdd{x}
+		\\ &\qquad\qquad 
+			+ \pqty\big{
+				x\sinh\theta
+				- t\cosh\theta
+			} \,2z\pdd{z}
+		\bigg\}
+	\end{aligned}
+	\end{gather}
+
+	We note that the $\pdd{z}$ term vanishes in the following two cases:
+	\begin{itemize}[noitemsep,topsep=0pt]
+	\item as $z\to 0$, i.e.~near the asymptotic boundary;
+	\item within the whole plane: $
+			x\sinh\theta
+			= t\cosh\theta
+		$ where the RT surface lies. 
+	\end{itemize}
+
+\section{Effective local entanglement temperature: more examples}
+
+	Another example is the Rindler patch, \sidenote{better to integrate from $l$ to $\infty$},
+	\begin{equation}
+	\xi\propto x\partial_x-t\partial_x
+	\end{equation}
+	\begin{equation}
+	\beta(x)=2\pi x
+	\label{eq:beta_rindler}
+	\end{equation}
+	\begin{equation}
+	S=\int_{a}^{l}\frac{c}{6x}=\frac{c}{6}\log \frac{l}{a}
+	\end{equation}
+	The factor $\frac{c}{6}$ is that in this case, one only considers one of the endpoints instead of two.
+One can read the C-function from \eqref{eq:beta_thermal}\eqref{eq:beta_rindler}, when $\beta$ is linear of $x$.
+	\begin{equation}
+	C=\frac{c}{6}
+	\end{equation}
+
+	The discussion above is in the framework of $\mrm{CFT}_2$, but with different modular flow generator.
+Now we consider the framework of $T\bar{T}$ deformed theories.
+The thermal entropy with unit length is
+	\begin{equation}
+	S_{thermal}=\frac{\pi c}{3\beta}\eta
+	\end{equation}
+	\begin{equation}
+	\eta=\frac{1}{\sqrt{1+\frac{4\pi^2c\mu}{3\beta^2}}}
+	\end{equation}
+	Consider the half line case,
+	\begin{equation}
+	\beta(x)=2\pi x
+	\end{equation}
+	One can get the C-function,
+	\begin{equation}
+	C(l)=\frac{c}{6}\frac{1}{\sqrt{1+\frac{c\mu}{3l^2}}}
+	\end{equation}
+	Again, there is ``one endpoint'' in this case, which will give one half contribution of the C-function with the pre-factor $c/3$.
 
@@
 \bibliographystyle{JHEP} 
-\bibliography{cutoffModular-alpha.bib}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\bibliography{cutoff.bib}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \end{document}

### 2021-06-14 HW-Gravity/gravity1/gravity1.tex
Add minor tweaks to various notes
Finish gravity1 homework, add mathematica script

@@
+% !TeX document-id = {09950f11-703a-4175-9f6c-5ae00c774d6a}
 % !TeX encoding = UTF-8
@@
 \input{../.modules/basics/biblatex.tex}
+
+\addbibresource{../gravity.bib}
 
@@
 
-	From now on we shall focus on the $p^2 \ne 0$ situation. Note that we can complete the square on the right hand side of the $k^\mu$ conservation such that:
+	From now on we shall focus on the $p^2 \ne 0$ situation. Note that we can complete the square on the right-hand side of the $k^\mu$ conservation such that:
 	\begin{equation}
@@
 		\begin{enumerate}
-		\item For $p^2 > 0$, again we have $\frac{L}{2} = \frac{1}{\norm{p}} > 0$, and $\gamma$ is again a cross section of the one-sheet hyperboloid.
+		\item For $p^2 > 0$, again we have $\frac{L}{2} = \frac{1}{\norm{p}} > 0$, and $\gamma$ is again a cross-section of the one-sheet hyperboloid.
 However, now we have $z \le \frac{L}{2}$, namely $z$ is bounded from above, and:
@@
 
-		\item For $p^2 < 0$, we have $(\frac{L}{2})^2 = \frac{1}{p^2} < 0$, and $\gamma$ is now a cross section of the two-sheet hyperboloid.
+		\item For $p^2 < 0$, we have $(\frac{L}{2})^2 = \frac{1}{p^2} < 0$, and $\gamma$ is now a cross-section of the two-sheet hyperboloid.
 Again as $z\to 0$ it lands at $x^\mu = a^\mu \pm \frac{L}{2}\,\widehat{p}^\mu$; however, $\abs{x^\mu}$ grows with $z$ and extends into the bulk instead of returning to the boundary, i.e.~$z,\abs{x^\mu} \to \infty$.
@@
 
-	On the other hand, $\eta$ should be treated like an einbein: $\eta = \sqrt{-\gamma}$, here $\gamma = \gamma_{\tau\tau}$ is the worldline metric; $\gamma < 0$ due to the Lorentzian signature. We have:
+	On the other hand, $\eta$ should be treated like an einbein: $\eta = \sqrt{-\gamma}$, here $\gamma = \gamma_{\tau\tau}$ is the worldline metric; $\gamma < 0$ due to the Lorentzian signature \cite{Polchinski:1998rq}.
+We have:
 	\begin{gather}
@@
 
+	To find the connection form, we first note the \textit{Cartan's structure equation} \cite{Carroll:1997ar}:
+	\begin{equation}
+	\begin{aligned}
+		\dd{e^a}
+		= \dd{\pqty{e^a_\nu \dd{x^\nu}}}
+		&= \pdd{\mu} e^a_\nu
+			\dd{x^\mu} \wedge \dd{x^\nu} \\
+		&= \pqty{
+				- \omega^{a}_{\mu b} e^b_\nu
+				+ \Gamma^{\lambda}_{\mu\nu} e^a_\lambda
+			}
+			\dd{x^\mu} \wedge \dd{x^\nu} \\
+		&= -\omega\id{^a_b} \wedge e^b
+			+ T^a
+	\end{aligned}
+	\end{equation}
+	Where $T^a$ is the torsion tensor. 
+	Here we've used the relation between spin connection $\omega^a_{\mu b}$ and the affine connection $\Gamma^\lambda_{\mu\nu}$. For the torsion-free Levi-Civita connection, we have $
+		\dd{e^a}
+		= -\omega\id{^a_b} \wedge e^b
+	$.
+
+	Rigidity of the veilbein, namely $
+		\cdv{\mu} \pqty{g_{\mu\nu} e^\mu_a e^\nu_b}
+		= \cdv{\mu} \eta_{ab} = 0
+	$, further implies that:
+	\begin{equation}
+		\omega_{\mu ab}
+		= -\omega_{\mu ba}
+	\end{equation}
+	With these constraints we can solve for the connection form, and we find that only the following components are non-vanishing\footnote{
+		Go to \url{https://github.com/bryango/Archive/blob/master/HW-Gravity/gravity1/nb/vielbein.wl} for a Mathematica script for this calculation.
+	}:
+	\begin{gather}\allowdisplaybreaks
+		\omega\id{^t_r}
+		= \frac{f'}{2\sqrt{fh}} \dd{t}
+		= -\omega\id{^r_t}
+	\\
+		\omega\id{^r_\theta}
+		= \frac{-1}{\sqrt{h}} \dd{\theta}
+		= -\omega\id{^\theta_r}
+	\\
+		\omega\id{^r_\phi}
+		= \frac{-\sin\theta}{\sqrt{h}} \dd{\phi}
+		= -\omega\id{^\phi_r}
+	\\
+		\omega\id{^\theta_\phi}
+		= -\cos\theta \dd{\phi}
+		= -\omega\id{^\phi_\theta}
+	\end{gather}
+
+	The curvature form is thus given by:
+	\begin{equation}
+		\Omega\id{^a_b}
+		= \dd{\omega\id{^a_b}}
+			+ \omega\id{^a_c} \wedge \omega\id{^c_b}
+	\end{equation}
+	The exterior derivative is easily computed in the $\dd{x^\mu}$ basis; however, to get to the Ricci tensor, it would be convenient to switch to the $e^a$ basis.
+Here we only write down the upper half of $\Omega\id{^a_b}$ since the lower half can be inferred from anti-symmetry:
+	\begin{equation}
+	\Omega\id{^a_b}
+	\sim
+	\pqty{
+	\begin{array}{cccc}
+		0
+		& R\id{^t_r_t_r}\,e^t\wedge e^r
+		& R\id{^t_\theta_t_\theta}\,e^t\wedge e^\theta
+		& R\id{^t_\phi_t_\phi}\,e^t\wedge e^\phi \\
+		\cdots & 0
+		& R\id{^r_\theta_r_\theta}\,e^r\wedge e^\theta
+		& R\id{^r_\phi_r_\phi}\,e^r\wedge e^\phi \\
+		\cdots & \cdots & 0
+		& R\id{^\theta_\phi_\theta_\phi}\,e^\theta\wedge e^\phi \\
+		\cdots & \cdots & \cdots & 0 \\
+	\end{array}
+	}
+	\end{equation}
+	\begin{equation}
+	\begin{aligned}
+		R\id{^t_r_t_r}
+		&= \frac{f'^2}{4f^2 h}
+			+ \frac{f'h'}{4fh^2}
+			- \frac{f''}{2fh},
+	\\
+		R\id{^t_\theta_t_\theta}
+		&= \frac{-f'}{2rfh}
+		= R\id{^t_\phi_t_\phi},
+	\\
+		R\id{^r_\theta_r_\theta}
+		&= \frac{h'}{2rh^2}
+		= R\id{^r_\phi_r_\phi},
+	\\
+		R\id{^\theta_\phi_\theta_\phi}
+		&= \frac{h - 1}{r^2 h}
+	\end{aligned}
+	\end{equation}
+
+	The Ricci tensor in $e^a$ basis is given by $
+		R_{ab} = R\id{^c_a_c_b}
+	$. Note that the components are non-zero iff.~$a = b$, i.e.~the Ricci tensor is diagonal. We have:
+	\begin{equation}
+	\begin{aligned}
+		R_{ab}
+		&\sim \mop{diag} \pqty\big{
+			R\id{^r_t_r_t}
+			+ R\id{^\theta_t_\theta_t}
+			+ R\id{^\phi_t_\phi_t},
+			\cdots,\cdots,\cdots
+		} \\
+		&= \mop{diag} \pqty\big{
+			R\id{^t_r_t_r}
+			+ R\id{^t_\theta_t_\theta}
+			+ R\id{^t_\phi_t_\phi},
+			\cdots,\cdots,\cdots
+		} \\
+		&= \mop{diag} \Big(\,
+			R\id{^t_r_t_r}
+			+ R\id{^t_\theta_t_\theta}
+			+ R\id{^t_\phi_t_\phi},
+		\\[-1ex] & \hspace{4.5em}
+			R\id{^t_r_t_r}
+			+ R\id{^r_\theta_r_\theta}
+			+ R\id{^r_\phi_r_\phi},
+		\\[-.5ex] & \hspace{4.5em}
+			R\id{^t_\theta_t_\theta}
+			+ R\id{^r_\theta_r_\theta}
+			+ R\id{^\theta_\phi_\theta_\phi},
+		\\[-1ex] & \hspace{4.5em}
+			R\id{^t_\phi_t_\phi}
+			+ R\id{^r_\phi_r_\phi}
+			+ R\id{^\theta_\phi_\theta_\phi}
+		\,\Big) \\
+		&= \mop{diag} \Big(\,
+			R\id{^t_r_t_r}
+			+ 2R\id{^t_\theta_t_\theta},
+		\\[-1ex] & \hspace{4.5em}
+			R\id{^t_r_t_r}
+			+ 2R\id{^r_\theta_r_\theta},
+		\\[-.5ex] & \hspace{4.5em}
+			R_{\theta\theta} = R\id{^t_\theta_t_\theta}
+			+ R\id{^r_\theta_r_\theta}
+			+ R\id{^\theta_\phi_\theta_\phi},
+		\\[-1ex] & \hspace{4.5em}
+			R_{\phi\phi} = R_{\theta\theta}
+		\,\Big) \\
+		&= \mop{diag} \bigg(\,
+			\frac{f'^2}{4f^2 h}
+			+ \frac{f'h'}{4fh^2}
+			- \frac{f''}{2fh}
+			- \frac{f'}{rfh},
+		\\[-0ex] & \hspace{4.5em}
+			\frac{f'^2}{4f^2 h}
+			+ \frac{f'h'}{4fh^2}
+			- \frac{f''}{2fh}
+			+ \frac{h'}{rh^2},
+		\\[-0ex] & \hspace{4.5em}
+			R_{\theta\theta}
+			= - \frac{f'}{2rfh}
+			+ \frac{h'}{2rh^2}
+			+ \frac{h - 1}{r^2 h},
+		\\[-0ex] & \hspace{4.5em}
+			R_{\phi\phi} = R_{\theta\theta}
+		\,\bigg),
+	\end{aligned}
+	\end{equation}
+	To go back to the $\dd{x^\mu}$ basis, we have $R_{\mu\nu} = R_{ab} e^a_\mu e^b_\nu$. In particular, here we have $R_{\mu\mu} = R_{aa} (e^a_\mu)^2$, therefore:
+	\begin{equation}
+	\begin{aligned}
+		R_{\mu\nu}
+		&= \mop{diag} \bigg(\,
+			\frac{f'^2}{4f h}
+			+ \frac{f'h'}{4h^2}
+			- \frac{f''}{2h}
+			- \frac{f'}{rh},
+		\\[-0ex] & \hspace{4.5em}
+			\frac{f'^2}{4f^2}
+			+ \frac{f'h'}{4fh}
+			- \frac{f''}{2f}
+			+ \frac{h'}{rh},
+		\\[-0ex] & \hspace{4.5em}
+			R_{\theta\theta}
+			= - \frac{rf'}{2fh}
+			+ \frac{rh'}{2h^2}
+			+ \frac{h - 1}{h},
+		\\[-0ex] & \hspace{4.5em}
+			R_{\phi\phi} = R_{\theta\theta} \sin^2\theta
+		\,\bigg)
+	\end{aligned}
+	\end{equation}
+
+\section{Jackiw--Teitelboim Gravity}
+	The Jackiw--Teitelboim (JT) action is given by:
+	\begin{equation}
+		S = \frac{1}{16\pi G}
+			\int \dd[2]{x} \sqrt{-g}\,\Phi\,
+			\pqty{R + 2}
+	\end{equation}
+	$\fdv{S}{\Phi} = 0$ gives us $R = -2$. Now consider $\fdv{S}{g^{\mu\nu}}$, and we have:
+	\begin{equation}
+	\begin{aligned}
+		\var_g {S}
+		&= \frac{1}{16\pi G} \int \dd[2]{x}
+			\Phi\,\var \pqty\Big{
+				\sqrt{-g}\,\pqty{R + 2}
+			},
+		\quad R = g^{\mu\nu} R_{\mu\nu}, \\
+		&= \frac{1}{16\pi G} \int \dd[2]{x} \sqrt{-g}\,
+			\Phi\,\Bqty{
+				\pqty{
+					R_{\mu\nu} - \frac{1}{2} g_{\mu\nu} (R + 2)
+				} \var{g^{\mu\nu}}
+				+ g^{\mu\nu} \var{R_{\mu\nu}}
+			}
+	\end{aligned}
+	\end{equation}
+
+	Note that the $
+		g^{\mu\nu} \var{R_{\mu\nu}}
+	$ term is a total derivative\footnote{
+		See the amazing lecture note by Matthias Blau at \url{http://www.blau.itp.unibe.ch/GRLecturenotes.html}.
+	}:
+	\begin{equation}
+	\begin{aligned}
+		g^{\mu\nu} \var{R_{\mu\nu}}
+		&= \pqty{
+				\nabla^\mu \nabla^\nu
+				- g^{\mu\nu} \nabla^\lambda \nabla_\lambda
+			} \var{g_{\mu\nu}} \\
+		&= - \pqty{
+				\cdv{\mu} \cdv{\nu}
+				- g_{\mu\nu} \nabla^\lambda \nabla_\lambda
+			} \var{g^{\mu\nu}} \\
+		&= \cdv{\lambda} \pqty\Big{
+				g^{\mu\nu} \var{\Gamma^\lambda_{\mu\nu}}
+				- g^{\mu\lambda} \var{\Gamma^\nu_{\nu\mu}}
+			}
+	\end{aligned}
+	\end{equation}
+	In Einstein gravity this gets reduced to a boundary term.
+But here we have an additional factor of $\Phi$, so after integration by parts, we actually get the equation of motion (EoM) for $\Phi$, up to some boundary terms\footnote{
+		See e.g.~Section 2 of \cite{Harlow:2018tqv}. 
+	}:
+	\begin{equation}
+	\begin{aligned}
+		\var_g {S}
+		\sim \frac{1}{16\pi G} \int \dd[2]{x} \sqrt{-g}\,
+			\Bqty{
+				\Phi\,\pqty{
+					R_{\mu\nu}
+					- \frac{1}{2} g_{\mu\nu} (R + 2)
+				} - \pqty\Big{
+					\cdv{\mu} \cdv{\nu}
+					- g_{\mu\nu} \nabla^\lambda \nabla_\lambda
+				} \Phi
+			} \var{g^{\mu\nu}}
+	\end{aligned}
+	\end{equation}
+
+	In 2D, we have $
+		R_{\mu\nu}
+		\equiv \frac{1}{2} g_{\mu\nu} R
+	$, so the EoM is simply:
+	\begin{equation}
+		\pqty{
+			\cdv{\mu} \cdv{\nu}
+			- g_{\mu\nu} \nabla^\lambda \nabla_\lambda
+			+ g_{\mu\nu}
+		}\, \Phi = 0
+	\end{equation}
+	Contraction with $g^{\mu\nu}$ further gives us $
+		\pqty{
+			\nabla^\lambda \nabla_\lambda - 2
+		} \Phi = 0
+	$, so in the end we have:
+	\begin{equation}
+		\pqty{
+			\cdv{\mu} \cdv{\nu}
+			- g_{\mu\nu}
+		}\, \Phi = 0,
+	\quad
+		R = -2
+	\end{equation}
+
+\pagebreak
 \appendix
-
 \section{Derivation of the special conformal transformations}

### 2021-06-17 alpha/CutoffModularFlow/draft1.tex
Update conventions for cutoff mod flow note

@@
 	\begin{equation}
-	z=\frac{1}{ir_1}e^{ir_1w},\ \ \ r_1=\frac{2\pi}{\beta}
+	z=\frac{1}{r_1}e^{r_1w},\ \ \ r_1=\frac{2\pi}{\beta}
 	\end{equation} 
@@
 	\begin{equation}
-	w\sim w+\beta
+	w\sim w+i\beta
 	\end{equation}
@@
 	\begin{equation}
-	w=\pm l i
+	w=\pm l
 	\end{equation} 
@@
 	\begin{equation}
-	\frac{1}{ir_1}e^{\mp r_1 l}
+	\frac{1}{r_1}e^{\pm r_1 l}
 	\end{equation}
@@
 	\begin{equation}
+	e^{r_1(w+\bar{w})}
+	\end{equation}
+	Note that compared to the usual map from cylinder to plane $z=e^{r_1 w}$, we put the overall scaling factor $\frac{1}{r_1}$ to make sure that the conformal factor at the endpoints is $1$.
+From 1806.07444, the entanglement entropy for $l_p$ is
+	\begin{equation}
+	S_p(l)=\frac{c}{3}ArcSinh\frac{l_p}{a}
+	\end{equation}
+	where
+	\begin{equation}
+	a^2=\frac{\mu c}{12}
+	\end{equation}
+	The C-function reads,
+	\begin{equation}
+	C(L)=L S'(L=2l)=\frac{c}{3}\frac{1}{\sqrt{1+4a^2/L^2}}
+	\end{equation}
+	Now in the thermal case, $l_p\rightarrow \frac{1}{r_1}\sinh(l r_1)$
+	\begin{equation}
+	S_t=\frac{c}{3}ArcSinh(\frac{1}{r_1 a}\sinh(l r_1))
+	\end{equation}
+	which is the same as the results obtained from the local temperature trick \eqref{} and the gravity calculation \eqref{}. Now consider the finite size case, the conformal transformation is,
+	\begin{equation}
+	z=\frac{1}{ir_1}e^{iwr_1},\quad
+		r_1 = \frac{2\pi}{\lambda}
+	\end{equation}
+	where $w$ is the cylinder coordinate,
+	\begin{equation}
+	w\sim w+ \lambda
+	\end{equation}
+	The endpoints of the interval are 
+	\begin{equation}
+	w\pm l
+	\end{equation}
+	The conformal factor is
+	\begin{equation}
 	e^{ir_1(w+\bar{w})}
 	\end{equation}
-	Note that compared to the usual map from cylinder to plane $z=e^{ir_1 w}$, we put the overall scaling factor $\frac{1}{ir_1}$ to make sure that the conformal factor at the endpoints is $1$.
-From 1806.07444, the entanglement entropy for $l_p$ is
-	\begin{equation}
-	S_p(l)=\frac{c}{3}ArcSinh\frac{l_p}{a}
-	\end{equation}
-	where
-	\begin{equation}
-	a^2=\frac{\mu c}{12}
-	\end{equation}
-	The C-function reads,
-	\begin{equation}
-	C(L)=L S'(L=2l)=\frac{c}{3}\frac{1}{\sqrt{1+4a^2/L^2}}
-	\end{equation}
-	Now in the thermal case, $l_p\rightarrow \frac{1}{r_1}\sinh(l r_1)$
-	\begin{equation}
-	S_t=\frac{c}{3}ArcSinh(\frac{1}{r_1 a}\sinh(l r_1))
-	\end{equation}
-	which is the same as the results obtained from the local temperature trick \eqref{} and the gravity calculation\eqref{}. Now consider the finite size case, the conformal transformation is,
-	\begin{equation}
-	z=\frac{1}{r_1}e^{wr_1}
-	\end{equation}
-	where $w$ is the cylinder coordinate,
-	\begin{equation}
-	w\sim w+i{\color{red} R}
-	\end{equation}
-	The endpoints of the interval are 
-	\begin{equation}
-	w\pm i l
-	\end{equation}
-	The conformal factor is
-	\begin{equation}
-	e^{r_1(w+\bar{w})}
-	\end{equation}
 	which is $1$ at the endpoints. The plane length reads,
@@
 	\end{equation}
+
+\pagebreak
+
 	The global AdS reads,
@@
 
-\subsubsection{Zero temperature: cutoff Poincar\'e $\mrm{AdS}_3$ and the loss of $2\pi$ periodicity}
+\subsection{Euclidean periodicity of the modular flow}
+\subsubsection{Cutoff Poincar\'e $\mrm{AdS}_3$ and the loss of $2\pi$ periodicity}
 

### 2021-06-21 HW-Gravity/gravity7/Physica/init.m
Add Schwarzschild charges for gravity homework

@@ -1,0 +1,15 @@
+#!/usr/bin/env wolframscript
+(* ::Package:: *)
+(* Linked to `~/.Mathematica/Autoload/FrontEnd/init.m` *)
+
+"### Spelunking";
+Quiet[Get["Spelunking`"];];
+
+"### Add quit kernel shortcut";
+FrontEndExecute[
+    FrontEnd`AddMenuCommands["MenuListQuitEvaluators", {MenuItem[
+        "Quit Default"
+        , FrontEnd`KernelExecute[ToExpression["Quit[]"]]
+        , MenuKey["q", Modifiers -> {"Control", "Shift"}]
+        , System`MenuEvaluator -> Automatic
+]}]]

### 2021-06-21 HW-Gravity/gravity7/libsync.sh

@@ -1,0 +1,16 @@
+#!/bin/bash
+# sync mathematica dependencies
+
+DEPS_PATH=(
+    ~/Templates/diffgeoM
+    ~/Templates/Physica
+)
+
+for origin in "${DEPS_PATH[@]}"; do
+    rsync \
+        --exclude='.git*' --recursive --copy-links \
+        --update --partial \
+        --progress --verbose \
+        "$@" \
+        "$origin" .
+done

### 2021-06-21 alpha/CutoffModularFlow/draft1.tex
Update draft with new notations & charge details

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{Modular flow and holographic entanglement entropy in cutoff AdS} 
-\author[a]{The EE $T\bar{T}$ Project}
+\usepackage{xspace}
+\newcommand{\TTbar}{\ensuremath{T\bar{T}}\xspace}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\title{Modular flow and holographic entanglement entropy in cutoff AdS / \TTbar deformed theory} 
+\author[a]{The EE \TTbar Project}
 %\author[a]{Luis Apolo,} 
@@
 
-	\item The $T\bar{T}$ deformation is parametrized by the deformation parameter $\mu$ with mass dimension $(-2)$, defined in \cite{Apolo:2019zai}; sometimes it is more convenient to use the dimensionless \textit{worldsheet} deformation parameter $\lambda = \mu/\ell_s^2$, where $\ell_s$ is the string length.
+	\item The \TTbar deformation is parametrized by the deformation parameter $\mu$ with mass dimension $(-2)$, defined in \cite{Apolo:2019zai}; sometimes it is more convenient to use the dimensionless \textit{worldsheet} deformation parameter $\lambda = \mu/\ell_s^2$, where $\ell_s$ is the string length.
 See \cite{Apolo:2019zai} section 2.3 and its (2.43).
@@
 		\xi_\mrm{CFT} = 2\pi \sum_{n=0,\pm 1} \pqty{
-				s_n L_n - \tilde{s}_n \tilde{L}_n
+				s_n L_n - \bar{s}_n \bar{L}_n
 			},
@@
 	\end{equation}
-	Where the $H_i$'s are given by $L_n,\tilde{L}_n$ with $n=0,\pm 1$, i.e.~the global conformal generators, and $(u,v)_\pm$ or $(t,x)_\pm$ marks the endpoints of the interval $\mcal{A}$.
+	Where the $H_i$'s are given by $L_n,\bar{L}_n$ with $n=0,\pm 1$, i.e.~the global conformal generators, and $(u,v)_\pm$ or $(t,x)_\pm$ marks the endpoints of the interval $\mcal{A}$.
 The overall coefficient $2\pi$ is fixed by requiring that $\kappa_\xi = 2\pi$.
@@
 		= x^2_\pm - t^2_\pm
-		= (\frac{L_\mrm{CFT}}{2})^2
+		= (\frac{{\tilde L}}{2})^2
 	$, where $x_\pm = -x_\mp$, and same for $t_\pm, u_\pm, v_\pm$. 
@@
 	\begin{equation}
-		x_\pm = \pm \frac{L_\mrm{CFT}}{2} \cosh \theta,
-	\quad
-		t_\pm = \pm \frac{L_\mrm{CFT}}{2} \sinh \theta,
+		x_\pm = \pm \frac{{\tilde L}}{2} \cosh \theta,
+	\quad
+		t_\pm = \pm \frac{{\tilde L}}{2} \sinh \theta,
 	\end{equation}
@@
 	\begin{aligned}
-		\xi_\mrm{CFT} &= \frac{2\pi}{L_\mrm{CFT}} \bigg\{
+		\xi_\mrm{CFT} &= \frac{2\pi}{{\tilde L}} \bigg\{
 			\pqty\Big{
 				\pqty{
-					(\tfrac{L_\mrm{CFT}}{2})^2
+					(\tfrac{{\tilde L}}{2})^2
 					- (t^2 + x^2)
@@
 				\pqty{
-					(\tfrac{L_\mrm{CFT}}{2})^2
+					(\tfrac{{\tilde L}}{2})^2
 					+ (t^2 + x^2)
@@
 		\xi_\mrm{CFT}|_{t = 0} 
-		= \frac{2\pi}{L_\mrm{CFT}}
+		= \frac{2\pi}{{\tilde L}}
 			\pqty{
-				\pqty{\frac{L_\mrm{CFT}}{2}}^2
+				\pqty{\frac{{\tilde L}}{2}}^2
 				- x^2
@@
 
-	However, after the $T\bar{T}$-deformation, the scaling and special conformal transformations are no longer symmetries of the theory, so we cannot simply take $\xi_\mrm{CFT}$ as the modular flow in the deformed theory.
+	However, after the \TTbar-deformation, the scaling and special conformal transformations are no longer symmetries of the theory, so we cannot simply take $\xi_\mrm{CFT}$ as the modular flow in the deformed theory.
 
@@
 This leads us to the following proposal of $\xi_{T\bar{T}}|_{t = 0}$, for an interval $\mcal{A}$ with coordinate length $L$:
-	\begin{equation}
-		\xi_{T\bar{T}}|_{t = 0} 
-		= \frac{2\pi}{\sqrt{L^2 + 8\lambda}}
-			\pqty{
-				\pqty{\frac{L}{2}}^2
-				- x^2
-			} \,\pdd{t}
-	\end{equation}
+
 	Note that:
 	\begin{enumerate}[topsep=0pt]
-	\item The dependence of $\xi_{T\bar{T}}|_{t = 0}$ w.r.t.~$L$ is very similar to the dependence of $\xi_\mrm{CFT}|_{t = 0}$ w.r.t.~$L_\mrm{CFT}$, except that now the normalization is slightly modified to include the deformation parameter $\lambda$.
+	\item The dependence of $\xi_{T\bar{T}}|_{t = 0}$ w.r.t.~$L$ is very similar to the dependence of $\xi_\mrm{CFT}|_{t = 0}$ w.r.t.~${\tilde L}$, except that now the normalization is slightly modified to include the deformation parameter $\lambda$.
 	\item This is not yet a proposal for the full modular flow, but only its values around the $t = 0$ slice.
-But we shall see that this is enough to give us the entanglement entropy of a $T\bar{T}$-deformed theory.
+But we shall see that this is enough to give us the entanglement entropy of a \TTbar-deformed theory.
 	\end{enumerate}
@@
 		\beta(x)
-		= \frac{2\pi}{L_\mrm{CFT}}
+		= \frac{2\pi}{{\tilde L}}
 			\pqty{
-				\pqty{\frac{L_\mrm{CFT}}{2}}^2
+				\pqty{\frac{{\tilde L}}{2}}^2
 				- x^2
@@
 	\begin{equation}
-	S= \frac{c}{3} \int_{-L_\mrm{CFT}/2}^{L_\mrm{CFT}/2}
-			\frac{L_\mrm{CFT}/2}{(L_\mrm{CFT}/2)^2-x^2}dx,
+	S= \frac{c}{3} \int_{-{\tilde L}/2}^{{\tilde L}/2}
+			\frac{{\tilde L}/2}{({\tilde L}/2)^2-x^2}dx,
 	\end{equation}
 	The indefinite integral $
-		\int \frac{L_\mrm{CFT}/2}{(L_\mrm{CFT}/2)^2-x^2}dx
-		= \mop{arctanh}\frac{2x}{L_\mrm{CFT}}
+		\int \frac{{\tilde L}/2}{({\tilde L}/2)^2-x^2}dx
+		= \mop{arctanh}\frac{2x}{{\tilde L}}
 %		\rightarrow\mrm{CFT}
-	$ diverges as $x\rightarrow L_\mrm{CFT}/2$, so one needs a cutoff:
-	\begin{equation}
-	S=\frac{c}{3}\int_{-L_\mrm{CFT}/2+\epsilon}^{L_\mrm{CFT}/2-\epsilon}
-		\frac{L_\mrm{CFT}/2}{(L_\mrm{CFT}/2)^2-x^2}dx
+	$ diverges as $x\rightarrow {\tilde L}/2$, so one needs a cutoff:
+	\begin{equation}
+	S=\frac{c}{3}\int_{-{\tilde L}/2+\epsilon}^{{\tilde L}/2-\epsilon}
+		\frac{{\tilde L}/2}{({\tilde L}/2)^2-x^2}dx
 	=\frac{2c}{3} \mop{arctanh} \pqty{
-			1-\frac{2\epsilon}{L_\mrm{CFT}}
+			1-\frac{2\epsilon}{{\tilde L}}
 		}
@@
 		\mop{arctanh} \pqty{
-			1-\frac{2\epsilon}{L_\mrm{CFT}}
-		}\rightarrow \frac{1}{2}\log\frac{L_\mrm{CFT}}{\epsilon}
+			1-\frac{2\epsilon}{{\tilde L}}
+		}\rightarrow \frac{1}{2}\log\frac{{\tilde L}}{\epsilon}
 	\end{equation}
@@
 	\begin{equation}
-	S=\frac{c}{3}\log\frac{L_\mrm{CFT}}{\epsilon}
-	\end{equation}
-
-	Now for the cutoff field theory living at the boundary, where
-	\begin{equation}
-		\beta(x) = \frac{2\pi}{\sqrt{L^2 + 8\lambda}}
-			\pqty{
-				\pqty{\frac{L}{2}}^2
-				- x^2
-			} \,\pdd{t}
-	\end{equation}
+	S=\frac{c}{3}\log\frac{{\tilde L}}{\epsilon}
+	\end{equation}
+
+	{\color{red} For TTbar,  \begin{equation}
+	S=\frac{c}{3}\int_{- L/2}^{L/2}
+		\frac{{\tilde L}/2}{({\tilde L}/2)^2-x^2}dx
+		={c\over6} \mop{arctanh} {2x\over {\tilde L}}\bigg|^{L/2}_{-{L/2}}
+	\end{equation}   }
+	where integration range $L$ is related to $\tilde L$ by requiring that the distance to the pole at $\pm{\tilde L\over 2}$ is cutff
+	\eq{
+({\tilde L\over 2})^2=2\lambda+({ L\over 2})^2}
+
+%	{\color{red} looks wrong : Now for the cutoff field theory living at the boundary, where
+%	\begin{equation}
+%		\beta(x) = \frac{2\pi}{\sqrt{L^2 + 8\lambda}}
+%			\pqty{
+%				\pqty{\frac{L}{2}}^2
+%				- x^2
+%			} \,\pdd{t}
+%	\end{equation}}
 	The entanglement entropy is
@@
 
-	Note that in the above arguments we've assumed conformal symmetry, which we no longer have after a $T\bar{T}$ deformation.
+	Note that in the above arguments we've assumed conformal symmetry, which we no longer have after a \TTbar deformation.
 However, as we've demonstrated above, it seems that this trick still works for the deformed theory.
@@
 	\end{equation}
-	The relation between $l_b$ and $l$ comes from the gravitational side,
+	\sidenote{The relation between $l_b$ and $l$ comes from the gravitational side, [no way to explain this from the field theory side]}
 	\begin{equation}
@@
 	$, where $x_\pm = -x_\mp$, and same for $t_\pm, u_\pm, v_\pm$. 
-	$L_\infty$ is the coordinate length of the boundary interval $\mcal{A}$ at the asymptotic infinity; this corresponds to the field theory side $L_\mrm{CFT}$. 
+	$L_\infty$ is the coordinate length of the boundary interval $\mcal{A}$ at the asymptotic infinity; this corresponds to the field theory side ${\tilde L}$. 
 	For now the coordinates $u_\pm, v_\pm, x_\pm, t_\pm$ and the coordinate length $L_\infty$ are all specified at $z\to 0$, i.e.~at the \textbf{asymptotic boundary}.
@@
 
-\subsection{Euclidean periodicity of the modular flow}
-\subsubsection{Cutoff Poincar\'e $\mrm{AdS}_3$ and the loss of $2\pi$ periodicity}
+\subsubsection{Zero temperature: cutoff Poincar\'e $\mrm{AdS}_3$ and the loss of $2\pi$ periodicity}
 
@@
 		\sqrt{1 + (2z_c/L)^2}
-	$ which is featured prominently in the $T\bar{T}$ deformed $C(L)$ function, given in \cite{Lewkowycz:2019xse}:
+	$ which is featured prominently in the \TTbar deformed $C(L)$ function, given in \cite{Lewkowycz:2019xse}:
 	\begin{equation}
@@
 	$ guarantees that after Wick rotation, the Euclidean periodicity around the horizon is normalized to $\beta = 1$.
-However, if we restrict to the field theory living at constant cutoff $z = z_c$, which corresponds to a $T\bar{T}$ deformed theory \cite{McGough:2016lol,Lewkowycz:2019xse} \sidenote{[more citations needed]}, since it has no knowledge of the $\pdd{z}$ component of $\xi$, we should reduce it to a modular flow within the $z = z_c$ plane by, e.g.~projecting the $z$ component out, which leaves us:
+However, if we restrict to the field theory living at constant cutoff $z = z_c$, which corresponds to a \TTbar deformed theory \cite{McGough:2016lol,Lewkowycz:2019xse} \sidenote{[more citations needed]}, since it has no knowledge of the $\pdd{z}$ component of $\xi$, we should reduce it to a modular flow within the $z = z_c$ plane by, e.g.~projecting the $z$ component out, which leaves us:
 	\begin{equation}
@@
 	\begin{itemize}
-	\item The $T\bar{T}$ deformation might somehow correspond to a variation of temperature at the cutoff; instead of $\rho = e^{-\mcal{H}}$, we now have:
+	\item The \TTbar deformation might somehow correspond to a variation of temperature at the cutoff; instead of $\rho = e^{-\mcal{H}}$, we now have:
 	\begin{equation}
@@
 
-	\item The non-local nature of $T\bar{T}$ deformation creates some $\order{z_c}$ ``fuzziness'' in the cutoff theory at $z = z_c$; $\beta \sim 1$ holds only up to some coarse-graining of points. 
+	\item The non-local nature of \TTbar deformation creates some $\order{z_c}$ ``fuzziness'' in the cutoff theory at $z = z_c$; $\beta \sim 1$ holds only up to some coarse-graining of points. 
 %	Q: again, how do we make this precise?
@@
 	Maybe we should not expect that the entire time-evolved deformed theory can be embedded into the bulk.
-\sidenote{We could look at the proof of $T\bar{T}$ duality and check if this is really implied.
+\sidenote{We could look at the proof of \TTbar duality and check if this is really implied.
 It is quite possible that we only need to embed the boundary theory at a specific time slice, and the trace flow arguments will go through.}
@@
 	\end{equation}
+	\begin{equation}
+		(\chi_\xi)_r
+		= \frac{T\var{T}}{G}
+			\frac{1}{(r^2 - 4T^2)^{3/2}}
+			\frac{\sinh 2T\phi}{\sinh TL}
+	\end{equation}
 
@@
 	\end{equation}
+
+	\sidenote{Observation:}
+	\begin{equation}
+		\var{Q}_\xi
+		= \int_{r = \mrm{const}} \dd{\phi} (\chi_\xi)_\phi
+		= \frac{\var{T} \coth L_\infty T}{2G}
+			\int_{-L/2}^{L/2} \dd{\phi}
+			\pqty{
+				1 - {\frac{r}{\sqrt{r^2 - 4T^2}}}
+				\frac{\cosh 2T\phi}{\cosh TL_\infty}
+			}
+	\end{equation}
+	\sidenote{The integral seems to rely on the $r$ coordinate!} However, as $T\to 0$ they are the same. \sidenote{How is this consistent with the finite temperature field theory calculation?}
 
@@
 	The discussion above is in the framework of $\mrm{CFT}_2$, but with different modular flow generator.
-Now we consider the framework of $T\bar{T}$ deformed theories.
+Now we consider the framework of \TTbar deformed theories.
 The thermal entropy with unit length is

### 2021-06-21 alpha/CutoffModularFlow/draft1.tex
Update draft with outlines & update TeXplates

@@
 \addtocounter{section}{-1}
+
+\begin{itemize}
+\item add black hole spectrum 
+\item geometric picture
+\item maybe consider later: SSA 
+\item maybe consider later: finite size effect  
+\end{itemize}
+
 \section{Conventions}
@@
 
-\section{Boundary story}
+\section{$T \bar T$ deformation and cutoff AdS}
+
+\subsection{Brief review of the duality}
+
+\subsection{ gravitional charges}
+\subsection{black spectrum from gravitional charges}
+
+\section{Entanglement in the boundary story}
 	A boundary interval $\mcal{A}$ defines a denisty matrix:
@@
 	\end{equation}
-	\sidenote{The relation between $l_b$ and $l$ comes from the gravitational side, [no way to explain this from the field theory side]}
+	\sidenote{The relation between $l_b$ and $l$ comes from the gravitational side, [explain through coordinate map]}
 	\begin{equation}

### 2021-06-21 Strings2020/strings2/strings2.tex
Add minor tweaks to various notes
Update strings with note on finite transformations

@@
 %\InputIfFileExists{../id.tex}{}{}
+
+\usepackage{cancel}
 
@@
 	\begin{enumerate}
-	\item For simplicity, assume for now $X = X(z)$: holomorphic. Note that the $\alpha'$ term comes from the transformation of \textit{internal} degrees of freedom. We have:
+	\item For simplicity, assume for now $X = X(z)$: holomorphic.
+Note that the $\alpha'$ term comes from the transformation of ``\textit{internal}'' degrees of freedom, associated with the conformal properties of $X$.
+We have:
 	\begin{gather}
@@
 		= -\frac{\alpha' V}{2}\,\pd\epsilon
-			+ \order{\epsilon^2},
+			+ \order{\epsilon^2}
 %		\simeq -\frac{\alpha' V}{2}\,\pqty{
@@
 	\end{gather}
-	This is a first order approximation of the finite transformation $z\mapsto z' = w(z)$.
-
-	To obtain a full expression, notice that for the above transformation to be a \textit{symmetry}, the action should be invariant under $X(z)\mapsto X'(z)$:
-	\begin{equation}
-		S' = S
-		\ \Longrightarrow\ %
-		\int \dd[2]{z}
-			\pd X'^\mu \pdbar X'_\mu (z,\bar{z})
-		\xlongequal{(*)} \int \dd[2]{z'}
-			\pd' X'^\mu \pdbar' X'_\mu (z',\bar{z}')
-		= \int \dd[2]{z}
-			\pd X^\mu \pdbar X_\mu (z,\bar{z})
-	\end{equation}
-	Here at $(*)$ we use the diff-invariant property of the action. 
-	Restore the anti-holomorphic component and insert \eqref{eq:dilaton_holomorphic}, then we find that in order to cancel the $\order{\epsilon^2}$ terms, we have to fix:
-%	\begin{gather}
-%		X'(z',\bar{z}') - \alpha'V
-%		\simeq X(z,\bar{z})
-%			- \frac{\alpha' V}{2}\,\pqty{
-%				\dv{z'}{z} + \dv{\bar{z}'}{\bar{z}}
-%			},\\[1ex]
-%		X\longmapsto
-%		X'(z,\bar{z})
-%		\simeq X\pqty\Big{
-%				w^{-1}(z),\bar{w}^{-1}(\bar{z})
-%			} + \alpha'V
-%			- \frac{\alpha' V}{2}\,\pqty{
-%				\dv{w}{z} + \dv{\bar{w}}{\bar{z}}
-%			},
-%	\end{gather}
-	\begin{equation}
-		X'(z') - X(z)
-		= -\frac{\alpha' V}{2}\,\pqty{
-			\pd\epsilon
-			- \frac{1}{2}\,(\pd\epsilon)^2
-			+ \order{\epsilon^3}
-		}
-	\end{equation}
-	The above process can be done order by order, in the end we obtain that\footnote{
+	This is a first order approximation of the finite transformation, where the transformation parameters are the modes $\epsilon_n$ of $\epsilon(z)$; namely, we have:
+	\begin{equation}
+		w(z) = z + \epsilon(z) + \order{\epsilon^2},
+	\quad
+		\epsilon(z) = \sum_n \epsilon_n z^n
+	\end{equation}
+	\vspace{-.5\baselineskip}
+	\begin{equation}
+		F[w(z)] = X'(z') - X(z)
+	\ \xlongrightarrow{w\to 0\,}\ %
+		-\frac{\alpha' V}{2}\,\pd\epsilon
+			+ \order{\epsilon^2}
+	\end{equation}
+
+%	For the finite ``internal'' transformation induced by $w(z)$, 
+	What the above actually means is that:
+	\begin{equation}
+		\fdv{\epsilon_n} F[w(z)]_{\epsilon\to 0}
+		= -\frac{\alpha' V}{2}\,\fdv{\epsilon_n}\,
+			\pdd{z} \pqty\big{w(z) - z}
+		= -\frac{\alpha' V}{2}\,
+			n z^{n-1}
+	\end{equation}
+	Where $\epsilon\to 0$ corresponds to $w \to z$, i.e.~the transformation goes to the identity. 
+	On the other hand,
+	\begin{equation}
+	\begin{aligned}
+		\fdv{F}{\epsilon_n}
+		&= \pdv{F}{w} \fdv{w}{\epsilon_n}
+			+ \pdv{F}{(\pd w)} \fdv{(\pd w)}{\epsilon_n}
+			+ \pdv{F}{(\pd^2 w)} \fdv{(\pd^2 w)}{\epsilon_n}
+			+ \cdots \\
+		&= \pdv{F}{w}\, z^n
+			+ \pdv{F}{(\pd w)}\, n z^{n-1}
+			+ \pdv{F}{(\pd^2 w)}\, n(n-1)\,z^{n-2}
+			+ \cdots
+	\end{aligned}
+	\end{equation}
+
+	By comparing the two above equations, and noting that $\pdv{F}{(\pd^\bullet w)}$ should have no dependence on $n$, we obtain the following constraints on the form of $F[w(z)]$:
+	\begin{equation}
+		F|_{w\to z} = 0,
+	\quad
+		\pdv{F}{w}\bigg|_{w\to z} = 0,
+	\quad
+		\pdv{F}{(\pd w)}\bigg|_{w\to z}
+		= -\frac{\alpha' V}{2},
+	\quad
+		\pdv{F}{(\pd^k w)}\bigg|_{w\to z} = 0,
+	\quad k = 2,3,\cdots
+	\end{equation}
+	We can think of this as the first order ``Taylor'' coefficients of $F[w]$ in the functional space, around the point $w(z) \to z$. Note that $\pd w|_{w\to z} = 1$, while $
+		\pd^k w|_{w\to z} = 0
+	$, it is thus natural to consider the following ansatz:
+	\begin{equation}
+		F = F[\pd w],
+	\quad
+		F[1] = 0,
+	\quad
+		\pdv{F[x]}{x}\bigg|_{x\to 1}
+		= -\frac{\alpha' V}{2}
+	\end{equation}
+
+	In the end we shall obtain that\footnote{
 		I would like to thank Lucy Smith for helpful discussions. 
-A better recipe to find finite transformations is to consider its properties under composition, which will lead to some constraints that can be solved to obtain the result.
 	}:
@@
 		X'(z',\bar{z}') - X(z,\bar{z})
-		&= -\frac{\alpha' V}{2}\,\pqty{
-			\pd\epsilon
-			- \frac{1}{2}\,(\pd\epsilon)^2
-			+ \frac{1}{3}\,(\pd\epsilon)^2
-			- \cdots
-		} + \pqty{\mrm{conjugate}} \\
-		&= -\frac{\alpha' V}{2}\,
-			\ln (1 + \pd\epsilon)
-		+ \pqty{\mrm{conjugate}} \\[.5ex]
 		&= -\frac{\alpha' V}{2}\,
@@
 	\end{equation}
+	A better recipe to find finite transformations is to consider its properties under composition, which will lead to some constraints that can be solved to obtain the result\footnote{
+		See \https{bryango.github.io/resources/archive/alpha/schwarzian.pdf} for some detailed discussions.
+	}.
 

### 2021-06-21 Strings2020/strings5/strings5.tex
Add various updates to homework

@@
 See also section 6.3 of Blumenhagen et al, \textit{Basic Concepts of String Theory}.
+See also section 2.1, 2.2 of \arxiv{1912.07654} where the switch between ensembles is reviewed in the context of holography.
 	}.
@@
 	\begin{enumerate}
-	\item The first contributions to the orbifold partition function comes from the states that are invariant reflection $r$; we have:
+	\item The first contributions to the orbifold partition function comes from the states that are invariant under reflection $r$; we have:
 	\begin{equation}

### 2021-06-21 alpha/HolographicEntanglement/holography.tex
Add beamer on holographic entanglement

% !TeX document-id = {c68ea1ac-ebac-4541-a297-17005c6d2297}
% !TeX encoding = UTF-8
% !TeX spellcheck = en_US
% !TeX TS-program = pdflatex
% !TeX TXS-program:bibliography = biber -l zh__pinyin --output-safechars %

\documentclass[aspectratio=169,10pt
%	,handout
	,noamsthm
]{beamer}

\input{preamble.tex}

\usepackage{tikz}
%\usepackage{snapshot}

%Title
	\title{Understanding Holographic Entanglement}
	\subtitle{With gravitational path integral \& tensor network}
	\author{\textkai{赖文昕} \texttt{2019311369}}
	\institute{\large\ccbyncsajp}
	\date{}

\newcommand{\veccol}[1]{\pqty{
	\begin{smallmatrix}
		#1
	\end{smallmatrix}
}}

\addbibresource{holography.bib}
%\usepackage{cprotect}

\usepackage{cancel}
\newcommand{\slot}{{\,\bullet}}

\begin{document}
{%%% TITLEPAGE
\setbeamercolor{title in head/foot}{
		use=palette quaternary
		,fg=palette quaternary.bg
	}
\logo{}
\begin{frame}
	\titlegraphic{\vspace{2\baselineskip}}
	\titlepage
	\tikz [remember picture,overlay]
	\node at ([
		yshift=-3.2\baselineskip,xshift=.2\linewidth
	] current page.center) {
		\begin{minipage}{.6\textwidth}
		\flushright
		\includegraphics[height=.45\textheight]{img/escher.jpg}
		\quad
		\includegraphics[height=.45\textheight]{img/escher_links.png}
		\\[1ex]
		\footnotesize\textcite{Dunham:Escher} on Escher's art
		\hspace{0em}
		\end{minipage}
	};

\end{frame}
}%%% TITLEPAGE

\begin{frame}{Introduction}
\begin{itemize}
\item \textbf{Question:} how can we \textit{``prepare'' / construct a state,} e.g.
	\begin{itemize}
	\item vacuum: $\rho = \dyad{0}$
	\item thermal: $\rho \propto \sum_n e^{-\beta H} \dyad{n}$
	\end{itemize}
	... in a \textit{holographic} system? \\
\pause
\item \textbf{Answer:} via holography! (\textit{duh...})
	\begin{itemize}
	\item Gravitational path integral\pause
	\item Tensor network
	\end{itemize}\pause
\item Entanglement entropy captures some ``structure'' of the state
\end{itemize}
\end{frame}

\section{Review: boundary entanglement as gravitational saddles}

\begin{frame}{Recall: Path Integral in the Boundary \& the Bulk}{%
	\textcite{Lewkowycz:2013nqa}:\,\citetitle{Lewkowycz:2013nqa}%
}
	\begin{columns}
	\begin{column}{.3\textwidth}
		\begin{figure}[!h]
		\centering
		\includegraphics[width=\linewidth]{img/blackhole_donut.png}
		\caption{Thermal $\mcal{Z}_\beta$}

		\footnotesize
		Thermal partition function \\ in the bulk \& the boundary
		\\[2ex]
		\scriptsize
		Image made from \textcite{Benjamin:2020mfz} and the EHT black hole photo
		\end{figure}
	\end{column}
	\begin{column}{.7\textwidth}
		\begin{itemize}
		\item In \textit{any} field theory, a thermal state\\ can be prepared by a path integral;
		\item In a \textit{holographic} theory, $
			\mcal{Z}_{\pd B} = \mcal{Z}_{B\textit{ulk}}
		$,\\
		a boundary state can be prepared by a bulk path integral.
	\pause
		\begin{itemize}
		\item e.g.~the thermo-field double $\leftrightarrow$ the BTZ black hole\\
			Note that the Euclidean BTZ geometry is smooth:\\
			filling in the $t_E$ cycle (\textit{not} the $\phi$ cycle) of the torus

		\item c.f.~Chern-Simons/WZW: not quite the same
		\end{itemize}
		\end{itemize}
	\end{column}
	\end{columns}
\end{frame}

\begin{frame}{Recall: Gravitational Path Integral}{%
	\textcite{Lewkowycz:2013nqa}:\,\citetitle{Lewkowycz:2013nqa}%
}
	\begin{columns}
	\begin{column}{.3\textwidth}
		\begin{figure}[!h]
		\centering
		\includegraphics[width=\linewidth]{img/blackhole_donut.png}
		\caption{Thermal $\mcal{Z}_\beta$}

		\footnotesize
		Thermal partition function \\ in the bulk \& the boundary
		\\[2ex]
		\scriptsize
		Image made from \textcite{Benjamin:2020mfz} and the EHT black hole photo
		\end{figure}
	\end{column}
	\begin{column}{.7\textwidth}
		\begin{equation}
			\mcal{Z}_{\pd B} = \mcal{Z}_{B\textit{ulk}}
		\end{equation}
		\vspace{-1.2\baselineskip}
		\begin{itemize}
		\item Replica trick: entanglement entropy for a region $R$:
		\begin{equation}
			S_R
			= \Tr
				\rho_R \log \rho_R
			\ \Leftarrow\ %
			\Tr \rho_R^n \equiv \mcal{Z}_n
		\end{equation}
		i.e.~reduced to the partition function of the $n$-replica.\\
		It can be deployed in the boundary \& the bulk!
			\begin{itemize}
			\item Boundary: static geometry, but the field theory is usually strongly coupled --- often difficult!
		\pause
			\item Bulk: dynamic geometry, weakly coupled gravity:\\
			gravity fills in the bulk smoothly, \\
			$
				\mcal{Z} \sim \sum_i e^{-S_i[g_{\mu\nu}]}
			$: sum over classical saddles
			\end{itemize}
		\end{itemize}
	\end{column}
	\end{columns}
\end{frame}

\begin{frame}{Recall: Replica Trick and the Ryu--Takayanagi Proposal}{%
	\textcite{Lewkowycz:2013nqa}:\,\citetitle{Lewkowycz:2013nqa}%
}
	\begin{columns}
	\begin{column}{.425\textwidth}
		\begin{figure}[!h]
		\centering
		\includegraphics[width=\linewidth]{img/replica.png}
		\caption{The bulk replica \cite{Lewkowycz:2013nqa}}
		\end{figure}
	\end{column}
	\begin{column}{.55\textwidth}
		\begin{itemize}
		\item $\mcal{Z} \sim \sum_i e^{-S_i[g_{\mu\nu}]}$, saddle pt.\ approx.\\
			$\To$ minimize $S[g_{\mu\nu}]$ on the $n$-replica $\widetilde{\mcal{M}}_n$
		\item $\widetilde{\mcal{M}}_n/\mbb{Z}_n$: conical singularity at the $\mbb{Z}_n$; $n\to 1$,\\
			$\To$ minimize the area of the $\mbb{Z}_n$ fixed point\\
			$\To$ the extremal surface, the RT surface
		\\[2ex]
	\pause
		\item \textbf{Lesson:} use bulk path integral to:
			\begin{itemize}
			\item prepare the states
			\vspace{-1ex}
			\item compute the entanglement entropy
			\end{itemize}
			This requires holography, \\
			but not necessarily $\mrm{AdS/CFT}$!
		\end{itemize}
	\end{column}
	\end{columns}
\end{frame}

\section{Compare: bulk emergence from tensor networks}

\begin{frame}{Prepare states via Tensor Networks}{%
	\textcite{Vidal:2007hda}, \textcite{Swingle:2009bg}. Reviewed by \textcite{Rangamani:2016dms}.
}
	\begin{columns}
	\begin{column}{.4\textwidth}
		\begin{figure}[!h]
		\centering
		\includegraphics[width=\textwidth]{img/MERA.png}
		\caption{MERA}

		\small
		Multi-scale Entanglement\\
		Renormalization Ansatz
		\\[2ex]
		\footnotesize
		Image from \https{tensornetwork.org}
		\end{figure}
	\end{column}
	\begin{column}{.6\textwidth}
		\begin{itemize}
		\item Gravitational path integral: a spacetime perspective\\
		Tensor network: on a constant time slice
	\pause
		\item States constructed with tensor networks:\\
		common in condensed matter (e.g.~DMRG)\\
		\item To find the ground state of a system
			\begin{itemize}
			\item Write down a tensor network \\
			as an \textbf{ansatz} for the ground state;\\
			\item Vary the components of each tensor \\
			to achieve minimal energy --- \textbf{optimization!}
			\end{itemize}
		\end{itemize}
	\end{column}
	\end{columns}
\end{frame}

\begin{frame}{AdS Bulk as a Tensor Network}{Reviewed by \textcite{Harlow:2018fse}:\,\citetitle{Harlow:2018fse}}
	\begin{columns}
	\begin{column}{.35\textwidth}
		\begin{figure}[!h]
		\centering
		\includegraphics[height=.55\textheight]{img/pentagonpush.pdf}
		\caption{The HaPPY code \cite{Pastawski:2015qua,Harlow:2018fse}}
		\end{figure}
	\end{column}
	\begin{column}{.65\textwidth}
		\begin{itemize}
		\item Gravitational path integral: a spacetime perspective\\
		Tensor network: on a constant time slice
	\pause
		\item Dual geometry in the bulk is understood as\\ the ``continuous limit'' of a \textit{tensor network}\\
			\begin{itemize}
			\item Node: tensor acting on the Hilbert space
			\item Leg: index to be contracted
				\begin{itemize}
				\item $1\times{}$free leg \\takes in bulk local operator insertions
				\item $5\times{}$contracted leg \\propagates the bulk insertions to the boundary
				\end{itemize}
			\end{itemize}
		\end{itemize}
	\end{column}
	\end{columns}
\end{frame}

\begin{frame}{RT from the tensor network}{\textcite{Harlow:2018fse}:\,\citetitle{Harlow:2018fse}}
	\begin{columns}
	\begin{column}{.35\textwidth}
		\begin{figure}[!h]
		\centering
		\includegraphics[height=.55\textheight]{img/cutnetwork.pdf}
		\caption{The HaPPY code \cite{Pastawski:2015qua,Harlow:2018fse}}
		\end{figure}
	\end{column}
	\begin{column}{.65\textwidth}
		\begin{itemize}
		\item ``Entanglement'' between $R$ and $\bar{R}$:\\
		$\propto$ min \# of links connecting the two regions\\
		Naturally, entropy $=$ bulk area!
	\pause
		\item ``Complexity'': \# of nodes\\
		Proposal: complexity $=$ bulk volume!\\
		{\footnotesize See e.g.~\textcite{Susskind:2014rva}}
	\pause
		\item Note: how to actually take the continuous limit?\\
		``Real time'' path integral on a constant time slice
			\begin{itemize}
			\item cMERA: \textcite{Nozaki:2012zj}
			\item ``Path-Integral Optimization'':\\
			\textcite{Boruch:2021hqs}
			\end{itemize}
		\end{itemize}
	\end{column}
	\end{columns}
\end{frame}

\begin{frame}{The Lesson}
	\begin{itemize}\large
	\item The Ryu--Takayanagi proposal: $S \sim \frac{A}{4G_N}$
		\begin{itemize}\normalsize
		\item ... seems to be universal in holographic systems, 
		\item ... where boundary states can be constructed from some sort of bulk operations:
			\begin{itemize}
			\item Gravitational path integral
			\item Tensor network
			\end{itemize}
		\end{itemize}
	\item Applications: beyond standard $\mrm{AdS}_3/\mrm{CFT}_2$
		\begin{itemize}\normalsize
		\item Cutoff holography: \textcite{Lewkowycz:2019xse}
		\vspace{-.5ex}
		\item Flat holography: \textcite{Apolo:2020bld,Apolo:2020qjm}
		\end{itemize}
	\end{itemize}
\end{frame}

\section{Application: cutoff $\mrm{AdS}_3\,/\,T\bar{T}$ deformed theory}

\begin{frame}{Cutoff $\mrm{AdS}_3\,/\,T\bar{T}$ deformed theory}{%
	\textcite{McGough:2016lol}%
}
	\begin{columns}
	\begin{column}{.35\textwidth}
		\begin{figure}[!h]
		\centering
		\includegraphics[height=.55\textheight]{img/cutnetwork.pdf}
		\caption{The HaPPY code \cite{Pastawski:2015qua,Harlow:2018fse}}
		\end{figure}
	\end{column}
	\begin{column}{.65\textwidth}
		\begin{itemize}
		\item $\mrm{AdS}_3$ with finite cutoff:\\
		\textit{holographic renormalization} of the boundary theory

	\pause

			\begin{itemize}
			\item This is clear in the tensor network picture\\
			``coarse-graining''
			\end{itemize}

	\pause

		\item Deform the boundary $\mrm{CFT}_2$ with some operator:\\
		$\mrm{CFT}_2^{\,(\mrm{UV})} \leadsto {}$deformed theory$^{\,(\mrm{IR})}$

		\item Surprisingly, we were able to find the deformed theory!\\
		$
			\var{S} \propto \mu\,(T\bar{T})_\mu,\ %
			T\bar{T}
			= \frac{1}{8} \pqty{
					T^{\alpha\beta} T_{\alpha\beta}
					- (T^\alpha_\alpha)^2
				}
		$

			\begin{itemize}

			\item See e.g.~\textcite{Smirnov:2016lqw}

			\item \textcite{McGough:2016lol}:\\
			\citetitle{McGough:2016lol}

			\end{itemize}

		\end{itemize}
	\end{column}
	\end{columns}
\end{frame}

\begin{frame}{Holographic Entanglement in Cutoff $\mrm{AdS}_3$}{%
	\textcite{Lewkowycz:2019xse}%
}
	\begin{columns}
	\begin{column}{.35\textwidth}
		\begin{figure}[!h]
		\centering
		\includegraphics[height=.55\textheight]{img/cutnetwork.pdf}
		\caption{The HaPPY code \cite{Pastawski:2015qua,Harlow:2018fse}}
		\end{figure}
	\end{column}
	\begin{column}{.65\textwidth}
		\begin{itemize}
		\item If we \textit{assume} that the tensor network intuition is valid,\\
		Then the RT proposal should still hold!

			\begin{itemize}
			\item This is shown by \textcite{Lewkowycz:2019xse}
			\end{itemize}

	\pause

		\item Generalization of $A$ in $S \sim \frac{A}{4G_N}$:
		$A$ is actually the gravitational charge of the \textit{replica symmetry},

			\begin{itemize}
			\item ... \textit{analytically continued} from $\mbb{Z}_n$ to $U(1)$,
		\vspace{-.5ex}
			\item ... corresponds to the Killing horizon generator / \textit{modular flow generator} $\xi$.

			\item This would in turn give us a hint of the modular flow\\
			 in the $T\bar{T}$ deformed theory! (\textit{ongoing work})

			\end{itemize}

		\end{itemize}
	\end{column}
	\end{columns}
\end{frame}

\begin{frame}{Further Reading \& Outlook}
	\begin{itemize}
	\item Single-trace $T\bar{T}$ duality and the flow towards to UV
		\begin{itemize}
		\item \fullcite{Apolo:2019zai}
		\end{itemize}
	\item Quantum error correction:
		\begin{itemize}
		\item \fullcite{Jahn:2021uqr}
		\end{itemize}
	\item Tensor network for flat spacetime?
		\begin{itemize}
		\item \fullcite{May:2016dgv}
		\end{itemize}
	\end{itemize}
\end{frame}

\begin{frame}[allowframebreaks]{References}
\renewcommand*{\bibfont}{\footnotesize}
\printbibliography[%
%	title = {参考文献} %
	,heading = bibintoc
]
\end{frame}

\end{document}

### 2021-06-22 alpha/CutoffModularFlow/notes.tex
Add notes on gravitational charges

--- 2021-06-21 alpha/CutoffModularFlow/draft1.tex
@@
 \section{$T \bar T$ deformation and cutoff AdS}
+In this section we first review the holographic duality between $T\bar T$ deformed CFT$_2$ and Einstein gravity on asymptically AdS$_3$ spacetime with a finite cutoff,  and then we use the covariant phase space method to calculate the gravitational charges for BTZ black holes with finite cutoff and show that the black hole spectrum matches that of  $T\bar T$ deformed CFT$_2$.
 
@@
 
-\subsection{ gravitional charges}
+review TTbar and cutoff AdS
+
 \subsection{black spectrum from gravitional charges}
+	Ref: \textcite{Wald:1993nt,Iyer:1994ys,Iyer:1995kg}, \textcite{Lewkowycz:2013nqa}, and \textcite{Faulkner:2013ana}.
+
+	Here we derive the quasilocal energy of the BTZ black hole using the covariant formulation of conserved charges and reproduce the spectrum of $T\bar{T}$-deformed CFTs.
+
+\subsubsection*{Covariant charges}
+
+	Let us first recall the definition of asymptotic charges.
+Given an asymptotic Killing vector $\xi$ generating a symmetry of the theory, the infinitesimal variation of the corresponding charge is given by~\cite{Barnich:2001jy}
+	  %
+	  \eq{
+	  \d Q_{\xi} [\d g, g] =  \frac{1}{16 \pi G} \int_{\p\ss} \sqrt{|g|} \diff x^{\a} \ve_{\a\mu\nu} k_\xi^{\mu\nu} [\d g, g],  \label{charges}
+	  }
+	  %
+	where $\d g$ denotes the variation of the metric, $\p \ss$ is the boundary of a codimension-1 spacelike surface, and  in Einstein gravity $k_\xi^{\mu\nu} [\d g, g]$ is given by
+	  %
+	  \eqsp{
+	  k_\xi^{\mu\nu}[\d g, g] = \frac{1}{2} \Big \{ & \xi^{\nu}\nabla^{\mu} \d g^{\a}{}_{\a} - \xi^{\nu} \nabla_{\a} \d g^{\a\mu} + \xi_{\a} \nabla^{\nu} \d g^{\a\mu} + \frac{1}{2} \d g^{\a}{}_{\a} \nabla^{\nu} \xi^{\mu} - \frac{1}{2} \d g^{\nu\a} \nabla_{\a}\xi^{\mu} \\
+	  &+ \frac{1}{2} \d g^{\nu\a} \nabla^{\mu} \xi_{\a} - (\mu \lra \nu) \Big \}. \label{kdef}
+	  }
+	  %
+	As discussed in~\cite{Compere:2015knw}, in three-dimensional gravity the asymptotic charges~\eqref{charges} can be evaluated on any surface and not only at the asymptotic boundary.
+This is true provided the asymptotic Killing vectors are appropriately continued to the interior so that the integrability condition on the charges is satisfied.
+
+\subsubsection*{Killing vectors}
+
+	The quasilocal energy discussed in~\cite{Brown:1994gs} differs from the asymptotic charges~\eqref{charges} in the choice of Killing vectors or, alternatively, in the choice of observers.
+More precisely, asymptotic charges are measured by asymptotic observers at the asymptotic boundary while quasilocal charges are measured by locally nonrotating observers on a codimension-2 spacelike surface $\p\Sigma$.
+To determine the quasilocal energy, first recall that in Schwarzschild coordinates the BTZ metric may be written as~\cite{Banados:1992wn}
+	  %
+	  \eq{
+	  ds^2 = - f(r) dt^2 + \frac{dr^2}{f(r)} + r^2 \bigg ( d\phi + \frac{4 G J}{r^2} dt \bigg )^2, \label{btz}
+	  }
+	  %
+	where $f(r)$ reads
+	  %
+	  \eq{
+	  f(r) = r^2 - 8 GM + \frac{16G^2 J^2}{r^2}. \label{fr}
+	  }
+	  %
+	The induced metric on an $r = r_c$ hypersurface $\ss_{r_c}$ has vanishing curvature and is given by
+	  %
+	  \eq{
+	  ds^2_{c} = \g_{\mu\nu} dx^{\mu} dx^{\nu} =  r_c^2 \Bigg [ -\frac{f (r_c)}{r_c^2} dt^2 + \bigg ( d\phi + \frac{4 G J}{r_c^2} dt \bigg )^2 \Bigg ]. \label{inducedmetric}
+	  }
+	  %
+	%The quasilocal energy at $\p \ss_{r_c}$ depends on the definition of the Killing vector $\xi$ in the geometry~\eqref{inducedmetric}.
+
+	Let us denote by $\xi_c$ the timelike Killing vector associated with the quasilocal energy $Q_{\xi_c}$.
+The Killing vector $\xi_c$ is proportional to the unit vector normal to surfaces of fixed time.
+This vector evolves constant-$t$ slices forward in time and provides a natural definition of the energy in the background given by eq.~\eqref{inducedmetric}.
+In particular, $\xi_c$ can be chosen to satisfy
+	  %
+	  \eq{
+	  \xi_c = -{r_c \sqrt{f(r_c)}} \g^{\mu \nu } \d^{t}_{\mu}\, \p_{\nu}, \qquad \qquad \xi_c \cdot \xi_c = -r_c^2, \label{xi2}
+	  }
+	  %
+	where the inner product is defined with respect to the induced metric~\eqref{inducedmetric}.
+The norm in eq.~\eqref{xi2} is chosen to match that of the asymptotic timelike Killing vector $\p_t$ used in the definition of the total energy of the spacetime, in the limit when $r_c \to r$.
+In particular, in this limit we find $\xi_c \to \p_t$.
+
+	Alternatively, note that we can perform a coordinate transformation 
+	 % 
+	 \eq{
+	 \til{t}  = \frac{\sqrt{f(r_c)}}{r_c} t, \qquad \qquad \til{\phi} = \phi + \frac{4 G J }{r_c^2}t,
+	 }
+	 %
+	to turn the induced metric~\eqref{inducedmetric} into the Minkowski metric,
+	  %
+	  \eq{
+	  ds^2_{c} = r_c^2 \big (- d\til{t}^2 + d \til{\phi}^2 \big ), \label{mink}
+	  }
+	with the identifications of the original coordinates left intact, i.e.
+	  %
+	  \eq{
+	  (\til{t},\,\til{\phi}) \sim (\tilde{t},\,\til{\phi} + 2 \pi).
+	  }
+	  %
+	We thus find that the Killing vector $\xi_c$ is, up to a normalization, nothing but the generator of time translations in a locally nonrotating frame~\cite{Misner:1974qy},
+	  %
+	  \eq{
+	  \xi_c  = \frac{r_c}{\sqrt{f(r_c)}} \bigg (\p_t - \frac{4 G J}{r_c^2} \p_{\phi} \bigg ) = \p_{\tilde{t}}. \label{xi1}
+	  }
+	  %
+
+	The Killing vector~\eqref{xi1} satisfies the following properties:
+	 %
+	 \begin{enumerate}
+	 \item[(i)] it leads to integrable charges, see eq.~\eqref{quasilocalcharge2};
+	 \item[(ii)] its normalization is background-independent and proportional to $r_c^2$;
+	 \item[(iii)] it measures the energy of a locally nonrotating observer in the orthonormal frame;
+	 \item[(iv)] it reduces to the Killing vector measuring the total (ADM) energy when $r_c \to \infty$.
+	 \end{enumerate}
+
+\subsubsection*{Quasilocal energy}
+
+	We define the infinitesimal variation of the quasilocal energy $\delta Q_{\xi_c}$ as the conserved charge~\eqref{charges} measured by the locally nonrotating observer at the cutoff surface $r = r_c$,
+	  %
+	  \eq{
+	  \d Q_{\xi_c} [\d g, g] & = \frac{r_c}{\sqrt{f(r_c)}} \,\d M - \frac{4 G J}{r_c\sqrt{f(r_c)}} \,\d J, \\
+	 % \d Q_{\xi_c} [\d g, g]  
+	 & = - \frac{r_c}{4 G} \d \sqrt{f(r_c)}. \label{quasilocalcharge2}
+	  }
+	  %  
+	The integrability condition of $Q_{\xi_c}$ is manifestly satisfied in eq.~\eqref{quasilocalcharge2}, where we have used the expression for $f(r)$ given in eq.~\eqref{fr}.
+The finite charge can be integrated to be
+	  %
+	  \eq{
+	Q_{\xi_c} = \frac{r_c^2}{ 4G} - \frac{r_c^2}{ 4G}  \sqrt{1 -\frac{8GM}{r_c^2} + \frac{16G^2 J^2}{ r_c^4}}, \label{quasilocalcharge3}
+	 }
+	 %
+	where the first term is an integration constant fixed by requiring $Q_{\xi_c}\big |_{M=J=0}=0$.
+Note that eq.~\eqref{quasilocalcharge3} is the quasilocal energy given in~\cite{McGough:2016lol}.
+Furthermore, when the cutoff $r_c$ is taken to infinity, the quasilocal energy~\eqref{quasilocalcharge3} reduces to the ADM mass $M$ of the spacetime.
+
+	\noindent Let us conclude with comments on other definitions of the quasilocal energy discussed in the literature.
+As noted in ref.~\cite{Brown:1994gs} one can in principle define other measures of ``energy'' at a finite cutoff by choosing an appropriate normalization for the timelike Killing vector.
+The Killing vector considered in~\cite{Brown:1994gs} differs from ours in its overall normalization (by a factor of $r_c$) and fails to satisfy conditions (ii) and (iv) above.
+Relatedly, while the Killing vector considered in the quasilocal energy of BTZ-like solutions in ref.~\cite{Giribet:2013yka} does satisfy condition (iv) it is incompatible with condition (ii).
+In particular, we note that the expression for the quasilocal energy reported in~\cite{McGough:2016lol} contains a typo and \emph{does not} correspond to the expression originally given in~\cite{Brown:1994gs}.
+Indeed, to match the spectrum of the $T\bar{T}$ deformed theory one needs to use the Killing vector $\xi_c$ given in eq.~\eqref{xi1}.
+This provides further evidence for the physical requirements constraining our definition of $\xi_c$.
+
+	\noindent\hrulefill
+
+	On the other hand, gravitational entropy is the Noether charge $Q_\xi$ associated with some horizon generator $\xi$.
+In the case of entanglement entropy between a simple interval and its complement, we've found its corresponding modular flow in the bulk, which is precisely the horizon generator of the Rindler patch.
+We then aim to compute the charge variation using the covariant formula:
+	\begin{equation}
+		\var{Q}_{\xi} [\var{g}, g]
+		= \int_{\pd\Sigma}
+			\chi_\xi
+		= \frac{1}{16 \pi G}
+			\int_{\pd\Sigma}
+			\sqrt{|g|} \dd{x}^{\alpha}
+				\varepsilon_{\alpha\mu\nu}\,
+				k_\xi^{\mu\nu} [\var{g}, g]
+	\end{equation}
+	\begin{equation}
+	\begin{aligned}
+		k_\xi^{\mu\nu}[\var g, g]
+		= \frac{1}{2} \Big \{
+		& \xi^{\nu}\nabla^{\mu} \var g^{\alpha}{}_{\alpha}
+		- \xi^{\nu} \nabla_{\alpha} \var g^{\alpha\mu}
+		+ \xi_{\alpha} \nabla^{\nu} \var g^{\alpha\mu}  \\
+		&+ \frac{1}{2} \var g^{\alpha}{}_{\alpha} \nabla^{\nu} \xi^{\mu}
+		- \frac{1}{2} \var g^{\nu\alpha} \nabla_{\alpha}\xi^{\mu}
+		+ \frac{1}{2} \var g^{\nu\alpha} \nabla^{\mu} \xi_{\alpha} \\
+		&- (\mu \leftrightarrow \nu) \Big \}
+	\end{aligned}
+	\label{kdef}
+	\end{equation}
+	However, to compute $\var{Q}$ we need to consider a particular metric variation $\var{g}_{\mu\nu}$ in the phase space of solutions.
+There is no free parameter in Poincar\'e $\mrm{AdS}_3$, unless we turn on temperature; namely we have to start with the BTZ geometry.
 

### 2021-06-22 alpha/CutoffModularFlow/notes.tex
Clean up notes a bit more

@@
 
-%	\item[] In Section 1,
+	\item[] On the field theory side,
+
+	\item Following \cite{Lewkowycz:2019xse,Donnelly:2018bef}, we derive the entanglement entropy for a \TTbar deformed theory, and extend the result to the finite temperature case.
+
+	\item We note that it is possible to generalize the \textit{effective inverse temperature $\beta(x)$} trick introduced in \cite{Wong:2013gua,Cardy:2016fqc}, and re-derive the \TTbar entanglement entropy using the $\mrm{CFT}_2$ modular flow at the \mbox{codim-2} cutoff surface (line).
+\sidenote{[relation with partial entanglement entropy?]}
+
+	\item[] On the bulk side,
 
@@
 This could be related to the violation of boosted strong subadditivity (boosted SSA) in \cite{Lewkowycz:2019xse}.
+\sidenote{We should probably look at the boosted interval.}
 
@@
 
-	\item We try to obtain the entanglement entropy using the modular flow at the \mbox{codim-2} cutoff surface, using the \textit{effective inverse temperature $\beta(x)$} introduced in \cite{Wong:2013gua,Cardy:2016fqc}, which relates the entanglement entropy to some thermal entropy.
-\sidenote{[relation with partial entanglement entropy?]}
-
-	\item \sidenote{We should look at the boosted interval.}
-
-%	\item[] In Section 2,
-
 	\item We map the the modular flow in the Poincar\'e $\mrm{AdS}_3$ vacuum to the BTZ background, and compute the entanglement entropy as gravitational charge. 
-
-	\item We then consider constant $r$ cutoff in the Schwarzschild coordinates, which corresponds to the proposal of \cite{McGough:2016lol}.
-This gives a finite temperature generalization of the result of \cite{Lewkowycz:2019xse}.
+	We then consider constant $r$ cutoff in the Schwarzschild coordinates, which corresponds to the proposal of \cite{McGough:2016lol}.
+This agrees with the finite temperature result we've obtained on the field theory side.
+
+	\item The bulk calculation provides an intuitive explanation of the generalized local temperature trick. \sidenote{Details to be understood.}
 
@@
 
+\pagebreak
+
 \section{Conventions}
@@
 
-review TTbar and cutoff AdS
-
-\subsection{black spectrum from gravitional charges}
+{\color{red}\itshape Review TTbar and cutoff AdS. }
+
+\subsection{Black spectrum from gravitional charges}
 	Ref: \textcite{Wald:1993nt,Iyer:1994ys,Iyer:1995kg}, \textcite{Lewkowycz:2013nqa}, and \textcite{Faulkner:2013ana}.
@@
 This provides further evidence for the physical requirements constraining our definition of $\xi_c$.
-
-	\noindent\hrulefill
-
-	On the other hand, gravitational entropy is the Noether charge $Q_\xi$ associated with some horizon generator $\xi$.
-In the case of entanglement entropy between a simple interval and its complement, we've found its corresponding modular flow in the bulk, which is precisely the horizon generator of the Rindler patch.
-We then aim to compute the charge variation using the covariant formula:
-	\begin{equation}
-		\var{Q}_{\xi} [\var{g}, g]
-		= \int_{\pd\Sigma}
-			\chi_\xi
-		= \frac{1}{16 \pi G}
-			\int_{\pd\Sigma}
-			\sqrt{|g|} \dd{x}^{\alpha}
-				\varepsilon_{\alpha\mu\nu}\,
-				k_\xi^{\mu\nu} [\var{g}, g]
-	\end{equation}
-	\begin{equation}
-	\begin{aligned}
-		k_\xi^{\mu\nu}[\var g, g]
-		= \frac{1}{2} \Big \{
-		& \xi^{\nu}\nabla^{\mu} \var g^{\alpha}{}_{\alpha}
-		- \xi^{\nu} \nabla_{\alpha} \var g^{\alpha\mu}
-		+ \xi_{\alpha} \nabla^{\nu} \var g^{\alpha\mu}  \\
-		&+ \frac{1}{2} \var g^{\alpha}{}_{\alpha} \nabla^{\nu} \xi^{\mu}
-		- \frac{1}{2} \var g^{\nu\alpha} \nabla_{\alpha}\xi^{\mu}
-		+ \frac{1}{2} \var g^{\nu\alpha} \nabla^{\mu} \xi_{\alpha} \\
-		&- (\mu \leftrightarrow \nu) \Big \}
-	\end{aligned}
-	\label{kdef}
-	\end{equation}
-	However, to compute $\var{Q}$ we need to consider a particular metric variation $\var{g}_{\mu\nu}$ in the phase space of solutions.
-There is no free parameter in Poincar\'e $\mrm{AdS}_3$, unless we turn on temperature; namely we have to start with the BTZ geometry.
 
@@
 
-	Ref: \textcite{Wald:1993nt,Iyer:1994ys,Iyer:1995kg}, \textcite{Lewkowycz:2013nqa}, and \textcite{Faulkner:2013ana}.
-
 	Gravitational entropy is the Noether charge $Q_\xi$ associated with some horizon generator $\xi$.
-In the case of entanglement entropy between a simple interval and its complement, we've found its corresponding modular flow in the bulk, which is precisely the horizon generator of the Rindler patch.
-We then aim to compute the charge variation using the covariant formula:
-	\begin{equation}
-		\var{Q}_{\xi} [\var{g}, g]
-		= \int_{\pd\Sigma}
-			\chi_\xi
-		= \frac{1}{16 \pi G}
-			\int_{\pd\Sigma}
-			\sqrt{|g|} \dd{x}^{\alpha}
-				\varepsilon_{\alpha\mu\nu}\,
-				k_\xi^{\mu\nu} [\var{g}, g]
-	\end{equation}
-	\begin{equation}
-	\begin{aligned}
-		k_\xi^{\mu\nu}[\var g, g]
-		= \frac{1}{2} \Big \{
-		& \xi^{\nu}\nabla^{\mu} \var g^{\alpha}{}_{\alpha}
-		- \xi^{\nu} \nabla_{\alpha} \var g^{\alpha\mu}
-		+ \xi_{\alpha} \nabla^{\nu} \var g^{\alpha\mu}  \\
-		&+ \frac{1}{2} \var g^{\alpha}{}_{\alpha} \nabla^{\nu} \xi^{\mu}
-		- \frac{1}{2} \var g^{\nu\alpha} \nabla_{\alpha}\xi^{\mu}
-		+ \frac{1}{2} \var g^{\nu\alpha} \nabla^{\mu} \xi_{\alpha} \\
-		&- (\mu \leftrightarrow \nu) \Big \}
-	\end{aligned}
-	\label{kdef}
-	\end{equation}
-	However, to compute $\var{Q}$ we need to consider a particular metric variation $\var{g}_{\mu\nu}$ in the phase space of solutions.
-There is no free parameter in Poincar\'e $\mrm{AdS}_3$, unless we turn on temperature; this leads to the BTZ geometry.
+In the case of entanglement entropy between a simple interval and its complement, its corresponding modular flow in the bulk is precisely the horizon generator of the Rindler patch.
+We can then compute the charge variation using the covariant formula \eqref{charges}.
+
+	Again, to compute $\var{Q}$ we need to consider a particular metric variation $\var{g}_{\mu\nu}$ in the phase space of solutions.
+There is no free parameter in Poincar\'e $\mrm{AdS}_3$, unless we turn on temperature; namely we have to start with the BTZ geometry.
 

### 2021-06-22 alpha/CutoffModularFlow/notes.tex
Update the boundary story in notes

@@
 \newcommand{\TTbar}{\ensuremath{T\bar{T}}\xspace}
+\newcommand{\arcsinh}{\ensuremath{\mop{arcsinh}}}
 
@@
 \section{Entanglement in the boundary story}
+
+\subsection{Rindler map in finite temperature}
+
+\newcommand{\lp}{\ensuremath{l_p}}
+\newcommand{\halfL}{\ensuremath{\frac{L}{2}}}
+
+	One can use the method in \cite{Lewkowycz:2019xse} to calculate the entanglement entropy in the thermal case and finite size case from the field theory side.
+The Rindler transformation from the domain of dependence of the interval $(-\lp,\lp)$ to the sphere is
+	\begin{equation}
+	t=\lp\frac{\sin\theta \sinh(\tau/\lp)}{1+\sin\theta \cosh(\tau/\lp)},\ \  x=\lp\frac{\cos\theta}{1+\sin\theta\cosh(\tau/\lp)}
+	\end{equation}
+	the conformal factor reads,
+	\begin{equation}
+	\Omega=\frac{1}{1+\sin\theta\cosh(\tau/\lp)}
+	\end{equation}
+	At endpoints, it becomes $1$.
+From the discussion in \cite{Lewkowycz:2019xse}, the contribution to the entanglement entropy totally comes from the endpoints of the interval, so one can use the such conformal transformation where the conformal factor at the endpoints is $1$ to calculate the entanglement entropy.
+Also, in the conformal map above from the casual diamond to the sphere, only the length of the interval matters.
+If these two endpoints lie at other position, one can use the rotation and translation symmetry to put it at $(\pm \lp,0)$, since the $T\bar T$ deformed theory also admits these symmetries.
+
+	Now let's consider the thermal case. The conformal transformation from the thermal cylinder to the plane reads,
+	\begin{equation}
+	z=\frac{1}{\kappa}e^{\kappa w},\ \ \ \kappa=\frac{2\pi}{\beta}
+	\end{equation} 
+	where $z$ is the coordinate on the plane, and $w$ is the coordinate on the thermal cylinder with identification,
+	\begin{equation}
+	w\sim w+i\beta
+	\end{equation}
+	The endpoints of the interval on the thermal cylinder is
+	\begin{equation}
+	w=\pm \halfL
+	\end{equation} 
+%	The length of the interval is $L=2l$. 
+	Under the conformal map, the endpoints on the plane is
+	\begin{equation}
+	\frac{1}{\kappa}e^{\pm \kappa \frac{L}{2}}
+	\end{equation}
+	the length is $\frac{2}{\kappa}\sinh(\halfL \kappa)$, so one can use translations and rotations to map the endpoints to $(\pm \lp, 0)$ on the plane 
+	\begin{equation}
+	l_p=\frac{1}{\kappa}\sinh(\halfL \kappa)
+	\end{equation}
+	The conformal factor is
+	\begin{equation}
+	e^{\kappa(w+\bar{w})}
+	\end{equation}
+	Note that compared to the usual map from cylinder to plane $z=e^{\kappa w}$, we put the overall scaling factor $\frac{1}{\kappa}$ to make sure that the conformal factor at the endpoints is $1$.
+
+	From \cite{Donnelly:2018bef}, the entanglement entropy for zero temperature is
+	\begin{equation}
+	S(L)=\frac{c}{3} \arcsinh \frac{\lp}{a}
+	\end{equation}
+	where
+	\begin{equation}
+	a^2=\frac{\mu c}{12}
+	\end{equation}
+	The $C$-function reads,
+	\begin{equation}
+	C(L)=L S'(L)=\frac{c}{3}\frac{1}{\sqrt{1+4a^2/L^2}}
+	\end{equation}
+	Now in the thermal case, $l_p\rightarrow \frac{1}{\kappa}\sinh(\halfL \kappa)$
+	\begin{equation}
+	S_t=\frac{c}{3}\arcsinh \pqty{
+			\frac{1}{\kappa a}\sinh(\halfL \kappa)
+		}
+	\end{equation}
+	which is the same as the results obtained from the local temperature trick \eqref{} and the gravity calculation \eqref{}. Now consider the finite size case, the conformal transformation is,
+	\begin{equation}
+	z=\frac{1}{ir_1}e^{iwr_1},\quad
+		r_1 = \frac{2\pi}{\lambda}
+	\end{equation}
+	where $w$ is the cylinder coordinate,
+	\begin{equation}
+	w\sim w+ \lambda
+	\end{equation}
+	The endpoints of the interval are 
+	\begin{equation}
+	w\pm l
+	\end{equation}
+	The conformal factor is
+	\begin{equation}
+	e^{ir_1(w+\bar{w})}
+	\end{equation}
+	which is $1$ at the endpoints. The plane length reads,
+	\begin{equation}
+	l_p=\frac{1}{r_1}\sin lr_1
+	\end{equation}
+	So the final result is
+	\begin{equation}
+	S_f=\frac{c}{3}ArcSinh(\frac{1}{r_1a}\sin(lr_1))
+	\end{equation}
+
+\pagebreak
+
+	The global AdS reads,
+	\begin{equation}
+	 ds^2=-(r^2+1)dt^2+\frac{dr^2}{r^2+1}+r^2d\phi^2,\ \ \phi\sim\phi+2\pi
+	\end{equation}
+	\begin{equation}
+	\phi\rightarrow r1\phi,\ \ r\rightarrow \frac{r}{r_1}, \ \ \ t\rightarrow r_2 t
+	\end{equation}
+	\begin{equation}
+	 ds^2=-(r^2+r_1^2)dt^2+\frac{dr^2}{r^2+r_1^2}+r^2d\phi^2,\ \ \phi\sim\phi+\beta
+	\end{equation}
+	Compared to the planer BTZ,
+	\begin{equation}
+	ds^2=-(r^2-r_1^2)dt^2+\frac{dr^2}{r^2-r_1^2}+r^2dx^2
+	\end{equation}
+	For the holographic entanglement entropy
+	\begin{equation}
+	r_1\rightarrow ir_1
+	\end{equation}
+	There is no topological obstacle in global AdS, so one can do the replacement above to get the holographic entanglement entropy in global AdS from the HEE in planer BTZ.
+	\begin{equation}
+	S_f=\frac{c}{3}ArcSinh(\frac{1}{r_1a}\sin(lr_1))
+	\end{equation}
+
+\pagebreak
+\subsection{Boundary modular flows}
+
 	A boundary interval $\mcal{A}$ defines a denisty matrix:
@@
 	\end{equation}
-\subsection{Boundary modular flows}
+
 	In usual $\mrm{CFT}_2$, this prescription gives us the modular flow generators for a single interval $\mcal{A}$:
@@
 			\pqty{
-				\pqty{\frac{{\tilde L}}{2}}^2
+				(\tfrac{{\tilde L}}{2})^2
 				- x^2
@@
 	However, after the \TTbar-deformation, the scaling and special conformal transformations are no longer symmetries of the theory, so we cannot simply take $\xi_\mrm{CFT}$ as the modular flow in the deformed theory.
-
-	On the other hand, we still expect the basic properties of the modular flow to hold after the deformation; for example, we expect the endpoints $\pd\mcal{A}$ of $\mcal{A}$ to be fixed under the modular flow, and we suppose the $\xi_{T\bar{T}}$ should reduce back to $\xi_\mrm{CFT}$ as the deformation parameter $\lambda \to 0$.
-This leads us to the following proposal of $\xi_{T\bar{T}}|_{t = 0}$, for an interval $\mcal{A}$ with coordinate length $L$:
-
-	Note that:
-	\begin{enumerate}[topsep=0pt]
-	\item The dependence of $\xi_{T\bar{T}}|_{t = 0}$ w.r.t.~$L$ is very similar to the dependence of $\xi_\mrm{CFT}|_{t = 0}$ w.r.t.~${\tilde L}$, except that now the normalization is slightly modified to include the deformation parameter $\lambda$.
-	\item This is not yet a proposal for the full modular flow, but only its values around the $t = 0$ slice.
-But we shall see that this is enough to give us the entanglement entropy of a \TTbar-deformed theory.
-	\end{enumerate}
+	But we shall see that by properly specifying the integration range, this is enough to give us the entanglement entropy of a \TTbar-deformed theory.
 
@@
 	\end{equation}
-
-\subsection{Rindler map in finite temperature}
-	One can use the method in (1909.13808) to calculate the entanglement entropy in the thermal case and finite size case from the field theory side.
-The Rindler transformation from the domain of dependence of the interval $(-l_p,l_p)$ to the sphere is
-	\begin{equation}
-	t=l_p\frac{\sin\theta \sinh(\tau/l_p)}{1+\sin\theta \cosh(\tau/l_p)},\ \  x=l_p\frac{\cos\theta}{1+\sin\theta\cosh(\tau/l_p)}
-	\end{equation}
-	the conformal factor reads,
-	\begin{equation}
-	\Omega=\frac{1}{1+\sin\theta\cosh(\tau/l_p)}
-	\end{equation}
-	At endpoints, it becomes $1$.
-From the discussion in (1909.13808), the contribution to the entanglement entropy totally comes from the endpoints of the interval, so one can use the such conformal transformation where the conformal factor at the endpoints is $1$ to calculate the entanglement entropy.
-Also, in the conformal map above from the casual diamond to the sphere, only the length of the interval matters.
-If these two endpoints lie at other position, one can use the rotation and translation symmetry to put it at $(0,\pm l_p)$, since the $T\bar T$ deformed theory also admits these symmetries.
-Now let's consider the thermal case, the conformal transformation from the thermal cylinder to the plane reads,
-	\begin{equation}
-	z=\frac{1}{r_1}e^{r_1w},\ \ \ r_1=\frac{2\pi}{\beta}
-	\end{equation} 
-	where $z$ is the coordinate on the plane, and $w$ is the coordinate on the thermal cylinder with identification,
-	\begin{equation}
-	w\sim w+i\beta
-	\end{equation}
-	The endpoints of the interval on the thermal cylinder is
-	\begin{equation}
-	w=\pm l
-	\end{equation} 
-	The length of the interval is $L=2l$. Under the conformal map, the endpoints on the plane is
-	\begin{equation}
-	\frac{1}{r_1}e^{\pm r_1 l}
-	\end{equation}
-	the length is $\frac{2}{r_1}\sinh(l r_1)$, so
-	\begin{equation}
-	l_p=\frac{1}{r_1}\sinh(l r_1)
-	\end{equation}
-	The conformal factor is
-	\begin{equation}
-	e^{r_1(w+\bar{w})}
-	\end{equation}
-	Note that compared to the usual map from cylinder to plane $z=e^{r_1 w}$, we put the overall scaling factor $\frac{1}{r_1}$ to make sure that the conformal factor at the endpoints is $1$.
-From 1806.07444, the entanglement entropy for $l_p$ is
-	\begin{equation}
-	S_p(l)=\frac{c}{3}ArcSinh\frac{l_p}{a}
-	\end{equation}
-	where
-	\begin{equation}
-	a^2=\frac{\mu c}{12}
-	\end{equation}
-	The C-function reads,
-	\begin{equation}
-	C(L)=L S'(L=2l)=\frac{c}{3}\frac{1}{\sqrt{1+4a^2/L^2}}
-	\end{equation}
-	Now in the thermal case, $l_p\rightarrow \frac{1}{r_1}\sinh(l r_1)$
-	\begin{equation}
-	S_t=\frac{c}{3}ArcSinh(\frac{1}{r_1 a}\sinh(l r_1))
-	\end{equation}
-	which is the same as the results obtained from the local temperature trick \eqref{} and the gravity calculation \eqref{}. Now consider the finite size case, the conformal transformation is,
-	\begin{equation}
-	z=\frac{1}{ir_1}e^{iwr_1},\quad
-		r_1 = \frac{2\pi}{\lambda}
-	\end{equation}
-	where $w$ is the cylinder coordinate,
-	\begin{equation}
-	w\sim w+ \lambda
-	\end{equation}
-	The endpoints of the interval are 
-	\begin{equation}
-	w\pm l
-	\end{equation}
-	The conformal factor is
-	\begin{equation}
-	e^{ir_1(w+\bar{w})}
-	\end{equation}
-	which is $1$ at the endpoints. The plane length reads,
-	\begin{equation}
-	l_p=\frac{1}{r_1}\sin lr_1
-	\end{equation}
-	So the final result is
-	\begin{equation}
-	S_f=\frac{c}{3}ArcSinh(\frac{1}{r_1a}\sin(lr_1))
-	\end{equation}
-
-\pagebreak
-
-	The global AdS reads,
-	\begin{equation}
-	 ds^2=-(r^2+1)dt^2+\frac{dr^2}{r^2+1}+r^2d\phi^2,\ \ \phi\sim\phi+2\pi
-	\end{equation}
-	\begin{equation}
-	\phi\rightarrow r1\phi,\ \ r\rightarrow \frac{r}{r_1}, \ \ \ t\rightarrow r_2 t
-	\end{equation}
-	\begin{equation}
-	 ds^2=-(r^2+r_1^2)dt^2+\frac{dr^2}{r^2+r_1^2}+r^2d\phi^2,\ \ \phi\sim\phi+\beta
-	\end{equation}
-	Compared to the planer BTZ,
-	\begin{equation}
-	ds^2=-(r^2-r_1^2)dt^2+\frac{dr^2}{r^2-r_1^2}+r^2dx^2
-	\end{equation}
-	For the holographic entanglement entropy
-	\begin{equation}
-	r_1\rightarrow ir_1
-	\end{equation}
-	There is no topological obstacle in global AdS, so one can do the replacement above to get the holographic entanglement entropy in global AdS from the HEE in planer BTZ.
-	\begin{equation}
-	S_f=\frac{c}{3}ArcSinh(\frac{1}{r_1a}\sin(lr_1))
-	\end{equation}
-
-\pagebreak
 

### 2021-06-23 alpha/CutoffModularFlow/notes.tex
Add various updates of the cutoff AdS notes

@@
 	One can use the method in \cite{Lewkowycz:2019xse} to calculate the entanglement entropy in the thermal case and finite size case from the field theory side.
-The Rindler transformation from the domain of dependence of the interval $(-\lp,\lp)$ to the sphere is
+The Rindler transformation from the domain of dependence of the interval $(-\lp,\lp)$ on the plane to the sphere is
 	\begin{equation}
 	t=\lp\frac{\sin\theta \sinh(\tau/\lp)}{1+\sin\theta \cosh(\tau/\lp)},\ \  x=\lp\frac{\cos\theta}{1+\sin\theta\cosh(\tau/\lp)}
+	\label{eq:rindler_sphere}
 	\end{equation}
@@
 	\end{equation}
-	At endpoints, it becomes $1$.
+	At the endpoints, it becomes $1$.
 From the discussion in \cite{Lewkowycz:2019xse}, the contribution to the entanglement entropy totally comes from the endpoints of the interval, so one can use the such conformal transformation where the conformal factor at the endpoints is $1$ to calculate the entanglement entropy.
 Also, in the conformal map above from the casual diamond to the sphere, only the length of the interval matters.
-If these two endpoints lie at other position, one can use the rotation and translation symmetry to put it at $(\pm \lp,0)$, since the $T\bar T$ deformed theory also admits these symmetries.
-
-	Now let's consider the thermal case. The conformal transformation from the thermal cylinder to the plane reads,
-	\begin{equation}
-	z=\frac{1}{\kappa}e^{\kappa w},\ \ \ \kappa=\frac{2\pi}{\beta}
-	\end{equation} 
-	where $z$ is the coordinate on the plane, and $w$ is the coordinate on the thermal cylinder with identification,
+If these two endpoints lie at other position, one can use the rotation and translation symmetry to put it at $x = \pm \lp$, since the $T\bar T$ deformed theory also admits these symmetries.
+
+	Now let's consider the thermal case.
+We will make use of two successive conformal maps: first we map the thermal cylinder to the plane, and then we use \eqref{eq:rindler_sphere} to map the plane to the sphere.
+	The conformal transformation from the thermal cylinder to the plane reads,
+	\begin{equation}
+	z=\frac{\beta}{2\pi}\,e^{\frac{2\pi}{\beta} w},
+%	\ \ \ \kappa=\frac{2\pi}{\beta}
+	\end{equation} 
+	where $z = x + it$ is the coordinate on the plane, and $w$ is the coordinate on the thermal cylinder with identification,
 	\begin{equation}
@@
 	\begin{equation}
-	\frac{1}{\kappa}e^{\pm \kappa \frac{L}{2}}
-	\end{equation}
-	the length is $\frac{2}{\kappa}\sinh(\halfL \kappa)$, so one can use translations and rotations to map the endpoints to $(\pm \lp, 0)$ on the plane 
-	\begin{equation}
-	l_p=\frac{1}{\kappa}\sinh(\halfL \kappa)
+	\frac{\beta}{2\pi}e^{\pm \frac{2\pi}{\beta} \frac{L}{2}}
+	\end{equation}
+	the length is $\frac{\beta}{\pi}\sinh(\halfL \frac{2\pi}{\beta})$, so one can use translations and rotations to map the endpoints to $x = \pm\lp$ on the plane, where
+	\begin{equation}
+	l_p=\frac{\beta}{2\pi}\sinh(\halfL \frac{2\pi}{\beta})
 	\end{equation}
@@
 	\begin{equation}
-	e^{\kappa(w+\bar{w})}
-	\end{equation}
-	Note that compared to the usual map from cylinder to plane $z=e^{\kappa w}$, we put the overall scaling factor $\frac{1}{\kappa}$ to make sure that the conformal factor at the endpoints is $1$.
+	e^{\frac{2\pi}{\beta}(w+\bar{w})}
+	\end{equation}
+	Note that compared to the usual map from cylinder to plane $z=e^{\frac{2\pi}{\beta} w}$, we put the overall scaling factor $\frac{\beta}{2\pi}$ to make sure that the conformal factor at the endpoints is $1$.
 
@@
 	\begin{equation}
-	C(L)=L S'(L)=\frac{c}{3}\frac{1}{\sqrt{1+4a^2/L^2}}
-	\end{equation}
-	Now in the thermal case, $l_p\rightarrow \frac{1}{\kappa}\sinh(\halfL \kappa)$
+	C(L)=L S'(L = 2l)=\frac{c}{3}\frac{1}{\sqrt{1+4a^2/L^2}}
+	\end{equation}
+	Now in the thermal case, $l_p\rightarrow \frac{\beta}{2\pi}\sinh(\halfL \frac{2\pi}{\beta})$
 	\begin{equation}
 	S_t=\frac{c}{3}\arcsinh \pqty{
-			\frac{1}{\kappa a}\sinh(\halfL \kappa)
-		}
-	\end{equation}
-	which is the same as the results obtained from the local temperature trick \eqref{} and the gravity calculation \eqref{}. Now consider the finite size case, the conformal transformation is,
+			\frac{1}{\kappa a}\sinh(\halfL \frac{2\pi}{\beta})
+		}
+	\end{equation}
+	\sidenote{which is the same as the results obtained from the local temperature trick \eqref{} and the gravity calculation \eqref{} [This is now the first non-trivial result of the paper.
+This comment should be moved to later.]}
+
+	------------
+
+	Now consider the finite size case, the conformal transformation is,
 	\begin{equation}
 	z=\frac{1}{ir_1}e^{iwr_1},\quad
-		r_1 = \frac{2\pi}{\lambda}
-	\end{equation}
-	where $w$ is the cylinder coordinate,
-	\begin{equation}
-	w\sim w+ \lambda
+		r_1 = \frac{2\pi}{\sidenote{R}}
+	\end{equation}
+	where $w$ is the cylinder coordinate, and $R$ is the \textit{spatial} size of the cylinder:
+	\begin{equation}
+	w\sim w+ R
 	\end{equation}
@@
 			\pqty{
-				\pqty{\frac{{\tilde L}}{2}}^2
+				\pqty{\tfrac{{\tilde L}}{2}}^2
 				- x^2
@@
 \section{Bulk story}
+	This reproduces known results in e.g.~\cite{Lashkari:2016idm,Czech:2019vih,Apolo:2020qjm} \sidenote{[more citations needed]}. We first compute everything in Poincar\'e $\mrm{AdS}_3$ for simplicity. 
+\subsection{Bulk modular flows for Poincar\'e $\mrm{AdS}_3$}
 	We follow the recipe from the swing surface proposal \cite{Apolo:2020bld,Apolo:2020qjm} to extend the boundary modular flow to the bulk, by matching symmetries of the bulk and the boundary.
-This reproduces known results in e.g.~\cite{Lashkari:2016idm,Czech:2019vih,Apolo:2020qjm} \sidenote{[more citations needed]}.
-We first compute everything in Poincar\'e $\mrm{AdS}_3$ for simplicity.
-\subsection{Bulk modular flows for Poincar\'e $\mrm{AdS}_3$}
+
 	By requiring that a linear combination of the bulk Killing vectors for Poincar\'e $\mrm{AdS}_3$ reduces to the boundary $L_n$'s, one can uniquely extend the $L_n,\tilde{L}_n$'s into the bulk.

### 2021-06-24 alpha/CutoffModularFlow/notes.tex
Update notes: merge upstream changes

@@
+% !TeX encoding = UTF-8
 % !TeX TS-program = pdflatex
@@
 
-\documentclass[11pt,a4paper]{article}
+\documentclass[11pt,a4paper,utf8]{article}
+
+\ifdefined\pdfoutput
 	\pdfoutput=1
+\fi
 
@@
 \section{Entanglement in the boundary story}
-
-\subsection{Rindler map in finite temperature}
+\subsection{Review of entanglement at zero temperature}
+
+\subsection{Entanglement entropy at finite temperature}
 
@@
 		\xi_\mrm{CFT} &= \frac{2\pi}{{\tilde L}} \bigg\{
-			\pqty\Big{
+			\pqty{
 				\pqty{
@@
 		\\ &\qquad\qquad 
-			+ \pqty\Big{
+			+ \pqty{
 				\pqty{
@@
 	$, namely $\theta$ is constant along the RT surface.
+
+	{\color{red} use $l_u,\,l_v$}
+
 	We have:
@@
 		\xi &= \frac{2\pi}{L_\infty} \bigg\{
-			\pqty\Big{
+			\pqty{
 				\pqty{
@@
 		\\ &\qquad\qquad 
-			+ \pqty\big{
+			+ \pqty{
 				x\sinh\theta
@@
 
+The RT surface is the set of the fixed points of the modular flow, ....bifurcating surface....
+
+\eq{ &\pqty{
+					(\tfrac{L_\infty}{2})^2 - z^2
+					- (t^2 + x^2)
+				} \cosh\theta
+				+ 2tx \sinh\theta =0\\
+			&	x\sinh\theta
+				- t\cosh\theta
+				}
+
 	We note that the $\pdd{z}$ term vanishes in the following two cases:
-	\begin{itemize}[noitemsep,topsep=0pt]
+	\begin{itemize}%[noitemsep,topsep=0pt]
 	\item as $z\to 0$, i.e.~near the asymptotic boundary;
@@
 
+\begin{comment}
 	We then consider $\xi$ evaluated at the {constant finite cutoff} $z = z_c$,
@@
 		& \bigg\{
-			\pqty\Big{
+			\pqty{
 				\pqty{
@@
 		\\[-.5ex] &\quad 
-			+ \pqty\Big{
+			+ \pqty{
 				\pqty{
@@
 		\\ &\quad 
-			+ \pqty\big{
+			+ \pqty{
 				x\sinh\theta
@@
 	\end{equation}
+\end{comment}
 
@@
 However, if we restrict to the field theory living at constant cutoff $z = z_c$, which corresponds to a \TTbar deformed theory \cite{McGough:2016lol,Lewkowycz:2019xse} \sidenote{[more citations needed]}, since it has no knowledge of the $\pdd{z}$ component of $\xi$, we should reduce it to a modular flow within the $z = z_c$ plane by, e.g.~projecting the $z$ component out, which leaves us:
+
+	{\color{red} delete
 	\begin{equation}
@@
 		\xi^{\mrm{FT}}_c
-		\equiv \proj{\sslash} \xi|_{z_c}
+		\equiv \proj{\text{/\!/}} \xi|_{z_c}
 		= \frac{2\pi}{
@@
 		\\[-2ex] &\quad 
-			+ \pqty\Big{
+			+ \pqty{
 				\pqty{
@@
 	\end{equation}
-	Which no longer has normalized $\beta$ if $z_c \ne 0$. In fact, compared to the $z_c \to 0$ situation which \textit{does} have $\beta = 1$, $\xi^{\mrm{FT}}_c$ is rescaled by a factor of $
+	Which no longer has normalized $\beta$ if $z_c \ne 0$.
+}
+
+	 In fact, compared to the $z_c \to 0$ situation which \textit{does} have $\beta = 1$, $\xi^{\mrm{FT}}_c$ is rescaled by a factor of $
 		\frac{L}{L_\infty}
@@
 				- \sqrt{
-					\pqty\big{(L_\infty/2)^2 - \alpha z_c^2}^2
+					\pqty{(L_\infty/2)^2 - \alpha z_c^2}^2
 					+ 4t^2 \alpha z_c^2
@@
 		r(\phi) = \frac{2T\cosh TL}{
-				\sqrt{\cosh^2 TL - \pqty\big{
+				\sqrt{\cosh^2 TL - \pqty{
 					1 - \frac{4T^2}{r_c^2}
@@
 	We note that the $\pdd{z}$ term vanishes in the following two cases:
-	\begin{itemize}[noitemsep,topsep=0pt]
+	\begin{itemize}%[noitemsep,topsep=0pt]
 	\item as $z\to 0$, i.e.~near the asymptotic boundary;

### 2021-06-24 alpha/CovariantPhaseSpace/charge.tex
Add intro to note on Noether charge

@@
 
-\title{Covariant Phase Space\\\large\it A Pedagogical Introduction}
+\title{Covariant Phase Space\\[-.2ex]\large\it A Pedagogical Introduction}
 \addbibresource{charge.bib}
@@
 \addtocounter{section}{-1}
-\section{Conventions}
+\section{Introduction \& Conventions}
+	The phase space is understood as the space of \textit{all solutions} of the equations of motion (EoMs), satisfying the boundary conditions; alternatively, we can think of it as a collection of all possible \textit{initial configurations} of the system, and the additional \textit{symplectic structure} specifies their evolutions.
+This idea is best explained by \textcite{Crnkovic:1986ex}.
+
+	Traditionally we construct the phase space variables $(\pi,\phi)$ as follows: we first pick a special time coordinate $t$, and then introduce the canonical momentum:
+	\begin{equation}
+		\pi = \pdv{\mcal{L}}{\dot{\phi}},
+	\quad
+		\dot{\phi} = \pdd{t} \phi
+	\end{equation}
+	Unfortunately, this procedure breaks general covariance. We would like to find a construction of phase space that respects general covariance.
+
+	The inspiration comes from the Lagrangian treatment of field theory, where we work with:
+	\begin{equation}
+		\pi^\mu = \pdv{\mcal{L}}{(\pd_\mu\phi)}
+	\end{equation}
+	Which preserves general covariance.
+But $(\pi_\mu,\phi)$ is not a set of independent coordinates; they are constrained by the equations of motion (EoMs).
+The rough idea is that we start with $(\pi_\mu,\phi)$, and then reduce it to the independent variables $(\pi,\phi)$ by imposing the EoMs, and possibly, additional constraints due to gauge redundancy.
+
+	In this note we review the covariant formalism in a systematic yet pedagogical manner. 
 	We follow Prof.~Wei Song's lecture notes on $\mrm{AdS}_3/\mrm{CFT}_2$, which include a very nice introduction to the covariant formalism and its application. 
@@
 	\item Raising and lowering indices are denoted by $\sharp$ and $\flat$ respectively; these are given the cool name of \textit{musical isomorphisms}.
+
+	For simplicity, sometimes we might omit the explicit notations of musical isomorphisms, but they are nonetheless implied; e.g.~the normal (co-)vector $n$ can be understood as $n^\mu$ or $n_\mu$.
 
@@
 	\quad
-		\hstar V^\flat
-		= V\cdot \sqrt{\abs{g}} \dd[D]{x}
-	\end{equation}
+		\hstar \theta^\flat
+		= \theta\cdot \sqrt{\abs{g}} \dd[D]{x}
+	\end{equation}
+	It's convenient to only act $\hstar$ on the form of a smaller degree to get the form of a larger degree; in this way we don't need to worry about the $(-1)^s$ factor. 
 	A particular useful relation is:
 	\begin{equation}
-		\dd{\hstar V^\flat}
-		= \hstar\,(\cdv{\mu} V^\mu)
+		\dd{\hstar \theta^\flat}
+		= \hstar\,(\cdv{\mu} \theta^\mu)
 	\end{equation}

### 2021-06-24 alpha/CovariantPhaseSpace/charge.tex
Update Noether notes on background fields & more

@@
+% !TeX TS-program = pdflatex
 % !TeX document-id = {b5392a94-51a3-49d1-9ba5-698bc09f9d35}
@@
 \input{../.modules/basics/biblatex.tex}
+\input{../.modules/basics/theorem.tex}
+
+\declaretheorem[
+	numbered=no
+	,style=nonumber
+	,name=Remark
+]{remark*}
 
@@
 \section{Introduction \& Conventions}
-	The phase space is understood as the space of \textit{all solutions} of the equations of motion (EoMs), satisfying the boundary conditions; alternatively, we can think of it as a collection of all possible \textit{initial configurations} of the system, and the additional \textit{symplectic structure} specifies their evolutions.
+	The phase space is understood as the space of \textit{all solutions} of the equations of motion (EoMs), satisfying the boundary conditions.
+Alternatively, we can think of it as a collection of all possible \textit{initial configurations} of the system, and the additional \textit{symplectic structure} specifies their evolutions.
 This idea is best explained by \textcite{Crnkovic:1986ex}.
@@
 	\begin{itemize}
-	\item $\mcal{F}$ denotes the field space including \textbf{off-shell} configurations; the variation $\delta$ is assumed to be off-shell unless otherwise specified.
-
-	\item $\tilde{\mcal{P}}$ denotes the field space including \textbf{on-shell} configurations only; one can then define a symplectic form $\omega$ on $\tilde{\mcal{P}}$, but it might be degenerate due to gauge redundancies;
-
-	\item $\mcal{P}$ denotes the \textbf{physical phase space}, with a nice, non-degenerate sympletic structure.
+	\item $\mcal{F}$ denotes the field space including \textbf{off-shell} configurations: $\phi^I$,\\
+	and also \textbf{background fields} $\phi^B$; \\
+	the variation $\delta$ is assumed to be off-shell unless otherwise specified.
+
+	\item $\tilde{\mcal{P}}$ denotes the field space including \textbf{on-shell} configurations only; \\
+	one can then define a symplectic form $\omega$ on $\tilde{\mcal{P}}$, \\
+	but it might be degenerate due to gauge redundancies.
+
+	\item $\mcal{P}$ denotes the \textbf{physical phase space}, \\
+	with background fields turned off: $\var{\phi^B}|_{\mcal{P}} = 0$, \\
+	and with a ``physical'' (non-degenerate) sympletic structure
+
+	\item The index $I$ labels \textbf{all fields} in the theory, \\
+	including non-dynamical \textbf{background fields}, \\
+	which is labeled by the index $B$.
 
@@
 %\smallskip
-\textit{Diffeomorphism and stress tensor:}
+\textit{Diffeomorphism and the stress tensor:}
 
@@
 	\begin{equation}
-		x\mapsto x - \xi = x + \var_\xi {x},
-	\quad
-		\var_\xi {x}
-		= -\xi,
+		x\mapsto x - \xi,
 	\quad
@@
 		= +\ldv{\xi} \phi,
-	\end{equation}
-	Here the sign convention is chose such that $\var_\xi \phi$ corresponds to a positive Lie derivative along $\xi$.
-Note that \cite{Banados:2016zim} chose a unconventional Lie derivative which contains a minus sign in its definition; we are \textit{not} going to follow that.
+	\label{eq:diffeo_convention}
+	\end{equation}
+	Here the sign convention is chosen such that $\var_\xi \phi$ corresponds to a positive Lie derivative along $\xi$.
+Note that \textcite{Banados:2016zim} picks a unconventional Lie derivative which contains a minus sign in its definition; we are \textit{not} going to follow that.
 In this convention the usual current for spacetime translation is given by:
 	\begin{equation}
-		\xi = -\pdd{\sigma},
-	\quad
-		j^\mu_\xi = j^\mu_{-\pdd{\sigma}}
+	\begin{aligned}
+		\xi &= -\pdd{\sigma},
+	&
+		j^\mu_\xi
+		&= j^\mu_{-\pdd{\sigma}}
 		= T^{\mu\nu} \eta_{\nu\sigma}
-		= T^{\mu\nu} (\pdd{\sigma})_\nu
+		= T^{\mu\nu} (\pdd{\sigma})_\nu,
+%	\\
+%		\xi &= -\epsilon
+%		= -\epsilon^\sigma \pdd{\sigma},
+%	\quad
+%	&
+%		j^\mu_\xi
+%		&= \epsilon^\sigma j^\mu_{-\pdd{\sigma}}
+%		= \epsilon_\nu T^{\mu\nu}
+%		= \epsilon^\nu T\id{^\mu_\nu},
+	\end{aligned}
 	\label{eq:Noether_stress_convention}
@@
 	$, are left invariant. This is the convention introduced in \textcite{Polchinski:1998rq}, Appendix A. 
-
-	For example, the Einstein-Hilbert action is given by:
-	\begin{equation}
-		S_L = \frac{1}{16\pi G_N}
-			\int \sqrt{-g} \dd[D]{x} R,
-	\quad
-		S_E = -\frac{1}{16\pi G_N}
-			\int \sqrt{g} \dd[D]{x} R
-	\end{equation}
+	For example, the Einstein-Hilbert action is given by\footnote{
 		For a closed Riemann surface in 2D, by Gauss--Bonnet theorem, we see that the Euclidean action is proportional to genus of the surface:
@@
 		$ is the closed string coupling. 
+	}:
+	\begin{equation}
+		S_L = \frac{1}{16\pi G_N}
+			\int \sqrt{-g} \dd[D]{x} R,
+	\quad
+		S_E = -\frac{1}{16\pi G_N}
+			\int \sqrt{g} \dd[D]{x} R
+	\end{equation}
 
@@
 		\int \dd[D]{x}
-	$, without the $\sqrt{\abs{g}}$ factor.
-
+	$, without the $\sqrt{\abs{g}}$ factor\footnote{
 		An action can thus be thought of as the contraction between some fields and some operators with multiple $x$ ``indices'': $\Box_{x,x',\cdots}$.
@@
 		$. 
+	}.
 
@@
 \section{Covariant formalism and Noether's theorem}
-	The phase space is understood as the space of \textit{all solutions} of the equations of motion (EoMs), satisfying the boundary conditions; alternatively, we can think of it as a collection of all possible \textit{initial configurations} of the system, and the additional \textit{symplectic structure} specifies their evolutions.
-This idea is best explained by \textcite{Crnkovic:1986ex}.
-
-	Traditionally we construct the phase space variables $(\pi,\phi)$ as follows: we first pick a special time coordinate $t$, and then introduce the canonical momentum:
-	\begin{equation}
-		\pi = \pdv{\mcal{L}}{\dot{\phi}},
-	\quad
-		\dot{\phi} = \pdd{t} \phi
-	\end{equation}
-	Unfortunately, this procedure breaks general covariance. We would like to find a construction of phase space that respects general covariance.
-
-	The inspiration comes from the Lagrangian treatment of field theory, where we work with:
-	\begin{equation}
-		\pi^\mu = \pdv{\mcal{L}}{(\pd_\mu\phi)}
-	\end{equation}
-	Which preserves general covariance.
-But $(\pi_\mu,\phi)$ is not a set of independent coordinates; they are constrained by the equations of motion (EoMs).
-The rough idea is that we start with $(\pi_\mu,\phi)$, and then reduce it to the independent variables $(\pi,\phi)$ by imposing the EoMs, and possibly, additional constraints due to gauge redundancy.
 \subsection{Off-shell variation on the field space}
@@
 	\end{equation}
-%	We've promoted $\phi^\mu$ to $\phi^I$ to include all fields, e.g.~the metric $g_{\mu\nu}$. 
 	We've defined $\Theta$ which comes from the total derivative terms of the bulk $M$ variation, and we've performed an integration by parts and reduced $\int_M \dd{\Theta} = \int_{\pd M} \Theta$.
@@
 
-	Note that $\mcal{F}$ \textbf{includes possible ``background'' fields $\phi^B$} such as the fixed metric $g^{\mu\nu}$ for a field theory defined on a curved spacetime.
-These fields are fixed on-shell and therefore are absent in $\tilde{\mcal{P}}$.
+	Note that $\mcal{F}$ \textbf{includes possible ``background'' fields $\phi^B$} such as the static metric $g^{\mu\nu}$ for a field theory defined on a curved spacetime.
+These fields are fixed on-shell and therefore are absent in $\mcal{P}$.
+A proper treatment of background fields is nicely summarized by \textcite{Banados:2016zim}, but we will take a slightly different approach, as we shall see later.
 
@@
 
-	What we've done here is simply a rewrite of the usual variation procedure; we just re-think it as a differential in the field space.
-To get to the physical phase space, we \textbf{suppress the variation of ``background'' fields $\phi^B$}, and then require the action to be \textbf{stationary, up to terms in the future / past boundary $\Sigma^\pm$:}
-	\begin{empheq}{equation}
-		\var{\phi^B}|_{\tilde{\mcal{P}}}
-		= 0,
-	\quad
+	What we've done here is simply a rewrite of the usual variation procedure; we just re-think it as a differential in the field space. To get to the physical phase space, we
+%	\textbf{suppress the variation of background fields $\phi^B$}, and then 
+	require the action to be \textbf{stationary, up to
+	variation of the background fields, and
+	up to terms in the future / past boundary $\Sigma^\pm$:}
+	\begin{empheq}{equation}
+%		\var{\phi^B}|_{\tilde{\mcal{P}}}
+%		= 0,
+%	\quad
 		\var{S}|_{\tilde{\mcal{P}}}
-		= \int_{\Sigma^+} ({\cdots})
+		= \int_M E_B \var{\phi^B}
+			+ \int_{\Sigma^+} ({\cdots})
 			- \int_{\Sigma^-} ({\cdots})
-		= \int_{\Sigma^\pm} ({\cdots})
-	\end{empheq}
-%\pagebreak[4]
+		= \int_M E_B \var{\phi^B}
+			+ \int_{\Sigma^\pm} ({\cdots})
+	\end{empheq}
 
 	This differs slightly from what we are used to in most physics literature, where we simply set $\var{S} = 0$ to find the EoMs.
-The reason is that in physics, we usually impose the initial \& final conditions, or in other words, in \& out states, and the variation at $\Sigma^\pm$ is \textit{required} to vanish: $\var{\phi}|_{\Sigma^\pm} = 0$.
+The reason is that in physics, we usually \textit{impose} the initial \& final conditions, or in other words, in \& out states, and the variation at $\Sigma^\pm$ is \textit{required} to vanish: $\var{\phi}|_{\Sigma^\pm} = 0$.
 	Consider the simplest example: the (0+1)\,D worldline action of a point particle; we have:
@@
 		= \int E_I(t) \var{q^I(t)}
-			+ \Theta\Big|^{\Sigma^+}_{\Sigma^-}
+			+ \Theta\big|^{\Sigma^+}_{\Sigma^-}
 	\end{equation}
@@
 	Traditionally, we impose $\var{q^I}|_{\Sigma^\pm} = 0$ as we fix the in \& out states, and then we find the EoMs $E_I = 0$. 
+	Same applies to the background field variation, where we simply set $\var{\phi^B} = 0$. 
 	However, this is slightly clumsy to implement in our new language, since $\var{\phi}$ is now a differential form in the phase space.
@@
 	\begin{equation}
-		\var{\phi^B}|_{\tilde{\mcal{P}}}
-		= 0,
-	\quad
 		\var{S}|_{\tilde{\mcal{P}}}
-		= \int_{\Sigma^\pm} ({\cdots})
+		= \int_M E_B \var{\phi^B}
+			+ \int_{\Sigma^\pm} ({\cdots})
 	\quad\Longrightarrow\quad
@@
 	Here $N$ is the spatial boundary. 
-	In this way we've obtained the subspace (submanifold) $\tilde{\mcal{P}}$ of solutions constrained by the EoMs.
-We are one step closer to the physical phase space; in fact this \textit{is} the physical phase space if there are no gauge redundancies in the fields.
+	In this way we've obtained the subspace (submanifold) $\tilde{\mcal{P}}$ of \mbox{solutions} constrained by the EoMs.
+We are one step closer to the physical phase space; in fact this \textit{is} the physical phase space $\mcal{P}$ if there are no gauge redundancies in the fields, and the variation of background fields are turned off: $\var{\phi^B} = 0$.
 
@@
 	In fact, $N$ is where the dual theory lives for many holographic systems, so one would imagine that it's highly non-trivial. Generally \cite{Harlow:2019yfa},
-	\begin{equation}
+	\begin{empheq}{gather}
 		(\Theta + \var{l})_{\tilde{\mcal{P}},N}
@@
 	\label{eq:boundary_cond}
-	\end{equation}
-	\vspace{-.8\baselineskip}
-	\begin{equation}
-%	\Longrightarrow\ %
+	\\
+	\Longrightarrow\ %
 		\int_{N} (\Theta + \var{l})_{\tilde{\mcal{P}}}
@@
 			+ \int_{\Sigma^\pm} ({\cdots})
-	\end{equation}
+	\end{empheq}
 
@@
 Also, off-shell variation will be quite useful if we want to quantize our theory, where we have to integrate over off-shell configurations as well.
-
-%\pagebreak
 \subsection{Symmetry variation and the Noether current}
@@
 However, we can still interpret it as a variation on $\tilde{\mcal{P}}$, by simple restriction.
-\pagebreak
 
@@
 	\begin{empheq}{equation}
-		\var_\xi {\phi^B}
-		= 0,
-	\quad
 		\var_\xi S = X_\xi \cdot \var{S}
@@
 	\end{empheq}
-	In other words, symmetries should act trivially on the background fields $\phi^B$, and its action in the field space is characterized by the kernel, or \textit{zero modes} (0-modes) of $\var{S}$, \textbf{again up to boundary terms at $\Sigma^\pm$}.
+	In other words, the action of symmetries in the field space is characterized by the kernel, or \textit{zero modes} (0-modes) of $\var{S}$, \textbf{again up to boundary terms at $\Sigma^\pm$}.
 
@@
 
-	Compared to the definition of $\tilde{\mcal{P}}$, namely $\var{S}|_{\tilde{\mcal{P}}}$ vanishes up to $\Sigma^\pm$ terms, we see that for a symmetry $\xi$, $X_\xi$ is always tangent to $\tilde{\mcal{P}}$, so that the restriction of the off-shell $\var_\xi \phi$ to on-shell $\tilde{\mcal{P}}$ is well-defined, as expected.
+	Also, here we \textbf{do allow ``generalized'' symmetries to act no-trivially on the background fields $\phi^B$}, but it has to combine with other variations and altogether reduce to some boundary terms at $\Sigma^\pm$.
+This is different from the treatment of \textcite{Banados:2016zim}, but it will prove to be convenient when we deal with background gauge fields, such as a background metric.
+
+	Intuitively, the generalized symmetries which act non-trivially on the background fields come from some ``true'' symmetries in a larger system $\hat{S}$, where the fields $\phi^B$ are dynamically \textit{turned on}.
+A prominent example is again, the static background metric $g^{\mu\nu}$ for a field theory on a curved spacetime.
+General diffeomorphism is \textit{not} truly a symmetry of the theory, since it disturbs the background metric; however, it is truly a (gauge) symmetry when we turn on dynamic $g^{\mu\nu}$.
+We will come back to this example shortly.
+
+	\newparagraph
+	Compared to the definition of $\tilde{\mcal{P}}$, namely $\var{S}|_{\tilde{\mcal{P}}}$ vanishes up to $\var{\phi^B}$ and $\Sigma^\pm$ terms, we see that for a symmetry $\xi$, $X_\xi$ is always tangent to $\tilde{\mcal{P}}$, so that the restriction of the off-shell $\var_\xi \phi$ to $\tilde{\mcal{P}}$ (on-shell) is well-defined, as expected.
+
+\pagebreak
 
@@
 		= X_\xi \cdot (\var{S}|_{\tilde{\mcal{P}}})
-		= \int_{\Sigma^\pm} ({\cdots})
+		= \int_M E_B \,\var_\xi{\phi^B}
+			+ \int_{\Sigma^\pm} ({\cdots})
 	\end{equation}
@@
 	\begin{equation}
-		0 = X_\xi \cdot (\var{S}|_{\tilde{\mcal{P}}})
+	\begin{aligned}
+		0
+		= X_\xi \cdot (\var{S}|_{\tilde{\mcal{P}}})
 		- (X_\xi \cdot \var{S})\big|_{\tilde{\mcal{P}}}
-		= \int_{\Sigma^\pm} ({\cdots})
-		= \pqty{
+		&= \int_M E_B \,\var_\xi{\phi^B}
+			+ \int_{\Sigma^\pm} ({\cdots}) \\
+		&= \int_M E_B \,\var_\xi{\phi^B}
+			+ \pqty{
 				\int_{\Sigma^+} - \int_{\Sigma^-}
-			}\, ({\cdots})
-		= H_\xi^+ - H_\xi^-
+			}\, ({\cdots}) \\
+		&= \int_M E_B \,\var_\xi{\phi^B}
+			+ H_\xi^+ - H_\xi^-
+	\end{aligned}
 	\label{eq:charge_conserve_schematic}
@@
 
-	We've thus obtained the conserved charge $H_\xi$ associated with $\xi$.
-The above arguments are a bit schematic; now let's write down the $({\cdots})$ explicitly.
-Let's assume that the off-shell symmetry variation is given by:
+	We've thus obtained the charge $H_\xi$ associated with $\xi$. Generally, it is conserved when the background fields are unchanged under the variation w.r.t.~$\xi$:
+	\begin{equation}
+		\var_\xi {\phi^B} = 0
+	\end{equation}
+	Otherwise the charge $H_\xi$ might change due to the contribution of $\var_\xi {\phi^B}$.
+Some examples of this are given in \cite{Banados:2016zim}.
+Intuitively, one can understand this as follows: through the restriction to a subsystem where the field $\phi^B$ is ``external'' and held fixed, we are \textit{explicitly breaking} some symmetries of the larger system.
+The remaining symmetries are those that act trivially on $\phi^B$, namely the \textit{stabilizer subgroup}, or the \textit{little group} associated with $\phi^B$.
+
+	The above arguments are a bit schematic; now let's write down the $({\cdots})$ explicitly. Let's assume that the off-shell symmetry variation is given by:
 	\begin{empheq}{equation}
@@
 	\begin{equation}
+	\begin{aligned}
 		X_\xi \cdot (\var{S}|_{\tilde{\mcal{P}}})
-		= \int_M E_I|_{\tilde{\mcal{P}}} \,\var_\xi {\phi^I}
+		&= \int_M E_I|_{\tilde{\mcal{P}}} \,\var_\xi {\phi^I}
 			+ \int_{\pd M} \pqty{
 				X_\xi \cdot \Theta + \var_\xi {l}
-			}_{\tilde{\mcal{P}}}
-		= 0 + \int_{\Sigma^\pm} \pqty{
+			}_{\tilde{\mcal{P}}} \\
+		&= 0 
+			+ \int_M E_B|_{\tilde{\mcal{P}}}
+				\,\var_\xi {\phi^B}
+			+ \int_{\Sigma^\pm} \pqty{
 				X_\xi \cdot \Theta + \var_\xi {l}
-			},
-	\end{equation}
-
-\pagebreak[3]
+			}
+	\end{aligned}
+	\end{equation}
+
+\pagebreak
 
@@
 	\begin{empheq}{equation}
-		0 = X_\xi \cdot (\var{S}|_{\tilde{\mcal{P}}})
+	\begin{aligned}
+		0
+		= X_\xi \cdot (\var{S}|_{\tilde{\mcal{P}}})
 		- (X_\xi \cdot \var{S})\big|_{\tilde{\mcal{P}}}
-		= \int_{\Sigma^\pm} J_\xi
-		= \pqty{
+		&= \int_M E_B \,\var_\xi{\phi^B}
+			+ \int_{\Sigma^\pm} J_\xi \\
+		&= \int_M E_B \,\var_\xi{\phi^B}
+			+ \pqty{
 				\int_{\Sigma^+} - \int_{\Sigma^-}
-			}\, J_\xi
-		= H_\xi^+ - H_\xi^-
+			}\, J_\xi \\
+		&= \int_M E_B \,\var_\xi{\phi^B}
+			+ H_\xi^+ - H_\xi^-
+	\end{aligned}
 	\label{eq:charge_conserve_global}
@@
 
-	The above derivation is a proof of the \textit{global} version of Noether's theorem, namely charge conservation from $\Sigma_-$ to $\Sigma_+$.
+	The above derivation is a proof of the \textit{global} version of Noether's theorem, namely charge conservation from $\Sigma^-$ to $\Sigma^+$.
 However, there is also a \textit{local} version, namely current conservation.
@@
 	\label{eq:current_differential}
+\pagebreak[3]
 	\end{equation}
@@
 \begin{aligned}
+	&\begin{aligned}
 		\dd{J_\xi}
@@
 				+ \dd (\var_\xi l - K_\xi)
+			}
+	\end{aligned}
+	\\
+	&\begin{aligned}
+		\phantom{\dd{J_\xi}}
+		&= - E_I \,\var_\xi{\phi^I},
+			&&\textsl{\footnotesize%
+				by \eqref{eq:symmetry_var_field},
 			} \\
-		&= - E_I \,\var_\xi{\phi^I},
-	\,\ \textsl{\footnotesize by \eqref{eq:symmetry_var_field}}
-	\end{aligned}
-	\end{empheq}
-
-	We've finally arrived at the current conservation $\dd{J_\xi}|_{\tilde{\mcal{P}}} = 0$, which only holds \textbf{on-shell}.
+		&\leadsto - E_B \,\var_\xi{\phi^B},
+			&&\textsl{\footnotesize%
+				in $\tilde{\mcal{P}}$,
+			} \\
+		&\leadsto 0,
+			&&\textsl{\footnotesize%
+				in $\mcal{P}$.
+			} \\
+	\end{aligned}
+\end{aligned}
+	\end{empheq}
+
+	We've finally arrived at the current conservation $\dd{J_\xi}|_{\mcal{P}} = 0$, which only holds \textbf{on-shell,} and with background fields suppressed: $\var \phi^B|_{\mcal{P}} = \var_\xi \phi^B|_{\mcal{P}} = 0$.
 Note that the boundary term $K_\xi$ is crucial in all of the above derivations, so it cannot be dropped casually.
@@
 	\end{equation}
+\pagebreak[3]%
 	We now use the covariant derivative since it commutes with the metric, which will soon prove to be convenient. We now perform the integration by parts:
@@
 	\begin{aligned}
-		\dd{(V\cdot \sqrt{\abs{g}} \dd[D]{x})}
+		\dd{(\theta\cdot \sqrt{\abs{g}} \dd[D]{x})}
 		&= \dd{\pqty{
-			V^\mu \sqrt{\abs{g}}
+			\theta^\mu \sqrt{\abs{g}}
 			\ \frac{1}{d!}\,
@@
 	\quad d = D-1 \\
-		&= \cdv{\sigma} V^\mu \sqrt{\abs{g}}
+		&= \cdv{\sigma} \theta^\mu \sqrt{\abs{g}}
 			\ \frac{1}{d!}\,
@@
 			\cdots \wedge \dd{x^{\mu_d}} \\
-		&= \cdv{\sigma} V^\mu \sqrt{\abs{g}}\,
+		&= \cdv{\sigma} \theta^\mu \sqrt{\abs{g}}\,
 			\delta^\sigma_\mu \dd[D]{x} \\
-		&= \cdv{\mu} V^\mu
+		&= \cdv{\mu} \theta^\mu
 			\sqrt{\abs{g}} \dd[D]{x}
@@
 	\begin{equation}
-		\star \dd{(V\cdot \sqrt{\abs{g}} \dd[D]{x})}
-		= \star \dd{\hstar V^\flat}
-		= \sidenote{(-1)^s}\cdv{\mu} V^\mu
-	\end{equation}
-
-	With $V^\mu = \pi^\mu \var{\phi}$, $
+		\dd{(\theta\cdot \sqrt{\abs{g}} \dd[D]{x})}
+		= \dd{\hstar \theta^\flat}
+		= \hstar \cdv{\mu} \theta^\mu
+	\end{equation}
+
+	With $\theta^\mu = \pi^\mu \var{\phi}$, $
 		\pi^\mu = \pdv{\mcal{L}}{(\cdv{\mu} \phi)}
@@
 		E = \hstar \pdv{\mcal{L}}{\phi}
-			- \dd{(\star \pi^\flat)}
+			- \dd{(\hstar \pi^\flat)}
 		= \hstar \pqty{
@@
 	As we've seen before, $\Theta$ is to be integrated along $\pd M$, so we mostly care about its projection $\Theta_{\pd M}$ along the induced volume form $\mrm{Vol}_{\pd M}$. We have\footnote{
-		We've been cavaliar about the index of $n$, by treating $n$ both as a vector and as a co-vector, without raising or lowering indices using musical isomorphisms.
+		We've been cavaliar about the index of $\theta$ and $n$, treating them as a vector $\theta^\mu, n^\mu$ and also as a co-vector $\theta_\mu, n_\mu$, without raising or lowering indices explicitly using musical isomorphisms.
 Whether it should be a vector or a co-vector can be inferred from the context.
@@
 
-\pagebreak[4]
-
-	On the other hand, if $g^{\mu\nu}$ is a fixed background field, then we have additional \textbf{constraints on $\xi$}, namely $\var_\xi {g^{\mu\nu}} = 0$ since $\var{g^{\mu\nu}}|_{\tilde{\mcal{P}}} \equiv 0$.
+	On the other hand, if $g^{\mu\nu}$ is a fixed background field, then we have additional \textbf{constraints on $\xi$} for it to be a ``true'' symmetry, namely $\var_\xi {g^{\mu\nu}} = 0$ since $\var{g^{\mu\nu}}|_{\mcal{P}} \equiv 0$.
 	This is precisely the \textit{Killing equation}; $\xi$ has to be a \textit{Killing vector}, which generates some \textit{isometry} instead of arbitrary diffeo:
@@
 
+	\newparagraph
 	Finally, the conserved current for diffeo in scalar field theory is given by:
@@
 	\end{equation}
-	We now consider flat spacetime; the energy-momentum \textit{stress tensor} $T^{\mu\nu}$ is then found by plugging in $\xi^\mu = \sidenote{-}\delta^\mu_\nu$, i.e.~the generator of translations; note that we've included \textbf{an extra minus sign} in the definition of $T^{\mu\nu}$ for future convenience:
+	The energy-momentum \textit{stress tensor} $T^{\mu\nu}$ is then found by plugging in $\xi = \sidenote{-}\pdd{\sigma}$, i.e.~the generator of translations; the minus sign is due to our convention for diffeomorphism:
 	\begin{equation}
@@
 		x^\mu \mapsto x^\mu - \xi^\mu
-		= x^\mu + \delta^\mu_\sigma,
+		= x^\mu + \delta_\sigma^\mu,
 	\end{equation}
@@
 		T^{\mu\nu}
-		= -\pi^\mu \pd^\nu\phi + \eta^{\mu\nu} \mcal{L}
+		= -\pi^\mu \nabla^\nu\phi + g^{\mu\nu} \mcal{L}
 	\label{eq:Noether_stress_tensor}
@@
 	Note that for now $T^{\mu\nu}$ is generally \textit{not} symmetric as $\mu\leftrightarrow \nu$, and only $\mu$ is the index for $j^\mu$, while $\nu$ is an index labeling the $D$ translations.
+The divergence of the current is then given by:
+	\begin{equation}
+		\xi = -\pdd{\sigma},
+	\quad
+		\cdv{\mu} j^\mu_\xi
+		= \cdv{\mu} T\id{^\mu_{(\sigma)}}
+		= \cdv{\mu} \pqty\Big{
+				T^{\mu\nu} \pqty{\pdd{(\sigma)}}_{\!\nu}
+			}
+		= g_{\nu\sigma} \cdv{\mu} T^{\mu\nu}
+			- T^{\mu\nu} \cdv{\mu} \xi_\nu
+	\end{equation}
+	Here we use the notation $(\sigma)$ to protect the $\sigma$ index from the action of $\cdv{\mu}$; namely, in $\cdv{\mu} T\id{^\mu_{(\sigma)}}$ the derivative only acts on the $\mu,\nu$ index, treating it like a (co-)vector, while $\cdv{\mu} T^{\mu\nu}$ is the usual covariant derivative of a 2-tensor.
+
+	Note that if $T^{\mu\nu}$ \textit{were} a symmetric tensor, i.e.~$T^{\mu\nu} = T^{\nu\mu}$, and if $\xi = -\pdd{\sigma}$ is a Killing vector, namely $\cdv{(\mu} \xi_{\nu)} = 0$,
+	then the current conservation gets reduced to $\cdv{\mu} T^{\mu\nu}|_{\tilde{\mcal{P}}} = 0$, since $
+		\cdv{\mu} j^\mu_\xi
+			|_{\tilde{\mcal{P}}}
+		= g_{\nu\sigma} \cdv{\mu} T^{\mu\nu}
+			|_{\tilde{\mcal{P}}}
+		= 0
+	$. This motivates us to construct a symmetric stress tensor, which we will discuss in details shortly.
 
@@
 		= -\frac{1}{2}
-			\cdv{\mu} \phi
+			\cdv{\mu} \phi\,
 			\nabla^\mu \phi,
@@
 		T_{\mu\nu}
-		= +\cdv{\mu} \phi \cdv{\nu} \phi
+		= +\cdv{\mu} \phi \,\cdv{\nu} \phi
 			+ g_{\mu\nu} \mcal{L}
+		= \cdv{\mu} \phi \,\cdv{\nu} \phi
+			-\frac{1}{2} g_{\mu\nu}
+				\cdv{\rho} \phi\,
+				\nabla^\rho \phi,
 	\end{equation}
@@
 
+\pagebreak[3]
+
 	For the free scalar field theory in flat sapcetime, with $\xi^\mu = -\delta^\mu_\nu$, we have:
@@
 	\begin{equation}
-		T_{\mu\nu} = 0
-	\end{equation}
+		T_{\mu\nu} \equiv E_{\mu\nu} = 0
+	\end{equation}
+\pagebreak[3]%
 	Namely, the \textbf{\textit{total} stress tensor} must vanish.
@@
 	\begin{equation}
-		0 = T_{\mu\nu}
+		0 = E_{\mu\nu}
 		= T^M_{\mu\nu}
@@
 	Here $T^M_{\mu\nu}$ is the \textit{matter} stress tensor.
-We now have a new puzzle: since $T_{\mu\nu} = 0$ in gravity, how should we define the stress tensor for the gravitational field itself?
+We now have a new puzzle: since the total $T_{\mu\nu} = E_{\mu\nu} = 0$ in gravity, how should we define the stress tensor for the gravitational field itself?
 As we shall see later, the covariant formalism provides a neat solution for this problem.
@@
 
-\pagebreak[4]
+%\pagebreak[4]
 
 	One can think of this process as \textit{turning on} a dynamic $g_{\mu\nu}$ field coupled to the matter theory; there is the usual \textbf{minimal coupling}, i.e.~we replace $\eta_{\mu\nu} \mapsto g_{\mu\nu}$, $\pdd{\mu} \mapsto \cdv{\mu}$, and then compute the variation.
+In this case the matter action is cleanly separated from the gravitational kinetic terms: $S = S^M[\phi^I,g_{\mu\nu}] + S^G[g_{\mu\nu}]$, and there is a clear definition of $T^M_{\mu\nu}$ from $S^M[\phi^I,g_{\mu\nu}]$.
+
 	However, we can introduce additional couplings between the matter fields and $g_{\mu\nu}$, e.g.~the dilaton coupling \cite{Polchinski:1998rq}:
 	\begin{equation}
-		S \propto \int
+%		S \propto \int
 			\sqrt{\abs{g}} \dd[D]{x}
-			R\,\Phi[\phi^I]
+			\pqty{R - 2\Lambda}\,\Phi[\phi^I]
 	\end{equation}
@@
 This is an example of \textit{non-minimal} coupling.
+In this case the gravitational action is mixed with the matter action, and we don't have an explicit formula for $T^M_{\mu\nu}$; but usually it's still possible to split the total (vanishing) stress tensor into two parts:
+	\begin{equation}
+		0 = E_{\mu\nu}
+		= T^M_{\mu\nu}
+			- \mcal{G}_{\mu\nu}
+	\end{equation}
+	Here $\mcal{G}_{\mu\nu}$ is the gravitational contribution. For Einstein gravity, we have $
+		\mcal{G}_{\mu\nu}
+		= \frac{1}{8\pi G_N}\,G_{\mu\nu}
+	$. For dilaton coupling, we have
 
 	\newparagraph
-	To understand the equivalence of the Hilbert stress tensor with the Noether stress tensor, we shall revisit the idea that \textbf{Noether's theorem is in fact a local statement,} even when the symmetries involved are global symmetries.
+	To understand the equivalence of the Hilbert stress tensor with the Noether stress tensor, we shall revisit the idea that \textbf{Noether's theorem is in fact a local statement,} even when the symmetries involved are the so-called ``global'' symmetries.
 \subsection{Noether current from ``localized'' variation}
-	As we've noted before, we can always choose $\var_\eta \phi(x)$ to be compactly supported around some point $x_0$, by weighting it with some arbitrary, localized bump function $\epsilon(x)$.
+	As we've noted before, we can always choose $\var_\epsilon \phi(x)$ to be compactly supported around some point $x_0$, by weighting it with some arbitrary, localized bump function $\epsilon(x)$.
 One can think of this as promoting\footnote{
@@
 		\var_\xi \phi
-		\mapsto \var_\eta \phi
+		\leadsto \var_\epsilon \phi
 		= \epsilon(x)\,\var_\xi \phi,
@@
 		X_\xi \cdot \var{\phi}
-		\mapsto X_\eta \cdot \var{\phi}
+		\leadsto X_\epsilon \cdot \var{\phi}
 		= \epsilon(x)\,X_\xi \cdot \var{\phi}
@@
 	We see that \textbf{when contracted with $\var{\phi}$, we can simply replace $
-		X_\eta \mapsto \epsilon(x)\,X_\xi
-	$}. \textbf{However, note that this does \textit{not} imply that $
-		X_\eta = \epsilon(x)\, X_\xi 
-	$}, nor does it work for contractions with general variations such as $\var{L}$.
-In fact, $X_\eta$ is a flow in the field space $\mcal{F}$, so it should not have explicit dependence on the $x$ coordinate; see e.g.~\eqref{eq:symmetry_var_field}.
-By definition, the correct form of $X_\eta$ should be:
-	\begin{equation}
-		X_\eta
+		X_\epsilon \leadsto \epsilon(x)\,X_\xi
+	$}. 
+	\textbf{However, note that this does \textit{not} imply that $
+		X_\epsilon = \epsilon(x)\, X_\xi 
+	$}, 
+\pagebreak[3]
+	nor does it work for contractions with general variations such as $\var{L}$. 
+	In fact, $X_\epsilon$ is a flow in the field space $\mcal{F}$, so it should not have explicit dependence on the $x$ coordinate; see e.g.~\eqref{eq:symmetry_var_field}.
+By definition, the correct form of $X_\epsilon$ should be:
+	\begin{equation}
+		X_\epsilon
 		= \int_M \dd[D]{x}
@@
 	\end{equation}
-%	
-	We then look at the variation $\var_\eta L$; by definition,
+
+	We then look at the variation $\var_\epsilon L$; by definition,
 	\begin{equation}
 	\begin{aligned}
-		\var_\eta L
-		&= X_\eta \cdot \var{L} \\
+		\var_\epsilon L
+		&= X_\epsilon \cdot \var{L} \\
 		&= \epsilon\,E_I\,\var_\xi {\phi^I}
-			+ \dd{(X_\eta \cdot \Theta)} \\
+			+ \dd{(X_\epsilon \cdot \Theta)} \\
 		&= \epsilon\,E_I\,\var_\xi {\phi^I}
@@
 	\begin{aligned}
-		\var_\eta L
+		\var_\epsilon L
 		&= \epsilon\,\var_\xi L
@@
 	\end{aligned}
+	\label{eq:localized_variation}
 	\end{empheq}
@@
 		\var_\xi L = \dd{(K_\xi - \var_\xi l)}
-	$, \textbf{$\eta$~is generally \textit{not} a symmetry of the action:} by definition, we require an \textbf{off-shell} symmetry variation of the action to be a total derivative; this is not the case for $\var_\eta L$, as we have an extra term $
+	$, \textbf{$\eta$~is generally \textit{not} a symmetry of the action:} by definition, we require an \textbf{off-shell} symmetry variation of the action to be a total derivative; this is not the case for $\var_\epsilon L$, as we have an extra term $
 		(\dd{\epsilon}) \wedge J_\xi
@@
 	\begin{aligned}
-		\var_\eta L
+		\var_\epsilon L
 		&= \dd{\pqty\big{
@@
 			- \epsilon \dd{J_\xi} \\
-		&= \dd{\Theta_\eta} 
+		&= \dd{\Theta_\epsilon} 
 			- \epsilon \dd{J_\xi}
@@
 	\begin{aligned}
-		0 = \var_\eta S|_{\tilde{\mcal{P}}}
-		= \int_M \var_\eta L|_{\tilde{\mcal{P}}}
+		0 = \var_\epsilon S|_{\tilde{\mcal{P}}}
+		= \int_M \var_\epsilon L|_{\tilde{\mcal{P}}}
 		&= \cancel{
@@
 	The on-shell condition is necessary to guarantee that $
-		\var_\eta S|_{\tilde{\mcal{P}}} = 0
+		\var_\epsilon S|_{\tilde{\mcal{P}}} = 0
 	$, and any possible boundary terms at $\Sigma^\pm$ vanishes since it's weighted by $\epsilon(x)$. Alternatively, we can see this locally by noting that:
 	\begin{equation}
-		\dd{\Theta_\eta}
+		\dd{\Theta_\epsilon}
 			+ \epsilon\, E_I \,\var_\xi \phi^I
-		= \var_\eta L
-		= \dd{\Theta_\eta} 
+		= \var_\epsilon L
+		= \dd{\Theta_\epsilon} 
 			- \epsilon \dd{J_\xi}
 	\end{equation}
-	We see that the boundary term $\dd{\Theta_\eta}$ actually cancels between the left and right-hand side, therefore even we choose some $\epsilon(x)$ which does not vanish along $\pd M$, we still have $
+	We see that the boundary term $\dd{\Theta_\epsilon}$ actually cancels between the left and right-hand side, therefore even we choose some $\epsilon(x)$ which does not vanish along $\pd M$, we still have $
 		\dd{J_\xi} = -E_I \,\var_\xi \phi^I
@@
 		\var_\xi \phi
+		\leadsto \var_\epsilon \phi
+		= \epsilon\,\var_\xi \phi
+	$ suggests a convenient method of finding the Noether current $J_\xi$, without worrying about the boundary term $K_\xi$; we need only compute $\var_\epsilon L$, throw away the total derivatives, and arrange the final result as some factors of $\dd{\epsilon}$, which will automatically include $K_\xi$ contributions and give us a conserved $J_\xi$.
 		\mapsto \var_\eta \phi

### 2021-06-24 alpha/CovariantPhaseSpace/charge.tex
Add discussions on local variation trick

@@
 	$ suggests a convenient method of finding the Noether current $J_\xi$, without worrying about the boundary term $K_\xi$; we need only compute $\var_\epsilon L$, throw away the total derivatives, and arrange the final result as some factors of $\dd{\epsilon}$, which will automatically include $K_\xi$ contributions and give us a conserved $J_\xi$.
-		\mapsto \var_\eta \phi
-	$ suggests a convenient method of finding the Noether current $J_\xi$, without worrying about the boundary term $K_\xi$; we need only compute $\var_\eta L$, ignore the total derivatives, and collect the factors of $\dd{\epsilon}$, which will automatically include $K_\xi$ contributions and give us a conserved $J_\xi$.
+
+	In fact, we don't even need to impose $
+		\var_\epsilon \phi
+		= \epsilon(x)\,\var_\xi \phi
+	$; we need only require that $\var_\epsilon \phi$ has the following properties: it's compactly supported around some point $x_0$, within the support of $\epsilon(x)$, and with $\epsilon \to 1$ it reduces to the usual symmetry variation $\var_\xi \phi$:
+	\begin{empheq}{equation}
+		\var_\epsilon \phi
+		= \var_\epsilon \phi_{\,[\epsilon(x)]},
+	\quad
+		\var_\epsilon \phi_{\,[\epsilon(x) = 1]}
+		= \var_\xi \phi
+	\label{eq:gauging_conditions}
+	\end{empheq}
+	We follow the arguments of \textcite{Polchinski:1998rq}: consider a ``Taylor expansion'' in the functional space around the ``point'' $\epsilon(x) = 1$; up to total derivative terms, $\var_\epsilon S$ would vanish if $\epsilon$ were a constant, so its variation must be proportional to the gradient $\dd{\epsilon}$,
+	\begin{empheq}{equation}
+		\var_\epsilon L
+		= \dd{\pqty\big{
+				\epsilon(K_\xi - \var_\xi l)
+			}} 
+			+ (\dd{\epsilon}) \wedge J_\xi
+			+ \order{\epsilon^2}
+	\end{empheq}
+	The total derivative terms must be proportional to $\epsilon(x)$, since it comes from the constant piece (0-mode) of $\epsilon(x)$, and its contribution is simply proportional to the $\epsilon(x) = 1$ contribution.
+
+	We see that we've recover the result of \eqref{eq:localized_variation} just from basic analysis, without assuming the explicit form of $\var_\xi \phi$.
+The rest of the arguments that leads to $\dd{J_\xi}|_{\mcal{\tilde{P}}} = 0$ follows through with no issues.
+We see that as long as it satisfies some basic conditions \eqref{eq:gauging_conditions}, how we promote $\var_\xi \phi \leadsto \var_\epsilon \phi$ doesn't actually matter; in the end we will get a valid conserved current $J_\xi$.
+
+	This result comes in handy, as the promotion of $\var_\xi \phi \leadsto \var_\epsilon \phi$ can be taken to be the usual ``gauging'' process that promotes a global symmetry to a local symmetry, by adding coordinates dependence to the symmetry parameter: $\xi \leadsto \epsilon(x)$.
+
+	\newparagraph
 	There will still be ambiguities as one can shift $\Theta$ by a total derivative $\dd{Y}$, as we've seen before.
+In fact it's highly possible that this $\dd{\epsilon}$ procedure described here may produce a different current, compared with the conventional Noether's procedure; we have:
+	\begin{equation}
+		\dd{\epsilon} \wedge
+			\pqty{J_\xi + \dd{Y_\xi}}
+		= \dd{\epsilon} \wedge J_\xi
+			+ \dd{\pqty{
+				\epsilon \dd{Y_\xi}
+			}}
+	\end{equation}
+	Indeed the coefficient of $\dd{\epsilon}$ is only defined up to a total derivative. 
+	This actually provides a way to connect the Hilbert and Noether stress tensor.
+
+\subsection{Derivation for the Hilbert stress tensor}
+	Again consider $\xi^\mu = \epsilon^\mu$, i.e.~the generator for translations in flat spacetime; we now promote it to some localized diffeomorphism:
+	\begin{equation}
+		x\mapsto x - \xi \leadsto x - \epsilon(x),
+	\quad
+		\xi^\mu = \epsilon^\mu
+		\leadsto \epsilon^\mu(x),
+	\quad
+		\var_\xi \phi
+		\leadsto \var_\epsilon \phi
+		= \ldv{\epsilon} \phi
+	\end{equation}
 

### 2021-06-24 alpha/AreaTTbar/areaTTbar.tex
Add various preliminary notes, incl. SUSY notes

% !TeX TS-program = pdflatex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Packages and settings
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[11pt,a4paper]{article}
%\usepackage[dvips]{graphicx}
%\usepackage[pdftex]{graphicx}     %Allows other formats for images
%\usepackage{subfigure}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{cite}
\usepackage{setspace}
\usepackage[top=2.5cm, bottom=2.75cm, left=2.5cm, right=2.5cm]{geometry}
\usepackage[colorlinks=true
            	,urlcolor=blue
            	,anchorcolor=blue
            	,citecolor=blue
            	,filecolor=blue
            	,linkcolor=blue
            	,menucolor=blue
            	,linktoc=page
            	]{hyperref}
 \usepackage{float}
\restylefloat{table}
\renewcommand*\arraystretch{1.5}
%\numberwithin{equation}{section}

%\doublespacing
\onehalfspacing

%\setcounter{section}{-1}
\setlength{\parskip}{1ex plus 0.5ex minus 0.2ex}
\setcounter{tocdepth}{1}

\allowdisplaybreaks

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Macros and definitions
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\long\def\symfootnote[#1]#2{\begingroup%
\def\thefootnote{\fnsymbol{footnote}}\footnote[#1]{#2}\endgroup}

% Colored notes
\def\rednote#1{{\color{red} #1}}
\def\bluenote#1{{\color{blue} #1}}

% Definitions
\def\({\left (}
\def\){\right )}
\def\lb{\left [}
\def\rb{\right ]}
\def\lB{\left \{}
\def\rB{\right \}}

\def\Int#1#2{\int \textrm{d}^{#1} x \sqrt{|#2|}}
\def\Bra#1{\left\langle#1\right|} 
\def\Ket#1{\left|#1\right\rangle}
\def\BraKet#1#2{\left\langle#1|#2\right\rangle} 
\def\Vev#1{\left\langle#1\right\rangle}
\def\Vevm#1{\left\langle \Phi |#1| \Phi \right\rangle}\def\bbox{\bar{\Box}}
\def\til#1{\tilde{#1}}
\def\wtil#1{\widetilde{#1}}
\def\ph#1{\phantom{#1}}

\def\ra{\rightarrow}
\def\la{\leftarrow}
\def\lra{\leftrightarrow}
\def\p{\partial}
\def\diff{\mathrm{d}}

\def\sinh{\mathrm{sinh}}
\def\cosh{\mathrm{cosh}}
\def\tanh{\mathrm{tanh}}
\def\coth{\mathrm{coth}}
\def\sech{\mathrm{sech}}
\def\csch{\mathrm{csch}}

\def\a{\alpha}
\def\b{\beta}
\def\g{\gamma}
\def\d{\delta}
\def\e{\epsilon}
\def\ve{\varepsilon}
\def\k{\kappa}
\def\l{\lambda}
\def\n{\nabla}
\def\om{\omega}
\def\s{\sigma}
\def\t{\theta}
\def\z{\zeta}
\def\vp{\varphi}

\def\ss{\Sigma}
\def\dd{\Delta}
\def\GG{\Gamma}
\def\ll{\Lambda}
\def\tt{\Theta}

\def\A{{\cal A}}
\def\B{{\cal B}}
\def\C{{\cal C}}
\def\cE{{\cal E}}
\def\D{{\cal D}}
\def\F{{\cal F}}
\def\H{{\cal H}}
\def\I{{\cal I}}
\def\J{{\cal J}}
\def\K{{\cal K}}
\def\L{{\cal L}}
\def\N{{\cal N}}
\def\O{{\cal O}}
\def\P{{\cal P}}
\def\cS{{\cal S}}
\def\W{{\cal W}}
\def\X{{\cal X}}
\def\Z{{\cal Z}}

\def\mfa{\mathfrak{a}}
\def\mfb{\mathfrak{b}}
\def\mfc{\mathfrak{c}}
\def\mfd{\mathfrak{d}}

\def\we{\wedge}
\def\re{\textrm{Re}}

\def\tilw{\tilde{w}}
\def\tile{\tilde{e}}

\def\tilL{\tilde{L}}
\def\tilJ{\tilde{J}}

\def\zz{\bar z}
\def\xx{\bar x}
\def\xp{x^{+}}
\def\xm{x^{-}}

\def\RR{\mathbb{R}}

\def\tr{\mathrm{Tr}}
\def\bnabla{\overline{\nabla}}

\def\sint{\int_{\ss}}
\def\dsint{\int_{\p\ss}}
\def\hint{\int_{H}}

% Equation environments
\newcommand{\eq}[1]{\begin{align}#1\end{align}}
\newcommand{\eqst}[1]{\begin{align*}#1\end{align*}}
\newcommand{\eqsp}[1]{\begin{equation}\begin{split}#1\end{split}\end{equation}}

% Square-root of determinants
\newcommand{\absq}[1]{{\textstyle\sqrt{\left |#1\right |}}}
%\newcommand{\absqeq}[1]{{\sqrt{|#1|}}}
%\newcommand{\absq}[1]{{\sqrt{-#1}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Beginning of WX's macros
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{physics}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Ending of WX's macros
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Beginning of document
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\begin{center}
{\Large \bf The contribution of the $B$-field to the area in $T\bar T$}\\
%authors
\today
\vspace{5pt}

\bigskip
\parbox{\textwidth} {\hrulefill\\
\emph{We check if the $B$-field contributes to the area term of candidate RT surfaces in single-trace $T\bar T$-deformed backgrounds.deformations.}\vspace{-5pt}

\hrulefill
}
\end{center}

\tableofcontents

\bigskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{A replica geometry from TsT}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Let us first consider an example a-la Lewkowycz-Maldacena. We would like to construct a smooth background invariant under $\tau \sim \tau + 2\pi n$ with a horizon in the bulk where the $\tau$-circle shrinks to zero (this is the fixed point of the replica symmetry). We can achieve this by considering the Euclidean TsT black string with $T_u = T_v = T$ which in the string frame reads
\eqsp{
ds^2 &= \frac{dr^2}{4(r^2 - 4 T_u^2 T_v^2)} + \frac{r du dv + T_u^2 du^2 + T_v^2 dv^2}{1 + 2 \lambda r + 4 \lambda^2 T_u^2 T_v^2},\\
B &= \frac{r + 4 \lambda T_u^2 T_v^2}{2(1 + 2 \lambda r + 4 \lambda^2 T_u^2 T_v^2} dv \we du, \\
e^{2\phi} &= \frac{k}{p} \bigg(\frac{1- 4 \l^2 T_u^2 T_v^2}{1 + 2 \lambda r + 4 \lambda^2 T_u^2 T_v^2} \bigg), \label{tstbackground}
}
where $u = \vp + i \tau$ and $v = \vp - i \tau$. Near the horizon $r = 2T^2 + \epsilon^2$ we find that 
\eq{
ds^2 =  \bigg( \frac{1}{4T^2} d\epsilon^2 + \frac{1}{1 + 2 \lambda T^2} d\tau^2 + \frac{4T^2}{1+2\l T^2} d\vp^2 \bigg).
}
When $\l=0$ we can choose $4T^2 = 1/n^2$ to get a smooth $n$-replica geometry where $\tau \sim \tau + 2\pi n$. Crucially, in the $\l = 0$, this identification between $T$ and $n$ does not spoil the boundary conditions, which are $T$-independent.

The situation is more subtle in the TsT case. We see from \eqref{tstbackground} that while the metric and the $B$ field are independent of the phase space variables at the boundary $r \to \infty$, namely
\eq{
ds^2\big|_{r\to \infty} \sim \frac{dr^2}{4r^2} + \frac{1}{2\l} du dv, \qquad B\big|_{r\to\infty} \sim \frac{1}{4\l} dv \we du,
}
the dilaton does depend on $T_u$ and $T_v$, that is
\eq{
e^{2\phi} \big|_{r\to\infty} \sim \frac{k}{p} \bigg(\frac{1 - 4 \l^2 T_u^2 T_v^2}{2\l r}\bigg) .
}
This means, in particular, that in different frames, e.g.~the Einstein frame, the boundary conditions for the metric will also depend on $T_u$ and $T_v$. We can make the boundary conditions of all of the fields of the theory by a simple rescaling of the radial coordinate
\eq{
r \to z = \frac{r}{1 - 4 \l^2 T_u^2 T_v^2},
}
which is well-defined in the limit $\l\to 0$.

In the $z$-gauge, the near horizon limit of the nonrotating TsT black string is obtained by letting $z = 2T^2/(1 - 4 \l^2 T^4) + \epsilon_z^2$, whereupon the metric becomes
\eq{
ds^2 =  \bigg(\frac{1 - 4 \l^2 T^4}{4T^2} \bigg) \bigg[ d\epsilon_z^2 + \frac{4 T^2}{1 + 2 \l T^2} \epsilon_z^2 d\tau^2 + {\color{red} \frac{1}{1-2\l T^2}\Big(\frac{4T^2}{1+2\l T^2}\Big)^2 d\vp^2 \textrm{(check)}}   \bigg].
}
Thus we can obtain an $n$-replica geometry with $\tau \sim \tau + 2 \pi n$ by letting
\eq{
\frac{4 T^2}{1 + 2 \l T^2} = \frac{1}{n^2} \quad \implies \quad T^2 = \frac{1}{2(2n^2 - \l)}.
}
Consequently, we find that near the horizon, the background becomes
\eqsp{
ds^2 &= \bigg(\frac{2n^2 - 2 \l}{2n^2 - \l} \bigg) \big( n^2 d\epsilon_z^2 + \epsilon_z^2 d\tau^2 + \dots \big), \\
B&= \frac{1}{4n^2} dv \wedge du, \\
e^{2\phi} &= \frac{k}{p} \bigg( \frac{n^2}{n^2 - \l} \bigg). \label{tstreplica}
}
Interestingly, we note that 
\begin{itemize}
\item[($i$)] the $B$ field at the horizon is independent of $\lambda$. This fact is independent of the choice of gauge we work in. The choice of gauge only affects the factor in front of the metric in \eqref{tstreplica};
\item[($ii$)] since the $B$ is independent of $\l$, i.e.~since it takes the same value as in the BTZ background, we don't expect it to contribute to the on-shell action. We'll see what this means in what follows.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The $B$-field $\theta$-term}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We now take a look at the value of $\theta$ corresponding to the $B$-field. For the supergravity action in the Einstein frame where $(g_E)_{\mu\nu} = e^{-4\phi} g_{\mu\nu}$,
\eq{
S = \alpha \int d^3x \sqrt{-g} \Big( R - 4 \p_\mu \phi \p^\mu \phi + 4 e^{4\phi} - \frac{e^{-8\phi}}{12} H_{\mu\nu\a} H^{\mu\nu\a}\Big).
} 
The $\theta$-term for the $B$-field is given by
\eq{
\xi \cdot \theta_B = \frac{\a}{2} \big( e^{-8\phi} \xi^\mu H^{\nu\a\b} \d B_{\a\b}\big) \epsilon_{\mu\nu\a} dx^\a,
}
where $\xi$ is some vector. The contribution of the $\theta$-term to the on-shell gravitational action (in the Einstein frame) is then
\eq{
\int_{\gamma \times S^1} \theta_B = \int_\gamma \xi \cdot \theta_B = \a \int \sqrt{-g_E} \,e^{-8\phi} \xi^\tau H^{ruv} \delta B_{uv}\epsilon_{tr\vp},
}
where $\xi = \p_\tau$ is the generator of the $S^1$ and $\gamma$ is the horizon.

\subsubsection*{The $\l = 0$ case}

Let us first consider the $\l=0$ case. From \eqref{tstreplica} we see that $\delta B_{uv} = (2/n^3) du\we dv$. Furthermore the field strength $H = d B$ is a top form, meaning that it is proportional to $\epsilon_{\mu\nu\a}$. As a result the $\theta$-term does not vanish. This is a puzzle since we now that in the $\l = 0$ case, the on-shell action should be given just by the area of the horizon. In order to solve this puzzle we note that
\begin{itemize}
\item[($i$)] the $\theta$-term is not gauge invariant since $\delta B_{\mu\nu}$ appears explicitly in the $\theta$-term;
\item[($ii$)] the norm of the gauge field diverges at the horizon.
\end{itemize}
We expect (or should require) that all of our fields are smooth at the horizon. Then it is possible to remedy the divergent norm of the $B$ field by a gauge transformation such that 
\eq{
B_{\mu\nu} \to B'_{\mu\nu}  = B_{\mu\nu} + T_u T_v du \we dv = - \frac{1}{2} ( r - 2T_u T_v) du \we dv.
}
The gauge transformation we used above is uniquely determined by requiring a finite norm at the horizon. In particular, it does not spoil the boundary conditions of the $B$-field (since the gauge transformation is a constant) and it does not spoil the value of the conserved charges. Importantly, this gauge transformation makes both the norm and the value of the $B$-field at the horizon vanish. As a result we find that the $\theta$ term no longer contributes.

\bigskip
\noindent{Questions and comments:} 
\begin{itemize}
\item[($i$)] is it possible that there is another contribution to $\theta_B$ that I'm missing before or after the gauge transformation such that the final answer is independent of the choice of gauge?
\item[($ii$)] is it possible that when the norm of the $B$-field diverges that we cannot ignore the volume contribution of the on-shell action somehow?
\end{itemize}

\subsubsection*{The general case}

When $\l \ne 0$, the norm of the $B$-field is given by
\eq{
B_{\mu\nu}B^{\mu\nu} = - 2 e^{-8\phi} \frac{(r + 4 \l T_u^2 T_v^2)^2}{(r^2 - 4 T_u^2 T_v^2)},
}
and also diverges at the horizon. In this case there is also a unique gauge transformation that renders the norm finite, namely
\eq{
B_{\mu\nu} \to B'_{\mu\nu} = B_{\mu\nu} + \frac{T_u T_v}{1 + 2 \l T_u T_v} = - \frac{1}{2} \bigg(\frac{1 - 2\l T_u T_v}{1 + 2 \l T_u T_v} \bigg) \bigg( \frac{r - 2 T_u T_v}{1 + 2 \l r + 4 \l^2 T_u^2 T_v^2}\bigg) du \we dv.
}
We see that the $B$-field also vanishes at the horizon and as result there is \emph{seemingly} no contribution of the $B$-field $\theta$-term to the on-shell action. This not the end of the story, however, since the gauge transformation introduced above spoils the boundary conditions of the $B$-field. Since the $B$-field asymptotes to a constant at infinity, any constant gauge transformations changes its boundary conditions. In this case we have
\eq{
B_{\mu\nu} \big|_{r \to \infty} \sim - \frac{1}{4\l} du \we dv, \qquad B'_{\mu\nu} \big|_{r \to \infty} \sim - \frac{1}{4\l} \bigg( \frac{1 - 2 \l T_u T_v}{1 + 2 \l T_u T_v}\bigg) du \we dv.
}
This means that the replica background fields would not satisfy the same boundary conditions for general $n$ and $n = 1$.

\noindent{Comments:}
\begin{itemize}
\item[($i$)] We note that the gravitational charges are unchanged after the gauge transformation. This is a consequence of having ``the right" value for the dilaton of the TsT black string. More concretely, before the gauge transformation any constant shift of the dilaton leads to integrable charges. However, there is only one choice for which $T_u$ and $T_v$ dependent shifts of the gauge field leave the charges unchanged. This is the value of the dilaton used in~\eqref{tstbackground}.

\item[($ii$)] A natural thing to try is to shift the $B$-field before performing the TsT transformation to obtain a background that presumably will feature a $B$-field with a finite norm at the horizon. This background will most likely differ from \eqref{tstbackground} with $B_{\mu\nu} \to B'_{\mu\nu}$. This seems worth understanding.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The $B$-field and the RT surface}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Let us now consider the contribution of the $B$-field to the area of the RT surface. In both the BTZ and TsT geometries constructed above, we have one unphysical feature, namely that they require a gauge transformation that depends on the location of the fixed point of the replica symmetry. On the other hand, for the set of fixed points that correspond to the RT surface, any such gauge transformations should be universal and independent of the RT surface we're interested in. We will now show that whenever we have an RT surface that is orthogonal to the asymptotic boundary near infinity, then the contribution of the $B$-field to the area vanishes.

Let us first consider the Rindler parametrization of the RT surface such that near the RT surface at $\rho = 0$ we have
\eq{
ds^2 = d\rho^2 + \rho^2 d\tau^2 + dy^2 + \dots,
}
where $y$ is the coordinate along the RT surface while $\rho$ and $\tau \sim \tau + 2 \pi$ describe the plane orthogonal to the RT surface. In three-dimensional gravity --- i.e.~for both the BTZ and TsT geometries --- the field strength of the $B$-field is a top form, meaning that we can write
\eq{
H = c_1 \epsilon_{\mu\nu\a} dx^{\mu} \we dx^{\nu} \we dx^{\alpha},
}
where $\epsilon_{\mu\nu\a}$ contains a factor of $\sqrt{-g}$ and $c_1$ is a constant that depends on the phase space variables and, in the case of the TsT black string, also on the deformation parameter. Consequently we find that the field strength $H$ is given by
\eq{
H \sim c_1 \rho\, d\rho \we d \tau \we  d y. \label{Hdef}
}

The contribution of the $B$-field to the area of the RT surface is thus given by
\eq{
\int_{\gamma \times S^1} \theta_B = \int_\gamma \xi \cdot \theta_B = \frac{\a}{2} \int_\gamma e^{-8\phi} \xi^\tau H^{\rho\mu\nu} \delta B_{\mu\nu}\epsilon_{\tau \rho y}dy \sim \a c_1 e^{-8\phi} \int_\gamma \delta B_{\tau y} dy.
}
Hence we learn that the only possible contributions of the gauge field to the area of the RT surface come from $B_{\tau y}$. Solving for the value of the $B$-field from the field strength \eqref{Hdef} yields
\eq{
B \sim \frac{c_1}{2} ( \rho^2 + b) d\tau \we dy + \dots, \label{Bfieldbootstrap}
}
where we have ignored the other components of the gauge field and $b$ is an integration constant. Thus, we learn that the only contribution of the $B$-field to the $\theta_B$-term comes from this integration constant.

In order to determine the integration constant in \eqref{Bfieldbootstrap} it we note that near the asymptotic boundary the plane orthogonal to the RT surface is parallel to the asymptotic boundary, meaning that we can identify the following coordinates (up to a conformal factor) 
\eq{
d\rho^2 + \rho^2 d\tau^2 \sim e^{-4\phi} f(r) du dv, \label{boundarymatching}
}
where $f(r) = r$ for AdS$_3$ backgrounds while $f(r) = 1/2\l$ for TsT backgrounds. The $B$ field of the AdS$_3$ and TsT geometries features only $u$ and $v$ components, meaning that
\eq{
B = - \frac{f(r)}{2} du \we dv.
}
near the asymptotic boundary. Note that this is the same $f(r)$ function used in the parametrization of the metric at the boundary \eqref{boundarymatching}. As a result, we learn that the $B$-field at the endpoints of the RT surface features only $B_{\rho\tau}$ components, such that $B_{\tau y} = 0$ to leading order in $\rho$. This implies that the integration constant in \eqref{Bfieldbootstrap} vanishes and we have
\eq{
B \sim \frac{c_1}{2}  \rho^2  d\tau \we dy + \dots, 
%\label{Bfieldbootstrap}
}
Consequently the $\theta_B$-term vanishes along the RT surface and the $B$-term does not contribute to the area of the RT surface.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The $B$-field and the string frame geodesic}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We've shown that whenever we have an RT surface that is \textbf{orthogonal} to the asymptotic boundary near infinity, then the contribution of the $B$-field to the area vanishes. We shall demonstrate below that such contribution also vanishes if we compute the on-shell action of a curve $\gamma$ that goes \textbf{parallel} to the asymptotic boundary as it approaches infinity. This is what happens if we consider $\gamma$: the string frame geodesic; see \texttt{notesEETTbar.pdf}.

All the arguments up till \eqref{Bfieldbootstrap} go through in the above section; now instead of \eqref{boundarymatching}, near the asymptotic boundary, we have:
\begin{equation}
\begin{aligned}
	d\rho^2 + \rho^2 d\tau^2 + dy^2
	&\sim e^{-4\phi} \pqty{
			\frac{\dd{r}^2}{4r^2}
			+ f(r)\,\pqty{\dd{t}^2 + \dd{\varphi}^2}
		} \\
	&\sim e^{-4\phi} \pqty{
			\pqty{\dd{\tfrac{\ln r}{2}}}^2
			+ f(r)\,\pqty{\dd{t}^2 + \dd{\varphi}^2}
		} \\
\end{aligned}
\end{equation}
Namely, the plane orthogonal to the RT surface is now perpendicular to the asymptotic boundary. 
Here for simplicity we use $\tau$ for the \textit{local} Euclidean time around $\gamma$, and $t$ for the Euclidean time in the \textit{global} metric. We have the following observations:
\begin{itemize}
\item As in \eqref{Bfieldbootstrap}, only the $B_{\tau y}$ component in the local coordinates contributes to $\theta_B$; this means that only the $B_{t\vp}, B_{r\vp}$ components in the global coordinates contribute to $\theta_B$, as only $\varphi$ is related to $y$ near the asymptotic boundary.

\item The $B$ field profile in the TsT geometries contains only the $B_{uv}$ component; compared with the previous observation, this means that only the $B_{t\vp}$ component could possibly contribute. 
\end{itemize}
On the other hand, from the $B$-field profile we see that:
\begin{equation}
\begin{aligned}
	B_{t\varphi}
	\propto f(r) \dd{t} \we \dd{\vp}
	&\sim e^{4\phi} \rho \dd{\tau} \we \dd{\vp} \\
	&\sim \frac{1}{r_0^2} \pqty{
			\rho - \frac{2}{r_0^2}\,\rho^2
		} \dd{\tau} \we \dd{\vp} \\
\end{aligned}
\end{equation}
Where $r_0 \to \infty$ is the $r$ coordinate for $\gamma$. We see that there is no constant piece in the $B$-field profile, therefore again the $B$-field does not contribute as $\gamma$ goes parallel to the asymptotic boundary.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Conclusions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\bigskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection*{Acknowledgments}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\begin{thebibliography}{137}

%\end{thebibliography}

\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% The end
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2021-06-24 alpha/SUSY/susy.tex
Add various preliminary notes, incl. SUSY notes

--- 2021-06-06 alpha/Ising/ising.tex
@@
 
-\input{../preamble.tex}
-\input{../.modules/basics/biblatex.tex}
+\input{preamble.tex}
 
-\title{Understanding the Ising CFT}
-\addbibresource{ising.bib}
+\title{Understanding Supersymmetry}
+\addbibresource{susy.bib}
 
@@
 
-\section{Primaries and their physical meanings}
-	Primaries:
-	\begin{itemize}[noitemsep]
-	\item $\idty$
-	\item Spin field: $\sigma(z,\bar{z})$ w/ weight $(\frac{1}{16},\frac{1}{16})$
-	\item Energy operator: $\epsilon(z,\bar{z})$ w/ weight $(\frac{1}{2},\frac{1}{2})$
-	\end{itemize}
-	Question: how do we get this?
-	One can answer this question through bootstrap, namely under the constraints of conformal symmetry and unitarity, this is the only possible situation for a $c = \tilde{c} = \frac{1}{2}$ CFT.
-But this doesn't quite explain the physical meaning of these fields.
-
-	To really understand the physical origin, we have to go back to the lattice model.
-Taking the continuous limit of the lattice model is quite a subtle process.
-We will summarize this procedure here, in a very rough and very schematic language.
-For a detailed account with exact equations, see e.g.~\cite{Atanasov:2017abc,Kogut:1979wt,Fradkin:1991nr}.
-\subsection{Ising model on the lattice}
-	First, we start with the 2D Ising action, with the field $s(x,\tau) = \pm\frac{1}{2}$, defined on a square lattice labeled by $(x,\tau)$. Consider:
-	\begin{equation}
-		\mcal{Z} = \int \DD{s} e^{-S[s]}
-	\end{equation}
-	It can be interpreted in the following 2 ways:
-	\begin{enumerate}
-	\item If we think of $\tau$ as another spatial direction, then $\mcal{Z}$ is precisely the \textbf{classical partition function} of this 2D lattice.
-The inverse temperature $\beta$ is related with the coupling of the system.
-When it's tuned to the critical point, we have a CFT.
-
-	\item Alternatively, if the column direction is interpreted as the Euclidean time $\tau$, while the row direction is interpreted as the only spatial direction $x$, then this is the \textbf{Euclidean path integral} of a quantum system, where $\beta$ is the size of the $\tau$ circle.
-	\end{enumerate}
-
-	Some choose to call this the \textit{quantum--classical correspondence}\footnote{
-		See \cite{Simmons-Duffin:2016gjk} and \url{https://mcgreevy.physics.ucsd.edu/s19/2019-215C-lectures.pdf}. 
-	}. Here we shall take the second perspective, and the Hilbert space consists of the 2-component Pauli spinor $s(x)$ located at each site~$x$.
-
-	We first take the continous $\tau$ limit by switching to the Hamiltonian description. We then rewrite the time evolution using the \textit{transfer matrix}:
-	\begin{equation}
-		e^{-\tau H}
-	\end{equation}
-	Where $H$ is a $2\times 2$ matrix acting on the vector space of $s(x,\tau)$ values. 
-	$H[\sigma^\pm]$ can be written down explicitly using the Pauli matrices $\sigma^\pm$, and it is in fact $\tau$-independent. Roughly speaking, we have:
-	\begin{equation}
-		\sigma \sim \sigma^z
-		= 2\sigma^+ \sigma^- - 1
-	\end{equation}
-
-	Note that the original Ising action contains only the $s \sim s^z$ field, with no mention of the $s^x,s^y$ or $s^\pm$ component.
-Why do we have $\sigma^\pm$ now?
-In fact, this captures the dynamics of spin flips and serves as the momentum term in the Hamiltonian.
-
-	Note that $H = H[\sigma^\pm]$ itself closely resembles a 1D Ising model with $s$ replaced by $\sigma$, defined along the one spatial direction: $\sigma = \sigma(x)$. 
-	Some would like to call it the 1D ``quantum'' Ising model, and call this the correspondence between the 2D ``classical'' model and the 1D ``quantum'' model.
-But we see here that this is simply the Lagrangian and Hamiltonian descriptions of the same system.
-
-\subsection{Fermionization by Jordan--Wigner}
-
-	Why the central charge is only $\frac{1}{2}$? We are looking at Weyl fermions. $\mrm{Ising}^2$ is $c = \tilde{c} = 1$ free boson CFT, with the usual fermionization as in string theory.
+\section{Algebra \& Unitary Representations}
 

### 2021-06-24 alpha/SUSY/package.sh

@@ -1,0 +1,27 @@
+#!/bin/bash
+# package LaTeX source for distribution
+
+# FILENAME="${1%.tex}"; shift
+FILENAME=susy
+TARGET=release
+
+[[ -r "$FILENAME".tex ]] \
+    || { echo "# Couldn't access $FILENAME.tex"; exit 1; }
+
+mkdir "$TARGET" || true
+# echo "*" > "$TARGET/.gitignore"
+
+PREAMBLE=preamble.tex
+sed-latex "$PREAMBLE" > "$TARGET/$PREAMBLE"
+
+rsync \
+    --exclude='.git*' --recursive --copy-links \
+    --update --partial \
+    --progress --verbose \
+    "$@" \
+    "$FILENAME.tex" \
+    "$FILENAME.bib" \
+    "$FILENAME.bbl" \
+    "$FILENAME.pdf" \
+    "img/" \
+    "$TARGET"

### 2021-06-24 alpha/CutoffModularFlow/nb/diffgeo.m
Add sync script for notes & restructure nb

@@ -1,1006 +1,1 @@
-(* 
-
-diffgeo.m			
-
-A Mathematica package for tensor algebra and calculus, by M. Headrick
-
-June 2015 version 1 (see end of package for changelog)
-
-
-Before loading this package, the following quantities must be defined:
-
-coord
-  a list of the coordinates
-metric
-  the metric in the form of a matrix
-metricsign (optional)
-  the sign of the determinant of the metric; if this is not specified then
-  Mathematica will attempt to determine it
-
-Furthermore, information about the ranges of coordinates and parameters appearing in the metric may be specified by the variable $Assumptions (this helps Simplify, which processes the output of the functions defined in this package, to do a better job). By default, all coordinates are assumed real.
-
-Example:
-
-coord = { r, theta, phi };
-$Assumptions = And[ r>0, theta>0, theta<Pi, Element[phi,Reals] ];
-metric = DiagonalMatrix[ { 1, r^2, r^2 Sin[theta]^2 } ];
-
-When the package is loaded, the following tensors and other quantities are calculated by Mathematica (some immediately, others only when they are called):
-
-*)
-
-dimen::usage =		"dimen is the dimensionality of the space (number of coordinates)"
-inverse::usage =	"Inverse metric."
-Christoffel::usage =	"Christoffel symbol, with the upper index first."
-rg::usage =		"Square root of the absolute value of the determinant of the metric."
-LeviCivita::usage =	"Levi-Civita tensor, with all indices down; equivalent to volumeForm, but as a tensor (array)."
-Riemann::usage =	"Riemann tensor, with first three indices down and fourth index up."
-RicciTensor::usage =	"Ricci tensor, with both indices down."
-RicciScalar::usage =	"Ricci scalar."
-Einstein::usage =	"Einstein tensor, with both indices down."
-Weyl::usage =		"Weyl tensor, with all indices down."
-Cotton::usage =		"Cotton tensor, with both indices down (defined only in 3 dimensions)."
-volumeForm::usage =	"Metric volume form; equivalent to LeviCivita, but as a \[DoubleStruckD] expression."
-
-(*
-
-For the curvature tensors we follow the conventions of Wald.
-
-Index values for tensors can be specified either by number or by the name of the coordinate, as in:
-
-Riemann[[r,theta,r,theta]]
-
-This applies not just to the tensors listed above but to any tensor, and can be used when setting the value of a component of a tensor.
-
-The following functions are also defined:
-
-*)
-
-coordQ::usage =
[…]

### 2021-06-24 alpha/CutoffModularFlow/upload.sh

@@ -1,0 +1,30 @@
+#!/bin/bash
+# package LaTeX source for distribution
+
+# FILENAME="${1%.tex}"; shift
+FILENAME=notes
+TARGET=upstream
+
+[[ -r "$FILENAME".tex ]] \
+    || { echo "# Couldn't access $FILENAME.tex"; exit 1; }
+
+function sync {
+    rsync \
+        --exclude='.git*' --recursive --copy-links \
+        --update --partial \
+        --progress --verbose \
+        "$@" \
+        "$FILENAME.tex" \
+        "$FILENAME.bbl" \
+        "$FILENAME.pdf" \
+        "cutoff.bib" \
+        "img" \
+        "nb" \
+        "$TARGET"
+}
+
+sync --dry-run
+echo
+read -r -p "### Continue?"
+echo
+sync "$@"

### 2021-08-01 beta/Renormalization/wilson.tex
Move finalized notes to new folder `beta`
Add major updates to the Wilsonian RG note

--- 2020-10-10 alpha/Renormalization/wilson.tex
@@
 % !TeX spellcheck = en_US
+% !TeX TS-program = pdflatex
 % !TeX TXS-program:bibliography = biber -l zh__pinyin --output-safechars %
@@
 \vspace*{-.5\baselineskip}
-	\textbf{Reason:} The continuum limit $\Lambda\to\infty$ is \textbf{not} well-defined.
+	\textbf{Philosophy:} The continuum limit $\Lambda\to\infty$ is \textbf{not} well-defined.
 	Renormalization provides a way to \emph{define} the theory when
@@
 
-	\textbf{My belief:} The only way to fully understand renormalization is
+	\textbf{Personal Belief:} The only way to fully understand renormalization is
 	through Wilson's arguments; all other ``interpretations'' of
@@
 
-	\textbf{Keywords:}
-	\begin{itemize}[nosep,topsep=-.5\parskip]
-	\item Renormalization group
-	\item Counterterms
-	\item Regularization and cutoff
-	\end{itemize}
+%	\textbf{Keywords:}
+%	\begin{itemize}[nosep,topsep=-.5\parskip]
+%	\item Renormalization group
+%	\item Counterterms
+%	\item Regularization and cutoff
+%	\end{itemize}
 
@@
 
+\addtocounter{section}{-1}
 \section{References}
@@
 
-	\begin{itemize}[parsep=0pt,itemsep=.5\parskip]
+	\begin{itemize}[parsep=0pt,itemsep=.5\parskip,labelindent=.1\parindent]
 	\item David Skinner's note:
@@
 	\item Schwartz, Chapter 15
-	\item Peskin \& Schroeder, Chapter 10 \& 12
+	\item Peskin \& Schroeder, Chapter 10, 11 \& 12
 	\item Hollowood's book:
@@
 
-\section{Wilson's picture}
-	Seed theory parameters (i.e.\ \emph{bare parameters}):
-	$(Z_\phi,g,\Lambda)_0$, where $g = (m,\lambda,\cdots)$ is the collection of all possible couplings. $Z_\phi$ is the coefficient of the kinetic term.
+\pagebreak[4]
 
+\section{Wilson's Picture}
+	We start with a \textit{seed theory} with \textit{bare} parameters: $(Z_\phi,g,\Lambda)_0$, where $g = (m,\lambda,\cdots)$ is the collection of all possible couplings.
+$Z_\phi$ is the coefficient of the kinetic term.
+	We \textbf{coarse-grain} the theory by integrating out some high energy modes:
 	\begin{equation}
 	\begin{aligned}
-	  \phi_{\Lambda_0}(x)
+	  \phi^{\Lambda_0}(x)
 	  \sim \int^{\Lambda_0} \dd{p}
@@
 	    \tilde{\phi}(p) \\
-	  &=\colon \phi_{\Lambda}(x) + \chi(x)
+	  &=\colon \phi^{\Lambda}(x) + \chi(x)
 	\end{aligned}
@@
 	\begin{aligned}
-	  \DD\phi_{\Lambda_0}(x)
+	  \DD\phi^{\Lambda_0}(x)
 	  \sim \prod_{\norm{p} < \Lambda_0}
@@
 	  &\sim
-	    \DD\phi_{\Lambda}(x)\,
+	    \DD\phi^{\Lambda}(x)\,
 	    \DD\chi(x)
@@
 	  \mcal{Z} (g_0,\Lambda_0)
-	  &= \int \DD\phi_{\Lambda_0}
-	      e^{iS[\phi_{\Lambda_0}]} \\
-	  &= \int \DD\phi_{\Lambda}
+	  &= \int \DD\phi^{\Lambda_0}
+	      e^{iS[\phi^{\Lambda_0}]} \\
+	  &= \int \DD\phi^{\Lambda}
 	    \int \DD\chi
-	      e^{iS[\phi_\Lambda + \chi]} \\
-	  &=: \int \DD\phi_{\Lambda}
-	      e^{iS_{\mathrm{eff}} [\phi_\Lambda]}
+	      e^{iS[\phi^\Lambda + \chi]} \\
+	  &=: \int \DD\phi^{\Lambda}
+	      e^{iS^\Lambda [\phi^\Lambda]}
 	  =: \mcal{Z}\pqty{g(\Lambda),\Lambda}
@@
 	\end{equation}
-	Coarse-grained parameters: $(Z_\phi,g,\Lambda)$.
+	The coarse-grained parameters are given by $(Z_\phi,g,\Lambda)$.
 
@@
 	\begin{equation}
-	  S_{\mathrm{eff}}[\phi]
+	  S^\Lambda[\phi]
 	  = -i \ln \int \DD \chi
@@
 	\end{equation}
-	$\phi = \phi_\Lambda$ is treated as constant when doing
-	$\int \DD \chi$. Perturbatively, we integrate over loops with $\chi$ propagators as internal lines
+	$\phi = \phi^\Lambda$ is treated as an external source or a background field when we compute $\int \DD \chi$. Perturbatively, we integrate over loops with $\chi$ propagators as internal lines.
 	\begin{equation}
@@
 	\begin{equation}
-	  S_{\mathrm{eff}}[\phi_\Lambda]
-	  = S[\phi_\Lambda]
+	  S^\Lambda[\phi^\Lambda]
+	  = S[\phi^\Lambda]
 	    - i \ln \int \DD \chi
-	      e^{i\,\Delta S[\phi_\Lambda + \chi]} \\
+	      e^{i\,\Delta S[\phi^\Lambda + \chi]} \\
 	\end{equation}
 
-	If $\Lambda \lesssim \Lambda_0$, then $S_{\mathrm{eff}}$ is almost
+	If $\Lambda \lesssim \Lambda_0$, then $S^\Lambda$ is almost
 	the same as the original $S$, with minor corrections from the
@@
 	\end{equation}
-	This is an example of a \textbf{RG Equation}.
-\subsection{Free theory \& CFT}
+	This is an example of a {renormalization group (RG) equation}.
+
+	\newparagraph
+	Note that the Euclidean path integral along a time circle of length $\beta$ computes the thermal partition function with inverse temperature $\beta$.
+This leads to an intuitive relation between $\beta$ and the cutoff $\Lambda$.
+
+	Let's focus on the Euclidean time direction.
+Again suppose we lower $\Lambda_0 \leadsto \Lambda$ by coarse-graining.
+In a thermal field theory, this can be achieved not only through integrating out UV modes (as we've done before), but also by enlarging the $\beta$ circle.
+Therefore, coarse-graining corresponds to a lowering of temperature.
+
+	Note that this is only a rough intuition, but there are more rigorous generalizations of this picture for theories based on a compact manifold, where the size of the manifold corresponds to some energy scale of the theory.
+\subsection{Free theory, scale invariance \& CFT}
 	We first observe that a massless free theory with $
@@
 	  \mcal{Z}
-	  &= \int \DD\phi_{\Lambda_0}
+	  &= \int \DD\phi^{\Lambda_0}
 	      e^{iS[\phi_0]} \\
-	  &= \int \DD\phi_{\Lambda}
+	  &= \int \DD\phi^{\Lambda}
 	    \int \DD\chi
 	      e^{iS[\phi + \chi]} \\
-	  &\sim \int \DD\phi_{\Lambda}
+	  &\sim \int \DD\phi^{\Lambda}
 	      e^{iS[\phi]}
@@
 
-	On the other hand, we can restore $\Lambda = s\Lambda_0$ back to $\Lambda_0$ by rescaling.
+	On the other hand, we can restore $\Lambda = s\Lambda_0$ back to $\Lambda_0$ by \textbf{rescaling}.
 This is easy to understand when we think of a lattice theory: to probe the IR behavor, we first ``coarse-grain'' by grouping points together, effectively lowering $\Lambda$; then we ``zoom out'' to see the bigger picture.
@@
 
+	Another motivation for rescaling is that we would like to compare the theories before and after coarse-graining; this comparison only makes sense if they share the same cutoff $\Lambda_0$.
+In summary, the conventional definition for renormalization group flow (RG flow) contains 2 operations:
+	\begin{enumerate}[noitemsep]
+	\item \textbf{Coarse-graining:} integrate out higher modes to obtain a low energy effective action at $\Lambda$;
+	\item \textbf{Rescaling:} restore $\Lambda = s\Lambda_0 \leadsto \Lambda_0$ the original cutoff by field re-definition.
+	\end{enumerate}
+
 	When taking $\Lambda\mapsto \Lambda_0 = \Lambda / s$, first note that the kinetic term $\int \dd[d]{x} (\pd\phi)^2$ is scale-invariant if we rescale $\phi$ accordingly:
-	\begin{equation}
+	\begin{gather}
 		\Lambda\mapsto \Lambda_0 = \Lambda / s,
 	\quad
+		s < 1,
+	\notag\\
 		x\mapsto x' = sx,
@@
 		\phi'(x') = s^{1 - \frac{d}{2}} \phi(x)
-	\end{equation}
+	\end{gather}
 	The $s^{1 - \frac{d}{2}}$ factor is consistent with the mass dimension of $\phi$, and we have $S'[\phi'] = S[\phi]$ invariant under rescaling.
+
+\pagebreak[4]
 
@@
 	\begin{equation}
-		\sqrt{Z_\phi^\#} \DD\phi_{\Lambda}
+		\sqrt{Z_\phi^\#} \DD\phi^{\Lambda}
 		\sim \sqrt{Z_\phi^\#}
@@
 			\dd{\tilde{\phi}'(p')}
-		\sim \DD\phi'_{\Lambda_0}
+		\sim \DD\phi'^{\,\Lambda_0}
 	\end{equation}
-	Therefore the complete path integral is invariant under RG flow \& rescaling; $Z_\phi$ is also unchanged during this process.
+	Therefore the complete path integral is invariant under coarse-graining \& rescaling.
+$Z_\phi$ is also unchanged during this process.
 Therefore we can simply set $Z_\phi \equiv 1$ by an appropriate \textit{normalization} of $\phi$.
 
-	One can see how this process might fail in a curved background: in flat space the Fourier modes are equally spaced, and rescaling $\DD\phi_{\Lambda}$ can be achived by simply adding back a total of $\#$ modes.
-However, in a curved background the Fourier modes are complicated (e.g.\ think of spherical harmonics) and we generally do not expect the Jacobian of $\DD\phi_{\Lambda} \mapsto \DD\phi'_{\Lambda_0}$ to cancel out the $Z_\phi$ factor precisely.
+	One can see how this process might fail in a curved background: in flat space the Fourier modes are equally spaced, and rescaling $\DD\phi^{\Lambda}$ can be achived by simply adding back a total of $\#$ modes.
+However, in a curved background the Fourier modes are complicated (e.g.\ think of spherical harmonics) and we generally do not expect the Jacobian of $\DD\phi^{\Lambda} \mapsto \DD\phi'^{\,\Lambda_0}$ to cancel out the $Z_\phi$ factor precisely.
 This is a hint of \textit{Weyl anomaly} in curved backgrounds.
 For a concrete discussion with path integral, see \textit{Di Francesco et al}, 5.A.
-\pagebreak[4]
+
+%\pagebreak[4]
 
@@
 	CFTs are the \textit{fixed points} of RG flow.
-\subsection{Massive theory \& the space of theories}
+\subsection{From mass deformation to the space of theories}
 	What about \textit{massive} free theories?
@@
 Therefore $m$ is a \textit{relevant} parameter as we flow towards IR; it grows and flows away from the massless free CFT.
-For an explicitly path integral calculation (along with $\phi^{2n}$ interactions), see \textit{Hollowood}, 2.1.
+For an explicitly path integral calculation (along with $\phi^{2n}$ interactions), see \textit{Hollowood}, \S2.1.
 
@@
 		g(\Lambda) = \pqty{
-			g^{(2)} = \frac{m^2_{(\Lambda)}}{\Lambda^2},
+			Z_\phi,
+			\ g^{(2)} = \frac{m^2_{(\Lambda)}}{\Lambda^2},
 			\ g^{(4)} = \lambda,
@@
 
+	In summary, we have:
+	\begin{empheq}{equation*}
+		\text{
+			\textbf{Fact:} dimensionless couplings $g(\Lambda)$ are invariant under rescaling!
+		}
+	\end{empheq}
+	To recover the dimensionful couplings:
+	\begin{itemize}[noitemsep]
+	\item ... after coarse-graining but before rescaling: multiply by $\Lambda^\#$;
+	\item ... after rescaling: multiply by $\Lambda_0^\#$.
+	\end{itemize}
+	Here $\#$ is the mass dimension of the coupling.
+
 	\begin{figure}[!h]
 	\centering
-	\includegraphics[width=.35\linewidth]{img/RG-flow.png}
+	\includegraphics[width=.45\linewidth]{img/RG-flow.png}
 	\end{figure}
-\subsection{Physical Scales vs the Cutoff}
-	LSZ reduction (with the ``mostly plus'' metric convention, see \textit{Srednicki}):
+
+\subsection{From the running cutoff to the physical scales}
+	To get to the physical amplitudes, we apply LSZ reduction (see e.g.~\textit{Srednicki}):
 	\begin{equation}
@@
 		\frac{-i\sqrt{Z_\phi}}{k^2 + m^2 - i\epsilon}
-		\mel{p}{S}{k}
+		\mel{p}{\mcal{S}}{k}
 	\end{equation}
@@
 	\end{equation}
-	$S \sim \idty + i\mcal{M}(\mu)$, physical amplitude $\mcal{M}(\mu)$ scale with energy $\mu$, but is cutoff-independent.
+	Here $\mcal{S} \sim \idty + i\mcal{M}(\mu)$, and the amplitude $\mcal{M}(\mu)$ scale with energy $\mu$, but is cutoff-independent.
 
-	How to relate $\mcal{M}(\mu)$ to $g(\Lambda)$? Note that the canonical Green function \textit{does} scale with $\Lambda$! With the help of Poincar\'e invariance, we have:
+	How to relate $\mcal{M}(\mu)$ to $g(\Lambda)$? Note that the canonical Green function $G_\Lambda$ \textit{does} scale with $\Lambda$! With the help of Poincar\'e invariance, we have:
 	\begin{equation}
@@
 	\quad
-		Z_\lambda := (Z_\phi)_\Lambda
+		Z_\Lambda := (Z_\phi)_\Lambda
 	\end{equation}
-	Physical scale: $l = \abs{x_1 - x_2}$, or center of mass momentum $\mu$ in amplitudes; $l\cdot \mu \sim 1$. $\Lambda$-dependence enters through $Z_\phi$. For general $n$-pt function, RG flow:
+	Here the physical scale is given by $l = \abs{x_1 - x_2}$, or the center of mass momentum $\mu$ in amplitudes; we have $l\cdot \mu \sim 1$.
+$\Lambda$-dependence enters through $Z_\phi$.
+For general $n$-pt function, RG flow leads to:
 	\begin{equation}
 	\begin{aligned}
-		\ave[\big]{\phi^n(\cdots)}
+		\ave[\big]{\phi^n({\cdots})}
 		= \frac{1}{\mcal{Z}}
 			\int \DD{\phi_\Lambda} e^{iS_\Lambda[\phi]}\,
-			\phi^n(\cdots)
+			\phi^n({\cdots})
 		&= Z^{-n/2}_\Lambda
@@
 			G_{\Lambda} \pqty\big{sl; g(s\Lambda)}\,
-			\pqty{s^{1 - \frac{d}{2}}}^{-n}
+			\pqty{s^{1 - \frac{d}{2}}}^{-n},
 	\end{aligned}
 	\end{equation}
-
-	This is a key result! We have:
 	\begin{equation}
@@
 	\end{equation}
-	Or in terms of energy scale $\mu$,
+
+	We see that the flow of correlation as a function of the physical scale $l$ is related to the flow of coupling as a function of the cutoff $\Lambda$. 
+	In terms of energy scale $\mu$, we have:
 	\begin{gather}
@@
 	\\[1ex]
+		\pdv{s}
+		\ \To\ %
 		\mu\,\pdv{\mcal{M}}{\mu}
-		= \pdv{M}{g}\,\pqty{
-				\Lambda\,\pdv{g}{\Lambda}
-			}
+		= \Lambda\,\pdv{g}{\Lambda}
+			\pdv{\mcal{M}}{g}
+		= \beta(g) \pdv{\mcal{M}}{g}
 	\end{gather}
+
 \section{Perturbative Renormalization}
-	However, in naïve perturbation theory, we wish to complete the entire
+	In naïve perturbation theory, we wish to complete the entire
 	path integral $\mcal{Z} (g_0,\Lambda_0)$. We can think of this as
@@
 
-\subsection{Counterterms}
+\subsection{The nature of counterterms}
 	In the above analysis, the theory flows from UV to IR. However, in
@@
 \subsection{Perturbation}
-	The above results are non-perturbative and should always hold.
+	The above understanding is in fact non-perturbative and should always hold.
 	Perturbation theory is only a way to calculate the RG flow from UV to
@@
 	\item
-	  Increase order $n$ and go to step 1
+	  Increase order $n$ and go to step 1. 
 	\end{enumerate}
@@
 
-\subsection{Renormalization Schemes}
+\subsection{Renormalization schemes}
 
@@
 	renormalization schemes:
-
-	\begin{itemize}[nosep]
-
+	\begin{itemize}[noitemsep]
 	\item
@@
 	\end{itemize}
+	A review of these schemes can be found in most of the main references.
 
-\section{Renormalizability}
+	The lesson is that we should tune $(g,\Lambda)_{\Lambda\to 0}$ such that it well approximates the physical couplings, but they are still not quite the same.
+To actually get to the physical couplings we really need to complete the path integral, all the way down to $\Lambda = 0$.
+The physical couplings are then read out from the full quantum effective action $\Gamma[\varphi]$, as we shall review later.
+
+\subsection{Renormalizability}
 	As we've mentioned before, most parameters $g^{(i)} \in g$ are, in fact, \emph{irrelevant} --- such terms in the Lagrangian get suppressed by $\Lambda/\Lambda_0$ in IR.
-We shall see how this arise from dimensional anlaysis.
+This simply arises from dimensional anlaysis: imagine that we lower the cutoff gradually, by coarse-graining.
+Recall that the coupling before rescaling is given by $g^{(i)}_{(\Lambda)} \Lambda^\#$, which is only \textit{mildly} modified as long as $\Lambda\lesssim\Lambda_0$.
+By dimensional analysis,
+	\begin{equation}
+		g^{(i)}_{(\Lambda)}
+		\sim \pqty{\frac{\Lambda}{\Lambda_0}}^{\!\!-\#}
+	\end{equation}
+	This means that all couplings with negative mass dimensions is suppressed in the IR (at the classical level, due to rescaling).
 
@@
 	$g_0$, and one has to tune infinitely many bare parameters to obtain
-	the physical IR values. Such theory is hardly \emph{fundamental}, since
+	the physical IR values. Such theory is hardly fundamental, since
 	it depends on infinitely many parameters; but it's a good
@@
 
-\section{Effective Action}
-	After $\phi_\Lambda$ is completely integrated out, we
+\section{Effective Action Formalism}
+	After $\phi^\Lambda$ is completely integrated out, we
 	have:
-
 	\begin{equation}
-	  S_{\mathrm{eff}}[\phi] \to W,\quad
+	  S^\Lambda[\phi] \to W,\quad
 	  Z(g_0,\Lambda_0) = e^{iW}
@@
 	$(g,\Lambda)$. $W$ in fact contains all information about the seed
-	theory, labeled by $(g_0,\Lambda_0)$. To extract this information, we
-	usually perturb the original action $S[\phi]$ with a source term; then
-	we have:
+	theory, labeled by $(g_0,\Lambda_0)$.
 
+	To extract this information, we probe the system with an external source $J$; namely, we perturb the original action $S[\phi]$ with a source term:
 	\begin{equation}
 		S[\phi,J]
-	  = S[\phi] + \int \dd{x}\,J(x)\,\phi(x),\quad
+		= S[\phi] + J\cdot \phi,\quad
 		W \to W[J]
 	\end{equation}
+	Here $J\cdot \phi$ is understood as $
+		\int \dd{x} J(x)\,\phi(x)
+	$. 
+	Expand $W[J]$ in terms of $J$-modes, and then its coefficients give us physical coupling constants in the IR.
 
-	Expand $W[J]$ in terms of $J$-modes, and its coefficient gives us
-	physical coupling constants in the IR. More precisely, we can define the Legendre-transformed $\Gamma[\varphi]$.
+	Alternatively, we can define the Legendre-transformed $\Gamma[\varphi]$, where:
+	\begin{equation}
+		\varphi \equiv \fdv{W}{J} = \ave{\phi}_J,
+	\quad
+		\Gamma[\varphi]
+		= W[J] - J\cdot\varphi,
+	\quad
+		\fdv{\Gamma}{\varphi}
+		= -J
+	\label{eq:legendre_transform}
+	\end{equation}
+	The Legendre transformation can be implemented by a Fourier (or Laplace) transform, under the semi-classical limit $\hbar\to 0$, when the saddle point approximation applies\footnote{
+		We've been cavaliar about overall factors. 
+		Here the proportionality factor is in general a functional of $J$, but it is a power series in $\hbar$ starting with terms of $\order{\hbar^0}$.
+Hence it can be safely dropped as $\hbar\to 0$, as we focus on the $\order{\hbar^{-1}}$ terms.
+	}:
+	\begin{equation}
+	\begin{aligned}
+		Z[J] = \exp \frac{i}{\hbar} W[J]
+		&= \exp \frac{i}{\hbar} \pqty\Big{
+				\Gamma[\varphi]
+				+ J\cdot\varphi
+			}_{
+				\mathlarger{\fdv{\Gamma}{\varphi}}
+				= -J
+			} \\
+		&\propto \lim_{\hbar\to 0} \int
+			\DD{\varphi}\,
+			\exp \frac{i}{\hbar} \pqty\Big{
+				\Gamma[\varphi]
+				+ J\cdot\varphi
+			}
+	\end{aligned}
+	\end{equation}
+
+\pagebreak[3]
+
+	On the other hand, the path integral expansion in $\hbar$ has a diagrammatic interpretation: it counts the number of loops in Feynman diagrams.
+All propagators contribute a factor of $\hbar$, while all vertices carry a factor of $\hbar^{-1}$.
+In the end we have:
+	\begin{equation}
+		\hbar^{\,\#\text{edges}\,-\,\#\text{vertices}}
+		\equiv \hbar^{\,\#\text{loops}\,-\,1}
+	\end{equation}
+	Here $(\#\,\text{loops})$ is the same as the number of faces in planar diagrams\footnote{
+		For non-planar diagrams, see \https{physics.stackexchange.com/q/391454}. 
+	}. In the $\hbar\to 0$ limit, only tree (0-loop) diagrams survive.
+
+	However, $Z[J] = \exp \frac{i}{\hbar} W[J]$ itself is given by the sum over all Feynman diagrams, while at the same time it can be reproduced by a sum over only tree level diagrams with $\Gamma[\varphi]$.
+Therefore, all higher loop connections must have already been packed up inside $\Gamma[\varphi]$, namely it is the \textit{quantum effective action}.
+In terms of correlators, we have:
+	\begin{equation}
+	\begin{aligned}
+		\ave{\phi(x_1)\cdots\phi(x_n)}
+		&= \int
+			\DD{\phi}
+			\,\phi(x_1)\cdots\phi(x_n)\,
+			\exp \frac{i}{\hbar}
+%			\pqty\Big{
+				S[\phi]
+%				+ J\cdot\phi
+%			}
+	\\
+		&= \int\limits_{\hbar\to 0}
+			\DD{\varphi}
+			\,\varphi(x_1)\cdots\varphi(x_n)\,
+			\exp \frac{i}{\hbar}
+%			\pqty\Big{
+				\Gamma[\varphi]
+%				+ J\cdot\varphi
+%			}
+		= \ave{\varphi(x_1)\cdots\varphi(x_n)}_{\hbar\to 0}
+	\end{aligned}
+	\end{equation}
+	The right hand side is a sum over tree diagrams and $\varphi^n$ vertices, whose coefficient is given by:
+	\begin{equation}
+		\frac{\var[n]{i\Gamma}}{
+			\var{\varphi(x_1)}\cdots\var{\varphi(x_n)}
+		}
+	\end{equation}
+
+	In particular, the coefficient $
+		\frac{\var[2]{i\Gamma}}{
+			\var{\varphi(x_1)} \var{\varphi(x_2)}
+		}
+	$ of the $\varphi^2$ vertex is precisely minus the inverse of the full propagator, i.e. for scalar fields:
+	\begin{equation}
+		i\,(\pd^2-m^2) \sim -i\,(p^2 + m^2)
+	\end{equation}
+	Here $m$ is the renomalized mass $m$.
+In general the terms in $\Gamma[\varphi]$ are the \textit{renomalized vertices}, which pack up all higher loop quantum corrections.
+Diagrammatically, they are produced by the one particle irreducible (1PI) diagrams.
+
+	The meaning of $\Gamma[\varphi]$ can also be understood order by order, from the defining Legendre transformation \eqref{eq:legendre_transform}.
+For example, the full propagator is given by the connected 2-point diagram:
+	\begin{equation}
+	\begin{aligned}
+		D
+		&= \ave{\phi\,\phi}_c
+		= \ave[\Big]{
+			(\phi - \ave{\phi})\,(\phi - \ave{\phi})
+		} \\
+		&= \frac{1}{i^2}
+		\frac{\var[2]{iW}}{
+			\var{J} \var{J}
+		}
+		= -i\,\fdv{J} \pqty{\fdv{W}{J}}
+		= -i\,\fdv{\varphi}{J}
+	\end{aligned}
+	\end{equation}
+	We see that indeed:
+	\begin{equation}
+		\frac{\var[2]{i\Gamma}}{
+			\var{\varphi} \var{\varphi}
+		}
+		= i\,\fdv{\varphi} \pqty{\fdv{\Gamma}{\varphi}}
+		= i\,\fdv{\,(-J)}{\varphi}
+		= - D^{-1}
+	\end{equation}
+
+	For higher point vertices, similar results are well illustrated in \S11.5 of \textit{Peskin \& Schroeder}. 
+	In summary, we have:
+	\begin{equation}
+	\def\arraystretch{2.2}
+	\begin{array}{
+		*1{>{\displaystyle}r}
+		l
+	}
+		\quad
+		\frac{1}{i^n}\frac{\var[n]{Z}}{
+			\var{J(x_1)}\cdots\var{J(x_n)}
+		}
+		\colon&
+		\text{All Feynman diagrams}
+	\\
+		Z[J] = \exp \frac{i}{\hbar} W[J],
+		\quad
+		\frac{1}{i^n}
+		\frac{\var[n]{iW}}{
+			\var{J(x_1)}\cdots\var{J(x_n)}
+		}
+		\colon&
+		\text{\textbf{Connected} diagrams}
+	\\
+		Z[J] = 
+			\int\limits_{\hbar\to 0}
+			\DD{\varphi}\,
+			\exp \frac{i}{\hbar} \pqty\Big{
+				\Gamma[\varphi]
+				+ J\cdot\varphi
+			},
+		\quad
+		\frac{\var[n]{i\Gamma}}{
+			\var{\varphi(x_1)}\cdots\var{\varphi(x_n)}
+		}
+		\colon&
+		\text{\textbf{1PI} diagrams}
+	\end{array}
+	\end{equation}
 

### 2021-08-07 alpha/CutoffModularFlow/dirichlet.tex
Clean up the cutoff modular flow project

% !TeX encoding = UTF-8
% !TeX TS-program = pdflatex
% !BIB TS-program = biblatex

\documentclass[12pt,a4paper,utf8]{article}

\ifdefined\pdfoutput
	\pdfoutput=1
\fi

\input{preamble.tex}

\newcommand{\lui}[2]{\textcolor{red}{#1}\todo[color=yellow]{\scriptsize{L: #2}}}

\usepackage{xspace}
\newcommand{\TTbar}{\ensuremath{T\bar{T}}\xspace}
\newcommand{\arcsinh}{\ensuremath{\mop{arcsinh}}}
\newcommand{\tvar}[1]{\mathinner{\tilde{\delta} #1}}
\usepackage{enumitem}
%\usepackage{mathtools}
\counterwithout{equation}{section}

\begin{document}

\setlength{\parskip}{.5\baselineskip}
\setlength{\parindent}{0pt}

\addtocounter{section}{-1}
\section{On boundary conditions}

\textbf{Claim:} the Dirichlet boundary condition, by our definition,

\begin{itemize}[nosep]
\item ... specifies the set of solutions uniquely,
\item ... but admits \textbf{different symplectic structures}, \\
	... which are specified by $\var{g_{\mu\nu}}$, or more precisely, the total variations $h_{\mu\nu}$. 
\end{itemize}

This leads to \textbf{different charge variations $\var{Q}$}.

Consider the set of BTZ solutions $g_{\mu\nu}(T_u,T_v)$ in some gauge $(u,v,\rho)$, where we only require $\phi \cong \phi + 2\pi$, $\phi = \frac{u + v}{2}$.

\subsection{General definition of Dirichlet radial cutoff}

	\textbf{Definition:} given $g_{\mu\nu}(T_u,T_v)$, if there exists a coordinate transformation:
	\begin{equation}
		(u,v,\rho) \mapsto (u',v',\rho'),
	\end{equation}
	such that:
	\begin{equation}
		\dd{s}^2_{\rho_c}
		= r_c^2 \dd{u'} \dd{v'},
	\end{equation}
	then the collection of $g_{\mu\nu}(T_u,T_v)$ with $\rho \le \rho_c$ is the set of BTZ solutions with Dirichlet boundary condition at the radial cutoff $\rho_c$.

	\textbf{Note:} this definition is quite general.
	\begin{itemize}
	\item It specifies the set of solutions uniquely.
	\item It seems to be \textbf{compatible with everything},\\
		including Verlinde et al \cite{McGough:2016lol} and Guica et al \cite{Guica:2019nzm,Kraus:2021cwf}.

	\item But, it \textbf{implies no symplectic structure}. \\
		Namely it does not fix $\var{g_{\mu\nu}}$ or $h_{\mu\nu}$ completely. 
	\item The definition of Guica et al \cite{Guica:2019nzm,Kraus:2021cwf} is \textbf{actually more restrictive}. \\
		They fix a special symplectic structure given by $h_{\mu\nu}$.
	\end{itemize}

\pagebreak

\subsection{Metric variation $\var{g}$}

Given the above boundary condition, we still need a prescription for $\var{g}$ to compute the charge variation $\var{Q}$.

\begin{itemize}
\item \textbf{Our prescription:} we simply require that:
	\begin{equation}
		0 = \delta g'_{i'j'}(x')\big|_{\rho'=\rho'_c}
		= \bigg(
			\delta \Big(\,
				\pdv{x^\mu}{x'^i}
				\pdv{x^\nu}{x'^j}
				g_{\mu\nu}
			\Big)
			+ \delta x^\sigma\, \partial_\sigma \Big(\,
				\pdv{x^\mu}{x'^i}
				\pdv{x^\nu}{x'^j}
				g_{\mu\nu}
			\Big)
		\bigg) \bigg|_{\rho=\rho_c}
		\label{eq:variation_transform}
	\end{equation}
	in the locally flat $(u',v',\rho')$ gauge, and solve for $
		\zeta^\mu = \delta x^\mu
		= (\var{u},\var{v},\delta\rho)
	$ in the original gauge.

	\begin{itemize}
	\item \textbf{When expanded in Fefferman--Graham or Schwarzschild, this equation has no dependence on $\var{u},\var{v}$}.

	\item Solving $\delta g'_{\phi'\phi'} = 0$ gives us $\var{\rho}$; when substituted back to \eqref{eq:variation_transform} the equation holds \textbf{for all components automatically:} $
			\delta g'_{i'j'}\big|_{\rho'=\rho'_c} = 0
		$.

	\item The total variation is then given by:
		\begin{equation}
			h_{\mu\nu}
			= \delta g_{\mu\nu}
				+ \mathcal{L}_{\zeta} \,g_{\mu\nu},
		\quad
			\zeta^\mu = \delta x^\mu
			= (\var{u},\var{v},\delta\rho)
		\label{varimetric}
		\end{equation}
		$h_{\mu\nu}$ indicates how different states in the phase space are ``neighboring'' each other, and can be used to defined the symplectic form $\Omega$. If $\var{u},\var{v}$ is unconstrained we don't really know the symplectic structure.

	\color{purple}
	\item However, it's physically natural to set:
		\begin{equation}
			\var{u} = \var{v} = 0
		\end{equation}
		This means that we apply no extra boundary diffeomorphisms as we construct $h_{\mu\nu}$. In this way we inherit the symplectic structure of the original Brown--Henneaux phase space.

		With this choice the charge $\var{Q}[g_{\mu\nu},h_{\mu\nu},\xi]$ of the modular flow $\xi$ matches the variation of the area of the RT surface. In this case,
		\begin{equation}
			h_{ij}|_{\rho = \rho_c} \ne 0
		\end{equation}

	\end{itemize}

\item \textbf{Their prescription \cite{Guica:2019nzm,Kraus:2021cwf}:} Guica et al require that we compute charges $\var{Q}[g',h',\xi']$ directly in the $(u',v',\rho')$ gauge, with:
	\begin{equation}
		h'_{\mu'\nu'}
		= \delta g'_{\mu'\nu'}
	\end{equation}
	I am still doing the calculations, because the metric $g'_{\mu'\nu'}$ becomes messed up after the coordinate map.

\pagebreak

	However, I have computed:
	\begin{equation}
		\var{Q}[g,\tilde{h},\xi],
	\quad\text{where we \textbf{define:}}\quad
		\tilde{h}_{\mu\nu} = h'_{\mu'\nu'}
			\pdv{x'^{\mu'}}{x^\mu}
			\pdv{x'^{\nu'}}{x^\nu}
	\end{equation}

\pagebreak[3]

	We should have:
	\begin{equation}
		\var{Q}[g,\tilde{h},\xi]
		= \var{Q}[g',h',\xi']
	\end{equation}
	Because although $\var{Q}[g,\var{g},\xi]$ is not gauge invariant, since it involves the non-tensorial $\var{g_{\mu\nu}}$, $\var{Q}[g,\tilde{h},\xi]$ \textbf{as a functional of $g,\tilde{h},\xi$ is gauge invariant}. This follows from the formula directly:
	\begin{gather}
		\d Q [g_{\mu\nu}, \tilde{h}_{\mu\nu}, \xi]
		= \int_\gamma
			\hstar k [g_{\mu\nu}, \tilde{h}_{\mu\nu}, \xi],
	\\
		k_{\mu\nu} [g_{\mu\nu}, \tilde{h}_{\mu\nu}, \xi]
		= \frac{1}{2} \pqty{
				\xi_\nu \cdv{\mu} \tilde{h}^\alpha_\alpha
				- \xi_\nu \cdv{\alpha} \tilde{h}^\alpha{}_\mu
				+ \cdots
			}
	\end{gather}
	We see that $\var{Q}[g,\tilde{h},\xi]$ is indeed a tensor, as a function of $g,\tilde{h},\xi$. \\
	\mbox{$
		\tilde{h}_{\mu\nu} = h'_{\mu'\nu'}
			\pdv{x'^{\mu'}}{x^\mu}
			\pdv{x'^{\nu'}}{x^\nu}
	$} here is a tensor, by construction. \\
	But this does \textit{not} match with the variation of the area of the RT surface.

	When computing $\var{Q}[g,h,\xi]$, basically we have imposed:
	\begin{equation}
		h_{ij}|_{\rho = \rho_c}
		= h'_{i'j'}
			\pdv{x'^{i'}}{x^i}
			\pdv{x'^{j'}}{x^j}
			\bigg|_{\rho = \rho_c}
		= 0
	\end{equation}
	\textbf{In all gauges!} This is possible, because
%	although $\var{g_{\mu\nu}}$ is not gauge invariant (not a tensor), $
%		h_{\mu\nu}
%		= \delta g_{\mu\nu}
%			+ \mathcal{L}_{\eta} \,g_{\mu\nu}
%	$ 
	$h_{\mu\nu}$ here
	is gauge invariant, \textbf{by construction.}
%	i.e.\ we choose $\eta = (\var{u},\var{v},\var{\rho})$ such that $\mathcal{L}_{\eta} \,g_{\mu\nu}$ compensates for $\delta g_{\mu\nu}$ and the whole $h_{\mu\nu}$ is a tensor. 
	This does not seem to be equivalent with our prescription, where similarly we compute $\var{Q}[g,h,\xi]$, but $
		h_{ij}|_{\rho = \rho_c} \ne 0
	$.

%	In this case, the symplectic structure $\Omega$ is explicitly constructed from $\var{g'_{\mu'\nu'}}$, by Kraus et al \cite{Kraus:2021cwf}.

\end{itemize}

\section{Things to think about}
	\begin{itemize}[nosep]
	\item Contribution of boundary terms to $\var{Q}$
	\item Variation while holding $\tilde{l}$ at $\infty$ fixed
	\end{itemize}

%%%%%%%% migrated from sect4.tex

\begin{colored}
Things to work on:
\begin{itemize}[nosep]
	\item Mixed boundary condition at $\infty$
\end{itemize}
\end{colored}

\bigskip\hrule\bigskip

In usual AdS/CFT, holographic entanglement entropy is given by the gravitational entropy \cite{Lewkowycz:2013nqa,}. Consider a family of solutions such as BTZ black holes, holographic entanglement entropy can be calculated in the covariant formalism by integrating the infinitesimal charges
\eq{
\d S_{\mrm{HEE}}
		= \d Q_{\xi} [\gamma, g_{\mu\nu}]=\int_\gamma k_\xi [h, \,g]
}
where $\xi$ is the modular flow generator, $\gamma$ is the RT surface, and $h$ is the infinitesimal variation of the metric in the phase space which is determined by the boundary conditions. For Brown--Henneaux boundary conditions which are Dirichlet boundary conditions imposed at the asymptotic boundary, $h$ is the variation with respect to phase space variables. In the cutoff AdS/$T\bar T$ picture, however, we have to be careful about how to implement the Dirichlet boundary conditions. 
At the cutoff surface $r=r_c$ \eqref{} which is defined by requiring $g_{\phi\phi}=r_c^2$, the induced metric can always be put locally flat without changing the size of the circle \eq{ ds^2|_{r=r_c}= r_c^2 d u' d v', \quad (u', v')= (u'+2\pi , v'+2\pi ). }
Let us denote the coordinate transformation as
\eq{
		x^\mu \mapsto x'^\mu,
	\quad
		g'_{\mu\nu}
		= \pdv{x^\rho}{x'^\mu}
			\pdv{x^\sigma}{x'^\nu}
			g_{\rho\sigma},}
The Dirichlet boundary condition is then given by 
\eq{\delta' g'(x')_{i'j'}|_{r=r_c} =0\label{dirichlet}}
where the variation is with respect to phase space parameters only in the locally flat coordinate system.
It is more convenient to rewrite the boundary conditions in the Ba\~nados metric \eqref{}. 
The boundary condition \eqref{dirichlet} then implies 
\eq{
		0&=\delta g'_{i'j'}(x')\big|_{r=r_c}
		=\bigg( \delta\Big(\,\pdv{x^\mu}{x'^{i'}}
			\pdv{x^\nu}{x'^{j'}}
			g_{\mu\nu}\Big)
			+ \delta x^\sigma\, \partial_\sigma
			\Big(\,\pdv{x^\mu}{x'^{i'}}
			\pdv{x^\nu}{x'^{j'}}
			g_{\mu\nu} \Big) \bigg) \bigg|_{\rho=\rho_c}
		\label{eq:variation_transform}
	}where in the second expression we have expressed everything in the Ba\~nados metric \eqref{}, 
and $\delta $ denotes variation with respect to the phase space parameters in the Ba\~nados metric:
	\begin{equation}
		\delta
		= \var{T_u} \pdv{}{T_u}
		+ \var{T_v} \pdv{}{T_v} 
	\end{equation} 
This is because the coordinate transformation depends on the phase space variables, and varying the phase space variables in the $x'$ coordinate is equivalent to varying the same variables accompanied by some additional diffeomorphisms in the $x$ coordinates.  As a result, the boundary condition written in terms of the old coordinate system should contain the second term. 
Using the Ba\~nados metric \eqref{}, 
we get the solution for the %accompanied
necessary diffeomorphism
\begin{equation}
			\var{\rho}
		= -\frac{1}{2\,(r^4 - T_u^2 T_v^2)}
			\pqty{
				r \var{(T_u^2 T_v^2)}
				+ r^3 \var{(T_u^2 + T_v^2)}
			}
	\label{eq:rho_variation}
	\end{equation}
Consequently, the total infinitesimal change of the metric satisfying the boundary condition \eqref{eq:variation_transform}  is given by
\eq{h_{\mu\nu}=\delta g_{\mu\nu}+ \mathcal{L}_{\zeta} \,g_{\mu\nu},\quad
\zeta^\mu = \delta x^\mu
= (0,0,\delta\rho)
\label{varimetric}}
where again $\delta g_{\mu\nu}$ denotes variation with respect to the phase space variables, which are $T_u$ and $T_v$ for the BTZ black holes. 
It is important not to confuse the total variation \eqref{varimetric} in the Ba\~nados metric with the boundary conditions \eqref{eq:variation_transform}.
In particular, the boundary condition \eqref{eq:variation_transform} does not imply $h_{ij}|_{r=r_c}=0$. %The former is imposed in the $x'$ coordinates at point $x'$, which can be rewritten in terms of variables  $T_u, T_v$ and coordinates $x$. On the other hand, $h_{ij}$ is directly defined in the $x$ coordinate system, and the meaning is the total infinitesimal change of  the metric due to the change of

\begin{colored}
	Note that in \eqref{eq:rho_variation} we can, in principle, include additional diffeomorphisms
	\begin{equation}
		\eta^\mu = \delta x^\mu
		= (\var{u},\var{v},\delta\rho)
	\end{equation}
	In particular, arbitrary boundary variations $\var{u},\var{v}$ can be included while the condition \eqref{eq:variation_transform} is still satisfied. However, this is physically undesirable, as it introduces unnecessary boundary diffeomorphisms. It is thus natural to set:
\end{colored}
	\begin{equation}
\begin{colored}
		\var{u} = \var{v} = 0,
	\quad
		\zeta^\mu = \delta x^\mu
		= (0,0,\delta\rho)
\end{colored}
	\end{equation}
%	In this way we inherit the symplectic structure of the original Brown--Henneaux phase space.

	By explicit calculations, we have:
	\begin{equation}
		\var{Q}_\xi[\gamma_c,g_{\mu\nu},h_{\mu\nu}]
		= \delta S[l_u,l_v;T_u,T_v],
	\quad
		\delta
		= \var{T_u} \pdv{}{T_u}
		+ \var{T_v} \pdv{}{T_v} 
	\end{equation}
	where $\gamma_c$ is the RT cutoff by the surface $\rho=\rho_c$, and $S[l_u,l_v;T_u,T_v] = \frac{A}{4G_N}$ is the entropy \eqref{eq:entropy_RT} given by the RT proposal, i.e.~the area $A$ of the RT surface. 
	In particular, for $l_u = l_v = l$ and $T_u = T_v = T$, we have:
	\begin{equation}
		\delta S^{T\bar T}_{\mrm{HEE}}=\int_{\gamma_c} k_\xi [h, \,g]
		= \delta\pqty{
				\frac{1}{2G} \mop{arcsinh}
				\frac{r_c \sinh Tl}{2T}
			}
		= \delta S[l,T]
	\end{equation}
	Thereby we have provided an alternative calculation of the holographic entanglement entropy in the cutoff AdS/$T\bar T$ correspondence based on covariant charges,  and the result agrees with the RT proposal \eqref{eq:entropy_RT}.

	\begin{equation}
		\var{Q_\xi}
		= \int_\mcal{C} \Big\{
				\delta\!\pqty{
					-\tfrac{1}{16\pi G_N}
					\sqrt{\abs{g}}\,
					\epsilon_{\mu\nu\sigma}
					\nabla^\mu \xi^\nu
					\dd{x^\sigma}
				}
				- \xi\cdot\Theta
			\Big\}
	\end{equation}

\subsection{Legacy version}

	Gravitational entropy is the Noether charge $Q_\xi$ associated with the horizon generator $\xi$ \cite{Lewkowycz:2013nqa,}. In the case of entanglement entropy between a simple interval and its complement, its corresponding modular flow in the bulk is precisely the horizon generator of the Rindler patch. We can then compute the charge variation using the covariant formula \eqref{charges}.

	Again, to compute $\var{Q}_\xi$ we need to consider a particular metric variation $\var{g}_{\mu\nu}$ in the phase space of solutions:
	\begin{equation}
		\d Q_\xi
		= \d Q_{\xi} [\d g_{\mu\nu}, g_{\mu\nu}]
	\end{equation}
	However, before plugging everything into the formula we need to address one crucial subtlety: the phase space variation $\var{g_{\mu\nu}}$ is generally, \textit{not} gauge invariant. The variation $\delta$ in general does not commute with a coordinate transformation. More explicitly, we have:
	\begin{gather}
		x^\mu \mapsto x'^\mu,
	\quad
		g'_{\mu\nu}
		= \pdv{x^\rho}{x'^\mu}
			\pdv{x^\sigma}{x'^\nu}
			g_{\rho\sigma},
	\\[1ex]
		\var{g'_{\mu\nu}}
		= \pdv{x^\rho}{x'^\mu}
			\pdv{x^\sigma}{x'^\nu}
			\var{g_{\rho\sigma}}
		+ g_{\rho\sigma} \var{\pqty{
				\pdv{x^\rho}{x'^\mu}
				\pdv{x^\sigma}{x'^\nu}
			}}
%		\label{eq:variation_transform}
	\end{gather}
	In particular, if the coordinate transformation involves some phase space variables (e.g.\ $T_u,T_v$), then the second term in \eqref{eq:variation_transform} does not vanish. In this case $\var{g_{\mu\nu}}$ does \textit{not} transform as a tensor. Therefore, the charge variation $
		\d Q_{\xi} [\d g_{\mu\nu}, g_{\mu\nu}]
	$ is not always gauge invariant.

	A more careful analysis shows that $
		\d Q_{\xi}
	$ is in fact invariant under small gauge transformations, but not invariant under \textit{large} gauge transformations that affect the boundary conditions \sidenote{[citations needed]}. 
	We did not pay much attention to gauge dependence before, and that's because when the cutoff is pushed to infinity, the asymptotic falloff is often unchanged when we compute $\var{g_{\mu\nu}}$ in usual coordinates. However, when there is a finite cutoff, this ambiguity becomes a problem, since a coordinate change can easily modify the boundary condition at the finite cutoff \cite{Guica:2019nzm,Kraus:2021cwf}.

	Before we continue, we note that it is convenient to rewrite the metric variation in terms of the variation of the length element $\dd{s}^2$: 
	\begin{equation}
	\begin{aligned}
		\var{(\dd{s}^2)}
		&= (\var{g_{\mu\nu}}) \dd{x^\mu} \dd{x^\nu}
			+ g_{\mu\nu} \var{(\dd{x^\mu})} \dd{x^\nu}
			+ g_{\mu\nu} \dd{x^\mu} \var{(\dd{x^\nu})} \\
		&\equiv \tvar{g}_{\mu\nu} \dd{x^\mu} \dd{x^\nu},
	\end{aligned}
	\end{equation}
	where the aforementioned gauge dependency is contained in the $\var{(\dd{x^\nu})} = \dd{(\var{x^\nu})}$ term, namely the coordinate is also varied. It depends on our prescription for the variation of coordinates $\var{x}$:
	\begin{equation}
		\var{(\dd{x^\sigma})}
		= \dd{(\var{x^\sigma})}
		= \pdv{\,\var{x^\sigma}}{x^\nu} \dd{x^\nu},
	\end{equation}
	The total variation $\tvar{g}_{\mu\nu}$ can thus be expanded as:
	\begin{equation}
	\begin{aligned}
		\tvar{g}_{\mu\nu}
		&= \delta g_{\mu\nu}
			+ g_{\mu\sigma}
				\pdv{\,\var{x^\sigma}}{x^\nu}
			+ g_{\nu\sigma}
				\pdv{\,\var{x^\sigma}}{x^\mu}
	\\[.3ex]
		&= \pqty{
			\delta g_{\mu\nu}\big|_{\var{x} = 0}
			+ \pdv{g_{\mu\nu}}{x^\sigma} \var{x^\sigma}
		}
			+ g_{\mu\sigma}
				\pdv{\,\var{x^\sigma}}{x^\nu}
			+ g_{\nu\sigma}
				\pdv{\,\var{x^\sigma}}{x^\mu}
	\\[.3ex]
		&= \delta g_{\mu\nu}\big|_{\var{x} = 0}
			+ \pqty{
				\pdv{g_{\mu\nu}}{x^\sigma} \var{x^\sigma}
				+ g_{\mu\sigma}
					\pdv{\,\var{x^\sigma}}{x^\nu}
				+ g_{\nu\sigma}
					\pdv{\,\var{x^\sigma}}{x^\mu}
			}
	\\[.3ex]
		&= \delta g_{\mu\nu}\big|_{\var{x} = 0}
			+ \ldv{\eta} g_{\mu\nu},
	\quad \eta^\mu = \var{x^\mu}
	\end{aligned}
	\label{eq:metric_variation}
	\end{equation}

	The term $\delta g_{\mu\nu}\big|_{\var{x} = 0}$ is the variation of the metric with respect to the phase space variable $T_u,T_v$, without considering the variation of the coordinate $\var{x^\mu} = \eta^\mu$. When restricted to the BTZ backgrounds, we have:
	\begin{equation}
		\delta g_{\mu\nu}\big|_{\var{x} = 0}
		= \pdv{g_{\mu\nu}}{T_u} \var{T_u}
			+ \pdv{g_{\mu\nu}}{T_v} \var{T_v}
	\end{equation}
	On the other hand, the Lie derivative term $\ldv{\eta} g_{\mu\nu}$ captures how the coordinates are varied, and therefore characterizes the ambiguity of gauge choices in the process.

	To resolve such ambiguity, we need to carefully specify the phase space of solutions that we are considering. 
	Recall the proposal of \cite{McGough:2016lol}, where we have a \textit{constant} radial cutoff $r_c$. Namely, the codim-1 cutoff is defined with the following equation:
	\begin{equation}
	\text{Cutoff:}\quad
		g_{\phi\phi}%|_{\rho_c}
		= r_c^2,
	\quad
		\phi = \frac{u + v}{2},
	\quad
		\phi \cong \phi + 2\pi
	\label{eq:cutoff_surface}
	\end{equation}
	This is a gauge invariant definition of the radial cutoff, as long as we choose the $\phi$ coordinate of the cutoff $S^1$ cycle to be properly normalized. Variation of the above equation gives us:
	\begin{equation}
		\var{g_{\phi\phi}} = 0,
	\end{equation}
	\begin{equation}
	\Longrightarrow\quad
		\var{\rho}
		= -\frac{1}{2\,(r^4 - T_u^2 T_v^2)}
			\pqty{
				r \var{(T_u^2 T_v^2)}
				+ r^3 \var{(T_u^2 + T_v^2)}
			}
%	\label{eq:rho_variation}
	\end{equation}
	This fixes the $\rho$ component of $\eta^\mu = \var{x^\mu}$.

%	As we switch to the Ba\~nados metric, the cutoff $\rho_c$ becomes state-dependent \eqref{eq:cutoff_relations}. 
%	On the other hand, by \eqref{eq:banados_metric} we have:
%	\begin{equation}
%	\begin{aligned}
%		\dd{s}^2_c
%		\equiv \dd{s}^2|_{\rho_c}
%		&= \pqty{\rho_c\dd{u} + \frac{T_v^2}{\rho_c}\dd{v}}
%		\pqty{\rho_c\dd{v} + \frac{T_u^2}{\rho_c}\dd{u}}
%	\\[.8ex]
%		&= T_u^2 \dd{u}^2
%			+ T_v^2 \dd{v}^2
%			+ (r_c^2 - T_u^2 - T_v^2) \dd{u} \dd{v},
%	\quad u,v = \phi\pm t,
%	\\[.8ex]
%		&= \pqty{-r_c^2 + 2\,(T_u^2 + T_v)^2} \dd{t}^2
%			+ 2\,(T_u^2 - T_v^2) \dd{t} \dd{\phi}
%			+ r_c^2 \dd{\phi}^2
%	\end{aligned}
%	\end{equation}
%	Namely, the induced metric at $\rho_c$ also involves the phase space variables $T_u,T_v$. 
%	This means that these coordinates are not so convenient for Dirichlet boundary condition at the spatial cutoff $\rho_c$. 
%	In the covariant formalism, we would like to choose the boundary condition at the spatial boundary to be independent of the phase space variables. In fact, the spatial boundary condition \textit{defines} the phase space of solutions. On the other hand, the phase space variables {are} allowed to appear in the initial and final time slice $\Sigma^\pm$, which defines a specific {state} in the phase space that we are considering. 
%	
%	One way to avoid $T_u,T_v$ dependencies at the cutoff is to switch to a special gauge that eliminates the state dependence. This is carried out in \cite{Guica:2019nzm,Kraus:2021cwf}. A more general prescription is to include the variation of coordinates, namely the $\ldv{\var{x}} g_{\mu\nu}$ term in \eqref{eq:metric_variation}. Dirichlet boundary condition at the cutoff is then given by:
%	\begin{equation}
%		\var{(\dd{s}^2)}\big|_{\,\rho = \rho_c}
%		= 0
%	\end{equation}
%	\begin{equation}
%	\text{i.e.}\ \,
%		h_{\mu\nu}|_{\rho = \rho_c}
%		= \pqty{
%				\delta g_{\mu\nu}\big
%					|_{\var{x} = 0}
%				+ \ldv{\var{x}} g_{\mu\nu}
%			}_{\!\rho = \rho_c\!\!}
%		= 0
%	\label{eq:generalized_Killing}
%	\end{equation}
%	This ``generalized'' Killing equation is solved by the following $\var{x}$ (see \autoref{app:solve_Killing}):
%	\begin{equation}
%	\begin{aligned}
%		\var{\rho}
%		&= \frac{\var{\rho_c}}{\rho_c} \rho,
%	\\[.5ex]
%		\var{u}
%%		&= \var{\pqty{
%%				\frac{r_c^2 - T_u^2 + T_v^2}{
%%					\sqrt{r_c^2 f(r_c)}
%%				}
%%			}} \frac{\sqrt{f(r_c)}}{r_c} \frac{u - v}{2}
%		&= \frac{
%			4T_v \pqty{
%				2T_u T_v \var{T_u}
%				+ \pqty{r_c^2 - (T_u^2 + T_v^2)} \var{T_v}
%			}
%		}{r_c^2 f(r_c)}
%		\frac{u - v}{2},
%	\\
%		\var{v}
%%		&= \var{\pqty{
%%				-\frac{r_c^2 + T_u^2 - T_v^2}{
%%					\sqrt{r_c^2 f(r_c)}
%%				}
%%			}} \frac{\sqrt{f(r_c)}}{r_c} \frac{u - v}{2}.
%		&= \frac{
%			-4T_u \pqty{
%				2T_u T_v \var{T_v}
%				+ \pqty{r_c^2 - (T_u^2 + T_v^2)} \var{T_u}
%			}
%		}{r_c^2 f(r_c)}
%		\frac{u - v}{2}.
%	\end{aligned}
%	\label{eq:coord_variation}
%	\end{equation}
%	Note that the variations depend only on $\rho$ and $t = \frac{u - v}{2}$, therefore it respects the $\phi$ periodicity: $\phi \cong \phi + 2\pi$.

%	Fortunately, these issues can be easily fixed by ``completing the squares'':
%	\begin{equation}
%	\begin{aligned}
%		\dd{s}^2_c
%		\equiv \dd{s}^2|_{\rho_c}
%		&= \pqty{-r_c^2 + 2\,(T_u^2 + T_v)^2} \dd{t}^2
%			+ 2\,(T_u^2 - T_v^2) \dd{t} \dd{\phi}
%			+ r_c^2 \dd{\phi}^2 \\
%		&= r_c^2 (-\dd{t'}^2 + \dd{\phi'}^2)
%	\end{aligned}
%	\end{equation}
%	Namely, we normalize the metric at the cutoff such that is a cylinder with radius $r_c$ and $\phi' \cong \phi' + 2\pi$. This can be achieved with:
%%	defining a new set of coordinates $(t',\phi',\rho')$:
%%	as we've done in Section \ref{sect:2}
%	\begin{equation}
%		\rho'
%		= \frac{r_c}{\rho_c} \rho,
%	\quad
%		\phi'
%		= \phi + \frac{T_u^2 - T_v^2}{r_c^2}\,t,
%	\quad
%		t'
%		= \frac{\sqrt{f(r_c)}}{r_c}\,t,
%	\end{equation}
%%	\begin{equation}
%%		ds^2_{c}
%%		= r_c^2 ( -dt'^2 + d\phi'^2 )
%%	\end{equation}
%	Physically this is the coordinates for a locally nonrotating observer in the orthonormal frame. The $\rho$ rescaling is necessary so that the cutoff is then fixed at $\rho' = r_c$, with no dependence of $T_u, T_v$. Dirichlet boundary condition at the cutoff is then given by:
%	\begin{equation}
%		\var{(\dd{s}^2)}|_{\rho = \rho_c}
%		= 0
%	\end{equation}
%	\begin{equation}
%	\text{i.e.}\ \,
%		\var{\rho'}
%		= \var{\phi'}
%		= \var{t'}
%		= 0
%	\end{equation}

%	Note that the primed coordinates also appear in \cite{Guica:2019nzm,Kraus:2021cwf} based on similar logic. 
%	On the other hand, we have been careful about the coordinate transformation so that the $2\pi$ periodicity is preserved along the $\phi$ circle: \mbox{$\phi \cong \phi + 2\pi$}, \mbox{$\phi' \cong \phi' + 2\pi$}.

%	In light-cone coordinates, we have:
%	\begin{equation}
%		u' = \frac{u + v}{2}
%			+ \frac{
%				T_u^2 - T_v^2 + r_c \sqrt{f(r_c)}
%			}{r_c^2} \frac{u - v}{2},
%	\quad
%		v' = \frac{u + v}{2}
%			+ \frac{
%				T_u^2 - T_v^2 - r_c \sqrt{f(r_c)}
%			}{r_c^2} \frac{u - v}{2}
%	\end{equation}
%	Note that the transformation from $(u,v,\rho)$ to $(u',v',\rho')$ is completely linear in the coordinates. We then compute $\var{g'_{\mu\nu}}$ in this new gauge, which basically defines the phase space\footnote{
%		More precisely, since we are considering infinitesimal variation $\var{g'_{\mu\nu}}$, we are considering the tangent space around a solution $g'_{\mu\nu}$ in the phase space. 
%	} we are considering. It is then straight-forward to show that the variation actually vanishes at the boundary, i.e.\ it imposes the Dirichlet boundary condition at the cutoff:
%	\begin{equation}
%		\var{g'_{\mu\nu}}|_{\rho' = r_c}
%		\equiv 0
%	\label{eq:Dirichlet_boundary}
%	\end{equation}
%	
%	For convenience, we can then define:
%	\begin{equation}
%		h'_{\mu\nu} = \var{g'_{\mu\nu}}
%	\end{equation}
%	And pull it back to the original Ba\~nados coordinates $(u,v,\rho)$, then proceed with our calculations in the old gauge.

	For now variations of the boundary coordinates $u,v$ are not yet constrained. We look at the following two possibilities:

\subsubsection{Dirichlet at finite cutoff}
\label{subsubsect:dirichlet}
	This is the prescription of \cite{Guica:2019nzm,Kraus:2021cwf}, namely we impose Dirichlet boundary condition at the finite cutoff:
	\begin{equation}
		\var{(\dd{s}^2)}\big|_{\,\rho = \rho_c}
		= 0
	\quad\Longleftrightarrow\quad
		\tvar{g_{ij}}\big|_{\,\rho = \rho_c} = 0,
	\end{equation}
	where $i,j$ labels the boundary directions $u,v$. Note that $\tvar{g_{ij}}$ and $\var{g_{ij}}$ should be interpreted as follows: we first vary the full 3-dimensional metric $g_{\mu\nu}$, and then restrict it to the boundary by setting $\mu,\nu = i,j$ and $\rho = \rho_c$. Namely\footnote{
		Note that in general the variation $\mquote{\tilde{\delta}}$ or $\mquote{\delta}$ do not commute with the restriction to the boundary: $
			( \tvar{g_{\mu\nu}} )
				_{\mu,\nu = i,j}
				|_{\rho = \rho_c}
			\not\equiv
			\tilde{\delta}\,(
				g_{ij}
				|_{\rho = \rho_c\!}
			)
		$. 
	}, 
	\begin{equation}
		\tvar{g_{ij}}\big|_{\,\rho = \rho_c}
		= \big( \tvar{g_{\mu\nu}} \big)
			_{\mu,\nu = i,j\,}
			\big|_{\,\rho = \rho_c}
	\end{equation}

	This prescription eliminates $T_u,T_v$ dependencies at the cutoff, so that there is no state dependence in the boundary condition. One way to achieve this is to switch to a special gauge $(u',v',\rho')$ where the $T_u,T_v$ dependencies drop out automatically, and the induced metric is simply $
		\dd{s^2}|_{\rho'_c}
		= r_c^2 \dd{u'} \dd{v'}
	$. This is carried out explicitly in \cite{Guica:2019nzm,Kraus:2021cwf}. 
	An alternative realization of this is to include the variation of coordinates, namely the $\ldv{\eta} g_{\mu\nu}$ term in \eqref{eq:metric_variation}. We have:
	\begin{equation}
		0 = \tvar{g_{ij}}\big|_{\,\rho = \rho_c}
		= \pqty{
				\delta g_{ij}\big
					|_{\var{x} = 0}
				+ \ldv{\eta} g_{ij}
			}_{\!\rho = \rho_c\!},
	\label{eq:generalized_Killing}
	\end{equation}
	\begin{equation}
		\eta^\mu = \var{x^\mu}
		= (\var{u},\var{v},\var{\rho}),
	\end{equation}
	Where $\var{\rho}$ is given by \eqref{eq:rho_variation}, while $(\var{u},\var{v})$ is unknown. 
	This ``generalized'' Killing equation can be solved by the following $(\var{u},\var{v})$ (see \autoref{app:solve_Killing}):
	\begin{equation}
	\begin{aligned}
		\var{u}
%		&= \var{\pqty{
%				\frac{r_c^2 - T_u^2 + T_v^2}{
%					\sqrt{r_c^2 f(r_c)}
%				}
%			}} \frac{\sqrt{f(r_c)}}{r_c} \frac{u - v}{2}
		&= \frac{
			4T_v \pqty{
				2T_u T_v \var{T_u}
				+ \pqty{r_c^2 - (T_u^2 + T_v^2)} \var{T_v}
			}
		}{r_c^2 f(r_c)}
		\frac{u - v}{2},
	\\
		\var{v}
%		&= \var{\pqty{
%				-\frac{r_c^2 + T_u^2 - T_v^2}{
%					\sqrt{r_c^2 f(r_c)}
%				}
%			}} \frac{\sqrt{f(r_c)}}{r_c} \frac{u - v}{2}.
		&= \frac{
			-4T_u \pqty{
				2T_u T_v \var{T_v}
				+ \pqty{r_c^2 - (T_u^2 + T_v^2)} \var{T_u}
			}
		}{r_c^2 f(r_c)}
		\frac{u - v}{2}.
	\end{aligned}
	\label{eq:uv_variation}
	\end{equation}
	Note that the variations depend only on $t = \frac{u - v}{2}$, therefore it respects the $\phi$ periodicity: $\phi \cong \phi + 2\pi$, and it's also compatible with the equation of the cutoff \eqref{eq:cutoff_surface}. 
	In summary, by imposing Dirichlet boundary condition at the finite cutoff, we now have:
	\begin{equation}
		\tvar{g^\mrm{D}_{\mu\nu}}
		= \delta g_{\mu\nu}\big|_{\var{x} = 0}
			+ \ldv{\eta} g_{\mu\nu},
	\quad
		\tvar{g_{ij}}\big|_{\,\rho = \rho_c}
		= 0,
	\end{equation}
	where $
		\eta^\mu = \var{x^\mu}
		= (\var{u},\var{v},\var{\rho})
	$ is given by \eqref{eq:rho_variation} and \eqref{eq:uv_variation}.

\subsubsection{Brown--Henneaux falloff at asymptotic infinity}

	Here we look at a different proposal: rather than focusing on the boundary condition at the finite cutoff, we instead examine the falloff behavior at the asymptotic infinity, and demand that it satisfies the Brown--Henneaux boundary conditions \cite{Brown:1986nw}:
	\begin{equation}
	\rho\to\infty, \qquad
	\begin{gathered}
		\tvar{g_{tt}} \sim \order{1},
	\quad
		\tvar{g_{t\phi}} \sim \order{1},
	\quad
		\tvar{g_{\phi\phi}} \sim \order{1},
	\\[1ex]
		\tvar{g_{t\rho}}
		\sim \order{\frac{1}{\rho^3}},
	\quad
		\tvar{g_{\phi\rho}}
		\sim \order{\frac{1}{\rho^3}},
	\quad
		\tvar{g_{\rho\rho}}
		\sim \order{\frac{1}{\rho^4}}.
	\end{gathered}
	\end{equation}

\pagebreak[3]

	We first note that if we fix Dirichlet boundary condition at the finite cutoff, as is done in \S\ref{subsubsect:dirichlet}, the corresponding $\tvar{g_{\mu\nu}}$ will \textit{not} satisfy the above falloff:
	\begin{equation}
		\eta^\mu = \var{x^\mu}
		= (\var{u},\var{v},\var{\rho})
	\,\ \text{as defined by \eqref{eq:rho_variation}, \eqref{eq:uv_variation}},
	\end{equation}
	\vspace*{-.8\baselineskip}
	\begin{equation}
		\tvar{g^\mrm{D}_{\mu\nu}}
		= \delta g_{\mu\nu}\big|_{\var{x} = 0}
			+ \ldv{\eta} g_{\mu\nu},
	\ \quad
	\begin{aligned}
		\tvar{g_{\phi\phi}}
		&= 0
		= \tvar{g_{t\rho}}
		= \tvar{g_{\phi\rho}},
	\\[.5ex]
		\tvar{g_{tt}}
		&\sim \order{r^2},
	\\[.5ex]
		\tvar{g_{t\phi}}
		&\sim \order{r^2},
	\\[.5ex]
		\tvar{g_{\rho\rho}}
		&\sim \order{\frac{1}{\rho^4}},
	\end{aligned}
%	\qquad
		\rho\to\infty
	\end{equation}
	On the other hand, simply setting $\var{u} = \var{v} = 0$ gives us a $\tvar{g_{\mu\nu}}$ that \textit{does} satisfy the Brown--Henneaux asymptotics. More explicitly, we have:
	\begin{equation}
		\zeta^\mu = \var{x^\mu}
		= (\var{u},\var{v},\var{\rho})
		= (0,0,\var{\rho}),
	\end{equation}
	\vspace{-.8\baselineskip}
	\begin{equation}
		\tvar{g^\mrm{BH}_{\mu\nu}}
		= \delta g_{\mu\nu}\big|_{\var{x} = 0}
			+ \ldv{\zeta} g_{\mu\nu},
	\ \quad
	\begin{aligned}
		\tvar{g_{\phi\phi}}
		&= 0
		= \tvar{g_{t\rho}}
		= \tvar{g_{\phi\rho}},
	\\[.5ex]
		\tvar{g_{tt}}
		&= 2 \var{(T_u^2 + T_v^2)}
		\sim \order{1},
	\\[.5ex]
		\tvar{g_{t\phi}}
		&= \var{(T_u^2 - T_v^2)}
		\sim \order{1},
	\\[.5ex]
		\tvar{g_{\rho\rho}}
		&= (\ldv{\zeta} g)_{\rho\rho}
		\sim \order{\frac{1}{\rho^4}},
	\end{aligned}
	\quad \rho\to\infty
	\end{equation}

	In general, let's consider:
	\begin{equation}
		\zeta'
		= \zeta + \sigma
		= (0,0,\var{\rho}) + \sigma
	\end{equation}
	Note that $
		\ldv{\zeta'} g_{\mu\nu}
		= \ldv{(\zeta + \sigma)} g_{\mu\nu}
		= \ldv{\zeta} g_{\mu\nu}
			+ \ldv{\sigma} g_{\mu\nu}
	$, therefore $
		\tvar{g_{\mu\nu}}
		= \delta g_{\mu\nu}\big|_{\var{x} = 0}
			+ \ldv{\zeta'} g_{\mu\nu}
	$ satisfies the Brown--Henneaux falloff condition if and only $
		\ldv{\sigma} g_{\mu\nu}
	$ follows the same falloff. This is precisely the asymptotic Killing equation \cite{Brown:1986nw}. The solution $\sigma$ is then given by the asymptotic Killing vectors. This means that $\zeta = (0,0,\var{\rho})$ and therefore $\tvar{g^\mrm{BH}_{\mu\nu}}$ is unique up to some shifts by asymptotic Killing vectors, which corresponds to a symmetry transformation in the phase space. \sidenote{[more discussions?]}

%	\begin{enumerate}
%	\item Simply take $\var{u} = \var{v} = 0$, thus $
%			\eta = (\var{u},\var{v},\var{\rho})
%			= (0,0,\var{\rho})
%		$;
%	\item Or alternatively, we can normalize the boundary metric to be:
%		\begin{equation}
%			\dd{s^2}|_{\rho_c}
%			= r_c^2 \dd{u'} \dd{v'}
%			= r_c^2 (\dd{\phi'}^2 - \dd{t'}^2)
%		\end{equation}
%		This can be achieved with the following coordinate transformation:
%		\begin{equation}
%		\begin{aligned}
%			u' &= \frac{u + v}{2}
%				+ \frac{
%					T_u^2 - T_v^2 + r_c \sqrt{f(r_c)}
%				}{r_c^2} \frac{u - v}{2},
%		\\
%			v' &= \frac{u + v}{2}
%				+ \frac{
%					T_u^2 - T_v^2 - r_c \sqrt{f(r_c)}
%				}{r_c^2} \frac{u - v}{2}.
%		\end{aligned}
%		\label{eq:normalized_coord}
%		\end{equation}
%		Note that this coordinate map respects the $\phi$ periodicity: $\phi' \cong \phi' + 2\pi$ and is in fact linear in $\phi = \frac{u+v}{2}$, thus it's compatible with \eqref{eq:cutoff_surface}. We then have $\eta = (\var{u},\var{v},\var{\rho})$, where:
%		\begin{equation}
%			\var{u'} = \var{v'} = 0
%		\end{equation}
%		\begin{equation}
%		\hspace{-2em}\Longrightarrow\quad
%		\begin{aligned}
%			\var{u}
%%			&= \var{\pqty{
%%					\frac{r_c^2 - T_u^2 + T_v^2}{
%%						\sqrt{r_c^2 f(r_c)}
%%					}
%%				}} \frac{\sqrt{f(r_c)}}{r_c} \frac{u - v}{2}
%			&= \frac{
%				4T_v \pqty{
%					2T_u T_v \var{T_u}
%					+ \pqty{r_c^2 - (T_u^2 + T_v^2)} \var{T_v}
%				}
%			}{r_c^2 f(r_c)}
%			\frac{u - v}{2},
%		\\
%			\var{v}
%%			&= \var{\pqty{
%%					-\frac{r_c^2 + T_u^2 - T_v^2}{
%%						\sqrt{r_c^2 f(r_c)}
%%					}
%%				}} \frac{\sqrt{f(r_c)}}{r_c} \frac{u - v}{2}.
%			&= \frac{
%				-4T_u \pqty{
%					2T_u T_v \var{T_v}
%					+ \pqty{r_c^2 - (T_u^2 + T_v^2)} \var{T_u}
%				}
%			}{r_c^2 f(r_c)}
%			\frac{u - v}{2}.
%		\end{aligned}
%		\label{eq:coord_variation}
%		\end{equation}
%	\end{enumerate}

	\hfil -----------------

	In summary, we have two different proposals for the total variation $\tvar{g_{ij}}$,
	\begin{itemize}[nosep]
	\item $\tvar{g^\mrm{D}_{ij}}$ which satisfies Dirichlet boundary condition at the finite cutoff, and:
	\item $\tvar{g^\mrm{BH}_{ij}}$ which satisfies the Brown--Henneaux falloff at the asymptotic infinity.
	\end{itemize}
	The charge variation is then given by:
	\begin{equation}
		\var{Q_\xi}
		= \var{Q_\xi}[\tvar{g_{ij}},g_{\mu\nu}]
	\end{equation}

	Explicit calculations reveal that they indeed produce different $\var{Q}$. 
	Surprisingly, only $\tvar{g^\mrm{BH}_{ij}}$ gives us the result that agrees with the RT proposal \eqref{eq:entropy_RT}. 
	In particular, for $l_u = l_v = l$ and $T_u = T_v = T$, we have:
	\begin{equation}
		\var{Q_\xi}
		= \delta\pqty{
				\frac{1}{2G} \mop{arcsinh}
				\frac{r_c \sinh Tl}{2T}
			}
	\end{equation}

%	On the other hand, following \cite{McGough:2016lol}, we can carry out a similar calculation in the Schwarzschild gauge \eqref{eq:schwarzshild} where the cutoff is constant $r_c$. In this case the boundary metric is given by:
%	\begin{equation}
%	\begin{aligned}
%		\dd{s}^2_c
%		\equiv \dd{s}^2|_{r_c}
%		&= T_u^2 \dd{u}^2
%			+ T_v^2 \dd{v}^2
%			+ (r_c^2 - T_u^2 - T_v^2) \dd{u} \dd{v},
%	\quad u,v = \phi\pm t,
%	\\[.5ex]
%		&= \pqty{-r_c^2 + 2\,(T_u^2 + T_v)^2} \dd{t}^2
%			+ 2\,(T_u^2 - T_v^2) \dd{t} \dd{\phi}
%			+ r_c^2 \dd{\phi}^2
%	\end{aligned}
%	\end{equation}
%	Again it is clearly state dependent, and the metric variation at the cutoff is non-vanishing:
%	\begin{equation}
%		\var{g_{\mu\nu}}|_{r = r_c}
%		\not\equiv 0,
%	\ \,
%		\text{in Schwarzschild gauge \eqref{eq:schwarzshild}}
%	\end{equation}
%	So it is not obvious that the cutoff covariant charge computed in the Schwarzschild gauge should agree with the previous case, where the Dirichlet boundary condition \eqref{eq:Dirichlet_boundary} is imposed. However, for $l_u = l_v = l$ and $T_u = T_v = T$, we do recover the same result from charge variation:
%	\begin{equation}
%		\var{Q_\xi}
%		= \delta\pqty{
%				\frac{1}{2G} \mop{arcsinh}
%				\frac{r_c \sinh Tl}{2T}
%			}
%	\end{equation}
%	\sidenote{How should we understand this? Why does the Schwarzschild gauge ``just works''? In \cite{Guica:2019nzm} they demonstrate that the states are indeed in one to one correspondence between the two gauges, but here the charge variation seems to be different: at the cutoff, $\var{g_{\mu\nu}}$ vanishes in one case while the other one doesn't. If both are correct there should be a way to understand this.}
%	
%	\sidenote{Another possibility: for $l_u \ne l_v$ the charge variation from the $(u',v',\rho')$ gauge and the Schwarzschild gauge do \textit{not} obviously agree with each other. Maybe there are some coincidence happening for the $l_u = l_v = l$ case.}

\pagebreak

\appendix
\section{Solving the generalized Killing equation}
\label{app:solve_Killing}
	Here we try to find a solution for \eqref{eq:generalized_Killing} in the Fefferman--Graham coordinates. 
%	
%	Firstly, $h_{\rho\rho}|_{\rho_c} = 0$ gives us:
%	\begin{equation}
%		\pdv{\,\var{\rho}}{\rho}\bigg|_{\rho_c}
%		= \frac{\var{\rho}}{\rho}\bigg|_{\rho_c}
%	\end{equation}
%	This is solved in terms of $\rho$ expansion by:
%	\begin{equation}
%		\var{\rho} = c(u,v)
%			+ \frac{\var{\rho_c}}{\rho_c} \rho
%			+ \order{\rho^2}
%	\end{equation}
%	Here $c(u,v)$ is some arbitrary function independent of $\rho$. 
%	Note that the solution is far from unique. This reflects the huge amount of gauge redundancy in the theory. For simplicity, we shall take:
%	\begin{equation}
%		\var{\rho}
%		= \frac{\var{\rho_c}}{\rho_c} \rho
%%		= \rho \var{\log \rho_c}
%	\end{equation}
%	
	Note that $\tvar{g_{ij}}|_{\,\rho_c} = 0$ only involves $
		\pdd{i}\var{x^j}|_{\,\rho_c}
	$, where the $i,j$ indices label the boundary $u,v$ directions. 
	Therefore we can consistently impose:
	\begin{equation}
		\pdd{\rho}\var{u}%|_{\,\rho_c}
		= \pdd{\rho}\var{v}%|_{\,\rho_c}
		= 0,
	\end{equation}
	\begin{equation}
	\text{i.e.}\ \,
		\var{u} = \var{u}(u,v),
	\quad
		\var{v} = \var{v}(u,v)
	\end{equation}
	This means that the variations along the boundary directions $\var{u}, \var{v}$ do not depend on the radial direction $\rho$. This is a physically natural choice. Note that the solution is far from unique, which reflects the gauge redundancies and residual symmetries of the theory.

	Due to $\tvar{g_{ij}} = \tvar{g_{ji}}$, there are 3 independent equations. These equations involve linear combinations of:
	\begin{equation}
		\pdd{u}\var{u}%|_{\rho_c},
		,\ \pdd{v}\var{u}%|_{\rho_c},
		,\ \pdd{u}\var{v}%|_{\rho_c},
		,\ \pdd{v}\var{v}%|_{\rho_c}
	\end{equation}
	And therefore they can be solved by:
	\begin{equation}
	\begin{aligned}
		\var{u}(u,v) &= a_{uu} u + a_{uv} v \\
		\var{v}(u,v) &= a_{vu} u + a_{vv} v
	\end{aligned}
	\end{equation}

	There are 3 equations and 4 variables, so the system is under constrained. However, before continuing, we note that $\phi = \frac{u + v}{2}$ is defined mod $2\pi$, i.e.~$\phi \cong \phi + 2\pi$. $\var{u}(u,v),\var{v}(u,v)$ should also respect such periodicity along the $\phi = \frac{u + v}{2}$ direction. The only way to achieve at the linear order is by:
	\begin{equation}
	\begin{aligned}
		\var{u}(u,v) &= a_u\,\frac{u - v}{2},\ %
			& a_u &= a_{uu} = -a_{uv} \\
		\var{v}(u,v) &= a_v\,\frac{u - v}{2},
			& a_v &= a_{vu} = -a_{vv}
	\end{aligned}
	\end{equation}
	Plug this back to $
		h_{\mu\nu}|_{\rho_c}
		= 0
	$, and we have 3 equations with 2 unknowns. It seems that now the system is over constrained. However, only 2 of the 3 equations are linearly independent, and we have a unique solution:
	\begin{equation}
	\begin{aligned}
		a_u &= \frac{
			4T_v \pqty{
				2T_u T_v \var{T_u}
				+ \pqty{r_c^2 - (T_u^2 + T_v^2)} \var{T_v}
			}
		}{r_c^2 f(r_c)}
	\\[1ex]
		a_v &= \frac{
			-4T_u \pqty{
				2T_u T_v \var{T_v}
				+ \pqty{r_c^2 - (T_u^2 + T_v^2)} \var{T_u}
			}
		}{r_c^2 f(r_c)}
	\end{aligned}
	\end{equation}

%\pagebreak
\vspace{\baselineskip}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{JHEP} 
\bibliography{cutoff.bib}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2021-08-07 alpha/CelestialHolography/celestial.tex
Add comments on string partition function & more
Add minor updates to various notes

@@
 \subsection{\textsl{What} is the celestial sphere?}
-	The celestial sphere, \textit{天球}, is a basic concept in astronomy.
+	The celestial sphere, \textkai{天球}, is a basic concept in astronomy.
 According to \href{https://en.wikipedia.org/wiki/Celestial_sphere}{\textsl{Wikipedia}}, the celestial sphere is an abstract sphere that has an arbitrarily large radius and is concentric to the observer.
@@
 
-	\textsl{We will primarily work in \textbf{4D}, where the celestial spheres are \textbf{2-spheres}}, $CS^\pm \ni (z,\bar{z})$. 
+	\textsl{We will primarily work in \textbf{4D}, where the celestial spheres} $CS^\pm \simeq S^2 \ni (z,\bar{z})$. 
 	\begin{equation}
@@
 	\begin{equation}
+	\arraycolsep=.25em
+	\begin{array}{ccccccccc}
 		F(u,z,\bar{z})|_{\mscr{I}^+\to i^0}
-		= F(u\to -\infty,z,\bar{z})
-		\equiv F(z,\bar{z})
-		= F(v\to +\infty,z,\bar{z})
-		= F(v,z,\bar{z})|_{\mscr{I}^-\to i^0}
+		&=& F(u\to -\infty,z,\bar{z})
+		&\equiv& F(z,\bar{z})
+		&=& F(v\to +\infty,z,\bar{z})
+		&=& F(v,z,\bar{z})|_{\mscr{I}^-\to i^0}
+	\end{array}
 	\end{equation}
@@
 
-		One can implement the \textbf{Euclidean holography} $\mrm{EAdS}_3/\mrm{CFT}_2$ in the red patch, along \textbf{a specific time slice} of the causal future \cite{deBoer:2003vf,Ball:2019atb}. 
+		One can implement the \textbf{Euclidean holography} $\mrm{EAdS}_3/\mrm{CFT}_2$ in the red patches, along \textbf{a specific time slice} of the causal future \cite{deBoer:2003vf,Ball:2019atb}. 
 		On the other hand, in the blue Rindler patches we can apply Lorentzian $\mrm{dS}_3/\mrm{CFT}_2$.
@@
 	\item Also \textcite{Witten:2001kn},
-	\item And Maldacena's comments \textcite{Maldacena:2002vr}. 
+	\item And Maldacena's comments: \citefield{Maldacena:2002vr}[eprint:arxivid]{eprint}~\cite{Maldacena:2002vr}. 
 	\end{itemize}
@@
 	\centering
-	\includegraphics[width=.7\linewidth]{img/IRtriangle.pdf}
+	\includegraphics[width=.85\linewidth]{img/IRtriangle.pdf}
 	\caption[The universal IR triangle]{
@@
 	\end{equation}
-	e.g.~In asymptotically flat 4D gravity, if we restrict to Lorentz plus ``small translations'', we obtain $\mrm{BMS}_4 = \mrm{BMS}^+ \times \mrm{BMS}^- \supset \mrm{Poincar\'e}$, i.e.~it is \textbf{$\infty$-ly larger} than the isometry of Minkowski!
+	e.g.~In asymptotically flat 4D gravity, if we restrict to Lorentz plus ``small translations'', we obtain $\mrm{BMS}_4 = \mrm{BMS}^+ \times \mrm{BMS}^- \supset \text{Poincar\'e}$, i.e.~it is \textbf{$\infty$-ly larger} than the isometry of Minkowski!
 
@@
 	\begin{center}
-	\includegraphics[width=.635\linewidth]{img/ASGflat.pdf}
+	\includegraphics[width=.85\linewidth]{img/ASGflat.pdf}
 	\end{center}

### 2021-08-07 alpha/SUSY/susy.tex
Add minor updates to various notes

@@
 % !TeX spellcheck = en_US
+% !TeX TS-program = pdflatex
 % !TeX TXS-program:bibliography = biber -l zh__pinyin --output-safechars %
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%% NOTE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% Please do not touch the file `preamble.tex`
+% ... which is auto-generated,
+% ... and your changes might be OVERWRITTEN
+% ... in later builds.
+%
+% Feel free to modify this file
+% ... in any way you want!
+%
+% Bryan
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%% END of NOTE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \title{Understanding Supersymmetry}
+\author{The Superfilm Club, Summer 2021 @ \textkai{近春园}}
 \addbibresource{susy.bib}
-
-%%% ID: sensitive, do NOT publish!
-\InputIfFileExists{id.tex}{}{}
 
@@
 \makeatother
+
+\newcommand{\speaker}[1]{\noindent\textbf{Speaker:} #1}
+\newcommand{\references}[1]{\noindent\textbf{References:} #1}
+
+\let\narrowbar\bar
+\newcommand{\thinbar}[1]{\narrowbar{#1}}
+\renewcommand{\bar}[1]{\narrowbar{#1}}
+
+\let\widebar\overline
+\newcommand{\wbar}[1]{\widebar{#1}}
+
+\def\vev#1{\ave{#1}}
 
@@
 
+This is a note for our recreational journal club on supersymmetry (SUSY).
+It is not meant to be self-contained; rather it's aimed to be an outline and a supplement for the main references listed below.
+We try not to repeat the main references too much, but to document our new understandings and additional references on relevant subjects.
+
 \setlength{\parskip}{.1\baselineskip}
@@
 \addtocounter{section}{-1}
-\section{References}
+\section{Main References}
 \raggedright
 \begin{itemize}
-	\item \cite{Atanasov:2017abc}~\fullcite{Atanasov:2017abc}
+\item Primary:
+	\begin{itemize}[itemsep=\parskip]%[leftmargin=2em]
+	\item[\cite{Argyres:1996abc}]\fullcite{Argyres:1996abc}
+		\par \textit{Recommended by Yanyan.}
+
+	\item[\cite{Tachikawa:2018sae}]\fullcite{Tachikawa:2018sae}
+		\par \textit{Recommended by Chi-Ming.}
+
+	\item[\cite{Figueroa-OFarrill:2001xbd}]\fullcite{Figueroa-OFarrill:2001xbd}
+		\par \textit{Recommended by Mauricio.}
+
+	\item[\cite{VanProeyen:1999ni}]\fullcite{VanProeyen:1999ni}
+		\par \textit{Recommended by Mauricio.}
+
+	\end{itemize}
+\pagebreak[3]
+\item Secondary:
 	\begin{itemize}
-		\item \textbf{Appendix E} of: \par
-		\cite{Belavin:1984vu}~\fullcite{Belavin:1984vu}.
+	\item[\cite{Freedman:2012zz}]\fullcite{Freedman:2012zz}
 
-		\item \textbf{Section \Romannum{4}} of: \par
-		\cite{Kogut:1979wt}~\fullcite{Kogut:1979wt}.
+	\item[\cite{Wess:1992cp}]\fullcite{Wess:1992cp}
 
-		\item \textbf{Chapter 5} of:\par
-		\cite{Fradkin:1991nr}~\fullcite{Fradkin:1991nr}.
+	\item[\cite{Hori:2003ic}]\fullcite{Hori:2003ic}
+
+	\item[\cite{figueroa2015majorana}]\fullcite{figueroa2015majorana}
+
+	\item[\cite{Zhou:2018abc}]\fullcite{Zhou:2018abc}
+
+	\item[\cite{Kapranov:2015nft}]\fullcite{Kapranov:2015nft}
+		\par \textit{Recommended by Yuan.}
 
@@
 \section{Algebra \& Unitary Representations}
+	\speaker{Yanyan ``Handsome'' Li}\\
+	\references{
+	\begin{enumerate}[noitemsep,topsep=0pt]
+	\item \textcite{Argyres:1996abc}, Section 5
+	\item \textcite{Wess:1992cp}, Chapter II
+	\end{enumerate}
+	}\vspace{.5\baselineskip}
+
+	The generic form of a 4D SUSY algebra with centeral charge is given by \cite{Wess:1992cp}:
+	\begin{equation}
+		\{ Q^i_\alpha, \bar{Q}_{\dot{\alpha},j} \}
+		= 2\sigma^\mu_{\alpha\dot{\alpha}} P_\mu
+			\delta^i_j,
+	\quad
+		\{ Q^i_\alpha, Q^j_{\beta} \}
+		= 2\epsilon_{\alpha\beta} Z^{ij}
+	\end{equation}
+	Here $i,j$ labels $\mcal{N}$ ``flavors'' of SUSY.
+For minimal SUSY we have $\mcal{N} = 1$, and we can drop the $i,j$ indices.
+Also $Z^{ij} = -Z^{ji}$, so there is no central extension when $\mcal{N} = 1$.
+
+	$Q$ is understood as the ``square root'' of $P$. 
+	Note that it's been a fine tradition\footnote{
+		\textkai{优良传统}.
+	} of physicists (and experimental mathematicians) to take the square root of un-rootable things.
+For example, $\sqrt{-1}$ gives us $i$, and $\sqrt{\Box^2} = \sqrt{-P_u P^\mu}$ gives us the $\gamma$ matrices (thanks to Dirac).
+
+	Remarks:
+	\begin{enumerate}
+	\item $Q$ carries a spinor index $\alpha$ (or $\dot{\alpha}$), so it lives in the spinor representation of the Lorentz group, or equivalently, the fundamental representation of the Spin group\footnote{
+		See a surprisingly good summary of the topic on \wikiref{https://en.wikipedia.org/wiki/Representation\_theory\_of\_the\_Lorentz\_group\#Finite-dimensional\_representations}{Representation theory of the Lorentz group \# Finite-dimensional representations}.
+	}.
+
+	\item The structure of this algebra can be generalized to $D$ dimensions. $(Q_\alpha, \bar{Q}_{\dot{\alpha}})$ forms a \mbox{(symplectic)}\footnote{
+		This happens when the metric signature $p - q \equiv 3,4,5\,\mop{mod}\,8$.
+See e.g.~\textcite{figueroa2015majorana}, or Section~3.3 and 12.1 of \textit{Supergravity} \cite{Freedman:2012zz}, or Mauricio Romo's lecture notes.
+In Lorentzian signature ($p = D-1, q = 1$), this corresponds to $D = 5,6,7$ dimensions; see e.g.~Table B.1 of \textcite{Polchinski:1998rq}.
+A worked example in 6D is given by \cite{Gustavsson:2001uw}.
+Also, higher form centeral charges are possible in higher dimensions.
+	} (pseudo)\footnote{
+		Pseudo-Majorana spinors exist for spacetime signature $(p,q)$ if and only if Majorana spinors exist for $(q,p)$.
+See \textcite{figueroa2015majorana} and Section~3.3 of \textit{Supergravity} \cite{Freedman:2012zz}
+	} Majorana spinor, where $\bar{Q}$ denotes charge conjugation \cite{Freedman:2012zz}.
+
+	\item $(Q_\alpha, \bar{Q}_{\dot{\alpha}})$ act like (fermionic) annilation and creation operators (ladder operators).
+We can write down its unitary irreducible representations (unitary irreps) on the Hilbert space, following Wigner's little group representation for the Poincar\'e group.
+	\end{enumerate}
+\subsection{Equal amount of bosonic \& fermionic (excited) states}
+	$Q$ maps bosonic states to fermionic states, and vice versa. We thus have:
+	\begin{equation}
+		(-1)^F Q = - Q\,(-1)^F
+	\label{eq:fermion_number_sign}
+	\end{equation}
+	$F$ is the fermion number operator. $(-1)^F$ can be explicitly constructed from a $2\pi$ rotation \cite{Argyres:1996abc,Witten:1982df}: \mbox{$
+		(-1)^F = e^{2\pi i J_z}
+	$}. This follows from the fact that spin-$\frac{1}{2}$ objects gain a $(-1)$ factor under a $2\pi$ rotation.
+
+	On the other hand, recall that $Q$ acts as a ladder operator, therefore:
+	\begin{equation}
+		F Q = Q\,(F \pm 1),
+	\quad\text{i.e.}\quad
+		[F, Q] = \pm Q
+	\label{eq:fermion_number_R_symmetry}
+	\end{equation}
+	The \mquote{+} sign corresponds to $\bar{Q}_{\dot{\alpha}}$, while the \mquote{-} sign corresponds to $Q_\alpha$. 
+	\eqref{eq:fermion_number_sign} can thus be understood as the exponential of \eqref{eq:fermion_number_R_symmetry}, i.e.\ $(-1)^F = e^{i\pi F} = e^{-i\pi F}$,
+	\begin{equation}
+		(-1)^F Q\,(-1)^F
+		= e^{i\pi F} Q\,e^{-i\pi F}
+		= e^{\pm i\pi} Q
+		= -Q
+	\end{equation}
+
+	There is more story behind \eqref{eq:fermion_number_R_symmetry}; in fact, $F$ generates an automorphism of the SUSY algebra.
+It is part of the \textit{R-symmetry}, and can be added to the algebra as an extension.
+	In Lorentzian 4D, the maximal amount of R-symmetry\footnote{
+		This comes from the maximal extension of the SUSY algebra. It is common that, given a specific theory, only some of the R-symmetries are preserved, while others are broken. 
+	} is $\mrm{U}(\mcal{N})$, and $F$ is the generator of the $\mrm{U}(1)_V$ subgroup; here the \mbox{subscript V} stands for ``vector'', meaning that the supercharge $Q^i$ transforms as a vector with index $i$ under the $\mrm{U}(1)_V$ action: all components labeled by $i$ gains the same phase shift under $\mrm{U}(1)$.
+
+	\newparagraph
+	Using \eqref{eq:fermion_number_sign} along with a bit of algebra \cite{Wess:1992cp}, we find that:
+	\begin{equation}
+		0 = \Tr \pqty\Big{
+			(-1)^F
+			\{ Q^i_\alpha, \bar{Q}_{\dot{\alpha},j} \}
+		}
+		= 2\sigma^\mu_{\alpha\dot{\alpha}} \delta^i_j
+			\Tr \pqty\Big{
+			(-1)^F P_\mu
+		}
+	\end{equation}
+	This implies that for fixed $P_\mu \ne 0$ we have:
+	\begin{equation}
+		\Tr_P (-1)^F = 0,
+	\quad
+		\mcal{H}_P = \Bqty\big{ \ket{P_\mu} }
+	\end{equation}
+
+	This means that we have equal amount of bosonic \& fermionic (excited) states at each energy level in a SUSY theory. 
+	Note that for ground states $P_\mu = 0$, we don't necessary have $\Tr_0 (-1)^F = 0$. In fact, this is precisely the \textit{Witten index} \cite{Witten:1982df}:
+	\begin{equation}
+		\Tr\,(-1)^F e^{-\beta H}
+	\end{equation}
+	Here the trace goes over the entire Hilbert space, but only the zero energy ground states actually contribute, since excited states are all paired up and canceled.
+The $e^{-\beta H}$ factor can be understood as regularization, and the final answer should simply be $\Tr\,(-1)^F = \Tr_0 (-1)^F$ with no $\beta$ dependence.
+In fact, it's also robust under small deformations of the theory, i.e.\ it's a \textit{topological invariant} of the theory.
+
+	\begin{itemize}
+	\item If one finds that $\Tr\,(-1)^F \ne 0$, that means there is at least one zero energy ground state, namely, SUSY is unbroken.
+
+	\item On the other hand, if SUSY is spontaneously broken, then there are no zero energy ground states, so $\Tr\,(-1)^F = 0 - 0 = 0$.
+
+	\item It's also possible to have $\Tr\,(-1)^F = 0$ while SUSY is unbroken, namely the ground states also pair up exactly: $N_B = N_F$.
+However, practically speaking, SUSY is broken, since if not, an arbitrarily small perturbation by a relevant operator will give energy to the ground state, thus breaking SUSY \cite{Argyres:1996abc}.
+	\end{itemize}
+
+\subsection{Witten index \& elliptic genus}
+
+	The Witten index can actually be understood as the index of an operator \cite{Witten:1982df}. We may split the Hilbert space $\mcal{H}$ of our theory into bosonic and fermionic subspaces:
+	\begin{equation}
+		\mcal{H} = \mcal{H}_B \oplus \mcal{H}_F,
+	\end{equation}
+	\vspace{-\baselineskip}
+	\begin{equation}
+		Q(\mcal{H}_B) \equiv \mcal{Q(}\mcal{H}_F),
+	\quad
+		Q(\mcal{H}_F) \equiv \mcal{Q}^\dagger(\mcal{H}_B),
+	\end{equation}
+	Here we've used the self-adjoint Majorana super charge $Q$, which decomposes into:
+	\begin{equation}
+		\mcal{Q}\colon \mcal{H}_B \longto \mcal{H}_F,
+	\quad
+		\mcal{Q}^\dagger\colon \mcal{H}_F \longto \mcal{H}_B,
+	\end{equation}
+
+	Zero energy bosonic states are zero-modes of $M$, while zero energy fermionic states are zero-modes of $M^\dagger$. We see that the Witten index is precisely the index of $M$:
+	\begin{equation}
+		\Tr\,(-1)^F
+		= N_B - N_F
+		= \dim \ker \mcal{Q} - \dim \ker \mcal{Q}^\dagger
+	\end{equation}
+	For more on this, check out the first few sections of the original paper: \textcite{Witten:1982df}.
+
+	\newparagraph
+	A more refined invariant in 2D that involves only the left-moving (or right-moving) part of theory is the \textit{elliptic genus}.
+For 2D $\mcal{N} = (2,2)$ superconformal theory (SCFT), the fermion number:
+	\begin{equation}
+		F = F_V = J_0 + \bar{J}_0
+	\end{equation}
+	Here $J(z),\bar{J}(\bar{z})$ are bosonic currents.
+They can be understood as the infinite dimensional enhancement of the R-symmetry generators in an SCFT, while their 0-modes $J_0,\bar{J}_0$ corresponds to the original R-symmetry generators in the SUSY algebra.
+$F_V = J_0 + \bar{J}_0$ is the $\mrm{U}(1)_V$ generator, while $F_A = \bar{J}_0 - J_0$ is the $\mrm{U}(1)_A$ generator.
+The \mbox{subscript A} stands for ``axial'', meaning that $Q^i$ transforms in an axial representation of $\mrm{U}(1)$.
+For more on this, see e.g.~\cite{MauricioStuff}.
+
+	We can now define the elliptic genus, which looks just like the Witten index but with an additional insertion $y^{J_0}$, while the trace is restricted to the R-R sector:
+	\begin{equation}
+		\mrm{EG}(\tau,z)
+		= \Tr_{\text{R-R}} \pqty{
+			(-1)^{J_0 + \bar{J}_0}
+			y^{J_0}
+			q^{L_0 - \frac{c}{24}}
+			\bar{q}^{\bar{L}_0 - \frac{c}{24}}
+		}, \quad y = e^{2\pi i z}
+	\end{equation}
+	Here R-R stands for Ramond-Ramond, i.e.\ left and right-moving states both with periodic boundary conditions along the spatial cycle\footnote{
+		In the path integral formalism, the thermal circle is also periodic due to the $(-1)^F$ insertion. 
+	}. 
+	For a review on this, see e.g.~\cite{Anagiannis:2018jqf}.
+
+	$z$ is understood as the chemical potential associated with the charge $J_0$.
+Note that there is no $\bar{\tau}$ dependence in EG, for the same resaon that there is no $\beta$ dependence in the Witten index.
+Also the elliptic genus gets reduced to the Witten index when we take $z = 0$, and in this case the $\tau,\bar{\tau}$ dependences all drop out; here we note that although we often trace over the entire R-R sector for the Witten index, only the supersymmetric R-R ground states actually contributes.
+
+	On the other hand, for general $z$ the elliptic genus counts states that are R ground state on the one side, but includes R excited states on the other side. 
+	It contains a lot more information but still has the rigidity property of the Witten index which makes it possible to compute for many SCFTs, and as such it offers a good balance between information content and computability.
+
+	Geometrically, the elliptic genus is a generalization of the usual genus.
+In particular, for $z = 0$ we recover the Witten index, which evalutates to the Euler characteristic $\chi(M)$, where $M$ is the \textit{target} manifold\footnote{
+		See Chapter 10.4 of \textit{Mirror Symmetry} \cite{Hori:2003ic}, or \textcite{Witten:1982df}. See also \cite{MauricioStuff} and:
+		\begin{itemize}[
+			topsep=.5ex,noitemsep,
+			leftmargin=4em
+		]
+		\item \https{physicsoverflow.org/23261}
+		\item \https{physics.stackexchange.com/a/183620}
+		\end{itemize}
+		\vspace{-.8\baselineskip}
+	}.
+This is due to the fact that $Q$ gets identified with the de Rham differential $\mquote{\dd}$ on the target $M$.
+This should become apparent as we introduce the superfield formalism and K\"ahler geometry in \S2.
+
+\subsection{Representations of the SUSY algebra}
+	We've noted that $(Q_\alpha, \bar{Q}_{\dot{\alpha}})$ act like ladder operators, therefore we can construct a highest weight representation starting from some \textit{Clifford vacuum} $\ket{\Omega}$ that is annihilated by $Q_\alpha,\alpha = 1,2$, and also $J_z$, which is the angular momentum along the $z$ direction.
+
+	Note that $\ket{\Omega}$ is only a highest weight state in a representation of the $\{Q,Q\}$ subalgebra, defined in the \textit{comoving frame} of a particle; it is not the Poincar\'e invariant vacuum $\ket{0}$ that we usually talk about in QFT.
+
+	For 4D $\mcal{N} = 1$, suppose $\ket{\Omega}$ has spin $j$, namely $J_z \ket{\Omega} = j\ket{\Omega}$, then we have:
+	\begin{itemize}[leftmargin=0pt,itemindent=*]
+	\item \textbf{Massive representation:}
+		\begin{equation}
+			\ket{\Omega},
+			\ \bar{Q}_{\dot{\alpha}=1,2}
+				\ket{\Omega},
+			\ \bar{Q}_{\dot{1}}\bar{Q}_{\dot{2}}
+				\ket{\Omega}
+		\end{equation}
+		i.e.~a $1+2+1 = 4$ dimensional representation of the $\{Q,Q\}$ subalgebra. 
+		Note that this is \textit{not} yet invariant under the little group $\mrm{Spin}(3) \supset \mrm{SO}(3)$.
+For that we need to include the $\mrm{Spin}(3)$ descendents by acting on the angular momentum lowering operator $J_-$.
+	\end{itemize}
+
+	Before actually doing that, let's first look at the spin of these states. 
+	The $J_z$ eigenvalue for these states can be read out from the $[J_z,\bar{Q}_{\dot{\alpha}}]$ commutator.
+Recall that $\bar{Q}_{\dot{\alpha}}$ itself carries a spinor index $\dot{\alpha}$, namely it also lives in a representation of the Lorentz group!
+	The result is that\footnote{
+		See Mauricio Romo's lecture notes, and also \cite{Terning:2006bq}. 
+	} $\bar{Q}_{\dot{\alpha}=1,2} \ket{\Omega}$ will be a $\mrm{Spin}(3)$ highest weight state of $J_z$ eigenvalue $j \pm \frac{1}{2}$,
+	\begin{equation}
+		J_z\,\pqty\Big{
+			\idty,
+			\ \bar{Q}_{\dot{\alpha}=1,2},
+			\ \bar{Q}_{\dot{1}}\bar{Q}_{\dot{2}}
+		} \ket{\Omega} = \pqty\Big{
+			j,\ j\pm\tfrac{1}{2},\ j
+		} \ket{\Omega}
+	\end{equation}
+
+	\begin{itemize}[label=--]
+	\item \textbf{Chiral multiplet} $\{\phi,\psi_\alpha\}$: for $j = 0$, the $\pm\frac{1}{2}$ states actually combine to live in a \textit{single} $\mrm{Spin}(3)$ fundamental representation, denoted as $\frac{1}{2}$.
+	In terms of field content, we have 1 Weyl spinor $\psi_\alpha$ and 2 real scalars $\phi_{1,2}$, which can be combined into 1 complex scalar $\phi$. These are ``quarks'' and ``squarks''.
+
+	\item \textbf{Vector multiplet} $
+		\{\phi',\psi_\alpha,\lambda_\alpha,A'_\mu\}
+	$: for $j = \frac{1}{2}$, the $j\pm\frac{1}{2} = 0,1$ states and their $\mrm{Spin}(3)$ descendents live in a $0\oplus 1$ representation of $\mrm{Spin}(3)$. 
+	In terms of field content, we have 1 \textit{real} scalars $\phi'$, 1 massive vector $A'_\mu$, and 2 Weyl spinors $\psi_\alpha, \lambda_\alpha$. 
+	\end{itemize}
+
+	In general, the $j \pm \frac{1}{2}$ states and their $\mrm{Spin}(3)$ descendents live in a $
+		\pqty{j - \frac{1}{2}}
+		\oplus
+		\pqty{j + \frac{1}{2}}
+	$ representation of $\mrm{Spin}(3)$. We can check that the degrees of freedom indeed match:
+	\begin{equation}
+	\begin{array}{ccccc}
+		\Bqty\Big{
+			(J_-)^k\,
+			\bar{Q}_{\dot{\alpha}=1,2}
+			\ket{\Omega}
+		}_{k\,\le\,2j+1}
+		&=& \pqty{j - \tfrac{1}{2}}
+			&\oplus&
+			\pqty{j + \tfrac{1}{2}}
+	\\[2ex]
+		2\times (2j+1)
+		&=& 2\,(j-\tfrac{1}{2}) + 1
+			&+&
+			2\,(j+\tfrac{1}{2}) + 1
+	\end{array}
+	\end{equation}
+	Here $J_-$ is the $\mrm{Spin}(3)$ lowering operator. 
+	Namely, including the $\mrm{Spin}(3)$ descendents, the dimension of the $\mrm{super} \times \mrm{Spin}(3)$ representation is thus $4\times (2j+1)$. 
+	Note that for $j = 0$ the situation is special; in that case we simply have:
+	\begin{equation}
+	\begin{array}{ccccc}
+		\Bqty\Big{
+			\bar{Q}_{\dot{1}} \ket{\Omega},
+			\ \bar{Q}_{\dot{2}} \ket{\Omega}
+			\propto J_-\,
+				\bar{Q}_{\dot{1}} \ket{\Omega}
+		} 
+		&=& \pqty{\tfrac{1}{2}}
+	\\[2ex]
+		2\times (2\times 0+1)
+		&=& 2\,(\tfrac{1}{2}) + 1
+	\end{array}
+	\end{equation}
+
+	\begin{itemize}[leftmargin=0pt,itemindent=*]
+	\item \textbf{Massless representation:}
+		\begin{equation}
+			\ket{\Omega},
+			\ \bar{Q}_{\dot{\alpha}=1} \ket{\Omega}
+		\end{equation}
+		i.e.~a $1+1 = 2$ dimensional representation of the $\{Q,Q\}$ subalgebra.
+They have helicity $\lambda,\lambda + \frac{1}{2}$.
+Combined with their CPT conjugates, we have 4 states with helicity: $\pm\lambda,\pm\pqty{\lambda + \frac{1}{2}}$.
+	\end{itemize}
+
+	\begin{itemize}[label=--]
+	\item \textbf{Chiral multiplet} $\{\phi, \psi_\alpha\}$: for $\lambda = 0$, we have 2 real scalars $\phi_{1,2}$ (or 1 complex scalar $\phi$) and 1 Weyl spinor $\psi_\alpha$.
+Note that the field content is precisely the same as the massive chiral multiplet.
+
+	\item \textbf{Vector multiplet} $\{\lambda_\alpha, A_\mu\}$: for $\lambda = \frac{1}{2}$, we have 1 massless vector $A_\mu$ and 1 Weyl spinor $\lambda_\alpha$.
+These are gauge bosons and ``gauginos''.
+Note that this multiplet is significantly ``smaller'' than the massive vector multiplet.
+	\end{itemize}
+
+	Starting with higher spin Clifford vacua results in multiplets with spins higher than 1.
+This is undesirable for \textit{massless} particles in non-gravitational theories, due to \textit{Weinberg--Witten}\footnote{
+		See e.g.\ \https{physics.stackexchange.com/a/15164}. 
+	}.
+
+	Also, the multiplets grow large if we have extended SUSY, and the massless representation contains states with helicity $\lambda,\cdots,\lambda + \frac{\mcal{N}}{2}$ \cite{Terning:2006bq}.
+
+	\begin{itemize}
+	\item \textbf{16 supercharges without gravity:} $\abs{\lambda} \le 1$, $\abs{\lambda + \frac{\mcal{N}}{2}} \le 1$, which give us $\mcal{N} = 4$ in 4D. There are in total 16 supercharges: $
+		\{ Q^i_\alpha, \bar{Q}_{\dot{\alpha},j} \}_{i,j = 1,\cdots 4}
+	$. In fact 16 is the maximal amount of SUSY in \textit{any} dimension, if we want spin $\le 1$.
+
+	\item \textbf{32 supercharges with gravity:} $\abs{\lambda} \le 2$, $\abs{\lambda + \frac{\mcal{N}}{2}} \le 2$, which give us $\mcal{N} = 8$ supergravity (SUGRA) in 4D.
+Similarly 32 is the maximal amount of SUSY in any dimension, if we want spin $\le 2$.
+For example, in 11D $\mcal{N} = 1$ we have precisely 32 supercharges, and the SUGRA multiplet is the smallest multiplet.
+Therefore the maximum dimension for SUGRA is 11.
+	\end{itemize}
+	Note that these massless supermultiplets have helicity $-\abs{\lambda},\cdots,\abs{\lambda}$ and is thus CPT self-conjugate.
+
+	\newparagraph
+	We actually care more about the massless representations and less about the massive ones.
+The reason is that massless representations are considered more ``fundamental'', since masses are usually generated dynamically through spontaneous symmetry breaking.
+This philosophy is discussed in later sections in more details.
+
+	For 4D $\mcal{N} = 1$, we can already see this by counting degrees of freedom:
+	\begin{equation}
+	\begin{array}{ccccc}
+		\text{(massless chiral)}
+		&\oplus&
+		\text{(massless vector)}
+		&\cong&
+		\text{(massive vector)}
+	\\[1ex]
+		\{\phi, \psi_\alpha\}
+		&\oplus&
+		\{\lambda_\alpha, A_\mu\}
+		&\cong&
+		\{\phi',\psi_\alpha,\lambda_\alpha,A'_\mu\}
+	\end{array}
+	\end{equation}
+	This is indeed the case dynamically: massive vector multiplets arise by a supersymmetric analog of the Higgs mechanism \cite{Argyres:1996abc}.
+	$\phi$ is like the complex Higgs field.
+One component (the Goldstone mode) of $\phi$ gets ``eaten'' by the gauge field $A_\mu$ through symmetry breaking.
+The degrees of freedom combine into the massive vector $A'_\mu$.
+The other component of $\phi$ remains as the real scalar $\phi'$.
+
+\section{Superspace \& Superfields}
+	\speaker{Ban ``Bo'' Lin}\\
+	\references{
+	\begin{enumerate}[noitemsep,topsep=0pt]
+	\item \textcite{Argyres:1996abc}, Section 6
+	\item \citetitle{Hori:2003ic} \cite{Hori:2003ic}, Chapter 12
+	\end{enumerate}
+	}\vspace{.5\baselineskip}
+
+	Superspace \& superfields encode the SUSY transformation implicitly, so we can write down manifestly SUSY-invariant actions.
+This is exactly similar to how we write down diff-invariant actions in usual QFT.
+
+	A generic superfield will give a \textit{reducible} representation of the superalgebra.
+To get an \textit{irreducible} representation (\textit{irrep}), we must impose a constraint on the superfield which (anti-)commutes with the superalgebra.
+There are two possibilities for 4D $\mcal{N} = 1$:
+	\begin{enumerate}%[noitemsep]
+	\item \textbf{Reality condition:} this lead to a vector multiplet. We shall revisit this in the future. For now we will proceed to the next condition, which is:
+
+	\item \textbf{Chirality condition:}
+	\begin{equation}
+		\bar{D}_{\dot{\alpha}} \Phi = 0
+	\quad\Leftrightarrow\quad
+		\Phi = \Phi(y,\theta),
+	\quad
+		y^\mu \equiv x^\mu
+			+ i\theta \sigma^\mu \bar{\theta}
+	\end{equation}
+	This gives us the chiral superfield $\Phi$. It can be expanded in components as follows:
+	\begin{equation}
+	\begin{aligned}
+		\Phi
+		&= \phi(y) + \sqrt{2}\,\theta\,\psi(y)
+			+ \theta^2 F(y) \\
+		&= \phi(x) + \cdots
+			+ \theta^2 F(x)
+	\end{aligned}
+	\label{eq:chiral_components}
+	\end{equation}
+	Note that the first line is not the end of the story; to get to the actual component fields we have to write everything in terms of $(x,\theta)$, like in the second line. 
+	\end{enumerate}
+
+	For 4D $\mcal{N} = 1$, a generic SUSY-invariant Lagrangian of the chiral superfields $\Phi$ is given by:
+	\begin{equation}
+		\mcal{L}
+		= \int \dd[4]{\theta} \mcal{K}(\Phi, \bar{\Phi})
+			+ \int \dd[2]{\theta}
+				\mcal{W}(\Phi)
+			+ \int \dd[2]{\bar{\theta}}
+				\wbar{\mcal{W}}(\bar{\Phi})
+	\end{equation}
+	$\Phi$ can be a collection of chiral superfields $\Phi^a$, but here for simplicity we've dropped the $a$ indices.
+
+	\begin{enumerate}
+	\item $\mcal{K}(\Phi, \bar{\Phi})$ is the \textbf{K\"ahler potential} and gives us the kinetic terms of the component fields. 
+	The target automatically becomes a K\"ahler manifold where the component field $\phi$ is the target coordinate.
+A non-degenerate kinetic term corresponds to a positive definite metric \cite{Hori:2003ic}:
+	\begin{equation}
+		g_{i\wbar{j}}
+		= \pdd{i} \pdd{\wbar{j}}
+			\mcal{K}(\Phi, \bar{\Phi}),
+	\quad \pdd{i} = \pdv{\phi^i}
+	\end{equation}
+	On the other hand, the fermion fields $\psi$ are naturally interpreted as vectors in the tangent space to the K\"ahler manifold:
+	\begin{equation}
+		\psi, \bar{\psi}
+		\in \Gamma\pqty{
+				\Sigma,
+				\phi^* \mrm{T}M \otimes \mbb{C}
+			}
+	\end{equation}
+	Here $\Gamma\pqty{\Sigma,-}$ stands for sections of some bundle over $\Sigma$. See e.g.~\textit{Mirror Symmetry} \cite{Hori:2003ic}.
+
+%	\pagebreak[3]
+
+	\item $\mcal{W}(\Phi)$ is the \textbf{superpotential;} it is holomorphic w.r.t.\,$\Phi$, and it generates the potential and interaction vertices for the component fields.
+It's also called an \textbf{$F$-term}, probably due to the fact that:
+	\begin{equation}
+		\text{For}\ \,\mcal{W} = \Phi,
+	\ \,
+		\int \dd[2]{\theta} \mcal{W}
+		= F(x)
+	\end{equation}
+	Here $F(x)$ is the last component of a chiral superfield \eqref{eq:chiral_components}. Generally, we have:
+	\begin{equation}
+		\int \dd[2]{\theta}
+			\mcal{W}(\Phi^i)
+		= F^i \pdd{i}\mcal{W}
+			- \frac{1}{2} \psi^i \psi^j
+				\pdd{i} \pdd{j} \mcal{W}
+	\end{equation}
+
+	\end{enumerate}
+
+	A full expansion of the Lagrangian $\mcal{L}$ (including $\mcal{K}$ and $\mcal{W}$) reveals that $F$ has no kinetic term and is quadratic in the action, thus it can be safely integrated out.
+The result gives us the potential for the scalar component $\phi$:
+	\begin{equation}
+		V(\phi,\bar{\phi})
+		= g^{i\wbar{j}}
+			\,\pdd{i} \mcal{W}
+			\,\pdd{\wbar{j}} \wbar{\mcal{W}}
+		= \abs{\pd\mcal{W}}^2
+	\end{equation}
+	The classical vacua satisfy $\pd_i V = 0$. 
+%	Spontaneous breaking of internal symmetry happens if we have $\vev{\phi} \ne 0$. 
+	On the other hand, we see that $V\ge 0$ for a positive-definite metric $g_{i\wbar{j}}$, therefore if $V = 0$ we have $\pdd{i} V = 0$ and $\pdd{i} \mcal{W} = 0$.
+In this case we have SUSY vacua, i.e.~SUSY is unbroken.
+
+	In summary,
+	\begin{itemize}[noitemsep]
+	\item Vacua: $
+		\pdd{i} V
+		= \pdd{i}\,\pqty\big{\abs{\pdd{i} \mcal{W}}^2}
+		= 0
+	$
+	\item SUSY vacua: $\pdd{i} \mcal{W} = 0$, which implies $V = 0$ thus $\pdd{i} V = 0$. 
+	\end{itemize}
+	Spontaneous breaking of SUSY happens if $\pdd{i} V = 0$ while $V \ne 0$, namely we don't have a SUSY vacua.
+	Fig.\,1.4 of \textcite{Terning:2006bq} is a nice summary of the situations.
+These backgrounds will come in handy in later sections.
+
+\section{Holomorphy and Non-renormalization}
+	\speaker{Wen-Xin ``Bryan'' Lai}\\
+	\references{
+	\begin{enumerate}[noitemsep,topsep=0pt]
+	\item \textcite{Argyres:1996abc}, Section 7
+	\item \textcite{Intriligator:1995au}, Section 2
+	\item \textcite{Seiberg:1993vc}
+	\end{enumerate}
+	}\vspace{.5\baselineskip}
+
+\pagebreak[3]
+
+	\begin{quotation}
+		``If a bare parameter is unnaturally set to zero, radiative corrections lead to a renormalized non-zero value.
+Therefore, if we want a small renormalized value \textit{without} a symmetry, the bare value has to be \textit{fine-tuned}.''
+
+		\vspace{1ex}\hfill
+		--- \textcite{Seiberg:1993vc} on naturalness. 
+	\end{quotation}
+	\begin{equation}
+		\boxed{\text{Symmetry}}
+		\quad\xrightleftharpoons[
+			\text{``natural''}
+		]{\text{Ward}}\quad
+		\boxed{\text{Amplitudes / Couplings} \approx 0}\,,
+		\ \text{(almost) vanishing}
+	\end{equation}
+
+	\noindent%
+	The argument of non-renormalization by Dine, Polchinski and Seiberg \cite{Seiberg:1993vc}:
+
+	\begin{enumerate}[beginpenalty=10000]
+	\item \textbf{Philosophy:} we \textit{believe} that the UV theory \textit{should} have almost no coupling and a lot of fields; think of string theory (where we have only one coupling) and string field theory (where there are $\infty$-ly many fields).
+In fact, this was explicitly pointed out in Section 4.2 of \mbox{\textcite{Dine:1996ui}}\footnote{
+		Oh my, it's \texttt{hep-ph}! This must come from a simpler time when SUSY is expected to be found by experiments. 
+	}:
+
+		\begin{quote}
+			In string theory, all of the parameters \textit{are} expectation values of chiral fields.
+
+			Indeed, non-renormalization theorems in string theory, both for worldsheet and string perturbation theory, were proved by the sort of reasoning we have used above, long ago. 
+		\end{quote}
+
+	However, the following argument should still hold even if such understanding is not true. For more on this, see the exposition in the following subsection.
+
+	\item \textbf{Wilsonian RG:} we flow towards an effective field theory in the IR, where we have many couplings and only a few fields.
+Almost all IR couplings $\lambda$ come from vacuum expectation values (VEVs) of some UV fields, $\lambda = \ave{\lambda(x)}$.
+This is the Higgs mechanism.
+
+	\item Assuming \textbf{SUSY is not broken} from $\Lambda_{\mrm{UV}}$ all the way down to the scale of our interest $\mu$, we can then promote the coupling $\lambda$ to a chiral superfield $\lambda(y,\theta)$, i.e.~we ``turn it on'' or make it dynamical, as we perform the RG flow.
+We have these powerful constraints:
+
+		\begin{enumerate}
+		\item \textbf{Holomorphy:} due to SUSY, the superpotential $\mcal{W}(\Phi,\lambda)$ is holomorphic along the flow. 
+		In particular, the $\lambda$ dependence is holomorphic, since it's now been promoted to a chiral superfield\footnote{
+			There are subtleties about this statement; see \cite{Dine:1994su} for a more careful discussion. 
+		}.
+
+%		\pagebreak[3]
+
+		\item \textbf{Global symmetries:} as we promote $\lambda\leadsto\lambda(y,\theta)$ we see global symmetries in the UV.
+$\ave{\lambda(y,\theta)} = \lambda$ is understood as the \textit{spontaneous breaking} of these symmetries.
+They are restored as we promote $\lambda\leadsto\lambda(y,\theta)$, and they constrain the form of $\mcal{W}(\Phi,\lambda)$.
+
+		This is an example of \textit{selection rules}, just like what we've seen in quantum mechanics (QM) where symmetries constrain the spectrum.
+
+		\item \textbf{Weak coupling limits:} we can take various weak coupling limits in the IR.
+		\end{enumerate}
+	These constraints fix the form of $\mcal{W}(\Phi,\lambda)$ almost entirely. 
+	\end{enumerate}
+
+	\textit{Note:} in \cite{Seiberg:1993vc} Seiberg chose to call the non-renormalization in SUSY \textit{a violation of naturalness} in the conventional sense, since in the IR we see no global symmetry but we still have many vanishing amptitudes.
+But I believe it's okay to understand this as a new sense of naturalness, where the vanishing of amplitudes (or the rigid form of the potentials) is protected by supersymmetry and some ``hidden'' global symmetries (that are spontaneously broken in the IR).
+
+\subsection{Why can we turn on the couplings?}
+	We've argued that it's physically reasonable to turn on the coupling $\lambda$ and make it a dynamical field\footnote{
+		I believe this is the so-called ``un-Higgs-ing'' procedure, and the unHiggsed field is called a ``spurion''. \\
+		\hspace*{2em}
+		See \https{physicsforums.com/threads/spurion-symmetry.205417}.
+	}. On the other hand, as pointed out by \textcite{Argyres:1996abc}, we can simply think of this as ``just a trick''\footnote{
+		See also \https{physics.stackexchange.com/q/110926/162487}. 
+	}:
+
+	\begin{quote}\small
+	We are certainly allowed to do so if we like (since the couplings enter in the microscopic (UV) theory in the same way a backgound chiral superfield would).
+The point of this trick is that it makes the restrictions on possible quantum corrections allowed by supersymmetry apparent.
+These restrictions are just a supersymmetric version of the familiar “selection rules” of QM.
+
+	Perhaps an example from QM will make this clear: Recall the Stark effect, in which one calculates corrections to the hydrogen atom spectrum in a constant background electric field $E$...
+But the resulting perturbed energy levels cannot depend on the perturbing parameters $E$ arbitrarily.
+Indeed, one simply remarks that the electric field transforms as a vector $E$ under rotational symmetries, thus giving selection rules for which terms in a perturbative expansion in the electric field strength it can contribute to.
+\textit{On the other hand, these selection rules are equally valid without the interpretation of the electic field as a background field transforming in a certain way under a symmetry (which it breaks).
+Instead, one could think of it as an abstract perturbation, and the selection rules follow simply because it is \textbf{consistent} to assign the perturbation transformation rules under the broken rotational symmetry.}
+	\end{quote}
+
+	I believe the best way to make sense of this is to have a generalized notion of symmetry, where background fields are allowed to transform non-trivially.
+In the QM example given above, we have $E$ as a background field, where in the field theory case we have the couplings $\lambda$ as background fields.
+
+	Ususally we demand a symmetry to keep the background fields invariant; this is not always convenient.
+We should also consider symmetries that act on \textit{the collection of all possible background configurations}.
+This is precisely the degenrate vacua we've seen when studying the Higgs mechanism.
+This justifies the trick of turning on $\lambda$.
+For more on this, see Section 2.1.3 of \textcite{Banados:2016zim}%
+%	, and also Section 1.2 of \cite{Lai:2021abc}
+	.
+
+\subsection{Wilsonian RG of the Wess--Zumino model}
+	A worked example of this for the Wess--Zumino model is given in \textcite{Argyres:1996abc} and also \cite{Seiberg:1993vc,Intriligator:1995au}.
+We start with the superpotential at $\Lambda_{\mrm{UV}}$:
+	\begin{equation}
+		\mcal{W}_{\mrm{UV}}
+		= m \Phi^2 + \lambda \Phi^3
+	\end{equation}
+	Here $\lambda$ and $m$ are bare parameters in the UV.
+
+	We imagine that the parameters are VEVs of some Higgs fields $\Psi$ with mass $M \gg \Lambda_{\mrm{UV}}$. Basically we are ``embedding'' the theory inside a parent theory with a larger symmetry. 
+	For $M \gg \Lambda_{\mrm{UV}}$ we can't see the fluctuations of $\Psi$, namely its value is ``frozen'' to $\vev{\Psi}$.
+It's thus natural to ``integrate out'' $\Psi$, and then the theory reduces to the effective theory with $\mcal{W}_{\mrm{UV}}$.
+This is the Higgs mechanism.
+
+\pagebreak[3]
+
+	However, we can also leave $\Psi$ as it is without integrating it out, and compute all physical observables with the enlarged, parent theory.
+The results should be exactly the same.
+In particular, since SUSY is assumed to be preserved along the RG flow, then $\mcal{W} = \mcal{W}(\Psi,\Phi)$ is always holomorphic.
+This is the main idea of Seiberg's argument.
+
+	One concrete realization of this procedure for the $m\Phi^2$ term is given by \cite{Dine:1996ui}:
+	\begin{equation}
+	\begin{aligned}
+		m\Phi^2
+		\leadsto{}&
+			M \pqty{
+				\Psi - m
+			}^2 + \Psi \Phi^2 \\
+	\end{aligned}
+	\end{equation}
+	Here we've been cavaliar about constant shifts of $\mcal{W}$, as they do not affect the physics\footnote{
+		On the other hand, constant shifts of $V = \abs{\pd\mcal{W}}^2$ \textit{do} matter in SUSY theories, as they are related to spontaneous SUSY breaking; see \S2 and \S4. 
+	}. 
+	Also, we are free to include a kinetic term for $\Psi$ in the K\"ahler potential so that it does look like a physical field.
+However, this does not matter much, as for $M \gg \Lambda_{\mrm{UV}}$, the $
+		M \pqty{\Psi - m}^2
+	$ term dominates and we always have $m \simeq \vev{\Psi}$.
+In the end the superpotential reduces back to $m\Phi^2$.
+Holomorphy of $\mcal{W}$ with respect to $m$ then follows from holomorphy with respect to $\Psi$.
+
+	There are of course many ways to realize $m$ as the VEV of some dynamical operator.
+However, the end result is universal, namely $\mcal{W}$ should be holomorphic with respect to $m$.
+Also, since $m$ is now promoted to be dynamic, it can transform under a larger global symmetry group.
+
+	We now perform the RG flow down to the IR scale $\mu$. Note that we have three scales:
+	\begin{equation}
+		M \gg \Lambda_{\mrm{UV}} \gg \mu
+	\end{equation}
+	The idea is that:
+	\begin{itemize}[noitemsep]
+	\item We start with $\mcal{W}_{\mrm{UV}}$ at $\Lambda_{\mrm{UV}}$;
+	\item We ``embed'' it into a parent theory that works up to the energy scale $M$;
+	\item We derive constraints for the IR theory at $\mu$. 
+	\end{itemize}
+
+	\newparagraph
+	Let's imagine doing Wilsonian renormalization from $\Lambda_{\mrm{UV}}$ down to $\mu$. We are summing over Feynman diagrams where:
+	\begin{itemize}[noitemsep]
+	\item The internal lines are UV modes, carrying some momenta ranging from $\mu$ to $\Lambda_{\mrm{UV}}$;
+	\item The external lines are IR modes, carrying momenta lower than $\mu$ and are treated as non-dynamical background fields as we integrate out the UV modes. 
+	\end{itemize}
+	There will be loop integrals of the form:
+	\begin{equation}
+		\int_\mu^{\Lambda_{\mrm{UV}}}
+			\dd[D]{p}
+	\end{equation}
+	Everything is finite and there is no divergence from the loop integrals! We need not worry about UV or IR divergence. This is the beauty of Wilsonian RG.
+
+	If we want to compute the contribution of the high energy modes to the partition function $Z\sim e^{-\mcal{W}}$, we should sum over all diagrams.
+However, we are interested in the effective potential $\mcal{W}\sim -\log Z$, therefore we need only sum over connected diagrams.
+Recall that the sum over all diagrams is basically the exponential of the sum over connected diagrams.
+
+%\pagebreak[4]
+
+	\newparagraph
+	After summing over all connected diagrams, we will obtain an IR effective potential $\mcal{W}_{(\mu)}$ at the scale $\mu$.
+On the other hand, for theories with a mass gap, we can integrate all the way to $\mu \to 0$ with no IR divergence.
+It is claimed without proof \cite{Argyres:1996abc,Seiberg:1993vc,Intriligator:1995au} that in this case, $\mcal{W}_{\mu\to 0}[\Phi]$ agrees with the quantum effective potential, which is the generating functional of renormalized vertices, or 1PI diagrams.
+
+	Generally, we have:
+	\begin{equation}
+		\mcal{Z}
+		= \int
+			\DD{\Phi}\,
+			\exp \frac{i}{\hbar} S[\Phi]
+		= \int\limits_{\hbar\to 0}
+			\DD{\Phi}\,
+			\exp \frac{i}{\hbar} \Gamma[\Phi]
+	\end{equation}
+	$\Gamma[\Phi]$ is the quantum effective action. 
+	The path integral over $\Gamma[\Phi]$ is evaluated under the semiclassical limit: $\hbar\to 0$.
+This corresponds to a loop expansion of the Feynman diagrams, where we keep only the leading order terms, namely tree level (0-loop) diagrams.
+The full path integral is thus re-written as a sum over tree diagrams with 1PI vertices.
+
+	The relation between the Wilsonian effective action $S_{(\mu)}$ and the quantum effective action $\Gamma$ is explained in \cite{Shifman:1986zi}, which I don't fully understand.
+Some very help insights are given by \cite{Arkani-Hamed:1997lye,Arkani-Hamed:1997qui}.
+Here we try to provide some very rough arguments on how $S_{\mu\to 0} = \Gamma$ for a gapped theory.
+
+	\begin{itemize}
+	\item As is pointed out by \cite{Arkani-Hamed:1997qui}, this statement is actually scheme dependent.
+With a physical choice of renormalization scheme, one can define the 1PI couplings by the gauge field correlations at a fixed Euclidean momentum transfer $q^2$ within the background field formalism.
+By changing the cutoff $\mu$ down to a scale very close to $q^2$, namely $\mu^2 \approx q^2$, one can minimize the difference between $S_{(\mu)}$ and the classical 1PI effective action $\Gamma_{(q)}$ for external fields of momentum $O(q^2)$, since the path integral over quantum fields generates little correction.
+
+	\item We provide another rough argument inspired by \cite{physics_stack371789}.
+Again recall that the sum over connected diagrams can be re-written as the sum over trees with 1PI blobs.
+On the other hand, note that the external legs carry momenta $\lesssim\mu$, therefore the internal ``bridges'' between 1PI ``islands'' carry momenta ranging between $\mu$ and $\order{n\mu}$, where $n$ is the number of external legs.
+These bridge momenta are fixed by conservation and are \textit{not} integrated over.
+For $\mu \to 0$, diagrams with these bridges (i.e.~one particle \textit{reducible} (1PR) diagrams) are suppressed by the mass gap, and thus only 1PI diagrams survive.
+	\end{itemize}
+
+\subsection{Non-renormalization from symmetries \& asymptotics}
+
+	Holomorphy plus global symmetry constrains $\mcal{W}_{(\mu)}$ to be of the form \cite{Seiberg:1993vc,Argyres:1996abc}:
+	\begin{equation}
+		\mcal{W}_{(\mu)}
+		= m\Phi^2
+			f\pqty{\frac{\lambda\Phi}{m}}
+		= \sum_n a_n(\mu)\,
+			\lambda^n m^{1-n} \Phi^{n+2}
+	\end{equation}
+	Here we've written $\mcal{W}_{(\mu)}$ as a Laurent series. At this stage it seems that $a_n$ may depend on the running cutoff $\mu$. 
+	By looking at the asymptotics we can eliminate a bunch of terms: \pagebreak[3]
+	\begin{itemize}[
+		noitemsep
+%		,beginpenalty=10000
+	]
+	\item For $\lambda\to 0$, the theory is free, $\mcal{W} \to m\Phi^2$, therefore only terms with $n\ge 0$ are allowed.
+	\item For $\lambda\to 0$ and $m/\lambda\to 0$, the theory should be\footnote{
+		I guess the more accurate way to say it is that the theory is \textit{assumed} to be weakly coupled. 
+	} weakly coupled, therefore only terms with $n\le 1$ are allowed.
+
+	\end{itemize}
+
+	Alternatively, we can look at possible Feynman diagrams to eliminate the $n\ge 2$ terms.
+There are only tree level diagrams that can generate these terms, but they are not 1PI for $n\ge 2$.
+These 1PR diagrams should not contribute to $\mcal{W}_{\mu\to 0}$, due to the following logic \cite{Argyres:1996abc,Seiberg:1993vc}:
+
+	\begin{itemize}
+	\item If there is a mass gap: $m > 0$, then $\mcal{W}_{\mu\to 0}$ is identified with the 1PI effective potential, and thus 1PR diagrams should not contribute;
+
+	\item If $m = 0$, then $\mcal{W}_{\mu\to 0}$ does not coincide with the 1PI effective potential, so in principle we should include these tree diagrams in $\mcal{W}_{(\mu)}$.
+
+	However, the $m \to 0$ limit is completely smooth for $\mcal{W}_{(\mu)}$, since to obtain $\mcal{W}_{(\mu)}$ we only integrate modes with momenta $\gtrsim \mu$ and never reach the IR.
+Therefore the form of $\mcal{W}_{(\mu)}$ with $m = 0$ is identical to that with $m > 0$.
+	\end{itemize}
+
+	Now we've eliminated most of the terms in the expansion. We have:
+	\begin{equation}
+		\mcal{W}_{(\mu)}
+		= a_0(\mu)\,m\Phi^2
+			+ a_1(\mu)\,\lambda\Phi^3
+	\end{equation}
+	This is already quite remarkable: there is no new vertex generated from RG flow. 
+	Note that $a_{0,1}(\mu)$ may depend on $\mu$ but not $m$ or $\lambda$. We can again look at the limits: as $\lambda\to 0$, $\mcal{W} \to m\Phi^2$ for any $\mu$, therefore $a_0(\mu) \equiv 1$,
+	\begin{equation}
+		\mcal{W}_{(\mu)}
+		= m\Phi^2
+			+ a_1(\mu)\,\lambda\Phi^3
+	\end{equation}
+
+	There are again two proposals to fix $a_1(\mu)$:
+	\begin{itemize}
+	\item Consider $\lambda\to 0$, $m\to 0$ with arbitrary $m/\lambda$. We should have \cite{Intriligator:1995au}:
+	\begin{equation}
+		\mcal{W}_{(\mu)} = \mcal{W}_{\mrm{UV}},
+	\quad
+		f\pqty{t = \frac{\lambda\Phi}{m}}
+		= 1 + t,
+	\end{equation}
+	where $t$ is now arbitrary, thus $a_1(\mu) \equiv 1$. However, to me this sounds like an additional weak coupling \textit{assumption}.
+
+	\item According to \textcite{Argyres:1996abc}, $a_1(\mu)$ can be fixed by matching to perturbation theory for small $\lambda$. Let's try to do this! We have:
+	\begin{equation}
+		\mcal{W}_{\mrm{UV}} [\Phi+\chi]
+		= \mcal{W}_{\mrm{UV}} [\Phi]
+			+ m\chi^2
+			+ 2m\Phi\chi
+			+ 3\lambda\Phi^2\chi
+			+ 3\lambda\Phi\chi^2
+			+ \lambda\chi^3
+	\end{equation}
+	To generate the $a_1(\mu)\,\lambda\Phi^3$, we cannot include any $m$ coefficients, and we must include $\lambda$ and $\Phi$. Therefore only the $
+		3\lambda\Phi^2\chi, 3\lambda\Phi\chi^2
+	$ terms might contribute.
+There is only one diagram that I can think of which might contribute: $(3\lambda\Phi\chi^2)^3$ with the internal $\chi$'s contracted, forming a 1-loop diagram.
+However.
+the internal $\chi$ contractions again generate $m$ dependence.
+Therefore this diagram must not contribute to $a_1(\mu)\,\lambda\Phi^3$.
+In the end, we must have $a_1(\mu) \equiv 1$.
+
+	\end{itemize}
+
+	Finally, we have:
+	\begin{equation}
+		\mcal{W}_{(\mu)}
+		= m\Phi^2 + \lambda\Phi^3
+	\end{equation}
+	Namely, the superpotential is not renormalized.
+In our current scheme where the field strength $\Phi$ is not renormalized, $m,\lambda$ is constant along the flow.
+However, the K\"ahler potential is non-holomorphic from the start and it is renormalized, which leads to field strength renormalization.
+
+\section{Moduli Space of Vacua}
+	\speaker{Yuan Zhong}\\
+	\references{%
+%	\begin{enumerate}[noitemsep,topsep=0pt]
+%	\item
+	\textcite{Argyres:1996abc}, Section 7
+%	\end{enumerate}
+	}\vspace{.5\baselineskip}
 

### 2021-08-07 alpha/CutoffModularFlow/notes.tex
Clean up the cutoff modular flow project
Prepare notes on modular flow for a fresh start

@@
 
+\usepackage{comment}
 \newcommand{\lui}[2]{\textcolor{red}{#1}\todo[color=yellow]{\scriptsize{L: #2}}}
+\newcommand{\wei}[2]{\textcolor{magenta}{#1}\todo[color=yellow]{\scriptsize{WS: #2}}}
+\newcommand{\wx}[2]{\textcolor{purple}{#1}\todo[color=teal]{\scriptsize{X: #2}}}
 
@@
 \newcommand{\arcsinh}{\ensuremath{\mop{arcsinh}}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\renewcommand{\tilde}[1]{\ensuremath{\widetilde{#1}}}
+\usepackage{ccicons}
+\usepackage{enumitem}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{Modular flow and holographic entanglement entropy in cutoff AdS / \TTbar deformed theory} 
+
+\title{Modular flow and holographic entanglement entropy in cutoff AdS} 
 \author[a]{The EE \TTbar Project}
-%\author[a]{Luis Apolo,} 
-%\author[a]{Pengxiang Hao,} 
-%\author[a]{Wen-Xin Lai,}
-%\author[a]{and Wei Song}
-
-\affiliation[a]{Yau Mathematical Sciences Center, Tsinghua University, Beijing 100084, China}
-
-%  \emailAdd{apolo@mail.tsinghua.edu.cn, wsong2014@mail.tsinghua.edu.cn}
+
+\affiliation[a]{Yau Mathematical Sciences Center, Tsinghua University, Beijing 100084, China\ \,\ccbyncsajp}
 
@@
 }
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \begin{document}
@@
 %\flushbottom
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \addtocounter{section}{-1}
-
-\begin{itemize}
+\begin{itemize}[nosep]
 \item add black hole spectrum 
@@
 
-\section{Introduction}
-
 \section{$T \bar T$ deformation and cutoff AdS}
 In this section we first review the holographic duality between $T\bar T$ deformed CFT$_2$ and Einstein gravity on asymptically AdS$_3$ spacetime with a finite cutoff,  and then we use the covariant phase space method to calculate the gravitational charges for BTZ black holes with finite cutoff and show that the black hole spectrum matches that of  $T\bar T$ deformed CFT$_2$.
-
-\subsection{Brief review of the duality}
-
-{\color{red}\itshape Review TTbar and cutoff AdS. }
 
@@
 	&&& \text{i.e.}\ \,
-		L^2
+		L_\infty^2
 		= \pqty{x_+ - x_-}^2
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \end{document}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2021-08-07 alpha/CutoffModularFlow/notes.tex
Clean up the notes on modular flow, more

@@
 
-\affiliation[a]{Yau Mathematical Sciences Center, Tsinghua University, Beijing 100084, China\ \,\ccbyncsajp}
+\affiliation[a]{Yau Mathematical Sciences Center, Tsinghua University, Beijing 100084, China\ \,\normalsize\ccbyncsajp}
 
@@
 \begin{itemize}[nosep]
-\item add black hole spectrum 
-\item geometric picture
 \item maybe consider later: SSA 
@@
 \pagebreak
-
 \section{Conventions}
@@
 
-\section{$T \bar T$ deformation and cutoff AdS}
-In this section we first review the holographic duality between $T\bar T$ deformed CFT$_2$ and Einstein gravity on asymptically AdS$_3$ spacetime with a finite cutoff,  and then we use the covariant phase space method to calculate the gravitational charges for BTZ black holes with finite cutoff and show that the black hole spectrum matches that of  $T\bar T$ deformed CFT$_2$.
-
-\subsection{Black spectrum from gravitional charges}
+\section{Black spectrum from gravitional charges}
 	Ref: \textcite{Wald:1993nt,Iyer:1994ys,Iyer:1995kg}, \textcite{Lewkowycz:2013nqa}, and \textcite{Faulkner:2013ana}.
@@
 
-\subsubsection*{Covariant charges}
+\subsection{Covariant charges}
 
@@
 
-\subsubsection*{Killing vectors}
+\subsection{Killing vectors}
 
@@
 	  \eq{
-	  ds^2_{c} = r_c^2 \big (- d\til{t}^2 + d \til{\phi}^2 \big ), \label{mink}
+	  ds^2_{c} = r_c^2 \big({- d\til{t}^2} + d \til{\phi}^2 \big ), \label{mink}
 	  }
@@
 	 %
-	 \begin{enumerate}
+	 \begin{enumerate}[nosep]
 	 \item[(i)] it leads to integrable charges, see eq.~\eqref{quasilocalcharge2};
@@
 
-\subsubsection*{Quasilocal energy}
+\subsection{Quasilocal energy}
 
@@
 
-\section{Entanglement in the boundary story}
-\subsection{Review of entanglement at zero temperature}
-
-\subsection{Entanglement entropy at finite temperature}
-
-\newcommand{\lp}{\ensuremath{l_p}}
-\newcommand{\halfL}{\ensuremath{\frac{L}{2}}}
-
-	One can use the method in \cite{Lewkowycz:2019xse} to calculate the entanglement entropy in the thermal case and finite size case from the field theory side.
-The Rindler transformation from the domain of dependence of the interval $(-\lp,\lp)$ on the plane to the sphere is
-	\begin{equation}
-	t=\lp\frac{\sin\theta \sinh(\tau/\lp)}{1+\sin\theta \cosh(\tau/\lp)},\ \  x=\lp\frac{\cos\theta}{1+\sin\theta\cosh(\tau/\lp)}
-	\label{eq:rindler_sphere}
-	\end{equation}
-	the conformal factor reads,
-	\begin{equation}
-	\Omega=\frac{1}{1+\sin\theta\cosh(\tau/\lp)}
-	\end{equation}
-	At the endpoints, it becomes $1$.
-From the discussion in \cite{Lewkowycz:2019xse}, the contribution to the entanglement entropy totally comes from the endpoints of the interval, so one can use the such conformal transformation where the conformal factor at the endpoints is $1$ to calculate the entanglement entropy.
-Also, in the conformal map above from the casual diamond to the sphere, only the length of the interval matters.
-If these two endpoints lie at other position, one can use the rotation and translation symmetry to put it at $x = \pm \lp$, since the $T\bar T$ deformed theory also admits these symmetries.
-
-	Now let's consider the thermal case.
-We will make use of two successive conformal maps: first we map the thermal cylinder to the plane, and then we use \eqref{eq:rindler_sphere} to map the plane to the sphere.
-	The conformal transformation from the thermal cylinder to the plane reads,
-	\begin{equation}
-	z=\frac{\beta}{2\pi}\,e^{\frac{2\pi}{\beta} w},
-%	\ \ \ \kappa=\frac{2\pi}{\beta}
-	\end{equation} 
-	where $z = x + it$ is the coordinate on the plane, and $w$ is the coordinate on the thermal cylinder with identification,
-	\begin{equation}
-	w\sim w+i\beta
-	\end{equation}
-	The endpoints of the interval on the thermal cylinder is
-	\begin{equation}
-	w=\pm \halfL
-	\end{equation} 
-%	The length of the interval is $L=2l$. 
-	Under the conformal map, the endpoints on the plane is
-	\begin{equation}
-	\frac{\beta}{2\pi}e^{\pm \frac{2\pi}{\beta} \frac{L}{2}}
-	\end{equation}
-	the length is $\frac{\beta}{\pi}\sinh(\halfL \frac{2\pi}{\beta})$, so one can use translations and rotations to map the endpoints to $x = \pm\lp$ on the plane, where
-	\begin{equation}
-	l_p=\frac{\beta}{2\pi}\sinh(\halfL \frac{2\pi}{\beta})
-	\end{equation}
-	The conformal factor is
-	\begin{equation}
-	e^{\frac{2\pi}{\beta}(w+\bar{w})}
-	\end{equation}
-	Note that compared to the usual map from cylinder to plane $z=e^{\frac{2\pi}{\beta} w}$, we put the overall scaling factor $\frac{\beta}{2\pi}$ to make sure that the conformal factor at the endpoints is $1$.
-
-	From \cite{Donnelly:2018bef}, the entanglement entropy for zero temperature is
-	\begin{equation}
-	S(L)=\frac{c}{3} \arcsinh \frac{\lp}{a}
-	\end{equation}
-	where
-	\begin{equation}
-	a^2=\frac{\mu c}{12}
-	\end{equation}
-	The $C$-function reads,
-	\begin{equation}
-	C(L)=L S'(L = 2l)=\frac{c}{3}\frac{1}{\sqrt{1+4a^2/L^2}}
-	\end{equation}
-	Now in the thermal case, $l_p\rightarrow \frac{\beta}{2\pi}\sinh(\halfL \frac{2\pi}{\beta})$
-	\begin{equation}
-	S_t=\frac{c}{3}\arcsinh \pqty{
-			\frac{1}{\kappa a}\sinh(\halfL \frac{2\pi}{\beta})
-		}
-	\end{equation}
-	\sidenote{which is the same as the results obtained from the local temperature trick \eqref{} and the gravity calculation \eqref{} [This is now the first non-trivial result of the paper.
-This comment should be moved to later.]}
-
-	------------
-
-	Now consider the finite size case, the conformal transformation is,
-	\begin{equation}
-	z=\frac{1}{ir_1}e^{iwr_1},\quad
-		r_1 = \frac{2\pi}{\sidenote{R}}
-	\end{equation}
-	where $w$ is the cylinder coordinate, and $R$ is the \textit{spatial} size of the cylinder:
-	\begin{equation}
-	w\sim w+ R
-	\end{equation}
-	The endpoints of the interval are 
-	\begin{equation}
-	w\pm l
-	\end{equation}
-	The conformal factor is
-	\begin{equation}
-	e^{ir_1(w+\bar{w})}
-	\end{equation}
-	which is $1$ at the endpoints. The plane length reads,
-	\begin{equation}
-	l_p=\frac{1}{r_1}\sin lr_1
-	\end{equation}
-	So the final result is
-	\begin{equation}
-	S_f=\frac{c}{3}ArcSinh(\frac{1}{r_1a}\sin(lr_1))
-	\end{equation}
-
 \pagebreak
-
-	The global AdS reads,
-	\begin{equation}
-	 ds^2=-(r^2+1)dt^2+\frac{dr^2}{r^2+1}+r^2d\phi^2,\ \ \phi\sim\phi+2\pi
-	\end{equation}
-	\begin{equation}
-	\phi\rightarrow r1\phi,\ \ r\rightarrow \frac{r}{r_1}, \ \ \ t\rightarrow r_2 t
-	\end{equation}
-	\begin{equation}
-	 ds^2=-(r^2+r_1^2)dt^2+\frac{dr^2}{r^2+r_1^2}+r^2d\phi^2,\ \ \phi\sim\phi+\beta
-	\end{equation}
-	Compared to the planer BTZ,
-	\begin{equation}
-	ds^2=-(r^2-r_1^2)dt^2+\frac{dr^2}{r^2-r_1^2}+r^2dx^2
-	\end{equation}
-	For the holographic entanglement entropy
-	\begin{equation}
-	r_1\rightarrow ir_1
-	\end{equation}
-	There is no topological obstacle in global AdS, so one can do the replacement above to get the holographic entanglement entropy in global AdS from the HEE in planer BTZ.
-	\begin{equation}
-	S_f=\frac{c}{3}ArcSinh(\frac{1}{r_1a}\sin(lr_1))
-	\end{equation}
-
-\pagebreak
-\subsection{Boundary modular flows}
+\section{The boundary story: modular flow \& entanglement entropy}
+
+\subsection{Boundary modular flow}
 
@@
 		= x^2_\pm - t^2_\pm
-		= (\frac{{\tilde L}}{2})^2
+		= (\frac{\tilde{l}}{2})^2
 	$, where $x_\pm = -x_\mp$, and same for $t_\pm, u_\pm, v_\pm$. 
@@
 	\begin{equation}
-		x_\pm = \pm \frac{{\tilde L}}{2} \cosh \theta,
-	\quad
-		t_\pm = \pm \frac{{\tilde L}}{2} \sinh \theta,
+		x_\pm = \pm \frac{\tilde{l}}{2} \cosh \theta,
+	\quad
+		t_\pm = \pm \frac{\tilde{l}}{2} \sinh \theta,
 	\end{equation}
@@
 	\begin{aligned}
-		\xi_\mrm{CFT} &= \frac{2\pi}{{\tilde L}} \bigg\{
-			\pqty{
-				\pqty{
-					(\tfrac{{\tilde L}}{2})^2
+		\xi_\mrm{CFT} &= \frac{2\pi}{\tilde{l}} \bigg\{
+			\pqty{
+				\pqty{
+					(\tfrac{\tilde{l}}{2})^2
 					- (t^2 + x^2)
@@
 				\pqty{
-					(\tfrac{{\tilde L}}{2})^2
+					(\tfrac{\tilde{l}}{2})^2
 					+ (t^2 + x^2)
@@
 		\xi_\mrm{CFT}|_{t = 0} 
-		= \frac{2\pi}{{\tilde L}}
-			\pqty{
-				(\tfrac{{\tilde L}}{2})^2
+		= \frac{2\pi}{\tilde{l}}
+			\pqty{
+				(\tfrac{\tilde{l}}{2})^2
 				- x^2
@@
 		\beta(x)
-		= \frac{2\pi}{{\tilde L}}
-			\pqty{
-				\pqty{\tfrac{{\tilde L}}{2}}^2
+		= \frac{2\pi}{\tilde{l}}
+			\pqty{
+				\pqty{\tfrac{\tilde{l}}{2}}^2
 				- x^2
@@
 	\begin{equation}
-	S= \frac{c}{3} \int_{-{\tilde L}/2}^{{\tilde L}/2}
-			\frac{{\tilde L}/2}{({\tilde L}/2)^2-x^2}dx,
+	S= \frac{c}{3} \int_{-\tilde{l}/2}^{\tilde{l}/2}
+			\frac{\tilde{l}/2}{(\tilde{l}/2)^2-x^2}dx,
 	\end{equation}
 	The indefinite integral $
-		\int \frac{{\tilde L}/2}{({\tilde L}/2)^2-x^2}dx
-		= \mop{arctanh}\frac{2x}{{\tilde L}}
+		\int \frac{\tilde{l}/2}{(\tilde{l}/2)^2-x^2}dx
+		= \mop{arctanh}\frac{2x}{\tilde{l}}
 %		\rightarrow\mrm{CFT}
-	$ diverges as $x\rightarrow {\tilde L}/2$, so one needs a cutoff:
-	\begin{equation}
-	S=\frac{c}{3}\int_{-{\tilde L}/2+\epsilon}^{{\tilde L}/2-\epsilon}
-		\frac{{\tilde L}/2}{({\tilde L}/2)^2-x^2}dx
+	$ diverges as $x\rightarrow \tilde{l}/2$, so one needs a cutoff:
+	\begin{equation}
+	S=\frac{c}{3}\int_{-\tilde{l}/2+\epsilon}^{\tilde{l}/2-\epsilon}
+		\frac{\tilde{l}/2}{(\tilde{l}/2)^2-x^2}dx
 	=\frac{2c}{3} \mop{arctanh} \pqty{
-			1-\frac{2\epsilon}{{\tilde L}}
+			1-\frac{2\epsilon}{\tilde{l}}
 		}
@@
 		\mop{arctanh} \pqty{
-			1-\frac{2\epsilon}{{\tilde L}}
-		}\rightarrow \frac{1}{2}\log\frac{{\tilde L}}{\epsilon}
+			1-\frac{2\epsilon}{\tilde{l}}
+		}\rightarrow \frac{1}{2}\log\frac{\tilde{l}}{\epsilon}
 	\end{equation}
@@
 	\begin{equation}
-	S=\frac{c}{3}\log\frac{{\tilde L}}{\epsilon}
+	S=\frac{c}{3}\log\frac{\tilde{l}}{\epsilon}
 	\end{equation}
@@
 	S=\frac{c}{3}\int_{- L/2}^{L/2}
-		\frac{{\tilde L}/2}{({\tilde L}/2)^2-x^2}dx
-		={c\over6} \mop{arctanh} {2x\over {\tilde L}}\bigg|^{L/2}_{-{L/2}}
+		\frac{\tilde{l}/2}{(\tilde{l}/2)^2-x^2}dx
+		={c\over6} \mop{arctanh} {2x\over \tilde{l}}\bigg|^{L/2}_{-{L/2}}
 	\end{equation}   }
@@
 
-	***
-
-	In the thermal CFT$_2$,
-	\begin{equation}
-	w=e^{\frac{2\pi z}{\beta}}
-	\end{equation}
-	From this transformation between the cylinder and the plane, we can find the "local" temperature $\tilde{\beta}$
-	\begin{equation}
-	\tilde{\beta}(x)=2\pi\frac{sinh[\pi(x+l_b)/\beta]sinh[\pi(x-l_b)/\beta]}{sinh(2\pi l_b/\beta)}
-	\end{equation}
-	After integrating out,
-	\begin{equation}
-	f(x)=\frac{\log(sinh\frac{\pi(l_b+x)}{\beta})-\log(sinh\frac{\pi(l_b-x)}{\beta})}{2\pi}
-	\end{equation}
-	\sidenote{The relation between $l_b$ and $l$ comes from the gravitational side, [explain through coordinate map]}
-	\begin{equation}
-	2l_b=Arccoth(\frac{r_c\cosh(lr_1/2)}{\sqrt{r_1^2+r_c^2\sinh^2(lr_1/2)}})/r_1
-	\end{equation}
-	where
-	\begin{equation}
-	r_1=\frac{2\pi}{\beta}
-	\end{equation}
-	is the outer horizon, and $r_c$ is the cutoff, related to the deformation parameter $\lambda$. The entanglement entropy reads,
-	\begin{equation}
-	S(L=2l)=\frac{\pi c}{6}(f(l)-f(-l))=\frac{c}{3}\log(\frac{r_c}{r_1}\sinh(l r_1)+\sqrt{1+\frac{r_c^2}{r_1^2}\sinh^2(l r_1)})
-	\end{equation}
-	The C-function is
-	\begin{equation}
-	C(l)=lS'(l)=\frac{c}{3}lr_1\coth(lr_1)\sqrt{\frac{r_c^2}{r_c^2+r_1^2csch^2(l r_1)}}
-	\end{equation}
-	\begin{equation}
-	C(L)=\frac{L\pi c}{3\beta}\coth\frac{L\pi}{\beta}\sqrt{\frac{1}{1+\frac{4\pi^2\epsilon^2}{\beta^2\sinh^2\frac{L\pi}{\beta}}}}
-	\end{equation}
-	In CFT
-	\begin{equation}
-	S(L)=\frac{c}{3}\log(\frac{\beta}{\pi \epsilon}\sinh\frac{L\pi}{\beta})
-	\end{equation}
-	\begin{equation}C(L)=\frac{L\pi c}{3\beta}\coth\frac{L\pi}{\beta}
-	\end{equation}
-
-\section{Bulk story}
-	This reproduces known results in e.g.~\cite{Lashkari:2016idm,Czech:2019vih,Apolo:2020qjm} \sidenote{[more citations needed]}. We first compute everything in Poincar\'e $\mrm{AdS}_3$ for simplicity. 
-\subsection{Bulk modular flows for Poincar\'e $\mrm{AdS}_3$}
+\pagebreak
+\section{Zero temperature: the bulk modular flow for Poincar\'e $\mrm{AdS}_3$}
+
 	We follow the recipe from the swing surface proposal \cite{Apolo:2020bld,Apolo:2020qjm} to extend the boundary modular flow to the bulk, by matching symmetries of the bulk and the boundary. 
+	We first compute everything in Poincar\'e $\mrm{AdS}_3$ for simplicity. 
+	This reproduces known results in e.g.~\cite{Lashkari:2016idm,Czech:2019vih,Apolo:2020qjm} \sidenote{[more citations needed]}.
 
@@
 	$, where $x_\pm = -x_\mp$, and same for $t_\pm, u_\pm, v_\pm$. 
-	$L_\infty$ is the coordinate length of the boundary interval $\mcal{A}$ at the asymptotic infinity; this corresponds to the field theory side ${\tilde L}$. 
+	$L_\infty$ is the coordinate length of the boundary interval $\mcal{A}$ at the asymptotic infinity; this corresponds to the field theory side $\tilde{l}$. 
 	For now the coordinates $u_\pm, v_\pm, x_\pm, t_\pm$ and the coordinate length $L_\infty$ are all specified at $z\to 0$, i.e.~at the \textbf{asymptotic boundary}.
@@
 	$, namely $\theta$ is constant along the RT surface.
-
-	{\color{red} use $l_u,\,l_v$}
 
@@
 
-The RT surface is the set of the fixed points of the modular flow, ....bifurcating surface....
-
 \eq{ &\pqty{
@@
 	We note that the $\pdd{z}$ term vanishes in the following two cases:
-	\begin{itemize}%[noitemsep,topsep=0pt]
+	\begin{itemize}[noitemsep,topsep=0pt]
 	\item as $z\to 0$, i.e.~near the asymptotic boundary;
@@
 
-\subsubsection{Zero temperature: cutoff Poincar\'e $\mrm{AdS}_3$ and the loss of $2\pi$ periodicity}
+\subsection{Cutoff Poincar\'e $\mrm{AdS}_3$ and the loss of $2\pi$ periodicity}
 
@@
 However, if we restrict to the field theory living at constant cutoff $z = z_c$, which corresponds to a \TTbar deformed theory \cite{McGough:2016lol,Lewkowycz:2019xse} \sidenote{[more citations needed]}, since it has no knowledge of the $\pdd{z}$ component of $\xi$, we should reduce it to a modular flow within the $z = z_c$ plane by, e.g.~projecting the $z$ component out, which leaves us:
-
-	{\color{red} delete
 	\begin{equation}
@@
 	Which no longer has normalized $\beta$ if $z_c \ne 0$.
-}
 
@@
 
-\subsubsection{Restoring the $2\pi$ periodicity by following the flow}
+\subsection{Restore the $2\pi$ periodicity by following the flow}
 
@@
 \pagebreak
-\subsection{Gravitational charges}
+\section{Finite temperature: entanglement entropy as gravitational charges}
 
@@
 
-\subsubsection{Finite temperature: modular flow in $\mrm{BTZ}_3$ and entanglement entropy}
+\subsection{Modular flow in $\mrm{BTZ}_3$ and entanglement entropy}
 \textbf{Summary:} We map the the modular flow in the Poincar\'e $\mrm{AdS}_3$ vacuum to the BTZ background, and compute the entanglement entropy as gravitational charge.
@@
 \pagebreak
-\subsubsection{BTZ with constant cutoff}
+\subsection{BTZ with constant cutoff}
 \textbf{Summary:} We then consider constant $r$ cutoff in the Schwarzschild coordinates, which corresponds to the proposal of \cite{McGough:2016lol}.
@@
 
+\pagebreak
 \appendix
-
 \section{Modular flow for Poincar\'e $\mrm{AdS}_3/\mrm{CFT}_2$}
@@
 	\end{gather}
-
 	We note that the $\pdd{z}$ term vanishes in the following two cases:
-	\begin{itemize}%[noitemsep,topsep=0pt]
+	\begin{itemize}[noitemsep,topsep=0pt]
 	\item as $z\to 0$, i.e.~near the asymptotic boundary;

### 2021-08-07 alpha/CutoffModularFlow/notes.tex
Add more tweaks to the note on modular flow

@@
 
-	\item Coordinate length of the boundary interval $\mcal{A}$ at the asymptotic infinity is denoted as $L_\infty$; the coordinate length at finite cutoff is denoted as $L$.
+	\item Coordinate length of the boundary interval $\mcal{A}$ at the asymptotic infinity is denoted as $\tilde{l}$; the coordinate length at finite cutoff is denoted as $L$.
 For an interval lying on the constant time slice $t = 0$ in the Poincar\'e patch, we have $L = \Delta x$; for a boosted interval, we have $
@@
 
-	In such case there is a generalized Rindler transformation $f$ that maps the casual domain $\mcal{D}$ to a patch $\{(\tau,\tilde{x})\}$ in some noncompact generalized Rindler spacetime, with $\pdd{\tau}$ an isometry of the spacetime.
+	In such case there is a generalized Rindler transformation $f$ that maps the casual domain $\mcal{D}$ to a patch $\{(\tau,x')\}$ in some noncompact generalized Rindler spacetime, with $\pdd{\tau}$ an isometry of the spacetime.
 Then we have:
@@
 	\begin{equation}
-		\xi_\mrm{CFT} = 2\pi \sum_{n=0,\pm 1} \pqty{
+		\xi = 2\pi \sum_{n=0,\pm 1} \pqty{
 				s_n L_n - \bar{s}_n \bar{L}_n
@@
 	\begin{aligned}
-		\xi_\mrm{CFT} &= \frac{2\pi}{\tilde{l}} \bigg\{
+		\xi &= \frac{2\pi}{\tilde{l}} \bigg\{
 			\pqty{
@@
 	\begin{equation}
-		\xi_\mrm{CFT}|_{t = 0} 
+		\xi|_{t = 0} 
 		= \frac{2\pi}{\tilde{l}}
@@
 
-	However, after the \TTbar-deformation, the scaling and special conformal transformations are no longer symmetries of the theory, so we cannot simply take $\xi_\mrm{CFT}$ as the modular flow in the deformed theory.
+	However, after the \TTbar-deformation, the scaling and special conformal transformations are no longer symmetries of the theory, so we cannot simply take $\xi$ as the modular flow in the deformed theory.
 	But we shall see that by properly specifying the integration range, this is enough to give us the entanglement entropy of a \TTbar-deformed theory.
@@
 
-	Let's see this trick in action in CFT$_2$; the \textit{entropy density} is given by:
-	\begin{equation}
-	s = \frac{c}{6} \frac{2\pi}{\beta(x)}
-	\end{equation}
-	in terms of the effective inverse temperature $\beta(x)$, and the total entropy of the interval $\mcal{A}$ is given by:
+	Let's see this trick in action in CFT$_2$; in terms of the effective inverse temperature $\beta(x)$, the \textit{entropy density} is given by:
+	\begin{equation}
+	s = \frac{c}{6} \frac{2\pi}{\beta(x)},
+	\end{equation}
+	while the total entropy of the interval $\mcal{A}$ is given by:
 	\begin{equation}
@@
 	\end{equation}
-
-	For example, for a single interval in CFT$_2$,
+	For a single interval in CFT$_2$,
 	\begin{equation}
@@
 				- x^2
-			} \,\pdd{t}
-	\end{equation}
-	\begin{equation}
+			} \,\pdd{t},
+	\quad
 	S= \frac{c}{3} \int_{-\tilde{l}/2}^{\tilde{l}/2}
-			\frac{\tilde{l}/2}{(\tilde{l}/2)^2-x^2}dx,
-	\end{equation}
-	The indefinite integral $
+			\frac{\tilde{l}/2}{(\tilde{l}/2)^2-x^2}dx
+	\end{equation}
+	The indefinite integral:
+	\begin{equation}
 		\int \frac{\tilde{l}/2}{(\tilde{l}/2)^2-x^2}dx
 		= \mop{arctanh}\frac{2x}{\tilde{l}}
-%		\rightarrow\mrm{CFT}
-	$ diverges as $x\rightarrow \tilde{l}/2$, so one needs a cutoff:
+	\end{equation}
+	diverges as $x\rightarrow \tilde{l}/2$, so one needs a cutoff:
 	\begin{equation}
@@
 		}
+	\label{eq:cft_local_entropy}
 	\end{equation}
@@
 	\end{equation}
-	So we get the usual result
+	So we get the usual result:
 	\begin{equation}
@@
 	\end{equation}
-
-	{\color{red} For TTbar,  \begin{equation}
-	S=\frac{c}{3}\int_{- L/2}^{L/2}
-		\frac{\tilde{l}/2}{(\tilde{l}/2)^2-x^2}dx
-		={c\over6} \mop{arctanh} {2x\over \tilde{l}}\bigg|^{L/2}_{-{L/2}}
-	\end{equation}   }
-	where integration range $L$ is related to $\tilde L$ by requiring that the distance to the pole at $\pm{\tilde L\over 2}$ is cutff
-	\eq{
-({\tilde L\over 2})^2=2\lambda+({ L\over 2})^2}
-
-%	{\color{red} looks wrong : Now for the cutoff field theory living at the boundary, where
-%	\begin{equation}
-%		\beta(x) = \frac{2\pi}{\sqrt{L^2 + 8\lambda}}
-%			\pqty{
-%				\pqty{\frac{L}{2}}^2
-%				- x^2
-%			} \,\pdd{t}
-%	\end{equation}}
-	The entanglement entropy is
-	\begin{equation}
-	S=\frac{c}{6}\mop{arctanh}\frac{2x}{\sqrt{L^2 + 8\lambda}}\Big|_{x=-L/2}^{x=L/2}
-	=\frac{c}{3}\mop{arctanh}\frac{L}{\sqrt{L^2 + 8\lambda}}
-	=\frac{c}{3}\mop{arcsinh}\frac{L}{2\sqrt{2\lambda}}
-	\end{equation}
-	with the Casini--Huerta $C(L)$-function:
-	\begin{equation}
-	C(l)=\frac{c}{3}\frac{1}{\sqrt{1+\frac{8\lambda}{L^2}}}
-	\end{equation}
-	Which agrees with \cite{Lewkowycz:2019xse}. \sidenote{This provides a field theory side calculation of the cutoff entanglement entropy, based on the input of the modular flow $\xi$. }
-	Note that we only need to know the modular flow $\xi$ along the $t = 0$ slice. We don't need to know the full modular flow\footnote{
-		\sidenote{This seems to be consistent with holographic entropy, a la Lewkowycz--Maldacena \cite{Lewkowycz:2013nqa}, where the charge only depends linearly on $\xi$ along the RT surface, as long as $\xi$ is a Killing vector.
-See \eqref{kdef}.
-}
-	}.
 
@@
 		(t,x)
-		&\longmapsto (\tau,\tilde{x}),
+		&\longmapsto (\tau,{x}),
 	\end{aligned}
@@
 	\end{equation}
-	Note that although $\xi$ is a Killing vector when it's extended to the bulk, it is only a \textit{conformal Killing vector} when it's restricted to the boundary.
+	Note that although $\xi$ is a Killing vector when it's extended to the bulk (as is done in later sections), it is only a \textit{conformal Killing vector} when it's restricted to the boundary.
 
@@
 		= \dd{t}^2 + \dd{x}^2
-		= \Omega^2(\tau,\tilde{x}) \pqty{
-				\dd{\tau}^2 + \dd{\tilde{x}}^2
+		= \Omega^2(\tau,x') \pqty{
+				\dd{\tau}^2 + \dd{x'}^2
 			},
@@
 		\Omega_{t = 0} = \pdv{t}{\tau}
-		= \frac{\beta(x)}{2\pi}
-	\end{equation}
-	Here we've properly rescaled the $\tilde{x}$ coordinate to make the $(\tau,\tilde{x})$ coordinates conformally flat.
-
-	In the case where the theory is conformally invariant, one can further drop the conformal factor $\Omega^2(\tau,\tilde{x})$ from the metric, while the thermal entropy of the system remains unchanged.
+		= \frac{\beta(x)}{2\pi},
+	\end{equation}
+	where we've properly rescaled the $x'$ coordinate to make the $(\tau,x')$ coordinates conformally flat.
+
+	In the case where the theory is conformally invariant, one can further drop the conformal factor $\Omega^2(\tau,x')$ from the metric, while the thermal entropy of the system remains unchanged.
 We now have a flat annulus:
 	\begin{equation}
-		\tilde{\mcal{R}}
-		= S^1_\beta \times [0,\tilde{L}],
-	\quad
-		\dd{\tilde{s}}^2
+		\mcal{R}'
+		= S^1_\beta \times [0,l'],
+	\quad
+		\dd{s'}^2
 		= \frac{1}{\Omega^2} \dd{s}^2
-		= \dd{\tau}^2 + \dd{\tilde{x}}^2
+		= \dd{\tau}^2 + \dd{x'}^2
 	\end{equation}
 	This is the corresponding geometry of a thermal partition function, with a constant temperature $\beta_\tau = 2\pi$. 
-	Now $\pdd{\tau}$ is truly a Killing vector of $\tilde{\mcal{R}}$. 
+	Now $\pdd{\tau}$ is truly a Killing vector of $\mcal{R}'$. 
 	In this case the thermal entropy is extensive: the total entropy $S_\mcal{A}$ is proportional to the size of the system:
@@
 		S_\mcal{A}
-		= \frac{c}{6} \tilde{L}
-	\end{equation}
-	Here $\tilde{L}$ denotes the $\tilde{\mcal{R}}$ length of the interval $f(\mcal{A})$:
-	\begin{equation}
-		\tilde{L}
-		= \int_{f(\mcal{A})} \dd{\tilde{s}}
+		= \frac{c}{6} l'
+	\end{equation}
+	Here $l'$ denotes the $\mcal{R}'$ length of the interval $f(\mcal{A})$:
+	\begin{equation}
+		l'
+		= \int_{f(\mcal{A})} \dd{s'}
 		= \int_{f(\mcal{A})} \frac{\dd{s}}{\Omega}
@@
 But now we are committed to a purely field theoretical calculation, so we will apply Cardy's arguments here, which do not rely on holographic duality.
-	}, where we have: 
-%	First note that by rescaling the Rindler map $f$ we can tune the temperature of the Rindler spacetime $\mcal{R}$ to be arbitrarily high.
+	}.
+%	, where we have: 
+	First note that by rescaling the Rindler map $f$ we can tune the temperature of the Rindler spacetime $\mcal{R}$ to be arbitrarily high.
 We've chosen $\beta_\tau = 2\pi$ only for convenience.
@@
 check!]}
-%	Therefore we may apply the high temperature (or low $\beta$) limit of the Cardy formula; namely, by modular invariance of the partition function, we have:
-%	\begin{equation}
-%	\begin{aligned}
-%		Z[\tau = i\tfrac{\beta}{2\pi}]
-%		&= Z[-\tfrac{1}{\tau} = i\tfrac{2\pi}{\beta}],
-%	\\[1ex]
-%		Z[\beta]
-%		&= Z[\beta\to \tfrac{4\pi^2}{\beta}] \\
-%		&= \Tr e^{
-%			-\frac{4\pi^2}{\beta} \pqty{
-%				L_0 + \tilde{L}_0 - \frac{c}{12}
-%			} \frac{\tilde{L}}{2\pi}
-%		}, \quad \beta\ll 1 \\
-%		&\sim e^{
-%			\frac{4\pi^2}{\beta}
-%			\frac{c}{12}
-%			\frac{\tilde{L}}{2\pi}
-%		}
-%		= e^{
-%			\frac{2\pi}{\beta}
-%			\frac{c}{12} \tilde{L}
-%		},
-%	\end{aligned}
-%	\end{equation}
-%	Here we've used the saddle point approximation and assumed that the vacuum (the $h = \tilde{h} = 0$ state) contribution dominates. The entropy is thus given by:
+	Therefore we may apply the high temperature (or low $\beta$) limit of the Cardy formula; namely, by modular invariance of the partition function, we have:
+	\begin{equation}
+	\begin{aligned}
+		Z[\tau = i\tfrac{\beta}{2\pi}]
+		&= Z[-\tfrac{1}{\tau} = i\tfrac{2\pi}{\beta}],
+	\\[1ex]
+		Z[\beta]
+		&= Z[\beta\to \tfrac{4\pi^2}{\beta}] \\
+		&= \Tr e^{
+			-\frac{4\pi^2}{\beta} \pqty{
+				L_0 + \bar{L}_0 - \frac{c}{12}
+			} \frac{l'}{2\pi}
+		}, \quad \beta\ll 1 \\
+		&\sim e^{
+			\frac{4\pi^2}{\beta}
+			\frac{c}{12}
+			\frac{l'}{2\pi}
+		}
+		= e^{
+			\frac{2\pi}{\beta}
+			\frac{c}{12} \tilde{L}
+		},
+	\end{aligned}
+	\end{equation}
+	Here we've used the saddle point approximation and assumed that the vacuum (the $h = \tilde{h} = 0$ states) contribution dominates. The entropy is thus given by:
 	\begin{equation}
 		S
-%		= \pqty{
-%				1 - \beta\, \pdd{\beta}
-%			} \log Z[\beta]
-		= \frac{2\pi}{\beta} \frac{c}{6} \tilde{L}
+		= \pqty{
+				1 - \beta\, \pdd{\beta}
+			} \log Z[\beta]
+		= \frac{2\pi}{\beta} \frac{c}{6} l'
 	\end{equation}
 	With $\beta = \beta_\tau = 2\pi$, we recover the result $
-		S = \frac{c}{6} \tilde{L}
+		S = \frac{c}{6} l'
 	$.
@@
 	Note that in the above arguments we've assumed conformal symmetry, which we no longer have after a \TTbar deformation.
-However, as we've demonstrated above, it seems that this trick still works for the deformed theory.
-\sidenote{Perhaps the reason is again, that the conformal factor vanishes at the endpoints, due to $2\pi$ periodicity of $\xi$, which we will show in later sections.
+On the other hand, as an irrelevant deformation, \TTbar is often understood as some sort of cutoff of the original CFT.
+With this intuition in mind, let's tweak \eqref{eq:cft_local_entropy} as follows:
+	\begin{equation}
+	S=\frac{c}{3}\int_{-l/2}^{l/2}
+		\frac{\tilde{l}/2}{(\tilde{l}/2)^2-x^2}dx
+		={c\over3} \mop{arctanh} {2x\over \tilde{l}}\bigg|^{l/2}_{-{l/2}}
+	\end{equation}   
+	where the integration range is given by the length $l$ of the interval $\mcal{A}$ in the \TTbar-deformed theory. If we \textit{assume} that $l$ is related to $\tilde l$ by:
+	\begin{equation}
+		\Big(\frac{\tilde{l}}{2}\Big)^2
+		= \Big(\frac{l}{2}\Big)^2 + 2\lambda
+	\label{eq:cutoff_relation}
+	\end{equation}
+	Then the entanglement entropy is given by
+	\begin{equation}
+	S=\frac{c}{6}\mop{arctanh}\frac{2x}{\sqrt{l^2 + 8\lambda}}\bigg|_{x=-l/2}^{x=l/2}
+	=\frac{c}{3}\mop{arctanh}\frac{l}{\sqrt{l^2 + 8\lambda}}
+	=\frac{c}{3}\mop{arcsinh}\frac{l}{2\sqrt{2\lambda}}
+	\end{equation}
+	with the Casini--Huerta $C(L)$-function:
+	\begin{equation}
+	C(l)=\frac{c}{3}\frac{1}{\sqrt{1+\frac{8\lambda}{L^2}}}
+	\end{equation}
+	Which agrees with \cite{Lewkowycz:2019xse}. \sidenote{This provides a field theory side calculation of the cutoff entanglement entropy, based on the input of the modular flow $\xi$. }
+	Note that we only need to know the modular flow $\xi$ along the $t = 0$ slice. We don't need to know the full modular flow\footnote{
+		\sidenote{This seems to be consistent with holographic entropy, a la Lewkowycz--Maldacena \cite{Lewkowycz:2013nqa}, where the charge only depends linearly on $\xi$ along the RT surface, as long as $\xi$ is a Killing vector.
+See \eqref{kdef}.
+}
+	}.
+
+	As we've demonstrated above, it seems that the local temperature trick still works for the deformed theory, assuming the mysterious relation \eqref{eq:cutoff_relation}.
+The meaning of this relation will be made clear in the holographic setting.
+As for why the trick still works in the absence of conformal symmetry, \sidenote{perhaps the reason is again, that one can deploy a Rindler-like map as in \cite{Lewkowycz:2019xse}, where the conformal factor vanishes at the endpoints, due to $2\pi$ periodicity of $\xi$, which we will show in later sections.
 }
@@
 	We first compute everything in Poincar\'e $\mrm{AdS}_3$ for simplicity. 
-	This reproduces known results in e.g.~\cite{Lashkari:2016idm,Czech:2019vih,Apolo:2020qjm} \sidenote{[more citations needed]}.
+	This reproduces known results in e.g.~\cite{Lashkari:2016idm,Czech:2019vih,Apolo:2020qjm} \needcites.
 
@@
 		= x^2_\pm - t^2_\pm
-		= (\frac{L_\infty}{2})^2
+		= (\frac{\tilde{l}}{2})^2
 	$, where $x_\pm = -x_\mp$, and same for $t_\pm, u_\pm, v_\pm$. 
-	$L_\infty$ is the coordinate length of the boundary interval $\mcal{A}$ at the asymptotic infinity; this corresponds to the field theory side $\tilde{l}$. 
-	For now the coordinates $u_\pm, v_\pm, x_\pm, t_\pm$ and the coordinate length $L_\infty$ are all specified at $z\to 0$, i.e.~at the \textbf{asymptotic boundary}.
+	$\tilde{l}$ is the coordinate length of the boundary interval $\mcal{A}$ at the asymptotic infinity; this corresponds to the field theory side $\tilde{l}$. 
+	For now the coordinates $u_\pm, v_\pm, x_\pm, t_\pm$ and the coordinate length $\tilde{l}$ are all specified at $z\to 0$, i.e.~at the \textbf{asymptotic boundary}.
 Note that the RT surface lies on the plane $
@@
 	\begin{aligned}
-		\xi &= \frac{2\pi}{L_\infty} \bigg\{
-			\pqty{
-				\pqty{
-					(\tfrac{L_\infty}{2})^2 - z^2
+		\xi &= \frac{2\pi}{\tilde{l}} \bigg\{
+			\pqty{
+				\pqty{
+					(\tfrac{\tilde{l}}{2})^2 - z^2
 					- (t^2 + x^2)
@@
 				\pqty{
-					(\tfrac{L_\infty}{2})^2 - z^2
+					(\tfrac{\tilde{l}}{2})^2 - z^2
 					+ (t^2 + x^2)
@@
 	\end{gather}
-
-\eq{ &\pqty{
-					(\tfrac{L_\infty}{2})^2 - z^2
-					- (t^2 + x^2)
-				} \cosh\theta
-				+ 2tx \sinh\theta =0\\
-			&	x\sinh\theta
-				- t\cosh\theta
-				}
-
 	We note that the $\pdd{z}$ term vanishes in the following two cases:
@@
 	\begin{equation}
-		\pqty{\frac{L}{2}}^{\!\!2}
-		= \pqty{\frac{L_\infty}{2}}^{\!\!2} - z_c^2,
+		\pqty{\frac{l}{2}}^{\!\!2}
+		= \bigg(\frac{\tilde{l}}{2}\bigg)^{\!\!2} - z_c^2,
 	\quad
@@
 	\begin{aligned}
-		\xi^{\mrm{FT}}_c
-		\equiv \proj{\text{/\!/}} \xi|_{z_c}
+		\xi_c
+		\equiv \xi^\text{/\!/}|_{z_c}
 		= \frac{2\pi}{
@@
 
-	 In fact, compared to the $z_c \to 0$ situation which \textit{does} have $\beta = 1$, $\xi^{\mrm{FT}}_c$ is rescaled by a factor of $
-		\frac{L}{L_\infty}
+	 In fact, compared to the $z_c \to 0$ situation which \textit{does} have $\beta = 1$, $\xi_c$ is rescaled by a factor of $
+		\frac{L}{\tilde{l}}
 		= 1/\sqrt{1 + (2z_c/L)^2}
@@
 	\begin{equation}
-		\beta^{\mrm{FT}}_c
+		\beta_c
 		= \sqrt{1 + (2z_c/L)^2}
@@
 %	\vspace{-2ex}
-	\caption{Integral surface of the modular flow starting from $t = 0,\ z = z_c$. Here we've chosen $\frac{L_\infty}{2} = 1$ while $z_c = 0.4$.}
+	\caption{Integral surface of the modular flow starting from $t = 0,\ z = z_c$. Here we've chosen $\frac{\tilde{l}}{2} = 1$ while $z_c = 0.4$.}
 	\end{figure}
@@
 		\dv{z}{t}
-		= \frac{2tz}{\alpha z^2 + t^2 - (L_\infty/2)^2},
+		= \frac{2tz}{\alpha z^2 + t^2 - (\tilde{l}/2)^2},
 	\quad
@@
 		= \frac{
-				(L_\infty/2)^2 + \alpha z_c^2
+				(\tilde{l}/2)^2 + \alpha z_c^2
 				- \sqrt{
-					\pqty{(L_\infty/2)^2 - \alpha z_c^2}^2
+					\pqty{(\tilde{l}/2)^2 - \alpha z_c^2}^2
 					+ 4t^2 \alpha z_c^2
@@
 	\begin{aligned}
-		t &= \frac{L_\infty}{2} \frac{
+		t &= \frac{\tilde{l}}{2} \frac{
 				\pqty{\rho - T_u T_v}
@@
 	\\
-		x &= \frac{L_\infty}{2} \frac{
+		x &= \frac{\tilde{l}}{2} \frac{
 				\sqrt{\rho^2 - T_u^2 T_v^2}
@@
 	\\
-		z &= \frac{L_\infty}{2} \frac{
+		z &= \frac{\tilde{l}}{2} \frac{
 				\sqrt{2T_u T_v}
@@
 	This is a BTZ \textit{black string} with \textit{non-compact} $\phi$ direction. 
-	One can check that the $(u,v,\rho)$ coordinates indeed cover the $L_\infty$-sized entanglement wedge specified by $\xi$. 
+	One can check that the $(u,v,\rho)$ coordinates indeed cover the $\tilde{l}$-sized entanglement wedge specified by $\xi$. 
 	Here we've reused the variable names $(u,v)$ for the planar BTZ coordinates, and we've tweaked the expressions in \cite{Song:2016gtd} to be more symmetric in $(u,v)$.
@@
 	\begin{equation}
-		z_c = \frac{L_\infty}{2} \frac{
+		z_c = \frac{\tilde{l}}{2} \frac{
 				\sqrt{2}\,T
@@
 
-		The flow starts from $t = 0,\ z = z_c$, and here we've chosen $\frac{L_\infty}{2} = 1$ while $z_c = 0.1,\,0.2,\,\cdots,\,0.9$. 
+		The flow starts from $t = 0,\ z = z_c$, and here we've chosen $\frac{\tilde{l}}{2} = 1$ while $z_c = 0.1,\,0.2,\,\cdots,\,0.9$. 
 		Note that the asymptotic boundary $z\to 0$ corresponds to $\rho \to \infty$. 
@@
 					\cosh\,(2T\phi) \sqrt{
-						1 - (\frac{2z_c}{L_\infty})^2 \sinh^2 (2T\phi)
+						1 - (\frac{2z_c}{\tilde{l}})^2 \sinh^2 (2T\phi)
 					} - 1
@@
 		\sqrt{
-			1 - (\frac{2z_c}{L_\infty})^2 \sinh^2 (2T\phi)
+			1 - (\frac{2z_c}{\tilde{l}})^2 \sinh^2 (2T\phi)
 		}
@@
 First, the coordinates are different: in \eqref{eq:poincare2btz} we have $(u,v,\rho)$ and here we have Schwarzschild $(t,r,\phi)$; but that's not essential.
-What's crucial is that here, we map \textbf{the \textsl{whole} of Poincar\'e into BTZ with a \textsl{compact} $\phi$ circle}, while before in \eqref{eq:poincare2btz} we map a \textbf{$L_\infty$-sized wedge in Poincar\'e into BTZ with a \textsl{non-compact} $\phi$ line}.
+What's crucial is that here, we map \textbf{the \textsl{whole} of Poincar\'e into BTZ with a \textsl{compact} $\phi$ circle}, while before in \eqref{eq:poincare2btz} we map a \textbf{$\tilde{l}$-sized wedge in Poincar\'e into BTZ with a \textsl{non-compact} $\phi$ line}.
 
@@
 	Now we consider constant cutoff at $r = r_c$.
-Again we need to trade the $L_\infty$ above with the coordinate length of the interval $L$ at the cutoff $r_c$.
+Again we need to trade the $\tilde{l}$ above with the coordinate length of the interval $L$ at the cutoff $r_c$.
 The relation can be solved by looking at the geodesic equation, which is slightly non-trivial this time:
 	\begin{equation}
-		\frac{\cosh L_\infty T}{\cosh LT}
+		\frac{\cosh \tilde{l} T}{\cosh LT}
 		= \frac{r_c}{\sqrt{r_c^2 - 4T^2}}
@@
 		= \int_{r = \mrm{const}} \dd{\phi} (\chi_\xi)_\phi
-		= \frac{\var{T} \coth L_\infty T}{2G}
+		= \frac{\var{T} \coth \tilde{l} T}{2G}
 			\int_{-L/2}^{L/2} \dd{\phi}
@@
 				1 - {\frac{r}{\sqrt{r^2 - 4T^2}}}
-				\frac{\cosh 2T\phi}{\cosh TL_\infty}
+				\frac{\cosh 2T\phi}{\cosh T\tilde{l}}
 			}
@@
 		- \pqty{t - \frac{t_+ + t_-}{2}}^{\!\!2}
-		= \pqty{\frac{L_\infty}{2}}^{\!\!2}
+		= \pqty{\frac{\tilde{l}}{2}}^{\!\!2}
 		= \pqty{\frac{x_+ - x_-}{2}}^{\!\!2}
@@
 	&&& \text{i.e.}\ \,
-		L_\infty^2
+		\tilde{l}^2
 		= \pqty{x_+ - x_-}^2
@@
 		= x^2_\pm - t^2_\pm
-		= (\frac{L_\infty}{2})^2
+		= (\frac{\tilde{l}}{2})^2
 	$, where $x_\pm = -x_\mp$, and same for $t_\pm, u_\pm, v_\pm$. 
@@
 	\begin{equation}
-		x_\pm = \pm \frac{L_\infty}{2} \cosh \theta,
-	\quad
-		t_\pm = \pm \frac{L_\infty}{2} \sinh \theta,
-	\end{equation}
-	For now the coordinates $u_\pm, v_\pm, x_\pm, t_\pm$ and the coordinate length $L_\infty$ are all specified at $z\to 0$, i.e.~at the \textbf{asymptotic boundary}.
+		x_\pm = \pm \frac{\tilde{l}}{2} \cosh \theta,
+	\quad
+		t_\pm = \pm \frac{\tilde{l}}{2} \sinh \theta,
+	\end{equation}
+	For now the coordinates $u_\pm, v_\pm, x_\pm, t_\pm$ and the coordinate length $\tilde{l}$ are all specified at $z\to 0$, i.e.~at the \textbf{asymptotic boundary}.
 Note that the RT surface lies on the plane $

### 2021-08-12 alpha/SUSY/susy.tex
Add comments on conjugations to the SUSY notes

@@
 
+\usepackage{pifont}
+\newcommand{\quabla}{\text{\ding{113}\hspace{.1em}}}
+
 \begin{document}
@@
 
-	\item[\cite{Tachikawa:2018sae}]\fullcite{Tachikawa:2018sae}
-		\par \textit{Recommended by Chi-Ming.}
-
 	\item[\cite{Figueroa-OFarrill:2001xbd}]\fullcite{Figueroa-OFarrill:2001xbd}
@@
 
-	\item[\cite{VanProeyen:1999ni}]\fullcite{VanProeyen:1999ni}
-		\par \textit{Recommended by Mauricio.}
+	\item[\cite{Hori:2003ic}]\fullcite{Hori:2003ic}
+
+	\item[\cite{Freedman:2012zz}]\fullcite{Freedman:2012zz}
 
@@
 	\begin{itemize}
-	\item[\cite{Freedman:2012zz}]\fullcite{Freedman:2012zz}
 
@@
 
-	\item[\cite{Hori:2003ic}]\fullcite{Hori:2003ic}
+	\item[\cite{figueroa2015majorana}]\fullcite{figueroa2015majorana}
 
-	\item[\cite{figueroa2015majorana}]\fullcite{figueroa2015majorana}
+	\item[\cite{VanProeyen:1999ni}]\fullcite{VanProeyen:1999ni}
+		\par \textit{Recommended by Mauricio.}
+
+	\item[\cite{Tachikawa:2018sae}]\fullcite{Tachikawa:2018sae}
+		\par \textit{Recommended by Chi-Ming.}
 
@@
 	\begin{enumerate}[noitemsep,topsep=0pt]
-	\item \textcite{Argyres:1996abc}, Section 5
+	\item \textcite{Argyres:1996abc}, \S5
 	\item \textcite{Wess:1992cp}, Chapter II
@@
 
-	Remarks:
+	\textit{Remarks:}
 	\begin{enumerate}
-	\item $Q$ carries a spinor index $\alpha$ (or $\dot{\alpha}$), so it lives in the spinor representation of the Lorentz group, or equivalently, the fundamental representation of the Spin group\footnote{
+	\item $Q$ carries a spinor index $\alpha$ (or $\dot{\alpha}$), so it lives in the spinor representation of the Lorentz group, or equivalently, the fundamental (spin-$\frac{1}{2}$) representation of the Spin group\footnote{
 		See a surprisingly good summary of the topic on \wikiref{https://en.wikipedia.org/wiki/Representation\_theory\_of\_the\_Lorentz\_group\#Finite-dimensional\_representations}{Representation theory of the Lorentz group \# Finite-dimensional representations}.
+
+		Note that higher spin supercharges are not allowed, since they cannot combine into $P_\mu$ or $J_{\mu\nu}$, but they must, due to Coleman--Mandula.
+Moreover in 4D higher spin charges simply violate Haag--Łopuszański--Sohnius (the SUSY extension of Coleman--Mandula).
+A thorough introduction of this is given in \S32 of \textcite{Weinberg:2000cr}, Vol.\,III.
+		See also \https{physics.stackexchange.com/a/418025}. 
 	}.
 
-	\item The structure of this algebra can be generalized to $D$ dimensions. $(Q_\alpha, \bar{Q}_{\dot{\alpha}})$ forms a \mbox{(symplectic)}\footnote{
-		This happens when the metric signature $p - q \equiv 3,4,5\,\mop{mod}\,8$.
-See e.g.~\textcite{figueroa2015majorana}, or Section~3.3 and 12.1 of \textit{Supergravity} \cite{Freedman:2012zz}, or Mauricio Romo's lecture notes.
-In Lorentzian signature ($p = D-1, q = 1$), this corresponds to $D = 5,6,7$ dimensions; see e.g.~Table B.1 of \textcite{Polchinski:1998rq}.
+	\item The structure of this algebra can be generalized to $D$ dimensions. In general, $Q$ transforms as a \mbox{(symplectic)}\footnote{
+		Symplectic Majorana happens when the metric signature $p - q \equiv 3,4,5\,\mop{mod}\,8$.
+See e.g.~\textcite{figueroa2015majorana}, or \S3.3 and \S12.1 of \textit{Supergravity} \cite{Freedman:2012zz}, or Mauricio Romo's lecture notes.
+In Lorentzian signature ($p = D-1, q = 1$), this corresponds to $D = 5,6,7$ dimensions; see e.g.~Table B.1 of \textcite{Polchinski:1998rr}.
 A worked example in 6D is given by \cite{Gustavsson:2001uw}.
+
 		Also, higher form centeral charges are possible in higher dimensions. 
@@
 		Pseudo-Majorana spinors exist for spacetime signature $(p,q)$ if and only if Majorana spinors exist for $(q,p)$.
-See \textcite{figueroa2015majorana} and Section~3.3 of \textit{Supergravity} \cite{Freedman:2012zz}
-	} Majorana spinor, where $\bar{Q}$ denotes charge conjugation \cite{Freedman:2012zz}.
+See \textcite{figueroa2015majorana} and \S3.3 of \textit{Supergravity} \cite{Freedman:2012zz}.
+	} Majorana spinor.
+
+	\item Complex conjugation maps $Q_\alpha \mapsto \bar{Q}_{\dot{\alpha}}$.
+The supercharges have to live in a \textit{real} representation, where both $Q_\alpha$ and $\bar{Q}_{\dot{\alpha}}$ are included.
+Otherwise they can't combine into the Hermitian $P_\mu$.
+Here we've chosen to write the 4D charges as Weyl spinor $Q_\alpha$ with 2 complex components, but they are not actually Weyl; they are secretly Majorana with 4 real components.
+The translation between these two descriptions is documented in \S3.4.2 of \textit{Supergravity} \cite{Freedman:2012zz}.
 
@@
 	\end{enumerate}
+\subsection{More on conjugations}
+	The bar notation in e.g.\ $\bar{Q}$ denotes \textit{some sort of} conjugation, usually Dirac or charge conjugation in 4D.
+More precisely, for a Dirac spinor $\psi^\bullet = (\lambda^\alpha, \bar{\chi}_{\dot{\alpha}})$, up to various constant coefficients (which may depend on the dimension $D$), we have:
+	\begin{equation*}
+	\newcommand{\coef}{\text{\tiny\#\,}}
+	\renewcommand{\arraystretch}{1.2}
+	\begin{array}{rccll}
+	\textbf{Type of Conjugation}
+		& \psi^\bullet 
+		&=& (\lambda^\alpha,\bar{\chi}_{\dot{\alpha}})
+		\hspace*{.5em}
+		& \textbf{Notes}\\
+\midrule
+	\text{Complex}
+		& (\psi^*)^\bullet
+		&\sim& (\bar{\lambda}^{\dot{\alpha}},\chi_{\alpha})
+		& \text{Exchange $\alpha$ with $\dot{\alpha}$} \\
+	\text{Dirac}
+		& (i\psi^\dagger\gamma_0)_\bullet
+		&\sim& ({\chi}_\alpha,\bar{\lambda}^{\dot{\alpha}})
+		& \text{Switch chirality (handedness)} \\
+	\text{Majorana}
+		& (\psi\,\mcal{C})_\bullet = (\psi^\mrm{T} C)_\bullet
+		&\sim& (\bar{\lambda}_{{\alpha}},{\chi}^{\dot{\alpha}})
+		& \text{Transpose (dual representation)} \\
+	\text{Charge}
+		& (i\gamma_0\,C^{-1} \psi^*)^\bullet
+		&\sim& ({\chi}^\alpha,\bar{\lambda}_{\dot{\alpha}})
+		& [\text{Majorana}]^{-1} \circ [\text{Dirac}]
+	\end{array}
+	\end{equation*}
+	Remarks:
+	\begin{itemize}
+
+	\item In components, the bar notation is actually redundant.
+It simply indicates that we have taken some sort of conjugation \cite{Freedman:2012zz}.
+To know what kind of conjugation this is, we have to read the indices.
+
+		\begin{itemize}
+		\item Dotted indices denote the complex conjugate representation.
+
+		\item The position of an index indicates how it transforms under the Spin group (covariant spinor or its dual). 
+		\end{itemize}
+
+	\item $C\id{^\bullet_\bullet}$ is the charge conjugation matrix, while $\mcal{C}_{\bullet\bullet}$ is the corresponding bilinear form.
+$\mcal{C}_{\bullet\bullet}$ works like a metric, and is used to raise and lower the spinor indices.
+It is anti-symmetric, compatible with the anti-commuting $\psi$.
+
+	\item Charge conjugation is basically Dirac conjugation, but without the lowering of indices with $\mcal{C}$.
+We see that when $\lambda = \chi$, $\psi$ is invariant under charge conjugation: $\psi^C = \psi$.
+This is the reality condition, and $\psi = (\chi^\alpha,\bar{\chi}_{\dot{\alpha}})$ is a \textit{Majorana spinor}.
+
+	\item Charge conjugation is convenient as it preserves the ordering of matrices (since it does not include a transpose).
+On the other hand it works just like Dirac conjugation, switching between left and right-handed components.
+
+	\item When the indices are suppressed, they are assumed to be contracted with $\mcal{C}$. In this case we do need to specify the meaning of $\bar{\psi}$.
+
+	When the indices are suppressed, charge and Dirac conjugations are equivalent (up to some constant coefficients) as they differ only by index positions.
+Similarly, complex and Majorana conjugations are equivalent.
+
+	For majorana spinors (such as the supercharges $Q$), we have $\lambda = \chi$, and all four conjugations are equivalent when the indices are suppressed.
+
+	\item In 4D we usually take $\bar{\psi}$ to denote Dirac conjugate, as in \S2 of \textit{Supergravity} \cite{Freedman:2012zz}.
+However, since \S3 they switch their conventions and $\bar{\psi}$ denotes Majorana conjugate instead\footnote{
+		See \S3.2 of \textcite{Freedman:2012zz}. 
+	}. \textcite{Polchinski:1998rr} seems to define $\bar{\psi}$ as Dirac conjugate\footnote{
+		See (B.1.29) of \textcite{Polchinski:1998rr}, Vol.\,II. 
+	}.
+
+	\end{itemize}
+
+	\newparagraph
+	These have always been confusing concepts for me.
+For a pedagogical treatment in general dimensions, see \S2 and \S3 of \textit{Supergravity} \cite{Freedman:2012zz}.
+One can then compare it to the results in 4D, discussed in Appendix A.4 to A.8 of \textcite{Figueroa-OFarrill:2001xbd}.
+Fortunately their conventions seem to agree with each other, most of the time.
+
 \subsection{Equal amount of bosonic \& fermionic (excited) states}
@@
 	\end{equation}
-	\vspace{-\baselineskip}
+	\vspace*{-\baselineskip}
 	\begin{equation}
@@
 $F_V = J_0 + \bar{J}_0$ is the $\mrm{U}(1)_V$ generator, while $F_A = \bar{J}_0 - J_0$ is the $\mrm{U}(1)_A$ generator.
-The \mbox{subscript A} stands for ``axial'', meaning that $Q^i$ transforms in an axial representation of $\mrm{U}(1)$.
+The \mbox{subscript A} stands for ``axial'', meaning that $Q^i$ transforms in an axial representation of $\mrm{U}(1)$, where the group action discriminates between left and right-handed components.
 For more on this, see e.g.~\cite{MauricioStuff}.
@@
 		\begin{itemize}[
-			topsep=.5ex,noitemsep,
-			leftmargin=4em
+%			topsep=0ex,
+			noitemsep,
+			leftmargin=3em
 		]
@@
 		\end{itemize}
-		\vspace{-.8\baselineskip}
+%		\vspace{-.8\baselineskip}
 	}.
@@
 	\references{
-	\begin{enumerate}[noitemsep,topsep=0pt]
-	\item \textcite{Argyres:1996abc}, Section 6
+	\begin{enumerate}[noitemsep,topsep=0pt,beginpenalty=10000]
+	\item \textcite{Argyres:1996abc}, \S6
 	\item \citetitle{Hori:2003ic} \cite{Hori:2003ic}, Chapter 12
@@
 	\begin{enumerate}[noitemsep,topsep=0pt]
-	\item \textcite{Argyres:1996abc}, Section 7
-	\item \textcite{Intriligator:1995au}, Section 2
+	\item \textcite{Argyres:1996abc}, \S7
+	\item \textcite{Intriligator:1995au}, \S2
 	\item \textcite{Seiberg:1993vc}
@@
 
-\pagebreak[3]
+%\pagebreak[3]
 
-	\begin{quotation}
-		``If a bare parameter is unnaturally set to zero, radiative corrections lead to a renormalized non-zero value.
-Therefore, if we want a small renormalized value \textit{without} a symmetry, the bare value has to be \textit{fine-tuned}.''
-
-		\vspace{1ex}\hfill
-		--- \textcite{Seiberg:1993vc} on naturalness. 
-	\end{quotation}
 	\begin{equation}
@@
 
+	\begin{quotation}
+		``If a bare parameter is unnaturally set to zero, radiative corrections lead to a renormalized non-zero value.
+Therefore, if we want a small renormalized value \textit{without} a symmetry, the bare value has to be \textit{fine-tuned}.''
+
+		\vspace{1ex}\hfill
+		--- \textcite{Seiberg:1993vc} on naturalness. 
+	\end{quotation}
+
+%	\vspace{\baselineskip}
 	\noindent%
@@
 	\item \textbf{Philosophy:} we \textit{believe} that the UV theory \textit{should} have almost no coupling and a lot of fields; think of string theory (where we have only one coupling) and string field theory (where there are $\infty$-ly many fields).
-In fact, this was explicitly pointed out in Section 4.2 of \mbox{\textcite{Dine:1996ui}}\footnote{
+In fact, this was explicitly pointed out in \S4.2 of \mbox{\textcite{Dine:1996ui}}\footnote{
 		Oh my, it's \texttt{hep-ph}! This must come from a simpler time when SUSY is expected to be found by experiments. 
@@
 This justifies the trick of turning on $\lambda$.
-For more on this, see Section 2.1.3 of \textcite{Banados:2016zim}%
-%	, and also Section 1.2 of \cite{Lai:2021abc}
+For more on this, see \S2.1.3 of \textcite{Banados:2016zim}%
+%	, and also \S1.2 of \cite{Lai:2021abc}
 	.
@@
 	There are again two proposals to fix $a_1(\mu)$:
-	\begin{itemize}
+	\begin{itemize}[beginpenalty=10000]
 	\item Consider $\lambda\to 0$, $m\to 0$ with arbitrary $m/\lambda$. We should have \cite{Intriligator:1995au}:
@@
 %	\item
-	\textcite{Argyres:1996abc}, Section 7
+	\textcite{Argyres:1996abc}, \S8
+%	\end{enumerate}
+	}\vspace{.5\baselineskip}
+
+\section{SUSY Breaking}
+	\speaker{Xia ``Summer'' Gu}\\
+	\references{%
+%	\begin{enumerate}[noitemsep,topsep=0pt]
+%	\item
+	\textcite{Argyres:1996abc}, \S9
+%	\end{enumerate}
+	}\vspace{.5\baselineskip}
+
+\section{Super Gauge Theory}
+	\speaker{Yuan Zhong}\\
+	\references{%
+%	\begin{enumerate}[noitemsep,topsep=0pt]
+%	\item
+	\textcite{Argyres:1996abc}, \S10
 %	\end{enumerate}

### 2021-09-04 alpha/SUSY/susy.tex
Add major comments on charge conjugation in SUSY

@@
 
-	The generic form of a 4D SUSY algebra with centeral charge is given by \cite{Wess:1992cp}:
+	The generic form of a 4D SUSY algebra with central charge is given by \cite{Wess:1992cp}:
 	\begin{equation}
@@
 For example, $\sqrt{-1}$ gives us $i$, and $\sqrt{\Box^2} = \sqrt{-P_u P^\mu}$ gives us the $\gamma$ matrices (thanks to Dirac).
+On the other hand, the energy $P^0$ is now written as a sum of $\abs{Q}^2$, which guarantees its positivity.
+See \S9 of \textcite{Argyres:1996abc}.
 
@@
 
-		Also, higher form centeral charges are possible in higher dimensions. 
+		Also, higher form central charges are possible in higher dimensions. 
 	} (pseudo)\footnote{
@@
 See \textcite{figueroa2015majorana} and \S3.3 of \textit{Supergravity} \cite{Freedman:2012zz}.
+
+		From now on we will \textit{not} distinguish between pseudo-Majorana and Majorana spinors, as they are both ``real'' under \textit{charge conjugation}, which we will define in \S1.1. 
 	} Majorana spinor.
@@
 
-	\item $(Q_\alpha, \bar{Q}_{\dot{\alpha}})$ act like (fermionic) annilation and creation operators (ladder operators).
+	\item $(Q_\alpha, \bar{Q}_{\dot{\alpha}})$ act like (fermionic) annihilation and creation operators (ladder operators).
 We can write down its unitary irreducible representations (unitary irreps) on the Hilbert space, following Wigner's little group representation for the Poincar\'e group.
@@
 \subsection{More on conjugations}
-	The bar notation in e.g.\ $\bar{Q}$ denotes \textit{some sort of} conjugation, usually Dirac or charge conjugation in 4D.
-More precisely, for a Dirac spinor $\psi^\bullet = (\lambda^\alpha, \bar{\chi}_{\dot{\alpha}})$, up to various constant coefficients (which may depend on the dimension $D$), we have:
+	The bar in e.g.\ $\bar{Q}$ denotes \textit{some sort of} conjugation. In 4D it usually means Dirac or charge conjugation. 
+	Dirac spinors exist in any dimension, but let's first look at \textit{even} dimensions, where a Dirac spinor can always be decomposed into 2 Weyl spinors:
+	\begin{equation}
+		\psi^\bullet
+		= (\lambda^\alpha, \bar{\chi}_{\dot{\alpha}})
+	\end{equation}
+	This is because in even dimensions we have a chirality operator $\Gamma$ \cite{Polchinski:1998rr}: 
+	\begin{equation}
+		D = 2k + 2,
+	\quad
+		\Gamma = i^{-k} \Gamma^0 \cdots \Gamma^{D-1},
+	\quad
+		\Gamma^2 = 1,
+	\quad
+		\{\Gamma, \Gamma^\mu\} = 0
+	\end{equation}
+	$\Gamma$ is the generalization of $\gamma_5$ in 4D, and serves as a chirality operator that distingushes the left and right handed part of a Dirac spinor.
+This gives us Weyl spinors with a definite chirality.
+We can then diagonalize $\Gamma$ such that it's all $+1$ on the upper half diagonal, and all $-1$ on the lower half diagonal.
+
+	There is no such chirality operator in odd dimensions, therefore in odd dimensions we don't have Weyl spinors at all, and there are only (symplectic) (pseudo) Majorana spinors.
+For example, in 5D $\gamma_5$ itself gets ``promoted'' to be the last $\gamma$ matrix\footnote{
+		For more on this, see \S3.1.7 of \textit{Supergravity} \cite{Freedman:2012zz}. 
+	}.
+
+	Back to even dimensions where $
+		\psi^\bullet
+		= (\lambda^\alpha, \bar{\chi}_{\dot{\alpha}})
+	$, we have, up to various constant coefficients (which may depend on the dimension $D$),
 	\begin{equation*}
+	\small
 	\newcommand{\coef}{\text{\tiny\#\,}}
@@
 		&=& (\lambda^\alpha,\bar{\chi}_{\dot{\alpha}})
-		\hspace*{.5em}
+%		\hspace*{.5em}
 		& \textbf{Notes}\\
@@
 		&\sim& (\bar{\lambda}^{\dot{\alpha}},\chi_{\alpha})
-		& \text{Exchange $\alpha$ with $\dot{\alpha}$} \\
+		& \text{Exchange $\alpha$ with $\dot{\alpha}$}
+\\
 	\text{Dirac}
@@
 		&\sim& ({\chi}_\alpha,\bar{\lambda}^{\dot{\alpha}})
-		& \text{Switch chirality (handedness)} \\
+		& \text{Switch chirality (handedness)}
+\\[.5ex]
 	\text{Majorana}
@@
 		&\sim& (\bar{\lambda}_{{\alpha}},{\chi}^{\dot{\alpha}})
-		& \text{Transpose (dual representation)} \\
+			_{D\equiv 4},
+		& \\
+	&
+		&\sim& ({\chi}_{\dot{\alpha}},\bar{\lambda}^{{\alpha}})
+			_{D\equiv 2},
+		\,\cdots
+		& \text{Transpose (dual representation)}
+\\[.5ex]
 	\text{Charge}
@@
 		&\sim& ({\chi}^\alpha,\bar{\lambda}_{\dot{\alpha}})
+			_{D\equiv 4},
+		& \\
+	&
+		&\sim& (\bar{\lambda}^{\dot{\alpha}},{\chi}_\alpha)
+			_{D\equiv 2},
+		\,\cdots
 		& [\text{Majorana}]^{-1} \circ [\text{Dirac}]
@@
 	Remarks:
-	\begin{itemize}
+	\begin{itemize}[beginpenalty=10000]
 
@@
 		\begin{itemize}
-		\item Dotted indices denote the complex conjugate representation.
+		\item Dotted indices such as $\dot{\alpha}$ denote the complex conjugate representation.
 
@@
 
-	\item Charge conjugation is basically Dirac conjugation, but without the lowering of indices with $\mcal{C}$.
-We see that when $\lambda = \chi$, $\psi$ is invariant under charge conjugation: $\psi^C = \psi$.
+	\item $\mcal{C}$ is sensitive about the dimension $D$, and so is the Majorana conjugation.
+For example, in 4D $\mcal{C}$ is block diagonal, thus it does not switch $\lambda$ with $\chi$.
+In 2D, however, $\mcal{C}$ is basically the antisymmetric $\epsilon_{\alpha\dot{\alpha}}$, therefore it does switch $\lambda$ with $\chi$.
+
+	\item In 4D, charge conjugation is basically Dirac conjugation, but without the lowering of indices with $\mcal{C}$.
+We see that in 4D, when $\lambda = \chi$, $\psi$ is invariant under charge conjugation: $\psi^C = \psi$.
 This is the reality condition, and $\psi = (\chi^\alpha,\bar{\chi}_{\dot{\alpha}})$ is a \textit{Majorana spinor}.
 
+	In 2D, on the other hand, we see that Majorana conjugation is basically Dirac conjugation, but without the complex conjugation $\alpha \leftrightarrow \dot{\alpha}$.
+Therefore, charge conjugation is basically complex conjugation.
+The reality condition $\psi^C = \psi$ now reduces to $\lambda^* = \lambda$, $\chi^* = \chi$.
+This gives us 2 independent \textit{Majorana--Weyl} spinors.
+
 	\item Charge conjugation is convenient as it preserves the ordering of matrices (since it does not include a transpose).
-On the other hand it works just like Dirac conjugation, switching between left and right-handed components.
-
-	\item When the indices are suppressed, they are assumed to be contracted with $\mcal{C}$. In this case we do need to specify the meaning of $\bar{\psi}$.
-
-	When the indices are suppressed, charge and Dirac conjugations are equivalent (up to some constant coefficients) as they differ only by index positions.
-Similarly, complex and Majorana conjugations are equivalent.
-
-	For majorana spinors (such as the supercharges $Q$), we have $\lambda = \chi$, and all four conjugations are equivalent when the indices are suppressed.
-
-	\item In 4D we usually take $\bar{\psi}$ to denote Dirac conjugate, as in \S2 of \textit{Supergravity} \cite{Freedman:2012zz}.
+One can think of it as a physical replacement for the na\"ive complex conjugation.
+
+	\item When the indices are suppressed, matrices are assumed to be contracted with $\mcal{C}$. In this case we do need to specify the meaning of $\bar{\psi}$.
+
+	In 4D we usually take $\bar{\psi}$ to denote Dirac conjugate, as in \S2 of \textit{Supergravity} \cite{Freedman:2012zz}.
 However, since \S3 they switch their conventions and $\bar{\psi}$ denotes Majorana conjugate instead\footnote{
 		See \S3.2 of \textcite{Freedman:2012zz}. 
-	}. \textcite{Polchinski:1998rr} seems to define $\bar{\psi}$ as Dirac conjugate\footnote{
+	}. \textcite{Polchinski:1998rr} seems to consistently define $\bar{\psi}$ as Dirac conjugate\footnote{
 		See (B.1.29) of \textcite{Polchinski:1998rr}, Vol.\,II. 
@@
 	These have always been confusing concepts for me.
+For a friendly introduction to Majorana spinors in 4D, check out \textcite{Pal:2010ih}.
 For a pedagogical treatment in general dimensions, see \S2 and \S3 of \textit{Supergravity} \cite{Freedman:2012zz}.
 One can then compare it to the results in 4D, discussed in Appendix A.4 to A.8 of \textcite{Figueroa-OFarrill:2001xbd}.
-Fortunately their conventions seem to agree with each other, most of the time.
+See also \textcite{Tachikawa:2018sae}.
+Fortunately their conventions seem to agree with each other, for most of the time.
 

### 2021-09-09 alpha/SUSY/susy.tex
Add comments on R symmetry in SUSY & style tweaks

@@
 \pagenumbering{arabic}
-\thispagestyle{empty}
 
@@
 
+%\pagebreak\thispagestyle{headless}
 \addtocounter{section}{-1}
@@
 
+\pagebreak\thispagestyle{headless}
 \section{Algebra \& Unitary Representations}
@@
 
+%\pagebreak[3]
+
 	There is more story behind \eqref{eq:fermion_number_R_symmetry}; in fact, $F$ generates an automorphism of the SUSY algebra.
 It is part of the \textit{R-symmetry}, and can be added to the algebra as an extension.
-	In Lorentzian 4D, the maximal amount of R-symmetry\footnote{
-		This comes from the maximal extension of the SUSY algebra. It is common that, given a specific theory, only some of the R-symmetries are preserved, while others are broken. 
-	} is $\mrm{U}(\mcal{N})$, and $F$ is the generator of the $\mrm{U}(1)_V$ subgroup; here the \mbox{subscript V} stands for ``vector'', meaning that the supercharge $Q^i$ transforms as a vector with index $i$ under the $\mrm{U}(1)_V$ action: all components labeled by $i$ gains the same phase shift under $\mrm{U}(1)$.
+	In Lorentzian 4D, the maximal amount of R-symmetry is $\mrm{U}(\mcal{N})$, and $F$ is the generator of the central $\mrm{U}(1)$ subgroup:
+	\begin{equation}
+		\mrm{U}(\mcal{N})
+		= \mrm{U}(1) \rtimes \mrm{SU}(\mcal{N})
+	\end{equation}
+	$\mrm{U}(\mcal{N})$ comes from the maximal extension of the SUSY algebra.
+It is common that, given a specific theory, only some of the R-symmetries are preserved, while others are broken.
+Even the fermion number $e^{i\theta F} \in \mrm{U}(1)$ can be broken, but it seems that the $\mbb{Z}_2$ subgroup generated by $e^{i\pi F} = (-1)^F$ always survives \needcites.
 
@@
 $F_V = J_0 + \bar{J}_0$ is the $\mrm{U}(1)_V$ generator, while $F_A = \bar{J}_0 - J_0$ is the $\mrm{U}(1)_A$ generator.
-The \mbox{subscript A} stands for ``axial'', meaning that $Q^i$ transforms in an axial representation of $\mrm{U}(1)$, where the group action discriminates between left and right-handed components.
-For more on this, see e.g.~\cite{MauricioStuff}.
+	The \mbox{subscript V} stands for ``vector'', meaning that the supercharge $Q^i$ transforms as a vector with index $i$ under the $\mrm{U}(1)_V$ action: all components labeled by $i$ gains the same phase shift under $\mrm{U}(1)$.
+The \mbox{subscript A} stands for ``axial'', meaning that $Q^i$ transforms in an axial representation of $\mrm{U}(1)$, where the group action discriminates between left and right-handed components\footnote{
+		This might generate some confusions when compared to 4D: if we think of $Q,\bar{Q}$ as two components of a Majorana spinor (in the Weyl basis), then the fermion number $\mrm{U}(1)$ looks like an \textit{axial} symmetry, as is given in \eqref{eq:fermion_number_R_symmetry}.
+This is indeed the case in 4D, where charge conjugation switches $Q$ and $\bar{Q}$, as described in \S1.1.
+We will come back to this in \S\ref{subsect:anomaly}, where we discuss axial anomaly.
+
+		However, charge conjugation in 2D looks very different: it actually switches between $Q_+$ and $Q_-$, where $\mquote{\pm}$ is the $\mcal{N} = 2$ indices.
+This is consistent with our discussions in \S1.1.
+		For example, a chiral $(2,0)$ theory is constructed not by throwing away $\bar{Q}$, but by throwing away $Q_-$ and $\bar{Q}_-$; see \S12.5.2 of \textit{Mirror Symmetry} \cite{Hori:2003ic}. 
+	}.
 

### 2021-09-10 alpha/SUSY/susy.tex
Add comments on SUSY vacua & illustrations

@@
 	\begin{enumerate}[noitemsep,topsep=0pt,beginpenalty=10000]
-	\item \textcite{Argyres:1996abc}, \S6
+	\item \textcite{Argyres:1996abc}, \S6 \& \S9
 	\item \citetitle{Hori:2003ic} \cite{Hori:2003ic}, Chapter 12
@@
 	\begin{enumerate}%[noitemsep]
-	\item \textbf{Reality condition:} this lead to a vector multiplet. We shall revisit this in the future. For now we will proceed to the next condition, which is:
+	\item \textbf{Reality condition:} $\bar{V} = V$, this gives us the vector superfield; see \S10.1 of \textcite{Argyres:1996abc}.
+We shall revisit this in \S6.
+For now we will proceed to the next condition, which is:
 
@@
 
+\subsection{$F$-term and the classical vacua}
 	A full expansion of the Lagrangian $\mcal{L}$ (including $\mcal{K}$ and $\mcal{W}$) reveals that $F$ has no kinetic term and is quadratic in the action, thus it can be safely integrated out.
-The result gives us the potential for the scalar component $\phi$:
+The equation of motion is simply:
+	\begin{equation}
+		F^i = - g^{i\wbar{i}}
+			\pdd{\wbar{i}} \wbar{\mcal{W}}
+		+ \frac{1}{2}\,\Gamma^i_{jk} \psi^j \psi^k
+	\end{equation}
+	This gives a potential for the scalar component $\phi$:
 	\begin{equation}
 		V(\phi,\bar{\phi})
+		= \norm{\pd\mcal{W}}^2
 		= g^{i\wbar{j}}
@@
 			\,\pdd{\wbar{j}} \wbar{\mcal{W}}
-		= \abs{\pd\mcal{W}}^2
-	\end{equation}
+		\xlongequal{\vev{\psi \psi} = 0}
+		g_{i\wbar{j}} F^i \wbar{F}^{\wbar{j}}
+		= \norm{F}^2
+	\end{equation}
+	Here we've used the fact that $\vev{\psi \psi} = 0$, so only the $\pd\mcal{W}$ term contributes to the VEV $\vev{F}$.
+Note that the non-zero fermion propagator is given by $\vev{\psi \bar{\psi}}$ instead.
+
 	The classical vacua satisfy $\pd_i V = 0$. 
@@
 		\pdd{i} V
-		= \pdd{i}\,\pqty\big{\abs{\pdd{i} \mcal{W}}^2}
+		= \pdd{i}\,\pqty\big{\norm{\pdd{i} \mcal{W}}^2}
 		= 0
@@
 %	\vspace{\baselineskip}
+	\pagebreak[3]
 	\noindent%
@@
 
-	\textit{Note:} in \cite{Seiberg:1993vc} Seiberg chose to call the non-renormalization in SUSY \textit{a violation of naturalness} in the conventional sense, since in the IR we see no global symmetry but we still have many vanishing amptitudes.
+	\textit{Note:} in \cite{Seiberg:1993vc} Seiberg chose to call the non-renormalization in SUSY \textit{a violation of naturalness} in the conventional sense, since in the IR we see no global symmetry but we still have many vanishing amplitudes.
 But I believe it's okay to understand this as a new sense of naturalness, where the vanishing of amplitudes (or the rigid form of the potentials) is protected by supersymmetry and some ``hidden'' global symmetries (that are spontaneously broken in the IR).
@@
 		I believe this is the so-called ``un-Higgs-ing'' procedure, and the unHiggsed field is called a ``spurion''. \\
-		\hspace*{2em}
 		See \https{physicsforums.com/threads/spurion-symmetry.205417}.
 	}. On the other hand, as pointed out by \textcite{Argyres:1996abc}, we can simply think of this as ``just a trick''\footnote{
-		See also \https{physics.stackexchange.com/q/110926/162487}. 
+		See also \https{physics.stackexchange.com/q/110926}. 
 	}:
@@
 	\end{equation}
-	Here we've been cavaliar about constant shifts of $\mcal{W}$, as they do not affect the physics\footnote{
-		On the other hand, constant shifts of $V = \abs{\pd\mcal{W}}^2$ \textit{do} matter in SUSY theories, as they are related to spontaneous SUSY breaking; see \S2 and \S4. 
+	Here we've been cavalier about constant shifts of $\mcal{W}$, as they do not affect the physics\footnote{
+		On the other hand, constant shifts of $V = \norm{\pd\mcal{W}}^2$ \textit{do} matter in SUSY theories, as they are related to spontaneous SUSY breaking; see \S2 and the following sections. 
 	}. 
@@
 
-\section{Moduli Space of Vacua}
+\section{Singularies from Integrating Out}
 	\speaker{Yuan Zhong}\\

### 2021-09-10 Strings2020/strings5/strings5.tex
Update strings note on compact boson & orbifolds

@@
 % !TeX TXS-program:bibliography = biber -l zh__pinyin --output-safechars %
-%% !TeX TS-program = lualatex
+%% !TeX TS-program = pdflatex
 %%% LuaLaTeX is required for `tikz-feynman`
@@
 	This, in fact, holds for any field theory\footnote{
-		Reference: discussions in \textit{Polchinski}, Chapter 8. 
+		Reference: discussions in \textit{Polchinski}, \S8.2. 
 	} defined for $X\in S^1$, including the ordinary quantum mechanics (a classical field theory) on $S^1$.
@@
 				},
+	\label{eq:modes_circle}
 	\end{gather}
@@
 At this stage $P$ is \textit{not} fixed, and we should sum over all states with various $P$.
-To go to the canonical ensemble, we do a Legendre transform and trade $\tau_1$ for some $P_0$.
-This is implemented by a Laplace / Fourier transform $\int \dd{\tau_1} e^{-i\,(2\pi\tau_1) P_0}$ of the partition function.
-
-	In string theory, we should actually work with the canonical ensemble (and eventually, the \textit{micro-}canonical ensemble), since we would like to impose the \textit{level matching condition}, namely $P_0 = 0$.
-
-	However, in string theory, the Legendre transform is implicit as we integrate along $\tau_1$ in the moduli space; roughly speaking, we have:
+To go to the canonical ensemble, we do a Legendre transform and trade $\tau_1$ for some $P'$.
+This is implemented by a Laplace / Fourier transform of the partition function:
+	\begin{equation}
+		\int \dd{\tau_1} e^{-i\,(2\pi\tau_1) P'}
+	\end{equation}
+	In string theory, we should actually work with the canonical ensemble (and eventually, the \textit{micro-}canonical ensemble), since we would like to impose the \textit{level matching condition}, namely $P' = 0$.
+This is because we would like to gauge the worldsheet translation along $\sigma^1$ generated by $P$, which is understood as a redundancy.
+
+	However, in string theory, the Fourier transform is implicit as we integrate along $\tau_1$ in the moduli space; roughly speaking, we have:
 	\begin{equation}
 		\int \dd{\tau_1} e^{-i\,(2\pi\tau_1) (P - 0)}
-		\propto \delta(P - 0)
+		\sim \delta(P - 0)
 	\end{equation}
@@
 		This is nicely explained in David Tong's \href{https://www.damtp.cam.ac.uk/user/tong/string.html}{\textit{String Theory}}.
-See also section 6.3 of Blumenhagen et al, \textit{Basic Concepts of String Theory}.
-See also section 2.1, 2.2 of \arxiv{1912.07654} where the switch between ensembles is reviewed in the context of holography.
+See also \S6.3 of Blumenhagen et al, \textit{Basic Concepts of String Theory}.
+See also \S2.1, 2.2 of \arxiv{1912.07654} where the switch between ensembles is reviewed in the context of holography.
 	}.
@@
 
-	For the second term, note that:
+	For the second term, note that the action of $r$ on a state can be deduced from its action on the modes $\alpha_m, \tilde{\alpha}_m$, which is in turn induced from the action $r\colon X\mapsto -X$ through the mode expansion \eqref{eq:modes_circle}.
+In particular, we have $r: \alpha_{-m} \mapsto -\alpha_{-m}$, which means that\footnote{
+		Reference: Blumenhagen et al, \textit{Basic Concepts of String Theory}, \S10.5. 
+	}:
+	\begin{equation}
+		r\circ\alpha_{-m}\circ r^{-1}
+		= -\alpha_{-m},
+	\quad
+		r \ket{N_m}
+		\sim r \circ \alpha_{-m}^{N_m} \ket{0}
+		\sim (-1)^{N_m} \ket{N_m},
+	\end{equation}
 	\begin{equation}
@@
 	\end{equation}
-	In particular, it reverses $n,w$, hence $r$ insertion gives vanishing amplitude unless $n = w = 0$; the summation is very much similar to the $Z_{S^1}$ case, i.e. we have:
+	In particular, it reverses $n,w$, hence $r$ insertion gives vanishing amplitude unless $n = w = 0$. 
+	The summation is very much similar to the $Z_{S^1}$ case, i.e. we have:
 	\begin{equation}
@@
 	\end{equation}
+
+	Physically, $r$ invariant states are stationary waves:
+	\begin{equation}
+		\frac{1 + r}{2}
+			\ket*{(N_l),(\tilde{N}_l);n,w}
+		= \frac{1}{2} \pqty{
+			\ket*{(N_l),(\tilde{N}_l);n,w}
+			+ (-1)^{\sum_l (N_l + \tilde{N}_l)}
+			\ket*{(N_l),(\tilde{N}_l);-n,-w}
+		},
+	\end{equation}
+	which is a superposition of states with opposite momentum and winding, such that $\ave{p_L} = \ave{p_R} = 0$.
+Note that a general $r$ invariant state is a linear combination of such states and may have non-vanishing momentum: $\ave{p} \ne 0$.
+	In position space these states have unconstrained $x = x_L + x_R \in [0,\pi R]$. More precisely, if we define the position basis: $x\ket{x'} = \delta(x - x') \ket{x'}$, then we have:
+	\begin{equation}
+	\begin{aligned}
+		\mel{(N_l),(\tilde{N}_l);x}{\frac{1 + r}{2}}{
+			(N_l),(\tilde{N}_l);n
+		}
+		&\propto \frac{1}{2} \pqty{
+			e^{i\frac{n}{R}x}
+			+ (-1)^{\sum_l (N_l + \tilde{N}_l)}
+			e^{-i\frac{n}{R}x}
+		} \\
+		&= \bigg\{
+		\begin{aligned}
+			& \cos\tfrac{nx}{R}, 
+			&&\textstyle\sum_l (N_l + \tilde{N}_l)\,\ \text{even}
+		\\[.5ex]
+			& \sin\tfrac{nx}{R}, 
+			&&\textstyle\sum_l (N_l + \tilde{N}_l)\,\ \text{odd}
+		\end{aligned}
+	\end{aligned}
+	\end{equation}
+
+	The wave function $(\cos\frac{nx}{R})$ is what we expect: we get the same result if we turn off the oscillator modes $N, \tilde{N}$ altogether; in this case we have a worldline quantum mechanics with target $S^1/\mbb{Z}_2$, which is equivalent to the spacetime QFT on $S^1/\mbb{Z}_2$.
+Since we are only considering the worldline geometry $S^1$, we are restricting to the 1-particle sector of the spacetime QFT, which is again a quantum mechanical system.
+The wave functions compatible with $\mbb{Z}_2$ action are precisely given by $(\cos\frac{nx}{R})$.
+	On the other hand, the case with $(\sin\tfrac{nx}{R})$ doesn't seem to be $\mbb{Z}_2$ invariant in the position space.
+This is due to the $\mbb{Z}_2$ odd stringy excitations, which can be understood as some additional degrees of freedom, similar to the spin of a particle.
+This compensates for the $\mbb{Z}_2$ odd $(\sin\tfrac{nx}{R})$, and the full wave function is $\mbb{Z}_2$ invariant.
 
@@
 	\end{gather}
-	Apply the boundary condition on $X$, and we find that $x = \pi R w'$; however, due to the identification $X + 2\pi R \cong X \cong -X$, there are only two inequivalent choices: $x = 0$ and $x =\pi R$, which correspond to the string localized around either of the two fixed points of the $\mbb{Z}_2$ action.
+	Apply the boundary condition on $X$, and we find that $x = \pi R w$; however, due to the identification $X + 2\pi R \cong X \cong -X$, there are only two inequivalent choices:
+	\begin{equation}
+		x = 0,\quad x =\pi R,
+	\end{equation}
+	which correspond to the string localized around either of the two fixed points of the $\mbb{Z}_2$ action. There is no momentum or winding, not even in the mode expansion.
+
+	Intuitively, the twisted boundary condition is realized only when the string is stretched around the fixed points of the orbifold action.
+For example, an open string that ends on $X$ and $X + 2\pi R \in \mbb{R}^1$ becomes a closed winding string when we consider $\mbb{R}^1/(2\pi R\,\mbb{Z}) = S^1$.
+Similarly, an open string that ends on $\pm X$ becomes a closed string in the twisted sector, after we take $S^1/\mbb{Z}_2$.
 
@@
 	\end{aligned}
-	\\[1ex]
+	\\[1.5ex]
 		L_0
@@
 	The trace can then be computed, following the same recipe as before:
+	\begin{equation}
+		r\colon\ %
+			\ket{(N_l),(\tilde{N}_l);x}
+		\longmapsto (-1)^{\sum_l (N_l + \tilde{N}_l)}
+			\ket{(N_l),(\tilde{N}_l);-x},
+	\quad -x \equiv x,
+	\quad x = 0,\pi R,
+	\end{equation}
+	\vspace*{-1.2\baselineskip}
 	\begin{equation}
@@
 	\end{equation}
-	The first term is modular invariant, as is proved in \boxed{1}\,.
+	The first term is modular invariant, as is proven in \boxed{1}\,.
 
@@
 			labelindent=3em,labelsep=1pt,
-			topsep=.1\baselineskip
+			topsep=.1\baselineskip,
+			noitemsep
 		]

### 2021-11-22 alpha/BeyondAdSCFT/beyondAdS.tex
Add Wei's notes on holography beyond AdS/CFT

% !TeX spellcheck = en_US
% !TeX TS-program = pdflatex
% !BIB TS-program = biblatex
\documentclass[11pt,a4paper]{article}
\pdfoutput=1

\input{preamble.tex}

\usepackage{comment}
%\newcommand{\lui}[2]{\textcolor{red}{#1}\todo[color=yellow]{\scriptsize{L: #2}}}
\newcommand{\wei}[2]{\textcolor{magenta}{#1}\todo[color=yellow]{\scriptsize{WS: #2}}}
\newcommand{\wx}[2]{\textcolor{purple}{#1}\todo[color=teal]{\scriptsize{XL: #2}}}

\usepackage{xspace}
\newcommand{\TTbar}{\texorpdfstring{\ensuremath{T\bar{T}}}{TTbar}\xspace}
\newcommand{\arcsinh}{\ensuremath{\mop{arcsinh}}}
\renewcommand{\tilde}[1]{\ensuremath{\widetilde{#1}}}
\newcommand{\ads}[1]{AdS\ensuremath{_{#1}}}
\newcommand{\cft}[1]{CFT\ensuremath{_{#1}}}

\usepackage{enumitem}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{Holographic duality beyond AdS/CFT}

%\author[a]{Wen-Xin Lai,}
\author[a]{Wei Song}

\affiliation[a]{Yau Mathematical Sciences Center, Tsinghua University, Beijing 100084, China}

%  \emailAdd{apolo@mail.tsinghua.edu.cn, wsong2014@mail.tsinghua.edu.cn}

\abstract{
	Lecture notes for the Southeast Summer School on Strings and Stuff, 2021. 
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\maketitle
%\flushbottom
\setlength{\parskip}{.5\baselineskip}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}

	Since the discovery of AdS/CFT duality \cite{Maldacena:1997re}, we have greatly furthered our understanding of quantum gravity in asymptotically AdS backgrounds. However, there are plenty of non-AdS geometries in our real worlds, including:
	\begin{itemize}%[noitemsep]
	\item The Kerr metric of a rotation black hole, \sidenote{which ... };
	\item The asymptotically flat / Minkowski spacetime, which well approximates our current universe at a smaller length (and time) scale;
	\item The asymptotically de Sitter spacetime, which well approximates our current (and future) universe at a larger length scale, and also during the period of inflation;
	\item The FRW metric (or more precisely, the Friedmann-Lemaître-Robertson-Walker \cite{Friedmann:1924bb,Lemaitre:1933gd,Robertson:1935zz,Walker:1937} metric), which describes the evolution of our homogeneous and isotropic universe from the big bang to its ;
	\item and more ...
	\end{itemize}
	Much less is known about quantum gravity in these backgrounds.

\section{Brief review of \ads{3}/\cft{2}}

\section{Bottom-up approach: %based on
from asymptotic symmetry}

\section{Top-down approach: %in 
from string theory}

	String theory is a self-consistent theory of quantum gravity.

	The first example of microscopic counting of black hole entropy, discovered by Strominger-Vafa \cite{Strominger:1996sh}, comes from the \mbox{D1-D5-$P$} system in string theory.

	The first incarnation of holographic principle was realized by Maldacena \cite{Maldacena:1997re}, by a stack of D3 branes in type IIB string theory.

\subsection{The \mbox{D1-D5-$P$} system}

	Let us look at the \mbox{D1-D5-$P$} brane configuration in type IIB string theory. This is well-reviewed in \cite{David:2002wn}. This configuration allows for an open string description and a closed string description.

	\begin{table}[!htbp]
	\centering%\small
	%\setlength{\tabcolsep}{3pt}
	%\begin{adjustwidth}{-2em}{-5em}
	\begin{tabularx}{.7\linewidth}{
		~C{1.5}| ^C{.3}| ^C{1.5}|
		^C{.3} *4{ | ^C{.3} }
	}
	\toprule
		\textsf{Geometry} &
		\multicolumn{2}{~c|}{%
			\setrowstyle{\sffamily}%
			$\mathbb{R}^{4,1}$%
		} &
		$S^1$ &
		\multicolumn{4}{^c}{
			$\mcal{M}_4 = T^4, \mrm{K3}$
		}
	\\ %\cline{2-3}
	\midrule
		\textsf{Direction}
		& 0 & 1, 2, 3, 4 & 5 & 6 & 7 & 8 & 9 \\
	\midrule
		$\mop{\#}\text{\small D5} = Q_5$ &
		$\times$ & &
		$\times$ & $\times$ & $\times$ & $\times$ & $\times$
	\\
		$\mop{\#}\text{\small D1} = Q_1$ &
		$\times$ & &
		$\times$ & & & &
	\\
		$P$ &
		$\times$ & &
		$\times$ & & & &
	\\
	\bottomrule
	\end{tabularx}
	\caption[Brane configuration of the D1-D5-$P$ system]{
		Brane configuration of the D1-D5-$P$ system. 
%	\\
		Here we are considering type IIB string theory on flat 6D spacetime, with a compactified $x^5\in S^1$ direction, along with an internal $\mcal{M}_4$ manifold. 
		We use $\mquote{\times}$ to mark the directions $x^\mu$ that an object occupies. Here $\mu = 0,1,\cdots,9$.
	}
	\end{table}

	The D5 branes wrap the compact $\mcal{M}_4$, while the D1 branes are localized on $\mcal{M}_4$. Both the D1 and D5 branes extend along the fifth direction $x^5$, which is compactified to a circle $S^1$ with a large radius.

	Open string excitations on the branes carry momentum and winding. Due to the large radius of $S^1$, we can focus on the momentum modes $P$ along $x^5 \in S^1$ and neglect the winding modes. On the other hand, we will neglect momentum modes along the $\mcal{M}_4$ directions, since $\mcal{M}_4$ is assumed to be compact and small.

	In the IR limit, type IIB string theory is described by the low energy effective action of type IIB supergravity (SUGRA). The field content and the action of type IIB SUGRA are well reviewed in the literature; see e.g.\ Appendix H of \cite{Kiritsis:1997hj}. In particular, there is a pair of 2-form gauge fields in type IIB SUGRA. One of them is the NS-NS field $B_2$, and the other is the R-R field $C_2$. 
	The D1 branes are electrically charged under $C_2$, while the D5 branes are magnetically charged under $C_2$.

	The bosonic part of the string frame action is then given by:
	\begin{gather}
		\frac{1}{16\pi G}
		\int \dd[10]{x} \sqrt{-g}
			\pqty{
				e^{-2\phi} \Big(
					R + 4\,(\nabla\phi)^2
					- \frac{1}{12} H^2
				\Big)
				- \frac{1}{12} F^2
			},
	\\
		H = \dd{B_2},\quad
		F = \dd{C_2}
	\end{gather}
	After dimension reduction of the compact $\mcal{M}_4$, the equations of motion lead to the following black string solution in 6D:
	\begin{equation}
	\begin{aligned}
		\dd{s}^2
		= {} & (f_1 f_5)^{-1/2} \pqty{
				-\dd{t}^2 + \dd{\phi}^2
				+ \frac{r_0^2}{r^2} \pqty{
					\cosh\sigma \dd{t}
					+ \sinh\sigma \dd{\phi}
				}^2
			} \\
		{} + {} & (f_1 f_5)^{+1/2} \pqty{
				\frac{\dd{r}^2}{1 - r_0^2 / r^2}
				+ r^2 \dd{\Omega_3^2}
			}
	\end{aligned}
	\end{equation}

\subsection{Type IIB string theory with NS-NS flux}

\section{Deformation of \ads{3}/\cft{2} in string theory}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pagebreak
\bibliographystyle{JHEP} 
\bibliography{beyondAdS.bib}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

### 2021-11-22 alpha/SUSY/susy.tex
Add Wei's notes on holography beyond AdS/CFT

@@
 	\end{equation}
-	$\Gamma$ is the generalization of $\gamma_5$ in 4D, and serves as a chirality operator that distingushes the left and right handed part of a Dirac spinor.
+	$\Gamma$ is the generalization of $\gamma_5$ in 4D, and serves as a chirality operator that distinguishes the left and right handed part of a Dirac spinor.
 This gives us Weyl spinors with a definite chirality.
@@
 		\{\phi',\psi_\alpha,\lambda_\alpha,A'_\mu\}
-	$: for $j = \frac{1}{2}$, the $j\pm\frac{1}{2} = 0,1$ states and their $\mrm{Spin}(3)$ descendents live in a $0\oplus 1$ representation of $\mrm{Spin}(3)$. 
+	$: for $j = \frac{1}{2}$, the $j\pm\frac{1}{2} = 0,1$ states and their $\mrm{Spin}(3)$ descendants live in a $0\oplus 1$ representation of $\mrm{Spin}(3)$. 
 	In terms of field content, we have 1 \textit{real} scalars $\phi'$, 1 massive vector $A'_\mu$, and 2 Weyl spinors $\psi_\alpha, \lambda_\alpha$. 
@@
 
-	In general, the $j \pm \frac{1}{2}$ states and their $\mrm{Spin}(3)$ descendents live in a $
+	In general, the $j \pm \frac{1}{2}$ states and their $\mrm{Spin}(3)$ descendants live in a $
 		\pqty{j - \frac{1}{2}}
@@
 	Here $J_-$ is the $\mrm{Spin}(3)$ lowering operator. 
-	Namely, including the $\mrm{Spin}(3)$ descendents, the dimension of the $\mrm{super} \times \mrm{Spin}(3)$ representation is thus $4\times (2j+1)$. 
+	Namely, including the $\mrm{Spin}(3)$ descendants, the dimension of the $\mrm{super} \times \mrm{Spin}(3)$ representation is thus $4\times (2j+1)$. 
 	Note that for $j = 0$ the situation is special; in that case we simply have:
@@
 
+	As is discussed in \S2, the classical SUSY vacua are given by $\pd\mcal{W} = 0$.
+This is an equation on the tangent bundle of the target, so it comes with an induced metric inherited from the target.
+However, it need not be a manifold (perhaps with singularities), but can also have intersections.
+
+	Let's look at a simple example where:
+	\begin{equation}
+		\mcal{W}[L,H] = \frac{1}{2} \lambda LH^2
+	\end{equation}
+	Extrema of $\mcal{W}$ are at $H = 0$ and \textit{arbitrary} $L$.
+The \textit{classical} vacuum moduli is thus given by the $\vev{L} \in \mbb{C}$ plane, with a K\"ahler metric $\dd{s^2} = \dd{L} \dd{\bar{L}}$ induced from the target.
+
+\subsection{Singular K\"ahler potential $\mcal{K}$}
+	To properly account for the quantum corrections, instead of setting $H = 0$, we need to \textit{integrate it out}.
+The path integral over $H$ includes the following 1-loop correction from the $LH^2$ vertex:
+	\begin{equation}
+		LH^2\, \bar{L} \bar{H}^2
+		= L\,(H^2\bar{H}^2)\,\bar{L}
+		\xrightarrow{\ {\textstyle\int} \DD{H}\ }
+		{}\propto - \bar{L}L
+			\abs{\lambda}^2
+			\log \abs{\frac{L}{\lambda}}^2
+	\label{eq:1-loop_kahler}
+	\end{equation}
+	where the internal $H$ fields are contracted.
+This renormalizes the $\bar{L}L$ term in the K\"ahler potential.
+We see that quantum corrections lead to a singularity in the K\"ahler metric at $\vev{L} = 0$:
+	\begin{equation}
+		\mcal{K}
+		\propsim - \bar{L}L
+			\abs{\lambda}^2
+			\log \abs{\frac{L}{\lambda}}^2
+		\to +\infty,
+	\quad L \to 0
+	\end{equation}
+
+	This has a physical interpretation: the mass of $H$ is proportional to $\lambda\vev{L}$; at $\vev{L} = 0$ it becomes massless.
+We've \textit{assumed} that $H$ is ``heavy'' and thus can be safely integrated out, but this is not the case at $\vev{L} = 0$.
+
+	It is a general phenomenon that singularities in the effective action correspond to ``new'' massless particles.
+They indicate the breakdown of our effective theory.
+In other words, we are using the effective action beyond its range of validity: as $L\to 0$ some new degrees of freedom are necessary to give a full description of our theory in the IR, in this case we \textit{have to} include $H$ as it becomes massless when $L \to 0$.
+
+	Note that the 1-loop result becomes exact as $L \to 0$, since $H$ is more and more weakly coupled in this limit.
+Again note that the effective coupling for $H$ is $\vev{\lambda L}$.
+On the other hand, as $L \to \infty$ the theory becomes strongly coupled and perturbative expansions become unreliable.
+Note that the 1-loop correction \eqref{eq:1-loop_kahler} carries a minus sign, so for large $\abs{L}$ the metric becomes negative: $\dd{s^2} \to -\infty$.
+This is a \textit{Landau pole} in the IR.
+
+\subsection{Singular superpotential $\mcal{W}$}
+	In the example above we see a singularity in the renormalized K\"ahler potential $\mcal{K}$ as we integrate out the $H$ field.
+Although the superpotential is usually not renormalized (as discussed in \S3), singularities can still arise from integrating out the $H$ field.
+
+	Let us do a more complicated example:
+	\begin{equation}
+		\mcal{W}[L,H]
+		= \frac{1}{2} mH^2
+			+ \lambda L^2 H
+			+ \frac{1}{6} g H^3
+	\end{equation}
+	At scales well below $m$, $H$ is frozen at $\vev{H}$, which is the solution of $\pdd{H} \mcal{W} = 0$ by saddle point approximation.
+This gives us an effective potential $\mcal{W}[L]$.
+Here we are assuming that:
+	\begin{itemize}
+	\item SUSY is not broken at or above the scale of the effective theory.
+In this case $\vev{H}$ is completely given by the VEV of its scalar component, because the VEV of a fermion vanishes due to Lorentz invariance of the vacuum, and $\vev{F} = 0$ since SUSY is not broken.
+
+	\item Unlike in the previous example, now we have an explicit mass gap for $H$ while we integrate it out, therefore at scales well below $m$ we can ignore all quantum fluctuations, and the classical limit is actually exact\footnote{
+		\textcite{Argyres:1996abc} claims that ``\textit{it is not hard to see that, together with the non-renormalization theorem, this is equivalent to the above more laborious procedure using the symmetries and the classical limit.}'' I can understand the spirit of this (as is explained in the following passage) but I am not sure how to see this rigorously.
+	}.
+
+		\begin{itemize}
+		\item Note that $L$ is treated as an external source as we integrate out $H$. If $\vev{L} = 0$ then the above argument goes through without issue.
+
+		\item If $\vev{L} \ne 0$, then the saddle point approximation is not quite valid.
+However, the functional dependence of $\mcal{W}[L;m,\lambda,g]$ is protected by symmetry (global symmetry and SUSY, namely holomorphy), as discussed in \S3.
+One can check explicitly that the result should hold even for $\vev{L} \ne 0$.
+		\end{itemize}
+
+	\end{itemize}
+
+	\begin{figure}[!h]
+	\centering
+	\includegraphics[width=.6\linewidth]{img/effective_potential_branch_cuts.pdf}
+	\caption[Behavior of the effective potential $\mcal{W}\[L\]$ in the $L$ plane]{%
+		Behavior of the effective potential $\mcal{W}[L]$ in the $L$ plane, based on \cite{Argyres:1996abc}.
+
+		The bubbles illustrate the behavior of the scalar potential $V[H] = \norm{\pd_H \mcal{W}\mspace{1.5mu}[L,H]}^2$ at given values of $\vev{L}$.
+Note that the vertical axis is not at $H = 0$ but at $H = -m/g$, and the plot covers only $\mbb{R}$eal values of $H$.
+
+		The original illustration in \cite{Argyres:1996abc} seems to be inaccurate. Here we try to clear up the confusions by redrawing parts of the diagrams. 
+	}
+	\label{fig:effective_potential_branch_cuts}
+	\end{figure}
+
+	The resulting $\mcal{W}[L]$ have branch points at:
+	\begin{equation}
+		L = \pm \sqrt{\frac{m^2}{2\lambda g}}\,,
+	\end{equation}
+	as depicted in \autoref{fig:effective_potential_branch_cuts}. 
+	At these points $H$ becomes massless, therefore we should not integrate it out in the first place. Generally, the \textit{effective} mass of $H$ is not simply $m$, but:
+	\begin{equation}
+		\pd^2_H \mcal{W} \mspace{1.5mu}[L,H]
+		\,\big|_{\vev{L},\vev{H}}
+		= \pm m \sqrt{
+			1 - \vev{L}^2 \Big/ \frac{m^2}{2\lambda g}
+		}
+	\label{eq:effective_mass}
+	\end{equation}
+	The 2 signs correspond to the 2 solutions of $\pd_H \mcal{W} = 0$, namely:
+	\begin{equation}
+		\vev{H}
+		= \frac{m}{g} \pqty{
+			-1 \pm \sqrt{
+				1 - \vev{L}^2 \Big/ \frac{m^2}{2\lambda g}
+			}
+		\,}
+	\label{eq:vev_H}
+	\end{equation}
+
+%\pagebreak[3]
+
+	On the other hand, we can look at the scalar potential:
+	\begin{equation}
+		V_{\vev{L}} [H] = \norm\big{\,
+			\pd_H \mcal{W}\mspace{1.5mu}[L,H]
+		\,}^2_{L = \vev{L}}
+	\end{equation}
+	at \textit{given} values of $\vev{L}$, as shown in \autoref{fig:effective_potential_branch_cuts}. 
+	\begin{itemize}
+	\item For $
+			-\sqrt{\frac{m^2}{2\lambda g}}
+			< \vev{L} <
+			+\sqrt{\frac{m^2}{2\lambda g}}
+		$ there are 2 inequivalent vacua, corresponding to the 2 branches of the square root in \eqref{eq:effective_mass} and \eqref{eq:vev_H}.
+They are reflected in the low energy effective potential $\mcal{W}[L]$ by the same multi-valued square root structure.
+
+	\item For $\vev{L} = \pm \sqrt{\frac{m^2}{2\lambda g}}$ there is an unique vacuum. This is the branch point in \eqref{eq:effective_mass}, \eqref{eq:vev_H} and $\mcal{W}[L]$.
+
+	\item For $\vev{L} > +\sqrt{\frac{m^2}{2\lambda g}}$ or $\vev{L} < +\sqrt{\frac{m^2}{2\lambda g}}$ it would appear that $V_{\vev{L}} [H] > 0$, and one would suppose that SUSY is spontaneously broken.
+However, if we allow for $H \in \mbb{C}$, then $V_{\vev{L}} [H] = 0$ can actually be solved with $H \in \mbb{C}$.
+There are still 2 inequivalent vacua.
+
+	Same applies for generic values of $\vev{L} \in \mbb{C}$.
+
+	\end{itemize}
+
 \section{SUSY Breaking}
@@
 \section{Super Gauge Theory}
-	\speaker{Yuan Zhong}\\
+	\speaker{Yihua ``Louiva'' Liu}\\
 	\references{%

### 2021-11-23 alpha/BeyondAdSCFT/beyondAdS.tex
Restructure notes on holography beyond AdS

@@
 \documentclass[11pt,a4paper]{article}
+\usepackage{jheppub}
+
 \pdfoutput=1
-
 \input{preamble.tex}
-
-\usepackage{comment}
-%\newcommand{\lui}[2]{\textcolor{red}{#1}\todo[color=yellow]{\scriptsize{L: #2}}}
-\newcommand{\wei}[2]{\textcolor{magenta}{#1}\todo[color=yellow]{\scriptsize{WS: #2}}}
-\newcommand{\wx}[2]{\textcolor{purple}{#1}\todo[color=teal]{\scriptsize{XL: #2}}}
 
@@
 \newcommand{\TTbar}{\texorpdfstring{\ensuremath{T\bar{T}}}{TTbar}\xspace}
-\newcommand{\arcsinh}{\ensuremath{\mop{arcsinh}}}
-\renewcommand{\tilde}[1]{\ensuremath{\widetilde{#1}}}
 \newcommand{\ads}[1]{AdS\ensuremath{_{#1}}}
 \newcommand{\cft}[1]{CFT\ensuremath{_{#1}}}
-
-\usepackage{enumitem}
 
@@
 \author[a]{Wei Song}
+%\author[a]{and Fengjun Xu}
 
@@
 
-%  \emailAdd{apolo@mail.tsinghua.edu.cn, wsong2014@mail.tsinghua.edu.cn}
+%\emailAdd{laiwx19@mails.tsinghua.edu.cn, wsong2014@mail.tsinghua.edu.cn}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{document}
@@
 \setlength{\parskip}{.5\baselineskip}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 	\item The asymptotically de Sitter spacetime, which well approximates our current (and future) universe at a larger length scale, and also during the period of inflation;
-	\item The FRW metric (or more precisely, the Friedmann-Lemaître-Robertson-Walker \cite{Friedmann:1924bb,Lemaitre:1933gd,Robertson:1935zz,Walker:1937} metric), which describes the evolution of our homogeneous and isotropic universe from the big bang to its ;
+	\item The FRW metric (or more precisely, the Friedmann-Lemaître-Robertson-Walker \cite{Friedmann:1924bb,Lemaitre:1933gd,Robertson:1935zz,Walker:1937} metric), which describes the evolution of our homogeneous and isotropic universe from the big bang to \sidenote{its ...} ;
 	\item and more ...
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \pagebreak
@@
 \bibliography{beyondAdS.bib}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2021-11-23 alpha/BeyondAdSCFT/package.sh

@@ -1,0 +1,31 @@
+#!/bin/bash
+# package LaTeX source for distribution
+
+# FILENAME="${1%.tex}"; shift
+FILENAME=beyondAdS
+TARGET=release
+
+[[ -r "$FILENAME".tex ]] \
+    || { echo "# Couldn't access $FILENAME.tex"; exit 1; }
+
+mkdir "$TARGET" || true
+# echo "*" > "$TARGET/.gitignore"
+
+PREAMBLE=preamble.tex
+sed-latex "$PREAMBLE" > "$TARGET/$PREAMBLE"
+
+rsync \
+    --exclude='.git*' --recursive --copy-links \
+    --update --partial \
+    --progress --verbose \
+    "$@" \
+    "$FILENAME.tex" \
+    "$FILENAME.bib" \
+    "$FILENAME.bbl" \
+    "$FILENAME.pdf" \
+    "img/" \
+    "README.md" \
+    "$TARGET"
+
+# cd "$TARGET" || exit
+# zip -r "$FILENAME.zip" .

### 2021-11-23 alpha/BeyondAdSCFT/beyondAdS.tex
Add notes on black string & minor stuff [overleaf]

@@
 
+\addtocounter{section}{-1}
 \section{Introduction}
@@
 %	\\
-		Here we are considering type IIB string theory on flat 6D spacetime, with a compactified $x^5\in S^1$ direction, along with an internal $\mcal{M}_4$ manifold. 
+		Here we are considering type IIB string theory on flat 6D spacetime, with a compactified $x^5 \in S^1$ direction, along with an internal $\mcal{M}_4$ manifold. 
 		We use $\mquote{\times}$ to mark the directions $x^\mu$ that an object occupies. Here $\mu = 0,1,\cdots,9$.
@@
 The field content and the action of type IIB SUGRA are well reviewed in the literature; see e.g.\ Appendix H of \cite{Kiritsis:1997hj}.
-In particular, there is a pair of 2-form gauge fields in type IIB SUGRA.
+In particular, there is a pair of 2-form gauge potentials in type IIB SUGRA.
 One of them is the NS-NS field $B_2$, and the other is the R-R field $C_2$.
@@
 	\end{gather}
-	After dimension reduction of the compact $\mcal{M}_4$, the equations of motion lead to the following black string solution in 6D:
-	\begin{equation}
+	where $H$ and $F$ are the 3-form field strengths, $H^2 = H_{\mu\nu\rho} H^{\mu\nu\rho} \mathbin{\sidenote{\propto}} H\wedge \hstar H$, and similar for $F^2$. 
+	After dimension reduction of the compact $\mcal{M}_4$, the equations of motion admit the following black string solution in 6D \needcites:
+	\begin{gather}
 	\begin{aligned}
@@
 				+ r^2 \dd{\Omega_3^2}
-			}
+			},
+	\qquad f_1 = 1 + \frac{r_1^2}{r^2},
+	\quad  f_5 = 1 + \frac{r_5^2}{r^2},
 	\end{aligned}
-	\end{equation}
+	\end{gather}
+
+	We note that the above black string solution is asymptotically flat, consistent with our brane construction in type IIB string theory.
+More specifically, parameters in this supergravity solution can be related to the brane construction in the following way:
+	\begin{itemize}
+	    \item $\phi \equiv x^5$ is the compactified $S^1$ direction along the D1 brane, normalized such that $\phi \cong \phi + 2\pi R$.
+
+	    Upon dimension reduction of the $\phi$ direction, this 6D black string solution will become a 5D black hole solution.
+In fact the resulting 5D black hole solution is precisely the Strominger-Vafa black hole \cite{Strominger:1996sh}, which serves as the first example of microscopic counting of the black hole entropy.
+
+	    \item $r_0$ marks the horizon of the black string, and it is related to the open string momentum $P$ attached to the branes: $P \propto r_0^2 \sinh 2\sigma$.
+
+	    \item $r_1^2$ and $r_5^2$ are related to the charges $Q_1$ and $Q_5$. 
+	\end{itemize}
 

### 2021-11-23 alpha/BeyondAdSCFT/package.sh

@@ -23,7 +23,7 @@ rsync \
     "$FILENAME.bib" \
     "$FILENAME.bbl" \
     "$FILENAME.pdf" \
-    "img/" \
+    "img" \
     "README.md" \
     "$TARGET"
 

### 2021-11-26 alpha/BeyondAdSCFT/beyondAdS.tex
Add notes on NH limit & dual CFT

--- 2021-11-23 alpha/BeyondAdSCFT/beyondAdS.tex
@@
 \newcommand{\TTbar}{\texorpdfstring{\ensuremath{T\bar{T}}}{TTbar}\xspace}
-\newcommand{\ads}[1]{AdS\ensuremath{_{#1}}}
-\newcommand{\cft}[1]{CFT\ensuremath{_{#1}}}
+\newcommand{\ads}[1]{\text{AdS}\ensuremath{_{#1}}}
+\newcommand{\cft}[1]{\text{CFT}\ensuremath{_{#1}}}
 
@@
 
-	The first example of microscopic counting of black hole entropy, discovered by Strominger-Vafa \cite{Strominger:1996sh}, comes from the \mbox{D1-D5-$P$} system in string theory.
+	The first example of a microscopic counting of black hole entropy, discovered by Strominger-Vafa \cite{Strominger:1996sh}, comes from the \mbox{D1-D5-$P$} system in string theory.
 
@@
 
-\subsection{The \mbox{D1-D5-$P$} system}
+\subsection{The \mbox{D1-D5-$P$} system and its IR limit}
 
@@
 
-	In the IR limit, type IIB string theory is described by the low energy effective action of type IIB supergravity (SUGRA).
-The field content and the action of type IIB SUGRA are well reviewed in the literature; see e.g.\ Appendix H of \cite{Kiritsis:1997hj}.
-In particular, there is a pair of 2-form gauge fields in type IIB SUGRA.
+\subsubsection{IR limit and the \ads{3} gravity}
+	In the IR limit, type IIB string theory is described by the low energy effective action of type IIB supergravity.
+The field content and the action of type IIB supergravity are well reviewed in the literature; see e.g.\ Appendix H of \cite{Kiritsis:1997hj}.
+In particular, there is a pair of 2-form gauge potentials in type IIB supergravity.
 One of them is the NS-NS field $B_2$, and the other is the R-R field $C_2$.
@@
 
-	The bosonic part of the string frame action is then given by:
+	The bosonic part of the string frame action is then given by \needcites:
 	\begin{gather}
@@
 					R + 4\,(\nabla\phi)^2
-					- \frac{1}{12} H^2
+					- \sidenote{\frac{1}{12}} H^2
 				\Big)
-				- \frac{1}{12} F^2
+				- \sidenote{\frac{1}{12}} F^2
 			},
@@
 	\end{gather}
-	After dimension reduction of the compact $\mcal{M}_4$, the equations of motion lead to the following black string solution in 6D:
-	\begin{equation}
+	where $H$ and $F$ are the 3-form field strengths, $H^2 = H_{\mu\nu\rho} H^{\mu\nu\rho} \mathbin{\sidenote{\propto}} H\wedge \hstar H$\wx{}{convention for the coefficients?}, and similar for $F^2$. 
+	After dimension reduction of the compact $\mcal{M}_4$, the equations of motion admit a \textit{black string} solution in 6D, where the metric is given by \needcites:
+	\begin{gather}
 	\begin{aligned}
@@
 			} \\
-		{} + {} & (f_1 f_5)^{+1/2} \pqty{
+		& {} + (f_1 f_5)^{+1/2} \pqty{
 				\frac{\dd{r}^2}{1 - r_0^2 / r^2}
 				+ r^2 \dd{\Omega_3^2}
+			},
+		\quad \phi \cong \phi + 2\pi R,
+	\end{aligned}
+	\\[1ex] \text{where}
+	\quad f_1 = 1 + \frac{r_1^2}{r^2},
+	\quad f_5 = 1 + \frac{r_5^2}{r^2}
+	\end{gather}
+	The parameters in this supergravity solution can be related to the brane construction as follows:
+	\begin{itemize}
+		\item $\phi \equiv x^5$ is the compactified $S^1$ direction along the D1 brane, normalized such that $\phi \cong \phi + 2\pi R$, where $R$ is the large radius of the $S^1$ circle.
+
+		Upon dimension reduction of the $\phi$ direction, this 6D black string solution will become a 5D black hole solution.
+In fact the resulting 5D black hole solution is precisely the Strominger-Vafa black hole \cite{Strominger:1996sh}, which serves as the first example of a microscopic counting of the black hole entropy.
+
+		\item $r_0$ marks the horizon of the black string, and it is related to the open string momentum $P$ attached to the branes: $P \propto r_0^2 \sinh 2\sigma$.
+
+		\item $r_1^2$ and $r_5^2$ are related to the charges $Q_1$ and $Q_5$. 
+	\end{itemize}
+
+	We further note that the above black string solution is asymptotically flat, consistent with our brane construction in string theory.
+On the other hand, if we zoom in to the near horizon region of this black string solution, we discover an $\ads{3}\times S^3$ geometry.
+This can be achieved by setting:
+	\begin{equation}
+		\ell^2 = r_1 r_5,
+	\quad r\mapsto \lambda\ell r,
+	\quad r_0\mapsto \lambda\ell r_0,
+	\quad t\mapsto t\ell / \lambda,
+	\quad \phi\mapsto \phi\ell / \lambda,
+	\end{equation}
+	where $\ell$ is the \ads{} radius, and now the $\phi$ coordinate is normalized such that $\phi \cong \phi + 2\pi$. 
+	More specially,
+	\begin{itemize}
+	\item For extremal black string with $r_0 = 0$ and thus $P = 0$, the near horizon limit leads to the zero mass BTZ geometry, with an additional $S^3$ factor:
+	\begin{equation}
+		\dd{s}^2
+		= \ell^2 \pqty{
+			r^2 (-\dd{t}^2 + \dd{\phi}^2)
+			+ \frac{\dd{r}^2}{r^2}
+			+ \dd{\Omega_3^2}
 		}
-	\end{aligned}
+	\end{equation}
+
+	\item For the near-extremal case with generic $r_0, \sigma$, the near horizon limit leads to the rotating BTZ geometry, again with an additional $S^3$ factor:
+	\begin{equation}
+		\dd{s}^2
+		= \ell^2 \pqty{
+			r^2 (-\dd{t}^2 + \dd{\phi}^2)
+			+ \frac{\dd{r}^2}{r^2 - r_0^2}
+			+ r_0^2 \pqty{
+				\cosh\sigma \dd{t}
+				+ \sinh\sigma \dd{\phi}
+			}^2
+			+ \dd{\Omega_3^2}
+		}
+	\end{equation}
+
+	\end{itemize}
+
+	It is convenient to define the left and right-moving temperature:
+	\begin{equation}
+		T_L = \frac{1}{2\pi}
+			\frac{r_0\,e^\sigma}{\ell^2},
+	\quad
+		T_R = \frac{1}{2\pi}
+			\frac{r_0\,e^{-\sigma}}{\ell^2}
+	\end{equation}
+	On the other hand, the Hawking temperature $T_H$ of this solution can be computed, and is given in terms of $T_L,T_R$ as follows:
+	\begin{equation}
+		\frac{2}{T_H}
+		= \frac{1}{T_L}
+		+ \frac{1}{T_R}
+	\end{equation}
+
+	One can understand the IR supergravity solution as the result of ``integrating out'' the dynamics of the branes, including the open string excitations.
+This process deforms the background geometry, and we end up with a closed string theory on the black string background.
+\sidenote{......}
+
+\subsubsection{Worldvolume \cft{2} and the duality}
+
+	On the other hand, we can consider the worldvolume theory of the brane construction.
+After dimension reduction of the compact $\mcal{M}_4$, we have a $(1+1)$ dimensional QFT living on the D1-D5 branes.
+This is a supersymmetric gauge theory with $\mcal{N} = (4,4)$ supersymmetry.
+	Similar to our previous discussions, we can consider the IR limit of this system. It should flow to an IR fixed point, which is a $(1+1)$ dimensional superconformal field theory (S\cft{2}).
+
+	The central charge of this S\cft{2} can be read off from the field contents of the worldvolume theory: the number of bosonic fields is given by: 
+	\begin{equation}
+		4Q_1 Q_5
+	\end{equation}
+	and the same amount for fermions.
+The factor $Q_1 Q_5$ comes from the open string excitations between the D1 and D5 branes, while the factor of 4 comes from the fact that the D1 branes can move inside the D5 branes \wx{along the compact $\mcal{M}_4$ directions.}{is this language accurate?} In the end we have the central charge:
+	\begin{equation}
+		c = 1\times 4Q_1 Q_5
+			+ \frac{1}{2}\times 4Q_1 Q_5
+		= 6Q_1 Q_5
 	\end{equation}
@@
 \end{document}
+
+% vim: set ts=4 sw=4 sts=4 noexpandtab:

### 2021-11-27 alpha/BeyondAdSCFT/beyondAdS.tex
Add notes on the top-down duality

@@
 \input{preamble.tex}
+
+%% detailed ToC
+\setcounter{tocdepth}{3}
 
@@
 
-\subsubsection{IR limit and the \ads{3} gravity}
+\subsubsection{Closed string picture: gravity on \ads{3} background}
 	In the IR limit, type IIB string theory is described by the low energy effective action of type IIB supergravity.
@@
 
-	One can understand the IR supergravity solution as the result of ``integrating out'' the dynamics of the branes, including the open string excitations.
-This process deforms the background geometry, and we end up with a closed string theory on the black string background.
-\sidenote{......}
+	\wx{Within the framework of string theory, one can understand the IR black string geometry as the result of ``integrating out'' the dynamics of the branes, which includes the open string excitations.}{accurate?} This process deforms the background geometry, and we end up with a closed string theory on the black string background.
+The near horizon limit brings us further to the IR fixed point, where the far region dynamics decouple and we are left with the \ads{3} geometry.
 
-\subsubsection{Worldvolume \cft{2} and the duality}
+	In other words, strings on $\ads{3}\times S^3\times \mcal{M}_4$ is understood as the \textit{closed string description} of the IR fixed point of the D1-D5-$P$ system.
 
-	On the other hand, we can consider the worldvolume theory of the brane construction.
-After dimension reduction of the compact $\mcal{M}_4$, we have a $(1+1)$ dimensional QFT living on the D1-D5 branes.
-This is a supersymmetric gauge theory with $\mcal{N} = (4,4)$ supersymmetry.
+\subsubsection{Open string picture: worldvolume \cft{2} and the duality}
+
+	On the other hand, we can consider the worldvolume theory of the brane construction. This provides the \textit{open string description} of the D1-D5-$P$ system.
+
+	After dimension reduction of the compact $\mcal{M}_4$, we have a $(1+1)$ dimensional QFT living on the D1-D5 branes. This is a supersymmetric gauge theory with $\mcal{N} = (4,4)$ supersymmetry. 
 	Similar to our previous discussions, we can consider the IR limit of this system. It should flow to an IR fixed point, which is a $(1+1)$ dimensional superconformal field theory (S\cft{2}).
 
-	The central charge of this S\cft{2} can be read off from the field contents of the worldvolume theory: the number of bosonic fields is given by: 
+	The central charge of this S\cft{2} can be read off from the field contents of the worldvolume theory: the number of bosonic fields is given by \needcites: 
 	\begin{equation}
@@
 	\end{equation}
-	and the same amount for fermions.
+	and same for the fermions.
 The factor $Q_1 Q_5$ comes from the open string excitations between the D1 and D5 branes, while the factor of 4 comes from the fact that the D1 branes can move inside the D5 branes \wx{along the compact $\mcal{M}_4$ directions.}{is this language accurate?} In the end we have the central charge:
@@
 	\end{equation}
+
+	We have thus discovered two equivalent descriptions of the D1-D5-$P$ system, summarized as follows:
+	\begin{equation*}
+	\begin{array}{ccc}
+		\pqty{
+			\ \begin{gathered}
+				\text{Far-region dynamics} \\
+				+ \\
+				\text{Strings on $\ads{3}\times S^3\times \mcal{M}_4$}
+			\end{gathered}\ %
+		}
+		&=&
+		\pqty{
+			\ \begin{gathered}
+				\text{Far-region dynamics} \\
+				+ \\
+				\text{S\cft{2} with target $\mcal{M}_4$}
+				\vphantom{S^3}
+			\end{gathered}\ %
+		}
+	\\[6ex]
+		\textit{Closed string picture}
+		& &
+		\textit{Open string picture}
+	\end{array}
+	\end{equation*}
+	The far-region dynamics decouple on both sides, and we have the following proposal of an \ads{3}/\cft{2} duality:
+	\begin{equation}
+	\begin{aligned}
+		&\text{Type IIB string theory on $\ads{3}\times S^3\times \mcal{M}_4$} \\
+		{} = {}
+		&\text{Deformations of some $\mcal{N} = (4,4)$ S\cft{2} with target $\mcal{M}_4$}
+	\end{aligned}
+	\end{equation}
+	\sidenote{Deformations? Symmetric orbifolds?}
 

### 2021-11-28 alpha/BeyondAdSCFT/beyondAdS.tex
Add comments on the symmetric orbifold & S-dual

@@
 	\end{equation*}
-	The far-region dynamics decouple on both sides, and we have the following proposal of an \ads{3}/\cft{2} duality:
+	The far-region dynamics decouple on both sides, and we have the following proposal of an \ads{3}/\cft{2} duality \needcites:
 	\begin{equation}
@@
 		{} = {}
-		&\text{Deformations of some $\mcal{N} = (4,4)$ S\cft{2} with target $\mcal{M}_4$}
+		&\text{Marginal deformations of some $\mcal{N} = (4,4)$ S\cft{2} with target $\mcal{M}_4$}
 	\end{aligned}
 	\end{equation}
-	\sidenote{Deformations? Symmetric orbifolds?}
+	Note that both sides of the duality includes a non-trivial moduli \needcites.
+\wx{In particular, the S\cft{2} on the right-hand side is proposed to be a \textit{symmetric product orbifold theory} \needcites, together with its exactly marginal deformations along the conformal manifold.
+}{elaborate?}
 
 \subsection{Type IIB string theory with NS-NS flux}
+
+	The D1-D5-$P$ system is tough to deal with on the worldsheet, within the framework of the RNS (or NSR) formalism, due to its non-trivial coupling to the R-R field $C_2$.
+This difficulty can be avoided by considering its S-dual, the NS1-NS5-$P$ system.
+
+	On the other hand, we can make use of the $\mrm{SL}(2,\mbb{Z})$ duality from type IIB string theory.
 

### 2021-12-04 alpha/BeyondAdSCFT/beyondAdS.tex
Add notes on the NS1-NS5 system

@@
 \subsection{The \mbox{D1-D5-$P$} system and its IR limit}
+\label{sect:d1-d5-p}
 
@@
 
-	The D1-D5-$P$ system is tough to deal with on the worldsheet, within the framework of the RNS (or NSR) formalism, due to its non-trivial coupling to the R-R field $C_2$.
-This difficulty can be avoided by considering its S-dual, the NS1-NS5-$P$ system.
+	Due to its non-trivial coupling to the R-R field $C_2$, the D1-D5 system is difficult to deal with on the worldsheet, within the framework of the RNS (or NSR) formalism.
+This difficulty can be avoided by considering its S-dual, the NS1-NS5 system.
 
-	On the other hand, we can make use of the $\mrm{SL}(2,\mbb{Z})$ duality from type IIB string theory.
+	First let us recall the $\mrm{SL}(2,\mbb{Z})$ duality of type IIB string theory, reviewed in \S12 and \S14 of \cite{Polchinski:1998rr}.
+In particular, the strong-weak S-duality is one of the generators of the $\mrm{SL}(2,\mbb{Z})$ action.
+When acted on the field strengths $H = \dd{B_2}$ and $F = \dd{C_2}$, it's given by:
+	\begin{gather}
+		S\colon\ %
+		\pqty{\begin{array}{c} H \\ F \end{array}}
+		\ \longmapsto\ %
+		\pqty{\begin{array}{cc}
+			0 & 1 \\
+			-1\hspace*{.2em} & 0
+		\end{array}}
+		\pqty{\begin{array}{c} H \\ F \end{array}}
+		= \pqty{\begin{array}{c} F \\ -H \end{array}},
+	\\[.5ex]
+		H = \dd{B_2},\quad F = \dd{C_2} \nonumber
+	\end{gather}
+	We note that S-duality exchanges the field strengths $H$ and $F$.
+On the other hand, the D1-D5 system couples to $C_2$ (electrically for D1, and magnetically for D5), while the NS1-NS5 system couples to $B_2$.
+Therefore S-duality corresponds to a map:
+	\begin{equation}
+	S\colon\quad
+	\begin{aligned}
+		Q_5\ \,\text{D5 branes}
+		\ \,&\longmapsto\ \,
+		k = Q_5\ \,\text{NS5 branes} \\
+		Q_1\ \,\text{D1 branes}
+		\ \,&\longmapsto\ \,
+		p = Q_1\ \,\text{NS1 branes} \\
+	\end{aligned}
+	\end{equation}
 
-\section{Deformation of \ads{3}/\cft{2} in string theory}
+	We can then repeat the analysis in \S\ref{sect:d1-d5-p} and obtain a similar black string solution in 6D.
+By taking the near horizon limit, we further obtain an asymptotically \ads{3} geometry, namely the BTZ solutions as described in \S\ref{sect:d1-d5-p}, but now with NS-NS flux instead of R-R flux.
+In particular, for $P = 0$ we have the massless BTZ solution \needcites:
+	\begin{gather}
+		\dd{s}^2
+		= k \pqty{
+			\dd{\rho}^2
+			+ e^{2\rho} \dd{\gamma} \dd{\bar{\gamma}}
+		},
+	\\
+		B_2 = \frac{1}{2} B_{\mu\nu}
+				\dd{x^\mu} \wedge \dd{x^\nu}
+		= - \frac{k}{2}\,e^{2\rho}
+				\dd{\gamma} \wedge \dd{\bar{\gamma}},
+	\quad e^{2\Phi} = \frac{k}{p},
+	\end{gather}
+	where we note that there is a non-trivial $B$-field and a dilaton profile $\Phi$.
+
+	Why are we interested in this S-dual system?
+As we've mentioned before, unlike the original D1-D5 system, the NS1-NS5 system admits a worldsheet description as an RNS superstring theory.
+Therefore we have a well understood \textit{worldsheet} \cft{2} for the bulk string theory.
+Furthermore, based on this worldsheet \cft{2}, we are able to construct explicitly the \textit{dual} \cft{2} on the asymptotic boundary of the spacetime.
+This is sometimes referred to as the \textit{spacetime} \cft{2}.
+Therefore the NS1-NS5 system serves as a realization of \ads{3}/\cft{2} where both sides of the holographic duality are in some sense, under control.
+
+\section{Holographic Dualities Beyond \ads{3}/\cft{2}}
+
+In the previous sections, we have laid down some basic aspects of \ads{3}/\cft{2} dualities in string theory.
+Starting from this section, we are going to introduce recent salient developments on holographic dualities beyond \ads{3}/\cft{2}.
+In particular, we will focus on $T\bar{T}$ deformation.
+This section is organized as follows:
+
+\subsection{Top-Down Approach: Deformations of \ads{3}/\cft{2} in string theory}
+In order to introduce deformations, we here remind the basic triangle among \ads{3}/\cft{2}.
 

### 2021-12-04 alpha/BeyondAdSCFT/beyondAdS.tex
Add notes of TTbar from Fengjun

@@
 
+\begin{figure}[ht!]
+\centering
+ \includegraphics[scale=0.45]{diagram4}
+\caption{The holographic correspondence between string theory on AdS$_3 \times M^7$ backgrounds and two-dimensional CFTs (inner triangle), and its relationship to the conjectured duality between TsT transformations of AdS$_3 \times M^7$ spacetimes, bi-current deformations of the worldsheet action, and single-trace irrelevant deformations of two-dimensional CFTs (outer triangle).
+Adapted from \cite{Apolo:2021wcn}}
+\label{fig:triangle}
+\end{figure}
+
+\subsection{$T\bar{T}$ deformation}
+In a Lorentzian invariant theory, the stress tensor $T^{\mu\nu}$ is conserved, i.e. $\partial_\mu T^{\mu\nu}=0$. One can define its determinant $\text{Det} T_{\mu\nu}$ as 
+\begin{equation}
+\begin{split}
+    \mathcal O_{T\bar T}&:= \text{Det} T_{\mu\nu} \\
+    &=T_{xx}T_{\bar x\bar x}-T_{x\bar x}T_{\bar{x} x} \\
+    &=\text{Lim}_{x \rightarrow y} (T_{xx}(x)T_{\bar x\bar x}(y)-T_{x\bar x}(x)T_{\bar{x} x}(y) )+ \text{derivatives}
+    \end{split}
+\end{equation}
+which is well-defined, and has 
+\begin{equation}
+    \langle n| \mathcal{O}_{T\bar T} |\rangle =\langle n| T |n\rangle \langle n|\bar T |n\rangle -\langle n| 
+    \Theta|n\rangle \langle n|\bar{\Theta} |n\rangle
+\end{equation}
+
+The $T\bar T$ deformations can be described by deforming the CFT by an extra term 
+\begin{equation}
+     \frac{\p S_{\mathcal M_\mu}}{\p \mu} = \int d^2x \mathcal{O}_{T\bar T}
+\end{equation}
+
+where we have combine the 2d spacetime coordinate $(\phi, t)$ into  $x=\phi+t$ and $\bar{x}=\phi-t$.
+
+When putting the deformed CFT on a cylinder, with $(x, \bar x) \sim (x+ 2\pi R, \bar x+2\pi R)$, one can then evaluate the energy spectra via invisited Burger's equation:
+\begin{equation}
+    \p E_n(R, \mu)= E_n(R, \mu) \p E(R, 0)+\frac 1{R} J_n^2(R)
+\end{equation}
+
+The spectrum
+
+  \eq{
+  E(\mu) &= - \frac{ R}{2 \mu} \Bigg[ 1 - \sqrt{1 + \frac{4 \mu}{ R} E(0) + \frac{4 \mu^2}{ R^4} J(0)^2} \,\Bigg], \qquad J(\mu) = J(0), \label{ttbarspectrum}
+  }
+  %  
+where $E = E_L + E_R$ and $J = R(E_L - E_R)$ denote the energy and angular momentum.
+
+Let us make some comments on the $T\bar T$ deformation:
+$\bullet$ it is irrelevant, since the dimension of $\mu$ is $2>0$.
+
+$\bullet$ It is also solvable, which is the main reason why people are interested in studying them.
+
+$\bullet$ It can also be reformulated as coupling to random geometry, flat $JT$ gravity, (non-) critical strings.
+
+$\bullet$ The partition function after the deformation is still modular invariant.
+
+$\bullet$ The scattering amplitude can be shown as dressed by a phase factor.
+
+From the histroric viewpoint,
+
+It was conjectured in \cite{Apolo:2019zai} that performing the following TsT transformation on the string theory is holographically equivalent to deforming the seed of the dual symmetric orbifold,
+\begin{equation}
+\textrm{TsT}_{(X^m,X^{\bar m};\check\mu)} \quad\Longleftrightarrow\quad  \frac{\p S_{\mathcal M_\mu}}{\p \mu} = -4 \int J_{(m)} \wedge J_{(\bar{m})}, \label{conjecture}
+\end{equation}
+where $\textrm{TsT}_{(X^m,X^{\bar m};\check\mu)}$ denotes T-duality on  $X^m$, shift $ X^{\bar m} \to X^{\bar m} - 2\check\mu X^m$,  and T-duality on $ X^m$, $S_{\mathcal M_\mu}$ is the action of the deformed seed, $\mu$($\check\mu$) is the dimensionful(less) deformation parameter, and $J_{(m)}$, $J_{(\bar{m})}$ are the Noether currents generating translations along $X^m$, $X^{\bar m}$.
+It is interesting to note that from a purely worldsheet perspective, a TsT transformation is equivalent to a \emph{marginal} bi-current deformation of the worldsheet action, the latter of which can be shown to be equivalent to a gauged $(SL(2,R) \times U(1))/ U(1)$ WZW model~\cite{Apolo:2019zai}.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2021-12-05 alpha/BeyondAdSCFT/beyondAdS.tex
Add image of the duality triangle
Add minor corrections of AdS notes

@@
 	Note that both sides of the duality includes a non-trivial moduli \needcites.
-\wx{In particular, the S\cft{2} on the right-hand side is proposed to be a \textit{symmetric product orbifold theory} \needcites, together with its exactly marginal deformations along the conformal manifold.
+\wx{In particular, the S\cft{2} on the right-hand side is proposed to be a \textit{symmetric orbifold theory} \needcites, together with its exactly marginal deformations along the conformal manifold.
 }{elaborate?}
@@
 \centering
- \includegraphics[scale=0.45]{diagram4}
+ \includegraphics[scale=0.45]{img/diagram4}
 \caption{The holographic correspondence between string theory on AdS$_3 \times M^7$ backgrounds and two-dimensional CFTs (inner triangle), and its relationship to the conjectured duality between TsT transformations of AdS$_3 \times M^7$ spacetimes, bi-current deformations of the worldsheet action, and single-trace irrelevant deformations of two-dimensional CFTs (outer triangle).

### 2021-12-08 alpha/BeyondAdSCFT/beyondAdS.tex
Add TTbar updates from John & minor stuff

@@
 
+\subsubsection{The worldsheet \cft{2}}
+
 \section{Holographic Dualities Beyond \ads{3}/\cft{2}}
@@
 
-\subsection{$T\bar{T}$ deformation}
+\eq{D(x,\bar x)=\int d^2z (\partial_x J \partial_x+2\partial_x^2J)(\partial_{\bar{x}} \bar{J} \partial_{\bar{x}}+2\partial_{\bar{x}}^2\bar{J}) \Phi_1}
+
+\eq{A^a(x,\bar{x})=\int d^2z k^a(z)(\partial_{\bar{x}} \bar{J} \partial_{\bar{x}}\Phi_1+2\partial_{\bar{x}}^2\bar{J}\Phi_1)}
+
+The dual spacetime CFT at large $p$ is argued to be the symmetric product orbifold $\mathcal{M}^p/S_p$, denoting the seed theory $\mathcal{M}$, the energy-momentum tensor can be written as 
+\eq{T(x)=\sum_{i=1}^p T_i(x)}
+
+which can be also written as 
+\eq{T(x)=\frac1{2k}(\partial_x J\partial_x \Phi_1+2\partial_x^2 J\Phi_1)\bar{J}(\bar{x};\bar{z})}
+
+The OPEs are 
+\eq{T(x, \bar{x}) D(y, \bar{y})\sim \frac{c_{\mathcal{M}}}{(x-y)^4}\bar{T}(\bar{y})+\cdots}
+
+\subsection{\TTbar deformation}
 In a Lorentzian invariant theory, the stress tensor $T^{\mu\nu}$ is conserved, i.e. $\partial_\mu T^{\mu\nu}=0$. One can define its determinant $\text{Det} T_{\mu\nu}$ as 

### 2022-01-06 alpha/BeyondAdSCFT/beyondAdS.tex
Add notes on the worldsheet CFT

@@
 		},
+	\label{eq:massless_btz_G}
 	\\
@@
 	\quad e^{2\Phi} = \frac{k}{p},
+	\label{eq:massless_btz_B}
 	\end{gather}
@@
 This is sometimes referred to as the \textit{spacetime} \cft{2}.
-Therefore the NS1-NS5 system serves as a realization of \ads{3}/\cft{2} where both sides of the holographic duality are in some sense, under control.
+Therefore the NS1-NS5 system serves as a realization of \ads{3}/\cft{2} where both sides of the holographic duality are, in some sense, under control.
 
 \subsubsection{The worldsheet \cft{2}}
+
+	The bosonic action of the worldsheet theory is given by \wx{the familiar non-linear sigma model \needcites:}{conventions?}
+	\begin{equation}
+	\begin{aligned}
+		S &= \sidenote{-} \frac{1}{4\pi\alpha'}
+			\int \dd[2]{z} \sqrt{-\eta}\,\big(
+					\eta^{ab} G_{\mu\nu} (X)
+					+ \epsilon^{ab} B_{\mu\nu} (X)
+				\big)\,\pdd{a} X^\mu \pdd{b} X^\nu \\
+		&= \frac{k}{2\pi}
+			\int \dd[2]{z} \pqty{
+				\pd\rho\,\pdbar\rho
+				+ e^{2\rho}\,\pd\bar{\gamma}\,\pdbar\gamma
+			} \\
+	\end{aligned}
+	\end{equation}
+	where in the second line we've restricted to the \ads{3} part and plugged in the BTZ solution given in \eqref{eq:massless_btz_G} and \eqref{eq:massless_btz_B}.
+We see that $\rho$ is a Liouville field.
+	We can further introduce an auxiliary field $\beta$, which leads us to the \wx{Wakimoto representation \needcites:}{conventions?}
+	\begin{equation}
+		S[\rho,\gamma,\bar{\gamma},\beta,\bar{\beta}]
+		= \frac{k}{2\pi}
+			\int \dd[2]{z} \pqty{
+				\pd\rho\,\pdbar\rho
+				+ \beta\,\pdbar\gamma
+				+ \bar{\beta}\,\pd\bar{\gamma}
+				- \beta \bar{\beta}\,e^{-2\rho}\,
+					\sidenote{\pdbar\bar{\gamma}\,\pd\gamma}
+			}
+	\end{equation}
+	It returns to the original action after we integrate out $\beta$.
+From this action it is clear that at large radius (large $\rho$), the last term in the action can be dropped, and the theory is well approximated by free fields, including a free scalar $\rho$, a pair of left-moving free fermions $(\beta,\gamma)$, and a pair of right-moving ones $(\bar{\beta},\bar{\gamma})$.
+
+	An alternative representation is given in terms of the $\widehat{\mrm{SL}}(2,\mbb{R})_k$ WZW model.
 

### 2022-12-28 HW-Gravity/gravity1/gravity1.tex
Fix minor issues on AdS geodesics
Add misc fixes & updates

@@
 		\ge 0
-	$, thus $\gamma$ can be either spacelike or null, but not timelike. In fact, $
-		\frac{1}{z}\dv{z}{\lambda} = 0,\pm 1
-	$, along with $\dv{x^\mu}{\lambda} = z^2 p^\mu$, we obtain:
+	$, thus $\gamma$ can be either spacelike or null, but not timelike. In fact, we have $
+		\frac{V^z}{z}
+		= \frac{1}{z}\dv{z}{\lambda}
+		= 0,\pm 1
+	$; along with $\dv{x^\mu}{\lambda} = z^2 p^\mu$, we obtain:
 	\begin{equation}
@@
 	\item $p^2 = 0$: parabolic, given in \eqref{eq:null_type}, with one end going to $z\to 0$ and the other end going to $z\to\infty$; it takes infinite proper length $\lambda$ for it to reach $0$ or $\infty$.
-	\item $p^2 > 0$: hyperbolic, given in \eqref{eq:unified_geodesic} and \eqref{eq:hyperbolic}, also with one end going to $z\to 0$ and the other end going to $z\to\infty$, but it reaches $\infty$ within finite $\lambda$.
+	\item $p^2 < 0$: hyperbolic, given in \eqref{eq:unified_geodesic} and \eqref{eq:hyperbolic}, also with one end going to $z\to 0$ and the other end going to $z\to\infty$, but it reaches $\infty$ within finite $\lambda$.
 	\item $p^2 > 0$: elliptic, given in \eqref{eq:unified_geodesic} and \eqref{eq:elliptic}, with both ends going to $z\to 0$, and it takes infinite proper length $\lambda$ for it to reach either end. 
@@
 		A
-		&= \int_{z=-\epsilon}^{z=\epsilon}
-			\frac{\dd{x}^2 + \dd{z}^2}{z^2} \\
-		&= \int_{-\Lambda}^{\Lambda}
+		&= \int_{z\ge\epsilon}
+			\sqrt{\frac{\dd{x}^2 + \dd{z}^2}{z^2}} \\
+		&= \int_{\abs{\lambda} \le \Lambda} \sqrt{
 			\frac{
@@
 				+ (\dd{\sech\lambda})^2
-			}{(\sech\lambda)^2},
+			}{(\sech\lambda)^2}
+		},
 		\quad \Lambda

### 2022-12-28 alpha/SUSY/susy.tex
Add misc fixes & updates

@@
 
+\subsection{Some cool facts about anomaly}
+\label{subsect:anomaly}
+\references{
+	\begin{enumerate}[noitemsep,topsep=0pt]
+	\item \textcite{Tong:2018gauge}, \S3
+	\item \textcite{Schwartz:2014sze}, \S30
+	\end{enumerate}
+}\vspace{\parskip}
+
+	At the classical level, a massless Dirac fermion in \textit{even} dimensions enjoys the symmetry:
+	\begin{equation}
+		\mrm{U}(1)_V \times \mrm{U}(1)_A
+	\end{equation}
+	But only a $\mrm{U}(1)$ subgroup survives after quantization of the continuum field theory. This is the so-called chiral anomaly.
+
+	The interesting thing is that we can actually choose the surviving $\mrm{U}(1)$ subgroup.
+The $\mrm{U}(1)_A$ subgroup is often doomed to suffer, which is why we often don't distinguish the chiral anomaly with the so-called axial anomaly.
+	On the other hand, the $\mrm{U}(1)_V$ subgroup is usually the lucky survivor, due to its close relation with the gauge symmetry, which affects our choice of regularization schemes.
+
+	Recall that in general, anomaly arises when it's impossible to choose a regularization scheme that is compatible with the symmetry.
+In usual computations of the chiral anomaly, we often assume the survival of $\mrm{U}(1)_V$, either explicitly or implicitly.
+	\begin{itemize}
+	\item Let's denote the axial current as $j^\sigma$ and the vector current as $J^\mu$.
+When computing the triangle diagram $\vev{j^\sigma J^\mu J^\nu}$ in 4D, there is a free paramter that we can tune to regularize the loop momentum integral, which ``distributes'' the anomalous amplitude between $\pdd{\sigma} j^\sigma$ and $\pdd{\mu} J^\mu$.
+More precisely, the result is that $\pdd{\sigma} \vev{j^\sigma J^\mu J^\nu}$ and $\pdd{\mu} \vev{j^\sigma J^\mu J^\nu}$ cannot vanish simultaneously.
+
+	\item Computing $\vev{j^\sigma J^\mu J^\nu}$ is equivalent to computing $\vev{j^\sigma}_A$, where $A^\mu$ is some non-dynamic background gauge field coupled to $J^\mu$. Basically\footnote{
+		This is taken from \S22.3 of \textcite{Weinberg:1996kr}, Vol.\,II, where there is an extra minus sign in the front, probabaly due to a different convention for the current $j$. 
+	},
+	\begin{equation}
+		\vev{j^\sigma}_A
+		= \frac{1}{2} \int \dd[D]{x} \dd[D]{y}
+			\vev{j^\sigma J^\mu(x) J^\nu(y)}\,
+			A_\mu(x) A_\nu(y)
+	\end{equation}
+	I believe the $\frac{1}{2}$ factor here is to cancel the overcounting as we integrate over both $x$ and $y$.
+
+	\item We usually compute the axial anomaly for a massless Dirac fermion.
+Equivalently, we can look at its components, which are a pair of left and right-handed Weyl fermions, charged $Q = \pm 1$ under $\mrm{U}(1)_A$.
+They each contribute half of the anomaly.
+To prove this, one can insert a projection matrix $\frac{1 \pm \gamma_5}{2}$ which reduces the action for a Dirac fermion to that of a Weyl fermion\footnote{
+		Note that the Dirac mass term mixes left and right-handed components and will always be projected out. 
+	}; see \S30.2.4 of \cite{Schwartz:2014sze}.
+
+	In general, we can consider a series of Weyl fermions charged $Q$ under $\mrm{U}(1)_A$.
+Their contribution to the anomaly will be given by $\Tr Q\gamma_5$, where the trace goes over the whole representation.
+For the massless Dirac fermion with $Q = \pm 1$, we have:
+	\begin{equation}
+	\begin{aligned}
+		\Tr_{\,\textsl{Dirac}} Q\gamma_5
+		&= \Tr_{\,\textsl{Dirac}} \pqty{
+				\frac{1 + \gamma_5}{2}\,Q
+				- \frac{1 - \gamma_5}{2}\,Q
+			} \\
+		&= \Tr_{\,\textsl{Dirac}} \pqty{
+				\frac{1 + \gamma_5}{2}\,(+1)
+				- \frac{1 - \gamma_5}{2}\,(-1)
+			}
+		= \frac{1}{2} + \frac{1}{2}
+		= 1
+	\end{aligned}
+	\end{equation}
+
+	\item Note that the axial $\mrm{U}(1)_A$ only exists in even dimensions, where we have a chirality matrix $\Gamma$ like $\gamma_5$, and we have Weyl spinors with definite chiralities; see \S1.1.
+In odd dimensions there are only (symplectic) Majorana spinors, so we can't even define $\mrm{U}(1)_A$ at the classical level.
+
+	On the other hand, massless Majorana spinors in even dimensions do admit $\mrm{U}(1)_A$ just like massless Dirac spinors, but it must be $\mrm{U}(1)_V$ neutral due to the reality condition\footnote{
+		It does have a $\mbb{Z}_2$ symmetry which can be understood as the remnant of the $\mrm{U}(1)_V$ at $\theta = \pi$, where $e^{i\theta} = -1$.
+This is quite similar to the fermion number symmetry $(-1)^F$ discussed in \S1.2.
+	}.
+
+	\end{itemize}
+
 \vspace{1.2\baselineskip}

### 2023-03-04 beta/Renormalization/wilson.tex
Add minor updates to various notes
Add minor updates on Wilsonian RG

@@
 	  \end{itemize}
+	\item Zee, III.1
 	\item Schwartz, Chapter 15
+	\item Srednicki, Chapter 29, \textit{Effective field theory}
 	\item Peskin \& Schroeder, Chapter 10, 11 \& 12
@@
 
-	The path integral measure, however, is \textit{not} scale-invariant; we have to add back some Fourier modes in between to return the path integral back to $\Lambda_0$.
-Luckily, the additional modes happen to cancels out the $Z_\phi$ factor in \eqref{eq:PI_free}:
+	The path integral measure, however, is generally not scale-invariant; we have to add back some Fourier modes in between to return the path integral back to $\Lambda_0$.
+Luckily, in the case of a massless free scalar on a flat background, the additional modes happen to cancels out the $Z_\phi$ factor in \eqref{eq:PI_free}:
 	\begin{equation}
@@
 Diagrammatically, they are produced by the one particle irreducible (1PI) diagrams.
+Roughly speaking, we have:
+	\begin{equation}
+		\log \sum \,(\text{all diagrams})
+		\sim \sum \,(\text{connected diagrams})
+		\sim \sum \,(\text{tree with 1PI vertices})
+	\end{equation}
 

### 2023-04-28 alpha/GlueonAdS/glueon-beamer.tex
Add slides for glueon AdS

% !TeX document-id = {c68ea1ac-ebac-4541-a297-17005c6d2297}
% !TeX encoding = UTF-8
% !TeX spellcheck = en_US
% !TeX TS-program = pdflatex
% !TeX TXS-program:bibliography = biber -l zh__pinyin --output-safechars %

\documentclass[aspectratio=169,10pt
%	,draft
%	,handout
	,noamsthm
]{beamer}

\input{preamble.tex}

\usepackage{tikz}
%\usepackage{snapshot}

\title{Glue-on AdS holography for $T\bar T$-deformed CFTs}
\subtitle{Holography duality beyond AdS/CFT}
\author{%
	Wen-Xin Lai 
	\texstringonly{\,}\textkai{赖文昕}%
	\texstringonly{\\[1ex]
		\textit{\small in collaboration with} \\
			Luis Apolo,
			Peng-Xiang Hao \textkai{郝鹏翔}
			and Wei Song \textkai{宋伟}\\[2ex]
		\sidenote{\arxiv{2303.04836}}
		\ submitted to \textit{JHEP}
	}%
}
\institute{\small%
	Yau Mathematical Sciences Center,
	Tsinghua\texstringonly{
%		\\\large\ccbyncsajp
	}%
}
\date{}

\newcommand{\veccol}[1]{\pqty{
	\begin{smallmatrix}
		#1
	\end{smallmatrix}
}}

\addbibresource{glueon-beamer.bib}
%\usepackage{cprotect}

\usepackage{cancel}
\newcommand{\slot}{{\,\bullet}}

\usepackage{xspace}
\newcommand{\TTbar}{\texorpdfstring{\ensuremath{T\bar{T}}}{TTbar}\xspace}

\begin{document}
{%%% TITLEPAGE
\setbeamercolor{title in head/foot}{
		use=palette quaternary
		,fg=palette quaternary.bg
	}
\logo{}
\begin{frame}
%	\titlegraphic{\vspace{2\baselineskip}}
	\titlepage
	\tikz [remember picture,overlay]
	\node at ([
		yshift=-2.5\baselineskip,xshift=.3\linewidth
	] current page.center) {
		\begin{minipage}{.5\textwidth}
		\centering
		\includegraphics[height=.45\textheight]{img/escher_links.png}
		\\[2ex]
		\footnotesize fig:~\textcite{Dunham:Escher} on Escher's art
		\hspace{-1em}
		\end{minipage}
	};

\end{frame}
}%%% TITLEPAGE

\begin{frame}{Outline}
\raggedbottom
\large
\tableofcontents
\end{frame}

\section{\textbf{Background:} AdS/CFT holography}

\newcommand{\stateAdsCft}{\ensuremath{
	\textrm{String Theory on $\mrm{AdS}_{d+1}$ background}
	&\ \equiv\ 
	\textrm{Conformal Field Theory $\mrm{CFT}_{d}$}
\\
	\textrm{Asymptotically $\mrm{AdS}_{d+1}$ Gravity}
	&\ \equiv\ 
	\textrm{Large $N$ $\mrm{CFT}_{d}$ at asympt.~boundary}
}}

\begin{frame}{AdS/CFT --- holography duality}{%
	\textcite{Maldacena:1997re} --- \citetitle{Maldacena:1997re}%
}
\vspace{-1\baselineskip}
\begin{align}
\stateAdsCft
\end{align}
\vspace{-1.5\baselineskip}
\pause
\begin{itemize}
\item (asympt.) AdS: Anti-de Sitter spacetime, geometry with negative Ricci curvature $R < 0$, solution of Einsteins equations with cosmological constant $\Lambda < 0$:
\begin{equation}
	R_{\mu\nu} - \frac{1}{2}\,R g_{\mu\nu}
	+ \Lambda g_{\mu\nu}
	= 8\pi G_N T_{\mu\nu}^{\textit{matter}},\quad
	\Lambda < 0
\label{eq:einstein}
\end{equation}

\pause
\item CFT: conformal field theory, quantum field theory (QFT) invariant under rescaling\textsuperscript{*}, well defined \& well understood in math
\begin{equation}
	g_{ij} \sim e^{2\Omega(x)} g_{ij}
\end{equation}
*\,``ruler-independent'', {\footnotesize unless there is an \textit{``anomaly''}, but everything is still under control}
\end{itemize}
\vspace{\baselineskip}
\end{frame}

\begin{frame}{AdS/CFT --- a model of quantum gravity}{%
	\textcite{Maldacena:1997re} -- \citetitle{Maldacena:1997re}%
}
\vspace{-1.5\baselineskip}
\begin{align*}
\stateAdsCft
\end{align*}
\vspace{-1.5\baselineskip}
\pause
\begin{itemize}

\item A model of \textsc{quantum gravity}, discovered from dualities in \textsc{string theory}
	\begin{itemize}
	\item Dualities: equivalent descriptions for the same theory, physicist's ``proof'' of AdS/CFT
	\item No general proof yet in the mathematical sense, but there is \textit{overwhelming} evidence
	\end{itemize}

\pause
\item Universal / ubiquitous
\begin{itemize}
	\item Model agnostic: $\mrm{AdS}_5\times S^5$, $\mrm{AdS}_3\times S^3 \times T^4$, symmetric orbifolds, minimal models, ``monsters'', ... \textit{\small Maldacena, Witten, GKP, ABJM, Gaberdiel, and many many more}
	\item Our work: based on universal properties of $\mrm{AdS}_3/\mrm{CFT}_2$ $(d=2)$.

\end{itemize}
\end{itemize}
\end{frame}

\newcommand{\figAdsCft}{
\begin{figure}[!h]
	\centering
	\includegraphics[width=\linewidth]{img/ads-cft.png}

	\vspace{-.3\baselineskip}
	\caption{$\mrm{AdS}_3/\mrm{CFT}_2$ cartoon}

	\vspace{-.3\baselineskip}
	\scriptsize\ Image courtesy: \textcite{AldegundePWSep22}
\end{figure}
}

\begin{frame}{$\mrm{AdS}_3/\mrm{CFT}_2$ --- gravity trapped in a \textit{Poincar\'e cylinder}}{%
	Title inspired by
	\textcite{Kraus:2021cwf} -- \citetitle{Kraus:2021cwf}%
}
\begin{columns}
\begin{column}{.45\textwidth}
\figAdsCft
\end{column}
\begin{column}{.55\textwidth}
	\begin{itemize}
	\item $\mrm{AdS}_3$ metric,
	\begin{equation}
	\hspace{-2em}
		ds^2 = \ell^2 \frac{d\rho^2}{4 \rho^2} + \pqty{\frac{1}{\rho} g^{(0)}_{ij} + g^{(2)}_{ij} + \rho\thinmspace g^{(4)}_{ij} + \cdots}\, dx^i dx^j \label{fggauge}
	\end{equation}

	\vspace{-.5\baselineskip}
	boundary at $\rho \to 0$, $x^{i} \sim \varphi, t$, $i = 1,2$

\pause
	\item Surprisingly the expansion simply terminates at~$\rho\thinmspace g^{(4)}_{ij}$ for pure Einstein gravity! Moreover,
	\begin{equation}
		g^{(4)}_{ij} = \frac{1}{4} g^{(2)}_{ik} g^{(0)\thinmspace kl}_{\phantom{kl}} g^{(2)}_{lj}
	\end{equation}
	\textcite{Fefferman:2007rka,Banados:1998gg}
	\end{itemize}
\end{column}
\end{columns}
\end{frame}

\begin{frame}{$\mrm{AdS}_3/\mrm{CFT}_2$ --- simple realization of holography}{%
	\textcite{Aharony:1999ti} -- \citetitle{Aharony:1999ti}
}
\begin{columns}
\begin{column}{.4\textwidth}
\figAdsCft
\end{column}
\begin{column}{.6\textwidth}
	\begin{itemize}
	\item $\mrm{AdS}_3$ metric for $\rho > 0$, \\
	\textcite{Banados:1998gg}
	\begin{equation}
	\hspace{-2.5em}
		ds^2 = \ell^2 \bigg( \frac{d\rho^2}{4 \rho^2} + \frac{ \big( du + \rho \, \mathcal {\bar L}(v)\, dv \big) \big( dv + \rho \, \mathcal L(u)\, du \big) }{\rho} \bigg)\ \label{banados}
	\end{equation}
	$g^{(2)} \leadsto \mathcal L(u)$, $\bar{\mathcal L}(v)$: arbitrary periodic functions,\\
	where $u,v = \varphi \mp it$, $du\,dv = d\varphi^2 + dt^2$
%	\vspace{-.5\baselineskip}

\pause
	\item A consequence of Einstein equations \eqref{eq:einstein} \\
	in $(2+1)$ dimensions.\\
	\textit{Too many constraints, too little freedom!}
	\end{itemize}
\end{column}
\end{columns}
\end{frame}

\begin{frame}{$\mrm{AdS}_3/\mrm{CFT}_2$ --- simple realization of holography}{%
	\textcite{Banados:1992wn} -- \citetitle{Banados:1992wn}
}
\begin{columns}
\begin{column}{.4\textwidth}
\figAdsCft
\end{column}
\begin{column}{.6\textwidth}
	\begin{itemize}
	\item Different \textbf{geometries} in the ``bulk''
	\begin{equation}
	\hspace{-2.5em}
		ds^2 = \ell^2 \bigg( \frac{d\rho^2}{4 \rho^2} + \frac{ \big( du + \rho \, \mathcal {\bar L}(v)\, dv \big) \big( dv + \rho \, \mathcal L(u)\, du \big) }{\rho} \bigg)\ \label{banados}
	\end{equation}
	specified by $\mathcal L(u)$, $\bar{\mathcal L}(v)$: arbitrary periodic functions

	\vspace{.5\baselineskip}

\pause
	\item ... maps to different \textbf{states} in the boundary $\mrm{CFT}_2$
	\begin{itemize}
		\item \textit{state:} excitations of the boundary field theory
		\item \textit{spectrum} of the Hamiltonian operator, $\hat{H}$
	\end{itemize}
%	\item In a \textit{holographic} theory, $,\\
%	a boundary state can be prepared by a bulk path integral.
	\end{itemize}
\end{column}
\end{columns}
\end{frame}

\begin{frame}{$\mrm{AdS}_3/\mrm{CFT}_2$ --- the holographic dictionary}{%
	\textcite{Aharony:1999ti} -- \citetitle{Aharony:1999ti}
}
\begin{columns}
\begin{column}{.4\textwidth}
\figAdsCft
\end{column}
\begin{column}{.6\textwidth}
	\begin{itemize}
	\item \textit{Dictionary:} bulk $\leftrightarrow$ boundary quantities

	\begin{itemize}
	\item spectrum,
	\item symmetry,
	\item correlations, ...
	\end{itemize}

	\item Partition function:
	\begin{equation}
		\mcal{Z}_{\pd B}
		= \sum_{i \in \textit{states}} \ave{e^{-\beta \hat{H}}}_i
		= \mcal{Z}_{B\textit{ulk}}
	\end{equation}
	weighted sum over the spectrum

	\end{itemize}
\end{column}
\end{columns}
\end{frame}

\section{\textbf{Review:} \TTbar deformation and cutoff AdS holography} \label{se:cutoffholography}

\begin{frame}{\TTbar deformations --- motivations}{%
	Comments taken from \textcite{Cui:2023jrb}
}
\begin{columns}
\begin{column}{.45\textwidth}
\figAdsCft
\end{column}
\begin{column}{.55\textwidth}
	\begin{itemize}
	\item Ideally: AdS/CFT
	\item Reality: non-AdS space and non-CFT
	\begin{itemize}
		\item possible to extend holographic principle to more general context?
		\item attempt: \textbf{\textit{deformations}} on both sides\\
		in a controllable way
	\end{itemize}
	\end{itemize}
\end{column}
\end{columns}
\end{frame}

\begin{frame}{\TTbar deformations --- definition}{%
	\textcite{Zamolodchikov:2004ce},\\
	revived by \textcite{Smirnov:2016lqw,Cavaglia:2016oda}
}
\begin{itemize}
\item Path integral formalism:
\begin{equation}
	\mcal{Z}
	= \sum_{i \in \textit{states}} \ave{e^{-\beta \hat{H}}}_i
	= \int \DD{\phi(x)} e^{-I[\phi(x)]}
\label{eq:partition}
\end{equation}
$I[\phi(x)]$: action (energy) functional of the fields $\phi(x)$\\
\phantom{$I[\phi(x)]$: }captures the dynamics of the theory

\pause

\item Stress tensor $T_{ij}[\phi(x)]$: energy momentum, local and covariant version of $\hat{H}$
\begin{equation}
%	\label{TTbardefintro}
	\partial_\mu I = -{8 \pi} \int d^2x \, T\bar T =  -{\pi} \int d^2x\,\big( T^{ij}T_{ij}- (T^i_i)^2 \big)
\end{equation}
For $\mrm{CFT}_2$,\ $T\bar{T} = T_{xx} T_{\bar{x}\bar{x}}$,\ where $x, \bar{x} = \varphi' \mp it'$.
{\footnotesize We've set the length scale $\ell = 1$.}

\end{itemize}
\end{frame}

\begin{frame}{\TTbar deformations --- ``solvable''}{%
	\textcite{Zamolodchikov:2004ce},\\
	revived by \textcite{Smirnov:2016lqw,Cavaglia:2016oda}
}
\vspace{-.3\baselineskip}
\begin{itemize}
\item Define of \TTbar as the flow of action:
\begin{equation}
	\label{TTbardefintro}
	\partial_\mu I = -{8 \pi} \int d^2x \, T\bar T =  -{\pi} \int d^2x\,\big( T^{ij}T_{ij}- (T^i_i)^2 \big)
\end{equation}
This is a \textit{flow equation} from some generic QFT specified by $I(\mu = 0)$.

\pause

\item \textbf{``Solvable'':} the deformed spectrum of $\hat{H}(\mu)$ and $\hat{J}(\mu)$ on a cylinder of radius $R$\\
can be solved, and it's a simple function of the undeformed $E(0)$, $J(0)$:
\begin{equation}
	E(\mu) = - \frac{R }{ 2\mu } \bigg(1-\sqrt{1 + \frac{4\mu}{R} E(0) + \frac{4\mu^2}{R^4} J(0)^2 }
	\,\bigg), \ \quad J(\mu)=J(0) % \label{ttbarspectrum}
\end{equation}
under simple (and reasonable) assumptions (e.g.~translation invariance et al).

\end{itemize}
\end{frame}

\begin{frame}{\TTbar deformations --- properties}{%
	\textcite{Zamolodchikov:2004ce}\\
	\citetitle{Zamolodchikov:2004ce}
}
\vspace{-1.\baselineskip}
\begin{equation}
	\partial_\mu I = -{8 \pi} \int d^2x\,T\bar T
	\label{TTbardef}
\end{equation}
\begin{equation}
	E(\mu) = - \frac{R }{ 2\mu } \bigg(1-\sqrt{1 + \frac{4\mu}{R} E(0) + \frac{4\mu^2}{R^4} J(0)^2 }
	\,\bigg), \ \quad J(\mu)=J(0)  \label{ttbarspectrum}
\end{equation}
\vspace{-\baselineskip}
\begin{itemize}
\item It seems that the \TTbar deformation is well-defined non-perturbatively for generic $\mrm{QFT}_2$,\\
yet mysterious: computations of many quantities are difficult\\
\begin{itemize}
\item e.g.~correlators: \textcite{Kraus:2018xrn,Cardy:2019qao,Cui:2023jrb}
\item ``asymptotic fragility'': \textcite{Dubovsky:2017cnj}
\end{itemize}

\pause
\item What if we start from a $\mrm{CFT}_2$, that enjoys a holographic dual to $\mrm{AdS}_3$...

\end{itemize}
\end{frame}

\newcommand{\figCutoffAds}{
\begin{figure}[!h]
	\hfill\includegraphics[width=.8\linewidth]{img/cutoff-ads.jpg}

	\centering
	\vspace{-.3\baselineskip}
	\caption{Cutoff $\mrm{AdS}_3/\TTbar$ duality}

	\vspace{-.3\baselineskip}
	\scriptsize\ Image courtesy: \textcite{AldegundePWSep22}
\end{figure}
}

\begin{frame}{Cutoff $\mrm{AdS}_3$ / \TTbar deformed $\mrm{CFT}_2$}{%
	\textcite{McGough:2016lol} --
	\citetitle{McGough:2016lol}
}
\begin{columns}
\begin{column}{.4\textwidth}
\figCutoffAds
\end{column}
\begin{column}{.6\textwidth}
	\begin{itemize}
	\item Question: what is the AdS dual of \TTbar deformation?\\

	\begin{itemize}
	\item look up \textit{double-trace deformations}\\
	in \textit{the dictionary}:\\
	\textcite{Heemskerk:2010hk}

\pause
	\item look at properties of \TTbar:\\
	signs of gravity and coarse-graining\\
	\textcite{Dubovsky:2012wk,Dubovsky:2013ira}
	\end{itemize}

	\pause
	\item Answer: AdS gravity within a finite Dirichlet wall

	\end{itemize}
\end{column}
\end{columns}
\end{frame}

\begin{frame}{Cutoff $\mrm{AdS}_3$ --- the dictionary}{%
	\textcite{McGough:2016lol} --
	\citetitle{McGough:2016lol}
}
\begin{columns}
\begin{column}{.35\textwidth}
\figCutoffAds
\end{column}
\begin{column}{.65\textwidth}
	\begin{itemize}
	\item Location (radius) of the cutoff surface:
	\begin{equation}
		\frac{1}{\zeta} \equiv \ell^{-2} g_{\varphi\varphi} \label{cutoff}
	\end{equation}
	gets mapped to the deformation parameter $\mu$:
	\begin{equation}
		\zeta_c = - \frac{c \mu}{3\ell^2}
		\label{dictionary}
	\end{equation}

\pause

	\item Passed many non-trivial tests
	\item Generalized to ``mixed boundary conditions''\\
	by \textcite{Guica:2019nzm}

	\end{itemize}
\end{column}
\end{columns}
\end{frame}

\begin{frame}{Cutoff $\mrm{AdS}_3$ --- gravity in a box}{%
	Title inspired by
	\textcite{Kraus:2021cwf} -- \citetitle{Kraus:2021cwf}%
}
\begin{columns}
\begin{column}{.35\textwidth}
\figCutoffAds
\end{column}
\begin{column}{.65\textwidth}
\vspace{-.5\baselineskip}
	\begin{itemize}
	\item \textbf{Significance:} gravity inside a finite box\\
		with hard Dirichlet walls

	\begin{itemize}
		\item Dual to some ``solvable'' non-conformal theory
		\item A step towards quantum gravity in reality!
	\end{itemize}

\pause
	\item \textbf{Caveat:} the duality only admits $\zeta_c > 0$ so $\mu < 0$
	\begin{equation}
		\zeta_c = - \frac{c \mu}{3\ell^2}
%		\label{dictionary}
	\end{equation}
	But \TTbar itself admits $\mu > 0$ with nice properties.\\
	\textit{What is the other side of the duality?}
	\end{itemize}
\end{column}
\end{columns}
\end{frame}

\section{\textbf{Proposal:} Glue-on AdS holography} \label{se:glueonproposal}

\begin{frame}{Glue-on $\mrm{AdS}_3$ --- analytic continuation}{%
	\textcite{Apolo:2023vnm} -- \citetitle{Apolo:2023vnm}
}
	\begin{itemize}
	\item $\mrm{AdS}_3$ metric has only simple poles:
	\begin{equation}
		ds^2 = \ell^2 \bigg( \frac{d\rho^2}{4 \rho^2} + \frac{ \big( du + \rho \, \mathcal {\bar L}(v)\, dv \big) \big( dv + \rho \, \mathcal L(u)\, du \big) }{\rho} \bigg)\ %\label{banados}
	\end{equation}
	thus it admits well-defined analytic continuation from $\rho > 0$ to $\rho \in \mbb{R}$.
	\item Continuation of the dictionary:
	\begin{equation}
		\frac{1}{\zeta} \equiv \ell^{-2} g_{\varphi\varphi} \in \mbb{R},
	\ \quad
		\zeta_c = - \frac{c \mu}{3\ell^2} \in \mbb{R}
	\end{equation}
%	\vspace{-.5\baselineskip}

	\end{itemize}
\end{frame}

\newcommand{\figGlueon}{
\begin{figure}[!h]
	\centering
	\includegraphics[width=.8\linewidth]{img/diagram.pdf}
	\vspace{-.3\baselineskip}
	\caption{Glue-on $\mrm{AdS}_3$}

	\vspace{-.3\baselineskip}
	\scriptsize\ Top-down view of the ``Poincare cylinder''
\end{figure}
}

\begin{frame}{Glue-on $\mrm{AdS}_3$ / \TTbar --- updating the dictionary}{%
	\textcite{Apolo:2023vnm} -- \citetitle{Apolo:2023vnm}
}
\begin{columns}
\begin{column}{.4\textwidth}
\figGlueon
\end{column}
\begin{column}{.6\textwidth}
\vspace{-\baselineskip}
\begin{equation}
	\frac{1}{\zeta} \equiv \ell^{-2} g_{\varphi\varphi} \in \mbb{R},
\ \quad
	\zeta_c = - \frac{c \mu}{3\ell^2} \in \mbb{R}
\end{equation}
\vspace{-.5\baselineskip}
\begin{itemize}
\item What have we done other than copy-pasting?
	\begin{itemize}
	\item Although the continuation is straightforward, physical quantities diverge as $\rho \to 0$

	\item A prescription is required to ``renormalize'' the divergences
	\end{itemize}

\end{itemize}
\end{column}
\end{columns}
\end{frame}

\begin{frame}{Glue-on $\mrm{AdS}_3$ / \TTbar --- updating the dictionary}{%
	\textcite{Kraus:2018xrn} -- \citetitle{Kraus:2018xrn}
}
\begin{itemize}
\item Firstly, matching energy momentum \& the flow equations:
	\begin{equation}
		T_{ij}= \frac{\sigma_{\zeta_c}}{8\pi G} \Big( K_{ij} -  K \gamma_{ij} + \frac{1}{\ell |\zeta_c|}\gamma_{ij}\Big), \ \quad \sigma_{\zeta_c} = \frac{\abs{\zeta_c}}{\zeta_c} = \pm 1,
		\label{BYtensor}
	\end{equation}
	The field theory metric $\gamma_{ij} = \zeta_c h_{ij}$, where $h_{ij}$ is the induced metric.

	\pause

	\begin{itemize}
	\item $\gamma_{ij}$ is always positive-definite, while $h_{ij}$ becomes negative-definite for the glue-on region.\\
		This discrepancy is the origin of the absolute values.
	\end{itemize}

	\pause

\item \TTbar flow is recast geometrically as the $i,j$ components of the Einstein equations. \\
Note that the geometry can be decomposed such that:
	\begin{equation}
		ds^2 = \frac{1}{\zeta} \gamma_{ij}dx^i dx^j+n_\mu n_\nu dx^\mu dx^\nu
	\end{equation}
\end{itemize}
\end{frame}

\begin{frame}{Glue-on $\mrm{AdS}_3$ --- beyond the infinity}{%
	\textcite{Apolo:2023vnm} -- \citetitle{Apolo:2023vnm}
}
\begin{itemize}
\item The geometry is foliated by constant $\zeta$ surfaces ${\mathcal N}_\zeta$:
	\begin{equation}
	\begin{aligned}
		ds^2 
		&= \ell^2 \bigg( \frac{d\rho^2}{4 \rho^2} + \frac{ \big( du + \rho \, \mathcal {\bar L}(v)\, dv \big) \big( dv + \rho \, \mathcal L(u)\, du \big) }{\rho} \bigg) \\
		&= \frac{1}{\zeta} \gamma_{ij}dx^i dx^j+n_\mu n_\nu dx^\mu dx^\nu,\ \quad
	\frac{1}{\zeta} \equiv \ell^{-2} g_{\varphi\varphi}
	\end{aligned}
	\end{equation}
	The \TTbar deformed theory lives on $\mcal{N}_{\zeta_c}$ with metric $\gamma_{ij}$.

\pause
\item Treatment for the singularity at $\zeta\to 0^\pm$: introduce $\mathcal N_{\zeta={\pm\epsilon}}$ and glue them together\\
	exclude the $-\epsilon < \zeta < \epsilon$ region until finally sending $\epsilon \to 0$. 
\item We formally denote the boundary surface by the limit $\mathcal N_{0}=\mathcal N_{0^+}=\mathcal N_{0^-}$, though we need to keep track of the asymptotic cutoff $\epsilon$ in actual computations.
\end{itemize}
\end{frame}

\newcommand{\stateGlueon}{\ensuremath{
	\textrm{Cutoff / \textit{glue-on} $\mrm{AdS}_{d+1}$ Gravity}
	\ \equiv\ %
	\textrm{\TTbar deformed $\mrm{CFT}_{d}$ at $\mcal{N}_{\zeta_c}$}\qquad
}}

\begin{frame}{Glue-on $\mrm{AdS}_3$ / \TTbar --- the proposal}{%
	\textcite{Apolo:2023vnm} -- \citetitle{Apolo:2023vnm}
}
\centering
\vspace{-.5\baselineskip}
\begin{minipage}{.5\textwidth}
\centering
\includegraphics[width=.8\linewidth]{img/diagram.pdf}
\end{minipage}
\vspace{-.8\baselineskip}
\begin{equation}
\stateGlueon
\end{equation}
\end{frame}

\section{\textbf{Check:} \TTbar deformed charges \& partition functions} \label{se:charges}

\begin{frame}{\TTbar quantities from bulk geometry}{%
	\textcite{Apolo:2023vnm} -- \citetitle{Apolo:2023vnm}
}
\begin{columns}
\begin{column}{.35\textwidth}
\figGlueon
\end{column}
\begin{column}{.65\textwidth}
\begin{itemize}
\item AdS/CFT: weak / strong duality
	\begin{itemize}
	\item \textit{quantum} quantities on the CFT side\\
		can be computed by (semi-)classical geometry
	\item inherited by the \TTbar deformation
	\end{itemize}

\pause
\item Demanding the extended geometry to be non-singular\\
	re-produces bounds on the \TTbar deformed theory, e.g.
	\begin{equation}
		\zeta_c \ge -1 \quad \Leftrightarrow \quad\mu\le \frac{ 3\ell^2 }{c} \label{reality}
	\end{equation}
	$\zeta_c = -1$ is a horizon of the glue-on geometry, \\
	where $\det g_{\mu\nu} = 0$.

\end{itemize}
\end{column}
\end{columns}
\end{frame}

\begin{frame}{\TTbar spectrum from bulk covariant charges}{%
	\textcite{Kraus:2021cwf,Apolo:2023vnm}
}
\begin{columns}
\begin{column}{.35\textwidth}
\figGlueon
\end{column}
\begin{column}{.65\textwidth}
\vspace{-.3\baselineskip}
\begin{itemize}
\item Spectrum: conserved charges of geometries,\\
	e.g.~black holes \textit{BTZ} \cite{Banados:1992wn}
	\begin{itemize}
	\item computed with the covariant formalism\\
		\textcite{Iyer:1994ys, Barnich:2001jy}
	\item manifest covariance (diff-invariance) depends on reparametrization redundancies (gauge),\\
		so delay gauge fixing until the very end
	\end{itemize}

\pause
\item We are careful to match the bulk \& boundary symmetries at $\mcal{N}_{\zeta_c}$

\item This reproduces $E(\mu)$, $J(\mu)$ with $\mu \in\mbb{R}$ in \eqref{ttbarspectrum}.

\end{itemize}
\end{column}
\end{columns}
\end{frame}

\begin{frame}{\TTbar partition functions from bulk on-shell actions}{%
	\textcite{Kraus:2021cwf,Apolo:2023vnm}
}
\begin{columns}
\begin{column}{.35\textwidth}
\figGlueon
\end{column}
\begin{column}{.65\textwidth}
\vspace{-.3\baselineskip}
\begin{itemize}
\item Bulk: weakly coupled gravity, the partition function \eqref{eq:partition} is approximated by the on-shell gravity action of the dominant saddle (method of steepest descent):
	\begin{equation}
		Z_{T\bar T} (\mu) = \mathcal Z (\zeta_c) \approx  e^{-I(\zeta_c)}\label{partition2}
	\end{equation}

\pause
\item $I(\zeta_c)$ is roughly the volume of the geometry, which diverges at $\zeta \to 0^\pm$. We apply a natural extension of \textit{holographic renormalization} to remove the divergence.

\pause
\item $I = -\log \mcal{Z}$ satisfies the \TTbar flow \eqref{TTbardef}.\\
	This is non-trivial because we've packaged the quantum corrections of the boundary theory.
\end{itemize}
\end{column}
\end{columns}
\end{frame}

\section{Summary \& future directions}

\begin{frame}{Glue-on $\mrm{AdS}_3$ / \TTbar deformed $\mrm{CFT}_2$}{%
	\textcite{Apolo:2023vnm} -- \citetitle{Apolo:2023vnm}
}
\vspace{-1.2\baselineskip}
\begin{equation}
\stateGlueon
\end{equation}
\vspace{-.3\baselineskip}
\begin{columns}
\begin{column}{.3\textwidth}
\centering
\includegraphics[width=\linewidth]{img/diagram.pdf}
\end{column}
\hspace{-1em}
\begin{column}{.7\textwidth}
\begin{itemize}
\item Holographic proposal for $T\bar T$-deformed CFTs with $\mu \in \mbb{R}$

\item As evidence, we show that the $T\bar T$ trace flow equation, the spectrum on the cylinder, and the partition function on the torus and the sphere, among other results, can all be reproduced from bulk calculations in glue-on AdS$_3$.

\pause
\item We hope to understand the entanglement structure of \TTbar deformed theories from bulk geometry.
\end{itemize}
\end{column}
\end{columns}
\end{frame}

\begin{frame}

\centering

\huge
\sidenote{Thank you!}
\bigskip

\large
froms Wen-Xin Lai\ \textkai{赖文昕}

\textit{\normalsize in collaboration with}

	Luis Apolo,
	Peng-Xiang Hao \textkai{郝鹏翔}
	and Wei Song \textkai{宋伟}\\[2ex]
\sidenote{\arxiv{2303.04836}}
\ submitted to \textit{JHEP}

\end{frame}

\begin{frame}[allowframebreaks]{References}
\renewcommand*{\bibfont}{\footnotesize}
\printbibliography %%% should not specify heading etc
\end{frame}

\end{document}

### 2023-06-20 alpha/GlueonAdS/glueon-beamer.tex
Tune glueon slides for physics audience

@@
 
-\documentclass[aspectratio=169,10pt
+\documentclass[
+	10pt
 %	,draft
-%	,handout
+	,handout
 	,noamsthm
@@
 \title{Glue-on AdS holography for $T\bar T$-deformed CFTs}
-\subtitle{Holography duality beyond AdS/CFT}
+\subtitle{An extended AdS\,/\,\TTbar duality \textit{(beyond infinity)}}
 \author{%
@@
 	\texstringonly{\,}\textkai{赖文昕}%
-	\texstringonly{\\[1ex]
+	\texstringonly{
 		\textit{\small in collaboration with} \\
@@
 			and Wei Song \textkai{宋伟}\\[2ex]
-		\sidenote{\arxiv{2303.04836}}
-		\ submitted to \textit{JHEP}
+		\sidenote{\arxiv{2303.04836}}%
+%		\ submitted to \textit{JHEP}
 	}%
@@
 \institute{\small%
-	Yau Mathematical Sciences Center,
+	Yau Mathematical Sciences Center,\\
 	Tsinghua\texstringonly{
@@
 	\node at ([
-		yshift=-2.5\baselineskip,xshift=.3\linewidth
+		yshift=-4.8\baselineskip,
+		xshift=.26\linewidth
 	] current page.center) {
@@
 		\centering
-		\includegraphics[height=.45\textheight]{img/escher_links.png}
-		\\[2ex]
-		\footnotesize fig:~\textcite{Dunham:Escher} on Escher's art
-		\hspace{-1em}
+		\includegraphics[height=.33\textheight]{img/smbc-cantor-cropped.png}
+		\\[.2ex]
+		\footnotesize \url{https://smbc-comics.com/comic/cantor}
+		\hspace{-1.5em}
 		\end{minipage}
 	};
-
 \end{frame}
@@
 
-\section{\textbf{Background:} AdS/CFT holography}
+\section{\textbf{Warmup:} $\mrm{AdS}_{d+1}$/$\mrm{CFT}_{d}$ at $d = 2$}
 
-\newcommand{\stateAdsCft}{\ensuremath{
-	\textrm{String Theory on $\mrm{AdS}_{d+1}$ background}
+\newcommand{\stateAdsCft}{
+\begin{align*}
+	\textrm{Strings on $\mrm{AdS}_{d+1}$ background}
 	&\ \equiv\ 
@@
 \\
-	\textrm{Asymptotically $\mrm{AdS}_{d+1}$ Gravity}
+	\textrm{\textit{asympt.}~$\mrm{AdS}_{d+1}$ Gravity}
 	&\ \equiv\ 
-	\textrm{Large $N$ $\mrm{CFT}_{d}$ at asympt.~boundary}
-}}
+	\textrm{Large $N$ $\mrm{CFT}_{d}$ at \textit{asympt.}~boundary}
+\end{align*}
+}
+
+\newcommand{\citeMaldacena}{%
+	\textcite{Maldacena:1997re} --- \scriptsize\citetitle{Maldacena:1997re}
+}
 
 \begin{frame}{AdS/CFT --- holography duality}{%
-	\textcite{Maldacena:1997re} --- \citetitle{Maldacena:1997re}%
+	\citeMaldacena%
 }
-\vspace{-1\baselineskip}
-\begin{align}
+\vspace{-2.5\baselineskip}
 \stateAdsCft
-\end{align}
-\vspace{-1.5\baselineskip}
-\pause
-\begin{itemize}
-\item (asympt.) AdS: Anti-de Sitter spacetime, geometry with negative Ricci curvature $R < 0$, solution of Einsteins equations with cosmological constant $\Lambda < 0$:
-\begin{equation}
-	R_{\mu\nu} - \frac{1}{2}\,R g_{\mu\nu}
-	+ \Lambda g_{\mu\nu}
-	= 8\pi G_N T_{\mu\nu}^{\textit{matter}},\quad
-	\Lambda < 0
-\label{eq:einstein}
-\end{equation}
+\vspace{-1.8\baselineskip}
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=.5\linewidth]{img/ads-cft.png}
 
-\pause
-\item CFT: conformal field theory, quantum field theory (QFT) invariant under rescaling\textsuperscript{*}, well defined \& well understood in math
-\begin{equation}
-	g_{ij} \sim e^{2\Omega(x)} g_{ij}
-\end{equation}
-*\,``ruler-independent'', {\footnotesize unless there is an \textit{``anomaly''}, but everything is still under control}
-\end{itemize}
-\vspace{\baselineskip}
+	\vspace{-.3\baselineskip}
+	\caption{$\mrm{AdS}_3/\mrm{CFT}_2$ cartoon}
+
+	\vspace*{-.8\baselineskip}
+	\scriptsize\ Image courtesy: \textcite{AldegundePWSep22}
+\end{figure}
+\vspace{-1.3\baselineskip}
 \end{frame}
 
+%\begin{equation}
+%	R_{\mu\nu} - \frac{1}{2}\,R g_{\mu\nu}
+%	+ \Lambda g_{\mu\nu}
+%	= 8\pi G_N T_{\mu\nu}^{\textit{matter}},\quad
+%	\Lambda < 0
+%\label{eq:einstein}
+%\end{equation}
+
 \begin{frame}{AdS/CFT --- a model of quantum gravity}{%
-	\textcite{Maldacena:1997re} -- \citetitle{Maldacena:1997re}%
+	\citeMaldacena
 }
-\vspace{-1.5\baselineskip}
-\begin{align*}
+\vspace{-2.4\baselineskip}
 \stateAdsCft
-\end{align*}
-\vspace{-1.5\baselineskip}
+\vspace{-1.6\baselineskip}
 \pause
@@
 
-\item A model of \textsc{quantum gravity}, discovered from dualities in \textsc{string theory}
-	\begin{itemize}
-	\item Dualities: equivalent descriptions for the same theory, physicist's ``proof'' of AdS/CFT
-	\item No general proof yet in the mathematical sense, but there is \textit{overwhelming} evidence
-	\end{itemize}
+\item A model of \textsc{quantum gravity}
+\item ... originating from \textsc{string theory}
+\item ... seemingly \textsc{Universal / ubiquitous}
 
 \pause
-\item Universal / ubiquitous
 \begin{itemize}
@@
 \textit{\small Maldacena, Witten, GKP, ABJM, Gaberdiel, and many many more}
-	\item Our work: based on universal properties of $\mrm{AdS}_3/\mrm{CFT}_2$ $(d=2)$.
+	\item Our work: pure Einstein gravity in $\mrm{AdS}_3$ / $\mrm{CFT}_2$ $(d=2)$.
 
@@
 
-\newcommand{\figAdsCft}{
+%%% LaTeX3e!
+\NewDocumentCommand{\figAdsCft}{ O{.28} }{
+\begin{column}{#1\textwidth}
 \begin{figure}[!h]
 	\centering
-	\includegraphics[width=\linewidth]{img/ads-cft.png}
+	\includegraphics[width=\linewidth]{img/ads-cft-cleaner.png}
 
-	\vspace{-.3\baselineskip}
-	\caption{$\mrm{AdS}_3/\mrm{CFT}_2$ cartoon}
-
-	\vspace{-.3\baselineskip}
-	\scriptsize\ Image courtesy: \textcite{AldegundePWSep22}
+	\vspace{-.01\baselineskip}
+	\scriptsize\textcite{AldegundePWSep22}\ \,
 \end{figure}
+\end{column}
 }
@@
 \begin{frame}{$\mrm{AdS}_3/\mrm{CFT}_2$ --- gravity trapped in a \textit{Poincar\'e cylinder}}{%
-	Title inspired by
-	\textcite{Kraus:2021cwf} -- \citetitle{Kraus:2021cwf}%
+	\textcite{Aharony:1999ti}
 }
 \begin{columns}
-\begin{column}{.45\textwidth}
 \figAdsCft
-\end{column}
-\begin{column}{.55\textwidth}
+\begin{column}{.75\textwidth}
 	\begin{itemize}
-	\item $\mrm{AdS}_3$ metric,
+	\item $\mrm{AdS}_3$ metric, $\rho \sim z^2 \sim r^{-2}$
 	\begin{equation}
@@
 
+\newcommand{\eqBanados}{
+	\begin{equation*}
+	\hspace{-2em}
+		ds^2 = \ell^2 \bigg( \frac{d\rho^2}{4 \rho^2} + \frac{ \big( du + \rho \, \mathcal {\bar L}(v)\, dv \big) \big( dv + \rho \, \mathcal L(u)\, du \big) }{\rho} \bigg)\ \,
+	\end{equation*}
+}
+
 \begin{frame}{$\mrm{AdS}_3/\mrm{CFT}_2$ --- simple realization of holography}{%
-	\textcite{Aharony:1999ti} -- \citetitle{Aharony:1999ti}
+	\textcite{Banados:1992wn}
 }
 \begin{columns}
-\begin{column}{.4\textwidth}
 \figAdsCft
-\end{column}
-\begin{column}{.6\textwidth}
+\begin{column}{.72\textwidth}
 	\begin{itemize}
@@
 	\textcite{Banados:1998gg}
-	\begin{equation}
-	\hspace{-2.5em}
-		ds^2 = \ell^2 \bigg( \frac{d\rho^2}{4 \rho^2} + \frac{ \big( du + \rho \, \mathcal {\bar L}(v)\, dv \big) \big( dv + \rho \, \mathcal L(u)\, du \big) }{\rho} \bigg)\ \label{banados}
-	\end{equation}
+	\eqBanados
 	$g^{(2)} \leadsto \mathcal L(u)$, $\bar{\mathcal L}(v)$: arbitrary periodic functions,\\
@@
 \pause
-	\item A consequence of Einstein equations \eqref{eq:einstein} \\
+	\item A consequence of Einstein equations \\
 	in $(2+1)$ dimensions.\\
@@
 \begin{frame}{$\mrm{AdS}_3/\mrm{CFT}_2$ --- simple realization of holography}{%
-	\textcite{Banados:1992wn} -- \citetitle{Banados:1992wn}
+	\textcite{Aharony:1999ti}
 }
 \begin{columns}
-\begin{column}{.4\textwidth}
 \figAdsCft
-\end{column}
-\begin{column}{.6\textwidth}
+\begin{column}{.72\textwidth}
 	\begin{itemize}
 	\item Different \textbf{geometries} in the ``bulk''
-	\begin{equation}
-	\hspace{-2.5em}
-		ds^2 = \ell^2 \bigg( \frac{d\rho^2}{4 \rho^2} + \frac{ \big( du + \rho \, \mathcal {\bar L}(v)\, dv \big) \big( dv + \rho \, \mathcal L(u)\, du \big) }{\rho} \bigg)\ \label{banados}
-	\end{equation}
-	specified by $\mathcal L(u)$, $\bar{\mathcal L}(v)$: arbitrary periodic functions
+	\eqBanados
+	specified by $\mathcal L(u)$, $\bar{\mathcal L}(v)$: periodic functions, maps to different \textbf{states} in the boundary $\mrm{CFT}_2$ with stress energy $\ave{T(u)}_\psi$, $\ave{\bar{T}(v)}_\psi$
 
-	\vspace{.5\baselineskip}
-
-\pause
-	\item ... maps to different \textbf{states} in the boundary $\mrm{CFT}_2$
-	\begin{itemize}
-		\item \textit{state:} excitations of the boundary field theory
-		\item \textit{spectrum} of the Hamiltonian operator, $\hat{H}$
-	\end{itemize}
-%	\item In a \textit{holographic} theory, $,\\
-%	a boundary state can be prepared by a bulk path integral.
-	\end{itemize}
-\end{column}
-\end{columns}
-\end{frame}
-
-\begin{frame}{$\mrm{AdS}_3/\mrm{CFT}_2$ --- the holographic dictionary}{%
-	\textcite{Aharony:1999ti} -- \citetitle{Aharony:1999ti}
-}
-\begin{columns}
-\begin{column}{.4\textwidth}
-\figAdsCft
-\end{column}
-\begin{column}{.6\textwidth}
-	\begin{itemize}
-	\item \textit{Dictionary:} bulk $\leftrightarrow$ boundary quantities
-
+	\item \textit{Dictionary:} bulk $\leftrightarrow$ boundary quantities:\\
 		\begin{itemize}
 		\item spectrum,
-	\item symmetry,
-	\item correlations, ...
+			symmetry,\\
+			partition functions,
+			correlators, ...
+		\end{itemize}
 	\end{itemize}
 
-	\item Partition function:
-	\begin{equation}
-		\mcal{Z}_{\pd B}
-		= \sum_{i \in \textit{states}} \ave{e^{-\beta \hat{H}}}_i
-		= \mcal{Z}_{B\textit{ulk}}
-	\end{equation}
-	weighted sum over the spectrum
-
-	\end{itemize}
 \end{column}
@@
 \begin{columns}
-\begin{column}{.45\textwidth}
 \figAdsCft
-\end{column}
-\begin{column}{.55\textwidth}
+\begin{column}{.72\textwidth}
 	\begin{itemize}
@@
 
-\begin{frame}{\TTbar deformations --- definition}{%
-	\textcite{Zamolodchikov:2004ce},\\
-	revived by \textcite{Smirnov:2016lqw,Cavaglia:2016oda}
+\newcommand{\citeTTbar}{%
+	\textcite{Zamolodchikov:2004ce}, revived by \textcite{Smirnov:2016lqw} and \textcite{Cavaglia:2016oda} \textit{et al}
+}
+
+\begin{frame}{\TTbar deformations --- ``solvable''}{%
+	\citeTTbar
 }
 \begin{itemize}
-\item Path integral formalism:
+
+\item Define ``\,\TTbar\,'' as the flow of action:
 \begin{equation}
-	\mcal{Z}
-	= \sum_{i \in \textit{states}} \ave{e^{-\beta \hat{H}}}_i
-	= \int \DD{\phi(x)} e^{-I[\phi(x)]}
-\label{eq:partition}
+	\partial_{\sidenote{\mu}} I = -{8 \pi} \int d^2x \, T\bar T =  -{\pi} \int d^2x\,\big( T^{ij}T_{ij}- (T^i_i)^2 \big)
+	\label{TTbardef}
 \end{equation}
-$I[\phi(x)]$: action (energy) functional of the fields $\phi(x)$\\
-\phantom{$I[\phi(x)]$: }captures the dynamics of the theory
+For $\mrm{CFT}_2$,\ $T\bar{T} = T_{xx} T_{\bar{x}\bar{x}}$,\ where $x, \bar{x} = \varphi' \mp it'$.
+
+\item The stress tensor $T_{ij}(\sidenote{\mu})$ on the right hand side flows with the deformation parametrized by $\sidenote{\mu}$.
 
@@
 
-\item Stress tensor $T_{ij}[\phi(x)]$: energy momentum, local and covariant version of $\hat{H}$
-\begin{equation}
-%	\label{TTbardefintro}
-	\partial_\mu I = -{8 \pi} \int d^2x \, T\bar T =  -{\pi} \int d^2x\,\big( T^{ij}T_{ij}- (T^i_i)^2 \big)
-\end{equation}
-For $\mrm{CFT}_2$,\ $T\bar{T} = T_{xx} T_{\bar{x}\bar{x}}$,\ where $x, \bar{x} = \varphi' \mp it'$.
-{\footnotesize We've set the length scale $\ell = 1$.}
+\item This is thus a \textit{differential equation} for a flow, starting from some generic QFT specified by $I(\mu = 0)$.
+In this work we shall start from $\mrm{CFT}_2$, but note that \TTbar is \textit{irrelevant}: conformal symmetry will be broken.
 
@@
 \begin{frame}{\TTbar deformations --- ``solvable''}{%
-	\textcite{Zamolodchikov:2004ce},\\
-	revived by \textcite{Smirnov:2016lqw,Cavaglia:2016oda}
+	\citeTTbar
 }
-\vspace{-.3\baselineskip}
 \begin{itemize}
-\item Define of \TTbar as the flow of action:
+
+\item \textbf{``Solvable'':} the deformed spectrum of $\hat{H}(\mu)$ and $\hat{J}(\mu)$ on a cylinder of radius $R$ can be solved, 
+and it's a simple function\\
+ of the undeformed $E(0)$, $J(0)$:
 \begin{equation}
-	\label{TTbardefintro}
-	\partial_\mu I = -{8 \pi} \int d^2x \, T\bar T =  -{\pi} \int d^2x\,\big( T^{ij}T_{ij}- (T^i_i)^2 \big)
-\end{equation}
-This is a \textit{flow equation} from some generic QFT specified by $I(\mu = 0)$.
-
-\pause
-
-\item \textbf{``Solvable'':} the deformed spectrum of $\hat{H}(\mu)$ and $\hat{J}(\mu)$ on a cylinder of radius $R$\\
-can be solved, and it's a simple function of the undeformed $E(0)$, $J(0)$:
-\begin{equation}
+\hspace{-2em}
 	E(\mu) = - \frac{R }{ 2\mu } \bigg(1-\sqrt{1 + \frac{4\mu}{R} E(0) + \frac{4\mu^2}{R^4} J(0)^2 }
@@
 
+\item \textbf{Variants:} suppose the theory has some ``components'' labeled by $w$,
+
+\begin{itemize}
+\item double-trace $\TTbar = (\sum_w T_w) (\sum_w \bar{T}_w)$ (this work)
+\item single-trace $\TTbar' = \sum_w (T_w \bar{T}_w)$ (e.g.~\textit{\citeauthor{Cui:2023jrb}},~23)
 \end{itemize}
+
+\end{itemize}
+
+\vspace{.5\baselineskip}
 \end{frame}
@@
 \begin{equation}
-	\partial_\mu I = -{8 \pi} \int d^2x\,T\bar T
-	\label{TTbardef}
-\end{equation}
-\begin{equation}
 	E(\mu) = - \frac{R }{ 2\mu } \bigg(1-\sqrt{1 + \frac{4\mu}{R} E(0) + \frac{4\mu^2}{R^4} J(0)^2 }
@@
 \begin{itemize}
-\item It seems that the \TTbar deformation is well-defined non-perturbatively for generic $\mrm{QFT}_2$,\\
-yet mysterious: computations of many quantities are difficult\\
+\item It seems that the \TTbar deformation is well-defined non-perturbatively for generic $\mrm{QFT}_2$,
+yet it's still mysterious and difficult\\
 \begin{itemize}
@@
 
-\newcommand{\figCutoffAds}{
+\newcommand{\figCutoffAds}[1][.3]{
+\begin{column}{#1\textwidth}
 \begin{figure}[!h]
-	\hfill\includegraphics[width=.8\linewidth]{img/cutoff-ads.jpg}
+	\hfill\includegraphics[width=\linewidth]{img/cutoff-ads.jpg}
 
-	\centering
-	\vspace{-.3\baselineskip}
-	\caption{Cutoff $\mrm{AdS}_3/\TTbar$ duality}
-
-	\vspace{-.3\baselineskip}
-	\scriptsize\ Image courtesy: \textcite{AldegundePWSep22}
+	\vspace{-.5\baselineskip}
+	\flushleft
+	\ \scriptsize\textcite{AldegundePWSep22}
 \end{figure}
+\end{column}
+\hspace{-2em}
 }
@@
 \begin{columns}
-\begin{column}{.4\textwidth}
 \figCutoffAds
-\end{column}
-\begin{column}{.6\textwidth}
+\hspace{-2em}
+\begin{column}{.75\textwidth}
 	\begin{itemize}
@@
 \begin{columns}
-\begin{column}{.35\textwidth}
 \figCutoffAds
-\end{column}
-\begin{column}{.65\textwidth}
+\hspace{-1em}
+\begin{column}{.7\textwidth}
 	\begin{itemize}
@@
 	\item Passed many non-trivial tests
-	\item Generalized to ``mixed boundary conditions''\\
+	\item Related to ``mixed boundary conditions''\\
 	by \textcite{Guica:2019nzm}
@@
 \begin{columns}
-\begin{column}{.35\textwidth}
 \figCutoffAds
-\end{column}
-\begin{column}{.65\textwidth}
+\hspace{-1em}
+\begin{column}{.75\textwidth}
 \vspace{-.5\baselineskip}
@@
 \sidenote{\arxiv{2303.04836}}
-\ submitted to \textit{JHEP}
+%\ submitted to \textit{JHEP}
 

### 2023-06-21 alpha/GlueonAdS/glueon-beamer.tex
Update glueon slides

@@
 %	,draft
-	,handout
+%	,handout
 	,noamsthm
@@
 %		\\\large\ccbyncsajp
-	}%
+	}\\[2ex]
+	\today\ @ BIMSA
 }
@@
 	\node at ([
-		yshift=-4.8\baselineskip,
-		xshift=.26\linewidth
+		yshift=-4.6\baselineskip,
+		xshift=.25\linewidth
 	] current page.center) {
@@
 
-\section{\textbf{Warmup:} $\mrm{AdS}_{d+1}$/$\mrm{CFT}_{d}$ at $d = 2$}
+\section{\textbf{Warmup:} Pure Einstein gravity in $\mrm{AdS}_3$ / $\mrm{CFT}_2$}
+
+\newcommand{\citeMaldacena}{%
+	\textcite{Maldacena:1997re} --- \scriptsize\citetitle{Maldacena:1997re}
+}
 
@@
 \end{align*}
-}
-
-\newcommand{\citeMaldacena}{%
-	\textcite{Maldacena:1997re} --- \scriptsize\citetitle{Maldacena:1997re}
 }
@@
 
-\begin{frame}{$\mrm{AdS}_3/\mrm{CFT}_2$ --- gravity trapped in a \textit{Poincar\'e cylinder}}{%
+\begin{frame}{$\mrm{AdS}_3/\mrm{CFT}_2$ --- gravity trapped in a cylinder}{%
 	\textcite{Aharony:1999ti}
@@
 
-\section{\textbf{Review:} \TTbar deformation and cutoff AdS holography} \label{se:cutoffholography}
+\section{\textbf{Review:} \TTbar deformation and cutoff AdS} \label{se:cutoffholography}
 
@@
 
-\begin{frame}{\TTbar deformations --- ``solvable''}{%
+\begin{frame}{\TTbar deformations --- definition}{%
 	\citeTTbar
@@
 
-\begin{frame}{\TTbar deformations --- ``solvable''}{%
+\begin{frame}{``Solvable'' deformations on the field theory side}{%
 	\citeTTbar
@@
 \item \textbf{Variants:} suppose the theory has some ``components'' labeled by $w$,
+
+\pause
 
@@
 	\end{equation}
+	\textit{Roughly $\mu \sim 1/r^2$}
 
@@
 \figCutoffAds
-\hspace{-1em}
+\hspace{-1.2em}
 \begin{column}{.75\textwidth}
@@
 	\begin{itemize}
-		\item Dual to some ``solvable'' non-conformal theory
+		\item Dual to some ``solvable'' no-longer-conformal ft
 		\item A step towards quantum gravity in reality!
@@
 	\textit{What is the other side of the duality?}
+		\begin{itemize}
+		\item For comparison, the proposal of \textcite{Guica:2019nzm} admits both signs of $\mu$
+		\end{itemize}
 	\end{itemize}
@@
 	\begin{itemize}
-	\item $\mrm{AdS}_3$ metric has only simple poles:
+	\item $\mrm{AdS}_3$ metric has only simple poles with the $\rho$ coordinate:
 	\begin{equation}
@@
 	\end{equation}
-	thus it admits well-defined analytic continuation from $\rho > 0$ to $\rho \in \mbb{R}$.
+	thus it admits well-defined analytic continuation \\
+	from $\rho > 0$ to $\rho \in \mbb{R}$.
 	\item Continuation of the dictionary:
@@
 
-\newcommand{\figGlueon}{
+\newcommand{\figGlueon}[1][.37]{
+\begin{column}{#1\textwidth}
 \begin{figure}[!h]
 	\centering
-	\includegraphics[width=.8\linewidth]{img/diagram.pdf}
-	\vspace{-.3\baselineskip}
+	\includegraphics[width=\linewidth]{img/diagram.pdf}
+	\vspace{-1.5\baselineskip}
 	\caption{Glue-on $\mrm{AdS}_3$}
@@
 	\vspace{-.3\baselineskip}
-	\scriptsize\ Top-down view of the ``Poincare cylinder''
+	\scriptsize\ Top-down view of the Poincar\'e disk
 \end{figure}
+\end{column}
 }
@@
 \begin{columns}
-\begin{column}{.4\textwidth}
 \figGlueon
-\end{column}
-\begin{column}{.6\textwidth}
+\begin{column}{.64\textwidth}
 \vspace{-\baselineskip}
@@
 \begin{itemize}
-\item Firstly, matching energy momentum \& the flow equations:
+\item Firstly, matching energy momentum (Brown-York) \& the flow equations:
 	\begin{equation}
@@
 	\begin{itemize}
-	\item $\gamma_{ij}$ is always positive-definite, while $h_{ij}$ becomes negative-definite for the glue-on region.\\
-		This discrepancy is the origin of the absolute values.
+	\item $\gamma_{ij}$ is always positive-definite, while $h_{ij}$ becomes negative-definite for the glue-on region.
+	This discrepancy is the origin of the $\abs{\zeta_c}$.
 	\end{itemize}
@@
 
-\item \TTbar flow is recast geometrically as the $i,j$ components of the Einstein equations. \\
+\item \TTbar flow is recast geometrically as the $i,j$ components of the Einstein equations. 
 Note that the geometry can be decomposed such that:
@@
 \pause
-\item Treatment for the singularity at $\zeta\to 0^\pm$: introduce $\mathcal N_{\zeta={\pm\epsilon}}$ and glue them together\\
+\item Treatment for the singularity at $\zeta\to 0^\pm$: introduce $\mathcal N_{\zeta={\pm\epsilon}}$ and glue them together (``glue-on'');
 	exclude the $-\epsilon < \zeta < \epsilon$ region until finally sending $\epsilon \to 0$. 
@@
 	\ \equiv\ %
-	\textrm{\TTbar deformed $\mrm{CFT}_{d}$ at $\mcal{N}_{\zeta_c}$}\qquad
+	\textrm{\TTbar deformed $\mrm{CFT}_{d}$ at $\mcal{N}_{\zeta_c}$}\ \,
 }}
@@
 \centering
-\includegraphics[width=.8\linewidth]{img/diagram.pdf}
+\includegraphics[width=.9\linewidth]{img/diagram.pdf}
 \end{minipage}
-\vspace{-.8\baselineskip}
-\begin{equation}
+\vspace{-.1\baselineskip}
+\begin{equation*}
 \stateGlueon
-\end{equation}
+\end{equation*}
 \end{frame}
@@
 \begin{columns}
-\begin{column}{.35\textwidth}
-\figGlueon
-\end{column}
-\begin{column}{.65\textwidth}
+\figGlueon[.3]
+\begin{column}{.75\textwidth}
 \begin{itemize}
@@
 \pause
-\item Demanding the extended geometry to be non-singular\\
+\item Demanding the extended geometry to be non-singular
 	re-produces bounds on the \TTbar deformed theory, e.g.
@@
 \begin{columns}
-\begin{column}{.35\textwidth}
-\figGlueon
-\end{column}
-\begin{column}{.65\textwidth}
+\figGlueon[.3]
+\begin{column}{.75\textwidth}
 \vspace{-.3\baselineskip}
@@
 
-\item This reproduces $E(\mu)$, $J(\mu)$ with $\mu \in\mbb{R}$ in \eqref{ttbarspectrum}.
+\item This reproduces $E(\mu)$, $J(\mu)$ with $\mu \in\mbb{R}$ in \eqref{ttbarspectrum}
 
@@
 
-\begin{frame}{\TTbar partition functions from bulk on-shell actions}{%
+\begin{frame}{\TTbar spectrum from bulk covariant charges}{%
 	\textcite{Kraus:2021cwf,Apolo:2023vnm}
@@
 \begin{columns}
-\begin{column}{.35\textwidth}
-\figGlueon
-\end{column}
-\begin{column}{.65\textwidth}
+%\figGlueon[.3]
+\begin{column}{\textwidth}
 \vspace{-.3\baselineskip}
 \begin{itemize}
-\item Bulk: weakly coupled gravity, the partition function \eqref{eq:partition} is approximated by the on-shell gravity action of the dominant saddle (method of steepest descent):
+\item Covariant charges of geometries
+	\begin{align*}
+		\delta E(\mu) &\equiv  \ell^{-1} \delta \mathcal Q_{\pd_{t'}}, \\ \delta J(\mu) &\equiv  \delta \mathcal Q_{\pd_{\varphi'}},
+	\end{align*}
+
+\item One needs to choose the appropriate boundary coordinates $(t',\varphi')$, such that
+	\begin{equation}
+		ds^2_c = \ell^2 ( -dt'^2 + d\varphi'^2) , \qquad \varphi' \sim \varphi' + 2\pi.\label{cutoffmetric}
+	\end{equation}
+
+\pause
+
+\item This is realized by the \textit{state-dependent} map of coordinates
+	\begin{align*}
+		dt' &= \sqrt{ \big(1 - \zeta_c (T_u+T_v)^2 \big) \big(1 - \zeta_c (T_u-T_v)^2 \big) } \, dt,  \\
+		 d\varphi' &= d\varphi + \zeta_c \big( T_u^2 - T_v^2 \big)\,dt.
+	\end{align*}
+\end{itemize}
+\end{column}
+\end{columns}
+\end{frame}
+
+\begin{frame}{\TTbar thermodynamics from bulk geometry}{%
+	\textcite{Giveon:2017nie,Apolo:2019zai}
+}
+\begin{columns}
+%\figGlueon[.3]
+\begin{column}{\textwidth}
+\vspace{-.3\baselineskip}
+\begin{itemize}
+
+\item \textit{State-dependent} map of coordinates
+	\begin{align*}
+		dt' &= \sqrt{ \big(1 - \zeta_c (T_u+T_v)^2 \big) \big(1 - \zeta_c (T_u-T_v)^2 \big) } \, dt, \\
+		 d\varphi' &= d\varphi + \zeta_c \big( T_u^2 - T_v^2 \big)\,dt.
+	\end{align*}
+
+\pause
+\item Many consequences: correct charges, signal propagation speed $v'_{\pm} \equiv \pm \frac{d\varphi'}{dt'}$, and thermodynamics when Wick rotated:
+	\begin{equation}
+		T_L(\mu)\,T_R(\mu) \le - \frac{1}{4\pi^2 \ell^2 \zeta_c} = \frac{3}{4\pi^2c\mu} = T_H(\mu)^2,
+	\quad \mu > 0
+	\end{equation}
+	$T_{L,R}$ are temperatures associated with $u',v' = \varphi' \pm t'$.
+
+\item $T_H$ is the \textit{Hagedorn temperature}: exceeding $T_H$ corresponds to a complex entropy
+\end{itemize}
+\end{column}
+\end{columns}
+\end{frame}
+
+\section{\textbf{Check:} \TTbar partition functions from glue-on AdS} \label{se:partitionfunction}
+
+\begin{frame}{\TTbar partition functions from bulk on-shell actions}{%
+	\textcite{Caputa:2020lpa}
+}
+\begin{columns}
+\figGlueon
+\hspace{-1.5em}
+\begin{column}{.7\textwidth}
+\vspace{-.3\baselineskip}
+\begin{itemize}
+\item Bulk: weakly coupled gravity, the partition function is approximated by the on-shell gravity action of the dominant saddle:
 	\begin{equation}
@@
 
+\begin{frame}{Comparison with field theory analysis}{%
+	\textcite{Datta:2018thy,Apolo:2023aho}
+}
+\begin{columns}
+%\figGlueon
+%\hspace{-1.5em}
+\begin{column}{\textwidth}
+\vspace{-.3\baselineskip}
+\begin{itemize}
+\item \textbf{Torus:} Large $c$, \textit{modular invariance} \& sparseness of the ``light'' spectrum \cite{Datta:2018thy,Apolo:2023aho},
+	c.f. \textcite{Hartman:2014oaa}
+	\begin{equation*}
+	\hspace{-1.5em}
+		\log   Z_{T\bar T}(\mu)  \approx \left\{ \begin{aligned}
+		& {-\frac{1}{2}}\,(\beta_L + \beta_R)\, RE_{\text{vac}}(\mu),  &\beta_L \beta_R > 1, \\
+		& {-2 \pi^2 \bigg(\frac{1}{\beta_L} + \frac{1}{\beta_R}\bigg)  RE_{\text{vac}}\bigg(\frac{4\pi^2}{\beta_L \beta_R} \mu \bigg)}, \ \, &\beta_L\beta_R < 1, %\\[2ex]
+		 \end{aligned} \right. %\label{ZTTbar}
+	\end{equation*}
+
+\item \textbf{Sphere:} maximally symmetric, \textcite{Donnelly:2018bef}
+	\begin{equation}
+%		\label{sphere:stresstensor}
+		\langle T_{ij}\rangle =-\frac{1}{4\pi\mu} \bigg(1-\sqrt{1-\frac{c\mu}{3L^2}}\, \bigg)  \gamma_{ij}.
+	\end{equation}
+\end{itemize}
+\end{column}
+\end{columns}
+\end{frame}
+
+\begin{frame}{Sphere partition functions}{%
+	\textcite{Donnelly:2018bef,Li:2020zjb}
+}
+\begin{columns}
+%\figGlueon
+%\hspace{-1.5em}
+\begin{column}{\textwidth}
+\vspace{-.3\baselineskip}
+\begin{itemize}
+
+\item Given the explicit stress tensor $\langle T_{ij}\rangle \propto \gamma_{ij}$, the flow equations:
+	\begin{align*}
+\partial_\mu \log Z_{\TTbar}(\mu)&=8\pi \int d^2x\sqrt{\gamma}\, \langle T\bar{T} \rangle \\
+-L\,\partial_L \log Z_{\TTbar}(\mu)&=\int d^2x\sqrt{\gamma}\,\langle T^i_i \rangle
+	\end{align*}
+
+	\item ... admit the general solution with a $\mu$-\textit{independent} integration $a$:
+	\begin{equation*}
+		\log Z_{\TTbar}(\mu, a) = \frac{c}{3} \log \bigg[\frac{L}{a}   \bigg(1+\sqrt{1-\frac{c \mu }{3  L^2}}\, \bigg) \bigg] - \frac{L^2}{\mu}  \sqrt{1-\frac{c \mu }{3 L^2}} + \frac{L^2}{\mu} %\label{Zsol}
+	\end{equation*}
+
+	\item \textcite{Donnelly:2018bef} is recovered with $a = \sqrt{c|\mu|/3}$ but one can also take $a = \epsilon$, thus decoupling the energy (RG) scale $\epsilon$ with the deformation $\mu$. 
+\end{itemize}
+\end{column}
+\end{columns}
+\end{frame}
+
+\begin{frame}{Gravitational actions: with counterterms}{%
+	\textcite{Donnelly:2018bef,Li:2020zjb}
+}
+\begin{columns}
+%\figGlueon
+%\hspace{-1.5em}
+\begin{column}{1.1\textwidth}
+\vspace{-.3\baselineskip}
+\begin{itemize}
+
+\item Gravitational actions, with counterterms:
+	\begin{align*}
+		I_{\mcal{M}}(\zeta_1, \zeta_2) & \coloneqq - \frac{1}{16\pi G} \int_{\zeta_1}^{\zeta_2} d\zeta \int d^2 x \sqrt{g} \, (R + 2 \ell^{-2}),  %\label{bulkaction} \\
+	\\
+		I_{\mathcal N_{\zeta}} & \coloneqq  - \frac{1}{8\pi G} \int_{\mathcal N_{\zeta}} d^2x \sqrt{h}\,h^{ij} K_{ij} 
+	\\& \qquad + \frac{\sigma_\zeta}{8\pi G} \int_{\mathcal N_{\zeta}} d^2x \sqrt{h} \, \bigg(\ell^{-1} - \frac{\ell  \mathcal{R}[h]}{4} \log |\zeta| \bigg), %\label{boundaryaction}
+	\end{align*}
+	... consistent with the Brown-York stress tensor $T_{ij}$, \\
+	fully renormalized at $\zeta \to 0^\pm$.
+
+	\item The lack of diff invariance of the $\log |\zeta|$ counterterm is known to be a reflection of the Weyl anomaly: \textsl{\citeauthor{Henningson:1998gx,deHaro:2000vlm,Papadimitriou:2010as}}.
+
+\end{itemize}
+\end{column}
+\end{columns}
+\end{frame}
+
+\begin{frame}{Gravitational actions: with counterterms}{%
+	\textcite{Caputa:2020lpa,Li:2020zjb}
+}
+\begin{columns}
+%\figGlueon
+%\hspace{-1.5em}
+\begin{column}{1.1\textwidth}
+\vspace{-.3\baselineskip}
+\begin{itemize}
+
+\item The $\log$ counterterm makes a crucial contribution to the on-shell action:
+	\begin{align*}
+		I_{\mcal{M}}(\zeta_1, \zeta_2) & \coloneqq - \frac{1}{16\pi G} \int_{\zeta_1}^{\zeta_2} d\zeta \int d^2 x \sqrt{g} \, (R + 2 \ell^{-2}),  %\label{bulkaction} \\
+	\\
+		I_{\mathcal N_{\zeta}} & \coloneqq  - \frac{1}{8\pi G} \int_{\mathcal N_{\zeta}} d^2x \sqrt{h}\,h^{ij} K_{ij} 
+	\\& \qquad + \frac{\sigma_\zeta}{8\pi G} \int_{\mathcal N_{\zeta}} d^2x \sqrt{h} \, \bigg(\ell^{-1} - \frac{\ell  \mathcal{R}[h]}{4} \log |\zeta| \bigg), %\label{boundaryaction}
+	\end{align*}
+	It guarantees that the partition function is compatible with the $T\bar T$ differential equation --- not the case for \textsl{\citeauthor{Donnelly:2018bef}}.
+
+	\item In general the space of deformed theories are parametrized by $(\mu,a)$, where $a$ is the length scale (inverse energy scale).
+In many contexts they are naturally related: $a = \sqrt{c|\mu|/3}$, but $a$ can be tuned by RG.
+
+\end{itemize}
+\end{column}
+\end{columns}
+\end{frame}
+
 \section{Summary \& future directions}
@@
 }
-\vspace{-1.2\baselineskip}
-\begin{equation}
+\vspace{-2\baselineskip}
+\begin{equation*}
 \stateGlueon
-\end{equation}
+\end{equation*}
+\vspace{-1.3\baselineskip}
+\begin{columns}
+\begin{column}{.37\textwidth}
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=\linewidth]{img/RT-AdS.pdf}
+	\vspace{-1.5\baselineskip}
+	\caption{RT for Glue-on $\mrm{AdS}_3$}
+
 	\vspace{-.3\baselineskip}
-\begin{columns}
-\begin{column}{.3\textwidth}
-\centering
-\includegraphics[width=\linewidth]{img/diagram.pdf}
+	\scriptsize\, Top-down view of the Poincar\'e disk
+\end{figure}
 \end{column}
 \hspace{-1em}
-\begin{column}{.7\textwidth}
+\begin{column}{.71\textwidth}
 \begin{itemize}
-\item Holographic proposal for $T\bar T$-deformed CFTs with $\mu \in \mbb{R}$
+\item Holographic proposal for $T\bar T$-deformed CFTs\\
+with $\mu \in \mbb{R}$.
 
@@
 \item We hope to understand the entanglement structure of \TTbar deformed theories from bulk geometry. 
+\end{itemize}
+\end{column}
+\end{columns}
+\end{frame}
+
+\begin{frame}{Glue-on $\mrm{AdS}_3$ / \TTbar deformed $\mrm{CFT}_2$}{%
+	\textcite{Apolo:2023vnm} -- \citetitle{Apolo:2023vnm}
+}
+\vspace{-2\baselineskip}
+\begin{equation*}
+\stateGlueon
+\end{equation*}
+\vspace{-1.3\baselineskip}
+\begin{columns}
+\begin{column}{.37\textwidth}
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=\linewidth]{img/RT-AdS.pdf}
+	\vspace{-1.5\baselineskip}
+	\caption{RT for Glue-on $\mrm{AdS}_3$}
+
+	\vspace{-.3\baselineskip}
+	\scriptsize\, Top-down view of the Poincar\'e disk
+\end{figure}
+\end{column}
+\hspace{-1em}
+\begin{column}{.71\textwidth}
+\begin{itemize}
+
+\item We hope to understand the entanglement structure of \TTbar deformed theories from bulk geometry. \pause
+	\begin{itemize}
+	\item \textcite{Donnelly:2018bef,Lewkowycz:2019xse}
+	\item \textcite{He:2023xnb,He:2023wko,Tian:2023fgf,Hou:2023ytl}
+	\end{itemize}
 \end{itemize}

### 2023-06-22 alpha/GlueonAdS/glueon-slides.tex
Experiment with beamer alternatives
Add bare minimal version of slides

--- 2023-06-21 alpha/GlueonAdS/glueon-beamer.tex
@@
 
-\documentclass[
-	10pt
-%	,draft
-%	,handout
-	,noamsthm
-]{beamer}
+\documentclass[10pt]{article}
 
-\input{preamble.tex}
+\input{preamble-slides.tex}
 
 \usepackage{tikz}
+\usepackage{caption}
 %\usepackage{snapshot}
 
+\renewenvironment{frame}[1]%
+	{\section*{#1}}%
+	{\clearpage}
+
+\newcommand{\pause}{}
+
+\newenvironment{columns}%
+	{\par\begin{minipage}{\textwidth}}%
+	{\end{minipage}}
+
+\newenvironment{column}[1]%
+	{\begin{minipage}{#1}}%
+	{\end{minipage}}
+
 \title{Glue-on AdS holography for $T\bar T$-deformed CFTs}
-\subtitle{An extended AdS\,/\,\TTbar duality \textit{(beyond infinity)}}
+%\subtitle{An extended AdS\,/\,\TTbar duality \textit{(beyond infinity)}}
 \author{%
@@
 	\texstringonly{\,}\textkai{赖文昕}%
-	\texstringonly{
-		\textit{\small in collaboration with} \\
-			Luis Apolo,
-			Peng-Xiang Hao \textkai{郝鹏翔}
-			and Wei Song \textkai{宋伟}\\[2ex]
-		\sidenote{\arxiv{2303.04836}}%
-%		\ submitted to \textit{JHEP}
-	}%
-}
-\institute{\small%
-	Yau Mathematical Sciences Center,\\
-	Tsinghua\texstringonly{
-%		\\\large\ccbyncsajp
-	}\\[2ex]
-	\today\ @ BIMSA
 }
@@
 \begin{document}
-{%%% TITLEPAGE
-\setbeamercolor{title in head/foot}{
-		use=palette quaternary
-		,fg=palette quaternary.bg
-	}
-\logo{}
-\begin{frame}
-%	\titlegraphic{\vspace{2\baselineskip}}
-	\titlepage
-	\tikz [remember picture,overlay]
-	\node at ([
-		yshift=-4.6\baselineskip,
-		xshift=.25\linewidth
-	] current page.center) {
-		\begin{minipage}{.5\textwidth}
+
+\setlength{\droptitle}{-3.5\baselineskip}
+\maketitle
+\thispagestyle{empty}
+
+\vspace{-3.5\baselineskip}
+
 \centering
-		\includegraphics[height=.33\textheight]{img/smbc-cantor-cropped.png}
-		\\[.2ex]
-		\footnotesize \url{https://smbc-comics.com/comic/cantor}
-		\hspace{-1.5em}
-		\end{minipage}
-	};
-\end{frame}
-}%%% TITLEPAGE
 
-\begin{frame}{Outline}
-\raggedbottom
+\textit{in collaboration with}
+\\[.8ex]
+	{\large Luis Apolo,
+	Peng-Xiang Hao \textkai{郝鹏翔}
+	and Wei Song \textkai{宋伟}}
+\\[2ex]
+	\sidenote{\arxiv{2303.04836}}
+\\[3ex]
+	\textsf{Yau Mathematical Sciences Center, Tsinghua}
+\\[1ex]
+	{\large\ccbyncsajp}
+\\[2ex]
+	\textsf{\today\ @ BIMSA}
+\\[4ex]
+	\includegraphics[height=.38\textheight]{img/smbc-cantor-cropped.png}
+\\[-.5ex]
+	{\footnotesize\url{https://smbc-comics.com/comic/cantor}}
+
+\clearpage
+\justifying
+
+%\raggedbottom
 \large
 \tableofcontents
-\end{frame}
+\pagebreak
 
@@
 \newcommand{\citeMaldacena}{%
-	\textcite{Maldacena:1997re} --- \scriptsize\citetitle{Maldacena:1997re}
+	\textcite{Maldacena:1997re}
 }
@@
 
-\begin{frame}{AdS/CFT --- holography duality}{%
-	\citeMaldacena%
-}
-\vspace{-2.5\baselineskip}
+\citeMaldacena
 \stateAdsCft
-\vspace{-1.8\baselineskip}
 \begin{figure}[!h]
@@
 
-	\vspace{-.3\baselineskip}
+	\vspace{-.2\baselineskip}
 	\caption{$\mrm{AdS}_3/\mrm{CFT}_2$ cartoon}
 
-	\vspace*{-.8\baselineskip}
 	\scriptsize\ Image courtesy: \textcite{AldegundePWSep22}
@@
 \vspace{-1.3\baselineskip}
-\end{frame}
 
@@
 
-\begin{frame}{AdS/CFT --- a model of quantum gravity}{%
+\section*{AdS/CFT --- a model of quantum gravity}
 \citeMaldacena
-}
-\vspace{-2.4\baselineskip}
 \stateAdsCft
-\vspace{-1.6\baselineskip}
-\pause
 \begin{itemize}
@@
 
-\pause
 \begin{itemize}
@@
 \end{itemize}
-\end{frame}
+
+\pagebreak
 
@@
 \NewDocumentCommand{\figAdsCft}{ O{.28} }{
-\begin{column}{#1\textwidth}
-\begin{figure}[!h]
+\begin{minipage}{#1\textwidth}
 	\centering
@@
 	\scriptsize\textcite{AldegundePWSep22}\ \,
-\end{figure}
-\end{column}
+\end{minipage}
 }
 
-\begin{frame}{$\mrm{AdS}_3/\mrm{CFT}_2$ --- gravity trapped in a cylinder}{%
+\begin{frame}{$\mrm{AdS}_3/\mrm{CFT}_2$ --- gravity trapped in a cylinder}
+
 \textcite{Aharony:1999ti}
-}
+
 \begin{columns}
 \figAdsCft
-\begin{column}{.75\textwidth}
+\begin{column}{.72\textwidth}
 	\begin{itemize}
@@
 \begin{column}{#1\textwidth}
-\begin{figure}[!h]
 	\hfill\includegraphics[width=\linewidth]{img/cutoff-ads.jpg}
@@
 	\ \scriptsize\textcite{AldegundePWSep22}
-\end{figure}
 \end{column}
@@
 \hspace{-1.2em}
-\begin{column}{.75\textwidth}
+\begin{column}{.72\textwidth}
 \vspace{-.5\baselineskip}
@@
 \newcommand{\figGlueon}[1][.37]{
-\begin{column}{#1\textwidth}
-\begin{figure}[!h]
+\begin{minipage}{#1\textwidth}
 	\centering
@@
 	\vspace{-1.5\baselineskip}
+	\captionsetup{type=figure}
 	\caption{Glue-on $\mrm{AdS}_3$}
@@
 	\scriptsize\ Top-down view of the Poincar\'e disk
-\end{figure}
-\end{column}
+\end{minipage}
 }
@@
 \figGlueon
-\begin{column}{.64\textwidth}
-\vspace{-\baselineskip}
+\begin{column}{.6\textwidth}
 \begin{equation}
@@
 \end{equation}
-\vspace{-.5\baselineskip}
 \begin{itemize}
@@
 }
+
 \centering
-\vspace{-.5\baselineskip}
+
 \begin{minipage}{.5\textwidth}
@@
 \end{minipage}
-\vspace{-.1\baselineskip}
+
 \begin{equation*}
@@
 \figGlueon[.3]
-\begin{column}{.75\textwidth}
+\begin{column}{.7\textwidth}
 \begin{itemize}
@@
 \figGlueon[.3]
-\begin{column}{.75\textwidth}
-\vspace{-.3\baselineskip}
+\begin{column}{.7\textwidth}
 \begin{itemize}
@@
 \hspace{-1.5em}
-\begin{column}{.7\textwidth}
+\begin{column}{.6\textwidth}
 \vspace{-.3\baselineskip}
@@
 }
-\begin{columns}
-%\figGlueon
-%\hspace{-1.5em}
-\begin{column}{\textwidth}
+
 \vspace{-.3\baselineskip}
+
 \begin{itemize}
@@
 \end{itemize}
-\end{column}
-\end{columns}
 \end{frame}
@@
 }
-\begin{columns}
-%\figGlueon
-%\hspace{-1.5em}
-\begin{column}{\textwidth}
-\vspace{-.3\baselineskip}
+
 \begin{itemize}
@@
 }
-\begin{columns}
-%\figGlueon
-%\hspace{-1.5em}
-\begin{column}{1.1\textwidth}
-\vspace{-.3\baselineskip}
+
 \begin{itemize}
@@
 \end{itemize}
-\end{column}
-\end{columns}
+
 \end{frame}
@@
 
-\begin{frame}{Glue-on $\mrm{AdS}_3$ / \TTbar deformed $\mrm{CFT}_2$}{%
+\begin{frame}{Glue-on $\mrm{AdS}_3$ / \TTbar deformed $\mrm{CFT}_2$}
+\noindent
 	\textcite{Apolo:2023vnm} -- \citetitle{Apolo:2023vnm}
-}
-\vspace{-2\baselineskip}
+
 \begin{equation*}
@@
 \end{equation*}
-\vspace{-1.3\baselineskip}
+
 \begin{columns}
 \begin{column}{.37\textwidth}
-\begin{figure}[!h]
 	\centering
@@
 	\vspace{-1.5\baselineskip}
-	\caption{RT for Glue-on $\mrm{AdS}_3$}
+	\captionof{figure}{RT for Glue-on $\mrm{AdS}_3$}
 
@@
 	\scriptsize\, Top-down view of the Poincar\'e disk
-\end{figure}
 \end{column}
 \hspace{-1em}
-\begin{column}{.71\textwidth}
+\begin{column}{.65\textwidth}
 \begin{itemize}
@@
 }
-\vspace{-2\baselineskip}
 \begin{equation*}
@@
 \end{equation*}
-\vspace{-1.3\baselineskip}
 \begin{columns}
-\begin{column}{.37\textwidth}
-\begin{figure}[!h]
+\begin{column}{.3\textwidth}
 	\centering
@@
 	\scriptsize\, Top-down view of the Poincar\'e disk
-\end{figure}
 \end{column}
@@
 
-\begin{frame}
+\begin{frame}{}
 
@@
 
-\begin{frame}[allowframebreaks]{References}
+\begin{frame}{}
 \renewcommand*{\bibfont}{\footnotesize}

### 2023-06-29 alpha/GlueonAdS/glueon-poster.tex
Update poster [wip]

--- 2023-06-22 alpha/GlueonAdS/glueon-slides.tex
@@
 
-\documentclass[10pt]{article}
+\documentclass[11pt]{article}
 
-\input{preamble-slides.tex}
+\input{preamble-poster.tex}
 
@@
 	{\section*{#1}}%
-	{\clearpage}
+	{}
 
-\newcommand{\pause}{}
-
-\newenvironment{columns}%
-	{\par\begin{minipage}{\textwidth}}%
-	{\end{minipage}}
-
-\newenvironment{column}[1]%
-	{\begin{minipage}{#1}}%
-	{\end{minipage}}
-
-\title{Glue-on AdS holography for $T\bar T$-deformed CFTs}
 %\subtitle{An extended AdS\,/\,\TTbar duality \textit{(beyond infinity)}}
-\author{%
-	Wen-Xin Lai
-	\texstringonly{\,}\textkai{赖文昕}%
-}
-\date{}
 
@@
 
+\newcommand{\jokeInfinity}{
+	\includegraphics[height=.2\linewidth]{img/smbc-cantor-cropped.png}
+\\[-.5ex]
+	{\footnotesize\url{https://smbc-comics.com/comic/cantor}}
+}
+
+\setlength{\droptitle}{-3.2\baselineskip}
+\pretitle{\huge\bfseries\noindent}
+\title{Glue-on AdS holography for $T\bar T$-deformed CFTs}
+\posttitle{\ \,}
+
+\preauthor{\large}
+\author{Wen-Xin Lai \textkai{赖文昕}}
+\postauthor{, \textit{\footnotesize with}
+	Luis Apolo,
+	Peng-Xiang Hao \textkai{郝鹏翔}
+	and Wei Song \textkai{宋伟}
+	\ \arxiv{2303.04836}
+	\par\vspace{.5\baselineskip}
+	\hrule\vspace{.3\baselineskip}
+}
+
+\predate{\noindent\sffamily\,%
+	Yau Mathematical Sciences Center YMSC, Tsinghua
+	---
+}
+\date{July 2023}
+\postdate{
+	@ ICBS @ BIMSA
+	\vspace{.5\baselineskip}
+}
+
+\pagestyle{empty}
+
 \begin{document}
 
-\setlength{\droptitle}{-3.5\baselineskip}
 \maketitle
@@
 
-\vspace{-3.5\baselineskip}
+\begin{multicols}{3}
 
-\centering
+\section*{Foundation: pure Einstein in $\mrm{AdS}_3$~/~$\mrm{CFT}_2$}
 
-\textit{in collaboration with}
-\\[.8ex]
-	{\large Luis Apolo,
-	Peng-Xiang Hao \textkai{郝鹏翔}
-	and Wei Song \textkai{宋伟}}
-\\[2ex]
-	\sidenote{\arxiv{2303.04836}}
-\\[3ex]
-	\textsf{Yau Mathematical Sciences Center, Tsinghua}
-\\[1ex]
-	{\large\ccbyncsajp}
-\\[2ex]
-	\textsf{\today\ @ BIMSA}
-\\[4ex]
-	\includegraphics[height=.38\textheight]{img/smbc-cantor-cropped.png}
-\\[-.5ex]
-	{\footnotesize\url{https://smbc-comics.com/comic/cantor}}
-
-\clearpage
-\justifying
-
-%\raggedbottom
-\large
-\tableofcontents
-\pagebreak
-
-\section{\textbf{Warmup:} Pure Einstein gravity in $\mrm{AdS}_3$ / $\mrm{CFT}_2$}
-
-\newcommand{\citeMaldacena}{%
-	\textcite{Maldacena:1997re}
-}
-
-\newcommand{\stateAdsCft}{
+\textcite{Maldacena:1997re}\\
+\textcite{Aharony:1999ti}
 \begin{align*}
@@
 \end{align*}
-}
-
-\citeMaldacena
-\stateAdsCft
-\begin{figure}[!h]
-	\centering
-	\includegraphics[width=.5\linewidth]{img/ads-cft.png}
+\begin{center}
+	\includegraphics[width=.6\linewidth]{img/ads-cft.png}
 
 	\vspace{-.2\baselineskip}
+	\captionsetup{type=figure}
 	\caption{$\mrm{AdS}_3/\mrm{CFT}_2$ cartoon}
 
+	\vspace{.1\baselineskip}
 	\scriptsize\ Image courtesy: \textcite{AldegundePWSep22}
-\end{figure}
-\vspace{-1.3\baselineskip}
+\end{center}
 
-%\begin{equation}
-%	R_{\mu\nu} - \frac{1}{2}\,R g_{\mu\nu}
-%	+ \Lambda g_{\mu\nu}
-%	= 8\pi G_N T_{\mu\nu}^{\textit{matter}},\quad
-%	\Lambda < 0
-%\label{eq:einstein}
-%\end{equation}
-
-\section*{AdS/CFT --- a model of quantum gravity}
-\citeMaldacena
-\stateAdsCft
 \begin{itemize}
 
-\item A model of \textsc{quantum gravity}
-\item ... originating from \textsc{string theory}
-\item ... seemingly \textsc{Universal / ubiquitous}
+\item \textsc{Universal / ubiquitous}
 
@@
 \textit{\small Maldacena, Witten, GKP, ABJM, Gaberdiel, and many many more}
-	\item Our work: pure Einstein gravity in $\mrm{AdS}_3$ / $\mrm{CFT}_2$ $(d=2)$.
 
 \end{itemize}
-\end{itemize}
 
-\pagebreak
-
-%%% LaTeX3e!
-\NewDocumentCommand{\figAdsCft}{ O{.28} }{
-\begin{minipage}{#1\textwidth}
-	\centering
-	\includegraphics[width=\linewidth]{img/ads-cft-cleaner.png}
-
-	\vspace{-.01\baselineskip}
-	\scriptsize\textcite{AldegundePWSep22}\ \,
-\end{minipage}
-}
-
-\begin{frame}{$\mrm{AdS}_3/\mrm{CFT}_2$ --- gravity trapped in a cylinder}
-
-\textcite{Aharony:1999ti}
-
-\begin{columns}
-\figAdsCft
-\begin{column}{.72\textwidth}
-	\begin{itemize}
-	\item $\mrm{AdS}_3$ metric, $\rho \sim z^2 \sim r^{-2}$
+\item Our work: pure Einstein gravity in $\mrm{AdS}_3$ / $\mrm{CFT}_2$ $(d=2)$.\\
+$\mrm{AdS}_3$ metric, $\rho \sim z^2 \sim r^{-2}$
 \begin{equation}
 \hspace{-2em}
-		ds^2 = \ell^2 \frac{d\rho^2}{4 \rho^2} + \pqty{\frac{1}{\rho} g^{(0)}_{ij} + g^{(2)}_{ij} + \rho\thinmspace g^{(4)}_{ij} + \cdots}\, dx^i dx^j \label{fggauge}
+\begin{aligned}
+	ds^2
+	&= \ell^2 \frac{d\rho^2}{4 \rho^2} + \pqty{\frac{1}{\rho} g^{(0)}_{ij} + g^{(2)}_{ij} + \rho\thinmspace g^{(4)}_{ij} + \cdots}\, dx^i dx^j
+\\[.5ex]
+	&= \ell^2 \bigg( \frac{d\rho^2}{4 \rho^2} + \frac{ \big( du + \rho \, \mathcal {\bar L}(v)\, dv \big) \big( dv + \rho \, \mathcal L(u)\, du \big) }{\rho} \bigg)
+	\label{fggauge}
+\end{aligned}
 \end{equation}
@@
 \vspace{-.5\baselineskip}
-	boundary at $\rho \to 0$, $x^{i} \sim \varphi, t$, $i = 1,2$
+boundary at $\rho \to 0$, $x^{i} \sim \varphi, t$, indices $i,j = 1,2$
 
-\pause
 \item Surprisingly the expansion simply terminates at~$\rho\thinmspace g^{(4)}_{ij}$ for pure Einstein gravity! Moreover,
@@
 \end{equation}
-	\textcite{Fefferman:2007rka,Banados:1998gg}
+\textcite{Fefferman:2007rka}\\
+\textcite{Banados:1992wn}\\
+\textcite{Banados:1998gg}
 \end{itemize}
-\end{column}
-\end{columns}
-\end{frame}
 
@@
 	\hspace{-2em}
-		ds^2 = \ell^2 \bigg( \frac{d\rho^2}{4 \rho^2} + \frac{ \big( du + \rho \, \mathcal {\bar L}(v)\, dv \big) \big( dv + \rho \, \mathcal L(u)\, du \big) }{\rho} \bigg)\ \,
+		ds^2 \ \,
 	\end{equation*}
@@
 
-\begin{frame}{$\mrm{AdS}_3/\mrm{CFT}_2$ --- simple realization of holography}{%
-	\textcite{Banados:1992wn}
-}
-\begin{columns}
-\figAdsCft
-\begin{column}{.72\textwidth}
 \begin{itemize}
-	\item $\mrm{AdS}_3$ metric for $\rho > 0$, \\
-	\textcite{Banados:1998gg}
-	\eqBanados
-	$g^{(2)} \leadsto \mathcal L(u)$, $\bar{\mathcal L}(v)$: arbitrary periodic functions,\\
+\item $g^{(2)} \leadsto \mathcal L(u)$, $\bar{\mathcal L}(v)$: arbitrary periodic functions,\\
 where $u,v = \varphi \mp it$, $du\,dv = d\varphi^2 + dt^2$
@@
 
-\pause
 \item A consequence of Einstein equations \\
@@
 \end{itemize}
-\end{column}
-\end{columns}
-\end{frame}
 
-\begin{frame}{$\mrm{AdS}_3/\mrm{CFT}_2$ --- simple realization of holography}{%
-	\textcite{Aharony:1999ti}
-}
-\begin{columns}
-\figAdsCft
-\begin{column}{.72\textwidth}
 \begin{itemize}
 \item Different \textbf{geometries} in the ``bulk''
-	\eqBanados
+
 specified by $\mathcal L(u)$, $\bar{\mathcal L}(v)$: periodic functions, maps to different \textbf{states} in the boundary $\mrm{CFT}_2$ with stress energy $\ave{T(u)}_\psi$, $\ave{\bar{T}(v)}_\psi$
 
-	\item \textit{Dictionary:} bulk $\leftrightarrow$ boundary quantities:\\
+\item \textit{Dictionary:} bulk $\leftrightarrow$ boundary quantities:
 	\begin{itemize}
@@
 
-\end{column}
-\end{columns}
-\end{frame}
-
-\section{\textbf{Review:} \TTbar deformation and cutoff AdS} \label{se:cutoffholography}
-
 \begin{frame}{\TTbar deformations --- motivations}{%
@@
 }
-\begin{columns}
-\figAdsCft
-\begin{column}{.72\textwidth}
 	\begin{itemize}
@@
 	\end{itemize}
-\end{column}
-\end{columns}
 \end{frame}
@@
 \item The stress tensor $T_{ij}(\sidenote{\mu})$ on the right hand side flows with the deformation parametrized by $\sidenote{\mu}$.
-
-\pause
 
@@
 
-\pause
-
 \begin{itemize}
@@
 }
-\vspace{-1.\baselineskip}
+\vspace{-.1\baselineskip}
 \begin{equation}
@@
 
-\pause
 \item What if we start from a $\mrm{CFT}_2$, that enjoys a holographic dual to $\mrm{AdS}_3$...
@@
 
-\newcommand{\figCutoffAds}[1][.3]{
-\begin{column}{#1\textwidth}
-	\hfill\includegraphics[width=\linewidth]{img/cutoff-ads.jpg}
+\newcommand{\figCutoffAds}[1][.5]{
+\begin{center}
+	\hspace{.15\linewidth}
+	\includegraphics[width=#1\linewidth]{img/cutoff-ads.jpg}
 
 	\vspace{-.5\baselineskip}
-	\flushleft
 	\ \scriptsize\textcite{AldegundePWSep22}
-\end{column}
-\hspace{-2em}
+\end{center}
 }
@@
 }
-\begin{columns}
+
 \figCutoffAds
-\hspace{-2em}
-\begin{column}{.75\textwidth}
+
 \begin{itemize}
-	\item Question: what is the AdS dual of \TTbar deformation?\\
+\item Question: what is the AdS dual of \TTbar deformation?
 
@@
 
-\pause
 \item look at properties of \TTbar:\\
@@
 
-	\pause
 \item Answer: AdS gravity within a finite Dirichlet wall
@@
 \end{itemize}
-\end{column}
-\end{columns}
+
 \end{frame}
 
-\begin{frame}{Cutoff $\mrm{AdS}_3$ --- the dictionary}{%
-	\textcite{McGough:2016lol} --
-	\citetitle{McGough:2016lol}
-}
-\begin{columns}
-\figCutoffAds
-\hspace{-1em}
-\begin{column}{.7\textwidth}
+\begin{frame}{Cutoff $\mrm{AdS}_3$ --- the dictionary}{}
+
 	\begin{itemize}
@@
 
-\pause
-
-	\item Passed many non-trivial tests
-	\item Related to ``mixed boundary conditions''\\
+	\item Passed many non-trivial tests,\\
+	related to ``mixed boundary conditions''\\
 	by \textcite{Guica:2019nzm}
@@
 	\end{itemize}
-\end{column}
-\end{columns}
+
 \end{frame}
@@
 }
-\begin{columns}
-\figCutoffAds
-\hspace{-1.2em}
-\begin{column}{.72\textwidth}
-\vspace{-.5\baselineskip}
+
 \begin{itemize}
@@
 
-\pause
 \item \textbf{Caveat:} the duality only admits $\zeta_c > 0$ so $\mu < 0$
@@
 
-\newcommand{\figGlueon}[1][.37]{
-\begin{minipage}{#1\textwidth}
+\newcommand{\figGlueon}[1][1]{
+\begin{minipage}{#1\linewidth}
 	\centering
-	\includegraphics[width=\linewidth]{img/diagram.pdf}
+	\includegraphics[width=.5\linewidth]{img/diagram.pdf}
 	\vspace{-1.5\baselineskip}
@@
 }
-\begin{columns}
+
 \figGlueon
-\begin{column}{.6\textwidth}
+
 \begin{equation}
@@
 
-	\pause
-
 	\begin{itemize}
@@
 	\end{itemize}
-
-	\pause
 
@@
 
-\pause
 \item Treatment for the singularity at $\zeta\to 0^\pm$: introduce $\mathcal N_{\zeta={\pm\epsilon}}$ and glue them together (``glue-on'');
@@
 	\ \equiv\ %
-	\textrm{\TTbar deformed $\mrm{CFT}_{d}$ at $\mcal{N}_{\zeta_c}$}\ \,
+	\textrm{\TTbar deformed $\mrm{CFT}_{d}$ at $\mcal{N}_{\zeta_c}$}
 }}
 
-\begin{frame}{Glue-on $\mrm{AdS}_3$ / \TTbar --- the proposal}{%
-	\textcite{Apolo:2023vnm} -- \citetitle{Apolo:2023vnm}
-}
+\begin{frame}{Glue-on $\mrm{AdS}_3$ / \TTbar --- the proposal}{}
 
-\centering
-
-\begin{minipage}{.5\textwidth}
-\centering
-\includegraphics[width=.9\linewidth]{img/diagram.pdf}
-\end{minipage}
-
+\begin{center}
+\includegraphics[width=.6\linewidth]{img/diagram.pdf}
 \begin{equation*}
@@
 \end{equation*}
+\end{center}
+
 \end{frame}
@@
 }
-\begin{columns}
-\figGlueon[.3]
-\begin{column}{.7\textwidth}
+
 \begin{itemize}
@@
 
-\pause
 \item Demanding the extended geometry to be non-singular
@@
 
-\pause
 \item We are careful to match the bulk \& boundary symmetries at $\mcal{N}_{\zeta_c}$
@@
 }
-\begin{columns}
-%\figGlueon[.3]
-\begin{column}{\textwidth}
-\vspace{-.3\baselineskip}
+
 \begin{itemize}
@@
 
-\pause
-
 \item This is realized by the \textit{state-dependent} map of coordinates
@@
 }
-\begin{columns}
-%\figGlueon[.3]
-\begin{column}{\textwidth}
-\vspace{-.3\baselineskip}
+
 \begin{itemize}
 
-\item \textit{State-dependent} map of coordinates
-	\begin{align*}
-		dt' &= \sqrt{ \big(1 - \zeta_c (T_u+T_v)^2 \big) \big(1 - \zeta_c (T_u-T_v)^2 \big) } \, dt, \\
-		 d\varphi' &= d\varphi + \zeta_c \big( T_u^2 - T_v^2 \big)\,dt.
-	\end{align*}
-
-\pause
 \item Many consequences: correct charges, signal propagation speed $v'_{\pm} \equiv \pm \frac{d\varphi'}{dt'}$, and thermodynamics when Wick rotated:
@@
 }
-\begin{columns}
-\figGlueon
-\hspace{-1.5em}
-\begin{column}{.6\textwidth}
-\vspace{-.3\baselineskip}
+
 \begin{itemize}
@@
 
-\pause
 \item $I(\zeta_c)$ is roughly the volume of the geometry, which diverges at $\zeta \to 0^\pm$. We apply a natural extension of \textit{holographic renormalization} to remove the divergence.
 
-\pause
 \item $I = -\log \mcal{Z}$ satisfies the \TTbar flow \eqref{TTbardef}.\\
@@
 
-\begin{frame}{Glue-on $\mrm{AdS}_3$ / \TTbar deformed $\mrm{CFT}_2$}
+\section*{Glue-on $\mrm{AdS}_3$ / \TTbar deformed $\mrm{CFT}_2$}
 \noindent
@@
 
-\begin{columns}
-\begin{column}{.37\textwidth}
-	\centering
-	\includegraphics[width=\linewidth]{img/RT-AdS.pdf}
-	\vspace{-1.5\baselineskip}
+\begin{center}
+	\includegraphics[width=.5\linewidth]{img/RT-AdS.pdf}
+	\vspace{-1\baselineskip}
 	\captionof{figure}{RT for Glue-on $\mrm{AdS}_3$}
 
-	\vspace{-.3\baselineskip}
+	\vspace{.1\baselineskip}
 	\scriptsize\, Top-down view of the Poincar\'e disk
-\end{column}
-\hspace{-1em}
-\begin{column}{.65\textwidth}
+\end{center}
+
 \begin{itemize}
@@
 
-\pause
 \item We hope to understand the entanglement structure of \TTbar deformed theories from bulk geometry. 
 \end{itemize}
-\end{column}
-\end{columns}
-\end{frame}
 
@@
 \end{equation*}
-\begin{columns}
-\begin{column}{.3\textwidth}
-	\centering
-	\includegraphics[width=\linewidth]{img/RT-AdS.pdf}
-	\vspace{-1.5\baselineskip}
-	\captionof{figure}{RT for Glue-on $\mrm{AdS}_3$}
 
-	\vspace{-.3\baselineskip}
-	\scriptsize\, Top-down view of the Poincar\'e disk
-\end{column}
-\hspace{-1em}
-\begin{column}{.71\textwidth}
 \begin{itemize}
 
-\item We hope to understand the entanglement structure of \TTbar deformed theories from bulk geometry. \pause
+\item We hope to understand the entanglement structure of \TTbar deformed theories from bulk geometry. 
 	\begin{itemize}
@@
 \end{itemize}
-\end{column}
-\end{columns}
-\end{frame}
-
-\begin{frame}{}
-
-\centering
-
-\huge
-\sidenote{Thank you!}
-\bigskip
-
-\large
-froms Wen-Xin Lai\ \textkai{赖文昕}
-
-\textit{\normalsize in collaboration with}
-
-	Luis Apolo,
-	Peng-Xiang Hao \textkai{郝鹏翔}
-	and Wei Song \textkai{宋伟}\\[2ex]
-\sidenote{\arxiv{2303.04836}}
-%\ submitted to \textit{JHEP}
 
@@
 
-\begin{frame}{}
 \renewcommand*{\bibfont}{\footnotesize}
-\printbibliography %%% should not specify heading etc
-\end{frame}
+\printbibliography %%% should not specify heading
+
+\end{multicols}
 

### 2023-08-24 alpha/GlueonAdS/glueon-poster-alt1.tex
Revamp glueon poster

--- 2023-06-29 alpha/GlueonAdS/glueon-poster.tex
@@
 
-\documentclass[11pt]{article}
+\documentclass[10pt]{article}
 
@@
 	{}
+
+\newcommand{\citations}[1]{{\footnotesize#1\par}}
+\newcommand{\reality}{reality\textsuperscript{TM}}
 
@@
 
-\preauthor{\large}
+\preauthor{\par\large\noindent}
 \author{Wen-Xin Lai \textkai{赖文昕}}
-\postauthor{, \textit{\footnotesize with}
+\postauthor{, \textit{\normalsize with}
 	Luis Apolo,
@@
 	and Wei Song \textkai{宋伟}
-	\ \arxiv{2303.04836}
+	\hfill\arxiv{2303.04836}
 	\par\vspace{.5\baselineskip}
@@
 
-\section*{Foundation: pure Einstein in $\mrm{AdS}_3$~/~$\mrm{CFT}_2$}
+\subsection*{Foundations:\texstringonly{\\}Pure Einstein gravity in $\mrm{AdS}_3$~/~$\mrm{CFT}_2$}
 
-\textcite{Maldacena:1997re}\\
-\textcite{Aharony:1999ti}
-\begin{align*}
-	\textrm{Strings on $\mrm{AdS}_{d+1}$ background}
-	&\ \equiv\ 
-	\textrm{Conformal Field Theory $\mrm{CFT}_{d}$}
-\\
-	\textrm{\textit{asympt.}~$\mrm{AdS}_{d+1}$ Gravity}
-	&\ \equiv\ 
-	\textrm{Large $N$ $\mrm{CFT}_{d}$ at \textit{asympt.}~boundary}
-\end{align*}
-\begin{center}
-	\includegraphics[width=.6\linewidth]{img/ads-cft.png}
+\noindent\citations{%
+\textcite{Fefferman:2007rka}\\
+\textcite{Banados:1992wn}\\
+\textcite{Banados:1998gg}
+}
 
-	\vspace{-.2\baselineskip}
-	\captionsetup{type=figure}
-	\caption{$\mrm{AdS}_3/\mrm{CFT}_2$ cartoon}
-
-	\vspace{.1\baselineskip}
-	\scriptsize\ Image courtesy: \textcite{AldegundePWSep22}
-\end{center}
-
-\begin{itemize}
-
-\item \textsc{Universal / ubiquitous}
-
-\begin{itemize}
-	\item Model agnostic: $\mrm{AdS}_5\times S^5$, $\mrm{AdS}_3\times S^3 \times T^4$, symmetric orbifolds, minimal models, ``monsters'', ...
-\textit{\small Maldacena, Witten, GKP, ABJM, Gaberdiel, and many many more}
-
-\end{itemize}
-
-\item Our work: pure Einstein gravity in $\mrm{AdS}_3$ / $\mrm{CFT}_2$ $(d=2)$.\\
-$\mrm{AdS}_3$ metric, $\rho \sim z^2 \sim r^{-2}$
+We focus on pure Einstein gravity without matter in the bulk; the Einstein equations are solved by the metric:
 \begin{equation}
@@
 	ds^2
-	&= \ell^2 \frac{d\rho^2}{4 \rho^2} + \pqty{\frac{1}{\rho} g^{(0)}_{ij} + g^{(2)}_{ij} + \rho\thinmspace g^{(4)}_{ij} + \cdots}\, dx^i dx^j
-\\[.5ex]
-	&= \ell^2 \bigg( \frac{d\rho^2}{4 \rho^2} + \frac{ \big( du + \rho \, \mathcal {\bar L}(v)\, dv \big) \big( dv + \rho \, \mathcal L(u)\, du \big) }{\rho} \bigg)
+	&= \ell^2 \bigg( \frac{d\rho^2}{4 \rho^2} + \frac{ \big( du + \rho \, \mathcal {\bar L}(v)\, dv \big) \big( dv + \rho \, \mathcal L(u)\, du \big) }{\rho} \bigg)\\
+	&= n_\mu n_\nu dx^\mu dx^\nu + \frac{1}{\zeta} \gamma_{ij}dx^i dx^j,\quad
+\frac{1}{\zeta} \equiv \ell^{-2} g_{\varphi\varphi} \equiv r^2
+\end{aligned}
 \label{fggauge}
-\end{aligned}
 \end{equation}
+The radial coordinate: $\rho \approx r^{-2} \equiv \zeta$,
+where $r$ is the ``proper radius''; $\mathcal L(u)$ and $\bar{\mathcal L}(v)$ are arbitrary periodic functions.
 
-\vspace{-.5\baselineskip}
-boundary at $\rho \to 0$, $x^{i} \sim \varphi, t$, indices $i,j = 1,2$
+\noindent%
+The geometry is foliated by constant $\zeta$ surfaces ${\mathcal N}_\zeta$. 
+\\
+The asymptotic boundary $\mcal{N}_0$ is at $\zeta \to 0$, with coordinates: $x^{i} \sim \varphi, t$, while $u,v = \varphi \pm t$.
 
-\item Surprisingly the expansion simply terminates at~$\rho\thinmspace g^{(4)}_{ij}$ for pure Einstein gravity! Moreover,
-\begin{equation}
-	g^{(4)}_{ij} = \frac{1}{4} g^{(2)}_{ik} g^{(0)\thinmspace kl}_{\phantom{kl}} g^{(2)}_{lj}
-\end{equation}
-\textcite{Fefferman:2007rka}\\
-\textcite{Banados:1992wn}\\
-\textcite{Banados:1998gg}
-\end{itemize}
+\noindent%
+Our work is based on the $\mrm{AdS}_3/\mrm{CFT}_2$ duality:
+\begin{align*}
+%\hspace{-1em}
+	\textrm{\textit{asympt.}~$\mrm{AdS}_3$ Gravity}
+	&\ \equiv\ 
+	\textrm{Large $N$ $\mrm{CFT}_2$ at $\mcal{N}_0$}
+\end{align*}
+\citations{\noindent%
+	\textcite{Maldacena:1997re}\\
+	\textcite{Aharony:1999ti} \textit{et al}
+}
+%\begin{center}
+%	\includegraphics[width=.7\linewidth]{img/ads-cft.png}\\[.5ex]
+%	\scriptsize\ Image courtesy: \textcite{AldegundePWSep22}
+%\end{center}
 
-\newcommand{\eqBanados}{
-	\begin{equation*}
-	\hspace{-2em}
-		ds^2 \ \,
-	\end{equation*}
+%\begin{itemize}
+
+%\item Universal / ubiquitous:
+%
+%\begin{itemize}
+%	\item Model agnostic: $\mrm{AdS}_5\times S^5$, $\mrm{AdS}_3\times S^3 \times T^4$, symmetric orbifolds, minimal models, ``monsters'', ...
+\textit{\small Maldacena, Witten, GKP, ABJM, Gaberdiel, and many many more}
+%	
+%\end{itemize}
+
+%\item
+
+%\end{itemize}
+
+\subsection*{\TTbar deformations \& cutoff $\mrm{AdS}_3$}
+
+\citations{
+\textcite{Zamolodchikov:2004ce}\\
+\textcite{Dubovsky:2012wk}\\
+\textcite{Dubovsky:2013ira}\\
+\textcite{Smirnov:2016lqw}\\
+\textcite{Cavaglia:2016oda}\\
+\textcite{Dubovsky:2017cnj} \textit{et al}
 }
@@
 \begin{itemize}
-\item $g^{(2)} \leadsto \mathcal L(u)$, $\bar{\mathcal L}(v)$: arbitrary periodic functions,\\
-where $u,v = \varphi \mp it$, $du\,dv = d\varphi^2 + dt^2$
-%	\vspace{-.5\baselineskip}
 
-\item A consequence of Einstein equations \\
-in $(2+1)$ dimensions.\\
-\textit{Too many constraints, too little freedom!}
-\end{itemize}
-
-\begin{itemize}
-\item Different \textbf{geometries} in the ``bulk''
-
-specified by $\mathcal L(u)$, $\bar{\mathcal L}(v)$: periodic functions, maps to different \textbf{states} in the boundary $\mrm{CFT}_2$ with stress energy $\ave{T(u)}_\psi$, $\ave{\bar{T}(v)}_\psi$
-
-\item \textit{Dictionary:} bulk $\leftrightarrow$ boundary quantities:
-	\begin{itemize}
-	\item spectrum,
-		symmetry,\\
-		partition functions,
-		correlators, ...
-	\end{itemize}
-\end{itemize}
-
-\begin{frame}{\TTbar deformations --- motivations}{%
-	Comments taken from \textcite{Cui:2023jrb}
-}
-	\begin{itemize}
-	\item Ideally: AdS/CFT
-	\item Reality: non-AdS space and non-CFT
-	\begin{itemize}
-		\item possible to extend holographic principle to more general context?
-		\item attempt: \textbf{\textit{deformations}} on both sides\\
-		in a controllable way
-	\end{itemize}
-	\end{itemize}
-\end{frame}
-
-\newcommand{\citeTTbar}{%
-	\textcite{Zamolodchikov:2004ce}, revived by \textcite{Smirnov:2016lqw} and \textcite{Cavaglia:2016oda} \textit{et al}
-}
-
-\begin{frame}{\TTbar deformations --- definition}{%
-	\citeTTbar
-}
-\begin{itemize}
-
-\item Define ``\,\TTbar\,'' as the flow of action:
+\item Define ``\,$\TTbar$\,'' as the flow of action:
 \begin{equation}
-	\partial_{\sidenote{\mu}} I = -{8 \pi} \int d^2x \, T\bar T =  -{\pi} \int d^2x\,\big( T^{ij}T_{ij}- (T^i_i)^2 \big)
+	\partial_{\sidenote{\mu}} I = {8 \pi} \int d^2x \, T\bar T_{(\sidenote{\mu})} = {\pi} \int d^2x\,\big( T^{ij}T_{ij}- (T^i_i)^2 \big)_{(\sidenote{\mu})}
 	\label{TTbardef}
 \end{equation}
-For $\mrm{CFT}_2$,\ $T\bar{T} = T_{xx} T_{\bar{x}\bar{x}}$,\ where $x, \bar{x} = \varphi' \mp it'$.
+where $x, \bar{x} = \varphi' \pm t'$.
+We shall start from $\mrm{CFT}_2$ such that $T\bar{T}_{(\mu = 0)} = T_{xx} T_{\bar{x}\bar{x}}$, but note that the deformation is \textit{irrelevant}: conformal symmetry will be broken for $\mu \ne 0$.
 
-\item The stress tensor $T_{ij}(\sidenote{\mu})$ on the right hand side flows with the deformation parametrized by $\sidenote{\mu}$.
-
-\item This is thus a \textit{differential equation} for a flow, starting from some generic QFT specified by $I(\mu = 0)$.
-In this work we shall start from $\mrm{CFT}_2$, but note that \TTbar is \textit{irrelevant}: conformal symmetry will be broken.
-
-\end{itemize}
-\end{frame}
-
-\begin{frame}{``Solvable'' deformations on the field theory side}{%
-	\citeTTbar
-}
-\begin{itemize}
-
-\item \textbf{``Solvable'':} the deformed spectrum of $\hat{H}(\mu)$ and $\hat{J}(\mu)$ on a cylinder of radius $R$ can be solved, 
-and it's a simple function\\
- of the undeformed $E(0)$, $J(0)$:
+\item \textbf{Solvable:} the deformed spectrum of $\hat{H}(\mu)$ and $\hat{J}(\mu)$ on a cylinder of radius $R$ is a simple function:
 \begin{equation}
 \hspace{-2em}
+\begin{gathered}
 	E(\mu) = - \frac{R }{ 2\mu } \bigg(1-\sqrt{1 + \frac{4\mu}{R} E(0) + \frac{4\mu^2}{R^4} J(0)^2 }
-	\,\bigg), \ \quad J(\mu)=J(0) % \label{ttbarspectrum}
+	\,\bigg), \\[1ex] J(\mu)=J(0)
+\end{gathered} \label{ttbarspectrum}
 \end{equation}
-under simple (and reasonable) assumptions (e.g.~translation invariance et al).
-
-\item \textbf{Variants:} suppose the theory has some ``components'' labeled by $w$,
-
-\begin{itemize}
-\item double-trace $\TTbar = (\sum_w T_w) (\sum_w \bar{T}_w)$ (this work)
-\item single-trace $\TTbar' = \sum_w (T_w \bar{T}_w)$ (e.g.~\textit{\citeauthor{Cui:2023jrb}},~23)
-\end{itemize}
+of the undeformed spectrum $E(0)$, $J(0)$,
+under reasonable assumptions (e.g.~translation invariance).
 
@@
 
-\vspace{.5\baselineskip}
-\end{frame}
+\subsection*{Cutoff $\mrm{AdS}_3$ duality:\texstringonly{\\} Holography within a finite Dirichlet wall}
 
-\begin{frame}{\TTbar deformations --- properties}{%
-	\textcite{Zamolodchikov:2004ce}\\
-	\citetitle{Zamolodchikov:2004ce}
-}
-\vspace{-.1\baselineskip}
-\begin{equation}
-	E(\mu) = - \frac{R }{ 2\mu } \bigg(1-\sqrt{1 + \frac{4\mu}{R} E(0) + \frac{4\mu^2}{R^4} J(0)^2 }
-	\,\bigg), \ \quad J(\mu)=J(0)  \label{ttbarspectrum}
-\end{equation}
-\vspace{-\baselineskip}
-\begin{itemize}
-\item It seems that the \TTbar deformation is well-defined non-perturbatively for generic $\mrm{QFT}_2$,
-yet it's still mysterious and difficult\\
-\begin{itemize}
-\item e.g.~correlators: \textcite{Kraus:2018xrn,Cardy:2019qao,Cui:2023jrb}
-\item ``asymptotic fragility'': \textcite{Dubovsky:2017cnj}
-\end{itemize}
-
-\item What if we start from a $\mrm{CFT}_2$, that enjoys a holographic dual to $\mrm{AdS}_3$...
-
-\end{itemize}
-\end{frame}
-
-\newcommand{\figCutoffAds}[1][.5]{
+\citations{
+\textcite{McGough:2016lol}\\
+\textcite{Kraus:2018xrn} \textit{et al}
+}\vspace{-.8\baselineskip}
 \begin{center}
-	\hspace{.15\linewidth}
-	\includegraphics[width=#1\linewidth]{img/cutoff-ads.jpg}
+	\hspace{.1\linewidth}
+	\includegraphics[width=.48\linewidth]{img/cutoff-ads.jpg}
 
 	\vspace{-.5\baselineskip}
-	\ \scriptsize\textcite{AldegundePWSep22}
+	\scriptsize\ Image courtesy: \textcite{AldegundePWSep22}
 \end{center}
-}
-
-\begin{frame}{Cutoff $\mrm{AdS}_3$ / \TTbar deformed $\mrm{CFT}_2$}{%
-	\textcite{McGough:2016lol} --
-	\citetitle{McGough:2016lol}
-}
-
-\figCutoffAds
-
-\begin{itemize}
-\item Question: what is the AdS dual of \TTbar deformation?
-
-\begin{itemize}
-\item look up \textit{double-trace deformations}\\
-in \textit{the dictionary}:\\
-\textcite{Heemskerk:2010hk}
-
-\item look at properties of \TTbar:\\
-signs of gravity and coarse-graining\\
-\textcite{Dubovsky:2012wk,Dubovsky:2013ira}
-\end{itemize}
-
-\item Answer: AdS gravity within a finite Dirichlet wall
-
-\end{itemize}
-
-\end{frame}
-
-\begin{frame}{Cutoff $\mrm{AdS}_3$ --- the dictionary}{}
-
-	\begin{itemize}
-	\item Location (radius) of the cutoff surface:
-	\begin{equation}
-		\frac{1}{\zeta} \equiv \ell^{-2} g_{\varphi\varphi} \label{cutoff}
-	\end{equation}
-	gets mapped to the deformation parameter $\mu$:
+\textbf{Dictionary:} the \TTbar deformed theory lives on $\mcal{N}_{\zeta_c}$ with metric $\gamma_{ij}$.
+Location (radius) of the cutoff surface gets mapped to the deformation parameter $\mu$:
 \begin{equation}
@@
 \end{equation}
-	\textit{Roughly $\mu \sim 1/r^2$}
+\TTbar flow is recast geometrically as the $i,j$ components of the Einstein equations.
 
-	\item Passed many non-trivial tests,\\
-	related to ``mixed boundary conditions''\\
-	by \textcite{Guica:2019nzm}
+\columnbreak
+
+\begin{itemize}
+
+\item \textbf{Significance:} gravity inside a finite box, dual to some ``solvable'' no-longer-conformal theory.
+
+\textit{A step towards quantum gravity in \reality!}
+
+\item \textbf{Caveat:} the duality only admits $\zeta_c > 0$ so $\mu < 0$.
+But \TTbar itself admits $\mu > 0$ with nice properties.
+
+For comparison, the related proposal of \textcite{Guica:2019nzm} admits both signs of $\mu$.
+
+\textit{What is the other side of the duality?}
 
@@
 
-\end{frame}
+\section*{\textbf{Proposal:}\texstringonly{\\}Glue-on $\mrm{AdS}_3$ -- beyond the infinity}
+\label{se:glueonproposal}
 
-\begin{frame}{Cutoff $\mrm{AdS}_3$ --- gravity in a box}{%
-	Title inspired by
-	\textcite{Kraus:2021cwf} -- \citetitle{Kraus:2021cwf}%
+\parbox{\linewidth}{
+\vspace{-\baselineskip}
+\begin{equation*}
+	\textrm{Cutoff / \textit{glue-on} $\mrm{AdS}_{d+1}$ Gravity}
+	\ \equiv\ %
+	\textrm{\TTbar deformed $\mrm{CFT}_{d}$ at $\mcal{N}_{\zeta_c}$}
+\end{equation*}
+\begin{center}
+	\vspace{-.8\baselineskip}%
+	\centering
+	\includegraphics[width=.6\linewidth]{img/diagram.pdf}
+
+	\vspace{-.5\baselineskip}
+	\scriptsize\ Top-down view of a constant $t$ slice
+\end{center}
+%\vspace{-\baselineskip}
 }
@@
 \begin{itemize}
-\item \textbf{Significance:} gravity inside a finite box\\
-	with hard Dirichlet walls
 
-\begin{itemize}
-	\item Dual to some ``solvable'' no-longer-conformal ft
-	\item A step towards quantum gravity in reality!
-\end{itemize}
-
-\item \textbf{Caveat:} the duality only admits $\zeta_c > 0$ so $\mu < 0$
-\begin{equation}
-	\zeta_c = - \frac{c \mu}{3\ell^2}
-%		\label{dictionary}
-\end{equation}
-But \TTbar itself admits $\mu > 0$ with nice properties.\\
-\textit{What is the other side of the duality?}
-	\begin{itemize}
-	\item For comparison, the proposal of \textcite{Guica:2019nzm} admits both signs of $\mu$
-	\end{itemize}
-\end{itemize}
-
-\end{frame}
-
-\section{\textbf{Proposal:} Glue-on AdS holography} \label{se:glueonproposal}
-
-\begin{frame}{Glue-on $\mrm{AdS}_3$ --- analytic continuation}{%
-	\textcite{Apolo:2023vnm} -- \citetitle{Apolo:2023vnm}
-}
-	\begin{itemize}
-	\item $\mrm{AdS}_3$ metric has only simple poles with the $\rho$ coordinate:
-	\begin{equation}
-		ds^2 = \ell^2 \bigg( \frac{d\rho^2}{4 \rho^2} + \frac{ \big( du + \rho \, \mathcal {\bar L}(v)\, dv \big) \big( dv + \rho \, \mathcal L(u)\, du \big) }{\rho} \bigg)\ %\label{banados}
-	\end{equation}
-	thus it admits well-defined analytic continuation \\
-	from $\rho > 0$ to $\rho \in \mbb{R}$.
-	\item Continuation of the dictionary:
+\item \textbf{Analytic continuation:} metric \eqref{fggauge} has only simple poles, thus admits well-defined analytic continuation:
+%\begin{equation}
+%	\rho,\ \zeta,\ \mu\ \in\ \mbb{R}
+%\end{equation}
 \begin{equation}
@@
 \end{equation}
-%	\vspace{-.5\baselineskip}
+What are we doing other than copy-pasting?
+	\begin{itemize}
+	\item Physical quantities diverge as $\rho \to 0$.
+	A prescription is required to ``renormalize'' the divergences.
 
+	\item Treatment for the singularity at $\zeta\to 0^\pm$: introduce $\mathcal N_{\zeta={\pm\epsilon}}$ and glue them together (``\textbf{glue-on}'');
+		exclude the $-\epsilon < \zeta < \epsilon$ region until finally sending $\epsilon \to 0$. 
+	\item We formally denote the boundary surface by the limit $\mathcal N_{0}=\mathcal N_{0^+}=\mathcal N_{0^-}$, though we need to keep track of the asymptotic cutoff $\epsilon$ in actual computations.
 	\end{itemize}
-\end{frame}
 
-\newcommand{\figGlueon}[1][1]{
-\begin{minipage}{#1\linewidth}
-	\centering
-	\includegraphics[width=.5\linewidth]{img/diagram.pdf}
-	\vspace{-1.5\baselineskip}
-	\captionsetup{type=figure}
-	\caption{Glue-on $\mrm{AdS}_3$}
+\item \textbf{Extending the flow:} matching energy-momentum (Brown-York) \& the \TTbar flow equations:
+	\begin{equation}
+	\begin{gathered}
+		T_{ij}= \frac{\sigma_{\zeta_c}}{8\pi G} \Big( K_{ij} -  K \gamma_{ij} + \frac{1}{\ell |\zeta_c|}\gamma_{ij}\Big), \\ \sigma_{\zeta_c} = \frac{\abs{\zeta_c}}{\zeta_c} = \pm 1,\\
+		\gamma_{ij} = \zeta_c h_{ij},
+	\end{gathered}	\label{BYtensor}
+	\end{equation}
+	where $h_{ij}$ is the induced metric.
 
-	\vspace{-.3\baselineskip}
-	\scriptsize\ Top-down view of the Poincar\'e disk
-\end{minipage}
-}
-
-\begin{frame}{Glue-on $\mrm{AdS}_3$ / \TTbar --- updating the dictionary}{%
-	\textcite{Apolo:2023vnm} -- \citetitle{Apolo:2023vnm}
-}
-
-\figGlueon
-
-\begin{equation}
-	\frac{1}{\zeta} \equiv \ell^{-2} g_{\varphi\varphi} \in \mbb{R},
-\ \quad
-	\zeta_c = - \frac{c \mu}{3\ell^2} \in \mbb{R}
-\end{equation}
-\begin{itemize}
-\item What have we done other than copy-pasting?
-	\begin{itemize}
-	\item Although the continuation is straightforward, physical quantities diverge as $\rho \to 0$
-
-	\item A prescription is required to ``renormalize'' the divergences
-	\end{itemize}
+	The field theory metric $\gamma_{ij}$ is always positive-definite, while $h_{ij}$ becomes negative-definite for the glue-on region $\rho,\zeta < 0$.
+	This discrepancy is the origin of the $\abs{\zeta_c}$.
 
@@
 
-\end{frame}
-
-\begin{frame}{Glue-on $\mrm{AdS}_3$ / \TTbar --- updating the dictionary}{%
-	\textcite{Kraus:2018xrn} -- \citetitle{Kraus:2018xrn}
-}
-\begin{itemize}
-\item Firstly, matching energy momentum (Brown-York) \& the flow equations:
-	\begin{equation}
-		T_{ij}= \frac{\sigma_{\zeta_c}}{8\pi G} \Big( K_{ij} -  K \gamma_{ij} + \frac{1}{\ell |\zeta_c|}\gamma_{ij}\Big), \ \quad \sigma_{\zeta_c} = \frac{\abs{\zeta_c}}{\zeta_c} = \pm 1,
-		\label{BYtensor}
-	\end{equation}
-	The field theory metric $\gamma_{ij} = \zeta_c h_{ij}$, where $h_{ij}$ is the induced metric.
+\subsection*{\TTbar physics from the glue-on geometry}
 
 \begin{itemize}
-	\item $\gamma_{ij}$ is always positive-definite, while $h_{ij}$ becomes negative-definite for the glue-on region.
-	This discrepancy is the origin of the $\abs{\zeta_c}$.
-	\end{itemize}
-
-\item \TTbar flow is recast geometrically as the $i,j$ components of the Einstein equations. 
-Note that the geometry can be decomposed such that:
-	\begin{equation}
-		ds^2 = \frac{1}{\zeta} \gamma_{ij}dx^i dx^j+n_\mu n_\nu dx^\mu dx^\nu
-	\end{equation}
-\end{itemize}
-\end{frame}
-
-\begin{frame}{Glue-on $\mrm{AdS}_3$ --- beyond the infinity}{%
-	\textcite{Apolo:2023vnm} -- \citetitle{Apolo:2023vnm}
-}
-\begin{itemize}
-\item The geometry is foliated by constant $\zeta$ surfaces ${\mathcal N}_\zeta$:
-	\begin{equation}
-	\begin{aligned}
-		ds^2 
-		&= \ell^2 \bigg( \frac{d\rho^2}{4 \rho^2} + \frac{ \big( du + \rho \, \mathcal {\bar L}(v)\, dv \big) \big( dv + \rho \, \mathcal L(u)\, du \big) }{\rho} \bigg) \\
-		&= \frac{1}{\zeta} \gamma_{ij}dx^i dx^j+n_\mu n_\nu dx^\mu dx^\nu,\ \quad
-	\frac{1}{\zeta} \equiv \ell^{-2} g_{\varphi\varphi}
-	\end{aligned}
-	\end{equation}
-	The \TTbar deformed theory lives on $\mcal{N}_{\zeta_c}$ with metric $\gamma_{ij}$.
-
-\item Treatment for the singularity at $\zeta\to 0^\pm$: introduce $\mathcal N_{\zeta={\pm\epsilon}}$ and glue them together (``glue-on'');
-	exclude the $-\epsilon < \zeta < \epsilon$ region until finally sending $\epsilon \to 0$. 
-\item We formally denote the boundary surface by the limit $\mathcal N_{0}=\mathcal N_{0^+}=\mathcal N_{0^-}$, though we need to keep track of the asymptotic cutoff $\epsilon$ in actual computations.
-\end{itemize}
-\end{frame}
-
-\newcommand{\stateGlueon}{\ensuremath{
-	\textrm{Cutoff / \textit{glue-on} $\mrm{AdS}_{d+1}$ Gravity}
-	\ \equiv\ %
-	\textrm{\TTbar deformed $\mrm{CFT}_{d}$ at $\mcal{N}_{\zeta_c}$}
-}}
-
-\begin{frame}{Glue-on $\mrm{AdS}_3$ / \TTbar --- the proposal}{}
-
-\begin{center}
-\includegraphics[width=.6\linewidth]{img/diagram.pdf}
-\begin{equation*}
-\stateGlueon
-\end{equation*}
-\end{center}
-
-\end{frame}
-
-\section{\textbf{Check:} \TTbar deformed charges \& partition functions} \label{se:charges}
-
-\begin{frame}{\TTbar quantities from bulk geometry}{%
-	\textcite{Apolo:2023vnm} -- \citetitle{Apolo:2023vnm}
-}
-
-\begin{itemize}
-\item AdS/CFT: weak / strong duality
-	\begin{itemize}
-	\item \textit{quantum} quantities on the CFT side\\
-		can be computed by (semi-)classical geometry
-	\item inherited by the \TTbar deformation
-	\end{itemize}
 
@@
 	\end{equation}
-	$\zeta_c = -1$ is a horizon of the glue-on geometry, \\
-	where $\det g_{\mu\nu} = 0$.
+	This is a Killing horizon of the glue-on geometry;
+	$(\det g_{\mu\nu})_{\,\zeta = -1} = 0$.
 
-\end{itemize}
+\item \textbf{Spectrum from the extended geometry:} \mbox{conserved} charges of the Killing symmetries, can be computed with the \textit{covariant formalism}:
 
-\end{frame}
-
-\begin{frame}{\TTbar spectrum from bulk covariant charges}{%
-	\textcite{Kraus:2021cwf,Apolo:2023vnm}
-}
-
-\begin{itemize}
-\item Spectrum: conserved charges of geometries,\\
-	e.g.~black holes \textit{BTZ} \cite{Banados:1992wn}
-	\begin{itemize}
-	\item computed with the covariant formalism\\
-		\textcite{Iyer:1994ys, Barnich:2001jy}
-	\item manifest covariance (diff-invariance) depends on reparametrization redundancies (gauge),\\
-		so delay gauge fixing until the very end
-	\end{itemize}
-
-\item We are careful to match the bulk \& boundary symmetries at $\mcal{N}_{\zeta_c}$
-
-\item This reproduces $E(\mu)$, $J(\mu)$ with $\mu \in\mbb{R}$ in \eqref{ttbarspectrum}
-
-\end{itemize}
-
-\end{frame}
-
-\begin{frame}{\TTbar spectrum from bulk covariant charges}{%
-	\textcite{Kraus:2021cwf,Apolo:2023vnm}
-}
-
-\begin{itemize}
-\item Covariant charges of geometries
+\citations{
+	\textcite{Iyer:1994ys}\\
+	\textcite{Barnich:2001jy}\\
+	With \TTbar: \textcite{Kraus:2021cwf}
+}\vspace{-1.5\baselineskip}
 	\begin{align*}
@@
 	\end{align*}
+	This reproduces $E(\mu)$, $J(\mu)$ with $\mu \in\mbb{R}$ in \eqref{ttbarspectrum}.
 
-\item One needs to choose the appropriate boundary coordinates $(t',\varphi')$, such that
+\item We are careful to match the bulk \& boundary symmetries at $\mcal{N}_{\zeta_c}$.
+One needs to choose the appropriate boundary coordinates $(t',\varphi')$, such that
 	\begin{equation}
@@
 	\end{equation}
-
-\item This is realized by the \textit{state-dependent} map of coordinates
+This is realized by:
 	\begin{align*}
@@
 	\end{align*}
+
+\item The above \textbf{\textit{state-dependent} map of \mbox{coordinates}} leads to the correct charges, the modified signal propagation speed $v'_{\pm} \equiv \pm \frac{d\varphi'}{dt'}$, and the \TTbar \textbf{thermodynamics} when Wick rotated.
+In particular,
+	\begin{equation}
+	\hspace{-2.5em} \mu > 0,\ \quad
+		T_L(\mu)\,T_R(\mu) \le - \frac{1}{4\pi^2 \ell^2 \zeta_c} = \frac{3}{4\pi^2c\mu} = T_H(\mu)^2.
+	\end{equation}
+	$T_{L,R}$ are temperatures associated with $u',v' = \varphi' \pm t'$.\\
+	$T_H$ is the \textit{Hagedorn temperature}: exceeding $T_H$ corresponds to a complex entropy.
+
+\citations{
+\textcite{Giveon:2017nie}\\
+\textcite{Apolo:2019zai}
+}
 \end{itemize}
 
-\end{frame}
+\subsection*{\TTbar partition functions from bulk actions} \label{se:partitionfunction}
 
-\begin{frame}{\TTbar thermodynamics from bulk geometry}{%
-	\textcite{Giveon:2017nie,Apolo:2019zai}
-}
-
-\begin{itemize}
-
-\item Many consequences: correct charges, signal propagation speed $v'_{\pm} \equiv \pm \frac{d\varphi'}{dt'}$, and thermodynamics when Wick rotated:
-	\begin{equation}
-		T_L(\mu)\,T_R(\mu) \le - \frac{1}{4\pi^2 \ell^2 \zeta_c} = \frac{3}{4\pi^2c\mu} = T_H(\mu)^2,
-	\quad \mu > 0
-	\end{equation}
-	$T_{L,R}$ are temperatures associated with $u',v' = \varphi' \pm t'$.
-
-\item $T_H$ is the \textit{Hagedorn temperature}: exceeding $T_H$ corresponds to a complex entropy
-\end{itemize}
-
-\end{frame}
-
-\section{\textbf{Check:} \TTbar partition functions from glue-on AdS} \label{se:partitionfunction}
-
-\begin{frame}{\TTbar partition functions from bulk on-shell actions}{%
+\citations{
 \textcite{Caputa:2020lpa}
@@
 \begin{itemize}
-\item Bulk: weakly coupled gravity, the partition function is approximated by the on-shell gravity action of the dominant saddle:
+\item The \TTbar partition function is approximated by the bulk on-shell action of the dominant saddle:
 	\begin{equation}
@@
 
-\item $I(\zeta_c)$ is roughly the volume of the geometry, which diverges at $\zeta \to 0^\pm$. We apply a natural extension of \textit{holographic renormalization} to remove the divergence.
+\item $I(\zeta_c)$ is roughly the volume of the geometry, which \mbox{diverges} at $\zeta \to 0^\pm$. We apply a natural extension of \textit{holographic renormalization} to remove the divergence.
 
-\item $I = -\log \mcal{Z}$ satisfies the \TTbar flow \eqref{TTbardef}.\\
+\item $I = -\log \mcal{Z}$ satisfies the \TTbar flow \eqref{TTbardef}.
 	This is non-trivial because we've packaged the quantum corrections of the boundary theory.
 \end{itemize}
-\end{frame}
 
-\begin{frame}{Comparison with field theory analysis}{%
-	\textcite{Datta:2018thy,Apolo:2023aho}
-}
-
-\vspace{-.3\baselineskip}
+\subsection*{Comparison with field theory analysis}
 
 \begin{itemize}
-\item \textbf{Torus:} Large $c$, \textit{modular invariance} \& sparseness of the ``light'' spectrum \cite{Datta:2018thy,Apolo:2023aho},
-	c.f. \textcite{Hartman:2014oaa}
+\item \textbf{Torus:} Large $c$, \textit{modular invariance} \& sparseness of the ``light'' spectrum:
+
+\citations{
+	\textcite{Datta:2018thy}\\
+	\textcite{Apolo:2023aho}\\
+	cf.~\textcite{Hartman:2014oaa}
+}\vspace{-\baselineskip}
 	\begin{equation*}
@@
 
-\item \textbf{Sphere:} maximally symmetric, \textcite{Donnelly:2018bef}
+\item \textbf{Sphere:} maximally symmetric, \mbox{\footnotesize \textcite{Donnelly:2018bef}}
 	\begin{equation}
@@
 \end{itemize}
-\end{frame}
 
-\begin{frame}{Sphere partition functions}{%
-	\textcite{Donnelly:2018bef,Li:2020zjb}
-}
+\citations{\textcite{Donnelly:2018bef,Li:2020zjb}}
 
@@
 \end{itemize}
-\end{frame}
 
-\begin{frame}{Gravitational actions: with counterterms}{%
-	\textcite{Donnelly:2018bef,Li:2020zjb}
-}
+\subsection*{Gravitational actions: with counterterms}
+
+\textcite{Donnelly:2018bef,Caputa:2020lpa,Li:2020zjb}
 
@@
 
-\end{itemize}
-
-\end{frame}
-
-\begin{frame}{Gravitational actions: with counterterms}{%
-	\textcite{Caputa:2020lpa,Li:2020zjb}
-}
-
-\begin{itemize}
-
-\item The $\log$ counterterm makes a crucial contribution to the on-shell action:
-	\begin{align*}
-		I_{\mcal{M}}(\zeta_1, \zeta_2) & \coloneqq - \frac{1}{16\pi G} \int_{\zeta_1}^{\zeta_2} d\zeta \int d^2 x \sqrt{g} \, (R + 2 \ell^{-2}),  %\label{bulkaction} \\
-	\\
-		I_{\mathcal N_{\zeta}} & \coloneqq  - \frac{1}{8\pi G} \int_{\mathcal N_{\zeta}} d^2x \sqrt{h}\,h^{ij} K_{ij} 
-	\\& \qquad + \frac{\sigma_\zeta}{8\pi G} \int_{\mathcal N_{\zeta}} d^2x \sqrt{h} \, \bigg(\ell^{-1} - \frac{\ell  \mathcal{R}[h]}{4} \log |\zeta| \bigg), %\label{boundaryaction}
-	\end{align*}
-	It guarantees that the partition function is compatible with the $T\bar T$ differential equation --- not the case for \textsl{\citeauthor{Donnelly:2018bef}}.
+\item The $\log$ counterterm makes a crucial contribution to the on-shell action; it guarantees that the partition function is compatible with the $T\bar T$ differential equation --- not the case for \textsl{\citeauthor{Donnelly:2018bef}}.
 
@@
 \end{itemize}
-\end{frame}
 
-\section{Summary \& future directions}
-
-\section*{Glue-on $\mrm{AdS}_3$ / \TTbar deformed $\mrm{CFT}_2$}
-\noindent
-	\textcite{Apolo:2023vnm} -- \citetitle{Apolo:2023vnm}
-
-\begin{equation*}
-\stateGlueon
-\end{equation*}
+\section*{Summary \& future directions}
 
@@
 	\includegraphics[width=.5\linewidth]{img/RT-AdS.pdf}
+
 	\vspace{-1\baselineskip}
-	\captionof{figure}{RT for Glue-on $\mrm{AdS}_3$}
-
-	\vspace{.1\baselineskip}
-	\scriptsize\, Top-down view of the Poincar\'e disk
+	RT surface for the extended $\mrm{AdS}_3$
 \end{center}
@@
 \item We hope to understand the entanglement structure of \TTbar deformed theories from bulk geometry. 
-\end{itemize}
-
-\begin{frame}{Glue-on $\mrm{AdS}_3$ / \TTbar deformed $\mrm{CFT}_2$}{%
-	\textcite{Apolo:2023vnm} -- \citetitle{Apolo:2023vnm}
-}
-\begin{equation*}
-\stateGlueon
-\end{equation*}
-
-\begin{itemize}
-
-\item We hope to understand the entanglement structure of \TTbar deformed theories from bulk geometry. 
 	\begin{itemize}
@@
 \end{itemize}
-
-\end{frame}
 

### 2023-08-24 alpha/GlueonAdS/glueon-poster-v0.tex
Prepare for new version of the poster

--- 2023-08-24 alpha/GlueonAdS/glueon-poster-alt1.tex
@@
 
-\setlength{\droptitle}{-3.2\baselineskip}
-\pretitle{\huge\bfseries\noindent}
+\setlength{\droptitle}{-3.25\baselineskip}
+\pretitle{\LARGE\bfseries\noindent}
 \title{Glue-on AdS holography for $T\bar T$-deformed CFTs}
-\posttitle{\ \,}
+\posttitle{\ \,\normalsize\textsl{JHEP 06 (2023) 117}}
 
@@
 	and Wei Song \textkai{宋伟}
-	\hfill\arxiv{2303.04836}
-	\par\vspace{.5\baselineskip}
-	\hrule\vspace{.3\baselineskip}
+	\ \arxiv{2303.04836}
+	\par%\vspace{.5\baselineskip}
+	\vspace{-.6\baselineskip}
+	\noindent\rule{.66\linewidth}{1pt}\par
+	\vspace{-.1\baselineskip}
+%	\vspace{.3\baselineskip}
 }
@@
 
-\subsection*{Foundations:\texstringonly{\\}Pure Einstein gravity in $\mrm{AdS}_3$~/~$\mrm{CFT}_2$}
+\noindent%
+\textbf{Abstract:}
+\TTbar-deformed CFTs with $\mu < 0$ have been proposed by \textcite{McGough:2016lol} to be holographically dual to Einstein gravity with a finite \mbox{Dirichlet} cutoff.
 
-\noindent\citations{%
-\textcite{Fefferman:2007rka}\\
-\textcite{Banados:1992wn}\\
-\textcite{Banados:1998gg}
-}
+In this work we put forward a holographic proposal for \TTbar-deformed CFTs with $\mu > 0$, in which case the bulk dual geometry is constructed by gluing-on a patch of $\mrm{AdS}_3$ to the original spacetime.
+We provide various evidence for this extended holography, now valid for $\mu \in \mbb{R}$.
 
-We focus on pure Einstein gravity without matter in the bulk; the Einstein equations are solved by the metric:
+\vspace{.8\baselineskip}
+\hrule
+\vspace{.3\baselineskip}
+
+We start from \textbf{pure Einstein gravity} without matter in $\mrm{AdS}_3$; the Einstein equations are solved by the metric:
 \begin{equation}
@@
 
-\noindent%
-Our work is based on the $\mrm{AdS}_3/\mrm{CFT}_2$ duality:
+\noindent\citations{%
+\textcite{Fefferman:2007rka}\\
+\textcite{Banados:1992wn}\\
+\textcite{Banados:1998gg}
+}
+\vspace{-.5\baselineskip}
+\subsection*{Foundations: $\mrm{AdS}_3/\mrm{CFT}_2$ holography}
+\vspace{-.5\baselineskip}
 \begin{align*}
@@
 \end{align*}
+
 \citations{\noindent%
@@
 
-%\item
-
 %\end{itemize}
-
-\subsection*{\TTbar deformations \& cutoff $\mrm{AdS}_3$}
-
-\citations{
-\textcite{Zamolodchikov:2004ce}\\
-\textcite{Dubovsky:2012wk}\\
-\textcite{Dubovsky:2013ira}\\
-\textcite{Smirnov:2016lqw}\\
-\textcite{Cavaglia:2016oda}\\
-\textcite{Dubovsky:2017cnj} \textit{et al}
-}
 
@@
 
-\item Define ``\,$\TTbar$\,'' as the flow of action:
+\item Define \textbf{``\,$\TTbar$\,'' deformation} as the flow of action:
 \begin{equation}
@@
 	E(\mu) = - \frac{R }{ 2\mu } \bigg(1-\sqrt{1 + \frac{4\mu}{R} E(0) + \frac{4\mu^2}{R^4} J(0)^2 }
-	\,\bigg), \\[1ex] J(\mu)=J(0)
+	\,\bigg), \\ J(\mu)=J(0) \\[-1.5ex]
 \end{gathered} \label{ttbarspectrum}
@@
 under reasonable assumptions (e.g.~translation invariance).
+
+\citations{
+\textcite{Zamolodchikov:2004ce}\\
+\textcite{Dubovsky:2012wk}\\
+\textcite{Dubovsky:2013ira}\\
+\textcite{Smirnov:2016lqw}\\
+\textcite{Cavaglia:2016oda}\\
+\textcite{Dubovsky:2017cnj} \textit{et al}
+}
+
+\vspace{-.5\baselineskip}
 
@@
 \textcite{Kraus:2018xrn} \textit{et al}
-}\vspace{-.8\baselineskip}
-\begin{center}
-	\hspace{.1\linewidth}
-	\includegraphics[width=.48\linewidth]{img/cutoff-ads.jpg}
+}
 
-	\vspace{-.5\baselineskip}
-	\scriptsize\ Image courtesy: \textcite{AldegundePWSep22}
-\end{center}
 \textbf{Dictionary:} the \TTbar deformed theory lives on $\mcal{N}_{\zeta_c}$ with metric $\gamma_{ij}$.
@@
 \end{equation}
-\TTbar flow is recast geometrically as the $i,j$ components of the Einstein equations.
+\TTbar flow is recast geometrically as the $i,j$ components of the Einstein equations. This is a ``non-AdS'' / non-CFT duality.
+
+\noindent%
+\textit{A step towards quantum gravity in \reality!}
 
@@
 
+\vspace*{-4\baselineskip}
+\begin{center}
+	\hspace{.1\linewidth}
+	\includegraphics[width=.4\linewidth]{img/cutoff-ads.jpg}
+
+	\vspace{-.5\baselineskip}\small
+	Cutoff $\mrm{AdS}_3$\,/\,\TTbar-deformed $\mrm{CFT}_2$
+
+	\vspace{-.2\baselineskip}
+	\scriptsize\ Image courtesy: \textcite{AldegundePWSep22}
+\end{center}
+
 \begin{itemize}
 
-\item \textbf{Significance:} gravity inside a finite box, dual to some ``solvable'' no-longer-conformal theory.
+\item[] \textbf{Caveat:} the duality only admits $\zeta_c > 0$ so $\mu < 0$.\\
+But \TTbar itself admits $\mu > 0$ with cool properties.
 
-\textit{A step towards quantum gravity in \reality!}
-
-\item \textbf{Caveat:} the duality only admits $\zeta_c > 0$ so $\mu < 0$.
-But \TTbar itself admits $\mu > 0$ with nice properties.
-
-For comparison, the related proposal of \textcite{Guica:2019nzm} admits both signs of $\mu$.
+\citations{The related proposal of \textcite{Guica:2019nzm}\\
+admits both signs of $\mu$.}
 
@@
 \end{itemize}
+
+\vspace{-\baselineskip}
 
@@
 \begin{equation*}
+\hspace{-.8em}
 	\textrm{Cutoff / \textit{glue-on} $\mrm{AdS}_{d+1}$ Gravity}
@@
 
-\item \textbf{Analytic continuation:} metric \eqref{fggauge} has only simple poles, thus admits well-defined analytic continuation:
+\item \textbf{Analytic continuation:} metric \eqref{fggauge} has a simple pole, thus admits well-defined analytic continuation:
 %\begin{equation}
@@
 	\begin{itemize}
-	\item Physical quantities diverge as $\rho \to 0$.
+	\item Physical quantities diverge as $\zeta \to 0$.
 	A prescription is required to ``renormalize'' the divergences.
@@
 		exclude the $-\epsilon < \zeta < \epsilon$ region until finally sending $\epsilon \to 0$. 
-	\item We formally denote the boundary surface by the limit $\mathcal N_{0}=\mathcal N_{0^+}=\mathcal N_{0^-}$, though we need to keep track of the asymptotic cutoff $\epsilon$ in actual computations.
+%	\item We formally denote the boundary surface by the limit $\mathcal N_{0}=\mathcal N_{0^+}=\mathcal N_{0^-}$, though we need to keep track of the asymptotic cutoff $\epsilon$ in actual computations.
 	\end{itemize}
 
-\item \textbf{Extending the flow:} matching energy-momentum (Brown-York) \& the \TTbar flow equations:
+\item \textbf{Extending the flow:} matching energy momentum (Brown-York) \& the \TTbar flow equations:
 	\begin{equation}
 	\begin{gathered}
-		T_{ij}= \frac{\sigma_{\zeta_c}}{8\pi G} \Big( K_{ij} -  K \gamma_{ij} + \frac{1}{\ell |\zeta_c|}\gamma_{ij}\Big), \\ \sigma_{\zeta_c} = \frac{\abs{\zeta_c}}{\zeta_c} = \pm 1,\\
-		\gamma_{ij} = \zeta_c h_{ij},
+		T_{ij}= \frac{\sigma_{\zeta_c}}{8\pi G} \Big( K_{ij} -  K \gamma_{ij} + \frac{1}{\ell |\zeta_c|}\gamma_{ij}\Big), \\ \sigma_{\zeta_c} = \tfrac{\abs{\zeta_c}}{\zeta_c} = \pm 1,\quad
+		\gamma_{ij} = \zeta_c h_{ij}, \\[-1ex]
 	\end{gathered}	\label{BYtensor}
@@
 
-\end{itemize}
+%\end{itemize}
+%
+%\subsection*{\TTbar physics from the glue-on geometry}
+%
+%\begin{itemize}
 
-\subsection*{\TTbar physics from the glue-on geometry}
-
-\begin{itemize}
-
-\item Demanding the extended geometry to be non-singular
-	re-produces bounds on the \TTbar deformed theory, e.g.
+\item Demanding a \textbf{non-singular extended geometry} reproduces bounds on the \TTbar deformed theory, e.g.
 	\begin{equation}
@@
 	\end{equation}
-	This is a Killing horizon of the glue-on geometry;
+	This is a Killing horizon in the glue-on region of the \mbox{extended} geometry;
 	$(\det g_{\mu\nu})_{\,\zeta = -1} = 0$.
 
-\item \textbf{Spectrum from the extended geometry:} \mbox{conserved} charges of the Killing symmetries, can be computed with the \textit{covariant formalism}:
+\item \textbf{Spectrum from the extended geometry:} they are \mbox{conserved} charges of the Killing symmetries, and can be computed with the \textit{covariant formalism}.
 
 \citations{
-	\textcite{Iyer:1994ys}\\
-	\textcite{Barnich:2001jy}\\
+	\textsl{\citeauthor{Iyer:1994ys,Barnich:2001jy}} et al\\
 	With \TTbar: \textcite{Kraus:2021cwf}
@@
 	\begin{align*}
-		\delta E(\mu) &\equiv  \ell^{-1} \delta \mathcal Q_{\pd_{t'}}, \\ \delta J(\mu) &\equiv  \delta \mathcal Q_{\pd_{\varphi'}},
+		\delta E(\mu) &\equiv  \ell^{-1} \delta \mathcal Q_{\pd_{t'}}, \quad \delta J(\mu) \equiv  \delta \mathcal Q_{\pd_{\varphi'}}.
 	\end{align*}
@@
 
-\item We are careful to match the bulk \& boundary symmetries at $\mcal{N}_{\zeta_c}$.
-One needs to choose the appropriate boundary coordinates $(t',\varphi')$, such that
+\columnbreak
+
+\vspace*{-8\baselineskip}
+%\item The covariant charges (variation):
+
+	\item To match the bulk \& boundary symmetries at $\mcal{N}_{\zeta_c}$, we choose the appropriate coordinates $(t',\varphi')$, such that
 	\begin{equation}
@@
 
-\item The above \textbf{\textit{state-dependent} map of \mbox{coordinates}} leads to the correct charges, the modified signal propagation speed $v'_{\pm} \equiv \pm \frac{d\varphi'}{dt'}$, and the \TTbar \textbf{thermodynamics} when Wick rotated.
+\item The above \textbf{\textit{state-dependent} map of \mbox{coordinates}} leads to the correct charges, the modified signal propagation speed $v'_{\pm} \equiv \pm {d\varphi'}/{dt'}$, and the \TTbar \textbf{thermodynamics} when Wick rotated.
 In particular,
-	\begin{equation}
-	\hspace{-2.5em} \mu > 0,\ \quad
+	\begin{equation*}
+	\hspace{-.5em} \mu > 0,\quad
 		T_L(\mu)\,T_R(\mu) \le - \frac{1}{4\pi^2 \ell^2 \zeta_c} = \frac{3}{4\pi^2c\mu} = T_H(\mu)^2.
-	\end{equation}
+	\end{equation*}
 	$T_{L,R}$ are temperatures associated with $u',v' = \varphi' \pm t'$.\\
-	$T_H$ is the \textit{Hagedorn temperature}: exceeding $T_H$ corresponds to a complex entropy.
+	$T_H$ is the \textit{Hagedorn temperature}: exceeding $T_H$ leads to a complex entropy.
 
+\begin{flushright}
+\vspace{-.5\baselineskip}
 \citations{
@@
 }
+\vspace{-\baselineskip}
+\end{flushright}
+
 \end{itemize}
@@
 
-\citations{
-\textcite{Caputa:2020lpa}
-}
-
 \begin{itemize}
@@
 	\begin{equation}
-		Z_{T\bar T} (\mu) = \mathcal Z (\zeta_c) \approx  e^{-I(\zeta_c)}\label{partition2}
+		Z_{T\bar T} (\mu) = \mathcal Z (\zeta_c) \approx  e^{-I(\zeta_c)}. \label{partition2}
 	\end{equation}
+$I(\zeta_c)$ \mbox{diverges} at $\zeta \to 0^\pm$. We apply a natural extension of \textit{holographic renormalization} to remove the divergence.
+It includes the boundary action (with counterterms):
+	\begin{align}
+%		I_{\mcal{M}}(\zeta_1, \zeta_2) & \coloneqq - \frac{1}{16\pi G} \int_{\zeta_1}^{\zeta_2} d\zeta \int d^2 x \sqrt{g} \, (R + 2 \ell^{-2}),  %\label{bulkaction} \\
+%	\\
+		I_{\mathcal N_{\zeta}} & \coloneqq  - \frac{1}{8\pi G} \int_{\mathcal N_{\zeta}} d^2x \sqrt{h}\,h^{ij} K_{ij} \notag
+	\\& \qquad + \frac{\sigma_\zeta}{8\pi G} \int_{\mathcal N_{\zeta}} d^2x \sqrt{h} \, \bigg(\ell^{-1} - \frac{\ell  \mathcal{R}[h]}{4} \log |\zeta| \bigg). \label{boundaryaction}
+	\end{align}
+	The lack of diff invariance of the $\log |\zeta|$ counterterm is known to be a reflection of the Weyl anomaly. 
+	The \mbox{action} is consistent with the Brown-York stress \mbox{tensor} in \eqref{BYtensor}.
 
-\item $I(\zeta_c)$ is roughly the volume of the geometry, which \mbox{diverges} at $\zeta \to 0^\pm$. We apply a natural extension of \textit{holographic renormalization} to remove the divergence.
+	\hfill{\footnotesize \textcite{Henningson:1998gx} \textit{et al}}
 
-\item $I = -\log \mcal{Z}$ satisfies the \TTbar flow \eqref{TTbardef}.
-	This is non-trivial because we've packaged the quantum corrections of the boundary theory.
-\end{itemize}
+The resulting $I = -\log \mcal{Z}$ satisfies the \TTbar flow \eqref{TTbardef}.\\
+Furthermore, it agrees with the field theory analysis:
 
-\subsection*{Comparison with field theory analysis}
-
-\begin{itemize}
-\item \textbf{Torus:} Large $c$, \textit{modular invariance} \& sparseness of the ``light'' spectrum:
-
-\citations{
+\item \textbf{Torus:} {modular invariance} \& sparseness of the ``light'' spectrum at large $c$ leads to the universal form :
+	\begin{equation*}\small
+	\hspace{-1.5em}
+		\log   Z_{T\bar T}(\mu)  \approx \left\{ \begin{aligned}
+		& {-\frac{1}{2}}\,(\beta_L + \beta_R)\, RE_{\text{vac}}(\mu),  &\beta_L \beta_R > 1, \\
+		& {-2 \pi^2 \bigg(\frac{1}{\beta_L} + \frac{1}{\beta_R}\bigg)  RE_{\text{vac}}\bigg(\frac{4\pi^2}{\beta_L \beta_R} \mu \bigg)},  &\beta_L\beta_R < 1. %\\[2ex]
+		 \end{aligned} \right. %\label{ZTTbar}
+	\end{equation*}
+	\citations{\noindent%
 		\textcite{Datta:2018thy}\\
@@
 		cf.~\textcite{Hartman:2014oaa}
-}\vspace{-\baselineskip}
-	\begin{equation*}
-	\hspace{-1.5em}
-		\log   Z_{T\bar T}(\mu)  \approx \left\{ \begin{aligned}
-		& {-\frac{1}{2}}\,(\beta_L + \beta_R)\, RE_{\text{vac}}(\mu),  &\beta_L \beta_R > 1, \\
-		& {-2 \pi^2 \bigg(\frac{1}{\beta_L} + \frac{1}{\beta_R}\bigg)  RE_{\text{vac}}\bigg(\frac{4\pi^2}{\beta_L \beta_R} \mu \bigg)}, \ \, &\beta_L\beta_R < 1, %\\[2ex]
-		 \end{aligned} \right. %\label{ZTTbar}
-	\end{equation*}
+%		\textcite{Apolo:2023aho}, \mbox{following \textcite{Datta:2018thy} and \textsl{\citeauthor{Hartman:2014oaa}}}
+	}
 
-\item \textbf{Sphere:} maximally symmetric, \mbox{\footnotesize \textcite{Donnelly:2018bef}}
+\item \textbf{Sphere:} maximally symmetric,\\ \mbox{\footnotesize \textcite{Donnelly:2018bef}}
 	\begin{equation}
 %		\label{sphere:stresstensor}
-		\langle T_{ij}\rangle =-\frac{1}{4\pi\mu} \bigg(1-\sqrt{1-\frac{c\mu}{3L^2}}\, \bigg)  \gamma_{ij}.
+		\langle T_{ij}\rangle = -\frac{1}{4\pi\mu} \bigg(1-\sqrt{1-\frac{c\mu}{3R^2}}\, \bigg)  \gamma_{ij}.
 	\end{equation}
+Then the trace relation \mbox{$
+%	\begin{align*}
+%\partial_\mu \log Z_{\TTbar}(\mu)&=8\pi \int d^2x\sqrt{\gamma}\, \langle T\bar{T} \rangle \\
+(-R)\,\partial_R \log Z_{\TTbar}(\mu)=\int d^2x\sqrt{\gamma}\,\langle T^i_i \rangle
+%	\end{align*}
+$} along with the flow equation \eqref{TTbardef} 
+admits the general \mbox{solution} with a $\mu$-\textit{independent} integration constant $a$:
+	\begin{equation*}\small
+	\hspace{-1.2em}
+		\log Z_{\TTbar}(\mu, a) = \frac{c}{3} \log \bigg[\frac{R}{a}   \bigg(1+\sqrt{1-\frac{c \mu }{3  R^2}}\, \bigg) \bigg] - \frac{R^2}{\mu}  \sqrt{1-\frac{c \mu }{3 R^2}} + \frac{R^2}{\mu}.
+%\label{Zsol}
+	\end{equation*}
+	\cite{Donnelly:2018bef} is recovered with $a = \sqrt{c|\mu|/3}$ but one can also take $a = \epsilon$, thus decoupling the renormalization length scale $\epsilon$ with the deformation $\mu$.
+In general the space of deformed theories can be parametrized by independent $(\mu,a)$.
+
+	The $\log$ counterterm in \eqref{boundaryaction} makes a crucial contribution to the on-shell action; it guarantees that the partition function is compatible with the $T\bar T$ differential equation, which is not the case for \cite{Donnelly:2018bef}.
+	\begin{flushright}
+		\vspace{-.6\baselineskip}
+		\citations{
+			\textcite{Caputa:2020lpa}\\
+			\textcite{Li:2020zjb}
+		}\vspace{-.8\baselineskip}
+	\end{flushright}
+
+	\item Following these results, we would like to understand the entanglement structure of \TTbar deformed theories with the help of bulk geometry in future studies.
+	\begin{flushright}
+		\vspace{-.5\baselineskip}
+		\citations{
+			\textcite{Lewkowycz:2019xse}
+		}
+	\end{flushright}
 \end{itemize}
 
-\citations{\textcite{Donnelly:2018bef,Li:2020zjb}}
-
-\begin{itemize}
-
-\item Given the explicit stress tensor $\langle T_{ij}\rangle \propto \gamma_{ij}$, the flow equations:
-	\begin{align*}
-\partial_\mu \log Z_{\TTbar}(\mu)&=8\pi \int d^2x\sqrt{\gamma}\, \langle T\bar{T} \rangle \\
--L\,\partial_L \log Z_{\TTbar}(\mu)&=\int d^2x\sqrt{\gamma}\,\langle T^i_i \rangle
-	\end{align*}
-
-	\item ... admit the general solution with a $\mu$-\textit{independent} integration $a$:
-	\begin{equation*}
-		\log Z_{\TTbar}(\mu, a) = \frac{c}{3} \log \bigg[\frac{L}{a}   \bigg(1+\sqrt{1-\frac{c \mu }{3  L^2}}\, \bigg) \bigg] - \frac{L^2}{\mu}  \sqrt{1-\frac{c \mu }{3 L^2}} + \frac{L^2}{\mu} %\label{Zsol}
-	\end{equation*}
-
-	\item \textcite{Donnelly:2018bef} is recovered with $a = \sqrt{c|\mu|/3}$ but one can also take $a = \epsilon$, thus decoupling the energy (RG) scale $\epsilon$ with the deformation $\mu$. 
-\end{itemize}
-
-\subsection*{Gravitational actions: with counterterms}
-
-\textcite{Donnelly:2018bef,Caputa:2020lpa,Li:2020zjb}
-
-\begin{itemize}
-
-\item Gravitational actions, with counterterms:
-	\begin{align*}
-		I_{\mcal{M}}(\zeta_1, \zeta_2) & \coloneqq - \frac{1}{16\pi G} \int_{\zeta_1}^{\zeta_2} d\zeta \int d^2 x \sqrt{g} \, (R + 2 \ell^{-2}),  %\label{bulkaction} \\
-	\\
-		I_{\mathcal N_{\zeta}} & \coloneqq  - \frac{1}{8\pi G} \int_{\mathcal N_{\zeta}} d^2x \sqrt{h}\,h^{ij} K_{ij} 
-	\\& \qquad + \frac{\sigma_\zeta}{8\pi G} \int_{\mathcal N_{\zeta}} d^2x \sqrt{h} \, \bigg(\ell^{-1} - \frac{\ell  \mathcal{R}[h]}{4} \log |\zeta| \bigg), %\label{boundaryaction}
-	\end{align*}
-	... consistent with the Brown-York stress tensor $T_{ij}$, \\
-	fully renormalized at $\zeta \to 0^\pm$.
-
-	\item The lack of diff invariance of the $\log |\zeta|$ counterterm is known to be a reflection of the Weyl anomaly: \textsl{\citeauthor{Henningson:1998gx,deHaro:2000vlm,Papadimitriou:2010as}}.
-
-\item The $\log$ counterterm makes a crucial contribution to the on-shell action; it guarantees that the partition function is compatible with the $T\bar T$ differential equation --- not the case for \textsl{\citeauthor{Donnelly:2018bef}}.
-
-	\item In general the space of deformed theories are parametrized by $(\mu,a)$, where $a$ is the length scale (inverse energy scale).
-In many contexts they are naturally related: $a = \sqrt{c|\mu|/3}$, but $a$ can be tuned by RG.
-
-\end{itemize}
-
-\section*{Summary \& future directions}
-
-\begin{center}
-	\includegraphics[width=.5\linewidth]{img/RT-AdS.pdf}
-
-	\vspace{-1\baselineskip}
-	RT surface for the extended $\mrm{AdS}_3$
-\end{center}
-
-\begin{itemize}
-\item Holographic proposal for $T\bar T$-deformed CFTs\\
-with $\mu \in \mbb{R}$.
-
-\item As evidence, we show that the $T\bar T$ trace flow equation, the spectrum on the cylinder, and the partition function on the torus and the sphere, among other results, can all be reproduced from bulk calculations in glue-on AdS$_3$.
-
-\item We hope to understand the entanglement structure of \TTbar deformed theories from bulk geometry. 
-	\begin{itemize}
-	\item \textcite{Donnelly:2018bef,Lewkowycz:2019xse}
-	\item \textcite{He:2023xnb,He:2023wko,Tian:2023fgf,Hou:2023ytl}
-	\end{itemize}
-\end{itemize}
-
-\renewcommand*{\bibfont}{\footnotesize}
-\printbibliography %%% should not specify heading
+%\begin{center}
+%	\includegraphics[width=.5\linewidth]{img/RT-AdS.pdf}
+%	
+%	\vspace{-.8\baselineskip}
+%	RT surface for the extended $\mrm{AdS}_3$
+%\end{center}
+%
+%\citations{
+%\begin{itemize}[noitemsep]
+%\item \textcite{He:2023xnb}
+%\item \textcite{He:2023wko}
+%\item \textcite{Tian:2023fgf}
+%\end{itemize}
+%}
+%
+%\renewcommand*{\bibfont}{\footnotesize}
+%\printbibliography %%% should not specify heading
 

### 2023-08-24 alpha/GlueonAdS/glueon-poster-v2.tex
Prepare for new version of the poster

--- 2023-08-24 alpha/GlueonAdS/glueon-poster-v0.tex
@@
 
-In this work we put forward a holographic proposal for \TTbar-deformed CFTs with $\mu > 0$, in which case the bulk dual geometry is constructed by gluing-on a patch of $\mrm{AdS}_3$ to the original spacetime.
-We provide various evidence for this extended holography, now valid for $\mu \in \mbb{R}$.
+We generalize the proposal for $\mu > 0$ and \mbox{provide} various evidence for this extended holography, now valid for $\mu \in \mbb{R}$.
 
@@
 
-We start from \textbf{pure Einstein gravity} without matter in $\mrm{AdS}_3$; the Einstein equations are solved by the metric:
+\noindent
+\textbf{Pure Einstein gravity} without matter in $\mrm{AdS}_3$:
 \begin{equation}
@@
 	&= \ell^2 \bigg( \frac{d\rho^2}{4 \rho^2} + \frac{ \big( du + \rho \, \mathcal {\bar L}(v)\, dv \big) \big( dv + \rho \, \mathcal L(u)\, du \big) }{\rho} \bigg)\\
-	&= n_\mu n_\nu dx^\mu dx^\nu + \frac{1}{\zeta} \gamma_{ij}dx^i dx^j,\quad
-\frac{1}{\zeta} \equiv \ell^{-2} g_{\varphi\varphi} \equiv r^2
+	&= n_\mu n_\nu dx^\mu dx^\nu + \frac{1}{\zeta} \gamma_{ij}dx^i dx^j,
 \end{aligned}
@@
 \end{equation}
-The radial coordinate: $\rho \approx r^{-2} \equiv \zeta$,
-where $r$ is the ``proper radius''; $\mathcal L(u)$ and $\bar{\mathcal L}(v)$ are arbitrary periodic functions.
+$\mathcal L(u)$ and $\bar{\mathcal L}(v)$: arbitrary periodic functions.
+\begin{itemize}%[noitemsep]
+\item Change of radial coordinate: $\rho \leadsto \zeta$:
+\begin{equation*}
+	\frac{1}{\zeta} \equiv \ell^{-2} g_{\varphi\varphi} \equiv r^2
+\end{equation*}
+$r$ is the ``proper radius'', $\rho \approx r^{-2}$ but \textit{not exactly}.
 
-\noindent%
-The geometry is foliated by constant $\zeta$ surfaces ${\mathcal N}_\zeta$. 
+\item The geometry is foliated by constant $\zeta$ surfaces ${\mathcal N}_\zeta$.
 \\
-The asymptotic boundary $\mcal{N}_0$ is at $\zeta \to 0$, with coordinates: $x^{i} \sim \varphi, t$, while $u,v = \varphi \pm t$.
+Asymptotic boundary: $\mcal{N}_0$, at $\rho, \zeta \to 0$, \\
+with coordinates: $x^{i} \sim \varphi, t$, while $u,v = \varphi \pm t$.
+\end{itemize}
 
@@
 \vspace{-.5\baselineskip}
-\begin{align*}
+{\large \begin{align*}
 %\hspace{-1em}
@@
 	\textrm{Large $N$ $\mrm{CFT}_2$ at $\mcal{N}_0$}
-\end{align*}
+\end{align*}}
 
@@
 
-\item Define \textbf{``\,$\TTbar$\,'' deformation} as the flow of action:
+\item \textbf{``\,$\TTbar$\,'' deformation} as the flow of action:
 \begin{equation}
@@
 where $x, \bar{x} = \varphi' \pm t'$.
-We shall start from $\mrm{CFT}_2$ such that $T\bar{T}_{(\mu = 0)} = T_{xx} T_{\bar{x}\bar{x}}$, but note that the deformation is \textit{irrelevant}: conformal symmetry will be broken for $\mu \ne 0$.
+
+\item \textbf{Irrelevant:} start from $\mrm{CFT}_2$ where $T\bar{T}_{(\mu = 0)} = T_{xx} T_{\bar{x}\bar{x}}$, but conformal symmetry will be broken for $\mu \ne 0$.
 
@@
 of the undeformed spectrum $E(0)$, $J(0)$,
-under reasonable assumptions (e.g.~translation invariance).
+under reasonable assumptions.
 
@@
 \textbf{Dictionary:} the \TTbar deformed theory lives on $\mcal{N}_{\zeta_c}$ with metric $\gamma_{ij}$.
-Location (radius) of the cutoff surface gets mapped to the deformation parameter $\mu$:
+Parameter $\zeta_c$ related to $\mu$:
 \begin{equation}
@@
 \end{equation}
-\TTbar flow is recast geometrically as the $i,j$ components of the Einstein equations. This is a ``non-AdS'' / non-CFT duality.
+\TTbar flow recast geometrically as the $i,j$ components of the Einstein equations. This is a ``non-AdS'' / non-CFT duality.
 
@@
 	\hspace{.1\linewidth}
-	\includegraphics[width=.4\linewidth]{img/cutoff-ads.jpg}
+	\includegraphics[width=.45\linewidth]{img/cutoff-ads.jpg}
 
@@
 \vspace{-\baselineskip}
-\begin{equation*}
-\hspace{-.8em}
-	\textrm{Cutoff / \textit{glue-on} $\mrm{AdS}_{d+1}$ Gravity}
-	\ \equiv\ %
-	\textrm{\TTbar deformed $\mrm{CFT}_{d}$ at $\mcal{N}_{\zeta_c}$}
-\end{equation*}
+\textbf{\begin{equation*}
+\hspace{-1.8em}
+\begin{aligned}
+	\textrm{Cutoff}
+	\ &/\ %
+	\text{\textit{glue-on} $\mrm{AdS}_3$ Gravity}
+	\!\!&\equiv\ %
+	\textrm{\TTbar deformed $\mrm{CFT}_2$ at $\mcal{N}_{\zeta_c}$} \\
+	\zeta_c > 0
+	\ &/\ %
+	\zeta_c < 0
+	& \mu \in \mbb{R}\quad
+\end{aligned}
+\end{equation*}}
 \begin{center}
-	\vspace{-.8\baselineskip}%
+	\vspace{-1\baselineskip}%
 	\centering
@@
 What are we doing other than copy-pasting?
-	\begin{itemize}
-	\item Physical quantities diverge as $\zeta \to 0$.
-	A prescription is required to ``renormalize'' the divergences.
-
-	\item Treatment for the singularity at $\zeta\to 0^\pm$: introduce $\mathcal N_{\zeta={\pm\epsilon}}$ and glue them together (``\textbf{glue-on}'');
-		exclude the $-\epsilon < \zeta < \epsilon$ region until finally sending $\epsilon \to 0$. 
+A prescription to ``renormalize'' the divergences at $\zeta \to 0$:
+	\begin{itemize}[noitemsep]\small
+	\item Introduce $\mathcal N_{\zeta={\pm\epsilon}}$ and glue them together (``\textbf{glue-on}'');
+	\item Exclude the $-\epsilon < \zeta < \epsilon$ region until finally sending $\epsilon \to 0$. 
 %	\item We formally denote the boundary surface by the limit $\mathcal N_{0}=\mathcal N_{0^+}=\mathcal N_{0^-}$, though we need to keep track of the asymptotic cutoff $\epsilon$ in actual computations.
@@
 	\end{equation}
-	where $h_{ij}$ is the induced metric.
+	$h_{ij}$: the induced metric.
 
@@
 
-\item \textbf{Spectrum from the extended geometry:} they are \mbox{conserved} charges of the Killing symmetries, and can be computed with the \textit{covariant formalism}.
+\item \textbf{Spectrum from the extended geometry:} they are \mbox{conserved} charges $\mcal{Q}$ of the Killing symmetries, and can be computed with the \textit{covariant formalism}.
 
@@
 	\end{align*}
-	This reproduces $E(\mu)$, $J(\mu)$ with $\mu \in\mbb{R}$ in \eqref{ttbarspectrum}.
+	This reproduces $E(\mu)$, $J(\mu)$ with $\mu \in\mbb{R}$ in \eqref{ttbarspectrum}.\\
+	$(t',\varphi')$: normalized boundary coordinates:
+	\begin{equation}
+		ds^2_c = \ell^2 ( -dt'^2 + d\varphi'^2) , \qquad \varphi' \sim \varphi' + 2\pi.\label{cutoffmetric}
+	\end{equation}
 
@@
 
-	\item To match the bulk \& boundary symmetries at $\mcal{N}_{\zeta_c}$, we choose the appropriate coordinates $(t',\varphi')$, such that
-	\begin{equation}
-		ds^2_c = \ell^2 ( -dt'^2 + d\varphi'^2) , \qquad \varphi' \sim \varphi' + 2\pi.\label{cutoffmetric}
-	\end{equation}
-This is realized by:
-	\begin{align*}
-		dt' &= \sqrt{ \big(1 - \zeta_c (T_u+T_v)^2 \big) \big(1 - \zeta_c (T_u-T_v)^2 \big) } \, dt,  \\
+	\item $(t',\varphi')$: from \textbf{\textit{state-dependent} maps of \mbox{coordinates}}
+	\begin{align}
+		dt' &= \sqrt{ \big(1 - \zeta_c (T_u+T_v)^2 \big) \big(1 - \zeta_c (T_u-T_v)^2 \big) } \, dt, \notag \\
 		 d\varphi' &= d\varphi + \zeta_c \big( T_u^2 - T_v^2 \big)\,dt.
-	\end{align*}
-
-\item The above \textbf{\textit{state-dependent} map of \mbox{coordinates}} leads to the correct charges, the modified signal propagation speed $v'_{\pm} \equiv \pm {d\varphi'}/{dt'}$, and the \TTbar \textbf{thermodynamics} when Wick rotated.
-In particular,
+	\label{eq:state_dependent_map}
+	\end{align}
+	$\leadsto$ correct charges, the modified signal propagation speed $v'_{\pm} \equiv \pm {d\varphi'}/{dt'}$, and the \TTbar \textbf{thermodynamics} when Wick rotated. In particular,
 	\begin{equation*}
@@
 	\end{equation*}
-	$T_{L,R}$ are temperatures associated with $u',v' = \varphi' \pm t'$.\\
-	$T_H$ is the \textit{Hagedorn temperature}: exceeding $T_H$ leads to a complex entropy.
+	$T_{L,R}$: temperatures associated with $u',v' = \varphi' \pm t'$.\\
+	$T_H$: the \textit{Hagedorn temperature}: exceeding $T_H$ leads to a complex entropy.
 
 \begin{flushright}
-\vspace{-.5\baselineskip}
+\vspace{-\baselineskip}
 \citations{
@@
 }
-\vspace{-\baselineskip}
+\vspace{-.8\baselineskip}
 \end{flushright}
@@
 
-\subsection*{\TTbar partition functions from bulk actions} \label{se:partitionfunction}
+\subsection*{\TTbar partition functions from the bulk} \label{se:partitionfunction}
 
 \begin{itemize}
-\item The \TTbar partition function is approximated by the bulk on-shell action of the dominant saddle:
+\item Via bulk on-shell action of the dominant saddle:
 	\begin{equation}
@@
 	\end{equation}
-$I(\zeta_c)$ \mbox{diverges} at $\zeta \to 0^\pm$. We apply a natural extension of \textit{holographic renormalization} to remove the divergence.
-It includes the boundary action (with counterterms):
+$I(\zeta_c)$ \mbox{diverges} at $\zeta \to 0^\pm$: require a natural extension of \textit{holographic renormalization}, with the boundary action:
 	\begin{align}
@@
 	\end{align}
-	The lack of diff invariance of the $\log |\zeta|$ counterterm is known to be a reflection of the Weyl anomaly. 
-	The \mbox{action} is consistent with the Brown-York stress \mbox{tensor} in \eqref{BYtensor}.
-
 	\hfill{\footnotesize \textcite{Henningson:1998gx} \textit{et al}}
 
-The resulting $I = -\log \mcal{Z}$ satisfies the \TTbar flow \eqref{TTbardef}.\\
-Furthermore, it agrees with the field theory analysis:
+	$\log |\zeta|$: not diff-invariant, due to the Weyl anomaly.
+
+	$I_{\mcal{N}_\zeta}$ consistent with the Brown-York stress \mbox{tensor} \eqref{BYtensor}.\\
+	$Z_{\TTbar}$ agrees with the field theory analysis, using \eqref{eq:state_dependent_map}:
 
@@
 	\end{equation}
-Then the trace relation \mbox{$
+Trace relation: \mbox{$
 %	\begin{align*}
@@
 %	\end{align*}
-$} along with the flow equation \eqref{TTbardef} 
-admits the general \mbox{solution} with a $\mu$-\textit{independent} integration constant $a$:
+$} and the flow equation \eqref{TTbardef} 
+admit the general \mbox{solution} with a $\mu$-\textit{independent} integration constant $a$:
 	\begin{equation*}\small
-	\hspace{-1.2em}
+	\hspace{-1.35em}
 		\log Z_{\TTbar}(\mu, a) = \frac{c}{3} \log \bigg[\frac{R}{a}   \bigg(1+\sqrt{1-\frac{c \mu }{3  R^2}}\, \bigg) \bigg] - \frac{R^2}{\mu}  \sqrt{1-\frac{c \mu }{3 R^2}} + \frac{R^2}{\mu}.
@@
 	\end{equation*}
-	\cite{Donnelly:2018bef} is recovered with $a = \sqrt{c|\mu|/3}$ but one can also take $a = \epsilon$, thus decoupling the renormalization length scale $\epsilon$ with the deformation $\mu$.
-In general the space of deformed theories can be parametrized by independent $(\mu,a)$.
+	\begin{itemize}%[noitemsep]
+	\item $a = \sqrt{c|\mu|/3}$: recover {\footnotesize \textcite{Donnelly:2018bef}} \\
+	$a = \epsilon$: also a valid choice, where the the RG length scale $\epsilon$ is decoupled from the deformation $\mu$.
 
-	The $\log$ counterterm in \eqref{boundaryaction} makes a crucial contribution to the on-shell action; it guarantees that the partition function is compatible with the $T\bar T$ differential equation, which is not the case for \cite{Donnelly:2018bef}.
+	\item Enlarge the \textbf{space of \TTbar deformed theories:}\\
+	with \mbox{independent} parameters $(\mu,a)$.
+
+	\item The $\log |\zeta|$ term in \eqref{boundaryaction} guarantees that $I = -\log Z_{\TTbar}$ satisfies the $T\bar T$ flow \eqref{TTbardef}; not the case for \cite{Donnelly:2018bef}.
+	\end{itemize}
+
 	\begin{flushright}
@@
 
-	\item Following these results, we would like to understand the entanglement structure of \TTbar deformed theories with the help of bulk geometry in future studies.
+	\item Future: to understand the \textbf{entanglement structure} of \TTbar deformed theories with the help of bulk geometry.
 	\begin{flushright}
@@
 \end{itemize}
+\centering\vspace{-.8\baselineskip}
+\includegraphics[width=.5\linewidth]{img/RT-AdS.pdf}
 
-%\begin{center}
-%	\includegraphics[width=.5\linewidth]{img/RT-AdS.pdf}
-%	
-%	\vspace{-.8\baselineskip}
-%	RT surface for the extended $\mrm{AdS}_3$
-%\end{center}
+\vspace{-1.2\baselineskip}
+{\footnotesize RT surface for the extended $\mrm{AdS}_3$}
+
 %

### 2023-08-26 alpha/GlueonAdS/glueon-poster-v2.tex
Update poster v2: revamped again

@@
 \title{Glue-on AdS holography for $T\bar T$-deformed CFTs}
-\posttitle{\ \,\normalsize\textsl{JHEP 06 (2023) 117}}
+\posttitle{\ \footnotesize\textsl{JHEP 06 (2023) 117}}
 
 \preauthor{\par\large\noindent}
-\author{Wen-Xin Lai \textkai{赖文昕}}
-\postauthor{, \textit{\normalsize with}
+\author{
 	Luis Apolo,
-	Peng-Xiang Hao \textkai{郝鹏翔}
-	and Wei Song \textkai{宋伟}
-	\ \arxiv{2303.04836}
+	Peng-Xiang Hao \textkai{\normalsize 郝鹏翔},
+	\textbf{Wen-Xin Lai} \textkai{\small 赖文昕},
+	and Wei Song \textkai{\small 宋伟}
+}
+\postauthor{
+	\,\arxiv{2303.04836}
 	\par%\vspace{.5\baselineskip}
 	\vspace{-.6\baselineskip}
-	\noindent\rule{.66\linewidth}{1pt}\par
+	\noindent\rule{.68\linewidth}{1pt}\par
 	\vspace{-.1\baselineskip}
@@
 }
-\date{July 2023}
+\date{September 2023}
 \postdate{
-	@ ICBS @ BIMSA
-	\vspace{.5\baselineskip}
+	@ YITP, Kyoto
+%	\vspace{0\baselineskip}
 }
@@
 \textbf{Abstract:}
-\TTbar-deformed CFTs with $\mu < 0$ have been proposed by \textcite{McGough:2016lol} to be holographically dual to Einstein gravity with a finite \mbox{Dirichlet} cutoff.
 
-We generalize the proposal for $\mu > 0$ and \mbox{provide} various evidence for this extended holography, now valid for $\mu \in \mbb{R}$.
+\TTbar-deformed CFTs with $\mu < 0$ have been proposed by \mbox{\textcite{McGough:2016lol}} to be holographically dual to Einstein gravity with a finite \mbox{Dirichlet} cutoff.
+
+We generalize the proposal for $\mu > 0$ by \textit{gluing-on} another patch of $\mrm{AdS}_3$, and \mbox{provide} various evidence for this extended holography, now valid for $\mu \in \mbb{R}$.
 
@@
 
-\noindent
 \textbf{Pure Einstein gravity} without matter in $\mrm{AdS}_3$:
 \begin{equation}
-\hspace{-2em}
+\hspace{-2.5em}
 \begin{aligned}
@@
 	&= \ell^2 \bigg( \frac{d\rho^2}{4 \rho^2} + \frac{ \big( du + \rho \, \mathcal {\bar L}(v)\, dv \big) \big( dv + \rho \, \mathcal L(u)\, du \big) }{\rho} \bigg)\\
-	&= n_\mu n_\nu dx^\mu dx^\nu + \frac{1}{\zeta} \gamma_{ij}dx^i dx^j,
+	&= n_\mu n_\nu dx^\mu dx^\nu + \frac{1}{\zeta} \gamma_{ij}dx^i dx^j,\quad
 \end{aligned}
@@
 \end{equation}
-$\mathcal L(u)$ and $\bar{\mathcal L}(v)$: arbitrary periodic functions.
-\begin{itemize}%[noitemsep]
-\item Change of radial coordinate: $\rho \leadsto \zeta$:
-\begin{equation*}
-	\frac{1}{\zeta} \equiv \ell^{-2} g_{\varphi\varphi} \equiv r^2
-\end{equation*}
-$r$ is the ``proper radius'', $\rho \approx r^{-2}$ but \textit{not exactly}.
 
-\item The geometry is foliated by constant $\zeta$ surfaces ${\mathcal N}_\zeta$.
-\\
-Asymptotic boundary: $\mcal{N}_0$, at $\rho, \zeta \to 0$, \\
-with coordinates: $x^{i} \sim \varphi, t$, while $u,v = \varphi \pm t$.
+\begin{itemize}
+\item Transverse coordinates: $x^{i} \sim \varphi, t$ \\
+	Lightcone coordinates: $u,v = \varphi \pm t$
+
+	$\mathcal L(u), \bar{\mathcal L}(v)$: arbitrary periodic functions
+\item Radial coordinate: $
+	\ell^{-2} g_{\varphi\varphi} \equiv r^2 \equiv \frac{1}{\zeta}$\\
+	$r$: the ``proper radius''
+\end{itemize}
+\begin{center}
+	\vspace{-.5\baselineskip}
+	\includegraphics[width=.52\linewidth]{img/foliation.pdf}
+
+	\vspace{-.3\baselineskip}\scriptsize
+	Image courtesy: \textsl{R. Szalai},\\
+	\tiny\texttt{DOI:10.1007/s11071-020-05891-1}
+
+	\vspace{-.5\baselineskip}
+\end{center}
+\begin{itemize}
+\item Structure: foliated by constant $\zeta$ surfaces ${\mathcal N}_\zeta$\\[.7ex]
+Asymptotic boundary: $\mcal{N}_0$ is at $\zeta \to 0$
+\\[1ex]
+\citations{%
+	\textcite{Fefferman:2007rka}\\
+	\textcite{Banados:1992wn}%\\
+%	\textcite{Banados:1998gg}
+}
 \end{itemize}
 
-\noindent\citations{%
-\textcite{Fefferman:2007rka}\\
-\textcite{Banados:1992wn}\\
-\textcite{Banados:1998gg}
-}
-\vspace{-.5\baselineskip}
-\subsection*{Foundations: $\mrm{AdS}_3/\mrm{CFT}_2$ holography}
-\vspace{-.5\baselineskip}
-{\large \begin{align*}
-%\hspace{-1em}
-	\textrm{\textit{asympt.}~$\mrm{AdS}_3$ Gravity}
-	&\ \equiv\ 
-	\textrm{Large $N$ $\mrm{CFT}_2$ at $\mcal{N}_0$}
-\end{align*}}
-
-\citations{\noindent%
-	\textcite{Maldacena:1997re}\\
-	\textcite{Aharony:1999ti} \textit{et al}
-}
-%\begin{center}
-%	\includegraphics[width=.7\linewidth]{img/ads-cft.png}\\[.5ex]
-%	\scriptsize\ Image courtesy: \textcite{AldegundePWSep22}
-%\end{center}
-
-%\begin{itemize}
-
-%\item Universal / ubiquitous:
-%
-%\begin{itemize}
-%	\item Model agnostic: $\mrm{AdS}_5\times S^5$, $\mrm{AdS}_3\times S^3 \times T^4$, symmetric orbifolds, minimal models, ``monsters'', ...
-\textit{\small Maldacena, Witten, GKP, ABJM, Gaberdiel, and many many more}
-%	
-%\end{itemize}
-
-%\end{itemize}
+\textbf{``\,$\TTbar$\,'' deformation} as the flow of action:
+\begin{align}
+\hspace{-1.5em}
+	\partial_{\sidenote{\mu}} I &= {8 \pi} \int d^2x \, T\bar T_{(\sidenote{\mu})} = {\pi} \int d^2x\,\big( T^{ij}T_{ij}- (T^i_i)^2 \big)_{(\sidenote{\mu})},\notag\\
+	&x, \bar{x} = \varphi' \pm t'
+	\label{TTbardef}
+\end{align}
 
@@
 
-\item \textbf{``\,$\TTbar$\,'' deformation} as the flow of action:
-\begin{equation}
-	\partial_{\sidenote{\mu}} I = {8 \pi} \int d^2x \, T\bar T_{(\sidenote{\mu})} = {\pi} \int d^2x\,\big( T^{ij}T_{ij}- (T^i_i)^2 \big)_{(\sidenote{\mu})}
-	\label{TTbardef}
-\end{equation}
-where $x, \bar{x} = \varphi' \pm t'$.
-
-\item \textbf{Irrelevant:} start from $\mrm{CFT}_2$ where $T\bar{T}_{(\mu = 0)} = T_{xx} T_{\bar{x}\bar{x}}$, but conformal symmetry will be broken for $\mu \ne 0$.
+\item \textbf{Irrelevant:} initially $\mrm{CFT}_2$: $T\bar{T}_{(\mu = 0)} = T_{xx} T_{\bar{x}\bar{x}}$, \\
+but conformal symmetry will be broken for $\mu \ne 0$.
 
@@
 \end{equation}
-of the undeformed spectrum $E(0)$, $J(0)$,
-under reasonable assumptions.
+of the undeformed spectrum $E(0)$, $J(0)$.\\
+(\textit{under reasonable assumptions})
 
@@
 \textcite{Smirnov:2016lqw}\\
-\textcite{Cavaglia:2016oda}\\
-\textcite{Dubovsky:2017cnj} \textit{et al}
+\textcite{Cavaglia:2016oda} \textit{et al}%\\
+%\textcite{Dubovsky:2017cnj} 
 }
@@
 
-\textbf{Dictionary:} the \TTbar deformed theory lives on $\mcal{N}_{\zeta_c}$ with metric $\gamma_{ij}$.
-Parameter $\zeta_c$ related to $\mu$:
+\textbf{Dictionary:} radial location $\zeta_c$ of the cutoff surface $\mcal{N}_{\zeta_c}$ gets mapped to the deformation parameter $\mu$:
 \begin{equation}
@@
 \end{equation}
-\TTbar flow recast geometrically as the $i,j$ components of the Einstein equations. This is a ``non-AdS'' / non-CFT duality.
+\TTbar flow recast geometrically as the $i,j$ components of the Einstein equations.
 
-\noindent%
+This is a ``non-AdS'' / non-CFT duality.\\
 \textit{A step towards quantum gravity in \reality!}
 
-\columnbreak
-
-\vspace*{-4\baselineskip}
-\begin{center}
-	\hspace{.1\linewidth}
-	\includegraphics[width=.45\linewidth]{img/cutoff-ads.jpg}
-
-	\vspace{-.5\baselineskip}\small
-	Cutoff $\mrm{AdS}_3$\,/\,\TTbar-deformed $\mrm{CFT}_2$
-
-	\vspace{-.2\baselineskip}
-	\scriptsize\ Image courtesy: \textcite{AldegundePWSep22}
-\end{center}
-
-\begin{itemize}
-
-\item[] \textbf{Caveat:} the duality only admits $\zeta_c > 0$ so $\mu < 0$.\\
+\textbf{Caveat:} the duality only admits $\zeta_c > 0$ so $\mu < 0$.\\
 But \TTbar itself admits $\mu > 0$ with cool properties.
@@
 
-\end{itemize}
+\columnbreak
 
-\vspace{-\baselineskip}
+\vspace*{-4\baselineskip}
+\begin{center}
+	\mbox{
+		\hspace{-3em}
+		\includegraphics[width=1.19\linewidth]{img/ads-cft-cutoff.png}
+	}
+
+	\vspace{-.9\baselineskip}\small
+	Cutoff $\mrm{AdS}_3$\,/\,\TTbar-deformed $\mrm{CFT}_2$
+
+	\vspace{-.3\baselineskip}
+	\scriptsize\ Image courtesy: \textcite{AldegundePWSep22}
+\end{center}
+
+%\begin{itemize}
+%
+%\item[] \textbf{Caveat:} the duality only admits $\zeta_c > 0$ so $\mu < 0$.\\
+%But \TTbar itself admits $\mu > 0$ with cool properties.
+%
+%\citations{The related proposal of \textcite{Guica:2019nzm}\\
+%admits both signs of $\mu$.}
+%
+%\textit{What is the other side of the duality?}
+%
+%\end{itemize}
+
+\vspace{-1.5\baselineskip}
 
@@
 \textbf{\begin{equation*}
-\hspace{-1.8em}
+\hspace{-3em}
 \begin{aligned}
@@
 	\zeta_c < 0
-	& \mu \in \mbb{R}\quad
+	& \mu \in \mbb{R}\hspace{1em}\,
 \end{aligned}
@@
 	\centering
-	\includegraphics[width=.6\linewidth]{img/diagram.pdf}
+	\includegraphics[width=.65\linewidth]{img/diagram.pdf}
 
@@
 
-\item \textbf{Analytic continuation:} metric \eqref{fggauge} has a simple pole, thus admits well-defined analytic continuation:
+\item The metric \eqref{fggauge} has a simple pole, thus admits a well-defined \textbf{analytic continuation:}
 %\begin{equation}
@@
 \end{equation}
-What are we doing other than copy-pasting?
-A prescription to ``renormalize'' the divergences at $\zeta \to 0$:
+What are we doing other than copy-pasting?\\
+``Renormalize'' the divergences as $\zeta \to 0^\pm$:
 	\begin{itemize}[noitemsep]\small
-	\item Introduce $\mathcal N_{\zeta={\pm\epsilon}}$ and glue them together (``\textbf{glue-on}'');
-	\item Exclude the $-\epsilon < \zeta < \epsilon$ region until finally sending $\epsilon \to 0$. 
-%	\item We formally denote the boundary surface by the limit $\mathcal N_{0}=\mathcal N_{0^+}=\mathcal N_{0^-}$, though we need to keep track of the asymptotic cutoff $\epsilon$ in actual computations.
+	\item introduce $\mathcal N_{\zeta={\pm\epsilon}}$ and \textbf{``glue''} them together;
+	\item i.e.~exclude the $-\epsilon < \zeta < \epsilon$ region, \\ until finally sending $\epsilon \to 0$. 
 	\end{itemize}
@@
 	The field theory metric $\gamma_{ij}$ is always positive-definite, while $h_{ij}$ becomes negative-definite for the glue-on region $\rho,\zeta < 0$.
-	This discrepancy is the origin of the $\abs{\zeta_c}$.
+
+	This discrepancy is the origin of $\abs{\zeta_c}$.
 
@@
 
-	\item $(t',\varphi')$: from \textbf{\textit{state-dependent} maps of \mbox{coordinates}}
+	\item \textbf{\textit{State-dependent} maps of \mbox{coordinates}}
 	\begin{align}
@@
 	\end{align}
-	$\leadsto$ correct charges, the modified signal propagation speed $v'_{\pm} \equiv \pm {d\varphi'}/{dt'}$, and the \TTbar \textbf{thermodynamics} when Wick rotated. In particular,
+	$\leadsto$ correct charges, the modified signal propagation speed $v'_{\pm} \equiv \pm {d\varphi'}/{dt'}$, and \TTbar \textbf{thermodynamics} when Wick rotated. In particular,
 	\begin{equation*}
-	\hspace{-.5em} \mu > 0,\quad
+	\hspace{-.5em} \mu > 0,\ \ \,
 		T_L(\mu)\,T_R(\mu) \le - \frac{1}{4\pi^2 \ell^2 \zeta_c} = \frac{3}{4\pi^2c\mu} = T_H(\mu)^2.
@@
 \begin{flushright}
-\vspace{-\baselineskip}
+\vspace{-.5\baselineskip}
 \citations{
@@
 	\end{equation}
-$I(\zeta_c)$ \mbox{diverges} at $\zeta \to 0^\pm$: require a natural extension of \textit{holographic renormalization}, with the boundary action:
+$I(\zeta_c)$ \mbox{diverges} at $\zeta \to 0^\pm$: we need \textit{holographic renormalization}, with the boundary action:
 	\begin{align}
@@
 %	\\
-		I_{\mathcal N_{\zeta}} & \coloneqq  - \frac{1}{8\pi G} \int_{\mathcal N_{\zeta}} d^2x \sqrt{h}\,h^{ij} K_{ij} \notag
-	\\& \qquad + \frac{\sigma_\zeta}{8\pi G} \int_{\mathcal N_{\zeta}} d^2x \sqrt{h} \, \bigg(\ell^{-1} - \frac{\ell  \mathcal{R}[h]}{4} \log |\zeta| \bigg). \label{boundaryaction}
+		I_{\mathcal N_{\zeta}} & \coloneqq  - \frac{1}{8\pi G} \int_{\mathcal N_{\zeta}} d^2x \sqrt{h}\,h^{ij} K_{ij} \label{boundaryaction}
+	\\& \qquad + \frac{\sigma_\zeta}{8\pi G} \int_{\mathcal N_{\zeta}} d^2x \sqrt{h} \, \bigg(\ell^{-1} - \frac{\ell  \mathcal{R}[h]}{4} \log |\zeta| \bigg). \notag
 	\end{align}
@@
 
-	$\log |\zeta|$: not diff-invariant, due to the Weyl anomaly.
+	$\log |\zeta|$: not diff-invariant, due to the Weyl anomaly. \\
+	$I_{\mcal{N}_\zeta}$: consistent with the B-Y stress tensor \eqref{BYtensor}.
 
-	$I_{\mcal{N}_\zeta}$ consistent with the Brown-York stress \mbox{tensor} \eqref{BYtensor}.\\
 	$Z_{\TTbar}$ agrees with the field theory analysis, using \eqref{eq:state_dependent_map}:
@@
 	\begin{equation*}\small
-	\hspace{-1.5em}
+	\hspace{-2em}
 		\log   Z_{T\bar T}(\mu)  \approx \left\{ \begin{aligned}
@@
 	\begin{equation*}\small
-	\hspace{-1.35em}
-		\log Z_{\TTbar}(\mu, a) = \frac{c}{3} \log \bigg[\frac{R}{a}   \bigg(1+\sqrt{1-\frac{c \mu }{3  R^2}}\, \bigg) \bigg] - \frac{R^2}{\mu}  \sqrt{1-\frac{c \mu }{3 R^2}} + \frac{R^2}{\mu}.
+	\hspace{-1.3em}
+		\log Z_{\TTbar}(\mu, a) = \tfrac{c}{3} \log \Big[\tfrac{R}{a}   \Big(1+\sqrt{1-\tfrac{c \mu }{3  R^2}}\, \Big) \Big] - \tfrac{R^2}{\mu}  \sqrt{1-\tfrac{c \mu }{3 R^2}} + \tfrac{R^2}{\mu}.
 %\label{Zsol}
@@
 	\begin{itemize}%[noitemsep]
-	\item $a = \sqrt{c|\mu|/3}$: recover {\footnotesize \textcite{Donnelly:2018bef}} \\
-	$a = \epsilon$: also a valid choice, where the the RG length scale $\epsilon$ is decoupled from the deformation $\mu$.
+	\item $a = \sqrt{c|\mu|/3}$: \mbox{recover {\footnotesize \textcite{Donnelly:2018bef}}} \\
+	$a = \epsilon$: also a valid choice, where the the RG length scale $\epsilon$ is decoupled from $\mu$.
 
@@
 
-	\item The $\log |\zeta|$ term in \eqref{boundaryaction} guarantees that $I = -\log Z_{\TTbar}$ satisfies the $T\bar T$ flow \eqref{TTbardef}; not the case for \cite{Donnelly:2018bef}.
+	\item The $\log |\zeta|$ in \eqref{boundaryaction} guarantees that $I = -\log Z_{\TTbar}$ \mbox{satisfies} the $T\bar T$ flow \eqref{TTbardef}; not the case for \cite{Donnelly:2018bef}.
 	\end{itemize}
@@
 
-	\item Future: to understand the \textbf{entanglement structure} of \TTbar deformed theories with the help of bulk geometry.
+	\item Future: understand the \textbf{entanglement structure} of \TTbar deformation with the help of bulk geometry.
 	\begin{flushright}
@@
 \centering\vspace{-.8\baselineskip}
-\includegraphics[width=.5\linewidth]{img/RT-AdS.pdf}
+\includegraphics[width=.6\linewidth]{img/RT-AdS.pdf}
 

### 2023-08-26 alpha/GlueonAdS/glueon-poster-v2.tex
Add qr-code & finalize poster

@@
 \textbf{Caveat:} the duality only admits $\zeta_c > 0$ so $\mu < 0$.\\
-But \TTbar itself admits $\mu > 0$ with cool properties.
+But \TTbar itself admits $\mu > 0$ with nice properties.
 
@@
 	\mbox{
-		\hspace{-3em}
-		\includegraphics[width=1.19\linewidth]{img/ads-cft-cutoff.png}
+		\hspace{-2.6em}
+		\includegraphics[width=1.17\linewidth]{img/ads-cft-cutoff.png}
 	}
@@
 	\centering
-	\includegraphics[width=.65\linewidth]{img/diagram.pdf}
+	\includegraphics[width=.7\linewidth]{img/diagram.pdf}
 
-	\vspace{-.5\baselineskip}
+	\vspace{-.45\baselineskip}
 	\scriptsize\ Top-down view of a constant $t$ slice
@@
 	\end{align}
-	$\leadsto$ correct charges, the modified signal propagation speed $v'_{\pm} \equiv \pm {d\varphi'}/{dt'}$, and \TTbar \textbf{thermodynamics} when Wick rotated. In particular,
+	$\leadsto$ correct charges, the modified signal propagation speed $v'_{\pm} \equiv \pm {d\varphi'}/{dt'}$, and \TTbar \textbf{thermodynamics} upon Wick rotation. In particular,
 	\begin{equation*}
@@
 
-\item \textbf{Torus:} {modular invariance} \& sparseness of the ``light'' spectrum at large $c$ leads to the universal form :
+\item \textbf{Torus:} {modular invariance} \& sparseness of the ``light'' spectrum at large $c$ $\leadsto$ universal form:
 	\begin{equation*}\small
@@
 	\end{equation*}
+	\begin{flushright}
+		\vspace{-.5\baselineskip}
 		\citations{\noindent%
@@
 			cf.~\textcite{Hartman:2014oaa}
-%		\textcite{Apolo:2023aho}, \mbox{following \textcite{Datta:2018thy} and \textsl{\citeauthor{Hartman:2014oaa}}}
 		}
+		\vspace{-.5\baselineskip}
+	\end{flushright}
 
-\item \textbf{Sphere:} maximally symmetric,\\ \mbox{\footnotesize \textcite{Donnelly:2018bef}}
+\item \textbf{Sphere:} maximally symmetric,\\[-1.4\baselineskip]
+
+\hfill\mbox{\footnotesize \textcite{Donnelly:2018bef}}
 	\begin{equation}
@@
 	\begin{itemize}%[noitemsep]
-	\item $a = \sqrt{c|\mu|/3}$: \mbox{recover {\footnotesize \textcite{Donnelly:2018bef}}} \\
+	\item $a = \sqrt{c|\mu|/3}$: \mbox{recover {\small
+		\textsl{\citeauthor{Donnelly:2018bef}}
+		\cite{Donnelly:2018bef}
+	}} \\
 	$a = \epsilon$: also a valid choice, where the the RG length scale $\epsilon$ is decoupled from $\mu$.
@@
 \end{itemize}
-\centering\vspace{-.8\baselineskip}
+\centering\vspace{-1\baselineskip}
 \includegraphics[width=.6\linewidth]{img/RT-AdS.pdf}
 
-\vspace{-1.2\baselineskip}
+\vspace{-1\baselineskip}
 {\footnotesize RT surface for the extended $\mrm{AdS}_3$}
 
-%
-%\citations{
-%\begin{itemize}[noitemsep]
-%\item \textcite{He:2023xnb}
-%\item \textcite{He:2023wko}
-%\item \textcite{Tian:2023fgf}
-%\end{itemize}
-%}
-%
-%\renewcommand*{\bibfont}{\footnotesize}
-%\printbibliography %%% should not specify heading
+\vspace{.8\baselineskip}
+\hrule
+\vspace{.1\baselineskip}
+
+\hspace{-.7em}
+\begin{minipage}[c]{.81\linewidth}
+\begin{itemize}[noitemsep,leftmargin=5em]\small
+\item[\texttt{Email:}]
+	\url{bryanlais@gmail.com}
+\item[\texttt{Inspire:}]
+	\href{https://inspirehep.net/authors/2640135}{
+		\texttt{inspirehep.net/authors/2640135}
+	}
+\item[\texttt{GitHub:}]
+	\href{https://github.com/bryango}{
+		\texttt{github.com/bryango}
+	}
+\end{itemize}
+\end{minipage}%
+\hfill%
+\begin{minipage}{.17\linewidth}
+\includegraphics[width=\linewidth]{img/inspire-qr.png}
+\end{minipage}%
+~\mbox{}
 

### 2023-08-28 alpha/GlueonAdS/glueon-poster-v2.tex
Add minor tweaks & update graphics

@@
 \preauthor{\par\large\noindent}
-\author{
+\author{%
 	Luis Apolo,
 	Peng-Xiang Hao \textkai{\normalsize 郝鹏翔},
-	\textbf{Wen-Xin Lai} \textkai{\small 赖文昕},
+	\textbf{Wen-Xin Lai \textkai{\small 赖文昕}},
 	and Wei Song \textkai{\small 宋伟}
@@
 
-\predate{\noindent\sffamily\,%
+\predate{\noindent\sffamily%
+	\begin{minipage}{3em}
+		\includegraphics[width=2.7em]{img/ymsc-logo.pdf}
+	\end{minipage}
 	Yau Mathematical Sciences Center YMSC, Tsinghua
@@
 
-\noindent%
-\textbf{Abstract:}
+%\textbf{Abstract:}
+\,\\[-2.2\baselineskip]
 
@@
 \textbf{Pure Einstein gravity} without matter in $\mrm{AdS}_3$:
-\begin{equation}
-\hspace{-2.5em}
-\begin{aligned}
+\begin{align}
+\hspace{-.8em}
 	ds^2
-	&= \ell^2 \bigg( \frac{d\rho^2}{4 \rho^2} + \frac{ \big( du + \rho \, \mathcal {\bar L}(v)\, dv \big) \big( dv + \rho \, \mathcal L(u)\, du \big) }{\rho} \bigg)\\
-	&= n_\mu n_\nu dx^\mu dx^\nu + \frac{1}{\zeta} \gamma_{ij}dx^i dx^j,\quad
-\end{aligned}
-\label{fggauge}
-\end{equation}
+	&= \ell^2 \bigg( \frac{d\rho^2}{4 \rho^2} + \frac{ \big( du + \rho \, \mathcal {\bar L}(v)\, dv \big) \big( dv + \rho \, \mathcal L(u)\, du \big) }{\rho} \bigg) \notag\\
+	&= n_\mu n_\nu dx^\mu dx^\nu + \frac{1}{\zeta} \gamma_{ij}dx^i dx^j, \label{fggauge}
+\end{align}
 
@@
 \item Transverse coordinates: $x^{i} \sim \varphi, t$ \\
-	Lightcone coordinates: $u,v = \varphi \pm t$
+	Light-cone coordinates: $u,v = \varphi \pm t$
 
@@
 \item Radial coordinate: $
-	\ell^{-2} g_{\varphi\varphi} \equiv r^2 \equiv \frac{1}{\zeta}$\\
+	\ell^{-2} g_{\varphi\varphi} \equiv r^2 \equiv \zeta^{-1}$\\
 	$r$: the ``proper radius''
@@
 \begin{itemize}
-\item Structure: foliated by constant $\zeta$ surfaces ${\mathcal N}_\zeta$\\[.7ex]
+\item Structure: foliated by constant $\zeta$ surfaces ${\mathcal N}_\zeta$\\[.6ex]
 Asymptotic boundary: $\mcal{N}_0$ is at $\zeta \to 0$
@@
 
-\textbf{``\,$\TTbar$\,'' deformation} as the flow of action:
+\textbf{``$\thinmspace[.9]\TTbar$\,'' deformation} as the flow of action:
 \begin{align}
-\hspace{-1.5em}
+\hspace{-.1em}
 	\partial_{\sidenote{\mu}} I &= {8 \pi} \int d^2x \, T\bar T_{(\sidenote{\mu})} = {\pi} \int d^2x\,\big( T^{ij}T_{ij}- (T^i_i)^2 \big)_{(\sidenote{\mu})},\notag\\
@@
 
-\vspace{-.5\baselineskip}
+\vspace{-.8\baselineskip}
 
@@
 \subsection*{Cutoff $\mrm{AdS}_3$ duality:\texstringonly{\\} Holography within a finite Dirichlet wall}
-
+\vspace{-.2\baselineskip}
 \citations{
@@
 
-\vspace*{-4\baselineskip}
+\vspace*{-3.6\baselineskip}
 \begin{center}
 	\mbox{
-		\hspace{-2.6em}
-		\includegraphics[width=1.17\linewidth]{img/ads-cft-cutoff.png}
+		\hspace{-1.55em}
+		\includegraphics[width=1.14\linewidth]{img/ads-cft-cutoff.png}
 	}
 
-	\vspace{-.9\baselineskip}\small
+	\vspace{-.8\baselineskip}\small
 	Cutoff $\mrm{AdS}_3$\,/\,\TTbar-deformed $\mrm{CFT}_2$
@@
 \textbf{\begin{equation*}
-\hspace{-3em}
+\hspace{-2.8em}
 \begin{aligned}
@@
 
-	\item \textbf{\textit{State-dependent} maps of \mbox{coordinates}}
+	\item \textbf{\textit{State-dependent} maps of \mbox{coordinates}:}
 	\begin{align}
@@
 	\begin{equation*}\small
-	\hspace{-2em}
+	\hspace{-2.3em}
 		\log   Z_{T\bar T}(\mu)  \approx \left\{ \begin{aligned}
@@
 	\begin{equation*}\small
-	\hspace{-1.3em}
+	\hspace{-1.6em}
 		\log Z_{\TTbar}(\mu, a) = \tfrac{c}{3} \log \Big[\tfrac{R}{a}   \Big(1+\sqrt{1-\tfrac{c \mu }{3  R^2}}\, \Big) \Big] - \tfrac{R^2}{\mu}  \sqrt{1-\tfrac{c \mu }{3 R^2}} + \tfrac{R^2}{\mu}.
@@
 	}} \\
-	$a = \epsilon$: also a valid choice, where the the RG length scale $\epsilon$ is decoupled from $\mu$.
+	$a = \epsilon$: also a valid choice, where the RG length scale $\epsilon$ is decoupled from $\mu$.
 
@@
 \begin{minipage}{.17\linewidth}
-\includegraphics[width=\linewidth]{img/inspire-qr.png}
+\includegraphics[width=\linewidth]{img/inspire-qr-cy.png}
 \end{minipage}%
